### 2017-01-16 tex/Latence-artv1.tex
debut

\documentclass{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{graphicx,graphics} 
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{complexity}

\newcommand\rmatching{assignment\xspace}
\newcommand\mdelay{$\cal M$-delay\xspace}
\newcommand\matchedgraph{{\bf matched graph}}
\begin{document}

\graphicspath{{figures/}}
\newtheorem{rem}{Remarque}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{fact}{Fact}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}

\title{Graph algorithm for deterministic routing to ensure latence in cloud RAN networks}

\newcommand{\todo}[1]{}
\renewcommand{\todo}[1]{{\color{red} TODO: {#1}}}

\author{MG, DB, CC, OM, YS}

  % ?

\maketitle

\section{Introduction}

\todo{A REPRENDRE POUR LA JUSTIFICTION RESEAU AVEC LE DETERMINISTIC ROUTING (OM?) ET INSERER LA PROBLMATIQUE GRAPHE (DB)}
 In this article, we will work on latency constraints in fronthaul.
Thus, this type of architecture confronts the problem of controlling 
the latency in the transfer process.  Low latency is considered critical for the 5G, in particular for the deployment of the C-RAN approach 
(allowing time constraints like HARQ to be fulfilled over non dedicated networks), or to reach E2E expected latency from 1 to 10ms 
(depending on targeted services). One specificity in the C-RAN context is not only the latency constraint, but also the periodicity of 
the data transfer between RRH and BBU.  New scheduling and routing paradigms and new technologies have to be considered to  guarantee 
delay constrained periodic data transfers. Dynamical optical bypass and dynamical management of the emission should be considered to
guarantee latency constraints. This is why this study is a contribution to the ANR project N-Green.

N-GREEN proposes a new type of switching/routing node and a specific network architecture exploiting WDM packets thanks to a new generation of optical add/drop multiplexers (WSADM: WDM slotted add/drop multiplexer). These packets having a fixed duration close to $1\mu $s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.

 Thus, this subject targets new scheduling and routing paradigms to solve this periodic and delay constrained data transfer.
 Indeed, one of the most promising approaches relies on the concept of Deterministic Networking (DN) such that one get rid of
 statistical multiplexing. The traditional queue managements are replaced by time based forwarding. Solutions for Deterministic 
 Networking are under standardization in IEEE 802.1 TSN group, as well at IETF DetNet working group.  To make DN working over a
 network composed of several nodes, it is required to manage the time at which the packets of deterministic paths are crossing each nodes.

Considering a graph, modeling the network topology, and a set of routes from source nodes (modeling connections to the BBU) and destination 
nodes (modeling the RRH) in this graph, the purpose is to select, for each destination node a route from one source node to it and a periodic 
routing scheme allowing to periodically sent a packet to each base station without congestion conflicts between all such packets and to insure a minimum latency. In a slotted time model, the aim is here to minimize the duration of the period, with a constraint of the maximum length of routes to be
selected. Even if the selected set of routes is given this optimization problem has been shown to be  \NP-hard. From an algorithmic point of view,
the purpose of this project is first, to study the complexity and the approximability of this problem when the length of the routes is small
(which corresponds to realistic cases), and secondly, to propose and implement some heuristics to solve this problem on realistic topologies.

The major difficulty of this problem is the periodicity of the process. Indeed, a deterministic sending for the messages
between each pair BBU/RRH must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous
and following periods. This problem may look like wormhole problem \cite{cole1996benefit}, very popular few years ago, but here, we want to minimize the time lost in buffers and not just avoid the deadlock, and the wormhole does not treat about the periodicity.

\subsection*{Related works}
\todo{IL FAUT REPARTIR DE CE QUI EST DANS LE MEMOIRE DE MAEL, PLUS LES ARTICLES D'ORDONNANCMENT DE TRAINS. JE (DB) M'EN CHARGE.}
\section{Model and problem description}
\subsection{Definitions}
We consider a symmetric directed graph $G=(V,A)$ modeling a slotted network. Each arc  $(u,v)$ in $A$ is characterized by an integer delay $Dl(u,v) \geq 1$ representing the number of slots from $u$ to $v$ on this arc. Note that for any arc $(u,v)$, $DL(u,v)=DL(v,u)$.

A route $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.  The {\em latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} Dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.  A routing function $\cal R$ in $G$ associates a route from $u$ to $v$ for any couple of different vertices $<u,v>$ in $G$.\\

Let $\cal C$ be an {assignment} in $G$, i.e., set of couples of different vertices of $G$. We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $<u,v>$ in $\cal C$.

Consider now a positive integer $P$ called {\bf period}. A {\bf $P$-periodic affectation} of $\cal C$ in $(G,{\cal R})$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$
of $c$ integers that we call {\bf offset}, with $c$ the cardinal of $\cal C$. Indeed, time is consider as consecutive periods of $P$ slots each and the number $m_i$ represents the first slot number used by the route $r_i \in {\cal R}_{\cal C}$ at its source.
We define the first time slot at which a message reaches any vertex $v$ in this route by $$t(v,r_i) = m_i+\lambda(v,r_i) \mod P.$$

Let us call $[t(v,r_i)]$ the values of the time slots used by a route $r_i$ in such a vertex $v$. 
Those values are forming a continuous set of values starting at $t(v,r_i) \mod P$ and ending at $t(v,r_i) + \tau \mod P$. A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}_{\cal C}$, that is $\forall r_i, r_j \in {\cal R}_{\cal C}, i \ne j$, with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$

The main theoretical problem we have to deal with in this context is the following.\\

\noindent {\bf Problem  Periodic Routes Assignment (PRA)}

\noindent {\bf Input:} graph $G=(V,A)$, set $\cal C$ of couples of vertices, routing function $\cal R$, integer $P$.

\noindent {\bf Question:} does there exist a $P$-periodic affectation of $\cal C$ in $(G,{\cal R})$?

We deal in next section with complexity of Problem PRA.\\

 \begin{figure}[H]
\label{could-ran}
\begin{center}
% \begin{tabular}{cc}
\includegraphics[scale=0.5]{Total-latence.pdf}
\caption{Complete process for a leaf in $L$.}
\end{center}
\end{figure}
%\end{tabular}\newline

In the context of cloud-RAN applications, we consider here in digraph $G=(V,A)$ modeling the target network two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. We consider a {\bf matching} defined as an application $\rho:S\rightarrow L$. We consider a $P$-periodic affectation $\cal M$, associating respectively integers $m_l$ and $m_{\overline l}$ to couples $(l,\rho(l))$ and $(\rho(l),l)$ for all $l \in L$. The process realized periodically (i.e. initiated in each window of size $P$) for each leaf $l \in L$ is the following one (see Figure \ref{cloud-ran}). First, a message of $\tau$ slots is sent from $l$ to $\rho(l)$ on ${\cal R}(l,\rho(l))$ at slot $m_l$ in the current window. After receiving this message, $\rho(l)$ computes it during a time equal to $\theta$ slots. Then, a message of $\tau$ slots containing the computed result is sent back from $\rho(l)$ to $l$ on ${\cal R}(\rho(l),l)$, at the first occurrence of  step $m_{\overline l}$ in a window (i.e., in the current window at the end of computation or the next one). We denote by $\omega(l)$ the {\bf waiting time}of $l$, i.e.,  the number of slots between the end of the computation time in $\rho(l)$ and the first occurrence of  step $m_{\overline l}$ in a window. Thus, the whole proccess time for $l$ is equal to
$$
PT(l)=\lambda({\cal R}(l,\rho(l)))+\theta+\omega(l)+\lambda({\cal R}(\rho(l),l)).
$$

Let us denote by ${\cal C}_{\rho}$ the set of couples $<l,\rho(l)>$ and $<\rho(l),l>$, for any $l \in L$. Consider a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$. The maximum process time of ${\cal M}$ is equal to equal to $MT({\cal M})=\max\limits_{l \in L} PT(l)$. Thus, we have to deal with the following problem.\\

\noindent {\bf Problem Periodic Assignment for Low Latency(PALL)}

\noindent {\bf Input:}  a digraph $G$, a matching $\rho$ of a set $S$ into a set $L$ in $G$, a routing function $\cal R$, a period $P$, an integer $T_{max}$.

\noindent {\bf Question:} does there exist  a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?

The related optimisation problem we will focus on  consists in minimizing  $MT({\cal M})$. Note that in the context of cloud-RAN networks, we consider $P=1ms$, $\theta=2.6ms$ and $T_{max}$ must be less or equal to $3ms$.

 \section{Complexity results}
\subsection{Complexity of PRA and PALL}
Consider an instance of Problem PRA, i.e., a digraph $G=(V,A)$, an assignment $\cal C$, a routing function $\cal R$ and a period $P$. 
The \emph{conflict depth} of an assignment $\cal C$ is the  number of arcs crossed by at least two routes in ${\cal R}_{\cal C}$; in other words it is the number of potential conflicts between these routes. 
The \emph{load} of  an assignment is the maximal number of routes sharing a same arc (i.e., the congestion of this arc).
It is clear that a $P$-periodic affectation must satisfy that $P$ is larger or equal to the load.

We give two alternate proofs that PRA is $\NP$-complete.
The first one works for conflict depth $2$ and is minimal in this regards since we later prove that for conflict depth one,
it is easy to solve PRA. The second one reduces the problem to graph coloring and implies inapproximability. \\

 \begin{proposition}
Problem PRA is $\NP$-complete, for a routing with conflict depth two.
\end{proposition}
 \begin{proof}
  Let $H=(V,E)$ be a graph and $d$ its maximal degree. We want to determine whether $H$ is edge-colorable
  with $d$ or $d+1$ colors. We reduce this edge coloring problem to PRA. We define  from $H$ an instance $G,{\cal C}, {\cal R}, P$ as follows. For each 
  $v \in V$ there are two vertices in $G$  connected by an arc $(v_1,v_2)$ and none of these arcs are incident. The delay of these arcs is equal to $1$.
  The set $\cal C$ is made of couples of vertices $<s_{u,v}, l_{u,v}>$ for each edge $[u,v]$ in $H$ and the routes associated is ${\cal R} =s_{u,v},u_1,u_2,v_1,v_2,l_{u,v}$.  The delays of arcs $(s_{u,v},u_1)$ and $(v_2,l_{u,v})$ are equal to $d(d+1)-1$.

  Let $\phi$ be an edge coloring with $k$ colors of $H$. We can build a $k$-periodic affectation of $\cal C$ in $(G,{\cal R})$
  by assigning to the source $s_{u,v}$ of each route an offset  of $\phi(s_{u,v})$. Indeed, 
  if two routes $r_1$ and $r_2$ in ${\cal R}_{\cal C}$ share the same edge, say $(v_1,v_2)$ then they represent two edges $e_1$ and $e_2$ of $H$ incident  
  to the vertex $v$. Therefore $\lambda(v_1,r_1) = \phi(e_1) \mod k$ because the delays of the edges before $v_1$ sum to $d(d+1)$ or 
  $2(d(d+1))$ which are equal to $0$ modulo $k$ since $k=d$ or $k=d+1$. Thus $\lambda(v_1,r_1) - \lambda(v_1,r_2) \mod k = \phi(e_1) - \phi(e_2) \mod k$
  and $\lambda(v_1,r_1) - \lambda(v_1,r_2) \mod k > 0$ since $\phi(e_1) \neq \phi(e_2) $.

  Now consider a $k$-periodic affectation of $\cal C$ in $(G,{\cal R})$ . For each $[u,v]$ in $H$, we define $\phi(u,v)$ to be the offset of the route
  beginning at $s_{u,v}$ in ${\cal R}_{\cal C}$. For the same reasons as in the last paragraph, $\phi$ is an edge coloring with $k$ colors.
  Therefore we have reduced edge coloring which is $\NP$-hard~\cite{holyer1981np} to PRA which concludes the proof. 
 \end{proof}
Solving Problem PALL implies to solve PRA for an assignment ${\cal C}_{\rho}$ defined on $S$ and $L$ (see Section 2). Thus, we have the following corollary :

\begin{corollary}
Problem PALL is NP-Hard.
\end{corollary}

As another corollary of the previous proposition,  given $G$, $\cal R$, $P$ and two disjoint subsets $S$ and $L$ in $G$, the problem of  knowing if there is a matching $\rho$  from $L$ in $S$ such that the answer to problem PRA for instance $G,{\cal C_{\rho}},{\cal R}, P$ is  $\NP$-hard since checking a potential feasible solution for this problem implies to solve PRA.\\

\todo{SOMMES NOUS SURS DE CES COROLLAIRES (YS et CC)????}

Consider now MIN-PRA as the minimisation problem related to PRA, consisting in minimizing the peril $P$.

\begin{theorem}
 Problem MIN-PRA cannot be approximate within a factor $n^{1-o(1)}$ unless $\P = \NP$ even when the load is two
 and $n$ is the number of vertices.
\end{theorem}

\begin{proof}
 We reduce PRA to graph coloring. Let $H$ be a graph instance of the $k$-coloring problem. 
 We define $G$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in $G$.
 Two routes $r_v$ and $r_u$ share an arc if and only if $[u,v]$ is an edge in $H$; this arc is the only one shared by these two routes.   We put delays inbetween shared arcs in a route so that there is a delay $k$ between two such arcs.

 As in the previous proof, a $k$-coloring of $H$ gives a $k$-periodic affectation in $G$
 and conversely. Therefore if we can approximate the minimum value of $P$  within a factor $f$,
 we could approximate the minimal number of colors needed to color a graph within a fator $f$, 
 by doing the previous reduction for all possible $k$. The proof follows from the hardness of approximability
 of finding a minimal coloring~\cite{zuckerman2006linear}.
\end{proof}

In particular, this reduction shows that even with small maximal load, the 
minimal period can be large.

 \begin{proposition}
The solution to MIN-PRA is either the load or the load plus one.
Moreover, a solution of  load plus one can be built in polynomial time.
\end{proposition}

\begin{proof}
 First we define an alerning path and how it characterizes an optimal solution of PRA.
 Let $v$ be a vertex of degree $d$ in the congestion graph (to be defined). We assume that the 
 coloring of the edges is optimal (to define in the case of a congestion graph). 
 The color $\alpha$ is not used in it neighborood. For every edge of color $\beta$ from this vertex
 we build an $\alpha - \beta$ path, that is a maximal path $u_0,u_1,\dots, u_l$ so that 
 $(u_0,u_1)$ is of color $\beta,\beta + \lambda(u_0,u_1)$, then $(u_1,u_2)$ is of color $\alpha + \lambda(u_0,u_1),\alpha +\lambda(u_0,u_2)$
 and so on (changer $\lambda$ car on ne suit pas des routes).

 A maximal $\alpha - \beta$ path must be a cycle or the coloring is not minimal.
\end{proof}
\todo{FINALISER CETTE DERNIERE PROPOSTION S'I Y A LIEU (YS ET CC)}

 \subsection{A polynomial case about PRA}

We now study special cases of problem MIN-PRA restricted to a subset.  First, we consider in this section instances $(G=(V,A),{\cal R}, {\cal C}_{\rho})$ of MIN-PRA in which the routing function is coherent.  A  routing function $\cal R$ is {\bf coherent} if and only if for any couples $<u,v>$ and $ <u',v'>$ of nodes in $V$ such that the two routes ${\cal R}(u,v)$ and ${\cal R}(u',v')$ cross two same vertices $x$ and $y$  in this same order, then the subroutes  from $x$ to $y$  in ${\cal R}(u,v)$ and ${\cal R}(u',v')$ are equal. As a consequence, for each node $u$ in $V$, the subgraph of $G$ induced by all the routes from $u$ to all the other nodes in $G$ is a tree.

Moreover, we also consider that for any pair of symmetric arcs $(u,v)$ and $v,u)$, routes ${\cal R}(u,v)$ and ${\cal R}(v,u)$ are also symmetric.

Finally, considering sets $S$ and $L$, set  ${\cal C}_{\rho}$ is obtained from an assignment $\rho$ of $S$ in $L$ such that  there are no common arcs for routes originating from different sources ($\rho$ is said {\bf source-free}).

\begin{proposition}
\label{DP-PRA}
Problem MIN-PRA restricted to instances $(G=(V,A),{\cal R}, {\cal C}_{\rho})$ within a coherent routing can be solved in linear time according to the size of $A$.
\end{proposition}

 The definition of source-free assignment ensures that an arc cannot belong to two routes in $\cal R$ originating from different sources in $S$. Moreover, the definition of a coherent routing  ensures that if two routes originate from the same source $x$, they share the same arcs from $x$ to a given vertex $y$ and cannot share an arc after. This means that $\forall (u,v) \in A$, the arcs $(u,v)$ with the highest load $l_{max} = max(load(u,v))$ are arcs $a_0^j$ sharing a common origin $u_0 \in S$ and a $P$-periodic affectation for those arcs is a $P$-periodic affectation for all the arcs in $A$.

A $P$-periodic affectation is such that routes on a same arc must be separated by a delay that is strictly superior to an integer $\delta \geq 0$. As a consequence, the minimum size of the period $P$ is equal to $l_{max} \times (\delta + 1)$. This means that that on the arc with the highest load, we can schedule the first route at the moment $m_k = 0$, the second route at a moment $m_{k'} = \delta + 1$ and so on for all $l_{max}$ routes.

\begin{proposition}
\label{DP-NPA}
Giving $G$ and a coherent routing ${\cal R}$ ,finding a source-free assignment $\rho$ such that the  period solution to MIN-PRA is minimum over all such assignment can be done in linear time according to the size of $A$.
\end{proposition}

In any source-free assignment, the minimum size of $P$  is obtained by minimizing the highest load of the first arc of any route from a source to a leaf. As all sources in $S$ are connected to all sources vertices in $L$ by a route in $\cal R$, a simple load balancing allows to obtain a maximum load equal to  $max_{load} = \lceil \frac{\cal L}{|S|} \rceil$. Once the \rmatching is computed,  the minimum value of $P$ is thus equal to $max_{load} \times (\delta + 1)$.

%%%%%%%
We consider now instances $(G,{\cal R}, {\cal C}_{\rho})$ of MIN-PRA, called {\bf $1$-instances} in which the routing function is still coherent and $\rho$ is such that there exists one and only on arc crossed by at least $2$ routes originated from different sources.  
\begin{proposition}
\label{1-arc PRA}
Problem MIN-PRA restricted to $1$-instances can be solved in linear time according to the size of $A$.
\end{proposition}

Let $(a,b)$be the arc in $G$ crossed by at least $2$ routes originated from different sources, and let $r(a,b)$ be the set of such routes.  
In order to have a $P$-periodic affectation, the period $P$ must be large enough for all arcs in $r(a,b)$, thus the minimal size of $P$ is $P= load(a,b) \times (\delta + 1)$. Moreover, this is also the minimum solution for $MIN-PRA$. If we consider that if there exists a $load(a_b)$-periodic affectation $m_i \in \cal M'$ of each route $r_i$ in $r(a,b)$ , then $m_j$ in $\cal M$ corresponding to $r_i$ is $m_j = m_i - \lambda(u_b) mod P$ . As the routing function is coherent, no two routes originating from a same source can use different routes to attain $(a,b)$ thus the $P$-periodic affectation is valid for any arc $(u,v) \in A$ if it is valid on $(a,b)$.

\section{Heuristic approaches to solve PALL}
\subsection{Network topologies}
We will especially focus on three symmetric digraph topologies corresponding to realistic cases  of  fronthaul network. In those kinds of networks, we can differentiate three kinds of
topologies. Each one of them correspond to a real configuration, depending of the distance between the BBU and the RRH.
\begin{enumerate}
 \item Topology 1: A basic network topology, composed of some base stations, represented by source nodes $S$, all connected to the same switch,
which will be a vertex, connected itself to another vertex, corresponding to a switch, connected to some leave nodes $L$ representing the RRH.
\item Topology 2: A network containing an optical ring, such that some sources nodes be connected to it anywhere, not intersecting themselves before the ring,
and some set of leave nodes are also connected at any point of the ring.
\item Topology 3: The general case: A DAG, on which we may restrict parameters as the degree or the number of vertices to represent graphs corresponding to realistic networks.
\end{enumerate}

 \begin{figure}[H]

\begin{center}

\includegraphics[scale=0.3]{fronthaul0.png}\\

\end{center}
\caption{From left to right: Topologies 2, 3 and 1 representing respectively the far, mid and near fronthaul.}
\end{figure}

\subsection{Algorithms}
...
\subsection{Performance evaluation}
...
\section{Conclusion}
...
\newpage
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
\section{ANNEXE : MATERIEL SUPPLEMENTAIRE?}
\subsection{Coloring and $P$-periodic affectation}
We define two characteristic graphs associated to an assignment in $G$.

%\begin{definition}[Edge Conflict Graph]
%  The Edge Conflict Graph (ECG) of an \rmatching $\cal C$ in a digraph $G=(V,A)$ is the graph $G'=(V',E')$ such that 
 % a vertex of $V'$ is an arc of $A$ with a load greater than one. There is an edge between two vertices of $V'$
 % if and only if there is a route in ${\cal R}_{\cal C}$ which contains the two arcs of $A$ corresponding to the two vertices.

 % This graph can be oriented so that an edge is oriented as the route it represents and
 % we can associate as weight to this edge, the delay of the corresponding path.
%\end{definition}

\begin{definition}[Route Conflict Graph]
The Route Conflict Graph (RCG) of an \rmatching $\cal C$ in a digraph $G=(V,A)$ is the graph $G'=(V',E')$ where 
the vertices of $V'$ are the routes  in ${\cal R}_{\cal C}$ and there is an edges between two vertices in $V'$
corresponding to two routes in ${\cal R}_{\cal C}$ if and only if they share a same arc.

We fix an arbitrary ordering on the elements of $V'=\{v_1,\dots,v_n\}$.
We associate a weight to each edge $(v_i,v_j)$. Assume that $i < j$, 
and that the routes $r_i$ and $r_j$ in ${\cal R}_{\cal C}$ corresponding to $v_i$ and $v_j$ in $G'$ have $u$ as first common vertex.
Then the weight of $[v_i,v_j]$ is $\lambda(u,r_i) - \lambda(u,r_j)$.
\end{definition}
\todo{FAIRE LE LIEN ENTRE COLLORATION DU RCG ET P-PERIODIC AFFECTATION. NE FAUT-IL PAS INTRODUIRE LA TAILLE DE MESSAGE $T$ DANS LE SYSTEME D'INEQUATIONS? }
We define $\alpha(u,r_i,r_j) = | \lambda(u,r_i)-\lambda(u,r_j)|$. To the route conflict graph, we can associate a system of inequations representing the constraints that the 
$P$-periodic affectation must satisfy.

\begin{definition}[Conflict system]
 Let $G$ be a weighted RCG, we associate to each vertex $v_i$ of $G$ the variable $x_i$.
 The conflict system is the set of inequations $ x_i \neq x_j + w(e)$ for $i < j$ and $e=(v_i,v_j)$ edge of $G$.
\end{definition}

It is simple to see that the conflict system of a \rmatching has a solution modulo $P$ if and only if 
the \rmatching has a $P$-periodic affectation. This kind of system can be solved by SAT solver or CSP solver and those two methods will be investigated on practical instances.
\todo{Donner la formulation pour ces solvers et donner le résultat d'expérience dans une partie indépendante. 
Les comparer avec un solveur de notre cru avec quelques heuristiques simples.}

\begin{definition}[Additive coloring]
 Le $G$ be a weighted graph, we say that $G$ has an additive coloring with $p$ colors if and only if its associated
 conflict system has a solution over $\mathbb{Z} \diagup p\mathbb{Z}$. The minimal $p$ for which the system has a solution is the additive chromatic number of $G$ denoted by $\chi_{+}(G)$.
\end{definition}

Finding an optimal additive coloring is thus the same as solving our problem of finding a $P$-periodic affectation
and is at least as hard as finding an optimal coloring.  Because of the constraints on the edges, 
the additive chromatic number of a graph may be much larger than its chromatic number.
When the graph is a clique both additive and regular chromatic number may be the size of the graph.
However, we will now prove that for bipartite graphs the chromatic number is two while its additive 
chromatic number is arbitrary large.

We have the following values obtained by exhaustive search.

\todo{généraliser chi+ aux graphes sans poids en faisant un max ?}
\begin{fact}
 The values we list here are the maximal ones we obtain 
 by weighting bipartite graphs.
 \begin{enumerate}
  \item  $\chi_{+}(K_{2,2})= \chi_{+}(K_{3,3}) = 3$ with weight $0,1$
  \item $\chi_{+}(K_{3,4}) = \chi_{+}(K_{3,5}) =3$ 
  \item $\chi_{+}(K_{3,6}) = 4$ 
  \item  $\chi_{+}(K_{4,4})=\chi_{+}(K_{4,5})=\chi_{+}(K_{4,6})=4$
  \item $\chi_{+}(K_{5,5})= ?$
 \end{enumerate}
 \end{fact}

 A nice theoretical question would be to find the way to put weights
 on a bipartite graph so that its additive chromatic number is maximal. 
 My conjecture is that a $K_{l,l}$ can have an additive chromatic number in $O(l)$.
 The question is also interesting when we restrict the weights to $0,1$.

\begin{theorem}
 There is a weighting of $K_{l^2,\binom{l}{l^2}}$ such that 
 $\chi_{+}(K_{l^2,\binom{l}{l^2}}) > l$.
\end{theorem}

\begin{proof}
Let $V_1, V_2$ be the bipartition of the graph we build and let $|V_1| = l^2$. 
For all $S \subseteq V_1$ with $|S| = l$, we denote by $v_1,\dots,v_l$ its elements,
there is a single element $v_S$ in $V_2$ which is connected to exactly the elements of $S$
and such that the weight of $v_S,v_i$ is $i-1$. Because of this construction, $V_2$ is of size
$\binom{l}{l^2}$. Moreover for any additive coloring of the graph we have constructed,
a set of $l$ elements in $V_1$ cannot have all the same color. But by the extended pigeon principle, since there 
are $l^2$ elements in $V_1$ at least $l$ amongst them must have the same color. 
This prove that the graph we have built cannot have an additive coloring with $l$ colors.
\end{proof}

The theorem can be improved so that the number of colors is logarithmic in 
the size of the bipartite graph.

\begin{theorem}
 There is a weighting of $K_{l^2,\binom{l}{l^2}}$ such that 
 $\chi_{+}(K_{l^2,\binom{l}{l^2}}) > l$.
\end{theorem}

\begin{proof}
 Let $\mathcal{F}$ be a family of perfect  hash functions from $[l^2]$ to $[l]$. It means that for any 
 subset $S$ of size $l$ of $[l^2]$, there is an hash function $f \in \mathcal{F}$ such that $f_S$ is injective.
 The construction of the bipartite graph is similar to the previous proof. 
 Let $V_1, V_2$ be the bipartition of the graph we build and let $V_1 = \{v_1,\dots,v_{l^2}\}$. 
 For each function $f \in \mathcal{F}$ there is a vertex $v_f \in V_2$ and the weight of $(v_i,v_f)$ is $f(i)$.
 By \cite{schmidt1990spatial,alon1995color} there is a family of perfect hash functions of size $2^{O(l)}$ therefore $V_2$ is of size $2^{O(l)}$.
 Again by using the pigeon principle and the perfect property of the family of functions, we prove that no additive coloring with $l$ colors is possible.
\end{proof}

\todo{explain the removal of low degree vertices = kernelization + heuristic on the degree
Also implement it in the solver}

\todo{Comprendre la valeur sur d'autre familles de graphe, notemment celles qu'on peut rencontrer en pratique, par exemple petite tree width }

%%%%%%%%%%%%%%%%%%

\subsection{The disjoint paths NPAC-Problem : DP-NPAC}

In this problem, there is a delay constraint that must be satisfied by a \rmatching. This means that we must remove the routes in $r' \in \cal R$ where $\lambda(r') > K$.

\begin{proposition}
\label{DP-NPAC}
Problem DP-NPAC can be solved in polynomial time according to the size of $V$.
\end{proposition}

In a similar way to problem DP-PRA, the arcs with the highest load can only be the arcs $a_0^j$ sharing a common origin $u_i \in S$. In order to minimize the size of the period $P$, we have to find a \rmatching such that the maximum number $k_i$ of routes originating from a same source $u_i \in S$ is minimal. Having found this minimal value $k$, we face a problem equivalent to the DP-PRA problem.

In order to find a matching of vertices in $S$ with vertices in $L$ such that the maximum number of vertices in $L$ assigned to a vertex $s_i \in S$ is inferior or equal to $k$, we will transform our problem in a flow problem.

\subsubsection{Construction of a flow graph}

Let us consider an instance $I= (G=(V,A), S, L, \cal R, P, \delta, K$ and $M)$ of NPA where the routes in $\cal R$ are only those that respect the delay constraint $K$. We first construct a complete bipartite graph $G'=(V',A')$ where $V'$ is made of two sets of vertices : vertices $V'_1$ corresponding to $S$ and $V'_2$ corresponding to $ L$. $A'$ is made of all possible arcs from vertices $v'_1 \in V'_1$ to vertices $v'_2 \in V'_2$, with a capacity 1. We then add to $V'$ a source node $S'$ and a sink node $T'$. Finally we add to $A'$ all the arcs from $S'$ to each vertex $v'_1 \in V'_1$, with a capacity $k$  and all the arcs from each vertex $v'_2 \in V'_2$ to $T'$, with a capacity 1, where there is a route $\cal R$$(v'_1, v'_2)$. We have thus obtained a flow graph $G'$ whose size is polynomial in regards to the size of $G$. We will now compute the maximum flow in $G'$ in order to determine if its size is at least $\cal L$, in order to be able to connect all the leaves.

We can compute the size of a maximum flow in $G'$ in a polynomial time using a generic flow algorithm as Ford-Fulkerson (it will terminate as arcs capacity are rational numbers). In order to minimize the objective $k$, we can begin with a value $k$ = 1 and use a dichotomic approach to find the minimal value of $k$ for which a maximal flow of size $\cal L$ exists in $G'$. The maximum value of $k$ is $M$. If $k = M$ and the maximum flow value in $G' < \cal L$, then there is no valid \rmatching of $S$ in $L$.

The complexity of minimizing $k$ is thus $0(m^2n \times log_2 n)$ where $m = |A|$ and $n=|V|$. We obtain in the end a \rmatching minimizing the maximal number of routes originating from a single source $u_s \in S$ and we are faced with the DP-PRA problem for this instance.

\begin{figure}[!t]
\centering
includegraphics[scale=0.3]{DP-NPA.pdf}
\caption{Reduction of DPA-NPA into a flow problem}
\label{Modelling of DP-NPA Problem}
\end{figure}

\end{document}
%%%%%%%%%%%%%%%%%%

\section{Real Network Topologies}

We consider 3 kinds of topologies corresponding to the different kinds of fronthaul networks: 
\begin{enumerate}
 \item Topology 1 : a basic network topology, composed of some base stations, represented by source nodes $S$, all connected to the same switch,
which will be a vertex, connected himself to another vertex, corresponding to a switch, connected to some leave nodes $L$ representing the Antennas.
\item Topology 2 : A network containing an optical ring, such that some sources nodes may join it anywhere, not intersecting themselves before the ring,
and some set of leave nodes are also leaving at any point of the ring.
\item Topology 3 : A ''random`` network, generated with some realistic properties (number of vertices, degree ...)
\end{enumerate}

\subsection{Topology 1}
\begin{center}

\includegraphics[scale=1]{Fig4.pdf}\\
Example of topology 1.
\end{center}

In this topology, there is 3 cases :
\begin{itemize}
 \item 1: When the weight of the links from source nodes are all equal. This is the closest case to the reality, but also the easier to solve.
 \item 2: When the weight of the leave nodes links are all equal .
 \item 3: When all the links have different weights.
\end{itemize}
The middle link can be represented without weight, because it is common to all the routes, so it can be simplified in calculations. 
Likewise, we do not consider $\theta$, the calculation time.

The first case is the easiest to solve. Indeed, it is obvious that if we schedule all messages following each others, we will obtain an optimal
$T_{max}$ : there is no waiting times on any routes.
Also, all the message will cross the first switch, without collisions, then 
they will not be another conflict point between all routes.

This solution is optimal because the messages will not wait on source nodes, so $\omega(r) = 0$, $\forall r \in \rho$. $T_{max}$ is
equal to the physical delay of the longer route, that we can not minimize.\\

Given this observation, one can try to solve a simpler problem for cases 2 and 3 : is it possible to find a two way trip
with all $w_i = 0$ ?

It is always possible when the windows $P$ is large enough(for example: send all messages one by one, waiting the previous one to be back),
therefore the problem is to find the smallest windows such that it is possible.

The following example shows us that you can find a 2-way-trip affectation such that there is no waiting time, but it needs a greater time window P than a
solution with waiting times.

Consider the graph : 
\begin{center}

\includegraphics[scale=0.7]{Fig10.pdf}
\end{center}

Consider messages of 10 slots. If you search for a P-periodic affectation, without using waiting times, there are 2 choices : 
\begin{itemize}
 \item l1 is sent before l2 : the message from l1 will leave A after 11 slots.X is he minimal time slot in which l2 can emit. 
 To avoid collisions with the message from l1 in A,l2 must emit after 1 slot :  $X\ge1$.
 In the other way, the message from l1 will use B from time slot 21 to 30. The route from l2 is 12 units long from l2 to B. So, to avoid collisions with 
 the message from l1 in B $X+12 \ge 31 \rightarrow x\ge 19$. Then, by taking $X=19$, the time
 windows is at least 38 slots in A (corresponding to the transit time of the 2 messages and the time lost between those 2 transits).
 \item l2 is sent before l1: symmetrically the collision the collision occurs in node A if l1 emits before time 19. The time window in B is at least 38 too.
\end{itemize}

If we allow waiting times: there is an easy scheduling using only a 3 time slots windows : 
Sending message 1 at time 0, message 2 at time 1, so the messages will not cross A in the same time. to be sent back,
message 2 comes back immediately and is using B from slots 13 to 22,then message 1 is using B from slots 23 to 32, waiting 2 time slots at s1.

So the smaller time windows is 20, half smaller than best solution without waiting times.

\todo{temps de traje 22 contre 24 On peut utiliser l'exemple d√©crit en rajoutant un tr√®s long chemin de mani√®re √† ce que les 
waiting times ne changent pas la taille du plus long two way trip.}

Let us define a simplification of a matched graph. Ignore weights on arcs starting from leaves, and find a starting order without collisions 
(then to find the real values,add the corresponding delay to each routes). 
We obtain a graph in which we have a central node, and different routes going to each sources.
Such a graph is called a \emph{star}. A star is a non-oriented graph in which each edge between the central node $C$ and each source node $s_i$
has a weight $a_i$ (corresponding to the weight of the arc in $N$), where i is the number of the route in $\rho$. The r-matching $\rho$ is now
associating a route $r_i$ to a source node $s_i$.

\begin{center}

\includegraphics[scale=0.7]{Fig11.pdf}\\
example of a star for a matched graph with 3 routes
\end{center}

We can do this simplification of a matched graph N only if we search an affectation without waiting times : in this case, any solution
will be optimal, because the $T_{max}$ will be twice the delay of the longer route. So, a solution for a star, is a solution for a matched
graph, without waiting times. If waiting times are allowed, we are forced to consider the delay of the routes and this model is not
available anymore.

A \emph{star affectation} is a 2-way-trip affectation of the corresponding matched-graph $N$
in which there is no waiting time,$\omega(r) = 0 \,\forall\, r \,\in\, \rho$.

In this simplified model, we have two parameters left: the begin offsets $o_i$ and the travel time of each routes $2a_i$.
A route may have no collisions with the others : $\forall$ i,j $\in \rho$, 
$$o_i \notin [b_i,...,b_i+T] \, and\, o_i+2a_i\notin [o_j+2a_j,...,o_j+2a_j+T].$$
T is the size of the message.

We define a new problem :

\noindent {\bf Star affectation (SA)}

\noindent {\bf Input:} a star s, integer $P$.

\noindent {\bf Question:} does there exist a star affectation of s in a period P.

\noindent {\bf Optimization :} minimizing P .\\

Solving this problem in P is finding the best solution for cases 2 and 3 of the topology 1.

We suggest the following algorithm to find a star affectation in which $d_0$ is the shortest route, and $d_{l-1}$ the longest one, 
l is the number of routes and T is the size of the messages :

\begin{algorithm}[H]
\caption{Star affectation from shortest to longest}
\begin{algorithmic}
\REQUIRE star s
\ENSURE star affectation in $P \le l*T + 2d_{l-1} - 2d_0$
\STATE $offset \leftarrow 0$
\FORALL{routes i in $\rho$ from the shortest to the longest }
\STATE $o_i \leftarrow offset$
\STATE $offset \leftarrow offset+T$
\ENDFOR

\end{algorithmic}
\end{algorithm}

The message using the shortest route is sent before the others, so it come back to the central node before the others.
Recursively, the second message is sent before the others, and also will be back before the other messages. 
Because the second message is sent T slots after the first message ($o_2 = o_1 + T$, where T is the size of the message), it come back after
the end of the message one : $o_1+ T + 2a_1 \le o_2 + 2a_2$ with $a_2 \ge a_1$.

The period given by this algorithm is P = 2$\lambda(r_{{\cal L}-1}$) + ${\cal L}$ * T - 2$\lambda(r_0)$, if routes $\{r_0,...,r_{{\cal L}-1}\}$ are ordered
from the shortest to the longest. 2$\lambda(r_0)$ is the first slot in which the first message is back, and 2$\lambda(r_{{\cal L}-1})$ is
the first slot in which the last message is back.${\cal L}$ * T is the time to transfer the messages from all routes.\\

We can also use a greedy algorithm, choosing the offset of each packet in turn so that there is no collision. We must chose an offset $o_i$ for each route $r_i$, so that no two routes have a collision on the central link the two times they use it.  We denote by $[o_i]_P$ the set of times $\{ t \mod P \mid o_i \geq t < o_i + T \}$ which are the time used by the route $r_i$ on the central link on its first use. There are no collision if for all $i\neq j$
 $[o_i]_P \cap [o_j]_P = \emptyset$. Moreover no two routes must have a collision on the way back, hence we must have for all $i\neq j$
 $[o_i + a_i]_P \cap [o_j + a_j]_P = \emptyset$.

One can prove that if $P$ is large enough with regard to $l$ and $T$, then there is always a two way trip
with waiting time $0$ with this algorithm.
 Assume $P \geq 4lT$, the algorithm works as follows. 
We cut the time windows of size $P$ into $2l$ slots of size $2T$ and we will asign one to each route.
A different slot is assigned to each route, where the offset is chosen inside the slot so that 
no collision on the first go in the central link is possible. If the slot chosen for the route $r_i$ is $[cT,(c+2)T]$,
then we set $o_i \in [cT,cT+1]$ so that $o_i + a_i \mod P = dT$. Assume that the offset of the first $i-1$ routes have been 
chosen in the previous way so that there is no collision. Since we have $P \geq 4lT$, we have at least $2l-i$ possible choices of offset without collision on the first use of the central link. Each of these choices uses a time slot of size $T$ on the way back on the central link. Since there are $i$ time slots used, and $i \leq l$, we have strictly more than $l$ possible choices and less than $l$ of them are forbidden, therefore there is a choice of offset with no collision. 
Since the algorithm works for all $i \leq l$, it finds a two way trip with waiting times $0$.

\todo{On peutfaire mieux que $4lT$, avec une meilleure analyse √ßa doit juste gagner un tout petit peu, 
avec un meilleur algo de placement peut-on faire $3lT$ ou m√™me $2lT$ ? Il doit √™tre possible
de montrer qu'on ne peut pas faire mieux que $2lT$.}

\begin{algorithm}[H]
\caption{start assignment greedy algorithm}
\begin{algorithmic}
\REQUIRE star s, window size $p$
\ENSURE star affectation in P<p 
\STATE $P1[p/2T]$ slots in first way period.
\STATE $P2[p/T]$ slots in back way period.
\FORALL{route i in $\rho$ }

\FORALL{slot j in P1}

\IF{P1[j] is free}

\STATE shift $\leftarrow$ T- 2$a_i \mod p$

\IF{P2[shift + 2Tj] is free}

\STATE $o_i \leftarrow 2Tj + shift$
\ENDIF

\ENDIF

\ENDFOR

\ENDFOR

\end{algorithmic}
\end{algorithm}

In this algorithm,for each route, search for a free time slot in P1,then set $o_i \in [cT,cT+1]$ so that $o_i + a_i \mod P = dT$.
If $[dT,(d+1)T]$ is free, and allow the route to use the time slot $[cT,cT+1]$ at the first use of middle link.\\

The following algorithm is a simplified way to find a star affectation

\begin{algorithm}[H]
\caption{start assignment greedy algorithm v2}
\begin{algorithmic}
\REQUIRE star s, window size $p$
\ENSURE star affectation in P<p 
\STATE $P1[p]$ slots in first way period.
\STATE $P2[p]$ slots in back way period.
\FORALL{route i in $\rho$ }

\FORALL{slot j in P1}

\IF{$[j,j+T]_P$ is free in P1}

\IF{$[j + 2r_j,j + 2r_j+T]_P$ is free in P2}

\STATE $o_i \leftarrow j$
\ENDIF

\ENDIF

\ENDFOR

\ENDFOR

\end{algorithmic}
\end{algorithm}

In this algorithm,for each route, search for the first free slot [j,j+T] in P1 such that the slot $[j + 2r_j,j + 2r_j+T]_P$ in P2 is free too,
then give the route the offset j(shifted by the distance from the leave to the first node).\\

Now, the waiting times are allowed, and try to solve PALL on topologie 1.
The following heuristic is suggested :

\begin{algorithm}[H]
\caption{Longest to shortest with waiting times}
\begin{algorithmic}
\REQUIRE Matched graph N, window size $P$, packed size T
\ENSURE 2way Trip affectation in P
\STATE offset $\leftarrow$ 0
\FORALL{route i in $\rho$ from the longest to the shortest }
\STATE  $m_i \leftarrow$ offset
\STATE offset $\leftarrow$ offset + T
\ENDFOR
\STATE offset $\leftarrow$ 0
\STATE take i such that $r_i$ is the first route to come back in sources node
\STATE $w_i \leftarrow $ offset;
\STATE offset $\leftarrow$ $a_i$ + T
\WHILE{there is a route which has no $w_i$}
\STATE take i such that $r_i$ is the longest route able to come back in source node before the last one has totally passed
\STATE $w_i \leftarrow $ offset - $a_i$;
\STATE offset $\leftarrow$ offset + T

\ENDWHILE

\end{algorithmic}
\end{algorithm}

The running of this algorithm is the following one :
\begin{itemize}
 \item 1 On leaves node, the messages are scheduled so that they are following each others, from the longest route to the shortest route.
 \item 2 On sources node, let the message able to come back first pass.
 \item 3 Once this message has passed, look at all the eligibles message able to be back at the sources node during the transit of the previous one.
 \item 4 Let the eligible message on the longest route transit in the node first after the previous one, possibly delayed by a little waiting time to avoid crossing.
 \item 5 delay the others with a waiting time.
 \item 6 while all the messages are not scheduled, get back to 3
\end{itemize}

This algorithm gives us solution with the minimum period possible : ${\cal L}$ x T. Indeed, all the messages are scheduled following each others on conflict node :
there is no wasted time between the transit of two messages.

For the case 1, this algorithm is similar to the obvious way to schedule the messages mentioned above. It gives optimal solution without increase 
the calculation time.

For the case 2, this algorithm gives optimal solutions: Indeed, in the manner we order messages, from leaves toward sources,
the messages are sent from the one using the longest route to the one using the shortest one. Number the routes in this order from 1 to ${\cal L-1}$.

We have $\forall \ i<j$, $r_i<r_j$.
The first message leaves the source switch at time 2$r_1+T$, the second message, can use it at the time 2$r_2+T$.
The second message waited $2r_1+T-2r_2+T = 2(r_1+r_2)$ to use the middle link. So, the second message leave the source switch at time
2$r_2+T + 2(r_1+r_2) = 2r_1 +T$.
Recursively, all messages will take $2r_1 +T$ slots for the Two Way Trip.
Consequently, for this case, the heuristic is optimal, because the longer route has no waiting time and no TwoWayTrip is longer than the longer route one.

For the case 3, after some simulations on values corresponding to reality $(P\simeq19500,T\simeq2500,l\simeq2000)$, good solutions are obtained.

The average of solutions given by this heuristics gives solutions close to the average of $2*r_max$.

\todo{interessant de dire que la pire solution correspond souvent a celle trouv√© par l'algo ? (sur ce genre de ''pire`` solutions, on ne peux pas
faire mieux.}
\todo{mettre l'exemple ou ca marche mal alors qu'en espacant un peu ca rentre tres bien}

% \section{Heuristics to solve PRA}
% Consider an instance problem of the optimization problem related to PRA, i.e., a set ($G$, $S$, $L$, $\cal R$, $\rho$, $\delta$). Let us denote by $G_{\rho}$ the subgraph of $G$ induced by all the arcs crossed by at least one route in $\rho$. 
% 
% Let $a=(u,v)$ be an arc in $G_{\rho}$ and let $n_a$ be the cardinal of ${\rho}(u,v)$. Giving an affectation ${\cal M_k}=\{m_0, \ldots ,m_{{\cal L}-1}\}$, for each route $r^j \in  {\rho}(u,v)$, in which $a$ is the $i^{th}$ arc, we consider a couple of integers $(t,M)$ defined by $t=\lambda(i,j)+m_j$ and $M=\lambda(r_j)+m_j$. Let  $I_a=\{(t^a_1, M^a_1), \ldots , (t^a_{n_a},M^a_{n_a})\}$ the collection of such $n_a$ obtained couples for $a$ from ${\rho}(u,v)$.\\
% 
% Consider a complete ordering $\cal O$ of the set of arcs $A_{\rho}$ of $G_{\rho}$. Such an ordering is a {\bf sort} of $\rho$ iff for any par of arcs $a$ and $a'$ with ${\cal O}(a)< {\cal O}(a')$, there is no route of $\rho$ in which $a'$ appears before $a$.\\
% 
% Let us first consider that such a {\bf sort} $\cal O$ of $\rho$ exists.\\
% 
% \noindent {\bf Problem  Minimal Delay Switching (MDS)} 
% 
% \noindent {\bf Input:}  A set of couples of integers $I=\{(t_1,M1), \ldots , (t_n,M_n)\}$ with $t_i<M_i$ for any $1\geq i \geq n$, an integer $P$ and an integer $K$.  
% 
% \noindent {\bf Question:}  Does there exist a set of integers $\{x_1, \ldots , x_n\}$ such that
% \begin{itemize}
% \item for any $i\neq j$, we have $(t_i+x_i)-(t_j+x_j)~mod~P>\delta$ and $(t_j+x_j)-(t_i+x_i)~mod~P>\delta$,
% \item $\max\limits_{1 \leq i \leq n} M_i+x_i \leq K$.
% \end{itemize}
% 
% \noindent {\bf Optimisation goal:} minimizing $\max\limits_{1 \leq i \leq n} M_i+x_i$.\\
% 
% 
% For each route $r_j$, let us denote by $s_j=(t^j_1,M^j_1), \ldots , (t^j_{n_j},M^j_{n_j})$ the sequence of couples of integers in each arc crossed by $r_j$.
% 
% \begin{enumerate}
% \item Define a sort $\cal O$ of $\rho$.
% \item At each step $s$ of the algorithm,consider arc $a$ such that ${\cal o}(a)=s$.
% \item Solve problem MDS on $I_a$. Let us denote $x^a_j$ the integer assigned to route $r_j \in \rho(a)$.
% \item Consider that $a$ is the $i^{th}$ arc of $r_j$. Add $x^a_j$ to each integer in couples $(t^j_y,M^j_y)$ for each $i \leq y\leq n_j$.
% \end{enumerate}
% Finally, the $P$-periodic affectation computed by the algorithm ${\cal M_k}=\{m_0, \ldots ,m_{{\cal L}-1}\}$ is such that $m_j$ is the sum of all

\bibliographystyle{plain}
\bibliography{Modele-latence-2}

\end{document}

### 2017-01-18 article/article.tex
plan

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}

%opening
\title{Contention Management for 5G}
\author{DB,CC,MG,OM,YS}

\begin{document}

\maketitle

\begin{abstract}
This article treats about Contention Management for 5G.
\end{abstract}

\section{Introduction}
  \itemize
    \item Context and problematic
    \item Related works
    \item Article contribution

\section{Model, Problems}

  \subsection{Definitions}
    Définition du Modele, du 2 WayTrip

  \subsection{Problems}
    Définition de PRA, et de PALL.

\section{PRA Solving}

  \subsection{NP-Hardness}
    Etude de la complexité

  \subsection{MIN-PRA}
    Exemple de cas simple

\section{Proposed Solutions, solving PALL}

  \subsection{Intro}
    PALL NP-Hard car PRA NP-Hard\\
    Résultats valables sur Topologie 1 avec nos paramètres

  \subsection{No waiting times}
    \subsubsection{Star affectation}
      Définir star affectation en partant de PALL
    \subsubsection{Shortest-longest}
      \paragraph{Algo}
      \paragraph{Period}
    \subsubsection{Exhaustive generation}
      Décrire l'algo, expliquer les coupes
    \subsubsection{Results}
      Resultats des simulations : Shortest-longest optimal pour ces parametres.

   \subsection{Allowing waiting times}
     \subsubsection{Intro}
	Importance des waiting times quand la période est donnée (Résultats D'éxepriences et preuve avec l'exemple)
     \subsubsection{LSG}
	\paragraph{Algorithm}
	\paragraph{Analysis}
	  Parler de LSO et expliquer pourquoi LSG mieux avec nos params
     \subsubsection{Results}
	 \paragraph{Random}
	 \paragraph{Distributions}

\section{Conclusion}

\end{document}

### 2017-01-20 article/article.tex
testssh

@@
 \usepackage[utf8]{inputenc}
+\usepackage{xspace}
+\usepackage{graphicx,graphics} 
+\usepackage{color}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{algorithm}
+\usepackage{algorithmic}
+\usepackage{longtable}
+\usepackage{complexity}
+\usepackage{tkz-graph}
+\usepackage{float}
+\usepackage{setspace}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+
+\graphicspath{{figures/}}
+\newcommand\rmatching{${\cal R}$-matching\xspace}
+\newcommand\mdelay{$\cal M$-delay\xspace}
+\newcommand\matchedgraph{{\bf matched graph}}
+\newtheorem{proposition}{Proposition}
+\newtheorem{theorem}{Theorem}
+\newcommand{\reporttitle}{Contention management for Deterministic Networking}     % Titre
+\newcommand{\reportauthor}{Maël \textsc{Guiraud }} % Auteur
+\newcommand{\reportsubject}{Master Thesis} 
+\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
+\setlength{\parskip}{1ex} % Espace entre les paragraphes
+
+\newcommand{\todo}[1]{{\color{red} TODO: {#1}}}
 
@@
   \subsection{Definitions}
-    Définition du Modele, du 2 WayTrip
+	  A network can be considered as a directed graph $G=(V,A)$ with two non intersecting subsets of vertices: 
+	a subset $L$ of nodes which are called {\bf leaves} and a subset $S$ of nodes which are called {\bf sources}.  
+      The indegree of nodes in $S$, and the outdegree of nodes in $L$ are equal to 0. 
+      We denote by ${\cal L}$ the cardinal of $L$ and by ${\cal S}$ the cardinal of $S$. 
+      Each arc  $(u,v)$ in $A$ has an integer weight $Dl(u,v)$, called {\bf delay}, representing the time taken by a data to go from $u$ to $v$
+      using this arc.
+
+      We consider $G^r=(V,A^r)$ wherein the set of vertices is the same as in $G$, and $A^r$ represents the edges of $A$ directed in the other way. 
+      \newline
+      \begin{center}
+      \fbox{\parbox{11cm}{
+      \begin{figure}[H]
+      \begin{center}
+      \begin{tabular}{cc}
+      \includegraphics[scale=0.8]{Fig2.pdf} & \includegraphics[scale=0.8]{Fig3.pdf}\\
+      $G=(V,A)$ & $G^r=(V,A^r)$\\
+      \end{tabular}
+      \end{center}
+      \caption{$G$ and $G^r$ with ${\cal L} = {\cal S} = 1$.}
+      \end{figure}
+
+      }}\end{center}
+
+      A {\bf route} $r$ is a sequence of arcs $a_0, \ldots , a_{n-1}$, with $a_i=(u_i,u_{i+1}) \in A$ such that $u_0 \in L$ and $u_n \in S$.
+      The delay of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq k <i} Dl(a_k)$$ We also define $\lambda(u_0,r)=0$.
+      The delay of the route $r$ is defined by $\lambda (r)= \lambda (u_n,r)$. It is the weight of all the arcs on the route.
+
+      A {\bf routing function}  ${\cal R}$ is an application associating a route  ${\cal R}(s,l)$ to each couple $(s,l) \in S \times L$ in $G$.
+      Moreover ${\cal R}$ satisfies the {\bf coherent routing} property: the intersection of two routes must be a path.
+
+      For simplicity, we assume that we have as many source nodes as we have leaves (${\cal S} = {\cal L})$.
+      A {\bf ${\cal R}$-matching} is a bijection $\rho:S\rightarrow L$ which associates to each $s_i \in \{s_0,...,s_{{\cal S}-1}\}$ 
+      a $l_i \in \{l_0,...,l_{{\cal L}-1}\}$.
+      A \rmatching defines a set $\{r_0, \ldots ,r_{{\cal L}-1}\}$ of ${\cal L}$ routes in ${\cal R}$ such that $\forall i\,, r_i = {\cal R}(s_i,l_i)$.
+
+      The quintuplet $N=(G,S,L,{\cal R},\rho)$ defines a \matchedgraph. We call $N^r$ the quintuplet $(G^r,S,L,{\cal R},\rho^r)$, 
+      where $\rho^r$ is the \rmatching obtained using the same routes, with inverted arcs.
+
+      \subsection{Slotted time Model}
+      \label{slottedtime}
+      In our model, the time is discrete. The unit of time is one slot. Two values are expressed in time slots: 
+      \enumerate
+      \item The emission time of a message by a node, the {\bf message length}, We denote by {\bf T} this time.
+      \item The time taken by a message to cross a link, the delay of an arc.
+
+      Let $P>0$ be an integer called {\bf period}. 
+      A {\bf $P$-periodic affectation} of $N$(a matched graph) consists in a set  ${\cal M}=(m_0, \ldots ,m_{{\cal L}-1})$
+      of ${\cal L}$ integers that we call {\bf offset}. 
+      Each period is divided in $P$ slots and the number $m_i$ represents the first slot number used by the route $r_i$ at its source.
+      We define the first time slot at which a message arrive at any vertex $v$ of the route by $$t(v,r_i) = m_i+\lambda(u,r_i) \mod P.$$
+
+      Let us call $[t(v,r_i)]_{T,P}$ the values of the time slots used by a route $r_i$ in a vertex $v$. 
+      Those values are forming a continuous set of values starting at $t(v,r_i) \mod P$ and ending at $t(v,r_i) + T \mod P$.
+      For a given instance, $P$ and T does not change at any moment, indeed, the size of the messages is the same for any route, and the period is also the same for any vertex.
+      So, since $P$ and T are fixed, we simplify the notation by $[t(v,r_i)]$.
+
+      A $P$-periodic affectation must have no {\bf collision} between two routes in $\rho$, that is $\forall r_i, r_j \in \rho, i \ne j$,
+      we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$
 
   \subsection{Problems}
-    Définition de PRA, et de PALL.
+
+    The application we address here by studying the problems defined above is the following. Consider a fronthaul network in which source nodes in $S$ represent BBU.
+    Each of the source nodes do a computation for its associated RRH represented by a leaf node in $L$.
+Consider a ${\cal R}$-matching $\rho$ of $S$ in $L$.
+Consider a leaf $l$, its dedicated source node $s$
+    and $R(l,s)$ the route from $l$ to $s$ in $R$. We consider a $P$-periodic affectation of N, and also another $P$-periodic affectation of $N^{r}$.
+    The periodic process is, for each route, the following one:
+    \begin{enumerate}
+    \item During each period of duration $P$, $l$ sends a message to its source $s=\rho(l)$, using its routes according to the $P$-periodic affectation of N. 
+    \item When a source $s=\rho(l)$ receive a message from $l$, it makes a computation. This computation time is the same for all sources.
+    \item After this computation time, $s$ sends a message to $l=\rho(l)$ according to the $P$-periodic affectation of $N^{r}$.
+    \end{enumerate}
+
+    \begin{center}
+    \fbox{\parbox{11cm}{
+    \begin{figure}[H]
+    \begin{center}
+    \scalebox{0.6}{
+    \begin{tikzpicture}
+      \SetGraphUnit{5}
+      \Vertex[x=0,y=0]{l3}
+      \Vertex[x=0,y=4]{l2}
+      \Vertex[x=0,y=8]{l1}
+
+      \Vertex[x=16,y=0]{s3}
+      \Vertex[x=16,y=4]{s2}
+      \Vertex[x=16,y=8]{s1}
+
+      \Vertex[x=4,y=4]{Switch 1}
+      \Vertex[x=12,y=4]{Switch 2}  
+      \tikzset{
+      EdgeStyle/.append style = {green} }
+      \Edge(s1)(Switch 2)
+      \Edge(Switch 1)(l1)
+
+      \tikzset{
+      EdgeStyle/.append style = {blue} }
+      \Edge(s2)(Switch 2)
+      \Edge(Switch 1)(l2)
+
+      \tikzset{
+      EdgeStyle/.append style = {red} }
+      \Edge(s3)(Switch 2)
+      \Edge(Switch 1)(l3)
+
+      \tikzset{
+      EdgeStyle/.append style = {black} }
+      \Edge(Switch 1)(Switch 2)
+
+      \draw[->,line width=1pt,green] (1,8) parabola bend (8,5) (15,7.5);
+      \node[draw,green] at (14,8) {Computation};
+      \draw[<-,line width=1pt,green] (1,8.5) parabola bend (8,5.5) (14,7.5);
+
+    \end{tikzpicture}
+    }
+    \end{center}
+    \caption{The periodic process of a message on a route in the fronthaul.}
+    \end{figure}
+
+    }}\end{center}
+
+    On source nodes, between the end of the computation time and the emission time of the message (given by the $P$-periodic affectation), there is a {\bf waiting time}. 
+    We define by $\omega: r \rightarrow \mathbb{N}$ the waiting time of a route $r$ in the ${\cal R}$-matching considered, i.e. the time during which the
+    message is ''sleeping``, waiting to be sent through the network.
+
+    We have to find two $P$-periodic affectations, one for the messages going from the RRH to the BBU, and another one for the answers going from BBU to the RRH.
+Those two $P$-periodic affectations have the same period $P$.
+    If the messages have to be buffered, we can only do it in sources nodes.
+    We define by $\theta$ the computation time required at the source node before sending an answer to its leaf node.
+
+    A {\bf TwoWayTrip} is, for a route, the full travel leaf-leaf, including the waiting time and the computation time.
+
+    Let us call $T (r)$ the time of a TwoWayTrip on a route $r$: $$ T (r) = 2\lambda (r) + \omega (r) + \theta$$
+
+    Since $\theta$ is the same on every route, we can simplify the model by removing $\theta$. Whether we want to consider it, we only have to lengthen all 
+    links before source nodes by $\frac{\theta}{2}$.
+
+    In our network application, since $P$ and the ${\cal R}-matching$ are given, we do not need to minimize $P$.
+    Therefore we want to optimize the time taken by the messages to do the TwoWayTrip in order to ensure a good level of quality of service.
+
+    A {\bf TwoWayTrip affectation} of $N$ is a set of pairs $ ((m_0,x_0),...,(m_{{\cal L}-1},x_{{\cal L}-1}))$ in which ${\cal M} = (m_0,...,m_{{\cal L}-1})$ 
+    is a $P$-periodic affectation of $N$,${\cal X} = (x_0,...,x_{{\cal L}-1})$ is a $P$-periodic affectation of $N^r$, and we define the waiting time of the route $r_i$ by:
+    $$ \omega_i = x_i - (m_i + \lambda(r_i)) \mod P .$$
+
+    Since ${\cal M}$ and ${\cal X}$ are some $P$-periodic affectation, they must have no collisions as we have already defined.
+
+    % In this topology, once the first central switch passed, there is no more possible collisions between two routes, so, 
+    % there is an unique vertex on each matched graph N or N$^r$ on which a collision is possible.
+    % We can simplify the notation of  $[t(u,r_i)]$ by $[t(i)]$, where $[t(i)]$ is the interval taken by the route $r_i$
+    % in the conflict point of the matched graph corresponding to the $P$-periodic affectation.
+
+    In the network problem, it is not allowed to have a route such that $T(r) > D$. This maximal value $D$ is called the {\bf deadline}.
+    Thus, the problem we want to solve is the following:\\
+
+    \noindent {\bf Periodic Assignment for Low Latency (PALL)}
+
+    \noindent {\bf Input:} Matched graph $N$, integer $P$, $ T_{max}$.
+
+    \noindent {\bf Question:} does there exist a TwoWayTrip affectation of $N$, such that $\forall r \in \rho$, $T(r) \le T_{max}$.
+
+    Once this decision problem established, we can consider two optimization problems, derived from the previous problem in which
+    we try to minimize different functions of $T(r)$.\\
+
+    \noindent {\bf Optimization goal 1:} minimizing max($T(r)$).
+
+    Minimizing the longest TwoWayTrip time of all routes allows us to win some time, and consequently some distance between the BBU and the RRH.\\
+
+    \noindent {\bf Optimization goal 2:} minimizing $\sum_{r \in \rho}  T(r)$ (equivalent to minimizing $\sum_{r \in \rho}  \omega(r)$.
+
+    By minimizing the sum of all the routes, we allow a better global Quality of Service through the network.\\
 
@@
   \subsection{NP-Hardness}
-    Etude de la complexité
+
+    \begin{theorem}
+    Problem PRA cannot be approximate within a factor $n^{1-o(1)}$ unless $\P = \NP$ even when the load is two
+    and $n$ is the number of vertices.
+    \end{theorem}
+
+    \begin{proof}
+    We reduce PRA to graph coloring. Let $G$ be a graph instance of the $k$-coloring problem. 
+    We define $H$ in the following way: for each vertex $v$ in $G$, there is a route $r_v$ in $H$.
+    Two routes $r_v$ and $r_u$ share an edge if and only if $(u,v)$ is an edge in $G$ and this edge is only in this two routes. 
+    We put weight inbetween shared edges in a route so that there is a delay $k$ between two such edges.
+
+    As in the previous proof, a $k$-coloring of $G$ gives a $k$-periodic schedule of $H$
+    and conversly. Therefore if we can approximate the value of PRA  within a factor $f$,
+    we could approximate the minimal number of colors needed to color a graph within a fator $f$, 
+    by doing the previous reduction for all possible $k$. The proof follows from the hardness of approximability
+    of finding a minimal coloring~\cite{zuckerman2006linear}.
+    \end{proof}
 

### 2017-01-24 article/article.tex
modele dominique

--- 2017-01-18 article/article.tex
@@
   \subsection{Definitions}
-    Définition du Modele, du 2 WayTrip
+
+	We consider a symmetric directed graph $G=(V,A)$ modeling a slotted network.
+Each arc  $(u,v)$ in $A$ is characterized by an integer delay $Dl(u,v) \geq 1$ representing the number of slots from $u$ to $v$ on this arc.
+Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$.
+
+      A route $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
+The {\em latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} Dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
+      The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
+A routing function $\cal R$ in $G$ associates a route from $u$ to $v$ for any couple of different vertices $<u,v>$ in $G$.\\
+
+      Let $\cal C$ be an {assignment} in $G$, i.e., set of couples of different vertices of $G$. We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $<u,v>$ in $\cal C$.
+
+   \subsection{Slotted time Model}
+      Consider now a positive integer $P$ called {\bf period}. A {\bf $P$-periodic affectation} of $\cal C$ in $(G,{\cal R})$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$
+      of $c$ integers that we call {\bf offset}, with $c$ the cardinal of $\cal C$.
+Indeed, time is consider as consecutive periods of $P$ slots each and the number $m_i$ represents the first slot number used by the route $r_i \in {\cal R}_{\cal C}$ at its source.
+      We define the first time slot at which a message reaches any vertex $v$ in this route by $$t(v,r_i) = m_i+\lambda(v,r_i) \mod P.$$
+
+      Let us call $[t(v,r_i)]$ the values of the time slots used by a route $r_i$ in such a vertex $v$. 
+      Those values are forming a continuous set of values starting at $t(v,r_i) \mod P$ and ending at $t(v,r_i) + \tau \mod P$.
+A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}_{\cal C}$, that is $\forall r_i, r_j \in {\cal R}_{\cal C}, i \ne j$, with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
+      we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$
 
    \subsection{Problems}
-    Définition de PRA, et de PALL.
+
+      The main theoretical problem we have to deal with in this context is the following.\\
+
+      \noindent {\bf Problem  Periodic Routes Assignment (PRA)}
+
+      \noindent {\bf Input:} graph $G=(V,A)$, set $\cal C$ of couples of vertices, routing function $\cal R$, integer $P$.
+
+      \noindent {\bf Question:} does there exist a $P$-periodic affectation of $\cal C$ in $(G,{\cal R})$?
+
+      We deal in next section with complexity of Problem PRA.\\
+
+      \begin{figure}[H]
+      \label{could-ran}
+      \begin{center}
+      % \begin{tabular}{cc}
+      \includegraphics[scale=0.5]{Total-latence.pdf}
+      \caption{Complete process for a leaf in $L$.}
+      \end{center}
+      \end{figure}
+      %\end{tabular}\newline
+
+      In the context of cloud-RAN applications, we consider here in digraph $G=(V,A)$ modeling the target network two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH.
+We consider a {\bf matching} defined as an application $\rho:S\rightarrow L$.
+We consider a $P$-periodic affectation $\cal M$, associating respectively integers $m_l$ and $m_{\overline l}$ to couples $(l,\rho(l))$ and $(\rho(l),l)$ for all $l \in L$.
+The process realized periodically (i.e.
+initiated in each window of size $P$) for each leaf $l \in L$ is the following one (see Figure \ref{cloud-ran}).
+First, a message of $\tau$ slots is sent from $l$ to $\rho(l)$ on ${\cal R}(l,\rho(l))$ at slot $m_l$ in the current window.
+After receiving this message, $\rho(l)$ computes it during a time equal to $\theta$ slots.
+Then, a message of $\tau$ slots containing the computed result is sent back from $\rho(l)$ to $l$ on ${\cal R}(\rho(l),l)$, at the first occurrence of  step $m_{\overline l}$ in a window (i.e., in the current window at the end of computation or the next one).
+We denote by $\omega(l)$ the {\bf waiting time}of $l$, i.e.,  the number of slots between the end of the computation time in $\rho(l)$ and the first occurrence of  step $m_{\overline l}$ in a window.
+Thus, the whole proccess time for $l$ is equal to
+      $$
+      PT(l)=\lambda({\cal R}(l,\rho(l)))+\theta+\omega(l)+\lambda({\cal R}(\rho(l),l)).
+      $$
+
+      Let us denote by ${\cal C}_{\rho}$ the set of couples $<l,\rho(l)>$ and $<\rho(l),l>$, for any $l \in L$.
+Consider a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$.
+The maximum process time of ${\cal M}$ is equal to equal to $MT({\cal M})=\max\limits_{l \in L} PT(l)$.
+Thus, we have to deal with the following problem.\\
+
+      \noindent {\bf Problem Periodic Assignment for Low Latency(PALL)}
+
+      \noindent {\bf Input:}  a digraph $G$, a matching $\rho$ of a set $S$ into a set $L$ in $G$, a routing function $\cal R$, a period $P$, an integer $T_{max}$.
+
+      \noindent {\bf Question:} does there exist  a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
+
+      The related optimisation problem we will focus on  consists in minimizing  $MT({\cal M})$.
+Note that in the context of cloud-RAN networks, we consider $P=1ms$, $\theta=2.6ms$ and $T_{max}$ must be less or equal to $3ms$.
 

### 2017-01-26 article/article.tex
code+modele

@@
 
-	We consider a symmetric directed graph $G=(V,A)$ modeling a slotted network.
-Each arc  $(u,v)$ in $A$ is characterized by an integer delay $Dl(u,v) \geq 1$ representing the number of slots from $u$ to $v$ on this arc.
-Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$.
-
-      A route $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
-The {\em latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} Dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
-      The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
+	We consider a symmetric directed graph $G=(V,A)$ modelling a slotted network.
+Each arc  $(u,v)$ in $A$ is characterised by an integer delay $Dl(u,v) \geq 1$ representing the number of slots taken by a signal to go from $u$ to $v$ using this arc.
+Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$.\\
+      A {\bf route} $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$. \\ 
+      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} Dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
+      The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.\\
       A routing function $\cal R$ in $G$ associates a route from $u$ to $v$ for any couple of different vertices $<u,v>$ in $G$.\\
-
       Let $\cal C$ be an {assignment} in $G$, i.e., set of couples of different vertices of $G$. We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $<u,v>$ in $\cal C$.
@@
    \subsection{Slotted time Model}
-      Consider now a positive integer $P$ called {\bf period}. A {\bf $P$-periodic affectation} of $\cal C$ in $(G,{\cal R})$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$
+      Consider now a positive integer $P$ called {\bf period}. A {\bf $P$-periodic affectation} of $\cal R_{\cal C}$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$
       of $c$ integers that we call {\bf offset}, with $c$ the cardinal of $\cal C$.
-Indeed, time is consider as consecutive periods of $P$ slots each and the number $m_i$ represents the first slot number used by the route $r_i \in {\cal R}_{\cal C}$ at its source.
+Indeed, time is considered as consecutive periods of $P$ slots, and the number $m_i$ represents the first slot number used by the route $r_i \in {\cal R}_{\cal C}$ at its source.
       We define the first time slot at which a message reaches any vertex $v$ in this route by $$t(v,r_i) = m_i+\lambda(v,r_i) \mod P.$$
@@
 
+  In this section, we consider a particular case of the model, in which for each couple <u,v> , the route is the same in both directions.
+This means that ${\cal R}(u,v)$ uses the same arc than ${\cal R}(v,u)$ in the opposite orientation.
   \subsection{Intro}

### 2017-01-26 code/code.c

@@ -1,0 +1,71 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <assert.h>
+#include <time.h>
+
+
+typedef struct graphe{
+	int N; //nombre de sommets
+	int ** matrice;//matrice d'adjacence pondérée
+}Graphe ;
+
+void affiche_matrice(Graphe g)
+{
+	for(int i=0;i<g.N;i++)
+	{
+		for(int j=0;j<g.N;j++)
+		{
+			printf("%3d ",g.matrice[i][j]);
+		}
+		printf("\n");
+	}
+	printf("\n");
+}
+
+
+//Déclare une matrice remplie de 0 de taille N*N
+int ** declare_matrice(int N)
+{
+	int ** matrice;
+	assert(matrice = malloc(sizeof(int*)*N));
+	for(int i = 0;i<N;i++)
+	{
+		assert(matrice[i]= calloc(N,sizeof(int)));
+	}
+	return matrice;
+}
+
+
+Graphe init_graphe(int N)
+{
+	Graphe g;
+	g.N = N;
+	g.matrice = declare_matrice(N);
+	return g;
+}
+
+//prends un graphe vide en argument et le transforme en etoile
+void graphe_etoile(Graphe g,int taille_liens)
+{
+	if(!g.N%2){printf("Impossible de générer une étoile avec un nombre pair de sommets\n");exit(5);}
+	int pivot = g.N/2;
+	int alea;
+	for(int i=0;i<g.N;i++)
+	{
+		alea = rand()%taille_liens;
+		g.matrice[pivot][i] = alea;
+		g.matrice[i][pivot] = alea;
+	}
+	g.matrice[pivot][pivot] = 0;
+}
+
+int main()
+{
+	srand(time(NULL));
+	Graphe g = init_graphe(5);
+	affiche_matrice(g);
+	graphe_etoile(g,700);
+	affiche_matrice(g);
+	free(g.matrice);
+	return 0;
+}

### 2017-01-30 article/article.tex
code algo

--- 2017-01-24 article/article.tex
@@
 
-	We consider a symmetric directed graph $G=(V,A)$ modeling a slotted network.
-Each arc  $(u,v)$ in $A$ is characterized by an integer delay $Dl(u,v) \geq 1$ representing the number of slots from $u$ to $v$ on this arc.
-Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$.
+	We consider a symmetric directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $Dl(u,v) \geq 1$ that we call the delay and
+	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$.
 
-      A route $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
-The {\em latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} Dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
+      A {\bf route} $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
+
+      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} Dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
       The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
-A routing function $\cal R$ in $G$ associates a route from $u$ to $v$ for any couple of different vertices $<u,v>$ in $G$.\\
 
-      Let $\cal C$ be an {assignment} in $G$, i.e., set of couples of different vertices of $G$. We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $<u,v>$ in $\cal C$.
+      A {\bf routing function} $\cal R$ in $G$ associates to each pair of vertices $(u,v)$ a route from $u$ to $v$.
+Let $\cal C$ be an {\bf assignment} in $G$, i.e., a set of couples of different vertices of $G$.
+We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $(u,v)$ in $\cal C$.
+\todo{Est-ce qu'on doit ajouter que le routage est cohérent ?}
 
    \subsection{Slotted time Model}
-      Consider now a positive integer $P$ called {\bf period}. A {\bf $P$-periodic affectation} of $\cal C$ in $(G,{\cal R})$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$
-      of $c$ integers that we call {\bf offset}, with $c$ the cardinal of $\cal C$.
-Indeed, time is consider as consecutive periods of $P$ slots each and the number $m_i$ represents the first slot number used by the route $r_i \in {\cal R}_{\cal C}$ at its source.
+      Consider now a positive integer $P$ called the {\bf period}. A {\bf $P$-periodic affectation} of $\cal R_{\cal C}$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$
+      of $c$ integers that we call {\bf offsets}, with $c$ the cardinal of $\cal C$.
+In our problem the messages we send in the network will be periodic of period $P$ and thus we consider slices of time of $P$ slots.
+      The number $m_i$ represents the number of the first slot used by the route $r_i \in {\cal R}_{\cal C}$ at its source in a period.
       We define the first time slot at which a message reaches any vertex $v$ in this route by $$t(v,r_i) = m_i+\lambda(v,r_i) \mod P.$$
 
-      Let us call $[t(v,r_i)]$ the values of the time slots used by a route $r_i$ in such a vertex $v$. 
-      Those values are forming a continuous set of values starting at $t(v,r_i) \mod P$ and ending at $t(v,r_i) + \tau \mod P$.
-A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}_{\cal C}$, that is $\forall r_i, r_j \in {\cal R}_{\cal C}, i \ne j$, with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
+      A message usually cannot be transported in a single time slot. We denote by $\tau$ the number 
+      of slots necessary to transmit a message. %remarque sur le fait qu'un message est porté par des temps consécutifs ?
+      Let us call $[t(v,r_i)]$ the index of the time slots used by a route $r_i$ at a vertex $v$ in a period $P$.
+Those values are forming a consecutive set of values starting at $t(v,r_i)$ and ending at $t(v,r_i) + \tau \mod P$.
+A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}_{\cal C}$, that is $\forall (r_i, r_j) \in {\cal R}_{\cal C}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
       we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$
@@
 
+   \todo{Mettre une phrase ou deux pour faire le lien avec le problème concret, plus facile  faire une fois l'intro écrite}
       The main theoretical problem we have to deal with in this context is the following.\\
@@
 
-      \noindent {\bf Input:} graph $G=(V,A)$, set $\cal C$ of couples of vertices, routing function $\cal R$, integer $P$.
+      \noindent {\bf Input:} a graph $G=(V,A)$, a set $\cal C$ of pair of vertices, a routing function $\cal R$ and an integer $P$.
 
@@
 
-      We deal in next section with complexity of Problem PRA.\\
+      We deal in next section with the complexity of the Problem PRA.\\
+% 
+%       \begin{figure}[H]
+%       \label{could-ran}
+%       \begin{center}
+%       % \begin{tabular}{cc}
+%       \includegraphics[scale=0.5]{Total-latence.pdf}
+%       \caption{Complete process for a leaf in $L$.}
+%       \end{center}
+%       \end{figure}
+%       %\end{tabular}\newline
 
-      \begin{figure}[H]
-      \label{could-ran}
-      \begin{center}
-      % \begin{tabular}{cc}
-      \includegraphics[scale=0.5]{Total-latence.pdf}
-      \caption{Complete process for a leaf in $L$.}
-      \end{center}
-      \end{figure}
-      %\end{tabular}\newline
+      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
+      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
+      We denote by $n$ the size of $S$ and $L$.
+      We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which defines two disjoint assignments ${\cal C}_1 = \{(l,\rho(l))\}_{l \in L}$ and ${\cal C}_2 = \{(s,\rho^{-1}(s))\}_{s \in S}$.
+Let ${\cal M} = (m_1,\dots, m_n)$ and ${\cal W} = (w_1,\dots, w_n)$ be two $P$-periodic affectations, of respectively ${\cal R}_{{\cal C}_1}$ and ${\cal R}_{{\cal C}_2}$.
 
-      In the context of cloud-RAN applications, we consider here in digraph $G=(V,A)$ modeling the target network two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH.
-We consider a {\bf matching} defined as an application $\rho:S\rightarrow L$.
-We consider a $P$-periodic affectation $\cal M$, associating respectively integers $m_l$ and $m_{\overline l}$ to couples $(l,\rho(l))$ and $(\rho(l),l)$ for all $l \in L$.
       The process realized periodically (i.e.
@@
 First, a message of $\tau$ slots is sent from $l$ to $\rho(l)$ on ${\cal R}(l,\rho(l))$ at slot $m_l$ in the current window.
-After receiving this message, $\rho(l)$ computes it during a time equal to $\theta$ slots.
-Then, a message of $\tau$ slots containing the computed result is sent back from $\rho(l)$ to $l$ on ${\cal R}(\rho(l),l)$, at the first occurrence of  step $m_{\overline l}$ in a window (i.e., in the current window at the end of computation or the next one).
-We denote by $\omega(l)$ the {\bf waiting time}of $l$, i.e.,  the number of slots between the end of the computation time in $\rho(l)$ and the first occurrence of  step $m_{\overline l}$ in a window.
+After receiving this message, $\rho(l)$ computes it during a time equal to $\theta$ slots.\todo{Je suis contre
+      le theta dans le modèle, car il ne set à rien. On peut dire par contre dans le blabla autour du modèle qu'on simule le temps de calcul par des arêtes plus longues}
+
+      Then, a message of $\tau$ slots containing the computed result is sent back from $\rho(l)$ to $l$ on ${\cal R}(\rho(l),l)$, after waiting for $w_l$ slots. 
+      %at the first occurrence of  step $m_{\overline l}$ in a window (i.e., in the current window at the end of computation or the next one).
+We denote by $\omega(l)$ the {\bf waiting time} of $l$, i.e.,  the number of slots between the end of the computation time in $\rho(l)$ and the first occurrence of  step $m_{\overline l}$ in a window.
       Thus, the whole proccess time for $l$ is equal to
       $$
-      PT(l)=\lambda({\cal R}(l,\rho(l)))+\theta+\omega(l)+\lambda({\cal R}(\rho(l),l)).
+      PT(l)=\lambda({\cal R}(l,\rho(l)))+\theta+w_l+\lambda({\cal R}(\rho(l),l)).
       $$
 
-      Let us denote by ${\cal C}_{\rho}$ the set of couples $<l,\rho(l)>$ and $<\rho(l),l>$, for any $l \in L$.
+      \todo{Il manque le fait qu'il n'y a pas de collisions ni à l'aller ni au retour.}
+% 	
+%       Let us denote by ${\cal C}_{\rho}$ the set of couples $<l,\rho(l)>$ and $<\rho(l),l>$, for any $l \in L$.
 Consider a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$.
-The maximum process time of ${\cal M}$ is equal to equal to $MT({\cal M})=\max\limits_{l \in L} PT(l)$.
-Thus, we have to deal with the following problem.\\
+    The {\bf maximum process time} of $({\cal M},{\cal W})$ is defined by $MT(({\cal M},{\cal W}))=\max\limits_{l \in L} PT(l)$. The problem we want to solve, is the following.
 
@@
 
-      \noindent {\bf Question:} does there exist  a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
+      \noindent {\bf Question:} does there exist a pair of $({\cal M},{\cal W})$ $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
 
-      The related optimisation problem we will focus on  consists in minimizing  $MT({\cal M})$.
+      %The related optimisation problem we will focus on  consists in minimizing  $MT({\cal M})$.
 Note that in the context of cloud-RAN networks, we consider $P=1ms$, $\theta=2.6ms$ and $T_{max}$ must be less or equal to $3ms$.
+      %cette remarque doit être dans la partie expérimentale
 
@@
 
+   \todo{Definition of the load. La preuve se réfère à la précédente qui n'a pas été retenue, il faut du coup tout expliquer.}
+
     \begin{theorem}
-    Problem PRA cannot be approximate within a factor $n^{1-o(1)}$ unless $\P = \NP$ even when the load is two
-    and $n$ is the number of vertices.
+    Problem PRA cannot be approximated within a factor $n^{1-o(1)}$ unless $\P = \NP$ even when the load is two
+    and $n$ is the number of pairs in the assignment.
     \end{theorem}
@@
     Two routes $r_v$ and $r_u$ share an edge if and only if $(u,v)$ is an edge in $G$ and this edge is only in this two routes. 
-    We put weight inbetween shared edges in a route so that there is a delay $k$ between two such edges.
+    We put a weight inbetween shared edges in a route so that there is a delay $k$ between two such edges.
 
@@
 
+  In this section, we consider a particular case of the model, in which for each $(u,v)$ , the route is the same in both directions.
+This means that ${\cal R}(u,v)$ uses the same arcs as ${\cal R}(v,u)$ in the opposite orientation.
   \subsection{Intro}
@@
     Résultats valables sur Topologie 1 avec nos paramètres
+    \todo{J'ai viré star affectation, car je pense qu'il n'y a rien à dire là dessus.}
 
   \subsection{No waiting times}
-    \subsubsection{Star affectation}
-      Définir star affectation en partant de PALL
     \subsubsection{Shortest-longest}

### 2017-01-30 code/code.c

@@ -62,7 +62,6 @@ void graphe_etoile(Graphe g,int taille_liens)
 //met toutes les cases du message a 1 dans la periode
 void ecrire_message_periode(int * p,int periode, int debut, int fin)
 {
-	printf("on écrit de %d à %d \n",debut,fin);
 	if(debut > fin)
 	{
 		for(int i=0;i<=fin;i++)p[i]=1;
@@ -80,44 +79,48 @@ void affiche_periode(int *p, int periode)
 	{
 		if(p[i]!=actuel)
 		{
-			if(actuel)printf("fin d'un message en %d\n\n",i);
-			else	  printf("debut d'un message en %d\n\n",i);
+			if(actuel)printf("-%d[ ",i);
+			else	  printf("[%d",i);
 			actuel = 1-actuel;
 		}
 	}
+	printf("\n");
 }
 int greedy_prime(Graphe g,int periode,int taille_message)
 {
 	if(!g.N%2){printf("G n'est peut être pas une étoile\n");exit(5);}
 	int nb_routes = g.N/2;
 	int routes[nb_routes];
+	int nb_slots = periode / taille_message;
+
 	for(int i=0;i<nb_routes;i++)
 	{
 		routes[i]=2*g.matrice[nb_routes][i+nb_routes+1];
 	}
 
-	int aller[periode], retour[periode];
-	for(int i=0;i<periode;i++){aller[i]=0;retour[i]=0;}
+	int aller[nb_slots], retour[periode];
+	for(int i=0;i<nb_slots;i++){aller[i]=0;}
+	for(int i=0;i<periode;i++){retour[i]=0;}
 
 
 	//Pour chaque route
 	for(int i=0;i<nb_routes;i++)
 	{
 		//On recherche le depart le plus petit
-		for(int j=0;j<periode-taille_message;j++)
+		for(int j=0;j<nb_slots;j++)
 		{
-			if(!aller[j] && !aller[(j+taille_message-1)%periode] && !retour[(j+routes[i])%periode] && !retour[(j+routes[i]+taille_message-1)%periode])
+			if(!aller[j] && !retour[(j*taille_message+routes[i])%periode] && !retour[(j*taille_message+routes[i]+taille_message-1)%periode])
 			{
 
-				ecrire_message_periode(aller,periode,j,(j+taille_message-1)%periode);
-				ecrire_message_periode(retour,periode,(j+routes[i])%periode,(j+routes[i]+taille_message-1)%periode);
[…]

### 2017-01-31 article/article.tex
modele clean

@@
 
-\section{Model, Problems}
+\section{Model}
 
@@
 We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $(u,v)$ in $\cal C$.
-\todo{Est-ce qu'on doit ajouter que le routage est cohérent ?}
+\todo{Si on s'en sert, ajouter ici que le routage est cohérent.}
 
    \subsection{Slotted time Model}
-      Consider now a positive integer $P$ called the {\bf period}. A {\bf $P$-periodic affectation} of $\cal R_{\cal C}$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$
-      of $c$ integers that we call {\bf offsets}, with $c$ the cardinal of $\cal C$.
-In our problem the messages we send in the network will be periodic of period $P$ and thus we consider slices of time of $P$ slots.
-      The number $m_i$ represents the number of the first slot used by the route $r_i \in {\cal R}_{\cal C}$ at its source in a period.
-      We define the first time slot at which a message reaches any vertex $v$ in this route by $$t(v,r_i) = m_i+\lambda(v,r_i) \mod P.$$
+      Consider now a positive integer $P$ called the {\bf period}.
+In our problem the messages we send in the network will be periodic of period $P$ and thus we consider slices of time of $P$ discrete slots.
+Assume we send a message at the source of the route $r$,
+      at the time slot $m$ in the first period, then a message will be sent at time $m$ at each new period.
+We define the first time slot at which a message reaches a vertex $v$ in this route by $t(v,r) = m + \lambda(v,r) \mod P$.
 
       A message usually cannot be transported in a single time slot. We denote by $\tau$ the number 
-      of slots necessary to transmit a message. %remarque sur le fait qu'un message est porté par des temps consécutifs ?
-      Let us call $[t(v,r_i)]$ the index of the time slots used by a route $r_i$ at a vertex $v$ in a period $P$.
-Those values are forming a consecutive set of values starting at $t(v,r_i)$ and ending at $t(v,r_i) + \tau \mod P$.
+      of consecutive slots necessary to transmit a message.
+Let us call $[t(v,r)]$ the set of time slots used by $r$ at a vertex $v$ in a period $P$, that is $[t(v,r)] = \{t(v,r) + i \mod P \mid 0 \leq i \leq \tau \}$.
+
+      A {\bf $P$-periodic affectation} of $\cal R_{\cal C}$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $c$ integers that we call {\bf offsets}, with $c$ the cardinal of the assignment $\cal C$.
+The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in {\cal R}_{\cal C}$ at its source.
       A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}_{\cal C}$, that is $\forall (r_i, r_j) \in {\cal R}_{\cal C}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
@@
 
-   \todo{Mettre une phrase ou deux pour faire le lien avec le problème concret, plus facile  faire une fois l'intro écrite}
       The main theoretical problem we have to deal with in this context is the following.\\
@@
 
-      We deal in next section with the complexity of the Problem PRA.\\
+      We will prove in Sec.~\ref{sec:complexity} that the Problem PRA is $\NP$-complete, even in restricted settings.
+      In fact, even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.\\
 % 
@@
       We denote by $n$ the size of $S$ and $L$.
-      We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which defines two disjoint assignments ${\cal C}_1 = \{(l,\rho(l))\}_{l \in L}$ and ${\cal C}_2 = \{(s,\rho^{-1}(s))\}_{s \in S}$.
-Let ${\cal M} = (m_1,\dots, m_n)$ and ${\cal W} = (w_1,\dots, w_n)$ be two $P$-periodic affectations, of respectively ${\cal R}_{{\cal C}_1}$ and ${\cal R}_{{\cal C}_2}$.
+We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH.
+Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$.
+Let consider a $P$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to
+      $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.
 
-      The process realized periodically (i.e.
-initiated in each window of size $P$) for each leaf $l \in L$ is the following one (see Figure \ref{cloud-ran}).
-First, a message of $\tau$ slots is sent from $l$ to $\rho(l)$ on ${\cal R}(l,\rho(l))$ at slot $m_l$ in the current window.
-After receiving this message, $\rho(l)$ computes it during a time equal to $\theta$ slots.\todo{Je suis contre
-      le theta dans le modèle, car il ne set à rien. On peut dire par contre dans le blabla autour du modèle qu'on simule le temps de calcul par des arêtes plus longues}
+      This affectation represents the following process: first a message is sent in $l$, through the route $r_l$, at time $m_l$.
+      This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$. It is then sent back to $l$ at time $\bar{m_l}$,
+      which is in the same period if $m_{\rho(l)} > t(\rho(l),r_l)$ otherwise it is in the next. The time between the arrival of
+      the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
+      When a BBU receives a message, it must compute the answer before sending it back to the BBU. This time is taken into account
+      in the last arc leading to the BBU and thus we need not to consider it explicitely in our model.
 
-      Then, a message of $\tau$ slots containing the computed result is sent back from $\rho(l)$ to $l$ on ${\cal R}(\rho(l),l)$, after waiting for $w_l$ slots. 
-      %at the first occurrence of  step $m_{\overline l}$ in a window (i.e., in the current window at the end of computation or the next one).
-We denote by $\omega(l)$ the {\bf waiting time} of $l$, i.e.,  the number of slots between the end of the computation time in $\rho(l)$ and the first occurrence of  step $m_{\overline l}$ in a window.
-      Thus, the whole proccess time for $l$ is equal to
+      Thus, the whole proccess time for a vertex $l$ is equal to
       $$
-      PT(l)=\lambda({\cal R}(l,\rho(l)))+\theta+w_l+\lambda({\cal R}(\rho(l),l)).
+      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{\rho(l)}).
       $$
 
-      \todo{Il manque le fait qu'il n'y a pas de collisions ni à l'aller ni au retour.}
-% 	
-%       Let us denote by ${\cal C}_{\rho}$ the set of couples $<l,\rho(l)>$ and $<\rho(l),l>$, for any $l \in L$.
-Consider a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$.
-    The {\bf maximum process time} of $({\cal M},{\cal W})$ is defined by $MT(({\cal M},{\cal W}))=\max\limits_{l \in L} PT(l)$. The problem we want to solve, is the following.
+    The {\bf maximum process time} of the $P$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.
 
@@
 
-      \noindent {\bf Input:}  a digraph $G$, a matching $\rho$ of a set $S$ into a set $L$ in $G$, a routing function $\cal R$, a period $P$, an integer $T_{max}$.
+      \noindent {\bf Input:}  a digraph $G$, a matching $\rho$ from $L$ to $S$ two disjoint set of vertices of $G$, a routing function $\cal R$, a period $P$, an integer $T_{max}$.
 
-      \noindent {\bf Question:} does there exist a pair of $({\cal M},{\cal W})$ $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
+      \noindent {\bf Question:} does there exist a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
 
@@
 
-\section{PRA Solving}
-
+\section{Solving PRA}
+  \label{sec:complexity}
   \subsection{NP-Hardness}

### 2017-01-31 code/code.c
code prime vs 3NT

@@ -86,13 +86,15 @@ void affiche_periode(int *p, int periode)
 	}
 	printf("\n");
 }
-int greedy_prime(Graphe g,int periode,int taille_message)
+
+//retourne -1 si la periode donnée ne donne pas de solutions, la taille de la periode sinon
+int algo_3NT(Graphe g,int periode,int taille_message)
 {
 	if(!g.N%2){printf("G n'est peut être pas une étoile\n");exit(5);}
 	int nb_routes = g.N/2;
 	int routes[nb_routes];
 	int nb_slots = periode / taille_message;
-
+	int assigned = 0;
 	for(int i=0;i<nb_routes;i++)
 	{
 		routes[i]=2*g.matrice[nb_routes][i+nb_routes+1];
@@ -114,26 +116,119 @@ int greedy_prime(Graphe g,int periode,int taille_message)
 
 				ecrire_message_periode(aller,nb_routes,j,j);
 				ecrire_message_periode(retour,periode,(j*taille_message+routes[i])%periode,(j*taille_message+routes[i]+taille_message-1)%periode);
+				assigned = 1;
 				break;
 			}
 		}
-
+		if(!assigned)//Si une route n'a pas trouvé de départ possible, c'est que la fenètre est trop petite.
+			return -1;
+		assigned = 0;
 	}
-	printf("aller\n");
-	affiche_periode(aller,nb_slots);
-	printf("retour\n");
-	affiche_periode(retour,periode);
-	return 1;
+	return periode;
 }
 
+int linear_3NT(Graphe g,int taille_message)
+{
+	int result;
+	for(int i =0;i<taille_message*(g.N/2)*3;i++)
+	{
+		result = algo_3NT(g,i,taille_message);
+		if(result != -1)
+		{
+			return result;
+		}
+	}
+	return -1;
+}
+
+
+//retourne -1 si la periode donnée ne donne pas de solutions, la taille de la periode sinon
+int algo_prime(Graphe g,int periode,int taille_message)
+{
+	if(!g.N%2){printf("G n'est peut être pas une étoile\n");exit(5);}
+	int nb_routes = g.N/2;
+	int routes[nb_routes];
+	int assigned = 0;
+	for(int i=0;i<nb_routes;i++)
+	{
+		routes[i]=2*g.matrice[nb_routes][i+nb_routes+1];
+	}
+
+	int aller[periode], retour[periode];
[…]

### 2017-02-01 article/article.tex
code prime vs 3NT
merge

@@
 \newtheorem{theorem}{Theorem}
-\newcommand{\reporttitle}{Contention management for Deterministic Networking}     % Titre
-\newcommand{\reportauthor}{Maël \textsc{Guiraud }} % Auteur
-\newcommand{\reportsubject}{Master Thesis} 
-\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
-\setlength{\parskip}{1ex} % Espace entre les paragraphes
+\newtheorem{fact}{Fact}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{definition}{Definition}
+\newtheorem{corollary}{Corollary}
 
@@
 
-   \todo{Definition of the load. La preuve se réfère à la précédente qui n'a pas été retenue, il faut du coup tout expliquer.}
+Consider an instance of Problem PRA, i.e., a digraph $G=(V,A)$, an assignment $\cal C$, a routing function $\cal R$ and a period $P$. 
+The \emph{conflict depth} of an assignment $\cal C$ is the  number of arcs crossed by at least two routes in ${\cal R}_{\cal C}$; in other words it is the number of potential conflicts between these routes.
+The \emph{load} of  an assignment is the maximal number of routes sharing a same arc (i.e., the congestion of this arc).
+It is clear that a $P$-periodic affectation must satisfy that $P$ is larger or equal to the load.
+
+We give two alternate proofs that PRA is $\NP$-complete.
+The first one works for conflict depth $2$ and is minimal in this regards since we later prove that for conflict depth one,
+it is easy to solve PRA. The second one reduces the problem to graph coloring and implies inapproximability. \\
+
+ \begin{proposition}
+Problem PRA is $\NP$-complete, for a routing with conflict depth two.
+\end{proposition}
+ \begin{proof}
+  Let $H=(V,E)$ be a graph and $d$ its maximal degree. We want to determine whether $H$ is edge-colorable
+  with $d$ or $d+1$ colors. We reduce this edge coloring problem to PRA. We define  from $H$ an instance $G,{\cal C}, {\cal R}, P$ as follows. For each 
+  $v \in V$ there are two vertices in $G$  connected by an arc $(v_1,v_2)$ and none of these arcs are incident. The delay of these arcs is equal to $1$.
+  The set $\cal C$ is made of couples of vertices $<s_{u,v}, l_{u,v}>$ for each edge $[u,v]$ in $H$ and the routes associated is ${\cal R} =s_{u,v},u_1,u_2,v_1,v_2,l_{u,v}$.
+The delays of arcs $(s_{u,v},u_1)$ and $(v_2,l_{u,v})$ are equal to $d(d+1)-1$.
+
+  Let $\phi$ be an edge coloring with $k$ colors of $H$. We can build a $k$-periodic affectation of $\cal C$ in $(G,{\cal R})$
+  by assigning to the source $s_{u,v}$ of each route an offset  of $\phi(s_{u,v})$. Indeed, 
+  if two routes $r_1$ and $r_2$ in ${\cal R}_{\cal C}$ share the same edge, say $(v_1,v_2)$ then they represent two edges $e_1$ and $e_2$ of $H$ incident  
+  to the vertex $v$. Therefore $\lambda(v_1,r_1) = \phi(e_1) \mod k$ because the delays of the edges before $v_1$ sum to $d(d+1)$ or 
+  $2(d(d+1))$ which are equal to $0$ modulo $k$ since $k=d$ or $k=d+1$. Thus $\lambda(v_1,r_1) - \lambda(v_1,r_2) \mod k = \phi(e_1) - \phi(e_2) \mod k$
+  and $\lambda(v_1,r_1) - \lambda(v_1,r_2) \mod k > 0$ since $\phi(e_1) \neq \phi(e_2) $.
+
+  Now consider a $k$-periodic affectation of $\cal C$ in $(G,{\cal R})$ . For each $[u,v]$ in $H$, we define $\phi(u,v)$ to be the offset of the route
+  beginning at $s_{u,v}$ in ${\cal R}_{\cal C}$. For the same reasons as in the last paragraph, $\phi$ is an edge coloring with $k$ colors.
+  Therefore we have reduced edge coloring which is $\NP$-hard~\cite{holyer1981np} to PRA which concludes the proof. 
+ \end{proof}
+Solving Problem PALL implies to solve PRA for an assignment ${\cal C}_{\rho}$ defined on $S$ and $L$ (see Section 2). Thus, we have the following corollary :
+
+\begin{corollary}
+Problem PALL is NP-Hard.
+\end{corollary}
+
+As another corollary of the previous proposition,  given $G$, $\cal R$, $P$ and two disjoint subsets $S$ and $L$ in $G$, the problem of  knowing if there is a matching $\rho$  from $L$ in $S$ such that the answer to problem PRA for instance $G,{\cal C_{\rho}},{\cal R}, P$ is  $\NP$-hard since checking a potential feasible solution for this problem implies to solve PRA.\\
+
+Consider now MIN-PRA as the minimisation problem related to PRA, consisting in minimizing the peril $P$.
 
 \begin{theorem}
-    Problem PRA cannot be approximated within a factor $n^{1-o(1)}$ unless $\P = \NP$ even when the load is two
-    and $n$ is the number of pairs in the assignment.
+ Problem MIN-PRA cannot be approximate within a factor $n^{1-o(1)}$ unless $\P = \NP$ even when the load is two
+ and $n$ is the number of vertices.
 \end{theorem}
@@
 \begin{proof}
-    We reduce PRA to graph coloring. Let $G$ be a graph instance of the $k$-coloring problem. 
-    We define $H$ in the following way: for each vertex $v$ in $G$, there is a route $r_v$ in $H$.
-    Two routes $r_v$ and $r_u$ share an edge if and only if $(u,v)$ is an edge in $G$ and this edge is only in this two routes. 
-    We put a weight inbetween shared edges in a route so that there is a delay $k$ between two such edges.
+ We reduce PRA to graph coloring. Let $H$ be a graph instance of the $k$-coloring problem. 
+ We define $G$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in $G$.
+ Two routes $r_v$ and $r_u$ share an arc if and only if $[u,v]$ is an edge in $H$; this arc is the only one shared by these two routes.
+We put delays inbetween shared arcs in a route so that there is a delay $k$ between two such arcs.
 
-    As in the previous proof, a $k$-coloring of $G$ gives a $k$-periodic schedule of $H$
-    and conversly. Therefore if we can approximate the value of PRA  within a factor $f$,
+ As in the previous proof, a $k$-coloring of $H$ gives a $k$-periodic affectation in $G$
+ and conversely. Therefore if we can approximate the minimum value of $P$  within a factor $f$,
  we could approximate the minimal number of colors needed to color a graph within a fator $f$, 
@@
 \end{proof}
+
+In particular, this reduction shows that even with small maximal load, the 
+minimal period can be large.
 

### 2017-02-01 article/article.tex
algo ecrit

--- 2017-01-31 article/article.tex
@@
 
+      \begin{center}
+
+      \fbox{\parbox{12cm}{
+      Notice that the notion of $P$-periodic affectation \textbf{is not monotone} with regard to $P$. 
+      Indeed, consider messages of size 1, we can build a graph, with $c$ routes $r_i \in {\cal R}_{\cal C}, i < c$ which all intersect two by two and
+      such that if $r_i$ and $r_j$ have $v$ as first common vertex we have $\lambda(v,r_i) - \lambda(v,r_j)=1$.
+      Therefore there is a $2$-periodic affectation by setting all $m_i$ to $0$.
+
+      A {\bf conflict graph} represents the collision between the routes of $ {\cal R}_{\cal C}$.
+The vertices of a conflict graph $G = (V,E)$ are the routes of $ {\cal R}_{\cal C}$, and there is an edge between two vertices if and only if there is a common arc between the two routes in $ {\cal R}_{\cal C}$.
+
+      Given $u$ and $v$ two vertices of the conflict graph, corresponding to two routes colliding in $ {\cal R}_{\cal C}$.
+The weight of an edge, $w(u,v)$, is the absolute value of the difference between the distance of the two routes between their respective source node and the collision point.
+
+      A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.
+
+      \begin{tabular}{cc}
+      \includegraphics[scale=0.5]{Fig5.pdf} & \includegraphics[scale=1]{Fig7.pdf}\\
+      $\lambda(v,r_i) - \lambda(v,r_j)=1$ & Conflict graph\\
+      \end{tabular}\newline
+
+      On the other hand if we set all $\lambda(v,r_i) - \lambda(v,r_j)=P$, there is no $P$-periodic affectation if $P<l$.
+
+      \begin{tabular}{cc}
+      \includegraphics[scale=0.5]{Fig6.pdf} & \includegraphics[scale=1]{Fig8.pdf}\\
+      $\lambda(v,r_i) - \lambda(v,r_j)=2$ & Conflict graph\\
+      \end{tabular}\newline
+      \begin{center}
+      Here for P=2, there is no $P$-periodic affectation.
+      \end{center}
+
+      Therefore if we choose and odd value for $P$ and $l=P+1$, there is no $P$-periodic affectation but modulo $2$ all $\lambda(v,r_i) - \lambda(v,r_j)$
+      are equal to one thus we have a $2$-periodic affectation. 
+      }}
+
+      \end{center}
    \subsection{Problems}
@@
 
+    \scalebox{0.5}{
+
+    \begin{tikzpicture}
+
+    \tikzset{
+      LabelStyle/.style = { rectangle, rounded corners, draw,
+			  font = \bfseries },
+      EdgeStyle/.append style = {->} }
+      \SetGraphUnit{5}
+      \Vertex[x=4,y=2]{s3}
+      \Vertex[x=0,y=4]{s2}
+      \Vertex[x=0,y=6]{s1}
+
+      \Vertex[x=12,y=3]{l3}
+      \Vertex[x=14,y=4]{l2}
+      \Vertex[x=10,y=2]{l1}
+      \tikzstyle{VertexStyle}=[shape = circle, draw, minimum size = 20pt]
+	\tikzset{
+      VertexStyle/.append style = {blue} }
+	\Vertex[x=-8,y=3]{1}
+	      \tikzset{
+      VertexStyle/.append style = {green} }
+	  \Vertex[x=-7,y=5]{2}
+
+	    \tikzset{
+      VertexStyle/.append style = {red} }
+	  \Vertex[x=-6,y=4]{3}
+		\tikzset{
+      VertexStyle/.append style = {black} }
+
+      \SetVertexNoLabel
+      \Vertex[x=2,y=5]{A}
+      \Vertex[x=4,y=5]{B}
+      \Vertex[x=10,y=5]{C}
+      \Vertex[x=12,y=5]{D}
+      \Vertex[x=6,y=3]{E}
+      \Vertex[x=8,y=3]{F}
+      \tikzset{
+      EdgeStyle/.append style = {green} }
+      \Edge[label = 3](s2)(A)
+      \Edge(A)(B)
+      \Edge(B)(C)
+      \Edge(C)(D)
+      \Edge(D)(l2)
+
+      \tikzset{
+      EdgeStyle/.append style = {red} }
+      \Edge[label = 1](s3)(E)
+      \Edge(E)(F)
+      \Edge(F)(l3) 
+	\tikzset{
+      EdgeStyle/.append style = {blue} }
+      \Edge[label = 1](s1)(A)
+      \Edge[label = 1](A)(B)
+      \Edge[label = 1](B)(E)
+      \Edge(E)(F)
+      \Edge(F)(l1)
+
+	\tikzset{
+      EdgeStyle/.append style = {black,-} }
+
+      \Edge(1)(2)
+      \Edge(1)(3)
+    \node (1) at (-3,4){\Huge $\rightarrow$};
+    \end{tikzpicture}
+
+    }\\
+
   \subsection{MIN-PRA}
@@
       \paragraph{Period}
+    \subsubsection{Greedy Algorithm with higher bound}
+
+	\begin{algorithm}[H]
+	\caption{Greedy with Higher bound Period(GHP)}
+	\begin{algorithmic}
+	\REQUIRE ${\cal R}_{\cal C}$, period $P$
+	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
+	\STATE $P1[P]$ slots of size $\tau$ in first way period.
+	\STATE $P2[P]$ slots  of size $\tau$ in back way period.
+	\FORALL{route i in ${\cal R}_{\cal C}$ }
+
+	\FORALL{slot j in P1}
+
+	\IF{$P1[j]$ is free, and the corresponding slot(s) in P2 are free}
+
+	\STATE $o_i \leftarrow j$
+	\ENDIF
+
+	\IF{No intervals are found for i}
+	\STATE return FAILURE
+	\ENDIF
+	\ENDFOR
+
+	\ENDFOR
+
+	\end{algorithmic}
+	\end{algorithm}
+      \paragraph{Period}
+	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
+	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots.
+Let us call {\em forward period} the period in the central node when the messages goes to RRH to BBU, and {\em backward period} the period when the messages comes back in the other way.
+Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
+	\todo{Dessin qui illustre ça}\\
+	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period.
+Those $3.c - k$ gives us $3.c - k$ possible slots in the backward periods.\\
+	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period.
+Since $k<c$,  $2k < 3.c - k$, thus using the pigeonhole principle, there is at least one free slot in the backward period for the new message.
+
     \subsubsection{Exhaustive generation}

### 2017-02-01 article/article.tex

--- 2017-01-31 article/article.tex
@@
 
-	We consider a symmetric directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $Dl(u,v) \geq 1$ that we call the delay and
+	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $Dl(u,v) \geq 1$ that we call the delay and
 	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$.
@@
 \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}
+
+      \todo{Doit on définir un objet graphe + routes + assignement pour ensuite simplifier l'écriture}
 
@@
       This affectation represents the following process: first a message is sent in $l$, through the route $r_l$, at time $m_l$.
-      This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$. It is then sent back to $l$ at time $\bar{m_l}$,
-      which is in the same period if $m_{\rho(l)} > t(\rho(l),r_l)$ otherwise it is in the next. The time between the arrival of
-      the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
-      When a BBU receives a message, it must compute the answer before sending it back to the BBU. This time is taken into account
+      This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$.
+It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period.
+The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
+      When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
       in the last arc leading to the BBU and thus we need not to consider it explicitely in our model.
@@
 
-   \todo{Definition of the load. La preuve se réfère à la précédente qui n'a pas été retenue, il faut du coup tout expliquer.}
+ In this section we assume that the size of a message $\tau$ is equal to one, which implies hardness of PRA and PALL for all $\tau$. 
+Consider an instance of Problem PRA, i.e., a digraph $G=(V,A)$, an assignment $\cal C$, a routing function $\cal R$ and a period $P$. 
+The {\bf conflict depth} of a route is the number of other routes which share an edge with it. 
+The conflict depth of an assignment $\cal C$ is the maximum of the conflict depth of the routes in ${\cal R}_{\cal C}$.
+The {\bf load} of an assignment is the maximal number of routes sharing the same arc.
+It is clear that a $P$-periodic affectation must satisfy that $P$ is larger or equal to the load.
+
+We give two alternate proofs that PRA is $\NP$-complete.
+The first one works for conflict depth $2$ and is minimal in this regards since we later prove that for conflict depth one,
+it is easy to solve PRA. The second one reduces the problem to graph coloring and implies inapproximability when one tries to minimize the parameter $P$. \\
+
+ \begin{proposition}
+Problem PRA is $\NP$-complete, when the routing is of conflict depth two.
+\end{proposition}
+ \begin{proof}
+ The problem $PRA$ is in $\NP$ since given an offfset for each route in an affectation, it is easy to check in linear time in the number of edges whether there are collisions.
+
+  Let $H=(V,E)$ be a graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is edge-colorable
+  with $d$ or $d+1$ colors.
+The edge coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness.
+We define from $H$ an instance of PRA as follows.
+The graph $G$ has for vertices $V'= \{ v_1, v_2 \mid v \in V  \} \cup \{ l_{u,v}, s_{u,v} \mid (u,v) \in E \}$ that is two vertices for each vertex and for each edge of $H$.
+  Let $A$ bet the set of arcs of $G$, defined by 
+  $$A = \{(v_1,v_2) \mid v\in V\} \cup \{(u_2,v_1)\mid u \neq v \in V^2\} \cup \{(l_{u,v},u_1),(v_2,s_{u,v}) \mid (u,v) \in E \}. $$
+  All these arcs are of weigth $0$. 
+  For each edge $(u,v) \in E$, the is a route $r_{u,v} = s_{u,v},u_1,u_2,v_1,v_2,l_{u,v}$ in ${\cal R}$.  
+  The affectation ${\cal C}$ is the set of pair of vertices $(s_{u,v}, l_{u,v})$.
+
+  Observe that the existence of a $d$-coloring of $H$ is equivalent to the existence of a $d$-periodic affectation
+  for $(G,{\cal R},{\cal C})$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its edges by the integers
+  in $\{0,\dots,d-1\}$ and we have a correspondance between a $d$-coloring of $H$ and offests for the routes of $(G,{\cal R},{\cal C})$.
+  By contruction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent edges have
+  the same color. Therefore we have reduced edge coloring to PRA which concludes the proof. 
+ \end{proof}
+ \todo{Faire un dessin d'illustration ?}
+
+ Remark that we have used zero weigth in the proof. If the weigths must be strictly positive, which makes more sense in our model since
+ we model the latency of physical links, it is easy to adapt the proof.
+We just have to set them so that in any route the delay at $u_1$ is equal to $d$ and thus equal to $0$ modulo $d$.
+We now lift this hardness result to the problem PALL.
+
+\begin{corollary}
+Problem PALL is $\NP$-complete for routing of conflict depth two.
+\end{corollary}
+\begin{proof}
+ We consider $(G,{\cal R},{\cal C},P)$ an instance of $PRA$ such that no element appears both in the first and second position in a pair of ${\cal C}$.
+Remark that this condition is satisfied in the previous proof, which makes the problem $PRA$ restricted to these instances $\NP$-complete.
+ Let us define $T_{max} = 2 \times \max_{r \in {\cal R}} \lambda(r) + P$. We define $\rho$ as the function which maps 
+ $u$ to $v$ when $(u,v) \in {\cal C}$. The instance $(G,{\cal R},\rho,P,T_{max})$ is in PALL if and only if $(G,{\cal R},{\cal C},P)$
+ is in $PRA$.
+Indeed the waiting time of each route is by definition less than $P$ and thus the maximal process time less than $T_{max}$.
+Therefore the fact that $(G,{\cal R},\rho,P,T_{max})$ is in PALL is equivalent to the existence of a $P$-periodic assignment of ${\cal C}_{\rho}$ which is equal to ${\cal C}$.
+\end{proof}
+% 
+% 
+% As another corollary of the previous proposition,  given $G$, $\cal R$, $P$ and two disjoint subsets $S$ and $L$ in $G$, the problem of  knowing if there is a matching $\rho$  from $L$ in $S$ such that the answer to problem PRA for instance $G,{\cal C_{\rho}},{\cal R}, P$ is  $\NP$-hard since checking a potential feasible solution for this problem implies to solve PRA.\\
+
+Let MIN-PRA be the problem, given a graph, a routing and an affectation, to find the minimal period $P$ such that there is a $P$-periodic affectation.
 
 \begin{theorem}
-    Problem PRA cannot be approximated within a factor $n^{1-o(1)}$ unless $\P = \NP$ even when the load is two
-    and $n$ is the number of pairs in the assignment.
+ The problem MIN-PRA cannot be approximated in polynomial time within a factor $n^{1-o(1)}$, with $n$ the number of routes, unless $\P = \NP$ even when the load is two.
 \end{theorem}
@@
 \begin{proof}
-    We reduce PRA to graph coloring. Let $G$ be a graph instance of the $k$-coloring problem. 
-    We define $H$ in the following way: for each vertex $v$ in $G$, there is a route $r_v$ in $H$.
-    Two routes $r_v$ and $r_u$ share an edge if and only if $(u,v)$ is an edge in $G$ and this edge is only in this two routes. 
-    We put a weight inbetween shared edges in a route so that there is a delay $k$ between two such edges.
+ We reduce graph coloring to PRA. Let $H$ be a graph instance of the $k$-coloring problem. 
+ We define $G$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in $G$.
+ Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an edge in $H$; this arc is the only one shared by these two routes.   
+ All arcs are of delay $0$.
 
-    As in the previous proof, a $k$-coloring of $G$ gives a $k$-periodic schedule of $H$
-    and conversly. Therefore if we can approximate the value of PRA  within a factor $f$,
-    we could approximate the minimal number of colors needed to color a graph within a fator $f$, 
-    by doing the previous reduction for all possible $k$. The proof follows from the hardness of approximability
-    of finding a minimal coloring~\cite{zuckerman2006linear}.
+ Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $k$-periodic affectation in $G$, 
+ by converting an offset of a route into a color of a vertex and reciprocally. Therefore if we can approximate the minimum value of $P$ within a factor $f$,
+ we could approximate the minimal number of colors needed to color a graph within a factor $f$, by doing the previous reduction for all possible $k$.
+The proof follows from the hardness of approximability of finding a minimal coloring~\cite{zuckerman2006linear}.
 \end{proof}
 
+In particular, this reduction shows that even with small maximal load, the 
+minimal period can be large.
+
   \subsection{MIN-PRA}
-    Exemple de cas simple
+    Exemple de cas polynomiaux
 
@@
       \paragraph{Period}
+    \subsubsection{Greedy Algorithm with higher bound}
+      \paragraph{Algo}
+	Todo
+      \paragraph{Period}
+	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.N$, if we have N routes.\\
+	Suppose that we have a period of $3.\tau.N$ slots, divided in $\tau$ macro-slots.
     \subsubsection{Exhaustive generation}

### 2017-02-01 article/article.tex

@@
 
+    \scalebox{0.5}{
+
+    \begin{tikzpicture}
+
+    \tikzset{
+      LabelStyle/.style = { rectangle, rounded corners, draw,
+			  font = \bfseries },
+      EdgeStyle/.append style = {->} }
+      \SetGraphUnit{5}
+      \Vertex[x=4,y=2]{s3}
+      \Vertex[x=0,y=4]{s2}
+      \Vertex[x=0,y=6]{s1}
+
+      \Vertex[x=12,y=3]{l3}
+      \Vertex[x=14,y=4]{l2}
+      \Vertex[x=10,y=2]{l1}
+      \tikzstyle{VertexStyle}=[shape = circle, draw, minimum size = 20pt]
+	\tikzset{
+      VertexStyle/.append style = {blue} }
+	\Vertex[x=-8,y=3]{1}
+	      \tikzset{
+      VertexStyle/.append style = {green} }
+	  \Vertex[x=-7,y=5]{2}
+
+	    \tikzset{
+      VertexStyle/.append style = {red} }
+	  \Vertex[x=-6,y=4]{3}
+		\tikzset{
+      VertexStyle/.append style = {black} }
+
+      \SetVertexNoLabel
+      \Vertex[x=2,y=5]{A}
+      \Vertex[x=4,y=5]{B}
+      \Vertex[x=10,y=5]{C}
+      \Vertex[x=12,y=5]{D}
+      \Vertex[x=6,y=3]{E}
+      \Vertex[x=8,y=3]{F}
+      \tikzset{
+      EdgeStyle/.append style = {green} }
+      \Edge[label = 3](s2)(A)
+      \Edge(A)(B)
+      \Edge(B)(C)
+      \Edge(C)(D)
+      \Edge(D)(l2)
+
+      \tikzset{
+      EdgeStyle/.append style = {red} }
+      \Edge[label = 1](s3)(E)
+      \Edge(E)(F)
+      \Edge(F)(l3) 
+	\tikzset{
+      EdgeStyle/.append style = {blue} }
+      \Edge[label = 1](s1)(A)
+      \Edge[label = 1](A)(B)
+      \Edge[label = 1](B)(E)
+      \Edge(E)(F)
+      \Edge(F)(l1)
+
+	\tikzset{
+      EdgeStyle/.append style = {black,-} }
+
+      \Edge(1)(2)
+      \Edge(1)(3)
+    \node (1) at (-3,4){\Huge $\rightarrow$};
+    \end{tikzpicture}
+
+    }
+
   \subsection{MIN-PRA}
@@
 
-\section{Proposed Solutions, solving PALL}
+\section{The Star Topolgy}
 
@@
     \subsubsection{Greedy Algorithm with higher bound}
-      \paragraph{Algo}
-	Todo
+
+	\begin{algorithm}[H]
+	\caption{Greedy with Higher bound Period(GHP)}
+	\begin{algorithmic}
+	\REQUIRE ${\cal R}_{\cal C}$, period $P$
+	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
+	\STATE $P1[P]$ slots of size $\tau$ in first way period.
+	\STATE $P2[P]$ slots  of size $\tau$ in back way period.
+	\FORALL{route i in ${\cal R}_{\cal C}$ }
+
+	\FORALL{slot j in P1}
+
+	\IF{$P1[j]$ is free, and the corresponding slot(s) in P2 are free}
+
+	\STATE $o_i \leftarrow j$
+	\ENDIF
+
+	\IF{No intervals are found for i}
+	\STATE return FAILURE
+	\ENDIF
+	\ENDFOR
+
+	\ENDFOR
+
+	\end{algorithmic}
+	\end{algorithm}
       \paragraph{Period}
-	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.N$, if we have N routes.\\
-	Suppose that we have a period of $3.\tau.N$ slots, divided in $\tau$ macro-slots.
+	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
+	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots.
+Let us call {\em forward period} the period in the central node when the messages goes to RRH to BBU, and {\em backward period} the period when the messages comes back in the other way.
+Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
+	\todo{Dessin qui illustre ça}\\
+	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period.
+Those $3.c - k$ gives us $3.c - k$ possible slots in the backward periods.\\
+	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period.
+Since $k<c$,  $2k < 3.c - k$, thus using the pigeonhole principle, there is at least one free slot in the backward period for the new message.
+
     \subsubsection{Exhaustive generation}
@@
 
+\bibliographystyle{plain}
+\bibliography{Sources.bib}
+
 \end{document}

### 2017-02-07 article/article.tex
ltk

--- 2017-02-01 article/article.tex
@@
 \newtheorem{theorem}{Theorem}
-\newcommand{\reporttitle}{Contention management for Deterministic Networking}     % Titre
-\newcommand{\reportauthor}{Maël \textsc{Guiraud }} % Auteur
-\newcommand{\reportsubject}{Master Thesis} 
-\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
 \setlength{\parskip}{1ex} % Espace entre les paragraphes
@@
 We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $(u,v)$ in $\cal C$.
+$\cal R_{\cal C}$ is called an {\bf assigned graph}, and contains all the information needed in forthcoming problems (couples of vertices, routes and delay of the arcs).
+
       \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}
@@
 
-      \begin{center}
-
-      \fbox{\parbox{12cm}{
       Notice that the notion of $P$-periodic affectation \textbf{is not monotone} with regard to $P$. 
@@
 
-      A {\bf conflict graph} represents the collision between the routes of $ {\cal R}_{\cal C}$.
+%       A {\bf conflict graph} represents the collision between the routes of $ {\cal R}_{\cal C}$.
 The vertices of a conflict graph $G = (V,E)$ are the routes of $ {\cal R}_{\cal C}$, and there is an edge between two vertices if and only if there is a common arc between the two routes in $ {\cal R}_{\cal C}$.
+%       
+%       Given $u$ and $v$ two vertices of the conflict graph, corresponding to two routes colliding in $ {\cal R}_{\cal C}$.
+The weight of an edge, $w(u,v)$, is the absolute value of the difference between the distance of the two routes between their respective source node and the collision point.
+%       
+%       A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.
 
-      Given $u$ and $v$ two vertices of the conflict graph, corresponding to two routes colliding in $ {\cal R}_{\cal C}$.
-The weight of an edge, $w(u,v)$, is the absolute value of the difference between the distance of the two routes between their respective source node and the collision point.
+      \includegraphics[scale=0.5]{Fig5.pdf}\\
+       \begin{center}
+      $\lambda(v,r_i) - \lambda(v,r_j)=1$ 
+     \end{center}
 
-      A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.
+      On the other hand if we set all $\lambda(v,r_i) - \lambda(v,r_j)=P$, there is no $P$-periodic affectation if $P<c$.
 
-      \begin{tabular}{cc}
-      \includegraphics[scale=0.5]{Fig5.pdf} & \includegraphics[scale=1]{Fig7.pdf}\\
-      $\lambda(v,r_i) - \lambda(v,r_j)=1$ & Conflict graph\\
-      \end{tabular}\newline
+      \includegraphics[scale=0.5]{Fig6.pdf}\\
+       \begin{center}
+      $\lambda(v,r_i) - \lambda(v,r_j)=2$
 
-      On the other hand if we set all $\lambda(v,r_i) - \lambda(v,r_j)=P$, there is no $P$-periodic affectation if $P<l$.
-
-      \begin{tabular}{cc}
-      \includegraphics[scale=0.5]{Fig6.pdf} & \includegraphics[scale=1]{Fig8.pdf}\\
-      $\lambda(v,r_i) - \lambda(v,r_j)=2$ & Conflict graph\\
-      \end{tabular}\newline
-      \begin{center}
       Here for P=2, there is no $P$-periodic affectation.
@@
 
-      Therefore if we choose and odd value for $P$ and $l=P+1$, there is no $P$-periodic affectation but modulo $2$ all $\lambda(v,r_i) - \lambda(v,r_j)$
+      Therefore if we choose and odd value for $P$ and $c=P+1$, if there is no $P$-periodic affectation but modulo $2$ all $\lambda(v,r_i) - \lambda(v,r_j)$
       are equal to one thus we have a $2$-periodic affectation.
-      }}
 
-      \end{center}
    \subsection{Problems}
@@
 
+    For each arc $(u,v) \in A$, we denote by ${\rho}(u,v)$ the subset of routes of $\cal{R}$  containing $(u,v)$.
+    We define the load of an arc $(u,v)$ as the number of routes that use this arc thus : $load(u,v) = |\rho(u,v)|$.
+
     \begin{theorem}
@@
 
-    As in the previous proof, a $k$-coloring of $G$ gives a $k$-periodic schedule of $H$
-    and conversly. Therefore if we can approximate the value of PRA  within a factor $f$,
+    Let $\phi$ be an edge coloring with $k$ colors of $G$. We can build a $k$ periodic affectation
+    by assigning to the source $s_{u,v}$ of each route an offset  of $\phi(s_{u,v})$. Indeed, 
+    if two routes $r_1$ and $r_2$ share the same edge, say $(v_1,v_2)$ then they represent two edges $e_1$ and $e_2$ of $G$ incident  
+    to the vertex $v$. Therefore $\lambda(v_1,r_1) = \phi(e_1) \mod k$ because the delays of the edges before $v_1$ sum to $d(d+1)$ or 
+    $2(d(d+1))$ which are equal to $0$ modulo $k$ since $k=d$ or $k=d+1$. Thus $\lambda(v_1,r_1) - \lambda(v_1,r_2) \mod k = \phi(e_1) - \phi(e_2) \mod k$
+    and $\lambda(v_1,r_1) - \lambda(v_1,r_2) \mod k > 0$ since $\phi(e_1) \neq \phi(e_2) $.
+
+    Now consider a $k$-periodic affectation of $\rho$. For each $(u,v)$ in $G$, we define $\phi(u,v)$ to be the offset of the route
+    beginning at $s_{u,v}$. For the same reasons as in the last paragraph, $\phi$ is an edge coloring with $k$ colors.
+
+  Therefore if we can approximate the value of PRA  within a factor $f$,
     we could approximate the minimal number of colors needed to color a graph within a fator $f$, 
@@
     \node (1) at (-3,4){\Huge $\rightarrow$};
+
+    \node (2) at (-7,-2){\Huge G};
+    \node (3) at (10,-2){\Huge H};
     \end{tikzpicture}
@@
 
-	\IF{$P1[j]$ is free, and the corresponding slot(s) in P2 are free}
+	\IF{$P1[j]$ is free AND $P2[j+\lambda(r_i)]$ is free}
 

### 2017-02-07 code/code.c

@@ -162,7 +162,7 @@ int algo_prime(Graphe g,int periode,int taille_message)
 	for(int i=0;i<nb_routes;i++)
 	{
 		//On recherche le depart le plus petit
-		for(int j=0;j<periode-taille_message;j++)
+		for(int j=0;j<=periode-taille_message;j++)
 		{
 			if(!aller[j] && !aller[(j+taille_message)%periode] && !retour[(j*taille_message+routes[i])%periode] && !retour[(j*taille_message+routes[i]+taille_message-1)%periode])
 			{
@@ -204,22 +204,24 @@ void simuls_periode(int nb_routes, int taille_message, int taille_routes,int nb_
 	for(int j = 1 ; j<=nb_routes;j++)
 	{
 		printf("Calculs pour %d routes : \n",j);
-		g = init_graphe(j*2 + 1);
-		graphe_etoile(g,taille_routes);
+		
 		total_3NT = 0;
 		total_prime = 0;
 		for(int i = 0;i<nb_simuls;i++)
 		{
+			g = init_graphe(j*2 + 1);
+			graphe_etoile(g,taille_routes);
 			total_3NT += linear_3NT(g,taille_message);
 			total_prime += linear_prime(g,taille_message);
 			fprintf(stdout,"\rStep%5d /%d",i+1,nb_simuls);fflush(stdout);
+			free(g.matrice);
 		}
 		printf("\n");
 		printf("P moyen (sur %d simulations) 3NT  : %lld\n",nb_simuls,total_3NT/nb_simuls);
 		printf("P moyen (sur %d simulations) Prime: %lld\n",nb_simuls,total_prime/nb_simuls);
 
 
-		free(g.matrice);
+		
 		fprintf(F, "%d %lld %lld\n",j,total_3NT/nb_simuls,total_prime/nb_simuls);
 		printf("\n");
 	}
@@ -229,6 +231,6 @@ void simuls_periode(int nb_routes, int taille_message, int taille_routes,int nb_
 int main()
 {
 	srand(time(NULL));
-	simuls_periode(7,2500,700,100);
+	simuls_periode(7,2500,700,1000);
 	return 0;
 }

### 2017-02-07 article/article.tex

--- 2017-02-01 article/article.tex
@@
 \newtheorem{theorem}{Theorem}
+
+\setlength{\parskip}{1ex} % Espace entre les paragraphes
+
 \newtheorem{fact}{Fact}
@@
 We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $(u,v)$ in $\cal C$.
+$\cal R_{\cal C}$ is called an {\bf assigned graph}, and contains all the information needed in forthcoming problems (couples of vertices, routes and delay of the arcs).
+
       \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}
-
-      \todo{Doit on définir un objet graphe + routes + assignement pour ensuite simplifier l'écriture}
 

### 2017-02-08 code/code.c
dessins + courbes pour grande tailles

@@ -198,19 +198,20 @@ void simuls_periode(int nb_routes, int taille_message, int taille_routes,int nb_
 {
 	FILE * F = fopen("results_periode.data","w");
 	Graphe g;
-	long long int total_3NT, total_prime ;
+	long long int total_3NT, total_prime;
 
 
 	for(int j = 1 ; j<=nb_routes;j++)
 	{
-		printf("Calculs pour %d routes : \n",j);
+		printf("Calculs pour %d routes: \n",j);
 		
 		total_3NT = 0;
 		total_prime = 0;
+
 		for(int i = 0;i<nb_simuls;i++)
 		{
 			g = init_graphe(j*2 + 1);
-			graphe_etoile(g,taille_routes);
+			graphe_etoile(g,j*taille_message);
 			total_3NT += linear_3NT(g,taille_message);
 			total_prime += linear_prime(g,taille_message);
 			fprintf(stdout,"\rStep%5d /%d",i+1,nb_simuls);fflush(stdout);
@@ -222,15 +223,15 @@ void simuls_periode(int nb_routes, int taille_message, int taille_routes,int nb_
 
 
 		
-		fprintf(F, "%d %lld %lld\n",j,total_3NT/nb_simuls,total_prime/nb_simuls);
+		fprintf(F, "%d %lld %lld %d %d\n",j,total_3NT/nb_simuls,total_prime/nb_simuls,j*taille_message,2*j*taille_message);
 		printf("\n");
 	}
 	fclose(F);
-
 }
+
 int main()
 {
 	srand(time(NULL));
-	simuls_periode(7,2500,700,1000);
+	simuls_periode(7,2500,10000,1000);
 	return 0;
 }

### 2017-02-08 article/article.tex
dessins + courbes pour grande tailles
améliorations définitions, exemple de non monotonie

@@
 	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $Dl(u,v) \geq 1$ that we call the delay and
-	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$.
+	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. 
+	%Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$. Dominique voulait être plus général, on mettera cette propriété dans notre topologie
 
@@
 We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $(u,v)$ in $\cal C$.
-$\cal R_{\cal C}$ is called an {\bf assigned graph}, and contains all the information needed in forthcoming problems (couples of vertices, routes and delay of the arcs).
+We call $\cal R_{\cal C}$ a {\bf routage graph}, it contains all the informations needed in the forthcoming problems (assignment, routes and delays of the arcs).
 
+     \todo{Dire après  la définition des problèmes qu'on pourrait demander de trouver l'assignement et même le routage pour optimiser, mais pas dans cet article
+     et qu'on travail avec des réseaux déjà constitués}
       \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}
@@
    \subsection{Slotted time Model}
-      Consider now a positive integer $P$ called the {\bf period}.
-In our problem the messages we send in the network will be periodic of period $P$ and thus we consider slices of time of $P$ discrete slots.
-Assume we send a message at the source of the route $r$,
-      at the time slot $m$ in the first period, then a message will be sent at time $m$ at each new period.
-We define the first time slot at which a message reaches a vertex $v$ in this route by $t(v,r) = m + \lambda(v,r) \mod P$.
+      Consider now a positive integer $P$ called the {\bf period}. In our problem, we send in the network
+      periodic messages of period $P$.
+The time will thus be cut into slices of $P$ discrete slots.
+Assume we send a message at the source of the route $r$, at the time slot $m$ in the first period, then a message will be sent at time slot $m$ at each new period.
+We define the first time slot at which the message reaches a vertex $v$ in this route by $t(v,r) = m + \lambda(v,r) \mod P$.
 
@@
       of consecutive slots necessary to transmit a message.
-Let us call $[t(v,r)]$ the set of time slots used by $r$ at a vertex $v$ in a period $P$, that is $[t(v,r)] = \{t(v,r) + i \mod P \mid 0 \leq i \leq \tau \}$.
+Let us call $[t(v,r)]_{P,\tau}$ the set of time slots used by $r$ at a vertex $v$ in a period $P$, that is $[t(v,r)]_{P,\tau} = \{t(v,r) + i \mod P \mid 0 \leq i < \tau \}$.
+Usually $P$ and $\tau$ will be clear from the context and we will denote $[t(v,r)]_{P,\tau}$ by $[t(v,r)]$
 
-      A {\bf $P$-periodic affectation} of $\cal R_{\cal C}$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $c$ integers that we call {\bf offsets}, with $c$ the cardinal of the assignment $\cal C$.
-The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in {\cal R}_{\cal C}$ at its source.
-      A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}_{\cal C}$, that is $\forall (r_i, r_j) \in {\cal R}_{\cal C}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
+      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $c$ integers that we call {\bf offsets}, with $c$ the number of routes in $\cal R$.
+The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in {\cal R}$ at its source.
+      A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}$, that is $\forall (r_i, r_j) \in {\cal R}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
       we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$
 
-      Notice that the notion of $P$-periodic affectation \textbf{is not monotone} with regard to $P$. 
-      Indeed, consider messages of size 1, we can build a graph, with $c$ routes $r_i \in {\cal R}_{\cal C}, i < c$ which all intersect two by two and
-      such that if $r_i$ and $r_j$ have $v$ as first common vertex we have $\lambda(v,r_i) - \lambda(v,r_j)=1$.
-      Therefore there is a $2$-periodic affectation by setting all $m_i$ to $0$.
+%       Notice that the notion of $P$-periodic affectation \textbf{is not monotone} with regard to $P$. 
+      As an exemple of a $(2,1)$-periodic affectation, let consider a routage graph with routes $\{r_i\}_{i=1,\dots,c}$, such that all pairs of routes intersect at a different edge.
+      We set $\tau = 1$ and the delays are chosen so that if $r_i$ and $r_j$ have $v$ as first common vertex then we have $\lambda(v,r_i) - \lambda(v,r_j)=1$.There is a $(2,1)$-periodic affectation by setting all $m_i$ to $0$.
 
@@
 %       A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.
-
-      \includegraphics[scale=0.5]{Fig5.pdf}\\
+      \begin{figure}[h]
        \begin{center}
-      $\lambda(v,r_i) - \lambda(v,r_j)=1$ 
+      \includegraphics[scale=0.7]{Fig5.pdf}
       \end{center}
-
-      On the other hand if we set all $\lambda(v,r_i) - \lambda(v,r_j)=P$, there is no $P$-periodic affectation if $P<c$.
-
-      \includegraphics[scale=0.5]{Fig6.pdf}\\
-       \begin{center}
-      $\lambda(v,r_i) - \lambda(v,r_j)=2$
-
-      Here for P=2, there is no $P$-periodic affectation.
-      \end{center}
-
-      Therefore if we choose and odd value for $P$ and $c=P+1$, if there is no $P$-periodic affectation but modulo $2$ all $\lambda(v,r_i) - \lambda(v,r_j)$
-      are equal to one thus we have a $2$-periodic affectation.
+       \caption{A routage graph with $(0,\dots,0)$ as a $(2,1)$-periodic affectation}
+      \end{figure}
 
@@
 
-      The main theoretical problem we have to deal with in this context is the following.\\
+    We want to ensure that there is an affectation which allows to send periodic messages from elements in $S$ to elements in $L$.
+    The problem we need to solve is thus the following:
 
-      \noindent {\bf Problem Periodic Routes Assignment (PRA)}
+      \noindent {\bf  Periodic Routes Assignment (PRA)}
 
-      \noindent {\bf Input:} a graph $G=(V,A)$, a set $\cal C$ of pair of vertices, a routing function $\cal R$ and an integer $P$.
+      \noindent {\bf Input:} a routage graph $\cal R$, an integer $\tau$ and an integer $P$.
 
-      \noindent {\bf Question:} does there exist a $P$-periodic affectation of $\cal C$ in $(G,{\cal R})$?
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R$ ?
 
-      We will prove in Sec.~\ref{sec:complexity} that the Problem PRA is $\NP$-complete, even in restricted settings.
-      In fact, even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.\\
+      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
+      Even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.
+      Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
+      $(P',\tau)$-periodic affectation with $P' > P$, the property is thus not monotone with regards to $P$.
+
+	\begin{lemma} 
+	 For any $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
+	\end{lemma}
+\begin{proof}
+      Consider the routage graph ${\cal R}$ given in the previous subsection. 
+      We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
+      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
+      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
+      On the other hand, if we want to find a $(P,1)$-periodic affectation, then $\lambda(v,r_i) - \lambda(v,r_j) = 0 $ modulo $P$.
+      Thus we must find $m_i \in \{0,\dots,P-1\}$ such that for all $i \neq j \in \{1,\dots,c\}^2$, $m_i \neq m_j$, which is impossible since $P < c$.
+
+\end{proof}
+
 % 

### 2017-02-09 article/article.tex
harmonisation avec les nouvelles définitions en cours

@@
 \section{Introduction}
-  \itemize
+  \begin{itemize}
     \item Context and problematic
@@
     \item Article contribution
+  \end{itemize}
 
@@
   \subsection{Definitions}
+
+  \todo{Remplacer Dl par dl}
 
@@
       A {\bf route} $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$. 
+      We will often refer to the first element of the route as a source and the last as a target.
 
@@
 
-      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $c$ integers that we call {\bf offsets}, with $c$ the number of routes in $\cal R$.
+      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $c$ integers that we call {\bf offsets}, with $c$ the number of routes in $\cal R$.
 The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in {\cal R}$ at its source.
@@
 
-      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
+      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, in very restricted settings.
       Even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.
@@
       Consider the routage graph ${\cal R}$ given in the previous subsection. 
-      We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
-      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
-      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
+      For each pair of routes $r_i$ and $r_j$, $v$ the first vertex which belongs to both routes,
+      we set $\lambda(v,r_i) - \lambda(v,r_j)$ to $P$ instead of $1$.
+We chose $P$ to be an odd number smaller than $c$ the number of routes in ${\cal R}$.
+If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$.
+Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
       On the other hand, if we want to find a $(P,1)$-periodic affectation, then $\lambda(v,r_i) - \lambda(v,r_j) = 0 $ modulo $P$.
@@
       In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
-      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
-      We denote by $n$ the size of $S$ and $L$.
-We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH.
+      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $T$ is the set of RRH. 
+      We denote by $n$ the size of $S$ and $T$.
+We are given a period $P$, a message size $\tau$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH.
 Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$.
-Let consider a $P$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to
+Let consider a $(P,\tau)$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to
       $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.
@@
       This affectation represents the following process: first a message is sent in $l$, through the route $r_l$, at time $m_l$.
-      This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$.
+
+%       \begin{center}
+%       \includegraphics[scale=0.2]{rrh.jpeg}
+%       \end{center}
+%       
+%       This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$.
 It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period.
 The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
+%       
+%        \begin{center}
+%       \includegraphics[scale=0.2]{BBU1.jpeg}
+%       
+%       \includegraphics[scale=0.2]{BBU2.jpeg}
+%       \end{center}
+%
+
       When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
@@
 
-      Thus, the whole proccess time for a vertex $l$ is equal to
+      Thus, the whole proccess time for a message sent at vertex $l$ is equal to
       $$
@@
 
-      \noindent {\bf Problem Periodic Assignment for Low Latency(PALL)}
+      \noindent {\bf Periodic Assignment for Low Latency(PALL)}
 
-      \noindent {\bf Input:}  a digraph $G$, a matching $\rho$ from $L$ to $S$ two disjoint set of vertices of $G$, a routing function $\cal R$, a period $P$, an integer $T_{max}$.
+      \noindent {\bf Input:}  a matching $\rho$ from $L$ to $S$ two disjoint set of elements, a routage graph $\cal R$ whose set of sources is $S$ and whose set of targets is $T$, a period $P$, an integer $\tau$, an integer $T_{max}$.
 
-      \noindent {\bf Question:} does there exist a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation ${\cal M}$ of ${\cal R}$ such that $MT({\cal M}) \leq T_{max}$?
 
@@
 
- In this section we assume that the size of a message $\tau$ is equal to one, which implies hardness of PRA and PALL for all $\tau$. 
-Consider an instance of Problem PRA, i.e., a digraph $G=(V,A)$, an assignment $\cal C$, a routing function $\cal R$ and a period $P$. 
+ In this section we assume that the size of a message $\tau$ is equal to one. 
+ We will prove the hardness of PRA and PALL for this parameter, which implies the hardness of the general problems. 
+Consider an instance of the problem PRA, i.e., a routing graph $\cal{R}$, a message size $\tau$ and a period $P$. 
 The {\bf conflict depth} of a route is the number of other routes which share an edge with it. 
-The conflict depth of an assignment $\cal C$ is the maximum of the conflict depth of the routes in ${\cal R}_{\cal C}$.
-The {\bf load} of an assignment is the maximal number of routes sharing the same arc.
+The conflict depth of an assignment $\cal C$ is the maximum of the conflict depth of the routes in ${\cal R}$.
+The {\bf load} of a routing graph is the maximal number of routes sharing the same arc.
 It is clear that a $P$-periodic affectation must satisfy that $P$ is larger or equal to the load.
@@
 
- Remark that we have used zero weigth in the proof. If the weigths must be strictly positive, which makes more sense in our model since
- we model the latency of physical links, it is easy to adapt the proof.
+ Remark that we have used zero weigth in the proof. If we ask the weigths to be strictly positive, which makes sense in our model since
+they represent the latency of physical links, it is easy to adapt the proof.
 We just have to set them so that in any route the delay at $u_1$ is equal to $d$ and thus equal to $0$ modulo $d$.
@@
 
+Open questions. Can we improve the results if:
+\begin{itemize}
+ \item The routes are smaller than the size of a message. 
+\item The routes are smaller than the period.
+\item The largest difference between two routes is smallest than one of these parameters
+\end{itemize}
+
+ On a general graph:
+
+\begin{itemize}
+\item The routing is coherent
+ \item The graph is symmetric
+\end{itemize}
+
 \bibliographystyle{plain}

### 2017-02-09 article/article.tex
pb

--- 2017-02-08 article/article.tex
@@
 
-      \noindent {\bf Input:} a routage graph $\cal R$, an integer $\tau$ and an integer $P$.
+      \noindent {\bf Input:} a routage graph $\cal R_{\cal C}$, an integer $\tau$ and an integer $P$.
 
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R$ ?
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R_{\cal C}$ ?
 
       We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
-      Even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.
+      Even approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic affectation is hard.
       Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
@@
 \begin{proof}
-      Consider the routage graph ${\cal R}$ given in the previous subsection. 
+      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
       We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
@@
       and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
-      We denote by $n$ the size of $S$ and $L$.
+       We have as much BBUs as RRH in the network. We denote by ${\cal c}$ the size of $S$ and $L$, and so, the number of routes.
+       We are given a period $P$, a routing function ${\cal R}$, and an assignment ${\cal C}:L\rightarrow S$  which assigns a BBU to each RRH. 
+       $l_i,i<{\cal c}$ is the RRH of the route $i$ and ${\cal C}(l_i)$, or $s_i$ is its corresponding BBU. The routing between each RRH and BBU is given by the routage graph ${\cal R}_{\cal C}$.
+
+       Let consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_l$ to 
+      $(l,{\cal C}(l))$ and $m_{{\cal C}(l)}$ to $({\cal C}(l),l)$.
+
+%       
+%       We denote by $n$ the size of $S$ and $L$.
 We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH.
@@
 Let consider a $P$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to
-      $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.
+%       $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.
 
       This affectation represents the following process: first a message is sent in $l$, through the route $r_l$, at time $m_l$.
-      This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$.
-It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period.
-The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
+
+      \begin{center}
+      \includegraphics[scale=0.2]{rrh.jpeg}
+      \end{center}
+
+      This message is received by ${\cal C}(l)$ at time $t({\cal C}(l),r_l)$.
+It is then sent back to $l$ in the same period at time $m_{{\cal C}(l)}$ if $m_{{\cal C}(l)} > t({\cal C}(l),r_l)$, otherwise at time $m_{{\cal C}(l)}$ in the next period.
+The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{{\cal C}(l)} - t({\cal C}(l),r_l)$ if $m_{{\cal C}(l)} > t({\cal C}(l),r_l)$ and $w_l = m_{{\cal C}(l)} + P - t({\cal C}(l),r_l)$ otherwise.
+
+       \begin{center}
+      \includegraphics[scale=0.2]{BBU1.jpeg}
+
+      \includegraphics[scale=0.2]{BBU2.jpeg}
+      \end{center}
+
       When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
@@
       $$
-      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{\rho(l)}).
+      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{{\cal C}(l)}).
       $$
 
-    The {\bf maximum process time} of the $P$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.
+    The {\bf maximum process time} of the $(P,\tau)$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.
 
@@
 
-      \noindent {\bf Input:}  a digraph $G$, a matching $\rho$ from $L$ to $S$ two disjoint set of vertices of $G$, a routing function $\cal R$, a period $P$, an integer $T_{max}$.
+      \noindent {\bf Input:}  A routage graph ${\cal R}_{\cal C}$, a period $P$, an integer $T_{max}$.
 
@@
 
-    \node (2) at (-7,-2){\Huge G};
-    \node (3) at (10,-2){\Huge H};
+    \node (2) at (-7,0){\Huge H};
+    \node (3) at (10,0){\Huge G};
     \end{tikzpicture}

### 2017-02-09 article/article.tex

@@
 
-	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $Dl(u,v) \geq 1$ that we call the delay and
+	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $dl(u,v) \geq 1$ that we call the delay and
 	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. 
@@
       A {\bf route} $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$. 
+      We will often refer to the first element of the route as a source and the last as a target.
 
-      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} Dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
+      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
       The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
@@
       Even approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic affectation is hard.
+
       Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
@@
 	\begin{lemma} 
-	 For any $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
+	 For any odd $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
 	\end{lemma}
 \begin{proof}
+
       Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
@@
       we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
-      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
-      On the other hand, if we want to find a $(P,1)$-periodic affectation, then $\lambda(v,r_i) - \lambda(v,r_j) = 0 $ modulo $P$.
-      Thus we must find $m_i \in \{0,\dots,P-1\}$ such that for all $i \neq j \in \{1,\dots,c\}^2$, $m_i \neq m_j$, which is impossible since $P < c$.
+      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R_{\cal C}}$.
 
@@
       In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network
+
       and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
@@
 
+%       \begin{center}
+%       \includegraphics[scale=0.2]{rrh.jpeg}
+%       \end{center}
+%       
+%       This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$.
+It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period.
+The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
+%       
+%        \begin{center}
+%       \includegraphics[scale=0.2]{BBU1.jpeg}
+%       
+%       \includegraphics[scale=0.2]{BBU2.jpeg}
+%       \end{center}
+%
+
       When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
@@
 
-      \noindent {\bf Problem Periodic Assignment for Low Latency(PALL)}
+      \noindent {\bf Periodic Assignment for Low Latency(PALL)}
 
@@
 
-      \noindent {\bf Question:} does there exist a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation ${\cal M}$ of ${\cal R}$ such that $MT({\cal M}) \leq T_{max}$?
 

### 2017-02-10 article/article.tex
preuve 3nt

@@
        \begin{center}
-      \includegraphics[scale=0.2]{BBU1.jpeg}
 
@@
 Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
-	\todo{Dessin qui illustre ça}\\
+      \begin{center}
+      \includegraphics[scale=0.2]{ex3nt.png}
+      \end{center}
 	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period.

### 2017-02-13 article/article.tex
algobrute
merge

--- 2017-02-09 article/article.tex
@@
 
-	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $dl(u,v) \geq 1$ that we call the delay and
+  \todo{Remplacer Dl par dl}
+
+	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $Dl(u,v) \geq 1$ that we call the delay and
 	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. 
@@
 
-      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
+      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} Dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
       The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
@@
 
-      \noindent {\bf Input:} a routage graph $\cal R_{\cal C}$, an integer $\tau$ and an integer $P$.
+      \noindent {\bf Input:} a routage graph $\cal R$, an integer $\tau$ and an integer $P$.
 
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R_{\cal C}$ ?
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R$ ?
 
-      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
-      Even approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic affectation is hard.
-
+      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, in very restricted settings.
+      Even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.
       Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
@@
 	\begin{lemma} 
-	 For any odd $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
+	 For any $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
 	\end{lemma}
 \begin{proof}
-
-      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
-      We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
-      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
-      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R_{\cal C}}$.
+      Consider the routage graph ${\cal R}$ given in the previous subsection. 
+      For each pair of routes $r_i$ and $r_j$, $v$ the first vertex which belongs to both routes,
+      we set $\lambda(v,r_i) - \lambda(v,r_j)$ to $P$ instead of $1$.
+We chose $P$ to be an odd number smaller than $c$ the number of routes in ${\cal R}$.
+If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$.
+Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
+      On the other hand, if we want to find a $(P,1)$-periodic affectation, then $\lambda(v,r_i) - \lambda(v,r_j) = 0 $ modulo $P$.
+      Thus we must find $m_i \in \{0,\dots,P-1\}$ such that for all $i \neq j \in \{1,\dots,c\}^2$, $m_i \neq m_j$, which is impossible since $P < c$.
 
@@
       In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
-
-      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
-       We have as much BBUs as RRH in the network. We denote by ${\cal c}$ the size of $S$ and $L$, and so, the number of routes.
-       We are given a period $P$, a routing function ${\cal R}$, and an assignment ${\cal C}:L\rightarrow S$  which assigns a BBU to each RRH. 
-       $l_i,i<{\cal c}$ is the RRH of the route $i$ and ${\cal C}(l_i)$, or $s_i$ is its corresponding BBU. The routing between each RRH and BBU is given by the routage graph ${\cal R}_{\cal C}$.
-
-       Let consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_l$ to 
-      $(l,{\cal C}(l))$ and $m_{{\cal C}(l)}$ to $({\cal C}(l),l)$.
-
-%       
-%       We denote by $n$ the size of $S$ and $L$.
-We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH.
+      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $T$ is the set of RRH. 
+      We denote by $n$ the size of $S$ and $T$.
+We are given a period $P$, a message size $\tau$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH.
 Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$.
-Let consider a $P$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to
-%       $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.
+Let consider a $(P,\tau)$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to
+      $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.
 
@@
 
-      This message is received by ${\cal C}(l)$ at time $t({\cal C}(l),r_l)$.
-It is then sent back to $l$ in the same period at time $m_{{\cal C}(l)}$ if $m_{{\cal C}(l)} > t({\cal C}(l),r_l)$, otherwise at time $m_{{\cal C}(l)}$ in the next period.
-The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{{\cal C}(l)} - t({\cal C}(l),r_l)$ if $m_{{\cal C}(l)} > t({\cal C}(l),r_l)$ and $w_l = m_{{\cal C}(l)} + P - t({\cal C}(l),r_l)$ otherwise.
+      This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$.
+It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period.
+The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
 
@@
 
-%       \begin{center}
-%       \includegraphics[scale=0.2]{rrh.jpeg}
-%       \end{center}
-%       
-%       This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$.
-It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period.
-The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
-%       
-%        \begin{center}
-%       \includegraphics[scale=0.2]{BBU1.jpeg}
-%       
-%       \includegraphics[scale=0.2]{BBU2.jpeg}
-%       \end{center}
-%
-
       When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
@@
       $$
-      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{{\cal C}(l)}).
+      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{\rho(l)}).
       $$
 
-    The {\bf maximum process time} of the $(P,\tau)$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.
+    The {\bf maximum process time} of the $P$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.
 
@@
 
-      \noindent {\bf Input:}  A routage graph ${\cal R}_{\cal C}$, a period $P$, an integer $T_{max}$.
+      \noindent {\bf Input:}  a matching $\rho$ from $L$ to $S$ two disjoint set of elements, a routage graph $\cal R$ whose set of sources is $S$ and whose set of targets is $T$, a period $P$, an integer $\tau$, an integer $T_{max}$.
 
@@
 
-    \node (2) at (-7,0){\Huge H};
-    \node (3) at (10,0){\Huge G};
+    \node (2) at (-7,-2){\Huge G};
+    \node (3) at (10,-2){\Huge H};
     \end{tikzpicture}

### 2017-02-13 article/article.tex

--- 2017-02-10 article/article.tex
@@
       Consider now a positive integer $P$ called the {\bf period}. In our problem, we send in the network
-      periodic messages of period $P$.
+      messages with period $P$.
 The time will thus be cut into slices of $P$ discrete slots.
@@
 Let us call $[t(v,r)]_{P,\tau}$ the set of time slots used by $r$ at a vertex $v$ in a period $P$, that is $[t(v,r)]_{P,\tau} = \{t(v,r) + i \mod P \mid 0 \leq i < \tau \}$.
-Usually $P$ and $\tau$ will be clear from the context and we will denote $[t(v,r)]_{P,\tau}$ by $[t(v,r)]$
+Usually $P$ and $\tau$ will be clear from the context and we will denote $[t(v,r)]_{P,\tau}$ by $[t(v,r)]$.
 
@@
 
-    We want to ensure that there is an affectation which allows to send periodic messages from elements in $S$ to elements in $L$.
-    The problem we need to solve is thus the following:
+    We want to ensure that there is an affectation which allows to send periodic messages from sources to target
+    without collisions. The problem we need to solve is thus the following:
 
@@
 
-      \noindent {\bf Input:} a routage graph $\cal R_{\cal C}$, an integer $\tau$ and an integer $P$.
+      \noindent {\bf Input:} a routage graph $\cal R$, an integer $\tau$ and an integer $P$.
 
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R_{\cal C}$ ?
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R$ ?
 
@@
 
-      Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
-      $(P',\tau)$-periodic affectation with $P' > P$, the property is thus not monotone with regards to $P$.
+      An unusual property of affectation is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
+      $(P',\tau)$-periodic affectation with $P' > P$: the existence of an affectation is not monotone with regards to $P$.
 
@@
 
-      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
-      We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
+      Consider the routage graph ${\cal R}$ given in the previous subsection. 
+      We change the delays so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
       we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
-      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R_{\cal C}}$.
+      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
 
@@
       In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
+      and two disjoint subsets of vertices $S$ and $T$ of equal cardinality, where $S$ is the set of RRHs and $T$ is the set of BBUs. 
+      A \textbf{symmetric} assignment ${\cal C}$, is an involutive function from $S$ to $T$, which maps each element $s\in S$ to ${\cal C}(s)$ and ${\cal C}(s)$ to $s$.
+It can also be seen as the set of pairs $(s,{\cal C}(s))$ and $({\cal C}(s),s)$.
 
-      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
-       We have as much BBUs as RRH in the network. We denote by ${\cal c}$ the size of $S$ and $L$, and so, the number of routes.
-       We are given a period $P$, a routing function ${\cal R}$, and an assignment ${\cal C}:L\rightarrow S$  which assigns a BBU to each RRH. 
-       $l_i,i<{\cal c}$ is the RRH of the route $i$ and ${\cal C}(l_i)$, or $s_i$ is its corresponding BBU. The routing between each RRH and BBU is given by the routage graph ${\cal R}_{\cal C}$.
-
-       Let consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_l$ to 
-      $(l,{\cal C}(l))$ and $m_{{\cal C}(l)}$ to $({\cal C}(l),l)$.
+       We are given a period $P$, a routing function ${\cal R}$, and we consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_s$ to the route $r_s$ which begins by $s$.
+This affectation represents the following process: first a message is sent at $s$, through the route $r_s$, at time $m_s$.
 
@@
 
-      This affectation represents the following process: first a message is sent in $l$, through the route $r_l$, at time $m_l$.
-
       \begin{center}
@@
 
-      This message is received by ${\cal C}(l)$ at time $t({\cal C}(l),r_l)$.
-It is then sent back to $l$ in the same period at time $m_{{\cal C}(l)}$ if $m_{{\cal C}(l)} > t({\cal C}(l),r_l)$, otherwise at time $m_{{\cal C}(l)}$ in the next period.
-The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{{\cal C}(l)} - t({\cal C}(l),r_l)$ if $m_{{\cal C}(l)} > t({\cal C}(l),r_l)$ and $w_l = m_{{\cal C}(l)} + P - t({\cal C}(l),r_l)$ otherwise.
+      This message is received by ${\cal C}(s)$ at time $t({\cal C}(s),r_s)$.
+It is then sent back to $s$ in the same period at time $m_{{\cal C}(s)}$ if $m_{{\cal C}(s)} > t({\cal C}(s),r_s)$, otherwise at time $m_{{\cal C}(s)}$ in the next period.
+The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_s = m_{{\cal C}(s)} - t({\cal C}(s),r_s)$ if $m_{{\cal C}(s)} > t({\cal C}(s),r_s)$ and $w_s = m_{{\cal C}(s)} + P - t({\cal C}(s),r_s)$ otherwise.
 
@@
 
-%       \begin{center}
-%       \includegraphics[scale=0.2]{rrh.jpeg}
-%       \end{center}
-%       
-%       This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$.
-It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period.
-The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
-%       
-%        \begin{center}
-%       \includegraphics[scale=0.2]{BBU1.jpeg}
-%       
-%       \includegraphics[scale=0.2]{BBU2.jpeg}
-%       \end{center}
-%
+      When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
+      in the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
 
-      When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
-      in the last arc leading to the BBU and thus we need not to consider it explicitely in our model.
-
-      Thus, the whole proccess time for a message sent at vertex $l$ is equal to
+      Thus, the whole process time for a message sent at vertex $s$ is equal to
       $$
-      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{{\cal C}(l)}).
+      PT(s)=\lambda(r_s)+ w_s+\lambda(r_{{\cal C}(s)}).
       $$
 
-    The {\bf maximum process time} of the $(P,\tau)$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.
+    The {\bf maximum process time} of the $(P,\tau)$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{s \in S} PT(s)$. The problem we want to solve is the following.
 
@@
 
-      \noindent {\bf Input:}  A routage graph ${\cal R}_{\cal C}$, a period $P$, an integer $T_{max}$.
+      \noindent {\bf Input:}  A routage graph ${\cal R}_{\cal C}$ with ${\cal C}$ a symmetric assignment, a period $P$, an integer $\tau$, an integer $T_{max}$.
 
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation ${\cal M}$ of ${\cal R}$ such that $MT({\cal M}) \leq T_{max}$?
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation ${\cal M}$ of ${\cal R}_{\cal C}$ such that $MT({\cal M}) \leq T_{max}$?
 
+      \todo{Si on veut, on peut parler du temps moyen aussi ici, seulement si on fait quelque chose dessus dans la suite}
       %The related optimisation problem we will focus on  consists in minimizing  $MT({\cal M})$.
@@
  We will prove the hardness of PRA and PALL for this parameter, which implies the hardness of the general problems. 
-Consider an instance of the problem PRA, i.e., a routing graph $\cal{R}$, a message size $\tau$ and a period $P$. 
+Consider an instance of the problem PRA, i.e., a routage graph $\cal{R}$, a message size $\tau$ and a period $P$. 
 The {\bf conflict depth} of a route is the number of other routes which share an edge with it. 
-The conflict depth of an assignment $\cal C$ is the maximum of the conflict depth of the routes in ${\cal R}$.
-The {\bf load} of a routing graph is the maximal number of routes sharing the same arc.
-It is clear that a $P$-periodic affectation must satisfy that $P$ is larger or equal to the load.
+The conflict depth of a routage graph  $\cal{R}$ is the maximum of the conflict depth of the routes in ${\cal R}$.
+The {\bf load} of a routage graph is the maximal number of routes sharing the same arc.
+It is clear that a $(P,\tau)$-periodic affectation must satisfy that $P$ is larger or equal to the load times $\tau$.
 
@@
  \begin{proof}
- The problem $PRA$ is in $\NP$ since given an offfset for each route in an affectation, it is easy to check in linear time in the number of edges whether there are collisions.
+ The problem $PRA$ is in $\NP$ since given an offset for each route in an affectation, it is easy to check in linear time in the number of edges whether there are collisions.
 
@@
 We define from $H$ an instance of PRA as follows.
-The graph $G$ has for vertices $V'= \{ v_1, v_2 \mid v \in V  \} \cup \{ l_{u,v}, s_{u,v} \mid (u,v) \in E \}$ that is two vertices for each vertex and for each edge of $H$.
-  Let $A$ bet the set of arcs of $G$, defined by 
-  $$A = \{(v_1,v_2) \mid v\in V\} \cup \{(u_2,v_1)\mid u \neq v \in V^2\} \cup \{(l_{u,v},u_1),(v_2,s_{u,v}) \mid (u,v) \in E \}. $$
-  All these arcs are of weigth $0$. 
-  For each edge $(u,v) \in E$, the is a route $r_{u,v} = s_{u,v},u_1,u_2,v_1,v_2,l_{u,v}$ in ${\cal R}$.  
-  The affectation ${\cal C}$ is the set of pair of vertices $(s_{u,v}, l_{u,v})$.
+The graph $G$ has for vertices $v_1, v_2$ for each $v$ in $V$
+  and $s_{u,v}, t_{u,v}$ for each $(u,v) \in E$. The set $A$ of arcs of $G$ is: 
+  $$ \{(v_1,v_2) \mid v\in V\} \cup \{(u_2,v_1)\mid u \neq v \in V^2\} \cup \{(s_{u,v},u_1),(v_2,t_{u,v}) \mid (u,v) \in E \}. $$
+  All these arcs are of weight $0$. 
+  For each edge $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.  
+  The affectation ${\cal C}$ is the set of pair of vertices $(s_{u,v}, t_{u,v})$.
 
-  Observe that the existence of a $d$-coloring of $H$ is equivalent to the existence of a $d$-periodic affectation
-  for $(G,{\cal R},{\cal C})$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its edges by the integers
-  in $\{0,\dots,d-1\}$ and we have a correspondance between a $d$-coloring of $H$ and offests for the routes of $(G,{\cal R},{\cal C})$.
-  By contruction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent edges have
+  Observe that the existence of a $d$-coloring of $H$ is equivalent to the existence of a $(d,1)$-periodic affectation
+  of ${\cal R}_{\cal C}$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its edges by the integers
+  in $\{0,\dots,d-1\}$ and we have a bijection between $d$-colorings of $H$ and offsets of the routes of ${\cal R}_{\cal C}$.
+  By construction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent edges have
   the same color. Therefore we have reduced edge coloring to PRA which concludes the proof. 
@@
 
- Remark that we have used zero weigth in the proof. If we ask the weigths to be strictly positive, which makes sense in our model since
+ Remark that we have used zero weight in the proof. If we ask the weights to be strictly positive, which makes sense in our model since
 they represent the latency of physical links, it is easy to adapt the proof.
@@
 \begin{proof}
- We consider $(G,{\cal R},{\cal C},P)$ an instance of $PRA$ such that no element appears both in the first and second position in a pair of ${\cal C}$.
-Remark that this condition is satisfied in the previous proof, which makes the problem $PRA$ restricted to these instances $\NP$-complete.
- Let us define $T_{max} = 2 \times \max_{r \in {\cal R}} \lambda(r) + P$. We define $\rho$ as the function which maps 
- $u$ to $v$ when $(u,v) \in {\cal C}$. The instance $(G,{\cal R},\rho,P,T_{max})$ is in PALL if and only if $(G,{\cal R},{\cal C},P)$
+ We consider $({\cal R}_{\cal C},P,\tau)$ an instance of $PRA$.
+We assume that no vertex appears both in the first and second position in a pair of ${\cal C}$.
+Remark that this condition is satisfied in the previous proof, which makes the problem $PRA$ restricted to this kind of instances $\NP$-complete.
+ Let us define $T_{max} = 2 \times \max_{r \in {\cal R}} \lambda(r) + P$.
+We consider ${\cal C}'$ and ${\cal R}'_{\cal C'}$ symmetrized versions of ${\cal C}$ and  ${\cal R}_{\cal C}$ where for every route there is a symmetric route with new arcs and the same weights.
+ The instance $({\cal R'}_{\cal C'},P,\tau,T_{max})$ is in PALL if and only if $({\cal R}_{\cal C},P,\tau)$
  is in $PRA$.
-Indeed the waiting time of each route is by definition less than $P$ and thus the maximal process time less than $T_{max}$.
-Therefore the fact that $(G,{\cal R},\rho,P,T_{max})$ is in PALL is equivalent to the existence of a $P$-periodic assignment of ${\cal C}_{\rho}$ which is equal to ${\cal C}$.
+Indeed the waiting time of each route is by definition less than $P$ and thus the maximal process time is always less than $T_{max}$.
+Moreover a $(P,\tau)$-affectation of ${\cal R}_{\cal C}$ can be extended into a $(P,\tau)$-affectation of ${\cal R'}_{\cal C'}$ in the following way.
+For each route $r_{u,v}$, the time at which the message arrives is $t(v,r_{u,v})$, then we choose as offset for $r_{v,u}$, $-t(v,r_{u,v}) \mod P$.
+The symmetry ensures that each new route $r_{v,u}$ in ${\cal R'}_{\cal C'}$ uses the same times slot as $r_{u,v}$ and thus avoid collisions.
 \end{proof}
-% 
-% 
-% As another corollary of the previous proposition,  given $G$, $\cal R$, $P$ and two disjoint subsets $S$ and $L$ in $G$, the problem of  knowing if there is a matching $\rho$  from $L$ in $S$ such that the answer to problem PRA for instance $G,{\cal C_{\rho}},{\cal R}, P$ is  $\NP$-hard since checking a potential feasible solution for this problem implies to solve PRA.\\
 
-Let MIN-PRA be the problem, given a graph, a routing and an affectation, to find the minimal period $P$ such that there is a $P$-periodic affectation.
+Let MIN-PRA be the problem, given a routage graph and an assignment, to find the minimal period $P$ such that there is a $P$-periodic affectation.
 
@@
  We reduce graph coloring to PRA. Let $H$ be a graph instance of the $k$-coloring problem. 
- We define $G$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in $G$.
+ We define ${\cal R}$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
  Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an edge in $H$; this arc is the only one shared by these two routes.   
@@
 
- Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $k$-periodic affectation in $G$, 
- by converting an offset of a route into a color of a vertex and reciprocally. Therefore if we can approximate the minimum value of $P$ within a factor $f$,
- we could approximate the minimal number of colors needed to color a graph within a factor $f$, by doing the previous reduction for all possible $k$.
+ Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic affectation in $G$, 
+ by converting an offset of a route into a color of a vertex and reciprocally.
+Therefore if we can approximate the minimum value of $P$ within some factor, we could approximate the minimal number of colors needed to color a graph within the same factor.
 The proof follows from the hardness of approximability of finding a minimal coloring~\cite{zuckerman2006linear}.
@@
 This means that ${\cal R}(u,v)$ uses the same arcs as ${\cal R}(v,u)$ in the opposite orientation.
+  \todo{décrire précisément la topologie}
+
   \subsection{Intro}
@@
     \subsubsection{Exhaustive generation}
-      Décrire l'algo, expliquer les coupes
+	\begin{algorithm}[H]
+	\caption{Exhaustive Generation}  
+	\begin{algorithmic}
+	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
+	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
+	\STATE BUDGET $\leftarrow$ $P$ - ${\cal c}$ * $\tau$
+	\STATE offset $\leftarrow$ 0
+	\FORALL{route i in  ${\cal R}_{\cal C}$}
+	\FORALL{j from offset to offset + BUDGET }
+	\IF{Message of the route i does not collides with scheduled routes AND budget > 0}
+	\STATE Give i the offset j
+	\STATE BUDGET $\leftarrow$ BUDGET - (j - offset)
+	\STATE offset $\leftarrow$ j
+	\STATE call Exhaustive Generation on remaining routes
+	\ENDIF
+	\ENDFOR
+	\ENDFOR
+
+      \end{algorithmic}
+      \end{algorithm}
     \subsubsection{Results}

### 2017-02-13 article/article.tex
a

--- 2017-02-10 article/article.tex
@@
 
-  In this section, we consider a particular case of the model, in which for each $(u,v)$ , the route is the same in both directions.
-This means that ${\cal R}(u,v)$ uses the same arcs as ${\cal R}(v,u)$ in the opposite orientation.
   \subsection{Intro}
     PALL NP-Hard car PRA NP-Hard\\
-    Résultats valables sur Topologie 1 avec nos paramètres
-    \todo{J'ai viré star affectation, car je pense qu'il n'y a rien à dire là dessus.}
+
+      In this section, we consider a particular case of the model, in which for each $(u,v)$ , the route is the same in both directions.
+This means that $\forall (u,v) \in {\cal C}, {\cal R}_{\cal C}(u,v)$ uses the same arcs as ${\cal R}_{\cal C}(v,u)$ in the opposite direction.\\
+      Furthermore, the following algorithms and results were designed for a particular topology of network, in which all the routes uses a same common switch.
+        \begin{center}
+	  \includegraphics[scale=0.8]{Fig4.pdf}
+	\end{center}
+      Let us call {\bf LN} (leaves node) the central node connected to leaves, and {\bf SN} (sources node), the one connected to sources.
+The period in those nodes are respectively called {\em forward period}, and {\em backward period}.
+      The weight on the link between the two central nodes is simplified in the forthcoming calculations.
 
@@
 	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots.
-Let us call {\em forward period} the period in the central node when the messages goes to RRH to BBU, and {\em backward period} the period when the messages comes back in the other way.
 Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
@@
     \subsubsection{Exhaustive generation}
-      Décrire l'algo, expliquer les coupes
+	\begin{algorithm}[H]
+	\caption{Exhaustive Generation}  
+	\begin{algorithmic}
+	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
+	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
+	\STATE Forward-budget $\leftarrow$ $P$ - {\cal c} * $\tau$
+	\STATE Backward-budget $\leftarrow$ $P$ - {\cal c} * $\tau$
+	\STATE Free-Intervals $\leftarrow$ list of free intervals, init to $[0;P[$
+	\FORALL{route i in  ${\cal R}_{\cal C}$}
+	\FORALL{j in Free-Intervals }
+	\IF{Message of the route i does not collides with scheduled routes}
+	\STATE $m_i \leftarrow $ the first slot of Free-Intervals[j]
+	\STATE Split the Free-Intervals considering the new packet
+	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
+	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
+	\STATE call Exhaustive Generation on remaining routes
+	\ENDIF
+	\ENDFOR
+	\ENDFOR
+
+      \end{algorithmic}
+      \end{algorithm}
+      {\bf {\em Lost size}}, is the size lost when an interval is too few to put another packet.
+Ex : if the interval [250;3250[ receives a packet of size 2500, there is 500 slots lost, because there is no way to uses the slots for another packet.\\
+
+      This algorithm enumerates all the solutions by traversing a tree. The leaves of the tree are 
+      the $(P\tau)$-periodic affectations, and the nodes are partial solutions. A partial solution is a choice of a starting time for a subset of the routes.
+      For each route, the algorithm tries every possible starting offset until it finds one available (that allows the message to come back without collisions).
+When a route have been scheduled, it take another route that have not been scheduled yet.
+      This creates a new sub-tree in which the algorithm will try every possible starting offset too, and create a sub-tree on the following route too.
+      If no offset are available for a route, this means that the partial solution is not good, so the algorithm backtracks over the tree that is,
+      it goes back to the father of the current sub-tree.
+      Once a leaf is obtained, the algorithm stops and return the scheduling.\\      
+      To reduce the number of useless calculation, in each time we add another packet, we consider the lost size in both periods, thus, we know when a period has no many great enough free area to put a packet.
+
     \subsubsection{Results}

### 2017-02-13 article/article.tex

--- 2017-02-13 article/article.tex
@@
 
-  In this section, we consider a particular case of the model, in which for each $(u,v)$ , the route is the same in both directions.
-This means that ${\cal R}(u,v)$ uses the same arcs as ${\cal R}(v,u)$ in the opposite orientation.
-  \todo{décrire précisément la topologie}
-
   \subsection{Intro}
     PALL NP-Hard car PRA NP-Hard\\
-    Résultats valables sur Topologie 1 avec nos paramètres
-    \todo{J'ai viré star affectation, car je pense qu'il n'y a rien à dire là dessus.}
+
+      In this section, we consider a particular case of the model, in which for each $(u,v)$ , the route is the same in both directions.
+This means that $\forall (u,v) \in {\cal C}, {\cal R}_{\cal C}(u,v)$ uses the same arcs as ${\cal R}_{\cal C}(v,u)$ in the opposite direction.\\
+      Furthermore, the following algorithms and results were designed for a particular topology of network, in which all the routes uses a same common switch.
+        \begin{center}
+	  \includegraphics[scale=0.8]{Fig4.pdf}
+	\end{center}
+      Let us call {\bf LN} (leaves node) the central node connected to leaves, and {\bf SN} (sources node), the one connected to sources.
+The period in those nodes are respectively called {\em forward period}, and {\em backward period}.
+      The weight on the link between the two central nodes is simplified in the forthcoming calculations.
 
@@
 	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
-	\STATE BUDGET $\leftarrow$ $P$ - ${\cal c}$ * $\tau$
-	\STATE offset $\leftarrow$ 0
+	\STATE Forward-budget $\leftarrow$ $P$ - {\cal c} * $\tau$
+	\STATE Backward-budget $\leftarrow$ $P$ - {\cal c} * $\tau$
+	\STATE Free-Intervals $\leftarrow$ list of free intervals, init to $[0;P[$
 	\FORALL{route i in  ${\cal R}_{\cal C}$}
-	\FORALL{j from offset to offset + BUDGET }
-	\IF{Message of the route i does not collides with scheduled routes AND budget > 0}
-	\STATE Give i the offset j
-	\STATE BUDGET $\leftarrow$ BUDGET - (j - offset)
-	\STATE offset $\leftarrow$ j
+	\FORALL{j in Free-Intervals }
+	\IF{Message of the route i does not collides with scheduled routes}
+	\STATE $m_i \leftarrow $ the first slot of Free-Intervals[j]
+	\STATE Split the Free-Intervals considering the new packet
+	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
+	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
 	\STATE call Exhaustive Generation on remaining routes
@@
       \end{algorithm}
+      {\bf {\em Lost size}}, is the size lost when an interval is too few to put another packet.
+Ex : if the interval [250;3250[ receives a packet of size 2500, there is 500 slots lost, because there is no way to uses the slots for another packet.\\
+
+      This algorithm enumerates all the solutions by traversing a tree. The leaves of the tree are 
+      the $(P\tau)$-periodic affectations, and the nodes are partial solutions. A partial solution is a choice of a starting time for a subset of the routes.
+      For each route, the algorithm tries every possible starting offset until it finds one available (that allows the message to come back without collisions).
+When a route have been scheduled, it take another route that have not been scheduled yet.
+      This creates a new sub-tree in which the algorithm will try every possible starting offset too, and create a sub-tree on the following route too.
+      If no offset are available for a route, this means that the partial solution is not good, so the algorithm backtracks over the tree that is,
+      it goes back to the father of the current sub-tree.
+      Once a leaf is obtained, the algorithm stops and return the scheduling.\\      
+      To reduce the number of useless calculation, in each time we add another packet, we consider the lost size in both periods, thus, we know when a period has no many great enough free area to put a packet.
+
     \subsubsection{Results}

### 2017-02-14 article/article.tex
retouche star topology without waiting time

@@
 
-  \subsection{MIN-PRA}
-    Exemple de cas polynomiaux
+  \subsection{Tractable cases of PRA}
 
-\section{The Star Topolgy}
+    In this section, we present a few polynomial cases, in particular when the conflict depth is one.
 
-  \subsection{Intro}
-    PALL NP-Hard car PRA NP-Hard\\
+    The problem PALL seems to be hard to solve, even for very simple classes of graphs, as seen in the next section.
 
-      In this section, we consider a particular case of the model, in which for each $(u,v)$ , the route is the same in both directions.
-This means that $\forall (u,v) \in {\cal C}, {\cal R}_{\cal C}(u,v)$ uses the same arcs as ${\cal R}_{\cal C}(v,u)$ in the opposite direction.\\
-      Furthermore, the following algorithms and results were designed for a particular topology of network, in which all the routes uses a same common switch.
+\section{The Star Topology}
+
+      In this section, we consider graphs with a very simple topology that we call the {\bf star topology}. 
+      First, for each arc $(u,v)$, there is also an arc $(v,u)$ with the same weight.
+      Moreover, there is a special arc, the central arc, which is shared by all routes.
+      All routes consist from an arc from its source to the source node, denoted by {\bf SN},
+      then the central arc to {\bf TN}, the target node, and an arc to its target. In addition to SN and TN,
+      there are two sets $S$ and $T$ of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$. 
+      The routes are the directed paths of the form $s_i,SN,TN,t_i$ and $t_i,TN,SN,s_i$.
+
        \begin{center}
@@
 	\end{center}
-      Let us call {\bf LN} (leaves node) the central node connected to leaves, and {\bf SN} (sources node), the one connected to sources.
+
+      We assume the weight of the central arc to be $0$ since it appears in every route,
+      its value does not matter when considering affectations. Collisions between messages can 
+      only appear at node SN on the way forward and at node TN on the way back. 
+  \todo{Définir la forward period et la backward period et dire à quoi correspond une affectation en terme de forward et backward period (placement de messages dans la première période}     
+%       Therefore, 
+%       finding an $(P,\tau)$-periodic affectation without collision, is equivalent to fix ...
+
+%       
+%       between the two central nodes is simplified in the forthcoming calculations.
+%       Let us call {\bf SN} (source node) the central node connected to leaves, and {\bf SN} (sources node), the one connected to sources.
 The period in those nodes are respectively called {\em forward period}, and {\em backward period}.
-      The weight on the link between the two central nodes is simplified in the forthcoming calculations.
 
-  \subsection{No waiting times}
-    \subsubsection{Shortest-longest}
+  \subsection{Solving PALL without waiting times}
+
+  In this subsection, we deal with a simpler version of the problem PALL.
+  We ask for a $(P,\tau)$-periodic affectation with all waiting times equal to $0$. 
+  In that case $T_{max}$ is not relevant anymore. Since $w_i=0$, choosing $m_i$, the offset of the route from
+  $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + t(r_i)$.
+  Moreover, in this context the weight of the arcs from $s_i$ to SN have no impact, therefore we assume they are 
+  equal to $0$.
+
+    \subsubsection{Shortest-longest policy}
+
+    We present a simple policy, which works when the period is large with regards to the delay of the routes.
+    We send the messages in order from the shortest route to the longest route. 
+    \todo{Preuve en deux lignes que ça ne collisionne pas à condition que la période soit assez grande}
+
       \paragraph{Algo}
       \paragraph{Period}
-    \subsubsection{Greedy Algorithm with higher bound}
+
+    \subsubsection{Greedy Algorithm}
+
+    We introduce a greedy algorithm to build a $(P,\tau)$-periodic affectation, which provably works when
+    the period is large enough with regards to the number of routes and size of messages. In other words, 
+    we can always find a solution when the network is far from saturated.
+
+    \begin{proposition}
+    There is an algorithm, which finds a $(P,\tau)$-periodic affectation in time $O(n^2)$ when $P \geq 3n\tau$.
+    \end{proposition}
+    \begin{proof}
+     We consider the time period at the vertex SN and cut it into consecutive macro slots of time of size $\tau$.
+The algorithm works in the following way: select the first route for which the offset as not been chosen.
+Try every offset which put the message in a
+     free macro slot in the period at SN. It also fixes the position of a message a TN, and we choose the first offset which does not create a collision at TN. 
+     Assume we choose the offset of the route $r_{k+1}$, we have  at least $3n - k$ free macro-slots, since $P \geq 3n\tau$.
+Each of these $3n - k$ possible offset values translates into $3n - k$ positions of messages in the period at TN.
+All these positions are separated by at least $\tau$ slots.
+There are already $k$ messages of size $\tau$ in the period at TN.
+One such message can intersect at most $2k$ potential positions, therefore  amongst the possible $3n - k$ positions, there are  $3n - k -2k$ which are without collision.
+Since $k < n$, one of the choice is without collision, which proves that the algorithm terminates and find a
+     $(P,\tau)$-periodic affectation. To ensure a complexity linear in $n$, it is enough to maintain a list of the free slices at SN and a list of the free intervals at TN. 
+    \end{proof}
+
+    \todo{Avec une structure de données plus maligne on doit pouvoir faire n, non ?}
 
 	\begin{algorithm}[H]
-	\caption{Greedy with Higher bound Period(GHP)}
+	\caption{Greedy affectation}
 	\begin{algorithmic}

### 2017-02-16 article/article.tex
relecture + updates

@@
 
-      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $c$ integers that we call {\bf offsets}, with $c$ the number of routes in $\cal R$.
+      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
 The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in {\cal R}$ at its source.
-      A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}$, that is $\forall (r_i, r_j) \in {\cal R}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
+      A $(P,\tau)$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}$, that is $\forall (r_i, r_j) \in {\cal R_{\cal C}}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
       we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$
@@
 %       Notice that the notion of $P$-periodic affectation \textbf{is not monotone} with regard to $P$. 
-      As an exemple of a $(2,1)$-periodic affectation, let consider a routage graph with routes $\{r_i\}_{i=1,\dots,c}$, such that all pairs of routes intersect at a different edge.
+      As an example of a $(2,1)$-periodic affectation, let consider a routage graph with routes $\{r_i\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
       We set $\tau = 1$ and the delays are chosen so that if $r_i$ and $r_j$ have $v$ as first common vertex then we have $\lambda(v,r_i) - \lambda(v,r_j)=1$.There is a $(2,1)$-periodic affectation by setting all $m_i$ to $0$.
@@
 
-      \noindent {\bf Input:} a routage graph $\cal R$, an integer $\tau$ and an integer $P$.
+      \noindent {\bf Input:} a routage graph $\cal R_{\cal C}$, an integer $\tau$ and an integer $P$.
 
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R$ ?
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R_{\cal C}$ ?
 
@@
 
-      Consider the routage graph ${\cal R}$ given in the previous subsection. 
+      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
       We change the delays so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
-      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
-      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
+      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$.
+In such a graph, there is no $(P,\tau)$-periodic affectation, because of $P < n$.\\
+      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
 
@@
       A \textbf{symmetric} assignment ${\cal C}$, is an involutive function from $S$ to $T$, which maps each element $s\in S$ to ${\cal C}(s)$ and ${\cal C}(s)$ to $s$.
-It can also be seen as the set of pairs $(s,{\cal C}(s))$ and $({\cal C}(s),s)$.
-
+It can also be seen as the set of pairs $(s,{\cal C}(s))$ and $({\cal C}(s),s)$.\\
+      The Routing function ${\cal R}$ associtates to each couple $(s,{\cal C}(s))$ a route called $r_s$ and to each couples $({\cal C}(s),s)$ a route called $r_{{\cal C}(s)}$.\\     
        We are given a period $P$, a routing function ${\cal R}$, and we consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_s$ to the route $r_s$ which begins by $s$.
@@
       \begin{center}
-      \includegraphics[scale=0.2]{rrh.jpeg}
+      \includegraphics[scale=0.3]{rrh.png}
       \end{center}
@@
        \begin{center}
-
-      \includegraphics[scale=0.2]{BBU2.jpeg}
+      \includegraphics[scale=0.3]{BBU2.png}
       \end{center}
@@
 
+  In this article, we works on given routages, but we could imagine a problem, in which, considering a given graph $G = (V,A)$ and a period P, the question is to find, if it exists, a routage graph ${\cal R}_{\cal C}$, in which there is $(P,\tau)$-periodic affectation.
 \section{Solving PRA}
@@
  We will prove the hardness of PRA and PALL for this parameter, which implies the hardness of the general problems. 
-Consider an instance of the problem PRA, i.e., a routage graph $\cal{R}$, a message size $\tau$ and a period $P$. 
+Consider an instance of the problem PRA, i.e., a routage graph $\cal{R_{\cal C}}$, a message size $\tau$ and a period $P$. \\
 The {\bf conflict depth} of a route is the number of other routes which share an edge with it. 
-The conflict depth of a routage graph  $\cal{R}$ is the maximum of the conflict depth of the routes in ${\cal R}$.
+The conflict depth of a routage graph  $\cal{R_{\cal C}}$ is the maximum of the conflict depth of the routes in $\cal{R_{\cal C}}$.\\
 The {\bf load} of a routage graph is the maximal number of routes sharing the same arc.
@@
 
-      \Vertex[x=12,y=3]{l3}
-      \Vertex[x=14,y=4]{l2}
-      \Vertex[x=10,y=2]{l1}
+      \Vertex[x=12,y=3]{t3}
+      \Vertex[x=14,y=4]{t2}
+      \Vertex[x=10,y=2]{t1}
       \tikzstyle{VertexStyle}=[shape = circle, draw, minimum size = 20pt]
@@
       EdgeStyle/.append style = {green} }
-      \Edge[label = 3](s2)(A)
+      \Edge(s2)(A)
       \Edge(A)(B)
@@
       \Edge(C)(D)
-      \Edge(D)(l2)
+      \Edge(D)(t2)
 
@@
       EdgeStyle/.append style = {red} }
-      \Edge[label = 1](s3)(E)
+      \Edge(s3)(E)
       \Edge(E)(F)
-      \Edge(F)(l3) 
+      \Edge(F)(t3) 
 	\tikzset{
       EdgeStyle/.append style = {blue} }
-      \Edge[label = 1](s1)(A)
-      \Edge[label = 1](A)(B)
-      \Edge[label = 1](B)(E)
+      \Edge(s1)(A)
+      \Edge(A)(B)
+      \Edge(B)(E)
       \Edge(E)(F)
-      \Edge(F)(l1)
+      \Edge(F)(t1)
 
@@
       Moreover, there is a special arc, the central arc, which is shared by all routes.
-      All routes consist from an arc from its source to the source node, denoted by {\bf SN},
-      then the central arc to {\bf TN}, the target node, and an arc to its target. In addition to SN and TN,
-      there are two sets $S$ and $T$ of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$. 
-      The routes are the directed paths of the form $s_i,SN,TN,t_i$ and $t_i,TN,SN,s_i$.
+      All routes consist from an arc from its source to the central source node, denoted by {\bf $c_s$},
+      then the central arc to {\bf $c_t$}, the central target node, and an arc to its target.
+In addition to those central nodes, there are two sets of vertices, $S$ and $T$, of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$.
+      The routes are the directed paths of the form $s_i,c_s,c_t,t_i$ and $t_i,c_t,c_s,s_i$.
 
@@
       its value does not matter when considering affectations. Collisions between messages can 
-      only appear at node SN on the way forward and at node TN on the way back. 
-  \todo{Définir la forward period et la backward period et dire à quoi correspond une affectation en terme de forward et backward period (placement de messages dans la première période}     
+      only appear at node $c_s$ on the way forward and at node $c_t$ on the way back. \\
+      Let us call {\bf forward period} and {\bf backward period} the time windows in respectively $c_s$ and $c_t$.
+A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1})$ in the forward period, and  $c_t$ at time $m_{{\cal C}(s_1)} + t(c_t,r_{{\cal C}(s_1)})$ in the backward period.
+      A $(P,\tau)$-periodic affectation consist in choosing $\forall i \in n, m_i$, and $m_{{\cal C}(s_i)}$ such that, for any couples of routes $(r_{s_j}, r_{s_k}), j,k \in n$,
+      we have $[t(c_s,r_j)] \cap [t(c_s,r_k)] = \emptyset$.
+      and for any couples of routes $(r_{{\cal C}(s_j)}, r_{{\cal C}(s_k)}), j,k \in n$, we have $[t(c_s,r_{{\cal C}(s_j)})] \cap [t(c_s,r_{{\cal C}(s_k)})] = \emptyset$
+%       
+%   \todo{Définir la forward period et la backward period et dire à quoi correspond une affectation en terme de forward et backward period (placement de messages dans la première période}     
 %       Therefore, 
@@
   In that case $T_{max}$ is not relevant anymore. Since $w_i=0$, choosing $m_i$, the offset of the route from
-  $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + t(r_i)$.
-  Moreover, in this context the weight of the arcs from $s_i$ to SN have no impact, therefore we assume they are 
-  equal to $0$.
+  $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i)$.
+  Moreover, in this context the weight of the arcs from $s_i$ to $c_s$ have no impact, therefore we assume they are 
+  equal to $0$. Thus, in this case, we can consider only the forward and backward periods. The goal is now to put messages in the forward periods such that there is no collisions in the both periods.
 
@@
     \begin{proof}
-     We consider the time period at the vertex SN and cut it into consecutive macro slots of time of size $\tau$.
+     We consider the forward period and cut it into consecutive macro slots of time of size $\tau$.
 The algorithm works in the following way: select the first route for which the offset as not been chosen.
 Try every offset which put the message in a
-     free macro slot in the period at SN. It also fixes the position of a message a TN, and we choose the first offset which does not create a collision at TN. 
+     free macro slot in the forward period. It also fixes the position of a message in the backward period, and we choose the first offset which does not create a collision in the backward period. 
      Assume we choose the offset of the route $r_{k+1}$, we have  at least $3n - k$ free macro-slots, since $P \geq 3n\tau$.
-Each of these $3n - k$ possible offset values translates into $3n - k$ positions of messages in the period at TN.
+Each of these $3n - k$ possible offset values translates into $3n - k$ positions of messages in the backward period.
 All these positions are separated by at least $\tau$ slots.
-There are already $k$ messages of size $\tau$ in the period at TN.
+There are already $k$ messages of size $\tau$ in the backward period.
 One such message can intersect at most $2k$ potential positions, therefore  amongst the possible $3n - k$ positions, there are  $3n - k -2k$ which are without collision.
 Since $k < n$, one of the choice is without collision, which proves that the algorithm terminates and find a
-     $(P,\tau)$-periodic affectation. To ensure a complexity linear in $n$, it is enough to maintain a list of the free slices at SN and a list of the free intervals at TN. 
+     $(P,\tau)$-periodic affectation.
+To ensure a complexity linear in $n$, it is enough to maintain a list of the free slices in the forward period and a list of the free intervals in the backward period.
     \end{proof}
+
+      \begin{center}
+      \includegraphics[scale=0.3]{ex3nt.png}
+      \end{center}
 
@@
 	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
-	\STATE $P1[P]$ slots of size $\tau$ in first way period.
-	\STATE $P2[P]$ slots  of size $\tau$ in back way period.
-	\FORALL{route i in ${\cal R}_{\cal C}$ }
+	\STATE $P1[P]$ slots of size $\tau$ in forward period.
+	\STATE $P2[P]$ slots  of size $\tau$ in backward period.
+	\FORALL{source i in S }
 
@@
 	\end{algorithm}
-      \paragraph{Period}
-	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
-	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots.
+%       \paragraph{Period}
+% 	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
+% 	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots.
 Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
-      \begin{center}
-      \includegraphics[scale=0.2]{ex3nt.png}
-      \end{center}
-	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period.
+
+% 	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period.
 Those $3.c - k$ gives us $3.c - k$ possible slots in the backward periods.\\
-	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period.
+% 	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period.
 Since $k<c$,  $2k < 3.c - k$, thus using the pigeonhole principle, there is at least one free slot in the backward period for the new message.
@@
 	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
-	\STATE Forward-budget $\leftarrow$ $P$ - {\cal c} * $\tau$
-	\STATE Backward-budget $\leftarrow$ $P$ - {\cal c} * $\tau$
+	\STATE Forward-budget $\leftarrow$ $P$ - n * $\tau$
+	\STATE Backward-budget $\leftarrow$ $P$ - n * $\tau$
 	\STATE Free-Intervals $\leftarrow$ list of free intervals, init to $[0;P[$

### 2017-02-16 article/article.tex
code

@@
   Moreover, in this context the weight of the arcs from $s_i$ to $c_s$ have no impact, therefore we assume they are 
-  equal to $0$. Thus, in this case, we can consider only the forward and backward periods. The goal is now to put messages in the forward periods such that there is no collisions in the both periods.
+  equal to $0$.
+Thus, in this case, we can consider only the forward and backward periods.
+The goal is now to put messages in the forward periods such that there is no collisions in the both periods.\\
+  In this section, the offsets $m_{s_i}, i<n$ are in reality $[t(c_s,r_{s_i})]$, but to find the real values, there is just to change the values of the offset considering the dealy of the arcs $(s_i, c_s) , \forall i$.
 
@@
 
+    \paragraph{Algo}
     We present a simple policy, which works when the period is large with regards to the delay of the routes.
-    We send the messages in order from the shortest route to the longest route. 
-    \todo{Preuve en deux lignes que ça ne collisionne pas à condition que la période soit assez grande}
+    We send the messages in order from the shortest route to the longest route, on after each others in the forward period.
 
-      \paragraph{Algo}
+The message using the shortest route is sent before the others, so it comes back to the central node before the following ones.
+Recursively, the second message is sent before the others, and also will be back before the following messages. 
+Because the second message is sent T slots after the first message ($m_{s_2} = m_{s_1} + \tau$, it comes back after
+the end of the message one: $m_{s_1}+ \tau + 2.\lambda(r_{{\cal C}(s_1)}) \le m_{s_2} + 2.\lambda(r_{{\cal C}(s_2)})$ with $\lambda(r_{{\cal C}(s_2)}) \ge \lambda(r_{{\cal C}(s_1)})$.
+
       \paragraph{Period}
+The period given by this policy is $P = \tau * n + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0}))$, if routes $\{r_0,...,r_{s_{n-1}}\}$ are ordered
+from the shortest to the longest. $2.\lambda(r_{s_0})$ is the first slot in which the first message is coming back in the backward period,
+and 2$\lambda(r_{s_{n-1}}) + n . \tau $ is the time at which the last message has totally passed the switch.
+Therefore, the period only depends of the difference between the longest and the shortest route: the larger this value is, the larger
+the period is.
 
@@
 
-	\STATE $o_i \leftarrow j$
+	\STATE $m_{s_i} \leftarrow j$
 	\ENDIF
@@
 	\IF{Message of the route i does not collides with scheduled routes}
-	\STATE $m_i \leftarrow $ the first slot of Free-Intervals[j]
+	\STATE $m_{s_i} \leftarrow $ the first slot of Free-Intervals[j]
 	\STATE Split the Free-Intervals considering the new packet

### 2017-02-16 code/bruteforce.c

@@ -1,0 +1,249 @@
+
+
+#include <stdio.h>
+#include <stdlib.h>
+#include "struct.h"
+#include <assert.h>
+//intervalle fermé à gauche et ouvert à droite
+// le codage debut, taille serait sans doute légèrement mieux
+typedef struct{
+  int debut;
+  int fin;
+  int suivant;
+}intervalle_liste;
+
+intervalle_liste *initialise(int nbr_route,int taille_paquets, int periode){//initialise les intervalles de temps restants pour le retour
+  intervalle_liste* l= malloc(sizeof(intervalle_liste)*nbr_route);
+  l[0].suivant = -1;
+  l[0].debut = taille_paquets;
+  l[0].fin = periode;
+  return l;
+} 
+
+void affiche_intervalle(intervalle_liste *liste){
+  int pos = 0;
+  while(pos != -1 ){
+    printf("[%d,%d[  ",liste[pos].debut,liste[pos].fin);
+    pos = liste[pos].suivant;
+  }
+  printf("\n");
+}
+
+
+int ajoute_element(intervalle_liste *liste, int debut, int taille, int taille_paquets, int *nombre_slot, int nbr_route){//renvoie 0 si l'insertion n'est pas possible, 1 sinon et modifie alors liste
+  //pour couper en deux l'intervalle approprié
+  int pos=0;
+  while(pos != -1){//détecte l'intervalle à découper si il existe
+    if(liste[pos].debut <= debut && liste[pos].fin - debut >=  taille_paquets){//l'intervalle existe, on le découpe
+      //on calcule le nombre de slot après décooupage (en prenant en compte les paquets déjà placés)
+      *nombre_slot+= (debut - liste[pos].debut)/taille_paquets +  (liste[pos].fin - debut)/taille_paquets -  (liste[pos].fin - liste[pos].debut)/taille_paquets;
+      if(*nombre_slot >= nbr_route){ // si le nombre de slots retour est insuffisant, on ne permet pas l'ajout de l'élément à cet endroit     
+      liste[taille].debut = debut + taille_paquets;
+      liste[taille].fin = liste[pos].fin;
+      liste[taille].suivant = liste[pos].suivant;
+      liste[pos].fin = debut;
+      liste[pos].suivant = taille;
+      return 1;
+      }
+      else{  
+		*nombre_slot+=1;
+		return 0;
+		}
+		
+    }
+    pos = liste[pos].suivant;
+  }
+  return 0;
+}
+
[…]

### 2017-02-16 code/code.c

@@ -3,11 +3,9 @@
 #include <assert.h>
 #include <time.h>
 
+#include "struct.h"
+#include "bruteforce.h"
 
-typedef struct graphe{
-	int N; //nombre de sommets
-	int ** matrice;//matrice d'adjacence pondérée
-}Graphe ;
 
 void affiche_matrice(Graphe g)
 {
@@ -47,7 +45,7 @@ Graphe init_graphe(int N)
 //prends un graphe vide en argument et le transforme en etoile
 void graphe_etoile(Graphe g,int taille_liens)
 {
-	if(!g.N%2){printf("Impossible de générer une étoile avec un nombre pair de sommets\n");exit(5);}
+	if(!(g.N%2)){printf("Impossible de générer une étoile avec un nombre pair de sommets\n");exit(5);}
 	int pivot = g.N/2;
 	int alea;
 	for(int i=0;i<g.N;i++)
@@ -86,11 +84,59 @@ void affiche_periode(int *p, int periode)
 	}
 	printf("\n");
 }
+void affiche_tab(int * tab, int taille)
+{
+	for(int i=0;i<taille;i++)
+	{
+		printf("%d ",tab[i]);
+	}
+	printf("\n");
+}
+void tri_bulles(int* tab,int taille)
+{
+	int sorted;
+	int tmp;
+	for(int i=taille-1;i>=1;i--)
+	{
+		sorted = 1;
+		for(int j = 0;j<=i-1;j++)
+		{
+			if(tab[j+1]<tab[j])
+			{
+				tmp = tab[j+1];
+				tab[j+1]= tab[j];
+				tab[j]= tmp;
+				sorted = 0;
+			}
+			if(sorted)return;
+		}
+	}
+}
+
+//retourne -1 si la periode donnée ne donne pas de solutions, la taille de la periode sinon
+int algo_shortest_longest(Graphe g,int periode,int taille_message)
+{
+	if(!(g.N%2)){printf("G n'est peut être pas une étoile\n");exit(5);}
+	int nb_routes = g.N/2;
+	int min = g.matrice[nb_routes][nb_routes+1];
+	int max = min;
+	for(int i=1;i<nb_routes;i++)
+	{
+		if(g.matrice[nb_routes][i+nb_routes+1] < min)
+			min = g.matrice[nb_routes][i+nb_routes+1];
+		if(g.matrice[nb_routes][i+nb_routes+1] > max)
+			max = g.matrice[nb_routes][i+nb_routes+1];
+	}
[…]

### 2017-02-16 code/struct.h

@@ -1,0 +1,5 @@
+
+typedef struct graphe{
+	int N; //nombre de sommets
+	int ** matrice;//matrice d'adjacence pondérée
+}Graphe ;

### 2017-02-20 article/article.tex
dessin

@@
 
-     \todo{Dire après  la définition des problèmes qu'on pourrait demander de trouver l'assignement et même le routage pour optimiser, mais pas dans cet article
-     et qu'on travail avec des réseaux déjà constitués}
       \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}
@@
 
-      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
-The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in {\cal R}$ at its source.
-      A $(P,\tau)$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}$, that is $\forall (r_i, r_j) \in {\cal R_{\cal C}}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
+      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R_{\cal C}$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R_{\cal C}$.
+The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in \cal R_{\cal C}$ at its source.
+      A $(P,\tau)$-periodic affectation must have no {\bf collision} between two routes in $\cal R_{\cal C}$, that is $\forall (r_i, r_j) \in {\cal R_{\cal C}}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
       we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$
@@
        \begin{center}
-      \includegraphics[scale=0.7]{Fig5.pdf}
+
+\begin{tikzpicture}
+
+\tikzset{
+  LabelStyle/.style = { rectangle, rounded corners, draw,
+                       font = \bfseries },
+  EdgeStyle/.append style = {->} }
+  \SetGraphUnit{5}
+  \node[draw,circle] (s3) at (4, 2) {$s_3$}; 
+  \node[draw,circle] (s2) at (0, 4) {$s_2$}; 
+  \node[draw,circle] (s1) at (0, 6) {$s_1$};
+
+  \node[draw,circle] (t3) at (14, 7) {$t_3$}; 
+  \node[draw,circle] (t2) at (14, 4) {$t_2$}; 
+  \node[draw,circle] (t1) at (10, 2) {$t_1$};
+
+  \SetVertexNoLabel
+  \Vertex[x=2,y=5]{A}
+  \Vertex[x=4,y=5]{B}
+  \Vertex[x=10,y=5]{C}
+  \Vertex[x=12,y=5]{D}
+  \Vertex[x=6,y=3]{E}
+  \Vertex[x=8,y=3]{F}
+  \tikzset{
+  EdgeStyle/.append style = {green} }
+  \Edge[label = 2](s2)(A)
+  \Edge[label = 1](A)(B)
+  \Edge[label = 2](B)(C)
+  \Edge[label = 1](C)(D)
+  \Edge[label = 1](D)(t2)
+
+   \tikzset{
+  EdgeStyle/.append style = {red} }
+  \Edge[label = 2](s3)(E)
+  \Edge[label = 1](E)(F)
+  \Edge[label = 1](F)(C)
+  \Edge[label = 1](C)(D)
+  \Edge[label = 1](D)(t3) 
+     \tikzset{
+  EdgeStyle/.append style = {blue} }
+  \Edge[label = 1](s1)(A)
+  \Edge[label = 1](A)(B)
+  \Edge[label = 1](B)(E)
+  \Edge[label = 1](E)(F)
+  \Edge[label = 1](F)(t1)
+
+\end{tikzpicture}
       \end{center}
@@
 	\begin{lemma} 
-	 For any odd $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
+	 For any odd $P$, there is a routage graph such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
 	\end{lemma}
@@
 In such a graph, there is no $(P,\tau)$-periodic affectation, because of $P < n$.\\
-      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
+      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R_{\cal C}}$.
 
@@
 It can also be seen as the set of pairs $(s,{\cal C}(s))$ and $({\cal C}(s),s)$.\\
-      The Routing function ${\cal R}$ associtates to each couple $(s,{\cal C}(s))$ a route called $r_s$ and to each couples $({\cal C}(s),s)$ a route called $r_{{\cal C}(s)}$.\\     
-       We are given a period $P$, a routing function ${\cal R}$, and we consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_s$ to the route $r_s$ which begins by $s$.
+      The Routing function ${\cal R}$ associates to each couple $(s,{\cal C}(s))$ a route called $r_s$ and to each couples $({\cal C}(s),s)$ a route called $r_{{\cal C}(s)}$.\\     
+       We are given a period $P$, a routing function ${\cal R}$, and we consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_s$ to the route $r_s$ which begins by $s$, and $m_{C(s)}$ to the routes $r_{C(s)}$ which begins by $C(s)$.
 This affectation represents the following process: first a message is sent at $s$, through the route $r_s$, at time $m_s$.

### 2017-02-20 code/code.c

@@ -41,6 +41,14 @@ Graphe init_graphe(int N)
 	g.matrice = declare_matrice(N);
 	return g;
 }
+void libere_matrice(Graphe g)
+{
+	for(int i=0;i<g.N;i++)
+	{
+		free(g.matrice[i]);
+	}
+	free(g.matrice);
+}
 
 //prends un graphe vide en argument et le transforme en etoile
 void graphe_etoile(Graphe g,int taille_liens)
@@ -262,7 +270,7 @@ void simuls_periode(int nb_routes, int taille_message, int taille_routes,int nb_
 			total_3NT += linear_3NT(g,taille_message);
 			total_prime += linear_prime(g,taille_message);
 			fprintf(stdout,"\rStep%5d /%d",i+1,nb_simuls);fflush(stdout);
-			free(g.matrice);
+			libere_matrice(g);
 		}
 		printf("\n");
 		printf("P moyen (sur %d simulations) 3NT  : %lld\n",nb_simuls,total_3NT/nb_simuls);
@@ -283,7 +291,7 @@ void echec(int nb_routes, int taille_message,int taille_routes, int nb_simuls)
 	long long int total_3NT, total_brute, total_sl;
 
 
-	for(int j = taille_message*nb_routes ; j<=3*taille_message*nb_routes;j+=100)
+	for(int j = taille_message*nb_routes ; j<=3*taille_message*nb_routes;j+=1)
 	{
 		
 		total_3NT = 0;
@@ -293,11 +301,11 @@ void echec(int nb_routes, int taille_message,int taille_routes, int nb_simuls)
 		for(int i = 0;i<nb_simuls;i++)
 		{
 			g = init_graphe(nb_routes *2 +1);
-			graphe_etoile(g,j);
+			graphe_etoile(g,taille_routes);
 			if(algo_3NT(g,j,taille_message) != -1) total_3NT++;
-			if(bruteforceiter(g,j,taille_message) != -1) total_brute++;
+			//if(bruteforceiter(g,j,taille_message) != -1) total_brute++;
 			if(algo_shortest_longest(g,j,taille_message)!= -1) total_sl++;
-			free(g.matrice);
+			libere_matrice(g);
 			fprintf(stdout,"\rStep = %5d/%d [Period : %d]",i+1,nb_simuls,j);fflush(stdout);
 		}
 
@@ -311,7 +319,7 @@ int main()
 {
 	srand(time(NULL));
[…]

### 2017-02-21 article/article.tex
courbes

@@
       The Routing function ${\cal R}$ associates to each couple $(s,{\cal C}(s))$ a route called $r_s$ and to each couples $({\cal C}(s),s)$ a route called $r_{{\cal C}(s)}$.\\     
-       We are given a period $P$, a routing function ${\cal R}$, and we consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_s$ to the route $r_s$ which begins by $s$, and $m_{C(s)}$ to the routes $r_{C(s)}$ which begins by $C(s)$.
+       We are given a period $P$, a routing function ${\cal R}$, and we consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_s$ to the route $r_s$ which begins by $s$, and $m_{{\cal C}(s)}$ to the routes $r_{{\cal C}(s)}$ which begins by ${\cal C}(s)$.
 This affectation represents the following process: first a message is sent at $s$, through the route $r_s$, at time $m_s$.
@@
   Let $H=(V,E)$ be a graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is edge-colorable
-  with $d$ or $d+1$ colors.
-The edge coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness.
-We define from $H$ an instance of PRA as follows.
-The graph $G$ has for vertices $v_1, v_2$ for each $v$ in $V$
-  and $s_{u,v}, t_{u,v}$ for each $(u,v) \in E$. The set $A$ of arcs of $G$ is: 
-  $$ \{(v_1,v_2) \mid v\in V\} \cup \{(u_2,v_1)\mid u \neq v \in V^2\} \cup \{(s_{u,v},u_1),(v_2,t_{u,v}) \mid (u,v) \in E \}. $$
+  with $d$ or $d+1$ colors. The edge coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness. We define from $H$ an instance of PRA as follows. 
+  For each $v$ in $V$, the graph $G$ has two vertices $v_1, v_2$, and for each $(u,v) \in E$,the graph g has two vertices $s_{u,v}, t_{u,v}$.
+
+%   The set $A$ of arcs of $G$ is: 
+%   $$ \{(v_1,v_2) \mid v\in V\} \cup \{(u_2,v_1)\mid u \neq v \in V^2\} \cup \{(s_{u,v},u_1),(v_2,t_{u,v}) \mid (u,v) \in E \}. $$
+  For each edge $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.  
+  The set of arcs of G is the union between all the arcs of the previous routes.
+  The affectation ${\cal C}$ is the set of pair of vertices $(s_{u,v}, t_{u,v})$.
+
   All these arcs are of weight $0$.
-  For each edge $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.  
-  The affectation ${\cal C}$ is the set of pair of vertices $(s_{u,v}, t_{u,v})$.
 
@@
       only appear at node $c_s$ on the way forward and at node $c_t$ on the way back. \\
-      Let us call {\bf forward period} and {\bf backward period} the time windows in respectively $c_s$ and $c_t$.
+      In such a topology, there is only two possible collision points between the routes : $c_s$ and $c_t$.
+To avoid collisions, we only have to check if there is no collisions in a period on those two points.
+      Let us take a period P for each central nodes, that are called the {\bf forward period} and the {\bf backward period} for, respectively $c_s$ and $c_t$.
 A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1})$ in the forward period, and  $c_t$ at time $m_{{\cal C}(s_1)} + t(c_t,r_{{\cal C}(s_1)})$ in the backward period.
@@
   Moreover, in this context the weight of the arcs from $s_i$ to $c_s$ have no impact, therefore we assume they are 
-  equal to $0$.
-Thus, in this case, we can consider only the forward and backward periods.
+  equal to $0$. \\
+  For those reasons, in this case, we only have to consider the forward and backward periods.
+Indeed, setting the offset $m_{s_i}$ in the forward period automatically set the offsets $m_{{\cal C}(s_i)}$ in the backward period.
   The goal is now to put messages in the forward periods such that there is no collisions in the both periods.\\
-  In this section, the offsets $m_{s_i}, i<n$ are in reality $[t(c_s,r_{s_i})]$, but to find the real values, there is just to change the values of the offset considering the dealy of the arcs $(s_i, c_s) , \forall i$.
+  In this section, the offsets $m_{s_i}$ are in reality $[t(c_s,r_{s_i})]$, but to find the real values, there is just to change the values of the offset considering the delay of the arcs $(s_i, c_s) , \forall i$.
 
@@
     We present a simple policy, which works when the period is large with regards to the delay of the routes.
-    We send the messages in order from the shortest route to the longest route, on after each others in the forward period.
+    Send the messages in order from the shortest route to the longest route, on after each others in the forward period, without any slots between two messages, that is $m_{s_i} = \tau.i$, if the routes $r_i$ are ordered by $\lambda(r_i)$ from the shortest to the longest one.
 
 The message using the shortest route is sent before the others, so it comes back to the central node before the following ones.
-Recursively, the second message is sent before the others, and also will be back before the following messages. 
-Because the second message is sent T slots after the first message ($m_{s_2} = m_{s_1} + \tau$, it comes back after
-the end of the message one: $m_{s_1}+ \tau + 2.\lambda(r_{{\cal C}(s_1)}) \le m_{s_2} + 2.\lambda(r_{{\cal C}(s_2)})$ with $\lambda(r_{{\cal C}(s_2)}) \ge \lambda(r_{{\cal C}(s_1)})$.
+Then, the second message is sent before the others, and also will be back before the third etc... 
+Because the second message is sent $\tau$ slots after the first message ($m_{s_2} = m_{s_1} + \tau$, it comes back after
+the end of the message one: $m_{s_1}+ \tau + 2.\lambda(r_{s_1}) \le m_{s_2} + 2.\lambda(r_{s_2})$ because of $\lambda(r_{s_2}) \ge \lambda(r_{s_1})$.
 
       \paragraph{Period}
-The period given by this policy is $P = \tau * n + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0}))$, if routes $\{r_0,...,r_{s_{n-1}}\}$ are ordered
-from the shortest to the longest. $2.\lambda(r_{s_0})$ is the first slot in which the first message is coming back in the backward period,
+      To ensure that there is no collisions in the backward period, we must ensure that the last message will not collide with the first message of the next period.
+We have to find the minimum period P such that the last message have totally came back before P slots after the first message.
+
+      The this policy ensure us a period of $$P = \tau * n + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0}))$$ if routes $\{r_0,...,r_{s_{n-1}}\}$ are ordered
+from the shortest to the longest. 
+ \begin{proof}
+We have to calculate the time taken by the last message to reach $c_t$. $2.\lambda(r_{s_0})$ is the first slot in which the first message is coming back in the backward period,
 and 2$\lambda(r_{s_{n-1}}) + n . \tau $ is the time at which the last message has totally passed the switch.
@@
 the period is.
+  \end{proof}
 
@@
      $(P,\tau)$-periodic affectation. 
-To ensure a complexity linear in $n$, it is enough to maintain a list of the free slices in the forward period and a list of the free intervals in the backward period.
      \end{proof}
@@
      \subsubsection{LSG}
+
+To find a solution allowing waiting times, the following heuristic is suggested:
+
+On leaves switch, the messages are scheduled so that they are following each others, from the one using the longest route, to the one using the shortest route.
+
+On sources switch, the politic is the following one, after setting the clock to 0, do:
+\begin{enumerate}
+ \item To be eligible, a job needs to be able to come back on the switch at the current clock (if clock = 0, take the first message able to come back).
+ \item Between the eligible jobs, schedule first the one which has the longest route gives it the starting time $o_i = clock$.
+ \item Update the clock at the time in which the scheduled task is over: $$clock = clock + message\ length$$.
+\end{enumerate}
+
+This algorithm defines the offsets of the first $P$-periodic affectation by sending the messages from the longest route to the shortest route, then it uses a greedy algorithm to schedule the messages in the second $P$-periodic affectation.
+We denote this algorithm by LSG (Longest Shortest + Greedy).
+
+\begin{algorithm}[H]
+\caption{LSG}
+\begin{algorithmic}
+\REQUIRE Matched graph $N$, period $P$, packet size T
+\ENSURE 2way Trip affectation in P
+\STATE clock $\leftarrow$ 0
+\FORALL{route i in $\rho$ from the longest to the shortest }
+\STATE  $m_i \leftarrow$ clock
+\STATE clock $\leftarrow$ clock + T
+\ENDFOR
+\STATE clock $\leftarrow$ 0
+\STATE take i such that $r_i$ is the first route to come back in sources switch
+\STATE $o_i \leftarrow $ clock;
+\STATE clock $\leftarrow$ $a_i$ + T
+\WHILE{there is a route which has no $w_i$}
+\STATE take i such that $r_i$ is the eligible route.
+\STATE $o_i \leftarrow $ clock - $a_i$;
+\STATE clock $\leftarrow$ clock + T
+
+\ENDWHILE
+
+\end{algorithmic}
+\end{algorithm}
+
 	\paragraph{Algorithm}

### 2017-02-21 code/bruteforce.c

@@ -118,7 +118,7 @@ void print_sol(int *solution_pos,int *solution_num,int nbr_route,int budget){
 //on pourrait utiliser un entier dont les bits représente les routes restantes et trouver la première route libre avec une instruction processeur spéciale
 
 int bruteforceiter(Graphe g, int periode,int taille_paquets){
-
+  int compteur = 0;
  
   if(!(g.N%2)){printf("G n'est peut être pas une étoile\n");exit(5);}
 
@@ -173,6 +173,16 @@ int bruteforceiter(Graphe g, int periode,int taille_paquets){
 
 
 	while(solution_taille > 0){
+    compteur++;
+    if(compteur==10000000)
+    {
+      free(solution_num);
+    free(solution_pos);
+    free(route_restante);
+    free(temps_retour);
+    return -1;
+
+    }
     if(solution_taille == nbr_route) {
 		//print_sol(solution_pos,solution_num,nbr_route,budget);
 		//printf("PERIODE %d \n",periode);

### 2017-02-21 code/code.c

@@ -291,7 +291,7 @@ void echec(int nb_routes, int taille_message,int taille_routes, int nb_simuls)
 	long long int total_3NT, total_brute, total_sl;
 
 
-	for(int j = taille_message*nb_routes ; j<=3*taille_message*nb_routes;j+=1)
+	for(int j = taille_message*nb_routes ; j<=3*taille_message*nb_routes;j+=100)
 	{
 		
 		total_3NT = 0;
@@ -303,7 +303,7 @@ void echec(int nb_routes, int taille_message,int taille_routes, int nb_simuls)
 			g = init_graphe(nb_routes *2 +1);
 			graphe_etoile(g,taille_routes);
 			if(algo_3NT(g,j,taille_message) != -1) total_3NT++;
-			//if(bruteforceiter(g,j,taille_message) != -1) total_brute++;
+			if(bruteforceiter(g,j,taille_message) != -1) total_brute++;
 			if(algo_shortest_longest(g,j,taille_message)!= -1) total_sl++;
 			libere_matrice(g);
 			fprintf(stdout,"\rStep = %5d/%d [Period : %d]",i+1,nb_simuls,j);fflush(stdout);
@@ -319,7 +319,7 @@ int main()
 {
 	srand(time(NULL));
 	//simuls_periode(15,2500,10000,1000);
-	echec(8,2500,25000,10000);
+	echec(8,2500,25000,1000);
 
 	return 0;
 }

### 2017-02-22 article/article.tex
longest shortest intro db

@@
 
-\section{Introduction}
-  \begin{itemize}
-    \item Context and problematic
-    \item Related works
-    \item Article contribution
-  \end{itemize}
+The evolutions proposed in next generations of mobile network architectures aim at evolving toward centralized radio network architectures (C-RAN, for Cloud Radio Access Network) to reduce consumption costs and power at the base stations \cite{Mo11}.
+This type of architecture faces the challenge of mastering the latency in the transfer process between the Remote Radio Heads (RRHs) on the field and baseband units (BBUs) in the cloud.
+Low latency is already critical for the deployment of C-RAN approach.
+The standard requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in less than from 1 to 10ms \cite{BM12}
+(depending on targeted services).
+One specificity in the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRH and BBU (this HARQ constraints must be enforced for each frame emitted every millisecond).
+
+ Thus in this article, we work on latency and periodicity constraints in fronthaul.
+The best current solution is to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches \cite{GPA16}.
+This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
+It is then needed to find a solution to offer low latency over commoditized packet based networks.
+Indeed,  dynamical optical bypass and dynamical management of the emission should be considered to guarantee latency constraints, as it is considered in the french ANR project N-GREEN.
+This project proposes a new type of switching/routing node and a specific network architecture exploiting WDM packets thanks to a new generation of optical add/drop multiplexers (WSADM: WDM slotted add/drop multiplexer).
+These packets having a fixed duration close to $1\mu $s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.\\
+
+ Thus, new scheduling and routing paradigms and new technologies have to be considered to  guarantee  delay constrained periodic data transfers.
+One of the most promising approaches relies on the concept of Deterministic Networking (DN) such that one get rid of
+ statistical multiplexing. The traditional queue managements are replaced by time based forwarding. Solutions for Deterministic
+ Networking are under standardization in IEEE 802.1 TSN group \cite{FT16}, as well at IETF DetNet working group \cite{ieee802}.
+Several patents on concepts and mechanisms for DetNet have been already published, see for example \cite{Ho05,LM16}.
+To make DN working over a
+ network composed of several nodes, it is required to manage the time at which the packets of deterministic paths are crossing each nodes.
+The major difficulty of this problem is the periodicity of the process.
+Indeed, a deterministic sending for the messages
+between each pair BBU/RRH must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous
+and following periods.\\
+
+Considering a graph, modeling the network topology, and a set of routes from source nodes (modeling connections to the BBU) and destination
+nodes (modeling the RRH) in this graph, the purpose is to select, for each destination node a route from one source node to it and a periodic
+routing scheme allowing to periodically sent a packet to each base station without congestion conflicts between all such packets and to insure a minimum latency.
+In a slotted time model, the aim is here to minimize the duration of the period, with a constraint of the maximum length of routes to be
+selected. Even if the selected set of routes is given this optimization problem has been shown to be  \NP-hard. From an algorithmic point of view,
+the purpose of this project is first, to study the complexity and the approximability of this problem when the length of the routes is small
+(which corresponds to realistic cases), and secondly, to propose and implement some heuristics to solve this problem on realistic topologies.\\
+
+This problem may look like wormhole problem \cite{cole1996benefit}, very popular few years ago, but here, we want to minimize the time lost in buffers and not just avoid the deadlock, and the wormhole does not treat about the periodicity.
+Several graph colorings have been introduced to model similar problems such as the allocation of frequencies \cite{BM98}, bandwidths \cite{EJ01}[17] or routes \cite{CS96}[18] in a network or train schedules \cite{St07}[19].
+Unfortunately, they do not take into account the periodicity and the associated problems are also NP-complete.
+The only model which incorporates some periodicity is the circular coloring \cite{Zho13, Zhu01,Zhu06}but is not expressive enough to capture our problem.
+
+\subsection*{Paper organisation}
+ In the next section, ...
 
@@
   We ask for a $(P,\tau)$-periodic affectation with all waiting times equal to $0$. 
-  In that case $T_{max}$ is not relevant anymore. Since $w_i=0$, choosing $m_i$, the offset of the route from
+  In that case $MT({\cal M})$ is not relevant anymore. Since $w_i=0$, choosing $m_i$, the offset of the route from
   $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i)$.
@@
 
-    \paragraph{Algo}
+    \paragraph{Algorithm}
     We present a simple policy, which works when the period is large with regards to the delay of the routes.
@@
    \subsection{Allowing waiting times}
+
      \subsubsection{Intro}
-	Importance des waiting times quand la période est donnée (Résultats D'éxepriences et preuve avec l'exemple)
+	  We now consider waiting times.
+The weights on links from sources to $c_s$ are now relevant because the goal is to minimize $MT({\cal M})$, with ${\cal M}$ the $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$.
+	  To build such a $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, we must choose the offsets $m_{s_i}$ and $m_{\cal C(s_i)}$, such that there is no $PT(s)$ superior than a given $T_{max}$.
+	  As a reminder, $ PT(s)=\lambda(r_s)+ w_s+\lambda(r_{{\cal C}(s)})$.
      \subsubsection{LSG}
 
-To find a solution allowing waiting times, the following heuristic is suggested:
+To find a solution with waiting times, the following heuristic is suggested:
 
-On leaves switch, the messages are scheduled so that they are following each others, from the one using the longest route, to the one using the shortest route.
+On the forward period, the messages are scheduled so that they are following each others, from the one using the longest route, to the one using the shortest route.
+Thus, we set the $m_{s_i}$ of the routes such that  $t(c_s,r_{s_i}) = \tau.i$, if the routes $r_i$ are ordered from the longest to the shortest.
 
-On sources switch, the politic is the following one, after setting the clock to 0, do:
+On $c_t$, the politic is the following one, after setting the clock to 0, do:
 \begin{enumerate}
  \item To be eligible, a job needs to be able to come back on the switch at the current clock (if clock = 0, take the first message able to come back).
- \item Between the eligible jobs, schedule first the one which has the longest route gives it the starting time $o_i = clock$.
+ \item Between the eligible jobs, schedule first the one which has the longest route gives it the offset time $m_{\cal C(s_i)} = clock$.
  \item Update the clock at the time in which the scheduled task is over: $$clock = clock + message\ length$$.
 \end{enumerate}
-
-This algorithm defines the offsets of the first $P$-periodic affectation by sending the messages from the longest route to the shortest route, then it uses a greedy algorithm to schedule the messages in the second $P$-periodic affectation.
-We denote this algorithm by LSG (Longest Shortest + Greedy).
 
@@
 \begin{algorithmic}
-\REQUIRE Matched graph $N$, period $P$, packet size T
-\ENSURE 2way Trip affectation in P
+\REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, packet size $\tau$
+\ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$
 \STATE clock $\leftarrow$ 0
-\FORALL{route i in $\rho$ from the longest to the shortest }
-\STATE  $m_i \leftarrow$ clock
-\STATE clock $\leftarrow$ clock + T
+\FORALL{route i in $r_{s_i}$ from the longest to the shortest }
+\STATE  $m_{s_i} \leftarrow$ clock
+\STATE clock $\leftarrow$ clock + $\tau$
 \ENDFOR
 \STATE clock $\leftarrow$ 0
-\STATE take i such that $r_i$ is the first route to come back in sources switch
-\STATE $o_i \leftarrow $ clock;
-\STATE clock $\leftarrow$ $a_i$ + T
-\WHILE{there is a route which has no $w_i$}
-\STATE take i such that $r_i$ is the eligible route.
-\STATE $o_i \leftarrow $ clock - $a_i$;
-\STATE clock $\leftarrow$ clock + T
+\STATE take i such that $r_{\cal C(s_i)}$ is the first route to come back in sources switch
+\STATE $m_{\cal C(s_i)} \leftarrow $ clock;
+\STATE clock $\leftarrow$ $t(c_t,r_{\cal C(s_i)})$ + $\tau$
+\WHILE{there is a route which has not been scheduled}
+\STATE take i such that $r_{\cal C(s_i)}$ is the eligible route.
+\STATE $m_{\cal C(s_i)} \leftarrow $ clock - $t(c_t,r_{\cal C(s_i)})$;
+\STATE clock $\leftarrow$ clock + $\tau$
 
@@
 	\paragraph{Analysis}
-	  Parler de LSO et expliquer pourquoi LSG mieux avec nos params
+
+One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the, this algorithm gives an optimal solution.
+Indeed, all the same weight can be simplified by 0, thus the scheduling in the forward and backward period is the same, that is, all message following each others, so the period is minimal : $2 .\tau$, where n is the number of couples $(s,{\cal C}(s))$.
+Furthermore, all the waiting times are set to 0 i.e.
+$w_i = 0 \forall i \in n$, thus, $MT({\cal M})$ is equal to twice the longer delay of the routes, that is not alterable.
+
+Another case of this topology is the case in which all the weight on the arcs between $c_s$ and the sources are the same.
+In this case, the algorithm gives optimal solutions too:\\
+
+We consider only the delay between $c_t$ and the targets, that are $\lambda(r_{s})$.
+Order the routes such that $\lambda(r_{s_i}) > \lambda(r_{s_j}), i,j \in n, i<j$, i.e.
+the route 1 is the longest one, and the route $n$ is the shortest.
+The messages are sent in the forward period from 0 to $n-1$, that is $m_{s_i} = \tau * n$.
+
+The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is so $PT(s_0) = 2.\lambda(r_{s_0}) + \tau$.
+The second message is eligible in the backward period at time $\tau + 2.\lambda(r_{s_1})$.
+Thus, the waiting time of the second route is $w_{s_1} = 2.\lambda(r_{s_0})+\tau - (\tau + 2.\lambda(r_{s_1})) = 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))$.
+Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1})) +\tau = 2.\lambda(r_{s_0}) + \tau = PT(s_0)$.
+By induction, $PT(s_i) = PT(s_0), \forall i \in n$. 
+Consequently, for this case, the heuristic is optimal, because the longest route has no waiting time all the other routes will take exactly the same time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) + \tau$, which is not alterable
+
      \subsubsection{Results}
@@
 \bibliography{Sources.bib}
+\begin{thebibliography}{abcde}
+
+\bibitem{BM12} Y. Bouguen, E. Hardouin, A. Maloberti, and F.-X. Wolff, LTE et les r ́eseaux 4G. Editions Eyrolles, 2012.
+
+\bibitem{Mo11} C. Mobile, “C-ran: the road towards green ran,” White Paper, ver, vol. 2, 2011.
+
+ \bibitem{CS96}R.
+J.
+Cole, B.
+M.
+Maggs, and R.
+K.
+Sitaraman, “On the benefit of sup- porting virtual channels in wormhole routers,” in Proceedings of the eighth annual ACM symposium on Parallel algorithms and architectures, pp.
+131– 141, ACM, 1996.
+
+\bibitem{GPA16} G. P. A. W. Group, “View on 5g architecture,” White Paper, ver, vol. 1.0, 2016.
+
+\bibitem{BM98} R. Borndorfer, A. Eisenblatter, M. Grotschel, and A. Martin, “Frequency assignment in cellular phone networks,” Annals of Operations Research, vol. 76, pp. 73–93, 1998.
+\bibitem{EJ01} T. Erlebach and K. Jansen, “The complexity of path coloring and call scheduling,” Theoretical Computer Science, vol. 255, no. 1, pp. 33–50, 2001.
+\bibitem{CS96} R.
+J.
+Cole, B.
+M.
+Maggs, and R.
+K.
+Sitaraman, “On the benefit of sup- porting virtual channels in wormhole routers,” in Proceedings of the eighth annual ACM symposium on Parallel algorithms and architectures, pp.
+131– 141, ACM, 1996.
+\bibitem{St07} C. Strotmann, Railway scheduling problems and their decomposition. PhD thesis, PhD thesis, Universit ̈at Osnabru ̈ck, 2007.
+\bibitem{Zhu06} X. Zhu, “Recent developments in circular colouring of graphs,” in Topics in discrete mathematics, pp. 497–550, Springer, 2006.
+\bibitem{Zho13} B. Zhou, “Multiple circular colouring as a model for scheduling,” 2013.
+\bibitem{ZHu01} X. Zhu, “Circular chromatic number: a survey,” Discrete mathematics, vol. 229, no. 1, pp. 371–410, 2001.
+\bibitem{FT16} N. Finn and P. Thubert, “Deterministic Networking Architecture,” Internet-Draft draft-finn-detnet-architecture-08, Internet Engineering Task Force, Sept. 2016. Work in Progress.
+\bibitem{iee802} “Time-sensitive networking task group.” http://www.ieee802.org/1/ pages/tsn.html. Accessed: 2016-09-22.
+\bibitem{Ho05}W. Howe, “Time-scheduled and time-reservation packet switching,” Mar. 17 2005. US Patent App. 10/947,487.
+\bibitem{LM16}B. Leclerc and O. Marce, “Transmission of coherent data flow within packet-switched network,” June 15 2016. EP Patent App. EP20,140,307,006.
+
+\end{thebibliography}
 

### 2017-02-24 article/article.tex
article corrige + essai 3d gnuplot

@@
 \usepackage{xspace}
+\usepackage{url}
 \usepackage{graphicx,graphics} 
@@
 \maketitle
-
 \begin{abstract}
@@
 \end{abstract}
-
-The evolutions proposed in next generations of mobile network architectures aim at evolving toward centralized radio network architectures (C-RAN, for Cloud Radio Access Network) to reduce consumption costs and power at the base stations \cite{Mo11}.
+The evolutions proposed in next generations of mobile network architectures aim at evolving toward centralized radio network architectures (C-RAN, for Cloud Radio Access Network) to reduce consumption costs and power at the base stations \cite{mobile2011c}.
 This type of architecture faces the challenge of mastering the latency in the transfer process between the Remote Radio Heads (RRHs) on the field and baseband units (BBUs) in the cloud.
 Low latency is already critical for the deployment of C-RAN approach.
-The standard requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in less than from 1 to 10ms \cite{BM12}
+The standard requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in less than from 1 to 10ms \cite{bouguen2012lte}
 (depending on targeted services).
-One specificity in the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRH and BBU (this HARQ constraints must be enforced for each frame emitted every millisecond).
-
+One specificity in the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRH and BBU (this HARQ constraints must be enforced for each frame emitted every millisecond).\\
  Thus in this article, we work on latency and periodicity constraints in fronthaul.
-The best current solution is to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches \cite{GPA16}.
+The best current solution is to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches \cite{5gppparchitecture}.
 This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
@@
 These packets having a fixed duration close to $1\mu $s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.\\
-
  Thus, new scheduling and routing paradigms and new technologies have to be considered to  guarantee  delay constrained periodic data transfers.
@@
  statistical multiplexing. The traditional queue managements are replaced by time based forwarding. Solutions for Deterministic
- Networking are under standardization in IEEE 802.1 TSN group \cite{FT16}, as well at IETF DetNet working group \cite{ieee802}.
-Several patents on concepts and mechanisms for DetNet have been already published, see for example \cite{Ho05,LM16}.
+ Networking are under standardization in IEEE 802.1 TSN group \cite{finn-detnet-architecture-08}, as well at IETF DetNet working group \cite{ieee802}.
+Several patents on concepts and mechanisms for DetNet have been already published, see for example \cite{howe2005time,leclerc2016transmission}.
 To make DN working over a
@@
 
-Considering a graph, modeling the network topology, and a set of routes from source nodes (modeling connections to the BBU) and destination
-nodes (modeling the RRH) in this graph, the purpose is to select, for each destination node a route from one source node to it and a periodic
-routing scheme allowing to periodically sent a packet to each base station without congestion conflicts between all such packets and to insure a minimum latency.
+Considering a graph, modeling the network topology, and a set of routes from source nodes (modeling connections to the BBU) and destination nodes (modeling the RRH) in this graph, the purpose is to select, for each destination node a route from one source node to it and a periodic routing scheme allowing to periodically sent a packet to each base station without congestion conflicts between all such packets and to insure a minimum latency.
 In a slotted time model, the aim is here to minimize the duration of the period, with a constraint of the maximum length of routes to be
@@
 This problem may look like wormhole problem \cite{cole1996benefit}, very popular few years ago, but here, we want to minimize the time lost in buffers and not just avoid the deadlock, and the wormhole does not treat about the periodicity.
-Several graph colorings have been introduced to model similar problems such as the allocation of frequencies \cite{BM98}, bandwidths \cite{EJ01}[17] or routes \cite{CS96}[18] in a network or train schedules \cite{St07}[19].
+Several graph colorings have been introduced to model similar problems such as the allocation of frequencies \cite{borndorfer1998frequency}, bandwidths \cite{erlebach2001complexity}[17] or routes \cite{cole1996benefit}[18] in a network or train schedules \cite{strotmann2007railway}[19].
 Unfortunately, they do not take into account the periodicity and the associated problems are also NP-complete.
-The only model which incorporates some periodicity is the circular coloring \cite{Zho13, Zhu01,Zhu06}but is not expressive enough to capture our problem.
+The only model which incorporates some periodicity is the circular coloring \cite{zhou2013multiple, zhu2001circular,zhu2006recent}but is not expressive enough to capture our problem.
 
@@
    \subsection{Slotted time Model}
-      Consider now a positive integer $P$ called the {\bf period}. In our problem, we send in the network
-      messages with period $P$.
+      Consider now a positive integer $P$ called the {\bf period}.
+In our problem, we send messages in the network with period $P$.
 The time will thus be cut into slices of $P$ discrete slots.
-Assume we send a message at the source of the route $r$, at the time slot $m$ in the first period, then a message will be sent at time slot $m$ at each new period.
-We define the first time slot at which the message reaches a vertex $v$ in this route by $t(v,r) = m + \lambda(v,r) \mod P$.
+Assume we send a message at the source $s_i$ of the route $r_{s_i}$, at the time slot $m_{s_i}$ in the first period, then a message will be sent at time slot $m_{s_i}$ at each new period.
+We define the first time slot at which the message reaches a vertex $v$ in this route by $t(v,r_{s_i}) = m_{s_i} + \lambda(v,r) \mod P$.
 
@@
       of consecutive slots necessary to transmit a message.
-Let us call $[t(v,r)]_{P,\tau}$ the set of time slots used by $r$ at a vertex $v$ in a period $P$, that is $[t(v,r)]_{P,\tau} = \{t(v,r) + i \mod P \mid 0 \leq i < \tau \}$.
-Usually $P$ and $\tau$ will be clear from the context and we will denote $[t(v,r)]_{P,\tau}$ by $[t(v,r)]$.
+Let us call $[t(v,r_{s_i})]_{P,\tau}$ the set of time slots used by $r_{s_i}$ at a vertex $v$ in a period $P$, that is $[t(v,r_{s_i})]_{P,\tau} = \{t(v,r_{s_i}) + k \mod P \mid 0 \leq k < \tau \}$.
+Usually $P$ and $\tau$ will be clear from the context and we will denote $[t(v,r_{s_i})]_{P,\tau}$ by $[t(v,r_{s_i})]$.
 
-      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R_{\cal C}$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R_{\cal C}$.
-The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in \cal R_{\cal C}$ at its source.
-      A $(P,\tau)$-periodic affectation must have no {\bf collision} between two routes in $\cal R_{\cal C}$, that is $\forall (r_i, r_j) \in {\cal R_{\cal C}}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
-      we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$
+      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R_{\cal C}$ is a sequence  ${\cal M}=(m_{s_0}, \ldots ,m_{s_{n-1}})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R_{\cal C}$.
+The number $m_{s_i}$ represents the index of the first slot used in a period  by the route $r_{s_i} \in \cal R_{\cal C}$ at its source $s_i$.
+      A $(P,\tau)$-periodic affectation must have no {\bf collision} between two routes in $\cal R_{\cal C}$, that is $\forall (r_{s_i}, r_{s_j}) \in {\cal R_{\cal C}}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
+      we have $$[t(u,r_{s_i})] \cap [t(u,r_{s_j})] = \emptyset .$$
 
 %       Notice that the notion of $P$-periodic affectation \textbf{is not monotone} with regard to $P$. 
-      As an example of a $(2,1)$-periodic affectation, let consider a routage graph with routes $\{r_i\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
-      We set $\tau = 1$ and the delays are chosen so that if $r_i$ and $r_j$ have $v$ as first common vertex then we have $\lambda(v,r_i) - \lambda(v,r_j)=1$.There is a $(2,1)$-periodic affectation by setting all $m_i$ to $0$.
+      As an example of a $(2,1)$-periodic affectation, let consider a routage graph with routes $\{r_{s_i}\}_{i=0,\dots,n-1}$, such that all pairs of routes intersect at a different edge.
+      We set $\tau = 1$ and the delays are chosen so that if $r_{s_i}$ and $r_{s_j}$ have $v$ as first common vertex then we have $\lambda(v,r_{s_i}) - \lambda(v,r_{s_j})=1$.There is a $(2,1)$-periodic affectation by setting all $m_{s_i}$ to $0$.
 
@@
 %       A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.
-      \begin{figure}[h]
+
+      \begin{figure}[ht]
        \begin{center}
@@
   \SetGraphUnit{5}
-  \node[draw,circle] (s3) at (4, 2) {$s_3$}; 
-  \node[draw,circle] (s2) at (0, 4) {$s_2$}; 
-  \node[draw,circle] (s1) at (0, 6) {$s_1$};
+  \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
+  \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
+  \node[draw,circle] (s1) at (0, 6) {$s_0$};
 
-  \node[draw,circle] (t3) at (14, 7) {$t_3$}; 
-  \node[draw,circle] (t2) at (14, 4) {$t_2$}; 
-  \node[draw,circle] (t1) at (10, 2) {$t_1$};
+  \node[draw,circle] (t3) at (14, 7) {$t_2$}; 
+  \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
+  \node[draw,circle] (t1) at (10, 2) {$t_0$};
 
@@
 It can also be seen as the set of pairs $(s,{\cal C}(s))$ and $({\cal C}(s),s)$.\\
-      The Routing function ${\cal R}$ associates to each couple $(s,{\cal C}(s))$ a route called $r_s$ and to each couples $({\cal C}(s),s)$ a route called $r_{{\cal C}(s)}$.\\     
+      The routing function ${\cal R}$ associates to each couple $(s,{\cal C}(s))$ a route called $r_s$ and to each couples $({\cal C}(s),s)$ a route called $r_{{\cal C}(s)}$.\\     
        We are given a period $P$, a routing function ${\cal R}$, and we consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_s$ to the route $r_s$ which begins by $s$, and $m_{{\cal C}(s)}$ to the routes $r_{{\cal C}(s)}$ which begins by ${\cal C}(s)$.
@@
       $$
+
+      The message size $\tau$ in this process time, if we want to consider the time between the emission of the first slot and the reception of the last slot of the message.
+Since $\tau$ is the same for every routes, it does not change the calculations.
 
@@
   with $d$ or $d+1$ colors. The edge coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness. We define from $H$ an instance of PRA as follows. 
-  For each $v$ in $V$, the graph $G$ has two vertices $v_1, v_2$, and for each $(u,v) \in E$,the graph g has two vertices $s_{u,v}, t_{u,v}$.
+  For each $v$ in $V$, the graph $G$ has two vertices $v_1, v_2$, and for each $(u,v) \in E$,the graph G has two vertices $s_{u,v}, t_{u,v}$.
+Set an arbitrary orientation of the edge $(u,v)$, such that the following route is directed from $u$ to $v$.
 
@@
   For each edge $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.  
+  All these arcs are of weight $0$. 
   The set of arcs of G is the union between all the arcs of the previous routes.
   The affectation ${\cal C}$ is the set of pair of vertices $(s_{u,v}, t_{u,v})$.
-
-  All these arcs are of weight $0$.
 
@@
 We consider ${\cal C}'$ and ${\cal R}'_{\cal C'}$ symmetrized versions of ${\cal C}$ and  ${\cal R}_{\cal C}$ where for every route there is a symmetric route with new arcs and the same weights.
- The instance $({\cal R'}_{\cal C'},P,\tau,T_{max})$ is in PALL if and only if $({\cal R}_{\cal C},P,\tau)$
+ The instance $({\cal R'}_{\cal C'},P,\tau,T_{max})$ is in PALL if and only if $({\cal R}_{\cal C},P,\tau)	$
  is in $PRA$.
@@
       \SetGraphUnit{5}
-      \Vertex[x=4,y=2]{s3}
-      \Vertex[x=0,y=4]{s2}
-      \Vertex[x=0,y=6]{s1}
 
-      \Vertex[x=12,y=3]{t3}
-      \Vertex[x=14,y=4]{t2}
-      \Vertex[x=10,y=2]{t1}
+      \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
+      \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
+      \node[draw,circle] (s1) at (0, 6) {$s_0$};
+
+      \node[draw,circle] (t3) at (12, 3) {$t_2$}; 
+      \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
+      \node[draw,circle] (t1) at (10, 2) {$t_0$};
+
       \tikzstyle{VertexStyle}=[shape = circle, draw, minimum size = 20pt]
@@
       then the central arc to {\bf $c_t$}, the central target node, and an arc to its target.
-In addition to those central nodes, there are two sets of vertices, $S$ and $T$, of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$.
+In addition to those central nodes, there are two sets of vertices, $S={s_0,...,s_{n-1}}$ and $T={t_0,...,t_{n-1}}$, of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$.
       The routes are the directed paths of the form $s_i,c_s,c_t,t_i$ and $t_i,c_t,c_s,s_i$.
@@
        \begin{center}
-	  \includegraphics[scale=0.8]{Fig4.pdf}
+
+\begin{tikzpicture}
+
+\tikzset{
+  LabelStyle/.style = { rectangle, rounded corners, draw,
+                       font = \bfseries },
+  EdgeStyle/.append style = {->} }
+
+  \SetGraphUnit{5}
+
+  \node[draw,circle] (s3) at (0, 0) {$s_2$}; 
+  \node[draw,circle] (s2) at (0, 2) {$s_1$}; 
+  \node[draw,circle] (s1) at (0, 4) {$s_0$};
+
+  \node[draw,circle] (t3) at (8, 0) {$t_2$}; 
+  \node[draw,circle] (t2) at (8, 2) {$t_1$}; 
+  \node[draw,circle] (t1) at (8, 4) {$t_0$};
+
+  \node[draw,circle] (cs) at (2, 2) {$c_s$}; 
+  \node[draw,circle] (ct) at (6, 2) {$c_t$};
+
+  \Edge(s1)(cs)
+  \Edge(s2)(cs)
+  \Edge(s3)(cs)
+
+  \Edge(ct)(t1)
+  \Edge(ct)(t2)
+  \Edge(ct)(t3)
+
+  \Edge(cs)(ct)
+
+\end{tikzpicture}
+
   \end{center}
@@
       only appear at node $c_s$ on the way forward and at node $c_t$ on the way back. \\
-      In such a topology, there is only two possible collision points between the routes : $c_s$ and $c_t$.
-To avoid collisions, we only have to check if there is no collisions in a period on those two points.
-      Let us take a period P for each central nodes, that are called the {\bf forward period} and the {\bf backward period} for, respectively $c_s$ and $c_t$.
-A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1})$ in the forward period, and  $c_t$ at time $m_{{\cal C}(s_1)} + t(c_t,r_{{\cal C}(s_1)})$ in the backward period.
+      In such a topology, there is only two possible collision points between the routes: $c_s$ and $c_t$. We only have to check if there is no collisions in a period at those two points.
+      We consider two periods P at these vertices, the the {\bf forward period} at $c_s$, and the {\bf backward period} at $c_t$.
+A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1})$ in the forward period, and  $c_t$ at time $m_{t_1} + t(c_t,r_{t_1})$ in the backward period.
       A $(P,\tau)$-periodic affectation consist in choosing $\forall i \in n, m_i$, and $m_{{\cal C}(s_i)}$ such that, for any couples of routes $(r_{s_j}, r_{s_k}), j,k \in n$,
       we have $[t(c_s,r_j)] \cap [t(c_s,r_k)] = \emptyset$.
-      and for any couples of routes $(r_{{\cal C}(s_j)}, r_{{\cal C}(s_k)}), j,k \in n$, we have $[t(c_s,r_{{\cal C}(s_j)})] \cap [t(c_s,r_{{\cal C}(s_k)})] = \emptyset$
+      and for any couples of routes $(r_{t_j}, r_{t_k}), j,k \in n$, we have $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$
 %       
@@
   We ask for a $(P,\tau)$-periodic affectation with all waiting times equal to $0$. 
-  In that case $MT({\cal M})$ is not relevant anymore. Since $w_i=0$, choosing $m_i$, the offset of the route from
+  In that case $MT({\cal M})$ is equal to twice the delay of the longer route, thus, $T_{max}$ is not relevant anymore. Since $w_i=0$, choosing $m_i$, the offset of the route from
   $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i)$.
@@
 Indeed, setting the offset $m_{s_i}$ in the forward period automatically set the offsets $m_{{\cal C}(s_i)}$ in the backward period.
-  The goal is now to put messages in the forward periods such that there is no collisions in the both periods.\\
-  In this section, the offsets $m_{s_i}$ are in reality $[t(c_s,r_{s_i})]$, but to find the real values, there is just to change the values of the offset considering the delay of the arcs $(s_i, c_s) , \forall i$.
+  The goal is now to put messages in the forward period such that there is no collision in both periods.\\
+  Here, weight of arcs $(s_i,c_s)$ can be ignored, thus, the offsets $m_{s_i}$ are calculated like if all these weight are equal to 0.
+To find the real values, it is easy to delay the real sending in sources by the weight of the corresponding arc.
 
@@
     We present a simple policy, which works when the period is large with regards to the delay of the routes.
-    Send the messages in order from the shortest route to the longest route, on after each others in the forward period, without any slots between two messages, that is $m_{s_i} = \tau.i$, if the routes $r_i$ are ordered by $\lambda(r_i)$ from the shortest to the longest one.
+    Send the messages in order from the shortest route to the longest route, on after each others in the forward period, without any slots between two messages, that is $m_{s_i} = \tau.i$, if the routes $r_i, i \in {0,...,n-1}$ are ordered by $\lambda(r_i)$ from the shortest to the longest one.
 
@@
 Then, the second message is sent before the others, and also will be back before the third etc... 
-Because the second message is sent $\tau$ slots after the first message ($m_{s_2} = m_{s_1} + \tau$, it comes back after
-the end of the message one: $m_{s_1}+ \tau + 2.\lambda(r_{s_1}) \le m_{s_2} + 2.\lambda(r_{s_2})$ because of $\lambda(r_{s_2}) \ge \lambda(r_{s_1})$.
+Because the message $i$ is sent $\tau$ slots after the message $i-1$ ($m_{s_i} = m_{s_{i-1}} + \tau$), it comes back after the end of the message $i-1$: $m_{s_{i-1}}+ \tau + 2.\lambda(r_{s_{i-1}}) \le m_{s_i} + 2.\lambda(r_{s_i})$ because of $\lambda(r_{s_i}) \ge \lambda(r_{s_{i-1}})$.
 
       \paragraph{Period}
-      To ensure that there is no collisions in the backward period, we must ensure that the last message will not collide with the first message of the next period.
+      Because of $m_{s_i} = \tau.i$ in the forward period, there is no collisions.
+      To ensure that there is no collisions in the backward period, we must ensure that the last message ends before the end of the period P.
 We have to find the minimum period P such that the last message have totally came back before P slots after the first message.
@@
 from the shortest to the longest.
- \begin{proof}
+
 We have to calculate the time taken by the last message to reach $c_t$. $2.\lambda(r_{s_0})$ is the first slot in which the first message is coming back in the backward period,
@@
 the period is.
-  \end{proof}
 
@@
      We consider the forward period and cut it into consecutive macro slots of time of size $\tau$.
-The algorithm works in the following way: select the first route for which the offset as not been chosen.
-Try every offset which put the message in a
-     free macro slot in the forward period. It also fixes the position of a message in the backward period, and we choose the first offset which does not create a collision in the backward period. 
+The algorithm works in the following way: select the first route $k+1$ for which the offset as not been chosen.
+Try every of the $3N-k$ offsets which put the message in one free macro slot in the forward period.
+It also fixes the position of a message in the backward period, and we choose the first offset which does not create a collision in the backward period.
      Assume we choose the offset of the route $r_{k+1}$, we have  at least $3n - k$ free macro-slots, since $P \geq 3n\tau$.
@@
      \end{proof}
-
+     This algorithm works in a complexity $n^2$, since we have to try every free macro-slots for every routes.
       \begin{center}
@@
       \end{center}
-
     \todo{Avec une structure de données plus maligne on doit pouvoir faire n, non ?}
-
 	\begin{algorithm}[H]
@@
 	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
-	\STATE $P1[P]$ slots of size $\tau$ in forward period.
-	\STATE $P2[P]$ slots  of size $\tau$ in backward period.
-	\FORALL{source i in S }
+	\STATE $P1[P/\tau]$ slots of size $\tau$ in forward period.
+	\STATE $P2[P]$ slots backward period.
+	\FORALL{source $s_i$ in S }
 
-	\FORALL{slot j in P1}
+	\FORALL{macro slot j in P1}
 
-	\IF{$P1[j]$ is free AND $P2[j+\lambda(r_i)]$ is free}
+	\IF{$P1[j]$ is free AND the corresponding area in P2 is free}
 
-	\STATE $m_{s_i} \leftarrow j$
+	\STATE $m_{s_i} \leftarrow j.\tau$
 	\ENDIF
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{ieeetr}
 \bibliography{Sources.bib}
-\begin{thebibliography}{abcde}
-
-\bibitem{BM12} Y. Bouguen, E. Hardouin, A. Maloberti, and F.-X. Wolff, LTE et les r ́eseaux 4G. Editions Eyrolles, 2012.
-
-\bibitem{Mo11} C. Mobile, “C-ran: the road towards green ran,” White Paper, ver, vol. 2, 2011.
-
- \bibitem{CS96}R.
-J.
-Cole, B.
-M.
-Maggs, and R.
-K.
-Sitaraman, “On the benefit of sup- porting virtual channels in wormhole routers,” in Proceedings of the eighth annual ACM symposium on Parallel algorithms and architectures, pp.
-131– 141, ACM, 1996.
-
-\bibitem{GPA16} G. P. A. W. Group, “View on 5g architecture,” White Paper, ver, vol. 1.0, 2016.
-
-\bibitem{BM98} R. Borndorfer, A. Eisenblatter, M. Grotschel, and A. Martin, “Frequency assignment in cellular phone networks,” Annals of Operations Research, vol. 76, pp. 73–93, 1998.
-\bibitem{EJ01} T. Erlebach and K. Jansen, “The complexity of path coloring and call scheduling,” Theoretical Computer Science, vol. 255, no. 1, pp. 33–50, 2001.
-\bibitem{CS96} R.
-J.
-Cole, B.
-M.
-Maggs, and R.
-K.
-Sitaraman, “On the benefit of sup- porting virtual channels in wormhole routers,” in Proceedings of the eighth annual ACM symposium on Parallel algorithms and architectures, pp.
-131– 141, ACM, 1996.
-\bibitem{St07} C. Strotmann, Railway scheduling problems and their decomposition. PhD thesis, PhD thesis, Universit ̈at Osnabru ̈ck, 2007.
-\bibitem{Zhu06} X. Zhu, “Recent developments in circular colouring of graphs,” in Topics in discrete mathematics, pp. 497–550, Springer, 2006.
-\bibitem{Zho13} B. Zhou, “Multiple circular colouring as a model for scheduling,” 2013.
-\bibitem{ZHu01} X. Zhu, “Circular chromatic number: a survey,” Discrete mathematics, vol. 229, no. 1, pp. 371–410, 2001.
-\bibitem{FT16} N. Finn and P. Thubert, “Deterministic Networking Architecture,” Internet-Draft draft-finn-detnet-architecture-08, Internet Engineering Task Force, Sept. 2016. Work in Progress.
-\bibitem{iee802} “Time-sensitive networking task group.” http://www.ieee802.org/1/ pages/tsn.html. Accessed: 2016-09-22.
-\bibitem{Ho05}W. Howe, “Time-scheduled and time-reservation packet switching,” Mar. 17 2005. US Patent App. 10/947,487.
-\bibitem{LM16}B. Leclerc and O. Marce, “Transmission of coherent data flow within packet-switched network,” June 15 2016. EP Patent App. EP20,140,307,006.
-
-\end{thebibliography}
 

### 2017-02-24 code/code.c

@@ -315,11 +315,40 @@ void echec(int nb_routes, int taille_message,int taille_routes, int nb_simuls)
 	}
 	fclose(F);
 }
+
+void echec_taille_route(int nb_routes, int taille_message,int taille_routes, int nb_simuls)
+{
+	FILE * F = fopen("results_taille_route_echec.data","w");
+	Graphe g;
+	long long int total;
+
+	for(int k = 1000;k<taille_routes;k+=1000)
+	{
+		for(int j = taille_message*nb_routes ; j<=3*taille_message*nb_routes;j+=100)
+		{
+			total = 0;
+
+			for(int i = 0;i<nb_simuls;i++)
+			{
+				g = init_graphe(nb_routes *2 +1);
+				graphe_etoile(g,k);
+				if(algo_shortest_longest(g,j,taille_message)!= -1) total++;
+				libere_matrice(g);
+				fprintf(stdout,"\rStep = %5d/%d [Period : %d| Routes : %d]",i+1,nb_simuls,j,k);fflush(stdout);
+			}
+
+		
+			fprintf(F, "%d %d %lld \n",j,k,total);
+
+		}
+	}
+	fclose(F);
+}
 int main()
 {
 	srand(time(NULL));
 	//simuls_periode(15,2500,10000,1000);
-	echec(8,2500,25000,1000);
+	echec_taille_route(8,2500,25000,1000);
 
 	return 0;
 }

### 2017-03-14 article/article.tex

@@
 	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
-	\STATE $P1[P/\tau]$ slots of size $\tau$ in forward period.
+	\STATE $P1[P/\tau]$ macro slots of size $\tau$ in forward period.
 	\STATE $P2[P]$ slots backward period.
@@
 
-	\IF{$P1[j]$ is free AND the corresponding area in P2 is free}
+	\IF{$P1[j]$ is free AND the corresponding slots in P2 are free}
 
@@
 
-	\IF{No intervals are found for i}
+	\IF{No intervals are found for $s_i$}
 	\STATE return FAILURE
@@
 	\STATE Backward-budget $\leftarrow$ $P$ - n * $\tau$
-	\STATE Free-Intervals $\leftarrow$ list of free intervals, init to $[0;P[$
-	\FORALL{route i in  ${\cal R}_{\cal C}$}
+	\STATE Free-Intervals $\leftarrow$ list of free intervals in the backward period, init to $[0;P[$
+	\FORALL{source $s_i$ in S}
 	\FORALL{j in Free-Intervals }
-	\IF{Message of the route i does not collides with scheduled routes}
+	\IF{Message of the route $r_{s_i}$ does not collides with scheduled routes}
 	\STATE $m_{s_i} \leftarrow $ the first slot of Free-Intervals[j]
@@
 Ex : if the interval [250;3250[ receives a packet of size 2500, there is 500 slots lost, because there is no way to uses the slots for another packet.\\
+      \todo{ecrire l'algo? si ou le réécrire}
 
@@
       This creates a new sub-tree in which the algorithm will try every possible starting offset too, and create a sub-tree on the following route too.
-      If no offset are available for a route, this means that the partial solution is not good, so the algorithm backtracks over the tree that is,
-      it goes back to the father of the current sub-tree.
-      Once a leaf is obtained, the algorithm stops and return the scheduling.\\      
-      To reduce the number of useless calculation, in each time we add another packet, we consider the lost size in both periods, thus, we know when a period has no many great enough free area to put a packet.
+      If no offset are available for a route, this means that the partial solution is not good, so the algorithm backtracks over the tree that is,  it goes back to the father of the current sub-tree, and continue from there.
+      Once a leaf is obtained, the algorithm stops and return the $(P\tau)$-periodic affectation.\\      
+      To reduce the number of useless calculation, we can imagine cuts in the tree :
+      \begin{enumerate}
+       \item In the forward windows, each message is placed after the previous one, that is $m_{s_i} > m_{s_j}$ (here, $s_i$ is the source taken first in the algorithm, the order is not fixed).
+Thus, if the number of the remaining slots in the forward period is inferior than the number of slots needed to put the remaining messages, we can consider that the actual partial solution is not good.
+       \item  Each time we add a new message, we cut a free interval in two new free intervals, plus the scheduled message.
+Each free intervals has a number of macro slots (ex: 2,6), and if the number of all macro slots is inferior than the number of remaining messages, the actual partial solution is not good.
+       \item ...
+      \end{enumerate}
 

### 2017-03-14 article/article.tex
debut results article

@@
     \subsubsection{Results}
-      Resultats des simulations : Shortest-longest optimal pour ces parametres.
+      The following performance evaluation results compares the previous algorithms in terms of periods, and success rate for given instances. 
+      In a first time, we will have a look at the results with the parameters corresponding to Cloud-RAN context, then some more global results will be shown.
+      \paragraph{Short routes}
+      To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(r_{s_i}) < 2100}$, that is, at the most, 5 km between the RRH and its BBU.
+The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data.
+The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.
+
+      For each algorithm, we made a linear research of the minimal period for which, there is a solution on the given instance.
+The following figure shows us the average periods on 1000 graphs, for a growing number of routes.
+      The results of the Exhaustive generation can be considered as a lower bound, indeed, for a given period, this algorithm finds the solution, if it exists.
+      As an information, we drew the $\tau.n$ (i.e. the size taken by the messages in the period) and the $2.(\tau.n) $ lines.
+
+      Since we try to find a linear solution for the problem PALL, Exhaustive Generation is not a good solution.
+However, Greedy 3NT and Shortest-Longest are some greedy heuristics and gives us linear solutions.
+      With those parameters, we can observe that the average period of the Shortest-Longest algorithm, which is determined by the difference between the longest and the shortest route, is always equal to the Exhaustive generation, that is, the lower bound.
+      The next results is to theoretically prove that, with those parameters, the Shortest-Longest algorithm gives optimal solutions, like this experimental study suggests it does. 
+      About the Greedy 3NT Algorithm, with those parameters, it always gives us bigger periods than the Shortest longest. 
+      We can also observe that, for any algorithm, the average minimal periods increases linearly with the number of routes. Thus, the following experiences are made on a fixed number of routes : 8.
+
+      Then, we looked at the evolution of the minimal period required with the different algorithm if we significantly increase the size of the route.
+The following figure shows us the success rate of the algorithms, for 8 routes of size 14000 max, according to the period.
+
+      As we can see, the Shortest longest has a very low success rate, because of the distribution of the size of the routes is now broader, so is the required period.
+      Whereas, the Geedy 3NT gives us solutions with much lower period than Shortest Longest.
+      Because of it's polynomial complexity, the Exhaustive generation can freeze the simulation when the solution is not easy to find. Thus, we let it stop after a defined number of calculation. 
+      The Exhaustive Generation curve gives us the solution when the algorithm has found a solution, and the theoretical curve gives us the number of found solutions plus the number of time the algorithm stopped.
+The real lower bound is probably between those two curves.
 

### 2017-03-14 code/code.c

@@ -273,9 +273,9 @@ int algo_prime(Graphe g,int periode,int taille_message)
 			return -1;
 		assigned = 0;
 	}
-	affiche_periode(aller,periode);
-	affiche_periode(retour,periode);
-	printf("%d \n",periode);
+	//affiche_periode(aller,periode);
+	//affiche_periode(retour,periode);
+//	printf("%d \n",periode);
 	return periode;
 }
 
@@ -296,7 +296,7 @@ int linear_prime(Graphe g,int taille_message)
 
 void simuls_periode(int nb_routes, int taille_message, int taille_routes,int nb_simuls)
 {
-	FILE * F = fopen("results_periode.data","w");
+	FILE * F = fopen("results_periode_longues.data","w");
 	Graphe g;
 	long long int total_3NT, total_prime,total_sl;
 	int res_sl,res_prime,res_3NT;
@@ -325,7 +325,7 @@ void simuls_periode(int nb_routes, int taille_message, int taille_routes,int nb_
 			if(res_sl != -1)total_sl+=res_sl;
 			else printf("error (Sl = -1)\n");
 
-			if(res_sl < res_prime)affiche_matrice(g);
+			//if(res_sl < res_prime)affiche_matrice(g);
 			fprintf(stdout,"\rStep%5d /%d",i+1,nb_simuls);fflush(stdout);
 			libere_matrice(g);
 		}
@@ -344,7 +344,7 @@ void echec(int nb_routes, int taille_message,int taille_routes, int nb_simuls)
 	long long int total_3NT, total_brute, total_sl,total_theorique;
 	int res_brute;
 
-	for(int j = taille_message*nb_routes ; j<=3*taille_message*nb_routes;j+=1000)
+	for(int j = taille_message*nb_routes ; j<=3*taille_message*nb_routes;j+=2500)
 	{
 		
 		total_3NT = 0;
@@ -559,8 +559,7 @@ int longest_etoile(Graphe g,int taille_paquets, int Tmax)
 
 	}
 
-	affiche_tab(m_i,nb_routes);
-	affiche_tab(w_i,nb_routes);
+
 	int max = w_i[0]+2*routes[0];
 	for(int i=0;i<nb_routes;i++)
 	{
[…]

### 2017-03-21 modeleanneau/model.tex
modele ngreen

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{graphicx,graphics}

%opening
\title{Algorithmic model for N-GREEN optical ring}

\begin{document}

\maketitle

\section*{Definitions, model}
We consider an optical ring composed of $k$ nodes. We can see this ring like $N$ slots rotating to the following position at each time step $t$. The number of slots is given by the length of the ring, and the time step $t$ is the switching granularity. The capacity of a slot depends of the bandwidth of the network (eg, 100 Gbit/s).
\begin{center}

      \includegraphics[scale=0.5]{anneau1.pdf}
      \hspace{3cm}
      \includegraphics[scale=0.5]{anneau2.pdf}

\end{center}
This optical ring is modelled by a graph $G=(V,A)$, in which the vertices in $V$ are the nodes of the ring, and the arcs in $A$ are the links between the nodes. The weight of the arcs is the time taken by a slot to travel the link, i.e. a multiple of $t$. The sum of all the weight of the arcs in the graph in $N$.

\section*{Periodic process}
We define a set $\cal C$ of pair of vertices $(u,v) \in V$. Between each pair of $\cal C$, the following periodic process of period $P$ ($P$ is a multiple of $N$) is observed.
\begin{enumerate}
 \item The node $u$ receives (from an external way) some latency critical data addressed to $v$.
 \item Those data are transferred to $v$ through the ring .
 \item After reception and computing of the message, the node $v$ sends an answer to $u$.
\end{enumerate}
 This periodic process has a critical end to end latency, thus a messages has to be the less buffered as possible before being send in the ring.

\section*{Sending policy}

\section*{}
\end{document}

### 2017-03-21 code/code.c

@@ -716,7 +716,7 @@ int main()
 	int c=0;	
 	for(int i = 0;i<10000;i++)
 	{
-		g = init_graphe(15);
+		g = init_graphe(7);
 		graphe_etoile(g,7000);
 		affiche_matrice(g);
 		//printf("normal\n");

### 2017-03-21 code/simons.c

@@ -747,15 +747,19 @@ Ensemble * crisis(Ensemble * ens,Element * crisise, Element * elemspere,Element 
 	return debut;
 	
 }
+
 int is_ok(Graphe g, int taille_paquet, int * mi, int * wi)
 {
 	int nbr_route = g.N /2;
-	for(int i=0;i<nbr_route;i++)
+	for(int i=1;i<nbr_route;i++)
 	{
-		for(int j=0;j<i;j++)
+		for(int j=i-1;j>=0;j--)
 		{
 			if( fabs(mi[j]+g.matrice[nbr_route][j]-mi[i]-g.matrice[nbr_route][i]) <taille_paquet )
+			{
+				printf("PB(aller) entre %d(%d) et %d(%d)\n",i,mi[j]+g.matrice[nbr_route][j],j,mi[i]+g.matrice[nbr_route][i]);
 				return 0;
+			}
 		}
 	}
 
@@ -763,8 +767,11 @@ int is_ok(Graphe g, int taille_paquet, int * mi, int * wi)
 	{
 		for(int j=0;j<i;j++)
 		{
-			if( fabs(mi[j]+g.matrice[nbr_route][j]+2*g.matrice[nbr_route][nbr_route+1+j]-mi[i]-g.matrice[nbr_route][i]-2*g.matrice[nbr_route][nbr_route+1+i]) <taille_paquet )
+			if( fabs(mi[j]+g.matrice[nbr_route][j]+2*g.matrice[nbr_route][nbr_route+1+j]+wi[j]-wi[i]-mi[i]-g.matrice[nbr_route][i]-2*g.matrice[nbr_route][nbr_route+1+i]) <taille_paquet )
+			{
+				printf("PB(retour) entre %d(%d) et %d(%d)\n",i,mi[j]+g.matrice[nbr_route][j]+2*g.matrice[nbr_route][nbr_route+1+j],j,mi[i]+g.matrice[nbr_route][i]+2*g.matrice[nbr_route][nbr_route+1+i]);
 				return 0;
+			}	
 		}
 	}
 	return 1;

### 2017-03-27 article/article.tex

@@
       We assume the weight of the central arc to be $0$ since it appears in every route,
-      its value does not matter when considering affectations. Collisions between messages can 
-      only appear at node $c_s$ on the way forward and at node $c_t$ on the way back. \\
-      In such a topology, there is only two possible collision points between the routes: $c_s$ and $c_t$. We only have to check if there is no collisions in a period at those two points.
+      its value does not matter when considering affectations.\\
+      Collisions between messages can only appear at node $c_s$ on the way forward and at node $c_t$ on the way back.
+      Thus, we only have to check if there is no collisions in a period at those two points.
       We consider two periods P at these vertices, the the {\bf forward period} at $c_s$, and the {\bf backward period} at $c_t$.
@@
 
-    \subsubsection{Exhaustive generation}
-	\begin{algorithm}[H]
-	\caption{Exhaustive Generation}  
-	\begin{algorithmic}
-	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
-	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
-	\STATE Forward-budget $\leftarrow$ $P$ - n * $\tau$
-	\STATE Backward-budget $\leftarrow$ $P$ - n * $\tau$
-	\STATE Free-Intervals $\leftarrow$ list of free intervals in the backward period, init to $[0;P[$
-	\FORALL{source $s_i$ in S}
-	\FORALL{j in Free-Intervals }
-	\IF{Message of the route $r_{s_i}$ does not collides with scheduled routes}
-	\STATE $m_{s_i} \leftarrow $ the first slot of Free-Intervals[j]
-	\STATE Split the Free-Intervals considering the new packet
-	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
-	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
-	\STATE call Exhaustive Generation on remaining routes
-	\ENDIF
-	\ENDFOR
-	\ENDFOR
-
-      \end{algorithmic}
-      \end{algorithm}
-      {\bf {\em Lost size}}, is the size lost when an interval is too few to put another packet.
+%     \subsubsection{Exhaustive generation}
+% 	\begin{algorithm}[H]
+% 	\caption{Exhaustive Generation}  
+% 	\begin{algorithmic}
+% 	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
+% 	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
+% 	\STATE Forward-budget $\leftarrow$ $P$ - n * $\tau$
+% 	\STATE Backward-budget $\leftarrow$ $P$ - n * $\tau$
+% 	\STATE Free-Intervals $\leftarrow$ list of free intervals in the backward period, init to $[0;P[$
+% 	\FORALL{source $s_i$ in S}
+% 	\FORALL{j in Free-Intervals }
+% 	\IF{Message of the route $r_{s_i}$ does not collides with scheduled routes}
+% 	\STATE $m_{s_i} \leftarrow $ the first slot of Free-Intervals[j]
+% 	\STATE Split the Free-Intervals considering the new packet
+% 	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
+% 	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
+% 	\STATE call Exhaustive Generation on remaining routes
+% 	\ENDIF
+% 	\ENDFOR
+% 	\ENDFOR
+% 
+% 
+%       \end{algorithmic}
+%       \end{algorithm}
+%       {\bf {\em Lost size}}, is the size lost when an interval is too few to put another packet.
 Ex : if the interval [250;3250[ receives a packet of size 2500, there is 500 slots lost, because there is no way to uses the slots for another packet.\\
-      \todo{ecrire l'algo? si ou le réécrire}
-
-      This algorithm enumerates all the solutions by traversing a tree. The leaves of the tree are 
-      the $(P\tau)$-periodic affectations, and the nodes are partial solutions. A partial solution is a choice of a starting time for a subset of the routes.
+%       \todo{ecrire l'algo? si ou le réécrire}
+% 	    
+      We can try to enumerates all the solutions by traversing a tree. The leaves of the tree are 
+      the $(P-\tau)$-periodic affectations, and the nodes are partial solutions. A partial solution is a choice of a starting time for a subset of the routes.
       For each route, the algorithm tries every possible starting offset until it finds one available (that allows the message to come back without collisions).
@@
       If no offset are available for a route, this means that the partial solution is not good, so the algorithm backtracks over the tree that is,  it goes back to the father of the current sub-tree, and continue from there.
-      Once a leaf is obtained, the algorithm stops and return the $(P\tau)$-periodic affectation.\\      
+      Once a leaf is obtained, the algorithm stops and return the $(P-\tau)$-periodic affectation.\\  
+      Such an algorithm is an {\bf Exhaustive Generation} and has an exponential complexity.
+Thus, once we search for $(P-\tau)$-periodic affectations on graphs with a huge number of routes and an huge period P, if there is no solutions available, this algorithm takes too many time.
       To reduce the number of useless calculation, we can imagine cuts in the tree :
       \begin{enumerate}
-       \item In the forward windows, each message is placed after the previous one, that is $m_{s_i} > m_{s_j}$ (here, $s_i$ is the source taken first in the algorithm, the order is not fixed).
-Thus, if the number of the remaining slots in the forward period is inferior than the number of slots needed to put the remaining messages, we can consider that the actual partial solution is not good.
-       \item  Each time we add a new message, we cut a free interval in two new free intervals, plus the scheduled message.
-Each free intervals has a number of macro slots (ex: 2,6), and if the number of all macro slots is inferior than the number of remaining messages, the actual partial solution is not good.
+       \item In the forward windows, each message is placed after the previous one, that is $m_{s_i} > m_{s_j}$ (here, $s_i$ is the source placed before $s_j$ by the algorithm).
+Each time a new message is scheduled, there is some possible lost slots between $m_{s_i}+\tau$ and $ m_{s_j}$.
+We hold a counter of remaining slots and decrease it from the number of lost slots each time a new message is scheduled.
+Thus, if the number of the remaining slots in the forward period is lower than the number of slots needed to put the remaining messages, we can consider that the actual partial solution is not good.
+       \item  Each time we add a new message in the backward period, we cut a free interval in two new smaller free intervals, plus the scheduled message.
+Each free intervals has a number of macro slots (ex: 2,6).
+If the sum of all the integer parts of the macro slots is lower than the number of remaining messages to schedule, the actual partial solution is not good.
        \item ...
@@
     \subsubsection{Results}
-      The following performance evaluation results compares the previous algorithms in terms of periods, and success rate for given instances. 
-      In a first time, we will have a look at the results with the parameters corresponding to Cloud-RAN context, then some more global results will be shown.
+      The following performance evaluation results compares the previous algorithms.
+Since we try to find a linear time algorithm for the problem PALL, Exhaustive Generation is not a good solution.
+However, Greedy 3NT and Shortest-Longest are some greedy heuristics and gives us a linear complexity.
+We tried to determine which algorithm gives a solution with the minimal period.
+      In a first time, we will have a look at the results with the parameters corresponding to Cloud-RAN context.
       \paragraph{Short routes}
-      To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(r_{s_i}) < 2100}$, that is, at the most, 5 km between the RRH and its BBU.
-The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data.
+      To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(r_{s_i}) < 2100$ slots, that is, at the most, 5 km between the RRH and its BBU.
+The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route.
 The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.
@@
 
-      Since we try to find a linear solution for the problem PALL, Exhaustive Generation is not a good solution.
-However, Greedy 3NT and Shortest-Longest are some greedy heuristics and gives us linear solutions.
+      \begin{center}
+      \includegraphics[scale=0.4]{periode_petite.pdf}
+      \end{center}
+
       With those parameters, we can observe that the average period of the Shortest-Longest algorithm, which is determined by the difference between the longest and the shortest route, is always equal to the Exhaustive generation, that is, the lower bound.
@@
       Then, we looked at the evolution of the minimal period required with the different algorithm if we significantly increase the size of the route.
-The following figure shows us the success rate of the algorithms, for 8 routes of size 14000 max, according to the period.
+The following figure shows us the success rate of the algorithms, for 8 routes of size between 0 and 60000 slots, according to the period.
+
+       \begin{center}
+      \includegraphics[scale=0.4]{echec_longues.pdf}
+      \end{center}
 
@@
       Because of it's polynomial complexity, the Exhaustive generation can freeze the simulation when the solution is not easy to find. Thus, we let it stop after a defined number of calculation. 
-      The Exhaustive Generation curve gives us the solution when the algorithm has found a solution, and the theoretical curve gives us the number of found solutions plus the number of time the algorithm stopped.
-The real lower bound is probably between those two curves.
+      The Exhaustive Generation curve gives us the solution when the algorithm has found a solution, and the Upper bound gives us the number of found solutions plus the number of time the algorithm stopped.
+The real Upper bound is probably between those two curves.
+
+      So, those experiences shows us that for real topologies with small routes, the Shortest-Longest algorithm finds some affectations with small Periods, but, the longer the routes are, the better it is to use the Greedy policy to find a solution without waiting times.\\
+      Nevertheless, if we want to consider networks, the period is fixed.
+As we just saw, if the load increases, the needed period increases too, and it is not possible anymore to find a solution without waiting times with a small period.
+The solution is to allow some messages to wait on target nodes, as described in the next section.
 
@@
 The weights on links from sources to $c_s$ are now relevant because the goal is to minimize $MT({\cal M})$, with ${\cal M}$ the $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$.
-	  To build such a $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, we must choose the offsets $m_{s_i}$ and $m_{\cal C(s_i)}$, such that there is no $PT(s)$ superior than a given $T_{max}$.
-	  As a reminder, $ PT(s)=\lambda(r_s)+ w_s+\lambda(r_{{\cal C}(s)})$.
+	  To build such a $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, we must choose the offsets $m_{s_i}$ and $m_{t_i}$, such that there is no $PT(s)$ greater than a given $T_{max}$.
+	  As a reminder, $ PT(s)=\lambda(r_s)+ w_s+\lambda(r_{t_i})$.
      \subsubsection{LSG}
@@
 
-On $c_t$, the politic is the following one, after setting the clock to 0, do:
+On $c_t$, the policy is the following one, after setting the clock to 0:
 \begin{enumerate}
  \item To be eligible, a job needs to be able to come back on the switch at the current clock (if clock = 0, take the first message able to come back).
- \item Between the eligible jobs, schedule first the one which has the longest route gives it the offset time $m_{\cal C(s_i)} = clock$.
+ \item Between the eligible jobs, schedule first the one which has the longest route and gives it the offset time $m_{\cal C(s_i)} = clock$.
  \item Update the clock at the time in which the scheduled task is over: $$clock = clock + message\ length$$.
@@
 One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the, this algorithm gives an optimal solution.
-Indeed, all the same weight can be simplified by 0, thus the scheduling in the forward and backward period is the same, that is, all message following each others, so the period is minimal : $2 .\tau$, where n is the number of couples $(s,{\cal C}(s))$.
+Indeed, all the same weight can be simplified by 0, thus the scheduling in the forward and backward period is the same, that is, all message following each others, so the period is minimal : $n.\tau$, where $n$ is the number of couples $(s,{\cal C}(s))$.
 Furthermore, all the waiting times are set to 0 i.e.
-$w_i = 0 \forall i \in n$, thus, $MT({\cal M})$ is equal to twice the longer delay of the routes, that is not alterable.
+$w_i = 0,\forall i \in n$, thus, $MT({\cal M})$ is equal to twice the longer delay of the routes, that is not alterable.
 

### 2017-03-27 modeleanneau/model.tex

@@
 a multiple of $t$.
-The sum of all the weight of the arcs in the graph in $N$.
+The sum of all the weight of the arcs in the graph is equal to $t.N$.
 
@@
 \section*{Sending policy}
+In the studied model, the ring has a {\bf broadcast and select} policy: when a node sends some data in a slot, this slot is {\em taken} by this node for an entire ride of the ring.
+This means that every nodes of the ring can collect the information addressed to it, but it does not delete the data in the slot.
+The slot is fully cleared by the node that sent it, when it came back after a ride of the ring.
 
-\section*{}
+Thus, a node has to wait for a free slot before sending some data in the ring. To avoid overloading the ring, a node sends some data only if some criteria  are satisfied.
+We define by $Q$ the size of the buffer of a node, $\alpha$ the {\em minimum load} of the buffer, $0 \leq  \alpha \leq 1$, and $\delta$ the {\em maximum delay}.
+
+The node sends some data in a slot if:
+\begin{itemize}
+ \item The amount of data $q$ in the buffer is greater than $\alpha . Q$,
+ \item or the older data in the buffer is waiting for more than $\delta$.
+\end{itemize}
+
+In C-RAN context, this amount of data $q$ contains two kinds of data: the latency critical flow coming from RRH or BBU, and an other flow, called {\em best effort}.
+
+We can consider two buffers containing $x$ and $y$ amount of data, respectively for the C-RAN flow and the best effort flow.
+The data in the first buffer are inserted first in the buffer of the node, and comes periodically in regard of the period $P$. 
+The best effort data comes more randomly (can be modelled by a Poisson distribution, for example), and are inserted in the buffer if $x = 0$.
+
+\begin{center}
+
+      \includegraphics[scale=0.7]{insertion.pdf}
+
+\end{center}
+
+\section*{Study}
+The purpose is here to reduce the latency of the C-RAN data. Two event can increase this latency: 
+\begin{enumerate}
+  \item The node has enough data $q$ to emit in the ring, but no slots are available.
+ \item The node does not have enough data $q$ to emit and a data from $x$ is waiting for less than $\delta$.
+\end{enumerate}
+
+In a first time, we will look at the first problem, and try to determine from what load of the ring, the time taken to wait a free slot in the ring is too long.
+
+\section*{Parameters}
+The following parameters are considered for the study:
+\begin{itemize}
+ \item $k \in {3,..,10}$ nodes on the ring.
+ \item The switching granularity $t = 10\mu s$. 
+ \item The length of the ring = 50km. Thus $N = 25$ slots.
+ \item Capacity of one slot $= 1Mb$.
+ \item One slot of the ring can carry all the data stacked in $Q$ ($Q < 1Mb$).
+ \item $\delta =$ ?
+ \item $\alpha =$ ?
+\end{itemize}
+
 \end{document}

### 2017-03-27 modeleanneau/model.tex
model temps

@@
 We consider an optical ring composed of $k$ nodes.
-We can see this ring like $N$ slots rotating to the following position at each time step $t$.
+We are in a discrete time Model: The time is split in $N$ slot, rotating to the following position each time step $t$.
 The number of slots is given by the length of the ring, and the time step $t$ is the switching granularity.
-The capacity of a slot depends of the bandwidth of the network (eg, 100 Gbit/s).
 \begin{center}
@@
 \end{center}
-This optical ring is modelled by a graph $G=(V,A)$, in which the vertices in $V$ are the nodes of the ring, and the arcs in $A$ are the links between the nodes.
+
+We consider a ring as a graph model.
 The weight of the arcs is the time taken by a slot to travel the link, i.e.
@@
 \section*{Periodic process}
-We define a set $\cal C$ of pair of vertices $(u,v) \in V$. Between each pair of $\cal C$, the following periodic process of period $P$ ($P$ is a multiple of $N$) is observed.
+We define a set $\cal C$ of couple of vertices $(u,v) \in V$. Between each couple of $\cal C$, the following periodic process of period $P$ ($P$ is a multiple of $N$) is observed.
 \begin{enumerate}

### 2017-03-27 article/article.tex

@@
       we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$.
-In such a graph, there is no $(P,\tau)$-periodic affectation, because of $P < n$.\\
+In such a graph, there is no $(P,\tau)$-periodic affectation, since the problem reduces to finding a $P$-coloring in a complete graph with $n > P$ vertices.\\
       If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R_{\cal C}}$.
@@
 
-  In this article, we works on given routages, but we could imagine a problem, in which, considering a given graph $G = (V,A)$ and a period P, the question is to find, if it exists, a routage graph ${\cal R}_{\cal C}$, in which there is $(P,\tau)$-periodic affectation.
+  In this article, we works on a given routage, but we could imagine a problem, in which, considering a given graph $G = (V,A)$ and a period P, the question is to find, if it exists, a routage graph ${\cal R}_{\cal C}$, in which there is $(P,\tau)$-periodic affectation.
+
+  \todo{Dire si on regle le probleme de trouver un bon routage dans un cas particulier après}
+
 \section{Solving PRA}
@@
  We will prove the hardness of PRA and PALL for this parameter, which implies the hardness of the general problems. 
-Consider an instance of the problem PRA, i.e., a routage graph $\cal{R_{\cal C}}$, a message size $\tau$ and a period $P$. \\
+Consider an instance of the problem PRA, i.e., a routage graph $\cal{R_{\cal C}}$ and a period $P$. \\
 The {\bf conflict depth} of a route is the number of other routes which share an edge with it. 
@@
 The {\bf load} of a routage graph is the maximal number of routes sharing the same arc.
-It is clear that a $(P,\tau)$-periodic affectation must satisfy that $P$ is larger or equal to the load times $\tau$.
+It is clear that a $(P,1)$-periodic affectation must satisfy that $P$ is larger or equal to the load.
 
@@
       then the central arc to {\bf $c_t$}, the central target node, and an arc to its target.
-In addition to those central nodes, there are two sets of vertices, $S={s_0,...,s_{n-1}}$ and $T={t_0,...,t_{n-1}}$, of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$.
+In addition to those central nodes, there are two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$, of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$.
       The routes are the directed paths of the form $s_i,c_s,c_t,t_i$ and $t_i,c_t,c_s,s_i$.
@@
       We consider two periods P at these vertices, the the {\bf forward period} at $c_s$, and the {\bf backward period} at $c_t$.
-A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1})$ in the forward period, and  $c_t$ at time $m_{t_1} + t(c_t,r_{t_1})$ in the backward period.
-      A $(P,\tau)$-periodic affectation consist in choosing $\forall i \in n, m_i$, and $m_{{\cal C}(s_i)}$ such that, for any couples of routes $(r_{s_j}, r_{s_k}), j,k \in n$,
-      we have $[t(c_s,r_j)] \cap [t(c_s,r_k)] = \emptyset$.
-      and for any couples of routes $(r_{t_j}, r_{t_k}), j,k \in n$, we have $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$
-%       
-%   \todo{Définir la forward period et la backward period et dire à quoi correspond une affectation en terme de forward et backward period (placement de messages dans la première période}     
-%       Therefore, 
-%       finding an $(P,\tau)$-periodic affectation without collision, is equivalent to fix ...
-
-%       
-%       between the two central nodes is simplified in the forthcoming calculations.
-%       Let us call {\bf SN} (source node) the central node connected to leaves, and {\bf SN} (sources node), the one connected to sources.
-The period in those nodes are respectively called {\em forward period}, and {\em backward period}.
+A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1}) \mod P$ in the forward period, and  $c_t$ at time $m_{t_1} + t(c_t,r_{t_1})\mod P$ in the backward period.
+      A $(P,\tau)$-periodic affectation consist in choosing for all $i < n$, $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$,
+      we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$
 
@@
   In this subsection, we deal with a simpler version of the problem PALL.
-  We ask for a $(P,\tau)$-periodic affectation with all waiting times equal to $0$. 
-  In that case $MT({\cal M})$ is equal to twice the delay of the longer route, thus, $T_{max}$ is not relevant anymore. Since $w_i=0$, choosing $m_i$, the offset of the route from
-  $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i)$.
-  Moreover, in this context the weight of the arcs from $s_i$ to $c_s$ have no impact, therefore we assume they are 
-  equal to $0$. \\
-  For those reasons, in this case, we only have to consider the forward and backward periods.
-Indeed, setting the offset $m_{s_i}$ in the forward period automatically set the offsets $m_{{\cal C}(s_i)}$ in the backward period.
-  The goal is now to put messages in the forward period such that there is no collision in both periods.\\
-  Here, weight of arcs $(s_i,c_s)$ can be ignored, thus, the offsets $m_{s_i}$ are calculated like if all these weight are equal to 0.
-To find the real values, it is easy to delay the real sending in sources by the weight of the corresponding arc.
+  We ask for a $(P,\tau)$-periodic affectation {\bf with all waiting times equal to $0$} and we call this restricted problem  ??????????????? . 
+  In that case $MT({\cal M})$ is equal to twice the delay of the longer route, thus $T_{max}$ is not relevant anymore. 
+  Since $w_i=0$, choosing $m_i$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i) \mod P$.
+  Remark that we can assume that the weight of the arcs from $s_i$ to $c_s$ are all equal to $0$, since we can change 
+  all $m_i$ into $m_i - t(c_s,r_i) \mod P$ and obtain the same affectation.
 
@@
 
-    \paragraph{Algorithm}
     We present a simple policy, which works when the period is large with regards to the delay of the routes.
-    Send the messages in order from the shortest route to the longest route, on after each others in the forward period, without any slots between two messages, that is $m_{s_i} = \tau.i$, if the routes $r_i, i \in {0,...,n-1}$ are ordered by $\lambda(r_i)$ from the shortest to the longest one.
+    The message are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
+    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{s_i} = i\tau$.
+    We call this algorithm {\bf Shortest-Longest}.
 
-The message using the shortest route is sent before the others, so it comes back to the central node before the following ones.
-Then, the second message is sent before the others, and also will be back before the third etc... 
-Because the message $i$ is sent $\tau$ slots after the message $i-1$ ($m_{s_i} = m_{s_{i-1}} + \tau$), it comes back after the end of the message $i-1$: $m_{s_{i-1}}+ \tau + 2.\lambda(r_{s_{i-1}}) \le m_{s_i} + 2.\lambda(r_{s_i})$ because of $\lambda(r_{s_i}) \ge \lambda(r_{s_{i-1}})$.
+     By definition, there are no collision in the forward period and if the period is long enough, 
+     it is easy to see that the order of the messages are the same as in the forward period and that no collision can occur.
 
-      \paragraph{Period}
-      Because of $m_{s_i} = \tau.i$ in the forward period, there is no collisions.
-      To ensure that there is no collisions in the backward period, we must ensure that the last message ends before the end of the period P.
+      \begin{proposition}
+       The algorithm Shortest-Longest solves ??????????? if $n\tau + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0})) \leq P$.
+      \end{proposition}
+      \begin{proof}
+       Since $m_{s_i} = i\tau$, $[t(c_s,r_{s_i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.
+       We assume that $\lambda(r_{s_0}) = 0$, by removing $\lambda(r_{s_0})$ to every route, it does not change their order
+       or the result of this algorithm.
+
+      We have  $[t(c_s,r_{t_i})] = \{2 \lambda(r_{s_i}) + i\tau, \dots,  2 \lambda(r_{s_i}) + (i+1)\tau -1\}$ since $2 \lambda(r_{s_{n-1 }}) + n\tau \leq P$.
+       Since $ \lambda(r_{s_i}) \leq  \lambda(r_{s_{i+1}})$ by construction, we have  $2 \lambda(r_{s_i}) + (i+1)\tau -1 < 2 \lambda(r_{s_{i+1}}) + (i+1)\tau$
+       which proves that there are no collision on the backward period. 
+      \end{proof}
+
+      If the period is slightly smaller that the bound, a collision will occur on the route in the backward period, making 
+      this policy not useful even as a heuristic for longer routes.
+
+%       
+% The message using the shortest route is sent before the others, therefore on the backward period it cannot conflict 
+% 
+% comes back to the central node before the following ones.
+% Then, the second message is sent before the others, and also will be back before the third etc... 
+% Because the message $i$ is sent $\tau$ slots after the message $i-1$ ($m_{s_i} = m_{s_{i-1}} + \tau$), it comes back after the end of the message $i-1$: $m_{s_{i-1}}+ \tau + 2.\lambda(r_{s_{i-1}}) \le m_{s_i} + 2.\lambda(r_{s_i})$ because of $\lambda(r_{s_i}) \ge \lambda(r_{s_{i-1}})$.
+% 
+%       Because of $m_{s_i} = \tau.i$ in the forward period, there is no collisions.
+%       To ensure that there is no collisions in the backward period, we must ensure that the last message ends before the end of the period P.
 We have to find the minimum period P such that the last message have totally came back before P slots after the first message.
-
-      The this policy ensure us a period of $$P = \tau * n + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0}))$$ if routes $\{r_0,...,r_{s_{n-1}}\}$ are ordered
-from the shortest to the longest.
-
-We have to calculate the time taken by the last message to reach $c_t$. $2.\lambda(r_{s_0})$ is the first slot in which the first message is coming back in the backward period,
-and 2$\lambda(r_{s_{n-1}}) + n . \tau $ is the time at which the last message has totally passed the switch.
-Therefore, the period only depends of the difference between the longest and the shortest route: the larger this value is, the larger
-the period is.
+%       
+%       The this policy ensure us a period of $$P = \tau * n + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0}))$$ if routes $\{r_0,...,r_{s_{n-1}}\}$ are ordered
+% from the shortest to the longest. 
+% 
+% We have to calculate the time taken by the last message to reach $c_t$. $2.\lambda(r_{s_0})$ is the first slot in which the first message is coming back in the backward period,
+% and 2$\lambda(r_{s_{n-1}}) + n . \tau $ is the time at which the last message has totally passed the switch.
+% Therefore, the period only depends of the difference between the longest and the shortest route: the larger this value is, the larger
+% the period is.
+%
 

### 2017-03-27 modeleanneau/model.tex
2

@@
 \begin{enumerate}
- \item The node $u$ receives (from an external way) some latency critical data addressed to $v$.
+ \item The node $u$ receives (from another source) some latency critical data addressed to $v$.
  \item Those data are transferred to $v$ through the ring .
- \item After reception and computing of the message, the node $v$ sends an answer to $u$.
+ \item After a computation time of the message, the node $v$ sends an answer to $u$.
 \end{enumerate}
@@
 \section*{Sending policy}
-In the studied model, the ring has a {\bf broadcast and select} policy: when a node sends some data in a slot, this slot is {\em taken} by this node for an entire ride of the ring.
+In the studied model, the ring has a {\bf broadcast and select} policy.
+When a node send some a packet on the ring, it contains data for several destinations.
+Every node of the ring reads all the slots and keep the data addressed to it.
+It copy the data of the packet in the slot, but does not remove anything.
+The only node that can free a slot is the one which sent a packet in it.
+
+/%when a node sends some data in a slot, this slot is {\em taken} by this node for an entire ride of the ring.
 This means that every nodes of the ring can collect the information addressed to it, but it does not delete the data in the slot.
@@
 Thus, a node has to wait for a free slot before sending some data in the ring. To avoid overloading the ring, a node sends some data only if some criteria  are satisfied.
-We define by $Q$ the size of the buffer of a node, $\alpha$ the {\em minimum load} of the buffer, $0 \leq  \alpha \leq 1$, and $\delta$ the {\em maximum delay}.
+We define by $Q$ the capacity of the buffer of a node, $\alpha$ the {\em minimum load} of the buffer, $0 \leq  \alpha \leq 1$, and $\delta$ the {\em maximum delay}.
 

### 2017-03-28 modeleanneau/model.tex
avant merge

@@
 We consider an optical ring composed of $k$ nodes.
-We are in a discrete time Model: The time is split in $N$ slot, rotating to the following position each time step $t$.
+We are in a discrete time model: The time is split in $N$ slot, rotating to the following position each time step $t$.
 The number of slots is given by the length of the ring, and the time step $t$ is the switching granularity.
@@
 \end{enumerate}
- This periodic process has a critical end to end latency, thus a messages has to be the less buffered as possible before being send in the ring.
+ This periodic process has a critical end to end latency, thus a messages has to be as little buffered as possible before being sent in the ring.
 
 \section*{Sending policy}
-In the studied model, the ring has a {\bf broadcast and select} policy.
-When a node send some a packet on the ring, it contains data for several destinations.
+In the studied model, the nodes of the ring have a {\bf broadcast and select} policy.
+When a node sends a packet on the ring, it contains data for several destinations.
 Every node of the ring reads all the slots and keep the data addressed to it.
 It copy the data of the packet in the slot, but does not remove anything.
-The only node that can free a slot is the one which sent a packet in it.
+The only node that can free a slot is the one which send a packet in it.
 
-/%when a node sends some data in a slot, this slot is {\em taken} by this node for an entire ride of the ring.
+%when a node sends some data in a slot, this slot is {\em taken} by this node for an entire ride of the ring.
 This means that every nodes of the ring can collect the information addressed to it, but it does not delete the data in the slot.
@@
 
-Thus, a node has to wait for a free slot before sending some data in the ring. To avoid overloading the ring, a node sends some data only if some criteria  are satisfied.
+Thus, a node has to wait for a free slot before sending a packet in the ring. To avoid overloading the ring, a node sends a packet only if some criteria  are satisfied.
 We define by $Q$ the capacity of the buffer of a node, $\alpha$ the {\em minimum load} of the buffer, $0 \leq  \alpha \leq 1$, and $\delta$ the {\em maximum delay}.
 
-The node sends some data in a slot if:
+The node sends a packet in a slot if:
 \begin{itemize}
@@
 \end{itemize}
+
+The buffer of a node is filled with the FIFO rule by a traffic coming from external sources.
+Then, when the node has an available free slot, the packet is inserted in the slot if one of the previous constraints are satisfied.
+Otherwise the node does not send anything in the ring and wait for the next free slot.
+
+\begin{center}
+
+      \includegraphics[scale=0.7]{insertion0.pdf}
+
+\end{center}
+
+\section{C-RAN context}
 
@@
  \item One slot of the ring can carry all the data stacked in $Q$ ($Q < 1Mb$).
- \item $\delta =$ ?
- \item $\alpha =$ ?
+
 \end{itemize}

### 2017-03-29 article/article.tex
article algos sans waiting time

@@
 
-    We introduce a greedy algorithm to build a $(P,\tau)$-periodic affectation, which provably works when
+    We propose a greedy algorithm to build a $(P,\tau)$-periodic affectation, which provably works when
     the period is large enough with regards to the number of routes and size of messages. In other words, 
@@
     \begin{proposition}
-    There is an algorithm, which finds a $(P,\tau)$-periodic affectation in time $O(n^2)$ when $P \geq 3n\tau$.
+    There is an algorithm, which finds a $(P,\tau)$-periodic affectation in time $O(n^2)$ when $P \geq 3n\tau$,
+    where $n$ is the number of routes.
     \end{proposition}
     \begin{proof}
-     We consider the forward period and cut it into consecutive macro slots of time of size $\tau$.
-The algorithm works in the following way: select the first route $k+1$ for which the offset as not been chosen.
-Try every of the $3N-k$ offsets which put the message in one free macro slot in the forward period.
-It also fixes the position of a message in the backward period, and we choose the first offset which does not create a collision in the backward period.
-     Assume we choose the offset of the route $r_{k+1}$, we have  at least $3n - k$ free macro-slots, since $P \geq 3n\tau$.
+     We consider the forward period and cut it into consecutive macro slots of $\tau$ time slots.
+The algorithm works by chosing an offset for each route in the following way: try all offests which put the message in a yet not used macro slot in the forward
+     period.
+An offset also fixes the position of the message in the backwward period, chose the first one which does not create a collision.
+We now prove that this algorithm always find an offset for all routes when $P \geq 3n\tau$.
+
+     Assume we are choosing the offset of the route $r_{k+1}$, we have  at least $P - k \geq 3n - k$ free macro-slots, since $P \geq 3n\tau$.
 Each of these $3n - k$ possible offset values translates into $3n - k$ positions of messages in the backward period.
@@
 There are already $k$ messages of size $\tau$ in the backward period.
-One such message can intersect at most $2k$ potential positions, therefore  amongst the possible $3n - k$ positions, there are  $3n - k -2k$ which are without collision.
-Since $k < n$, one of the choice is without collision, which proves that the algorithm terminates and find a
-     $(P,\tau)$-periodic affectation. 
+One such message can intersect at most $2$ potential positions since they are disjoint intervals.
+Therefore  amongst the possible $3n - k$ positions, there are  $3n - k -2k$ which are without collision.
+Since $k < n$, one of the choice is without collision, which proves that the algorithm terminates and find a  $(P,\tau)$-periodic affectation.
+
+     This algorithm works with a complexity $O(n^2)$, since for the $k^{\text{th}}$ route we have to try at most $2k$ offsets before finding a correct one.
+We can test the $2k$ offsets of the backward period in time $O(k)$ by maintaining an ordered list of the intervals used by already set routes.
      \end{proof}
-     This algorithm works in a complexity $n^2$, since we have to try every free macro-slots for every routes.
+
       \begin{center}
@@
       \end{center}
-    \todo{Avec une structure de données plus maligne on doit pouvoir faire n, non ?}
 	\begin{algorithm}[H]
@@
 	\end{algorithm}
-%       \paragraph{Period}
-% 	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
-% 	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots.
-Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
 
-% 	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period.
-Those $3.c - k$ gives us $3.c - k$ possible slots in the backward periods.\\
-% 	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period.
-Since $k<c$,  $2k < 3.c - k$, thus using the pigeonhole principle, there is at least one free slot in the backward period for the new message.
+This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
+In fact, experimental data in Subsection~\cite{} suggest that the algorithm works well as soon as $P \geq ????? \tau$.
 
-%     \subsubsection{Exhaustive generation}
+	\subsubsection{Exhaustive generation}
 % 	\begin{algorithm}[H]
@@
 %       \end{algorithm}
-%       {\bf {\em Lost size}}, is the size lost when an interval is too few to put another packet.
-Ex : if the interval [250;3250[ receives a packet of size 2500, there is 500 slots lost, because there is no way to uses the slots for another packet.\\
-%       \todo{ecrire l'algo? si ou le réécrire}
+
 % 	    
-      We can try to enumerates all the solutions by traversing a tree. The leaves of the tree are 
-      the $(P-\tau)$-periodic affectations, and the nodes are partial solutions. A partial solution is a choice of a starting time for a subset of the routes.
-      For each route, the algorithm tries every possible starting offset until it finds one available (that allows the message to come back without collisions).
-When a route have been scheduled, it take another route that have not been scheduled yet.
-      This creates a new sub-tree in which the algorithm will try every possible starting offset too, and create a sub-tree on the following route too.
-      If no offset are available for a route, this means that the partial solution is not good, so the algorithm backtracks over the tree that is,  it goes back to the father of the current sub-tree, and continue from there.
-      Once a leaf is obtained, the algorithm stops and return the $(P-\tau)$-periodic affectation.\\  
-      Such an algorithm is an {\bf Exhaustive Generation} and has an exponential complexity.
-Thus, once we search for $(P-\tau)$-periodic affectations on graphs with a huge number of routes and an huge period P, if there is no solutions available, this algorithm takes too many time.
-      To reduce the number of useless calculation, we can imagine cuts in the tree :
+      We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found
+      a $(P,\tau)$-periodic affectation. The algorithm is a depth-first traversal of a tree whose leaves are the $(P,\tau)$-periodic
+      affectations or failures and the nodes are partial solutions.
+A partial solution $S$ is a choice of a starting time for a subset of the routes such that none of these routes collide in the forward or backward period.
+For simplicity we will also denote by $S$ the set of routes whose offsets are fixed by $S$.
+A partial solution $S'$ extends $S$ if $S' = S \cup \{r'\}$ and for all $r \in S$, $m_r + \tau \leq m_{r'}$, that is the route $r'$ comes after all routes in $S$ in the forward period.
+In the tree, the children of a partial solutions are all partial solutions which extend it.
+Therefore a node corresponding to $k$ fixed routes can have as many as $(n-k)P$ children.
+Since the tree is of depth $n$, we can have as many as $n!P^n$ elements and while $n$ is often small, $P$ may be large.
+Therefore we have to find cuts in the tree to avoid to explore it entirely and henceforth make the algorithm practical.
+We propose the three following ones, the first two being useful when the period is small with regards to the number of routes:
+
+      \todo{       Trouver un meilleur vocabulaire, peut-être avec des intervalles triés pour représenter les solutions partielles}
+
       \begin{enumerate}
-       \item In the forward windows, each message is placed after the previous one, that is $m_{s_i} > m_{s_j}$ (here, $s_i$ is the source placed before $s_j$ by the algorithm).
+       \item We maintain a counter $c_f$ which counts the number of routes which can be placed in the forward
+       period. If at some point this number is less than the number of routes which are not in the partial solution,
+       it is a failure and the algorithm backtracks. At the beginning of the algorithm $c_f = P / \tau$.
+       Then when a route is fixed at some offset $m_r$, larger than all previous offsets, then $c_f = (P - m_r) / \tau $.
+
+       \item We maintain a counter $c_b$ which counts the number of routes which can be placed in the backward
+       period. If at some point this number is less than the number of routes which are not in the partial solution,
+       it is a failure and the algorithm backtracks. At the beginning of the algorithm $c_f = P / \tau$.
+       Consider a partial solution with $k$ routes and denote by $a_i$ their offset in the backward period.
+       The $a_i$ are in increasing order and without loss of generality we assume that $a_1 = 0$.
+Remark that the number of routes which can be placed in the interval of free slots $\{a_i+\tau, a_{i+1}-1\}$
+       is $(a_{i+1} -a_i) / \tau) -1 $.
+Therefore the total number of routes which can be placed in the backward period is $\displaystyle{\left( \sum_{i=1}^{k-1} (a_{i+1} -a_i)/\tau - 1 \right)} + (P - a_k) / \tau $.
+       The counter $c_b$ can be maintained in constant time since each time a route is added, an interval is split into two and we can 
+       use these two new intervals only to update its value.
+
+%        In the forward windows, each message is placed after the previous one, that is $m_{s_i} > m_{s_j}$ (here, $s_i$ is the source placed before $s_j$ by the algorithm).
 Each time a new message is scheduled, there is some possible lost slots between $m_{s_i}+\tau$ and $ m_{s_j}$.
@@
 Thus, if the number of the remaining slots in the forward period is lower than the number of slots needed to put the remaining messages, we can consider that the actual partial solution is not good.
-       \item  Each time we add a new message in the backward period, we cut a free interval in two new smaller free intervals, plus the scheduled message.
+%        \item  Each time we add a new message in the backward period, we cut a free interval in two new smaller free intervals, plus the scheduled message.
 Each free intervals has a number of macro slots (ex: 2,6).
 If the sum of all the integer parts of the macro slots is lower than the number of remaining messages to schedule, the actual partial solution is not good.
-       \item ...
+       \item 
+       Let $S_1$ and $S_2$ be two partial solutions with the same subset of fixed routes, but different offsets.
+       A sequence of extensions of a partial solution $S$ is a sequence of pair of route and offset, which define a path from $S$ in the tree.
+We say that $S_1$ dominates $S_2$, if any sequences of extensions of $S_2$, is a sequence of extensions of $S_1$.
+       Then if there is a solution in $S_2$, there must be also one in $S_1$, therefore if we detect that some node is dominated in the tree we can backtrak when we encounter it.
+
+       %Meilleure explication notion de slots utilisables.
+Si une solution partielle a strictement moins de slots utilisables (vu en tant qu'ensemble) qu'une autre avec les mêmes routes alors elle est dominée
+
+       Consider a partial solution $S$ which we extend into $S' = S \cup \{ r \}$ such that the offset of 
+       $r$ is the smallest possible, denoted by $m$.
+       Say that the offset of $r$ in the backward period is $m+ \lambda$ and that the end of the message before $m + \lambda$ in the backward period is $a$.
+Then all extensions of $S$ into $S'' = S \cup \{ r \}$ with $ m < m_r < a + \tau - \lambda$.
+       are dominated by $S'$. Indeed, $S''$ have striclty less empty slots in the forward period and in the backward period, there are only two intervals ...
+
+       \todo{       Mettre un dessin !!!!  Dire comment la coupe 3 interragit bien avec la 1, car elle force $m_i$ à croitre vite, ce qui
+       permet d'appliquer rapidement la coupe}
+
              \end{enumerate}

### 2017-03-31 code/simons.c
toujours buggé

@@ -611,7 +611,11 @@ Ensemble * crisis(Ensemble * ens,Element * crisise, Element * elemspere,Element 
 	if(ens == NULL)
 		return NULL;
 	//printf("ens != NULL\n");
-	//affiche_ensemble(ens);printf("\n");
+	printf("Ensemble et elems pere a l'entree de crisis\n");
+	affiche_ensemble(ens);printf("\n");
+	affichejobs(elemspere);
+	printf("\n Et la crisis est :");affichejobs(crisise);printf("\n");
+	printf("fin\n");
 	Ensemble * ens2 = NULL;
 	Ensemble * tmp = NULL;
 	Ensemble * debut = ens;
@@ -637,7 +641,7 @@ Ensemble * crisis(Ensemble * ens,Element * crisise, Element * elemspere,Element 
 				//printf("PULL X = %d\n",elemtmp->index);
 				ajoute_elemt_fin(elemspere,elemtmp->index,elemtmp->release,elemtmp->deadline);
 				date = ens->temps_depart;
-				//printf("PULL(%d) = %d\n",crisise->index,elemtmp->index);
+				printf("PULL(%d) = %d\n",crisise->index,elemtmp->index);
 				if(ens2 == NULL)
 				{
 					ens2 = cree_ensemble(-2,-1);
@@ -696,14 +700,14 @@ Ensemble * crisis(Ensemble * ens,Element * crisise, Element * elemspere,Element 
 		if(ens->frereG)//on regarde si on est pas au debut de l'ensemble
 		{
 			
-			//printf("On ajoute ");affiche_ensemble(ens);printf("au r.s\n");
+			printf("On ajoute ");affiche_ensemble(ens);printf("au r.s\n");
 			ens = ens->frereG;
 			libereens(ens->frereD);
 			ens->frereD = NULL;
 		}
 		else
 		{
-			//printf("On ajoute ");affiche_ensemble(ens);printf("au r.s\n");
+			printf("On ajoute ");affiche_ensemble(ens);printf("au r.s\n");
 			libereens(ens);
 			ens = NULL;
 		}
@@ -712,18 +716,22 @@ Ensemble * crisis(Ensemble * ens,Element * crisise, Element * elemspere,Element 
 		if(ens == NULL)return NULL;
 	}
 	
-	//affiche_ensemble(ens2);printf(" R.S.\n");
-	//affichejobs(elems);
+
 	
 	Ensemble* ens3 = NULL;
[…]

### 2017-04-12 article/article.tex
toujours buggé
res without wt

@@
 
-   \subsection{Problems}
+   \subsection{Problems}\label{nonmonotone}
 
@@
 
-	\subsubsection{Exhaustive generation}
+	\subsubsection{Exhaustive search}
 % 	\begin{algorithm}[H]
@@
       The following performance evaluation results compares the previous algorithms.
-Since we try to find a linear time algorithm for the problem PALL, Exhaustive Generation is not a good solution.
-However, Greedy 3NT and Shortest-Longest are some greedy heuristics and gives us a linear complexity.
+Since we try to find a polynomial time algorithm for the problem PALL, Exhaustive Generation is not a good solution.
+However, Greedy 3NT and Shortest-Longest are some greedy heuristics and gives us a polynomial complexity.
 We tried to determine which algorithm gives a solution with the minimal period.
@@
       \paragraph{Short routes}
-      To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(r_{s_i}) < 2100$ slots, that is, at the most, 5 km between the RRH and its BBU.
+      To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU.
 The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route.
@@
 
-      For each algorithm, we made a linear research of the minimal period for which, there is a solution on the given instance.
+      To find the minimal period on a given instance with an algorithm, it is necessary to run the algorithm with some different periods and take the shortest one that does not fail.
+Since the existence of a $(P-\tau)-periodic affectation)$ is not monotone with regard to P (see section \ref{nonmonotone}), a dichotomous search is not appropriate.
+Thus, for each algorithm, we made a linear search of the minimal period for which, there is a solution on the given instance.
 The following figure shows us the average periods on 1000 graphs, for a growing number of routes.
       The results of the Exhaustive generation can be considered as a lower bound, indeed, for a given period, this algorithm finds the solution, if it exists.
-      As an information, we drew the $\tau.n$ (i.e. the size taken by the messages in the period) and the $2.(\tau.n) $ lines.
+      As an information, we drew the $\tau.n$ (i.e. the size taken by the messages in the period) and the $3.(\tau.n) $ lines.
 
@@
       Then, we looked at the evolution of the minimal period required with the different algorithm if we significantly increase the size of the route.
-The following figure shows us the success rate of the algorithms, for 8 routes of size between 0 and 60000 slots, according to the period.
+The following figure shows us the success rate of the algorithms, according to the period, for 8 routes in which  $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 30000 slots, that correspond to have the size of the route and the period approximately in the same order of magnitude.
 
+      By increasing the size of the routes, the cuts of the exhaustive search, are less efficient.
+Thus, we defined a counter that allow the search to end if no solution are found.
+On the following figure, the upper bound represents the cases in which the exhaustive search found a solution plus the number of {\em early} halts of the search.
+The real upper bound is probably between those two curves.
+
+      The reason why the shortest longest were optimal in the previous experiences (i.e.
+having routes shorter than message size) is no longer reviewed.
+We can also imagine that sending the shortest route first on long routes significantly increases the period, because there will be a lot of lost size in the backward and forward periods.
+
+      One the other hand, one can imagine that the greedy $3n\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
        \begin{center}
@@
       Whereas, the Geedy 3NT gives us solutions with much lower period than Shortest Longest.
-      Because of it's polynomial complexity, the Exhaustive generation can freeze the simulation when the solution is not easy to find. Thus, we let it stop after a defined number of calculation. 
-      The Exhaustive Generation curve gives us the solution when the algorithm has found a solution, and the Upper bound gives us the number of found solutions plus the number of time the algorithm stopped.
-The real Upper bound is probably between those two curves.
+The exhaustive search keeps finding good solutions in short periods but it fails a lot for periods until $2.n.\tau$.
 

### 2017-04-12 code/code.c

@@ -698,9 +698,8 @@ void echec_periode(int nb_routes, int taille_paquets,int taille_route,int tmax, 
 	FILE * F = fopen("results_echec_periode.data","w");
 	Graphe g ;
 	float a,b,c;
-	int resultat = INT_MAX;
 	int tmp;
-	for(int j=taille_paquets*nb_routes;j<taille_paquets*nb_routes*2;j+=1000)
+	for(int j=taille_paquets*nb_routes;j<taille_paquets*nb_routes+2500;j+=100)
 	{
 		a=0;
 		b=0;
@@ -712,21 +711,21 @@ void echec_periode(int nb_routes, int taille_paquets,int taille_route,int tmax, 
 			//affiche_matrice(g);
 			
 			//b=longest_etoile_2(g,2500,40000);
-			for(int k =0;k<1000;k++)
+			for(int k =0;k<10;k++)
 			{
 				tmp = simons(g, taille_paquets,tmax,1,0);
 				
-				if(tmp != -1)
-					if(tmp < j)
-						if(tmp < resultat)
-							resultat = tmp;
+				if(tmp != -1)//si tmax trop petite (peu probable)
+					if(tmp <= j)
+					{
+						a++;
+						break;
+					}
 			}
 			
-			if(resultat != INT_MAX)
-				a++;
-			if(simons(g, taille_paquets, tmax,1,1) < j)
+			if(simons(g, taille_paquets, tmax,1,1) <= j)
 				b++;
-			if(simons(g, taille_paquets, tmax,1,2)< j)
+			if(simons(g, taille_paquets, tmax,1,2)<= j)
 				c++;
 			libere_matrice(g);
 		}
@@ -768,8 +767,8 @@ int main()
 		 simons(g,2500,28000,400000,0);
 		libere_matrice(g);
 	*/
-	departs(8,2500,7000,31000,1000);
-	//echec_periode(8,2500,7000,31000,1000);
+	//departs(8,2500,7000,31000,1000);
+	echec_periode(8,2500,7000,31000,1000);
 	//echec_tmax(8,2500,7000,40000,1000);
 
 	return 0;

### 2017-04-12 code/simons.c

@@ -1327,7 +1327,7 @@ int simons(Graphe g, int taille_paquet, int TMAX, int mode_test,int mode)
 		int periode_aller = aller[greater(aller,nbr_route)]-aller[lower(aller,nbr_route)]+taille_paquet;
 		int periode_retour = retour[greater(retour,nbr_route)]-retour[lower(retour,nbr_route)]+taille_paquet;
 		maximum = max(periode_retour,periode_aller);
-
+		affiche_tab(retour,nbr_route);printf("maximum = %d\n",maximum);
 	}
 	
 	return maximum;

### 2017-04-19 article/article.tex
eojv

@@
 Since we try to find a polynomial time algorithm for the problem PALL, Exhaustive Generation is not a good solution.
-However, Greedy 3NT and Shortest-Longest are some greedy heuristics and gives us a polynomial complexity.
+However, Greedy $3.n.\tau$ and Shortest-Longest are some greedy heuristics and gives us a polynomial complexity.
 We tried to determine which algorithm gives a solution with the minimal period.
@@
       The next results is to theoretically prove that, with those parameters, the Shortest-Longest algorithm gives optimal solutions, like this experimental study suggests it does. 
-      About the Greedy 3NT Algorithm, with those parameters, it always gives us bigger periods than the Shortest longest. 
+      About the Greedy $3.n.\tau$ Algorithm, with those parameters, it always gives us bigger periods than the Shortest longest. 
       We can also observe that, for any algorithm, the average minimal periods increases linearly with the number of routes. Thus, the following experiences are made on a fixed number of routes : 8.
@@
 
-      One the other hand, one can imagine that the greedy $3n\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
+      One the other hand, one can imagine that the greedy $3.n.\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
        \begin{center}
@@
  \item To be eligible, a job needs to be able to come back on the switch at the current clock (if clock = 0, take the first message able to come back).
- \item Between the eligible jobs, schedule first the one which has the longest route and gives it the offset time $m_{\cal C(s_i)} = clock$.
- \item Update the clock at the time in which the scheduled task is over: $$clock = clock + message\ length$$.
+ \item Between the eligible jobs, schedule first the one which has the lowest deadline.
+ \item Repeat until all the messages had been scheduled.
 \end{enumerate}
+
+For any route i, the deadline correspond to $m_{s_i} + T_{max}$.
 
@@
 
-	\paragraph{Algorithm}
 	\paragraph{Analysis}

### 2017-04-19 code/simons.h

@@ -1,3 +1,5 @@
 
 int simons(Graphe g, int taille_paquet, int TMAX, int mode_test, int mode);
 int is_ok(Graphe g, int taille_paquet, int * mi, int * wi);
+void fisher_yates(int * tab, int taille);
+void tri_bulles_inverse(int* tab,int* ordre,int taille);

### 2017-04-25 article/article.tex

--- 2017-03-29 article/article.tex
@@
       A $(P,\tau)$-periodic affectation consist in choosing for all $i < n$, $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$,
-      we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$
+      we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$.
 
@@
   all $m_i$ into $m_i - t(c_s,r_i) \mod P$ and obtain the same affectation.
+
+  \todo{Attention cette simplification n'est pas assez explicite.}
 
@@
 This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
-In fact, experimental data in Subsection~\cite{} suggest that the algorithm works well as soon as $P \geq ????? \tau$.
+In fact, experimental data in Subsection~\ref{} suggest that the algorithm works well as soon as $P \geq ????? \tau$.
 
-	\subsubsection{Exhaustive generation}
+	\subsubsection{Exhaustive search}
 % 	\begin{algorithm}[H]
@@
 
+     \todo{Il faut faire une présentation modulaire avec d'un coté choix de de départ des messages, ->LS, ->SL, ->RANDOM
+     puis choix de retour, Greedy et Optimal. Ensuite on montre que dans le cas simple de toutes les arêtes de départ à la même valeur,
+     LSG est optimal (dire que c'est un cas raisonnable). Éventuellement deux valeurs différentes serait raisonnable mais je n'ai pas trouvé de bons algos.
+     Ensuite il faut expliquer proprement greedy et Simons (sans donner tous les détails pour Simons) et expliquer les limitations -> pas de gestion de la période pour Simons.
+     On peut gérer la période pour Simons en bruteforce sur les routes. Il faut que j'écrive mes algos FPTs en le nombre de routes même si on ne les implémente pas.}
+
 To find a solution with waiting times, the following heuristic is suggested:

### 2017-04-27 article/article.tex
modifications dans la partie sans waiting times

--- 2017-04-19 article/article.tex
@@
 
-	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $dl(u,v) \geq 1$ that we call the delay and
+	We consider a directed graph $G=(V,A)$ modeling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $dl(u,v) \geq 1$ that we call the delay and
 	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. 
@@
       \end{center}
-       \caption{A routage graph with $(0,\dots,0)$ as a $(2,1)$-periodic affectation}
+       \caption{A routage graph with $(0,0,0)$ as a $(2,1)$-periodic affectation}
       \end{figure}
@@
 
-	\begin{lemma} 
+	\begin{lemma} \label{lemma:monotonic}
 	 For any odd $P$, there is a routage graph such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
@@
 
-      The message size $\tau$ in this process time, if we want to consider the time between the emission of the first slot and the reception of the last slot of the message.
-Since $\tau$ is the same for every routes, it does not change the calculations.
+      In the process time, we count the time between the first time at which a message is emitted and 
+      the first time at which the message comes back.
+Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
+      However, since all messages are of size $\tau$, it will not change the problem we solve in the rest of the article and that we now introduce.
 
@@
 We give two alternate proofs that PRA is $\NP$-complete.
-The first one works for conflict depth $2$ and is minimal in this regards since we later prove that for conflict depth one,
-it is easy to solve PRA. The second one reduces the problem to graph coloring and implies inapproximability when one tries to minimize the parameter $P$. \\
+The first proof works already for conflict depth two. Remark that for conflict depth one,
+the graph can be seen as a set of disjoint pair of routes, on which PRA and PALL can be solved in linear time. 
+ The second proof reduces the problem to graph coloring and implies inapproximability when one tries to find the smallest possible $P$. \\
 
@@
 
-  \subsection{Tractable cases of PRA}
-
-    In this section, we present a few polynomial cases, in particular when the conflict depth is one.
-
-    The problem PALL seems to be hard to solve, even for very simple classes of graphs, as seen in the next section.
+%     
+%   \subsection{Tractable cases of PRA}
+%     
+%     In this section, we present a few polynomial cases, in particular when the conflict depth is one.
+%     When the conflict depth is one, every route can share an arc with only a single other route. 
+%     Therefore 
+%     
+%     
+%     The problem PALL seems to be hard to solve, even for very simple classes of graphs, as seen in the next section.
 
@@
 A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1}) \mod P$ in the forward period, and  $c_t$ at time $m_{t_1} + t(c_t,r_{t_1})\mod P$ in the backward period.
-      A $(P,\tau)$-periodic affectation consist in choosing for all $i < n$, $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$,
-      we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$
+      A $(P,\tau)$-periodic affectation consist in choosing for all $i < n$, $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$, we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$.
 
@@
   In this subsection, we deal with a simpler version of the problem PALL.
-  We ask for a $(P,\tau)$-periodic affectation {\bf with all waiting times equal to $0$} and we call this restricted problem  ??????????????? . 
-  In that case $MT({\cal M})$ is equal to twice the delay of the longer route, thus $T_{max}$ is not relevant anymore. 
+  We ask for a $(P,\tau)$-periodic affectation {\bf with all waiting times equal to $0$} and we call this restricted problem  
+  {\bf Periodic Assignment for Zero Latency} or PAZL. 
+  In that case $MT({\cal M})$ is equal to twice the delay of the longest route, thus $T_{max}$ is not relevant anymore. 
   Since $w_i=0$, choosing $m_i$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i) \mod P$.
-  Remark that we can assume that the weight of the arcs from $s_i$ to $c_s$ are all equal to $0$, since we can change 
+ We assume from now on that the weight of the arcs from $s_i$ to $c_s$ are all equal to $0$, since we can change 
   all $m_i$ into $m_i - t(c_s,r_i) \mod P$ and obtain the same affectation.
@@
      By definition, there are no collision in the forward period and if the period is long enough, 
-     it is easy to see that the order of the messages are the same as in the forward period and that no collision can occur.
+     it is easy to see that in the backward period the order of the messages are the same as in the forward period and that no collision can occur.
 
-      \begin{proposition}
-       The algorithm Shortest-Longest solves ??????????? if $n\tau + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0})) \leq P$.
+      \begin{proposition} When $n\tau + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0})) \leq P$, the algorithm Shortest-Longest solves PAZL.
       \end{proposition}
@@
        Since $m_{s_i} = i\tau$, $[t(c_s,r_{s_i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.
-       We assume that $\lambda(r_{s_0}) = 0$, by removing $\lambda(r_{s_0})$ to every route, it does not change their order
-       or the result of this algorithm.
 
+       We assume that $\lambda(r_{s_0}) = 0$, by removing $\lambda(r_{s_0})$ to every route, it does not change the order on the routes
+       nor the result of this algorithm.
       We have  $[t(c_s,r_{t_i})] = \{2 \lambda(r_{s_i}) + i\tau, \dots,  2 \lambda(r_{s_i}) + (i+1)\tau -1\}$ since $2 \lambda(r_{s_{n-1 }}) + n\tau \leq P$.
@@
     \begin{proposition}
-    There is an algorithm, which finds a $(P,\tau)$-periodic affectation in time $O(n^2)$ when $P \geq 3n\tau$,
-    where $n$ is the number of routes.
+    Let  $n$ be the number of routes and let $ 3n\tau \leq P$, then there is an algorithm which finds a $(P,\tau)$-periodic affectation in time $O(n^2)$.
     \end{proposition}
@@
      We consider the forward period and cut it into consecutive macro slots of $\tau$ time slots.
-The algorithm works by chosing an offset for each route in the following way: try all offests which put the message in a yet not used macro slot in the forward
+The algorithm works by choosing an offset for each route in the following way: try all offests which put the message in a yet not used macro slot in the forward
      period.
-An offset also fixes the position of the message in the backwward period, chose the first one which does not create a collision.
+The choice of an offset also fixes the position of the message in the backward period, chose the first one which does not create a collision.
 We now prove that this algorithm always find an offset for all routes when $P \geq 3n\tau$.
@@
       \end{center}
-	\begin{algorithm}[H]
-	\caption{Greedy affectation}
-	\begin{algorithmic}
-	\REQUIRE ${\cal R}_{\cal C}$, period $P$
-	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
-	\STATE $P1[P/\tau]$ macro slots of size $\tau$ in forward period.
-	\STATE $P2[P]$ slots backward period.
-	\FORALL{source $s_i$ in S }
-
-	\FORALL{macro slot j in P1}
-
-	\IF{$P1[j]$ is free AND the corresponding slots in P2 are free}
-
-	\STATE $m_{s_i} \leftarrow j.\tau$
-	\ENDIF
-
-	\IF{No intervals are found for $s_i$}
-	\STATE return FAILURE
-	\ENDIF
-	\ENDFOR
-
-	\ENDFOR
-
-	\end{algorithmic}
-	\end{algorithm}
+% 	\begin{algorithm}[H]
+% 	\caption{Greedy affectation}
+% 	\begin{algorithmic}
+% 	\REQUIRE ${\cal R}_{\cal C}$, period $P$
+% 	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
+% 	\STATE $T$ a table of the macro slots of size $\tau$ in the forward period.
+% 	\STATE $L$ a list of free intervals in the backward period%$P2[P]$ slots backward period.
+% 	\FORALL{source $s$ in S}
+% 
+% 	\FORALL{free intervals $[a,b]$ in $L$}
+% 	\FORALL{ $a/\tau - \lambda(s) <j< b/\tau - \lambda(s)$ }
+% 	\IF{ $T[j] == FREE$}
+% 	\STATE $m_{s} \leftarrow j.\tau$
+% 	\STATE $T[j] = USED$
+% 	\STATE update $[a,b]$ in $L$
+% 	\STATE BREAK
+% 	\ENDIF
+% 	\ENDFOR
+% 	\ENDFOR
+% % 	
+% % 	\IF{No intervals are found for $s_i$}
+% % 	\STATE return FAILURE
+% % 	\ENDIF
+% % 	\ENDFOR
+% 
+% 	\ENDFOR
+% 
+% 	\end{algorithmic}
+% 	\end{algorithm}
+\todo{J'ai commencé à modifier l'algo pour qu'il colle, mais ça n'est pas encore ça. 
+pas sur que ça vaille la peine de le mettre, je le commente pour l'instant.}
 
 This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
-In fact, experimental data in Subsection~\cite{} suggest that the algorithm works well as soon as $P \geq ????? \tau$.
+In fact, experimental data in Subsection~\ref{sec:experimental_results} suggest that the algorithm works well as soon as $P \geq 1.5 \tau$ for small routes.
+
+\todo{vérifier cette affirmation en faisant une expérience et une régression linéaire}
 
@@
       We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found
-      a $(P,\tau)$-periodic affectation. The algorithm is a depth-first traversal of a tree whose leaves are the $(P,\tau)$-periodic
-      affectations or failures and the nodes are partial solutions.
-A partial solution $S$ is a choice of a starting time for a subset of the routes such that none of these routes collide in the forward or backward period.
-For simplicity we will also denote by $S$ the set of routes whose offsets are fixed by $S$.
-A partial solution $S'$ extends $S$ if $S' = S \cup \{r'\}$ and for all $r \in S$, $m_r + \tau \leq m_{r'}$, that is the route $r'$ comes after all routes in $S$ in the forward period.
-In the tree, the children of a partial solutions are all partial solutions which extend it.
-Therefore a node corresponding to $k$ fixed routes can have as many as $(n-k)P$ children.
-Since the tree is of depth $n$, we can have as many as $n!P^n$ elements and while $n$ is often small, $P$ may be large.
+      a $(P,\tau)$-periodic affectation. We have $n$ routes denoted by $\{0,\dots,n-1\}$. A partial solution $S$ is 
+      a partial function from $[n]$ to $\{0,1,\dots,P-\tau -1\}$ which sets a starting time for a subset of the routes $R(S) \subseteq [n]$,
+      such that there are no collisions for these routes.
+A partial solution $S'$ extends $S$, if it sets one more routes than $S$ to a larger starting time than all routes in $S$, that is $R(S') = R(S) \cup \{r'\}$ and for all  $r \in R(S)$, $S(r) + \tau \leq S'{r'}$.
+We define a tree whose nodes are partial solutions and such that the root is the empty partial solution and
+      the children of a partial solution are the partial solutions which extend it. All solutions to our problem will be 
+      leaves in this tree, therefore our algorithm is simply a depth-first search of the tree.
+
+      Remark that a node $S$ with $|R(S)| = k$ can have as many as $(n-k)P$ children.
+Since the tree is of depth $n$, the tree may have as many as $n!P^n$ elements and while $n$ is often small, $P$ may be large which makes its traversal intractable.
 Therefore we have to find cuts in the tree to avoid to explore it entirely and henceforth make the algorithm practical.
-We propose the three following ones, the first two being useful when the period is small with regards to the number of routes:
-
-      \todo{       Trouver un meilleur vocabulaire, peut-être avec des intervalles triés pour représenter les solutions partielles}
+Cuts correspond to the detection of subtrees which contain no solutions and can thus be skipped.
+      We now propose three cuts, the first two being particularly useful when the network is loaded ($n\tau$ is not much smaller than $P$).
 
       \begin{enumerate}
-       \item We maintain a counter $c_f$ which counts the number of routes which can be placed in the forward
-       period. If at some point this number is less than the number of routes which are not in the partial solution,
-       it is a failure and the algorithm backtracks. At the beginning of the algorithm $c_f = P / \tau$.
-       Then when a route is fixed at some offset $m_r$, larger than all previous offsets, then $c_f = (P - m_r) / \tau $.
+       \item We consider the number of slots which can be used by routes not yet fixed by a partial solution in the 
+       \emph{forward period}.
+When we extend a solution into $S$ by a route at offset $m$, then at most $(P - m) / \tau $ routes can still be set without collisions in the forward period.
+If that value is less than the number of routes which are not in $R(S)$, it is a failure and the algorithm backtracks.
 
-       \item We maintain a counter $c_b$ which counts the number of routes which can be placed in the backward
-       period. If at some point this number is less than the number of routes which are not in the partial solution,
-       it is a failure and the algorithm backtracks. At the beginning of the algorithm $c_f = P / \tau$.
-       Consider a partial solution with $k$ routes and denote by $a_i$ their offset in the backward period.
-       The $a_i$ are in increasing order and without loss of generality we assume that $a_1 = 0$.
-Remark that the number of routes which can be placed in the interval of free slots $\{a_i+\tau, a_{i+1}-1\}$
-       is $(a_{i+1} -a_i) / \tau) -1 $.
-Therefore the total number of routes which can be placed in the backward period is $\displaystyle{\left( \sum_{i=1}^{k-1} (a_{i+1} -a_i)/\tau - 1 \right)} + (P - a_k) / \tau $.
-       The counter $c_b$ can be maintained in constant time since each time a route is added, an interval is split into two and we can 
-       use these two new intervals only to update its value.
+       \item 
+       For the next two cuts, we need to define the notion of the useful slots of a partial solution $S$ in the \emph{backward period}: a slot is said to be useful, if it is not used by a message set by $S$ in the backward period and it belongs to an interval of at least $\tau$ such slots.
+Useful slots are positions which can be used when extending $S$.
+We will denote by $([a_i,b_i[)_{i\leq l}$ the ordered sequence of intervals of useful slots of $S$.
+Without loss of generality we can assume that all $a_i, b_i \leq l$.
+The number of message of size $\tau$ which can be set in the useful slots of $S$ is thus  $\displaystyle{ \sum_{i=0}^{l} (b_{i} -a_i)/\tau } $.
+If that value is less than the number of routes which are not in $R(S)$, it is a failure and the algorithm backtracks.
+Notice that the list of intervals of useful slots and the value $\displaystyle{ \sum_{i=0}^{l} (b_{i} -a_i)/\tau } $ can be maintained in constant time, since each time a route is added, we only need to split an interval of useful slots into at most two such intervals.
 
-%        In the forward windows, each message is placed after the previous one, that is $m_{s_i} > m_{s_j}$ (here, $s_i$ is the source placed before $s_j$ by the algorithm).
-Each time a new message is scheduled, there is some possible lost slots between $m_{s_i}+\tau$ and $ m_{s_j}$.
-We hold a counter of remaining slots and decrease it from the number of lost slots each time a new message is scheduled.
-Thus, if the number of the remaining slots in the forward period is lower than the number of slots needed to put the remaining messages, we can consider that the actual partial solution is not good.
-%        \item  Each time we add a new message in the backward period, we cut a free interval in two new smaller free intervals, plus the scheduled message.
-Each free intervals has a number of macro slots (ex: 2,6).
-If the sum of all the integer parts of the macro slots is lower than the number of remaining messages to schedule, the actual partial solution is not good.
        \item 
-       Let $S_1$ and $S_2$ be two partial solutions with the same subset of fixed routes, but different offsets.
-       A sequence of extensions of a partial solution $S$ is a sequence of pair of route and offset, which define a path from $S$ in the tree.
-We say that $S_1$ dominates $S_2$, if any sequences of extensions of $S_2$, is a sequence of extensions of $S_1$.
-       Then if there is a solution in $S_2$, there must be also one in $S_1$, therefore if we detect that some node is dominated in the tree we can backtrak when we encounter it.
+       Let $S_1$ and $S_2$ be two partial solutions with $R(S_1) = R(S_2)$.
+Let $US_1$ (respectively $US_2$) be the set of useful slots of $S_1$ (resp.
+$S_2$).
+We say that $S_1$ dominates $S_2$ if the largest offset fixed in $S_1$ is smaller than the one in $S_2$ and $US_2 \subseteq US_1$.
+Remark that any valid sequence of extension of $S_2$ (fixing offsets of routes in the complementary of
+       $R(S_2)$) is also a valid sequence of extensions of $S_1$.
+Therefore if the tree rooted at $S_2$ contain a solution, then $S_1$ contains one too.
+Hence, in our exhaustive search of the tree of partial solutions, we can skip the tree rooted at $S_2$.
 
-       %Meilleure explication notion de slots utilisables.
-Si une solution partielle a strictement moins de slots utilisables (vu en tant qu'ensemble) qu'une autre avec les mêmes routes alors elle est dominée
-
-       Consider a partial solution $S$ which we extend into $S' = S \cup \{ r \}$ such that the offset of 
-       $r$ is the smallest possible, denoted by $m$.
-       Say that the offset of $r$ in the backward period is $m+ \lambda$ and that the end of the message before $m + \lambda$ in the backward period is $a$.
-Then all extensions of $S$ into $S'' = S \cup \{ r \}$ with $ m < m_r < a + \tau - \lambda$.
-       are dominated by $S'$. Indeed, $S''$ have striclty less empty slots in the forward period and in the backward period, there are only two intervals ...
-
-       \todo{       Mettre un dessin !!!!  Dire comment la coupe 3 interragit bien avec la 1, car elle force $m_i$ à croitre vite, ce qui
-       permet d'appliquer rapidement la coupe}
+       We now explain how we can detect some partial solutions which are dominated so that we do not explore their subtrees.
+       Consider a partial solution $S$ which we extend into $S'$ by setting the offset of the route $r$ to be the smallest possible.
+The offset of $r$ in the backward period is $S'(R)+ \lambda$ and we denote the end of the message before before by $a$.
+Then all extensions of $S$ into $S''$ with $S'(r)  < S''(r) < a + \tau - \lambda$ are dominated by $S'$.
+Therefore when computing the extension of $S$, we first build $S'$ and then $S''$ with $S''(r) =  a + \tau - \lambda$ , skipping all values in between.
 
@@
 
-    \subsubsection{Results}
-      The following performance evaluation results compares the previous algorithms.
-Since we try to find a polynomial time algorithm for the problem PALL, Exhaustive Generation is not a good solution.
-However, Greedy $3.n.\tau$ and Shortest-Longest are some greedy heuristics and gives us a polynomial complexity.
-We tried to determine which algorithm gives a solution with the minimal period.
-      In a first time, we will have a look at the results with the parameters corresponding to Cloud-RAN context.
-      \paragraph{Short routes}
+      The third cut works well in conjunction with the first one since it makes the offsets grow quickly and 
+      which makes the first cut more likely to apply. A last cut could be implemented, by computing whether for every 
+      route not in $R(S)$ the set of possible positions in the backward period and checking whether one s contained in the useful slots of $S$.
+
+    \subsubsection{Experimental Results}\label{sec:experimental_results}
+
+      The following performance evaluation results compares the three presented algorithms.
+      Notice that both the Greedy algorithm and the Shortest-Longest are polynomial time algorithm but are not always able to
+      find optimal solutions. On the other hand, the exhaustive search will find it but it works in exponential time.
+      We will compare the performance of the algorithms in two different regimes: the routes are either smaller than 
+      the size of a message or they are arbitrary long.
+
+            The graphs 
       To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU.
@@
 
-      To find the minimal period on a given instance with an algorithm, it is necessary to run the algorithm with some different periods and take the shortest one that does not fail.
-Since the existence of a $(P-\tau)-periodic affectation)$ is not monotone with regard to P (see section \ref{nonmonotone}), a dichotomous search is not appropriate.
-Thus, for each algorithm, we made a linear search of the minimal period for which, there is a solution on the given instance.
-The following figure shows us the average periods on 1000 graphs, for a growing number of routes.
-      The results of the Exhaustive generation can be considered as a lower bound, indeed, for a given period, this algorithm finds the solution, if it exists.
-      As an information, we drew the $\tau.n$ (i.e. the size taken by the messages in the period) and the $3.(\tau.n) $ lines.
+      \todo{Mettre les données concrètes plus proprement et éventuellement ne pas les mettre si on envoie pas à un truc de télécom}
+
+      \paragraph{Short routes}
+
+       We chose parameters coming from our C-RAN settings.
+A message is of $2500$ slots, while the values $\lambda(c_t,r_{t_i})$ are drawn uniformly between $0$ and $700$ slots.
+For each of the three different algorithms and for a given instance we look for the minimal period $P$ for which the problem has a $(P,\tau)$ periodic affectation.
+We then compute the average of these minimal periods for $1000$ random star topologies for different number of routes.
+To find the minimum period, we need to do a linear search on the value $P$, a dichotomy would not work because of Lemma~\ref{lemma:monotonic}.
+
+%our network has a throughput of 10Gbps throughput and 
+%       
+%       
+%       The messages size $\tau$ is of 2500 slots, that is, approximately 1.228 Gbps of data for each route.
+The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.
+
+      Since in this setting the exhaustive generation was always finishing in less than ten seconds, the results corresponding to this
+      algorithms are optimal and are a lower bounds for the period found for the other algorithms.
+      As an information, we draw the $f(n) = n\tau$, which is an absolute lower bound on the period and $g(n) = 3n\tau$ lines which is an upper bound on the period found by the greedy algorithm.
 
@@
       We can also observe that, for any algorithm, the average minimal periods increases linearly with the number of routes. Thus, the following experiences are made on a fixed number of routes : 8.
+
+      \paragraph{Long routes}
 

### 2017-04-27 code/bruteforce.c

@@ -43,7 +43,7 @@ int ajoute_element (intervalle_liste * liste, int debut, int taille,
     {       //détecte l'intervalle à découper si il existe
       if (liste[pos].debut <= debut
     && liste[pos].fin - debut >= taille_paquets)
-  {     //l'intervalle existe, on le découpe
+    {     //l'intervalle existe, on le découpe
     //on calcule le nombre de slot après décooupage (en prenant en compte les paquets déjà placés)
     *nombre_slot +=
       (debut - liste[pos].debut) / taille_paquets + (liste[pos].fin -
@@ -65,7 +65,7 @@ int ajoute_element (intervalle_liste * liste, int debut, int taille,
         return 0;
       }
 
-  }
+    }
       pos = liste[pos].suivant;
     }
   return 0;
@@ -91,19 +91,15 @@ retire_element (intervalle_liste * liste, int debut, int taille,
   liste[i].fin = liste[taille].fin;
 }
 
-int
-prochain_debut (intervalle_liste * liste, int debut, int taille,
-    int taille_paquets)
+int prochain_debut (intervalle_liste * liste, int debut, int taille, int taille_paquets)
 {       //renvoie la prochaine position possible pour la route (décalage à la position actuelle donnée par debut)
   int pos = 0;
-  while (liste[pos].suivant != -1)
-    {
-      if (debut < liste[pos].fin)
-  {
-    break;
-  }
-      pos = liste[pos].suivant;
-    }       //trouve le premier intervalle qui peut contenir la route
+  while (liste[pos].suivant != -1){
+    if (debut < liste[pos].fin){
+      break;
+    }
+    pos = liste[pos].suivant;
+  }       //trouve le premier intervalle qui peut contenir la route
   if (debut < liste[pos].debut)
     {       //debut avant l'intervalle
       if (liste[pos].fin - liste[pos].debut >= taille_paquets)
@@ -142,8 +138,7 @@ prochain_debut (intervalle_liste * liste, int debut, int taille,
 }
 
 
-int *
-genere_reseau (int nbr_route, int taille_route)
+int *genere_reseau (int nbr_route, int taille_route)
 {
   int *temps_retour = malloc (sizeof (int) * nbr_route);
   for (int i = 0; i < nbr_route; i++)
@@ -168,8 +163,7 @@ print_sol (int *solution_pos, int *solution_num, int nbr_route, int budget)
 //mettre debut_courant à la place de décalage_courant partout ? Ca pourrait simplifier un peu
[…]

### 2017-05-05 article/article.tex
aa

@@
       The following performance evaluation results compares the three presented algorithms.
-      Notice that both the Greedy algorithm and the Shortest-Longest are polynomial time algorithm but are not always able to
-      find optimal solutions. On the other hand, the exhaustive search will find it but it works in exponential time.
+      Notice that both Greedy algorithm and the Shortest-Longest are polynomial time algorithm but are not always able to
+      find optimal solutions. On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time.
       We will compare the performance of the algorithms in two different regimes: the routes are either smaller than 

### 2017-05-05 code/code.c

@@ -1004,6 +1004,7 @@ void echec_periode_gvsgp(int nb_routes, int taille_paquets,int taille_route,int 
 				e++;
 			}
 			
+
 			
 
 		
@@ -1090,7 +1091,7 @@ int main()
 		printf("%d %d\n",a,b);
 
 	}*/
-	echec_periode_gvsgp(8,2500,20000, 70000, 10000,3);
+	echec_periode_gvsgp(8,2500,20000, 80500, 10000,3);
 	/*for(int i=0;i<5;i++)
 		echec_periode_gvsgp3D(8,2500,20000, 1000,i);
 	*/

### 2017-05-05 article/article.tex
aaee

@@
       the size of a message or they are arbitrary long.
-
-            The graphs 
-      To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU.
+%             
+%             The graphs 
+%       To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU.
 The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route.
@@
       The next results is to theoretically prove that, with those parameters, the Shortest-Longest algorithm gives optimal solutions, like this experimental study suggests it does. 
-      About the Greedy $3.n.\tau$ Algorithm, with those parameters, it always gives us bigger periods than the Shortest longest. 
-      We can also observe that, for any algorithm, the average minimal periods increases linearly with the number of routes. Thus, the following experiences are made on a fixed number of routes : 8.
+      About the Greedy Algorithm, with those parameters, it always gives us bigger periods than the Shortest longest.
+However, the results show that this algorithm gives average periods lower theoretical upper bound of this algorithm ($3n\tau$).
+      We can also observe that, for any algorithm, the average minimal periods increases linearly with the number of routes.
+
+      \todo{regression linéaire}
 
@@
       Then, we looked at the evolution of the minimal period required with the different algorithm if we significantly increase the size of the route.
-The following figure shows us the success rate of the algorithms, according to the period, for 8 routes in which  $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 30000 slots, that correspond to have the size of the route and the period approximately in the same order of magnitude.
+The following figure shows us the success rate of the algorithms, according to the period, for 8 routes in which  $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform distribution between 0 and 30000 slots, that correspond to have the size of the route and the period approximately in the same order of magnitude.
 

### 2017-05-05 code/bruteforce.c

@@ -225,7 +225,8 @@ int bruteforceiter (Graphe g, int periode, int taille_paquets)
   /////////////////// Début de l'arbre de recherche ////////////////////////////
 
 
-  while (compteur < 500000000)
+  //while (compteur < 500000000)
+  while (solution_taille > 0)
     {
       compteur++;
       if (solution_taille == nbr_route)

### 2017-05-05 code/code.c

@@ -1070,7 +1070,7 @@ void echec_periode_gvsgp3D(int nb_routes, int taille_paquets,int taille_route, i
 int main()
 {
 	srand(time(NULL));
-	//simuls_periode(8,2500,7000,1000);
+	//simuls_periode(12,2500,700,1000);
 	//echec(8,2500,30000,1000);
 //echec_taille_route(8,2500,25000,1000);
 	/*Graphe g;
@@ -1091,7 +1091,7 @@ int main()
 		printf("%d %d\n",a,b);
 
 	}*/
-	echec_periode_gvsgp(8,2500,20000, 80500, 10000,3);
+	echec_periode_gvsgp(8,2500,20000, 81000, 10000,3);
 	/*for(int i=0;i<5;i++)
 		echec_periode_gvsgp3D(8,2500,20000, 1000,i);
 	*/

### 2017-05-10 article/article.tex
short rootes

@@
       find optimal solutions. On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time.
-      We will compare the performance of the algorithms in two different regimes: the routes are either smaller than 
-      the size of a message or they are arbitrary long.
+      We will compare the performance of the algorithms in two different regimes: the routes are either short or arbitrary long.
 %             
@@
 
-       We chose parameters coming from our C-RAN settings.
-A message is of $2500$ slots, while the values $\lambda(c_t,r_{t_i})$ are drawn uniformly between $0$ and $700$ slots.
-For each of the three different algorithms and for a given instance we look for the minimal period $P$ for which the problem has a $(P,\tau)$ periodic affectation.
-We then compute the average of these minimal periods for $1000$ random star topologies for different number of routes.
-To find the minimum period, we need to do a linear search on the value $P$, a dichotomy would not work because of Lemma~\ref{lemma:monotonic}.
+      Firstly, we made some performance evaluation on graphs in which the values $\lambda(c_t,r_{t_i})$ are drawn uniformly between $0$ and $700$ slots.
+This parameter is coming from our C-RAN context, in which the physical links are short enough.
+In C-RAN context, the size of a message is of $2500$ slots.\\
+
+      For a given instance, we try to determine the minimum period $P$ for which the graph has a $(P,\tau)$ periodic affectation; to that end,  we need to do a linear search on the value $P$, a dichotomy would not work because of Lemma~\ref{lemma:monotonic}.
+      We generated $1000$ random instances of PAZL, and we applied the linear search with each of the three algorithm.
+Then we measure the average minimal period, for each algorithm.
+We applied this test increasing the number of routes, until it was too long for the exhaustive search to find a solution quickly.
 
@@
 
-      Since in this setting the exhaustive generation was always finishing in less than ten seconds, the results corresponding to this
-      algorithms are optimal and are a lower bounds for the period found for the other algorithms.
-      As an information, we draw the $f(n) = n\tau$, which is an absolute lower bound on the period and $g(n) = 3n\tau$ lines which is an upper bound on the period found by the greedy algorithm.
+      Since the exhaustive search is optimal, the average periods founds by this algorithm is the lower lower bounds for the other algorithms.
+      As an information, we draw the $f(n) = n\tau$, which is an absolute lower bound on the period and $g(n) = 3n\tau$ lines which is the theoretical upper bound of the greedy algorithm.
 
@@
 
-      With those parameters, we can observe that the average period of the Shortest-Longest algorithm, which is determined by the difference between the longest and the shortest route, is always equal to the Exhaustive generation, that is, the lower bound.
-      The next results is to theoretically prove that, with those parameters, the Shortest-Longest algorithm gives optimal solutions, like this experimental study suggests it does. 
-      About the Greedy Algorithm, with those parameters, it always gives us bigger periods than the Shortest longest.
-However, the results show that this algorithm gives average periods lower theoretical upper bound of this algorithm ($3n\tau$).
+      As a reminder, the period needed by Shortest-Longest to find an optimal solution is determined by the difference between the longest and the shortest route.
+Here, because of the routes are short, this difference is small in regards to the period.
+Thus, we can imagine that this algorithm gives good solutions when the routes are short.
+      With those parameters, we can observe that the average period of Shortest-Longest is always equal to the Exhaustive generation, that is, the lower bound.
+      The next results is to theoretically prove that, with those parameters, Shortest-Longest gives optimal solutions, like this experimental study suggests it does. 
+      About the Greedy Algorithm, with those parameters, it always gives us bigger periods than Shortest longest.
+However, the results show that this algorithm gives average periods lower than the theoretical upper bound of this algorithm ($3n\tau$).
       We can also observe that, for any algorithm, the average minimal periods increases linearly with the number of routes.

### 2017-05-10 code/code.c

@@ -352,7 +352,7 @@ void simuls_periode(int nb_routes, int taille_message, int taille_routes,int nb_
 		}
 		printf("\n");
 		
-		fprintf(F, "%d %lld %lld %lld %d %d\n",j,total_3NT/nb_simuls,total_brute/nb_simuls,total_sl/nb_simuls,j*taille_message,2*j*taille_message);
+		fprintf(F, "%d %lld %lld %lld %d %d\n",j,total_3NT/nb_simuls,total_brute/nb_simuls,total_sl/nb_simuls,j*taille_message,3*j*taille_message);
 		printf("\n");
 	}
 	fclose(F);
@@ -1003,8 +1003,10 @@ void echec_periode_gvsgp3D(int nb_routes, int taille_paquets,int taille_route, i
 {
 
 	char nom[64];
-	sprintf(nom,"gvsgp3D_%d.data",mode);
+	sprintf(nom,"3d/gvsgp3D_%d.data",mode);
+
 	FILE * F = fopen(nom,"w");
+
 	Graphe g ;
 	int resa,resb,resc,resd;
 	float a,b,c,d;
@@ -1015,10 +1017,10 @@ void echec_periode_gvsgp3D(int nb_routes, int taille_paquets,int taille_route, i
 	{
 		for(int j=taille_paquets*nb_routes;j<taille_paquets*nb_routes*1.5;j+=500)
 			{
-				a=0;
-				b=0;
-				c=0;
-				d=0;
+				a=0.0;
+				b=0.0;
+				c=0.0;
+				d=0.0;
 
 				for(int i = 0;i<nb_simuls;i++)
 				{
@@ -1175,7 +1177,7 @@ int main()
 	}*/
 	//echec_periode_gvsgp(8,2500,20000, 0, 10000,3);
 	for(int i=0;i<5;i++)
-		echec_periode_gvsgp3D(8,2500,20000, 1000,i);
+		echec_periode_gvsgp3D(8,2500,700, 1000,i);
 	
 	/*Graphe g ;
 

### 2017-05-12 article/article.tex
sans waiting result

@@
 
+        \begin{figure}
+
       \begin{center}
@@
       \end{center}
+     \caption{Average minimum period of the algorithms according to the period for short routes.}
+\end{figure}
 
@@
 However, the results show that this algorithm gives average periods lower than the theoretical upper bound of this algorithm ($3n\tau$).
-      We can also observe that, for any algorithm, the average minimal periods increases linearly with the number of routes.
-
-      \todo{regression linéaire}
+      We can also observe that, for any algorithm, the average minimal periods seems increasing linearly with the number of routes.
+We made a linear regression on every set of data, and we observed that for the three algorithm, the correlation coefficient is greater than $0,999$.
 
       \paragraph{Long routes}
+      We now want to look at the performance of those algorithm if we significantly increase the size of the route.
+By increasing the size of the routes, the cuts of the exhaustive search, are less efficient.
+Thus, we defined a counter that allow the exhaustive search to end if no solutions are found.
 
-      Then, we looked at the evolution of the minimal period required with the different algorithm if we significantly increase the size of the route.
-The following figure shows us the success rate of the algorithms, according to the period, for 8 routes in which  $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform distribution between 0 and 30000 slots, that correspond to have the size of the route and the period approximately in the same order of magnitude.
+      Since the exhaustive generation can fail, this is necessary to change the method to measure the minimum period for each algorithm, when the routes are long.      
+      The following figure shows us the average success rate of the algorithms, on $1000$ instances, according to the period, with 8 routes, in which $\lambda(c_t,r_{t_i})$, are drawn following an uniform distribution between $0$ and $30000$ slots, that correspond to have the size of the route and the period approximately in the same range.
 
-      By increasing the size of the routes, the cuts of the exhaustive search, are less efficient.
-Thus, we defined a counter that allow the search to end if no solution are found.
+      The reason why the shortest longest were optimal in the previous experiences ,i.e.
+having a small difference between the longest and the shortest route, is no longer reviewed.
+In this situation, this difference can be considerable, and then the required period too.
+
+      One the other hand, one can imagine that the greedy $3.n.\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
+
       On the following figure, the upper bound represents the cases in which the exhaustive search found a solution plus the number of {\em early} halts of the search.
 The real upper bound is probably between those two curves.
+\begin{figure}
 
-      The reason why the shortest longest were optimal in the previous experiences (i.e.
-having routes shorter than message size) is no longer reviewed.
-We can also imagine that sending the shortest route first on long routes significantly increases the period, because there will be a lot of lost size in the backward and forward periods.
-
-      One the other hand, one can imagine that the greedy $3.n.\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
        \begin{center}
@@
       \end{center}
+      \caption{Success rate of the algorithms according to the period for long routes.}
+     \end{figure}
 
-      As we can see, the Shortest longest has a very low success rate, because of the distribution of the size of the routes is now broader, so is the required period.
-      Whereas, the Geedy 3NT gives us solutions with much lower period than Shortest Longest.
-The exhaustive search keeps finding good solutions in short periods but it fails a lot for periods until $2.n.\tau$.
+      As we can see, Shortest longest has a very low success rate, and is not efficient anymore with those parameters.
+      Whereas, the greedy algorithm gives us solutions with much lower period than Shortest Longest.
+The exhaustive search keeps finding good solutions in short periods but it fails a lot for periods that does not give a lot of flexibility in the backward period.
+This mean that, for a small period, a solution may exists, but the exhaustive search needs too much time to find it.
+In this situation, it could be better to use the greedy algorithm, that find a good solution in a polynomial time.
 
-      So, those experiences shows us that for real topologies with small routes, the Shortest-Longest algorithm finds some affectations with small Periods, but, the longer the routes are, the better it is to use the Greedy policy to find a solution without waiting times.\\
-      Nevertheless, if we want to consider networks, the period is fixed.
+      So, those experiences shows us that, for C-RAN topologies, with small routes, shortest-longest finds some optimal affectations in a polynomial time, but, the longer the routes are, the better it is to use the greedy policy to find a solution without waiting times in a polynomial time.\\
+
       As we just saw, if the load increases, the needed period increases too, and it is not possible anymore to find a solution without waiting times with a small period.
-The solution is to allow some messages to wait on target nodes, as described in the next section.
-
+The next sections treats about the proposed solutions to find a $(P,\tau)$ periodic affectation when the period is small.
    \subsection{Allowing waiting times}
@@
      \subsubsection{Intro}
+
 	  We now consider waiting times.

### 2017-05-12 code/code.c

@@ -86,6 +86,29 @@ void graphe_etoile(Graphe g,int taille_liens)
 	g.matrice[pivot][pivot] = 0;
 }
 
+//prends un graphe vide en argument et le transforme en etoile
+void graphe_etoile_moitier(Graphe g,int taille_liens)
+{
+	if(!(g.N%2)){printf("Impossible de générer une étoile avec un nombre pair de sommets\n");exit(5);}
+	int pivot = g.N/2;
+	int moitier = taille_liens /2;
+	int alea;
+	for(int i=0;i<g.N/2;i++)
+	{
+		alea = rand()%moitier;
+		g.matrice[pivot][i] = alea;
+		g.matrice[i][pivot] = alea;
+	}
+	for(int i=(g.N/2)+1;i<g.N;i++)
+	{
+		alea = rand()%moitier;
+		g.matrice[pivot][i] = alea+moitier;
+		g.matrice[i][pivot] = alea+moitier;
+	}
+	g.matrice[pivot][pivot] = 0;
+}
+
+
 //renvoie un anneau avec les routes
 Routage_Graph graphe_anneau(int nb_sommets,int nb_routes,int taille_liens)
 {
@@ -1025,7 +1048,7 @@ void echec_periode_gvsgp3D(int nb_routes, int taille_paquets,int taille_route, i
 				for(int i = 0;i<nb_simuls;i++)
 				{
 					g = init_graphe(2*nb_routes+1);
-					graphe_etoile(g,taille_route);
+					graphe_etoile_moitier(g,taille_route);
 					tmax = marge + longest_route(g);
 					//affiche_etoile(g);
 					//printf("TMAX = %d\n",tmax);
@@ -1038,6 +1061,7 @@ void echec_periode_gvsgp3D(int nb_routes, int taille_paquets,int taille_route, i
 						resb = longest_etoile_2(g,taille_paquets,j,tmax,mode);
 						resc = simons(g,taille_paquets,tmax,j,mode);
 						resd = simons_periodique(g,taille_paquets,tmax,j,mode);
+						//resd = 0;
 						//printf("%d %d \n",resa,resb);
 						if(resa != -2)
 						{	
@@ -1122,6 +1146,7 @@ void echec_periode_gvsgp3D(int nb_routes, int taille_paquets,int taille_route, i
 						for(int compteur_rand = 0;compteur_rand<nb_rand;compteur_rand++)
[…]

### 2017-05-12 code/simons.c

@@ -569,6 +569,7 @@ Ensemble * invade(Ensemble * ens,Element * touselems,int depart,int taille_paque
 					freeelems(elems);
 					return NULL;
 				}
+				
 				while(ens3->frereD)
 					ens3 = ens3->frereD;
 				//affiche_ensemble(ensembletmp);printf("Elemenent le plus a droite\n");

### 2017-05-12 modeljoannes/Modelisation.tex
regression add

\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,mathrsfs,latexsym}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{makeidx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{subcaption}
\usepackage{enumitem}
\begin{document}

\tableofcontents
\pagebreak
\section{Description and modeling}
The general context is about the modeling of the N-Green network. Starting from an overall description of the model, state specifications of each component so we set the foundation for what deserves special attention and critical parameters to make it a simulation

\subsection{Description}
In the description of optical ring we consider node's two types. The first one is \textbf{bridge} and the second is\textbf{ switches}.\\
Indeed, the bridges are simple nodes of the ring capable of being the source or recipient of a packet within the ring. All their operations are internal to the ring. Switches are special nodes that delimit the size of the ring; They are also used for interconnecting the second ring and also they are able to empty containers without being recipient or source.\\

About  distribution modes we  mention the mode \textbf{Unicast} and \textbf{Broadcast-and-Select} that attract our attention.\\  In Unicast mode, each source node sends packets for a specific destination. This means that each container contains information for an exact destination and the same for waiting. It's called one-to-one\\For the Broadcast-and-Select mode, each source node uses the same slot to address a recipient set, and when they receive packets, they make a copy and then extract what is intended. It's named  one-to-many. The constraints are posed by the type of traffic and the requirements on slot's padding.\\

On the ring there are two types of services: \textbf{premium} and \textbf{best effort}. The premium means the high priority of packets or critical limits on which the delay must be as minimal as possible while the best effort is to satisfy as soon as possible. Even if it's a best effort, it will also be necessary to minimize the routing time as much as possible.\\

For packet's insertion, we have also two mode to explore: \textbf{opportunistic} and \textbf{reservation}.\\ 
The opportunistic insertion means that when a slot is empty, a node can use it to transmit some packets; the node may decide not to use it if it considers that none of the packets currently being build is ready for transmission.\\
About reservation mode, a slot may be empty but reserved for another node, or another class of service.\\
When a node is allowed to insert data, and there are several packets ready for insertion, the node has to select which one to insert: this is \textbf{scheduling}. The scheduling is internal to each node.\\

As regards the reception  on ring, a node decides to receive packet when it's label with receiver number. First case, the node may receive the packet and free the corresponding slot by erasing the packet; this is typical for the unicast mode. The second case, the node get an copy of the packet to check which data is for him exactly. Only the source of packet can erase and release slot.\\

\subsection{Model of Ring}
In this section we present the framework of defining our work, some specifications, problem and the approach of our observations.
\subsubsection{Slotted time model}
In our model the time is discrete. The unit of time is one slot. Let's note \textbf{ST} this time. With each ST click, each node sees a container with a capacity\textbf{c}. During the ST, two basics operations are possible:  \textbf{Writing} and  \textbf{Reading}.\\
In reading, it is a matter of making a copy of the packets to extract  data; for writing, put the packet to be sent. The packet''s weight can be noted  as to{$w_{p}$}

\subsubsection{Problem and Constraint}
On this part we summarize the constraint that can be used for the ring observation.\\
Let's note \textbf{R} the set of request, \textbf{$R_{p}$} $\subset$ R the set of request premium and  \\ \textbf{$R_{b}$} $\subset$ R the set of best effort request\\

$\forall$ r $\in$ \textbf{R} ;  {$t_{r}$}={$t_{e}$}+{$\alpha_{i}$} and  if  r $\in$ {$R_{p}$} $\Rightarrow$ {$\alpha_{i}$} $\rightarrow$ 0\\

thus,   $\min$ ($\sum$ {$\alpha_{i}$})\\

For slot using, Let's note  \textbf{$q_{i}$} length of request; and \textbf{P} as packet\\
{$q_{i}$}=const with const=$\max$({$q_{i}$})\\

     $\min$ $\sum$( C- {$W_{p}$})\\
{$W_{p}$}=$\sum$({$q_{i}$}) and $\beta$ =$ \frac{W_{p}}{C} $  where  $\beta$  $\rightarrow$ 1\\

\subsubsection{About nodes} 
On a node, to manage request's list for preparation of packets to be sent. Each request has a arrival time  \textbf{$t_{a}$} which depend to period \textbf{p} of distribution on the ring.\\
 Whatever the type of request, it is necessary to be able to minimize the waiting time that's we note {$\alpha_{i}$} request for each node. Specially for premium request, the goal is to have no waiting time. Here It's important to explain how to create request on each node. On the ring we'll define period p for premium request creation on each node and quantity q. This implies that if we have request on time t on a node, the next request on the same node should be at t+p \\ 
Let's note  \textbf{MAX} maximum request production of the node 
\begin{algorithm}

\caption{creation of request}
\begin{algorithmic}
\State \textbf{Require:}  $start_{time}$; p
\State int $\delta$ =0;
\While{( $\neg$MAX)} 
\If{ $Current_{time}$ == $start_{time}$+$\delta$.p }
\State create request;
\State $\delta$++;
\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}  \\

For creating best effort request we'll use an uniform probability around the ring to add into all node this kind of request. All we need to use is the charge of ring.\\
Let's note $\delta$, $\sigma$ $\in$ [0;1] such as $\delta$ $\rightarrow$ 1 and  $\sigma$ $\rightarrow$ 0;
\begin{algorithm}
\caption{Best effort creation}
\begin{algorithmic}
\State \textbf{Require:}  $\sigma$, $\delta$
\If{ Uniform(0;1)$\geq$ $\delta$ \&  Uniform(0;1)$\geq$ $\sigma$ }
\State Create lots of Best effort
\Else
\State Create very little 
\EndIf
\end{algorithmic}
\end{algorithm}

\subsubsection{Insertion} 
For emission problem we use the opportunistic strategy but the goal is to make a good use of resources. During ST, each node must use the container to put a packet as big as it's possible in order to avoid using too much resources than it's necessary. This is to avoid waste of resources and leave the charge of the ring very low. This seems to be somewhat in contradiction with the fact of minimizing the wait times of packets especially those of the service "premium"; But to restore the equilibrium, we will put a mechanism of right of access in emission on the containers in such a way that certain containers can be used only for priority packets. This is a good alternative to improve the time wasting by idea of filling the containers to be full at maximum. Another criteria we can add is to define an maximum waiting time which after this, the packets that we want to be full before sending must be sent even if it's not. This time can be noted \textbf{ {$\alpha_{max}$}}.

\begin{algorithm}
\caption{Packet's insertion}
\begin{algorithmic}
\State \textbf{Require:}  $\alpha_{max}$; $\beta$ $\in$ [0;1]
\If{$Creation_{time}$ -- $Current_{time}$ == $\alpha_{max}$ $\mid$  $\mid$ $ \frac{W_{p}}{C} $ $\geq$ $\beta$ }
\State send packet
\Else
\State wait for packing 
\EndIf
\end{algorithmic}
\end{algorithm}  
\newpage
\subsubsection{Latency}
Here we define latency as the difference between the time a request was received and the time it should be received if it was sending since the moment it was created. Indeed we can get a deterministic estimate of the time separating the path of a request between source and its destination noted as "best case". So the latency is mainly due to {$\alpha_{i}$}. Let's note latency as  \textbf{l}, the estimation sending time as  \textbf{ {$t_{e}$} } and the reel time of receive as { {$t_{r}$} } .\\

Two major problems stand out: minimizing {$\alpha_{i}$} and maximizing containers for message transport.
\subsection{Presentation of Model 1}

This part concerns the general problem that we study without any specification of the type of request that the node must send. This means that all is Best effort.\\
Let's note R=\{ $r_{1}$, $r_{2}$, $r_{3}$,......,$r_{i}$  \}, the list which can be request or best effort on this model.\\
\begin{algorithm}
\caption{Model 1}
\begin{algorithmic}
\State \textbf{Require:} R
\State $\forall$ r $\in$ R try removing from R to the sending packet's;
\State call \textbf{ Packet's insertion}
\end{algorithmic}
\end{algorithm}

\begin{figure}[h!]
  \begin{subfigure}[b]{0.9\textwidth}
    \includegraphics[width=\textwidth]{etape1.PNG}
    \caption{Picture 1}
    \label{fig:1}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{etape2.PNG}
    \caption{Picture 2}
    \label{fig:2}
  \end{subfigure}
%
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{etape3.PNG}
    \caption{Picture 3}
    \label{fig:3}
  \end{subfigure}
\caption{Basic model1 view}
\end{figure}

\newpage
Figure 1: presents the model that we describe above and show how is the ring.
\begin{enumerate}[label=$\bullet$]
\item On Picture 1 the nodes 1,2 and 4 have respectively packets b, c and d on emission. Noticed that each node can read on left and read on right. So node 1 can read the packet a and puts its packet b on right.   
\item On picture 2 we can see the result of what is done during ST. Node 1 writes  on the slot at right and read on left. Node 2 can't write on the slot because the slot is used by packets e sending by another node. Node 4 doesn't write because the packet d isn't full enough for sending.
\item On picture 3, the next ST show that node 2 sends his packet by founding empty container and node 4 sends it too because packets d is full enough and ready to be sent .
\end{enumerate}

\subsection{Presentation of Model 2}
According to this model, node distinguishes the difference between request and best effort. So, for the node we model two packet's list: the first for requests and second for best effort. For sending, main solution is to empty the priority list before trying sending best effort. The goal for this model is to observe and compare with model 1 the gain for request versus loss for best effort.\\
Let's note $LP_{r}$ the list of packets for request sending; $LP_{b}$ the list of packets best effort.

\begin{algorithm}
\caption{Model 2 for priority }
\begin{algorithmic}
\State \textbf{Require:}  $LP_{r}$, $LP_{b}$
\While{($LP_{r}$ ! $\phi$)} 
\State call \textbf{ Packet's insertion} for $LP_{r}$
\EndWhile
\State call \textbf{ Packet's insertion} for $LP_{b}$
\end{algorithmic}
\end{algorithm}
\newpage
\begin{figure}
  \begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[width=\textwidth]{model21.PNG}
    \caption{Picture 1}
    \label{fig:1}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[width=\textwidth]{model22.PNG}
    \caption{Picture 2}
    \label{fig:2}
  \end{subfigure}
%
  \begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[width=\textwidth]{model23.PNG}
    \caption{Picture 3}
    \label{fig:3}
  \end{subfigure}
\caption{ model2 view}
\end{figure}

Figure 2: presents the sample model2 operation.
\begin{enumerate}[label=$\bullet$]
\item On Picture 1 the nodes 1 has two packets lists on emission. Request list contains a, b, c while best effort contains d, e, f.    
\item On picture 2 we can see the result of what is done after three ST. Node 1 sends all its priority packets before best effort. Noticed even if the packets c isn't full enough it was sent before best effort.
\item On picture 3, the next ST show that node 1 sends it's first best effort after having it's priority packet list empty.
\end{enumerate}

\subsection{Presentation of Model 3}
This model contains what we want improve after seeing mode 1 and 2. At first, get very fast as possible for priority packets like on model2; Avoid waste in the use of slot like model2, and improve waiting time for best effort and get it like in model1.\\
So, let's note\\
 $v_{r}$ $\subset$ $LP_{r}$ $\backslash$ $v_{r}$=\{ request \} and $v_{b}$ $\subset$ $LP_{r}$ $\backslash$ $v_{b}$=\{ request \} $\bigcup $ \{ best effort \} ; 
|$v_{r}$|=$\max$(|$v_{ri}$|) $\backslash$ $v_{ri}$  $\subset$ $LP_{r}$ ) and |$v_{b}$|=|$LP_{r}$|--|$v_{r}$|
For sending, algorithm is the same with model2; but we change best effort  insertion.

\begin{algorithm}
\caption{Best effort insertion}
\begin{algorithmic}
\State \textbf{Require:} b: best effort; $v_{r}$.Length; $v_{b}$.Length
\State find=false;
\While{$\neg$find} 
\If{|b| $\geq$ $v_{b}$.Length}
\State check place in the next $v_{r}$;
\EndIf
\EndWhile
\If{find}
\State put b in $v_{r}$ where place was found;
\Else
\State make insertion on $LP_{b}$;
\EndIf
\end{algorithmic}
\end{algorithm}
\newpage
\begin{figure}
  \begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[width=\textwidth]{model31.PNG}
    \caption{Picture 1}
    \label{fig:1}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[width=\textwidth]{model32.PNG}
    \caption{Picture 2}
    \label{fig:2}
  \end{subfigure}
\caption{ model3 view}
\end{figure}

Figure 4: shows amelioration  we think for model3 by using the same picture as model2.
\begin{enumerate}[label=$\bullet$]
\item On Picture 1 the nodes 1 has two packets lists on emission. It's important to notice that the packets c which is not full is used by best effort. In this, the best effort what we put in is the head of packet d. d is looks full again because we put the e in it and f in queue of e. That's why f looks less full of best effort. 
\item On picture 2 we can see the result of what is done after three ST. 
\end{enumerate}

\subsection{Model for  interconnection between two ring}
The second part of our work is about ring's interconnection. The problem that we have to solve is about lost of synchronization. When packets need to change node, difference between the slot's time click on the rings. we must point out our attention on the   \textbf{switch} node.\\
The node switch can erase container if it gets packets for another rings. So it means that he is a new 
transmitter of the packets. It's now important to think about how to use the container on the switch nodes. We can do it by using more ways.\\
\subsubsection{Priority to external packets}
In this case, it is considered that  on the switch node, priority will be given to the packets coming from an external node.The purpose of this is to minimize the additional waiting time for the packets on the waiting line of switch node. This could have very good results especially if inter-ring communications are even more numerous.\\

\subsubsection{Priority to internal packets}
In this case, it is considered that all priority is given to the packets inside the same ring. This results can be used when there isn't more packets between two rings. \\

\subsubsection{Mixed Priority}
With this model, we combine the two previous. So it's we can define an probabilistic aspect which can define when we get priority for internal packets or not.\\
 For sample, let's define  \textbf{$\Delta$} $\in$ [0;1]; \\

\begin{algorithm}
\caption{choose priority}
\begin{algorithmic}
\State \textbf{Require:} $\Delta$ $\in$ [0;1]
\If{$\Delta$ < 0.5}
\State return Priority to internal packets
\Else
\State return Priority to external packets
\EndIf
\end{algorithmic}
\end{algorithm}

\subsubsection{Observations}
In this part we show the main problem we explain in interconnection case and describe what we exactly do.\\
\begin{figure*}[h!]
\begin{center}
\includegraphics[scale=0.8]{inter1.PNG}
\caption{Rings interconnection}
\end{center}
\end{figure*}

Figure 3: presents the model that we describe above and show what happen on switch node. Here we show on node 2 a sample of move on this node. Node 2 packet's waiting list. On the list we have as much packets coming from ring A to B as packets which are introduced for ring B.
\clearpage
\begin{figure}
  \begin{subfigure}[b]{0.6\textwidth}
    \includegraphics[width=\textwidth]{inter2.PNG}
    \caption{Internal priority}
    \label{fig:1}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.6\textwidth}
    \includegraphics[width=\textwidth]{inter3.PNG}
    \caption{external priority}
    \label{fig:2}
  \end{subfigure}
\caption{Priority choice}
\end{figure}
Figure4: show us the different possibility for the switch to manage the list.\\
In (a) packets which source is the ring B is chosen to be put on the slot but in (b), the stranger pass at first.\\

Let's consider {$T_{A}$} , {$T_{B}$} the time that need packets turn around  ring A and B respectively. And also consider {$T_{R}$ as real time for packets transmission.\\
The goal to obtain:   {$T_{R}$  $\leq$ {$T_{A}$} + {$T_{B}$}.

\end{document}

### 2017-05-12 code/3d/script3D.sh

@@ -1,0 +1,25 @@
+#!/bin/bash
+
+for algo in `seq 3 6`
+do
+	for depart in `seq 0 4` 
+	do
+
+		echo "splot   'gvsgp3D_$depart.data'  using 1:2:$algo notitle with pm3d
+
+		set palette defined (0 \"red\",1 \"green\")
+		set pm3d interpolate 10,10
+		set view map
+		set cblabel \"reussite\"
+		set ylabel \"periode\"
+		set xlabel \"marge\"
+		set term postscript color solid
+		set output \"$algo.$depart.ps\"
+		set key left top
+		replot
+
+		" > /home/merelas/Bureau/ngreen/code/3d/$algo.$depart.gplt
+		gnuplot $algo.$depart.gplt
+		ps2pdf $algo.$depart.ps
+	done
+done

### 2017-05-12 code/simons2.c

@@ -569,7 +569,6 @@ Ensemble * invade(Ensemble * ens,Element * touselems,int depart,int taille_paque
 					freeelems(elems);
 					return NULL;
 				}
-				
 				while(ens3->frereD)
 					ens3 = ens3->frereD;
 				//affiche_ensemble(ensembletmp);printf("Elemenent le plus a droite\n");
@@ -677,8 +676,6 @@ Ensemble * invade(Ensemble * ens,Element * touselems,int depart,int taille_paque
 		}
 		tmp = ens2;
 		ens2 = ens2->frereD;
-		if(ens2 != NULL)
-			ens2->frereG = NULL;
 		if(tmp)
 			free(tmp);
 		
@@ -810,7 +807,10 @@ Ensemble * crisis(Ensemble * ens,Element * crisise, Element * elemspere,Element 
 				return NULL;
 			}
 	}
-
+	//if ens = NULL alors pull(X) etait le premier element, il faut recalculer toutes les deadlines
+	/*if(ens == NULL)
+		recalculer_deadlines(touselems,crisise->release+periode);
+	*/
 
 	
 	Ensemble* ens3 = NULL;
@@ -976,8 +976,6 @@ Ensemble * crisis(Ensemble * ens,Element * crisise, Element * elemspere,Element 
 		
 		tmp = ens2;
 		ens2 = ens2->frereD;
-		if(ens2 != NULL)
-			ens2->frereG = NULL;
 		if(tmp)
 			free(tmp);
 	}
@@ -1008,6 +1006,7 @@ Ensemble * crisis(Ensemble * ens,Element * crisise, Element * elemspere,Element 
 }
 
 
+
 int is_ok(Graphe g, int taille_paquet, int * mi, int * wi,int p)
 {
 	int nbr_route = g.N /2;
@@ -1023,7 +1022,7 @@ int is_ok(Graphe g, int taille_paquet, int * mi, int * wi,int p)
 			d= (c+taille_paquet-1)%p;
 			if( ( (c>=a)&&(c<=b) ) || ( (d>=a)&&(d<=b) ) )
 			{
-				printf("PB(aller ) entre %d(%d-%d) et %d(%d-%d)\n",i,a,b,j,c,d);
+				printf("PB(aller) entre %d(%d-%d) et %d(%d-%d)\n",i,a,b,j,c,d);
 				return 0;
 			}
 		}
[…]

### 2017-05-16 article/article.tex
debut waiting time

@@
 
-      In this section, we consider graphs with a very simple topology that we call the {\bf star topology}. 
+      In this paper, we consider graphs with a very simple topology that we call the {\bf star topology}. 
       First, for each arc $(u,v)$, there is also an arc $(v,u)$ with the same weight.
@@
 
-	  We now consider waiting times.
+	  In the previous section, we described some algorithm to solve an easier version of PALL, in which there is no waiting times.
+As we just conclude, this problem cannot be solved when the period is too small.
+The C-RAN context gives us a fixed period, thus, some topologies with a lot of routes might be impossible to schedule with the previous algorithms.
+We propose to allow some message to wait in the target vertices (BBU), with the aim of giving an higher degree of freedom for the scheduling.
+In this section, the waiting times $w_i$ are not necessarily null anymore.
+Thus, $MT({\cal M})$ might be superior to $T_{max}$ and it is necessary to minimize $MT({\cal M})$.
+
+% 	  We now consider waiting times.
 The weights on links from sources to $c_s$ are now relevant because the goal is to minimize $MT({\cal M})$, with ${\cal M}$ the $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$.
-	  To build such a $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, we must choose the offsets $m_{s_i}$ and $m_{t_i}$, such that there is no $PT(s)$ greater than a given $T_{max}$.
-	  As a reminder, $ PT(s)=\lambda(r_s)+ w_s+\lambda(r_{t_i})$.
-     \subsubsection{LSG}
+% 	  To build such a $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, we must choose the offsets $m_{s_i}$ and $m_{t_i}$, such that there is no $PT(s)$ greater than a given $T_{max}$.
+% 	  As a reminder, $ PT(s)=\lambda(r_s)+ w_s+\lambda(r_{t_i})$.
+
+     \subsubsection{A first approach}
 
@@
       \begin{enumerate}
- \item To be eligible, a job needs to be able to come back on the switch at the current clock (if clock = 0, take the first message able to come back).
- \item Between the eligible jobs, schedule first the one which has the lowest deadline.
+      \item To be eligible, a message needs to be able to come back on $c_t$ at the current clock (if clock = 0, take the first message able to come back).
+      \item Between the eligible messages, schedule first the one which has the lowest deadline.
       \item Repeat until all the messages had been scheduled.
@@
 
-For any route i, the deadline correspond to $m_{s_i} + T_{max}$.
+      For any route i, the deadline correspond to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$.
+This deadline corresponds to the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
+% 
+% \begin{algorithm}[H]
+% \caption{Longest Shortest Greedy (LSG)}
+% \begin{algorithmic}
+% \REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, packet size $\tau$
+% \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$
+% \STATE clock $\leftarrow$ 0
+% \FORALL{route i in $r_{s_i}$ from the longest to the shortest }
+% \STATE  $m_{s_i} \leftarrow$ clock
+% \STATE clock $\leftarrow$ clock + $\tau$
+% \ENDFOR
+% \STATE clock $\leftarrow$ 0
+% \STATE take i such that $r_{\cal C(s_i)}$ is the first route to come back in sources switch
+% \STATE $m_{\cal C(s_i)} \leftarrow $ clock;
+% \STATE clock $\leftarrow$ $t(c_t,r_{\cal C(s_i)})$ + $\tau$
+% \WHILE{there is a route which has not been scheduled}
+% \STATE take i such that $r_{\cal C(s_i)}$ is the eligible route.
+% \STATE $m_{\cal C(s_i)} \leftarrow $ clock - $t(c_t,r_{\cal C(s_i)})$;
+% \STATE clock $\leftarrow$ clock + $\tau$
+% 
+% \ENDWHILE
+% 
+% \end{algorithmic}
+% \end{algorithm}
+\todo{ecrire l'algo}
 
-\begin{algorithm}[H]
-\caption{LSG}
-\begin{algorithmic}
-\REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, packet size $\tau$
-\ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$
-\STATE clock $\leftarrow$ 0
-\FORALL{route i in $r_{s_i}$ from the longest to the shortest }
-\STATE  $m_{s_i} \leftarrow$ clock
-\STATE clock $\leftarrow$ clock + $\tau$
-\ENDFOR
-\STATE clock $\leftarrow$ 0
-\STATE take i such that $r_{\cal C(s_i)}$ is the first route to come back in sources switch
-\STATE $m_{\cal C(s_i)} \leftarrow $ clock;
-\STATE clock $\leftarrow$ $t(c_t,r_{\cal C(s_i)})$ + $\tau$
-\WHILE{there is a route which has not been scheduled}
-\STATE take i such that $r_{\cal C(s_i)}$ is the eligible route.
-\STATE $m_{\cal C(s_i)} \leftarrow $ clock - $t(c_t,r_{\cal C(s_i)})$;
-\STATE clock $\leftarrow$ clock + $\tau$
-
-\ENDWHILE
-
-\end{algorithmic}
-\end{algorithm}
-
-	\paragraph{Analysis}
+	\paragraph{Particular case corresponding to C-RAN}
 
 	One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the, this algorithm gives an optimal solution.
-Indeed, all the same weight can be simplified by 0, thus the scheduling in the forward and backward period is the same, that is, all message following each others, so the period is minimal : $n.\tau$, where $n$ is the number of couples $(s,{\cal C}(s))$.
+Indeed, all the same weight can be simplified by 0, thus the scheduling in the forward and backward period is the same, that is, all message following each others, so the period is minimal : $n.\tau$, where $n$ is the number of routes.
 Furthermore, all the waiting times are set to 0 i.e.
@@
 
-     \subsubsection{Results}
-	 \paragraph{Random}
-	 \paragraph{Distributions}
+     \subsubsection{Sending order}
+
+     \subsubsection{A better Algorithm : periodicity}
+
+     \subsubsection{Another better Algorithm : $T_{MAX}$}
+
+     \subsubsection{Mix : Simons periodic}
 
 \section{Conclusion}
-
-Open questions. Can we improve the results if:
-\begin{itemize}
- \item The routes are smaller than the size of a message. 
-\item The routes are smaller than the period.
-\item The largest difference between two routes is smallest than one of these parameters
-\end{itemize}
-
- On a general graph:
-
-\begin{itemize}
-\item The routing is coherent
- \item The graph is symmetric
-\end{itemize}
 

### 2017-05-17 article/article.tex

@@
 A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1}) \mod P$ in the forward period, and  $c_t$ at time $m_{t_1} + t(c_t,r_{t_1})\mod P$ in the backward period.
-      A $(P,\tau)$-periodic affectation consist in choosing for all $i < n$, $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$, we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$.
+
+      A $(P,\tau)$-periodic affectation is the choice for all $i < n$, of $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$, we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$.
 
@@
   In this subsection, we deal with a simpler version of the problem PALL.
-  We ask for a $(P,\tau)$-periodic affectation {\bf with all waiting times equal to $0$} and we call this restricted problem  
-  {\bf Periodic Assignment for Zero Latency} or PAZL. 
+  We ask for a $(P,\tau)$-periodic affectation {\bf with all waiting times equal to $0$} and we call this restricted problem {\bf Periodic Assignment for Zero Latency} or PAZL. 
   In that case $MT({\cal M})$ is equal to twice the delay of the longest route, thus $T_{max}$ is not relevant anymore. 
   Since $w_i=0$, choosing $m_i$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i) \mod P$.
- We assume from now on that the weight of the arcs from $s_i$ to $c_s$ are all equal to $0$, since we can change 
-  all $m_i$ into $m_i - t(c_s,r_i) \mod P$ and obtain the same affectation.
+  Remark that there is a bijection between the affectation of a star topology and the 
+  the affectation of the same star topology where all arcs from $s_i$ to $c_s$ have weight equal to $0$
+  by changing $m_i$ into $m_i - t(c_s,r_i) \mod P$. Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
+
+  \todo{Dire qu'on donne deux algos qui trouvent toujours une solution quand certains condtions sont remplies
+  et un dernier qui sait décider si il y a une solution oui ou non mais qui est exponentiel avec des optimisations pour le rendre pratique}
 
@@
 
-      \begin{proposition} When $n\tau + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0})) \leq P$, the algorithm Shortest-Longest solves PAZL.
+      \begin{proposition} When $n\tau + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0})) \leq P$,
+      the algorithm Shortest-Longest solves positively PAZL in time $O(n\log(n))$.\label{prop:SL}
       \end{proposition}
@@
 
-       We assume that $\lambda(r_{s_0}) = 0$, by removing $\lambda(r_{s_0})$ to every route, it does not change the order on the routes
-       nor the result of this algorithm.
+       We assume may that $\lambda(r_{s_0}) = 0$, since removing $\lambda(r_{s_0})$ to every route does not change the order on the length of the routes and thus the result of this algorithm.
       We have  $[t(c_s,r_{t_i})] = \{2 \lambda(r_{s_i}) + i\tau, \dots,  2 \lambda(r_{s_i}) + (i+1)\tau -1\}$ since $2 \lambda(r_{s_{n-1 }}) + n\tau \leq P$.
-       Since $ \lambda(r_{s_i}) \leq  \lambda(r_{s_{i+1}})$ by construction, we have  $2 \lambda(r_{s_i}) + (i+1)\tau -1 < 2 \lambda(r_{s_{i+1}}) + (i+1)\tau$
-       which proves that there are no collision on the backward period. 
+       Since $ \lambda(r_{s_i}) \leq  \lambda(r_{s_{i+1}})$ by construction, we have  $2 \lambda(r_{s_i}) + (i+1)\tau -1 < 2 \lambda(r_{s_{i+1}}) + (i+1)\tau$ which proves that there are no collision on the backward period.
+
+       The complexity of the algorithm is dominated by the sorting of the routes. 
       \end{proof}
 
-      If the period is slightly smaller that the bound, a collision will occur on the route in the backward period, making 
+      If the period is slightly smaller that the bound of Proposition~\ref{prop:SL}, a collision will occur on the route in the backward period, making 
       this policy not useful even as a heuristic for longer routes.
-
-%       
-% The message using the shortest route is sent before the others, therefore on the backward period it cannot conflict 
-% 
-% comes back to the central node before the following ones.
-% Then, the second message is sent before the others, and also will be back before the third etc... 
-% Because the message $i$ is sent $\tau$ slots after the message $i-1$ ($m_{s_i} = m_{s_{i-1}} + \tau$), it comes back after the end of the message $i-1$: $m_{s_{i-1}}+ \tau + 2.\lambda(r_{s_{i-1}}) \le m_{s_i} + 2.\lambda(r_{s_i})$ because of $\lambda(r_{s_i}) \ge \lambda(r_{s_{i-1}})$.
-% 
-%       Because of $m_{s_i} = \tau.i$ in the forward period, there is no collisions.
-%       To ensure that there is no collisions in the backward period, we must ensure that the last message ends before the end of the period P.
-We have to find the minimum period P such that the last message have totally came back before P slots after the first message.
-%       
-%       The this policy ensure us a period of $$P = \tau * n + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0}))$$ if routes $\{r_0,...,r_{s_{n-1}}\}$ are ordered
-% from the shortest to the longest. 
-% 
-% We have to calculate the time taken by the last message to reach $c_t$. $2.\lambda(r_{s_0})$ is the first slot in which the first message is coming back in the backward period,
-% and 2$\lambda(r_{s_{n-1}}) + n . \tau $ is the time at which the last message has totally passed the switch.
-% Therefore, the period only depends of the difference between the longest and the shortest route: the larger this value is, the larger
-% the period is.
-%
 
@@
     \begin{proposition}
-    Let  $n$ be the number of routes and let $ 3n\tau \leq P$, then there is an algorithm which finds a $(P,\tau)$-periodic affectation in time $O(n^2)$.
+    Let  $n$ be the number of routes and let $ 3n\tau \leq P$, then there is an algorithm which positively solves PAZL in time $O(n^2)$.
     \end{proposition}
     \begin{proof}
-     We consider the forward period and cut it into consecutive macro slots of $\tau$ time slots.
-The algorithm works by choosing an offset for each route in the following way: try all offests which put the message in a yet not used macro slot in the forward
+     We consider the forward period and cut it into consecutive interval of size $\tau$ that we call macro-slots.
+The algorithm works by choosing an offset for each route in the following way: try all offsets which put the message in a yet not used macro-slot in the forward
      period.
 The choice of an offset also fixes the position of the message in the backward period, chose the first one which does not create a collision.
-We now prove that this algorithm always find an offset for all routes when $P \geq 3n\tau$.
+We now prove that this algorithm always finds a $(P,\tau)$-periodic affectation without waiting time when $P \geq 3n\tau$.
 
-     Assume we are choosing the offset of the route $r_{k+1}$, we have  at least $P - k \geq 3n - k$ free macro-slots, since $P \geq 3n\tau$.
+     Assume we are choosing the offset of the route $r_{k+1}$, we have at least $P - k \geq 3n - k$ free macro-slots in the forward period, since $P \geq 3n\tau$.
 Each of these $3n - k$ possible offset values translates into $3n - k$ positions of messages in the backward period.
@@
 One such message can intersect at most $2$ potential positions since they are disjoint intervals.
-Therefore  amongst the possible $3n - k$ positions, there are  $3n - k -2k$ which are without collision.
-Since $k < n$, one of the choice is without collision, which proves that the algorithm terminates and find a  $(P,\tau)$-periodic affectation.
+Therefore  amongst the possible $3n - k$ positions, there are  at least $3n - k -2k$ which are without collision.
+Since $k < n$, $3n - k -2k \geq 1$, which proves that the algorithm terminates and find a  $(P,\tau)$-periodic affectation.
 
@@
 % 	\end{algorithm}
-\todo{J'ai commencé à modifier l'algo pour qu'il colle, mais ça n'est pas encore ça. 
-pas sur que ça vaille la peine de le mettre, je le commente pour l'instant.}
 
 This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
-In fact, experimental data in Subsection~\ref{sec:experimental_results} suggest that the algorithm works well as soon as $P \geq 1.5 \tau$ for small routes.
-
-\todo{vérifier cette affirmation en faisant une expérience et une régression linéaire}
+In fact, experimental data in Subsection~\ref{sec:experimental_results} suggests that the algorithm works well as soon as $P \geq 1.5 \tau$.
 
@@
 % 	    
-      We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found
-      a $(P,\tau)$-periodic affectation. We have $n$ routes denoted by $\{0,\dots,n-1\}$. A partial solution $S$ is 
-      a partial function from $[n]$ to $\{0,1,\dots,P-\tau -1\}$ which sets a starting time for a subset of the routes $R(S) \subseteq [n]$,
-      such that there are no collisions for these routes.
-A partial solution $S'$ extends $S$, if it sets one more routes than $S$ to a larger starting time than all routes in $S$, that is $R(S') = R(S) \cup \{r'\}$ and for all  $r \in R(S)$, $S(r) + \tau \leq S'{r'}$.
+      We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found a $(P,\tau)$-periodic affectation.
+Contrarily to the two previous algorithms, when it fails to find a solution, then it certifies there are no solution to PAZL.
+
+      We have $n$ routes denoted by $\{0,\dots,n-1\}$. A partial solution $S$ is 
+      a partial function from $[n]$ to $\{0,1,\dots,P-\tau -1\}$ which sets a starting time for a subset of the routes $R(S) \subseteq [n]$, such that there are no collisions for these routes.
+A partial solution $S'$ extends $S$, if $S'$ is defined over one more route than $S$ and this route has a larger starting offset than all routes of $S$: $R(S') = R(S) \cup \{r'\}$ and for all  $r \in R(S)$, $S(r) + \tau \leq S'{r'}$.
 We define a tree whose nodes are partial solutions and such that the root is the empty partial solution and
-      the children of a partial solution are the partial solutions which extend it. All solutions to our problem will be 
-      leaves in this tree, therefore our algorithm is simply a depth-first search of the tree.
+      the children of a partial solution are the partial solutions which extend it.
+The solutions to our problem will be the leaves of depth $n$ in the tree, therefore our algorithm is a depth-first search of the tree.
 
       Remark that a node $S$ with $|R(S)| = k$ can have as many as $(n-k)P$ children.
-Since the tree is of depth $n$, the tree may have as many as $n!P^n$ elements and while $n$ is often small, $P$ may be large which makes its traversal intractable.
+Since the tree is of depth $n$, the tree may have as many as $n!P^n$ elements and while $n$ is small, $P$ may be large which makes its traversal intractable.
 Therefore we have to find cuts in the tree to avoid to explore it entirely and henceforth make the algorithm practical.
 Cuts correspond to the detection of subtrees which contain no solutions and can thus be skipped.
-      We now propose three cuts, the first two being particularly useful when the network is loaded ($n\tau$ is not much smaller than $P$).
+      We now propose three cuts, the first two being particularly useful when the network is loaded ($n\tau$ is not far from $P$).
 
       \begin{enumerate}
-       \item We consider the number of slots which can be used by routes not yet fixed by a partial solution in the 
-       \emph{forward period}.
+       \item We consider the number of slots which can be used by routes not yet fixed by a partial solution in the \emph{forward period}.
 When we extend a solution into $S$ by a route at offset $m$, then at most $(P - m) / \tau $ routes can still be set without collisions in the forward period.
@@
 Without loss of generality we can assume that all $a_i, b_i \leq l$.
-The number of message of size $\tau$ which can be set in the useful slots of $S$ is thus  $\displaystyle{ \sum_{i=0}^{l} (b_{i} -a_i)/\tau } $.
+The number of messages of size $\tau$ which can be placed in the useful slots of $S$ is thus  $\displaystyle{ \sum_{i=0}^{l} (b_{i} -a_i)/\tau } $.
 If that value is less than the number of routes which are not in $R(S)$, it is a failure and the algorithm backtracks.
@@
 $S_2$).
-We say that $S_1$ dominates $S_2$ if the largest offset fixed in $S_1$ is smaller than the one in $S_2$ and $US_2 \subseteq US_1$.
-Remark that any valid sequence of extension of $S_2$ (fixing offsets of routes in the complementary of
-       $R(S_2)$) is also a valid sequence of extensions of $S_1$.
+We say that \emph{$S_1$ dominates $S_2$} if there are more useful slots both in the forward and backward periods for $S_1$ than for $S_2$.
+Formally, the largest offset fixed in $S_1$ is smaller than the one in $S_2$ and $US_2 \subseteq US_1$.
+Remark that any valid sequence of extensions of $S_2$ (choosing offsets of routes in the complementary of $R(S_2)$) is also a valid sequence of extensions of $S_1$.
 Therefore if the tree rooted at $S_2$ contain a solution, then $S_1$ contains one too.
@@
        Consider a partial solution $S$ which we extend into $S'$ by setting the offset of the route $r$ to be the smallest possible.
-The offset of $r$ in the backward period is $S'(R)+ \lambda$ and we denote the end of the message before before by $a$.
-Then all extensions of $S$ into $S''$ with $S'(r)  < S''(r) < a + \tau - \lambda$ are dominated by $S'$.
+The offset of $r$ in the backward period is $S'(r)+ \lambda$ and we denote the end of the message before before by $a$.
+Hence all extensions of $S$ into $S''$ such that $S'(r)  < S''(r) < a + \tau - \lambda$ are dominated by $S'$.
 Therefore when computing the extension of $S$, we first build $S'$ and then $S''$ with $S''(r) =  a + \tau - \lambda$ , skipping all values in between.
@@
       The third cut works well in conjunction with the first one since it makes the offsets grow quickly and 
-      which makes the first cut more likely to apply. A last cut could be implemented, by computing whether for every 
-      route not in $R(S)$ the set of possible positions in the backward period and checking whether one s contained in the useful slots of $S$.
+      which makes the first cut more likely to apply.
+A last cut could be implemented: compute for every route not in $R(S)$ the set of possible positions in the backward period and verify whether at least one is contained in the useful slots of $S$.
 
@@
 
-      The following performance evaluation results compares the three presented algorithms.
-      Notice that both Greedy algorithm and the Shortest-Longest are polynomial time algorithm but are not always able to
-      find optimal solutions. On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time.
-      We will compare the performance of the algorithms in two different regimes: the routes are either short or arbitrary long.
+      The following experimental results help compare the three presented algorithms.
+      Notice that both Greedy algorithm and the Shortest-Longest are polynomial time algorithm but are not always able to find a solution.
+On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time.
+We will compare the performance of the algorithms in two different regimes: the routes are either short with regards to $\tau$ and $P$ or unrestricted.
+      We choose the parameter realistic with regard to our C-RAN context. The number of routes 
+      is at most $n = 20$, $\tau$ is equal to $2500$ and the period is at most $3n\tau$ (otherwise the greedy algorithm always returns a solution).
+
+      \todo{Dire où on peut trouver le code (pas la peine de donner des infos sur la machine/compilateur car one ne fait pas d'étude de performances.}
 %             
@@
 The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.
-
-      \todo{Mettre les données concrètes plus proprement et éventuellement ne pas les mettre si on envoie pas à un truc de télécom}
+% 
+%       \todo{Mettre les données concrètes plus proprement et éventuellement ne pas les mettre si on envoie pas à un truc de télécom}
 
@@
 
-      Firstly, we made some performance evaluation on graphs in which the values $\lambda(c_t,r_{t_i})$ are drawn uniformly between $0$ and $700$ slots.
-This parameter is coming from our C-RAN context, in which the physical links are short enough.
-In C-RAN context, the size of a message is of $2500$ slots.\\
+      First we consider routes which are shorter than $\tau$, that is a message cannot be contained 
+      completely in a single edge.
+This is typical in our context and we will consider graphs in which the values $\lambda(c_t,r_{t_i})$ are drawn uniformly between $0$ and $700$ slots.
+It corresponds to messages of size blah and links of bandwidth 10Gbps and length less than blah.
 
-      For a given instance, we try to determine the minimum period $P$ for which the graph has a $(P,\tau)$ periodic affectation; to that end,  we need to do a linear search on the value $P$, a dichotomy would not work because of Lemma~\ref{lemma:monotonic}.
-      We generated $1000$ random instances of PAZL, and we applied the linear search with each of the three algorithm.
-Then we measure the average minimal period, for each algorithm.
-We applied this test increasing the number of routes, until it was too long for the exhaustive search to find a solution quickly.
+      \todo{à compléter}
 
-%our network has a throughput of 10Gbps throughput and 
-%       
-%       
-%       The messages size $\tau$ is of 2500 slots, that is, approximately 1.228 Gbps of data for each route.
-The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.
+      Our aim is to understand how well the algorithms are working when the network has a high load (when 
+      the load is low, the greedy algorithm always returns a solution). To do that we try to evaluate the 
+      minimal period for which a $(P,\tau)$ periodic affectation can be found by each algorithm. 
+      To that end we do a linear search on $P$, since a dichotomy would not work because of Lemma~\ref{lemma:monotonic}.
 
-      Since the exhaustive search is optimal, the average periods founds by this algorithm is the lower lower bounds for the other algorithms.
-      As an information, we draw the $f(n) = n\tau$, which is an absolute lower bound on the period and $g(n) = 3n\tau$ lines which is the theoretical upper bound of the greedy algorithm.
+      In our experiment, we generated $1000$ random instances of PAZL for $1$ to $12$ routes. 
+      We measured the average minimal period, for each algorithm.
+We needed to stop our experiments at $12$ routes since the exhaustive search was taking more than a second to finish on many instances.
+      Note that the exhaustive search is optimal, that is it finds the best possible period for a given instance. 
+      We also drew the function $f(n) = n\tau$, which is an absolute lower bound on the period and $g(n) = 3n\tau$ which is the theoretical upper bound of the greedy algorithm.
 
@@
 
-% 	  We now consider waiting times.
-The weights on links from sources to $c_s$ are now relevant because the goal is to minimize $MT({\cal M})$, with ${\cal M}$ the $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$.
-% 	  To build such a $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, we must choose the offsets $m_{s_i}$ and $m_{t_i}$, such that there is no $PT(s)$ greater than a given $T_{max}$.
-% 	  As a reminder, $ PT(s)=\lambda(r_s)+ w_s+\lambda(r_{t_i})$.
+% 
+%
 

### 2017-05-17 article/article.tex
amélioration expériences petites routes encore

@@
       \end{center}
-     \caption{Average minimum period of the algorithms according to the period for short routes.}
+     \caption{Minimum period found by the algorithms averaged over $1000$ random instances for each number of routes.}
 \end{figure}
 
-      As a reminder, the period needed by Shortest-Longest to find an optimal solution is determined by the difference between the longest and the shortest route.
-Here, because of the routes are short, this difference is small in regards to the period.
-Thus, we can imagine that this algorithm gives good solutions when the routes are short.
-      With those parameters, we can observe that the average period of Shortest-Longest is always equal to the Exhaustive generation, that is, the lower bound.
-      The next results is to theoretically prove that, with those parameters, Shortest-Longest gives optimal solutions, like this experimental study suggests it does. 
-      About the Greedy Algorithm, with those parameters, it always gives us bigger periods than Shortest longest.
-However, the results show that this algorithm gives average periods lower than the theoretical upper bound of this algorithm ($3n\tau$).
-      We can also observe that, for any algorithm, the average minimal periods seems increasing linearly with the number of routes.
-We made a linear regression on every set of data, and we observed that for the three algorithm, the correlation coefficient is greater than $0,999$.
+      First, we remark that the period found by the exhaustive search is only very slightly above the lower bound 
+      $n\tau$, which means that, in this regime, it is very well justified to look for a solution without waiting time even for a highly loaded network.
+
+      The period needed by Shortest-Longest to find an optimal solution is determined by the difference between the longest and the shortest route and could be easily determined theoretically.
+The algorithm was expected to be good since the routes are short, but it turns out it always finds the optimal solution in our experiments.
+Therefore, we should use it in practical application, in this regime, instead of the exhaustive search which is much more computationally expensive.
+
+      Finally we remark that the greedy algorithm have an average period much lower than the theoretical upper bound of $3n\tau$.
+We made a linear regression on this value and with a correlation coefficient greater than $0,999$ we find a slope of $1.53n\tau$.
 

### 2017-05-17 article/article.tex
avec wiaiting debut

--- 2017-05-16 article/article.tex
@@
 
+	\paragraph{Another particular case}
 	Another case of this topology is the case in which all the weight on the arcs between $c_s$ and the sources are the same.
@@
 
-	We consider only the delay between $c_t$ and the targets, that are $\lambda(r_{s})$.
+	Since we can simplify the weight on the arcs between $c_s$ and the sources, we consider only the delay between $c_t$ and the targets.
 Order the routes such that $\lambda(r_{s_i}) > \lambda(r_{s_j}), i,j \in n, i<j$, i.e.
@@
 	The messages are sent in the forward period from 0 to $n-1$, that is $m_{s_i} = \tau * n$.
-
-	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is so $PT(s_0) = 2.\lambda(r_{s_0}) + \tau$.
+	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is $PT(s_0) = 2.\lambda(r_{s_0}) $.
 	The second message is eligible in the backward period at time $\tau + 2.\lambda(r_{s_1})$.
 Thus, the waiting time of the second route is $w_{s_1} = 2.\lambda(r_{s_0})+\tau - (\tau + 2.\lambda(r_{s_1})) = 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))$.
-Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1})) +\tau = 2.\lambda(r_{s_0}) + \tau = PT(s_0)$.
+Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))  = 2.\lambda(r_{s_0})  = PT(s_0)$.
 	By induction, $PT(s_i) = PT(s_0), \forall i \in n$. 
-	Consequently, for this case, the heuristic is optimal, because the longest route has no waiting time all the other routes will take exactly the same time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) + \tau$, which is not alterable
+	Consequently, for this case, the heuristic is optimal, because the longest route has no waiting time all the other routes has the exact same process time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) $.
+
+	This results is available because we do not consider the weight on links before $c_s$.
 
      \subsubsection{Sending order}
+	When then tried to look at the behaviour of the greedy policy with different kind of sending the messages, in the first way.
 
+	We tried the five following sending policy, on the first way, and we applied the greedy heuristic to the way back, considering the offsets given by the sending policy used.
+	The different sending policy are the following :
+	\begin{enumerate}
+	 \item trying $X$ random permutations of the routes, until one gives an available $(P,\tau)$ periodic affectation.
+	 \item from the longest to the shortest route.
+	 \item from the shortest to the longest route.
+	 \item from the longest to the shortest arc between $c_t$ an the target.
+	 \item from the shortest to the longest arc between $c_t$ an the target.
+	\end{enumerate}
+
+	\todo{Mettre les prametres d'une experience ou on voit le taux de réussite des différents départs}
      \subsubsection{A better Algorithm : periodicity}
+
+     The previous algorithm is a greedy heuristic, which does not take the period into account. Thus, some given solution by this algorithm need a too large period an thus, are not available. 
+     We propose an improved version of the algorithm, still greedy, but which consider the period.
+
+     The greedy policy is the same, but
 

### 2017-05-17 code/code.c

@@ -91,7 +91,7 @@ void graphe_etoile_opti(Graphe g,int taille_liens)
 	if(!(g.N%2)){printf("Impossible de générer une étoile avec un nombre pair de sommets\n");exit(5);}
 	int pivot = g.N/2;
 	int alea;
-	for(int i=pivot+1;i<g.N;i++)
+	for(int i=0;i<pivot;i++)
 	{
 		alea = rand()%taille_liens;
 		g.matrice[pivot][i] = alea;

### 2017-05-17 article/article.tex
simons moitier

--- 2017-05-17 article/article.tex
@@
 This is typical in our context and we will consider graphs in which the values $\lambda(c_t,r_{t_i})$ are drawn uniformly between $0$ and $700$ slots.
-It corresponds to messages of size blah and links of bandwidth 10Gbps and length less than blah.
-
-      \todo{à compléter}
+It corresponds to messages of approximately 1Mb, links of bandwidth 10Gbps and length less than 5km between the BBU and the RRH.
 
@@
 	  In the previous section, we described some algorithm to solve an easier version of PALL, in which there is no waiting times.
-As we just conclude, this problem cannot be solved when the period is too small.
+As we conclude, this problem cannot be solved when the period is too small.
 The C-RAN context gives us a fixed period, thus, some topologies with a lot of routes might be impossible to schedule with the previous algorithms.
@@
 
-      To find a solution with waiting times, the following heuristic is suggested:
+      First, we imagined that prioritise the messages one the longest route could be a good idea. Thus, the following heuristic is suggested:
 
-      On the forward period, the messages are scheduled so that they are following each others, from the one using the longest route, to the one using the shortest route.
+      On the forward period, for the first way, the messages are scheduled so that they are following each others, from the one using the longest route, to the one using the shortest route.
 Thus, we set the $m_{s_i}$ of the routes such that  $t(c_s,r_{s_i}) = \tau.i$, if the routes $r_i$ are ordered from the longest to the shortest.
 
-      On $c_t$, the policy is the following one, after setting the clock to 0:
+      On $c_t$, the algorithm is the following one:
+
+  \begin{algorithm}[H]
+
+    \caption{Eligible route}
+    \label{algorithm:Eligible}
     \begin{enumerate}
-      \item To be eligible, a message needs to be able to come back on $c_t$ at the current clock (if clock = 0, take the first message able to come back).
+
+      \item To be eligible, a message needs to be able to come back on $c_t$ at the current clock (if clock = 0, or no messages are able to come back at this date, take the first message able to come back).
       \item Between the eligible messages, schedule first the one which has the lowest deadline.
-      \item Repeat until all the messages had been scheduled.
+      \item For any route i, the deadline correspond to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$.
+This deadline corresponds to the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
+
       \end{enumerate}
 
-      For any route i, the deadline correspond to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$.
-This deadline corresponds to the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
-% 
-% \begin{algorithm}[H]
-% \caption{Longest Shortest Greedy (LSG)}
-% \begin{algorithmic}
-% \REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, packet size $\tau$
-% \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$
-% \STATE clock $\leftarrow$ 0
-% \FORALL{route i in $r_{s_i}$ from the longest to the shortest }
-% \STATE  $m_{s_i} \leftarrow$ clock
-% \STATE clock $\leftarrow$ clock + $\tau$
-% \ENDFOR
-% \STATE clock $\leftarrow$ 0
-% \STATE take i such that $r_{\cal C(s_i)}$ is the first route to come back in sources switch
-% \STATE $m_{\cal C(s_i)} \leftarrow $ clock;
-% \STATE clock $\leftarrow$ $t(c_t,r_{\cal C(s_i)})$ + $\tau$
-% \WHILE{there is a route which has not been scheduled}
-% \STATE take i such that $r_{\cal C(s_i)}$ is the eligible route.
-% \STATE $m_{\cal C(s_i)} \leftarrow $ clock - $t(c_t,r_{\cal C(s_i)})$;
-% \STATE clock $\leftarrow$ clock + $\tau$
-% 
-% \ENDWHILE
-% 
-% \end{algorithmic}
-% \end{algorithm}
-\todo{ecrire l'algo}
+  \end{algorithm}
+
+    \begin{algorithm}[H]
+    \caption{Longest Shortest Greedy (LSG)}
+    \begin{algorithmic}
+    \REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, packet size $\tau$
+    \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$
+    \STATE $clock \leftarrow 0$
+    \FORALL{route i in $r_{s_i}$ sorted from the longest to the shortest }
+    \STATE  $m_{s_i} \leftarrow clock - t(c_s,r_{s_i}) \mod P$
+    \STATE $clock \leftarrow clock + \tau$
+    \ENDFOR
+
+    \STATE take i such that $r_{t_i}$ is the eligible route (Algorithm \ref{algorithm:Eligible})
+    \STATE $w_i \leftarrow 0$
+    \STATE $clock = \lambda(r_i) + t(c_t,r_{t_i}) + \tau$
+    \WHILE{there is a route which has not been scheduled}
+    \STATE take i such that $r_{t_i}$ is the eligible route (Algorithm \ref{algorithm:Eligible})
+    \IF{ the messages is able to come back before $clock$}
+    \STATE $w_i = clock - t(c_t,r_{t_i}) - (m_i + \lambda(r_i))$ 
+    \STATE $clock \leftarrow clock + \tau$
+    \ELSE
+    \STATE $w_i \leftarrow 0$
+    \STATE $clock = \lambda(r_i) + t(c_t,r_{t_i}) + \tau$
+   \ENDIF
+
+    \ENDWHILE
+
+    \end{algorithmic}
+    \end{algorithm}
+
+    This policy is split in two steps.
+First, we choose arbitrary a sending order for the routes, and we set the offsets $m_i$ such that the messages are following each others in $c_s$.
+Then, the way back is determined considering the time at which the messages reach their target.
+This greedy policy determines the $w_i$, such that the messages does not collide on $c_t$.
+One can expect that this policy prioritise the longest route, and thus helps to minimise $PT(s_i)$.
+Indeed, the messages on the longest routes will be less buffered in their target than the messages using the shortest ones.
+The goal is to balance the process times such that if there is a very long route, the message on it will not be buffered at all, and if there is a very short route, the message can be buffered, but not enough to have a process time greater than twice the delay on the longest route.
+In other words, if $i$ is the very long route, and $j$ the very short one, we want $w_i =0$, and $PT(s_i) = 2.\lambda(r_{s_i}) \geq  2.\lambda(r_{s_j}) + w_j = PT(s_j) $.
+    This greedy policy does not ensure that, but this is the main idea of the algorithm.
+    Furthermore, this heuristic does not take into account the period at all, thus, a solution given by this algorithm can satisfy the constraint $MT({\cal M}) \leq T_{max}$, but this solution might need a too large period.
+
+     \subsubsection{Sending order}
+
+	We tried to look at the behaviour of the greedy policy with different kind of sending order for the messages.
+
+	We tried the five following sending policy, each ones determines an order in which the messages will be sent, but the messages are still following each others in $c_s$.
+
+	The different sending policy that we tested are the following :
+	\begin{enumerate}
+	 \item Generate $X$ random permutations for the routes and tries the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic affectation.
+	 \item Send the messages from the one using longest to the one using shortest route (this is the sending order used in the previous heuristic).
+	 \item Send the messages from the one using shortest to the one using longest route
+	 \item Send the messages from the one having the longest arc between $c_t$ an the target to the one having the shortest one.
+	 \item Send the messages from the one having the shortest arc between $c_t$ an the target to the one having the longest one.
+	\end{enumerate}
+
+	The fifth order gives us the same policy than Shortest-Longest, the algorithm described in last section.
+This sending order gives us some $(P,\tau)$ periodic affectation in which all the $w_i = 0$, but needs a huge period if the difference between the longest and the shortest route is large (see proposition \ref{prop:SL}).
+
+	For the fourth order, in the case in which all the weight on the arcs between $c_s$ and the sources are the same, the algorithm gives optimal solutions.
+	Since we can simplify the weight on the arcs between $c_s$ and the sources, we consider only the delay between $c_t$ and the targets.
+Order the routes such that $\lambda(r_{s_i}) > \lambda(r_{s_j}), i,j \in n, i<j$, i.e.
+the route 1 is the longest one, and the route $n$ is the shortest.
+	The messages are sent in the forward period from 0 to $n-1$, that is $m_{s_i} = \tau * n$.
+	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is $PT(s_0) = 2.\lambda(r_{s_0}) $.
+	The second message is eligible in the backward period at time $\tau + 2.\lambda(r_{s_1})$.
+Thus, the waiting time of the second route is $w_{s_1} = 2.\lambda(r_{s_0})+\tau - (\tau + 2.\lambda(r_{s_1})) = 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))$.
+Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))  = 2.\lambda(r_{s_0})  = PT(s_0)$.
+	By induction, $PT(s_i) = PT(s_0), \forall i \in n$. 
+	Consequently, for this case, the heuristic is optimal, because the longest route has no waiting time all the other routes has the exact same process time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) $.
 
@@
 
-	Another case of this topology is the case in which all the weight on the arcs between $c_s$ and the sources are the same.
-	In this case, the algorithm gives optimal solutions too:\\
-
-	We consider only the delay between $c_t$ and the targets, that are $\lambda(r_{s})$.
-Order the routes such that $\lambda(r_{s_i}) > \lambda(r_{s_j}), i,j \in n, i<j$, i.e.
-the route 1 is the longest one, and the route $n$ is the shortest.
-	The messages are sent in the forward period from 0 to $n-1$, that is $m_{s_i} = \tau * n$.
-
-	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is so $PT(s_0) = 2.\lambda(r_{s_0}) + \tau$.
-	The second message is eligible in the backward period at time $\tau + 2.\lambda(r_{s_1})$.
-Thus, the waiting time of the second route is $w_{s_1} = 2.\lambda(r_{s_0})+\tau - (\tau + 2.\lambda(r_{s_1})) = 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))$.
-Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1})) +\tau = 2.\lambda(r_{s_0}) + \tau = PT(s_0)$.
-	By induction, $PT(s_i) = PT(s_0), \forall i \in n$. 
-	Consequently, for this case, the heuristic is optimal, because the longest route has no waiting time all the other routes will take exactly the same time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) + \tau$, which is not alterable
-
-     \subsubsection{Sending order}
-
      \subsubsection{A better Algorithm : periodicity}
 
-     \subsubsection{Another better Algorithm : $T_{MAX}$}
+     For the rest of the section, we look at the different algorithm suggested to improve the second part of the scheduling, after having set the sending order.
+     The previous algorithm is a greedy heuristic, which does not take the period into account. Thus, some solutions given by this algorithm might need a too large period an thus, not be available. 
+     We propose an improved version of the algorithm, still greedy, but which consider the period $P$.
+
+     We first remember the date at which the first messages starts to come back through $c_t$. Let us note $bp$ this date.
+     The greedy policy is the same until the message are scheduled in the period between $bp$ and $bp +P$. When a message is scheduled, we update a list of free intervals in the backward period.
+     Once $clock > bp+P$, we consider that we are in the second period, and thus search a free interval after $clock$, large enough to put a message.
+
+     This policy can significantly increase $w_i$, but ensures a periodic results. This policy is strictly better than the previous one.
+
+     \subsubsection{Another better Algorithm than LSG: optimal on PT}
+
+     The problem PALL is very similar to a scheduling problem, combined to the periodic aspect.
+Thus, the article ``A fast algorithm for single processor scheduling'', by Barbara Simons \cite{simons1978fast} gave us an optimal algorithm to schedule some jobs which has a release time, a deadline and the same execution time.
+We consider that the messages are the jobs, the release times are the date at which the messages are able to come back on $c_t$, and the deadlines are the latest date at which a message have to leave $c_t$ to comeback before $m_i + T_{max}$.
+This algorithm gives in $\mathcal{O}(n^2\log{}n)$ a solution with the earliest  possible completion time, if it exists.
+
+     This algorithm uses the exact same greedy scheduling than LSG.
+Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call \em{crisis message} this message), the algorithm call a subroutine that reschedule the previous message such that the crisis message will be scheduled earlier.
 

### 2017-05-17 code/code.c

@@ -1065,7 +1065,7 @@ void echec_periode_gvsgp3D(int nb_routes, int taille_paquets,int taille_route, i
 				for(int i = 0;i<nb_simuls;i++)
 				{
 					g = init_graphe(2*nb_routes+1);
-					graphe_etoile_opti(g,taille_route);
+					graphe_etoile_moitier(g,taille_route);
 					tmax = marge + longest_route(g);
 					//affiche_etoile(g);
 					//printf("TMAX = %d\n",tmax);
@@ -1195,6 +1195,7 @@ void echec_periode_gvsgp3D(int nb_routes, int taille_paquets,int taille_route, i
 	fclose(F);
 }
 
+
 int main()
 {
 	srand(time(NULL));
@@ -1220,8 +1221,8 @@ int main()
 
 	}*/
 	//echec_periode_gvsgp(8,2500,20000, 0, 10000,3);
-	for(int i=0;i<5;i++)
-		echec_periode_gvsgp3D(8,2500,700, 1000,i);
+	for(int i=3;i<5;i++)
+		echec_periode_gvsgp3D(8,2500,5000, 1000,i);
 	
 	/*Graphe g ;
 

### 2017-05-18 article/article.tex
merge

--- 2017-05-17 article/article.tex
@@
       \paragraph{Long routes}
-      We now want to look at the performance of those algorithm if we significantly increase the size of the route.
-By increasing the size of the routes, the cuts of the exhaustive search, are less efficient.
-Thus, we defined a counter that allow the exhaustive search to end if no solutions are found.
 
-      Since the exhaustive generation can fail, this is necessary to change the method to measure the minimum period for each algorithm, when the routes are long.      
-      The following figure shows us the average success rate of the algorithms, on $1000$ instances, according to the period, with 8 routes, in which $\lambda(c_t,r_{t_i})$, are drawn following an uniform distribution between $0$ and $30000$ slots, that correspond to have the size of the route and the period approximately in the same range.
+      We now want to understand the performance of these algorithms when the size of the routes are unbounded.
+When the routes are long, the cuts in the exhaustive search are less efficient and thus even for a small number of routes the algorithm may be impractical.
+To make the experimentations short enough, we have bounded the number of nodes of the tree of partial solutions the exhaustive search can visit to $10^9$.
 
-      The reason why the shortest longest were optimal in the previous experiences ,i.e.
-having a small difference between the longest and the shortest route, is no longer reviewed.
-In this situation, this difference can be considerable, and then the required period too.
-
-      One the other hand, one can imagine that the greedy $3.n.\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
+      In this experiment we will fix the number of routes to $8$ and the values $\lambda(c_t,r_{t_i})$ are drawn following an uniform distribution between $0$ and $30000$ slots (in the same range as the period).
+      We measure for each algorithm its percentage of success, for periods from $20000$ which is the minimum possible to $50000$.
 
@@
      \end{figure}
+
+      One the other hand, one can imagine that the greedy $3.n.\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
 
@@
 
-	\paragraph{Another particular case}
 	Another case of this topology is the case in which all the weight on the arcs between $c_s$ and the sources are the same.
@@
 
-	Since we can simplify the weight on the arcs between $c_s$ and the sources, we consider only the delay between $c_t$ and the targets.
+	We consider only the delay between $c_t$ and the targets, that are $\lambda(r_{s})$.
 Order the routes such that $\lambda(r_{s_i}) > \lambda(r_{s_j}), i,j \in n, i<j$, i.e.
@@
 	The messages are sent in the forward period from 0 to $n-1$, that is $m_{s_i} = \tau * n$.
-	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is $PT(s_0) = 2.\lambda(r_{s_0}) $.
+
+	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is so $PT(s_0) = 2.\lambda(r_{s_0}) + \tau$.
 	The second message is eligible in the backward period at time $\tau + 2.\lambda(r_{s_1})$.
 Thus, the waiting time of the second route is $w_{s_1} = 2.\lambda(r_{s_0})+\tau - (\tau + 2.\lambda(r_{s_1})) = 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))$.
-Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))  = 2.\lambda(r_{s_0})  = PT(s_0)$.
+Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1})) +\tau = 2.\lambda(r_{s_0}) + \tau = PT(s_0)$.
 	By induction, $PT(s_i) = PT(s_0), \forall i \in n$. 
-	Consequently, for this case, the heuristic is optimal, because the longest route has no waiting time all the other routes has the exact same process time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) $.
-
-	This results is available because we do not consider the weight on links before $c_s$.
+	Consequently, for this case, the heuristic is optimal, because the longest route has no waiting time all the other routes will take exactly the same time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) + \tau$, which is not alterable
 
      \subsubsection{Sending order}
-	When then tried to look at the behaviour of the greedy policy with different kind of sending the messages, in the first way.
 
-	We tried the five following sending policy, on the first way, and we applied the greedy heuristic to the way back, considering the offsets given by the sending policy used.
-	The different sending policy are the following :
-	\begin{enumerate}
-	 \item trying $X$ random permutations of the routes, until one gives an available $(P,\tau)$ periodic affectation.
-	 \item from the longest to the shortest route.
-	 \item from the shortest to the longest route.
-	 \item from the longest to the shortest arc between $c_t$ an the target.
-	 \item from the shortest to the longest arc between $c_t$ an the target.
-	\end{enumerate}
-
-	\todo{Mettre les prametres d'une experience ou on voit le taux de réussite des différents départs}
      \subsubsection{A better Algorithm : periodicity}
-
-     The previous algorithm is a greedy heuristic, which does not take the period into account. Thus, some given solution by this algorithm need a too large period an thus, are not available. 
-     We propose an improved version of the algorithm, still greedy, but which consider the period.
-
-     The greedy policy is the same, but
 

### 2017-05-18 article/article.tex
fin des modifs expérimentation sans waiting time

@@
 This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
-In fact, experimental data in Subsection~\ref{sec:experimental_results} suggests that the algorithm works well as soon as $P \geq 1.5 \tau$.
+In fact, experimental data in Subsection~\ref{sec:experimental_results} suggests that the algorithm finds a solution on average when $P \geq 1.5 n\tau$.
+Note that we also experimented with other greedy algorithms which do not use macro-slots, they work even better in practice but their theoretical upper bound is worse.
 
@@
       \end{center}
-     \caption{Minimum period found by the algorithms averaged over $1000$ random instances for each number of routes.}
+      \caption{Minimum period averaged over $1000$ random instances}
       \end{figure}
 
-      First, we remark that the period found by the exhaustive search is only very slightly above the lower bound 
+      First, we remark that the period found by the exhaustive search is only very slightly above the lower bound of 
       $n\tau$, which means that, in this regime, it is very well justified to look for a solution without waiting time even for a highly loaded network.
@@
 When the routes are long, the cuts in the exhaustive search are less efficient and thus even for a small number of routes the algorithm may be impractical.
-To make the experimentations short enough, we have bounded the number of nodes of the tree of partial solutions the exhaustive search can visit to $10^9$.
+To make the experimentations short enough, we have bounded the number of nodes of the tree of partial solutions the exhaustive search can visit by $10^9$.
 
@@
 
-    On the following figure, the upper bound represents the cases in which the exhaustive search found a solution plus the number of {\em early} halts of the search.
-The real upper bound is probably between those two curves.
+      Since the exhaustive search can fail because there are no solutions or because it does not have enough time to finish its calculation.
+We represent both the success rate of the algorithm, and an upper bound on the success rate of any algorithm solving PAZL by combining its successes and its failure because of lack of time.
+
 \begin{figure}
@@
       \end{center}
-      \caption{Success rate of the algorithms according to the period for long routes.}
+      \caption{Success rate for $8$ routes over $1000$ random instances}
      \end{figure}
 
-      One the other hand, one can imagine that the greedy $3.n.\tau$ algorithm finds reasonable solutions, because the algorithm does not consider the size of the route, and thus, is not impacted by this parameter.
+      In this regime, the performances of Shortest-Longest are abysmal since it depends on the difference between the longest and the smallest route
+      which is large here.
+On the other hand, the greedy algorithm has a performance not very different from the case of short routes, which is expected since it does not depends on the size of the route.
+\todo{Ajouter la moyenne pour la comparer aux routes courtes}
 
-      As we can see, Shortest longest has a very low success rate, and is not efficient anymore with those parameters.
-      Whereas, the greedy algorithm gives us solutions with much lower period than Shortest Longest.
-The exhaustive search keeps finding good solutions in short periods but it fails a lot for periods that does not give a lot of flexibility in the backward period.
-This mean that, for a small period, a solution may exists, but the exhaustive search needs too much time to find it.
-In this situation, it could be better to use the greedy algorithm, that find a good solution in a polynomial time.
+      When the period is less than $40000$, the exhaustive search find much more solutions than the greedy algorithms which justifies its use. 
+      However for small period, less than $30000$ the computation time is really important and without improvement it would not be possible to tackle 
+      larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small period, we see that there are very few instances
+      with a solution for PAZL. It means that with long routes and high load, looking for an affectation without waiting may be to restrictive.
+      That is why we present algorithms for the general PALL problem in our next section. We will test them on $8$ long routes and a period between 
+      $20000$ and $30000$ where, as we have shown here, there are often no easy to compute affectation without waiting time.
 
-      So, those experiences shows us that, for C-RAN topologies, with small routes, shortest-longest finds some optimal affectations in a polynomial time, but, the longer the routes are, the better it is to use the greedy policy to find a solution without waiting times in a polynomial time.\\
-
-      As we just saw, if the load increases, the needed period increases too, and it is not possible anymore to find a solution without waiting times with a small period.
-The next sections treats about the proposed solutions to find a $(P,\tau)$ periodic affectation when the period is small.
    \subsection{Allowing waiting times}

### 2017-05-18 article/article.tex
nouvel algo FPT

@@
       Since the exhaustive search can fail because there are no solutions or because it does not have enough time to finish its calculation.
-We represent both the success rate of the algorithm, and an upper bound on the success rate of any algorithm solving PAZL by combining its successes and its failure because of lack of time.
+We represent both the success rate of the algorithm, and an upper bound on the success rate of any algorithm solving PAZL by combining its successes and its failures because of lack of time.
 
@@
 
-      When the period is less than $40000$, the exhaustive search find much more solutions than the greedy algorithms which justifies its use. 
+      When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithm which justifies its use. 
       However for small period, less than $30000$ the computation time is really important and without improvement it would not be possible to tackle 
-      larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small period, we see that there are very few instances
-      with a solution for PAZL. It means that with long routes and high load, looking for an affectation without waiting may be to restrictive.
+      larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small periods, we see that there are very few instances
+      with a solution for PAZL. It means that with long routes and high load, looking for an affectation without waiting may be too restrictive.
       That is why we present algorithms for the general PALL problem in our next section. We will test them on $8$ long routes and a period between 
@@
 
-      First, we imagined that prioritise the messages one the longest route could be a good idea. Thus, the following heuristic is suggested:
+      First, we imagined that prioritize the messages one the longest route could be a good idea. Thus, the following heuristic is suggested:
 
@@
 
+     \subsubsection{A fixed parameter tractable solution}
+
+     In this part we try to give a fixed parameter tractable algorithm to solve the PALL problem with parameter $n$ the number of routes.
+     This is justified since $n$ is always very small (less than $20$) while $P$, or $\tau$ may be very large.
+
+     \begin{theorem}
+      There is an algorithm which solves PALL on star topologies in $O( )$.
+     \end{theorem}
+     \begin{proof}
+      In this algorithm we will guess a certain number of values related to an affectation and then compute in polynomial time
+      an affectation which satisfies these properties if it exists. Then the FPT algorithm will be to try every possible set of values 
+      and use the polynomial time algorithm.
+
+      We assume we are given the order at which the messages goes through the forward
+      period and the order at which the messages goes through the backward period. 
+      This is represented by the permutation $\sigma_f$ and $\sigma_b$. \todo{Des notations pour 
+      le début des routes dans la backward et la forward}.
+
+      Supposition sans perte de généralité : il n'y a pas de temps d'attente  pour le premier paquet qui passe dans 
+      la backward windows.
+      Fait: les paquets passent dans la backward windows à un temps au plus 2P plus grand que le premier paquet (peut-être 3P avec
+      le temps d'attente). 
+      On devine si ils sont entre $O$ et $P$, entre $P$ et $2P$.
+
+      On écrit un système linéaire très simple pour les contraintes de non collision et d'être dans la fenêtre
+      et ne pas dépasset $T_{max}$.
+      On montre qu'on peut toujours trouver une solution entière à ce système si on a une solution réelle (en tronquant).
+
+      Alternative: donner un algo plus efficace pour trouver la solution qu'un système linéaire avec de la prog dyn.
+
+     \end{proof}
+
 \section{Conclusion}

### 2017-05-18 article/article.tex

--- 2017-05-18 article/article.tex
@@
 
+    By using a binary heap to manage the eligible routes, this algorithm runs in $\mathcal{O}(n\log{}n)$.
+
     This policy is split in two steps.
@@
 
-     \subsubsection{Another better Algorithm than LSG: optimal on PT}
+     \subsubsection{Another better Algorithm than Greedy: optimal on PT}
 
@@
      This algorithm uses the exact same greedy scheduling than LSG.
-Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call \em{crisis message} this message), the algorithm call a subroutine that reschedule the previous message such that the crisis message will be scheduled earlier.
+Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call \em{crisis message} this message), the algorithm call a subroutine which, following some criteria, removes some previous messages such that the crisis message can be scheduled earlier.
 
-     \subsubsection{Mix : Simons periodic}
+     If this algorithm gives us a $(P,\tau)$ periodic affectation, it satisfies the criteria $MT({\cal M}) < T_{max}$ Also, the algorithm minimizes $MT({\cal M})$, but does not ensure the periodicity.
+
+     \subsubsection{Final algorithm}
+
+     We adapted the optimal algorithm presented in the previous paragraph, to ensure a periodic $(P,\tau)$ periodic affectation, if it exists, with the given offsets, which are determined by the sending order chose.
+
+    \begin{algorithm}[H]
+    \caption{Optimal Periodic}
+    \begin{algorithmic}
+    \REQUIRE A routage graph ${\cal R_{\cal C}}$,a period $P$, packet size $\tau$, the offsets $m_i$
+    \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, if it exists
+
+    \FORALL{route $r_{t_i}$}
+    \STATE  $w_i \leftarrow 0$
+    \STATE $end-period \leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
+    \FORALL{route $r_{t_j}$}
+    \STATE $deadline-route \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
+    \STATE $deadline \leftarrow (deadline-route,end-period)$
+    \ENDFOR
+
+    \STATE Call the optimal algorithm
+
+    \ENDFOR
+
+    \STATE return the best $(P-\tau)-$periodic affectation, or FAILURE
+
+    \end{algorithmic}
+    \end{algorithm}
+
+    This algorithm runs in $\mathcal{O}(n^3\log{}n)$.
+It tries for every routes of the routage graph, to fix the first route to comeback, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(determined by $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).
+
+    This algorithm guarantee an optimal scheduling for the messages, if it exists, once the offsets $m_i$ has been fixed.
+The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic affectation, even with a small period, and T$_{max}$.
+
+    \subsubsection{Results}
+
+    \paragraph{Comparer les departs}
+
+    \paragraph{Comparer les retours}
+
+    \paragraph{Comparer optimal + depart random avec stochastique}
 

### 2017-05-19 article/article.tex
merge main

--- 2017-05-18 article/article.tex
@@
 
-      When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithm which justifies its use. 
+      When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithms which justifies its use. 
       However for small period, less than $30000$ the computation time is really important and without improvement it would not be possible to tackle 
@@
      This algorithm uses the exact same greedy scheduling than LSG.
-Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call \em{crisis message} this message), the algorithm call a subroutine that reschedule the previous message such that the crisis message will be scheduled earlier.
+Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call {\em crisis message} this message), the algorithm call a subroutine which, following some criteria, removes some previous messages such that the crisis message can be scheduled earlier.
 
-     \subsubsection{Mix : Simons periodic}
+     If this algorithm gives us a $(P,\tau)$ periodic affectation, it satisfies the criteria $MT({\cal M}) < T_{max}$ Also, the algorithm minimizes $MT({\cal M})$, but does not ensure the periodicity.
+
+     \subsubsection{Final algorithm}
+
+     We adapted the optimal algorithm presented in the previous paragraph, to ensure a periodic $(P,\tau)$ periodic affectation, if it exists, with the given offsets, which are determined by the sending order chose.
+
+    \begin{algorithm}[H]
+    \caption{Optimal Periodic}
+    \begin{algorithmic}
+    \REQUIRE A routage graph ${\cal R_{\cal C}}$,a period $P$, packet size $\tau$, the offsets $m_i$
+    \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, if it exists
+
+    \FORALL{route $r_{t_i}$}
+    \STATE  $w_i \leftarrow 0$
+    \STATE $end-period \leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
+    \FORALL{route $r_{t_j}$}
+    \STATE $deadline-route \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
+    \STATE $deadline \leftarrow (deadline-route,end-period)$
+    \ENDFOR
+
+    \STATE Call the optimal algorithm
+
+    \ENDFOR
+
+    \STATE return the best $(P-\tau)-$periodic affectation, or FAILURE
+
+    \end{algorithmic}
+    \end{algorithm}
+
+    This algorithm runs in $\mathcal{O}(n^3\log{}n)$.
+It tries for every routes of the routage graph, to fix the first route to comeback, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(determined by $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).
+
+    This algorithm guarantee an optimal scheduling for the messages, if it exists, once the offsets $m_i$ has been fixed.
+The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic affectation, even with a small period, and T$_{max}$.
+
+    \subsubsection{Results}
+
+    \paragraph{Comparer les departs}
+
+    \paragraph{Comparer les retours}
+
+    \paragraph{Comparer optimal + depart random avec stochastique}
 

### 2017-05-19 article/article.tex
Reprise de l'intro

@@
 \begin{abstract}
-This article treats about Contention Management for 5G.
+We study the sending of periodic messages in a graph following predefined paths, a problem arising from the communication between radio antenna and their computing unit located in distant data-centers.
+We want to send the messages so that there are no congestion while minimizing the latency.
+We prove the problem is $\NP$-complete even when the graph is very simple.
+We then deal with the case of a star graph and for different regime of the parameters we propose several algorithms that are experimentally shown to work extremely well.
 \end{abstract}
-The evolutions proposed in next generations of mobile network architectures aim at evolving toward centralized radio network architectures (C-RAN, for Cloud Radio Access Network) to reduce consumption costs and power at the base stations \cite{mobile2011c}.
-This type of architecture faces the challenge of mastering the latency in the transfer process between the Remote Radio Heads (RRHs) on the field and baseband units (BBUs) in the cloud.
-Low latency is already critical for the deployment of C-RAN approach.
-The standard requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in less than from 1 to 10ms \cite{bouguen2012lte}
-(depending on targeted services).
-One specificity in the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRH and BBU (this HARQ constraints must be enforced for each frame emitted every millisecond).\\
- Thus in this article, we work on latency and periodicity constraints in fronthaul.
-The best current solution is to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches \cite{5gppparchitecture}.
+
+Next generations of mobile network architectures evolves toward centralized radio network architectures or C-RAN, for Cloud Radio Access Network, to reduce consumption costs and power at the base stations \cite{mobile2011c}.
+The main challenge for this type of architecture is the latency in the transfer process between the Remote Radio Heads (RRHs) on the field and baseband units (BBUs) in the cloud.
+The standard requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in 1 to 10ms depending on targeted services~\cite{bouguen2012lte}.
+One specificity in the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRH and BBU.
+
+ In this article, we study mechanisms to deal with the latency and periodicity constraints in fronthaul.
+The current solution is to use statistical multiplexing with a traditional queue management and use an optical network with a very large bandwidth to minimize latency.
+Here we propose to use a deterministic approach to schedule our periodic messages.
+This approach has gained some traction recently: Deterministic
+ Networking is under standardization in IEEE 802.1 TSN group \cite{finn-detnet-architecture-08}, as well at IETF DetNet working group \cite{ieee802}.
+Several patents on concepts and mechanisms for DetNet have been already published, see for example \cite{howe2005time,leclerc2016transmission}.
+
+ We must manage the time at which the packets of each paths are sent, and we can introduce a deterministic waiting time in the BBU before the packet is sent back to the RRH.
+The aim is to avoid any collision in the vertices of the graph, which allows to avoid buffering and to guarantee the latency.
+  One major difficulty of this problem is the periodicity of the process.
+Indeed, a deterministic sending for the messages between each pair BBU/RRH must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.\\
+
+%  to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches \cite{5gppparchitecture}.
 This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
@@
 These packets having a fixed duration close to $1\mu $s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.\\
- Thus, new scheduling and routing paradigms and new technologies have to be considered to  guarantee  delay constrained periodic data transfers.
+%  Thus, new scheduling and routing paradigms and new technologies have to be considered to  guarantee  delay constrained periodic data transfers.
 One of the most promising approaches relies on the concept of Deterministic Networking (DN) such that one get rid of
- statistical multiplexing. The traditional queue managements are replaced by time based forwarding. Solutions for Deterministic
- Networking are under standardization in IEEE 802.1 TSN group \cite{finn-detnet-architecture-08}, as well at IETF DetNet working group \cite{ieee802}.
+%  statistical multiplexing. The traditional queue managements are replaced by time based forwarding. Solutions for Deterministic
+%  Networking are under standardization in IEEE 802.1 TSN group \cite{finn-detnet-architecture-08}, as well at IETF DetNet working group \cite{ieee802}.
 Several patents on concepts and mechanisms for DetNet have been already published, see for example \cite{howe2005time,leclerc2016transmission}.
 To make DN working over a
- network composed of several nodes, it is required to manage the time at which the packets of deterministic paths are crossing each nodes.
+%  network composed of several nodes, it is required to manage the time at which the packets of deterministic paths are crossing each nodes.
 The major difficulty of this problem is the periodicity of the process.
 Indeed, a deterministic sending for the messages
-between each pair BBU/RRH must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous
-and following periods.\\
-
-Considering a graph, modeling the network topology, and a set of routes from source nodes (modeling connections to the BBU) and destination nodes (modeling the RRH) in this graph, the purpose is to select, for each destination node a route from one source node to it and a periodic routing scheme allowing to periodically sent a packet to each base station without congestion conflicts between all such packets and to insure a minimum latency.
-In a slotted time model, the aim is here to minimize the duration of the period, with a constraint of the maximum length of routes to be
-selected. Even if the selected set of routes is given this optimization problem has been shown to be  \NP-hard. From an algorithmic point of view,
-the purpose of this project is first, to study the complexity and the approximability of this problem when the length of the routes is small
-(which corresponds to realistic cases), and secondly, to propose and implement some heuristics to solve this problem on realistic topologies.\\
+% between each pair BBU/RRH must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous
+% and following periods.\\
+
+Considering a graph, modeling the network topology, and a set of routes from source nodes (modeling connections to the BBU) and destination nodes (modeling the RRH) in this graph, the purpose is to select, for each route from one source node to its destination a periodic routing scheme.
+It must ensure that there are no congestion conflicts between packets and guarantee a minimum latency.
+The time will be discretized and a unit of time corresponds to the transmission of a minimal unit of data over the network.
 
@@
 
+       Idée de David: deviner qu'est-ce qui coince, c'est à dire les routes qui ont une attente de 0, 
+       ça donne des intervalles collés.
+       Sinon on doit pouvoir faire du integer programming car le système est petit.
+
        Alternative: donner un algo plus efficace pour trouver la solution qu'un système linéaire avec de la prog dyn.

### 2017-05-24 article/article.tex
ek
mercredi soir

@@
   et un dernier qui sait décider si il y a une solution oui ou non mais qui est exponentiel avec des optimisations pour le rendre pratique}
+
+  We propose two algorithm that give solutions in polynomial time following some criteria (short routes or great enough period), and one exponential algorithm which determines if there is a solution, and find it if it exists.
 
@@
 
-      The following experimental results help compare the three presented algorithms.
-      Notice that both Greedy algorithm and the Shortest-Longest are polynomial time algorithm but are not always able to find a solution.
+      The following experimental results compare the three presented algorithms.
+      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithm but are not always able to find a solution.
 On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time.
@@
       Note that the exhaustive search is optimal, that is it finds the best possible period for a given instance. 
-      We also drew the function $f(n) = n\tau$, which is an absolute lower bound on the period and $g(n) = 3n\tau$ which is the theoretical upper bound of the greedy algorithm.
+      We also drew the functions $f(n) = n\tau$, which is an absolute lower bound on the period and $g(n) = 3n\tau$ which is the theoretical upper bound of the greedy algorithm.
 
@@
 
-     \subsubsection{Intro}
-
-	  In the previous section, we described some algorithm to solve an easier version of PALL, in which there is no waiting times.
-As we conclude, this problem cannot be solved when the period is too small.
-The C-RAN context gives us a fixed period, thus, some topologies with a lot of routes might be impossible to schedule with the previous algorithms.
+	  We just found solution to solve an easier version of PALL, in which there is no waiting times, that seems impossible to  solve when the period is too short.
 We propose to allow some message to wait in the target vertices (BBU), with the aim of giving an higher degree of freedom for the scheduling.
-In this section, the waiting times $w_i$ are not necessarily null anymore.
-Thus, $MT({\cal M})$ might be superior to $T_{max}$ and it is necessary to minimize $MT({\cal M})$.
-
-% 
-%
+Thus, the process time of a message $PT$ might be superior to $T_{max}$.
+The goal is to find some solutions with waiting time such that any message will be buffered too much, i.e.
+$MT({\cal M}) \leq T_{max}$.
+
+	\paragraph{Particular cases}
+
+	One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the same and so can be simplified by 0.
+In that case, the scheduling in the forward and backward period is the same.
+The trivial solution is to send all message following each others regardless the order.
+Thus, the period is minimal : $n.\tau$, where $n$ is the number of routes.
+Furthermore, all the waiting times are equal to 0 i.e.
+$w_i = 0,\forall i \in n$, thus, $MT({\cal M})$ is equal to twice the delay of the longest route, that is not alterable.
+
+	Another particular case is the following one:	
+	 \begin{theorem}
+      There is always an optimal solution when all the weight on the arcs between $c_s$ and the sources are the same.
+      \end{theorem}
+      \begin{proof}
+
+	Since we can simplify the weight on the arcs between $c_s$ and the sources, we consider only the delay between $c_t$ and the targets.
+Order the routes such that $\lambda(r_{s_i}) > \lambda(r_{s_j}), i<j$, i.e.
+the route 0 is the longest, and the route $n-1$ is the shortest one.
+	The messages are sent in the forward period from 0 to $n-1$, that is $m_{s_i} = \tau * n$.
+	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is $PT(s_0) = 2.\lambda(r_{s_0}) $.
+	The second message is eligible in the backward period at time $\tau + 2.\lambda(r_{s_1})$.
+Thus, the waiting time of the second route is $w_{s_1} = 2.\lambda(r_{s_0})+\tau - (\tau + 2.\lambda(r_{s_1})) = 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))$.
+Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))  = 2.\lambda(r_{s_0})  = PT(s_0)$.
+	By induction, $PT(s_i) = PT(s_0), \forall i \in n$. 
+	Consequently, for this case, sending the message, because the longest route has no waiting time all the other routes has the exact same process time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) $.
+     \end{proof}
 
@@
 
-      First, we imagined that prioritize the messages one the longest route could be a good idea. Thus, the following heuristic is suggested:
+	To solve PALL, we proposed some heuristics that prioritize the longest routes, and thus helps to minimize $PT(s_i)$.
+Indeed, one can imagine that, if the messages on the longest routes are be less buffered in their target than the messages using the shortest routes, the process times might be balanced.
+	In an optimal solution, if $i$ is the longest route, we want $w_i =0$, and $PT(s_i) = 2.\lambda(r_{s_i}) \geq  2.\lambda(r_{s_j}) + w_j = PT(s_j) $, where $j$ is any route $\neq i$.
+
+     We first suggest the following heuristic, that prioritize the message on longest routes:
 
@@
     \begin{algorithmic}
-    \REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, packet size $\tau$
+    \REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, $ T_{max}$, packet size $\tau$
     \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$
@@
 
-    This policy is split in two steps.
-First, we choose arbitrary a sending order for the routes, and we set the offsets $m_i$ such that the messages are following each others in $c_s$.
-Then, the way back is determined considering the time at which the messages reach their target.
-This greedy policy determines the $w_i$, such that the messages does not collide on $c_t$.
-One can expect that this policy prioritise the longest route, and thus helps to minimise $PT(s_i)$.
-Indeed, the messages on the longest routes will be less buffered in their target than the messages using the shortest ones.
-The goal is to balance the process times such that if there is a very long route, the message on it will not be buffered at all, and if there is a very short route, the message can be buffered, but not enough to have a process time greater than twice the delay on the longest route.
-In other words, if $i$ is the very long route, and $j$ the very short one, we want $w_i =0$, and $PT(s_i) = 2.\lambda(r_{s_i}) \geq  2.\lambda(r_{s_j}) + w_j = PT(s_j) $.
-    This greedy policy does not ensure that, but this is the main idea of the algorithm.
-    Furthermore, this heuristic does not take into account the period at all, thus, a solution given by this algorithm can satisfy the constraint $MT({\cal M}) \leq T_{max}$, but this solution might need a too large period.
+    This policy is split in two steps:
+    \begin{enumerate}
+    \item First, we choose arbitrary a sending order for the routes, and we set the offsets $m_i$ such that the messages are following each others in $c_s$.
+    \item  Then, the schedule order in the way back is determined, considering the time at which the messages reach their target. 
+    \end{enumerate}
+     This {\em Greedy} policy determines the $m_{c_{s_i}}$, such that the messages does not collide on $c_t$.
+It computes the deadlines for every messages, considering their offsets and the delay on their routes, and determine the time at which the messages must leave their target, prioritizing the messages with the lowest deadlines.
+
+     However, this heuristic does not take the period into account .
+Thus, a solution given by this algorithm can satisfy the constraint $MT({\cal M}) \leq T_{max}$, but this solution might need a too large period.
 
@@
 
-	We tried to look at the behaviour of the greedy policy with different kind of sending order for the messages.
+	We tried to look at the behavior of the that policy with different kind of sending order for the messages.
 
@@
 
-	The different sending policy that we tested are the following :
+	The different sending policy that we tried are the following :
 	\begin{enumerate}
-	 \item Generate $X$ random permutations for the routes and tries the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic affectation.
-	 \item Send the messages from the one using longest to the one using shortest route (this is the sending order used in the previous heuristic).
-	 \item Send the messages from the one using shortest to the one using longest route
-	 \item Send the messages from the one having the longest arc between $c_t$ an the target to the one having the shortest one.
-	 \item Send the messages from the one having the shortest arc between $c_t$ an the target to the one having the longest one.
+	 \item Random: Generate $X$ random permutations for the routes and tries the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic affectation.
+	 \item Longest-Shortest on Routes (LSR): Send the messages from the one using longest to the one using shortest route (this is the sending order used in the previous heuristic).
+	 \item Shortest-Longest on Routes (SLR): Send the messages from the one using shortest to the one using longest route
+	 \item Longest-Shortest on last Arc (LSA): Send the messages from the one having the longest arc between $c_t$ an the target to the one having the shortest one.
+	 \item Shortest-Longest on last Arc (SLA): Send the messages from the one having the shortest arc between $c_t$ an the target to the one having the longest one.
+This sending order gives us some $(P,\tau)$ periodic affectation in which all the $w_i = 0$, but needs a huge period if the difference between the longest and the shortest route is large (see proposition \ref{prop:SL}).
 	\end{enumerate}
 
-	The fifth order gives us the same policy than Shortest-Longest, the algorithm described in last section.
-This sending order gives us some $(P,\tau)$ periodic affectation in which all the $w_i = 0$, but needs a huge period if the difference between the longest and the shortest route is large (see proposition \ref{prop:SL}).
-
-	For the fourth order, in the case in which all the weight on the arcs between $c_s$ and the sources are the same, the algorithm gives optimal solutions.
-	Since we can simplify the weight on the arcs between $c_s$ and the sources, we consider only the delay between $c_t$ and the targets.
-Order the routes such that $\lambda(r_{s_i}) > \lambda(r_{s_j}), i,j \in n, i<j$, i.e.
-the route 1 is the longest one, and the route $n$ is the shortest.
-	The messages are sent in the forward period from 0 to $n-1$, that is $m_{s_i} = \tau * n$.
-	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is $PT(s_0) = 2.\lambda(r_{s_0}) $.
-	The second message is eligible in the backward period at time $\tau + 2.\lambda(r_{s_1})$.
-Thus, the waiting time of the second route is $w_{s_1} = 2.\lambda(r_{s_0})+\tau - (\tau + 2.\lambda(r_{s_1})) = 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))$.
-Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))  = 2.\lambda(r_{s_0})  = PT(s_0)$.
-	By induction, $PT(s_i) = PT(s_0), \forall i \in n$. 
-	Consequently, for this case, the heuristic is optimal, because the longest route has no waiting time all the other routes has the exact same process time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) $.
-
-	\paragraph{Particular case corresponding to C-RAN}
-
-	One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the, this algorithm gives an optimal solution.
-Indeed, all the same weight can be simplified by 0, thus the scheduling in the forward and backward period is the same, that is, all message following each others, so the period is minimal : $n.\tau$, where $n$ is the number of routes.
-Furthermore, all the waiting times are set to 0 i.e.
-$w_i = 0,\forall i \in n$, thus, $MT({\cal M})$ is equal to twice the longer delay of the routes, that is not alterable.
-
-     \subsubsection{A better Algorithm : periodicity}
-
      For the rest of the section, we look at the different algorithm suggested to improve the second part of the scheduling, after having set the sending order.
-     The previous algorithm is a greedy heuristic, which does not take the period into account. Thus, some solutions given by this algorithm might need a too large period an thus, not be available. 
-     We propose an improved version of the algorithm, still greedy, but which consider the period $P$.
+      \subsubsection{About the periodicity}
+     The previous algorithm is a greedy heuristic, which does not take the period into account. 
+     We propose an improved version of the algorithm, still greedy, but which tries to compute some solution that satisfies the period $P$: When we try to schedule some messages $P$ slots after the first message scheduled, the algorithm mind the already scheduled messages, and avoid collisions with them.
 
@@
 
-     This policy can significantly increase $w_i$, but ensures a periodic results. This policy is strictly better than the previous one.
-
-     \subsubsection{Another better Algorithm than Greedy: optimal on PT}
+     This policy can significantly increase $w_i$, but ensures a periodic results.
+This {\ Greedy Periodic} policy is strictly better than Greedy, because it finds some solutions that greedy would not find, by considering the periodicity in the scheduling.
+
+     \subsubsection{Near from scheduling problems}
 
@@
 This algorithm gives in $\mathcal{O}(n^2\log{}n)$ a solution with the earliest  possible completion time, if it exists.
-
-     This algorithm uses the exact same greedy scheduling than LSG.
-Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call {\em crisis message} this message), the algorithm call a subroutine which, following some criteria, removes some previous messages such that the crisis message can be scheduled earlier.
-
-     If this algorithm gives us a $(P,\tau)$ periodic affectation, it satisfies the criteria $MT({\cal M}) < T_{max}$ Also, the algorithm minimizes $MT({\cal M})$, but does not ensure the periodicity.
+Thus, it tries to minimize the time between the first and the last message in the scheduling.
+Let us call {\ Minimized Scheduling (MS)} this algorithm.
+
+     This algorithm uses the exact same main scheduling than Greedy.
+Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call {\em crisis message} this message), the algorithm call a subroutine which, following some criteria, removes some previous messages from the scheduling such that the crisis message can be scheduled earlier.
+Then, the main scheduling routines is applied again.
+Some stopping conditions are able to detect if there is no solution for the given routage graph.
+
+     If it exists a solution that satisfies the criteria $MT({\cal M}) < T_{max}$, this algorithm gives us a $(P,\tau)$ periodic affectation.
+Nevertheless, by setting the deadlines according to the size of the route only, the given $(P,\tau)$ periodic affectation might not respect the period $P$.
 
@@
 
-     We adapted the optimal algorithm presented in the previous paragraph, to ensure a periodic $(P,\tau)$ periodic affectation, if it exists, with the given offsets, which are determined by the sending order chose.
+     We adapted MS, presented in the previous paragraph, to consider the period, in the computation.
 
     \begin{algorithm}[H]
-    \caption{Optimal Periodic}
+    \caption{ Minimized Scheduling Periodic (MSP)}
     \begin{algorithmic}
-    \REQUIRE A routage graph ${\cal R_{\cal C}}$,a period $P$, packet size $\tau$, the offsets $m_i$
+    \REQUIRE A routage graph ${\cal R_{\cal C}}$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
     \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, if it exists
@@
 
-    \STATE Call the optimal algorithm
+    \STATE Call (MS)
 
@@
 
-    This algorithm guarantee an optimal scheduling for the messages, if it exists, once the offsets $m_i$ has been fixed.
+    This algorithm finds more solutions than MS, because it decrease the deadlines of the route considering the periodicity.
+Thus, a scheduling given by this algorithm fulfill both the periodicity and the $T_{max}$ criteria.
+
      The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic affectation, even with a small period, and T$_{max}$.
@@
     \subsubsection{Results}
+
+    To compare the previous algorithms, we first need to determine which of the sending order is the best.
+We know that Greedy Periodic is strictly better than Greedy, because it finds at least all the solutions given by Greedy.
+We compared the two algorithms on 10000 graphs on which the weight of the links are drawn uniformly between 0 and 20000, with a period of 21000, and giving, for each instance $T_{max} = 2\lambda(r_{longest-route})$ .
+We then look at the success rate of each algorithms, with every sending order.
+Both algorithms reach the higher success rate with the Random sending order, but the success of Greedy is 5,65 \%, while the success rate of Greedy Periodic is to 30,02 \%.
+    Those results confirms that Greedy Periodic is better than Greedy, this is the reason why we will compare the different sending orders with Greedy Periodic.
+
+   In this experiment, we fix the number of routes to 8.
+We want to compare the sending orders with the worst parameters, so we draw the links between 0 and 20000 slots (long routes).
+We look at the success rate of each sending order with Greedy Periodic to schedule the messages in the way back.
+We give to  $T_{max}$ some {\em flexibility}.
+This flexibility represents $T_{max} - 2\lambda(r_{longest-route})$.
+We let this flexibility vary from 0 to 3000.
+
+   We look at two different regimes: one in which the period represents $1,05n\tau$, and one with a greater period $1,5n\tau$. The following results are computed over 10000 instances.
+
+\begin{figure}
+
+       \begin{center}
+      \includegraphics[scale=0.4]{departs_gp_21000.pdf}
+      \end{center}
+      \caption{Success rate for $P = 21000$}
+     \end{figure}
+
+\begin{figure}
+
+       \begin{center}
+      \includegraphics[scale=0.4]{departs_gp_30000.pdf}
+      \end{center}
+      \caption{Success rate for a $P = 30000$}
+     \end{figure}
 
@@
 \section{Conclusion}
+test
 

### 2017-05-24 code/code.c

@@ -124,6 +124,8 @@ void graphe_etoile_moitier(Graphe g,int taille_liens)
 }
 
 
+/* EMPTY BODY LOOPS
+
 //renvoie un anneau avec les routes
 Routage_Graph graphe_anneau(int nb_sommets,int nb_routes,int taille_liens)
 {
@@ -160,9 +162,8 @@ Routage_Graph graphe_anneau(int nb_sommets,int nb_routes,int taille_liens)
 	rc.couples = couples;
 	return rc;
 
-
 }
-
+*/
 
 
 //met toutes les cases du message a 1 dans la periode
@@ -1044,6 +1045,96 @@ void echec_periode_gvsgp(int nb_routes, int taille_paquets,int taille_route,int 
 	fclose(F);
 }
 
+void echec_tmax_waitings(int nb_routes, int taille_paquets,int taille_route,int marge_max, int nb_simuls, int periode)
+{
+
+
+	FILE * F = fopen("compare_departs_30000.data","w");
+	Graphe g ;
+	int resa,resb,resc,resd,rese;
+	float a,b,c,d,e;
+	int tmax;
+	int nb_rand = 100;
+	for(int marge=0;marge<= marge_max;marge += 50)
+	{
+		a=0;
+		b=0;
+		c=0;
+		d=0;
+		e=0;
+
+		for(int i = 0;i<nb_simuls;i++)
+		{
+			g = init_graphe(2*nb_routes+1);
+			graphe_etoile(g,taille_route);
+			tmax = marge + longest_route(g);
+			//affiche_etoile(g);
+			//printf("TMAX = %d\n",tmax);
+			//printf("tmax = %d(%d + %d) \n",tmax,longest_route(g),marge);
+			
+			for(int compteur_rand = 0;compteur_rand<nb_rand;compteur_rand++)
+				{
+					resa = longest_etoile_periodique(g,taille_paquets,periode,tmax,0);
+					if(resa != -2)
+					{	
+						if(resa != -1)
+						{
+
+							a++;
+							//printf("On a trouvé pour a au %d ieme tick (%d) \n",compteur_rand,resa);
+							break;
+						}
+						
+					}
+				}
+
+			resb = longest_etoile_periodique(g,taille_paquets,periode,tmax,1);
+			resc = longest_etoile_periodique(g,taille_paquets,periode,tmax,2);
[…]

### 2017-05-30 article/article.tex
merge PAZL

@@
 
-    \subsubsection{A fixed parameter tractable solution}
-
-      In this part we try to give a fixed parameter tractable algorithm to solve the PALL problem with parameter $n$ the number of routes.
-      This is justified since $n$ is always very small (less than $20$) while $P$, or $\tau$ may be very large.
-
-      \begin{theorem}
-       There is an algorithm which solves PALL on star topologies in $O( )$.
-      \end{theorem}
-      \begin{proof}
-       In this algorithm we will guess a certain number of values related to an affectation and then compute in polynomial time
-       an affectation which satisfies these properties if it exists. Then the FPT algorithm will be to try every possible set of values 
-       and use the polynomial time algorithm.
-
-       We assume we are given the order at which the messages goes through the forward
-       period and the order at which the messages goes through the backward period. 
-       This is represented by the permutation $\sigma_f$ and $\sigma_b$. \todo{Des notations pour 
-       le début des routes dans la backward et la forward}.
-
-       Supposition sans perte de généralité : il n'y a pas de temps d'attente  pour le premier paquet qui passe dans 
-       la backward windows.
-       Fait: les paquets passent dans la backward windows à un temps au plus 2P plus grand que le premier paquet (peut-être 3P avec
-       le temps d'attente). 
-       On devine si ils sont entre $O$ et $P$, entre $P$ et $2P$.
-
-       On écrit un système linéaire très simple pour les contraintes de non collision et d'être dans la fenêtre
-       et ne pas dépasset $T_{max}$.
-       On montre qu'on peut toujours trouver une solution entière à ce système si on a une solution réelle (en tronquant).
-
-       Idée de David: deviner qu'est-ce qui coince, c'est à dire les routes qui ont une attente de 0, 
-       ça donne des intervalles collés.
-       Sinon on doit pouvoir faire du integer programming car le système est petit.
-
-       Alternative: donner un algo plus efficace pour trouver la solution qu'un système linéaire avec de la prog dyn.
-
-      \end{proof}
-
 \section{Conclusion}

### 2017-05-30 code/PAZL/PAZL.c

@@ -3,9 +3,9 @@
 #include <time.h>
 
 
-#define ROUTE_NUMBER 8
+#define ROUTE_NUMBER 12
 #define MESSAGE_SIZE 2500
-#define PERIOD 22000
+#define PERIOD 34000
 #define ROUTE_SIZE 20000
 
 
@@ -153,16 +153,16 @@ int recursive_search(int *id, int*start_slot, int *return_slot, stack *fw, stack
 
 
 int search(int message_size, int period, int route_number, int* return_time){
-	printf("Instance aléatoire :\n");//we assume that the value in return time are in [0,period[
-	for(int i = 0; i < route_number; i++) printf("%d  ",return_time[i]);
+	//printf("Instance aléatoire :\n");//we assume that the value in return time are in [0,period[
+	//for(int i = 0; i < route_number; i++) printf("%d  ",return_time[i]);
 	int shift = return_time[0];
-	printf("\nInstance aléatoire décalée :\n");
+	//printf("\nInstance aléatoire décalée :\n");
 	for (int i = 0; i < route_number; i++){//we shift the values so that the first route has return time 0
 		return_time[i] -= shift;
 		if (return_time[i] < 0) return_time[i] += period;
-		printf("%d  ",return_time[i]);
+		//printf("%d  ",return_time[i]);
 	}
-	printf("\n");
+	//printf("\n");
     /* Memory allocation */		
 	stack *fw = malloc(sizeof(stack)*route_number);
 	stack *bw = malloc(sizeof(stack)*route_number);
@@ -210,12 +210,12 @@ int search(int message_size, int period, int route_number, int* return_time){
 int main(){
   	srand(time(NULL));
   	int succes = 0;
-  	for(int i = 0; i < 10; i++){
+  	for(int i = 0; i < 100; i++){
   	int *return_time = genere_reseau(ROUTE_NUMBER,ROUTE_SIZE,PERIOD);
   	succes += search(MESSAGE_SIZE,PERIOD,ROUTE_NUMBER,return_time);
   	free(return_time);
   }
-  float res = succes / 10.0;
+  float res = succes / 100.0;
   printf(" Taux de réussite : %f \n",res);
   return 0;
 }

### 2017-05-30 code/Sources/PAZL.c

@@ -442,7 +442,7 @@ int ajoute_element (intervalle_liste * liste, int debut, int taille,
       if (liste[pos].debut <= debut
     && liste[pos].fin - debut >= taille_paquets)
     {     //l'intervalle existe, on le découpe
-    //on calcule le nombre de slot après décooupage (en prenant en compte les paquets déjà placés)
+    //on calcule le nombre de slot après découpage (en prenant en compte les paquets déjà placés)
     *nombre_slot +=
       (debut - liste[pos].debut) / taille_paquets + (liste[pos].fin -
                  debut) /

### 2017-05-30 article/article.tex

@@
 \begin{abstract}
-We study the sending of periodic messages in a graph following predefined paths, a problem arising from the communication between radio antenna and their computing unit located in distant data-centers.
-We want to send the messages so that there are no congestion while minimizing the latency.
-We prove the problem is $\NP$-complete even when the graph is very simple.
-We then deal with the case of a star graph and for different regime of the parameters we propose several algorithms that are experimentally shown to work extremely well.
+We study the sending of periodic messages in a graph following predefined paths, a problem arising from the communication between radio antennas and their signal processing units located in distant data-centers.
+The messages must be sent deterministically to minimize the latency.
+We prove that the problem is $\NP$-complete even for very restricted graphs.
+We then deal with the case of a star graph and for different regimes of the parameters we propose algorithms that are experimentally shown to work extremely well
+compared to traditional statistical multiplexing.
 \end{abstract}
 
-Next generations of mobile network architectures evolves toward centralized radio network architectures or C-RAN, for Cloud Radio Access Network, to reduce consumption costs and power at the base stations \cite{mobile2011c}.
-The main challenge for this type of architecture is the latency in the transfer process between the Remote Radio Heads (RRHs) on the field and baseband units (BBUs) in the cloud.
+Next generations of mobile network architectures evolve toward centralized radio network architectures or C-RAN, for Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c}.
+The main challenge for this type of architecture is the latency in the transfer process between the Remote Radio Heads (RRHs) on the field and the Baseband Units (BBUs) in the cloud.
 The standard requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in 1 to 10ms depending on targeted services~\cite{bouguen2012lte}.
@@
 
- In this article, we study mechanisms to deal with the latency and periodicity constraints in fronthaul.
-The current solution is to use statistical multiplexing with a traditional queue management and use an optical network with a very large bandwidth to minimize latency.
+ In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network.
+The current solution is to use statistical multiplexing with a traditional queue management in an optical network with a very large bandwidth to minimize latency.
 Here we propose to use a deterministic approach to schedule our periodic messages.
-This approach has gained some traction recently: Deterministic
- Networking is under standardization in IEEE 802.1 TSN group \cite{finn-detnet-architecture-08}, as well at IETF DetNet working group \cite{ieee802}.
-Several patents on concepts and mechanisms for DetNet have been already published, see for example \cite{howe2005time,leclerc2016transmission}.
-
- We must manage the time at which the packets of each paths are sent, and we can introduce a deterministic waiting time in the BBU before the packet is sent back to the RRH.
-The aim is to avoid any collision in the vertices of the graph, which allows to avoid buffering and to guarantee the latency.
-  One major difficulty of this problem is the periodicity of the process.
-Indeed, a deterministic sending for the messages between each pair BBU/RRH must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.\\
-
-%  to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches \cite{5gppparchitecture}.
-This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
-It is then needed to find a solution to offer low latency over commoditized packet based networks.
-Indeed,  dynamical optical bypass and dynamical management of the emission should be considered to guarantee latency constraints, as it is considered in the french ANR project N-GREEN.
-This project proposes a new type of switching/routing node and a specific network architecture exploiting WDM packets thanks to a new generation of optical add/drop multiplexers (WSADM: WDM slotted add/drop multiplexer).
-These packets having a fixed duration close to $1\mu $s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.\\
-%  Thus, new scheduling and routing paradigms and new technologies have to be considered to  guarantee  delay constrained periodic data transfers.
-One of the most promising approaches relies on the concept of Deterministic Networking (DN) such that one get rid of
-%  statistical multiplexing. The traditional queue managements are replaced by time based forwarding. Solutions for Deterministic
-%  Networking are under standardization in IEEE 802.1 TSN group \cite{finn-detnet-architecture-08}, as well at IETF DetNet working group \cite{ieee802}.
-Several patents on concepts and mechanisms for DetNet have been already published, see for example \cite{howe2005time,leclerc2016transmission}.
-To make DN working over a
-%  network composed of several nodes, it is required to manage the time at which the packets of deterministic paths are crossing each nodes.
-The major difficulty of this problem is the periodicity of the process.
-Indeed, a deterministic sending for the messages
-% between each pair BBU/RRH must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous
-% and following periods.\\
-
-Considering a graph, modeling the network topology, and a set of routes from source nodes (modeling connections to the BBU) and destination nodes (modeling the RRH) in this graph, the purpose is to select, for each route from one source node to its destination a periodic routing scheme.
-It must ensure that there are no congestion conflicts between packets and guarantee a minimum latency.
-The time will be discretized and a unit of time corresponds to the transmission of a minimal unit of data over the network.
-
-This problem may look like wormhole problem \cite{cole1996benefit}, very popular few years ago, but here, we want to minimize the time lost in buffers and not just avoid the deadlock, and the wormhole does not treat about the periodicity.
-Several graph colorings have been introduced to model similar problems such as the allocation of frequencies \cite{borndorfer1998frequency}, bandwidths \cite{erlebach2001complexity}[17] or routes \cite{cole1996benefit}[18] in a network or train schedules \cite{strotmann2007railway}[19].
-Unfortunately, they do not take into account the periodicity and the associated problems are also NP-complete.
-The only model which incorporates some periodicity is the circular coloring \cite{zhou2013multiple, zhu2001circular,zhu2006recent}but is not expressive enough to capture our problem.
-
-\subsection*{Paper organisation}
- In the next section, ...
-
-\section{Model}
+This approach has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}.
+Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}.
+
+ The network topology is modeled by a directed weighted graph and a set of routes (paths) from source nodes (RRH) to target nodes (BBUs).
+The time is discretized and a unit of time corresponds to the transmission of a minimal unit of data over the network.
+ The process must be periodic, that is if we look at the network at time $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the networks.
+Moreover, we want to avoid any  buffering in internal nodes of the graph, therefore the periodic process we need to design cannot collision between packets.
+To ensure that we need to propose a deterministic process.
+ We have two sets of parameters that we can choose when building a periodic sending process or a \textbf{periodic assignment}, first the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
+We have two major difficulties to overcome when building an periodic assignment.
+First the periodicity which makes many scheduling methods inapplicable, since one must ensure that a message does not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.
+Second, one must minimize the latency, that is the time
+ between the emission of a message and the complete return of its answer. It means that the only buffering we are allowed in the BBU
+ (the waiting time before sending back the answer) must be small, in particular when the route is long.
+
+This problem may look like wormhole problems~\cite{cole1996benefit}, but here we want to minimize the time lost in buffers and not just avoid deadlocks, moreover the periodicity is not considered in wormhole problems.
+Several graph colorings have been introduced to model similar problems such as the allocation of frequencies~\cite{borndorfer1998frequency}, bandwidths~\cite{erlebach2001complexity} or routes~\cite{cole1996benefit} in a network or train schedules~\cite{strotmann2007railway}.
+Unfortunately, they do not take into account the periodicity and the associated problems are also $\NP$-complete.
+The only model which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple, zhu2001circular,zhu2006recent} but is not expressive enough to capture our problem.
+
+\subsection*{Article organization}
+ In Sec.~\ref{sec:def} we define our model, we formalize our problems PRA (one way periodic assignment) and PALL (two ways periodic assignment) and study their basic properties.
+In Sec.~\ref{sec:complexity}, we prove that the problem PRA is $\NP$-hard and cannot be approximated even for very
+restricted graphs. In the next two sections, we study the problem PALL case on a star topology which often arises in practice.
+Since the problem is already quite complicated, we first study a variant called PAZL in Sec.\ref{sec:PAZL}, where the waiting times
+are all zero. We provide several algorithms, some of their theoretical properties and give experimental evidences that they work well
+when the network is no too loaded.
+Finally in Sec.\ref{sec:PALL}, we propose algorithms for the general problem and exhibit one which works extremely well in our experiments even in loaded networks.
+In particular we show that the deterministic communication schemes we design vastly outperform the traditional stochastic multiplexing.
+
+\section{Model}\label{sec:def}
 
@@
 
-	We consider a directed graph $G=(V,A)$ modeling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $dl(u,v) \geq 1$ that we call the delay and
-	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. 
-	%Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$. Dominique voulait être plus général, on mettera cette propriété dans notre topologie
-
-      A {\bf route} $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$. 
-      We will often refer to the first element of the route as a source and the last as a target.
-
-      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
+\todo{simplifier car les chemins sont toujours donnés dans l'article -> du coup le problème c'est un graphe + l'ensemble de routes
++ remplacer partout affectation par assignment -> simplifier au max et uniformiser les notations}
+
+The network is modeled as a directed graph $G=(V,A)$.
+Each arc  $(u,v)$ in $A$ is labeled by an integer $dl(u,v) \geq 1$ that we call the delay and which represents the time slots taken by a signal to go from $u$ to $v$ using this arc.
+A {\bf route} $r$ in $G$ is a path, that is sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
+The {\bf latency} of a vertex $u_i$ in a path $r$, with $i \geq 1$, is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} dl(a_j)$.
+We also define $\lambda(u_0,r)=0$.
 The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
@@
 
-\section{Solving PRA}
+\section{Hardness of PRA}
   \label{sec:complexity}
-  \subsection{NP-Hardness}
 
@@
 
-\section{The Star Topology}
-
-      In this paper, we consider graphs with a very simple topology that we call the {\bf star topology}. 
+\section{The star topology: no waiting time} \label{sec:PAZL}
+
+    \subsection{The star topology}
+
+      From now on, we will only consider graphs with a very simple topology that we call the {\bf star topology}. 
       First, for each arc $(u,v)$, there is also an arc $(v,u)$ with the same weight.
@@
 
-  \subsection{Solving PALL without waiting times}
+  \subsection{Algorithms for PAZL}
 
@@
 
-   \subsection{Allowing waiting times}
-
-	  We just found solution to solve an easier version of PALL, in which there is no waiting times, that seems impossible to  solve when the period is too short.
+   \section{The star topology: minimizing latency}\label{sec:PALL}
+
+	  We just found solution to solve a restricted version of PALL, in which no waiting times are allowed, 
+	  and the problem has no solution when the period is too short.
 We propose to allow some message to wait in the target vertices (BBU), with the aim of giving an higher degree of freedom for the scheduling.
@@
 
-\section{Conclusion}
-test
+ Ouvertures -> les autres topologies (arbres, cycles) +
+ découper les messages pour rendre ça plus simple
 

### 2017-05-30 code/Sources/PALL.c
openmp + article suite

@@ -385,7 +385,7 @@ int longest_etoile_periodique(Graphe g,int taille_paquets,int periode, int Tmax,
 		if(w_i[i]+2*routes[i] > Tmax)
 		{
 			/*affiche_matrice(g);
-			affiche_solution(g,taille_paquets,m_i, w_i);
+			
 
 			printf("Tmax depassé (%d = %d + %d + %d)\n\n",w_i[i]+2*routes[i]+taille_paquets,w_i[i],2*routes[i],taille_paquets);*/
 			return -1;
@@ -393,7 +393,9 @@ int longest_etoile_periodique(Graphe g,int taille_paquets,int periode, int Tmax,
 		if(w_i[i]+2*routes[i] > max)
 			max= w_i[i]+2*routes[i];
 	}
-	
+	//printf("Tmax = %d \n",max);
+	//affiche_etoile(g);
+	// affiche_solution(g,taille_paquets,m_i, w_i);
 	return max;
 }
 

### 2017-05-30 code/Sources/PAZL.c

@@ -160,6 +160,16 @@ int algo_prime(Graphe g,int periode,int taille_message)
 
  /* Brute Force Rapide ----
  ------------------------*/
+void graphe_to_temps_retour(Graphe g, int * tab,int periode)
+{
+	int nbr_route = g.N / 2;
+
+	for (int i = 0; i < nbr_route; i++)
+	  {
+	    tab[i] = (2 * g.matrice[nbr_route][i + nbr_route + 1])%periode;
+	  }
+
+}
 
 
 void print_solution(int *id, int *start_slot, int *return_slot,  int size, stack *fw, stack *bw){
@@ -291,8 +301,7 @@ int search(Graphe g,int message_size, int period){
 	int route_number = g.N/2;
 	int return_time[route_number];
 
-	for(int i = 0; i < route_number; i++)return_time[i]= (2 * g.matrice[route_number][i + route_number + 1]) %period;
-
+	graphe_to_temps_retour(g,return_time,period);
 	if(DEBUG)printf("Instance aléatoire :\n");//we assume that the value in return time are in [0,period[
 	if(DEBUG)for(int i = 0; i < route_number; i++) printf("%d  ",return_time[i]);
 	int shift = return_time[0];
@@ -523,13 +532,8 @@ int bruteforceiter (Graphe g, int periode, int taille_paquets)
     }
 
   int nbr_route = g.N / 2;
-  int temps_retour_param[nbr_route];
 
-  for (int i = 0; i < nbr_route; i++)
-    {
-      temps_retour_param[i] = (2 * g.matrice[nbr_route][i + nbr_route + 1])%periode;
-    }
-
+ 
 
   int *solution_pos, *solution_num, *temps_retour, *route_restante;
   assert (solution_pos = malloc (sizeof (int) * nbr_route));
@@ -538,11 +542,12 @@ int bruteforceiter (Graphe g, int periode, int taille_paquets)
   assert (route_restante = malloc (sizeof (int) * nbr_route));
   //affiche les données sur lesquelles on lance le bruteforce
 
-  temps_retour[0] = temps_retour_param[0];
+    graphe_to_temps_retour(g,temps_retour,periode);
+
   for (int j = 1; j < nbr_route; j++)
     {
       route_restante[j] = 1;  //on pourrait juste virer la première route ?
-      temps_retour[j] = temps_retour_param[j];
+ 
 
     }
 
@@ -570,15 +575,14 @@ if(DEBUG)
 {
  printf("\n");
[…]

### 2017-05-30 code/Sources/init.c

@@ -6,7 +6,7 @@
 
 
 #include "struct.h"
-
+#include "tests.h"
 
 //Déclare une matrice remplie de 0 de taille N*N
 int ** declare_matrice(int N)

### 2017-05-30 code/Sources/main.c

@@ -13,14 +13,14 @@ int main()
 	/*****
 	Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
 	*****/
-	//simuls_periode_PAZL(12,2500,20000,100);
+	//simuls_periode_PAZL(7,2500,700,100);
 
 	/******************************************/	
 
 	/*****
 	Taux de reussite de chaque algo PAZL en fonction de la periode
 	*****/
-	echec_PAZL(8,2500,30000,1000);
+	//echec_PAZL(8,2500,30000,1000);
 
 
 	/******************************************/
@@ -39,7 +39,7 @@ int main()
 	/*****
 	Taux de reussite de chaque algo PALL sur une periode donnée (on fait varier la marge)
 	*****/
-	// sucess_PALL_fixed_period(8,2500,20000,3000,10000,30000);
+	sucess_PALL_fixed_period(8,2500,20000,3000,10000,21000);
 
 
 

### 2017-05-30 code/Sources/simulations.c

@@ -1,5 +1,6 @@
 #include <stdio.h>
 #include <stdlib.h>
+#include <omp.h>
 
 #include "struct.h"
 #include "PAZL.h"
@@ -9,6 +10,7 @@
 #include "operations.h"
 #include "tests.h"
 
+#define PARALLEL 1
 
 //Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
 void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,int nb_simuls)
@@ -18,6 +20,7 @@ void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,in
 	long long int total_3NT, total_brute,total_sl,total_search;
 	int res_sl,res_brute,res_3NT,res_search;
 
+	
 	for(int j = 1 ; j<=nb_routes;j++)
 	{
 		printf("Calculs pour %d routes: \n",j);
@@ -26,27 +29,40 @@ void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,in
 		total_brute = 0;
 		total_sl =0;
 		total_search = 0;
+		#pragma omp parallel for private(res_sl,res_brute,res_3NT,res_search,g) if (PARALLEL) schedule (dynamic)
 		for(int i = 0;i<nb_simuls;i++)
 		{
 			g = init_graphe(j*2 + 1);
 			graphe_etoile(g,taille_routes);
 			res_3NT = linear_3NT(g,taille_message);
 			//if(res_3NT > total_3NT)total_3NT = res_3NT;
-			if(res_3NT != -1){total_3NT+=res_3NT;}
+			if(res_3NT != -1){
+				#pragma omp atomic
+				total_3NT+=res_3NT;
+			}
 			//else printf("error (3nt = -1)\n");
 
 			res_brute = linear_brute(g,taille_message);
 			//if(res_brute > total_brute)total_brute = res_brute;
-			if(res_brute != -1){total_brute+=res_brute;}
+			if(res_brute != -1){
+				#pragma omp atomic
+				total_brute+=res_brute;
+			}
 			//else printf("error (brute = -1)\n");
 
 			res_sl = algo_shortest_longest(g,3*taille_message*nb_routes,taille_message);
 			//if(res_sl > total_sl)total_sl = res_sl;
-			if(res_sl != -1){total_sl+=res_sl;}
+			if(res_sl != -1){
[…]

### 2017-05-30 article/article.tex
retours graphe

@@
 \maketitle
+
 \begin{abstract}
@@
 	 \item Random: Generate $X$ random permutations for the routes and tries the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic affectation.
+In the following experiments, we take $X = 100$.
 	 \item Longest-Shortest on Routes (LSR): Send the messages from the one using longest to the one using shortest route (this is the sending order used in the previous heuristic).
@@
 
-   We look at two different regimes: one in which the period represents $1,05n\tau$, and one with a greater period $1,5n\tau$. The following results are computed over 10000 instances.
+   We look at two different regimes: first, we take a period equal to $1,05n\tau$, and then, we take a greater period, that is, $1,5n\tau$. The following results are computed over 10000 instances.
 
@@
 
-    \paragraph{Comparer les departs}
-
-    \paragraph{Comparer les retours}
+     First, we remark that, for any sending order, the success rate is strictly better for large periods.
+This is due to the fact that the size of the period is a factor for failure.
+According to our results, the two SL sending orders are not good, in any cases.
+However, the LS orders seem to increase when the flexibility is large enough, but in the two regimes, they appear to be stagnating to a lower success rate than Random.
+As we can see the random finds near to 100\% of the solutions when the period is large enough, even when we give no flexibility.
+On average, it is necessary to draw 6 randoms sending order to find a solution, when the period is large, but in some particularly hard instances, it can be impossible to find a solution, even with 100 randoms sending orders.
+Since this algorithm is not really time expensive, it could be interesting to increase the number of sending orders generated, to decrease the probability of a failure.
+
+    Insister sur l'importance de ce nombre d'instances generess, par rapport au nombre d'instances possibles
+
+    \begin{figure}
+
+       \begin{center}
+      \includegraphics[scale=0.4]{retour_21000.pdf}
+      \end{center}
+      \caption{Success rate of the different algorithms for a $P = 21000$}
+     \end{figure}
+
+     ici pas besoin de tester pour des periodes longues : gp est deja au max, MSP strictment meilleur que GP ?
 

### 2017-05-30 code/Sources/main.c

@@ -13,7 +13,7 @@ int main()
 	/*****
 	Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
 	*****/
-	simuls_periode_PAZL(7,2500,20000,100);
+	//simuls_periode_PAZL(7,2500,20000,100);
 
 	/******************************************/	
 
@@ -37,11 +37,19 @@ int main()
 	/******************************************/
 	
 	/*****
-	Taux de reussite de chaque algo PALL sur une periode donnée (on fait varier la marge)
+	Taux de reussite de départ PALL avec un retour GP sur une periode donnée (on fait varier la marge)
 	*****/
-	//sucess_PALL_fixed_period(8,2500,20000,3000,10000,21000);
+	//sucess_aller_PALL(8,2500,20000,3000,10000,21000);
 
 
+
+	/******************************************/
+
+
+	/*****
+	Taux de reussite des algos PALL avec un aller random sur une periode donnée (on fait varier la marge)
+	*****/
+	sucess_retour_PALL(8,2500,20000,3000,10000,30000);
 
 
 

### 2017-05-30 code/Sources/simulations.h

@@ -1,4 +1,5 @@
 void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,int nb_simuls);
 void echec_PAZL(int nb_routes, int taille_message,int taille_routes, int nb_simuls);
-void sucess_PALL_fixed_period(int nb_routes, int taille_paquets,int taille_route,int marge_max, int nb_simuls, int periode);
+void sucess_aller_PALL(int nb_routes, int taille_paquets,int taille_route,int marge_max, int nb_simuls, int periode);
+void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int marge_max, int nb_simuls, int periode);
 void succes_PALL_3D(int nb_routes, int taille_paquets,int taille_route, int nb_simuls, int mode);

### 2017-06-01 article/article.tex
reprise du début et simplifications

@@
 %opening
-\title{Contention Management for 5G}
+\title{How to Schedule Periodic Messages in a Network Without Congestion}
 \author{DB,CC,MG,OM,YS}
@@
 We study the sending of periodic messages in a graph following predefined paths, a problem arising from the communication between radio antennas and their signal processing units located in distant data-centers.
-The messages must be sent deterministically to minimize the latency.
+The messages must be sent deterministically to avoid collisions on the network and thus to minimize the latency.
 We prove that the problem is $\NP$-complete even for very restricted graphs.
@@
 \end{abstract}
+
+\section{Introduction}
 
@@
 
- The network topology is modeled by a directed weighted graph and a set of routes (paths) from source nodes (RRH) to target nodes (BBUs).
+ The network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs).
 The time is discretized and a unit of time corresponds to the transmission of a minimal unit of data over the network.
- The process must be periodic, that is if we look at the network at time $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the networks.
-Moreover, we want to avoid any  buffering in internal nodes of the graph, therefore the periodic process we need to design cannot collision between packets.
-To ensure that we need to propose a deterministic process.
- We have two sets of parameters that we can choose when building a periodic sending process or a \textbf{periodic assignment}, first the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
-We have two major difficulties to overcome when building an periodic assignment.
-First the periodicity which makes many scheduling methods inapplicable, since one must ensure that a message does not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.
-Second, one must minimize the latency, that is the time
- between the emission of a message and the complete return of its answer. It means that the only buffering we are allowed in the BBU
- (the waiting time before sending back the answer) must be small, in particular when the route is long.
+ The process must be periodic, that is if we look at the network at time $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
+Moreover, we want to avoid any  buffering in internal nodes of the graph.
+Hence we need to design
+ a periodic process with no collision between messages.
+To ensure that this property is always true we propose a deterministic process.
+We have two sets of parameters that we can choose when building a periodic sending process, called a \textbf{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
+When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods inapplicable.
+Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.
+Moreover the latency must be minimized, that is the time
+ between the emission of a message and the complete return of its answer.
+It means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long.
 
@@
 
-\subsection*{Article organization}
- In Sec.~\ref{sec:def} we define our model, we formalize our problems PRA (one way periodic assignment) and PALL (two ways periodic assignment) and study their basic properties.
-In Sec.~\ref{sec:complexity}, we prove that the problem PRA is $\NP$-hard and cannot be approximated even for very
-restricted graphs. In the next two sections, we study the problem PALL case on a star topology which often arises in practice.
-Since the problem is already quite complicated, we first study a variant called PAZL in Sec.\ref{sec:PAZL}, where the waiting times
-are all zero. We provide several algorithms, some of their theoretical properties and give experimental evidences that they work well
-when the network is no too loaded.
-Finally in Sec.\ref{sec:PALL}, we propose algorithms for the general problem and exhibit one which works extremely well in our experiments even in loaded networks.
-In particular we show that the deterministic communication schemes we design vastly outperform the traditional stochastic multiplexing.
-
-\section{Model}\label{sec:def}
-
-  \subsection{Definitions}
-
-\todo{simplifier car les chemins sont toujours donnés dans l'article -> du coup le problème c'est un graphe + l'ensemble de routes
-+ remplacer partout affectation par assignment -> simplifier au max et uniformiser les notations}
+ In Sec.~\ref{sec:def} we propose a model of the network and the periodic sending of messages along its routes. 
+ We then formalize our two problems of finding a periodic assignment for sending messages without collisions: PRA (sending of the message only) and PALL (sending of the message and answer).  
+In Sec.~\ref{sec:complexity}, we prove that the problem PRA and PALL are $\NP$-hard and cannot be approximated even for very
+restricted graphs. 
+Therefore in the next two sections, we study a simple but very common topology, that we call the
+star topology, on which the messages can collide on only one arc.
+In Sec.\ref{sec:PAZL}, we study a variant of PALL called PAZL  where the waiting times must all be zero.
+We provide several algorithms, some of their theoretical properties and give experimental evidences that they find periodic assignments when the network is no too loaded.
+Finally in Sec.\ref{sec:PALL}, we propose algorithms for the general PALL problem and exhibit one which works extremely well in our experiments even in loaded networks.
+In particular we show that the deterministic communication schemes we design vastly outperform the traditional stochastic multiplexing with regards to latency.
+
+\section{Model and problems}\label{sec:def}
+
+  \subsection{Network modeling}
 
@@
 The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
-
-      A {\bf routing function} $\cal R$ in $G$ associates to each pair of vertices $(u,v)$ a route from $u$ to $v$.
-Let $\cal C$ be an {\bf assignment} in $G$, i.e., a set of couples of different vertices of $G$.
-We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $(u,v)$ in $\cal C$.
-We call $\cal R_{\cal C}$ a {\bf routage graph}, it contains all the informations needed in the forthcoming problems (assignment, routes and delays of the arcs).
-
-      \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}
+We denote by $\cal R$ a set of routes in $G$ such that no two routes have the same first vertices or the same last vertices.
+The pair $(G,\cal R)$ is called a {\bf routage graph} and represents our network.
+The first vertex of a route models an antenna (RRH) and the last one a data-center (BBU) which processes the messages sent by the antenna.
+We denote by $\rho$ the bijection induced by ${\cal R}$, $\rho(s) = t$ if $s$ is the first vertex of a route $r$ and $t$ the last.
 
    \subsection{Slotted time Model}
+
+      Consider a route $r$ from $s$ to $t$. If we send a message at some point in time $m$ from $s$,
+      then it will arrive at the vertex $v$ in $r$ at time $m + \lambda(v,r)$.
 Consider now a positive integer $P$ called the {\bf period}.
 In our problem, we send messages in the network with period $P$.
-The time will thus be cut into slices of $P$ discrete slots.
-Assume we send a message at the source $s_i$ of the route $r_{s_i}$, at the time slot $m_{s_i}$ in the first period, then a message will be sent at time slot $m_{s_i}$ at each new period.
-We define the first time slot at which the message reaches a vertex $v$ in this route by $t(v,r_{s_i}) = m_{s_i} + \lambda(v,r) \mod P$.
+The time will thus be cut into slices of $P$ discrete slots and we need to consider only one of such slices since they will all be identical.
+       Hence we define the first time slot at which a message sent from $s$ will reach a vertex $v$ in $r$ by $t(v,r) = m + \lambda(v,r) \mod P$.
 
       A message usually cannot be transported in a single time slot. We denote by $\tau$ the number 
-      of consecutive slots necessary to transmit a message.
-Let us call $[t(v,r_{s_i})]_{P,\tau}$ the set of time slots used by $r_{s_i}$ at a vertex $v$ in a period $P$, that is $[t(v,r_{s_i})]_{P,\tau} = \{t(v,r_{s_i}) + k \mod P \mid 0 \leq k < \tau \}$.
-Usually $P$ and $\tau$ will be clear from the context and we will denote $[t(v,r_{s_i})]_{P,\tau}$ by $[t(v,r_{s_i})]$.
-
-      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R_{\cal C}$ is a sequence  ${\cal M}=(m_{s_0}, \ldots ,m_{s_{n-1}})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R_{\cal C}$.
-The number $m_{s_i}$ represents the index of the first slot used in a period  by the route $r_{s_i} \in \cal R_{\cal C}$ at its source $s_i$.
-      A $(P,\tau)$-periodic affectation must have no {\bf collision} between two routes in $\cal R_{\cal C}$, that is $\forall (r_{s_i}, r_{s_j}) \in {\cal R_{\cal C}}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
-      we have $$[t(u,r_{s_i})] \cap [t(u,r_{s_j})] = \emptyset .$$
-
-%       Notice that the notion of $P$-periodic affectation \textbf{is not monotone} with regard to $P$. 
-      As an example of a $(2,1)$-periodic affectation, let consider a routage graph with routes $\{r_{s_i}\}_{i=0,\dots,n-1}$, such that all pairs of routes intersect at a different edge.
-      We set $\tau = 1$ and the delays are chosen so that if $r_{s_i}$ and $r_{s_j}$ have $v$ as first common vertex then we have $\lambda(v,r_{s_i}) - \lambda(v,r_{s_j})=1$.There is a $(2,1)$-periodic affectation by setting all $m_{s_i}$ to $0$.
+      of \emph{consecutive slots} necessary to transmit a message.
+Let us call $[t(v,r)]_{P,\tau}$ the set of time slots used by $r$ at a vertex $v$ in a period $P$, that is $[t(v,r)]_{P,\tau} = \{t(v,r) + k \mod P \mid 0 \leq k < \tau \}$.
+Usually $P$ and $\tau$ will be clear from the context and we will denote $[t(v,r)]_{P,\tau}$ by $[t(v,r)]$.
+
+      A {\bf $(P,\tau)$-periodic assignment} of a routage graph $(G,\cal R)$ is a sequence  ${\cal M}=(m_1, \ldots ,m_n)$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
+We will always consider that the $m_{i}$ are between $O$ and $P-1$.
+A $(P,\tau)$-periodic assignment must have no {\bf collision} between two routes in $\cal R$, that is $\forall (r_{i}, r_{j}) \in {\cal R}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
+      we have $$[t(u,r_{i})] \cap [t(u,r_{j})] = \emptyset .$$
+
+%       Notice that the notion of $P$-periodic assignment \textbf{is not monotone} with regard to $P$. 
+      As an example of a $(2,1)$-periodic assignment, let consider a routage graph with routes $\{r_{i}\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
+      We set $\tau = 1$ and the delays are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.
 
@@
 %       
-%       A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.
+%       A labeling $F$ of such a graph is an assignment of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.
 
       \begin{figure}[ht]
-       \begin{center}
+      % \begin{center}
 
@@
   \SetGraphUnit{5}
-  \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
-  \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
-  \node[draw,circle] (s1) at (0, 6) {$s_0$};
-
-  \node[draw,circle] (t3) at (14, 7) {$t_2$}; 
-  \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
-  \node[draw,circle] (t1) at (10, 2) {$t_0$};
+  \node[draw,circle] (s3) at (4, 2) {$s_3$}; 
+  \node[draw,circle] (s2) at (0, 4) {$s_2$}; 
+  \node[draw,circle] (s1) at (0, 6) {$s_1$};
+
+  \node[draw,circle] (t3) at (14, 7) {$t_3$}; 
+  \node[draw,circle] (t2) at (14, 4) {$t_2$}; 
+  \node[draw,circle] (t1) at (10, 2) {$t_1$};
 
@@
 \end{tikzpicture}
-      \end{center}
-       \caption{A routage graph with $(0,0,0)$ as a $(2,1)$-periodic affectation}
+     % \end{center}
+       \caption{A routage graph with $(0,0,0)$ as a $(2,1)$-periodic assignment}
       \end{figure}
@@
 
-    We want to ensure that there is an affectation which allows to send periodic messages from sources to target
-    without collisions. The problem we need to solve is thus the following:
+    We want to find an assignment which allows to send periodic messages from sources to targets
+    without collisions. We introduce the following associated decision problem, useful for hardness proofs.
 
@@
 
-      \noindent {\bf Input:} a routage graph $\cal R_{\cal C}$, an integer $\tau$ and an integer $P$.
-
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R_{\cal C}$ ?
+      \noindent {\bf Input:} a routage graph $(G,\cal R)$, an integer $\tau$ and an integer $P$.
+
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment of $(G,\cal R)$ ?
 
       We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
-      Even approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic affectation is hard.
-
-      An unusual property of affectation is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
-      $(P',\tau)$-periodic affectation with $P' > P$: the existence of an affectation is not monotone with regards to $P$.
+      Even approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic assignment is hard.
+
+      An unusual property of assignment is that given a routage graph, we may have a $(P,\tau)$-periodic assignment but no
+      $(P',\tau)$-periodic assignment with $P' > P$: the existence of an assignment is not monotone with regards to $P$.
 
 	\begin{lemma} \label{lemma:monotonic}
-	 For any odd $P$, there is a routage graph such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
+	 For any odd $P$, there is a routage graph such that there is $(2,1)$-periodic assignment but no $(P,1)$-periodic assignment.
 	\end{lemma}
@@
 
-      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
+      Consider the routage graph $(G,{\cal R})$ given in the previous subsection. 
       We change the delays so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
       we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$.
-In such a graph, there is no $(P,\tau)$-periodic affectation, since the problem reduces to finding a $P$-coloring in a complete graph with $n > P$ vertices.\\
-      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R_{\cal C}}$.
+In such a graph, there is no $(P,\tau)$-periodic assignment, since the problem reduces to finding a $P$-coloring in a complete graph with $n > P$ vertices.\\
+      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic assignment of ${\cal R}$.
 
@@
 
-      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
-      and two disjoint subsets of vertices $S$ and $T$ of equal cardinality, where $S$ is the set of RRHs and $T$ is the set of BBUs. 
-      A \textbf{symmetric} assignment ${\cal C}$, is an involutive function from $S$ to $T$, which maps each element $s\in S$ to ${\cal C}(s)$ and ${\cal C}(s)$ to $s$.
-It can also be seen as the set of pairs $(s,{\cal C}(s))$ and $({\cal C}(s),s)$.\\
-      The routing function ${\cal R}$ associates to each couple $(s,{\cal C}(s))$ a route called $r_s$ and to each couples $({\cal C}(s),s)$ a route called $r_{{\cal C}(s)}$.\\     
-       We are given a period $P$, a routing function ${\cal R}$, and we consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_s$ to the route $r_s$ which begins by $s$, and $m_{{\cal C}(s)}$ to the routes $r_{{\cal C}(s)}$ which begins by ${\cal C}(s)$.
-This affectation represents the following process: first a message is sent at $s$, through the route $r_s$, at time $m_s$.
+      In the context of cloud-RAN applications, we need to send message from a RRH $s$ to a BBUs $\rho(s)$ and then 
+      we must send the answer from $\rho(s)$ back to $s$. We say that a routage graph $(G, {\cal R})$ is \textbf{symmetric}
+      if for all route $r$ with first vertex $s$ and last vertex $target(s)$ there is a route $r'$ with first vertex $target(s)$
+      and last vertex $s$.
+In all practical cases the routes $r$ and $r'$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we will not enforce this property.
+      If the first vertex of $r$ is $s$, we will denote by $\rho(r)$ the route whose first vertex is $\rho(s)$.
+
+         We now give a new interpretation of a $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routing graph, so that it represents the sending of a message and of its answer.
+	This assignment represents the following process: first a message is sent at $s$, through the route $r$, at time $m$.
 
@@
 Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$.
-Let consider a $P$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to
+Let consider a $P$-periodic assignment of ${\cal C}_{\rho}$ which associates $m_l$ to
 %       $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.
@@
 
-      This message is received by ${\cal C}(s)$ at time $t({\cal C}(s),r_s)$.
-It is then sent back to $s$ in the same period at time $m_{{\cal C}(s)}$ if $m_{{\cal C}(s)} > t({\cal C}(s),r_s)$, otherwise at time $m_{{\cal C}(s)}$ in the next period.
-The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_s = m_{{\cal C}(s)} - t({\cal C}(s),r_s)$ if $m_{{\cal C}(s)} > t({\cal C}(s),r_s)$ and $w_s = m_{{\cal C}(s)} + P - t({\cal C}(s),r_s)$ otherwise.
+      This message is received by $\rho(s)$ at time $t(\rho(s),r)$.
+It is then sent back to $s$ on the route $\rho(r)$ in the same period at time $m_{\rho(s)}$ if $m_{\rho(s)} > t(\rho(s),r)$, otherwise at time $m_{\rho(s)}$ in the next period.
+The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_s = m_{\rho(s)} - t(\rho(s),r)$ if $m_{\rho(s)} > t(\rho(s),r)$ and $w_s = m_{\rho(s)} + P - t(\rho(s),r)$ otherwise.
 
@@
 
-      Thus, the whole process time for a message sent at vertex $s$ is equal to
+      Thus, the whole process time for a message sent at vertex $s$ on the route $r$ is equal to
       $$
-      PT(s)=\lambda(r_s)+ w_s+\lambda(r_{{\cal C}(s)}).
+      PT(s)=\lambda(r)+ w_s+\lambda(r).
       $$
@@
 
-    The {\bf maximum process time} of the $(P,\tau)$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{s \in S} PT(s)$. The problem we want to solve is the following.
-
-      \noindent {\bf Periodic Assignment for Low Latency(PALL)}
-
-      \noindent {\bf Input:}  A routage graph ${\cal R}_{\cal C}$ with ${\cal C}$ a symmetric assignment, a period $P$, an integer $\tau$, an integer $T_{max}$.
-
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation ${\cal M}$ of ${\cal R}_{\cal C}$ such that $MT({\cal M}) \leq T_{max}$?
-
-      \todo{Si on veut, on peut parler du temps moyen aussi ici, seulement si on fait quelque chose dessus dans la suite}
-      %The related optimisation problem we will focus on  consists in minimizing  $MT({\cal M})$.
-Note that in the context of cloud-RAN networks, we consider $P=1ms$, $\theta=2.6ms$ and $T_{max}$ must be less or equal to $3ms$.
-      %cette remarque doit être dans la partie expérimentale
-
-  In this article, we works on a given routage, but we could imagine a problem, in which, considering a given graph $G = (V,A)$ and a period P, the question is to find, if it exists, a routage graph ${\cal R}_{\cal C}$, in which there is $(P,\tau)$-periodic affectation.
-
-  \todo{Dire si on regle le probleme de trouver un bon routage dans un cas particulier après}
+    The {\bf maximum process time} of the $(P,\tau)$-periodic assignment ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{s \in S} PT(s)$. We consider the following decision problem.
+
+      \noindent {\bf Periodic Assignment for Low Latency (PALL)}
+
+      \noindent {\bf Input:}  A symmetric routage graph $(G,{\cal R})$, a period $P$, an integer $\tau$, an integer $T_{max}$.
+
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment ${\cal M}$ of $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
+
+      As a consequence of the $\NP$-hardness of PRA, we show in the next subsection that this problem is $\NP$-hard. 
+      In Sec.~\ref{sec:PALL} we will study heuristics which try to solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity.
 
@@
 
- In this section we assume that the size of a message $\tau$ is equal to one. 
- We will prove the hardness of PRA and PALL for this parameter, which implies the hardness of the general problems. 
-Consider an instance of the problem PRA, i.e., a routage graph $\cal{R_{\cal C}}$ and a period $P$. \\
+ In this section we always assume that the size of a message $\tau$ is equal to one. 
+ We will prove the hardness of PRA and PALL for $\tau =1$ which implies the hardness of the general problems. 
+Consider an instance of the problem PRA, i.e., a routage graph $(G,\cal{R})$ and a period $P$.
 The {\bf conflict depth} of a route is the number of other routes which share an edge with it. 
-The conflict depth of a routage graph  $\cal{R_{\cal C}}$ is the maximum of the conflict depth of the routes in $\cal{R_{\cal C}}$.\\
+The conflict depth of a routage graph $(G,\cal{R})$ is the maximum of the conflict depth of the routes in $\cal{R}$.
 The {\bf load} of a routage graph is the maximal number of routes sharing the same arc.
-It is clear that a $(P,1)$-periodic affectation must satisfy that $P$ is larger or equal to the load.
+Remark that a $(P,1)$-periodic assignment must satisfy that $P$ is larger or equal to the load.
 
@@
  \begin{proof}
- The problem $PRA$ is in $\NP$ since given an offset for each route in an affectation, it is easy to check in linear time in the number of edges whether there are collisions.
+ The problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of edges whether there are collisions.
 
@@
 Set an arbitrary orientation of the edge $(u,v)$, such that the following route is directed from $u$ to $v$.
-
 %   The set $A$ of arcs of $G$ is: 
@@
   For each edge $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.  
-  All these arcs are of weight $0$. 
-  The set of arcs of G is the union between all the arcs of the previous routes.
-  The affectation ${\cal C}$ is the set of pair of vertices $(s_{u,v}, t_{u,v})$.
-
-  Observe that the existence of a $d$-coloring of $H$ is equivalent to the existence of a $(d,1)$-periodic affectation
-  of ${\cal R}_{\cal C}$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its edges by the integers
-  in $\{0,\dots,d-1\}$ and we have a bijection between $d$-colorings of $H$ and offsets of the routes of ${\cal R}_{\cal C}$.
-  By construction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent edges have
-  the same color. Therefore we have reduced edge coloring to PRA which concludes the proof. 
+  All these arcs are of weight $0$. The set of arcs of G is the union between all the arcs of the previous routes.
+
+  Observe that the existence of a $d$-coloring of $H$ is equivalent to the existence of a $(d,1)$-periodic assignment
+  of $(G,{\cal R})$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its edges by the integers
+  in $\{0,\dots,d-1\}$ and we have a bijection between $d$-colorings of $H$ and offsets of the routes of ${\cal R}$.
+  By construction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent edges have the same color.
+Therefore we have reduced edge coloring to PRA which concludes the proof.
  \end{proof}
- \todo{Faire un dessin d'illustration ?}
 
@@
 \begin{proof}
- We consider $({\cal R}_{\cal C},P,\tau)$ an instance of $PRA$.
-We assume that no vertex appears both in the first and second position in a pair of ${\cal C}$.
-Remark that this condition is satisfied in the previous proof, which makes the problem $PRA$ restricted to this kind of instances $\NP$-complete.
+ We consider $((G,{\cal R}),P,\tau)$ an instance of $PRA$.
+We assume that no vertex is the first of some route and the last of another one.
+Remark that this condition is satisfied in the previous proof, which makes the problem $PRA$ restricted to this kind of instance $\NP$-complete.
  Let us define $T_{max} = 2 \times \max_{r \in {\cal R}} \lambda(r) + P$.
-We consider ${\cal C}'$ and ${\cal R}'_{\cal C'}$ symmetrized versions of ${\cal C}$ and  ${\cal R}_{\cal C}$ where for every route there is a symmetric route with new arcs and the same weights.
- The instance $({\cal R'}_{\cal C'},P,\tau,T_{max})$ is in PALL if and only if $({\cal R}_{\cal C},P,\tau)	$
- is in $PRA$.
+We define $(G',{\cal R}')$ a symmetric routage graph from $(G,{\cal R})$ where for every route we add a symmetric route with new arcs of opposite orientation and the same weights.
+ The instance $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL if and only if $((G,{\cal R}),P,\tau)$ is in $PRA$.
 Indeed the waiting time of each route is by definition less than $P$ and thus the maximal process time is always less than $T_{max}$.
-Moreover a $(P,\tau)$-affectation of ${\cal R}_{\cal C}$ can be extended into a $(P,\tau)$-affectation of ${\cal R'}_{\cal C'}$ in the following way.
-For each route $r_{u,v}$, the time at which the message arrives is $t(v,r_{u,v})$, then we choose as offset for $r_{v,u}$, $-t(v,r_{u,v}) \mod P$.
-The symmetry ensures that each new route $r_{v,u}$ in ${\cal R'}_{\cal C'}$ uses the same times slot as $r_{u,v}$ and thus avoid collisions.
+Moreover a $(P,\tau)$-assignment of $(G,{\cal R})$ can be extended into a $(P,\tau)$-assignment of $(G',{\cal R'})$ in the following way.
+For each route $r \in \cal{R}$ starting at $s$, the time at which the message arrives is $t(\rho(s),r)$, then we choose as offset for $\rho(r) \in \cal{R}'$ $-t(\rho(s),r) \mod P$.
+The symmetry ensures that each new route $\rho(r)$ in ${\cal R'}$ uses the same times slot as $r$ one each of its node and thus avoid collisions.
 \end{proof}
 
-Let MIN-PRA be the problem, given a routage graph and an assignment, to find the minimal period $P$ such that there is a $P$-periodic affectation.
-
-\begin{theorem}
+Let MIN-PRA be the problem, given a routage graph and an assignment, to find the minimal period $P$ such that there is a $P$-periodic assignment.
+
+\begin{theorem}\label{th:inapprox}
  The problem MIN-PRA cannot be approximated in polynomial time within a factor $n^{1-o(1)}$, with $n$ the number of routes, unless $\P = \NP$ even when the load is two.
@@
  We define ${\cal R}$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
- Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an edge in $H$; this arc is the only one shared by these two routes.   
- All arcs are of delay $0$.
-
- Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic affectation in $G$, 
+ Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an edge in $H$; this arc is the only one shared by these two routes. All arcs are of delay $0$.
+
+ Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic assignment in $G$, 
  by converting an offset of a route into a color of a vertex and reciprocally.
@@
 
-In particular, this reduction shows that even with small maximal load, the 
-minimal period can be large.
+In particular, this reduction shows that even with small maximal load, the minimal period can be large.
+
+    \begin{figure}[ht]
 
     \scalebox{0.5}{
-
     \begin{tikzpicture}
-
     \tikzset{
@@
     \node (1) at (-3,4){\Huge $\rightarrow$};
-
-    \node (2) at (-7,0){\Huge H};
-    \node (3) at (10,0){\Huge G};
+%     
+%     \node (2) at (-7,0){\Huge H};
+%     \node (3) at (10,0){\Huge G};
     \end{tikzpicture}
-
     }
-
-%     
-%   \subsection{Tractable cases of PRA}
-%     
-%     In this section, we present a few polynomial cases, in particular when the conflict depth is one.
-%     When the conflict depth is one, every route can share an arc with only a single other route. 
-%     Therefore 
-%     
-%     
-%     The problem PALL seems to be hard to solve, even for very simple classes of graphs, as seen in the next section.
+    \caption{Reduction from k-coloring to MIN-PRA}
+
+    \end{figure}
 
@@
       First, for each arc $(u,v)$, there is also an arc $(v,u)$ with the same weight.
-      Moreover, there is a special arc, the central arc, which is shared by all routes.
-      All routes consist from an arc from its source to the central source node, denoted by {\bf $c_s$},
-      then the central arc to {\bf $c_t$}, the central target node, and an arc to its target.
-In addition to those central nodes, there are two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$, of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$.
-      The routes are the directed paths of the form $s_i,c_s,c_t,t_i$ and $t_i,c_t,c_s,s_i$.
+      There are two sets of vertices, $S=\{s_1,...,s_n\}$ and $T=\{t_1,...,t_n\}$ of cardinality $n$ and two special nodes
+      the central source node {\bf $c_s$} and the central target node {\bf $c_t$}.
+There is an arc between {\bf $c_s$} and {\bf $c_t$} shared by all routes.
+For all $i$, there is an arc between $s_i$ and $c_s$ and between $t_i$ and $c_t$.
+      The routes are the directed paths $r_i = s_i,c_s,c_t,t_i$ and $\rho(r_i) = t_i,c_t,c_s,s_i$ and we have thus defined a 
+      symmetric routage graph.
 
@@
 
-      We assume the weight of the central arc to be $0$ since it appears in every route,
-      its value does not matter when considering affectations.\\
+      Since the central arc appears in every route, its value does not matter when considering assignments.
+      We assume the weight of the central arc to be $0$ \\
       Collisions between messages can only appear at node $c_s$ on the way forward and at node $c_t$ on the way back.
-      Thus, we only have to check if there is no collisions in a period at those two points.
-      We consider two periods P at these vertices, the the {\bf forward period} at $c_s$, and the {\bf backward period} at $c_t$.
-A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1}) \mod P$ in the forward period, and  $c_t$ at time $m_{t_1} + t(c_t,r_{t_1})\mod P$ in the backward period.
-
-      A $(P,\tau)$-periodic affectation is the choice for all $i < n$, of $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$, we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$.
-
-  \subsection{Algorithms for PAZL}
+      Thus, we only have to check if there is no collisions in a given period at those two vertices.
+      We will refer to the period at $c_s$ as the {\bf forward period}, and the period at $c_t$ as the {\bf backward period}.
+A message issued on the route $r$ at time $m_r$ will reach $c_s$ at time $m_{r} + t(c_s,r) \mod P$ in the forward period.
+If the offset of $\rho(r)$ is $m_\rho(r)$, the answer will reach $c_t$ at time $m_{\rho(r)} + t(c_t,\rho(r))\mod P$ in the backward period.
+
+      A $(P,\tau)$-periodic assignment is the choice for all $i < n$, of $m_{r_i}$ and $m_{\rho(r_i)}$ such that, for any couple $(i\neq j)$, we have $[t(c_s,r_{i})] \cap [t(c_s,r_{j})] = \emptyset$ and $[t(c_t,\rho(r_i))] \cap [t(c_t,\rho(r_j))] = \emptyset$.
+
+  \subsection{Solving PAZL}
 
   In this subsection, we deal with a simpler version of the problem PALL.
-  We ask for a $(P,\tau)$-periodic affectation {\bf with all waiting times equal to $0$} and we call this restricted problem {\bf Periodic Assignment for Zero Latency} or PAZL. 
+  We ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$} and we call this restricted problem {\bf Periodic Assignment for Zero Latency} or PAZL. 
   In that case $MT({\cal M})$ is equal to twice the delay of the longest route, thus $T_{max}$ is not relevant anymore. 
   Since $w_i=0$, choosing $m_i$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i) \mod P$.
-  Remark that there is a bijection between the affectation of a star topology and the 
-  the affectation of the same star topology where all arcs from $s_i$ to $c_s$ have weight equal to $0$
+  Remark that there is a bijection between the assignment of a star topology and the 
+  the assignment of the same star topology where all arcs from $s_i$ to $c_s$ have weight equal to $0$
   by changing $m_i$ into $m_i - t(c_s,r_i) \mod P$. Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
@@
 
-    We propose a greedy algorithm to build a $(P,\tau)$-periodic affectation, which provably works when
+    We propose a greedy algorithm to build a $(P,\tau)$-periodic assignment, which provably works when
     the period is large enough with regards to the number of routes and size of messages. In other words, 
@@
 The choice of an offset also fixes the position of the message in the backward period, chose the first one which does not create a collision.
-We now prove that this algorithm always finds a $(P,\tau)$-periodic affectation without waiting time when $P \geq 3n\tau$.
+We now prove that this algorithm always finds a $(P,\tau)$-periodic assignment without waiting time when $P \geq 3n\tau$.
 
@@
 Therefore  amongst the possible $3n - k$ positions, there are  at least $3n - k -2k$ which are without collision.
-Since $k < n$, $3n - k -2k \geq 1$, which proves that the algorithm terminates and find a  $(P,\tau)$-periodic affectation.
+Since $k < n$, $3n - k -2k \geq 1$, which proves that the algorithm terminates and find a  $(P,\tau)$-periodic assignment.
 
@@
 % 	\begin{algorithm}[H]
-% 	\caption{Greedy affectation}
+% 	\caption{Greedy assignment}
 % 	\begin{algorithmic}
 % 	\REQUIRE ${\cal R}_{\cal C}$, period $P$
-% 	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
+% 	\ENSURE A P-periodic assignment in p $\leq P$, or FAILURE
 % 	\STATE $T$ a table of the macro slots of size $\tau$ in the forward period.
@@
 % 	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
-% 	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
+% 	\ENSURE $(P,\tau)$-periodic assignment of ${\cal R}_{\cal C}$
 % 	\STATE Forward-budget $\leftarrow$ $P$ - n * $\tau$
@@
 % 	    
-      We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found a $(P,\tau)$-periodic affectation.
+      We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found a $(P,\tau)$-periodic assignment.
 Contrarily to the two previous algorithms, when it fails to find a solution, then it certifies there are no solution to PAZL.
@@
       the load is low, the greedy algorithm always returns a solution). To do that we try to evaluate the 
-      minimal period for which a $(P,\tau)$ periodic affectation can be found by each algorithm. 
+      minimal period for which a $(P,\tau)$ periodic assignment can be found by each algorithm. 
       To that end we do a linear search on $P$, since a dichotomy would not work because of Lemma~\ref{lemma:monotonic}.
@@
       larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small periods, we see that there are very few instances
-      with a solution for PAZL. It means that with long routes and high load, looking for an affectation without waiting may be too restrictive.
+      with a solution for PAZL. It means that with long routes and high load, looking for an assignment without waiting may be too restrictive.
       That is why we present algorithms for the general PALL problem in our next section. We will test them on $8$ long routes and a period between 
-      $20000$ and $30000$ where, as we have shown here, there are often no easy to compute affectation without waiting time.
+      $20000$ and $30000$ where, as we have shown here, there are often no easy to compute assignment without waiting time.
 
@@
     \REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, $ T_{max}$, packet size $\tau$
-    \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$
+    \ENSURE $(P-\tau)-$periodic assignment of ${\cal R_{\cal C}}$
     \STATE $clock \leftarrow 0$
@@
 	\begin{enumerate}
-	 \item Random: Generate $X$ random permutations for the routes and tries the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic affectation.
+	 \item Random: Generate $X$ random permutations for the routes and tries the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic assignment.
 In the following experiments, we take $X = 100$.
@@
 	 \item Shortest-Longest on last Arc (SLA): Send the messages from the one having the shortest arc between $c_t$ an the target to the one having the longest one.
-This sending order gives us some $(P,\tau)$ periodic affectation in which all the $w_i = 0$, but needs a huge period if the difference between the longest and the shortest route is large (see proposition \ref{prop:SL}).
+This sending order gives us some $(P,\tau)$ periodic assignment in which all the $w_i = 0$, but needs a huge period if the difference between the longest and the shortest route is large (see proposition \ref{prop:SL}).
 	\end{enumerate}
@@
 
-     If it exists a solution that satisfies the criteria $MT({\cal M}) < T_{max}$, this algorithm gives us a $(P,\tau)$ periodic affectation.
-Nevertheless, by setting the deadlines according to the size of the route only, the given $(P,\tau)$ periodic affectation might not respect the period $P$.
+     If it exists a solution that satisfies the criteria $MT({\cal M}) < T_{max}$, this algorithm gives us a $(P,\tau)$ periodic assignment.
+Nevertheless, by setting the deadlines according to the size of the route only, the given $(P,\tau)$ periodic assignment might not respect the period $P$.
 
@@
     \REQUIRE A routage graph ${\cal R_{\cal C}}$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
-    \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, if it exists
+    \ENSURE $(P-\tau)-$periodic assignment of ${\cal R_{\cal C}}$, if it exists
 
@@
 
-    \STATE return the best $(P-\tau)-$periodic affectation, or FAILURE
+    \STATE return the best $(P-\tau)-$periodic assignment, or FAILURE
 
@@
 
-     The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic affectation, even with a small period, and T$_{max}$.
+     The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic assignment, even with a small period, and T$_{max}$.
 
@@
 
- Ouvertures -> les autres topologies (arbres, cycles) +
- découper les messages pour rendre ça plus simple
+    \paragraph*{Future works}
+
+   \begin{itemize}
+    \item FPT algorithms for PAZL and PALL 
+    \item average latency instead of maximal latency
+    \item trees
+    \item cycles 
+    \item preemption (messages can be cut into pieces)
+    \item routes are not given and can be chosen
+   \end{itemize}
 

### 2017-06-01 code/Sources/main.c

@@ -39,7 +39,7 @@ int main()
 	/*****
 	Taux de reussite de départ PALL avec un retour GP sur une periode donnée (on fait varier la marge)
 	*****/
-	sucess_aller_PALL(8,2500,20000,3000,1000,21000);
+	sucess_aller_PALL(8,2500,20000,3000,2000,21000);
 
 
 

### 2017-06-01 code/Sources/simulations.c

@@ -10,7 +10,7 @@
 #include "operations.h"
 #include "tests.h"
 
-#define PARALLEL 1
+#define PARALLEL 0
 
 //Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
 void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,int nb_simuls)

### 2017-06-01 article/article.tex
code stochastique et article

--- 2017-05-30 article/article.tex
@@
 
+         We compared the two algorithms on 10000 graphs on which the weight of the links are drawn uniformly between 0 and 20000, with a period of 21000, and giving, for each instance $T_{max} = 2\lambda(r_{longest-route})$ .
+We then look at the success rate of each algorithms, with every sending order.
+Both algorithms reach the higher success rate with the Random sending order, but the success of Greedy is 5,65 \%, while the success rate of Greedy Periodic is to 30,02 \%.
+
      \subsubsection{Near from scheduling problems}
@@
     To compare the previous algorithms, we first need to determine which of the sending order is the best.
-We know that Greedy Periodic is strictly better than Greedy, because it finds at least all the solutions given by Greedy.
-We compared the two algorithms on 10000 graphs on which the weight of the links are drawn uniformly between 0 and 20000, with a period of 21000, and giving, for each instance $T_{max} = 2\lambda(r_{longest-route})$ .
-We then look at the success rate of each algorithms, with every sending order.
-Both algorithms reach the higher success rate with the Random sending order, but the success of Greedy is 5,65 \%, while the success rate of Greedy Periodic is to 30,02 \%.
-    Those results confirms that Greedy Periodic is better than Greedy, this is the reason why we will compare the different sending orders with Greedy Periodic.
+We know that Greedy Periodic is strictly better than Greedy, thus, we will compare the different sending orders with Greedy Periodic.
 
    In this experiment, we fix the number of routes to 8.
-We want to compare the sending orders with the worst parameters, so we draw the links between 0 and 20000 slots (long routes).
+We want to compare the sending orders with the worst parameters, so we draw the links between 0 and 20000 slots.
 We look at the success rate of each sending order with Greedy Periodic to schedule the messages in the way back.
@@
       \end{center}
-      \caption{Success rate for $P = 21000$}
+      \caption{Success rate of the sending orders for $P = 21000$}
      \end{figure}
@@
       \end{center}
-      \caption{Success rate for a $P = 30000$}
+      \caption{Success rate of the sending orders for a $P = 30000$}
      \end{figure}
@@
 On average, it is necessary to draw 6 randoms sending order to find a solution, when the period is large, but in some particularly hard instances, it can be impossible to find a solution, even with 100 randoms sending orders.
-Since this algorithm is not really time expensive, it could be interesting to increase the number of sending orders generated, to decrease the probability of a failure.
-
-    Insister sur l'importance de ce nombre d'instances generess, par rapport au nombre d'instances possibles
+
+     To observe  the impact of the number of random sending orders drawn, we compared the success rate of the following number of drawing, on graphs in which the links are drawn  between $0$ and $20000$ slots, with a period $P=20000$, and a flexibility of $0$.
+       \begin{figure}
+
+       \begin{center}
+   \begin{tabular}{|c|c|c|c|c|c|}
+    \hline
+    number of randoms & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
+    \hline
+    Success rate $(\simeq)$ & $60,5$&$77,7$&$80,5$&$80,5$&$80,5$\\
+    \hline
+      \end{tabular}
+      \end{center}
+   \caption{Impact of the number of randoms sending orders drawn}
+     \end{figure}
+
+     In our case of 8 routes, the number of different sending orders is $8!
+\simeq 40 000$.
+By drawing $1000$ random sending orders, we explore near to $2,5 \%$ of the cases, which seems enough to find as many solutions as if generate more random sending oredres.
+
+     We now want to compare the performances of the different algorithms.Since GP showed some excellent results on large periods (see Figure 5), it is more interesting to focus on the behavior of the algorithms on short periods.
+The following experience is realized on graph with 8 routes (links between $0$ and $20000$), and with a period of 21000.
+Since we just conclude that drawing 1000 sending order is a good number, with 8 routes.
+We now generate 1000 randoms sending orders for the first way.
 
@@
 
-     ici pas besoin de tester pour des periodes longues : gp est deja au max, MSP strictment meilleur que GP ?
-
     \paragraph{Comparer optimal + depart random avec stochastique}

### 2017-06-01 code/Sources/PALL.h

@@ -1,2 +1,5 @@
 int longest_etoile_2(Graphe g,int taille_paquets,int periode, int Tmax,int mode);
 int longest_etoile_periodique(Graphe g,int taille_paquets,int periode, int Tmax,int mode);
+int stochastic(Graphe g, int taille_paquets, int periode, int tmax);
+int linear_simons_per(Graphe g,int periode,int taille_message,int nb_rand);
+int linear_stochastic(Graphe g,int periode,int taille_message);

### 2017-06-01 code/Sources/main.c

@@ -49,18 +49,23 @@ int main()
 	/*****
 	Taux de reussite des algos PALL avec un aller random sur une periode donnée (on fait varier la marge)
 	*****/
-	sucess_retour_PALL(8,2500,20000,3000,10000,20000);
+
+	sucess_retour_PALL(8,2500,20000,3000,1000,21000);
 
 
 	/******************************************/
 
 	/*****
-	//Taux de reussite des différentes tailles PALL avec un aller random sur une periode donnée (on fait varier la marge)
+	//Taux de reussite des diferents nombres d'instances générées
 	*****/
 
 	//nombre_random_PALL(8,2500,20000,1000, 20000);
 
+	/*****
+	//Succes de sp contre stochastique en fonction de la marge
+	******/
 
+	//marge_PALL_stochastique(2500,700,100,20000,0);
 
 	return 0;
 }

### 2017-06-01 code/Sources/simulations.c

@@ -246,10 +246,10 @@ void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int m
 	sprintf(nom,"../datas/compare_retour_%d.data",periode);
 	FILE * F = fopen(nom,"w");
 	Graphe g ;
-	int resgp,ress,ressp;
-	float gp,s,sp;
+	int resgp,ress,ressp,resr;
+	float gp,s,sp,r;
 	int tmax;
-	int nb_rand = 100;
+	int nb_rand = 1000;
 
 	
 		
@@ -258,7 +258,8 @@ void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int m
 		gp=0;
 		s=0;
 		sp =0;
-		#pragma omp parallel for private(resgp,ress,ressp,g,tmax) if (PARALLEL) schedule (dynamic)
+		r=0;
+		#pragma omp parallel for private(resgp,ress,ressp,resr,g,tmax) if (PARALLEL) schedule (dynamic)
 		for(int i = 0;i<nb_simuls;i++)
 		{
 			g = init_graphe(2*nb_routes+1);
@@ -322,6 +323,13 @@ void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int m
 						
 					}
 				}
+				resr=stochastic(g, taille_paquets,periode,tmax);
+			
+				if(resr != -1)
+				{
+					#pragma omp atomic
+					r++;
+				}
 
 		
 			//printf("-----------------------------------------\n");
@@ -329,15 +337,15 @@ void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int m
 		}
 		
 	
-   			      fprintf(F,"%d %f %f %f \n",marge,gp/nb_simuls*100,s/nb_simuls*100,sp/nb_simuls*100);
-   		     fprintf(stdout,"%d %f %f %f \n",marge,gp/nb_simuls*100,s/nb_simuls*100,sp/nb_simuls*100);
+   			      fprintf(F,"%d %f %f %f %f\n",marge,gp/nb_simuls*100,s/nb_simuls*100,sp/nb_simuls*100,r/nb_simuls*100);
+   		     fprintf(stdout,"%d %f %f %f %f\n",marge,gp/nb_simuls*100,s/nb_simuls*100,sp/nb_simuls*100,r/nb_simuls*100);
 		
 
 	}
 	fclose(F);
 }
 
[…]

### 2017-06-01 code/Sources/simulations.h

@@ -4,3 +4,4 @@ void sucess_aller_PALL(int nb_routes, int taille_paquets,int taille_route,int ma
 void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int marge_max, int nb_simuls, int periode);
 void succes_PALL_3D(int nb_routes, int taille_paquets,int taille_route, int nb_simuls, int mode);
 void nombre_random_PALL(int nb_routes, int taille_paquets,int taille_route, int nb_simuls, int periode);
+void marge_PALL_stochastique(int taille_paquets,int taille_route, int nb_simuls, int periode, int marge);

### 2017-06-01 article/article.tex

--- 2017-06-01 article/article.tex
@@
      \end{figure}
-
-     ici pas besoin de tester pour des periodes longues : gp est deja au max, MSP strictment meilleur que GP ?
 

### 2017-06-01 article/article.tex
quelques corrections dans la partie star topology

--- 2017-06-01 article/article.tex
@@
 For all $i$, there is an arc between $s_i$ and $c_s$ and between $t_i$ and $c_t$.
-      The routes are the directed paths $r_i = s_i,c_s,c_t,t_i$ and $\rho(r_i) = t_i,c_t,c_s,s_i$ and we have thus defined a 
+      The routes are the directed paths $r_i = s_i,c_s,c_t,t_i$ and $\rho(r_i) = t_i,c_t,c_s,s_i$ which defines a 
       symmetric routage graph.
@@
 
-      Since the central arc appears in every route, its value does not matter when considering assignments.
-      We assume the weight of the central arc to be $0$ \\
+      Since the central arc appears in every route, its value do not matter when considering the process time of an assignment.
+      Moreover an assignment without collisions is also an assignment without collisions if the weight of the central arc 
+      is set to $0$, therefore we assume from now on it is indeed $0$.
       Collisions between messages can only appear at node $c_s$ on the way forward and at node $c_t$ on the way back.
@@
   Since $w_i=0$, choosing $m_i$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i) \mod P$.
-  Remark that there is a bijection between the assignment of a star topology and the 
-  the assignment of the same star topology where all arcs from $s_i$ to $c_s$ have weight equal to $0$
-  by changing $m_i$ into $m_i - t(c_s,r_i) \mod P$. Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
-
-  \todo{Dire qu'on donne deux algos qui trouvent toujours une solution quand certains condtions sont remplies
-  et un dernier qui sait décider si il y a une solution oui ou non mais qui est exponentiel avec des optimisations pour le rendre pratique}
-
-  We propose two algorithm that give solutions in polynomial time following some criteria (short routes or great enough period), and one exponential algorithm which determines if there is a solution, and find it if it exists.
-
-    \subsubsection{Shortest-longest policy}
-
-    We present a simple policy, which works when the period is large with regards to the delay of the routes.
+  Remark that there is a bijection between the assignments of a star topology and the 
+  assignments of the same star topology where all arcs from $s_i$ to $c_s$ have weight equal to $0$ by changing $m_i$ into $m_i - t(c_s,r_i) \mod P$.
+Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
+
+  We propose two algorithms that always find a solution in polynomial time if the instance meets some criteria (short routes or great enough period) but which may fail in other cases and one exponential algorithm which always finds a solution if it exists.
+
+    \subsubsection*{Shortest-longest policy}
+
+    We first present a simple policy, which works when the period is large with regards to the delay of the routes.
     The message are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
-    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{s_i} = i\tau$.
-    We call this algorithm {\bf Shortest-Longest}.
+    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{i}$ the offset of $r_i$ to $(i-1)\tau$. We call this algorithm {\bf Shortest-Longest}.
 
@@
 
-      \begin{proposition} When $n\tau + 2(\lambda(r_{s_{n-1}}) - \lambda(r_{s_0})) \leq P$,
-      the algorithm Shortest-Longest solves positively PAZL in time $O(n\log(n))$.\label{prop:SL}
+      \begin{proposition} When $n\tau + 2(\lambda(r_{n}) - \lambda(r_{1})) \leq P$,
+      there is always a solution to PAZL and Shortest-Longest finds it  in time $O(n\log(n))$.\label{prop:SL}
       \end{proposition}
       \begin{proof}
-       Since $m_{s_i} = i\tau$, $[t(c_s,r_{s_i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.
-
-       We assume may that $\lambda(r_{s_0}) = 0$, since removing $\lambda(r_{s_0})$ to every route does not change the order on the length of the routes and thus the result of this algorithm.
-      We have  $[t(c_s,r_{t_i})] = \{2 \lambda(r_{s_i}) + i\tau, \dots,  2 \lambda(r_{s_i}) + (i+1)\tau -1\}$ since $2 \lambda(r_{s_{n-1 }}) + n\tau \leq P$.
-       Since $ \lambda(r_{s_i}) \leq  \lambda(r_{s_{i+1}})$ by construction, we have  $2 \lambda(r_{s_i}) + (i+1)\tau -1 < 2 \lambda(r_{s_{i+1}}) + (i+1)\tau$ which proves that there are no collision on the backward period.
-
-       The complexity of the algorithm is dominated by the sorting of the routes. 
+       Since $m_{i} = (i-1)\tau$, $[t(c_s,r_{i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.
+
+       We may assume that $\lambda(r_{1}) = 0$, since removing $\lambda(r_{1})$ from every arc $(c_t,t_i)$ does not change the order on the length of the routes nor the collisions between messages.
+       Since $\lambda(r_{1}) = 0$, by hypothesis we have $n\tau + 2\lambda(r_{n}) \leq P$ which implies that
+       $[t(c_s,r_{i})] = \{2 \lambda(r_{i}) + (i-1)\tau, \dots,  2 \lambda(r_{i}) + i\tau -1\}$.
+       Since $ \lambda(r_{i}) \leq  \lambda(r_{i+1})$ by construction, we have  $2 \lambda(r_{i}) + i\tau -1 < 2 \lambda(r_{i+1}) + i\tau$ which proves that there are no collision on the backward period.
+
+       The complexity of the algorithm is dominated by the sorting of the routes in $O(n\log(n))$. 
       \end{proof}
 
-      If the period is slightly smaller that the bound of Proposition~\ref{prop:SL}, a collision will occur on the route in the backward period, making 
-      this policy not useful even as a heuristic for longer routes.
-
-    \subsubsection{Greedy Algorithm}
+      If the period is slightly smaller that the bound of Proposition~\ref{prop:SL}, a collision will occur on the first route in the backward period.
+Hence, this policy is not useful even as a heuristic for longer routes as confirmed by the experimental results of Subsection~\ref{sec:exp_PAZL}.
+
+    \subsubsection*{Greedy Algorithm}
 
@@
     \begin{proposition}
-    Let  $n$ be the number of routes and let $ 3n\tau \leq P$, then there is an algorithm which positively solves PAZL in time $O(n^2)$.
+    Let  $n$ be the number of routes and let $ 3n\tau \leq P$, then there is is always a solution to PAZL and there is an  algorithm which finds the assignment in time $O(n^2)$.
     \end{proposition}
@@
 This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
-In fact, experimental data in Subsection~\ref{sec:experimental_results} suggests that the algorithm finds a solution on average when $P \geq 1.5 n\tau$.
+In fact, experimental data in Subsection~\ref{sec:exp_PAZL} suggests that the algorithm finds a solution on average when $P \geq 1.5 n\tau$.
 Note that we also experimented with other greedy algorithms which do not use macro-slots, they work even better in practice but their theoretical upper bound is worse.
 
-	\subsubsection{Exhaustive search}
+	\subsubsection*{Exhaustive search}
 % 	\begin{algorithm}[H]
@@
       the children of a partial solution are the partial solutions which extend it.
-The solutions to our problem will be the leaves of depth $n$ in the tree, therefore our algorithm is a depth-first search of the tree.
+The solutions to our problem will be the leaves of depth $n$ in the tree, and our exhaustive search algorithm is a depth-first search of this tree.
 
@@
 Therefore we have to find cuts in the tree to avoid to explore it entirely and henceforth make the algorithm practical.
-Cuts correspond to the detection of subtrees which contain no solutions and can thus be skipped.
+Cuts correspond to the detection of subtrees which contain no solutions or solutions which can be found elsewhere and can thus be skipped.
 We now propose three cuts, the first two being particularly useful when the network is loaded ($n\tau$ is not far from $P$).
@@
        \item We consider the number of slots which can be used by routes not yet fixed by a partial solution in the \emph{forward period}.
-When we extend a solution into $S$ by a route at offset $m$, then at most $(P - m) / \tau $ routes can still be set without collisions in the forward period.
+When we extend a solution into $S$ with a new route at offset $m$, then at most $(P - m) / \tau $ routes can still be used to extend $S$ without collisions in the forward period.
 If that value is less than the number of routes which are not in $R(S)$, it is a failure and the algorithm backtracks.
@@
        For the next two cuts, we need to define the notion of the useful slots of a partial solution $S$ in the \emph{backward period}: a slot is said to be useful, if it is not used by a message set by $S$ in the backward period and it belongs to an interval of at least $\tau$ such slots.
-Useful slots are positions which can be used when extending $S$.
+Useful slots are positions of the backward period which can be used when extending $S$.
 We will denote by $([a_i,b_i[)_{i\leq l}$ the ordered sequence of intervals of useful slots of $S$.
@@
 
-    \subsubsection{Experimental Results}\label{sec:experimental_results}
+    \section{Experimental Evaluation}\label{sec:exp_PAZL}
 
@@
       is at most $n = 20$, $\tau$ is equal to $2500$ and the period is at most $3n\tau$ (otherwise the greedy algorithm always returns a solution).
-
-      \todo{Dire où on peut trouver le code (pas la peine de donner des infos sur la machine/compilateur car one ne fait pas d'étude de performances.}
+The code in C is available online on the webpages of the authors ~\cite{webpage}.
 %             
@@
       completely in a single edge.
-This is typical in our context and we will consider graphs in which the values $\lambda(c_t,r_{t_i})$ are drawn uniformly between $0$ and $700$ slots.
+This is very common in our context and we will consider graphs in which the values $\lambda(c_t,\rho(r_{i}))$ are drawn uniformly between $0$ and $700$ slots.
 It corresponds to messages of approximately 1Mb, links of bandwidth 10Gbps and length less than 5km between the BBU and the RRH.
@@
 
-      Finally we remark that the greedy algorithm have an average period much lower than the theoretical upper bound of $3n\tau$.
+      Finally we remark that the greedy algorithm has an average period much lower than the theoretical upper bound of $3n\tau$.
 We made a linear regression on this value and with a correlation coefficient greater than $0,999$ we find a slope of $1.53n\tau$.
@@
 
-      In this experiment we will fix the number of routes to $8$ and the values $\lambda(c_t,r_{t_i})$ are drawn following an uniform distribution between $0$ and $30000$ slots (in the same range as the period).
+      In this experiment we will fix the number of routes to $8$ and the values $\lambda(c_t,\rho(r_{i}))$ are drawn following an uniform distribution between $0$ and $30000$ slots (in the same range as the period).
       We measure for each algorithm its percentage of success, for periods from $20000$ which is the minimum possible to $50000$.
 
-      Since the exhaustive search can fail because there are no solutions or because it does not have enough time to finish its calculation.
-We represent both the success rate of the algorithm, and an upper bound on the success rate of any algorithm solving PAZL by combining its successes and its failures because of lack of time.
+      The exhaustive search can fail because there are no solutions or because it does not have enough time to finish its calculation.
+Hence we represent both the success rate of the algorithm, and an upper bound on the success rate of any algorithm solving PAZL by combining its successes and its failures because of lack of time.
 
@@
       When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithms which justifies its use. 
-      However for small period, less than $30000$ the computation time is really important and without improvement it would not be possible to tackle 
-      larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small periods, we see that there are very few instances
-      with a solution for PAZL. It means that with long routes and high load, looking for an assignment without waiting may be too restrictive.
-      That is why we present algorithms for the general PALL problem in our next section. We will test them on $8$ long routes and a period between 
-      $20000$ and $30000$ where, as we have shown here, there are often no easy to compute assignment without waiting time.
+      However for small period, less than $30000$ the computation time is really important and without improvements it would not be possible to tackle 
+      larger problems with $10$ to $20$ routes.
+Moreover, examining the upper bound curve for small periods less than $22000$, we see that there are very few instances with a solution for PAZL.
+It means that with long routes and high load, looking for an assignment without waiting time is far too restrictive.
+      That is why we present algorithms for the general PALL problem in our next section.
+We will test them on $8$ long routes and a period between $20000$ and $30000$ where, as we have shown here, there are often no easy to compute assignment without waiting time.
 

### 2017-06-02 article/article.tex
petites corrections

@@
 This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
-In fact, experimental data in Subsection~\ref{sec:exp_PAZL} suggests that the algorithm finds a solution on average when $P \geq 1.5 n\tau$.
+In fact, experimental data in Subsection~\ref{sec:exp_PAZL} suggests that the algorithm finds a solution on average when $P \geq 2 n\tau$.
 Note that we also experimented with other greedy algorithms which do not use macro-slots, they work even better in practice but their theoretical upper bound is worse.
@@
 
-    \section{Experimental Evaluation}\label{sec:exp_PAZL}
+    \subsection{Experimental Evaluation}\label{sec:exp_PAZL}
 
@@
       which is large here.
-On the other hand, the greedy algorithm has a performance not very different from the case of short routes, which is expected since it does not depends on the size of the route.
-\todo{Ajouter la moyenne pour la comparer aux routes courtes}
+On the other hand, the greedy algorithm has a performance not so far from the case of short routes, which is expected since it does not directly depend on the size of the route.
+When repeating the experiments of the previous section on routes of arbitrary length, we find that on average the greedy algorithm finds a solution if $P > 1.89n\tau$.
 
@@
 
-	\paragraph{Particular cases}
+	\subsection{Particular cases}
 
@@
 
-     \subsubsection{A first approach}
+     \subsection{A first approach}
 
@@
 
-     \subsubsection{Sending order}
+     \subsection{Sending order}
 
@@
      For the rest of the section, we look at the different algorithm suggested to improve the second part of the scheduling, after having set the sending order.
-      \subsubsection{About the periodicity}
+      \subsection{About the periodicity}
      The previous algorithm is a greedy heuristic, which does not take the period into account. 
@@
 
-     \subsubsection{Near from scheduling problems}
+     \subsection{Using a scheduling algorithm}
 
@@
 
-     \subsubsection{Final algorithm}
+     \subsection{Final algorithm}
 
@@
 
-    \subsubsection{Results}
+    \subsection{Results}
 
@@
 
-    \paragraph{Comparer optimal + depart random avec stochastique}
+    \todo{Comparer optimal + depart random avec stochastique}
 
@@
 
-   \begin{itemize}
-    \item FPT algorithms for PAZL and PALL 
-    \item average latency instead of maximal latency
-    \item trees
-    \item cycles 
-    \item preemption (messages can be cut into pieces)
-    \item routes are not given and can be chosen
-   \end{itemize}
+   We plan to generalize our study of the PALL problem to more topology,
+   such as trees and cycles which are the most common ones in real networks. 
+   We would like to design FPT algorithms in the number of routes for PAZL and PALL on the star topology, eventually by relaxing the contraint on the maximal process time into an constraint on the average process time, which seems much more tractable.
+   Moreoever we could allow preemption, that is the messages are allowed to be cut into pieces,
+   which could certainly change the complexity of the problem. 
+   Finally, the routes may not be fixed but chosen to optimize the latency, which would make the problem even more difficult ( maybe $\Pi_2$-complete instead of $\NP$-complete).
 

### 2017-06-02 article/article.tex
quelques petites corrections

@@
 \title{How to Schedule Periodic Messages in a Network Without Congestion}
-\author{DB,CC,MG,OM,YS}
+%\author{Dominique Barth - UVSQ ,Christian Cadéré - UVSQ,Maël Guiraud - UVSQ,Olivier Marcé - Nokia Bell Labs France,Yann Strozecki - UVSQ}
+
+\author{
+   Dominique {\bf Barth}, {\em UVSQ}
+   \and
+   Christian  {\bf Cad\'er\'e}, {\em UVSQ}
+      \and
+   Ma\"el  {\bf Guiraud}, {\em UVSQ}
+      \and
+   Olivier  {\bf Marcr\'e}, {\em Nokia Bell Labs France}
+      \and
+   Yann  {\bf Strozecki}, {\em UVSQ}
+}
 
@@
       \begin{figure}[ht]
-      % \begin{center}
+      \begin{center}
+          \scalebox{0.8}{
 
@@
 \end{tikzpicture}
-     % \end{center}
+
+}
+     \end{center}
        \caption{A routage graph with $(0,0,0)$ as a $(2,1)$-periodic assignment}
@@
 % 
-%       \todo{Mettre les données concrètes plus proprement et éventuellement ne pas les mettre si on envoie pas à un truc de télécom}
+%       \todo{Mettre les donn√©es concr√®tes plus proprement et √©ventuellement ne pas les mettre si on envoie pas √† un truc de t√©l√©com}
 
@@
       That is why we present algorithms for the general PALL problem in our next section.
-We will test them on $8$ long routes and a period between $20000$ and $30000$ where, as we have shown here, there are often no easy to compute assignment without waiting time.
+We will test them on $8$ long routes and a period between $20000$ and $30000$ where, as we have shown here, there are often no easy to compute assignment without waiting times.
 
@@
 
-	  We just found solution to solve a restricted version of PALL, in which no waiting times are allowed, 
-	  and the problem has no solution when the period is too short.
-We propose to allow some message to wait in the target vertices (BBU), with the aim of giving an higher degree of freedom for the scheduling.
+    In this section, we allow the messages to wait in the target vertices (BBU), to give an higher degree of freedom to the scheduling.
 Thus, the process time of a message $PT$ might be superior to $T_{max}$.
-The goal is to find some solutions with waiting time such that any message will be buffered too much, i.e.
+The goal is to find a solution with waiting time such that any message will be not be buffered too much, i.e.
 $MT({\cal M}) \leq T_{max}$.
@@
 	 \begin{theorem}
-      There is always an optimal solution when all the weight on the arcs between $c_s$ and the sources are the same.
+      There is always an optimal solution when all the weights on the arcs between $c_s$ and the sources are the same.
       \end{theorem}
@@
     \begin{algorithmic}
-    \REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, $ T_{max}$, packet size $\tau$
-    \ENSURE $(P-\tau)-$periodic assignment of ${\cal R_{\cal C}}$
+    \REQUIRE routage graph $(G,{\cal R})$, period $P$, $ T_{max}$, packet size $\tau$
+    \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$
     \STATE $clock \leftarrow 0$
@@
 
-    By using a binary heap to manage the eligible routes, this algorithm runs in $\mathcal{O}(n\log{}n)$.
+    By using a binary heap to manage the eligible routes, this algorithm runs in $O(n\log(n))$.
 
@@
 
-     However, this heuristic does not take the period into account .
+     However, this heuristic does not take the period into account.
 Thus, a solution given by this algorithm can satisfy the constraint $MT({\cal M}) \leq T_{max}$, but this solution might need a too large period.
 
-     \subsection{Sending order}
-
-	We tried to look at the behavior of the that policy with different kind of sending order for the messages.
+     \subsection{Choice of the Sending Order}
+
+	We tried to look at the behavior of the that policy with different kinds of sending order for the messages.
 
@@
     \begin{algorithmic}
-    \REQUIRE A routage graph ${\cal R_{\cal C}}$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
-    \ENSURE $(P-\tau)-$periodic assignment of ${\cal R_{\cal C}}$, if it exists
+    \REQUIRE A routage graph $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
+    \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$, if it exists
 
@@
 
-     The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic assignment, even with a small period, and T$_{max}$.
+     The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic assignment, even with a small period, and $T_{max}$.
 
@@
 \simeq 40 000$.
-By drawing $1000$ random sending orders, we explore near to $2,5 \%$ of the cases, which seems enough to find as many solutions as if generate more random sending oredres.
-
-     We now want to compare the performances of the different algorithms.Since GP showed some excellent results on large periods (see Figure 5), it is more interesting to focus on the behavior of the algorithms on short periods.
-The following experience is realized on graph with 8 routes (links between $0$ and $20000$), and with a period of 21000.
-Since we just conclude that drawing 1000 sending order is a good number, with 8 routes.
-We now generate 1000 randoms sending orders for the first way.
+By drawing $1000$ random sending orders, we explore near to $2,5 \%$ of the cases, which seems enough to find as many solutions as if generate more random sending ordres.
+
+     We now want to compare the performances of the different algorithms.Since GP showed some excellent results on large periods (see  Fig~\ref{fig:success21000}), it is more interesting to focus on the behavior of the algorithms on short periods.
+The following experience is realized on graph with $8$ routes (links between $0$ and $20000$), and with a period of $21000$.
+Since we just conclude that drawing $1000$ sending order is a good number, with 8 routes.
+We now generate $1000$ randoms sending orders for the first way.
 
     \begin{figure} 
-
        \begin{center}
@@
       \caption{Success rate of the different algorithms for a $P = 21000$}
+     \label{fig:success21000}
      \end{figure}
@@
 
-   We plan to generalize our study of the PALL problem to more topology,
-   such as trees and cycles which are the most common ones in real networks. 
-   We would like to design FPT algorithms in the number of routes for PAZL and PALL on the star topology, eventually by relaxing the contraint on the maximal process time into an constraint on the average process time, which seems much more tractable.
+   We plan to generalize our study of the PALL problem to more topologies,
+   such as trees and cycles which are commonly found in real networks. 
+   We would like to design FPT algorithms in the number of routes for PAZL and PALL on the star topology, eventually by relaxing the constraint on the maximal process time into an constraint on the average process time, which seems much more tractable.
    Moreoever we could allow preemption, that is the messages are allowed to be cut into pieces,
-   which could certainly change the complexity of the problem. 
-   Finally, the routes may not be fixed but chosen to optimize the latency, which would make the problem even more difficult ( maybe $\Pi_2$-complete instead of $\NP$-complete).
+   which would certainly change the complexity of the problem. 
+   Finally, the routes may not be fixed but chosen to optimize the latency, which would make the problem even more difficult (maybe $\Pi_2$-complete instead of $\NP$-complete).
 

### 2017-06-02 article/article.tex
a relire par moi avant d'envoyer

--- 2017-06-01 article/article.tex
@@
 \title{How to Schedule Periodic Messages in a Network Without Congestion}
-\author{DB,CC,MG,OM,YS}
+%\author{Dominique Barth - UVSQ ,Christian Cadéré - UVSQ,Maël Guiraud - UVSQ,Olivier Marcé - Nokia Bell Labs France,Yann Strozecki - UVSQ}
+
+\author{
+   Dominique {\bf Barth}, {\em UVSQ}
+   \and
+   Christian  {\bf Cad\'er\'e}, {\em UVSQ}
+      \and
+   Ma\"el  {\bf Guiraud}, {\em UVSQ}
+      \and
+   Olivier  {\bf Marc\'e}, {\em Nokia Bell Labs France}
+      \and
+   Yann  {\bf Strozecki}, {\em UVSQ}
+}
 
@@
        \begin{center}
-      \includegraphics[scale=0.3]{BBU2.png}
+      \includegraphics[scale=0.17]{BBU2.png}
       \end{center}
@@
        \begin{center}
-
+	 \scalebox{0.7}{
 \begin{tikzpicture}
@@
                        font = \bfseries },
-  EdgeStyle/.append style = {->} }
+  EdgeStyle/.append style = {<->} }
 
@@
 
-  \node[draw,circle] (s3) at (0, 0) {$s_2$}; 
-  \node[draw,circle] (s2) at (0, 2) {$s_1$}; 
-  \node[draw,circle] (s1) at (0, 4) {$s_0$};
-
-  \node[draw,circle] (t3) at (8, 0) {$t_2$}; 
-  \node[draw,circle] (t2) at (8, 2) {$t_1$}; 
-  \node[draw,circle] (t1) at (8, 4) {$t_0$};
+  \node[draw,circle] (s3) at (0, 0) {$s_3$}; 
+  \node[draw,circle] (s2) at (0, 2) {$s_2$}; 
+  \node[draw,circle] (s1) at (0, 4) {$s_1$};
+
+  \node[draw,circle] (t3) at (8, 0) {$t_3$}; 
+  \node[draw,circle] (t2) at (8, 2) {$t_2$}; 
+  \node[draw,circle] (t1) at (8, 4) {$t_1$};
 
@@
 \end{tikzpicture}
+}
 
@@
 Since we just conclude that drawing 1000 sending order is a good number, with 8 routes.
-We now generate 1000 randoms sending orders for the first way.
+We now generate 1000 randoms sending orders instead of 100.
 
@@
 
-    \paragraph{Comparer optimal + depart random avec stochastique}
+     The algorithm MS, that does not consider the periodicity for the scheduling is far worst than the others, and, even if GP seems to converge too 100\% of success rate when the flexibility is large enough, MSP is always strictly better.
+We remark that when the flexibility is low ($<500$) there is near to 5\% of failure.
+
+ To evaluate the performance of our best algorithm to find solutions, that is, generating $1000$ randoms sending orders and using MSP on the way back, we compared it's performance, against the actual way to manage the messages in a network.
+Nowadays, the networks are managed through a stochastic model.
+The messages in the nodes are scheduled following a FIFO rule.
+Even if this policy works well, in practice, it does not ensure a minimum latency.
+Thus, some latency critical applications like C-RAN needs some deterministic algorithms.
+To model such a network, we generate some randoms offsets in the sources.
+Then we simulate the behavior of a stochastic network during a great number of periods.
+The following figure shows the average latency of a stochastic network, compared to the latency of our algorithm.
+We tested the algorithms on $1000$ instances with $8$ long routes (links between $0$ and $20000$).
+The flexibility of the stochastic curve is computed by taking the message which have the highest process time, at which we subtract the delay of the longest route.
+We made a linear search to find the minimum flexibility needed by our algorithm to find a solution.
+ We measure the average flexibility, for periods from $20000$ ( network fully loaded), to $50000$ (40 \% of load).
+
+    \begin{figure}
+
+       \begin{center}
+      \includegraphics[scale=0.4]{stochastic.pdf}
+      \end{center}
+      \caption{Average latency, depending on the load of the network.}
+     \end{figure}
+
+    As expected, our algorithm gives some very satisfying results.
+There is a few cases when both the flexibility and the period are too restricted in which there is no solutions, but those case are impossible in practice.
+Furthermore, the stochastic policy can not ensure a minimal latency.
+In our context, this is crucial to use some deterministic algorithms to manage the messages in the network.
 

### 2017-06-02 code/Sources/PALL.c

@@ -400,7 +400,7 @@ int longest_etoile_periodique(Graphe g,int taille_paquets,int periode, int Tmax,
 	// affiche_solution(g,taille_paquets,m_i, w_i);
 	return max;
 }
-
+/*
 int stochastic(Graphe g, int taille_paquets, int periode, int tmax)
 {
 	if(!(g.N%2)){printf("Nombre de sommets impair, G n'est peut être pas une étoile\n");exit(5);}
@@ -496,7 +496,7 @@ int stochastic(Graphe g, int taille_paquets, int periode, int tmax)
 	return max;	
 
 }
-
+*/
 
 
 
@@ -535,7 +535,7 @@ int linear_simons_per(Graphe g,int periode,int taille_message,int nb_rand)
 	}while( (result == -1) && (result != -2 ));
 	return marge;
 }
-
+/*
 int linear_stochastic(Graphe g,int periode,int taille_message)
 {
 	int result;
@@ -554,5 +554,5 @@ int linear_stochastic(Graphe g,int periode,int taille_message)
 
 	}while((result == -1 )||(result == -2));
 	return marge;
-}
+}*/
 

### 2017-06-02 code/Sources/PALL.h

@@ -1,5 +1,5 @@
 int longest_etoile_2(Graphe g,int taille_paquets,int periode, int Tmax,int mode);
 int longest_etoile_periodique(Graphe g,int taille_paquets,int periode, int Tmax,int mode);
-int stochastic(Graphe g, int taille_paquets, int periode, int tmax);
+//int stochastic(Graphe g, int taille_paquets, int periode, int tmax);
 int linear_simons_per(Graphe g,int periode,int taille_message,int nb_rand);
-int linear_stochastic(Graphe g,int periode,int taille_message);
+//int linear_stochastic(Graphe g,int periode,int taille_message);

### 2017-06-02 code/Sources/main.c

@@ -5,7 +5,9 @@
 
 #include "simulations.h"
 
-
+#include "struct.h"
+#include "init.h"
+#include "random.h"
 int main()
 {
 	srand(time(NULL));
@@ -39,7 +41,7 @@ int main()
 	/*****
 	Taux de reussite de départ PALL avec un retour GP sur une periode donnée (on fait varier la marge)
 	*****/
-	sucess_aller_PALL(8,2500,20000,3000,2000,21000);
+	//sucess_aller_PALL(8,2500,20000,3000,2000,21000);
 
 
 
@@ -52,7 +54,7 @@ int main()
 	Taux de reussite des algos PALL avec un aller random sur une periode donnée (on fait varier la marge)
 	*****/
 
-	sucess_retour_PALL(8,2500,20000,3000,1000,21000);
+	//sucess_retour_PALL(8,2500,20000,3000,1000,21000);
 
 
 	/******************************************/
@@ -64,10 +66,11 @@ int main()
 	//nombre_random_PALL(8,2500,20000,1000, 20000);
 
 	/*****
-	//Succes de sp contre stochastique en fonction de la marge
-	******/
+	Tmax moyen pour sto vs sp
+	*******/
 
-	//marge_PALL_stochastique(2500,700,100,20000,0);
+	marge_PALL_stochastique(8,2500,20000,1000,50000);
+
 
 	return 0;
 }

### 2017-06-02 code/Sources/simulations.c

@@ -9,8 +9,9 @@
 #include "init.h"
 #include "operations.h"
 #include "tests.h"
+#include "random.h"
 
-#define PARALLEL 0
+#define PARALLEL 1
 
 //Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
 void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,int nb_simuls)
@@ -246,8 +247,8 @@ void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int m
 	sprintf(nom,"../datas/compare_retour_%d.data",periode);
 	FILE * F = fopen(nom,"w");
 	Graphe g ;
-	int resgp,ress,ressp,resr;
-	float gp,s,sp,r;
+	int resgp,ress,ressp;
+	float gp,s,sp;
 	int tmax;
 	int nb_rand = 1000;
 
@@ -258,8 +259,8 @@ void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int m
 		gp=0;
 		s=0;
 		sp =0;
-		r=0;
-		#pragma omp parallel for private(resgp,ress,ressp,resr,g,tmax) if (PARALLEL) schedule (dynamic)
+
+		#pragma omp parallel for private(resgp,ress,ressp,g,tmax) if (PARALLEL) schedule (dynamic)
 		for(int i = 0;i<nb_simuls;i++)
 		{
 			g = init_graphe(2*nb_routes+1);
@@ -323,13 +324,7 @@ void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int m
 						
 					}
 				}
-				resr=stochastic(g, taille_paquets,periode,tmax);
-			
-				if(resr != -1)
-				{
-					#pragma omp atomic
-					r++;
-				}
+
 
 		
 			//printf("-----------------------------------------\n");
@@ -337,8 +332,8 @@ void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int m
 		}
 		
 	
-   			      fprintf(F,"%d %f %f %f %f\n",marge,gp/nb_simuls*100,s/nb_simuls*100,sp/nb_simuls*100,r/nb_simuls*100);
-   		     fprintf(stdout,"%d %f %f %f %f\n",marge,gp/nb_simuls*100,s/nb_simuls*100,sp/nb_simuls*100,r/nb_simuls*100);
[…]

### 2017-06-02 code/Sources/simulations.h

@@ -4,4 +4,4 @@ void sucess_aller_PALL(int nb_routes, int taille_paquets,int taille_route,int ma
 void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int marge_max, int nb_simuls, int periode);
 void succes_PALL_3D(int nb_routes, int taille_paquets,int taille_route, int nb_simuls, int mode);
 void nombre_random_PALL(int nb_routes, int taille_paquets,int taille_route, int nb_simuls, int periode);
-void marge_PALL_stochastique(int taille_paquets,int taille_route, int nb_simuls, int periode, int marge);
+void marge_PALL_stochastique(int nb_routes,int taille_paquets,int taille_route, int nb_simuls, int periode_max);

### 2017-06-02 article/article.tex

--- 2017-06-02 article/article.tex
@@
       \and
-   Olivier  {\bf Marcr\'e}, {\em Nokia Bell Labs France}
+   Olivier  {\bf Marc\'e}, {\em Nokia Bell Labs France}
       \and
@@
      We now want to compare the performances of the different algorithms.Since GP showed some excellent results on large periods (see Fig~\ref{fig:success21000}), it is more interesting to focus on the behavior of the algorithms on short periods.
-The following experience is realized on graph with $8$ routes (links between $0$ and $20000$), and with a period of $21000$.
-Since we just conclude that drawing $1000$ sending order is a good number, with 8 routes.
-We now generate $1000$ randoms sending orders for the first way.
+The following experience is realized on graph with 8 routes (links between $0$ and $20000$), and with a period of 21000.
+Since we just conclude that drawing 1000 sending order is a good number, with 8 routes.
+We now generate 1000 randoms sending orders instead of 100.
 
@@
 
-    \todo{Comparer optimal + depart random avec stochastique}
+     The algorithm MS, that does not consider the periodicity for the scheduling is far worst than the others, and, even if GP seems to converge too 100\% of success rate when the flexibility is large enough, MSP is always strictly better.
+We remark that when the flexibility is low ($<500$) there is near to 5\% of failure.
+
+ To evaluate the performance of our best algorithm to find solutions, that is, generating $1000$ randoms sending orders and using MSP on the way back, we compared it's performance, against the actual way to manage the messages in a network.
+Nowadays, the networks are managed through a stochastic model.
+The messages in the nodes are scheduled following a FIFO rule.
+Even if this policy works well, in practice, it does not ensure a minimum latency.
+Thus, some latency critical applications like C-RAN needs some deterministic algorithms.
+To model such a network, we generate some randoms offsets in the sources.
+Then we simulate the behavior of a stochastic network during a great number of periods.
+The following figure shows the average latency of a stochastic network, compared to the latency of our algorithm.
+We tested the algorithms on $1000$ instances with $8$ long routes (links between $0$ and $20000$).
+The flexibility of the stochastic curve is computed by taking the message which have the highest process time, at which we subtract the delay of the longest route.
+We made a linear search to find the minimum flexibility needed by our algorithm to find a solution.
+ We measure the average flexibility, for periods from $20000$ ( network fully loaded), to $50000$ (40 \% of load).
+
+    \begin{figure}
+
+       \begin{center}
+      \includegraphics[scale=0.4]{stochastic.pdf}
+      \end{center}
+      \caption{Average latency, depending on the load of the network.}
+     \end{figure}
+
+    As expected, our algorithm gives some very satisfying results.
+There is a few cases when both the flexibility and the period are too restricted in which there is no solutions, but those case are impossible in practice.
+Furthermore, the stochastic policy can not ensure a minimal latency.
+In our context, this is crucial to use some deterministic algorithms to manage the messages in the network.
 

### 2017-06-05 article/article.tex
lundi aprem quelques typos

@@
 The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
-We will always consider that the $m_{i}$ are between $O$ and $P-1$.
+We will always consider that the $m_{i}$ are between $0$ and $P-1$.
 A $(P,\tau)$-periodic assignment must have no {\bf collision} between two routes in $\cal R$, that is $\forall (r_{i}, r_{j}) \in {\cal R}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
@@
 %       Notice that the notion of $P$-periodic assignment \textbf{is not monotone} with regard to $P$. 
-      As an example of a $(2,1)$-periodic assignment, let consider a routage graph with routes $\{r_{i}\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
+      As an example of a $(2,1)$-periodic assignment, let us consider a routage graph with routes $\{r_{i}\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
       We set $\tau = 1$ and the delays are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.
@@
 
-  We propose two algorithms that always find a solution in polynomial time if the instance meets some criteria (short routes or great enough period) but which may fail in other cases and one exponential algorithm which always finds a solution if it exists.
+  We propose two algorithms that always find a solution in polynomial time if the instances meets some criteria (short routes or great enough period) but which may fail in other cases and one exponential algorithm which always finds a solution if it exists.
 

### 2017-06-05 article/article.tex
relecture partie PALL3

@@
 
-	One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the same and so can be simplified by 0.
+	One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the same and so can be simplified by $0$.
 In that case, the scheduling in the forward and backward period is the same.
@@
 Thus, the period is minimal : $n.\tau$, where $n$ is the number of routes.
-Furthermore, all the waiting times are equal to 0 i.e.
+Furthermore, all the waiting times are equal to $0$ i.e.
 $w_i = 0,\forall i \in n$, thus, $MT({\cal M})$ is equal to twice the delay of the longest route, that is not alterable.
@@
 
-	Since we can simplify the weight on the arcs between $c_s$ and the sources, we consider only the delay between $c_t$ and the targets.
+	Since we can simplify the weight on the arcs between $c_s$ and the sources by $0$, we consider only the delay between $c_t$ and the targets.
 Order the routes such that $\lambda(r_{s_i}) > \lambda(r_{s_j}), i<j$, i.e.
-the route 0 is the longest, and the route $n-1$ is the shortest one.
-	The messages are sent in the forward period from 0 to $n-1$, that is $m_{s_i} = \tau * n$.
+the route $0$ is the longest, and the route $n-1$ is the shortest one.
+	The messages are sent in the forward period from $0$ to $n-1$, that is $m_{s_i} = \tau * i$.
 	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is $PT(s_0) = 2.\lambda(r_{s_0}) $.
@@
 	By induction, $PT(s_i) = PT(s_0), \forall i \in n$.
-	Consequently, for this case, sending the message, because the longest route has no waiting time all the other routes has the exact same process time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) $.
+
+	Consequently, for this case, sending the message from the one using the longest route to to one using the shortest route is optimal, because the longest route has no waiting time all the other routes has the exact same process time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) $.
+Moreover, the period used is exactly $n \tau$, in both the forward and backward periods.
      \end{proof}
@@
 
-	To solve PALL, we proposed some heuristics that prioritize the longest routes, and thus helps to minimize $PT(s_i)$.
-Indeed, one can imagine that, if the messages on the longest routes are be less buffered in their target than the messages using the shortest routes, the process times might be balanced.
-	In an optimal solution, if $i$ is the longest route, we want $w_i =0$, and $PT(s_i) = 2.\lambda(r_{s_i}) \geq  2.\lambda(r_{s_j}) + w_j = PT(s_j) $, where $j$ is any route $\neq i$.
-
-     We first suggest the following heuristic, that prioritize the message on longest routes:
-
-      On the forward period, for the first way, the messages are scheduled so that they are following each others, from the one using the longest route, to the one using the shortest route.
-Thus, we set the $m_{s_i}$ of the routes such that  $t(c_s,r_{s_i}) = \tau.i$, if the routes $r_i$ are ordered from the longest to the shortest.
+	To solve PALL, we propose some heuristics that prioritize the longest routes, and thus helps to minimize $PT(s_i)$.
+Indeed, one can imagine that, if the messages on the longest routes are less buffered in their target than the messages using the shortest routes, the process times might be balanced.
+	In an optimal solution, if $i$ is the longest route, we want $w_i =0$, such that $PT(s_i) = 2.\lambda(r_{s_i}) \geq  2.\lambda(r_{s_j}) + w_j = PT(s_j) $, where $j$ is any route $\neq i$.
+
+     We first suggest the following heuristic:
+
+      On the forward period, for the way forward, the messages are scheduled so that they are following each others, from the one using the longest route, to the one using the shortest route.
+Thus, we set the $m_{s_i}$ of the routes such that  $t(c_s,r_{s_i}) = \tau.i$, if the routes $r_{s_i}$ are ordered from the longest to the shortest.
 
@@
 
-      \item To be eligible, a message needs to be able to come back on $c_t$ at the current clock (if clock = 0, or no messages are able to come back at this date, take the first message able to come back).
+      \item To be eligible, a message needs to be able to come back on $c_t$ at the current clock (if clock = $0$, or no messages are able to come back at this date, take the first message able to come back).
       \item Between the eligible messages, schedule first the one which has the lowest deadline.
-      \item For any route i, the deadline correspond to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$.
-This deadline corresponds to the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
+      \item For any route i, the deadline correspond to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$, that is,  the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
 
@@
     \STATE $clock \leftarrow 0$
-    \FORALL{route i in $r_{s_i}$ sorted from the longest to the shortest }
+    \FORALL{route in $r_{s_i}$ sorted from the longest to the shortest }
     \STATE  $m_{s_i} \leftarrow clock - t(c_s,r_{s_i}) \mod P$
@@
 
-    \STATE take i such that $r_{t_i}$ is the eligible route (Algorithm \ref{algorithm:Eligible})
-    \STATE $w_i \leftarrow 0$
-    \STATE $clock = \lambda(r_i) + t(c_t,r_{t_i}) + \tau$
     \WHILE{there is a route which has not been scheduled}
@@
     \begin{enumerate}
-    \item First, we choose arbitrary a sending order for the routes, and we set the offsets $m_i$ such that the messages are following each others in $c_s$.
+    \item First, we choose an arbitrary sending order for the routes, and we set the offsets $m_i$ such that the messages are following each others in $c_s$.
     \item  Then, the schedule order in the way back is determined, considering the time at which the messages reach their target. 
     \end{enumerate}
-     This {\em Greedy} policy determines the $m_{c_{s_i}}$, such that the messages does not collide on $c_t$.
+     This {\bf Greedy} policy determines the $m_{\rho_{s_i}}$, such that the messages does not collide on $c_t$.
 It computes the deadlines for every messages, considering their offsets and the delay on their routes, and determine the time at which the messages must leave their target, prioritizing the messages with the lowest deadlines.
@@
 
-	We tried the five following sending policy, each ones determines an order in which the messages will be sent, but the messages are still following each others in $c_s$.
-
-	The different sending policy that we tried are the following :
+	We tried the five following sending orders, each ones determines the order in which the messages will be sent from sources, and, in each case the messages are following each others in $c_s$.
+
+	The different sending orders that we tried are the following :
 	\begin{enumerate}
-	 \item Random: Generate $X$ random permutations for the routes and tries the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic assignment.
+	 \item Random: Generate $X$ randoms permutations for the routes and try the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic assignment.
 In the following experiments, we take $X = 100$.
@@
 
-     For the rest of the section, we look at the different algorithm suggested to improve the second part of the scheduling, after having set the sending order.
+     In the rest of the section, we present the  different algorithms suggested to improve the second part of the scheduling.
       \subsection{About the periodicity}
@@
      The greedy policy is the same until the message are scheduled in the period between $bp$ and $bp +P$. When a message is scheduled, we update a list of free intervals in the backward period.
-     Once $clock > bp+P$, we consider that we are in the second period, and thus search a free interval after $clock$, large enough to put a message.
+     Once we try to schedule a message after $bp+P$, we consider that we are in the second period, and thus search a free interval in the period, large enough to put a message.
 
      This policy can significantly increase $w_i$, but ensures a periodic results.
-This {\ Greedy Periodic} policy is strictly better than Greedy, because it finds some solutions that greedy would not find, by considering the periodicity in the scheduling.
-
-         We compared the two algorithms on 10000 graphs on which the weight of the links are drawn uniformly between 0 and 20000, with a period of 21000, and giving, for each instance $T_{max} = 2\lambda(r_{longest-route})$ .
+This {\bf Greedy Periodic} policy is strictly better than Greedy, because it finds some solutions that greedy would not find, by considering the periodicity in the scheduling.
+
+         We compared the two algorithms on $10000$ graphs on which the weight of the links are drawn uniformly between $0$ and $20000$, with a period of $21000$, and giving, for each instance $T_{max} = 2\lambda(r_{longest-route})$ .
 We then look at the success rate of each algorithms, with every sending order.
-Both algorithms reach the higher success rate with the Random sending order, but the success of Greedy is 5,65 \%, while the success rate of Greedy Periodic is to 30,02 \%.
+Both algorithms reach the higher success rate with the Random sending order, but the success of Greedy is $5,65 \%$, while the success rate of Greedy Periodic is to $30,02 \%$.
 
@@
 
-     The problem PALL is very similar to a scheduling problem, combined to the periodic aspect.
+     The problem PALL is very similar to a scheduling problem, but many scheduling problem does not treat about the periodic aspect.
 Thus, the article ``A fast algorithm for single processor scheduling'', by Barbara Simons \cite{simons1978fast} gave us an optimal algorithm to schedule some jobs which has a release time, a deadline and the same execution time.
-We consider that the messages are the jobs, the release times are the date at which the messages are able to come back on $c_t$, and the deadlines are the latest date at which a message have to leave $c_t$ to comeback before $m_i + T_{max}$.
+We adapted this algorithm, considering the messages as the jobs, the release times as the date at which the messages are able to come back on $c_t$, and the deadlines as the latest date at which a message have to leave $c_t$ to comeback before $m_i + T_{max}$.
 This algorithm gives in $\mathcal{O}(n^2\log{}n)$ a solution with the earliest  possible completion time, if it exists.
 Thus, it tries to minimize the time between the first and the last message in the scheduling.
-Let us call {\ Minimized Scheduling (MS)} this algorithm.
+Let us call {\bf Minimized Scheduling (MS)} this algorithm.
 
@@
     This algorithm runs in $\mathcal{O}(n^3\log{}n)$.
-It tries for every routes of the routage graph, to fix the first route to comeback, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(determined by $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).
-
-    This algorithm finds more solutions than MS, because it decrease the deadlines of the route considering the periodicity.
+For every routes of the routage graph, the algorithm fixes the first route to comeback, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(determined by $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).
+
+    This algorithm finds more solutions than MS, because it compute the deadlines of the route considering the periodicity.
 Thus, a scheduling given by this algorithm fulfill both the periodicity and the $T_{max}$ criteria.
@@
    In this experiment, we fix the number of routes to 8.
-We want to compare the sending orders with the worst parameters, so we draw the links between 0 and 20000 slots.
+We want to compare the sending orders with the worst parameters, so we drew the links between $0$ and $20000$ slots.
 We look at the success rate of each sending order with Greedy Periodic to schedule the messages in the way back.
@@
 This flexibility represents $T_{max} - 2\lambda(r_{longest-route})$.
-We let this flexibility vary from 0 to 3000.
-
-   We look at two different regimes: first, we take a period equal to $1,05n\tau$, and then, we take a greater period, that is, $1,5n\tau$. The following results are computed over 10000 instances.
+We let this flexibility vary from $0$ to $3000$.
+
+   We look at two different regimes: first, we take a period equal to $1,05n\tau$, and then, we take a greater period, that is, $1,5n\tau$. The following results are computed over $10000$ instances.
 
@@
       \caption{Success rate of the sending orders for $P = 21000$}
+
      \end{figure}
@@
       \caption{Success rate of the sending orders for a $P = 30000$}
+      \label{fig:success30000}
      \end{figure}
 
-     First, we remark that, for any sending order, the success rate is strictly better for large periods.
+     First, we remark that, for every sending order, the success rate is strictly better for large periods.
 This is due to the fact that the size of the period is a factor for failure.
@@
 As we can see the random finds near to 100\% of the solutions when the period is large enough, even when we give no flexibility.
-On average, it is necessary to draw 6 randoms sending order to find a solution, when the period is large, but in some particularly hard instances, it can be impossible to find a solution, even with 100 randoms sending orders.
+     %On average, it is necessary to draw 6 randoms sending order to find a solution, when the period is large, but in some particularly hard instances, it can be impossible to find a solution, even with 100 randoms sending orders.
 
      To observe  the impact of the number of random sending orders drawn, we compared the success rate of the following number of drawing, on graphs in which the links are drawn  between $0$ and $20000$ slots, with a period $P=20000$, and a flexibility of $0$.
+The following table present the average success rate of each number of sending orders, on $1000$ instances.
        \begin{figure}
@@
        \begin{center}
-   \begin{tabular}{|c|c|c|c|c|c|}
+   \begin{tabular}{|c|c|c|c|c|c|c|}
     \hline
-    number of randoms & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
+    number of randoms & $1$ & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
     \hline
-    Success rate $(\simeq)$ & $60,5$&$77,7$&$80,5$&$80,5$&$80,5$\\
+    Success rate $(\simeq)$ & $17,8$ &$60,5$&$77,7$&$80,5$&$80,5$&$80,5$\\
     \hline
@@
 
-     In our case of 8 routes, the number of different sending orders is $8!
+     In our case of $8$ routes, the number of different possible sending orders is $8!
 \simeq 40 000$.
-By drawing $1000$ random sending orders, we explore near to $2,5 \%$ of the cases, which seems enough to find as many solutions as if generate more random sending ordres.
-
-     We now want to compare the performances of the different algorithms.Since GP showed some excellent results on large periods (see Fig~\ref{fig:success21000}), it is more interesting to focus on the behavior of the algorithms on short periods.
-The following experience is realized on graph with 8 routes (links between $0$ and $20000$), and with a period of 21000.
-Since we just conclude that drawing 1000 sending order is a good number, with 8 routes.
-We now generate 1000 randoms sending orders instead of 100.
+By drawing $1000$ random sending orders, we explore near to $2,5 \%$ of the cases, which seems enough to find as many solutions as if generate more random sending orders.
+
+     We now want to compare the performances of the different algorithms on the way back.
+Since GP showed some excellent results on large periods (see Fig~\ref{fig:success30000}), it is more interesting to focus on the behavior of the algorithms on short periods.
+The following experience is realized on graph with $8$ routes (links between $0$ and $20000$), and with a period of $21000$.
+Since we just conclude that drawing $1000$ sending order is enough, with $8$ routes, we now generate $1000$ randoms sending orders instead of $100$.
 
@@
      The algorithm MS, that does not consider the periodicity for the scheduling is far worst than the others, and, even if GP seems to converge too 100\% of success rate when the flexibility is large enough, MSP is always strictly better.
-We remark that when the flexibility is low ($<500$) there is near to 5\% of failure.
-
- To evaluate the performance of our best algorithm to find solutions, that is, generating $1000$ randoms sending orders and using MSP on the way back, we compared it's performance, against the actual way to manage the messages in a network.
+We remark that when the flexibility is low ($<500$) there is still near to 5\% of failure for MSP.
+
+   Thus, using the Random sending order combined with MSP for the way back seems to be a very good algorithm to solve PALL.
+Nevertheless, there is still a few number of instances in the worst area of parameters (very short period, and very low flexibility), that are impossible to solve with our algorithm.
+
+ To evaluate the performance of our best algorithm to find solutions, that is, generating $1000$ randoms sending orders and using MSP on the way back, we compared it's performance against the actual way to manage the messages in a network.
 Nowadays, the networks are managed through a stochastic model.
 The messages in the nodes are scheduled following a FIFO rule.
-Even if this policy works well, in practice, it does not ensure a minimum latency.
+Even if this policy works well, in practice when the network is not too loaded, it does not ensure a minimum latency.
 Thus, some latency critical applications like C-RAN needs some deterministic algorithms.

### 2017-06-05 code/Sources/main.c

@@ -63,13 +63,13 @@ int main()
 	//Taux de reussite des diferents nombres d'instances générées
 	*****/
 
-	//nombre_random_PALL(8,2500,20000,1000, 20000);
+	nombre_random_PALL(8,2500,20000,1000, 20000);
 
 	/*****
 	Tmax moyen pour sto vs sp
 	*******/
 
-	marge_PALL_stochastique(8,2500,20000,1000,50000);
+	//marge_PALL_stochastique(8,2500,20000,1000,50000);
 
 
 	return 0;

### 2017-06-05 code/Sources/simulations.c

@@ -353,7 +353,7 @@ void nombre_random_PALL(int nb_routes, int taille_paquets,int taille_route, int 
 	int tmax;
 	
 
-	for(int nb_rand=10;nb_rand<= 100000;nb_rand *= 10)
+	for(int nb_rand=1;nb_rand<= 1;nb_rand *= 10)
 	{
 		a=0;
 		#pragma omp parallel for private(res,g,tmax) if (PARALLEL) schedule (static)

### 2017-06-08 article/article.tex
mediane

@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
+\usepackage{authblk}
 
 \graphicspath{{figures/}}
+\makeatletter
+\def\input@path{{figures/}}
+\makeatother
 \newcommand\rmatching{${\cal R}$-matching\xspace}
@@
 %opening
-\title{How to Schedule Periodic Messages in a Network Without Congestion}
+\title{DRAFT : Scheduling Periodic Messages in a Network by a SDN approach}
 %\author{Dominique Barth - UVSQ ,Christian Cadéré - UVSQ,Maël Guiraud - UVSQ,Olivier Marcé - Nokia Bell Labs France,Yann Strozecki - UVSQ}
 
-\author{
-   Dominique {\bf Barth}, {\em UVSQ}
-   \and
-   Christian  {\bf Cad\'er\'e}, {\em UVSQ}
-      \and
-   Ma\"el  {\bf Guiraud}, {\em UVSQ}
-      \and
-   Olivier  {\bf Marc\'e}, {\em Nokia Bell Labs France}
-      \and
-   Yann  {\bf Strozecki}, {\em UVSQ}
-}
+\author[1]{Dominique Barth}
+\author[1]{Christian Cad\'er\'e}
+\author[1]{Ma\"el Guiraud}
+\author[2]{Olivier Marc\'e}
+\author[1]{Yann Strozecki}
+\affil[1]{David Laboratory, UVSQ}
+\affil[2]{Nokia Bell Labs France}
 
@@
  In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network.
-The current solution is to use statistical multiplexing with a traditional queue management in an optical network with a very large bandwidth to minimize latency.
+The current solution is to use stochastic multiplexing with a traditional queue management in an optical network with a very large bandwidth to minimize latency.
 Here we propose to use a deterministic approach to schedule our periodic messages.
@@
 We denote by $\cal R$ a set of routes in $G$ such that no two routes have the same first vertices or the same last vertices.
-The pair $(G,\cal R)$ is called a {\bf routage graph} and represents our network.
+The pair $(G,\cal R)$ is called a {\bf routed network} and represents our network.
 The first vertex of a route models an antenna (RRH) and the last one a data-center (BBU) which processes the messages sent by the antenna.
@@
 
-      A {\bf $(P,\tau)$-periodic assignment} of a routage graph $(G,\cal R)$ is a sequence  ${\cal M}=(m_1, \ldots ,m_n)$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=(m_1, \ldots ,m_n)$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
 The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
@@
 %       Notice that the notion of $P$-periodic assignment \textbf{is not monotone} with regard to $P$. 
-      As an example of a $(2,1)$-periodic assignment, let us consider a routage graph with routes $\{r_{i}\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
+      As an example of a $(2,1)$-periodic assignment, let us consider a routed network with routes $\{r_{i}\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
       We set $\tau = 1$ and the delays are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.
@@
      \end{center}
-       \caption{A routage graph with $(0,0,0)$ as a $(2,1)$-periodic assignment}
+       \caption{A routed network with $(0,0,0)$ as a $(2,1)$-periodic assignment}
       \end{figure}
@@
 
-      \noindent {\bf Input:} a routage graph $(G,\cal R)$, an integer $\tau$ and an integer $P$.
+      \noindent {\bf Input:} a routed network $(G,\cal R)$, an integer $\tau$ and an integer $P$.
 
@@
 
-      An unusual property of assignment is that given a routage graph, we may have a $(P,\tau)$-periodic assignment but no
+      An unusual property of assignment is that given a routed network, we may have a $(P,\tau)$-periodic assignment but no
       $(P',\tau)$-periodic assignment with $P' > P$: the existence of an assignment is not monotone with regards to $P$.
@@
 	\begin{lemma} \label{lemma:monotonic}
-	 For any odd $P$, there is a routage graph such that there is $(2,1)$-periodic assignment but no $(P,1)$-periodic assignment.
+	 For any odd $P$, there is a routed network such that there is $(2,1)$-periodic assignment but no $(P,1)$-periodic assignment.
 	\end{lemma}
@@
 
-      Consider the routage graph $(G,{\cal R})$ given in the previous subsection. 
+      Consider the routed network $(G,{\cal R})$ given in the previous subsection. 
       We change the delays so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
@@
       In the context of cloud-RAN applications, we need to send message from a RRH $s$ to a BBUs $\rho(s)$ and then 
-      we must send the answer from $\rho(s)$ back to $s$. We say that a routage graph $(G, {\cal R})$ is \textbf{symmetric}
+      we must send the answer from $\rho(s)$ back to $s$. We say that a routed network $(G, {\cal R})$ is \textbf{symmetric}
       if for all route $r$ with first vertex $s$ and last vertex $target(s)$ there is a route $r'$ with first vertex $target(s)$
@@
          We now give a new interpretation of a $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routing graph, so that it represents the sending of a message and of its answer.
-	This assignment represents the following process: first a message is sent at $s$, through the route $r$, at time $m$.
+	This assignment represents the following process: first a message is sent at $s$, through the route $r$, at time $m_s$.
 
@@
 
-      \noindent {\bf Input:}  A symmetric routage graph $(G,{\cal R})$, a period $P$, an integer $\tau$, an integer $T_{max}$.
+      \noindent {\bf Input:}  A symmetric routed network $(G,{\cal R})$, a period $P$, an integer $\tau$, an integer $T_{max}$.
 
@@
  We will prove the hardness of PRA and PALL for $\tau =1$ which implies the hardness of the general problems. 
-Consider an instance of the problem PRA, i.e., a routage graph $(G,\cal{R})$ and a period $P$.
+Consider an instance of the problem PRA, i.e., a routed network $(G,\cal{R})$ and a period $P$.
 The {\bf conflict depth} of a route is the number of other routes which share an edge with it. 
-The conflict depth of a routage graph $(G,\cal{R})$ is the maximum of the conflict depth of the routes in $\cal{R}$.
-The {\bf load} of a routage graph is the maximal number of routes sharing the same arc.
+The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of the routes in $\cal{R}$.
+The {\bf load} of a routed network is the maximal number of routes sharing the same arc.
 Remark that a $(P,1)$-periodic assignment must satisfy that $P$ is larger or equal to the load.
@@
  Let us define $T_{max} = 2 \times \max_{r \in {\cal R}} \lambda(r) + P$.
-We define $(G',{\cal R}')$ a symmetric routage graph from $(G,{\cal R})$ where for every route we add a symmetric route with new arcs of opposite orientation and the same weights.
+We define $(G',{\cal R}')$ a symmetric routed network from $(G,{\cal R})$ where for every route we add a symmetric route with new arcs of opposite orientation and the same weights.
  The instance $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL if and only if $((G,{\cal R}),P,\tau)$ is in $PRA$.
@@
 
-Let MIN-PRA be the problem, given a routage graph and an assignment, to find the minimal period $P$ such that there is a $P$-periodic assignment.
+Let MIN-PRA be the problem, given a routed network and an assignment, to find the minimal period $P$ such that there is a $P$-periodic assignment.
 
@@
       The routes are the directed paths $r_i = s_i,c_s,c_t,t_i$ and $\rho(r_i) = t_i,c_t,c_s,s_i$ which defines a 
-      symmetric routage graph.
+      symmetric routed network.
 
@@
       We will refer to the period at $c_s$ as the {\bf forward period}, and the period at $c_t$ as the {\bf backward period}.
-A message issued on the route $r$ at time $m_r$ will reach $c_s$ at time $m_{r} + t(c_s,r) \mod P$ in the forward period.
-If the offset of $\rho(r)$ is $m_\rho(r)$, the answer will reach $c_t$ at time $m_{\rho(r)} + t(c_t,\rho(r))\mod P$ in the backward period.
+A message issued on the route $r$ at time $m_s$ will reach $c_s$ at time $m_{s} + t(c_s,r) \mod P$ in the forward period.
+If the offset of $\rho(s)$ is $m_{\rho(s)}$, the answer will reach $c_t$ at time $m_{\rho(s)} + t(c_t,\rho(r))\mod P$ in the backward period.
 
@@
   In that case $MT({\cal M})$ is equal to twice the delay of the longest route, thus $T_{max}$ is not relevant anymore. 
-  Since $w_i=0$, choosing $m_i$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + \lambda(r_i) \mod P$.
+  Since $w_i=0$, choosing $m_{s_i}$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_{s_i} + \lambda(r_i) \mod P$.
   Remark that there is a bijection between the assignments of a star topology and the 
-  assignments of the same star topology where all arcs from $s_i$ to $c_s$ have weight equal to $0$ by changing $m_i$ into $m_i - t(c_s,r_i) \mod P$.
+  assignments of the same star topology where all arcs from $s_i$ to $c_s$ have weight equal to $0$ by changing $m_{s_i}$ into $m_{s_i} - t(c_s,r_i) \mod P$.
 Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
@@
     The message are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
-    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{i}$ the offset of $r_i$ to $(i-1)\tau$. We call this algorithm {\bf Shortest-Longest}.
+    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{s_i}$ the offset of $r_i$ to $(i-1)\tau$. We call this algorithm {\bf Shortest-Longest}.
 
@@
       \begin{proof}
-       Since $m_{i} = (i-1)\tau$, $[t(c_s,r_{i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.
+       Since $m_{s_i} = (i-1)\tau$, $[t(c_s,r_{i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.
 
@@
 the route $0$ is the longest, and the route $n-1$ is the shortest one.
-	The messages are sent in the forward period from $0$ to $n-1$, that is $m_{s_i} = \tau * i$.
+	The messages are sent in the forward period from the route $0$ to $n-1$, that is $m_{s_i} = \tau * i$.
 	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is $PT(s_0) = 2.\lambda(r_{s_0}) $.
@@
     \begin{algorithmic}
-    \REQUIRE routage graph $(G,{\cal R})$, period $P$, $ T_{max}$, packet size $\tau$
+    \REQUIRE routed network $(G,{\cal R})$, period $P$, $ T_{max}$, packet size $\tau$
     \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$
@@
 Then, the main scheduling routines is applied again.
-Some stopping conditions are able to detect if there is no solution for the given routage graph.
+Some stopping conditions are able to detect if there is no solution for the given routed network.
 
@@
     \begin{algorithmic}
-    \REQUIRE A routage graph $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
+    \REQUIRE A routed network $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
     \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$, if it exists
@@
     This algorithm runs in $\mathcal{O}(n^3\log{}n)$.
-For every routes of the routage graph, the algorithm fixes the first route to comeback, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(determined by $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).
+For every routes of the routed network, the algorithm fixes the first route to comeback, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(determined by $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 
@@
 The following table present the average success rate of each number of sending orders, on $1000$ instances.
-       \begin{figure}
+       \begin{figure}[H]
 
@@
 
-    \begin{figure} 
+    \begin{figure} [H] 
        \begin{center}
@@
 
-     The algorithm MS, that does not consider the periodicity for the scheduling is far worst than the others, and, even if GP seems to converge too 100\% of success rate when the flexibility is large enough, MSP is always strictly better.
-We remark that when the flexibility is low ($<500$) there is still near to 5\% of failure for MSP.
+     The algorithm MS, that does not consider the periodicity for the scheduling is far worst than the others, and, even if GP seems to converge too $100\%$ of success rate when the flexibility is large enough, MSP is always strictly better.
+We remark that when the flexibility is low ($<500$) there is still near to $5\%$ of failure for MSP.
 
@@
 Then we simulate the behavior of a stochastic network during a great number of periods.
-The following figure shows the average latency of a stochastic network, compared to the latency of our algorithm.
-We tested the algorithms on $1000$ instances with $8$ long routes (links between $0$ and $20000$).
-The flexibility of the stochastic curve is computed by taking the message which have the highest process time, at which we subtract the delay of the longest route.
-We made a linear search to find the minimum flexibility needed by our algorithm to find a solution.
- We measure the average flexibility, for periods from $20000$ ( network fully loaded), to $50000$ (40 \% of load).
-
-    \begin{figure}
-
-       \begin{center}
-      \includegraphics[scale=0.4]{stochastic.pdf}
-      \end{center}
-      \caption{Average latency, depending on the load of the network.}
+
+We simulated a stochastic network on $1000$ instances with $8$ long routes (links between $0$ and $20000$).
+The results are not really different if we use short routes.
+The flexibility needed by an instance of the network is computed by taking the message which have the highest process time, at which we subtract the delay of the longest route.
+We measure, for periods from $20000$ ( network fully loaded), to $50000$ ($40 \%$ of load), the medians, the first, and the third quartiles of $1000$ results.
+
+    \begin{figure}[H]
+
+       \begin{center}
+     % \includegraphics[scale=0.4]{stochastic.pdf}
+       \input{figures/stochastic}
+      \end{center}
+      \caption{Needed flexibility on stochastic networks according to the load.}
+      \label{fig:sto}
      \end{figure}
 
-    As expected, our algorithm gives some very satisfying results.
-There is a few cases when both the flexibility and the period are too restricted in which there is no solutions, but those case are impossible in practice.
-Furthermore, the stochastic policy can not ensure a minimal latency.
-In our context, this is crucial to use some deterministic algorithms to manage the messages in the network.
+    We also made a linear search to find the minimum flexibility needed by our algorithm on those loads to find a solution.
+There are few cases, when both the flexibility and the period are too restricted in which there is no solutions: with a period of $20000$, our algorithm needs in average $\simeq 80$ slots of flexibility to find a solution.
+Otherwise, the algorithm finds a solution with $0$ flexibility for every periods $>20000$.
+On the other hand, the stochastic policy does not ensure a minimal latency.
+As we can see in Fig~\ref{fig:sto}), the more the network is loaded, the higher the latency is.
+Even if the first quartile is to $0$ when the network is not highly loaded, many instances needs some flexibility.
+Moreover, the latency is not guaranteed with that policy.
+Indeed, even if half of the cases of our simulations works with less than $1000$ slots of flexibility on a light loaded network, that could be reasonable for specific applications, $25\%$ of the cases needs more than $2000$ slots of flexibility.
+With our algorithm, we control the latency, and here, we have optimal solutions that makes it really appropriate.
 
@@
 \bibliographystyle{ieeetr}
-\bibliography{Sources.bib}
+\bibliography{Sources}
 

### 2017-06-08 code/Calculs autres/ecart_type.c

@@ -1,0 +1,208 @@
+#include <stdio.h> 
+#include <stdlib.h>
+#include <math.h>
+
+#define taille 1000
+#define nb_periodes 30
+
+int donnes[nb_periodes][taille];
+float moyennes[nb_periodes];
+float en[nb_periodes];
+float ep[nb_periodes];
+
+
+
+//trié de la plus courte a la plus longue
+void tri_bulles(int* tab,int t)
+{
+	int sorted;
+	int tmp;
+
+	for(int i=t-1;i>=1;i--)
+	{
+		sorted = 1;
+		for(int j = 0;j<=i-1;j++)
+		{
+			if(tab[j+1]<tab[j])
+			{
+				tmp = tab[j+1];
+				tab[j+1]= tab[j];
+				tab[j]= tmp;
+				sorted = 0;
+			}
+		}
+		if(sorted){return;}
+	}
+
+}
+
+
+
+
+void lire_fichier()
+{
+	FILE * f = fopen("donnes_random_marge.data","r");
+	int trash;
+	for(int i=0;i<nb_periodes;i++)
+	{
+		for(int j=0;j<taille;j++)
+		{
+			fscanf(f,"%d %d",&trash,&donnes[i][j]);
+
+		}
+	}
+	fclose(f);
+
+}
+float moyenne(int numero_periode)
+{
+	float moy = 0;
+	for(int i=0;i<taille;i++)
+	{
+		moy += donnes[numero_periode][i];
+	}
+	return moy/taille;
+}
+float ecart_type_negatif(int numero_periode)
+{
+	float e = 0;
+	int t;
+	for(int i=0;i<taille;i++)
+	{
+		if(donnes[numero_periode][i] < moyennes[numero_periode])
+		{
+			e += ((donnes[numero_periode][i]-moyennes[numero_periode])*((donnes[numero_periode][i]-moyennes[numero_periode])));
+			t++;
+		}
+	}
+
+
+	e /= t;
+
+	return sqrt(e);
+}
+float ecart_type_positif(int numero_periode)
+{
+	float e = 0;
+	int t;
+	for(int i=0;i<taille;i++)
+	{
+		if(donnes[numero_periode][i] > moyennes[numero_periode])
+		{
+			e += ((donnes[numero_periode][i]-moyennes[numero_periode])*((donnes[numero_periode][i]-moyennes[numero_periode])));
+			t++;
+		}
[…]

### 2017-06-08 code/Calculs autres/grouped_violinplots.py

@@ -1,0 +1,49 @@
+import seaborn as sns
+sns.set(style="whitegrid", palette="pastel", color_codes=True)
+
+# Load the example tips dataset
+tips = sns.load_dataset("tips")
+
+# Draw a nested violinplot and split the violins for easier comparison
+plot = sns.violinplot(x="day", y="total_bill", hue="sex", data=tips, split=True,
+               inner="quart", palette={"Male": "b", "Female": "y"})
+sns.despine(left=True)
+
+fig = plot.get_figure()
+fig.savefig('gender_salary.png')
+'''
+from numpy import *
+import seaborn as sns
+
+
+file_data='donnes_random.data'
+ 
+ 
+# ouverture du fichier texte 
+f=open(file_data,'r')
+lignes =f.readlines()
+
+
+
+tableau = []
+
+for ligne in lignes:
+	ligne = str(ligne).split(" ")
+	tableau2 = []
+	tableau2.append(int(ligne[0]) )
+	tableau2.append(int(ligne[1].split("\\")[0]) )
+	tableau.append(tableau2 )
+
+
+
+
+sns.set(style="whitegrid", palette="pastel", color_codes=True)
+
+# Load the example tips dataset
+tips = sns.load_dataset("tips")
+
+# Draw a nested violinplot and split the violins for easier comparison
+sns.violinplot(x="day", y="total_bill", hue="sex", data=tableau)
+sns.despine(left=True)
+
+'''

### 2017-06-08 code/Sources/main.c

@@ -63,13 +63,13 @@ int main()
 	//Taux de reussite des diferents nombres d'instances générées
 	*****/
 
-	nombre_random_PALL(8,2500,20000,1000, 20000);
+	//nombre_random_PALL(8,2500,20000,1000, 20000);
 
 	/*****
 	Tmax moyen pour sto vs sp
 	*******/
 
-	//marge_PALL_stochastique(8,2500,20000,1000,50000);
+	marge_PALL_stochastique(8,2500,20000,1000,50000);
 
 
 	return 0;

### 2017-06-08 code/Sources/simulations.c

@@ -1,6 +1,8 @@
 #include <stdio.h>
 #include <stdlib.h>
 #include <omp.h>
+#include <limits.h>
+#include <math.h>
 
 #include "struct.h"
 #include "PAZL.h"
@@ -409,10 +411,14 @@ void marge_PALL_stochastique(int nb_routes,int taille_paquets,int taille_route, 
 
 	char nom[64];
 	sprintf(nom,"../datas/marge_PALL_stochastique.data");
+
 	FILE * F = fopen(nom,"w");
+	FILE * F2 = fopen("../datas/donnes_random.data","w");
 	Graphe g ;
 	long long int total_sto,total_sp;
+	float ecart_type;
 	int ressto;
+	int min,max;
 	int ressp;
 	int nb_rand = 100;
 
@@ -421,6 +427,9 @@ void marge_PALL_stochastique(int nb_routes,int taille_paquets,int taille_route, 
 	{
 		total_sto = 0;
 		total_sp = 0;
+		ecart_type =0;
+		min = INT_MAX;
+		max = 0;
 	
 		#pragma omp parallel for private(ressp,ressto,g) if (PARALLEL) schedule (static)
 		for(int i = 0;i<nb_simuls;i++)
@@ -429,29 +438,52 @@ void marge_PALL_stochastique(int nb_routes,int taille_paquets,int taille_route, 
 			graphe_etoile(g,taille_route);
 	
 
-		 	ressp = linear_simons_per(g, periode, taille_paquets,nb_rand);
+		 	///ressp = linear_simons_per(g, periode, taille_paquets,nb_rand);
+		 	ressp = 0;
 		 	#pragma omp atomic
 				total_sp+= ressp;
 
 			ressto=stochastic(g,taille_paquets,periode,1000,1);
-			ressto -=  longest_route(g);
-				#pragma omp atomic
-					total_sto+= ressto;
-			
-			
+			//ressto -=  longest_route(g);
+
+			#pragma omp atomic
+				total_sto+= ressto;
+
+			#pragma omp atomic
+				ecart_type += (ressto * ressto);
+			#pragma omp critical
+			{
+				if(ressto < min)
+				{
+						min = ressto;
+				}
+			}
+			#pragma omp critical
+			{
+				if(ressto>max)
+				{
+						max = ressto;
+				}
+			}
+			fprintf(F2,"%d %d\n",periode,ressto);
[…]

### 2017-06-15 article/article.tex
article repris

@@
 %opening
-\title{DRAFT : Scheduling Periodic Messages in a Network by a SDN approach}
+\title{DRAFT : Periodic Scheduling Messages in a Network by a SDN (deterministic) approach}
 %\author{Dominique Barth - UVSQ ,Christian Cadéré - UVSQ,Maël Guiraud - UVSQ,Olivier Marcé - Nokia Bell Labs France,Yann Strozecki - UVSQ}
 
+\author[1]{Ma\"el Guiraud}
 \author[1]{Dominique Barth}
 \author[1]{Christian Cad\'er\'e}
-\author[1]{Ma\"el Guiraud}
+\author[2]{Brice Leclerc}
 \author[2]{Olivier Marc\'e}
@@
 \begin{abstract}
-We study the sending of periodic messages in a graph following predefined paths, a problem arising from the communication between radio antennas and their signal processing units located in distant data-centers.
-The messages must be sent deterministically to avoid collisions on the network and thus to minimize the latency.
-We prove that the problem is $\NP$-complete even for very restricted graphs.
+We study the sending of periodic messages in a graph following predefined paths, a problem arising from communication between radio antennas and their signal processing units located in distant data-centers.
+Messages must be sent deterministically to avoid collisions on the network and thus to minimize the latency.
+We prove that problems related to this context are $\NP$-complete even for very restricted graphs.
 We then deal with the case of a star graph and for different regimes of the parameters we propose algorithms that are experimentally shown to work extremely well
@@
  In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network.
-The current solution is to use stochastic multiplexing with a traditional queue management in an optical network with a very large bandwidth to minimize latency.
+The current solution is to use stochastic multiplexing \todo{ref} with a traditional queue management in an optical network with a very large bandwidth to minimize latency.
 Here we propose to use a deterministic approach to schedule our periodic messages.
@@
 
- The network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs).
-The time is discretized and a unit of time corresponds to the transmission of a minimal unit of data over the network.
- The process must be periodic, that is if we look at the network at time $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
+Let us expose briefly our model: the network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs).
+Time is discretized and a unit of time corresponds to the transmission of a minimal unit of data over the network.
+ The process must be periodic, that is if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
 Moreover, we want to avoid any  buffering in internal nodes of the graph.
@@
 Several graph colorings have been introduced to model similar problems such as the allocation of frequencies~\cite{borndorfer1998frequency}, bandwidths~\cite{erlebach2001complexity} or routes~\cite{cole1996benefit} in a network or train schedules~\cite{strotmann2007railway}.
-Unfortunately, they do not take into account the periodicity and the associated problems are also $\NP$-complete.
+Unfortunately, they do not take into account the periodicity of the scheduling and the associated problems are also $\NP$-complete.
 The only model which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple, zhu2001circular,zhu2006recent} but is not expressive enough to capture our problem.
@@
 In Sec.~\ref{sec:complexity}, we prove that the problem PRA and PALL are $\NP$-hard and cannot be approximated even for very
-restricted graphs. 
+restricted classes of graphs. 
 Therefore in the next two sections, we study a simple but very common topology, that we call the
-star topology, on which the messages can collide on only one arc.
+star topology, where messages can collide on only one arc.
 In Sec.\ref{sec:PAZL}, we study a variant of PALL called PAZL  where the waiting times must all be zero.
@@
 The network is modeled as a directed graph $G=(V,A)$.
-Each arc  $(u,v)$ in $A$ is labeled by an integer $dl(u,v) \geq 1$ that we call the delay and which represents the time slots taken by a signal to go from $u$ to $v$ using this arc.
+Each arc  $(u,v)$ in $A$ is labeled by an integer $\omega(u,v) \geq 1$ which represents the time slots taken by a signal to go from $u$ to $v$ using this arc.
 A {\bf route} $r$ in $G$ is a path, that is sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
@@
 We will always consider that the $m_{i}$ are between $0$ and $P-1$.
-A $(P,\tau)$-periodic assignment must have no {\bf collision} between two routes in $\cal R$, that is $\forall (r_{i}, r_{j}) \in {\cal R}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
+A $(P,\tau)$-periodic assignment must have no {\bf collision} between two routes in $\cal R$, that is $\forall (r_{i}, r_{j}) \in {\cal R}^2, sharing and edge $(u,v)$ i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
       we have $$[t(u,r_{i})] \cap [t(u,r_{j})] = \emptyset .$$
@@
       is set to $0$, therefore we assume from now on it is indeed $0$.
-      Collisions between messages can only appear at node $c_s$ on the way forward and at node $c_t$ on the way back.
+      Collisions between messages can only appear in the arcs after node $c_s$ on the way forward and after node $c_t$ on the way back.
       Thus, we only have to check if there is no collisions in a given period at those two vertices.
-      We will refer to the period at $c_s$ as the {\bf forward period}, and the period at $c_t$ as the {\bf backward period}.
+      We try to schedule the messages such that they can pass thought the common arcs in a time window of $P$ max.
+We define the {\bf forward period}, a time window of size P at the beginning of the arc after $c_s$, and the {\bf backward period} the one at the beginning of the arc after $c_t$.
 A message issued on the route $r$ at time $m_s$ will reach $c_s$ at time $m_{s} + t(c_s,r) \mod P$ in the forward period.
@@
 
-      A $(P,\tau)$-periodic assignment is the choice for all $i < n$, of $m_{r_i}$ and $m_{\rho(r_i)}$ such that, for any couple $(i\neq j)$, we have $[t(c_s,r_{i})] \cap [t(c_s,r_{j})] = \emptyset$ and $[t(c_t,\rho(r_i))] \cap [t(c_t,\rho(r_j))] = \emptyset$.
+      A $(P,\tau)$-periodic assignment is then a choice for all $i < n$, of $m_{r_i}$ and $m_{\rho(r_i)}$ such that, for any couple $(i\neq j)$, we have $[t(c_s,r_{i})] \cap [t(c_s,r_{j})] = \emptyset$ and $[t(c_t,\rho(r_i))] \cap [t(c_t,\rho(r_j))] = \emptyset$.
 
@@
 
-  We propose two algorithms that always find a solution in polynomial time if the instances meets some criteria (short routes or great enough period) but which may fail in other cases and one exponential algorithm which always finds a solution if it exists.
+  We propose two algorithms that always find a solution in polynomial time if instances meets some criteria (short routes or great enough period) but which may fail in other cases and one exponential algorithm which always finds a solution if it exists.
 
@@
     We first present a simple policy, which works when the period is large with regards to the delay of the routes.
-    The message are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
+    The messages are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
     In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{s_i}$ the offset of $r_i$ to $(i-1)\tau$. We call this algorithm {\bf Shortest-Longest}.
@@
     we can always find a solution when the network is far from saturated.
+This algorithm defines an upper bound for the period.
+As a reminder, the lower bound is $n\tau$, that is, the size taken by the messages to be emitted.
 
@@
 On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time.
-We will compare the performance of the algorithms in two different regimes: the routes are either short with regards to $\tau$ and $P$ or unrestricted.
-      We choose the parameter realistic with regard to our C-RAN context. The number of routes 
+We will compare the performance of the algorithms in two different regimes: routes are either short with regards to $\tau$ and $P$, or unrestricted.
+      We choose the following realistic parameters with regard to our C-RAN context. The number of routes 
       is at most $n = 20$, $\tau$ is equal to $2500$ and the period is at most $3n\tau$ (otherwise the greedy algorithm always returns a solution).
@@
       minimal period for which a $(P,\tau)$ periodic assignment can be found by each algorithm. 
-      To that end we do a linear search on $P$, since a dichotomy would not work because of Lemma~\ref{lemma:monotonic}.
+      To that end we use linear search on $P$, since a dichotomy method would not work because of Lemma~\ref{lemma:monotonic}.
 
@@
 
-    In this section, we allow the messages to wait in the target vertices (BBU), to give an higher degree of freedom to the scheduling.
-Thus, the process time of a message $PT$ might be superior to $T_{max}$.
+    In this section, we still work on the start topology, but, from now, we allow the messages to wait in the target vertices (BBU),in order to give an higher degree of freedom to the scheduling.
+Thus, the process time  $PT$ of a message might be superior to $T_{max}$.
 The goal is to find a solution with waiting time such that any message will be not be buffered too much, i.e.
@@
 	 \begin{theorem}
-      There is always an optimal solution when all the weights on the arcs between $c_s$ and the sources are the same.
+      Instances of PALL with $\omega(c_t,t_i) = 0, \forall i \leq n$ always got an optimal solution.
       \end{theorem}
@@
 
-	To solve PALL, we propose some heuristics that prioritize the longest routes, and thus helps to minimize $PT(s_i)$.
+	To solve PALL, the goal is to not associate a too long waiting time $w_i$ to the longest routes .
+We propose some heuristics that prioritize the longest routes, and thus helps to minimize the process time $PT(s_i)$ of the routes in order to have no  $PT(s_i) > T_{max}$.
 Indeed, one can imagine that, if the messages on the longest routes are less buffered in their target than the messages using the shortest routes, the process times might be balanced.
-	In an optimal solution, if $i$ is the longest route, we want $w_i =0$, such that $PT(s_i) = 2.\lambda(r_{s_i}) \geq  2.\lambda(r_{s_j}) + w_j = PT(s_j) $, where $j$ is any route $\neq i$.
-
-     We first suggest the following heuristic:
-
-      On the forward period, for the way forward, the messages are scheduled so that they are following each others, from the one using the longest route, to the one using the shortest route.
+	In an optimal solution, if $r_i$ is the longest route, we want $w_i =0$, such that $PT(s_i) = 2.\lambda(r_{s_i}) \geq  2.\lambda(r_{s_j}) + w_j = PT(s_j) $, where $j$ is any route $\neq i$.
+
+     We first suggest the following heuristic, composed of two greedy parts.
+First, on the forward period, for the way forward, the messages are scheduled consecutively, from the one using the longest route, to the one using the shortest route.
 Thus, we set the $m_{s_i}$ of the routes such that  $t(c_s,r_{s_i}) = \tau.i$, if the routes $r_{s_i}$ are ordered from the longest to the shortest.
 
-      On $c_t$, the algorithm is the following one:
+     Thus, to schedule the messages on the backward period, we assign to each route it's deadline, equal to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$, that is,  the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
+     We then determine the eligible message.
+At a date $d$, if one or several messages are able to come back to $c_t$ before $d$, the eligible route is the one which have the lowest deadlines.
+Otherwise, if any messages are able to be back on $c_t$ before $d$, the eligible route is the one with the first message able to come back to $c_t$.
 
     \begin{algorithm}[H]
-
-    \caption{Eligible route}
-    \label{algorithm:Eligible}
-    \begin{enumerate}
-
-      \item To be eligible, a message needs to be able to come back on $c_t$ at the current clock (if clock = $0$, or no messages are able to come back at this date, take the first message able to come back).
-      \item Between the eligible messages, schedule first the one which has the lowest deadline.
-      \item For any route i, the deadline correspond to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$, that is,  the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
-
-      \end{enumerate}
-
-  \end{algorithm}
-
-    \begin{algorithm}[H]
-    \caption{Longest Shortest Greedy (LSG)}
+    \caption{Longest Shortest + Greedy }
     \begin{algorithmic}
@@
 
+\STATE compute the deadlines of each routes.
+
     \WHILE{there is a route which has not been scheduled}
-    \STATE take i such that $r_{t_i}$ is the eligible route (Algorithm \ref{algorithm:Eligible})
-    \IF{ the messages is able to come back before $clock$}
+    \STATE determine $r_{t_i}$ the eligible route
+    \IF{ $t(c_t,r{t_i}) < clock$}
     \STATE $w_i = clock - t(c_t,r_{t_i}) - (m_i + \lambda(r_i))$ 
@@
 
-	We tried to look at the behavior of the that policy with different kinds of sending order for the messages.
-
-	We tried the five following sending orders, each ones determines the order in which the messages will be sent from sources, and, in each case the messages are following each others in $c_s$.
+	We tried to look at the behavior of that policy with different kinds of sending order for the messages.
+
+	We tried the five following sending orders, each one determines the order in which messages will be sent from sources. In every case the messages are consecutive.
 
@@
      In the rest of the section, we present the  different algorithms suggested to improve the second part of the scheduling.
-      \subsection{About the periodicity}
+      \subsection{About periodicity}
      The previous algorithm is a greedy heuristic, which does not take the period into account. 
@@
 
-     The problem PALL is very similar to a scheduling problem, but many scheduling problem does not treat about the periodic aspect.
-Thus, the article ``A fast algorithm for single processor scheduling'', by Barbara Simons \cite{simons1978fast} gave us an optimal algorithm to schedule some jobs which has a release time, a deadline and the same execution time.
+     Problem PALL is very similar to a scheduling problem, but many scheduling problems do not consider the periodic aspect.
+The article \cite{simons1978fast} from Simons, schedule jobs which all have the same execution time.
+     This algorithm takes as input some jobs defined by a triplet id-release-deadlines, and an execution time for all jobs.
+A job is not able to be computed before it's release time, and must be finished before it's deadline.
+This algorithm gives in $\mathcal{O}(n^2\log{}n)$ a solution with the earliest  possible completion time, if it exists.
      We adapted this algorithm, considering the messages as the jobs, the release times as the date at which the messages are able to come back on $c_t$, and the deadlines as the latest date at which a message have to leave $c_t$ to comeback before $m_i + T_{max}$.
-This algorithm gives in $\mathcal{O}(n^2\log{}n)$ a solution with the earliest  possible completion time, if it exists.
 Thus, it tries to minimize the time between the first and the last message in the scheduling.
@@
 
-     This algorithm uses the exact same main scheduling than Greedy.
-Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call {\em crisis message} this message), the algorithm call a subroutine which, following some criteria, removes some previous messages from the scheduling such that the crisis message can be scheduled earlier.
+    % MS uses the exact same main scheduling than Greedy.
+Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call {\em crisis message} this message), the algorithm calls a subroutine which, following some criteria, removes some previous messages from the scheduling such that the crisis message can be scheduled earlier.
 Then, the main scheduling routines is applied again.
@@
     \STATE  $w_i \leftarrow 0$
-    \STATE $end-period \leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
+    \STATE period-end $\leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
     \FORALL{route $r_{t_j}$}
-    \STATE $deadline-route \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
-    \STATE $deadline \leftarrow (deadline-route,end-period)$
+    \STATE deadline-route$ \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
+    \STATE $deadline \leftarrow$ min(deadline-route,period-end)
     \ENDFOR

### 2017-06-15 code/Calculs autres/file.c

@@ -1,0 +1,12 @@
+#include <stdio.h> 
+#include <stdlib.h>
+#include <math.h>
+
+int main()
+{
+	
+	FILE * f = fopen("nb.data","w");
+	for(int i=1;i<257;i++)fprintf(f,"%d ",i);
+	fclose(f);
+
+}

### 2017-06-19 article/article.tex
partie 5 lundi soir

@@
       As an example of a $(2,1)$-periodic assignment, let us consider a routed network with routes $\{r_{i}\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
-      We set $\tau = 1$ and the delays are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.
+      We set $\tau = 1$ and the weight are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.
 
@@
       Consider the routed network $(G,{\cal R})$ given in the previous subsection. 
-      We change the delays so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
+      We change the weights so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
       we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$.
@@
 they represent the latency of physical links, it is easy to adapt the proof.
-We just have to set them so that in any route the delay at $u_1$ is equal to $d$ and thus equal to $0$ modulo $d$.
+We just have to set them so that in any route the weight at $u_1$ is equal to $d$ and thus equal to $0$ modulo $d$.
 We now lift this hardness result to the problem PALL.
@@
  We define ${\cal R}$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
- Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an edge in $H$; this arc is the only one shared by these two routes. All arcs are of delay $0$.
+ Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an edge in $H$; this arc is the only one shared by these two routes. All arcs are of weight $0$.
 
@@
       Thus, we only have to check if there is no collisions in a given period at those two vertices.
-      We try to schedule the messages such that they can pass thought the common arcs in a time window of $P$ max.
+      We try to order the messages such that they can pass thought the common arcs in a time window of $P$ max.
 We define the {\bf forward period}, a time window of size P at the beginning of the arc after $c_s$, and the {\bf backward period} the one at the beginning of the arc after $c_t$.
@@
   We ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$} and we call this restricted problem {\bf Periodic Assignment for Zero Latency} or PAZL. 
-  In that case $MT({\cal M})$ is equal to twice the delay of the longest route, thus $T_{max}$ is not relevant anymore. 
+  In that case $MT({\cal M})$ is equal to twice the weight of the longest route, thus $T_{max}$ is not relevant anymore. 
   Since $w_i=0$, choosing $m_{s_i}$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_{s_i} + \lambda(r_i) \mod P$.
@@
 
-    We first present a simple policy, which works when the period is large with regards to the delay of the routes.
+    We first present a simple policy, which works when the period is large with regards to the weight of the routes.
     The messages are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
@@
 
-    In this section, we still work on the start topology, but, from now, we allow the messages to wait in the target vertices (BBU),in order to give an higher degree of freedom to the scheduling.
-Thus, the process time  $PT$ of a message might be superior to $T_{max}$.
-The goal is to find a solution with waiting time such that any message will be not be buffered too much, i.e.
-$MT({\cal M}) \leq T_{max}$.
+    In this section, we still work on the start topology, but, from now, we allow the messages to wait in the target vertices (BBU),in order to find some solution that we cannot find with PALL.
+From now, the process times  $PT$ of the routes can be greater than twice the weight of the routes, but it might not be superior to $T_{max}$.
 
@@
 	One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the same and so can be simplified by $0$.
-In that case, the scheduling in the forward and backward period is the same.
+In that case, the order of the messages in the forward and backward period is the same.
 The trivial solution is to send all message following each others regardless the order.
@@
 Furthermore, all the waiting times are equal to $0$ i.e.
-$w_i = 0,\forall i \in n$, thus, $MT({\cal M})$ is equal to twice the delay of the longest route, that is not alterable.
+$w_i = 0,\forall i $, thus, $MT({\cal M})$ is equal to twice the weight of the longest route, that is not alterable.
 
@@
 	 \begin{theorem}
-      Instances of PALL with $\omega(c_t,t_i) = 0, \forall i \leq n$ always got an optimal solution.
-      \end{theorem}
+     There is always a solution with $MT({\cal M}) < T_{max}$ when  $ \forall (i,j), \omega(s_i,c_s) = \omega (s_j,c_s)$      \end{theorem}
       \begin{proof}
 
-	Since we can simplify the weight on the arcs between $c_s$ and the sources by $0$, we consider only the delay between $c_t$ and the targets.
+	Since we can simplify the weight on the arcs between $c_s$ and the sources by $0$, we consider only the weight between $c_t$ and the targets.
 Order the routes such that $\lambda(r_{s_i}) > \lambda(r_{s_j}), i<j$, i.e.
@@
 	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is $PT(s_0) = 2.\lambda(r_{s_0}) $.
-	The second message is eligible in the backward period at time $\tau + 2.\lambda(r_{s_1})$.
-Thus, the waiting time of the second route is $w_{s_1} = 2.\lambda(r_{s_0})+\tau - (\tau + 2.\lambda(r_{s_1})) = 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))$.
+	The second message is able to reach the backward period at time $\tau + 2.\lambda(r_{s_1})$.
+Thus, the waiting time of the second route is $w_1 = 2.\lambda(r_{s_0})+\tau - (\tau + 2.\lambda(r_{s_1})) = 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))$.
 Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))  = 2.\lambda(r_{s_0})  = PT(s_0)$.
@@
 
-	Consequently, for this case, sending the message from the one using the longest route to to one using the shortest route is optimal, because the longest route has no waiting time all the other routes has the exact same process time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) $.
+	Consequently, for this case, sending the message from the one using the longest route to to one using the shortest route is optimal, because the longest route has no waiting time, and all the other routes have the exact same process time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) $.
 Moreover, the period used is exactly $n \tau$, in both the forward and backward periods.
@@
 
-	To solve PALL, the goal is to not associate a too long waiting time $w_i$ to the longest routes .
-We propose some heuristics that prioritize the longest routes, and thus helps to minimize the process time $PT(s_i)$ of the routes in order to have no  $PT(s_i) > T_{max}$.
+	To solve PALL, we propose some heuristics that prioritize the longest routes, and thus helps to minimize the process time $PT(s_i)$ of the routes in order to have no  $PT(s_i) > T_{max}$.
 Indeed, one can imagine that, if the messages on the longest routes are less buffered in their target than the messages using the shortest routes, the process times might be balanced.
@@
      We first suggest the following heuristic, composed of two greedy parts.
-First, on the forward period, for the way forward, the messages are scheduled consecutively, from the one using the longest route, to the one using the shortest route.
+First, on the forward period, the messages are ordered consecutively, from the one using the longest route, to the one using the shortest route.
 Thus, we set the $m_{s_i}$ of the routes such that  $t(c_s,r_{s_i}) = \tau.i$, if the routes $r_{s_i}$ are ordered from the longest to the shortest.
 
-     Thus, to schedule the messages on the backward period, we assign to each route it's deadline, equal to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$, that is,  the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
-     We then determine the eligible message.
-At a date $d$, if one or several messages are able to come back to $c_t$ before $d$, the eligible route is the one which have the lowest deadlines.
+     Thus, to assign the messages on the backward period, we assign to each route it's deadline, equal to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$, that is,  the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
+     We then determine the order of the messages by choosing, one by one the message on the route that we want to prioritize (eligible route): At a date $d$, if one or several messages are able to come back to $c_t$ before $d$, the eligible route is the one which have the lowest deadline.
 Otherwise, if any messages are able to be back on $c_t$ before $d$, the eligible route is the one with the first message able to come back to $c_t$.
@@
     \REQUIRE routed network $(G,{\cal R})$, period $P$, $ T_{max}$, packet size $\tau$
-    \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$
+    \ENSURE $(P,\tau)-$periodic assignment of $(G,{\cal R})$
     \STATE $clock \leftarrow 0$
@@
 
-    \WHILE{there is a route which has not been scheduled}
+    \WHILE{there is a route which has not been assigned}
     \STATE determine $r_{t_i}$ the eligible route
     \IF{ $t(c_t,r{t_i}) < clock$}
-    \STATE $w_i = clock - t(c_t,r_{t_i}) - (m_i + \lambda(r_i))$ 
+    \STATE $w_i = clock - t(c_t,r_{t_i}) - (m_i + \lambda(r_i)) \mod P$ 
     \STATE $clock \leftarrow clock + \tau$
@@
     \begin{enumerate}
-    \item First, we choose an arbitrary sending order for the routes, and we set the offsets $m_i$ such that the messages are following each others in $c_s$.
-    \item  Then, the schedule order in the way back is determined, considering the time at which the messages reach their target. 
+    \item First, we choose an arbitrary sending order for the routes, and we set the offsets $m_i$.
+    \item  Then, we use a greedy policy to determine $m_{\rho_i}$. 
     \end{enumerate}
-     This {\bf Greedy} policy determines the $m_{\rho_{s_i}}$, such that the messages does not collide on $c_t$.
-It computes the deadlines for every messages, considering their offsets and the delay on their routes, and determine the time at which the messages must leave their target, prioritizing the messages with the lowest deadlines.
+     This {\bf Greedy} policy determines the $m_{\rho_{s_i}}$ avoiding collisions on $c_t$.
+It computes the deadlines for every messages, considering their offsets and the weight on their routes, and determine the time at which the messages must leave their target, prioritizing the messages with the lowest deadlines.
 
      However, this heuristic does not take the period into account.
-Thus, a solution given by this algorithm can satisfy the constraint $MT({\cal M}) \leq T_{max}$, but this solution might need a too large period.
+Thus, a solution given by this algorithm can satisfy the constraint $MT({\cal M}) \leq T_{max}$, but this solution might have some collisions between the last messages of the period and the first ones of the following period.
 
@@
 
-	We tried to look at the behavior of that policy with different kinds of sending order for the messages.
-
-	We tried the five following sending orders, each one determines the order in which messages will be sent from sources. In every case the messages are consecutive.
+	We tried to look at the behavior of our greedy policy with different kinds of sending orders for the messages.
+
+	We tried the five following sending orders.
+Each one determines the order in which messages are sent from sources.
+In every case the messages are consecutive.
+This means that there is no time in the forward period between the end of a message and the beginning of the following one.
 
@@
 
-     In the rest of the section, we present the  different algorithms suggested to improve the second part of the scheduling.
+     We made some simulations and determined that the Random order is the most efficient (see section \ref{sec:resultsPALL}).
+In the rest of the section, we focus on algorithms that computes the affectations for the way back of the process.
       \subsection{About periodicity}
-     The previous algorithm is a greedy heuristic, which does not take the period into account. 
-     We propose an improved version of the algorithm, still greedy, but which tries to compute some solution that satisfies the period $P$: When we try to schedule some messages $P$ slots after the first message scheduled, the algorithm mind the already scheduled messages, and avoid collisions with them.
-
-     We first remember the date at which the first messages starts to come back through $c_t$. Let us note $bp$ this date.
-     The greedy policy is the same until the message are scheduled in the period between $bp$ and $bp +P$. When a message is scheduled, we update a list of free intervals in the backward period.
-     Once we try to schedule a message after $bp+P$, we consider that we are in the second period, and thus search a free interval in the period, large enough to put a message.
+     We propose an improved version of the greedy algorithm, which tries to compute some solution that satisfies the period $P$:
+
+     First, we remember the date at which the first messages starts to come back through $c_t$. Let us note $bp$ this date.
+     The greedy policy is the same until the message are assigned in the period between $bp$ and $bp +P$. When a message is assigned, we update a list of free intervals in the backward period.
+     Once we try to assign a message after $bp+P$, we consider that we are in the second period, and thus search a free interval in the period, large enough to put a message.
 
      This policy can significantly increase $w_i$, but ensures a periodic results.
-This {\bf Greedy Periodic} policy is strictly better than Greedy, because it finds some solutions that greedy would not find, by considering the periodicity in the scheduling.
+This {\bf Greedy Periodic} policy is strictly better than Greedy, because it finds some solutions that greedy would not find, by considering the periodicity in the assignement.
 
@@
      We adapted this algorithm, considering the messages as the jobs, the release times as the date at which the messages are able to come back on $c_t$, and the deadlines as the latest date at which a message have to leave $c_t$ to comeback before $m_i + T_{max}$.
-Thus, it tries to minimize the time between the first and the last message in the scheduling.
+Thus, it tries to minimize the time between the first and the last message in the assignement.
 Let us call {\bf Minimized Scheduling (MS)} this algorithm.
@@
 
-     If it exists a solution that satisfies the criteria $MT({\cal M}) < T_{max}$, this algorithm gives us a $(P,\tau)$ periodic assignment.
-Nevertheless, by setting the deadlines according to the size of the route only, the given $(P,\tau)$ periodic assignment might not respect the period $P$.
+     If it exists a solution that satisfies $MT({\cal M}) < T_{max}$, this algorithm gives us a $(P,\tau)$ periodic assignment.
+Nevertheless, by setting the deadlines according to the size of the route only, the given $(P,\tau)$ periodic assignment might not respect the period $P$, because some messages at the end of the period could collide with the messages at the begining of the following period.
 
@@
      We adapted MS, presented in the previous paragraph, to consider the period, in the computation.
+
+      For every routes of the routed network, the algorithm fixes the first route to comeback in the backward period, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(equal to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).
 
@@
 
-    \STATE return the best $(P-\tau)-$periodic assignment, or FAILURE
+    \STATE return the best $(P,\tau)$-periodic assignment, or FAILURE
 
@@
     This algorithm runs in $\mathcal{O}(n^3\log{}n)$.
-For every routes of the routed network, the algorithm fixes the first route to comeback, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(determined by $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).
-
-    This algorithm finds more solutions than MS, because it compute the deadlines of the route considering the periodicity.
-Thus, a scheduling given by this algorithm fulfill both the periodicity and the $T_{max}$ criteria.
-
-     The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic assignment, even with a small period, and $T_{max}$.
+It finds more solutions than MS, because it compute the deadlines of the route considering the periodicity.
+Thus, an assignment given by this algorithm is a solution for PALL.
 
     \subsection{Results}
+    \label{sec:resultsPALL}
 
@@
 We want to compare the sending orders with the worst parameters, so we drew the links between $0$ and $20000$ slots.
-We look at the success rate of each sending order with Greedy Periodic to schedule the messages in the way back.
+We look at the success rate of each sending order with Greedy Periodic to assign the messages in the way back.
 We give to  $T_{max}$ some {\em flexibility}.
@@
 Nowadays, the networks are managed through a stochastic model.
-The messages in the nodes are scheduled following a FIFO rule.
+The messages in the nodes are assigned following a FIFO rule.
 Even if this policy works well, in practice when the network is not too loaded, it does not ensure a minimum latency.
@@
 The results are not really different if we use short routes.
-The flexibility needed by an instance of the network is computed by taking the message which have the highest process time, at which we subtract the delay of the longest route.
+The flexibility needed by an instance of the network is computed by taking the message which have the highest process time, at which we subtract the weight of the longest route.
 We measure, for periods from $20000$ ( network fully loaded), to $50000$ ($40 \%$ of load), the medians, the first, and the third quartiles of $1000$ results.

### 2017-06-20 article/article.tex
debut de la relecture avec commentaires de David et Dominique

@@
 %opening
-\title{DRAFT : Periodic Scheduling Messages in a Network by a SDN (deterministic) approach}
+\title{Deterministic Scheduling of Periodic Messages in a Network}% by a SDN (deterministic) approach}
 %\author{Dominique Barth - UVSQ ,Christian Cadéré - UVSQ,Maël Guiraud - UVSQ,Olivier Marcé - Nokia Bell Labs France,Yann Strozecki - UVSQ}
@@
 We study the sending of periodic messages in a graph following predefined paths, a problem arising from communication between radio antennas and their signal processing units located in distant data-centers.
-Messages must be sent deterministically to avoid collisions on the network and thus to minimize the latency.
-We prove that problems related to this context are $\NP$-complete even for very restricted graphs.
-We then deal with the case of a star graph and for different regimes of the parameters we propose algorithms that are experimentally shown to work extremely well
-compared to traditional statistical multiplexing.
+Messages must be sent deterministically to avoid collisions on the network and to minimize the latency.
+We prove that problems arising from this context are $\NP$-complete even for very restricted graphs.
+We then deal with the case of a star graph and for different regimes of the parameters we propose algorithms that are experimentally shown to work extremely well compared to traditional statistical multiplexing.
 \end{abstract}
@@
 The standard requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in 1 to 10ms depending on targeted services~\cite{bouguen2012lte}.
-One specificity in the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRH and BBU.
+The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRHs and BBUs.
 
@@
 Therefore in the next two sections, we study a simple but very common topology, that we call the
-star topology, where messages can collide on only one arc.
+star topology, where all messages can collide on a single arc.
 In Sec.\ref{sec:PAZL}, we study a variant of PALL called PAZL  where the waiting times must all be zero.
@@
 
-\section{Model and problems}\label{sec:def}
+\section{Model and Problems}\label{sec:def}
 
@@
 The network is modeled as a directed graph $G=(V,A)$.
-Each arc  $(u,v)$ in $A$ is labeled by an integer $\omega(u,v) \geq 1$ which represents the time slots taken by a signal to go from $u$ to $v$ using this arc.
+Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time slots taken by a signal to go from $u$ to $v$ using this arc.
 A {\bf route} $r$ in $G$ is a path, that is sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
-The {\bf latency} of a vertex $u_i$ in a path $r$, with $i \geq 1$, is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} dl(a_j)$.
+The {\bf latency} of a vertex $u_i$ in a path $r$, with $i \geq 1$, is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} \omega(a_j)$.
 We also define $\lambda(u_0,r)=0$.
 The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
-We denote by $\cal R$ a set of routes in $G$ such that no two routes have the same first vertices or the same last vertices.
-The pair $(G,\cal R)$ is called a {\bf routed network} and represents our network.
+\todo{remettre premier et dernier sommet disjoint ?
+VÈrifier si c'est gÈnant dans la suite, Áa l'est un peu quand on dÈfinit le graphe symmÈtrique}
+We denote by $\cal R$ a set of routes,  %in $G$ such that no two routes have the same first vertices or the same last vertices.
+the pair $(G,\cal R)$ is called a {\bf routed network} and represents our telecommunication network.
 The first vertex of a route models an antenna (RRH) and the last one a data-center (BBU) which processes the messages sent by the antenna.
-We denote by $\rho$ the bijection induced by ${\cal R}$, $\rho(s) = t$ if $s$ is the first vertex of a route $r$ and $t$ the last.
-
-   \subsection{Slotted time Model}
-
-      Consider a route $r$ from $s$ to $t$. If we send a message at some point in time $m$ from $s$,
-      then it will arrive at the vertex $v$ in $r$ at time $m + \lambda(v,r)$.
-Consider now a positive integer $P$ called the {\bf period}.
-In our problem, we send messages in the network with period $P$.
-The time will thus be cut into slices of $P$ discrete slots and we need to consider only one of such slices since they will all be identical.
-       Hence we define the first time slot at which a message sent from $s$ will reach a vertex $v$ in $r$ by $t(v,r) = m + \lambda(v,r) \mod P$.
+
+%We denote by $\rho$ the bijection induced by ${\cal R}$, $\rho(s) = t$ if $s$ is the first vertex of a route $r$ and $t$ the last.
+
+   \subsection{Messages dynamic}
+
+      Consider a route $r$, if a message is sent at time $m$ from $s$ the first vertex of $r$ then it will arrive at vertex $v$ in $r$ at time $m + \lambda(v,r)$.
+In our problem, we send one message on each route periodically and we denote the period by $P$.
+      Periodicity means that if we look at the messages going through an edge between time $0$ and $P-1$, then we would observe the same messages in the same order and position between time $kP$ and $(k+1)P -1$ for all $k$.
+      Therefore, we will always consider a period of $P$ discrete slots of time at each edge to characterize the working of the network.
+We define the first time slot at which a message sent from the first vertex of $r$ will reach a vertex $v$ in $r$ by $t(v,r) = m + \lambda(v,r) \mod P$.
 
@@
       of \emph{consecutive slots} necessary to transmit a message.
-Let us call $[t(v,r)]_{P,\tau}$ the set of time slots used by $r$ at a vertex $v$ in a period $P$, that is $[t(v,r)]_{P,\tau} = \{t(v,r) + k \mod P \mid 0 \leq k < \tau \}$.
+Let us call $[t(v,r)]_{P,\tau}$ the set of time slots used by route $r$ at vertex $v$ in a period $P$, that is $[t(v,r)]_{P,\tau} = \{t(v,r) + k \mod P \mid 0 \leq k < \tau \}$.
 Usually $P$ and $\tau$ will be clear from the context and we will denote $[t(v,r)]_{P,\tau}$ by $[t(v,r)]$.
+      Let $r_1$ and $r_2$ be two routes, on which messages are sent at time $m_1$ and $m_2$ in their first vertex.
+      We say that the two routes have a {\bf collision} if they share an arc of first vertex $v$ and $[t(v,r_{1})] \cap [t(v,r_{2})] \neq \emptyset$.
 
@@
 We will always consider that the $m_{i}$ are between $0$ and $P-1$.
-A $(P,\tau)$-periodic assignment must have no {\bf collision} between two routes in $\cal R$, that is $\forall (r_{i}, r_{j}) \in {\cal R}^2, sharing and edge $(u,v)$ i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$,
-      we have $$[t(u,r_{i})] \cap [t(u,r_{j})] = \emptyset .$$
+Moreover, \emph{no pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
 
 %       Notice that the notion of $P$-periodic assignment \textbf{is not monotone} with regard to $P$. 
-      As an example of a $(2,1)$-periodic assignment, let us consider a routed network with routes $\{r_{i}\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
-      We set $\tau = 1$ and the weight are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.
-
-%       A {\bf conflict graph} represents the collision between the routes of $ {\cal R}_{\cal C}$.
-The vertices of a conflict graph $G = (V,E)$ are the routes of $ {\cal R}_{\cal C}$, and there is an edge between two vertices if and only if there is a common arc between the two routes in $ {\cal R}_{\cal C}$.
-%       
-%       Given $u$ and $v$ two vertices of the conflict graph, corresponding to two routes colliding in $ {\cal R}_{\cal C}$.
-The weight of an edge, $w(u,v)$, is the absolute value of the difference between the distance of the two routes between their respective source node and the collision point.
-%       
-%       A labeling $F$ of such a graph is an assignment of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.
+      As an example of a $(2,1)$-periodic assignment, let us consider a routed network 
+      where all pairs of routes intersect at a different edge.
+It is easy to design such a network and an example is given in Fig.~\ref{fig:example}.
+We set $\tau = 1$ and the weights are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.
+There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.
 
@@
        \caption{A routed network with $(0,0,0)$ as a $(2,1)$-periodic assignment}
+       \label{fig:example}
       \end{figure}
@@
       we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$.
-In such a graph, there is no $(P,\tau)$-periodic assignment, since the problem reduces to finding a $P$-coloring in a complete graph with $n > P$ vertices.\\
+In such a graph, there is no $(P,\tau)$-periodic assignment, since the problem reduces to finding a $P$-coloring in a complete graph with $n > P$ vertices, the colors beings the offsets of the routes.\\
       If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic assignment of ${\cal R}$.
@@
 
-% 
-%       \begin{figure}[H]
-%       \label{could-ran}
-%       \begin{center}
-%       % \begin{tabular}{cc}
-%       \includegraphics[scale=0.5]{Total-latence.pdf}
-%       \caption{Complete process for a leaf in $L$.}
-%       \end{center}
-%       \end{figure}
-%       %\end{tabular}\newline
-
-      In the context of cloud-RAN applications, we need to send message from a RRH $s$ to a BBUs $\rho(s)$ and then 
-      we must send the answer from $\rho(s)$ back to $s$. We say that a routed network $(G, {\cal R})$ is \textbf{symmetric}
-      if for all route $r$ with first vertex $s$ and last vertex $target(s)$ there is a route $r'$ with first vertex $target(s)$
-      and last vertex $s$.
-In all practical cases the routes $r$ and $r'$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we will not enforce this property.
-      If the first vertex of $r$ is $s$, we will denote by $\rho(r)$ the route whose first vertex is $\rho(s)$.
-
-         We now give a new interpretation of a $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routing graph, so that it represents the sending of a message and of its answer.
-	This assignment represents the following process: first a message is sent at $s$, through the route $r$, at time $m_s$.
-
-%       
-%       We denote by $n$ the size of $S$ and $L$.
-We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH.
-Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$.
-Let consider a $P$-periodic assignment of ${\cal C}_{\rho}$ which associates $m_l$ to
-%       $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.
+      In the context of cloud-RAN applications, we need to send message from a RRH $u$ to a BBU $v$ and then 
+      we must send the answer from $v$ back to $u$. We say that a routed network $(G, {\cal R})$ is \textbf{symmetric}
+      if there is a bijection $\rho$ between routes such that for any route $r$ with first vertex $u$ and last vertex $v$, $\rho(r)$ has first vertex $v$ and last vertex $u$.
+In all practical cases the routes $r$ and $\rho(r)$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we need not to enforce this property.
+
+         We now give a new interpretation of a $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routed network, so that it represents the sending of a message and of its answer.
+	This assignment represents the following process: first a message is sent at $u$, through the route $r$, at time $m$.
 
@@
 
-      This message is received by $\rho(s)$ at time $t(\rho(s),r)$.
-It is then sent back to $s$ on the route $\rho(r)$ in the same period at time $m_{\rho(s)}$ if $m_{\rho(s)} > t(\rho(s),r)$, otherwise at time $m_{\rho(s)}$ in the next period.
+      This message is received by $v$ the last vertex of $r$ at time $t(v,r)$.
+It is then sent back to $u$ on the route $\rho(r)$ in the same period at time $m_{\rho(s)}$ if $m_{\rho(s)} > t(\rho(s),r)$, otherwise at time $m_{\rho(s)}$ in the next period.
 The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_s = m_{\rho(s)} - t(\rho(s),r)$ if $m_{\rho(s)} > t(\rho(s),r)$ and $w_s = m_{\rho(s)} + P - t(\rho(s),r)$ otherwise.

### 2017-06-20 article/article.tex
tout ce qui est avant star topology traité

@@
          We now give a new interpretation of a $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routed network, so that it represents the sending of a message and of its answer.
-	This assignment represents the following process: first a message is sent at $u$, through the route $r$, at time $m$.
+	This assignment represents the following process: first a message is sent at $u$, through the route $r$, at time $m_r$.
 
@@
       This message is received by $v$ the last vertex of $r$ at time $t(v,r)$.
-It is then sent back to $u$ on the route $\rho(r)$ in the same period at time $m_{\rho(s)}$ if $m_{\rho(s)} > t(\rho(s),r)$, otherwise at time $m_{\rho(s)}$ in the next period.
-The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_s = m_{\rho(s)} - t(\rho(s),r)$ if $m_{\rho(s)} > t(\rho(s),r)$ and $w_s = m_{\rho(s)} + P - t(\rho(s),r)$ otherwise.
+It is then sent back to $u$ on the route $\rho(r)$ in the same period at time $m_{\rho(r)}$ if $m_{\rho(r)} > t(v,r)$, otherwise at time $m_{\rho(r)}$ in the next period.
+The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_r = m_{\rho(r)} - t(v,r)$ if $m_{\rho(r)} > t(v,r)$ and $w_r = m_{\rho(r)} + P - t(v,r)$ otherwise.
 
@@
 
-      When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
-      in the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
-
-      Thus, the whole process time for a message sent at vertex $s$ on the route $r$ is equal to
-      $$
-      PT(s)=\lambda(r)+ w_s+\lambda(r).
-      $$
-
+      Thus, the whole process time for a message sent on the route $r$ is equal to
+      $PT(r)=\lambda(r)+ w_r+\lambda(r)$.      
       In the process time, we count the time between the first time at which a message is emitted and 
@@
 Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
-      However, since all messages are of size $\tau$, it will not change the problem we solve in the rest of the article and that we now introduce.
-
-    The {\bf maximum process time} of the $(P,\tau)$-periodic assignment ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{s \in S} PT(s)$. We consider the following decision problem.
+      However, since all messages are of size $\tau$, it will not change the problem we consider in the rest of the article.
+      Finally, we could add to the process time the computation time a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
+
+    The {\bf maximum process time} of the assignment ${\cal M}$ of $(G,{\cal R})$ is defined by $MT({\cal M})=\max\limits_{r \in {\cal R}} PT(r)$. We consider the following decision problem.
 
@@
 
-      \noindent {\bf Input:}  A symmetric routed network $(G,{\cal R})$, a period $P$, an integer $\tau$, an integer $T_{max}$.
+      \noindent {\bf Input:}  A symmetric routed network $(G,{\cal R})$, the integers $P$, $\tau$ and $T_{max}$.
 
@@
 Consider an instance of the problem PRA, i.e., a routed network $(G,\cal{R})$ and a period $P$.
-The {\bf conflict depth} of a route is the number of other routes which share an edge with it. 
-The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of the routes in $\cal{R}$.
+The {\bf conflict depth} of an edge is the number of routes to which the edge belongs. 
+The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its edges.
 The {\bf load} of a routed network is the maximal number of routes sharing the same arc.
@@
  The second proof reduces the problem to graph coloring and implies inapproximability when one tries to find the smallest possible $P$. \\
+ Finally, it is easy to see that PRA is easy on trees and it may be interesting to study its complexity on 
+ bounded treewidth networks, since it is a common property of real networks~\cite{} \todo{Trouver la ref qui dit ca}.
 
  \begin{proposition}
-Problem PRA is $\NP$-complete, when the routing is of conflict depth two.
+Problem PRA is $\NP$-complete on the class of routed networks with conflict depth two.
 \end{proposition}
  \begin{proof}
- The problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of edges whether there are collisions.
-
-  Let $H=(V,E)$ be a graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is edge-colorable
-  with $d$ or $d+1$ colors. The edge coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness. We define from $H$ an instance of PRA as follows. 
-  For each $v$ in $V$, the graph $G$ has two vertices $v_1, v_2$, and for each $(u,v) \in E$,the graph G has two vertices $s_{u,v}, t_{u,v}$.
-Set an arbitrary orientation of the edge $(u,v)$, such that the following route is directed from $u$ to $v$.
-%   The set $A$ of arcs of $G$ is: 
-%   $$ \{(v_1,v_2) \mid v\in V\} \cup \{(u_2,v_1)\mid u \neq v \in V^2\} \cup \{(s_{u,v},u_1),(v_2,t_{u,v}) \mid (u,v) \in E \}. $$
+ Problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of edges whether there are collisions.
+
+  Let $H=(V,E)$ be an undirected graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is edge-colorable
+  with $d$ or $d+1$ colors.
+The edge coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness.
+To do that, we define from $H$ a routed network $(G,{\cal R})$ as follows.
+  The vertices of $G$ are $v_1, v_2$ for each $v$ in $V$ and $s_{u,v}, t_{u,v}$ for each $(u,v) \in E$.
   For each edge $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
-  All these arcs are of weight $0$. The set of arcs of G is the union between all the arcs of the previous routes.
+
+   To define ${\cal R}$ an arbitrary orientation of each edge $(u,v)$ is chosen. 
+   Then for each arc $(u,v)$ there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
+  All these arcs are of weight $0$. The set of arcs of G is the union between all the arcs of the previously defined routes.
 
@@
   By construction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent edges have the same color.
-Therefore we have reduced edge coloring to PRA which concludes the proof.
+Therefore we have reduced edge coloring to PRA by a polynomial time transformation which concludes the proof.
  \end{proof}
 
- Remark that we have used zero weight in the proof. If we ask the weights to be strictly positive, which makes sense in our model since
+ Remark that we have used zero weights in the proof. If we ask the weights to be strictly positive, which makes sense in our model since
 they represent the latency of physical links, it is easy to adapt the proof.
@@
 \begin{corollary}
-Problem PALL is $\NP$-complete for routing of conflict depth two.
+Problem PALL is $\NP$-complete on the class of routed networks of conflict depth two.
 \end{corollary}
@@
 We define $(G',{\cal R}')$ a symmetric routed network from $(G,{\cal R})$ where for every route we add a symmetric route with new arcs of opposite orientation and the same weights.
- The instance $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL if and only if $((G,{\cal R}),P,\tau)$ is in $PRA$.
-Indeed the waiting time of each route is by definition less than $P$ and thus the maximal process time is always less than $T_{max}$.
+ We prove that the instance $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL if and only if $((G,{\cal R}),P,\tau)$ is in $PRA$.
+ If $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL, then a $(P,\tau)$-assignment of $(G',{\cal R'})$ restricted to $\R$ is a $(P,\tau)$-assignment of $((G,{\cal R})$ since they cannot be any collision between routes of ${\cal R}$.
+
+ Assume now that $((G,{\cal R}),P,\tau)$ is in $PRA$.
+First remark that the waiting time of each route is by definition less than $P$ and thus the maximal process time is always less than $T_{max}$, therefore the constraint on $T_{max}$ is satisfied.
 Moreover a $(P,\tau)$-assignment of $(G,{\cal R})$ can be extended into a $(P,\tau)$-assignment of $(G',{\cal R'})$ in the following way.
-For each route $r \in \cal{R}$ starting at $s$, the time at which the message arrives is $t(\rho(s),r)$, then we choose as offset for $\rho(r) \in \cal{R}'$ $-t(\rho(s),r) \mod P$.
-The symmetry ensures that each new route $\rho(r)$ in ${\cal R'}$ uses the same times slot as $r$ one each of its node and thus avoid collisions.
+For each route $r \in \cal{R}$ of last vertex $v$, the time at which the message arrives is $t(v,r)$, then we choose as offset for $\rho(r) \in \cal{R}'$ $-t(v,r) \mod P$.
+The symmetry ensures that each new route $\rho(r)$ in ${\cal R'}$ uses exactly the same times slot as $r$ one each of its node and thus avoid collisions.
 \end{proof}
@@
 \begin{theorem}\label{th:inapprox}
- The problem MIN-PRA cannot be approximated in polynomial time within a factor $n^{1-o(1)}$, with $n$ the number of routes, unless $\P = \NP$ even when the load is two.
+If $\P \neq \NP$, problem MIN-PRA on the classes of routed networks of load two cannot be approximated in polynomial time within a factor $n^{1-o(1)}$ where $n$ is the number of routes.
 \end{theorem}
@@
  We define ${\cal R}$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
- Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an edge in $H$; this arc is the only one shared by these two routes. All arcs are of weight $0$.
+ Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an edge in $H$; this arc is the only one shared by these two routes.
+All arcs are of weight $0$.
+Note that it is easy to build a graph with such routes as in Fig.~\ref{fig:reduction}.
 
@@
     \caption{Reduction from k-coloring to MIN-PRA}
-
+    \label{fig:reduction}
     \end{figure}

### 2017-06-20 article/article.tex
partie 4 presque finie

@@
 The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
-\todo{remettre premier et dernier sommet disjoint ?
-VÈrifier si c'est gÈnant dans la suite, Áa l'est un peu quand on dÈfinit le graphe symmÈtrique}
 We denote by $\cal R$ a set of routes,  %in $G$ such that no two routes have the same first vertices or the same last vertices.
@@
       First, for each arc $(u,v)$, there is also an arc $(v,u)$ with the same weight.
-      There are two sets of vertices, $S=\{s_1,...,s_n\}$ and $T=\{t_1,...,t_n\}$ of cardinality $n$ and two special nodes
+      There are two sets of vertices, $S=\{s_1,...,s_n\}$ and $T=\{t_1,...,t_n\}$ of cardinality $n$ and two special nodes:
       the central source node {\bf $c_s$} and the central target node {\bf $c_t$}.
@@
       is set to $0$, therefore we assume from now on it is indeed $0$.
-      Collisions between messages can only appear in the arcs after node $c_s$ on the way forward and after node $c_t$ on the way back.
-      Thus, we only have to check if there is no collisions in a given period at those two vertices.
-      We try to order the messages such that they can pass thought the common arcs in a time window of $P$ max.
+
+      Collisions between messages can only appear in the arc $(c_s,c_t)$ on the way forward and in the arc $(c_t,c_s)$
+      on the way back. The flow of messages in a star topology is completely described by their repartition in two 
+      time window of size $P$ that we call the {\bf forward period} (at $(c_s,c_t)$), and the {\bf backward period} (at $(c_t,c_s)$).
+
+%       
+%       on the way forward and after node $c_t$ on the way back.
+%       Thus, we only have to check if there is no collisions in a given period at those two vertices.
+%       We try to order the messages such that they can pass thought the common arcs in a time window of $P$ max.
 We define the {\bf forward period}, a time window of size P at the beginning of the arc after $c_s$, and the {\bf backward period} the one at the beginning of the arc after $c_t$.
@@
 If the offset of $\rho(s)$ is $m_{\rho(s)}$, the answer will reach $c_t$ at time $m_{\rho(s)} + t(c_t,\rho(r))\mod P$ in the backward period.
-
-      A $(P,\tau)$-periodic assignment is then a choice for all $i < n$, of $m_{r_i}$ and $m_{\rho(r_i)}$ such that, for any couple $(i\neq j)$, we have $[t(c_s,r_{i})] \cap [t(c_s,r_{j})] = \emptyset$ and $[t(c_t,\rho(r_i))] \cap [t(c_t,\rho(r_j))] = \emptyset$.
+% 
+%       A $(P,\tau)$-periodic assignment is then a choice for all $i < n$, of $m_{r_i}$ and $m_{\rho(r_i)}$ such that, for any couple $(i\neq j)$, we have $[t(c_s,r_{i})] \cap [t(c_s,r_{j})] = \emptyset$ and $[t(c_t,\rho(r_i))] \cap [t(c_t,\rho(r_j))] = \emptyset$.
 
@@
   We ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$} and we call this restricted problem {\bf Periodic Assignment for Zero Latency} or PAZL.
-  In that case $MT({\cal M})$ is equal to twice the weight of the longest route, thus $T_{max}$ is not relevant anymore. 
-  Since $w_i=0$, choosing $m_{s_i}$, the offset of the route from $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_{s_i} + \lambda(r_i) \mod P$.
-  Remark that there is a bijection between the assignments of a star topology and the 
-  assignments of the same star topology where all arcs from $s_i$ to $c_s$ have weight equal to $0$ by changing $m_{s_i}$ into $m_{s_i} - t(c_s,r_i) \mod P$.
-Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
-
-  We propose two algorithms that always find a solution in polynomial time if instances meets some criteria (short routes or great enough period) but which may fail in other cases and one exponential algorithm which always finds a solution if it exists.
+We consider PAZL since it is simpler to get theoretical results and good algorithms
+  than for PALL.
+Moreover, as we show in our experimentations of Sec.\ref{sec:exp_PAZL}, this problem can often be solved positively (albeit less often than the general problem).
+Finally, a solution to PAZL is simpler to implement in real telecommunication networks, since we do not need to implement any buffering at all.
+
+  When the waiting times are zero, $MT({\cal M})$ is equal to twice the weight of the longest route, thus $T_{max}$ is not relevant anymore.
+For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ $m_{\rho(r)} + \lambda(r) \mod P$.
+  Consider an assignment $\{m_1,\dots,m_n\}$ of a star topology and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
+  Then $\{m_1',\dots,m_n'\}$ is an assignment of the same star topology where the weights of the arcs from $s_i$ to $c_s$ are $0$
+  for all $i$. Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
+
+  One may consider a variant of PAZL where the central link is unidirectional, that is collisions can happen between messages going from $c_s$ to $c_t$ and messages  going from $c_t$ to $c_s$.
+This problem can be shown to be $\NP$-complete by a reduction from the subset sum problem as it is done for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
+We conjecture that the problem PAZL is also $\NP$-complete,  but we have yet not been able to prove it.
+  On the other hand we show positive results:  when the period is large or when the routes are short there is always a solution to PAZL and it can be found in polynomial time.
+We then give an exponential time branch and cut algorithm which always finds a solution if there is one.
 
@@
     The messages are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
-    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{s_i}$ the offset of $r_i$ to $(i-1)\tau$. We call this algorithm {\bf Shortest-Longest}.
+    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{i}$ the offset of $r_i$ to $(i-1)\tau$. We call this algorithm {\bf Shortest-Longest}.
 
@@
 
-      \begin{proposition} When $n\tau + 2(\lambda(r_{n}) - \lambda(r_{1})) \leq P$,
-      there is always a solution to PAZL and Shortest-Longest finds it  in time $O(n\log(n))$.\label{prop:SL}
+      \begin{proposition} Let $(G, {\cal R})$ be a symmetric routed network, and let $n\tau + 2(\lambda(r_{n}) - \lambda(r_{1})) \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which is given by Shortest-Longest in time $O(n\log(n))$.\label{prop:SL}
       \end{proposition}
@@
     \begin{proposition}
-    Let  $n$ be the number of routes and let $ 3n\tau \leq P$, then there is is always a solution to PAZL and there is an  algorithm which finds the assignment in time $O(n^2)$.
+     Let $(G, {\cal R})$ be a symmetric routed network, and let $ 3n\tau \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which can be found in time $O(n^2)$.
     \end{proposition}
@@
 
-	\subsubsection*{Exhaustive search}
+	\subsubsection*{Branch and cut}
 % 	\begin{algorithm}[H]
@@
 % 	    
-      We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found a $(P,\tau)$-periodic assignment.
+      We now present a branch and cut algorithm, which tries to set the offsets in all possible ways until it has found a $(P,\tau)$-periodic assignment.
 Contrarily to the two previous algorithms, when it fails to find a solution, then it certifies there are no solution to PAZL.
@@
       a partial function from $[n]$ to $\{0,1,\dots,P-\tau -1\}$ which sets a starting time for a subset of the routes $R(S) \subseteq [n]$, such that there are no collisions for these routes.
-A partial solution $S'$ extends $S$, if $S'$ is defined over one more route than $S$ and this route has a larger starting offset than all routes of $S$: $R(S') = R(S) \cup \{r'\}$ and for all  $r \in R(S)$, $S(r) + \tau \leq S'{r'}$.
-We define a tree whose nodes are partial solutions and such that the root is the empty partial solution and
-      the children of a partial solution are the partial solutions which extend it.
+A partial solution $S'$ extends $S$, if $S'$ is defined over one more route than $S$ and this route has a larger starting offset than all routes of $S$: $R(S') = R(S) \cup \{r'\}$ and for all  $r \in R(S)$, $S(r) + \tau \leq S'(r')$.
+We define a tree whose nodes are partial solutions and such that the root is the empty partial solution and the children of a partial solution are the partial solutions which extend it.
 The solutions to our problem will be the leaves of depth $n$ in the tree, and our exhaustive search algorithm is a depth-first search of this tree.
@@
       The following experimental results compare the three presented algorithms.
-      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithm but are not always able to find a solution.
-On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time.
+      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithm but are not always able to find a solution, depending on $P$, $\tau$, $n$ and the size of the routes.
+On the other hand, the exhaustive search will find an optimal solution if it exists, but works in exponential time.
 We will compare the performance of the algorithms in two different regimes: routes are either short with regards to $\tau$ and $P$, or unrestricted.
@@
 The code in C is available online on the webpages of the authors ~\cite{webpage}.
-%             
+
+      \todo{remarque sur la charge du rÈseau ntau / P -> dire diminuer P augmente la charge et donner les deux bornes pertinentes}
 %             The graphs 
@@
       We measured the average minimal period, for each algorithm.
-We needed to stop our experiments at $12$ routes since the exhaustive search was taking more than a second to finish on many instances.
-      Note that the exhaustive search is optimal, that is it finds the best possible period for a given instance. 
-      We also drew the functions $f(n) = n\tau$, which is an absolute lower bound on the period and $g(n) = 3n\tau$ which is the theoretical upper bound of the greedy algorithm.
+We needed to stop our experiments at $12$ routes since the branch and cut algorithm was too slow.
+Remind that the branch and cut always finds the best possible period for a given instance.
+      The functions $f(n) = n\tau$ and $g(n) = 3n\tau$ are also represented since they are respectively lower and upper bounds on the period.
 

### 2017-06-20 article/article.tex
corrections pour la partie 4

@@
 Finally in Sec.\ref{sec:PALL}, we propose algorithms for the general PALL problem and exhibit one which works extremely well in our experiments even in loaded networks.
-In particular we show that the deterministic communication schemes we design vastly outperform the traditional stochastic multiplexing with regards to latency.
+In particular we show that the deterministic communication schemes we design vastly outperform the traditional stochastic multiplexing with regard to latency.
 
@@
       An unusual property of assignment is that given a routed network, we may have a $(P,\tau)$-periodic assignment but no
-      $(P',\tau)$-periodic assignment with $P' > P$: the existence of an assignment is not monotone with regards to $P$.
+      $(P',\tau)$-periodic assignment with $P' > P$: the existence of an assignment is not monotone with regard to $P$.
 
@@
   On the other hand we show positive results:  when the period is large or when the routes are short there is always a solution to PAZL and it can be found in polynomial time.
-We then give an exponential time branch and cut algorithm which always finds a solution if there is one.
+We then give an exponential time exhaustive search algorithm which always finds a solution if there is one.
 
@@
 
-    We first present a simple policy, which works when the period is large with regards to the weight of the routes.
+    We first present a simple policy, which works when the period is large with regard to the weight of the routes.
     The messages are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
@@
     We propose a greedy algorithm to build a $(P,\tau)$-periodic assignment, which provably works when
-    the period is large enough with regards to the number of routes and size of messages. In other words, 
+    the period is large enough with regard to the number of routes and size of messages. In other words, 
     we can always find a solution when the network is far from saturated.
@@
 % 	    
-      We now present a branch and cut algorithm, which tries to set the offsets in all possible ways until it has found a $(P,\tau)$-periodic assignment.
+      We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found a $(P,\tau)$-periodic assignment.
 Contrarily to the two previous algorithms, when it fails to find a solution, then it certifies there are no solution to PAZL.
@@
 On the other hand, the exhaustive search will find an optimal solution if it exists, but works in exponential time.
-We will compare the performance of the algorithms in two different regimes: routes are either short with regards to $\tau$ and $P$, or unrestricted.
-      We choose the following realistic parameters with regard to our C-RAN context. The number of routes 
-      is at most $n = 20$, $\tau$ is equal to $2500$ and the period is at most $3n\tau$ (otherwise the greedy algorithm always returns a solution).
+We will compare the performance of the algorithms in two different regimes: routes are either short with regard to $\tau$, or unrestricted.
+      From our C-RAN context we choose the following parameters: the number of routes 
+      is at most $n = 20$, $\tau$ is equal to $2500$. Moreover the period is always larger than $n\tau$ otherwise 
+      no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution. 
       The code in C is available online on the webpages of the authors ~\cite{webpage}.
 
-      \todo{remarque sur la charge du rÈseau ntau / P -> dire diminuer P augmente la charge et donner les deux bornes pertinentes}
-%             The graphs 
-%       To correspond with the C-RAN applications, we made some simulations on graphs in which $\lambda(c_s,r_{s_i})$ and $\lambda(c_t,r_{t_i})$, are drawn following an uniform act between 0 and 700 slots, that is, at the most, 5 km between the RRH and its BBU.
-The messages size $\tau$ is to 2500 slots, that is, approximately 1.228 Gbps of data for each route.
-The size of a slot is given by the time taken to send 64 bytes on the network, in which the links has 10Gbps throughput.
-% 
-%       \todo{Mettre les donn√©es concr√®tes plus proprement et √©ventuellement ne pas les mettre si on envoie pas √† un truc de t√©l√©com}
+      We can define the load of the network as $\frac{n\tau}{P}$ (here a value between one and three) and in experiments we will try to understand how our algorithms work with regards to the load.
+Often rather than changing the load, we will change the period which is equivalent.
 
@@
       completely in a single edge.
-This is very common in our context and we will consider graphs in which the values $\lambda(c_t,\rho(r_{i}))$ are drawn uniformly between $0$ and $700$ slots.
+This is very common in our context and we will consider graphs in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ slots.
 It corresponds to messages of approximately 1Mb, links of bandwidth 10Gbps and length less than 5km between the BBU and the RRH.
 
-      Our aim is to understand how well the algorithms are working when the network has a high load (when 
-      the load is low, the greedy algorithm always returns a solution). To do that we try to evaluate the 
-      minimal period for which a $(P,\tau)$ periodic assignment can be found by each algorithm. 
-      To that end we use linear search on $P$, since a dichotomy method would not work because of Lemma~\ref{lemma:monotonic}.
-
-      In our experiment, we generated $1000$ random instances of PAZL for $1$ to $12$ routes. 
-      We measured the average minimal period, for each algorithm.
-We needed to stop our experiments at $12$ routes since the branch and cut algorithm was too slow.
-Remind that the branch and cut always finds the best possible period for a given instance.
-      The functions $f(n) = n\tau$ and $g(n) = 3n\tau$ are also represented since they are respectively lower and upper bounds on the period.
+      Our aim is to understand how well the algorithms are working under high load. To do that we try to evaluate the 
+      minimal period (that is the highest possible load) for which a $(P,\tau)$ periodic assignment can be found by each algorithm. 
+      To that end we use a linear search on $P$, since a dichotomy method would not work because of Lemma~\ref{lemma:monotonic}.
+
+      In our experiment, we generate $1000$ random instances of PAZL for $1$ to $12$ routes. 
+      We measure the average minimal period, for each algorithm.
+The experiments are stopped at $12$ routes because the exhaustive search algorithm becomes too slow for larger $n$.
+Remind that the exhaustive search always finds the best possible period for a given instance.
+The lower and upper bound $n\tau$ and $3n\tau$ are also represented.
 
@@
 
-      The period needed by Shortest-Longest to find an optimal solution is determined by the difference between the longest and the shortest route and could be easily determined theoretically.
-The algorithm was expected to be good since the routes are short, but it turns out it always finds the optimal solution in our experiments.
-Therefore, we should use it in practical application, in this regime, instead of the exhaustive search which is much more computationally expensive.
+      The period needed by the Shortest-Longest algorithm to find an optimal solution is a function of the difference between the longest and the shortest route and its average could be easily determined theoretically.
+The algorithm was expected to find a period close to the optimal one since the routes are short.
+It turns out it always finds the optimal period in our experiments.
+Therefore, we should use it in practical applications with short routes, instead of the exhaustive search which is much more computationally expensive.
 
@@
 
-      We now want to understand the performance of these algorithms when the size of the routes are unbounded.
+      We now want to understand the performance of these algorithms when the size of the routes is unbounded.
 When the routes are long, the cuts in the exhaustive search are less efficient and thus even for a small number of routes the algorithm may be impractical.
@@
 
-      In this experiment we will fix the number of routes to $8$ and the values $\lambda(c_t,\rho(r_{i}))$ are drawn following an uniform distribution between $0$ and $30000$ slots (in the same range as the period).
+      In this experiment we will fix the number of routes to $8$ and the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots (in the same range as the period).
       We measure for each algorithm its percentage of success, for periods from $20000$ which is the minimum possible to $50000$.
@@
       The exhaustive search can fail because there are no solutions or because it does not have enough time to finish its calculation.
-Hence we represent both the success rate of the algorithm, and an upper bound on the success rate of any algorithm solving PAZL by combining its successes and its failures because of lack of time.
+Hence we represent both the success rate of the algorithm, and an upper bound on the success rate of any algorithm solving PAZL by combining the successes and the failures because of lack of time of the exhaustive search.
 
@@
 
-      In this regime, the performances of Shortest-Longest are abysmal since it depends on the difference between the longest and the smallest route
-      which is large here.
+      In this regime, the performances of Shortest-Longest are abysmal since it depends on the difference between the longest and the smallest route which is large here.
 On the other hand, the greedy algorithm has a performance not so far from the case of short routes, which is expected since it does not directly depend on the size of the route.
-When repeating the experiments of the previous section on routes of arbitrary length, we find that on average the greedy algorithm finds a solution if $P > 1.89n\tau$.
+When repeating the experiments of the previous section on routes of arbitrary length, we find that on average the greedy algorithm finds a solution if $P>1.89n\tau$.
 
       When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithms which justifies its use.
-      However for small period, less than $30000$ the computation time is really important and without improvements it would not be possible to tackle 
-      larger problems with $10$ to $20$ routes.
-Moreover, examining the upper bound curve for small periods less than $22000$, we see that there are very few instances with a solution for PAZL.
-It means that with long routes and high load, looking for an assignment without waiting time is far too restrictive.
+However for small period, less than $30000$ the computation time is really important and without improvements it would not be possible to tackle larger problems with $10$ to $20$ routes.
+Moreover, examining the upper bound curve for periods less than $22000$, we see that there are very few instances with a solution for PAZL.
+It means that with long routes and high load (larger than $0.9$), looking for an assignment without waiting time is far too restrictive.
 That is why we present algorithms for the general PALL problem in our next section.
@@
 
-    In this section, we still work on the start topology, but, from now, we allow the messages to wait in the target vertices (BBU),in order to find some solution that we cannot find with PALL.
-From now, the process times  $PT$ of the routes can be greater than twice the weight of the routes, but it might not be superior to $T_{max}$.
-
-	\subsection{Particular cases}
+    In this section, we still work on the star topology, but we consider again the  PALL problem. 
+    It means that the messages can wait in the target vertices (BBU), in order to find solution that we cannot find without waiting time.
+We allow the process times $PT$ of the routes to be greater than twice the weight of the routes, but it should not be superior to $T_{max}$.
+
+	\subsection{Special cases}
+
+	Often in real networks, the length of the routes are not arbitrary. 
+	\todo{Reprendre les deux cas faciles, est-ce qu'il y en a d'autres ?}
 
@@
      We adapted this algorithm, considering the messages as the jobs, the release times as the date at which the messages are able to come back on $c_t$, and the deadlines as the latest date at which a message have to leave $c_t$ to comeback before $m_i + T_{max}$.
-Thus, it tries to minimize the time between the first and the last message in the assignement.
+Thus, it tries to minimize the time between the first and the last message in the assignment.
 Let us call {\bf Minimized Scheduling (MS)} this algorithm.

### 2017-06-22 article/article.tex
changements partie 5

@@
     It means that the messages can wait in the target vertices (BBU), in order to find solution that we cannot find without waiting time.
-We allow the process times $PT$ of the routes to be greater than twice the weight of the routes, but it should not be superior to $T_{max}$.
+We allow the process times $PT$ of the routes to be greater than twice the weight of the routes, but it should less than $T_{max}$.
 
@@
 
-	Often in real networks, the length of the routes are not arbitrary. 
-	\todo{Reprendre les deux cas faciles, est-ce qu'il y en a d'autres ?}
-
-	One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the same and so can be simplified by $0$.
-In that case, the order of the messages in the forward and backward period is the same.
-The trivial solution is to send all message following each others regardless the order.
-Thus, the period is minimal : $n.\tau$, where $n$ is the number of routes.
-Furthermore, all the waiting times are equal to $0$ i.e.
-$w_i = 0,\forall i $, thus, $MT({\cal M})$ is equal to twice the weight of the longest route, that is not alterable.
-
-	Another particular case is the following one:	
+	Often in real networks, the length of the routes are not arbitrary and we may exploit that to solve PALL easily.
+For instance if all the weights on the arcs $c_t,t_i$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.
+	The assignment in that case is trivial, just send all messages so that they follow each other without gaps in the central arc $(c_s,c_t)$.
+Since the arcs $(c_t,t_i)$ are of weigth $0$, all messages will go through  $(c_t,c_s)$ on their way back in
+	the same order and thus will not collide.
+
+	A more realistic assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same. It would correspond
+	to a situation where all the BBUs are in the same datacenter.
+
 	 \begin{theorem}
-     There is always a solution with $MT({\cal M}) < T_{max}$ when  $ \forall (i,j), \omega(s_i,c_s) = \omega (s_j,c_s)$      \end{theorem}
+	 Let $(G,{\cal R})$ be a symmetric routed network with $n$ routes and let $P \geq n\tau$.
+If for all $i$ and $j$ less than $n$ $\omega(s_i,c_s) = \omega (s_j,c_s)$, then there is a $(P,\tau)$-peridoic assignment with process time $2\max_{r\in {\cal R}} \lambda(r)$ and it can be built in time $O(n\log(n))$.
+	 \end{theorem}
       \begin{proof}
 
-	Since we can simplify the weight on the arcs between $c_s$ and the sources by $0$, we consider only the weight between $c_t$ and the targets.
-Order the routes such that $\lambda(r_{s_i}) > \lambda(r_{s_j}), i<j$, i.e.
-the route $0$ is the longest, and the route $n-1$ is the shortest one.
-	The messages are sent in the forward period from the route $0$ to $n-1$, that is $m_{s_i} = \tau * i$.
-	The first message has totally reach the backward period at time $2.\lambda(r_{s_0})+\tau$. The process time of the first message is $PT(s_0) = 2.\lambda(r_{s_0}) $.
-	The second message is able to reach the backward period at time $\tau + 2.\lambda(r_{s_1})$.
-Thus, the waiting time of the second route is $w_1 = 2.\lambda(r_{s_0})+\tau - (\tau + 2.\lambda(r_{s_1})) = 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))$.
-Thus $PT(s_1) = 2.\lambda(r_{s_1}) + 2.(\lambda(r_{s_0}) - \lambda(r_{s_1}))  = 2.\lambda(r_{s_0})  = PT(s_0)$.
-	By induction, $PT(s_i) = PT(s_0), \forall i \in n$.
-
-	Consequently, for this case, sending the message from the one using the longest route to to one using the shortest route is optimal, because the longest route has no waiting time, and all the other routes have the exact same process time, thus, $MT(M) = PT(s_0) = 2.\lambda(r_{s_0}) $.
-Moreover, the period used is exactly $n \tau$, in both the forward and backward periods.
+        We can simplify the weights on the arcs $(s_i,c_s)$ by setting them all to $0$. We order the routes
+        in decreasing order of their length, that is when $i<j$, $\lambda(r_{i}) > \lambda(r_{j})$.
+        The offset of the route $r_i$ is $i\tau$, which ensures that there are no collision on the way forward (on the arc 
+        $(c_s,c_t)$) as soon as $P \geq n\tau$ which is the minimal possible period.        
+	We set the waiting time of the first message to $0$, thus it reaches the vertex $c_t$ for the second time before going through the arc $(c_t,c_s)$ at time $2\lambda(r_{0})+\tau$.
+The process time of the first message is $PT(r_0) = 2\lambda(r_{0})$.
+	The second message reaches $c_t$ for the second time at $\tau + 2\lambda(r_{1})$. 
+	Therefore to avoid collision, we set the waiting time  $w_1 =  2\lambda(r_{0})+\tau - (\tau + 2\lambda(r_{1})) = 2(\lambda(r_{0}) - \lambda(r_{1}))$.
+
+	We generalize this by setting $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$ for all $i< n$.
+	There are no collision on the way back since the message of the route $r_i$ arrives at $c_t$
+	at time $(i-1)\tau + 2\lambda(r)$. We must also evaluate the process time. 
+	By defintion $PT(r_i) = 2\lambda(r_i) + w_i = 2\lambda(r_i) + 2(\lambda(r_{0}) - \lambda(r_{i})) = 2\lambda(r_0)$.
+	Since all process times are the same, the maximum process time is also equal to $2\lambda(r_0)$.
+
+	Finally, the time to build this assignment is dominated by the sorting of the routes from the longest to the shortest and is thus in $O(n\log(n)$.
      \end{proof}
+
+\todo{Une remarque sur le fait que la complexitÈ dÈpend sans doute du nombre de valeurs diffÈrentes sur les arcs et pas du nombre de routes.}
 

### 2017-06-22 article/article.tex
figures notations

@@
 
+\renewcommand{\thefootnote}{\*}
+
 \newcommand{\todo}[1]{{\color{red} TODO: {#1}}}
@@
 
+\footnote{This work is partialy supported by the french  ANR project N-GREEN.}
 \section{Introduction}
@@
 
-This problem may look like wormhole problems~\cite{cole1996benefit}, but here we want to minimize the time lost in buffers and not just avoid deadlocks, moreover the periodicity is not considered in wormhole problems.
+ Thus in this article, we work on latency and periodicity constraints in fron- thaul.
+The best current solution is to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches [7].
+This architecture is very ex- pensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
+It is then needed to find a solution to offer low latency over commoditized packet based networks.
+Indeed, dynamical optical bypass and dynamical management of the emission should be considered to guarantee latency constraints, as it is considered in the french ANR project N-GREEN.
+This project proposes a new type of switching/routing node and a specific net- work architecture exploiting WDM packets thanks to a new generation of optical add/drop multiplexers (WSADM: WDM slotted add/drop multiplexer).
+These packets having a fixed duration close to 1?s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.
+
+The problem we thus focus on here may look like wormhole problems~\cite{cole1996benefit}, but here we want to minimize the time lost in buffers and not just avoid deadlocks, moreover the periodicity is not considered in wormhole problems.
 Several graph colorings have been introduced to model similar problems such as the allocation of frequencies~\cite{borndorfer1998frequency}, bandwidths~\cite{erlebach2001complexity} or routes~\cite{cole1996benefit} in a network or train schedules~\cite{strotmann2007railway}.
@@
 
+      The following table summarize the main notations used in the paper.
+      \begin{center}
+   \begin{tabular}{|c|c|}
+    \hline
+     $(G,\cal R)$ & A Routed network \\
+     \hline
+      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
+      \hline
+      $\lambda (u_i,r)$ & The latency of the vertex $u_i$ through $r$\\
+         \hline
+         $\lambda (r)$ & The latency of a route $r$.\\
+         \hline
+         $P$ & Period\\
+         \hline
+         $\tau$ & Size of a message\\
+         \hline
+         $ [t(v,r)]$&The set of time slots used by route $r$ at vertex $v$ \\
+         & in a period $P$.\\
+         \hline 
+         ${\cal M}=(m_1, \ldots ,m_n)$&Offsets\\
+    \hline
+
+      \end{tabular}
+      \end{center}
+
    \subsection{Problems}\label{nonmonotone}
@@
       \begin{center}
-      \includegraphics[scale=0.3]{rrh.png}
+      \includegraphics[width=\textwidth]{RRH.pdf}
       \end{center}
@@
        \begin{center}
-      \includegraphics[scale=0.17]{BBU2.png}
+      \includegraphics[width=\textwidth]{BBU.pdf}
       \end{center}
@@
        \begin{center}
-	 \scalebox{0.7}{
+	 \scalebox{0.8}{
 \begin{tikzpicture}
@@
 
-  \node[draw,circle] (cs) at (2, 2) {$c_s$}; 
-  \node[draw,circle] (ct) at (6, 2) {$c_t$};
-
-  \Edge(s1)(cs)
-  \Edge(s2)(cs)
-  \Edge(s3)(cs)
-
-  \Edge(ct)(t1)
-  \Edge(ct)(t2)
-  \Edge(ct)(t3)
+  \node[draw,circle] (cs) at (3, 2) {$c_s$}; 
+  \node[draw,circle] (ct) at (5, 2) {$c_t$};
+
+  \Edge[label = $\omega(s_1.c_s)$](s1)(cs)
+  \Edge[label = $\omega(...)$](s2)(cs)
+  \Edge[label = $\omega(...)$](s3)(cs)
+
+  \Edge[label = $\omega(...)$](ct)(t1)
+  \Edge[label = $\omega(...)$](ct)(t2)
+  \Edge[label = $\omega(...)$](ct)(t3)
 
@@
      \end{proof}
-
-\todo{Une remarque sur le fait que la complexitÈ dÈpend sans doute du nombre de valeurs diffÈrentes sur les arcs et pas du nombre de routes.}
+\todo{Une remarque sur le fait que la complexite depend sans doute du nombre de valeurs differentes sur les arcs et pas du nombre de routes.}
 

### 2017-06-23 article/article.tex
preuve 3nt figure
merge

--- 2017-06-22 article/article.tex
@@
 	The second message reaches $c_t$ for the second time at $\tau + 2\lambda(r_{1})$. 
-	Therefore to avoid collision, we set the waiting time  $w_1 =  2\lambda(r_{0})+\tau - (\tau + 2\lambda(r_{1})) = 2(\lambda(r_{0}) - \lambda(r_{1}))$.
-
-	We generalize this by setting $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$ for all $i< n$.
+	Therefore to avoid collision, we set the waiting time  $w_1 =  2\lambda(r_{0})+\tau - (\tau + 2\lambda(r_{1})) = 2(\lambda(r_{0}) - \lambda(r_{1}))$, which is positive since $\lambda(r_{0}) > \lambda(r_{1})$.
+
+	We generalize this by setting $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$ which are positive for all $i< n$,
+	since by definition.
 	There are no collision on the way back since the message of the route $r_i$ arrives at $c_t$

### 2017-06-23 article/article.tex

--- 2017-06-22 article/article.tex
@@
       \begin{center}
-      \includegraphics[width=\textwidth]{RRH.pdf}
+      \includegraphics[width=\textwidth]{rrh.pdf}
       \end{center}
@@
       \begin{center}
-      \includegraphics[scale=0.3]{ex3nt.png}
+      \includegraphics[width=\textwidth]{ex3nt.png}
       \end{center}

### 2017-06-23 article/article.tex
modifs typo intro

--- 2017-06-22 article/article.tex
@@
 
-Next generations of mobile network architectures evolve toward centralized radio network architectures or C-RAN, for Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c}.
-The main challenge for this type of architecture is the latency in the transfer process between the Remote Radio Heads (RRHs) on the field and the Baseband Units (BBUs) in the cloud.
-The standard requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in 1 to 10ms depending on targeted services~\cite{bouguen2012lte}.
+Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost owenrship.
+The main challenge for this type of architecture is the latency in the transfer process that is an important factor for dimensioning the network.
+The latency is measured between the sending of a message by the Remote Radio Heads (RRHs) on the field and the receptions of the answers, computed by real-time virtualized network functions on Baseband Units (BBUs), in the cloud.
+For example, even if next radio protocols are less stringent, some standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in 1 to 10ms depending on targeted services~\cite{bouguen2012lte}.
 The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRHs and BBUs.
@@
  In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network.
-The current solution is to use stochastic multiplexing \todo{ref} with a traditional queue management in an optical network with a very large bandwidth to minimize latency.
+The current solution ~\cite{pizzinat2015things,tayq2017real} is to use use dedicated circuits, since statistical multiplexing even with a very large bandwidth, does not comply with the latency requirements.
 Here we propose to use a deterministic approach to schedule our periodic messages.
@@
 Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}.
+The aim is to operate a C-RAN on a low-cost shared switched network.
 
@@
 Time is discretized and a unit of time corresponds to the transmission of a minimal unit of data over the network.
- The process must be periodic, that is if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
+ The process must be  predictable (i.e.
+the date of arrival of packets is known beforehand).
+For the need of this study and to simplify we assume that it is periodic.
+That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
 Moreover, we want to avoid any  buffering in internal nodes of the graph.
@@
 
- Thus in this article, we work on latency and periodicity constraints in fron- thaul.
+ Thus in this article, we work on latency and periodicity constraints in fronthaul.
 The best current solution is to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches [7].
@@
 In Sec.\ref{sec:PAZL}, we study a variant of PALL called PAZL  where the waiting times must all be zero.
-We provide several algorithms, some of their theoretical properties and give experimental evidences that they find periodic assignments when the network is no too loaded.
+We provide several algorithms, some of their theoretical properties and give experimental evidences that they find periodic assignments when the network is not too loaded.
 Finally in Sec.\ref{sec:PALL}, we propose algorithms for the general PALL problem and exhibit one which works extremely well in our experiments even in loaded networks.
@@
 We also define $\lambda(u_0,r)=0$.
-The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
+The length of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
 We denote by $\cal R$ a set of routes,  %in $G$ such that no two routes have the same first vertices or the same last vertices.
@@
 
-      The following table summarize the main notations used in the paper.
-      \begin{center}
-   \begin{tabular}{|c|c|}
-    \hline
-     $(G,\cal R)$ & A Routed network \\
-     \hline
-      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
-      \hline
-      $\lambda (u_i,r)$ & The latency of the vertex $u_i$ through $r$\\
-         \hline
-         $\lambda (r)$ & The latency of a route $r$.\\
-         \hline
-         $P$ & Period\\
-         \hline
-         $\tau$ & Size of a message\\
-         \hline
-         $ [t(v,r)]$&The set of time slots used by route $r$ at vertex $v$ \\
-         & in a period $P$.\\
-         \hline 
-         ${\cal M}=(m_1, \ldots ,m_n)$&Offsets\\
-    \hline
-
-      \end{tabular}
-      \end{center}
-
    \subsection{Problems}\label{nonmonotone}
@@
 
+      The following table summarize the main notations used in the paper.
+      \begin{center}
+   \begin{tabular}{|c|c|}
+    \hline
+     $(G,\cal R)$ & A Routed network \\
+     \hline
+      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
+      \hline
+      $\lambda (u_i,r)$ & The latency of the vertex $u_i$ through $r$\\
+         \hline
+         $\lambda (r)$ & The length of a route $r$\\
+         \hline
+         $P$ & Period\\
+         \hline
+         $\tau$ & Size of a message\\
+         \hline
+         $ [t(v,r)]$&The set of time slots used by route $r$ at vertex $v$ \\
+         & in a period $P$\\
+         \hline 
+         ${\cal M}=(m_1, \ldots ,m_n)$&Assignment(Offsets of each routes)\\
+              \hline 
+         $w_r$& Waiting time on route $r$\\
+            \hline 
+         $PT(r)$&Process time on the route $r$\\
+           \hline 
+         $MT({\cal M})$&Maximum process time of the assignment\\
+    \hline
+
+      \end{tabular}
+      \end{center}
+
 \section{Hardness of PRA}
@@
  Remark that we have used zero weights in the proof. If we ask the weights to be strictly positive, which makes sense in our model since
-they represent the latency of physical links, it is easy to adapt the proof.
+they represent the delay of physical links, it is easy to adapt the proof.
 We just have to set them so that in any route the weight at $u_1$ is equal to $d$ and thus equal to $0$ modulo $d$.

### 2017-06-23 article/article.tex
two stages algorithm

--- 2017-06-23 article/article.tex
@@
 \usepackage{authblk}
+% \usepackage{hyperref}
 
@@
 
-\footnote{This work is partialy supported by the french  ANR project N-GREEN.}
+\footnote{This work is partially supported by the french ANR project N-GREEN.}
 \section{Introduction}
@@
 
-   \subsection{Problems}\label{nonmonotone}
+   \subsection{Periodic route assignment}\label{nonmonotone}
 
@@
 
+      \subsection{Periodic assignment for low latency}
       In the context of cloud-RAN applications, we need to send message from a RRH $u$ to a BBU $v$ and then 
-      we must send the answer from $v$ back to $u$. We say that a routed network $(G, {\cal R})$ is \textbf{symmetric}
-      if there is a bijection $\rho$ between routes such that for any route $r$ with first vertex $u$ and last vertex $v$, $\rho(r)$ has first vertex $v$ and last vertex $u$.
+      we must send the answer from $v$ back to $u$.
+We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitionned into the sets $F$ of forward routes and $B$ of backward routes.
+Moreover there is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
 In all practical cases the routes $r$ and $\rho(r)$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we need not to enforce this property.
@@
          We now give a new interpretation of a $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routed network, so that it represents the sending of a message and of its answer.
-	This assignment represents the following process: first a message is sent at $u$, through the route $r$, at time $m_r$.
+	This assignment represents the following process: first a message is sent at $u$, through the route $r \in F$, at time $m_r$.
 
@@
       $PT(r)=\lambda(r)+ w_r+\lambda(r)$.      
-      In the process time, we count the time between the first time at which a message is emitted and 
-      the first time at which the message comes back.
+      In the process time, we count the time between the first time at which a message is emitted and the first time at which the message comes back.
 Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
@@
 
-\section{The star topology: no waiting time} \label{sec:PAZL}
+\section{The Star Topology: No Waiting Time} \label{sec:PAZL}
 
@@
       From our C-RAN context we choose the following parameters: the number of routes 
-      is at most $n = 20$, $\tau$ is equal to $2500$. Moreover the period is always larger than $n\tau$ otherwise 
-      no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution. 
-      The code in C is available online on the webpages of the authors ~\cite{webpage}.
+      is at most $n = 20$, $\tau$ is equal to $2500$.
+Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.
+      The code in C is available online on the webpage of one of the authors~\cite{webpage}.
 
@@
       First we consider routes which are shorter than $\tau$, that is a message cannot be contained 
-      completely in a single edge.
-This is very common in our context and we will consider graphs in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ slots.
-It corresponds to messages of approximately 1Mb, links of bandwidth 10Gbps and length less than 5km between the BBU and the RRH.
+      completely in a single edge which is very common for our application.
+We generate star topologies in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ slots.
+It corresponds to messages of approximately $1$ Mb, links of bandwidth $10$ Gbps and length less than $5$ km between the BBU and the RRH.
 
@@
 
-   \section{The star topology: minimizing latency}\label{sec:PALL}
-
-    In this section, we still work on the star topology, but we consider again the  PALL problem. 
-    It means that the messages can wait in the target vertices (BBU), in order to find solution that we cannot find without waiting time.
+   \section{The Star Topology: Minimizing Latency}\label{sec:PALL}
+
+    In this section, we still work on the star topology, but we consider again the more general PALL problem.
+It means that the messages can wait in the target vertices (BBUs), in order to find solutions that we cannot find without waiting time.
 We allow the process times $PT$ of the routes to be greater than twice the weight of the routes, but it should less than $T_{max}$.
@@
 	Often in real networks, the length of the routes are not arbitrary and we may exploit that to solve PALL easily.
-For instance if all the weights on the arcs $c_t,t_i$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.
+For instance if all the weights on the arcs $(c_t,t_i)$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.
 	The assignment in that case is trivial, just send all messages so that they follow each other without gaps in the central arc $(c_s,c_t)$.
@@
 
-	A more realistic assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same. It would correspond
-	to a situation where all the BBUs are in the same datacenter.
+	A more realistic assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same. It would correspond to a situation where all the BBUs are in the same datacenter.
 
@@
 	 Let $(G,{\cal R})$ be a symmetric routed network with $n$ routes and let $P \geq n\tau$.
-If for all $i$ and $j$ less than $n$ $\omega(s_i,c_s) = \omega (s_j,c_s)$, then there is a $(P,\tau)$-peridoic assignment with process time $2\max_{r\in {\cal R}} \lambda(r)$ and it can be built in time $O(n\log(n))$.
+If for all $i$ and $j$ less than $n$ $\omega(s_i,c_s) = \omega (s_j,c_s)$, then there is a $(P,\tau)$-peridoic assignment with process time $2\displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
 	 \end{theorem}
@@
 
-        We can simplify the weights on the arcs $(s_i,c_s)$ by setting them all to $0$. We order the routes
-        in decreasing order of their length, that is when $i<j$, $\lambda(r_{i}) > \lambda(r_{j})$.
-        The offset of the route $r_i$ is $i\tau$, which ensures that there are no collision on the way forward (on the arc 
-        $(c_s,c_t)$) as soon as $P \geq n\tau$ which is the minimal possible period.        
-	We set the waiting time of the first message to $0$, thus it reaches the vertex $c_t$ for the second time before going through the arc $(c_t,c_s)$ at time $2\lambda(r_{0})+\tau$.
-The process time of the first message is $PT(r_0) = 2\lambda(r_{0})$.
-	The second message reaches $c_t$ for the second time at $\tau + 2\lambda(r_{1})$. 
-	Therefore to avoid collision, we set the waiting time  $w_1 =  2\lambda(r_{0})+\tau - (\tau + 2\lambda(r_{1})) = 2(\lambda(r_{0}) - \lambda(r_{1}))$, which is positive since $\lambda(r_{0}) > \lambda(r_{1})$.
-
-	We generalize this by setting $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$ which are positive for all $i< n$,
-	since by definition.
-	There are no collision on the way back since the message of the route $r_i$ arrives at $c_t$
-	at time $(i-1)\tau + 2\lambda(r)$. We must also evaluate the process time. 
-	By defintion $PT(r_i) = 2\lambda(r_i) + w_i = 2\lambda(r_i) + 2(\lambda(r_{0}) - \lambda(r_{i})) = 2\lambda(r_0)$.
-	Since all process times are the same, the maximum process time is also equal to $2\lambda(r_0)$.
-
-	Finally, the time to build this assignment is dominated by the sorting of the routes from the longest to the shortest and is thus in $O(n\log(n)$.
+        We can simplify the weights on the arcs $(s_i,c_s)$ by setting them all to $0$.
+        We find the route with maximal length, say that it is $\lambda(r_0)$. The idea is to 
+        set the waiting times of all routes so they behave exactly as the message in $r_0$.
+
+        The offset of the route $r_i$ is set to $i\tau$, which ensures that there are no collision on the way forward (on the arc $(c_s,c_t)$) as soon as $P \geq n\tau$ which is the minimal possible period.
+We fix the waiting time for the route $i$ to $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$.
+We can compute the time at which the message of the route $r_i$ arrives at the vertex $c_t$ on its way back: $t(r_i,(c_t,c_s)) = w_i + i\tau + 2\lambda(r_{i})$
+        by replacing $w_i$ by its value we obtain $t(r_i,(c_t,c_s)) =  i\tau + 2\lambda(r_{0})$
+        As a conclusion there are no collision on the edge $(c_t,c_s)$ as soon as the 
+        period is larger than $n\tau$ (there are no gaps between the messages).
+
+        Now let us compute the process time of the route $r_i$ defined by $PT(r_i) = w_i + 2\lambda(r_{i}) $.
+We obtain $PT(r_i) = 2\lambda(r_{0})$ and thus the maximum process time of the assignment is also equal to $2\lambda(r_0)$.
+	Finally the complexity is $O(n)$ since we have to find a maximum between the size of $n$ routes and the computation of each $w_i$ is done by a constant number of artihmetic operations.
      \end{proof}
-\todo{Une remarque sur le fait que la complexite depend sans doute du nombre de valeurs differentes sur les arcs et pas du nombre de routes.}
-
-     \subsection{A first approach}
-
-	To solve PALL, we propose some heuristics that prioritize the longest routes, and thus helps to minimize the process time $PT(s_i)$ of the routes in order to have no  $PT(s_i) > T_{max}$.
+
+     Remark that this assignment always exists and has no collision when $P \geq n\tau$. 
+     If the difference of the weights of the arcs $\omega(s_i,c_s)$ is bounded 
+     by $d$ and the length of the longest route is $l$, then the maximum process time is bounded 
+     by  $2l + d$.
+
+     \subsection{A two stage approach}
+
+     We can decompose any algorithm solving the PALL problem in two parts: first set the offsets of the forward routes and then the offset of the backward routes or equivalently the waiting times.  
+     The offsets of the forward routes will be chosen so that all messages have no collision on the central arc and such that there are no free slots inbeetween the end of a message on the central arc and the beginning of the next one.
+     We tried the five following orders. 
+	\begin{itemize}
+
+	 \item Longest-Shortest on Routes (LSR): Decreasing order on the length of the routes.
+	 \item Shortest-Longest on Routes (SLR): Increasing order on the length of the routes. 
+	 \item Longest-Shortest on last Arc (LSA): Decreasing order on the length of the arcs $(c_t,t_i)$.
+	 \item Shortest-Longest on last Arc (SLA): Increasing order on the length of the arcs $(c_t,t_i)$.
+This sending order yields a $(P,\tau)$ periodic assignment in which all the $w_i = 0$, if the period is large enough (see proposition \ref{prop:SL}).
+	 \item Random: A random order of the routes.
+	\end{itemize}
+
+   In the rest of the section we will study different methods to compute the offsets of the backward routes, once
+   the offsets of the forward routes are fixed by one of the previous orders.
+
+   \subsection{Returning messages greedily}
+
+    Definition of the deadline of the backward routes and an eligible route at time $t$.
+    Define the greedy algorithm as select the eligible route with smallest deadline, send the message
+    go to the next time. Deal with the periodicity.
+
+%     
+%      We made some simulations and determined that the Random order is the most efficient (see section \ref{sec:resultsPALL}).
+In the rest of the section, we focus on algorithms that computes the affectations for the way back of the process.
+% %      
+% 	To solve PALL, we propose some heuristics that prioritize the longest routes, and thus helps to minimize the process time $PT(s_i)$ of the routes in order to have no  $PT(s_i) > T_{max}$.
 Indeed, one can imagine that, if the messages on the longest routes are less buffered in their target than the messages using the shortest routes, the process times might be balanced.
-	In an optimal solution, if $r_i$ is the longest route, we want $w_i =0$, such that $PT(s_i) = 2.\lambda(r_{s_i}) \geq  2.\lambda(r_{s_j}) + w_j = PT(s_j) $, where $j$ is any route $\neq i$.
-
-     We first suggest the following heuristic, composed of two greedy parts.
+% 	In an optimal solution, if $r_i$ is the longest route, we want $w_i =0$, such that $PT(s_i) = 2.\lambda(r_{s_i}) \geq  2.\lambda(r_{s_j}) + w_j = PT(s_j) $, where $j$ is any route $\neq i$.
+% 
+% 
+%      We first suggest the following heuristic, composed of two greedy parts.
 First, on the forward period, the messages are ordered consecutively, from the one using the longest route, to the one using the shortest route.
 Thus, we set the $m_{s_i}$ of the routes such that  $t(c_s,r_{s_i}) = \tau.i$, if the routes $r_{s_i}$ are ordered from the longest to the shortest.
-
+%      
      Thus, to assign the messages on the backward period, we assign to each route it's deadline, equal to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$, that is,  the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
@@
 
-     However, this heuristic does not take the period into account.
+%      However, this heuristic does not take the period into account.
 Thus, a solution given by this algorithm can satisfy the constraint $MT({\cal M}) \leq T_{max}$, but this solution might have some collisions between the last messages of the period and the first ones of the following period.
-
-     \subsection{Choice of the Sending Order}
-
-	We tried to look at the behavior of our greedy policy with different kinds of sending orders for the messages.
-
-	We tried the five following sending orders.
-Each one determines the order in which messages are sent from sources.
-In every case the messages are consecutive.
-This means that there is no time in the forward period between the end of a message and the beginning of the following one.
-
-	The different sending orders that we tried are the following :
-	\begin{enumerate}
-	 \item Random: Generate $X$ randoms permutations for the routes and try the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic assignment.
-In the following experiments, we take $X = 100$.
-	 \item Longest-Shortest on Routes (LSR): Send the messages from the one using longest to the one using shortest route (this is the sending order used in the previous heuristic).
-	 \item Shortest-Longest on Routes (SLR): Send the messages from the one using shortest to the one using longest route
-	 \item Longest-Shortest on last Arc (LSA): Send the messages from the one having the longest arc between $c_t$ an the target to the one having the shortest one.
-	 \item Shortest-Longest on last Arc (SLA): Send the messages from the one having the shortest arc between $c_t$ an the target to the one having the longest one.
-This sending order gives us some $(P,\tau)$ periodic assignment in which all the $w_i = 0$, but needs a huge period if the difference between the longest and the shortest route is large (see proposition \ref{prop:SL}).
-	\end{enumerate}
-
-     We made some simulations and determined that the Random order is the most efficient (see section \ref{sec:resultsPALL}).
-In the rest of the section, we focus on algorithms that computes the affectations for the way back of the process.
-      \subsection{About periodicity}
+% 
+%
+
      We propose an improved version of the greedy algorithm, which tries to compute some solution that satisfies the period $P$:
@@
 
-     \subsection{Using a scheduling algorithm}
+     \subsection{Returning messages through earliest deadline scheduling}
 
@@
 
-     \subsection{Final algorithm}
+     \subsection{Dealing with the periodicity}
 
@@
 
-    \subsection{Results}
+    \subsection{Experimental evaluation}
     \label{sec:resultsPALL}
@@
     To compare the previous algorithms, we first need to determine which of the sending order is the best.
-We know that Greedy Periodic is strictly better than Greedy, thus, we will compare the different sending orders with Greedy Periodic.
 
@@
 
-   We plan to generalize our study of the PALL problem to more topologies,
-   such as trees and cycles which are commonly found in real networks. 
+   We plan to generalize our study of the PALL problem to more real topologies,
+   such as trees, cycles or bounded treewidth graphs. 
    We would like to design FPT algorithms in the number of routes for PAZL and PALL on the star topology, eventually by relaxing the constraint on the maximal process time into an constraint on the average process time, which seems much more tractable.
-   Moreoever we could allow preemption, that is the messages are allowed to be cut into pieces,
-   which would certainly change the complexity of the problem. 
-   Finally, the routes may not be fixed but chosen to optimize the latency, which would make the problem even more difficult (maybe $\Pi_2$-complete instead of $\NP$-complete).
+
+   We could also study variation of our problem. Instead of minimizing the maximum process time, we could try to minimize
+   the sum of the waiting time, a linear objective which could make linear programming useful.
+   Moreoever we could allow preemption, that is the messages are allowed to be cut into pieces, which would certainly change the complexity of the problem. 
+   Finally, the routes may not be fixed but chosen in the graph to minimize the maximum process time, which would make the problem even more difficult (maybe $\Pi_2$-complete instead of $\NP$-complete).
 

### 2017-06-23 article/article.tex

@@
 
-      The following table summarize the main notations used in the paper.
-      \begin{center}
-   \begin{tabular}{|c|c|}
-    \hline
-     $(G,\cal R)$ & A Routed network \\
-     \hline
-      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
-      \hline
-      $\lambda (u_i,r)$ & The latency of the vertex $u_i$ through $r$\\
-         \hline
-         $\lambda (r)$ & The latency of a route $r$.\\
-         \hline
-         $P$ & Period\\
-         \hline
-         $\tau$ & Size of a message\\
-         \hline
-         $ [t(v,r)]$&The set of time slots used by route $r$ at vertex $v$ \\
-         & in a period $P$.\\
-         \hline 
-         ${\cal M}=(m_1, \ldots ,m_n)$&Offsets\\
-    \hline
-
-      \end{tabular}
-      \end{center}
-
       \subsection{Periodic route assignment}\label{nonmonotone}
@@
       If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic assignment of ${\cal R}$.      
-
 \end{proof}
@@
       In Sec.~\ref{sec:PALL} we will study heuristics which try to solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity.
+
+      The following table summarize the main notations used in the paper.
+      \begin{center}
+   \begin{tabular}{|c|c|}
+    \hline
+     $(G,\cal R)$ & A Routed network \\
+     \hline
+      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
+      \hline
+      $\lambda (u_i,r)$ & The latency of the vertex $u_i$ through $r$\\
+         \hline
+         $\lambda (r)$ & The length of a route $r$\\
+         \hline
+         $P$ & Period\\
+         \hline
+         $\tau$ & Size of a message\\
+         \hline
+         $ [t(v,r)]$&The set of time slots used by route $r$ at vertex $v$ \\
+         & in a period $P$\\
+         \hline 
+         ${\cal M}=(m_1, \ldots ,m_n)$&Assignment(Offsets of each routes)\\
+              \hline 
+         $w_r$& Waiting time on route $r$\\
+            \hline 
+         $PT(r)$&Process time on the route $r$\\
+           \hline 
+         $MT({\cal M})$&Maximum process time of the assignment\\
+    \hline
+
+      \end{tabular}
+      \end{center}
 
@@
      Remark that this assignment always exists and has no collision when $P \geq n\tau$. 
-     If the difference of the weights of the arcs $\omega(s_i,c_s)$ is bounded 
-     by $d$ and the length of the longest route is $l$, then the maximum process time is bounded 
-     by  $2l + d$.
+     If for any $(i,j)$ the difference between the weights of the arcs $(s_i,c_s)$ and $(s_j,c_s)$ is bounded 
+     by $d$ and the length of the longest route is $l$, then the maximum process time is bounded by  $2l + d$.
 

### 2017-06-26 article/article.tex
greedy periodic refait

@@
 	 Let $(G,{\cal R})$ be a symmetric routed network with $n$ routes and let $P \geq n\tau$.
-If for all $i$ and $j$ less than $n$ $\omega(s_i,c_s) = \omega (s_j,c_s)$, then there is a $(P,\tau)$-peridoic assignment with process time $2\displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
+If for all $i$ and $j$ less than $n$ $\omega(s_i,c_s) = \omega (s_j,c_s)$, then there is a $(P,\tau)$-peridoic assignment with process time $2 \times \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
 	 \end{theorem}
@@
 
-     We can decompose any algorithm solving the PALL problem in two parts: first set the offsets of the forward routes and then the offset of the backward routes or equivalently the waiting times.  
+     We can decompose any algorithm solving the PALL problem in two parts: first set the offsets of the forward routes and then knowing this information set the offset of the backward routes or equivalently the waiting times.
      The offsets of the forward routes will be chosen so that all messages have no collision on the central arc and such that there are no free slots inbeetween the end of a message on the central arc and the beginning of the next one.
+     It is done to minimize the period needed to send the messages of the forward route.
      We tried the five following orders. 
@@
 
-   \subsection{Returning messages greedily}
-
-    Definition of the deadline of the backward routes and an eligible route at time $t$.
-    Define the greedy algorithm as select the eligible route with smallest deadline, send the message
-    go to the next time. Deal with the periodicity.
+   \subsection{Greedy scheduling of backward routes}
+
+    Assume that the offsets of the forward routes are fixed by some order. 
+    Consider a forward route $r_i$ and the corresponding backward route $r_{\rho(i)}$.
+    We define the {\bf deadline} of $r_{\rho(i)}$ as $m_{i} + T_{max} - \omega(s_i,c_s)$, that is the latest time at which the message can go out of $c_t$ such that $PT(r_i) \leq T_{max}$.
+    We say that a backward route $r_{\rho(i)}$ is {\bf eligible} at time $t$ if $m_{i} +  \lambda(r_i) + \omega(c_t,t_i) \leq t$, that is the message of the route $r_{\rho(i)}$ arrives at $c_t$ before the time $t$ when $w_i = 0$.
+
+    The first algorithm we propose is a greedy algorithm which sets the offset of the 
+    backward routes. It prioritizes the routes with the earliest deadline to best satisfy the
+    constraint on the process time.
+    Set $t=0$ and repeat the following: find $s \geq t$ the first time for which there is an eligible route with its offset not fixed.
+Then amongst all eligible routes at time $s$ choose the one with the smallest deadline, fix its offset to $s$ and set $t = s + \tau$.
+
+    This algorithm does not take into account the periodicity. Say that $t_0$ is the smallest offset that the algorithm has fixed
+    for a backward route. Then for all routes with an offset smaller than $t_0 + P - \tau$,
+    by construction, there are no collisions on the central arc.
+    However, for routes with larger offsets, since we  should consider everything modulo $P$, 
+    they may collide with any other route.
+Therefore we must adapt the greedy algorithm of the previous paragraph by finding $s \geq t$ the first time for which there is an eligible route with its offset not fixed and \emph{such that there is no collision if a message go
+    through the central arc at time $s$}.
+
+    The greedy algorithm can be made to work in time $O(n\log(n))$. 
+    To do that the set of eligible routes must be maintained in a binary heap
+    to be able to find the one with smallest deadline in time $O(\log(n))$. 
+    To deal with the possible collisions, one can maintain a list of the intervals
+    of time at which a message can be send on the arc $(c_t,c_s)$. Each time the offset of a 
+    route is fixed an interval is split into at most two intervals in constant time. 
+    Since the algorithm goes over the elements of the list at most twice when doing an insertion
+    or looking for the next free interval, the time needed to maintain it is $O(n)$.
 
 %     
-%      We made some simulations and determined that the Random order is the most efficient (see section \ref{sec:resultsPALL}).
-In the rest of the section, we focus on algorithms that computes the affectations for the way back of the process.
-% %      
-% 	To solve PALL, we propose some heuristics that prioritize the longest routes, and thus helps to minimize the process time $PT(s_i)$ of the routes in order to have no  $PT(s_i) > T_{max}$.
-Indeed, one can imagine that, if the messages on the longest routes are less buffered in their target than the messages using the shortest routes, the process times might be balanced.
-% 	In an optimal solution, if $r_i$ is the longest route, we want $w_i =0$, such that $PT(s_i) = 2.\lambda(r_{s_i}) \geq  2.\lambda(r_{s_j}) + w_j = PT(s_j) $, where $j$ is any route $\neq i$.
-% 
-% 
-%      We first suggest the following heuristic, composed of two greedy parts.
-First, on the forward period, the messages are ordered consecutively, from the one using the longest route, to the one using the shortest route.
-Thus, we set the $m_{s_i}$ of the routes such that  $t(c_s,r_{s_i}) = \tau.i$, if the routes $r_{s_i}$ are ordered from the longest to the shortest.
-%      
-     Thus, to assign the messages on the backward period, we assign to each route it's deadline, equal to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$, that is,  the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
-     We then determine the order of the messages by choosing, one by one the message on the route that we want to prioritize (eligible route): At a date $d$, if one or several messages are able to come back to $c_t$ before $d$, the eligible route is the one which have the lowest deadline.
-Otherwise, if any messages are able to be back on $c_t$ before $d$, the eligible route is the one with the first message able to come back to $c_t$.
-
-    \begin{algorithm}[H]
-    \caption{Longest Shortest + Greedy }
-    \begin{algorithmic}
-    \REQUIRE routed network $(G,{\cal R})$, period $P$, $ T_{max}$, packet size $\tau$
-    \ENSURE $(P,\tau)-$periodic assignment of $(G,{\cal R})$
-    \STATE $clock \leftarrow 0$
-    \FORALL{route in $r_{s_i}$ sorted from the longest to the shortest }
-    \STATE  $m_{s_i} \leftarrow clock - t(c_s,r_{s_i}) \mod P$
-    \STATE $clock \leftarrow clock + \tau$
-    \ENDFOR
-
-\STATE compute the deadlines of each routes.
-
-    \WHILE{there is a route which has not been assigned}
-    \STATE determine $r_{t_i}$ the eligible route
-    \IF{ $t(c_t,r{t_i}) < clock$}
-    \STATE $w_i = clock - t(c_t,r_{t_i}) - (m_i + \lambda(r_i)) \mod P$ 
-    \STATE $clock \leftarrow clock + \tau$
-    \ELSE
-    \STATE $w_i \leftarrow 0$
-    \STATE $clock = \lambda(r_i) + t(c_t,r_{t_i}) + \tau$
-   \ENDIF
-
-    \ENDWHILE
-
-    \end{algorithmic}
-    \end{algorithm}
-
-    By using a binary heap to manage the eligible routes, this algorithm runs in $O(n\log(n))$.
-
-    This policy is split in two steps:
-    \begin{enumerate}
-    \item First, we choose an arbitrary sending order for the routes, and we set the offsets $m_i$.
-    \item  Then, we use a greedy policy to determine $m_{\rho_i}$. 
-    \end{enumerate}
-     This {\bf Greedy} policy determines the $m_{\rho_{s_i}}$ avoiding collisions on $c_t$.
-It computes the deadlines for every messages, considering their offsets and the weight on their routes, and determine the time at which the messages must leave their target, prioritizing the messages with the lowest deadlines.
-
-%      However, this heuristic does not take the period into account.
-Thus, a solution given by this algorithm can satisfy the constraint $MT({\cal M}) \leq T_{max}$, but this solution might have some collisions between the last messages of the period and the first ones of the following period.
-% 
-%
-
-     We propose an improved version of the greedy algorithm, which tries to compute some solution that satisfies the period $P$:
-
-     First, we remember the date at which the first messages starts to come back through $c_t$. Let us note $bp$ this date.
-     The greedy policy is the same until the message are assigned in the period between $bp$ and $bp +P$. When a message is assigned, we update a list of free intervals in the backward period.
-     Once we try to assign a message after $bp+P$, we consider that we are in the second period, and thus search a free interval in the period, large enough to put a message.
-
-     This policy can significantly increase $w_i$, but ensures a periodic results.
-This {\bf Greedy Periodic} policy is strictly better than Greedy, because it finds some solutions that greedy would not find, by considering the periodicity in the assignement.
-
-         We compared the two algorithms on $10000$ graphs on which the weight of the links are drawn uniformly between $0$ and $20000$, with a period of $21000$, and giving, for each instance $T_{max} = 2\lambda(r_{longest-route})$ .
+%          We compared the two algorithms on $10000$ graphs on which the weight of the links are drawn uniformly between $0$ and $20000$, with a period of $21000$, and giving, for each instance $T_{max} = 2\lambda(r_{longest-route})$ .
 We then look at the success rate of each algorithms, with every sending order.
@@
 
-     \subsection{Returning messages through earliest deadline scheduling}
+     \subsection{Earliest deadline scheduling}
 

### 2017-06-29 article/article.tex
algo de scheduling, réécriture

@@
 
-    \subsubsection*{Greedy Algorithm}
+    \subsubsection*{Greedy algorithm}
 
@@
 
-	\subsubsection*{Branch and cut}
+	\subsubsection*{Exhaustive search}
 % 	\begin{algorithm}[H]
@@
 
-    \subsection{Experimental Evaluation}\label{sec:exp_PAZL}
+    \subsection{Experimental evaluation}\label{sec:exp_PAZL}
 
@@
 
-     Problem PALL is very similar to a scheduling problem, but many scheduling problems do not consider the periodic aspect.
-The article \cite{simons1978fast} from Simons, schedule jobs which all have the same execution time.
-     This algorithm takes as input some jobs defined by a triplet id-release-deadlines, and an execution time for all jobs.
-A job is not able to be computed before it's release time, and must be finished before it's deadline.
-This algorithm gives in $\mathcal{O}(n^2\log{}n)$ a solution with the earliest  possible completion time, if it exists.
-     We adapted this algorithm, considering the messages as the jobs, the release times as the date at which the messages are able to come back on $c_t$, and the deadlines as the latest date at which a message have to leave $c_t$ to comeback before $m_i + T_{max}$.
-Thus, it tries to minimize the time between the first and the last message in the assignment.
-Let us call {\bf Minimized Scheduling (MS)} this algorithm.
-
-    % MS uses the exact same main scheduling than Greedy.
-Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call {\em crisis message} this message), the algorithm calls a subroutine which, following some criteria, removes some previous messages from the scheduling such that the crisis message can be scheduled earlier.
-Then, the main scheduling routines is applied again.
-Some stopping conditions are able to detect if there is no solution for the given routed network.
-
-     If it exists a solution that satisfies $MT({\cal M}) < T_{max}$, this algorithm gives us a $(P,\tau)$ periodic assignment.
-Nevertheless, by setting the deadlines according to the size of the route only, the given $(P,\tau)$ periodic assignment might not respect the period $P$, because some messages at the end of the period could collide with the messages at the begining of the following period.
-
-     \subsection{Dealing with the periodicity}
-
-     We adapted MS, presented in the previous paragraph, to consider the period, in the computation.
-
-      For every routes of the routed network, the algorithm fixes the first route to comeback in the backward period, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(equal to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).
-
-    \begin{algorithm}[H]
-    \caption{ Minimized Scheduling Periodic (MSP)}
-    \begin{algorithmic}
-    \REQUIRE A routed network $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
-    \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$, if it exists
-
-    \FORALL{route $r_{t_i}$}
-    \STATE  $w_i \leftarrow 0$
-    \STATE period-end $\leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
-    \FORALL{route $r_{t_j}$}
-    \STATE deadline-route$ \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
-    \STATE $deadline \leftarrow$ min(deadline-route,period-end)
-    \ENDFOR
-
-    \STATE Call (MS)
-
-    \ENDFOR
-
-    \STATE return the best $(P,\tau)$-periodic assignment, or FAILURE
-
-    \end{algorithmic}
-    \end{algorithm}
-
-    This algorithm runs in $\mathcal{O}(n^3\log{}n)$.
-It finds more solutions than MS, because it compute the deadlines of the route considering the periodicity.
-Thus, an assignment given by this algorithm is a solution for PALL.
+     The second stage of our approach is very similar to the following scheduling problem: 
+     we are given a set of jobss and each job has a \emph{release time} and a \emph{deadline}. 
+     The problem is to schedule all jobs on a single processor so that no two jobs are scheduled at the same time, a job is always shedulded after its release time and job is finished before its deadline.
+Let us call $n$ the number of jobs, the problem can be solved in time $O(n^2\log(n))$~\cite{simons1978fast} when all jobs have the same running time and it gives a solution with the earliest possible deadline.
+On the other hand if the running times are different the problem is $\NP$-complete~\cite{lenstra1977complexity}.
+     The  polynomial time algorithm  which solves this scheduling problem is similar to the Greedy algorithm presented in the previous section.
+However, when it fails because a job will finish after its deadline, it changes the schedule of the last messages to solve find a possible schedule for the problematic job.
+It does it in a way that it will not fail on the same job a second time except if there is no solution, hence the polynomiality of the algorithm.
+
+     We reduce our problem of setting the offsets of the backwards routes once the order of the forward routes is fixed to this
+     scheduling problem. The backward routes are the jobs, the size of a message is the running time of a job,
+     the deadline of a route is the deadline of the corresponding job and the smallest time at which it is eligible is the release time.
+Let us call {\bf Minimal Latency Scheduling (MLS)} this algorithm.
+     Remark that we do not deal with the periodicity.
+A solution ${\cal M}$ the algorithm finds always respect $MT({\cal M}) < T_{max}$.
+On the other hand, it is guaranteed to be a $(P,\tau)$ periodic assignment only if $m_n - m_1 \leq P -\tau$ where $m_n$ is the largest offset and $m_1$ the smallest one.
+The algorithm we use minimize $m_n - m_1 $, so it may work quite well in practice (as show in Section.\ref{sec:resultsPALL}).
+
+     We now present a variant of the previous algorithm that we call {\bf Periodic Minimal Latency Scheduling (PMLS)}
+     which take into account the periodicity.
+We fix arbitrarily a backward route so that its message is the first to go through the central arc at time $t$.
+Then we modify the deadline of each forward route to be the minimum of their previous deadline and $t + P$.
+We execute this algorithm for every possible first backward route while no solution is found.
+Since we run the previous algorithm at most $n$ times, the complexity is in $O(n^3\log(n))$.
+Remark that it will always find more solution than MLS,
+     because if MLS find a solution with first route $r$ and such that $m_n - m_1 \leq P -\tau$, then this solution will be found by PMLS when it will fix $r$ as the first route.
+Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment
+     since we guarantee that all messages are scheduled in the same period of time of size $P$ and it satisfies $MT({\cal M}) < T_{max}$ by construction of the deadlines.
+Remark that it is possible that there is a solution and PMLS do not find it
+     since we do not allow to chose an offset for a route after $t+P- \tau$ which modulo $P$ does not collide with another route.
+
+%     \begin{algorithm}[H]
+%     \caption{ Minimized Scheduling Periodic (MSP)}
+%     \begin{algorithmic}
+%     \REQUIRE A routed network $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
+%     \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$, if it exists
+%   
+%     \FORALL{route $r_{t_i}$}
+%     \STATE  $w_i \leftarrow 0$
+%     \STATE period-end $\leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
+%     \FORALL{route $r_{t_j}$}
+%     \STATE deadline-route$ \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
+%     \STATE $deadline \leftarrow$ min(deadline-route,period-end)
+%     \ENDFOR
+%     
+%     \STATE Call (MS)
+% 
+%     
+%     \ENDFOR
+% 
+%     \STATE return the best $(P,\tau)$-periodic assignment, or FAILURE
+% 
+%     \end{algorithmic}
+%     \end{algorithm}
 
@@
 
-    To compare the previous algorithms, we first need to determine which of the sending order is the best.
-
-   In this experiment, we fix the number of routes to 8.
-We want to compare the sending orders with the worst parameters, so we drew the links between $0$ and $20000$ slots.
-We look at the success rate of each sending order with Greedy Periodic to assign the messages in the way back.
-We give to  $T_{max}$ some {\em flexibility}.
-This flexibility represents $T_{max} - 2\lambda(r_{longest-route})$.
-We let this flexibility vary from $0$ to $3000$.
-
-   We look at two different regimes: first, we take a period equal to $1,05n\tau$, and then, we take a greater period, that is, $1,5n\tau$. The following results are computed over $10000$ instances.
+    First we try to understand what is the best choice of order for the first phase of the algorithm.
+    We fix the number of routes to $8$, and we  draw uniformly the weigths of the arcs between $0$ and $20000$ slots.
+    For a given topology, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
+    Hence, for a given topology giving the margin or $T_{max}$ is the same, but since we will consider many topologies 
+    wich may have different longest route's size, it will be more meaningful to set the margin rather than $T_{max}$.
+    In fact the margin represents the latency imposed by the communication process without taking into account the physical length 
+    of the network which cannot be changed. In our experiments the margin range from  $0$ to $3000$ slots.
+   We look at two different regimes: first, we take a period equal to $1,05n\tau$ to represent a very loaded network
+   and then we chose $1,5n\tau$ for a mildly loaded network.
+Chosing a larger one is not relevant since then we know how to solve the problem without waiting times as shown in Section~\ref{sec:exp_PAZL}.
+We represent the success rate with regards to the margin,
+   for the five kind of orders using the Greedy algorithm for the second stage, computed over $10000$ random star topologies.
+Note that for the random order, we compute $100$ random orders and count it as a success as soon as there is a solution for one order.
 
@@
       \end{center}
-      \caption{Success rate of the sending orders for $P = 21000$}
+      \caption{Success rate of different orders with $P = 21000$}
 
      \end{figure}       
-
 \begin{figure}[H]
@@
       \end{center}
-      \caption{Success rate of the sending orders for a $P = 30000$}
+      \caption{Success rate of differents orders with $P = 30000$}
       \label{fig:success30000}
@@
 
-     First, we remark that, for every sending order, the success rate is strictly better for large periods.
-This is due to the fact that the size of the period is a factor for failure.
-According to our results, the two SL sending orders are not good, in any cases.
+     As expected, the  success rate is much better for large periods.
+According to our results, sending the messages from the sortest to the longest route or arc does not work well.
+It corresponds to the policy of Proposition~\ref{prop:SL} which does not work well when the routes are long as it is the case.
+Sending from the longest to the shortest route or arc works better and it seems that sorting the routes according to the length of $(c_t,t_i)$ is better at least in loaded network.
+     FInally the random order is much better than the other orders, when the load is not high ($P = 30000$) there is always a solution with margin $0$.
+
+    the two SL sending orders are not good, in any cases.
 However, the LS orders seem to increase when the flexibility is large enough, but in the two regimes, they appear to be stagnating to a lower success rate than Random.

### 2017-07-04 article/article.tex
corrections finales

@@
 
-     The second stage of our approach is very similar to the following scheduling problem: 
-     we are given a set of jobss and each job has a \emph{release time} and a \emph{deadline}. 
-     The problem is to schedule all jobs on a single processor so that no two jobs are scheduled at the same time, a job is always shedulded after its release time and job is finished before its deadline.
+     The problem to solve in the second stage of our approach is very similar to the following scheduling problem: 
+     we are given a set of jobs and each job has a \emph{release time} and a \emph{deadline}. 
+     The problem is to schedule all jobs on a single processor, that is choosing the time at which they are computed, so that no two jobs are scheduled at the same time.
+A job is always scheduled after its release time and it must be finished before its deadline.
 Let us call $n$ the number of jobs, the problem can be solved in time $O(n^2\log(n))$~\cite{simons1978fast} when all jobs have the same running time and it gives a solution with the earliest possible deadline.
@@
      The  polynomial time algorithm  which solves this scheduling problem is similar to the Greedy algorithm presented in the previous section.
-However, when it fails because a job will finish after its deadline, it changes the schedule of the last messages to solve find a possible schedule for the problematic job.
-It does it in a way that it will not fail on the same job a second time except if there is no solution, hence the polynomiality of the algorithm.
+However, when it fails because a job will finish after its deadline, it changes the schedule of the last messages to find a possible schedule for the problematic job.
+The change in the scheduling is so that the algorithm cannot fail on the same job a second time except if there is no solution, hence the polynomiality of the algorithm.
 
@@
      Remark that we do not deal with the periodicity.
-A solution ${\cal M}$ the algorithm finds always respect $MT({\cal M}) < T_{max}$.
-On the other hand, it is guaranteed to be a $(P,\tau)$ periodic assignment only if $m_n - m_1 \leq P -\tau$ where $m_n$ is the largest offset and $m_1$ the smallest one.
-The algorithm we use minimize $m_n - m_1 $, so it may work quite well in practice (as show in Section.\ref{sec:resultsPALL}).
+When MLS finds a solution ${\cal M}$ its always satisfies $MT({\cal M}) < T_{max}$.
+On the other hand, it is a $(P,\tau)$ periodic assignment only if $m_n - m_1 \leq P -\tau$ where $m_n$ is the largest offset and $m_1$ the smallest one.
+The algorithm we use minimize $m_n - m_1 $, so it may work quite well in practice (as shown in Section.\ref{sec:resultsPALL}).
 
@@
 Remark that it will always find more solution than MLS,
-     because if MLS find a solution with first route $r$ and such that $m_n - m_1 \leq P -\tau$, then this solution will be found by PMLS when it will fix $r$ as the first route.
+     because if MLS find a solution with first route $r$ and such that $m_n - m_1 \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route.
 Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment
-     since we guarantee that all messages are scheduled in the same period of time of size $P$ and it satisfies $MT({\cal M}) < T_{max}$ by construction of the deadlines.
-Remark that it is possible that there is a solution and PMLS do not find it
-     since we do not allow to chose an offset for a route after $t+P- \tau$ which modulo $P$ does not collide with another route.
+     since we guarantee that all messages are scheduled in a period of time of size $P$ and it satisfies $MT({\cal M}) < T_{max}$ by construction of the deadlines.
+Remark that it is possible that there is a solution and PMLS does not find it
+     since we do not allow to choose an offset for a route after $t+P- \tau$ which modulo $P$ may not collide with another route.
 
@@
 
-    First we try to understand what is the best choice of order for the first phase of the algorithm.
-    We fix the number of routes to $8$, and we  draw uniformly the weigths of the arcs between $0$ and $20000$ slots.
+    In this section, we first try to understand what is the best choice of order for the first stage of the algorithm.
+    We fix the number of routes to $8$ to make comparisons with the results of Section~\ref{sec:exp_PAZL} easier. 
+    We draw uniformly the weights of the arcs between $0$ and $20000$ slots.
     For a given topology, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
-    Hence, for a given topology giving the margin or $T_{max}$ is the same, but since we will consider many topologies 
-    wich may have different longest route's size, it will be more meaningful to set the margin rather than $T_{max}$.
-    In fact the margin represents the latency imposed by the communication process without taking into account the physical length 
-    of the network which cannot be changed. In our experiments the margin range from  $0$ to $3000$ slots.
-   We look at two different regimes: first, we take a period equal to $1,05n\tau$ to represent a very loaded network
-   and then we chose $1,5n\tau$ for a mildly loaded network.
-Chosing a larger one is not relevant since then we know how to solve the problem without waiting times as shown in Section~\ref{sec:exp_PAZL}.
-We represent the success rate with regards to the margin,
-   for the five kind of orders using the Greedy algorithm for the second stage, computed over $10000$ random star topologies.
-Note that for the random order, we compute $100$ random orders and count it as a success as soon as there is a solution for one order.
+    Hence, for a given topology choosing the margin or $T_{max}$ is the same, but since we will consider many topologies 
+    which may have different longest route's size, it will be more meaningful to set the margin rather than $T_{max}$.
+    In fact the margin represents the latency imposed by the communication process without taking into account the physical length of the network which cannot be changed.
+In our experiments the margin range from  $0$ to $3000$ slots.
+   We look at two different regimes: we take a period equal to $1,05n\tau$ to represent a very loaded network
+   and $1,5n\tau$ for a mildly loaded network.
+Choosing a larger period is not relevant since then we know how to solve the problem even without waiting times as shown in Section~\ref{sec:exp_PAZL}.
+We represent the success rate with regards to the margin, for the five kind of orders using the Greedy algorithm for the second stage, computed over $10000$ random star topologies.
+Note that for the random order, we compute $1000$ random orders and count it as a success as soon as there is a solution for one order.
 
@@
       \end{center}
-      \caption{Success rate of differents orders with $P = 30000$}
+      \caption{Success rate of different orders with $P = 30000$}
       \label{fig:success30000}
@@
      As expected, the  success rate is much better for large periods.
-According to our results, sending the messages from the sortest to the longest route or arc does not work well.
-It corresponds to the policy of Proposition~\ref{prop:SL} which does not work well when the routes are long as it is the case.
-Sending from the longest to the shortest route or arc works better and it seems that sorting the routes according to the length of $(c_t,t_i)$ is better at least in loaded network.
-     FInally the random order is much better than the other orders, when the load is not high ($P = 30000$) there is always a solution with margin $0$.
-
-    the two SL sending orders are not good, in any cases.
-However, the LS orders seem to increase when the flexibility is large enough, but in the two regimes, they appear to be stagnating to a lower success rate than Random.
-As we can see the random finds near to 100\% of the solutions when the period is large enough, even when we give no flexibility.
-     %On average, it is necessary to draw 6 randoms sending order to find a solution, when the period is large, but in some particularly hard instances, it can be impossible to find a solution, even with 100 randoms sending orders.
-
-     To observe  the impact of the number of random sending orders drawn, we compared the success rate of the following number of drawing, on graphs in which the links are drawn  between $0$ and $20000$ slots, with a period $P=20000$, and a flexibility of $0$.
-The following table present the average success rate of each number of sending orders, on $1000$ instances.
+According to our experiments, sending the messages from the shortest to the longest route or arc does not work well.
+It corresponds to the policy of Proposition~\ref{prop:SL} which does not work well when the routes are long as it is the case in these experiments.
+Sending from the longest to the shortest route or arc works better and it seems that sorting the routes according to the length of the last arc rather than the route is better, at least in a loaded network.
+
+     The random order is is the best by far. When the load is not too high ($P = 30000$) there is always a solution with margin $0$.
+     Note that, when disallowing waiting times, there were instance without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the PALL problem.
+Remark that the random order corresponds to the best of $1000$ orders drawn uniformly which means that a computation can be up to $1000$ time slower than for a fixed order.
+The choice of the number of random orders drawn yields a trade-off between the computation time and the success rate.
+Therefore we investigate the success rate of our algorithm with regards to the number of random orders drawn, a period of $21000$ and a margin $0$.
+The following table presents the average success rate for each number of sending orders, on $1000$ instances.
        \begin{figure}[H]
@@
 
-     In our case of $8$ routes, the number of different possible sending orders is $8!
-\simeq 40 000$.
-By drawing $1000$ random sending orders, we explore near to $2,5 \%$ of the cases, which seems enough to find as many solutions as if generate more random sending orders.
-
-     We now want to compare the performances of the different algorithms on the way back.
-Since GP showed some excellent results on large periods (see Fig~\ref{fig:success30000}), it is more interesting to focus on the behavior of the algorithms on short periods.
-The following experience is realized on graph with $8$ routes (links between $0$ and $20000$), and with a period of $21000$.
-Since we just conclude that drawing $1000$ sending order is enough, with $8$ routes, we now generate $1000$ randoms sending orders instead of $100$.
+    The number of different orders is $7!$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order.
+Therefore when doing $1000$ random draws, we explore less than $20\%$ of the possible orders but it is already enough to get the best results on average.
+
+     We now want to compare the performances of the three different algorithms used in the second stage.
+Since GD showed excellent results on mild loads, it is more interesting to focus on the behavior of the algorithms on high load.
+The following experience is realized on graph with $8$ routes, weights of the arcs drawn between $0$ and $20000$ and with a period of $21000$.
+We choose the best possible first stage found in the previous experiments, that is trying $1000$ random orders.
 
@@
 
-     The algorithm MS, that does not consider the periodicity for the scheduling is far worst than the others, and, even if GP seems to converge too $100\%$ of success rate when the flexibility is large enough, MSP is always strictly better.
-We remark that when the flexibility is low ($<500$) there is still near to $5\%$ of failure for MSP.
-
-   Thus, using the Random sending order combined with MSP for the way back seems to be a very good algorithm to solve PALL.
-Nevertheless, there is still a few number of instances in the worst area of parameters (very short period, and very low flexibility), that are impossible to solve with our algorithm.
-
- To evaluate the performance of our best algorithm to find solutions, that is, generating $1000$ randoms sending orders and using MSP on the way back, we compared it's performance against the actual way to manage the messages in a network.
-Nowadays, the networks are managed through a stochastic model.
-The messages in the nodes are assigned following a FIFO rule.
-Even if this policy works well, in practice when the network is not too loaded, it does not ensure a minimum latency.
-Thus, some latency critical applications like C-RAN needs some deterministic algorithms.
-To model such a network, we generate some randoms offsets in the sources.
-Then we simulate the behavior of a stochastic network during a great number of periods.
-
-We simulated a stochastic network on $1000$ instances with $8$ long routes (links between $0$ and $20000$).
-The results are not really different if we use short routes.
-The flexibility needed by an instance of the network is computed by taking the message which have the highest process time, at which we subtract the weight of the longest route.
-We measure, for periods from $20000$ ( network fully loaded), to $50000$ ($40 \%$ of load), the medians, the first, and the third quartiles of $1000$ results.
+     The algorithm MLS performs poorly, worst than GP and PMLS, which shows that taking into account the periodicity is fundamental.
+     The GP algorithms is close to $100\%$ success rate for margins larger than $1500$ while the PMLS finds a solution in more than $95\%$ of the experiments, even with a margin $0$.
+Therefore, for the worst possible constraints on load and margin, there are a few instances for which we do not find a solution.
+However, with a margin of $500$, which corresponds to about $0.025$ms of additional delay with the chosen parameters, we always find a solution.
+
+     Now that we have found the best amongst the algorithms solving PALL, we need to compare its performances against the actual way to manage the messages in a network.
+The classical way to manage messages in the network is statistical multiplexing,
+     where there is a FIFO buffer in each node of the network to deal with the collisions.
+The time at which the messages are sent in the network is not computed as in our approach, thus we fix the offsets of each route to some random value.
+     Even if this policy seems to work in practice when the network is not too loaded, it does not give any guarantee on the latency.
+Remark that the process is not periodic, therefore we must measure the process time of each route over several periods if we want to compute its maximum.
+We choose to simulate it for $1000$ periods and we have observed that it usually stabilizes after $10$ periods.
+The margin is also defined as the maximum process time, computed as explained, minus twice the size of the longest route.
+
+     We draw $1000$ instances of a star topology with $8$ routes, with weights on the arcs drawn between $0$ and $20000$.
+Note that the results are almost the same when the arcs are small.
+We measure, for periods from $20000$ (network fully loaded), to $50000$ ($40 \%$ of load), the median, the first, and the third quartiles of the margins computed in $1000$ simulations using FIFO buffer to resolve collisions.
 
@@
       \end{center}
-      \caption{Needed flexibility on stochastic networks according to the load.}
+      \caption{Needed margin with respect to the period for a stochastic policy}
       \label{fig:sto}
@@
 
-    We also made a linear search to find the minimum flexibility needed by our algorithm on those loads to find a solution.
-There are few cases, when both the flexibility and the period are too restricted in which there is no solutions: with a period of $20000$, our algorithm needs in average $\simeq 80$ slots of flexibility to find a solution.
-Otherwise, the algorithm finds a solution with $0$ flexibility for every periods $>20000$.
-On the other hand, the stochastic policy does not ensure a minimal latency.
+     We also computed the minimum margin needed by PMLS to find a solution.
+With a period of $20000$, our it needs in average $\simeq 80$ slots of flexibility to find a solution.
+Otherwise, the algorithm finds a solution with a margin $0$ for every period larger than $20000$.
+On the other hand, the simulations show clearly that the stochastic policy does not ensure a minimal latency.
 As we can see in Fig~\ref{fig:sto}), the more the network is loaded, the higher the latency is.
-Even if the first quartile is to $0$ when the network is not highly loaded, many instances needs some flexibility.
-Moreover, the latency is not guaranteed with that policy.
-Indeed, even if half of the cases of our simulations works with less than $1000$ slots of flexibility on a light loaded network, that could be reasonable for specific applications, $25\%$ of the cases needs more than $2000$ slots of flexibility.
-With our algorithm, we control the latency, and here, we have optimal solutions that makes it really appropriate.
+When the network is highly loaded,
+     we have instances with a margin of about $10000$ which corresponds to half the period, that is $0.5$ms. 
+     Even when the network is lightly loaded,  a quarter of the instances have a margin of more than $2000$
+     which is $x$ times more than PMLS for a network fully loaded ! 
+     We feel that it strongly justifies the use of a deterministic sending scheme for latency critical applications such as our C-RAN motivating problem.
 
@@
 
-   We plan to generalize our study of the PALL problem to more real topologies,
+   We plan to generalize our study of the PALL problem to other topologies,
    such as trees, cycles or bounded treewidth graphs. 
@@
    the sum of the waiting time, a linear objective which could make linear programming useful.
-   Moreoever we could allow preemption, that is the messages are allowed to be cut into pieces, which would certainly change the complexity of the problem. 
+   Moreover we could allow preemption, that is the messages are allowed to be cut into pieces, which would certainly change the complexity of the problem. 
    Finally, the routes may not be fixed but chosen in the graph to minimize the maximum process time, which would make the problem even more difficult (maybe $\Pi_2$-complete instead of $\NP$-complete).

### 2017-07-06 article/article.tex
codes variance

--- 2017-06-26 article/article.tex
@@
 
+     \begin{algorithm}[H]
+    \caption{ Greedy }
+    \begin{algorithmic}
+    \REQUIRE A routed network $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
+    \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$, of failure
+   \STATE  ${\cal H} \leftarrow$ empty binary min heap
+       \STATE  free\_ intervals $\leftarrow$ [0,$P$]
+
+    \FORALL{route $r_{i}$}
+    \STATE  deadline[$r_i$]  $\leftarrow$ add $m_{i} + T_{max} - \omega(s_i,c_s)$
+    \STATE  eligible\_time[$r_i$] $\leftarrow$ add $m_{i} +  \lambda(r_i) + \omega(c_t,t_i)$
+      \ENDFOR
+
+      \WHILE{There is some non-assigned routes}
+      \IF{${\cal H}$ is empty}
+      \STATE t $\leftarrow $ min\_non\_assigned(eligible\_time)
+      \STATE take $r_i$ the route with eligible\_time[$r_i$] = t
+      \STATE ${\cal H}$ $\leftarrow$ insert ($r_i$, deadlines($r_i$).
+      \ENDIF
+
+      \STATE extract the route $r_i$ with the lowest deadline from ${\cal H}$
+      \STATE t $\leftarrow$ beginning of the first free interval of size $\tau$ after t
+      \STATE $w_i \leftarrow$ t - eligible\_time[$r_i$]
+      \STATE update(free\_ intervals)
+      \STATE t $\leftarrow$ t + $\tau$
+      \FORALL{routes $r_i$ with  eligible\_time[$r_i$] = t}
+      \STATE ${\cal H}$ $\leftarrow$ insert ($r_i$, deadlines($r_i$).
+      \ENDFOR
+      \ENDWHILE
+%    \STATE  $w_i \leftarrow 0$
+%    \FORALL{route $r_{t_i}$}
+%    \STATE  $w_i \leftarrow 0$
+%    \STATE period-end $\leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
+%    \FORALL{route $r_{t_j}$}
+%    \STATE deadline-route$ \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
+%    \STATE $deadline \leftarrow$ min(deadline-route,period-end)
+%    \ENDFOR
+
+    \end{algorithmic}
+    \end{algorithm}
+    The function  min\_non\_assigned(eligible\_time) returns the lowest time in eligible\_time, for which the corresponding route is not assigned yet.
+The function update(free\_ intervals) cuts the interval used in a first part of size $\tau$, which correspond to the message, and a second part with the rest of the size, which is still free.
+
     The greedy algorithm can be made to work in time $O(n\log(n))$. 

### 2017-07-06 code/Calculs autres/ecart_type.c

@@ -153,11 +153,12 @@ void quartiles()
 {
 	FILE * f = fopen("traitement.data","w");
 	lire_fichier();
-	for(int i = 0;i<nb_periodes;i++)
+	for(int i = nb_periodes-1;i>=0;i--)
 	{
 		tri_bulles(donnes[i],taille);
-		fprintf(f,"%d %d %d %d\n",20000+i*1000,donnes[i][taille/4+1],donnes[i][taille/2+1],donnes[i][3*taille/4+1]);
-		fprintf(stdout,"%d %d %d %d\n",20000+i*1000,donnes[i][taille/4+1],donnes[i][taille/2+1],donnes[i][3*taille/4+1]);
+		fprintf(f,"%d %d %d %d 0\n",(int)(20000/(20000+i*1000.0)*100),donnes[i][taille/4+1]/20 ,donnes[i][taille/2+1]/20,donnes[i][3*taille/4+1]/20);
+		fprintf(stdout,"%d %d %d %d 0\n",(int)(20000/(20000+i*1000.0)*100),donnes[i][taille/4+1]/20 ,donnes[i][taille/2+1]/20,donnes[i][3*taille/4+1]/20);
+
 	}
 	fclose(f);
 }
@@ -201,8 +202,8 @@ int main()
 	/*for(int i=20000;i<49000;i+=5000)
 	trace_distribs(i);
 	//*/
-	//quartiles();
-	transfo();
-	genere_plot();
+	quartiles();
+	//transfo();
+	//genere_plot();
 
 }

### 2017-07-06 code/Calculs autres/variance.c

@@ -1,0 +1,48 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <time.h>
+#include <math.h>
+
+#define LAMBDA 14
+
+int loi_de_poisson_naif(float u)
+{
+	double p = exp (- LAMBDA);
+	int x = 0;
+	double f = p;
+	do
+	{
+		x += 1;
+		p = p*LAMBDA/x;
+		f += p;
+	} while (u > f);
+	return x;
+}
+
+
+int main(){
+	srand(time(NULL));
+	double variance = 0.0;
+	double moyenne = 0.0;
+
+	int nb_simuls = 1000000;
+	int result;
+	int max = 0;
+	float tirage; 
+	for(int i=0;i<nb_simuls;i++)
+	{
+		tirage = (float)rand() / RAND_MAX ;
+		result = loi_de_poisson_naif(tirage);
+		if(result*5 > max)max=result*5;
+		variance += (result*result);
+		moyenne += result;
+	}
+	moyenne /= nb_simuls;
+
+
+	variance /= nb_simuls;
+	variance -= (moyenne*moyenne);
+
+	printf("Variance = %f, Moyenne = %f, MAX = %d\n",variance,moyenne,max);
+	return 0;
+}

### 2017-07-07 article/article.tex
tableaux nombre random deplace

@@
      \begin{algorithm}[H]
-    \caption{ Greedy }
+    \caption{ Greedy deadline ({\bf GD}) }
     \begin{algorithmic}
@@
     \FORALL{route $r_{i}$}
-    \STATE  deadline[$r_i$]  $\leftarrow$ add $m_{i} + T_{max} - \omega(s_i,c_s)$
-    \STATE  eligible\_time[$r_i$] $\leftarrow$ add $m_{i} +  \lambda(r_i) + \omega(c_t,t_i)$
+    \STATE  deadline[$r_i$]  $\leftarrow$  $m_{i} + T_{max} - \omega(s_i,c_s)$
+    \STATE  eligible\_time[$r_i$] $\leftarrow$ $m_{i} +  \lambda(r_i) + \omega(c_t,t_i)$
       \ENDFOR
@@
       \STATE take $r_i$ the route with eligible\_time[$r_i$] = t
-      \STATE ${\cal H}$ $\leftarrow$ insert ($r_i$, deadlines($r_i$).
+      \STATE ${\cal H}$ $\leftarrow$ insert ($r_i$, deadlines($r_i$)).
       \ENDIF
 
-      \STATE extract the route $r_i$ with the lowest deadline from ${\cal H}$
+      \STATE Extract the route $r_i$ with the lowest deadline from ${\cal H}$
       \STATE t $\leftarrow$ beginning of the first free interval of size $\tau$ after t
@@
       \STATE t $\leftarrow$ t + $\tau$
-      \FORALL{routes $r_i$ with  eligible\_time[$r_i$] = t}
+      \FORALL{routes $r_i$ with  eligible\_time[$r_i$] $\leq$ t}
       \STATE ${\cal H}$ $\leftarrow$ insert ($r_i$, deadlines($r_i$).
@@
     The function  min\_non\_assigned(eligible\_time) returns the lowest time in eligible\_time, for which the corresponding route is not assigned yet.
-The function update(free\_ intervals) cuts the interval used in a first part of size $\tau$, which correspond to the message, and a second part with the rest of the size, which is still free.
+The function update(free\_ intervals) removes an interval of size $\tau$, which correspond to the message,  from free\_ intervals.
 
@@
 \begin{figure}[H] 
-
-       \begin{center}
-      \includegraphics[scale=0.4]{departs_gp_21000.pdf}
-      \end{center}
+    \begin{minipage}[c]{6cm}
+  \centering
+      \includegraphics[width=6cm]{departs_gp_21000.pdf}
+
       \caption{Success rate of different orders with $P = 21000$}
-
-     \end{figure}       
-\begin{figure}[H]
-
-       \begin{center}
-      \includegraphics[scale=0.4]{departs_gp_30000.pdf}
-      \end{center}
+      \end{minipage} \hfill
+        \begin{minipage}[c]{6cm}
+          \includegraphics[width=6cm]{departs_gp_30000.pdf}
       \caption{Success rate of different orders with $P = 30000$}
+
+            \end{minipage} \hfill
                   \label{fig:success30000}
@@
      Note that, when disallowing waiting times, there were instance without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the PALL problem. 
-Remark that the random order corresponds to the best of $1000$ orders drawn uniformly which means that a computation can be up to $1000$ time slower than for a fixed order.
-The choice of the number of random orders drawn yields a trade-off between the computation time and the success rate.
-Therefore we investigate the success rate of our algorithm with regards to the number of random orders drawn, a period of $21000$ and a margin $0$.
-The following table presents the average success rate for each number of sending orders, on $1000$ instances.
-       \begin{figure}[H]
-
-       \begin{center}
-   \begin{tabular}{|c|c|c|c|c|c|c|}
-    \hline
-    number of randoms & $1$ & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
-    \hline
-    Success rate $(\simeq)$ & $17,8$ &$60,5$&$77,7$&$80,5$&$80,5$&$80,5$\\
-    \hline
-      \end{tabular}
-      \end{center}
-   \caption{Impact of the number of randoms sending orders drawn}
-     \end{figure}
-
-    The number of different orders is $7!$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order.
-Therefore when doing $1000$ random draws, we explore less than $20\%$ of the possible orders but it is already enough to get the best results on average.
-
      We now want to compare the performances of the three different algorithms used in the second stage.
@@
 The following experience is realized on graph with $8$ routes, weights of the arcs drawn between $0$ and $20000$ and with a period of $21000$.
-We choose the best possible first stage found in the previous experiments, that is trying $1000$ random orders.
+We represent the success rate with regards to the margin, for the three algorithms, using the randoms sending orders for the first stage, computed over $10000$ random star topologies.
+We choose arbitrarily to try $1000$ random orders.
 
@@
        \begin{center}
-      \includegraphics[scale=0.4]{retour_21000.pdf}
+      \includegraphics[scale=0.45]{retour_21000.pdf}
       \end{center}
@@
 
-     The algorithm MLS performs poorly, worst than GP and PMLS, which shows that taking into account the periodicity is fundamental.
-     The GP algorithms is close to $100\%$ success rate for margins larger than $1500$ while the PMLS finds a solution in more than $95\%$ of the experiments, even with a margin $0$.
+     The algorithm MLS performs poorly, worst than GD and PMLS, which shows that taking into account the periodicity is fundamental.
+     The GD algorithms is close to $100\%$ success rate for margins larger than $1500$ while the PMLS finds a solution in more than $95\%$ of the experiments, even with a margin $0$.
 Therefore, for the worst possible constraints on load and margin, there are a few instances for which we do not find a solution.
 However, with a margin of $500$, which corresponds to about $0.025$ms of additional delay with the chosen parameters, we always find a solution.
+
+    Remark that the random order corresponds to the best of $1000$ orders drawn uniformly which means that a computation can be up to $1000$ time slower than for a fixed order.
+The choice of the number of random orders drawn yields a trade-off between the computation time and the success rate.
+Up to now, we chose $1000$ random orders arbitrarily.
+We investigate the success rate of our algorithm with regards to the number of random orders drawn, a period of $21000$ and a margin $0$.
+The following tables presents the average success rate for each number of sending orders, on $1000$ instances, for GD and PMLS.
+
+         \begin{figure}[H] 
+       \begin{center}
+   \begin{tabular}{|c|c|c|c|c|c|c|}
+    \hline
+    number of randoms & $1$ & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
+    \hline
+    Success rate $(\simeq)$ & $0.6$ &$7.1$&$33.4$&$76.4$&$90.0$&$90.0$\\
+    \hline
+      \end{tabular}
+      \end{center}
+   \caption{Impact of the number of randoms sending orders drawn with GD}
+     \end{figure}
+
+            \begin{figure}[H]
+
+       \begin{center}
+   \begin{tabular}{|c|c|c|c|c|c|c|}
+    \hline
+    number of randoms & $1$ & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
+    \hline
+    Success rate $(\simeq)$ & $41,1$ &$82,5$&$94,5$&$96,2$&$97,2$&$97,2$\\
+    \hline
+      \end{tabular}
+      \end{center}
+   \caption{Impact of the number of randoms sending orders drawn with PMLS}
+     \end{figure}
+
+The number of different orders is $7!$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order.
+Therefore when doing $1000$ random draws, we explore less than $20\%$ of the possible orders but it is already enough to get the best results on average.
+\todo{Dire ici qu'on a du coup tout explore en 10000, et que pour PMLS ca suffit de faire 1000}
 

### 2017-07-07 code/Sources/main.c

@@ -8,6 +8,8 @@
 #include "struct.h"
 #include "init.h"
 #include "random.h"
+
+#include "operations.h"
 int main()
 {
 	srand(time(NULL));
@@ -41,7 +43,7 @@ int main()
 	/*****
 	Taux de reussite de départ PALL avec un retour GP sur une periode donnée (on fait varier la marge)
 	*****/
-	//sucess_aller_PALL(8,2500,20000,3000,2000,21000);
+	//sucess_aller_PALL(8,2500,20000,3000,10000,21000);
 
 
 
@@ -54,7 +56,7 @@ int main()
 	Taux de reussite des algos PALL avec un aller random sur une periode donnée (on fait varier la marge)
 	*****/
 
-	//sucess_retour_PALL(8,2500,20000,3000,1000,21000);
+	//sucess_retour_PALL(8,2500,20000,3000,10000,21000);
 
 
 	/******************************************/
@@ -63,7 +65,7 @@ int main()
 	//Taux de reussite des diferents nombres d'instances générées
 	*****/
 
-	//nombre_random_PALL(8,2500,20000,1000, 20000);
+	//nombre_random_PALL(8,2500,20000,1000, 21000);
 
 	/*****
 	Tmax moyen pour sto vs sp
@@ -72,5 +74,25 @@ int main()
 	marge_PALL_stochastique(8,2500,20000,1000,50000);
 
 
+	/******
+	Bout de code pour tester la stabilisation de la marge necessaire quand on simule plusieurs periodes en stochastique
+
+	Graphe g;
+	int tmax;
+	for(int i = 1;i<=1000;i*=10)
+	{
+		tmax = 0;
+		for(int j=0;j<10000;j++)
+		{
+			
+			g = init_graphe(2*8+1);
+			graphe_etoile(g,20000);
+
+			tmax = max(tmax,stochastic(g,2500,20000,i,1));
+		}
+		printf(" %d : max = %d\n",i,tmax);
+
+	}
+	****/
 	return 0;
 }

### 2017-07-07 code/Sources/simulations.c

@@ -141,11 +141,11 @@ void sucess_aller_PALL(int nb_routes, int taille_paquets,int taille_route,int ma
 	int resa,resb,resc,resd,rese;
 	float a,b,c,d,e;
 	int tmax;
-	int nb_rand = 100;
+	int nb_rand = 1000;
 	float moyenne_etape;
 	
 		
-	for(int marge=0;marge<= marge_max;marge += 50)
+	for(int marge=0;marge<= marge_max;marge += 100)
 	{
 		a=0;
 		b=0;
@@ -256,7 +256,7 @@ void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int m
 
 	
 		
-	for(int marge=0;marge<= marge_max;marge += 50)
+	for(int marge=0;marge<= marge_max;marge += 150)
 	{
 		gp=0;
 		s=0;
@@ -355,7 +355,7 @@ void nombre_random_PALL(int nb_routes, int taille_paquets,int taille_route, int 
 	int tmax;
 	
 
-	for(int nb_rand=1;nb_rand<= 1;nb_rand *= 10)
+	for(int nb_rand=1;nb_rand<= 100000;nb_rand *= 10)
 	{
 		a=0;
 		#pragma omp parallel for private(res,g,tmax) if (PARALLEL) schedule (static)
@@ -370,6 +370,7 @@ void nombre_random_PALL(int nb_routes, int taille_paquets,int taille_route, int 
 			
 			for(int compteur_rand = 0;compteur_rand<nb_rand;compteur_rand++)
 				{
+					//res = longest_etoile_periodique(g,taille_paquets,periode,tmax,0);
 					res = simons_periodique(g,taille_paquets,tmax,periode,0);
 					if(res != -2)
 					{	
@@ -416,20 +417,18 @@ void marge_PALL_stochastique(int nb_routes,int taille_paquets,int taille_route, 
 	FILE * F2 = fopen("../datas/donnes_random.data","w");
 	Graphe g ;
 	long long int total_sto,total_sp;
-	float ecart_type;
+
 	int ressto;
-	int min,max;
+
 	int ressp;
-	int nb_rand = 100;
+	int nb_rand = 1000;
 
 
 	for(int periode=taille_paquets*nb_routes;periode<periode_max ;periode+=1000)
 	{
 		total_sto = 0;
 		total_sp = 0;
-		ecart_type =0;
-		min = INT_MAX;
-		max = 0;
+
 	
[…]

### 2017-07-10 article/article.tex
expérience random orders

@@
     In this section, we still work on the star topology, but we consider again the more general PALL problem.
-It means that the messages can wait in the target vertices (BBUs), in order to find solutions that we cannot find without waiting time.
-We allow the process times $PT$ of the routes to be greater than twice the weight of the routes, but it should less than $T_{max}$.
+It means that the messages can wait in the target vertices (BBUs) in order to find solutions when there are none without waiting time.
+We allow the process times $PT$ of the routes to be greater than twice the weights of the routes, but it should less than $T_{max}$.
 
@@
 	 Let $(G,{\cal R})$ be a symmetric routed network with $n$ routes and let $P \geq n\tau$.
-If for all $i$ and $j$ less than $n$ $\omega(s_i,c_s) = \omega (s_j,c_s)$, then there is a $(P,\tau)$-peridoic assignment with process time $2 \times \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
+If there is a constant $c$ such that $\forall i < n, \,\omega(s_i,c_s) = c$, then there is a $(P,\tau)$-peridoic assignment with process time $2 \times \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
 	 \end{theorem}
@@
         The offset of the route $r_i$ is set to $i\tau$, which ensures that there are no collision on the way forward (on the arc $(c_s,c_t)$) as soon as $P \geq n\tau$ which is the minimal possible period.
-We fix the waiting time for the route $i$ to $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$.
+We set the waiting time for the route $i$ to $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$.
 We can compute the time at which the message of the route $r_i$ arrives at the vertex $c_t$ on its way back: $t(r_i,(c_t,c_s)) = w_i + i\tau + 2\lambda(r_{i})$
@@
      Remark that this assignment always exists and has no collision when $P \geq n\tau$. 
-     If for any $(i,j)$ the difference between the weights of the arcs $(s_i,c_s)$ and $(s_j,c_s)$ is bounded 
+     If for any pair of indices $(i,j)$ the difference between the weights of the arcs $(s_i,c_s)$ and $(s_j,c_s)$ is bounded 
      by $d$ and the length of the longest route is $l$, then the maximum process time is bounded by  $2l + d$.
@@
     We define the {\bf deadline} of $r_{\rho(i)}$ as $m_{i} + T_{max} - \omega(s_i,c_s)$, that is the latest time at which the message can go out of $c_t$ such that $PT(r_i) \leq T_{max}$.
-    We say that a backward route $r_{\rho(i)}$ is {\bf eligible} at time $t$ if $m_{i} +  \lambda(r_i) + \omega(c_t,t_i) \leq t$, that is the message of the route $r_{\rho(i)}$ arrives at $c_t$ before the time $t$ when $w_i = 0$.
+    We say that a backward route $r_{\rho(i)}$ is {\bf eligible} at time $t$ if $m_{i} +  \lambda(r_i) + \omega(c_t,t_i) \leq t$, that is the message of the route $r_{\rho(i)}$ arrives at $c_t$ before time $t$ when $w_i = 0$.
 
@@
      The  polynomial time algorithm  which solves this scheduling problem is similar to the Greedy algorithm presented in the previous section.
-However, when it fails because a job will finish after its deadline, it changes the schedule of the last messages to find a possible schedule for the problematic job.
+However, when it fails because a job finishes after its deadline, it changes the schedule of the last messages to find a possible schedule for the problematic job.
 The change in the scheduling is so that the algorithm cannot fail on the same job a second time except if there is no solution, hence the polynomiality of the algorithm.
@@
 On the other hand, it is a $(P,\tau)$ periodic assignment only if $m_n - m_1 \leq P -\tau$ where $m_n$ is the largest offset and $m_1$ the smallest one.
-The algorithm we use minimize $m_n - m_1 $, so it may work quite well in practice (as shown in Section.\ref{sec:resultsPALL}).
+The algorithm we use minimize $m_n - m_1 $, so it may work quite well in practice (as shown in Section~\ref{sec:resultsPALL}).
 
      We now present a variant of the previous algorithm that we call {\bf Periodic Minimal Latency Scheduling (PMLS)}
-     which take into account the periodicity.
+     which takes into account the periodicity.
 We fix arbitrarily a backward route so that its message is the first to go through the central arc at time $t$.
@@
      since we guarantee that all messages are scheduled in a period of time of size $P$ and it satisfies $MT({\cal M}) < T_{max}$ by construction of the deadlines.
-Remark that it is possible that there is a solution and PMLS does not find it
-     since we do not allow to choose an offset for a route after $t+P- \tau$ which modulo $P$ may not collide with another route.
+The scheduling algorithm we use always finds a solution to the  original problem it solves.
+However, in our periodic context, we do not allow to choose an offset for a route after $t+P- \tau$ which modulo $P$ may not collide with another route.
+Therefore PMLS may fail while there is a solution.
 
@@
     We draw uniformly the weights of the arcs between $0$ and $20000$ slots.
-    For a given topology, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
-    Hence, for a given topology choosing the margin or $T_{max}$ is the same, but since we will consider many topologies 
-    which may have different longest route's size, it will be more meaningful to set the margin rather than $T_{max}$.
+    For a given routed network, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
+    Hence, for a routed network choosing the margin or $T_{max}$ is the same, but since we will consider many networks 
+    whith different longest route's size, it will be more meaningful to set the margin rather than $T_{max}$.
     In fact the margin represents the latency imposed by the communication process without taking into account the physical length of the network which cannot be changed.
@@
 
-     The random order is is the best by far. When the load is not too high ($P = 30000$) there is always a solution with margin $0$.
-     Note that, when disallowing waiting times, there were instance without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the PALL problem. 
+     The random order is the best by far. When the load is not too high ($P = 30000$) there is always a solution with margin $0$.
+     Note that, when disallowing waiting times, there were instances without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the PALL problem.
 We now want to compare the performances of the three different algorithms used in the second stage.
-Since GD showed excellent results on mild loads, it is more interesting to focus on the behavior of the algorithms on high load.
-The following experience is realized on graph with $8$ routes, weights of the arcs drawn between $0$ and $20000$ and with a period of $21000$.
-We represent the success rate with regards to the margin, for the three algorithms, using the randoms sending orders for the first stage, computed over $10000$ random star topologies.
-We choose arbitrarily to try $1000$ random orders.
+Since GD already showed excellent results on mild loads, it is more interesting to focus on the behavior of the algorithms on high load.
+Moreover, we will use $1000$ random orders for the first stage as it gives the best results.
+The following experiment is realized on routed networks with $8$ routes, weights of the arcs drawn between $0$ and $20000$ and with a period of $21000$.
+We represent the success rate with regards to the margin, for the three algorithms computed over $10000$ random star topologies.
 
@@
       \end{center}
-      \caption{Success rate of the different algorithms for a $P = 21000$}
+      \caption{Success rate of GD, MLS and PMLS for $P = 21000$}
      \label{fig:success21000}
@@
 
-     The algorithm MLS performs poorly, worst than GD and PMLS, which shows that taking into account the periodicity is fundamental.
-     The GD algorithms is close to $100\%$ success rate for margins larger than $1500$ while the PMLS finds a solution in more than $95\%$ of the experiments, even with a margin $0$.
+     The MLS algorithm performs poorly, worst than GD and PMLS, which shows that taking into account the periodicity is fundamental.
+     The GD algorithms is close to $100\%$ success rate for margins larger than $1500$ while the PMLS algorithm finds a solution in more than $95\%$ of the experiments, even with a margin $0$.
 Therefore, for the worst possible constraints on load and margin, there are a few instances for which we do not find a solution.
@@
     \hline
-    number of randoms & $1$ & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
-    \hline
-    Success rate $(\simeq)$ & $0.6$ &$7.1$&$33.4$&$76.4$&$90.0$&$90.0$\\
+    Number of random orders & $1$ & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
+    \hline
+    Percentage of success of GD & $0.6$ &$7.1$&$33.4$&$76.4$&$90.0$&$90.0$\\
+    \hline
+    Percentage of success of PMLS & $41,1$ &$82,5$&$94,5$&$96,2$&$97,2$&$97,2$\\
     \hline
@@
       \end{center}
-   \caption{Impact of the number of randoms sending orders drawn with GD}
+   \caption{Impact of the number of random sending orders}
      \end{figure}
 
-            \begin{figure}[H]
-
-       \begin{center}
-   \begin{tabular}{|c|c|c|c|c|c|c|}
-    \hline
-    number of randoms & $1$ & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
-    \hline
-    Success rate $(\simeq)$ & $41,1$ &$82,5$&$94,5$&$96,2$&$97,2$&$97,2$\\
-    \hline
-      \end{tabular}
-      \end{center}
-   \caption{Impact of the number of randoms sending orders drawn with PMLS}
-     \end{figure}
-
-The number of different orders is $7!$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order.
-Therefore when doing $1000$ random draws, we explore less than $20\%$ of the possible orders but it is already enough to get the best results on average.
-\todo{Dire ici qu'on a du coup tout explore en 10000, et que pour PMLS ca suffit de faire 1000}
+First remark that we can improve our previous results by taking $10000$ random orders, which 
+yields the best results for the two algorithms.
+The number of different orders is $7!= 5040$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order.
+Therefore instead of doing $10000$ random draws we could test every possible order in less time.
+However this method would not be practical already for $n = 12$.
+On the other hand, remark that the success rate of PMLS is already high for $100$ random orders, which means that we 
+can decrease the computing time without affecting the success rate tom much.
 
      Now that we have found the best amongst the algorithms solving PALL, we need to compare its performances against the actual way to manage the messages in a network.
-The classical way to manage messages in the network is statistical multiplexing,
-     where there is a FIFO buffer in each node of the network to deal with the collisions.
+The classical way to manage messages in the network is statistical multiplexing, where there is a FIFO buffer in each node of the network to deal with the collisions.
 The time at which the messages are sent in the network is not computed as in our approach, thus we fix the offsets of each route to some random value.

### 2017-07-10 article/article.tex
experiences

@@
 Therefore, for the worst possible constraints on load and margin, there are a few instances for which we do not find a solution.
-However, with a margin of $500$, which corresponds to about $0.025$ms of additional delay with the chosen parameters, we always find a solution.
+However, with a margin of $1000$, which corresponds to about $0.05$ms of additional delay with the chosen parameters, we always find a solution.
 
@@
 Therefore instead of doing $10000$ random draws we could test every possible order in less time.
-However this method would not be practical already for $n = 12$.
-On the other hand, remark that the success rate of PMLS is already high for $100$ random orders, which means that we 
-can decrease the computing time without affecting the success rate tom much.
+However this method would not be practical with regard to the computation time for $n = 15$.
+On the other hand, remark that the success rate of PMLS is already high for $100$ random orders, which means it will work even better than the other methods when $n$ is larger and that the number of random orders drawn is critical.
 
@@
 Remark that the process is not periodic, therefore we must measure the process time of each route over several periods if we want to compute its maximum.
-We choose to simulate it for $1000$ periods and we have observed that it usually stabilizes after $10$ periods.
-The margin is also defined as the maximum process time, computed as explained, minus twice the size of the longest route.
+We choose to simulate it for $1000$ periods and we have observed that the process time usually stabilizes after $10$ periods.
+The margin is defined as the maximum process time, computed as explained, minus twice the size of the longest route.
 
@@
 Note that the results are almost the same when the arcs are small.
-We measure, for periods from $20000$ (network fully loaded), to $50000$ ($40 \%$ of load), the median, the first, and the third quartiles of the margins computed in $1000$ simulations using FIFO buffer to resolve collisions.
+We measure, for periods from $20000$ (network fully loaded), to $50000$ ($40 \%$ of load), the median, the first, and the third quartile of the margins computed in $1000$ simulations using FIFO buffer to resolve collisions.
 
@@
 
-     We also computed the minimum margin needed by PMLS to find a solution.
-With a period of $20000$, our it needs in average $\simeq 80$ slots of flexibility to find a solution.
-Otherwise, the algorithm finds a solution with a margin $0$ for every period larger than $20000$.
-On the other hand, the simulations show clearly that the stochastic policy does not ensure a minimal latency.
+     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Figure~\ref{fig:sto} since even the third quartile was always at $0$ for a period of $20000$.
+     There is around $20\%$ of the instances for which the margin is larger than $0$ for $P=20000$ and $7\%$
+     for $P = 21000$. For the instances with a margin larger than $0$, the margin is on average $400$.
+
+     The simulations show clearly that the stochastic policy does not ensure a minimal latency.
 As we can see in Fig~\ref{fig:sto}), the more the network is loaded, the higher the latency is.
@@
      Even when the network is lightly loaded, a quarter of the instances have a margin of more than $2000$
-     which is $x$ times more than PMLS for a network fully loaded ! 
+     which is more than what PMLS finds for the worst instance and a network fully loaded ! 
      We feel that it strongly justifies the use of a deterministic sending scheme for latency critical applications such as our C-RAN motivating problem.

### 2017-07-12 article/article.tex
quelques corrections supplémentaires

@@
 \title{Deterministic Scheduling of Periodic Messages in a Network}% by a SDN (deterministic) approach}
-%\author{Dominique Barth - UVSQ ,Christian Cadéré - UVSQ,Maël Guiraud - UVSQ,Olivier Marcé - Nokia Bell Labs France,Yann Strozecki - UVSQ}
 
@@
 \author[1]{Dominique Barth}
-\author[1]{Christian Cad\'er\'e}
+% \author[1]{Christian Cad\'er\'e}
 \author[2]{Brice Leclerc}
@@
 
-Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost owenrship.
+Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost ownership.
 The main challenge for this type of architecture is the latency in the transfer process that is an important factor for dimensioning the network.
@@
 The current solution ~\cite{pizzinat2015things,tayq2017real} is to use use dedicated circuits, since statistical multiplexing even with a very large bandwidth, does not comply with the latency requirements.
+
+ \todo{mettre la suite de l'état de l'art}
+
  Here we propose to use a deterministic approach to schedule our periodic messages.
@@
 the date of arrival of packets is known beforehand).
-For the need of this study and to simplify we assume that it is periodic.
+For simplicity, in this article we assume that the process is periodic.
 That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
 Moreover, we want to avoid any  buffering in internal nodes of the graph.
-Hence we need to design
- a periodic process with no collision between messages.
+Hence we need to design a periodic process with no collision between messages.
 To ensure that this property is always true we propose a deterministic process.
@@
 
+ \todo{à revoir, citation ?}
  Thus in this article, we work on latency and periodicity constraints in fronthaul.
-The best current solution is to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches [7].
-This architecture is very ex- pensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
-It is then needed to find a solution to offer low latency over commoditized packet based networks.
-Indeed, dynamical optical bypass and dynamical management of the emission should be considered to guarantee latency constraints, as it is considered in the french ANR project N-GREEN.
-This project proposes a new type of switching/routing node and a specific net- work architecture exploiting WDM packets thanks to a new generation of optical add/drop multiplexers (WSADM: WDM slotted add/drop multiplexer).
+The best current solution is to rely on an almost full optical approach, where each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches [7].
+This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
+
+%  Hence a solution is needed to offer low latency over commoditized packet based networks.
+Indeed, dynamical optical bypass and dynamical management of the emission should be considered to guarantee latency constraints, as in the french ANR project N-GREEN.
+This project proposes a new type of switching/routing node and a specific network architecture exploiting WDM packets thanks to a new generation of optical add/drop multiplexers (WSADM: WDM slotted add/drop multiplexer).
 These packets having a fixed duration close to 1?s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.
-
-The problem we thus focus on here may look like wormhole problems~\cite{cole1996benefit}, but here we want to minimize the time lost in buffers and not just avoid deadlocks, moreover the periodicity is not considered in wormhole problems.
+%  
+The problem we focus on here may look like wormhole problems~\cite{cole1996benefit}, but here we want to minimize the time lost in buffers and not just to avoid deadlocks, moreover the periodicity is not considered in wormhole problems.
 Several graph colorings have been introduced to model similar problems such as the allocation of frequencies~\cite{borndorfer1998frequency}, bandwidths~\cite{erlebach2001complexity} or routes~\cite{cole1996benefit} in a network or train schedules~\cite{strotmann2007railway}.
-Unfortunately, they do not take into account the periodicity of the scheduling and the associated problems are also $\NP$-complete.
+Unfortunately, they do not take into account the periodicity of the scheduling and the associated problems are already $\NP$-complete.
 The only model which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple, zhu2001circular,zhu2006recent} but is not expressive enough to capture our problem.
@@
  In Sec.~\ref{sec:def} we propose a model of the network and the periodic sending of messages along its routes. 
- We then formalize our two problems of finding a periodic assignment for sending messages without collisions: PRA (sending of the message only) and PALL (sending of the message and answer).  
+ We then formalize our two problems of finding a periodic assignment for sending messages without collisions: PRA (sending of the message only) and PALL (sending of the message and of the answer).  
 In Sec.~\ref{sec:complexity}, we prove that the problem PRA and PALL are $\NP$-hard and cannot be approximated even for very
@@
 
+      \todo{commencer les routes à 0 ou pas ?}
+
       A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=(m_1, \ldots ,m_n)$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
@@
       We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
-      Even approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic assignment is hard.
+      In fact, approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic assignment is already hard.
 
@@
       we must send the answer from $v$ back to $u$.
-We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitionned into the sets $F$ of forward routes and $B$ of backward routes.
+We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of forward routes and $B$ of backward routes.
 Moreover there is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
@@
 Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
-      However, since all messages are of size $\tau$, it will not change the problem we consider in the rest of the article.
+      However, since all messages are of size $\tau$, it will not change the problems we consider in the rest of the article.
       Finally, we could add to the process time the computation time a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
@@
     \hline
-     $(G,\cal R)$ & A Routed network \\
+     $(G,\cal R)$ & Routed network \\
      \hline
@@
       \hline
-      $\lambda (u_i,r)$ & The latency of the vertex $u_i$ through $r$\\
-         \hline
-         $\lambda (r)$ & The length of a route $r$\\
+      $\lambda(u_i,r)$ & Latency of the vertex $u_i$ in $r$\\
+         \hline
+         $\lambda(r)$ & Length of the route $r$\\
          \hline
@@
          \hline
-         $ [t(v,r)]$&The set of time slots used by route $r$ at vertex $v$ \\
+         $ [t(v,r)]$& Set of time slots used by route $r$ at vertex $v$ \\
          & in a period $P$\\
          \hline 
-         ${\cal M}=(m_1, \ldots ,m_n)$&Assignment(Offsets of each routes)\\
-              \hline 
-         $w_r$& Waiting time on route $r$\\
-            \hline 
-         $PT(r)$&Process time on the route $r$\\
-           \hline 
-         $MT({\cal M})$&Maximum process time of the assignment\\
+         ${\cal M}=(m_1, \ldots ,m_n)$& Assignment: an offset for each route)\\
+              \hline 
+         $w_r$& Waiting time of the route $r$\\
+            \hline 
+         $PT(r)$& Process time of the route $r$\\
+           \hline 
+         $MT({\cal M})$& Maximum process time of the assignment\\
     \hline
@@
 
+  \paragraph*{Acknowledgments} The authors thanks Christian Cadere and David Auger for the friendly discussions
+  they had on the subject and their insightful remarks.
+
 \bibliographystyle{ieeetr}

### 2017-07-12 article/article.tex
article figures algo routes 0

@@
  In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network.
-The current solution ~\cite{pizzinat2015things,tayq2017real} is to use use dedicated circuits, since statistical multiplexing even with a very large bandwidth, does not comply with the latency requirements.
-
- \todo{mettre la suite de l'état de l'art}
+The current solution ~\cite{pizzinat2015things} is to use use dedicated circuits, since statistical multiplexing even with a very large bandwidth, does not comply with the latency requirements.
+ \todo{mettre la suite de l'Etat de l'art}
+ Thus in this article, we work on latency and periodicity constraints in fronthaul.
+The best current solution is to rely on an almost full optical approach, where each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches ~\cite{tayq2017real}.
+This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
 
@@
 
- \todo{à revoir, citation ?}
- Thus in this article, we work on latency and periodicity constraints in fronthaul.
-The best current solution is to rely on an almost full optical approach, where each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches [7].
-This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
-
 %  Hence a solution is needed to offer low latency over commoditized packet based networks.
@@
 
-      \todo{commencer les routes à 0 ou pas ?}
-
-      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=(m_1, \ldots ,m_n)$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+      \todo{commencer les routes  0 ou pas ?}
+
+      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{n-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
 The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
@@
   \SetGraphUnit{5}
-  \node[draw,circle] (s3) at (4, 2) {$s_3$}; 
-  \node[draw,circle] (s2) at (0, 4) {$s_2$}; 
-  \node[draw,circle] (s1) at (0, 6) {$s_1$};
-
-  \node[draw,circle] (t3) at (14, 7) {$t_3$}; 
-  \node[draw,circle] (t2) at (14, 4) {$t_2$}; 
-  \node[draw,circle] (t1) at (10, 2) {$t_1$};
+  \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
+  \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
+  \node[draw,circle] (s1) at (0, 6) {$s_0$};
+
+  \node[draw,circle] (t3) at (14, 7) {$t_2$}; 
+  \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
+  \node[draw,circle] (t1) at (10, 2) {$t_0$};
 
@@
       First, for each arc $(u,v)$, there is also an arc $(v,u)$ with the same weight.
-      There are two sets of vertices, $S=\{s_1,...,s_n\}$ and $T=\{t_1,...,t_n\}$ of cardinality $n$ and two special nodes:
+      There are two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes:
       the central source node {\bf $c_s$} and the central target node {\bf $c_t$}.
@@
 
-\tikzset{
-  LabelStyle/.style = { rectangle, rounded corners, draw,
-                       font = \bfseries },
-  EdgeStyle/.append style = {<->} }
-
+\tikzset{EdgeStyle/.style={<->,font=\scriptsize,above,sloped,midway}}
   \SetGraphUnit{5}
 
-  \node[draw,circle] (s3) at (0, 0) {$s_3$}; 
-  \node[draw,circle] (s2) at (0, 2) {$s_2$}; 
-  \node[draw,circle] (s1) at (0, 4) {$s_1$};
-
-  \node[draw,circle] (t3) at (8, 0) {$t_3$}; 
-  \node[draw,circle] (t2) at (8, 2) {$t_2$}; 
-  \node[draw,circle] (t1) at (8, 4) {$t_1$};
+  \node[draw,circle] (s3) at (0, 0) {$s_2$}; 
+  \node[draw,circle] (s2) at (0, 2) {$s_1$}; 
+  \node[draw,circle] (s1) at (0, 4) {$s_0$};
+
+  \node[draw,circle] (t3) at (8, 0) {$t_2$}; 
+  \node[draw,circle] (t2) at (8, 2) {$t_1$}; 
+  \node[draw,circle] (t1) at (8, 4) {$t_0$};
 
@@
 
-  \Edge[label = $\omega(s_1.c_s)$](s1)(cs)
+  \Edge[label = $\omega(s_1\,c_s)$](s1)(cs)
   \Edge[label = $\omega(...)$](s2)(cs)
@@
 For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ $m_{\rho(r)} + \lambda(r) \mod P$.
-  Consider an assignment $\{m_1,\dots,m_n\}$ of a star topology and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
-  Then $\{m_1',\dots,m_n'\}$ is an assignment of the same star topology where the weights of the arcs from $s_i$ to $c_s$ are $0$
+  Consider an assignment $\{m_0,\dots,m_{n-1}\}$ of a star topology and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
+  Then $\{m_0',\dots,m_{n-1}'\}$ is an assignment of the same star topology where the weights of the arcs from $s_i$ to $c_s$ are $0$
   for all $i$. Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
@@
     The messages are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
-    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{i}$ the offset of $r_i$ to $(i-1)\tau$. We call this algorithm {\bf Shortest-Longest}.
+    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{i}$ the offset of $r_i$ to $i\tau$. We call this algorithm {\bf Shortest-Longest}.
 
@@
 
-      \begin{proposition} Let $(G, {\cal R})$ be a symmetric routed network, and let $n\tau + 2(\lambda(r_{n}) - \lambda(r_{1})) \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which is given by Shortest-Longest in time $O(n\log(n))$.\label{prop:SL}
+      \begin{proposition} Let $(G, {\cal R})$ be a symmetric routed network, and let $n\tau + 2(\lambda(r_{n}) - \lambda(r_{0})) \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which is given by Shortest-Longest in time $O(n\log(n))$.\label{prop:SL}
       \end{proposition}
       \begin{proof}
-       Since $m_{s_i} = (i-1)\tau$, $[t(c_s,r_{i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.
-
-       We may assume that $\lambda(r_{1}) = 0$, since removing $\lambda(r_{1})$ from every arc $(c_t,t_i)$ does not change the order on the length of the routes nor the collisions between messages.
-       Since $\lambda(r_{1}) = 0$, by hypothesis we have $n\tau + 2\lambda(r_{n}) \leq P$ which implies that
-       $[t(c_s,r_{i})] = \{2 \lambda(r_{i}) + (i-1)\tau, \dots,  2 \lambda(r_{i}) + i\tau -1\}$.
-       Since $ \lambda(r_{i}) \leq  \lambda(r_{i+1})$ by construction, we have  $2 \lambda(r_{i}) + i\tau -1 < 2 \lambda(r_{i+1}) + i\tau$ which proves that there are no collision on the backward period.
+       Since $m_{s_i} = i\tau$, $[t(c_s,r_{i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.
+
+       We may assume that $\lambda(r_{0}) = 0$, since removing $\lambda(r_{0})$ from every arc $(c_t,t_i)$ does not change the order on the length of the routes nor the collisions between messages.
+       Since $\lambda(r_{0}) = 0$, by hypothesis we have $n\tau + 2\lambda(r_{n}) \leq P$ which implies that
+       $[t(c_t,r_{i})] = \{2 \lambda(r_{i}) + i\tau, \dots,  2 \lambda(r_{i}) + (i+1)\tau -1\}$.
+       Since $ \lambda(r_{i}) \leq  \lambda(r_{i+1})$ by construction, we have  $2 \lambda(r_{i}) + i\tau -1 < 2 \lambda(r_{i+1}) + (i+1)\tau$ which proves that there are no collision on the backward period.
 
@@
     \begin{algorithmic}
-    \REQUIRE A routed network $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
-    \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$, of failure
-   \STATE  ${\cal H} \leftarrow$ empty binary min heap
-       \STATE  free\_ intervals $\leftarrow$ [0,$P$]
+    \REQUIRE A routed network $(G,{\cal R})$, a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
+    \ENSURE $(P,\tau)$-periodic assignment of $(G,{\cal R})$, or failure
+   \STATE  ${\cal H} \leftarrow$ empty set //{\em set of eligible routes}
+       \STATE  free\_ intervals $\leftarrow$ [0,$P$] //{\em list of intervals of free slots}
 
@@
       \STATE take $r_i$ the route with eligible\_time[$r_i$] = t
-      \STATE ${\cal H}$ $\leftarrow$ insert ($r_i$, deadlines($r_i$)).
+      \STATE 
       \ENDIF
 
-      \STATE Extract the route $r_i$ with the lowest deadline from ${\cal H}$
-      \STATE t $\leftarrow$ beginning of the first free interval of size $\tau$ after t
+      \STATE $r \leftarrow $ extract\_min(${\cal H}$)
+      \STATE t $\leftarrow$ next\_free\_interval(free\_intervals, t) //{\em if there is no more free intervals of size $\tau$, the algorithm fails}
       \STATE $w_i \leftarrow$ t - eligible\_time[$r_i$]
-      \STATE update(free\_ intervals)
+      \STATE update(t,free\_ intervals)
       \STATE t $\leftarrow$ t + $\tau$
       \FORALL{routes $r_i$ with  eligible\_time[$r_i$] $\leq$ t}
-      \STATE ${\cal H}$ $\leftarrow$ insert ($r_i$, deadlines($r_i$).
+      \STATE insert ( ${\cal H}$,$r_i$).
       \ENDFOR
@@
     The function  min\_non\_assigned(eligible\_time) returns the lowest time in eligible\_time, for which the corresponding route is not assigned yet.
-The function update(free\_ intervals) removes an interval of size $\tau$, which correspond to the message,  from free\_ intervals.
+The function update(free\_intervals) removes an interval of size $\tau$ beginning at t, which correspond to the message,  from free\_intervals.
 

### 2017-07-12 article/article.tex
quelques corrections + debut FPT

--- 2017-07-12 article/article.tex
@@
 \footnote{This work is partially supported by the french ANR project N-GREEN.}
+
 \section{Introduction}
@@
 
+\todo{citation [7] pour les reseaux points a points ?}
  In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network. 
-The current solution ~\cite{pizzinat2015things,tayq2017real} is to use use dedicated circuits, since statistical multiplexing even with a very large bandwidth, does not comply with the latency requirements.
-
- \todo{mettre la suite de l'état de l'art}
-
+ Statistical multiplexing even with a large bandwidth does not comply with the latency requirements.
+Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits.
+Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches.
+This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
+ %Hence a solution is needed to offer low latency over cheap packet based networks. 
  Here we propose to use a deterministic approach to schedule our periodic messages.
@@
 
- \todo{à revoir, citation ?}
- Thus in this article, we work on latency and periodicity constraints in fronthaul.
-The best current solution is to rely on an almost full optical approach, where each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches [7].
-This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
-
-%  Hence a solution is needed to offer low latency over commoditized packet based networks.
-Indeed, dynamical optical bypass and dynamical management of the emission should be considered to guarantee latency constraints, as in the french ANR project N-GREEN.
-This project proposes a new type of switching/routing node and a specific network architecture exploiting WDM packets thanks to a new generation of optical add/drop multiplexers (WSADM: WDM slotted add/drop multiplexer).
-These packets having a fixed duration close to 1?s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.
-%  
-The problem we focus on here may look like wormhole problems~\cite{cole1996benefit}, but here we want to minimize the time lost in buffers and not just to avoid deadlocks, moreover the periodicity is not considered in wormhole problems.
+The problem we focus on here may look like wormhole problems~\cite{cole1996benefit}, but here we want to minimize the time lost in buffers and not just to avoid deadlocks, and we also need to deal with the periodicity.
 Several graph colorings have been introduced to model similar problems such as the allocation of frequencies~\cite{borndorfer1998frequency}, bandwidths~\cite{erlebach2001complexity} or routes~\cite{cole1996benefit} in a network or train schedules~\cite{strotmann2007railway}.
 Unfortunately, they do not take into account the periodicity of the scheduling and the associated problems are already $\NP$-complete.
-The only model which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple, zhu2001circular,zhu2006recent} but is not expressive enough to capture our problem.
+The only coloring which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple, zhu2001circular,zhu2006recent} but is not expressive enough to capture our problem.
 
@@
 Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time slots taken by a signal to go from $u$ to $v$ using this arc.
-A {\bf route} $r$ in $G$ is a path, that is sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
+A {\bf route} $r$ in $G$ is a path, that is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
 The {\bf latency} of a vertex $u_i$ in a path $r$, with $i \geq 1$, is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} \omega(a_j)$.
@@
 The length of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
-We denote by $\cal R$ a set of routes,  %in $G$ such that no two routes have the same first vertices or the same last vertices.
-the pair $(G,\cal R)$ is called a {\bf routed network} and represents our telecommunication network.
+We denote by $\cal R$ a set of routes, the pair $(G,\cal R)$ is called a {\bf routed network} and represents our telecommunication network.
 The first vertex of a route models an antenna (RRH) and the last one a data-center (BBU) which processes the messages sent by the antenna.
-
-%We denote by $\rho$ the bijection induced by ${\cal R}$, $\rho(s) = t$ if $s$ is the first vertex of a route $r$ and $t$ the last.
 
@@
 
-      \todo{commencer les routes à 0 ou pas ?}
-
       A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=(m_1, \ldots ,m_n)$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
@@
 
-%       Notice that the notion of $P$-periodic assignment \textbf{is not monotone} with regard to $P$. 
       As an example of a $(2,1)$-periodic assignment, let us consider a routed network 
@@
       we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$.
-In such a graph, there is no $(P,\tau)$-periodic assignment, since the problem reduces to finding a $P$-coloring in a complete graph with $n > P$ vertices, the colors beings the offsets of the routes.\\
+In such a graph, there is no $(P,\tau)$-periodic assignment, since the problem reduces to finding a $P$-coloring in a complete graph with $n > P$ vertices, the colors being the offsets of the routes.\\
       If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic assignment of ${\cal R}$.      
@@
 
-\section{The Star Topology: No Waiting Time} \label{sec:PAZL}
-
-    \subsection{The star topology}
+\section{The Star Routed Network: No Waiting Time} \label{sec:PAZL}
+
+    \subsection{The star routed network}
 
@@
 
-	\subsubsection*{Exhaustive search}
-% 	\begin{algorithm}[H]
-% 	\caption{Exhaustive Generation}  
-% 	\begin{algorithmic}
-% 	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
-% 	\ENSURE $(P,\tau)$-periodic assignment of ${\cal R}_{\cal C}$
-% 	\STATE Forward-budget $\leftarrow$ $P$ - n * $\tau$
-% 	\STATE Backward-budget $\leftarrow$ $P$ - n * $\tau$
-% 	\STATE Free-Intervals $\leftarrow$ list of free intervals in the backward period, init to $[0;P[$
-% 	\FORALL{source $s_i$ in S}
-% 	\FORALL{j in Free-Intervals }
-% 	\IF{Message of the route $r_{s_i}$ does not collides with scheduled routes}
-% 	\STATE $m_{s_i} \leftarrow $ the first slot of Free-Intervals[j]
-% 	\STATE Split the Free-Intervals considering the new packet
-% 	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
-% 	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
-% 	\STATE call Exhaustive Generation on remaining routes
-% 	\ENDIF
-% 	\ENDFOR
-% 	\ENDFOR
-% 
-% 
-%       \end{algorithmic}
-%       \end{algorithm}
-
-% 	    
-      We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found a $(P,\tau)$-periodic assignment.
+\subsection*{An FTP algorithm}
+
+In this section we show how every assignments without waiting time can be put in a special form.
+We use that to provide an algorithm which always finds an assignment if there is some, in fixed parameter 
+tractable time with parameters $n$ the number of routes. This is justified since $n$ is small in practice, 
+at most $20$ and $P$ is large, $20000$ in our context.
+
+We say that an assignment $\mathcal{M}$ is \textbf{compact} if for all forward routes $r$ but one,
+there is another forward route $r'$ such that $r$ and  $r'$ ``have no gap'' or $\rho(r)$ and  $\rho(r)'$ ``have no gap''.
+
+\begin{proposition}
+Let $(G, {\cal R})$ be a star routed network. If there is a $(P,\tau)$-periodic assignment to blah,
+then there is a compact $(P,\tau)$-periodic assignment.
+\end{proposition}
+\begin{proof}
+ On fait tourner les paquets jusqu'a contact on et on repete jusqu'a epuisement. 
+\end{proof}
+
+\begin{theorem}
+     Let $(G, {\cal R})$ be a star routed network with $n$ routes.
+There is an algorithm which finds a $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ if there is one in time $O(2^nq(|G|))$ with $q$ a polynomial.
+\end{theorem}
+
+\begin{proof}
+ Brute force on the compact assignments. 
+\end{proof}
+
+% 
+% 	\subsubsection*{Exhaustive search}
+% % 	\begin{algorithm}[H]
+% % 	\caption{Exhaustive Generation}  
+% % 	\begin{algorithmic}
+% % 	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
+% % 	\ENSURE $(P,\tau)$-periodic assignment of ${\cal R}_{\cal C}$
+% % 	\STATE Forward-budget $\leftarrow$ $P$ - n * $\tau$
+% % 	\STATE Backward-budget $\leftarrow$ $P$ - n * $\tau$
+% % 	\STATE Free-Intervals $\leftarrow$ list of free intervals in the backward period, init to $[0;P[$
+% % 	\FORALL{source $s_i$ in S}
+% % 	\FORALL{j in Free-Intervals }
+% % 	\IF{Message of the route $r_{s_i}$ does not collides with scheduled routes}
+% % 	\STATE $m_{s_i} \leftarrow $ the first slot of Free-Intervals[j]
+% % 	\STATE Split the Free-Intervals considering the new packet
+% % 	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
+% % 	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
+% % 	\STATE call Exhaustive Generation on remaining routes
+% % 	\ENDIF
+% % 	\ENDFOR
+% % 	\ENDFOR
+% % 
+% % 
+% %       \end{algorithmic}
+% %       \end{algorithm}
+% 
+% % 	    
+%       We now present an exhaustive search algorithm, which tries to set the offsets in all possible ways until it has found a $(P,\tau)$-periodic assignment.
 Contrarily to the two previous algorithms, when it fails to find a solution, then it certifies there are no solution to PAZL.
-
-      We have $n$ routes denoted by $\{0,\dots,n-1\}$. A partial solution $S$ is 
-      a partial function from $[n]$ to $\{0,1,\dots,P-\tau -1\}$ which sets a starting time for a subset of the routes $R(S) \subseteq [n]$, such that there are no collisions for these routes.
+%       
+%       We have $n$ routes denoted by $\{0,\dots,n-1\}$. A partial solution $S$ is 
+%       a partial function from $[n]$ to $\{0,1,\dots,P-\tau -1\}$ which sets a starting time for a subset of the routes $R(S) \subseteq [n]$, such that there are no collisions for these routes.
 A partial solution $S'$ extends $S$, if $S'$ is defined over one more route than $S$ and this route has a larger starting offset than all routes of $S$: $R(S') = R(S) \cup \{r'\}$ and for all  $r \in R(S)$, $S(r) + \tau \leq S'(r')$.
@@
 The solutions to our problem will be the leaves of depth $n$ in the tree, and our exhaustive search algorithm is a depth-first search of this tree.
-
-      Remark that a node $S$ with $|R(S)| = k$ can have as many as $(n-k)P$ children.
+%       
+%       Remark that a node $S$ with $|R(S)| = k$ can have as many as $(n-k)P$ children.
 Since the tree is of depth $n$, the tree may have as many as $n!P^n$ elements and while $n$ is small, $P$ may be large which makes its traversal intractable.
@@
 We now propose three cuts, the first two being particularly useful when the network is loaded ($n\tau$ is not far from $P$).
-
-      \begin{enumerate}
-       \item We consider the number of slots which can be used by routes not yet fixed by a partial solution in the \emph{forward period}.
+%       
+%       \begin{enumerate}
+%        \item We consider the number of slots which can be used by routes not yet fixed by a partial solution in the \emph{forward period}.
 When we extend a solution into $S$ with a new route at offset $m$, then at most $(P - m) / \tau $ routes can still be used to extend $S$ without collisions in the forward period.
 If that value is less than the number of routes which are not in $R(S)$, it is a failure and the algorithm backtracks.
-
-       \item 
-       For the next two cuts, we need to define the notion of the useful slots of a partial solution $S$ in the \emph{backward period}: a slot is said to be useful, if it is not used by a message set by $S$ in the backward period and it belongs to an interval of at least $\tau$ such slots.
+%        
+%        \item 
+%        For the next two cuts, we need to define the notion of the useful slots of a partial solution $S$ in the \emph{backward period}: a slot is said to be useful, if it is not used by a message set by $S$ in the backward period and it belongs to an interval of at least $\tau$ such slots.
 Useful slots are positions of the backward period which can be used when extending $S$.
@@
 Notice that the list of intervals of useful slots and the value $\displaystyle{ \sum_{i=0}^{l} (b_{i} -a_i)/\tau } $ can be maintained in constant time, since each time a route is added, we only need to split an interval of useful slots into at most two such intervals.
-
-       \item 
-       Let $S_1$ and $S_2$ be two partial solutions with $R(S_1) = R(S_2)$.
+%        
+%        \item 
+%        Let $S_1$ and $S_2$ be two partial solutions with $R(S_1) = R(S_2)$.
 Let $US_1$ (respectively $US_2$) be the set of useful slots of $S_1$ (resp.
@@
 Hence, in our exhaustive search of the tree of partial solutions, we can skip the tree rooted at $S_2$.
-
-       We now explain how we can detect some partial solutions which are dominated so that we do not explore their subtrees.
-       Consider a partial solution $S$ which we extend into $S'$ by setting the offset of the route $r$ to be the smallest possible.
+%        
+%        We now explain how we can detect some partial solutions which are dominated so that we do not explore their subtrees.
+%        Consider a partial solution $S$ which we extend into $S'$ by setting the offset of the route $r$ to be the smallest possible.
 The offset of $r$ in the backward period is $S'(r)+ \lambda$ and we denote the end of the message before before by $a$.
@@
 Therefore when computing the extension of $S$, we first build $S'$ and then $S''$ with $S''(r) =  a + \tau - \lambda$ , skipping all values in between.
-
-       \end{enumerate}
-
-      The third cut works well in conjunction with the first one since it makes the offsets grow quickly and 
-      which makes the first cut more likely to apply.
+%        
+%        \end{enumerate}
+%       
+%       The third cut works well in conjunction with the first one since it makes the offsets grow quickly and 
+%       which makes the first cut more likely to apply.
 A last cut could be implemented: compute for every route not in $R(S)$ the set of possible positions in the backward period and verify whether at least one is contained in the useful slots of $S$.

### 2017-07-12 article/article.tex

@@
 This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
- %Hence a solution is needed to offer low latency over cheap packet based networks. 
 Here we propose to use a deterministic approach to schedule our periodic messages.
@@
 
-  \paragraph*{Acknowledgments} The authors thanks Christian Cadere and David Auger for the friendly discussions
+  \paragraph*{Acknowledgments} The authors thanks Christian Cad\'er\'e and David Auger for the friendly discussions
   they had on the subject and their insightful remarks.

### 2017-07-13 article/article.tex
algo FPT, mais la def de compact ne va pas

@@
  Finally, it is easy to see that PRA is easy on trees and it may be interesting to study its complexity on 
- bounded treewidth networks, since it is a common property of real networks~\cite{} \todo{Trouver la ref qui dit ca}.
+ bounded treewidth networks, since it is a common property of real networks~\cite{de2011treewidth}.
 
@@
       on the way back. The flow of messages in a star topology is completely described by their repartition in two 
-      time window of size $P$ that we call the {\bf forward period} (at $(c_s,c_t)$), and the {\bf backward period} (at $(c_t,c_s)$).
+      time windows of size $P$ that we call the {\bf forward period} (at $(c_s,c_t)$), and the {\bf backward period} (at $(c_t,c_s)$).
 
@@
 
-\subsection*{An FTP algorithm}
-
-In this section we show how every assignments without waiting time can be put in a special form.
+\subsection*{An FPT algorithm}
+
+In this section we show how every assignment without waiting time can be put in a special form.
 We use that to provide an algorithm which always finds an assignment if there is some, in fixed parameter 
-tractable time with parameters $n$ the number of routes. This is justified since $n$ is small in practice, 
-at most $20$ and $P$ is large, $20000$ in our context.
-
-We say that an assignment $\mathcal{M}$ is \textbf{compact} if for all forward routes $r$ but one,
-there is another forward route $r'$ such that $r$ and  $r'$ ``have no gap'' or $\rho(r)$ and  $\rho(r)'$ ``have no gap''.
+tractable time with parameters $n$ the number of routes. This is justified since $n$ is small in practice and $P$ is large.
+
+Let $(G, {\cal R})$ be a star routed network and $r_1,r_2 \in {\cal R}$ two forward routes (resp. two backward routes) and 
+$\mathcal{M}$ a $(P,\tau)$-periodic assignment.
+We say that there is no gap between $r_1$ and $r_2$ in $\mathcal{M}$ if $\lambda(r_1,c_s) + \tau = \lambda(r_2,c_s)$ (resp.
+$\lambda(r_1,c_t) + \tau = \lambda(r_2,c_t)$).
+It means that the message of $r_2$ goes through the central arc just after the message of $r_1$ withtout wasting time.
+We say that a set of routes ${\cal R}$ is \textbf{compact} for the assignment $\mathcal{M}$ if for all forward routes $r \in {\cal R}$ but one, there is another forward route $r'$ such that there is no gap between $r'$ and $r$ or between $\rho(r')$ and  $\rho(r)$.
+If the set of all routes is compact for an assignment, we say that the assignment is compact.
 
 \begin{proposition}
-Let $(G, {\cal R})$ be a star routed network. If there is a $(P,\tau)$-periodic assignment to blah,
-then there is a compact $(P,\tau)$-periodic assignment.
+Let $(G, {\cal R})$ be a star routed network. If there is a $(P,\tau)$-periodic assignment of $(G, {\cal R})$,
+then there is a compact $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
 \end{proposition}
 \begin{proof}
- On fait tourner les paquets jusqu'a contact on et on repete jusqu'a epuisement. 
+Consider $\mathcal{M}$ a $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
+Let $r_0$ be an arbitrary route of ${\cal R}$,  and let $COMPACT = \{r_0\}$. Now we apply the following algorithm to $\mathcal{M}$ and $COMPACT$ while $COMPACT$ is not equal to ${\cal R}$.
+While there is no collision, remove $1$ (modulo $P$) from all offsets of routes in ${\cal R} \setminus COMPACT$.
+Then choose a route $r$ in ${\cal R} \setminus COMPACT$ which would have a collision with a route $r'$ of $COMPACT$ if one is subtracted from its offset.
+It implies that there is no gap between $r'$ and $r$.
+If $r'$ is a forward route, let $COMPACT = COMPACT \cup \{r, \rho(r)\}$ otherwise  $COMPACT = COMPACT \cup \{r, \rho^{-1}(r)\}$.
+It is clear that the set $COMPACT$ is compact for $\mathcal{M}$ at every step of the algorithm since at the beginning $|COMPACT| = 1$ and at each step we add two routes with the desired property.
+Finally, there was no collisions between routes at the beginning and since we modify $\mathcal{M}$ only if it creates no collision,
+the assignment we obtain at then end has no collisions between routes.
 \end{proof}
 
+We now present an algorithm to find a $(P,\tau)$-periodic assignment 
+by trying all compact assignments.
+
 \begin{theorem}
-     Let $(G, {\cal R})$ be a star routed network with $n$ routes.
+PALL is in $\FPT$ when parametrized by the number of routes.
+%      Let $(G, {\cal R})$ be a star routed network with $n$ routes.
 There is an algorithm which finds a $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ if there is one in time $O(2^nq(|G|))$ with $q$ a polynomial.
@@
 \begin{proof}
- Brute force on the compact assignments. 
+Let $(G, {\cal R})$ be a star routed network and let $\mathcal{M}$ be a $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
+There is at most one route, say $r$, which does not satifies the property to have
+
+Let
+
+Consider an assignment and a route $r$ with offset $m$, by removing $m$ to all ofsets,
+we can always assume that its offset is zero. Therefore we need to consider all compact assignments 
+with an offset $0$ for the route $r$. Then in a compact assignment there
+
+There is at most $n!$
+We build
+Fix arbitrarily a route $r \in \mathcal{R}$ and assume its offset is zero.
+
 \end{proof}
 
+Cuts in the search tree to make the algorithm more practical. 
 % 

### 2017-07-13 article/article.tex
article

--- 2017-07-12 article/article.tex
@@
 We prove that problems arising from this context are $\NP$-complete even for very restricted graphs.
-We then deal with the case of a star graph and for different regimes of the parameters we propose algorithms that are experimentally shown to work extremely well compared to traditional statistical multiplexing.
+We then deal with the case of a star graph and for different regimes of parameters we propose algorithms that are experimentally shown to work extremely well compared to traditional statistical multiplexing.
 \end{abstract}
@@
 \todo{citation [7] pour les reseaux points a points ?}
- In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network. 
+ In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network. \todo{The fronthaul network is the network located between the BUUs and the RRHs.
  Statistical multiplexing even with a large bandwidth does not comply with the latency requirements.
@@
 
-      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=(m_1, \ldots ,m_n)$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{n-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
 The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
@@
          \hline 
-         ${\cal M}=(m_1, \ldots ,m_n)$& Assignment: an offset for each route)\\
+         ${\cal M}=(m_0, \ldots ,m_{n-1})$& Assignment: an offset for each route)\\
               \hline 
@@
 
-  When the waiting times are zero, $MT({\cal M})$ is equal to twice the weight of the longest route, thus $T_{max}$ is not relevant anymore.
-For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ $m_{\rho(r)} + \lambda(r) \mod P$.
+  When the waiting times are zero, $MT({\cal M})$ is equal to twice the lenght of the longest route, thus $T_{max}$ is not relevant anymore.
+For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ to $m_{r} + \lambda(r) \mod P$.
   Consider an assignment $\{m_0,\dots,m_{n-1}\}$ of a star topology and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
@@
 
-      \begin{proposition} Let $(G, {\cal R})$ be a symmetric routed network, and let $n\tau + 2(\lambda(r_{n}) - \lambda(r_{0})) \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which is given by Shortest-Longest in time $O(n\log(n))$.\label{prop:SL}
+      \begin{proposition} Let $(G, {\cal R})$ be a symmetric routed network, and let $n\tau + 2(\lambda(r_{n-1}) - \lambda(r_{0})) \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which is given by Shortest-Longest in time $O(n\log(n))$.\label{prop:SL}
       \end{proposition}
@@
 We set the waiting time for the route $i$ to $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$.
-We can compute the time at which the message of the route $r_i$ arrives at the vertex $c_t$ on its way back: $t(r_i,(c_t,c_s)) = w_i + i\tau + 2\lambda(r_{i})$
-        by replacing $w_i$ by its value we obtain $t(r_i,(c_t,c_s)) =  i\tau + 2\lambda(r_{0})$
+We can compute the time at which the message of the route $r_i$ arrives at the vertex $c_t$ on its way back: $t((c_t,c_s),r_i) = w_i + i\tau + 2\lambda(r_{i})$
+        by replacing $w_i$ by its value we obtain $t((c_t,c_s),r_i) =  i\tau + 2\lambda(r_{0})$
         As a conclusion there are no collision on the edge $(c_t,c_s)$ as soon as the 
@@
     The function  min\_non\_assigned(eligible\_time) returns the lowest time in eligible\_time, for which the corresponding route is not assigned yet.
-The function update(free\_intervals) removes an interval of size $\tau$ beginning at t, which correspond to the message,  from free\_intervals.
+The function update(t,free\_intervals) removes an interval of size $\tau$ beginning at t, which correspond to the message,  from free\_intervals.
 
@@
 When MLS finds a solution ${\cal M}$ its always satisfies $MT({\cal M}) < T_{max}$.
-On the other hand, it is a $(P,\tau)$ periodic assignment only if $m_n - m_1 \leq P -\tau$ where $m_n$ is the largest offset and $m_1$ the smallest one.
-The algorithm we use minimize $m_n - m_1 $, so it may work quite well in practice (as shown in Section~\ref{sec:resultsPALL}).
+On the other hand, it is a $(P,\tau)$ periodic assignment only if $m_{n-1} - m_0 \leq P -\tau$ where $m_{n-1}$ is the largest offset and $m_0$ the smallest one.
+The algorithm we use minimize $m_{n-1} - m_0 $, so it may work quite well in practice (as shown in Section~\ref{sec:resultsPALL}).
 
@@
      We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Figure~\ref{fig:sto} since even the third quartile was always at $0$ for a period of $20000$.
-     There is around $20\%$ of the instances for which the margin is larger than $0$ for $P=20000$ and $7\%$
+     There is around $20\%$ of the instances for which the margin is larger than $0$ for $P=20000$ and $2\%$
      for $P = 21000$. For the instances with a margin larger than $0$, the margin is on average $400$.

### 2017-07-13 code/Calculs autres/ecart_type.c

@@ -3,7 +3,7 @@
 #include <math.h>
 
 #define taille 1000
-#define nb_periodes 20
+#define nb_periodes 30
 
 int donnes[nb_periodes][taille];
 float moyennes[nb_periodes];
@@ -41,15 +41,15 @@ void tri_bulles(int* tab,int t)
 
 void lire_fichier()
 {
-	FILE * f = fopen("../datas/donnes_random10000.data","r");
+	FILE * f = fopen("../datas/donnes_random1000.data","r");
 	if(!f){perror("Error opening file");exit(5);}
 	int trash;
 	for(int i=0;i<nb_periodes;i++)
 	{
 		for(int j=0;j<taille;j++)
 		{
-			fscanf(f,"%d %d %d",&trash,&trash,&donnes[i][j]);
-			//fscanf(f,"%d %d %d",&trash,&donnes[i][j],&trash);
+			//fscanf(f,"%d %d %d",&trash,&trash,&donnes[i][j]);
+			fscanf(f,"%d %d %d",&trash,&donnes[i][j],&trash);
 
 		}
 	}
@@ -158,8 +158,10 @@ void quartiles()
 	for(int i = nb_periodes-1;i>=0;i--)
 	{
 		tri_bulles(donnes[i],taille);
-		fprintf(f,"%d %d %d %d 0\n",(int)(20000/(20000+i*1000.0)*100),donnes[i][taille/4+1]/20 ,donnes[i][taille/2+1]/20,donnes[i][3*taille/4+1]/20);
-		fprintf(stdout,"%d %d %d %d 0\n",(int)(20000/(20000+i*1000.0)*100),donnes[i][taille/4+1]/20 ,donnes[i][taille/2+1]/20,donnes[i][3*taille/4+1]/20);
+		fprintf(f,"%d %d %d %d \n",20000+i*1000,donnes[i][taille/4+1],donnes[i][taille/2+1],donnes[i][3*taille/4+1]);
+		fprintf(stdout,"%d %d %d %d \n",20000+i*1000,donnes[i][taille/4+1],donnes[i][taille/2+1],donnes[i][3*taille/4+1]);
+		//fprintf(f,"%d %d %d %d 0\n",(int)(20000/(20000+i*1000.0)*100),donnes[i][taille/4+1]/20 ,donnes[i][taille/2+1]/20,donnes[i][3*taille/4+1]/20);
[…]

### 2017-07-13 code/Sources/main.c

@@ -71,14 +71,14 @@ int main()
 	Tmax moyen pour sto vs sp
 	*******/
 
-	//marge_PALL_stochastique(8,2500,20000,1000,50000);
+	marge_PALL_stochastique(8,2500,20000,1000,50000);
 
 
 
 	/****Nombre de routes pouvant être calculées en moins de "max" ms
 	****/
 
-	 number_max_search(2500,20000, 1000);
+	 //number_max_search(2500,20000, 1000);
 
 
 	/******

### 2017-07-13 code/Sources/simulations.c

@@ -423,7 +423,7 @@ void marge_PALL_stochastique(int nb_routes,int taille_paquets,int taille_route, 
 	int ressto;
 
 	int ressp;
-	int nb_rand = 10000;
+	int nb_rand = 1000;
 
 
 	for(int periode=taille_paquets*nb_routes;periode<periode_max ;periode+=1000)

### 2017-07-13 article/article.tex
typos, figure

@@
 \documentclass[a4paper,10pt]{article}
+%\documentclass[10pt, conference, letterpaper]{IEEEtran}
 \usepackage[utf8]{inputenc}
@@
 \todo{citation [7] pour les reseaux points a points ?}
- In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network. \todo{The fronthaul network is the network located between the BUUs and the RRHs.
+ In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network. \todo{The fronthaul network is the network located between the BUUs and the RRHs.}
  Statistical multiplexing even with a large bandwidth does not comply with the latency requirements.
@@
 Consider an instance of the problem PRA, i.e., a routed network $(G,\cal{R})$ and a period $P$.
-The {\bf conflict depth} of an edge is the number of routes to which the edge belongs. 
-The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its edges.
+The {\bf conflict depth} of an arc is the number of routes to which the edge belongs. 
+The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its arcs.
 The {\bf load} of a routed network is the maximal number of routes sharing the same arc.
@@
 	Often in real networks, the length of the routes are not arbitrary and we may exploit that to solve PALL easily.
-For instance if all the weights on the arcs $(c_t,t_i)$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.
+For instance if all the weights on the arcs $(c_t,t_i)$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.It would correspond to a situation where all the BBUs are in the same datacenter.
 	The assignment in that case is trivial, just send all messages so that they follow each other without gaps in the central arc $(c_s,c_t)$.
@@
 
-	A more realistic assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same. It would correspond to a situation where all the BBUs are in the same datacenter.
+ %A more realistic assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same. It would correspond to a situation where all the BBUs are in the same datacenter.
+	Another assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same.
 
@@
 We set the waiting time for the route $i$ to $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$.
-We can compute the time at which the message of the route $r_i$ arrives at the vertex $c_t$ on its way back: $t((c_t,c_s),r_i) = w_i + i\tau + 2\lambda(r_{i})$
-        by replacing $w_i$ by its value we obtain $t((c_t,c_s),r_i) =  i\tau + 2\lambda(r_{0})$
+We can compute the time at which the message of the route $r_i$ arrives at the vertex $c_t$ on its way back: $t(c_t,\rho_{r_i}) = w_i + i\tau + 2\lambda(r_{i})$
+        by replacing $w_i$ by its value we obtain $t(c_t,\rho_{r_i}) =  i\tau + 2\lambda(r_{0})$
         As a conclusion there are no collision on the edge $(c_t,c_s)$ as soon as the 
@@
 Then we modify the deadline of each forward route to be the minimum of their previous deadline and $t + P$.
-We execute this algorithm for every possible first backward route while no solution is found.
+We execute this algorithm for every possible first backward route and we return the solution that minimize $MT({\cal M})$.
 Since we run the previous algorithm at most $n$ times, the complexity is in $O(n^3\log(n))$.
 Remark that it will always find more solution than MLS,
-     because if MLS find a solution with first route $r$ and such that $m_n - m_1 \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route.
+     because if MLS find a solution with first route $r$ and such that $m_{n-1} - m_0 \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route.
 Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment
@@
        \begin{center}
-     % \includegraphics[scale=0.4]{stochastic.pdf}
-       \input{figures/stochastic}
+      \includegraphics[scale=0.4]{stochastic.pdf}
+       %\input{figures/stochastic}
       \end{center}

### 2017-07-13 code/Calculs autres/ecart_type.c

@@ -41,7 +41,7 @@ void tri_bulles(int* tab,int t)
 
 void lire_fichier()
 {
-	FILE * f = fopen("../datas/donnes_random1000.data","r");
+	FILE * f = fopen("../datas/donnes_random.data","r");
 	if(!f){perror("Error opening file");exit(5);}
 	int trash;
 	for(int i=0;i<nb_periodes;i++)

### 2017-07-13 code/Sources/main.c

@@ -71,14 +71,14 @@ int main()
 	Tmax moyen pour sto vs sp
 	*******/
 
-	marge_PALL_stochastique(8,2500,20000,1000,50000);
+	//marge_PALL_stochastique(8,2500,20000,1000,50000);
 
 
 
 	/****Nombre de routes pouvant être calculées en moins de "max" ms
 	****/
 
-	 //number_max_search(2500,20000, 1000);
+	search_efficiency(2500,20000,100);
 
 
 	/******

### 2017-07-13 code/Sources/simulations.c

@@ -472,28 +472,38 @@ double time_diff(struct timeval tv1, struct timeval tv2)
     return (((double)tv2.tv_sec*(double)1000 +(double)tv2.tv_usec/(double)1000) - ((double)tv1.tv_sec*(double)1000 + (double)tv1.tv_usec/(double)1000));
 }
 
-//Nombre de routes pouvant être calculées en moins de "max" ms
-int number_max_search(int taille_message,int taille_routes, int max)
+
+double time_search(int nb_routes, int taille_message,int taille_routes)
 {
 	
 	Graphe g;
 	struct timeval tv1, tv2;
 	double timer=0.0;
-	int nb_routes =1;
+	
+	g = init_graphe(nb_routes *2 +1);
+	graphe_etoile(g,taille_routes);
+	gettimeofday (&tv1, NULL);
+	search(g,taille_message,taille_routes*nb_routes);
+	gettimeofday (&tv2, NULL);
+	timer = time_diff(tv1,tv2);
+		
+	printf("%f\n",timer);
+		return timer;
 
-	while(timer < max)
+}
+void search_efficiency(int taille_message,int taille_routes, int nb_simuls)
+{
+	double average=0;
+	for(int nb_routes = 50;nb_routes<100;nb_routes+=5)
 	{
-		g = init_graphe(nb_routes *2 +1);
-		graphe_etoile(g,taille_routes);
-		gettimeofday (&tv1, NULL);
-		search(g,taille_message,taille_routes*nb_routes);
-		gettimeofday (&tv2, NULL);
-		timer = time_diff(tv1,tv2);
-		printf("We need %fms to compute %d routes\n",timer,nb_routes);
-		nb_routes++;
-	}
-	return 1;
+		for(int i=0;i<nb_simuls;i++)
+		{
+			average += time_search(nb_routes,2500,20000);
 
+		}
+		printf("%d routes : Average = %f ms \n",nb_routes,average / nb_simuls);
+	}
+	
 }
 
 //Fichiers en 3D pour PALL

### 2017-07-13 code/Sources/simulations.h

@@ -4,5 +4,5 @@ void sucess_aller_PALL(int nb_routes, int taille_paquets,int taille_route,int ma
 void sucess_retour_PALL(int nb_routes, int taille_paquets,int taille_route,int marge_max, int nb_simuls, int periode);
 void succes_PALL_3D(int nb_routes, int taille_paquets,int taille_route, int nb_simuls, int mode);
 void nombre_random_PALL(int nb_routes, int taille_paquets,int taille_route, int nb_simuls, int periode);
-int number_max_search(int taille_message,int taille_routes, int max);
+void search_efficiency(int taille_message,int taille_routes, int nb_simuls);
 void marge_PALL_stochastique(int nb_routes,int taille_paquets,int taille_route, int nb_simuls, int periode_max);

### 2017-07-17 article/article.tex
article offstes gd

@@
 \todo{citation [7] pour les reseaux points a points ?}
- In this article, we study mechanisms to deal with the latency and periodicity constraints in the fronthaul network. \todo{The fronthaul network is the network located between the BUUs and the RRHs.}
+ In this article, we study mechanisms to deal with the latency and periodicity constraints in the network located between the BUUs and the RRHs called fronthaul.
  Statistical multiplexing even with a large bandwidth does not comply with the latency requirements.
@@
 In our problem, we send one message on each route periodically and we denote the period by $P$.
-      Periodicity means that if we look at the messages going through an edge between time $0$ and $P-1$, then we would observe the same messages in the same order and position between time $kP$ and $(k+1)P -1$ for all $k$.
-      Therefore, we will always consider a period of $P$ discrete slots of time at each edge to characterize the working of the network.
+      Periodicity means that if we look at the messages going through an arc between time $0$ and $P-1$, then we would observe the same messages in the same order and position between time $kP$ and $(k+1)P -1$ for all $k$.
+      Therefore, we will always consider a period of $P$ discrete slots of time at each arc to characterize the working of the network.
 We define the first time slot at which a message sent from the first vertex of $r$ will reach a vertex $v$ in $r$ by $t(v,r) = m + \lambda(v,r) \mod P$.
@@
       As an example of a $(2,1)$-periodic assignment, let us consider a routed network 
-      where all pairs of routes intersect at a different edge.
+      where all pairs of routes intersect at a different arc.
 It is easy to design such a network and an example is given in Fig.~\ref{fig:example}.
@@
 Consider an instance of the problem PRA, i.e., a routed network $(G,\cal{R})$ and a period $P$.
-The {\bf conflict depth} of an arc is the number of routes to which the edge belongs. 
-The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its arcs.
+The {\bf conflict depth} of a route is the number of arcs of the route which also belong to other routes.
+The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its routes.
 The {\bf load} of a routed network is the maximal number of routes sharing the same arc.
@@
 
- \begin{proposition}
+ \begin{theorem}
 Problem PRA is $\NP$-complete on the class of routed networks with conflict depth two.
-\end{proposition}
+\end{theorem}
  \begin{proof}
- Problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of edges whether there are collisions.
-
-  Let $H=(V,E)$ be an undirected graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is edge-colorable
+ Problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of arcs whether there are collisions.
+
+  Let $H=(V,E)$ be an undirected graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is arc-colorable
   with $d$ or $d+1$ colors.
-The edge coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness.
+The arc coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness.
 To do that, we define from $H$ a routed network $(G,{\cal R})$ as follows.
   The vertices of $G$ are $v_1, v_2$ for each $v$ in $V$ and $s_{u,v}, t_{u,v}$ for each $(u,v) \in E$.
-  For each edge $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
-
-   To define ${\cal R}$ an arbitrary orientation of each edge $(u,v)$ is chosen. 
+  For each arc $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
+
+   To define ${\cal R}$ an arbitrary orientation of each arc $(u,v)$ is chosen. 
    Then for each arc $(u,v)$ there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
@@
   Observe that the existence of a $d$-coloring of $H$ is equivalent to the existence of a $(d,1)$-periodic assignment
-  of $(G,{\cal R})$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its edges by the integers
+  of $(G,{\cal R})$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its arcs by the integers
   in $\{0,\dots,d-1\}$ and we have a bijection between $d$-colorings of $H$ and offsets of the routes of ${\cal R}$.
-  By construction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent edges have the same color.
-Therefore we have reduced edge coloring to PRA by a polynomial time transformation which concludes the proof.
+  By construction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent arcs have the same color.
+Therefore we have reduced arc coloring to PRA by a polynomial time transformation which concludes the proof.
  \end{proof}
@@
  We define ${\cal R}$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
- Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an edge in $H$; this arc is the only one shared by these two routes.
+ Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an arc in $H$; this arc is the only one shared by these two routes.
 All arcs are of weight $0$.
@@
   When the waiting times are zero, $MT({\cal M})$ is equal to twice the lenght of the longest route, thus $T_{max}$ is not relevant anymore.
-For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ to $m_{r} + \lambda(r) \mod P$.
-  Consider an assignment $\{m_0,\dots,m_{n-1}\}$ of a star topology and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
+For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ to $m_{\rho(r)} = m_{r} + \lambda(r) \mod P$.
+  Consider an assignment $(m_0,\dots,m_{n-1})$ of a star topology and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
   Then $\{m_0',\dots,m_{n-1}'\}$ is an assignment of the same star topology where the weights of the arcs from $s_i$ to $c_s$ are $0$
@@
       First we consider routes which are shorter than $\tau$, that is a message cannot be contained 
-      completely in a single edge which is very common for our application.
+      completely in a single arc which is very common for our application.
 We generate star topologies in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ slots.
@@
 	Often in real networks, the length of the routes are not arbitrary and we may exploit that to solve PALL easily.
-For instance if all the weights on the arcs $(c_t,t_i)$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.It would correspond to a situation where all the BBUs are in the same datacenter.
+For instance if all the weights on the arcs $(c_t,t_i)$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.
+It corresponds to a situation where all the BBUs are in the same datacenter.
 	The assignment in that case is trivial, just send all messages so that they follow each other without gaps in the central arc $(c_s,c_t)$.
@@
         by replacing $w_i$ by its value we obtain $t(c_t,\rho_{r_i}) =  i\tau + 2\lambda(r_{0})$
-        As a conclusion there are no collision on the edge $(c_t,c_s)$ as soon as the 
+        As a conclusion there are no collision on the arc $(c_t,c_s)$ as soon as the 
         period is larger than $n\tau$ (there are no gaps between the messages).
@@
 
-    The first algorithm we propose is a greedy algorithm which sets the offset of the 
+    The first algorithm we propose is a greedy algorithm which sets the offset $m_{\rho(i)}$ of the 
     backward routes. It prioritizes the routes with the earliest deadline to best satisfy the
@@
     Set $t=0$ and repeat the following: find $s \geq t$ the first time for which there is an eligible route with its offset not fixed.
-Then amongst all eligible routes at time $s$ choose the one with the smallest deadline, fix its offset to $s$ and set $t = s + \tau$.
-
-    This algorithm does not take into account the periodicity. Say that $t_0$ is the smallest offset that the algorithm has fixed
-    for a backward route. Then for all routes with an offset smaller than $t_0 + P - \tau$,
+Then amongst all eligible routes at time $s$ choose the one with the smallest deadline, fix its offset to $s - \omega(c_t,t_i) $ and set $t = s + \tau$.
+
+    This algorithm does not take into account the periodicity. Say that $t_0 = t(c_t,r_{\rho_i} = m_{\rho_i} + t(c_t,r(\rho_i)$, where $m_{\rho_i}$ is the smallest offset that the algorithm has fixed
+    for a backward route. Then for all routes with $t(c_t,r_{\rho_i}$ smaller than $t_0 + P - \tau$,
     by construction, there are no collisions on the central arc.
-    However, for routes with larger offsets, since we  should consider everything modulo $P$, 
+    However, for routes with larger $t(c_t,r_{\rho_i}$, since we  should consider everything modulo $P$, 
     they may collide with any other route.
@@
 Remark that it will always find more solution than MLS,
-     because if MLS find a solution with first route $r$ and such that $m_{n-1} - m_0 \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route.
+     because if MLS finds a solution with first route $r$ and such that $m_{n-1} - m_0 \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route.
 Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment

### 2017-07-17 article/article.tex
FPT: fin

--- 2017-07-13 article/article.tex
@@
 Therefore in the next two sections, we study a simple but very common topology, that we call the
-star topology, where all messages can collide on a single arc.
+star routed network, where all messages can collide on a single arc.
 In Sec.\ref{sec:PAZL}, we study a variant of PALL called PAZL  where the waiting times must all be zero.
@@
 
-      From now on, we will only consider graphs with a very simple topology that we call the {\bf star topology}. 
-      First, for each arc $(u,v)$, there is also an arc $(v,u)$ with the same weight.
-      There are two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes:
+      Let us define a family of simple symmetric routed networks. 
+      The graph $G$ has two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes:
       the central source node {\bf $c_s$} and the central target node {\bf $c_t$}.
-There is an arc between {\bf $c_s$} and {\bf $c_t$} shared by all routes.
-For all $i$, there is an arc between $s_i$ and $c_s$ and between $t_i$ and $c_t$.
-      The routes are the directed paths $r_i = s_i,c_s,c_t,t_i$ and $\rho(r_i) = t_i,c_t,c_s,s_i$ which defines a 
-      symmetric routed network.
+      There is an arc between {\bf $c_s$} and {\bf $c_t$} and for all $i$, there is an arc between $s_i$ and $c_s$ and between $t_i$ and $c_t$.
+      All the symmetric arcs are also in the graph with the same weights.
+      The forward routes are the directed paths $r_i = (s_i,c_s,c_t,t_i)$ and $\rho(r_i) = (t_i,c_t,c_s,s_i)$ which defines a symmetric routed network. 
+      The symmetric routed networks $(G, \{r_i,\rho(r_i)\}_{i<n})$ is called a \textbf{star routed network}.
 
@@
 
-      Since the central arc appears in every route, its value do not matter when considering the process time of an assignment.
+      Since the central arc appears in every route, its value does not matter when considering the process time of an assignment.
       Moreover an assignment without collisions is also an assignment without collisions if the weight of the central arc 
@@
 
-      Collisions between messages can only appear in the arc $(c_s,c_t)$ on the way forward and in the arc $(c_t,c_s)$
-      on the way back. The flow of messages in a star topology is completely described by their repartition in two 
-      time windows of size $P$ that we call the {\bf forward period} (at $(c_s,c_t)$), and the {\bf backward period} (at $(c_t,c_s)$).
-
-%       
-%       on the way forward and after node $c_t$ on the way back.
-%       Thus, we only have to check if there is no collisions in a given period at those two vertices.
-%       We try to order the messages such that they can pass thought the common arcs in a time window of $P$ max.
-We define the {\bf forward period}, a time window of size P at the beginning of the arc after $c_s$, and the {\bf backward period} the one at the beginning of the arc after $c_t$.
-A message issued on the route $r$ at time $m_s$ will reach $c_s$ at time $m_{s} + t(c_s,r) \mod P$ in the forward period.
-If the offset of $\rho(s)$ is $m_{\rho(s)}$, the answer will reach $c_t$ at time $m_{\rho(s)} + t(c_t,\rho(r))\mod P$ in the backward period.
-% 
-%       A $(P,\tau)$-periodic assignment is then a choice for all $i < n$, of $m_{r_i}$ and $m_{\rho(r_i)}$ such that, for any couple $(i\neq j)$, we have $[t(c_s,r_{i})] \cap [t(c_s,r_{j})] = \emptyset$ and $[t(c_t,\rho(r_i))] \cap [t(c_t,\rho(r_j))] = \emptyset$.
+      Collisions between messages can only appear in the arc $(c_s,c_t)$ on the way forward and in the arc $(c_t,c_s)$ on the way back.
+The flow of messages in a star routed network is completely described by their repartition in two time windows of size $P$ that we call the {\bf forward period} (at $(c_s,c_t)$), and the {\bf backward period} (at $(c_t,c_s)$).
 
@@
 For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ to $m_{r} + \lambda(r) \mod P$.
-  Consider an assignment $\{m_0,\dots,m_{n-1}\}$ of a star topology and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
-  Then $\{m_0',\dots,m_{n-1}'\}$ is an assignment of the same star topology where the weights of the arcs from $s_i$ to $c_s$ are $0$
+  Consider an assignment $\{m_0,\dots,m_{n-1}\}$ of a star routed network and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
+  Then $\{m_0',\dots,m_{n-1}'\}$ is an assignment of the same star routed network where the weights of the arcs from $s_i$ to $c_s$ are $0$
   for all $i$. Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
@@
 
-In this section we show how every assignment without waiting time can be put in a special form.
-We use that to provide an algorithm which always finds an assignment if there is some, in fixed parameter 
-tractable time with parameters $n$ the number of routes. This is justified since $n$ is small in practice and $P$ is large.
-
-Let $(G, {\cal R})$ be a star routed network and $r_1,r_2 \in {\cal R}$ two forward routes (resp. two backward routes) and 
-$\mathcal{M}$ a $(P,\tau)$-periodic assignment.
-We say that there is no gap between $r_1$ and $r_2$ in $\mathcal{M}$ if $\lambda(r_1,c_s) + \tau = \lambda(r_2,c_s)$ (resp.
+In this section we show how every assignment without waiting time can be put in a canonical form.
+We use that to provide an algorithm which always finds an assignment if there is some, in fixed parameter tractable (FPT) time with parameter $n$ the number of routes (for more on parametrized complexity see~\cite{downey2012parameterized}).
+This is justified since $n$ is small in practice and the period $P$ is large.
+
+Let $(G, {\cal R})$ be a star routed network and $\mathcal{M}$ a $(P,\tau)$-periodic assignment.
+A set of routes $S$ is \textbf{coherent} if for all $r \in {\cal R}$, $r \in S$ if and only if $\rho(r) \in S$.
+We say that a coherent set $S \subseteq {\cal R}$ is \textbf{compact} for the assignment $\mathcal{M}$ if there is a route $r_0 \in S$ such that the following holds:
+for all coherent subsets $S'\subset S$ with $r_0 \notin S'$, if we remove $1$ from all offsets of routes in $S'$ then there is a collision with a route of $S \setminus S'$.
+We say that $\mathcal{M}$ is compact if ${\cal R}$ is compact for $\mathcal{M}$.
+% 
+% 
+% $r_1,r_2 \in {\cal R}$ two forward routes (resp. two backward routes) and 
+%  We say that there is no gap between $r_1$ and $r_2$ in $\mathcal{M}$ if $\lambda(r_1,c_s) + \tau = \lambda(r_2,c_s)$ (resp.
 $\lambda(r_1,c_t) + \tau = \lambda(r_2,c_t)$).
@@
 \begin{proposition}
-Let $(G, {\cal R})$ be a star routed network. If there is a $(P,\tau)$-periodic assignment of $(G, {\cal R})$,
-then there is a compact $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
+Let $(G, {\cal R})$ be a star routed network. If there is a $(P,\tau)$-periodic assignment of $(G, {\cal R})$, then there is a compact $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
 \end{proposition}
@@
 Then choose a route $r$ in ${\cal R} \setminus COMPACT$ which would have a collision with a route $r'$ of $COMPACT$ if one is subtracted from its offset.
-It implies that there is no gap between $r'$ and $r$.
 If $r'$ is a forward route, let $COMPACT = COMPACT \cup \{r, \rho(r)\}$ otherwise  $COMPACT = COMPACT \cup \{r, \rho^{-1}(r)\}$.
-It is clear that the set $COMPACT$ is compact for $\mathcal{M}$ at every step of the algorithm since at the beginning $|COMPACT| = 1$ and at each step we add two routes with the desired property.
-Finally, there was no collisions between routes at the beginning and since we modify $\mathcal{M}$ only if it creates no collision,
-the assignment we obtain at then end has no collisions between routes.
+
+We prove by induction that $COMPACT$ is compact for $\mathcal{M}$ at every step of the algorithm.
+At the beginning $|COMPACT| = 1$ and the property is trivially satisfied. Then we assume that 
+$COMPACT$ is compact and that we add to it $\{r, \rho(r)\}$ at some step of the algorithm.
+W.l.o.g we assume that it is the offset of $r$ which cannot be decremented without collision.
+Consider $S \subseteq   COMPACT$, if $S$ contains an element different from $r$ and $\rho(r)$ by induction hypothesis we cannot decrement the offsets of $S$ without collision.
+If $S =\{r, \rho(r)\}$
+by construction, we cannot decrement the offset of $r$.
+
+Finally, there was no collisions between routes at the beginning and since we modify $\mathcal{M}$ only if it creates no collision, the assignment we obtain at the end has no collisions between routes.
 \end{proof}
@@
 
-\begin{theorem}
-PALL is in $\FPT$ when parametrized by the number of routes.
-%      Let $(G, {\cal R})$ be a star routed network with $n$ routes.
-There is an algorithm which finds a $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ if there is one in time $O(2^nq(|G|))$ with $q$ a polynomial.
+\begin{theorem}\label{th:FPT}
+$PALL \in \FPT$ when parametrized by the number of routes.
 \end{theorem}
-
 \begin{proof}
 Let $(G, {\cal R})$ be a star routed network and let $\mathcal{M}$ be a $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
-There is at most one route, say $r$, which does not satifies the property to have
-
-Let
-
-Consider an assignment and a route $r$ with offset $m$, by removing $m$ to all ofsets,
-we can always assume that its offset is zero. Therefore we need to consider all compact assignments 
-with an offset $0$ for the route $r$. Then in a compact assignment there
-
-There is at most $n!$
-We build
-Fix arbitrarily a route $r \in \mathcal{R}$ and assume its offset is zero.
-
+First remark that for a given assignment and a route $r_0$ with offset $m$, by removing $m$ to all offsets, we can always assume that its offset is zero.
+Therefore we need only to consider all \emph{compact assignments} with an \emph{offset $0$} for the route $r_0$.
+We now evaluate the number of compact assignments and prove that it only depends
+on $n$ the number of routes which proves the theorem. 
+We give a way to build a compact assignment $\mathcal{M}$ by determining its offsets one after the other. We fix an arbitrary total order on ${\cal R})$.
+First a route $r_0$ is chosen arbitrarily and its offset set to $0$. 
+Then at each step, if the offsets of $S \subseteq  {\cal R}$ have been chosen,
+we select the smallest route $r$ in $S$ for the order. 
+Then we select a route in $r' \in {\cal R} \setminus S$ and set its offset such that 
+if we remove $1$ then $r'$ collides with $r$. Note that if $r$ is a forward route (resp. a backward route) then $r'$ is also a forward route (resp. a backward route). We can also decide to 
+not use route $r$. At a given step of the algorithm, if $|S| = 2i$, we have $n-i$ choices 
+of routes to select and the value of the offset is determined by the values of the offsets of routes in $S$. Therefore there at most $n!$ different compact assignments with offset $r_0$
+fixed to $0$.
+
+An algorithm to solve PALL build every possible compact assignment as described here, and
+test at each step whether there is a collision which can be done in time linear in the size of 
+$(G, {\cal R})$. Therefore $PALL \in \FPT$.
 \end{proof}
 
-Cuts in the search tree to make the algorithm more practical. 
+We call the algorithm described in Theorem~\ref{th:FPT} \textbf{Exhaustive Search of Compact Assignments (ESCA)}. To make it more efficient in practice, we make cuts in the search tree 
+used to explore all compact assignments.
+Consider a set of $k$ forward routes whose offsets has been fixed at some point in the search tree.
+We consider the times at which the messages of these routes cross the central arc.
+It divides the period into $[(a_0,b_0), \dots, (a_{k-1},b_{k-1})]$ such that the central arc is free only during the intervals $(a_i,b_i)$.
+Therefore at most $\displaystyle{ \sum_{i=0}^{k} \lfloor(b_{i} -a_i)/\tau\rfloor} $ forward routes can still use the central arc.
+If this value is more than $n - k$, it is not possible to create a compact assignment by extending the one on $S$ and we backtrack in the search tree.
+We do the same cut for the backward routes.
+
 % 
@@
       Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithm but are not always able to find a solution, depending on $P$, $\tau$, $n$ and the size of the routes.
-On the other hand, the exhaustive search will find an optimal solution if it exists, but works in exponential time.
-We will compare the performance of the algorithms in two different regimes: routes are either short with regard to $\tau$, or unrestricted.
+On the other hand, the exhaustive search finds an optimal solution if it exists, but works in exponential time.
+We compare the performance of the algorithms in two different regimes: routes are either short with regard to $\tau$, or unrestricted.
       From our C-RAN context we choose the following parameters: the number of routes 
@@
 Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.
-      The code in C is available online on the webpage of one of the authors~\cite{webpage}.
-
-      We can define the load of the network as $\frac{n\tau}{P}$ (here a value between one and three) and in experiments we will try to understand how our algorithms work with regards to the load.
-Often rather than changing the load, we will change the period which is equivalent.
+The code in C is available on the webpage of one of the authors~\cite{webpage} under a copyleft license.
+
+      We define the load of the network as $\frac{n\tau}{P}$ (here a value between one and three),
+      it is the proportion of time slots used by messages on the central arc.
+In our experiments we will try to understand how our algorithms work with regards to the load.
+To change the load, we fix the parameters $\tau$ and $n$ and modify the period $P$, which allows for a smoother control of the load and does not change the run time of our algorithms.
 
@@
 
-      First we consider routes which are shorter than $\tau$, that is a message cannot be contained 
-      completely in a single edge which is very common for our application.
-We generate star topologies in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ slots.
-It corresponds to messages of approximately $1$ Mb, links of bandwidth $10$ Gbps and length less than $5$ km between the BBU and the RRH.
-
-      Our aim is to understand how well the algorithms are working under high load. To do that we try to evaluate the 
-      minimal period (that is the highest possible load) for which a $(P,\tau)$ periodic assignment can be found by each algorithm. 
+      First we consider routes which are shorter than $\tau$, that is a message cannot be contained completely in a single arc which is very common for our application.
+We generate star routed networks in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ slots.
+It corresponds to messages of approximately $1$Mb, links of bandwidth $10$Gbps and length less than $5$km between the BBU and the RRH.
+
+      Our aim is to understand how well the algorithms are working under high load.
+To do that we try to evaluate the minimal period (that is the highest possible load) for which a $(P,\tau)$-periodic assignment can be found by each algorithm.
       To that end we use a linear search on $P$, since a dichotomy method would not work because of Lemma~\ref{lemma:monotonic}.
 
-      In our experiment, we generate $1000$ random instances of PAZL for $1$ to $12$ routes. 
+      In our experiment, we generate $1000$ random instances of PAZL for $1$ to $20$ routes. 
       We measure the average minimal period, for each algorithm.
-The experiments are stopped at $12$ routes because the exhaustive search algorithm becomes too slow for larger $n$.
 Remind that the exhaustive search always finds the best possible period for a given instance.
@@
 
-      First, we remark that the period found by the exhaustive search is only very slightly above the lower bound of 
-      $n\tau$, which means that, in this regime, it is very well justified to look for a solution without waiting time even for a highly loaded network.
+      First, we remark that the period found by the exhaustive search is only very slightly above the lower bound of $n\tau$, which means that, in this regime, it is very well justified to look for a solution without waiting time even for a highly loaded network.
 
@@
       We now want to understand the performance of these algorithms when the size of the routes is unbounded.
-When the routes are long, the cuts in the exhaustive search are less efficient and thus even for a small number of routes the algorithm may be impractical.
-To make the experimentations short enough, we have bounded the number of nodes of the tree of partial solutions the exhaustive search can visit by $10^9$.
-
-      In this experiment we will fix the number of routes to $8$ and the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots (in the same range as the period).
-      We measure for each algorithm its percentage of success, for periods from $20000$ which is the minimum possible to $50000$.
-
-      The exhaustive search can fail because there are no solutions or because it does not have enough time to finish its calculation.
-Hence we represent both the success rate of the algorithm, and an upper bound on the success rate of any algorithm solving PAZL by combining the successes and the failures because of lack of time of the exhaustive search.
+In this experiment we fix the number of routes to $8$ and the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots (in the same range as the period).
+We measure for each algorithm its percentage of success, for periods from $20000$ to $50000$ which corresponds to a load of $100\%$ down to $40\%$.
 
@@
 
-      When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithms which justifies its use.
-However for small period, less than $30000$ the computation time is really important and without improvements it would not be possible to tackle larger problems with $10$ to $20$ routes.
-Moreover, examining the upper bound curve for periods less than $22000$, we see that there are very few instances with a solution for PAZL.
-It means that with long routes and high load (larger than $0.9$), looking for an assignment without waiting time is far too restrictive.
+      When the load is larger than $50\%$ (period less than $40000$), the exhaustive search finds  more solutions than the greedy algorithms which justifies its use.
+However, for load larger than $80\%$ (period less than $25000$) there are many instances for which there are no solutions to PAZL.
+      It means that with long routes and high load, looking for an assignment without waiting time is far too restrictive.
 That is why we present algorithms for the general PALL problem in our next section.
-We will test them on $8$ long routes and a period between $20000$ and $30000$ where, as we have shown here, there are often no easy to compute assignment without waiting times.
-
-   \section{The Star Topology: Minimizing Latency}\label{sec:PALL}
-
-    In this section, we still work on the star topology, but we consider again the more general PALL problem.
+We will test them on $8$ long routes and a load between $100\%$ and $80\%$ for which, as shown here, there are often no assignment without waiting times.
+
+      \todo{Scalability, is the exhaustive search practical for more routes: conclusion yes for our settings, no if more routes}
+
+   \section{The Star Routed Network: Minimizing Latency}\label{sec:PALL}
+
+    In this section, we still work on star routed networks, but we consider again the more general PALL problem.
 It means that the messages can wait in the target vertices (BBUs) in order to find solutions when there are none without waiting time.
@@
 
-     We draw $1000$ instances of a star topology with $8$ routes, with weights on the arcs drawn between $0$ and $20000$.
+     We draw $1000$ star routed networks with $8$ routes, with weights on the arcs drawn between $0$ and $20000$.
 Note that the results are almost the same when the arcs are small.
@@
    such as trees, cycles or bounded treewidth graphs. 
-   We would like to design FPT algorithms in the number of routes for PAZL and PALL on the star topology, eventually by relaxing the constraint on the maximal process time into an constraint on the average process time, which seems much more tractable.
-
-   We could also study variation of our problem. Instead of minimizing the maximum process time, we could try to minimize
-   the sum of the waiting time, a linear objective which could make linear programming useful.
+   We would like to design FPT algorithms in the number of routes for PALL on the star routed network, by generalizing the compact assignment idea used for PAZL.
+
+   We could also study variations of our problem.
+Instead of minimizing the maximum process time, we could try to minimize the average process time, a linear objective which could make linear programming useful.
    Moreover we could allow preemption, that is the messages are allowed to be cut into pieces, which would certainly change the complexity of the problem. 

### 2017-07-17 article/article.tex

@@
 
-  When the waiting times are zero, $MT({\cal M})$ is equal to twice the lenght of the longest route, thus $T_{max}$ is not relevant anymore.
-For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ to $m_{r} + \lambda(r) \mod P$.
-  Consider an assignment $\{m_0,\dots,m_{n-1}\}$ of a star routed network and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
-  Then $\{m_0',\dots,m_{n-1}'\}$ is an assignment of the same star routed network where the weights of the arcs from $s_i$ to $c_s$ are $0$
-  for all $i$. Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
+  When the waiting times are zero, $MT({\cal M})$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
+For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ to $m_{\rho(r)} = m_{r} + \lambda(r) \mod P$.
+  Consider an assignment $(m_0,\dots,m_{n-1})$ of a star routed network and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
+  Then $\{m_0',\dots,m_{n-1}'\}$ is an assignment of the same star routed network where the weights of the arcs from $s_i$ to $c_s$ are $0$ for all $i$.
+Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
 

### 2017-07-18 article/article.tex
avant bosser

@@
 
-\todo{citation [7] pour les reseaux points a points ?}
  In this article, we study mechanisms to deal with the latency and periodicity constraints in the network located between the BUUs and the RRHs called fronthaul.
@@
 Choosing a larger period is not relevant since then we know how to solve the problem even without waiting times as shown in Section~\ref{sec:exp_PAZL}.
-We represent the success rate with regards to the margin, for the five kind of orders using the Greedy algorithm for the second stage, computed over $10000$ random star topologies.
+We represent the success rate with regards to the margin, for the five kind of orders using the Greedy algorithm for the second stage, computed over $10000$ random star routed networks.
 Note that for the random order, we compute $1000$ random orders and count it as a success as soon as there is a solution for one order.
@@
 The following experiment is realized on routed networks with $8$ routes, weights of the arcs drawn between $0$ and $20000$ and with a period of $21000$.
-We represent the success rate with regards to the margin, for the three algorithms computed over $10000$ random star topologies.
+We represent the success rate with regards to the margin, for the three algorithms computed over $10000$ random star routed networks.
 

### 2017-07-19 article/article.tex
mkdir infocom

@@
 
-      In our experiment, we generate $1000$ random instances of PAZL for $1$ to $20$ routes. 
+      In our experiment, we generate $1000$ random instances of PAZL for $1$ to $12$ routes. 
       We measure the average minimal period, for each algorithm.
@@
 
-      \todo{Scalability, is the exhaustive search practical for more routes: conclusion yes for our settings, no if more routes}
+      Since the exhaustive search solve PAZL in an FPT time, with parameter $n$ the number of routes, we study the scalability of the time needed by this algorithm, according to $n$.
+We made an experiment on $100$ random star routed networks, in which the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots.
+We fixed the period to $n\tau+1000$, that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
+         \begin{center}
+         \begin{tabular}{|c|c|c|c|c|c|}
+    \hline
+    Number of routes & $1$ & $6$ & $11$& $16$& $21$\\
+    \hline
+    Average time before answer (ms) & $0.004$ &$0.027$&$0.599$&$59.711$&$14866.1$\\
+    \hline
+      \end{tabular}
+      \end{center}
+
+      With our practical parameters ($n<20$ routes), the algorithm can solve PAZL quickly.
+As soon as we want to compute more routes, the time required to answer PAZL with the exhaustive search increase exponentially.
 
@@
 
-      \caption{Success rate of different orders with $P = 21000$}
+      \caption{Success rate of different orders, $95\%$ load.}
       \end{minipage} \hfill
         \begin{minipage}[c]{6cm}
-          \includegraphics[width=6cm]{departs_gp_30000.pdf}
-      \caption{Success rate of different orders with $P = 30000$}
+          \includegraphics[width=6cm]{departs_gp_25000.pdf}
+      \caption{Success rate of different orders, $80\%$ load.}
 

### 2017-07-19 code/Sources/main.c

@@ -17,7 +17,7 @@ int main()
 	/*****
 	Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
 	*****/
-	//simuls_periode_PAZL(7,2500,20000,100);
+	//simuls_periode_PAZL(20,2500,700,100);
 
 	/******************************************/	
 
@@ -43,7 +43,7 @@ int main()
 	/*****
 	Taux de reussite de départ PALL avec un retour GP sur une periode donnée (on fait varier la marge)
 	*****/
-	//sucess_aller_PALL(8,2500,20000,3000,10000,21000);
+	//sucess_aller_PALL(8,2500,20000,3000,10000,25000);
 
 
 
@@ -78,7 +78,7 @@ int main()
 	/****Nombre de routes pouvant être calculées en moins de "max" ms
 	****/
 
-	search_efficiency(2500,20000,100);
+	search_efficiency(2500,30000,100);
 
 
 	/******

### 2017-07-19 code/Sources/simulations.c

@@ -502,7 +502,7 @@ void search_efficiency(int taille_message,int taille_routes, int nb_simuls)
 		max = 0.0;
 		for(int i=0;i<nb_simuls;i++)
 		{
-			result = time_search(nb_routes,2500,20000);
+			result = time_search(nb_routes,2500,taille_routes);
 			average += result;
 			if(result>max)
 				max=result;

### 2017-07-19 infocom/infocom.tex
mkdir infocom

--- 2017-07-19 article/article.tex
@@
-\documentclass[a4paper,10pt]{article}
-%\documentclass[10pt, conference, letterpaper]{IEEEtran}
+%\documentclass[a4paper,10pt]{article}
+\documentclass[10pt, conference, letterpaper]{IEEEtran}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{float}
+\usepackage{tabularx}
 \usepackage{setspace}
@@
 
-\author[1]{Ma\"el Guiraud}
-\author[1]{Dominique Barth}
+%\author[1]{Ma\"el Guiraud}
+%\author[1]{Dominique Barth}
 % \author[1]{Christian Cad\'er\'e}
-\author[2]{Brice Leclerc}
-\author[2]{Olivier Marc\'e}
-\author[1]{Yann Strozecki}
-\affil[1]{David Laboratory, UVSQ}
-\affil[2]{Nokia Bell Labs France}
+%\author[2]{Brice Leclerc}
+%\author[2]{Olivier Marc\'e}
+%\author[1]{Yann Strozecki}
+%\affil[1]{David Laboratory, UVSQ}
+%\affil[2]{Nokia Bell Labs France}
 
@@
 
-\footnote{This work is partially supported by the french ANR project N-GREEN.}
+%\footnote{This work is partially supported by the french ANR project N-GREEN.}
 
@@
       \begin{center}
-          \scalebox{0.8}{
+          \scalebox{0.5}{
 
@@
       \begin{center}
-      \includegraphics[width=\textwidth]{rrh.pdf}
+     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{rrh.pdf}
       \end{center}
@@
        \begin{center}
-      \includegraphics[width=\textwidth]{BBU.pdf}
+     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{BBU.pdf}
       \end{center}
@@
 
-      The following table summarize the main notations used in the paper.
-      \begin{center}
-   \begin{tabular}{|c|c|}
-    \hline
-     $(G,\cal R)$ & Routed network \\
-     \hline
-      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
-      \hline
-      $\lambda(u_i,r)$ & Latency of the vertex $u_i$ in $r$\\
-         \hline
-         $\lambda(r)$ & Length of the route $r$\\
-         \hline
-         $P$ & Period\\
-         \hline
-         $\tau$ & Size of a message\\
-         \hline
-         $ [t(v,r)]$& Set of time slots used by route $r$ at vertex $v$ \\
-         & in a period $P$\\
-         \hline 
-         ${\cal M}=(m_0, \ldots ,m_{n-1})$& Assignment: an offset for each route)\\
-              \hline 
-         $w_r$& Waiting time of the route $r$\\
-            \hline 
-         $PT(r)$& Process time of the route $r$\\
-           \hline 
-         $MT({\cal M})$& Maximum process time of the assignment\\
-    \hline
-
-      \end{tabular}
-      \end{center}
+%      The following table summarize the main notations used in the paper.
+%      \begin{center}
+%   \begin{tabular}{|c|c|}
+%    \hline
+%     $(G,\cal R)$ & Routed network \\
+%     \hline
+%      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
+%      \hline
+%      $\lambda(u_i,r)$ & Latency of the vertex $u_i$ in $r$\\
+%         \hline
+%         $\lambda(r)$ & Length of the route $r$\\
+%         \hline
+%         $P$ & Period\\
+%         \hline
+%         $\tau$ & Size of a message\\
+%         \hline
+%         $ [t(v,r)]$& Set of time slots used by route $r$ at vertex $v$ \\
+%         & in a period $P$\\
+%         \hline 
+%         ${\cal M}=(m_0, \ldots ,m_{n-1})$& Assignment: an offset for each route)\\
+%              \hline 
+%         $w_r$& Waiting time of the route $r$\\
+%            \hline 
+%         $PT(r)$& Process time of the route $r$\\
+%           \hline 
+%         $MT({\cal M})$& Maximum process time of the assignment\\
+%    \hline
+%
+%      \end{tabular}
+%      \end{center}
 
@@
 
-    \scalebox{0.5}{
+    \hspace{0.5cm}\scalebox{0.35}{
     \begin{tikzpicture}
@@
       \begin{center}
-      \includegraphics[width=\textwidth]{ex3nt.png}
+      \includegraphics[width=0.48\textwidth]{ex3nt.png}
       \end{center}
@@
       \begin{center}
-	\includegraphics[scale=0.4]{periode_petite.pdf}
+	\includegraphics[width=0.5\textwidth]{periode_petite.pdf}
       \end{center}
@@
        \begin{center}
-      \includegraphics[scale=0.4]{echec_longues.pdf}
+      \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{echec_longues.pdf}
       \end{center}
@@
       Since the exhaustive search solve PAZL in an FPT time, with parameter $n$ the number of routes, we study the scalability of the time needed by this algorithm, according to $n$.
-We made an experiment on $100$ random star routed networks, in which the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots.
+In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots.
 We fixed the period to $n\tau+1000$, that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
+      The following table shows the average time before the exhaustive search ends, for $1$ to $21$ routes. Theses results are computed on $100$ random star routed networks.
          \begin{center}
-         \begin{tabular}{|c|c|c|c|c|c|}
+         \begin{tabularx}{0.5\textwidth}{|X|X|X|X|X|X|}
     \hline
-    Number of routes & $1$ & $6$ & $11$& $16$& $21$\\
+   $n$ & $1$ & $6$ & $11$& $16$& $21$\\
     \hline
-    Average time before answer (ms) & $0.004$ &$0.027$&$0.599$&$59.711$&$14866.1$\\
+   Time (ms) & $0.004$ &$0.027$&$0.599$&$59.711$&$14866.1$\\
     \hline
-      \end{tabular}
+      \end{tabularx}
       \end{center}
@@
 \begin{figure}[H] 
-    \begin{minipage}[c]{6cm}
+    \begin{minipage}[c]{0.5\textwidth}
   \centering
-      \includegraphics[width=6cm]{departs_gp_21000.pdf}
+      \includegraphics[width=0.5\textwidth]{departs_gp_21000.pdf}
 
@@
       \end{minipage} \hfill
-        \begin{minipage}[c]{6cm}
-          \includegraphics[width=6cm]{departs_gp_25000.pdf}
+        \begin{minipage}[c]{0.5\textwidth}
+          \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
       \caption{Success rate of different orders, $80\%$ load.}

### 2017-07-19 infocom/infocom.tex
11 pages

@@
 
-      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{n-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+    \subsection{The star routed network}
+
+      Let us define a family of simple symmetric routed networks. 
+      The graph $G$ has two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes:
+      the central source node {\bf $c_s$} and the central target node {\bf $c_t$}.
+      There is an arc between {\bf $c_s$} and {\bf $c_t$} and for all $i$, there is an arc between $s_i$ and $c_s$ and between $t_i$ and $c_t$.
+      All the symmetric arcs are also in the graph with the same weights.
+      The forward routes are the directed paths $r_i = (s_i,c_s,c_t,t_i)$ and $\rho(r_i) = (t_i,c_t,c_s,s_i)$ which defines a symmetric routed network. 
+      The symmetric routed networks $(G, \{r_i,\rho(r_i)\}_{i<n})$ is called a \textbf{star routed network}.
+
+       \begin{center}
+	 \scalebox{0.8}{
+\begin{tikzpicture}
+
+\tikzset{EdgeStyle/.style={<->,font=\scriptsize,above,sloped,midway}}
+  \SetGraphUnit{5}
+
+  \node[draw,circle] (s3) at (0, 0) {$s_2$}; 
+  \node[draw,circle] (s2) at (0, 2) {$s_1$}; 
+  \node[draw,circle] (s1) at (0, 4) {$s_0$};
+
+  \node[draw,circle] (t3) at (8, 0) {$t_2$}; 
+  \node[draw,circle] (t2) at (8, 2) {$t_1$}; 
+  \node[draw,circle] (t1) at (8, 4) {$t_0$};
+
+  \node[draw,circle] (cs) at (3, 2) {$c_s$}; 
+  \node[draw,circle] (ct) at (5, 2) {$c_t$};
+
+  \Edge[label = $\omega(s_1\,c_s)$](s1)(cs)
+  \Edge[label = $\omega(...)$](s2)(cs)
+  \Edge[label = $\omega(...)$](s3)(cs)
+
+  \Edge[label = $\omega(...)$](ct)(t1)
+  \Edge[label = $\omega(...)$](ct)(t2)
+  \Edge[label = $\omega(...)$](ct)(t3)
+
+  \Edge(cs)(ct)
+
+\end{tikzpicture}
+}
+
+  \end{center}
+
+      Since the central arc appears in every route, its value does not matter when considering the process time of an assignment.
+      Moreover an assignment without collisions is also an assignment without collisions if the weight of the central arc 
+      is set to $0$, therefore we assume from now on it is indeed $0$.
+
+      Collisions between messages can only appear in the arc $(c_s,c_t)$ on the way forward and in the arc $(c_t,c_s)$ on the way back.
+The flow of messages in a star routed network is completely described by their repartition in two time windows of size $P$ that we call the {\bf forward period} (at $(c_s,c_t)$), and the {\bf backward period} (at $(c_t,c_s)$).
+
+%      
+%
+%      
+%      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{n-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
 The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
@@
 Moreover, \emph{no pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
-
-      As an example of a $(2,1)$-periodic assignment, let us consider a routed network 
-      where all pairs of routes intersect at a different arc.
+%
+%      As an example of a $(2,1)$-periodic assignment, let us consider a routed network 
+%      where all pairs of routes intersect at a different arc.
 It is easy to design such a network and an example is given in Fig.~\ref{fig:example}.
@@
 There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.
-
-      \begin{figure}[ht]
-      \begin{center}
-          \scalebox{0.5}{
-
-\begin{tikzpicture}
-
-\tikzset{
-  LabelStyle/.style = { rectangle, rounded corners, draw,
-                       font = \bfseries },
-  EdgeStyle/.append style = {->} }
-  \SetGraphUnit{5}
-  \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
-  \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
-  \node[draw,circle] (s1) at (0, 6) {$s_0$};
-
-  \node[draw,circle] (t3) at (14, 7) {$t_2$}; 
-  \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
-  \node[draw,circle] (t1) at (10, 2) {$t_0$};
-
-  \SetVertexNoLabel
-  \Vertex[x=2,y=5]{A}
-  \Vertex[x=4,y=5]{B}
-  \Vertex[x=10,y=5]{C}
-  \Vertex[x=12,y=5]{D}
-  \Vertex[x=6,y=3]{E}
-  \Vertex[x=8,y=3]{F}
-  \tikzset{
-  EdgeStyle/.append style = {green} }
-  \Edge[label = 2](s2)(A)
-  \Edge[label = 1](A)(B)
-  \Edge[label = 2](B)(C)
-  \Edge[label = 1](C)(D)
-  \Edge[label = 1](D)(t2)
-
-   \tikzset{
-  EdgeStyle/.append style = {red} }
-  \Edge[label = 2](s3)(E)
-  \Edge[label = 1](E)(F)
-  \Edge[label = 1](F)(C)
-  \Edge[label = 1](C)(D)
-  \Edge[label = 1](D)(t3) 
-     \tikzset{
-  EdgeStyle/.append style = {blue} }
-  \Edge[label = 1](s1)(A)
-  \Edge[label = 1](A)(B)
-  \Edge[label = 1](B)(E)
-  \Edge[label = 1](E)(F)
-  \Edge[label = 1](F)(t1)
-
-\end{tikzpicture}
-
-}
-     \end{center}
-       \caption{A routed network with $(0,0,0)$ as a $(2,1)$-periodic assignment}
-       \label{fig:example}
-      \end{figure}
-
-      \subsection{Periodic route assignment}\label{nonmonotone}
-
-    We want to find an assignment which allows to send periodic messages from sources to targets
-    without collisions. We introduce the following associated decision problem, useful for hardness proofs.
-
-      \noindent {\bf  Periodic Routes Assignment (PRA)}
-
-      \noindent {\bf Input:} a routed network $(G,\cal R)$, an integer $\tau$ and an integer $P$.
-
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment of $(G,\cal R)$ ?
-
-      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
-      In fact, approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic assignment is already hard.
-
-      An unusual property of assignment is that given a routed network, we may have a $(P,\tau)$-periodic assignment but no
-      $(P',\tau)$-periodic assignment with $P' > P$: the existence of an assignment is not monotone with regard to $P$.
-
-	\begin{lemma} \label{lemma:monotonic}
-	 For any odd $P$, there is a routed network such that there is $(2,1)$-periodic assignment but no $(P,1)$-periodic assignment.
-	\end{lemma}
-\begin{proof}
-
-      Consider the routed network $(G,{\cal R})$ given in the previous subsection. 
-      We change the weights so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
-      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$.
+%
+%  
+%      \begin{figure}[ht]
+%      \begin{center}
+%          \scalebox{0.5}{
+%          
+%\begin{tikzpicture}
+%
+%
+%\tikzset{
+%  LabelStyle/.style = { rectangle, rounded corners, draw,
+%                       font = \bfseries },
+%  EdgeStyle/.append style = {->} }
+%  \SetGraphUnit{5}
+%  \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
+%  \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
+%  \node[draw,circle] (s1) at (0, 6) {$s_0$}; 
+%
+%  \node[draw,circle] (t3) at (14, 7) {$t_2$}; 
+%  \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
+%  \node[draw,circle] (t1) at (10, 2) {$t_0$}; 
+%
+%  
+%  \SetVertexNoLabel
+%  \Vertex[x=2,y=5]{A}
+%  \Vertex[x=4,y=5]{B}
+%  \Vertex[x=10,y=5]{C}
+%  \Vertex[x=12,y=5]{D}
+%  \Vertex[x=6,y=3]{E}
+%  \Vertex[x=8,y=3]{F}
+%  \tikzset{
+%  EdgeStyle/.append style = {green} }
+%  \Edge[label = 2](s2)(A)
+%  \Edge[label = 1](A)(B)
+%  \Edge[label = 2](B)(C)
+%  \Edge[label = 1](C)(D)
+%  \Edge[label = 1](D)(t2)
+%
+%  
+%   \tikzset{
+%  EdgeStyle/.append style = {red} }
+%  \Edge[label = 2](s3)(E)
+%  \Edge[label = 1](E)(F)
+%  \Edge[label = 1](F)(C)
+%  \Edge[label = 1](C)(D)
+%  \Edge[label = 1](D)(t3) 
+%     \tikzset{
+%  EdgeStyle/.append style = {blue} }
+%  \Edge[label = 1](s1)(A)
+%  \Edge[label = 1](A)(B)
+%  \Edge[label = 1](B)(E)
+%  \Edge[label = 1](E)(F)
+%  \Edge[label = 1](F)(t1)
+%
+%\end{tikzpicture}
+%
+%}
+%     \end{center}
+%       \caption{A routed network with $(0,0,0)$ as a $(2,1)$-periodic assignment}
+%       \label{fig:example}
+%      \end{figure}
+%
+%      \subsection{Periodic route assignment}\label{nonmonotone}
+%
+%    We want to find an assignment which allows to send periodic messages from sources to targets
+%    without collisions. We introduce the following associated decision problem, useful for hardness proofs.
+%    
+%
+%      \noindent {\bf  Periodic Routes Assignment (PRA)} 
+%
+%      \noindent {\bf Input:} a routed network $(G,\cal R)$, an integer $\tau$ and an integer $P$.
+%
+%      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment of $(G,\cal R)$ ?
+%
+%
+%      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
+%      In fact, approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic assignment is already hard.
+%        
+%   An unusual property of assignment is that given a routed network, we may have a $(P,\tau)$-periodic assignment but no
+%	\begin{lemma} \label{lemma:monotonic}
+%	 For any odd $P$, there is a routed network such that there is $(2,1)$-periodic assignment but no $(P,1)$-periodic assignment.
+%	\end{lemma}
+%\begin{proof}
+%
+%      Consider the routed network $(G,{\cal R})$ given in the previous subsection. 
+%      We change the weights so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
+%      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$.
 In such a graph, there is no $(P,\tau)$-periodic assignment, since the problem reduces to finding a $P$-coloring in a complete graph with $n > P$ vertices, the colors being the offsets of the routes.\\
-      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic assignment of ${\cal R}$.      
-\end{proof}
+%      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic assignment of ${\cal R}$.      
+%\end{proof}
 
@@
 
-         We now give a new interpretation of a $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routed network, so that it represents the sending of a message and of its answer.
+         A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a set of two sequence  ${\cal M}=\{(m_0, \ldots ,m_{n-1}),(m_{\rho_0}, \ldots ,m_{\rho_{n-1}})\}$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+The number $m_{i}$ (respectively $m_{\rho_i}$) represents the time at which a message is emitted at the first vertex of the route $r_{i}$ (respectively $r_{\rho_i}$).A $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routed network represents
+ the sending of a message and of its answer. \emph{No pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
    This assignment represents the following process: first a message is sent at $u$, through the route $r \in F$, at time $m_r$.
+
+      \todo{mettre le lemme sur la monotonie sans preuve?}
 
@@
 
-      As a consequence of the $\NP$-hardness of PRA, we show in the next subsection that this problem is $\NP$-hard. 
+     We show in the long version of this article that this problem is $\NP$-hard. 
       In Sec.~\ref{sec:PALL} we will study heuristics which try to solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity.
+
+One can consider a simpler version of PALL.
+       We ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$} and we call this restricted problem {\bf Periodic Assignment for Zero Latency} or PAZL.
+We consider PAZL since it is simpler to get theoretical results and good algorithms
+  than for PALL.
+Moreover, as we show in our experimentations of Sec.\ref{sec:exp_PAZL}, this problem can often be solved positively (albeit less often than the general problem).
+Finally, a solution to PAZL is simpler to implement in real telecommunication networks, since we do not need to implement any buffering at all.
+
+    One may consider a variant of PAZL where the central link is unidirectional, that is collisions can happen between messages going from $c_s$ to $c_t$ and messages  going from $c_t$ to $c_s$.
+This problem can be shown to be $\NP$-complete by a reduction from the subset sum problem as it is done for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
+We conjecture that the problem PAZL is also $\NP$-complete,  but we have yet not been able to prove it.
+  On the other hand we show positive results:  when the period is large or when the routes are short there is always a solution to PAZL and it can be found in polynomial time.
+We then give an exponential time exhaustive search algorithm which always finds a solution if there is one.
 
@@
 
-\section{Hardness of PRA}
-  \label{sec:complexity}
-
- In this section we always assume that the size of a message $\tau$ is equal to one. 
- We will prove the hardness of PRA and PALL for $\tau =1$ which implies the hardness of the general problems. 
-Consider an instance of the problem PRA, i.e., a routed network $(G,\cal{R})$ and a period $P$.
-The {\bf conflict depth} of a route is the number of arcs of the route which also belong to other routes.
-The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its routes.
-The {\bf load} of a routed network is the maximal number of routes sharing the same arc.
-Remark that a $(P,1)$-periodic assignment must satisfy that $P$ is larger or equal to the load.
-
-We give two alternate proofs that PRA is $\NP$-complete.
-The first proof works already for conflict depth two. Remark that for conflict depth one,
-the graph can be seen as a set of disjoint pair of routes, on which PRA and PALL can be solved in linear time. 
- The second proof reduces the problem to graph coloring and implies inapproximability when one tries to find the smallest possible $P$. \\
- Finally, it is easy to see that PRA is easy on trees and it may be interesting to study its complexity on 
- bounded treewidth networks, since it is a common property of real networks~\cite{de2011treewidth}.
-
- \begin{theorem}
-Problem PRA is $\NP$-complete on the class of routed networks with conflict depth two.
-\end{theorem}
- \begin{proof}
- Problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of arcs whether there are collisions.
-
-  Let $H=(V,E)$ be an undirected graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is arc-colorable
-  with $d$ or $d+1$ colors.
+%
+%\section{Hardness of PRA}
+%  \label{sec:complexity}
+%
+% In this section we always assume that the size of a message $\tau$ is equal to one. 
+% We will prove the hardness of PRA and PALL for $\tau =1$ which implies the hardness of the general problems. 
+%Consider an instance of the problem PRA, i.e., a routed network $(G,\cal{R})$ and a period $P$.
+%The {\bf conflict depth} of a route is the number of arcs of the route which also belong to other routes.
+%The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its routes.
+%The {\bf load} of a routed network is the maximal number of routes sharing the same arc.
+%Remark that a $(P,1)$-periodic assignment must satisfy that $P$ is larger or equal to the load.
+%
+%
+%We give two alternate proofs that PRA is $\NP$-complete.
+%The first proof works already for conflict depth two. Remark that for conflict depth one,
+%the graph can be seen as a set of disjoint pair of routes, on which PRA and PALL can be solved in linear time. 
+% The second proof reduces the problem to graph coloring and implies inapproximability when one tries to find the smallest possible $P$. \\
+% Finally, it is easy to see that PRA is easy on trees and it may be interesting to study its complexity on 
+% bounded treewidth networks, since it is a common property of real networks~\cite{de2011treewidth}.
+% 
+%
+% \begin{theorem}
+%Problem PRA is $\NP$-complete on the class of routed networks with conflict depth two.
+%\end{theorem}
+% \begin{proof}
+% Problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of arcs whether there are collisions.
+% 
+%  Let $H=(V,E)$ be an undirected graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is arc-colorable
+%  with $d$ or $d+1$ colors.
 The arc coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness.
 To do that, we define from $H$ a routed network $(G,{\cal R})$ as follows.
-  The vertices of $G$ are $v_1, v_2$ for each $v$ in $V$ and $s_{u,v}, t_{u,v}$ for each $(u,v) \in E$.
-  For each arc $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
-
-   To define ${\cal R}$ an arbitrary orientation of each arc $(u,v)$ is chosen. 
-   Then for each arc $(u,v)$ there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
-  All these arcs are of weight $0$. The set of arcs of G is the union between all the arcs of the previously defined routes.
-
-  Observe that the existence of a $d$-coloring of $H$ is equivalent to the existence of a $(d,1)$-periodic assignment
-  of $(G,{\cal R})$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its arcs by the integers
-  in $\{0,\dots,d-1\}$ and we have a bijection between $d$-colorings of $H$ and offsets of the routes of ${\cal R}$.
-  By construction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent arcs have the same color.
+%  The vertices of $G$ are $v_1, v_2$ for each $v$ in $V$ and $s_{u,v}, t_{u,v}$ for each $(u,v) \in E$.
+%  For each arc $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$. 
+%  
+%   To define ${\cal R}$ an arbitrary orientation of each arc $(u,v)$ is chosen. 
+%   Then for each arc $(u,v)$ there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
+%  All these arcs are of weight $0$. The set of arcs of G is the union between all the arcs of the previously defined routes.
+%   
+%    
+%  Observe that the existence of a $d$-coloring of $H$ is equivalent to the existence of a $(d,1)$-periodic assignment
+%  of $(G,{\cal R})$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its arcs by the integers
+%  in $\{0,\dots,d-1\}$ and we have a bijection between $d$-colorings of $H$ and offsets of the routes of ${\cal R}$.
+%  By construction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent arcs have the same color.
 Therefore we have reduced arc coloring to PRA by a polynomial time transformation which concludes the proof.
- \end{proof}
-
- Remark that we have used zero weights in the proof. If we ask the weights to be strictly positive, which makes sense in our model since
-they represent the delay of physical links, it is easy to adapt the proof.
+% \end{proof}
+% 
+% Remark that we have used zero weights in the proof. If we ask the weights to be strictly positive, which makes sense in our model since
+%they represent the delay of physical links, it is easy to adapt the proof.
 We just have to set them so that in any route the weight at $u_1$ is equal to $d$ and thus equal to $0$ modulo $d$.
 We now lift this hardness result to the problem PALL.
-
-\begin{corollary}
-Problem PALL is $\NP$-complete on the class of routed networks of conflict depth two.
-\end{corollary}
-\begin{proof}
- We consider $((G,{\cal R}),P,\tau)$ an instance of $PRA$.
+%
+%\begin{corollary}
+%Problem PALL is $\NP$-complete on the class of routed networks of conflict depth two.
+%\end{corollary}
+%\begin{proof}
+% We consider $((G,{\cal R}),P,\tau)$ an instance of $PRA$.
 We assume that no vertex is the first of some route and the last of another one.
 Remark that this condition is satisfied in the previous proof, which makes the problem $PRA$ restricted to this kind of instance $\NP$-complete.
- Let us define $T_{max} = 2 \times \max_{r \in {\cal R}} \lambda(r) + P$.
+% Let us define $T_{max} = 2 \times \max_{r \in {\cal R}} \lambda(r) + P$.
 We define $(G',{\cal R}')$ a symmetric routed network from $(G,{\cal R})$ where for every route we add a symmetric route with new arcs of opposite orientation and the same weights.
- We prove that the instance $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL if and only if $((G,{\cal R}),P,\tau)$ is in $PRA$.
- If $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL, then a $(P,\tau)$-assignment of $(G',{\cal R'})$ restricted to $\R$ is a $(P,\tau)$-assignment of $((G,{\cal R})$ since they cannot be any collision between routes of ${\cal R}$.
-
- Assume now that $((G,{\cal R}),P,\tau)$ is in $PRA$.
+% We prove that the instance $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL if and only if $((G,{\cal R}),P,\tau)$ is in $PRA$.
+% If $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL, then a $(P,\tau)$-assignment of $(G',{\cal R'})$ restricted to $\R$ is a $(P,\tau)$-assignment of $((G,{\cal R})$ since they cannot be any collision between routes of ${\cal R}$.
+% 
+% Assume now that $((G,{\cal R}),P,\tau)$ is in $PRA$.
 First remark that the waiting time of each route is by definition less than $P$ and thus the maximal process time is always less than $T_{max}$, therefore the constraint on $T_{max}$ is satisfied.
@@
 The symmetry ensures that each new route $\rho(r)$ in ${\cal R'}$ uses exactly the same times slot as $r$ one each of its node and thus avoid collisions.
-\end{proof}
-
-Let MIN-PRA be the problem, given a routed network and an assignment, to find the minimal period $P$ such that there is a $P$-periodic assignment.
-
-\begin{theorem}\label{th:inapprox}
-If $\P \neq \NP$, problem MIN-PRA on the classes of routed networks of load two cannot be approximated in polynomial time within a factor $n^{1-o(1)}$ where $n$ is the number of routes.
-\end{theorem}
-
-\begin{proof}
- We reduce graph coloring to PRA. Let $H$ be a graph instance of the $k$-coloring problem. 
- We define ${\cal R}$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
- Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an arc in $H$; this arc is the only one shared by these two routes.
+%\end{proof}
+%
+%Let MIN-PRA be the problem, given a routed network and an assignment, to find the minimal period $P$ such that there is a $P$-periodic assignment. 
+%
+%\begin{theorem}\label{th:inapprox}
+%If $\P \neq \NP$, problem MIN-PRA on the classes of routed networks of load two cannot be approximated in polynomial time within a factor $n^{1-o(1)}$ where $n$ is the number of routes.
+%\end{theorem}
+%
+%\begin{proof}
+% We reduce graph coloring to PRA. Let $H$ be a graph instance of the $k$-coloring problem. 
+% We define ${\cal R}$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
+% Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an arc in $H$; this arc is the only one shared by these two routes.
 All arcs are of weight $0$.
 Note that it is easy to build a graph with such routes as in Fig.~\ref{fig:reduction}.
-
- Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic assignment in $G$, 
- by converting an offset of a route into a color of a vertex and reciprocally.
+% 
+% Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic assignment in $G$, 
+% by converting an offset of a route into a color of a vertex and reciprocally.
 Therefore if we can approximate the minimum value of $P$ within some factor, we could approximate the minimal number of colors needed to color a graph within the same factor.
 The proof follows from the hardness of approximability of finding a minimal coloring~\cite{zuckerman2006linear}.
-\end{proof}
-
-In particular, this reduction shows that even with small maximal load, the minimal period can be large.
-
-    \begin{figure}[ht]
-
-    \hspace{0.5cm}\scalebox{0.35}{
-    \begin{tikzpicture}
-    \tikzset{
-      LabelStyle/.style = { rectangle, rounded corners, draw,
-			  font = \bfseries },
-      EdgeStyle/.append style = {->} }
-      \SetGraphUnit{5}
-
-      \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
-      \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
-      \node[draw,circle] (s1) at (0, 6) {$s_0$};
-
-      \node[draw,circle] (t3) at (12, 3) {$t_2$}; 
-      \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
-      \node[draw,circle] (t1) at (10, 2) {$t_0$};
-
-      \tikzstyle{VertexStyle}=[shape = circle, draw, minimum size = 20pt]
-	\tikzset{
-      VertexStyle/.append style = {blue} }
-	\Vertex[x=-8,y=3]{1}
-	      \tikzset{
-      VertexStyle/.append style = {green} }
-	  \Vertex[x=-7,y=5]{2}
-
-	    \tikzset{
-      VertexStyle/.append style = {red} }
-	  \Vertex[x=-6,y=4]{3}
-		\tikzset{
-      VertexStyle/.append style = {black} }
-
-      \SetVertexNoLabel
-      \Vertex[x=2,y=5]{A}
-      \Vertex[x=4,y=5]{B}
-      \Vertex[x=10,y=5]{C}
-      \Vertex[x=12,y=5]{D}
-      \Vertex[x=6,y=3]{E}
-      \Vertex[x=8,y=3]{F}
-      \tikzset{
-      EdgeStyle/.append style = {green} }
-      \Edge(s2)(A)
-      \Edge(A)(B)
-      \Edge(B)(C)
-      \Edge(C)(D)
-      \Edge(D)(t2)
-
-      \tikzset{
-      EdgeStyle/.append style = {red} }
-      \Edge(s3)(E)
-      \Edge(E)(F)
-      \Edge(F)(t3) 
-	\tikzset{
-      EdgeStyle/.append style = {blue} }
-      \Edge(s1)(A)
-      \Edge(A)(B)
-      \Edge(B)(E)
-      \Edge(E)(F)
-      \Edge(F)(t1)
-
-	\tikzset{
-      EdgeStyle/.append style = {black,-} }
-
-      \Edge(1)(2)
-      \Edge(1)(3)
-    \node (1) at (-3,4){\Huge $\rightarrow$};
-%     
-%     \node (2) at (-7,0){\Huge H};
-%     \node (3) at (10,0){\Huge G};
-    \end{tikzpicture}
-    }
-    \caption{Reduction from k-coloring to MIN-PRA}
-    \label{fig:reduction}
-    \end{figure}
+%\end{proof}
+%
+%
+%In particular, this reduction shows that even with small maximal load, the minimal period can be large.
+%
+%    \begin{figure}[ht]
+%    
+%    \hspace{0.5cm}\scalebox{0.35}{
+%    \begin{tikzpicture}
+%    \tikzset{
+%      LabelStyle/.style = { rectangle, rounded corners, draw,
+%			  font = \bfseries },
+%      EdgeStyle/.append style = {->} }
+%      \SetGraphUnit{5}
+%      
+%      
+%      \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
+%      \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
+%      \node[draw,circle] (s1) at (0, 6) {$s_0$}; 
+%
+%      \node[draw,circle] (t3) at (12, 3) {$t_2$}; 
+%      \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
+%      \node[draw,circle] (t1) at (10, 2) {$t_0$}; 
+%      
+%
+%      \tikzstyle{VertexStyle}=[shape = circle, draw, minimum size = 20pt]
+%	\tikzset{
+%      VertexStyle/.append style = {blue} }
+%	\Vertex[x=-8,y=3]{1}
+%	      \tikzset{
+%      VertexStyle/.append style = {green} }
+%	  \Vertex[x=-7,y=5]{2}
+%
+%	    \tikzset{
+%      VertexStyle/.append style = {red} }
+%	  \Vertex[x=-6,y=4]{3}
+%		\tikzset{
+%      VertexStyle/.append style = {black} }
+%      
+%      
+%      \SetVertexNoLabel
+%      \Vertex[x=2,y=5]{A}
+%      \Vertex[x=4,y=5]{B}
+%      \Vertex[x=10,y=5]{C}
+%      \Vertex[x=12,y=5]{D}
+%      \Vertex[x=6,y=3]{E}
+%      \Vertex[x=8,y=3]{F}
+%      \tikzset{
+%      EdgeStyle/.append style = {green} }
+%      \Edge(s2)(A)
+%      \Edge(A)(B)
+%      \Edge(B)(C)
+%      \Edge(C)(D)
+%      \Edge(D)(t2)
+%
+%      
+%      \tikzset{
+%      EdgeStyle/.append style = {red} }
+%      \Edge(s3)(E)
+%      \Edge(E)(F)
+%      \Edge(F)(t3) 
+%	\tikzset{
+%      EdgeStyle/.append style = {blue} }
+%      \Edge(s1)(A)
+%      \Edge(A)(B)
+%      \Edge(B)(E)
+%      \Edge(E)(F)
+%      \Edge(F)(t1)
+%      
+%	\tikzset{
+%      EdgeStyle/.append style = {black,-} }
+%
+%      \Edge(1)(2)
+%      \Edge(1)(3)
+%    \node (1) at (-3,4){\Huge $\rightarrow$};
+%%     
+%%     \node (2) at (-7,0){\Huge H};
+%%     \node (3) at (10,0){\Huge G};
+%    \end{tikzpicture}
+%    }
+%    \caption{Reduction from k-coloring to MIN-PRA}
+%    \label{fig:reduction}
+%    \end{figure}
 
@@
 
-    \subsection{The star routed network}
-
-      Let us define a family of simple symmetric routed networks. 
-      The graph $G$ has two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes:
-      the central source node {\bf $c_s$} and the central target node {\bf $c_t$}.
-      There is an arc between {\bf $c_s$} and {\bf $c_t$} and for all $i$, there is an arc between $s_i$ and $c_s$ and between $t_i$ and $c_t$.
-      All the symmetric arcs are also in the graph with the same weights.
-      The forward routes are the directed paths $r_i = (s_i,c_s,c_t,t_i)$ and $\rho(r_i) = (t_i,c_t,c_s,s_i)$ which defines a symmetric routed network. 
-      The symmetric routed networks $(G, \{r_i,\rho(r_i)\}_{i<n})$ is called a \textbf{star routed network}.
-
-       \begin{center}
-	 \scalebox{0.8}{
-\begin{tikzpicture}
-
-\tikzset{EdgeStyle/.style={<->,font=\scriptsize,above,sloped,midway}}
-  \SetGraphUnit{5}
-
-  \node[draw,circle] (s3) at (0, 0) {$s_2$}; 
-  \node[draw,circle] (s2) at (0, 2) {$s_1$}; 
-  \node[draw,circle] (s1) at (0, 4) {$s_0$};
-
-  \node[draw,circle] (t3) at (8, 0) {$t_2$}; 
-  \node[draw,circle] (t2) at (8, 2) {$t_1$}; 
-  \node[draw,circle] (t1) at (8, 4) {$t_0$};
-
-  \node[draw,circle] (cs) at (3, 2) {$c_s$}; 
-  \node[draw,circle] (ct) at (5, 2) {$c_t$};
-
-  \Edge[label = $\omega(s_1\,c_s)$](s1)(cs)
-  \Edge[label = $\omega(...)$](s2)(cs)
-  \Edge[label = $\omega(...)$](s3)(cs)
-
-  \Edge[label = $\omega(...)$](ct)(t1)
-  \Edge[label = $\omega(...)$](ct)(t2)
-  \Edge[label = $\omega(...)$](ct)(t3)
-
-  \Edge(cs)(ct)
-
-\end{tikzpicture}
-}
-
-  \end{center}
-
-      Since the central arc appears in every route, its value does not matter when considering the process time of an assignment.
-      Moreover an assignment without collisions is also an assignment without collisions if the weight of the central arc 
-      is set to $0$, therefore we assume from now on it is indeed $0$.
-
-      Collisions between messages can only appear in the arc $(c_s,c_t)$ on the way forward and in the arc $(c_t,c_s)$ on the way back.
-The flow of messages in a star routed network is completely described by their repartition in two time windows of size $P$ that we call the {\bf forward period} (at $(c_s,c_t)$), and the {\bf backward period} (at $(c_t,c_s)$).
-
   \subsection{Solving PAZL}
 
-  In this subsection, we deal with a simpler version of the problem PALL.
-  We ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$} and we call this restricted problem {\bf Periodic Assignment for Zero Latency} or PAZL.
-We consider PAZL since it is simpler to get theoretical results and good algorithms
-  than for PALL.
-Moreover, as we show in our experimentations of Sec.\ref{sec:exp_PAZL}, this problem can often be solved positively (albeit less often than the general problem).
-Finally, a solution to PAZL is simpler to implement in real telecommunication networks, since we do not need to implement any buffering at all.
-
+  In this subsection, we deal with the problem PAZL.  
   When the waiting times are zero, $MT({\cal M})$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
@@
 Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
-
-  One may consider a variant of PAZL where the central link is unidirectional, that is collisions can happen between messages going from $c_s$ to $c_t$ and messages  going from $c_t$ to $c_s$.
-This problem can be shown to be $\NP$-complete by a reduction from the subset sum problem as it is done for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
-We conjecture that the problem PAZL is also $\NP$-complete,  but we have yet not been able to prove it.
-  On the other hand we show positive results:  when the period is large or when the routes are short there is always a solution to PAZL and it can be found in polynomial time.
-We then give an exponential time exhaustive search algorithm which always finds a solution if there is one.
 
@@
 \begin{figure}[H]
-    \begin{minipage}[c]{0.5\textwidth}
+
   \centering
-      \includegraphics[width=0.5\textwidth]{departs_gp_21000.pdf}
+     \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}
 
       \caption{Success rate of different orders, $95\%$ load.}
-      \end{minipage} \hfill
-        \begin{minipage}[c]{0.5\textwidth}
+          \end{figure}
+\begin{figure}[H] 
           \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
       \caption{Success rate of different orders, $80\%$ load.}
-
-            \end{minipage} \hfill
            \label{fig:success30000}
@@
        \begin{center}
-      \includegraphics[scale=0.45]{retour_21000.pdf}
+      \includegraphics[width=0.5\textwidth]{retour_21000.pdf}
       \end{center}
@@
        \begin{center}
-   \begin{tabular}{|c|c|c|c|c|c|c|}
+   \begin{tabularx}{0.5\textwidth}{|c|X|X|X|X|X|X|}
     \hline
-    Number of random orders & $1$ & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
+    \# orders& $1$ & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
     \hline
-    Percentage of success of GD & $0.6$ &$7.1$&$33.4$&$76.4$&$90.0$&$90.0$\\
+    GD & $0.6$ &$7.1$&$33.4$&$76.4$&$90.0$&$90.0$\\
     \hline
-    Percentage of success of PMLS & $41,1$ &$82,5$&$94,5$&$96,2$&$97,2$&$97,2$\\
+  PMLS & $41,1$ &$82,5$&$94,5$&$96,2$&$97,2$&$97,2$\\
     \hline
-      \end{tabular}
+      \end{tabularx}
       \end{center}
@@
        \begin{center}
-      \includegraphics[scale=0.4]{stochastic.pdf}
+      \includegraphics[width = 0.5\textwidth]{stochastic.pdf}
        %\input{figures/stochastic}
@@
 
-  \paragraph*{Acknowledgments} The authors thanks Christian Cad\'er\'e and David Auger for the friendly discussions
-  they had on the subject and their insightful remarks.
+%   
+%  \paragraph*{Acknowledgments} The authors thanks Christian Cad\'er\'e and David Auger for the friendly discussions
+%  they had on the subject and their insightful remarks.
 

### 2017-07-19 infocom/infocom.tex
abstract et intro + petites modifs

@@
 %opening
-\title{Deterministic Scheduling of Periodic Messages in a Network}% by a SDN (deterministic) approach}
+\title{Deterministic Scheduling of Periodic Messages in a Network by a SDN (deterministic) approach}
 
@@
 \begin{abstract}
-We study the sending of periodic messages in a graph following predefined paths, a problem arising from communication between radio antennas and their signal processing units located in distant data-centers.
-Messages must be sent deterministically to avoid collisions on the network and to minimize the latency.
-We prove that problems arising from this context are $\NP$-complete even for very restricted graphs.
-We then deal with the case of a star graph and for different regimes of parameters we propose algorithms that are experimentally shown to work extremely well compared to traditional statistical multiplexing.
+A recent trend in mobile networks is to centralize the processing units which were attached to 
+antennas in distant data-centers. The main challenge is to guarantee that the latency of the periodic messages 
+sent from the antennas to their processing units and back is minimal. We show that traditional statistical multiplexing
+is bad at ensuring a low latency.
+Hence, we propose in this article to use a deterministic scheme which allows to send periodic messages without collisions in the network and thus without buffering and additional latency.
+We give several algorithms to compute such schemes for a common topology where one link is shared by all antennas.
+Some algorithm solves the problem when the routes are small or the load is small. Whe the parameters are unconstrained,
+and some buffering is allowed in the processing units, we propose an algorithm (PMLS) adapted from a classical scheduling method.
+The experimental results shows that even under full load, most of the time PMLS finds a sending scheme with no latency.
 \end{abstract}
@@
 
- In Sec.~\ref{sec:def} we propose a model of the network and the periodic sending of messages along its routes. 
- We then formalize our two problems of finding a periodic assignment for sending messages without collisions: PRA (sending of the message only) and PALL (sending of the message and of the answer).  
-In Sec.~\ref{sec:complexity}, we prove that the problem PRA and PALL are $\NP$-hard and cannot be approximated even for very
-restricted classes of graphs. 
-Therefore in the next two sections, we study a simple but very common topology, that we call the
-star routed network, where all messages can collide on a single arc.
-In Sec.\ref{sec:PAZL}, we study a variant of PALL called PAZL  where the waiting times must all be zero.
-We provide several algorithms, some of their theoretical properties and give experimental evidences that they find periodic assignments when the network is not too loaded.
-Finally in Sec.\ref{sec:PALL}, we propose algorithms for the general PALL problem and exhibit one which works extremely well in our experiments even in loaded networks.
+Our main contributions are the following.
+ In Sec.~\ref{sec:def} we propose a model of the network and the periodic sending of messages along its routes
+ and we introduce the star routed network we study in this article. 
+ We formalize the problem of finding a periodic assignment for sending messages without buffering (PAZL) or
+ with buffering in the processing unit only (PALL) and shows that they are $\NP$-hard even to approximate.
+In Sec.~\ref{sec:PAZL}, we propose two algorithms solving PAZL when the routes between RRHs and BBUs are small
+or when the load is light. Using a compact representation of an assignment, we show that PAZL is fixed parameter tractable when parametrized by the number of antenna on star routed networks.
+Finally in Sec.~\ref{sec:PALL}, we introduce a family of algorithms to solve PALL and our experimentation 
+allows to select one which works extremely well even in very loaded networks.
 In particular we show that the deterministic communication schemes we design vastly outperform the traditional stochastic multiplexing with regard to latency.
@@
 Consider $\mathcal{M}$ a $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
-Let $r_0$ be an arbitrary route of ${\cal R}$,  and let $COMPACT = \{r_0\}$. Now we apply the following algorithm to $\mathcal{M}$ and $COMPACT$ while $COMPACT$ is not equal to ${\cal R}$.
-While there is no collision, remove $1$ (modulo $P$) from all offsets of routes in ${\cal R} \setminus COMPACT$.
-Then choose a route $r$ in ${\cal R} \setminus COMPACT$ which would have a collision with a route $r'$ of $COMPACT$ if one is subtracted from its offset.
-If $r'$ is a forward route, let $COMPACT = COMPACT \cup \{r, \rho(r)\}$ otherwise  $COMPACT = COMPACT \cup \{r, \rho^{-1}(r)\}$.
-
-We prove by induction that $COMPACT$ is compact for $\mathcal{M}$ at every step of the algorithm.
-At the beginning $|COMPACT| = 1$ and the property is trivially satisfied. Then we assume that 
-$COMPACT$ is compact and that we add to it $\{r, \rho(r)\}$ at some step of the algorithm.
+Let $r_0$ be an arbitrary route of ${\cal R}$,  and let $COMP = \{r_0\}$. Now we apply the following algorithm to $\mathcal{M}$ and $COMP$ while $COMP$ is not equal to ${\cal R}$.
+While there is no collision, remove $1$ (modulo $P$) from all offsets of routes in ${\cal R} \setminus COMP$.
+Then choose a route $r$ in ${\cal R} \setminus COMP$ which would have a collision with a route $r'$ of $COMP$ if one is subtracted from its offset.
+If $r'$ is a forward route, let $COMP = COMP \cup \{r, \rho(r)\}$ otherwise  $COMP = COMP \cup \{r, \rho^{-1}(r)\}$.
+
+We prove by induction that $COMP$ is compact for $\mathcal{M}$ at every step of the algorithm.
+At the beginning $|COMP| = 1$ and the property is trivially satisfied. Then we assume that 
+$COMP$ is compact and that we add to it $\{r, \rho(r)\}$ at some step of the algorithm.
 W.l.o.g we assume that it is the offset of $r$ which cannot be decremented without collision.
-Consider $S \subseteq   COMPACT$, if $S$ contains an element different from $r$ and $\rho(r)$ by induction hypothesis we cannot decrement the offsets of $S$ without collision.
+Consider $S \subseteq   COMP$, if $S$ contains an element different from $r$ and $\rho(r)$ by induction hypothesis we cannot decrement the offsets of $S$ without collision.
 If $S =\{r, \rho(r)\}$
@@
 Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.
-The code in C is available on the webpage of one of the authors~\cite{webpage} under a copyleft license.
+%       The code in C is available on the webpage of one of the authors~\cite{webpage} under a copyleft license.
 
@@
 To do that we try to evaluate the minimal period (that is the highest possible load) for which a $(P,\tau)$-periodic assignment can be found by each algorithm.
-      To that end we use a linear search on $P$, since a dichotomy method would not work because of Lemma~\ref{lemma:monotonic}.
+%       To that end we use a linear search on $P$, since a dichotomy method would not work because of Lemma~\ref{lemma:monotonic}.
 
@@
 
-      Since the exhaustive search solve PAZL in an FPT time, with parameter $n$ the number of routes, we study the scalability of the time needed by this algorithm, according to $n$.
+      The computation time of the exhaustive search is in $O(n!)$, hence we need to study its scalability when $n$ grows.
 In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots.
-We fixed the period to $n\tau+1000$, that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
-      The following table shows the average time before the exhaustive search ends, for $1$ to $21$ routes. Theses results are computed on $100$ random star routed networks.
+We fixed a period of $n\tau+1000$.
+%       , that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
+      The following table shows the time before the exhaustive search ends, for $6$ to $21$ routes, averaged on $100$ random star routed networks.
+This shows that for less than $20$ routes, which corresponds to all current topologies, the algorithm is efficient enough, but on more routes we should improve it further.
          \begin{center}
-         \begin{tabularx}{0.5\textwidth}{|X|X|X|X|X|X|}
+         \begin{tabularx}{0.5\textwidth}{|l|X|X|X|X|}
     \hline
-   $n$ & $1$ & $6$ & $11$& $16$& $21$\\
+   $n$ & $6$ & $11$& $16$& $21$\\
     \hline
-   Time (ms) & $0.004$ &$0.027$&$0.599$&$59.711$&$14866.1$\\
+   Time (s) & $3.10^{-5}$&$6.10^{-4}$&$6.10^{-2}$& $15$\\
     \hline
@@
       \end{center}
-
-      With our practical parameters ($n<20$ routes), the algorithm can solve PAZL quickly.
-As soon as we want to compute more routes, the time required to answer PAZL with the exhaustive search increase exponentially.
 
@@
 
-    \paragraph*{Future works}
-
-   We plan to generalize our study of the PALL problem to other topologies,
-   such as trees, cycles or bounded treewidth graphs. 
-   We would like to design FPT algorithms in the number of routes for PALL on the star routed network, by generalizing the compact assignment idea used for PAZL.
-
-   We could also study variations of our problem.
+%     \paragraph*{Future works}
+%    
+%    We plan to generalize our study of the PALL problem to other topologies,
+%    such as trees, cycles or bounded treewidth graphs. 
+%    We would like to design FPT algorithms in the number of routes for PALL on the star routed network, by generalizing the compact assignment idea used for PAZL. 
+% 
+%    We could also study variations of our problem.
 Instead of minimizing the maximum process time, we could try to minimize the average process time, a linear objective which could make linear programming useful.
-   Moreover we could allow preemption, that is the messages are allowed to be cut into pieces, which would certainly change the complexity of the problem. 
-   Finally, the routes may not be fixed but chosen in the graph to minimize the maximum process time, which would make the problem even more difficult (maybe $\Pi_2$-complete instead of $\NP$-complete).
+%    Moreover we could allow preemption, that is the messages are allowed to be cut into pieces, which would certainly change the complexity of the problem. 
+%    Finally, the routes may not be fixed but chosen in the graph to minimize the maximum process time, which would make the problem even more difficult (maybe $\Pi_2$-complete instead of $\NP$-complete).
 

### 2017-07-19 infocom/infocom.tex
symetric avant star

--- 2017-07-19 infocom/infocom.tex
@@
 
+\author{}
 %\author[1]{Ma\"el Guiraud}
@@
 Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time slots taken by a signal to go from $u$ to $v$ using this arc.
-A {\bf route} $r$ in $G$ is a path, that is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
+A {\bf route} $r$ in $G$ is a path, that is, a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
 The {\bf latency} of a vertex $u_i$ in a path $r$, with $i \geq 1$, is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} \omega(a_j)$.
@@
 
-      Let us define a family of simple symmetric routed networks. 
+          In the context of cloud-RAN applications, we need to send message from a RRH $u$ to a BBU $v$ and then 
+      we must send the answer from $v$ back to $u$.
+We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of forward routes and $B$ of backward routes.
+Moreover there is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
+In all practical cases the routes $r$ and $\rho(r)$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we need not to enforce this property.
+
+      Let us define a family of simple symmetric routed networks on which we focus in this paper. 
       The graph $G$ has two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes:
@@
       \subsection{Periodic assignment for low latency}
-      In the context of cloud-RAN applications, we need to send message from a RRH $u$ to a BBU $v$ and then 
-      we must send the answer from $v$ back to $u$.
-We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of forward routes and $B$ of backward routes.
-Moreover there is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
-In all practical cases the routes $r$ and $\rho(r)$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we need not to enforce this property.
-
-         A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a set of two sequence  ${\cal M}=\{(m_0, \ldots ,m_{n-1}),(m_{\rho_0}, \ldots ,m_{\rho_{n-1}})\}$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+
+         A {\bf $(P,\tau)$-periodic assignment} of a star routed network $(G,\cal R)$ is a set of two sequence  ${\cal M}=\{(m_0, \ldots ,m_{n-1}),(m_{\rho_0}, \ldots ,m_{\rho_{n-1}})\}$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
 The number $m_{i}$ (respectively $m_{\rho_i}$) represents the time at which a message is emitted at the first vertex of the route $r_{i}$ (respectively $r_{\rho_i}$).A $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routed network represents
@@
 Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.
-The code in C is available on the webpage of one of the authors~\cite{webpage} under a copyleft license.
+      % The code in C is available on the webpage of one of the authors~\cite{webpage} under a copyleft license.
 
@@
 
-     We can decompose any algorithm solving the PALL problem in two parts: first set the offsets of the forward routes and then knowing this information set the offset of the backward routes or equivalently the waiting times.
+     We can decompose any algorithm solving the PALL problem in two parts: first set the offsets of the forward routes and then, knowing this information set the offset of the backward routes or equivalently the waiting times.
      The offsets of the forward routes will be chosen so that all messages have no collision on the central arc and such that there are no free slots inbeetween the end of a message on the central arc and the beginning of the next one.
      It is done to minimize the period needed to send the messages of the forward route.
-     We tried the five following orders. 
-	\begin{itemize}
-
-	 \item Longest-Shortest on Routes (LSR): Decreasing order on the length of the routes.
-	 \item Shortest-Longest on Routes (SLR): Increasing order on the length of the routes. 
-	 \item Longest-Shortest on last Arc (LSA): Decreasing order on the length of the arcs $(c_t,t_i)$.
-	 \item Shortest-Longest on last Arc (SLA): Increasing order on the length of the arcs $(c_t,t_i)$.
+%     We tried the five following orders. 
+%	\begin{itemize}
+%	 
+%	 \item Longest-Shortest on Routes (LSR): Decreasing order on the length of the routes.
+%	 \item Shortest-Longest on Routes (SLR): Increasing order on the length of the routes. 
+%	 \item Longest-Shortest on last Arc (LSA): Decreasing order on the length of the arcs $(c_t,t_i)$.
+%	 \item Shortest-Longest on last Arc (SLA): Increasing order on the length of the arcs $(c_t,t_i)$.
 This sending order yields a $(P,\tau)$ periodic assignment in which all the $w_i = 0$, if the period is large enough (see proposition \ref{prop:SL}).
-	 \item Random: A random order of the routes.
-	\end{itemize}
+%	 \item Random: A random order of the routes.
+%	\end{itemize}
 

### 2017-07-19 code/Sources/main.c

@@ -17,7 +17,7 @@ int main()
 	/*****
 	Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
 	*****/
-	//simuls_periode_PAZL(20,2500,700,100);
+	simuls_periode_PAZL(15,2500,700,100);
 
 	/******************************************/	
 
@@ -78,7 +78,7 @@ int main()
 	/****Nombre de routes pouvant être calculées en moins de "max" ms
 	****/
 
-	search_efficiency(2500,30000,100);
+	//search_efficiency(2500,30000,100);
 
 
 	/******

### 2017-07-19 infocom/infocom.tex

--- 2017-07-19 infocom/infocom.tex
@@
 Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.
+
+      % The code in C is available on the webpage of one of the authors~\cite{webpage} under a copyleft license.
+
 %       The code in C is available on the webpage of one of the authors~\cite{webpage} under a copyleft license.

### 2017-07-20 infocom/infocom.tex
modifs avant appel

@@
 
+   In the context of cloud-RAN applications, we need to send message from a RRH $u$ to a BBU $v$ and then 
+      we must send the answer from $v$ back to $u$.
+We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of forward routes and $B$ of backward routes.
+Moreover there is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
+In all practical cases the routes $r$ and $\rho(r)$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we need not to enforce this property.
+
    \subsection{Messages dynamic}
@@
 
+         A {\bf $(P,\tau)$-periodic assignment} of a star routed network $(G,\cal R)$ is a set of two sequence  ${\cal M}=\{(m_0, \ldots ,m_{n-1}),(m_{\rho_0}, \ldots ,m_{\rho_{n-1}})\}$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+The number $m_{i}$ (respectively $m_{\rho_i}$) represents the time at which a message is emitted at the first vertex of the route $r_{i}$ (respectively $r_{\rho_i}$).A $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routed network represents
+ the sending of a message and of its answer. \emph{No pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
+   This assignment represents the following process: first a message is sent at $u$, through the route $r \in F$, at time $m_r$.
+
+      \begin{center}
+     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{rrh.pdf}
+      \end{center}
+
+      This message is received by $v$ the last vertex of $r$ at time $t(v,r)$.
+It is then sent back to $u$ on the route $\rho(r)$ in the same period at time $m_{\rho(r)}$ if $m_{\rho(r)} > t(v,r)$, otherwise at time $m_{\rho(r)}$ in the next period.
+The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_r = m_{\rho(r)} - t(v,r)$ if $m_{\rho(r)} > t(v,r)$ and $w_r = m_{\rho(r)} + P - t(v,r)$ otherwise.
+
+       \begin{center}
+     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{BBU.pdf}
+      \end{center}
+
+      Thus, the whole process time for a message sent on the route $r$ is equal to
+      $PT(r)=\lambda(r)+ w_r+\lambda(r)$.      
+      In the process time, we count the time between the first time at which a message is emitted and the first time at which the message comes back.
+Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
+      However, since all messages are of size $\tau$, it will not change the problems we consider in the rest of the article.
+      Finally, we could add to the process time the computation time a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
+
     \subsection{The star routed network}
-
-          In the context of cloud-RAN applications, we need to send message from a RRH $u$ to a BBU $v$ and then 
-      we must send the answer from $v$ back to $u$.
-We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of forward routes and $B$ of backward routes.
-Moreover there is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
-In all practical cases the routes $r$ and $\rho(r)$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we need not to enforce this property.
 
@@
 
-         A {\bf $(P,\tau)$-periodic assignment} of a star routed network $(G,\cal R)$ is a set of two sequence  ${\cal M}=\{(m_0, \ldots ,m_{n-1}),(m_{\rho_0}, \ldots ,m_{\rho_{n-1}})\}$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
-The number $m_{i}$ (respectively $m_{\rho_i}$) represents the time at which a message is emitted at the first vertex of the route $r_{i}$ (respectively $r_{\rho_i}$).A $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routed network represents
- the sending of a message and of its answer. \emph{No pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
-   This assignment represents the following process: first a message is sent at $u$, through the route $r \in F$, at time $m_r$.
-
-      \todo{mettre le lemme sur la monotonie sans preuve?}
-
-      \begin{center}
-     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{rrh.pdf}
-      \end{center}
-
-      This message is received by $v$ the last vertex of $r$ at time $t(v,r)$.
-It is then sent back to $u$ on the route $\rho(r)$ in the same period at time $m_{\rho(r)}$ if $m_{\rho(r)} > t(v,r)$, otherwise at time $m_{\rho(r)}$ in the next period.
-The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_r = m_{\rho(r)} - t(v,r)$ if $m_{\rho(r)} > t(v,r)$ and $w_r = m_{\rho(r)} + P - t(v,r)$ otherwise.
-
-       \begin{center}
-     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{BBU.pdf}
-      \end{center}
-
-      Thus, the whole process time for a message sent on the route $r$ is equal to
-      $PT(r)=\lambda(r)+ w_r+\lambda(r)$.      
-      In the process time, we count the time between the first time at which a message is emitted and the first time at which the message comes back.
-Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
-      However, since all messages are of size $\tau$, it will not change the problems we consider in the rest of the article.
-      Finally, we could add to the process time the computation time a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
-
     The {\bf maximum process time} of the assignment ${\cal M}$ of $(G,{\cal R})$ is defined by $MT({\cal M})=\max\limits_{r \in {\cal R}} PT(r)$. We consider the following decision problem.
@@
 
-     We show in the long version of this article that this problem is $\NP$-hard. 
+ \begin{theorem}
+Problem PALL is $\NP$-complete on some class of routed networks with specific parameters.
+\end{theorem}
+ \begin{proof}
+ Problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of arcs whether there are collisions.
+
+  Let $H=(V,E)$ be an undirected graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is arc-colorable
+  with $d$ or $d+1$ colors.
+The arc coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness.
+To do that, we define from $H$ a routed network $(G,{\cal R})$.
+ The constraint of having no collision between the routes is equivalent to the fact that no two adjacent arcs have the same color.
+Therefore we have reduced arc coloring to PRA by a polynomial time transformation which concludes the proof.
+ \end{proof}
+
+     The long version of this article contains the entire proof about the $\NP$-hardness of PALL. 
       In Sec.~\ref{sec:PALL} we will study heuristics which try to solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity.
@@
       \begin{center}
-	\includegraphics[width=0.5\textwidth]{periode_petite.pdf}
+	 \hspace{-0.5cm}\includegraphics[width=0.53\textwidth]{periode_petite.pdf}
       \end{center}
@@
       \IF{${\cal H}$ is empty}
-      \STATE t $\leftarrow $ min\_non\_assigned(eligible\_time)
-      \STATE take $r_i$ the route with eligible\_time[$r_i$] = t
-      \STATE 
+      \STATE $r_i$ $\leftarrow $ min\_non\_assigned(eligible\_time)
       \ENDIF
@@
     \end{algorithm}
-    The function  min\_non\_assigned(eligible\_time) returns the lowest time in eligible\_time, for which the corresponding route is not assigned yet.
+    The function  min\_non\_assigned(eligible\_time) returns the route with lowest time in eligible\_time, which is not assigned yet.
 The function update(t,free\_intervals) removes an interval of size $\tau$ beginning at t, which correspond to the message,  from free\_intervals.
@@
      \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}
-
+\vspace{-0.75cm}
       \caption{Success rate of different orders, $95\%$ load.}
           \end{figure}
+          \vspace{-1cm}
 \begin{figure}[H] 
           \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
+          \vspace{-1cm}
       \caption{Success rate of different orders, $80\%$ load.}

### 2017-07-20 code/Calculs autres/ecart_type.c

@@ -155,11 +155,11 @@ void quartiles()
 {
 	FILE * f = fopen("traitement.data","w");
 	lire_fichier();
-	for(int i = nb_periodes-1;i>=0;i--)
+	for(int i = nb_periodes-1;i>0;i--)
 	{
 		tri_bulles(donnes[i],taille);
-		fprintf(f,"%d %d %d %d \n",20000+i*1000,donnes[i][taille/4+1],donnes[i][taille/2+1],donnes[i][3*taille/4+1]);
-		fprintf(stdout,"%d %d %d %d \n",20000+i*1000,donnes[i][taille/4+1],donnes[i][taille/2+1],donnes[i][3*taille/4+1]);
+		fprintf(f,"%d %d %d %d \n",(int)(20000/(20000+(float)i*1000)*100),donnes[i][taille/4+1],donnes[i][taille/2+1],donnes[i][3*taille/4+1]);
+		fprintf(stdout,"%d %d %d %d \n",(int)(20000/(20000+(float)i*1000)*100),donnes[i][taille/4+1],donnes[i][taille/2+1],donnes[i][3*taille/4+1]);
 		//fprintf(f,"%d %d %d %d 0\n",(int)(20000/(20000+i*1000.0)*100),donnes[i][taille/4+1]/20 ,donnes[i][taille/2+1]/20,donnes[i][3*taille/4+1]/20);
 		//fprintf(stdout,"%d %d %d %d 0\n",(int)(20000/(20000+i*1000.0)*100),donnes[i][taille/4+1]/20 ,donnes[i][taille/2+1]/20,donnes[i][3*taille/4+1]/20);
 

### 2017-07-20 code/Sources/main.c

@@ -17,7 +17,7 @@ int main()
 	/*****
 	Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
 	*****/
-	simuls_periode_PAZL(15,2500,700,100);
+	//simuls_periode_PAZL(15,2500,700,100);
 
 	/******************************************/	
 
@@ -78,7 +78,7 @@ int main()
 	/****Nombre de routes pouvant être calculées en moins de "max" ms
 	****/
 
-	//search_efficiency(2500,30000,100);
+	search_efficiency(2500,30000,10);
 
 
 	/******

### 2017-07-20 code/Sources/simulations.c

@@ -483,7 +483,7 @@ double time_search(int nb_routes, int taille_message,int taille_routes)
 	g = init_graphe(nb_routes *2 +1);
 	graphe_etoile(g,taille_routes);
 	gettimeofday (&tv1, NULL);
-	search(g,taille_message,taille_message*nb_routes+1000);
+	search(g,taille_message,taille_message*nb_routes*1.05);
 	gettimeofday (&tv2, NULL);
 	timer = time_diff(tv1,tv2);
 		
@@ -497,7 +497,7 @@ void search_efficiency(int taille_message,int taille_routes, int nb_simuls)
 	double average=0;
 	double max = 0.0;
 	double result;
-	for(int nb_routes = 1;nb_routes<22;nb_routes+=1)
+	for(int nb_routes = 1;nb_routes<25;nb_routes+=1)
 	{
 		max = 0.0;
 		for(int i=0;i<nb_simuls;i++)

### 2017-07-20 infocom/infocom.tex
petites corrections

@@
 %opening
-\title{Deterministic Scheduling of Periodic Messages in a Network by a SDN (deterministic) approach}
+\title{Deterministic Scheduling of Periodic Messages by a SDN Approach}
 
@@
 is bad at ensuring a low latency.
-Hence, we propose in this article to use a deterministic scheme which allows to send periodic messages without collisions in the network and thus without buffering and additional latency.
+Hence, we propose in this article to use a deterministic scheme to send periodic messages without collisions in the network and thus without buffering and additional latency.
 We give several algorithms to compute such schemes for a common topology where one link is shared by all antennas.
-Some algorithm solves the problem when the routes are small or the load is small. Whe the parameters are unconstrained,
+We show that there is always a solution when the routes are small or the load is small. When the parameters are unconstrained,
 and some buffering is allowed in the processing units, we propose an algorithm (PMLS) adapted from a classical scheduling method.
-The experimental results shows that even under full load, most of the time PMLS finds a sending scheme with no latency.
+The experimental results shows that even under full load, most of the time PMLS finds a deterministic sending scheme with no latency.
 \end{abstract}
@@
 The latency is measured between the sending of a message by the Remote Radio Heads (RRHs) on the field and the receptions of the answers, computed by real-time virtualized network functions on Baseband Units (BBUs), in the cloud.
-For example, even if next radio protocols are less stringent, some standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in 1 to 10ms depending on targeted services~\cite{bouguen2012lte}.
+For example, even if next radio protocols are less stringent, some standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in $1$ to $10$ms depending on targeted services~\cite{bouguen2012lte}.
 The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRHs and BBUs.
 
- In this article, we study mechanisms to deal with the latency and periodicity constraints in the network located between the BUUs and the RRHs called fronthaul.
+ In this article, we study mechanisms to deal with the latency and periodicity constraints in the network located between the BUUs and the RRHs called \emph{fronthaul}.
  Statistical multiplexing even with a large bandwidth does not comply with the latency requirements.
-Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits.
+Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits for the fronthaul.
 Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches.
-This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.
+This architecture is very expensive and hardly scales in the case of a mobile network composed of about $10000$ base stations.
 Here we propose to use a deterministic approach to schedule our periodic messages.
@@
 To ensure that this property is always true we propose a deterministic process.
-We have two sets of parameters that we can choose when building a periodic sending process, called a \textbf{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
+We have two sets of parameters that we can choose when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
 When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods inapplicable.
@@
 Unfortunately, they do not take into account the periodicity of the scheduling and the associated problems are already $\NP$-complete.
-The only coloring which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple, zhu2001circular,zhu2006recent} but is not expressive enough to capture our problem.
+The only coloring which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple, zhu2001circular,zhu2006recent} but it is not expressive enough to capture our problem.
 
@@
 allows to select one which works extremely well even in very loaded networks.
-In particular we show that the deterministic communication schemes we design vastly outperform the traditional stochastic multiplexing with regard to latency.
+In particular we show that the deterministic communication schemes we design vastly outperform the traditional statistical multiplexing with regard to latency.
 
@@
 The network is modeled as a directed graph $G=(V,A)$.
-Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time slots taken by a signal to go from $u$ to $v$ using this arc.
+Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time taken by a signal to go from $u$ to $v$ using this arc.
 A {\bf route} $r$ in $G$ is a path, that is, a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
@@
 Moreover there is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
-In all practical cases the routes $r$ and $\rho(r)$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we need not to enforce this property.
+%       In all practical cases the routes $r$ and $\rho(r)$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we need not to enforce this property.
 
@@
 
-      Consider a route $r$, if a message is sent at time $m$ from $s$ the first vertex of $r$ then it will arrive at vertex $v$ in $r$ at time $m + \lambda(v,r)$.
+      Let $r$ be a route, if a message is sent at time $m$ from $s$ the first vertex of $r$ then it will arrive at vertex $v$ in $r$ at time $m + \lambda(v,r)$.
 In our problem, we send one message on each route periodically and we denote the period by $P$.
@@
 
-         A {\bf $(P,\tau)$-periodic assignment} of a star routed network $(G,\cal R)$ is a set of two sequence  ${\cal M}=\{(m_0, \ldots ,m_{n-1}),(m_{\rho_0}, \ldots ,m_{\rho_{n-1}})\}$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
-The number $m_{i}$ (respectively $m_{\rho_i}$) represents the time at which a message is emitted at the first vertex of the route $r_{i}$ (respectively $r_{\rho_i}$).A $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routed network represents
- the sending of a message and of its answer. \emph{No pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
+         A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=\{(m_0, \ldots ,m_{n-1})\}$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
+A $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ routed network represents the sending of a message and of its answer.
+\emph{No pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
    This assignment represents the following process: first a message is sent at $u$, through the route $r \in F$, at time $m_r$.
@@
       In the process time, we count the time between the first time at which a message is emitted and the first time at which the message comes back. 
-Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
-      However, since all messages are of size $\tau$, it will not change the problems we consider in the rest of the article.
-      Finally, we could add to the process time the computation time a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
+%       Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
+%       However, since all messages are of size $\tau$, it will not change the problems we consider in the rest of the article.
+      Finally, we should add to the process time the computation time a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
 
@@
 
-\section{The Star Routed Network: No Waiting Time} \label{sec:PAZL}
-
-  \subsection{Solving PAZL}
+\section{Solving PAZL on Star Routed Networks} \label{sec:PAZL}
+
+  \subsection{Algorithms}
 
@@
 
-      \begin{proposition} Let $(G, {\cal R})$ be a symmetric routed network, and let $n\tau + 2(\lambda(r_{n-1}) - \lambda(r_{0})) \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which is given by Shortest-Longest in time $O(n\log(n))$.\label{prop:SL}
+      \begin{proposition} Let $(G, {\cal R})$ be a star routed network, and let $n\tau + 2(\lambda(r_{n-1}) - \lambda(r_{0})) \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which is given by Shortest-Longest in time $O(n\log(n))$.\label{prop:SL}
       \end{proposition}
@@
     \begin{proposition}
-     Let $(G, {\cal R})$ be a symmetric routed network, and let $ 3n\tau \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which can be found in time $O(n^2)$.
+     Let $(G, {\cal R})$ be a star routed network, and let $ 3n\tau \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which can be found in time $O(n^2)$.
     \end{proposition}
@@
 
-   \section{The Star Routed Network: Minimizing Latency}\label{sec:PALL}
+   \section{Solving PALL on Star Routed Networks}\label{sec:PALL}
 
@@
 	The assignment in that case is trivial, just send all messages so that they follow each other without gaps in the central arc $(c_s,c_t)$.
-Since the arcs $(c_t,t_i)$ are of weigth $0$, all messages will go through $(c_t,c_s)$ on their way back in
+Since the arcs $(c_t,t_i)$ are of weight $0$, all messages will go through $(c_t,c_s)$ on their way back in
 	the same order and thus will not collide.
@@
  %A more realistic assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same. It would correspond to a situation where all the BBUs are in the same datacenter.
-	Another assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same.
+	Another assumption would be that all weights of the arcs $(s_i,c_s)$ are the same.
 
 	 \begin{theorem}
-	 Let $(G,{\cal R})$ be a symmetric routed network with $n$ routes and let $P \geq n\tau$.
-If there is a constant $c$ such that $\forall i < n, \,\omega(s_i,c_s) = c$, then there is a $(P,\tau)$-peridoic assignment with process time $2 \times \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
+	 Let $(G,{\cal R})$ be a star routed network with $n$ routes and let $P \geq n\tau$.
+If there is a constant $c$ such that $\forall i < n, \,\omega(s_i,c_s) = c$, then there is a $(P,\tau)$-periodic assignment with process time $2 \times \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
 	 \end{theorem}
@@
 We obtain $PT(r_i) = 2\lambda(r_{0})$ and thus the maximum process time of the assignment is also equal to $2\lambda(r_0)$.
-	Finally the complexity is $O(n)$ since we have to find a maximum between the size of $n$ routes and the computation of each $w_i$ is done by a constant number of artihmetic operations.
+	Finally the complexity is $O(n)$ since we have to find a maximum between the size of $n$ routes and the computation of each $w_i$ is done by a constant number of arithmetic operations.
      \end{proof}
@@
      If for any pair of indices $(i,j)$ the difference between the weights of the arcs $(s_i,c_s)$ and $(s_j,c_s)$ is bounded 
-     by $d$ and the length of the longest route is $l$, then the maximum process time is bounded by  $2l + d$.
-
-     \subsection{A two stage approach}
-
-     We can decompose any algorithm solving the PALL problem in two parts: first set the offsets of the forward routes and then, knowing this information set the offset of the backward routes or equivalently the waiting times.
-     The offsets of the forward routes will be chosen so that all messages have no collision on the central arc and such that there are no free slots inbeetween the end of a message on the central arc and the beginning of the next one.
-     It is done to minimize the period needed to send the messages of the forward route.
+     by $d$ and the length of the longest route is $l$, then the maximum process time is bounded by  $2l + d$
+
 %     We tried the five following orders. 
@@
 %	\end{itemize}
-
-   In the rest of the section we will study different methods to compute the offsets of the backward routes, once
-   the offsets of the forward routes are fixed by one of the previous orders.
-
+% 
+%    In the rest of the section we will study different methods to compute the offsets of the backward routes, once
+%    the offsets of the forward routes are fixed by one of the previous orders.
+%    
    \subsection{Greedy scheduling of backward routes}
 
-    Assume that the offsets of the forward routes are fixed by some order. 
+    We can decompose any algorithm solving the PALL problem in two parts: first set the offsets of the forward routes and then, knowing this information set the offset of the backward routes or equivalently the waiting times.
+    The offsets of the forward routes are chosen so that messages have no collision on the central arc and such that there are no free slots in between the end of a message on the central arc and the beginning of the next one.
+    It is done to minimize the period needed to send the messages of the forward route. For this section and the next, we assume that the offsets of the forward routes are fixed by some order.
+
     Consider a forward route $r_i$ and the corresponding backward route $r_{\rho(i)}$.
@@
     they may collide with any other route.
-Therefore we must adapt the greedy algorithm of the previous paragraph by finding $s \geq t$ the first time for which there is an eligible route with its offset not fixed and \emph{such that there is no collision if a message go
-    through the central arc at time $s$}.
+Therefore we must adapt the greedy algorithm of the previous paragraph by finding $s \geq t$ the first time for which there is an eligible route with its offset not fixed and \emph{such that there is no collision if a message go through the central arc at time $s$}.
 

### 2017-07-20 infocom/infocom.tex
avant merge

--- 2017-07-20 infocom/infocom.tex
@@
 We give several algorithms to compute such schemes for a common topology where one link is shared by all antennas.
-Some algorithm solves the problem when the routes are small or the load is small. Whe the parameters are unconstrained,
+Some algorithm solves the problem when the routes are small or the load is small. When the parameters are unconstrained,
 and some buffering is allowed in the processing units, we propose an algorithm (PMLS) adapted from a classical scheduling method.

### 2017-07-20 code/Sources/main.c

@@ -78,7 +78,7 @@ int main()
 	/****Nombre de routes pouvant être calculées en moins de "max" ms
 	****/
 
-	search_efficiency(2500,30000,10);
+	search_efficiency(2500,20000,10);
 
 
 	/******

### 2017-07-20 code/Sources/simulations.c

@@ -483,7 +483,9 @@ double time_search(int nb_routes, int taille_message,int taille_routes)
 	g = init_graphe(nb_routes *2 +1);
 	graphe_etoile(g,taille_routes);
 	gettimeofday (&tv1, NULL);
-	search(g,taille_message,taille_message*nb_routes*1.05);
+	int period = taille_message*nb_routes*1.05;
+	//printf("%d \n",period);
+	search(g,taille_message,period);
 	gettimeofday (&tv2, NULL);
 	timer = time_diff(tv1,tv2);
 		

### 2017-07-20 infocom/infocom.tex
simplifications

--- 2017-07-20 infocom/infocom.tex
@@
 %opening
-\title{Deterministic Scheduling of Periodic Messages by a SDN Approach}
+\title{Deterministic Scheduling of Periodic Messages by an SDN Approach}
 
@@
 Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time taken by a signal to go from $u$ to $v$ using this arc.
-A {\bf route} $r$ in $G$ is a path, that is, a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
-The {\bf latency} of a vertex $u_i$ in a path $r$, with $i \geq 1$, is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} \omega(a_j)$.
-We also define $\lambda(u_0,r)=0$.
+A {\bf route} $r$ in $G$ is a path, that is, a sequence of adjacent vertices $u_0, \ldots , u_{k}$, with $(u_i,u_{i+1}) \in A$.
+The {\bf latency} of a vertex $u_i$ in a path $r$ is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} \omega(u_j, u_{j+1})$.
+% We also define $\lambda(u_0,r)=0$. 
 The length of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
@@
    In the context of cloud-RAN applications, we need to send message from a RRH $u$ to a BBU $v$ and then 
-      we must send the answer from $v$ back to $u$.
-We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of forward routes and $B$ of backward routes.
+      we must send the answer from $v$ back to $u$. Therefore we assume that all considered routed networks 
+      are \emph{symmetric}, that is for every arc $(u,v)$ there is an arc $(v,u)$ with the same weight.
+      We define the function $\rho$ which associates to a route $r = u_0,\dots,u_k$ the symmetric route $\rho(r) = u_k,\dots,u_0$.
+      The set ${\cal R}$ is partitioned into $F$ and $B$ such that $\rho$ is a bijection from $F$ to $B$.
+      The routes of $F$ are called \textbf{forward} routes and those of $B$ are called \textbf{backward} routes.
+%       
+%       We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of forward routes and $B$ of backward routes.
 Moreover there is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
@@
 
+      In the process we study, a message is sent on each route at each period, denoted by $P$.
       Let $r$ be a route, if a message is sent at time $m$ from $s$ the first vertex of $r$ then it will arrive at vertex $v$ in $r$ at time $m + \lambda(v,r)$.
-In our problem, we send one message on each route periodically and we denote the period by $P$.
-      Periodicity means that if we look at the messages going through an arc between time $0$ and $P-1$, then we would observe the same messages in the same order and position between time $kP$ and $(k+1)P -1$ for all $k$.
-      Therefore, we will always consider a period of $P$ discrete slots of time at each arc to characterize the working of the network.
-We define the first time slot at which a message sent from the first vertex of $r$ will reach a vertex $v$ in $r$ by $t(v,r) = m + \lambda(v,r) \mod P$.
+Since the process is periodic, if we look at the messages going through an arc between time $0$ and $P-1$, then we would observe the same messages in the same order and position between time $kP$ and $(k+1)P -1$ for all $k$.
+      Therefore, the first time slot at which a message sent at time $m$ on $r$ reaches a vertex $v$ in $r$ is $t(v,r) = m + \lambda(v,r) \mod P$.
 
@@
 
-         A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=\{(m_0, \ldots ,m_{n-1})\}$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
-The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
-A $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ routed network represents the sending of a message and of its answer.
+         A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a function which associate to each route 
+         $r \in \cal R$ its \textbf{offset} $m_r$ that is the time at which a message is emitted at the first vertex of the route $r$.
 \emph{No pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
-   This assignment represents the following process: first a message is sent at $u$, through the route $r \in F$, at time $m_r$.
-
+	 An assignment represents the following process: first a message is sent at $u$, through the forward route $r$, at time $m_r$.
       \begin{center}
@@
 
-             Let us define a family of simple symmetric routed networks on which we focus in this paper. 
-      The graph $G$ has two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes:
-      the central source node {\bf $c_s$} and the central target node {\bf $c_t$}.
-      There is an arc between {\bf $c_s$} and {\bf $c_t$} and for all $i$, there is an arc between $s_i$ and $c_s$ and between $t_i$ and $c_t$.
+             Let us define a family of simple routed networks that we will study in this paper. 
+      The graph $G$ has two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes, the central source node $c_s$ and the central target node $c_t$.
+      There is an arc between $c_s$ and  $c_t$ called the central arc and for all $i<n$ there is an arc between $s_i$ and $c_s$ and between $t_i$ and $c_t$.
 All the symmetric arcs are also in the graph with the same weights.
-      The forward routes are the directed paths $r_i = (s_i,c_s,c_t,t_i)$ and $\rho(r_i) = (t_i,c_t,c_s,s_i)$ which defines a symmetric routed network. 
-      The symmetric routed networks $(G, \{r_i,\rho(r_i)\}_{i<n})$ is called a \textbf{star routed network}.
+      The forward routes are the directed paths $r_i = (s_i,c_s,c_t,t_i)$ and the backward routes are $\rho(r_i) = (t_i,c_t,c_s,s_i)$.
+The routed network $(G, \{r_i,\rho(r_i)\}_{i<n})$ is called a \textbf{star routed network}.
 
@@
       Since the central arc appears in every route, its value does not matter when considering the process time of an assignment.
-      Moreover an assignment without collisions is also an assignment without collisions if the weight of the central arc 
-      is set to $0$, therefore we assume from now on it is indeed $0$.
-
-      Collisions between messages can only appear in the arc $(c_s,c_t)$ on the way forward and in the arc $(c_t,c_s)$ on the way back.
+      Moreover an assignment without collisions is also an assignment without collisions of the same star routed network with the weight of the central arc set to $0$.
+Hence, we assume from now on that the weight of the central arc is $0$.
+
+      Collisions between messages can only appear on the arc $(c_s,c_t)$ between forward routes or on the arc $(c_t,c_s)$
+      between backward routes.
 The flow of messages in a star routed network is completely described by their repartition in two time windows of size $P$ that we call the {\bf forward period} (at $(c_s,c_t)$), and the {\bf backward period} (at $(c_t,c_s)$).
@@
 
-      \noindent {\bf Input:}  A symmetric routed network $(G,{\cal R})$, the integers $P$, $\tau$ and $T_{max}$.
+      \noindent {\bf Input:}  A routed network $(G,{\cal R})$, the integers $P$, $\tau$ and $T_{max}$.
 
@@
 
+      In Sec.~\ref{sec:PALL} we will study algorithms which solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity. \todo{phrase utile finalement ?} 
+      It turns out that the problem PALL is hard to solve for \emph{general} routed networks.
+The long version of this article contains complete proofs of the $\NP$-hardness or hardness of approximation of PALL and of several of its variants.
+
  \begin{theorem}
-Problem PALL is $\NP$-complete on some class of routed networks with specific parameters.
+Problem PALL is $\NP$-complete.
 \end{theorem}
- \begin{proof}
- Problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of arcs whether there are collisions.
-
-  Let $H=(V,E)$ be an undirected graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is arc-colorable
-  with $d$ or $d+1$ colors.
-The arc coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness.
-To do that, we define from $H$ a routed network $(G,{\cal R})$.
- The constraint of having no collision between the routes is equivalent to the fact that no two adjacent arcs have the same color.
-Therefore we have reduced arc coloring to PRA by a polynomial time transformation which concludes the proof.
- \end{proof}
-
-     The long version of this article contains the entire proof about the $\NP$-hardness of PALL. 
-      In Sec.~\ref{sec:PALL} we will study heuristics which try to solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity.
-
-One can consider a simpler version of PALL.
-       We ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$} and we call this restricted problem {\bf Periodic Assignment for Zero Latency} or PAZL.
-We consider PAZL since it is simpler to get theoretical results and good algorithms
-  than for PALL.
+
+\noindent \emph{Sketch of proof:}
+ We first show that finding an assignment for the forward routes only with no collisions 
+ can be reduced to PALL by a symmetry argument.
+ We fix $\tau$ the size of messages to $1$ and we reduce the problem of $k$-coloring to the 
+ problem of finding an assignment without collisions for the forward routes.
+ Let $H$ be a graph instance of the $k$-coloring problem, the reduction is as follows. 
+ For each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
+Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an arc in $H$; this arc is the only one shared by these two routes.
+All arcs are of weight $0$.
+ Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic assignment in $G$, 
+ by converting an offset of a route into a color of a vertex and reciprocally. \qed
+
+       We consider a simpler version of PALL, that we call {\bf Periodic Assignment for Zero Latency} or PAZL: we ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$}.
+We introduce PAZL because it is simpler to study and we are able to prove theoretical results and find better algorithms than for PALL.
 Moreover, as we show in our experimentations of Sec.\ref{sec:exp_PAZL}, this problem can often be solved positively (albeit less often than the general problem).
@@
 
-    One may consider a variant of PAZL where the central link is unidirectional, that is collisions can happen between messages going from $c_s$ to $c_t$ and messages  going from $c_t$ to $c_s$.
-This problem can be shown to be $\NP$-complete by a reduction from the subset sum problem as it is done for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
-We conjecture that the problem PAZL is also $\NP$-complete,  but we have yet not been able to prove it.
-  On the other hand we show positive results:  when the period is large or when the routes are short there is always a solution to PAZL and it can be found in polynomial time.
+       We were not able to prove that PAZL is $\NP$-hard and we leave this question open for further work. 
+       It seems very likely to be hard, since a variant of PAZL where the central link is unidirectional (collisions can happen between forward and backward routes) can be shown to be $\NP$-complete.
+It is done by a reduction from the subset sum problem as for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
+
+% %        We conjecture that the problem PAZL is also $\NP$-complete,  but we have yet not been able to prove it.
+%   On the other hand we show positive results:  when the period is large or when the routes are short there is always a solution to PAZL and it can be found in polynomial time.
 We then give an exponential time exhaustive search algorithm which always finds a solution if there is one.
@@
 
-  \subsection{Algorithms}
-
-  In this subsection, we deal with the problem PAZL.  
-  When the waiting times are zero, $MT({\cal M})$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
-For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ to $m_{\rho(r)} = m_{r} + \lambda(r) \mod P$.
-  Consider an assignment $(m_0,\dots,m_{n-1})$ of a star routed network and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
-  Then $\{m_0',\dots,m_{n-1}'\}$ is an assignment of the same star routed network where the weights of the arcs from $s_i$ to $c_s$ are $0$ for all $i$.
+  In this section, we deal with the problem PAZL on star routed networks.
+Since we want an assignment with waiting times zero, $MT({\cal M})$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
+Moreover choosing the offset $m_r$ of a forward route $r$ also sets the offset of the backward route $\rho(r)$ to $m_{\rho(r)} = m_{r} + \lambda(r) \mod P$.
+Consider an assignment $m$ of a star routed network and let $m'_r= m_{r} - t(c_s,r) \mod P$.
+  Then $m'$ is an assignment of the same star routed network where, for all $i$, the weights of the arcs from $s_i$ to $c_s$ are set to $0$.
 Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
 
-    \subsubsection*{Shortest-longest policy}
+\subsection{Shortest-longest policy}
 
@@
     The messages are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
-    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{i}$ the offset of $r_i$ to $i\tau$. We call this algorithm {\bf Shortest-Longest}.
+    In other words, we assume that the route $r_i$ are sorted by increasing $\lambda(r_i)$ and we set $m_{r_i}$ the offset of $r_i$ to $i\tau$. We call this algorithm {\bf Shortest-Longest}.
 
@@
       \begin{proof}
-       Since $m_{s_i} = i\tau$, $[t(c_s,r_{i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.
+       Since $m_{r_i} = i\tau$, $[t(c_s,r_{i})] = \{i\tau,\dots, (i+1)\tau -1\}$ and there are no collision on the forward period.
 
@@
 
-    \subsubsection*{Greedy algorithm}
+    \subsection{Greedy algorithm}
+
+    \todo{Introduire la load là et faire un théorème avec ce paramètre ?}
 
@@
     \begin{proof}
-     We consider the forward period and cut it into consecutive interval of size $\tau$ that we call macro-slots.
+     We consider the forward period and cut it into consecutive intervals of size $\tau$ that we call macro-slots.
 The algorithm works by choosing an offset for each route in the following way: try all offsets which put the message in a yet not used macro-slot in the forward
      period.
-The choice of an offset also fixes the position of the message in the backward period, chose the first one which does not create a collision.
+Since the choice of an offset also fixes the position of the message in the backward period, chose the first one which does not create a collision.
 We now prove that this algorithm always finds a $(P,\tau)$-periodic assignment without waiting time when $P \geq 3n\tau$.
@@
 In fact, experimental data in Subsection~\ref{sec:exp_PAZL} suggests that the algorithm finds a solution on average when $P \geq 2 n\tau$.
-Note that we also experimented with other greedy algorithms which do not use macro-slots, they work even better in practice but their theoretical upper bound is worse.
-
-\subsection*{An FPT algorithm}
+Note that we have experimented with other greedy algorithms which do not use macro-slots, they work even better in practice but their theoretical upper bound is worse.
+
+\subsection{An FPT algorithm}
 
@@
 We use that to provide an algorithm which always finds an assignment if there is some, in fixed parameter tractable (FPT) time with parameter $n$ the number of routes (for more on parametrized complexity see~\cite{downey2012parameterized}).
-This is justified since $n$ is small in practice and the period $P$ is large.
+This is justified since $n$ is small in practice and the other parameters such as $P$, $\tau$ or the weights are large.
 

### 2017-07-20 infocom/infocom.tex
figures

--- 2017-07-20 infocom/infocom.tex
@@
 
-  \Edge[label = $\omega(s_1\,c_s)$](s1)(cs)
-  \Edge[label = $\omega(...)$](s2)(cs)
-  \Edge[label = $\omega(...)$](s3)(cs)
-
-  \Edge[label = $\omega(...)$](ct)(t1)
-  \Edge[label = $\omega(...)$](ct)(t2)
-  \Edge[label = $\omega(...)$](ct)(t3)
+  \Edge[label = $\omega({s_0,c_s})$](s1)(cs)
+  \Edge[label = $\omega({s_1,c_s})$](s2)(cs)
+  \Edge[label = $\omega({s_2,c_s})$](s3)(cs)
+
+  \Edge[label = $\omega({c_t,t_0})$](ct)(t1)
+  \Edge[label = $\omega({c_t,t_1})$](ct)(t2)
+  \Edge[label = $\omega({c_t,t_2})$](ct)(t3)
 
@@
 In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots.
-We fixed a period of $n\tau+1000$.
+We fixed a period of $1.05n\tau$, which corresponds to $95\%$ of load.
 %       , that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
-      The following table shows the time before the exhaustive search ends, for $6$ to $21$ routes, averaged on $100$ random star routed networks.
-This shows that for less than $20$ routes, which corresponds to all current topologies, the algorithm is efficient enough, but on more routes we should improve it further.
+      The following table shows the time before the exhaustive search ends, for $8$ to $16$ routes, averaged on $100$ random star routed networks.
+This shows that for less than $15$ routes, which corresponds to all current topologies, the algorithm is efficient enough, but on more routes we should improve it further.
          \begin{center}
@@
     \hline
-   $n$ & $6$ & $11$& $16$& $21$\\
+   $n$ & $8$ & $10$& $12$& $16$\\
     \hline
-   Time (s) & $3.10^{-5}$&$6.10^{-4}$&$6.10^{-2}$& $15$\\
+   Time (s) & $6.10^{-5}$&$8.10^{-4}$&$2.10^{-2}$& $15$\\
     \hline
@@
       \end{center}
-
          \section{Solving PALL on Star Routed Networks}\label{sec:PALL}

### 2017-07-20 code/Sources/main.c

@@ -78,7 +78,7 @@ int main()
 	/****Nombre de routes pouvant être calculées en moins de "max" ms
 	****/
 
-	search_efficiency(2500,20000,10);
+	search_efficiency(2500,20000,100);
 
 
 	/******

### 2017-07-20 code/Sources/simulations.c

@@ -499,7 +499,7 @@ void search_efficiency(int taille_message,int taille_routes, int nb_simuls)
 	double average=0;
 	double max = 0.0;
 	double result;
-	for(int nb_routes = 1;nb_routes<25;nb_routes+=1)
+	for(int nb_routes = 1;nb_routes<=16;nb_routes+=1)
 	{
 		max = 0.0;
 		for(int i=0;i<nb_simuls;i++)

### 2017-07-20 infocom/infocom.tex
temps 16 routes
figures vspace
trois modifs en relisant

@@
       Let $r$ be a route, if a message is sent at time $m$ from $s$ the first vertex of $r$ then it will arrive at vertex $v$ in $r$ at time $m + \lambda(v,r)$.
-Since the process is periodic, if we look at the messages going through an arc between time $0$ and $P-1$, then we would observe the same messages in the same order and position between time $kP$ and $(k+1)P -1$ for all $k$.
+Since the process is periodic, if we look at the messages going through an arc between time $0$ and $P-1$, then we see the same messages in the same order and position between time $kP$ and $(k+1)P -1$ for all $k$.
       Therefore, the first time slot at which a message sent at time $m$ on $r$ reaches a vertex $v$ in $r$ is $t(v,r) = m + \lambda(v,r) \mod P$.
@@
 
-Finally, there was no collisions between routes at the beginning and since we modify $\mathcal{M}$ only if it creates no collision, the assignment we obtain at the end has no collisions between routes.
+Finally, there is no collisions between routes at the beginning and since we modify $\mathcal{M}$ only if it creates no collision, the assignment we obtain at the end has no collisions between routes.
 \end{proof}
@@
 on $n$ the number of routes which proves the theorem. 
-We give a way to build a compact assignment $\mathcal{M}$ by determining its offsets one after the other. We fix an arbitrary total order on ${\cal R})$.
+We give a way to build a compact assignment $\mathcal{M}$ by determining its offsets one after the other. We fix an arbitrary total order on ${\cal R}$.
 First a route $r_0$ is chosen arbitrarily and its offset set to $0$. 
@@
 not use route $r$. At a given step of the algorithm, if $|S| = 2i$, we have $n-i$ choices 
-of routes to select and the value of the offset is determined by the values of the offsets of routes in $S$. Therefore there at most $n!$ different compact assignments with offset $r_0$
-fixed to $0$.
-
-An algorithm to solve PALL build every possible compact assignment as described here, and
-test at each step whether there is a collision which can be done in time linear in the size of 
+of routes to select.
+The value of the offset of the selected route is entirely determined by the values of the offsets of routes in $S$.
+Therefore there are at most $n!$ different compact assignments with offset $r_0$ fixed to $0$.
+
+The algorithm to solve PALL builds every possible compact assignment as described here, and
+tests at each step whether there is a collision which can be done in time linear in the size of 
 $(G, {\cal R})$. Therefore $PALL \in \FPT$.
@@
 
-We call the algorithm described in Theorem~\ref{th:FPT} \textbf{Exhaustive Search of Compact Assignments (ESCA)}. To make it more efficient in practice, we make cuts in the search tree 
-used to explore all compact assignments.
+We call the algorithm described in Theorem~\ref{th:FPT} \textbf{Exhaustive Search of Compact Assignments}.
+To make it more efficient in practice, we make cuts in the search tree used to explore all compact assignments.
 Consider a set of $k$ forward routes whose offsets has been fixed at some point in the search tree.
@@
 It divides the period into $[(a_0,b_0), \dots, (a_{k-1},b_{k-1})]$ such that the central arc is free only during the intervals $(a_i,b_i)$.
-Therefore at most $\displaystyle{ \sum_{i=0}^{k} \lfloor(b_{i} -a_i)/\tau\rfloor} $ forward routes can still use the central arc.
+Therefore at most $\displaystyle{ \sum_{i=0}^{k-1} \lfloor(b_{i} -a_i)/\tau\rfloor} $ forward routes can still use the central arc.
 If this value is more than $n - k$, it is not possible to create a compact assignment by extending the one on $S$ and we backtrack in the search tree.
@@
 
+      \todo{présenter ça comme une average load ?}
+
       \begin{figure}
@@
       \end{center}
+            \vspace{-1cm}
       \caption{Minimum period averaged over $1000$ random instances}
@@
       \end{center}
+            \vspace{-1cm}
       \caption{Success rate for $8$ routes over $1000$ random instances}
@@
     \hline
-   Time (s) & $6.10^{-5}$&$8.10^{-4}$&$2.10^{-2}$& $15$\\
+   Time (s) & $6.10^{-5}$&$8.10^{-4}$&$2.10^{-2}$& $11$\\
     \hline
@@
       \end{center}
+
          \section{Solving PALL on Star Routed Networks}\label{sec:PALL}
@@
 
-     \begin{algorithm}[H]
+     \begin{algorithm}
     \caption{ Greedy deadline ({\bf GD}) }
@@
           \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
-          \vspace{-1cm}
+          \vspace{-1.5cm}
       \caption{Success rate of different orders, $80\%$ load.}
@@
       \end{center}
+            \vspace{-1cm}
       \caption{Success rate of GD, MLS and PMLS for $P = 21000$}
@@
 
-    \begin{figure}[H]
+    \begin{figure}
 
        \begin{center}
-      \includegraphics[width = 0.5\textwidth]{stochastic.pdf}
+     \hspace{-0.5cm} \includegraphics[width = 0.5\textwidth]{stochastic.pdf}
        %\input{figures/stochastic}
       \end{center}
+      \vspace{-1cm}
       \caption{Needed margin with respect to the period for a stochastic policy}

### 2017-07-21 infocom/infocom.tex
figures reduites

@@
        \begin{center}
-	 \scalebox{0.8}{
+	 \scalebox{0.6}{
 \begin{tikzpicture}
@@
 We do the same cut for the backward routes.
-
-% 
 % 	\subsubsection*{Exhaustive search}
@@
 A last cut could be implemented: compute for every route not in $R(S)$ the set of possible positions in the backward period and verify whether at least one is contained in the useful slots of $S$.
-
     \subsection{Experimental evaluation}\label{sec:exp_PAZL}
-
       The following experimental results compare the three presented algorithms.
@@
 
-      \begin{figure}
+      \begin{figure}[H]
 
       \begin{center}
-	 \hspace{-0.5cm}\includegraphics[width=0.53\textwidth]{periode_petite.pdf}
+	 \hspace{-0.5cm}\includegraphics[width=0.315\textwidth]{periode_petite.pdf}
       \end{center}
@@
 
-\begin{figure}
+\begin{figure}[H]
 
        \begin{center}
-      \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{echec_longues.pdf}
+      \hspace{-0.5cm}\includegraphics[width=0.3\textwidth]{echec_longues.pdf}
       \end{center}
@@
 %     \end{algorithm}
-
     \subsection{Experimental evaluation}
     \label{sec:resultsPALL}
-
     In this section, we first try to understand what is the best choice of order for the first stage of the algorithm.
@@
 
-\begin{figure}[H]
-
+\begin{figure}[] 
+    \begin{minipage}[c]{0.2\textwidth}
   \centering
-     \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}
-\vspace{-0.75cm}
+      \includegraphics[width=3.5cm]{departs_gp_21000.pdf}
       \caption{Success rate of different orders, $95\%$ load.}
-          \end{figure}
-          \vspace{-1cm}
-\begin{figure}[H] 
-          \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
-          \vspace{-1.5cm}
+      \end{minipage} \hfill
+        \begin{minipage}[c]{0.2\textwidth}
+          \includegraphics[width=3.5cm]{departs_gp_25000.pdf}
       \caption{Success rate of different orders, $80\%$ load.}
+            \end{minipage} \hfill
                   \label{fig:success30000}
      \end{figure}
+%
+% 
+%\begin{figure}[H] 
+%  
+%  \centering
+%     \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}
+%\vspace{-0.75cm}
+%      \caption{Success rate of different orders, $95\%$ load.}
+%          \end{figure}
+%          \vspace{-1cm}
+%\begin{figure}[H] 
+%          \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
+%          \vspace{-1.5cm}
+%      \caption{Success rate of different orders, $80\%$ load.}
+%           \label{fig:success30000}
+%     \end{figure}
 
@@
        \begin{center}
-      \includegraphics[width=0.5\textwidth]{retour_21000.pdf}
+      \includegraphics[width=0.3\textwidth]{retour_21000.pdf}
       \end{center}
@@
        \begin{center}
-     \hspace{-0.5cm} \includegraphics[width = 0.5\textwidth]{stochastic.pdf}
+     \hspace{-0.5cm} \includegraphics[width = 0.3\textwidth]{stochastic.pdf}
        %\input{figures/stochastic}

### 2017-07-21 infocom/infocom.tex
fig 3 4 un peu plus grandes
copie de travail

@@
 
-      In Sec.~\ref{sec:PALL} we will study algorithms which solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity. \todo{phrase utile finalement ?} 
+%       In Sec.~\ref{sec:PALL} we will study algorithms which solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity. \todo{phrase utile finalement ?} 
       It turns out that the problem PALL is hard to solve for \emph{general} routed networks.
@@
 
-       We were not able to prove that PAZL is $\NP$-hard and we leave this question open for further work. 
-       It seems very likely to be hard, since a variant of PAZL where the central link is unidirectional (collisions can happen between forward and backward routes) can be shown to be $\NP$-complete.
+       We were not able to prove that PAZL is $\NP$-hard on star routed networks.
+       We leave this question open for further work and we conjecture that it is hard. 
+       Indeed a variant of PAZL where the central link is unidirectional (collisions can happen between forward and backward routes) can be shown to be $\NP$-complete.
 It is done by a reduction from the subset sum problem as for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
@@
 Consider an assignment $m$ of a star routed network and let $m'_r= m_{r} - t(c_s,r) \mod P$.
-  Then $m'$ is an assignment of the same star routed network where, for all $i$, the weights of the arcs from $s_i$ to $c_s$ are set to $0$.
-Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
+  Then $m'$ is an assignment of the same star routed network where, for all $i$, the weights of the arcs $(s_i,c_s)$ are set to $0$.
+Therefore we assume from now on that the \emph{weight of the arcs $(s_i,c_s)$ are all equal to $0$}.
 
@@
 
-    We first present a simple policy, which works when the period is large with regard to the weight of the routes.
+    We first present a simple policy, which works when the period is large with regard to the lengths of the routes.
     The messages are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
@@
 
-    \todo{Introduire la load là et faire un théorème avec ce paramètre ?}
-
-    We propose a greedy algorithm to build a $(P,\tau)$-periodic assignment, which provably works when
-    the period is large enough with regard to the number of routes and size of messages. In other words, 
-    we can always find a solution when the network is far from saturated.
-This algorithm defines an upper bound for the period.
-As a reminder, the lower bound is $n\tau$, that is, the size taken by the messages to be emitted.
+      We define the \textbf{load} of a star routed network as $\frac{n\tau}{P}$, it is the proportion of time slots used by messages on the central arc in a period.
+Therefore if the load is larger than $1$ there cannot be an assignment.
+We propose a greedy algorithm to build a $(P,\tau)$-periodic assignment, which always finds an assignment when the load is smaller than $1/3$.
+Therefore in the rest of the article we will be only concerned with load larger than $1/3$.
 
     \begin{proposition}
-     Let $(G, {\cal R})$ be a star routed network, and let $ 3n\tau \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which can be found in time $O(n^2)$.
+     Let $(G, {\cal R})$ be a star routed network, if the load is less than $1/3$ then there is a $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which can be found in time $O(n^2)$.
     \end{proposition}
@@
 Since the choice of an offset also fixes the position of the message in the backward period, chose the first one which does not create a collision.
-We now prove that this algorithm always finds a $(P,\tau)$-periodic assignment without waiting time when $P \geq 3n\tau$.
+We now prove that this algorithm always finds a $(P,\tau)$-periodic assignment without waiting time when $P \geq 3n\tau$ that is the load is less than $1/3$.
 
@@
 
-This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
-In fact, experimental data in Subsection~\ref{sec:exp_PAZL} suggests that the algorithm finds a solution on average when $P \geq 2 n\tau$.
+This algorithm, contrarily to the previous one, may work well, even when the condition on the load is not true.
+In fact, experimental data in Subsection~\ref{sec:exp_PAZL} suggests that the algorithm finds a solution when the load is less than $1/2$.
 Note that we have experimented with other greedy algorithms which do not use macro-slots, they work even better in practice but their theoretical upper bound is worse.
@@
 
-In this section we show how every assignment without waiting time can be put in a canonical form.
-We use that to provide an algorithm which always finds an assignment if there is some, in fixed parameter tractable (FPT) time with parameter $n$ the number of routes (for more on parametrized complexity see~\cite{downey2012parameterized}).
+In this section we show how every assignment without waiting time can be put into a canonical form.
+We use that to provide an algorithm which finds an assignment when it exists, in fixed parameter tractable time ($\FPT$) with parameter $n$ the number of routes (for more on parametrized complexity see~\cite{downey2012parameterized}).
 This is justified since $n$ is small in practice and the other parameters such as $P$, $\tau$ or the weights are large.
 
-Let $(G, {\cal R})$ be a star routed network and $\mathcal{M}$ a $(P,\tau)$-periodic assignment.
+Let $(G, {\cal R})$ be a star routed network and $m$ a $(P,\tau)$-periodic assignment.
 A set of routes $S$ is \textbf{coherent} if for all $r \in {\cal R}$, $r \in S$ if and only if $\rho(r) \in S$.
-We say that a coherent set $S \subseteq {\cal R}$ is \textbf{compact} for the assignment $\mathcal{M}$ if there is a route $r_0 \in S$ such that the following holds:
+We say that a coherent set $S \subseteq {\cal R}$ is \textbf{compact} for the assignment $m$ if there is a route $r_0 \in S$ such that the following holds:
 for all coherent subsets $S'\subset S$ with $r_0 \notin S'$, if we remove $1$ from all offsets of routes in $S'$ then there is a collision with a route of $S \setminus S'$.
-We say that $\mathcal{M}$ is compact if ${\cal R}$ is compact for $\mathcal{M}$.
+We say that $m$ is compact if ${\cal R}$ is compact for $m$.
 % 
@@
 \begin{proof}
-Consider $\mathcal{M}$ a $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
-Let $r_0$ be an arbitrary route of ${\cal R}$,  and let $COMP = \{r_0\}$. Now we apply the following algorithm to $\mathcal{M}$ and $COMP$ while $COMP$ is not equal to ${\cal R}$.
+Consider $m$ a $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
+Let $r_0$ be an arbitrary route of ${\cal R}$,  and let $COMP = \{r_0\}$. Now we apply the following algorithm to $m$ and $COMP$ while $COMP$ is not equal to ${\cal R}$.
 While there is no collision, remove $1$ (modulo $P$) from all offsets of routes in ${\cal R} \setminus COMP$.
@@
 
-We prove by induction that $COMP$ is compact for $\mathcal{M}$ at every step of the algorithm.
+We prove by induction that $COMP$ is compact for $m$ at every step of the algorithm.
 At the beginning $|COMP| = 1$ and the property is trivially satisfied. Then we assume that 
@@
 
-Finally, there is no collisions between routes at the beginning and since we modify $\mathcal{M}$ only if it creates no collision, the assignment we obtain at the end has no collisions between routes.
+Finally, there is no collisions between routes at the beginning and since we modify $m$ only if it creates no collision, the assignment we obtain at the end has no collisions between routes.
 \end{proof}
@@
 \begin{proof}
-Let $(G, {\cal R})$ be a star routed network and let $\mathcal{M}$ be a $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
+Let $(G, {\cal R})$ be a star routed network and let $m$ be a $(P,\tau)$-periodic assignment of $(G, {\cal R})$.
 First remark that for a given assignment and a route $r_0$ with offset $m$, by removing $m$ to all offsets, we can always assume that its offset is zero.
@@
 on $n$ the number of routes which proves the theorem. 
-We give a way to build a compact assignment $\mathcal{M}$ by determining its offsets one after the other. We fix an arbitrary total order on ${\cal R}$.
+We give a way to build a compact assignment $m$ by determining its offsets one after the other. We fix an arbitrary total order on ${\cal R}$.
 First a route $r_0$ is chosen arbitrarily and its offset set to $0$. 
@@
 Then we select a route in $r' \in {\cal R} \setminus S$ and set its offset such that 
-if we remove $1$ then $r'$ collides with $r$. Note that if $r$ is a forward route (resp. a backward route) then $r'$ is also a forward route (resp. a backward route). We can also decide to 
-not use route $r$. At a given step of the algorithm, if $|S| = 2i$, we have $n-i$ choices 
+if we remove $1$ then $r'$ collides with $r$.
+Note that if $r$ is a forward route (resp.
+a backward route) then $r'$ is also a forward route (resp.
+a backward route).
+We can also decide to definitly skip $r$.
+At a given step of the algorithm, if $|S| = 2i$, we have $n-i$ choices
 of routes to select.
@@
 Therefore at most $\displaystyle{ \sum_{i=0}^{k-1} \lfloor(b_{i} -a_i)/\tau\rfloor} $ forward routes can still use the central arc.
-If this value is more than $n - k$, it is not possible to create a compact assignment by extending the one on $S$ and we backtrack in the search tree.
-We do the same cut for the backward routes.
+If this value is less than $n - k$, it is not possible to create a compact assignment by extending the one on $S$ and we backtrack in the search tree.
+The same cut is used for the backward routes.
 % 	\subsubsection*{Exhaustive search}
@@
       The following experimental results compare the three presented algorithms.
-      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithm but are not always able to find a solution, depending on $P$, $\tau$, $n$ and the size of the routes.
+      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithms but are not always able to find a solution, depending on the load or the size of the routes.
 On the other hand, the exhaustive search finds an optimal solution if it exists, but works in exponential time.
 We compare the performance of the algorithms in two different regimes: routes are either short with regard to $\tau$, or unrestricted.
-      From our C-RAN context we choose the following parameters: the number of routes 
-      is at most $n = 20$, $\tau$ is equal to $2500$.
-Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.
+      From our C-RAN context we choose the following parameters: the number of routes is at most $n = 20$, $\tau$ is equal to $2500$.
+%       Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.
 
@@
 
-      We define the load of the network as $\frac{n\tau}{P}$ (here a value between one and three),
-      it is the proportion of time slots used by messages on the central arc.
        In our experiments we will try to understand how our algorithms work with regards to the load.
@@
 
-      First we consider routes which are shorter than $\tau$, that is a message cannot be contained completely in a single arc which is very common for our application.
-We generate star routed networks in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ slots.
-It corresponds to messages of approximately $1$Mb, links of bandwidth $10$Gbps and length less than $5$km between the BBU and the RRH.
-
-      Our aim is to understand how well the algorithms are working under high load.
-To do that we try to evaluate the minimal period (that is the highest possible load) for which a $(P,\tau)$-periodic assignment can be found by each algorithm.
-%       To that end we use a linear search on $P$, since a dichotomy method would not work because of Lemma~\ref{lemma:monotonic}.
-
-      In our experiment, we generate $1000$ random instances of PAZL for $1$ to $12$ routes. 
-      We measure the average minimal period, for each algorithm.
-Remind that the exhaustive search always finds the best possible period for a given instance.
-The lower and upper bound $n\tau$ and $3n\tau$ are also represented.
-
-      \todo{présenter ça comme une average load ?}
+      First we consider routes which are shorter than $\tau$: a message cannot be contained completely in a single arc which is very common for our applications.
+We generate star routed networks in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$.
+It corresponds to messages of approximately $1$Mb, links of bandwidth $10$Gbps and length of routes less than $5$km between the BBU and the RRH.
+
+      Our aim is to understand how well the algorithms are working under high load. To do that we evaluate the highest load 
+      under which a $(P,\tau)$-periodic assignment can be found by each algorithm when we change the number of routes. 
+      In our experiment, we generate $1000$ random instances of PAZL for $1$ to $15$ routes.
+We measure the average maximal possible load, for which each algorithm finds a solution.
+Remind that the exhaustive search always finds the highest load for a given instance.
+%       The lower and upper bound $n\tau$ and $3n\tau$ are also represented.
 
@@
       \end{center}
-            \vspace{-1cm}
+            \vspace{-0.75cm}
       \caption{Minimum period averaged over $1000$ random instances}
@@
 \begin{figure}[]
+
 \begin{minipage}[c]{0.2\textwidth}
-  \centering
-      \includegraphics[width=3.5cm]{departs_gp_21000.pdf}
+
+      \includegraphics[width=4.5cm]{departs_gp_21000.pdf}
       \caption{Success rate of different orders, $95\%$ load.}
+
       \end{minipage} \hfill
         \begin{minipage}[c]{0.2\textwidth}
-          \includegraphics[width=3.5cm]{departs_gp_25000.pdf}
+          \includegraphics[width=4.5cm]{departs_gp_25000.pdf}
      \caption{Success rate of different orders, $80\%$ load.}

### 2017-07-21 infocom/infocom.tex
debut aprem

--- 2017-07-20 infocom/infocom.tex
@@
 \newcommand{\todo}[1]{{\color{red} TODO: {#1}}}
-
+\newcommand\pazl{\textsc{pazl}\xspace}
+\newcommand\pall{\textsc{pall}\xspace}
 %opening
-\title{Deterministic Scheduling of Periodic Messages by an SDN Approach}
+\title{Deterministic Scheduling of Periodic Messages for Cloud RAN}
 
@@
 A recent trend in mobile networks is to centralize the processing units which were attached to 
-antennas in distant data-centers. The main challenge is to guarantee that the latency of the periodic messages 
-sent from the antennas to their processing units and back is minimal. We show that traditional statistical multiplexing
+antennas in distant data-centers. The main challenge is to guarantee the maximum latency of the periodic messages 
+sent from the antennas to their processing units and back. We show that traditional statistical multiplexing
 is bad at ensuring a low latency.
@@
 and some buffering is allowed in the processing units, we propose an algorithm (PMLS) adapted from a classical scheduling method.
-The experimental results shows that even under full load, most of the time PMLS finds a deterministic sending scheme with no latency.
+The experimental results show that even under full load, most of the time PMLS finds a deterministic sending scheme with no latency.
 \end{abstract}
@@
  and we introduce the star routed network we study in this article. 
- We formalize the problem of finding a periodic assignment for sending messages without buffering (PAZL) or
- with buffering in the processing unit only (PALL) and shows that they are $\NP$-hard even to approximate.
-In Sec.~\ref{sec:PAZL}, we propose two algorithms solving PAZL when the routes between RRHs and BBUs are small
-or when the load is light. Using a compact representation of an assignment, we show that PAZL is fixed parameter tractable when parametrized by the number of antenna on star routed networks.
-Finally in Sec.~\ref{sec:PALL}, we introduce a family of algorithms to solve PALL and our experimentation 
+ We formalize the problem of finding a periodic assignment for sending messages without buffering (\pazl) or
+ with buffering in the processing unit only (\pall) and shows that they are $\NP$-hard even to approximate.
+In Sec.~\ref{sec:PAZL}, we propose two algorithms solving \pazl when the routes between RRHs and BBUs are small
+or when the load is light. Using a compact representation of an assignment, we show that \pazl is fixed parameter tractable when parametrized by the number of antenna on star routed networks.
+Finally in Sec.~\ref{sec:PALL}, we introduce a family of algorithms to solve \pall and our experimentation 
 allows to select one which works extremely well even in very loaded networks.
@@
 The network is modeled as a directed graph $G=(V,A)$.
-Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time taken by a signal to go from $u$ to $v$ using this arc.
+Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time taken by a message to go from $u$ to $v$ using this arc.
 A {\bf route} $r$ in $G$ is a path, that is, a sequence of adjacent vertices $u_0, \ldots , u_{k}$, with $(u_i,u_{i+1}) \in A$.
@@
 
+      \subsection{Periodic assignment for low latency}
+
+    The {\bf maximum process time} of the assignment ${\cal M}$ of $(G,{\cal R})$ is defined by $MT({\cal M})=\max\limits_{r \in {\cal R}} PT(r)$. We consider the following decision problem.
+
+      \noindent {\bf Periodic Assignment for Low Latency (\pall)}
+
+      \noindent {\bf Input:}  A routed network $(G,{\cal R})$, the integers $P$, $\tau$ and $T_{max}$.
+
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment ${\cal M}$ of $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
+
+      In Sec.~\ref{sec:PALL} we will study algorithms which solve the search version of \pall (computing an assignment), also denoted by \pall for simplicity. \todo{phrase utile finalement ?} 
+      It turns out that the problem \pall is hard to solve for \emph{general} routed networks.
+The long version of this article contains complete proofs of the $\NP$-hardness or hardness of approximation of \pall and of several of its variants.
+
+ \begin{theorem}
+Problem \pall is $\NP$-complete.
+\end{theorem}
+
+\noindent \emph{Sketch of proof:}
+ We first show that finding an assignment for the forward routes only with no collisions 
+ can be reduced to \pall by a symmetry argument.
+ We fix $\tau$ the size of messages to $1$ and we reduce the problem of $k$-coloring to the 
+ problem of finding an assignment without collisions for the forward routes.
+ Let $H$ be a graph instance of the $k$-coloring problem, the reduction is as follows. 
+ For each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
+Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an arc in $H$; this arc is the only one shared by these two routes.
+All arcs are of weight $0$.
+ Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic assignment in $G$, 
+ by converting an offset of a route into a color of a vertex and reciprocally. \qed
+
+       We consider a simpler version of \pall, that we call {\bf Periodic Assignment for Zero Latency} or \pazl: we ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$}.
+We introduce \pazl because it is simpler to study and we are able to prove theoretical results and find better algorithms than for \pall.
+Moreover, as we show in our experimentations of Sec.\ref{sec:exp_PAZL}, this problem can often be solved positively (albeit less often than the general problem).
+Finally, a solution to \pazl is simpler to implement in real telecommunication networks, since we do not need to implement any buffering at all.
+
+       We were not able to prove that \pazl is $\NP$-hard and we leave this question open for further work. 
+       It seems very likely to be hard, since a variant of \pazl where the central link is unidirectional (collisions can happen between forward and backward routes) can be shown to be $\NP$-complete.
+It is done by a reduction from the subset sum problem as for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
+
     \subsection{The star routed network}
@@
   \end{center}
+
+  Even if this topology seems really basics, it's already complex to find some solutions for \pazl and \pall on it.
+Also, a star routed network corresponds to a Point-to-Multipoint fronthaul (PtMP), intended for C-RAN \cite{tayq2017real}.
 
@@
 %\end{proof}
-
-      \subsection{Periodic assignment for low latency}
-
-    The {\bf maximum process time} of the assignment ${\cal M}$ of $(G,{\cal R})$ is defined by $MT({\cal M})=\max\limits_{r \in {\cal R}} PT(r)$. We consider the following decision problem.
-
-      \noindent {\bf Periodic Assignment for Low Latency (PALL)}
-
-      \noindent {\bf Input:}  A routed network $(G,{\cal R})$, the integers $P$, $\tau$ and $T_{max}$.
-
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment ${\cal M}$ of $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
-
-      In Sec.~\ref{sec:PALL} we will study algorithms which solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity. \todo{phrase utile finalement ?} 
-      It turns out that the problem PALL is hard to solve for \emph{general} routed networks.
-The long version of this article contains complete proofs of the $\NP$-hardness or hardness of approximation of PALL and of several of its variants.
-
- \begin{theorem}
-Problem PALL is $\NP$-complete.
-\end{theorem}
-
-\noindent \emph{Sketch of proof:}
- We first show that finding an assignment for the forward routes only with no collisions 
- can be reduced to PALL by a symmetry argument.
- We fix $\tau$ the size of messages to $1$ and we reduce the problem of $k$-coloring to the 
- problem of finding an assignment without collisions for the forward routes.
- Let $H$ be a graph instance of the $k$-coloring problem, the reduction is as follows. 
- For each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
-Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an arc in $H$; this arc is the only one shared by these two routes.
-All arcs are of weight $0$.
- Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic assignment in $G$, 
- by converting an offset of a route into a color of a vertex and reciprocally. \qed
-
-       We consider a simpler version of PALL, that we call {\bf Periodic Assignment for Zero Latency} or PAZL: we ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$}.
-We introduce PAZL because it is simpler to study and we are able to prove theoretical results and find better algorithms than for PALL.
-Moreover, as we show in our experimentations of Sec.\ref{sec:exp_PAZL}, this problem can often be solved positively (albeit less often than the general problem).
-Finally, a solution to PAZL is simpler to implement in real telecommunication networks, since we do not need to implement any buffering at all.
-
-       We were not able to prove that PAZL is $\NP$-hard and we leave this question open for further work. 
-       It seems very likely to be hard, since a variant of PAZL where the central link is unidirectional (collisions can happen between forward and backward routes) can be shown to be $\NP$-complete.
-It is done by a reduction from the subset sum problem as for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
 
@@
 
-\section{Solving PAZL on Star Routed Networks} \label{sec:PAZL}
-
-  In this section, we deal with the problem PAZL on star routed networks.
+\section{Solving \pazl on Star Routed Networks} \label{sec:PAZL}
+
+  In this section, we deal with the problem \pazl on star routed networks.
 Since we want an assignment with waiting times zero, $MT({\cal M})$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
@@
 \begin{theorem}\label{th:FPT}
-$PALL \in \FPT$ when parametrized by the number of routes.
+$\pall \in \FPT$ when parametrized by the number of routes.
 \end{theorem}
@@
 
-The algorithm to solve PALL builds every possible compact assignment as described here, and
+The algorithm to solve \pall builds every possible compact assignment as described here, and
 tests at each step whether there is a collision which can be done in time linear in the size of 
-$(G, {\cal R})$. Therefore $PALL \in \FPT$.
+$(G, {\cal R})$. Therefore $\pall \in \FPT$.
 \end{proof}
@@
 
-      In our experiment, we generate $1000$ random instances of PAZL for $1$ to $12$ routes. 
+      In our experiment, we generate $1000$ random instances of \pazl for $1$ to $12$ routes. 
       We measure the average minimal period, for each algorithm.
@@
 The lower and upper bound $n\tau$ and $3n\tau$ are also represented.
-
       \todo{présenter ça comme une average load ?}
-
-      \begin{figure}
-
+      \begin{figure}[h]
       \begin{center}
-	 \hspace{-0.5cm}\includegraphics[width=0.53\textwidth]{periode_petite.pdf}
+	 \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{periode_petite.pdf}
       \end{center}
-            \vspace{-1cm}
+            \vspace{-0.75cm}
       \caption{Minimum period averaged over $1000$ random instances}
       \end{figure}
-
       First, we remark that the period found by the exhaustive search is only very slightly above the lower bound of $n\tau$, which means that, in this regime, it is very well justified to look for a solution without waiting time even for a highly loaded network.
@@
       When the load is larger than $50\%$ (period less than $40000$), the exhaustive search finds  more solutions than the greedy algorithms which justifies its use.
-However, for load larger than $80\%$ (period less than $25000$) there are many instances for which there are no solutions to PAZL.
+However, for load larger than $80\%$ (period less than $25000$) there are many instances for which there are no solutions to \pazl.
       It means that with long routes and high load, looking for an assignment without waiting time is far too restrictive.
-That is why we present algorithms for the general PALL problem in our next section.
+That is why we present algorithms for the general \pall problem in our next section.
 We will test them on $8$ long routes and a load between $100\%$ and $80\%$ for which, as shown here, there are often no assignment without waiting times.
@@
 
-         \section{Solving PALL on Star Routed Networks}\label{sec:PALL}
-
-    In this section, we still work on star routed networks, but we consider again the more general PALL problem.
+         \section{Solving \pall on Star Routed Networks}\label{sec:PALL}
+
+    In this section, we still work on star routed networks, but we consider again the more general \pall problem.
 It means that the messages can wait in the target vertices (BBUs) in order to find solutions when there are none without waiting time.
@@
 
-	Often in real networks, the length of the routes are not arbitrary and we may exploit that to solve PALL easily.
+	Often in real networks, the length of the routes are not arbitrary and we may exploit that to solve \pall easily.
 For instance if all the weights on the arcs $(c_t,t_i)$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.
@@
 
-    We can decompose any algorithm solving the PALL problem in two parts: first set the offsets of the forward routes and then, knowing this information set the offset of the backward routes or equivalently the waiting times.
+    We can decompose any algorithm solving the \pall problem in two parts: first set the offsets of the forward routes and then, knowing this information set the offset of the backward routes or equivalently the waiting times.
     The offsets of the forward routes are chosen so that messages have no collision on the central arc and such that there are no free slots in between the end of a message on the central arc and the beginning of the next one.
@@
 \begin{figure}[H] 
-          \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
-          \vspace{-1.5cm}
+          \includegraphics[width=0.4\textwidth]{departs_gp_25000.pdf}
+          \vspace{-0.5cm}
       \caption{Success rate of different orders, $80\%$ load.}
@@
      The random order is the best by far. When the load is not too high ($P = 30000$) there is always a solution with margin $0$.
-     Note that, when disallowing waiting times, there were instances without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the PALL problem.
+     Note that, when disallowing waiting times, there were instances without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the \pall problem.
 We now want to compare the performances of the three different algorithms used in the second stage.
@@
 We represent the success rate with regards to the margin, for the three algorithms computed over $10000$ random star routed networks.
-
     \begin{figure} [H] 
+      \vspace{-0.5cm}
        \begin{center}
@@
      \label{fig:success21000}
+       \vspace{-0.2cm}
      \end{figure}
-
      The MLS algorithm performs poorly, worst than GD and PMLS, which shows that taking into account the periodicity is fundamental.
@@
 The following tables presents the average success rate for each number of sending orders, on $1000$ instances, for GD and PMLS.
-
          \begin{figure}[H] 
@@
      \end{figure}
-
 First remark that we can improve our previous results by taking $10000$ random orders, which 
@@
 
-     Now that we have found the best amongst the algorithms solving PALL, we need to compare its performances against the actual way to manage the messages in a network.
+     Now that we have found the best amongst the algorithms solving \pall, we need to compare its performances against the actual way to manage the messages in a network.
 The classical way to manage messages in the network is statistical multiplexing, where there is a FIFO buffer in each node of the network to deal with the collisions.

### 2017-07-21 infocom/infocom.tex

@@
 \begin{abstract}
-A recent trend in mobile networks is to centralize the processing units which were attached to 
-antennas in distant data-centers. The main challenge is to guarantee the maximum latency of the periodic messages 
-sent from the antennas to their processing units and back. We show that traditional statistical multiplexing
-is bad at ensuring a low latency.
-Hence, we propose in this article to use a deterministic scheme to send periodic messages without collisions in the network and thus without buffering and additional latency.
+A recent trend in mobile networks is to centralize in distant data-centers the processing units which were attached to 
+antennas. The main challenge is to guarantee that the latency of the periodic messages sent from the antennas to their processing
+units and back fulfills protocol time constaints.
+We show that traditional statistical multiplexing does not allow such a low latency, due to collisions and buffering at nodes.
+Hence, we propose in this article to use a deterministic scheme for sending periodic messages without collisions in the network thus without buffering and the resulting additional latency.
 We give several algorithms to compute such schemes for a common topology where one link is shared by all antennas.
-We show that there is always a solution when the routes are small or the load is small. When the parameters are unconstrained,
+We show that there is always a solution when the routes are short or the load is small. When the parameters are unconstrained,
 and some buffering is allowed in the processing units, we propose an algorithm (PMLS) adapted from a classical scheduling method.
@@
 The latency is measured between the sending of a message by the Remote Radio Heads (RRHs) on the field and the receptions of the answers, computed by real-time virtualized network functions on Baseband Units (BBUs), in the cloud.
-For example, even if next radio protocols are less stringent, some standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in $1$ to $10$ms depending on targeted services~\cite{bouguen2012lte}.
+For example, even if next radio protocols are less stringent, some standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in $3$ms~\cite{bouguen2012lte}.
 The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRHs and BBUs.
@@
 
-      In Sec.~\ref{sec:PALL} we will study algorithms which solve the search version of \pall (computing an assignment), also denoted by \pall for simplicity. \todo{phrase utile finalement ?} 
+%       In Sec.~\ref{sec:\pall} we will study algorithms which solve the search version of \pall (computing an assignment), also denoted by \pall for simplicity. \todo{phrase utile finalement ?} 
       It turns out that the problem \pall is hard to solve for \emph{general} routed networks.
@@
 We introduce \pazl because it is simpler to study and we are able to prove theoretical results and find better algorithms than for \pall.
-Moreover, as we show in our experimentations of Sec.\ref{sec:exp_PAZL}, this problem can often be solved positively (albeit less often than the general problem).
+Moreover, as we  experimentally show in Sec.~\ref{sec:exp_PAZL}, this problem can often be solved positively (albeit less often than the general problem).
 Finally, a solution to \pazl is simpler to implement in real telecommunication networks, since we do not need to implement any buffering at all.
 
-       We were not able to prove that \pazl is $\NP$-hard and we leave this question open for further work. 
-       It seems very likely to be hard, since a variant of \pazl where the central link is unidirectional (collisions can happen between forward and backward routes) can be shown to be $\NP$-complete.
-It is done by a reduction from the subset sum problem as for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
-
     \subsection{The star routed network}
 
-             Let us define a family of simple routed networks that we will study in this paper. 
+      Let us define a family of simple routed networks which corresponds to a Point-to-Multipoint fronthaul (PtMP), intended for C-RAN \cite{tayq2017real}. 
       The graph $G$ has two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes, the central source node $c_s$ and the central target node $c_t$.
@@
 All the symmetric arcs are also in the graph with the same weights.
-      The forward routes are the directed paths $r_i = (s_i,c_s,c_t,t_i)$ and the backward routes are $\rho(r_i) = (t_i,c_t,c_s,s_i)$.
+      The forward routes are the directed paths $r_i = (s_i,c_s,c_t,t_i)$ and the backward routes are $\rho(r_i) =(t_i,c_t,c_s,s_i)$.
 The routed network $(G, \{r_i,\rho(r_i)\}_{i<n})$ is called a \textbf{star routed network}.
@@
 
-  Even if this topology seems really basics, it's already complex to find some solutions for \pazl and \pall on it.
-Also, a star routed network corresponds to a Point-to-Multipoint fronthaul (PtMP), intended for C-RAN \cite{tayq2017real}.
-
   Since the central arc appears in every route, its value does not matter when considering the process time of an assignment.
@@
 
-%      
+  Star routed networks seem really simple, but \pall or \pazl may be $\NP$-hard restricted to these networks.
+  We conjecture it is the case since  a variant of \pazl where the central link is unidirectional (collisions can happen between forward and backward routes) can be shown to be $\NP$-complete.
+It is done by a reduction from the subset sum problem as for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
+
 %
@@
 
-% %        We conjecture that the problem PAZL is also $\NP$-complete,  but we have yet not been able to prove it.
-%   On the other hand we show positive results:  when the period is large or when the routes are short there is always a solution to PAZL and it can be found in polynomial time.
-We then give an exponential time exhaustive search algorithm which always finds a solution if there is one.
-
-%      The following table summarize the main notations used in the paper.
-%      \begin{center}
-%   \begin{tabular}{|c|c|}
-%    \hline
-%     $(G,\cal R)$ & Routed network \\
-%     \hline
-%      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
-%      \hline
-%      $\lambda(u_i,r)$ & Latency of the vertex $u_i$ in $r$\\
-%         \hline
-%         $\lambda(r)$ & Length of the route $r$\\
-%         \hline
-%         $P$ & Period\\
-%         \hline
-%         $\tau$ & Size of a message\\
-%         \hline
-%         $ [t(v,r)]$& Set of time slots used by route $r$ at vertex $v$ \\
-%         & in a period $P$\\
-%         \hline 
-%         ${\cal M}=(m_0, \ldots ,m_{n-1})$& Assignment: an offset for each route)\\
-%              \hline 
-%         $w_r$& Waiting time of the route $r$\\
-%            \hline 
-%         $PT(r)$& Process time of the route $r$\\
-%           \hline 
-%         $MT({\cal M})$& Maximum process time of the assignment\\
-%    \hline
-%
-%      \end{tabular}
-%      \end{center}
-
-%
-%\section{Hardness of PRA}
-%  \label{sec:complexity}
-%
-% In this section we always assume that the size of a message $\tau$ is equal to one. 
-% We will prove the hardness of PRA and PALL for $\tau =1$ which implies the hardness of the general problems. 
-%Consider an instance of the problem PRA, i.e., a routed network $(G,\cal{R})$ and a period $P$.
-%The {\bf conflict depth} of a route is the number of arcs of the route which also belong to other routes.
-%The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its routes.
-%The {\bf load} of a routed network is the maximal number of routes sharing the same arc.
-%Remark that a $(P,1)$-periodic assignment must satisfy that $P$ is larger or equal to the load.
-%
-%
-%We give two alternate proofs that PRA is $\NP$-complete.
-%The first proof works already for conflict depth two. Remark that for conflict depth one,
-%the graph can be seen as a set of disjoint pair of routes, on which PRA and PALL can be solved in linear time. 
-% The second proof reduces the problem to graph coloring and implies inapproximability when one tries to find the smallest possible $P$. \\
-% Finally, it is easy to see that PRA is easy on trees and it may be interesting to study its complexity on 
-% bounded treewidth networks, since it is a common property of real networks~\cite{de2011treewidth}.
-% 
-%
-% \begin{theorem}
-%Problem PRA is $\NP$-complete on the class of routed networks with conflict depth two.
-%\end{theorem}
-% \begin{proof}
-% Problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of arcs whether there are collisions.
-% 
-%  Let $H=(V,E)$ be an undirected graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is arc-colorable
-%  with $d$ or $d+1$ colors.
-The arc coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness.
-To do that, we define from $H$ a routed network $(G,{\cal R})$ as follows.
-%  The vertices of $G$ are $v_1, v_2$ for each $v$ in $V$ and $s_{u,v}, t_{u,v}$ for each $(u,v) \in E$.
-%  For each arc $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$. 
-%  
-%   To define ${\cal R}$ an arbitrary orientation of each arc $(u,v)$ is chosen. 
-%   Then for each arc $(u,v)$ there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
-%  All these arcs are of weight $0$. The set of arcs of G is the union between all the arcs of the previously defined routes.
-%   
-%    
-%  Observe that the existence of a $d$-coloring of $H$ is equivalent to the existence of a $(d,1)$-periodic assignment
-%  of $(G,{\cal R})$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its arcs by the integers
-%  in $\{0,\dots,d-1\}$ and we have a bijection between $d$-colorings of $H$ and offsets of the routes of ${\cal R}$.
-%  By construction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent arcs have the same color.
-Therefore we have reduced arc coloring to PRA by a polynomial time transformation which concludes the proof.
-% \end{proof}
-% 
-% Remark that we have used zero weights in the proof. If we ask the weights to be strictly positive, which makes sense in our model since
-%they represent the delay of physical links, it is easy to adapt the proof.
-We just have to set them so that in any route the weight at $u_1$ is equal to $d$ and thus equal to $0$ modulo $d$.
-We now lift this hardness result to the problem PALL.
-%
-%\begin{corollary}
-%Problem PALL is $\NP$-complete on the class of routed networks of conflict depth two.
-%\end{corollary}
-%\begin{proof}
-% We consider $((G,{\cal R}),P,\tau)$ an instance of $PRA$.
-We assume that no vertex is the first of some route and the last of another one.
-Remark that this condition is satisfied in the previous proof, which makes the problem $PRA$ restricted to this kind of instance $\NP$-complete.
-% Let us define $T_{max} = 2 \times \max_{r \in {\cal R}} \lambda(r) + P$.
-We define $(G',{\cal R}')$ a symmetric routed network from $(G,{\cal R})$ where for every route we add a symmetric route with new arcs of opposite orientation and the same weights.
-% We prove that the instance $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL if and only if $((G,{\cal R}),P,\tau)$ is in $PRA$.
-% If $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL, then a $(P,\tau)$-assignment of $(G',{\cal R'})$ restricted to $\R$ is a $(P,\tau)$-assignment of $((G,{\cal R})$ since they cannot be any collision between routes of ${\cal R}$.
-% 
-% Assume now that $((G,{\cal R}),P,\tau)$ is in $PRA$.
-First remark that the waiting time of each route is by definition less than $P$ and thus the maximal process time is always less than $T_{max}$, therefore the constraint on $T_{max}$ is satisfied.
-Moreover a $(P,\tau)$-assignment of $(G,{\cal R})$ can be extended into a $(P,\tau)$-assignment of $(G',{\cal R'})$ in the following way.
-For each route $r \in \cal{R}$ of last vertex $v$, the time at which the message arrives is $t(v,r)$, then we choose as offset for $\rho(r) \in \cal{R}'$ $-t(v,r) \mod P$.
-The symmetry ensures that each new route $\rho(r)$ in ${\cal R'}$ uses exactly the same times slot as $r$ one each of its node and thus avoid collisions.
-%\end{proof}
-%
-%Let MIN-PRA be the problem, given a routed network and an assignment, to find the minimal period $P$ such that there is a $P$-periodic assignment. 
-%
-%\begin{theorem}\label{th:inapprox}
-%If $\P \neq \NP$, problem MIN-PRA on the classes of routed networks of load two cannot be approximated in polynomial time within a factor $n^{1-o(1)}$ where $n$ is the number of routes.
-%\end{theorem}
-%
-%\begin{proof}
-% We reduce graph coloring to PRA. Let $H$ be a graph instance of the $k$-coloring problem. 
-% We define ${\cal R}$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
-% Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an arc in $H$; this arc is the only one shared by these two routes.
-All arcs are of weight $0$.
-Note that it is easy to build a graph with such routes as in Fig.~\ref{fig:reduction}.
-% 
-% Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic assignment in $G$, 
-% by converting an offset of a route into a color of a vertex and reciprocally.
-Therefore if we can approximate the minimum value of $P$ within some factor, we could approximate the minimal number of colors needed to color a graph within the same factor.
-The proof follows from the hardness of approximability of finding a minimal coloring~\cite{zuckerman2006linear}.
-%\end{proof}
-%
-%
-%In particular, this reduction shows that even with small maximal load, the minimal period can be large.
-%
-%    \begin{figure}[ht]
-%    
-%    \hspace{0.5cm}\scalebox{0.35}{
-%    \begin{tikzpicture}
-%    \tikzset{
-%      LabelStyle/.style = { rectangle, rounded corners, draw,
-%			  font = \bfseries },
-%      EdgeStyle/.append style = {->} }
-%      \SetGraphUnit{5}
-%      
-%      
-%      \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
-%      \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
-%      \node[draw,circle] (s1) at (0, 6) {$s_0$}; 
-%
-%      \node[draw,circle] (t3) at (12, 3) {$t_2$}; 
-%      \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
-%      \node[draw,circle] (t1) at (10, 2) {$t_0$}; 
-%      
-%
-%      \tikzstyle{VertexStyle}=[shape = circle, draw, minimum size = 20pt]
-%	\tikzset{
-%      VertexStyle/.append style = {blue} }
-%	\Vertex[x=-8,y=3]{1}
-%	      \tikzset{
-%      VertexStyle/.append style = {green} }
-%	  \Vertex[x=-7,y=5]{2}
-%
-%	    \tikzset{
-%      VertexStyle/.append style = {red} }
-%	  \Vertex[x=-6,y=4]{3}
-%		\tikzset{
-%      VertexStyle/.append style = {black} }
-%      
-%      
-%      \SetVertexNoLabel
-%      \Vertex[x=2,y=5]{A}
-%      \Vertex[x=4,y=5]{B}
-%      \Vertex[x=10,y=5]{C}
-%      \Vertex[x=12,y=5]{D}
-%      \Vertex[x=6,y=3]{E}
-%      \Vertex[x=8,y=3]{F}
-%      \tikzset{
-%      EdgeStyle/.append style = {green} }
-%      \Edge(s2)(A)
-%      \Edge(A)(B)
-%      \Edge(B)(C)
-%      \Edge(C)(D)
-%      \Edge(D)(t2)
-%
-%      
-%      \tikzset{
-%      EdgeStyle/.append style = {red} }
-%      \Edge(s3)(E)
-%      \Edge(E)(F)
-%      \Edge(F)(t3) 
-%	\tikzset{
-%      EdgeStyle/.append style = {blue} }
-%      \Edge(s1)(A)
-%      \Edge(A)(B)
-%      \Edge(B)(E)
-%      \Edge(E)(F)
-%      \Edge(F)(t1)
-%      
-%	\tikzset{
-%      EdgeStyle/.append style = {black,-} }
-%
-%      \Edge(1)(2)
-%      \Edge(1)(3)
-%    \node (1) at (-3,4){\Huge $\rightarrow$};
-%%     
-%%     \node (2) at (-7,0){\Huge H};
-%%     \node (3) at (10,0){\Huge G};
-%    \end{tikzpicture}
-%    }
-%    \caption{Reduction from k-coloring to MIN-PRA}
-%    \label{fig:reduction}
-%    \end{figure}
-
-\section{Solving \pazl on Star Routed Networks} \label{sec:PAZL}
-
-  In this section, we deal with the problem \pazl on star routed networks.
+         \section{Solving \pazl on Star Routed Networks}\label{sec:PAZL}
+
+       In this section, we deal with the problem PAZL on star routed networks.
 Since we want an assignment with waiting times zero, $MT({\cal M})$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
@@
 Consider an assignment $m$ of a star routed network and let $m'_r= m_{r} - t(c_s,r) \mod P$.
-  Then $m'$ is an assignment of the same star routed network where, for all $i$, the weights of the arcs from $s_i$ to $c_s$ are set to $0$.
-Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
+Then $m'$ is an assignment of the same star routed network where, for all $i$, the weights of the arcs $(s_i,c_s)$ are set to $0$.
+Therefore we assume from now on that the \emph{weight of the arcs $(s_i,c_s)$ are all equal to $0$}.
 
@@
 
-      \begin{proposition} Let $(G, {\cal R})$ be a star routed network, and let $n\tau + 2(\lambda(r_{n-1}) - \lambda(r_{0})) \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which is given by Shortest-Longest in time $O(n\log(n))$.\label{prop:SL}
+      \begin{proposition} Let $(G, {\cal R})$ be a star routed network, and let $n\tau + 2(\lambda(r_{n-1}) - \lambda(r_{0})) \leq P$.
+There is a $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with waiting times $0$ given by Shortest-Longest in time $O(n\log(n))$.\label{prop:SL}
       \end{proposition}
@@
 
-    \todo{Introduire la load là et faire un théorème avec ce paramètre ?}
-
-    We propose a greedy algorithm to build a $(P,\tau)$-periodic assignment, which provably works when
-    the period is large enough with regard to the number of routes and size of messages. In other words, 
-    we can always find a solution when the network is far from saturated.
-This algorithm defines an upper bound for the period.
-As a reminder, the lower bound is $n\tau$, that is, the size taken by the messages to be emitted.
+      We define the \textbf{load} of a star routed network as $\frac{n\tau}{P}$, it is the proportion of time slots used by messages on the central arc in a period.
+Therefore if the load is larger than $1$ there cannot be an assignment.
+We propose a greedy algorithm to build a $(P,\tau)$-periodic assignment, which always finds an assignment when the load is less than $1/3$.
+Therefore in the rest of the article we will be only concerned with load larger than $1/3$.
 
     \begin{proposition}
-     Let $(G, {\cal R})$ be a star routed network, and let $ 3n\tau \leq P$, then there is $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with all waiting times $0$ which can be found in time $O(n^2)$.
+    There is a $(P,\tau)$-periodic assignment of a star routed network with waiting times $0$ if the load is less than $1/3$ and it can be found in time $O(n^2)$.
     \end{proposition}
@@
 A last cut could be implemented: compute for every route not in $R(S)$ the set of possible positions in the backward period and verify whether at least one is contained in the useful slots of $S$.
+
    \subsection{Experimental evaluation}\label{sec:exp_PAZL}
       The following experimental results compare the three presented algorithms.
-      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithm but are not always able to find a solution, depending on $P$, $\tau$, $n$ and the size of the routes.
+      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithms but are not always able to find a solution, depending on the load or the size of the routes.
 On the other hand, the exhaustive search finds an optimal solution if it exists, but works in exponential time.
 We compare the performance of the algorithms in two different regimes: routes are either short with regard to $\tau$, or unrestricted.
-      From our C-RAN context we choose the following parameters: the number of routes 
-      is at most $n = 20$, $\tau$ is equal to $2500$.
-Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.
+      From our C-RAN context we choose the following parameters: the number of routes is at most $n = 20$, $\tau$ is equal to $2500$.
+%       Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.
 
@@
 
-      We define the load of the network as $\frac{n\tau}{P}$ (here a value between one and three),
-      it is the proportion of time slots used by messages on the central arc.
-In our experiments we will try to understand how our algorithms work with regards to the load.
+       In our experiments we try to understand how our algorithms work with regards to the load.
 To change the load, we fix the parameters $\tau$ and $n$ and modify the period $P$, which allows for a smoother control of the load and does not change the run time of our algorithms.
@@
 
-      First we consider routes which are shorter than $\tau$, that is a message cannot be contained completely in a single arc which is very common for our application.
-We generate star routed networks in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ slots.
-It corresponds to messages of approximately $1$Mb, links of bandwidth $10$Gbps and length less than $5$km between the BBU and the RRH.
-
-      Our aim is to understand how well the algorithms are working under high load.
-To do that we try to evaluate the minimal period (that is the highest possible load) for which a $(P,\tau)$-periodic assignment can be found by each algorithm.
-%       To that end we use a linear search on $P$, since a dichotomy method would not work because of Lemma~\ref{lemma:monotonic}.
-
-      In our experiment, we generate $1000$ random instances of \pazl for $1$ to $12$ routes. 
-      We measure the average minimal period, for each algorithm.
-Remind that the exhaustive search always finds the best possible period for a given instance.
-The lower and upper bound $n\tau$ and $3n\tau$ are also represented.
-      \todo{présenter ça comme une average load ?}
+      First we consider routes which are shorter than $\tau$: a message cannot be contained completely in a single arc which is very common in our applications.
+We generate star routed networks in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$.
+It corresponds to messages of approximately $1$Mb, links of bandwidth $10$Gbps and length of routes less than $5$km between the BBU and the RRH.
+
+      Our aim is to understand how well the algorithms are working under high load. To do that we evaluate the highest load 
+      under which a $(P,\tau)$-periodic assignment can be found by each algorithm when we change the number of routes. 
+      In our experiment, we generate $1000$ random instances of \pazl for $1$ to $14$ routes.
+We measure the average maximal possible load, for which each algorithm finds a solution.
+Remind that the exhaustive search always finds the highest load for a given instance.
+%       The lower and upper bound $n\tau$ and $3n\tau$ are also represented.
+
       \begin{figure}[h]
+
       \begin{center}
@@
 In this experiment we fix the number of routes to $8$ and the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots (in the same range as the period).
-We measure for each algorithm its percentage of success, for periods from $20000$ to $50000$ which corresponds to a load of $100\%$ down to $40\%$.
-
-\begin{figure}[H]
+We measure for each algorithm its percentage of success, for load of $100\%$ down to $40\%$.
+
+\begin{figure}[h]
 
@@
 On the other hand, the greedy algorithm has a performance not so far from the case of short routes, which is expected since it does not directly depend on the size of the route.
-When repeating the experiments of the previous section on routes of arbitrary length, we find that on average the greedy algorithm finds a solution if $P>1.89n\tau$.
-
-      When the load is larger than $50\%$ (period less than $40000$), the exhaustive search finds  more solutions than the greedy algorithms which justifies its use.
-However, for load larger than $80\%$ (period less than $25000$) there are many instances for which there are no solutions to \pazl.
+In fact, if we do the previous experiment
+      for short routes but with long routes, we find that, on average, the greedy algorithm finds a solution when the load is less than $53\%$.
+
+      When the load is larger than $50\%$, the exhaustive search finds more solutions than the greedy algorithms which justifies its use.
+However, for load larger than $80\%$ there are many instances for which there are no solutions to \pazl.
       It means that with long routes and high load, looking for an assignment without waiting time is far too restrictive.
@@
 
-      The computation time of the exhaustive search is in $O(n!)$, hence we need to study its scalability when $n$ grows.
+      The computation time of the exhaustive search is in $O(n!)$ as shown int Th.~\ref{th:FPT}, hence we need to study its scalability when $n$ grows.
 In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots.
-We fixed a period of $1.05n\tau$, which corresponds to $95\%$ of load.
+We chosed $95\%$ of load.
 %       , that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
@@
 
-     \begin{algorithm}
-    \caption{ Greedy deadline ({\bf GD}) }
-    \begin{algorithmic}
-    \REQUIRE A routed network $(G,{\cal R})$, a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
-    \ENSURE $(P,\tau)$-periodic assignment of $(G,{\cal R})$, or failure
-   \STATE  ${\cal H} \leftarrow$ empty set //{\em set of eligible routes}
-       \STATE  free\_ intervals $\leftarrow$ [0,$P$] //{\em list of intervals of free slots}
-
-    \FORALL{route $r_{i}$}
-    \STATE  deadline[$r_i$]  $\leftarrow$  $m_{i} + T_{max} - \omega(s_i,c_s)$
-    \STATE  eligible\_time[$r_i$] $\leftarrow$ $m_{i} +  \lambda(r_i) + \omega(c_t,t_i)$
-      \ENDFOR
-
-      \WHILE{There is some non-assigned routes}
-      \IF{${\cal H}$ is empty}
-      \STATE $r_i$ $\leftarrow $ min\_non\_assigned(eligible\_time)
-      \ENDIF
-
-      \STATE $r \leftarrow $ extract\_min(${\cal H}$)
-      \STATE t $\leftarrow$ next\_free\_interval(free\_intervals, t) //{\em if there is no more free intervals of size $\tau$, the algorithm fails}
-      \STATE $w_i \leftarrow$ t - eligible\_time[$r_i$]
-      \STATE update(t,free\_ intervals)
-      \STATE t $\leftarrow$ t + $\tau$
-      \FORALL{routes $r_i$ with  eligible\_time[$r_i$] $\leq$ t}
-      \STATE insert ( ${\cal H}$,$r_i$).
-      \ENDFOR
-      \ENDWHILE
-%    \STATE  $w_i \leftarrow 0$
-%    \FORALL{route $r_{t_i}$}
-%    \STATE  $w_i \leftarrow 0$
-%    \STATE period-end $\leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
-%    \FORALL{route $r_{t_j}$}
-%    \STATE deadline-route$ \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
-%    \STATE $deadline \leftarrow$ min(deadline-route,period-end)
+%     
+%      \begin{algorithm}
+%     \caption{ Greedy deadline ({\bf GD}) }
+%     \begin{algorithmic}
+%     \REQUIRE A routed network $(G,{\cal R})$, a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
+%     \ENSURE $(P,\tau)$-periodic assignment of $(G,{\cal R})$, or failure
+%    \STATE  ${\cal H} \leftarrow$ empty set //{\em set of eligible routes}
+%        \STATE  free\_ intervals $\leftarrow$ [0,$P$] //{\em list of intervals of free slots}
+%   
+%     \FORALL{route $r_{i}$}
+%     \STATE  deadline[$r_i$]  $\leftarrow$  $m_{i} + T_{max} - \omega(s_i,c_s)$
+%     \STATE  eligible\_time[$r_i$] $\leftarrow$ $m_{i} +  \lambda(r_i) + \omega(c_t,t_i)$
 %       \ENDFOR
-
-    \end{algorithmic}
-    \end{algorithm}
+%       
+%       \WHILE{There is some non-assigned routes}
+%       \IF{${\cal H}$ is empty}
+%       \STATE $r_i$ $\leftarrow $ min\_non\_assigned(eligible\_time)
+%       \ENDIF
+%      
+%       \STATE $r \leftarrow $ extract\_min(${\cal H}$)
+%       \STATE t $\leftarrow$ next\_free\_interval(free\_intervals, t) //{\em if there is no more free intervals of size $\tau$, the algorithm fails}
+%       \STATE $w_i \leftarrow$ t - eligible\_time[$r_i$]
+%       \STATE update(t,free\_ intervals)
+%       \STATE t $\leftarrow$ t + $\tau$
+%       \FORALL{routes $r_i$ with  eligible\_time[$r_i$] $\leq$ t}
+%       \STATE insert ( ${\cal H}$,$r_i$).
+%       \ENDFOR
+%       \ENDWHILE
+% %    \STATE  $w_i \leftarrow 0$
+% %    \FORALL{route $r_{t_i}$}
+% %    \STATE  $w_i \leftarrow 0$
+% %    \STATE period-end $\leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
+% %    \FORALL{route $r_{t_j}$}
+% %    \STATE deadline-route$ \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
+% %    \STATE $deadline \leftarrow$ min(deadline-route,period-end)
+% %    \ENDFOR
+%     
+% 
+%     \end{algorithmic}
+%     \end{algorithm}
     The function  min\_non\_assigned(eligible\_time) returns the route with lowest time in eligible\_time, which is not assigned yet.
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 
@@
           \vspace{-1cm}
-\begin{figure}[H] 
+\begin{figure}[h] 
           \includegraphics[width=0.4\textwidth]{departs_gp_25000.pdf}
@@
 We represent the success rate with regards to the margin, for the three algorithms computed over $10000$ random star routed networks.
-    \begin{figure} [H] 
+    \begin{figure} [h] 
       \vspace{-0.5cm}
@@
 The following tables presents the average success rate for each number of sending orders, on $1000$ instances, for GD and PMLS.
-         \begin{figure}[H] 
+         \begin{figure}[h] 
        \begin{center}

### 2017-07-21 infocom/infocom.tex
presque tout corrigé

@@
       From our C-RAN context we choose the following parameters: the number of routes is at most $n = 20$, $\tau$ is equal to $2500$.
-%       Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.
-
-      % The code in C is available on the webpage of one of the authors~\cite{webpage} under a copyleft license.
+      It corresponds to messages of approximately $1$Mb for links of bandwidth $10$Gbps.
 
@@
       First we consider routes which are shorter than $\tau$: a message cannot be contained completely in a single arc which is very common in our applications.
-We generate star routed networks in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$.
-It corresponds to messages of approximately $1$Mb, links of bandwidth $10$Gbps and length of routes less than $5$km between the BBU and the RRH.
+We generate star routed networks in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ which corresponds to links of less than $5$km between the BBU and the RRH.
 
@@
       In our experiment, we generate $1000$ random instances of \pazl for $1$ to $14$ routes.
-We measure the average maximal possible load, for which each algorithm finds a solution.
+We represent in Fig.~\ref{fig:short} the average maximal possible load, for which each algorithm finds a solution.
 Remind that the exhaustive search always finds the highest load for a given instance.
@@
             \vspace{-0.75cm}
-      \caption{Minimum period averaged over $1000$ random instances}
+      \caption{Minimum period averaged over $1000$ random instances}\label{fig:short}
       \end{figure}
@@
 In this experiment we fix the number of routes to $8$ and the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots (in the same range as the period).
-We measure for each algorithm its percentage of success, for load of $100\%$ down to $40\%$.
+We represent in Fig.~\ref{fig:long} the percentage of success of each algorithm, for load from $100\%$ down to $40\%$.
 
@@
             \vspace{-1cm}
-      \caption{Success rate for $8$ routes over $1000$ random instances}
+      \caption{Success rate for $8$ routes over $1000$ random instances}\label{fig:long}
      \end{figure}
@@
 
-    In this section, we still work on star routed networks, but we consider again the more general \pall problem.
-It means that the messages can wait in the target vertices (BBUs) in order to find solutions when there are none without waiting time.
+    In this section, we consider the more general \pall problem on star routed networks.
+It means that the messages can wait in the target vertices (BBUs) in order to find assignments which is not possible for \pazl.
 We allow the process times $PT$ of the routes to be greater than twice the weights of the routes, but it should less than $T_{max}$.
@@
 For instance if all the weights on the arcs $(c_t,t_i)$ are the same, we can replace them all by $0$ and substract this weight to $T_{max}$.
-It corresponds to a situation where all the BBUs are in the same datacenter.
-	The assignment in that case is trivial, just send all messages so that they follow each other without gaps in the central arc $(c_s,c_t)$.
+It corresponds to a situation where all the BBUs are in the same datacenter and have the same processing power.
+	The assignment in that case is trivial, just send all messages so that they follow each other without gaps in the central arc.
 Since the arcs $(c_t,t_i)$ are of weight $0$, all messages will go through $(c_t,c_s)$ on their way back in
@@
  %A more realistic assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same. It would correspond to a situation where all the BBUs are in the same datacenter.
-	Another assumption would be that all weights of the arcs $(s_i,c_s)$ are the same.
-
-	 \begin{theorem}
+	Another possible assumption would be that all weights of the arcs $(s_i,c_s)$ are the same.
+
+	 \begin{theorem}\label{th:asym}
 	 Let $(G,{\cal R})$ be a star routed network with $n$ routes and let $P \geq n\tau$.
@@
 
-        The offset of the route $r_i$ is set to $i\tau$, which ensures that there are no collision on the way forward (on the arc $(c_s,c_t)$) as soon as $P \geq n\tau$ which is the minimal possible period.
+        The offset of the forward route $r_i$ is set to $i\tau$, which ensures that there are no collision on the arc $(c_s,c_t)$ as soon as $P \geq n\tau$ which is the minimal possible period.
 We set the waiting time for the route $i$ to $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$.
@@
 
-     Remark that this assignment always exists and has no collision when $P \geq n\tau$. 
-     If for any pair of indices $(i,j)$ the difference between the weights of the arcs $(s_i,c_s)$ and $(s_j,c_s)$ is bounded 
-     by $d$ and the length of the longest route is $l$, then the maximum process time is bounded by  $2l + d$
+     Assume that for any pair of indices $(i,j)$ the difference between the weights of the arcs $(s_i,c_s)$ and $(s_j,c_s)$ is bounded by $d$ and the length of the longest route is $l$.
+Using the same idea as in Th.~\ref{th:asym}, there is an assignment with maximum process time bounded by  $2l + d$
 
@@
 
-    We can decompose any algorithm solving the \pall problem in two parts: first set the offsets of the forward routes and then, knowing this information set the offset of the backward routes or equivalently the waiting times.
-    The offsets of the forward routes are chosen so that messages have no collision on the central arc and such that there are no free slots in between the end of a message on the central arc and the beginning of the next one.
+    We can decompose any algorithm solving the \pall problem in two stages: first set the offsets of the forward routes and then, knowing this information set the offset of the backward routes or equivalently the waiting times.
+    The offsets of the forward routes are chosen so that they have no collisions and such that there are no free slots in between the end of a message on the central arc and the beginning of the next one.
     It is done to minimize the period needed to send the messages of the forward route. For this section and the next, we assume that the offsets of the forward routes are fixed by some order.
 
-    Consider a forward route $r_i$ and the corresponding backward route $r_{\rho(i)}$.
-    We define the {\bf deadline} of $r_{\rho(i)}$ as $m_{i} + T_{max} - \omega(s_i,c_s)$, that is the latest time at which the message can go out of $c_t$ such that $PT(r_i) \leq T_{max}$.
-    We say that a backward route $r_{\rho(i)}$ is {\bf eligible} at time $t$ if $m_{i} +  \lambda(r_i) + \omega(c_t,t_i) \leq t$, that is the message of the route $r_{\rho(i)}$ arrives at $c_t$ before time $t$ when $w_i = 0$.
-
-    The first algorithm we propose is a greedy algorithm which sets the offset $m_{\rho(i)}$ of the 
+    Consider a forward route $r_i$ and the corresponding backward route $\rho(r_i)$.
+    We define the {\bf deadline} of $\rho(r_i)$ as $m_{r_i} + T_{max} - \omega(s_i,c_s)$, that is the latest time at which the message can go out of $c_t$ such that $PT(r_i) \leq T_{max}$.
+    We say that a backward route $\rho(r_i)$ is {\bf eligible} at time $t$ if $m_{i} +  \lambda(r_i) + \omega(c_t,t_i) \leq t$, that is the message of the route $\rho(r_i)$ arrives at $c_t$ before time $t$ when $w_i = 0$.
+
+    The first algorithm we propose is a greedy algorithm which sets the offset $m_{\rho(r_i)}$ of the 
     backward routes. It prioritizes the routes with the earliest deadline to best satisfy the
@@
 
-    This algorithm does not take into account the periodicity. Say that $t_0 = t(c_t,r_{\rho_i} = m_{\rho_i} + t(c_t,r(\rho_i)$, where $m_{\rho_i}$ is the smallest offset that the algorithm has fixed
-    for a backward route. Then for all routes with $t(c_t,r_{\rho_i}$ smaller than $t_0 + P - \tau$,
+    This algorithm does not take into account the periodicity.
+Say that $t_0 = t(c_t,r)$ such that $r$ is the first backward route selected by the algorithm.
+Then if all backward routes $r$ are such that $t(c_t,r)$ is smaller than $t_0 + P - \tau$,
     by construction, there are no collisions on the central arc.
-    However, for routes with larger $t(c_t,r_{\rho_i}$, since we  should consider everything modulo $P$, 
-    they may collide with any other route.
+    However, if a route $r$ has a larger $t(c_t,r)$, since we should consider everything modulo $P$, 
+    it may collide with another backward route.
 Therefore we must adapt the greedy algorithm of the previous paragraph by finding $s \geq t$ the first time for which there is an eligible route with its offset not fixed and \emph{such that there is no collision if a message go through the central arc at time $s$}.
@@
 %     \end{algorithm}
-    The function  min\_non\_assigned(eligible\_time) returns the route with lowest time in eligible\_time, which is not assigned yet.
+%     The function  min\_non\_assigned(eligible\_time) returns the route with lowest time in eligible\_time, which is not assigned yet.
 The function update(t,free\_intervals) removes an interval of size $\tau$ beginning at t, which correspond to the message,  from free\_intervals.
@@
 However, when it fails because a job finishes after its deadline, it changes the schedule of the last messages to find a possible schedule for the problematic job.
-The change in the scheduling is so that the algorithm cannot fail on the same job a second time except if there is no solution, hence the polynomiality of the algorithm.
+The change in the scheduling is so that the algorithm cannot fail on the same job a second time except if there is no solution, which proves that the algorithm is in polynomial time.
 
@@
      Remark that we do not deal with the periodicity.
-When MLS finds a solution ${\cal M}$ its always satisfies $MT({\cal M}) < T_{max}$.
-On the other hand, it is a $(P,\tau)$ periodic assignment only if $m_{n-1} - m_0 \leq P -\tau$ where $m_{n-1}$ is the largest offset and $m_0$ the smallest one.
-The algorithm we use minimize $m_{n-1} - m_0 $, so it may work quite well in practice (as shown in Section~\ref{sec:resultsPALL}).
+When MLS finds an assignment $m$ its always satisfies $MT(m) < T_{max}$.
+On the other hand, it is a $(P,\tau)$ periodic assignment only if $m_{max} - m_{min} \leq P -\tau$ where $m_{max}$ is the largest offset and $m_{min}$ the smallest one.
+The algorithm we use minimize this quantity, so it may work in practice (as shown in Section~\ref{sec:resultsPALL}).
 
@@
 We fix arbitrarily a backward route so that its message is the first to go through the central arc at time $t$.
-Then we modify the deadline of each forward route to be the minimum of their previous deadline and $t + P$.
-We execute this algorithm for every possible first backward route and we return the solution that minimize $MT({\cal M})$.
+Then we modify the deadline of each backward route to be the minimum of their previous deadline and $t + P$.
+We execute this algorithm for every possible first backward route and we return the solution that minimizes $MT({\cal M})$.
 Since we run the previous algorithm at most $n$ times, the complexity is in $O(n^3\log(n))$.
-Remark that it will always find more solution than MLS,
-     because if MLS finds a solution with first route $r$ and such that $m_{n-1} - m_0 \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route.
-Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment
-     since we guarantee that all messages are scheduled in a period of time of size $P$ and it satisfies $MT({\cal M}) < T_{max}$ by construction of the deadlines.
-The scheduling algorithm we use always finds a solution to the  original problem it solves.
-However, in our periodic context, we do not allow to choose an offset for a route after $t+P- \tau$ which modulo $P$ may not collide with another route.
-Therefore PMLS may fail while there is a solution.
+Remark that it will always find more solution than MLS, because if MLS finds a solution with first route $r$ and such that $m_{max} - m_{min} \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route.
+Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment since we guarantee that all messages are scheduled in a period of time of size $P$ and it satisfies $MT({\cal M}) < T_{max}$ by construction of the deadlines.
+Remark that PMLS may fail while there is an assignment.
+Indeed, in the algorithm we restrict the assignments we look for by not allowing to choose an offset for a route after $t+P- \tau$.
 
@@
     \label{sec:resultsPALL}
-    In this section, we first try to understand what is the best choice of order for the first stage of the algorithm.
+
     We fix the number of routes to $8$ to make comparisons with the results of Section~\ref{sec:exp_PAZL} easier. 
@@
 In our experiments the margin range from  $0$ to $3000$ slots.
-   We look at two different regimes: we take a period equal to $1,05n\tau$ to represent a very loaded network
-   and $1,5n\tau$ for a mildly loaded network.
-Choosing a larger period is not relevant since then we know how to solve the problem even without waiting times as shown in Section~\ref{sec:exp_PAZL}.
-We represent the success rate with regards to the margin, for the five kind of orders using the Greedy algorithm for the second stage, computed over $10000$ random star routed networks.
-Note that for the random order, we compute $1000$ random orders and count it as a success as soon as there is a solution for one order.
+   We look at two different regimes, a medium load of $80\%$ and a high load of $95\%$.
+   Considering smaller load is not relevant since then we know how to solve the problem even without waiting times as shown in Section~\ref{sec:exp_PAZL}.
+
+   We first try to understand what is the best choice of order for the first stage of the algorithm which are 
+   followed by the GD algorithm for this experiment.
+   We try the following ones: decreasing order on the length of the routes (LSR), decreasing order on the weigths of the arcs 
+   $(c_t,t_i)$ (LSA), increasing order on the length of the routes (SLR), decreasing order on the weigths of the arcs 
+   $(c_t,t_i)$ (SLA) as in Prop.~\ref{prop:SL}. We also consider the random order, which means we compute $1000$ random orders and 
+   stop as soon one yields an assignment.
+   In Fig.~\ref{fig:} and Fig.~\ref{fig:}, we represent the success rate of the five kind of orders 
+   with regards to the margin. The value is an average computed over $10000$ random star routed networks.
 

### 2017-07-21 infocom/infocom.tex
virgules, tableau 14

@@
 antennas. The main challenge is to guarantee that the latency of the periodic messages sent from the antennas to their processing
-units and back fulfills protocol time constaints.
+units and back fulfills protocol time constraints.
 We show that traditional statistical multiplexing does not allow such a low latency, due to collisions and buffering at nodes.
@@
 We compare the performance of the algorithms in two different regimes: routes are either short with regard to $\tau$, or unrestricted.
-      From our C-RAN context we choose the following parameters: the number of routes is at most $n = 20$, $\tau$ is equal to $2500$.
+      From our C-RAN context we choose the following parameters: the number of routes is at most $n = 20$, $\tau$ is equal to $2,500$.
       It corresponds to messages of approximately $1$Mb for links of bandwidth $10$Gbps.
@@
       under which a $(P,\tau)$-periodic assignment can be found by each algorithm when we change the number of routes. 
-      In our experiment, we generate $1000$ random instances of \pazl for $1$ to $14$ routes.
+      In our experiment, we generate $1,000$ random instances of \pazl for $1$ to $14$ routes.
 We represent in Fig.~\ref{fig:short} the average maximal possible load, for which each algorithm finds a solution.
@@
       Finally we remark that the greedy algorithm has an average period much lower than the theoretical upper bound of $3n\tau$.
-We made a linear regression on this value and with a correlation coefficient greater than $0,999$ we find a slope of $1.53n\tau$.
+We made a linear regression on this value and with a correlation coefficient greater than $0.999$ we find a slope of $1.53n\tau$.
 
@@
       We now want to understand the performance of these algorithms when the size of the routes is unbounded.
-In this experiment we fix the number of routes to $8$ and the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots (in the same range as the period).
+In this experiment we fix the number of routes to $8$ and the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30,000$ slots (in the same range as the period).
 We represent in Fig.~\ref{fig:long} the percentage of success of each algorithm, for load from $100\%$ down to $40\%$.
@@
       The computation time of the exhaustive search is in $O(n!)$ as shown int Th.~\ref{th:FPT}, hence we need to study its scalability when $n$ grows.
-In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots.
-We chosed $95\%$ of load.
+In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30,000$ slots.
+We chose  $95\%$ of load.
 %       , that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
@@
          \begin{center}
-         \begin{tabularx}{0.5\textwidth}{|l|X|X|X|X|}
+         \begin{tabularx}{0.5\textwidth}{|l|X|X|X|X|X|}
     \hline
-   $n$ & $8$ & $10$& $12$& $16$\\
+   $n$ & $8$ & $10$& $12$&$14$& $16$\\
     \hline
-   Time (s) & $6.10^{-5}$&$8.10^{-4}$&$2.10^{-2}$& $11$\\
+   Time (s) & $6.10^{-5}$&$8.10^{-4}$&$2.10^{-2}$& $0.4$& $11$\\
     \hline
@@
     We fix the number of routes to $8$ to make comparisons with the results of Section~\ref{sec:exp_PAZL} easier. 
-    We draw uniformly the weights of the arcs between $0$ and $20000$ slots.
+    We draw uniformly the weights of the arcs between $0$ and $20,000$ slots.
     For a given routed network, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
@@
     In fact the margin represents the latency imposed by the communication process without taking into account the physical length of the network which cannot be changed.
-In our experiments the margin range from  $0$ to $3000$ slots.
+In our experiments the margin range from  $0$ to $3,000$ slots.
    We look at two different regimes, a medium load of $80\%$ and a high load of $95\%$.
@@
    $(c_t,t_i)$ (LSA), increasing order on the length of the routes (SLR), decreasing order on the weigths of the arcs 
-   $(c_t,t_i)$ (SLA) as in Prop.~\ref{prop:SL}. We also consider the random order, which means we compute $1000$ random orders and 
+   $(c_t,t_i)$ (SLA) as in Prop.~\ref{prop:SL}. We also consider the random order, which means we compute $1,000$ random orders and 
    stop as soon one yields an assignment.
    In Fig.~\ref{fig:} and Fig.~\ref{fig:}, we represent the success rate of the five kind of orders 
-   with regards to the margin. The value is an average computed over $10000$ random star routed networks.
+   with regards to the margin. The value is an average computed over $10,000$ random star routed networks.
 
@@
 
-     The random order is the best by far. When the load is not too high ($P = 30000$) there is always a solution with margin $0$.
+     The random order is the best by far. When the load is not too high ($P = 30,000$) there is always a solution with margin $0$.
      Note that, when disallowing waiting times, there were instances without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the \pall problem.
@@
 Since GD already showed excellent results on mild loads, it is more interesting to focus on the behavior of the algorithms on high load.
-Moreover, we will use $1000$ random orders for the first stage as it gives the best results.
-The following experiment is realized on routed networks with $8$ routes, weights of the arcs drawn between $0$ and $20000$ and with a period of $21000$.
-We represent the success rate with regards to the margin, for the three algorithms computed over $10000$ random star routed networks.
+Moreover, we will use $1,000$ random orders for the first stage as it gives the best results.
+The following experiment is realized on routed networks with $8$ routes, weights of the arcs drawn between $0$ and $20,000$ and with a period of $21,000$.
+We represent the success rate with regards to the margin, for the three algorithms computed over $10,000$ random star routed networks.
     \begin{figure} [h] 
@@
      The MLS algorithm performs poorly, worst than GD and PMLS, which shows that taking into account the periodicity is fundamental.
-     The GD algorithms is close to $100\%$ success rate for margins larger than $1500$ while the PMLS algorithm finds a solution in more than $95\%$ of the experiments, even with a margin $0$.
+     The GD algorithms is close to $100\%$ success rate for margins larger than $1,500$ while the PMLS algorithm finds a solution in more than $95\%$ of the experiments, even with a margin $0$.
 Therefore, for the worst possible constraints on load and margin, there are a few instances for which we do not find a solution.
-However, with a margin of $1000$, which corresponds to about $0.05$ms of additional delay with the chosen parameters, we always find a solution.
-
-    Remark that the random order corresponds to the best of $1000$ orders drawn uniformly which means that a computation can be up to $1000$ time slower than for a fixed order.
+However, with a margin of $1,000$, which corresponds to about $0.05$ms of additional delay with the chosen parameters, we always find a solution.
+
+    Remark that the random order corresponds to the best of $1,000$ orders drawn uniformly which means that a computation can be up to $1,000$ time slower than for a fixed order.
 The choice of the number of random orders drawn yields a trade-off between the computation time and the success rate.
-Up to now, we chose $1000$ random orders arbitrarily.
-We investigate the success rate of our algorithm with regards to the number of random orders drawn, a period of $21000$ and a margin $0$.
-The following tables presents the average success rate for each number of sending orders, on $1000$ instances, for GD and PMLS.
+Up to now, we chose $1,000$ random orders arbitrarily.
+We investigate the success rate of our algorithm with regards to the number of random orders drawn, a period of $21,000$ and a margin $0$.
+The following tables presents the average success rate for each number of sending orders, on $1,000$ instances, for GD and PMLS.
          \begin{figure}[h] 
@@
     \hline
-    \# orders& $1$ & $10$ & $100$& $1 000$& $10 000$&$100 000$\\
+    \# orders& $1$ & $10$ & $100$& $1,000$& $10^{4}$&$10^{5}$\\
     \hline
@@
     \hline
-  PMLS & $41,1$ &$82,5$&$94,5$&$96,2$&$97,2$&$97,2$\\
+  PMLS & $41.1$ &$82.5$&$94.5$&$96.2$&$97.2$&$97.2$\\
     \hline
@@
 yields the best results for the two algorithms.
-The number of different orders is $7!= 5040$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order.
+The number of different orders is $7!= 5,040$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order.
 Therefore instead of doing $10000$ random draws we could test every possible order in less time.
@@
 
-     We draw $1000$ star routed networks with $8$ routes, with weights on the arcs drawn between $0$ and $20000$.
+     We draw $1000$ star routed networks with $8$ routes, with weights on the arcs drawn between $0$ and $20,000$.
 Note that the results are almost the same when the arcs are small.
-We measure, for periods from $20000$ (network fully loaded), to $50000$ ($40 \%$ of load), the median, the first, and the third quartile of the margins computed in $1000$ simulations using FIFO buffer to resolve collisions.
+We measure, for periods from $20000$ (network fully loaded), to $50,000$ ($40 \%$ of load), the median, the first, and the third quartile of the margins computed in $1000$ simulations using FIFO buffer to resolve collisions.
 
@@
 
-     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Figure~\ref{fig:sto} since even the third quartile was always at $0$ for a period of $20000$.
-     There is around $20\%$ of the instances for which the margin is larger than $0$ for $P=20000$ and $2\%$
-     for $P = 21000$. For the instances with a margin larger than $0$, the margin is on average $400$.
+     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Figure~\ref{fig:sto} since even the third quartile was always at $0$ for a period of $20,000$.
+     There is around $20\%$ of the instances for which the margin is larger than $0$ for $P=20,000$ and $2\%$
+     for $P = 21,000$. For the instances with a margin larger than $0$, the margin is on average $400$.
 
@@
 When the network is highly loaded,
-     we have instances with a margin of about $10000$ which corresponds to half the period, that is $0.5$ms. 
-     Even when the network is lightly loaded, a quarter of the instances have a margin of more than $2000$
+     we have instances with a margin of about $10,000$ which corresponds to half the period, that is $0.5$ms. 
+     Even when the network is lightly loaded, a quarter of the instances have a margin of more than $2,000$
      which is more than what PMLS finds for the worst instance and a network fully loaded ! 

### 2017-07-21 code/Sources/PAZL.c

@@ -740,6 +740,7 @@ int linear_search(Graphe g,int taille_message)
 	int nb_routes = g.N/2;
 	for(int i =nb_routes*taille_message;i<taille_message*(nb_routes)*3;i++)
 	{
+		//printf(" search for %d (%d) \n",i,result);
 		result = search(g, taille_message,i);
 		if(result != -1)
 		{

### 2017-07-21 code/Sources/main.c

@@ -17,7 +17,7 @@ int main()
 	/*****
 	Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
 	*****/
-	//simuls_periode_PAZL(15,2500,700,100);
+	simuls_periode_PAZL(12,2500,700,1000);
 
 	/******************************************/	
 
@@ -78,7 +78,7 @@ int main()
 	/****Nombre de routes pouvant être calculées en moins de "max" ms
 	****/
 
-	search_efficiency(2500,20000,100);
+	//search_efficiency(2500,20000,100);
 
 
 	/******

### 2017-07-21 code/Sources/simulations.c

@@ -33,7 +33,7 @@ void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,in
 		total_brute = 0;
 		total_sl =0;
 		total_search = 0;
-		#pragma omp parallel for private(res_sl,res_brute,res_3NT,res_search,g) if (PARALLEL) schedule (dynamic)
+		#pragma omp parallel for private(res_sl,res_brute,res_3NT,res_search,g) if (PARALLEL) schedule (static)
 		for(int i = 0;i<nb_simuls;i++)
 		{
 			g = init_graphe(j*2 + 1);
@@ -62,6 +62,7 @@ void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,in
 			}
 			//else printf("error (Sl = -1)\n");
 			res_search = linear_search(g,taille_message);
+			//res_brute = res_search;
 			//if(res_sl > total_sl)total_sl = res_sl;
 			if(res_search != -1){
 				#pragma omp atomic
@@ -84,8 +85,8 @@ void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,in
 		}
 		printf("\n");
 		
-		fprintf(F, "%d %lld %lld %lld %lld %d %d\n",j,(taille_message*j)/(total_3NT/nb_simuls),(taille_message*j)/(total_brute/nb_simuls),(taille_message*j)/(total_search/nb_simuls),(taille_message*j)/(total_sl/nb_simuls),j*taille_message,3*j*taille_message);
-		fprintf(stdout, "%d %lld %lld %lld %lld %d %d\n",j,(taille_message*j)/(total_3NT/nb_simuls),(taille_message*j)/(total_brute/nb_simuls),(taille_message*j)/(total_search/nb_simuls),(taille_message*j)/(total_sl/nb_simuls),j*taille_message,3*j*taille_message);
+		fprintf(F, "%d %f %f %f %f %d %d\n",j,(taille_message*j)/(total_3NT/(float)nb_simuls),(taille_message*j)/(total_brute/(float)nb_simuls),(taille_message*j)/(total_search/(float)nb_simuls),(taille_message*j)/(total_sl/(float)nb_simuls),j*taille_message,3*j*taille_message);
[…]

### 2017-07-24 infocom/infocom.tex
fin des corrections de cohérences

@@
 
-    The {\bf maximum process time} of the assignment ${\cal M}$ of $(G,{\cal R})$ is defined by $MT({\cal M})=\max\limits_{r \in {\cal R}} PT(r)$. We consider the following decision problem.
+    The {\bf maximum process time} of the assignment $m$ of $(G,{\cal R})$ is defined by $MT(m)=\max\limits_{r \in {\cal R}} PT(r)$. We consider the following decision problem.
 
@@
 
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment ${\cal M}$ of $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment $m$ of $(G,{\cal R})$ such that $MT(m) \leq T_{max}$?
 
@@
 \noindent \emph{Sketch of proof:}
- We first show that finding an assignment for the forward routes only with no collisions 
- can be reduced to \pall by a symmetry argument.
+ First, by a symmetry argument, the problem of finding an assignment with no collisions for the forward routes only
+ can be reduced to \pall.
  We fix $\tau$ the size of messages to $1$ and we reduce the problem of $k$-coloring to the 
  problem of finding an assignment without collisions for the forward routes.
- Let $H$ be a graph instance of the $k$-coloring problem, the reduction is as follows. 
+ Let $H$ be a graph instance of the $k$-coloring problem, from it we build a routed network $(G,{\cal R})$. 
  For each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
@@
 
-       We consider a simpler version of \pall, that we call {\bf Periodic Assignment for Zero Latency} or \pazl: we ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$}.
+       We also consider a simpler version of \pall, that we call {\bf Periodic Assignment for Zero Latency} or \pazl: we ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$}.
 We introduce \pazl because it is simpler to study and we are able to prove theoretical results and find better algorithms than for \pall.
-Moreover, as we  experimentally show in Sec.~\ref{sec:exp_PAZL}, this problem can often be solved positively (albeit less often than the general problem).
-Finally, a solution to \pazl is simpler to implement in real telecommunication networks, since we do not need to implement any buffering at all.
+As we  experimentally show in Sec.~\ref{sec:exp_PAZL}, this problem can often be solved positively albeit less often than the general problem.
+Finally, a solution to \pazl is simpler to implement in real telecommunication networks, since we do not need any buffering at all.
 
@@
 
-      Let us define a family of simple routed networks which corresponds to a Point-to-Multipoint fronthaul (PtMP), intended for C-RAN \cite{tayq2017real}. 
+      Let us define a family of simple routed networks modeling a Point-to-Multipoint fronthaul (PtMP), which has been designed for C-RAN \cite{tayq2017real}. 
       The graph $G$ has two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes, the central source node $c_s$ and the central target node $c_t$.
@@
 %      
-%      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{n-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+%      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  $m=(m_0, \ldots ,m_{n-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
 The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
@@
        In this section, we deal with the problem PAZL on star routed networks.
-Since we want an assignment with waiting times zero, $MT({\cal M})$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
+Since we want an assignment with waiting times zero, $MT(m)$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
 Moreover choosing the offset $m_r$ of a forward route $r$ also sets the offset of the backward route $\rho(r)$ to $m_{\rho(r)} = m_{r} + \lambda(r) \mod P$.
@@
       \end{figure}
-      First, we remark that the period found by the exhaustive search is only very slightly above the lower bound of $n\tau$, which means that, in this regime, it is very well justified to look for a solution without waiting time even for a highly loaded network.
-
-      The period needed by the Shortest-Longest algorithm to find an optimal solution is a function of the difference between the longest and the shortest route and its average could be easily determined theoretically.
-The algorithm was expected to find a period close to the optimal one since the routes are short.
-It turns out it always finds the optimal period in our experiments.
+      First, we remark that the exhaustive search finds a solution even when the load is high, especially when there are more routes.
+      It justifies the idea to look for an assignment without waiting time, in this short routes regime.
+      Second, remark that the Shortest-Longest algorithm is as good as the exhaustive search.
+While it was expected to be good with short routes, it turns out to be optimal for all the the random star routed networks we have tried.
 Therefore, we should use it in practical applications with short routes, instead of the exhaustive search which is much more computationally expensive.
-
-      Finally we remark that the greedy algorithm has an average period much lower than the theoretical upper bound of $3n\tau$.
-We made a linear regression on this value and with a correlation coefficient greater than $0.999$ we find a slope of $1.53n\tau$.
+      Finally, note that the greedy algorithm works on average when the load is less than       which is twice better than the theoritical bound.
+This algorithm seems to depends on the load only and not on the number of routes (linear regression).
 
@@
       The following table shows the time before the exhaustive search ends, for $8$ to $16$ routes, averaged on $100$ random star routed networks.
-This shows that for less than $15$ routes, which corresponds to all current topologies, the algorithm is efficient enough, but on more routes we should improve it further.
+This shows that for less than $15$ routes, which corresponds to all current topologies, the algorithm is efficient enough, but we should improve it further to work on more routes.
          \begin{center}
@@
 It means that the messages can wait in the target vertices (BBUs) in order to find assignments which is not possible for \pazl.
-We allow the process times $PT$ of the routes to be greater than twice the weights of the routes, but it should less than $T_{max}$.
+We allow the process time of the routes to be greater than twice the weights of the routes, but it should be less than $T_{max}$.
 
@@
 Since the arcs $(c_t,t_i)$ are of weight $0$, all messages will go through $(c_t,c_s)$ on their way back in
-	the same order and thus will not collide.
+	the same order and thus do not collide.
 
@@
 	 Let $(G,{\cal R})$ be a star routed network with $n$ routes and let $P \geq n\tau$.
-If there is a constant $c$ such that $\forall i < n, \,\omega(s_i,c_s) = c$, then there is a $(P,\tau)$-periodic assignment with process time $2 \times \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
+If there is a constant $c$ such that $\forall i < n, \,\omega(s_i,c_s) = c$, then there is a $(P,\tau)$-periodic assignment with process time $2 \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
 	 \end{theorem}
@@
 We set the waiting time for the route $i$ to $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$.
-We can compute the time at which the message of the route $r_i$ arrives at the vertex $c_t$ on its way back: $t(c_t,\rho_{r_i}) = w_i + i\tau + 2\lambda(r_{i})$
-        by replacing $w_i$ by its value we obtain $t(c_t,\rho_{r_i}) =  i\tau + 2\lambda(r_{0})$
+We can compute the time at which the message of the route $r_i$ arrives at the vertex $c_t$ on its way back: $t(c_t,\rho(r_i)) = w_i + i\tau + 2\lambda(r_{i})$
+        by replacing $w_i$ by its value we obtain $t(c_t,\rho(r_i)) =  i\tau + 2\lambda(r_{0})$
         As a conclusion there are no collision on the arc $(c_t,c_s)$ as soon as the 
@@
 We obtain $PT(r_i) = 2\lambda(r_{0})$ and thus the maximum process time of the assignment is also equal to $2\lambda(r_0)$.
-	Finally the complexity is $O(n)$ since we have to find a maximum between the size of $n$ routes and the computation of each $w_i$ is done by a constant number of arithmetic operations.
+	Finally the complexity is $O(n)$ since we have to find the maximum of the length of the $n$ routes and the computation of each $w_i$ is done by a constant number of arithmetic operations.
      \end{proof}
@@
     The offsets of the forward routes are chosen so that they have no collisions and such that there are no free slots in between the end of a message on the central arc and the beginning of the next one.
-    It is done to minimize the period needed to send the messages of the forward route. For this section and the next, we assume that the offsets of the forward routes are fixed by some order.
+    It is done to minimize the period needed to send the messages of the forward routes. For this section and the next, we assume that the offsets of the forward routes are fixed by some order.
 
@@
     To deal with the possible collisions, one can maintain a list of the intervals
-    of time at which a message can be send on the arc $(c_t,c_s)$. Each time the offset of a 
+    of time at which a message can be sent on the arc $(c_t,c_s)$. Each time the offset of a 
     route is fixed an interval is split into at most two intervals in constant time. 
@@
 Then we modify the deadline of each backward route to be the minimum of their previous deadline and $t + P$.
-We execute this algorithm for every possible first backward route and we return the solution that minimizes $MT({\cal M})$.
+We execute this algorithm for every possible first backward route and we return the solution that minimizes $MT(m)$.
 Since we run the previous algorithm at most $n$ times, the complexity is in $O(n^3\log(n))$.
-Remark that it will always find more solution than MLS, because if MLS finds a solution with first route $r$ and such that $m_{max} - m_{min} \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route.
-Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment since we guarantee that all messages are scheduled in a period of time of size $P$ and it satisfies $MT({\cal M}) < T_{max}$ by construction of the deadlines.
+Remark that it finds an assignment more often than MLS, because if MLS finds a solution with first route $r$ and such that $m_{max} - m_{min} \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route.
+Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment since we guarantee that all messages are scheduled in a period of time of size $P$ and it satisfies $MT(m) < T_{max}$ by construction of the deadlines.
 Remark that PMLS may fail while there is an assignment.
@@
     For a given routed network, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
-    Hence, for a routed network choosing the margin or $T_{max}$ is the same, but since we will consider many networks 
-    whith different longest route's size, it will be more meaningful to set the margin rather than $T_{max}$.
+    Hence, for a given routed network choosing the margin or $T_{max}$ is the same, but since we will consider many networks whith different longest route's size, it will be more meaningful to set a global margin rather than $T_{max}$.
     In fact the margin represents the latency imposed by the communication process without taking into account the physical length of the network which cannot be changed.
@@
 
-   We first try to understand what is the best choice of order for the first stage of the algorithm which are 
-   followed by the GD algorithm for this experiment.
-   We try the following ones: decreasing order on the length of the routes (LSR), decreasing order on the weigths of the arcs 
-   $(c_t,t_i)$ (LSA), increasing order on the length of the routes (SLR), decreasing order on the weigths of the arcs 
-   $(c_t,t_i)$ (SLA) as in Prop.~\ref{prop:SL}. We also consider the random order, which means we compute $1,000$ random orders and 
-   stop as soon one yields an assignment.
-   In Fig.~\ref{fig:} and Fig.~\ref{fig:}, we represent the success rate of the five kind of orders 
-   with regards to the margin. The value is an average computed over $10,000$ random star routed networks.
+   We first try to understand what is the best choice of order for the first stage of the algorithm which is followed by the GD algorithm in this experiment.
+We try the following ones: decreasing order on the length of the routes (LSR), decreasing order on the weigths of the arcs $(c_t,t_i)$ (LSA), increasing order on the length of the routes (SLR), increasing order on the weigths of the arcs $(c_t,t_i)$ (SLA).
+We also consider the random order, which means we compute $1,000$ random orders and stop as soon one yields an assignment.
+   In Fig.~\ref{fig:success95} and Fig.~\ref{fig:success80}, we represent the success rate of the five kind of orders with regards to the margin.
+The value is an average computed over $10,000$ random star routed networks.
 
@@
       \caption{Success rate of different orders, $95\%$ load.}
+      \label{fig:success95}
           \end{figure}
@@
       \caption{Success rate of different orders, $80\%$ load.}
-           \label{fig:success30000}
+           \label{fig:success80}
      \end{figure}
 
-     As expected, the  success rate is much better for large periods.
      According to our experiments, sending the messages from the shortest to the longest route or arc does not work well.
-It corresponds to the policy of Proposition~\ref{prop:SL} which does not work well when the routes are long as it is the case in these experiments.
+It corresponds to the policy of Prop.~\ref{prop:SL} which we already know to be bad for \pazl when the routes are long as it is the case in this experiment.
 Sending from the longest to the shortest route or arc works better and it seems that sorting the routes according to the length of the last arc rather than the route is better, at least in a loaded network.
 
-     The random order is the best by far. When the load is not too high ($P = 30,000$) there is always a solution with margin $0$.
+     The random order is the best by far.
+When the load is $80\%$ there is always a solution with margin $0$.
 Note that, when disallowing waiting times, there were instances without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the \pall problem.
@@
 Moreover, we will use $1,000$ random orders for the first stage as it gives the best results.
-The following experiment is realized on routed networks with $8$ routes, weights of the arcs drawn between $0$ and $20,000$ and with a period of $21,000$.
-We represent the success rate with regards to the margin, for the three algorithms computed over $10,000$ random star routed networks.
+In the following experiment, we represent the success rate of the three algorithms with regards to the margin,  computed over $10,000$ random star routed networks and the same parameters as previously.
+
     \begin{figure} [h] 
@@
             \vspace{-1cm}
-      \caption{Success rate of GD, MLS and PMLS for $P = 21000$}
+      \caption{Success rate of GD, MLS and PMLS, $95\%$ load}
      \label{fig:success21000}
@@
      \end{figure}
-     The MLS algorithm performs poorly, worst than GD and PMLS, which shows that taking into account the periodicity is fundamental.
-     The GD algorithms is close to $100\%$ success rate for margins larger than $1,500$ while the PMLS algorithm finds a solution in more than $95\%$ of the experiments, even with a margin $0$.
+     The MLS algorithm performs poorly, worst than GD and PMLS, which shows that \emph{taking into account the periodicity is fundamental}.
+     The GD algorithms is close to $100\%$ success rate for margins larger than $1,500$ while the PMLS algorithm finds a solution in more than $97\%$ of the experiments, even with a margin $0$.
 Therefore, for the worst possible constraints on load and margin, there are a few instances for which we do not find a solution.
@@
 
-    Remark that the random order corresponds to the best of $1,000$ orders drawn uniformly which means that a computation can be up to $1,000$ time slower than for a fixed order.
+    Recall that the random order corresponds to the best of $1,000$ orders drawn uniformly which means that a computation can be up to $1,000$ time slower than for a fixed order.
 The choice of the number of random orders drawn yields a trade-off between the computation time and the success rate.
 Up to now, we chose $1,000$ random orders arbitrarily.
-We investigate the success rate of our algorithm with regards to the number of random orders drawn, a period of $21,000$ and a margin $0$.
+We investigate the success rate of our algorithm with regards to the number of random orders drawn, a load of $95\%$ and a margin $0$.
 The following tables presents the average success rate for each number of sending orders, on $1,000$ instances, for GD and PMLS.
@@
      \end{figure}
-First remark that we can improve our previous results by taking $10000$ random orders, which 
-yields the best results for the two algorithms.
+First remark that we can improve our previous results by taking $10000$ random orders,
+instead of $1000$.
 The number of different orders is $7!= 5,040$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order.
 Therefore instead of doing $10000$ random draws we could test every possible order in less time.
-However this method would not be practical with regard to the computation time for $n = 15$.
-On the other hand, remark that the success rate of PMLS is already high for $100$ random orders, which means it will work even better than the other methods when $n$ is larger and that the number of random orders drawn is critical.
-
-     Now that we have found the best amongst the algorithms solving \pall, we need to compare its performances against the actual way to manage the messages in a network.
-The classical way to manage messages in the network is statistical multiplexing, where there is a FIFO buffer in each node of the network to deal with the collisions.
+However the computation time of this method would scale badly with $n$.
+On the other hand, remark that the success rate of PMLS is already high for $100$ random orders, which means it will work even better than the other methods when $n$ is larger and that the number of random orders drawn becomes critical.
+
+     Now that we have found the best amongst the algorithms solving \pall, we need to compare its performances against the actual way to manage the messages in a network:  statistical multiplexing, where there is a FIFO buffer in each node of the network to deal with the collisions.
 The time at which the messages are sent in the network is not computed as in our approach, thus we fix the offsets of each route to some random value.
@@
 Note that the results are almost the same when the arcs are small.
-We measure, for periods from $20000$ (network fully loaded), to $50,000$ ($40 \%$ of load), the median, the first, and the third quartile of the margins computed in $1000$ simulations using FIFO buffer to resolve collisions.
+We measure, for load from $100\%$ down to $40\%$, the median, the first, and the third quartile of the margins computed in $1000$ simulations using FIFO buffer to resolve collisions.
 
@@
       \vspace{-1cm}
-      \caption{Needed margin with respect to the period for a stochastic policy}
+      \caption{First and third quartile of the margin of statistical multiplexing}
       \label{fig:sto}
@@
 
-     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Figure~\ref{fig:sto} since even the third quartile was always at $0$ for a period of $20,000$.
-     There is around $20\%$ of the instances for which the margin is larger than $0$ for $P=20,000$ and $2\%$
-     for $P = 21,000$. For the instances with a margin larger than $0$, the margin is on average $400$.
+     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Figure~\ref{fig:sto} since even the third quartile was always at $0$ for a load of $100\%$.
+There is around $20\%$ of the instances for which the margin is larger than $0$ for a load of $100\%$ and $2\%$ for a load of $95\%$.
+For the instances with a margin larger than $0$, the margin is on average $400$.
 
      The simulations show clearly that the stochastic policy does not ensure a minimal latency.
-As we can see in Fig~\ref{fig:sto}), the more the network is loaded, the higher the latency is.
-When the network is highly loaded,
-     we have instances with a margin of about $10,000$ which corresponds to half the period, that is $0.5$ms. 
-     Even when the network is lightly loaded, a quarter of the instances have a margin of more than $2,000$
-     which is more than what PMLS finds for the worst instance and a network fully loaded ! 
+As we can see in Fig~\ref{fig:sto}, the more the network is loaded, the higher the latency is.
+When the network is highly loaded, we have instances with a margin of about $10,000$ which corresponds to half the period, that is $0.5$ms.
+Even when the network is lightly loaded, a quarter of the instances have a margin of more than $2,000$ which is more than what PMLS finds for the worst instance and a network fully loaded!
 We feel that it strongly justifies the use of a deterministic sending scheme for latency critical applications such as our C-RAN motivating problem.

### 2017-07-24 infocom/infocom.tex
regression

--- 2017-07-21 infocom/infocom.tex
@@
 \usepackage{setspace}
+\usepackage{icomma}
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
 Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches.
-This architecture is very expensive and hardly scales in the case of a mobile network composed of about $10000$ base stations.
+This architecture is very expensive and hardly scales in the case of a mobile network composed of about $1
+ 0$ base stations.
 Here we propose to use a deterministic approach to schedule our periodic messages.
@@
             \vspace{-0.75cm}
-      \caption{Minimum period averaged over $1000$ random instances}\label{fig:short}
+      \caption{Minimum period averaged over $1,000$ random instances}\label{fig:short}
       \end{figure}
@@
             \vspace{-1cm}
-      \caption{Success rate for $8$ routes over $1000$ random instances}\label{fig:long}
+      \caption{Success rate for $8$ routes over $1,000$ random instances}\label{fig:long}
      \end{figure}
@@
             \vspace{-1cm}
-      \caption{Success rate of GD, MLS and PMLS for $P = 21000$}
+      \caption{Success rate of GD, MLS and PMLS for $P = 21,000$}
      \label{fig:success21000}
@@
      \end{figure}
-First remark that we can improve our previous results by taking $10000$ random orders, which 
+First remark that we can improve our previous results by taking $10,000$ random orders, which 
 yields the best results for the two algorithms.
 The number of different orders is $7!= 5,040$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order.
-Therefore instead of doing $10000$ random draws we could test every possible order in less time.
+Therefore instead of doing $10,000$ random draws we could test every possible order in less time.
 However this method would not be practical with regard to the computation time for $n = 15$.
@@
 Remark that the process is not periodic, therefore we must measure the process time of each route over several periods if we want to compute its maximum.
-We choose to simulate it for $1000$ periods and we have observed that the process time usually stabilizes after $10$ periods.
+We choose to simulate it for $1,000$ periods and we have observed that the process time usually stabilizes after $10$ periods.
 The margin is defined as the maximum process time, computed as explained, minus twice the size of the longest route.
 
-     We draw $1000$ star routed networks with $8$ routes, with weights on the arcs drawn between $0$ and $20,000$.
+     We draw $1,000$ star routed networks with $8$ routes, with weights on the arcs drawn between $0$ and $20,000$.
 Note that the results are almost the same when the arcs are small.
-We measure, for periods from $20000$ (network fully loaded), to $50,000$ ($40 \%$ of load), the median, the first, and the third quartile of the margins computed in $1000$ simulations using FIFO buffer to resolve collisions.
+We measure, for periods from $20,000$ (network fully loaded), to $50,000$ ($40 \%$ of load), the median, the first, and the third quartile of the margins computed in $1,000$ simulations using FIFO buffer to resolve collisions.
 

### 2017-07-24 code/Calculs autres/regression.c

@@ -1,16 +1,16 @@
 #include <stdio.h> 
 #include <stdlib.h>
 #include <math.h>
-#define nb_points 12
+#define nb_points 13
 
 
-int x[nb_points];
-int y[nb_points];
+float x[nb_points];
+float y[nb_points];
 
 
 void lire_fichier(int algo_choisi)
 {
-	FILE * f = fopen("results_periodea.data","r");
+	FILE * f = fopen("../datas/results_periode.data","r");
 
 	int nombre_lu;
 	int colonne=0;
@@ -18,13 +18,16 @@ void lire_fichier(int algo_choisi)
 	while(fscanf(f,"%d",&nombre_lu))
 	{
 		if(colonne == 0)
-			x[ligne] = nombre_lu;
+			x[ligne] = (float)nombre_lu;
 
 		if(colonne == algo_choisi)
-			y[ligne] = nombre_lu;
+		{
+			y[ligne] = (x[ligne]*2500)/((float)nombre_lu);
+			//printf("%f %f \n",x[ligne], y[ligne]);
+		}
 		colonne++;
 
-		if(colonne == 6)
+		if(colonne == 7)
 		{
 			colonne = 0;
 			ligne ++;
@@ -37,20 +40,20 @@ void lire_fichier(int algo_choisi)
 }
 
 
-void affiche_tab(int *tab)
+void affiche_tab(float *tab)
 {
 	printf("[");
 	for(int i=0;i<nb_points;i++)
 	{
 		if(i < nb_points-1)
-			printf("%d;",tab[i]);
+			printf("%f;",tab[i]);
 		else
-			printf("%d]",tab[i]);
+			printf("%f]",tab[i]);
 	}
 	printf("\n");
 }
 
-float moyenne(int * tab)
+float moyenne(float * tab)
 {
 	float moy=0;
 	for(int i =0;i<nb_points;i++)
@@ -59,7 +62,7 @@ float moyenne(int * tab)
 	}
 	return moy/nb_points;
 }
-float variance(int * tab)
+float variance(float * tab)
 {
 	float var = 0;
 	for(int i=0;i<nb_points;i++)
@@ -97,10 +100,10 @@ float coefficient_correlation()
 }
 int main()
 {
-	for(int i=1;i<4;i++)
+	for(int i=1;i<5;i++)
 	{
 		lire_fichier(i);
[…]

### 2017-07-24 infocom/infocom.tex
intro retravaillé et complexité en moins

--- 2017-07-24 infocom/infocom.tex
@@
 Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost ownership.
-The main challenge for this type of architecture is the latency in the transfer process that is an important factor for dimensioning the network.
+The main challenge for this type of architecture is the latency in the periodic transfer process that is an important factor for dimensioning the network.
 The latency is measured between the sending of a message by the Remote Radio Heads (RRHs) on the field and the receptions of the answers, computed by real-time virtualized network functions on Baseband Units (BBUs), in the cloud.
 For example, even if next radio protocols are less stringent, some standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in $3$ms~\cite{bouguen2012lte}.
-The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRHs and BBUs.
-
- In this article, we study mechanisms to deal with the latency and periodicity constraints in the network located between the BUUs and the RRHs called \emph{fronthaul}.
- Statistical multiplexing even with a large bandwidth does not comply with the latency requirements.
-Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits for the fronthaul.
-Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches.
-This architecture is very expensive and hardly scales in the case of a mobile network composed of about $10000$ base stations.
-Here we propose to use a deterministic approach to schedule our periodic messages.
-This approach has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}.
-Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}.
-The aim is to operate a C-RAN on a low-cost shared switched network.
+The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer in the \emph{frontaul} network between RRHs and BBUs.
 
 Let us expose briefly our model: the network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs).
-Time is discretized and a unit of time corresponds to the transmission of a minimal unit of data over the network.
+Time is discretized and a unit of time or slot corresponds to the transmission of a minimal unit of data over the network.
 The process must be  predictable (i.e.
@@
 To ensure that this property is always true we propose a deterministic process.
-We have two sets of parameters that we can choose when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
+We have two sets of values that we can choose when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
 When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods inapplicable.
 Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.
-Moreover the latency must be minimized, that is the time
- between the emission of a message and the complete return of its answer.
+Moreover the latency, that is the time between the emission of a message and the complete return of its answer, must be minimized.
 It means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long.
-
-The problem we focus on here may look like wormhole problems~\cite{cole1996benefit}, but here we want to minimize the time lost in buffers and not just to avoid deadlocks, and we also need to deal with the periodicity.
+The aim is to operate a C-RAN on a low-cost shared switched network.
+The model is also compatible with an optical network with a fixed packet size.
+
+Our main contributions are the following.
+ In Sec.~\ref{sec:def} we propose a model of the network and the periodic sending of messages along its routes  and we introduce the star routed network we study in this article. 
+ We formalize the problem of finding a periodic assignment for sending messages without buffering (\pazl) or with buffering in the processing unit only (\pall) and shows that they are $\NP$-hard even to approximate.
+In Sec.~\ref{sec:PAZL}, we propose two algorithms solving \pazl when the routes between RRHs and BBUs are small or when the load is light.
+Using a compact representation of an assignment, we show that \pazl is fixed parameter tractable when parametrized by the number of antenna on star routed networks.
+Finally in Sec.~\ref{sec:PALL}, we introduce a family of algorithms to solve \pall and our experimentation allows to select one which works extremely well even in very loaded networks.
+In particular we show that the deterministic communication schemes we design vastly outperform the traditional statistical multiplexing with regard to latency.
+
+   \subsection*{Related works}
+
+ Statistical multiplexing even with a large bandwidth does not comply with the latency requirements of C-RAN.
+Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits for the fronthaul.
+Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches.
+This architecture is very expensive and hardly scales in the case of a mobile network composed of about $10000$ base stations.
+The deterministic approach we propose has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}.
+Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}.
+
+The algorithmic problem we focus on may look like wormhole problems~\cite{cole1996benefit}, but  we want to minimize the time lost in buffers and not just to avoid deadlocks.
 Several graph colorings have been introduced to model similar problems such as the allocation of frequencies~\cite{borndorfer1998frequency}, bandwidths~\cite{erlebach2001complexity} or routes~\cite{cole1996benefit} in a network or train schedules~\cite{strotmann2007railway}.
 Unfortunately, they do not take into account the periodicity of the scheduling and the associated problems are already $\NP$-complete.
-The only coloring which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple, zhu2001circular,zhu2006recent} but it is not expressive enough to capture our problem.
-
-Our main contributions are the following.
- In Sec.~\ref{sec:def} we propose a model of the network and the periodic sending of messages along its routes
- and we introduce the star routed network we study in this article. 
- We formalize the problem of finding a periodic assignment for sending messages without buffering (\pazl) or
- with buffering in the processing unit only (\pall) and shows that they are $\NP$-hard even to approximate.
-In Sec.~\ref{sec:PAZL}, we propose two algorithms solving \pazl when the routes between RRHs and BBUs are small
-or when the load is light. Using a compact representation of an assignment, we show that \pazl is fixed parameter tractable when parametrized by the number of antenna on star routed networks.
-Finally in Sec.~\ref{sec:PALL}, we introduce a family of algorithms to solve \pall and our experimentation 
-allows to select one which works extremely well even in very loaded networks.
-In particular we show that the deterministic communication schemes we design vastly outperform the traditional statistical multiplexing with regard to latency.
+The only coloring which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple} but it is not expressive enough to capture our problem.
 
@@
 
-    The {\bf maximum process time} of the assignment $m$ of $(G,{\cal R})$ is defined by $MT(m)=\max\limits_{r \in {\cal R}} PT(r)$. We consider the following decision problem.
+    The {\bf maximum process time} of the assignment $m$ of $(G,{\cal R})$ is defined by $MPT(m)=\max\limits_{r \in {\cal R}} PT(r)$. We consider the following decision problem.
 
@@
 
-      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment $m$ of $(G,{\cal R})$ such that $MT(m) \leq T_{max}$?
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment $m$ of $(G,{\cal R})$ such that $MPT(m) \leq T_{max}$?
 
@@
        In this section, we deal with the problem PAZL on star routed networks.
-Since we want an assignment with waiting times zero, $MT(m)$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
+Since we want an assignment with waiting times zero, $MPT(m)$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
 Moreover choosing the offset $m_r$ of a forward route $r$ also sets the offset of the backward route $\rho(r)$ to $m_{\rho(r)} = m_{r} + \lambda(r) \mod P$.
@@
       \begin{proposition} Let $(G, {\cal R})$ be a star routed network, and let $n\tau + 2(\lambda(r_{n-1}) - \lambda(r_{0})) \leq P$.
-There is a $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with waiting times $0$ given by Shortest-Longest in time $O(n\log(n))$.\label{prop:SL}
+There is a $(P,\tau)$-periodic assignment of $(G, {\cal R})$ with waiting times $0$ given by Shortest-Longest.\label{prop:SL}
       \end{proposition}
@@
        Since $ \lambda(r_{i}) \leq  \lambda(r_{i+1})$ by construction, we have  $2 \lambda(r_{i}) + i\tau -1 < 2 \lambda(r_{i+1}) + (i+1)\tau$ which proves that there are no collision on the backward period.
-
-       The complexity of the algorithm is dominated by the sorting of the routes in $O(n\log(n))$. 
+%        The complexity of the algorithm is dominated by the sorting of the routes in $O(n\log(n))$. 
       \end{proof}
@@
     \begin{proposition}
-    There is a $(P,\tau)$-periodic assignment of a star routed network with waiting times $0$ if the load is less than $1/3$ and it can be found in time $O(n^2)$.
+    There is a $(P,\tau)$-periodic assignment of a star routed network with waiting times $0$ if the load is less than $1/3$.
+%     and it can be found in time $O(n^2)$.
     \end{proposition}
@@
 Since $k < n$, $3n - k -2k \geq 1$, which proves that the algorithm terminates and find a  $(P,\tau)$-periodic assignment.
-
-     This algorithm works with a complexity $O(n^2)$, since for the $k^{\text{th}}$ route we have to try at most $2k$ offsets before finding a correct one.
+%      
+%      This algorithm works with a complexity $O(n^2)$, since for the $k^{\text{th}}$ route we have to try at most $2k$ offsets before finding a correct one.
 We can test the $2k$ offsets of the backward period in time $O(k)$ by maintaining an ordered list of the intervals used by already set routes.
@@
 	 Let $(G,{\cal R})$ be a star routed network with $n$ routes and let $P \geq n\tau$.
-If there is a constant $c$ such that $\forall i < n, \,\omega(s_i,c_s) = c$, then there is a $(P,\tau)$-periodic assignment with process time $2 \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
+If there is a constant $c$ such that $\forall i < n, \,\omega(s_i,c_s) = c$, then there is a $(P,\tau)$-periodic assignment with process time $2\, \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$.
+% 	 and it can be built in time $O(n)$.
 	 \end{theorem}
@@
         period is larger than $n\tau$ (there are no gaps between the messages).
-
-        Now let us compute the process time of the route $r_i$ defined by $PT(r_i) = w_i + 2\lambda(r_{i}) $.
+        The process time of the route $r_i$ defined by $PT(r_i) = w_i + 2\lambda(r_{i}) $.
 We obtain $PT(r_i) = 2\lambda(r_{0})$ and thus the maximum process time of the assignment is also equal to $2\lambda(r_0)$.
-	Finally the complexity is $O(n)$ since we have to find the maximum of the length of the $n$ routes and the computation of each $w_i$ is done by a constant number of arithmetic operations.
+% 	Finally the complexity is $O(n)$ since we have to find the maximum of the length of the $n$ routes and the computation of each $w_i$ is done by a constant number of arithmetic operations.
      \end{proof}
@@
      Remark that we do not deal with the periodicity.
-When MLS finds an assignment $m$ its always satisfies $MT(m) < T_{max}$.
+When MLS finds an assignment $m$ its always satisfies $MPT(m) < T_{max}$.
 On the other hand, it is a $(P,\tau)$ periodic assignment only if $m_{max} - m_{min} \leq P -\tau$ where $m_{max}$ is the largest offset and $m_{min}$ the smallest one.
@@
 Then we modify the deadline of each backward route to be the minimum of their previous deadline and $t + P$.
-We execute this algorithm for every possible first backward route and we return the solution that minimizes $MT(m)$.
+We execute this algorithm for every possible first backward route and we return the solution that minimizes $MPT(m)$.
 Since we run the previous algorithm at most $n$ times, the complexity is in $O(n^3\log(n))$.
 Remark that it finds an assignment more often than MLS, because if MLS finds a solution with first route $r$ and such that $m_{max} - m_{min} \leq P -\tau$, then this solution will be found by PMLS when it selects $r$ as the first route.
-Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment since we guarantee that all messages are scheduled in a period of time of size $P$ and it satisfies $MT(m) < T_{max}$ by construction of the deadlines.
+Moreover when PMLS finds a solution, it is always a $(P,\tau)$ periodic assignment since we guarantee that all messages are scheduled in a period of time of size $P$ and it satisfies $MPT(m) < T_{max}$ by construction of the deadlines.
 Remark that PMLS may fail while there is an assignment.
@@
     We fix the number of routes to $8$ to make comparisons with the results of Section~\ref{sec:exp_PAZL} easier. 
-    We draw uniformly the weights of the arcs between $0$ and $20,000$ slots.
+    We draw uniformly the weights of the arcs between $0$ and $20,000$.
     For a given routed network, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
@@
     In fact the margin represents the latency imposed by the communication process without taking into account the physical length of the network which cannot be changed.
-In our experiments the margin range from  $0$ to $3,000$ slots.
+In our experiments the margin range from  $0$ to $3,000$.
    We look at two different regimes, a medium load of $80\%$ and a high load of $95\%$.
@@
 
+ \section{Conclusion}
+
+ ???????????????
+
 %     \paragraph*{Future works}

### 2017-07-24 infocom/infocom.tex

--- 2017-07-24 infocom/infocom.tex
@@
       \begin{center}
-	 \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{periode_petite.pdf}
+	 \hspace{-0.5cm}\includegraphics[width=0.4\textwidth]{periode_petite.pdf}
       \end{center}
             \vspace{-0.75cm}
-      \caption{Minimum period averaged over $1000$ random instances}\label{fig:short}
+      \caption{Minimum period averaged over $1,000$ random instances}\label{fig:short}
       \end{figure}
@@
 Therefore, we should use it in practical applications with short routes, instead of the exhaustive search which is much more computationally expensive.
-      Finally, note that the greedy algorithm works on average when the load is less than       which is twice better than the theoritical bound.
-This algorithm seems to depends on the load only and not on the number of routes (linear regression).
+      Finally, note that the greedy algorithm works on average when the load is less than $2/3$ which is twice better than the theoretical bound.
+This algorithm seems to depends on the load only and not on the number of routes.
 
@@
        \begin{center}
-      \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{echec_longues.pdf}
+      \hspace{-0.5cm}\includegraphics[width=0.4\textwidth]{echec_longues.pdf}
       \end{center}
             \vspace{-1cm}
-      \caption{Success rate for $8$ routes over $1000$ random instances}\label{fig:long}
+      \caption{Success rate for $8$ routes over $1,000$ random instances}\label{fig:long}
      \end{figure}
@@
           \vspace{-1cm}
-\begin{figure}[h] 
-          \includegraphics[width=0.4\textwidth]{departs_gp_25000.pdf}
-          \vspace{-0.5cm}
-      \caption{Success rate of different orders, $80\%$ load.}
-           \label{fig:success80}
-     \end{figure}
+%\begin{figure}[h] 
+%          \includegraphics[width=0.4\textwidth]{departs_gp_25000.pdf}
+%          \vspace{-0.5cm}
+%      \caption{Success rate of different orders, $80\%$ load.}
+%           \label{fig:success80}
+%     \end{figure}
 
@@
        \begin{center}
-      \includegraphics[width=0.5\textwidth]{retour_21000.pdf}
+      \includegraphics[width=0.4\textwidth]{retour_21000.pdf}
       \end{center}
             \vspace{-1cm}
+
       \caption{Success rate of GD, MLS and PMLS, $95\%$ load}
+
      \label{fig:success21000}
@@
      \end{figure}
+
 First remark that we can improve our previous results by taking $10000$ random orders,
@@
        \begin{center}
-     \hspace{-0.5cm} \includegraphics[width = 0.5\textwidth]{stochastic.pdf}
+     \hspace{-0.5cm} \includegraphics[width = 0.4\textwidth]{stochastic.pdf}
        %\input{figures/stochastic}

### 2017-07-24 infocom/infocom.tex

--- 2017-07-24 infocom/infocom.tex
@@
 Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches.
-This architecture is very expensive and hardly scales in the case of a mobile network composed of about $10000$ base stations.
+This architecture is very expensive and hardly scales in the case of a mobile network composed of about $10,000$ base stations.
 The deterministic approach we propose has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}.
@@
       \begin{figure}[h]
-
       \begin{center}
-	 \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{periode_petite.pdf}
+	 \includegraphics[width=0.47\textwidth]{periode_petite.pdf}
       \end{center}
-            \vspace{-0.75cm}
-      \caption{Minimum period averaged over $1000$ random instances}\label{fig:short}
+      \caption{Minimum period averaged over $1,000$ random instances}\label{fig:short}
       \end{figure}
@@
       We now want to understand the performance of these algorithms when the size of the routes is unbounded.
-In this experiment we fix the number of routes to $8$ and the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30,000$ slots (in the same range as the period).
+In this experiment we fix the number of routes to $8$ and the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $20,000$ slots (in the same range as the period).
 We represent in Fig.~\ref{fig:long} the percentage of success of each algorithm, for load from $100\%$ down to $40\%$.
@@
        \begin{center}
-      \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{echec_longues.pdf}
+      \includegraphics[width=0.47\textwidth]{echec_longues.pdf}
       \end{center}
-            \vspace{-1cm}
-      \caption{Success rate for $8$ routes over $1000$ random instances}\label{fig:long}
+
+      \caption{Success rate for $8$ routes over $1,000$ random instances}\label{fig:long}
      \end{figure}
@@
       The computation time of the exhaustive search is in $O(n!)$ as shown int Th.~\ref{th:FPT}, hence we need to study its scalability when $n$ grows.
-In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30,000$ slots.
+In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $20,000$ slots.
 We chose  $95\%$ of load.
@@
 
-    The greedy algorithm can be made to work in time $O(n\log(n))$. 
-    To do that the set of eligible routes must be maintained in a binary heap
-    to be able to find the one with smallest deadline in time $O(\log(n))$. 
-    To deal with the possible collisions, one can maintain a list of the intervals
-    of time at which a message can be sent on the arc $(c_t,c_s)$. Each time the offset of a 
-    route is fixed an interval is split into at most two intervals in constant time. 
-    Since the algorithm goes over the elements of the list at most twice when doing an insertion
-    or looking for the next free interval, the time needed to maintain it is $O(n)$.
-
+    The greedy algorithm can be made to work in time $O(n\log(n))$ by using a binary heap for the set of eligible routes, and a list to maintain a list of the intervals
+    of time at which a message can be sent on the arc $(c_t,c_s)$.
+%    To do that the set of eligible routes must be maintained in a binary heap
+%    to be able to find the one with smallest deadline in time $O(\log(n))$. 
+%    To deal with the possible collisions, one can maintain a list of the intervals
+%    of time at which a message can be sent on the arc $(c_t,c_s)$. Each time the offset of a 
+%    route is fixed an interval is split into at most two intervals in constant time. 
+%    Since the algorithm goes over the elements of the list at most twice when doing an insertion
+%    or looking for the next free interval, the time needed to maintain it is $O(n)$. 
+%    
 %     
@@
 We also consider the random order, which means we compute $1,000$ random orders and stop as soon one yields an assignment.
-   In Fig.~\ref{fig:success95} and Fig.~\ref{fig:success80}, we represent the success rate of the five kind of orders with regards to the margin.
-The value is an average computed over $10,000$ random star routed networks.
+   In Fig.~\ref{fig:success95} , we represent the success rate of the five kind of orders with regards to the margin. The value is an average computed over $10,000$ random star routed networks.
 
 \begin{figure}[h] 
-
   \centering
-     \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}
-\vspace{-0.75cm}
+    \includegraphics[width=0.5\textwidth]{departs_gp_21000.pdf}
       \caption{Success rate of different orders, $95\%$ load.}
@@
           \end{figure}
-          \vspace{-1cm}
-\begin{figure}[h] 
-          \includegraphics[width=0.4\textwidth]{departs_gp_25000.pdf}
-          \vspace{-0.5cm}
-      \caption{Success rate of different orders, $80\%$ load.}
-           \label{fig:success80}
-     \end{figure}
+
+%\begin{figure}[h] 
+%          \includegraphics[width=0.4\textwidth]{departs_gp_25000.pdf}
+%          \vspace{-0.5cm}
+%      \caption{Success rate of different orders, $80\%$ load.}
+%           \label{fig:success80}
+%     \end{figure}
 
      According to our experiments, sending the messages from the shortest to the longest route or arc does not work well.
-It corresponds to the policy of Prop.~\ref{prop:SL} which we already know to be bad for \pazl when the routes are long as it is the case in this experiment.
+It corresponds to the policy of Prop.~\ref{prop:SL} which we already know to be bad for \pazl when the routes are long as in this experiment.
 Sending from the longest to the shortest route or arc works better and it seems that sorting the routes according to the length of the last arc rather than the route is better, at least in a loaded network.
 
-     The random order is the best by far.
-When the load is $80\%$ there is always a solution with margin $0$.
-Note that, when disallowing waiting times, there were instances without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the \pall problem.
+     The random order is the best by far: with a load of $95\%$, there is solution with margin $0$ most of the time.
+Note that, when disallowing waiting times, there were no instances with an asignment for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the \pall problem.
 We now want to compare the performances of the three different algorithms used in the second stage.
@@
     \begin{figure} [h] 
-      \vspace{-0.5cm}
        \begin{center}
@@
       \end{center}
-            \vspace{-1cm}
       \caption{Success rate of GD, MLS and PMLS, $95\%$ load}
      \label{fig:success21000}
-       \vspace{-0.2cm}
+
      \end{figure}
@@
 We investigate the success rate of our algorithm with regards to the number of random orders drawn, a load of $95\%$ and a margin $0$.
-The following tables presents the average success rate for each number of sending orders, on $1,000$ instances, for GD and PMLS.
+The following tables presents the average success rate for each number of sending orders, on $10,000$ instances, for GD and PMLS.
          \begin{figure}[h] 
@@
     \hline
-  PMLS & $41.1$ &$82.5$&$94.5$&$96.2$&$97.2$&$97.2$\\
+  PMLS & $38.9$ &$83.0$&$95.3$&$97.2$&$97.5$&$97.7$\\
     \hline
@@
      \end{figure}
-First remark that we can improve our previous results by taking $10000$ random orders,
-instead of $1000$.
+
+First remark that we can improve our previous results by taking $10,000$ random orders,
+instead of $1,000$.
 The number of different orders is $7!= 5,040$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order.
-Therefore instead of doing $10000$ random draws we could test every possible order in less time.
+Therefore instead of doing $10,000$ random draws we could test every possible order in less time.
 However the computation time of this method would scale badly with $n$.
@@
 Remark that the process is not periodic, therefore we must measure the process time of each route over several periods if we want to compute its maximum.
-We choose to simulate it for $1000$ periods and we have observed that the process time usually stabilizes after $10$ periods.
+We choose to simulate it for $1,000$ periods and we have observed that the process time usually stabilizes after $10$ periods.
 The margin is defined as the maximum process time, computed as explained, minus twice the size of the longest route.
@@
 Note that the results are almost the same when the arcs are small.
-We measure, for load from $100\%$ down to $40\%$, the median, the first, and the third quartile of the margins computed in $1000$ simulations using FIFO buffer to resolve collisions.
+We measure, for load from $100\%$ down to $40\%$, the median, the first, and the third quartile of the margins computed in $1,000$ simulations using FIFO buffer to resolve collisions.
 
@@
  \section{Conclusion}
-
- ???????????????
+In this paper, we proposed two kinds of solution to ensure a low latency for C-RAN in fronthaul networks.
+First, we can find some assignments without buffering the messages in the BBUs when the routes are short, by the shortest longest policy, or when the load of the network is small, with the greedy algorithm.
+The experience with the FPT algorithm shown that there is some instances when the network is highly loaded in which we need to use some buffers in BBU.
+Thus, we developed the PMLS algorithm, that gives some assignments even with restricted parameters.
+
+The future work is to adapt the main ideas of those algorithm to others common networks topologies, like an optical ring, or a tree.
 

### 2017-07-24 infocom/infocom.tex
reprise conclusion

@@
 Unfortunately, they do not take into account the periodicity of the scheduling and the associated problems are already $\NP$-complete.
-The only coloring which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple} but it is not expressive enough to capture our problem.
+The only coloring with periodicity is the circular coloring~\cite{zhou2013multiple} but it is not expressive enough to capture our problem.
 
@@
      \label{fig:success21000}
-
      \end{figure}
+
      The MLS algorithm performs poorly, worst than GD and PMLS, which shows that \emph{taking into account the periodicity is fundamental}.
@@
     \begin{figure}
-
        \begin{center}
-     \hspace{-0.5cm} \includegraphics[width = 0.4\textwidth]{stochastic.pdf}
+      \includegraphics[width = 0.45\textwidth]{stochastic.pdf}
        %\input{figures/stochastic}
@@
  \section{Conclusion}
-In this paper, we proposed two kinds of solution to ensure a low latency for C-RAN in fronthaul networks.
-First, we can find some assignments without buffering the messages in the BBUs when the routes are short, by the shortest longest policy, or when the load of the network is small, with the greedy algorithm.
-The experience with the FPT algorithm shown that there is some instances when the network is highly loaded in which we need to use some buffers in BBU.
-Thus, we developed the PMLS algorithm, that gives some assignments even with restricted parameters.
-
-The future work is to adapt the main ideas of those algorithm to others common networks topologies, like an optical ring, or a tree.
+In this paper, we proposed two deterministic methods to establish a low latency periodic communication between BBUs and RRHs in 
+a star shaped fronthaul network.
+The first method uses no buffering and has no latency overhead.
+It works when the routes are short (Longest-Shortest policy) or when the load is less than $80\%$ (Exhaustive search of compact assignments).
+When the load is higher, buffering is allowed in the BBUs and we are able to find a determinstic communication scheme 
+with no additionnal latency most of the time using our PMLS algorithm. 
+We plan to study other commons fronthaul topologies such as caterpillars, trees or ring; the latter being different since 
+the forward and backward routes are not symmetric.
+For other applications, it could be interesting to to optimize the average latency of the routes rather than the worst latency, a problem which could be solved using linear optimization.
 

### 2017-07-25 infocom/infocom.tex
modifs olivier + version longue

@@
 \author{}
+
+%\author[1]{Dominique Barth}
 %\author[1]{Ma\"el Guiraud}
-%\author[1]{Dominique Barth}
 % \author[1]{Christian Cad\'er\'e}
@@
 
-\section{Introduction}
-
-Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost ownership.
+%\section{Introduction}
+%
+%Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost ownership.
 The main challenge for this type of architecture is the latency in the periodic transfer process that is an important factor for dimensioning the network.
@@
 The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer in the \emph{frontaul} network between RRHs and BBUs.
-
-Let us expose briefly our model: the network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs).
+%
+%Let us expose briefly our model: the network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs).
 Time is discretized and a unit of time or slot corresponds to the transmission of a minimal unit of data over the network.
@@
 
+\section{Introduction}
+
+Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost of ownership.
+The main challenge for this type of architecture is to reach a latency compatible with transported protocols.
+The latency is measured between the sending of a message by the Remote Radio Heads (RRHs) on the field and the receptions of the answers, computed by real-time virtualized network functions of BaseBand Units (BBUs), in the cloud.
+For example, LTE standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in $3$ms~\cite{bouguen2012lte}.
+In 5G, some services need end to end latency as low as 1ms~\cite{3gpp5g}.
+The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer in the \emph{frontaul} network between RRHs and BBUs: frames need to be emitted and received every milliseconds~\cite{bouguen2012lte}.
+Our aim is to operate a C-RAN on a low-cost shared switched network.
+The question we address is the following : is it possible to schedule messages emission such that there is no collision, then no buffering nor latency corresponding to queuing delays ?
+
+Let us expose briefly our model: the network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs).
+Time is discretized and a unit of time or slot corresponds to the transmission of a minimal unit of data over the network.
+The process must be  predictable (i.e.
+the date of arrival of packets is known beforehand).Following LTE standard~\cite{bouguen2012lte}, in this article we assume that the process is periodic.
+That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
+As we want to avoid any  buffering in internal nodes of the graph.
+Hence we need to design a periodic process with no collision between messages.
+To ensure that this property is always true we propose a deterministic process.
+We have two sets of values that we can choose when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
+When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods inapplicable.
+Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.The latency, that is the time between the emission of a message and the complete return of its answer, must be minimized: this lefts budget for other latency causes, and leads to larger fiber lengths, then wider deployment areas.This means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long.
+Note that the
+model is technology agnostic, i.e. it is compatible with an optical network with a fixed packet size.
+
+\footnote{Others terminologies and functional splits exist in the literature.
+We choose the most classical one for sake of clarity.
+The results of this work is fully compatible with any C-RAN architecture definition.}
+
 Our main contributions are the following.
- In Sec.~\ref{sec:def} we propose a model of the network and the periodic sending of messages along its routes  and we introduce the star routed network we study in this article. 
+ In Sec.~\ref{sec:def} we propose a model of the network and the periodic sending of messages along its routes  and we introduce the star routed network that we study in this article. 
  We formalize the problem of finding a periodic assignment for sending messages without buffering (\pazl) or with buffering in the processing unit only (\pall) and shows that they are $\NP$-hard even to approximate.
@@
 Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches.
-This architecture is very expensive and hardly scales in the case of a mobile network composed of about $10,000$ base stations.
+This architecture is very expensive and hardly scales in the case of a mobile network composed of tenths of thousands of deployment sites.
 The deterministic approach we propose has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}.
@@
 
-         A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a function which associate to each route 
+         A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a function that associates to each route 
          $r \in \cal R$ its \textbf{offset} $m_r$ that is the time at which a message is emitted at the first vertex of the route $r$.
@@
 %       However, since all messages are of size $\tau$, it will not change the problems we consider in the rest of the article.
-      Finally, we should add to the process time the computation time a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
+      Finally, we should add to the process time the computation time that a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
 
@@
 In fact, if we do the previous experiment
-      for short routes but with long routes, we find that, on average, the greedy algorithm finds a solution when the load is less than $53\%$.
+      for short routes but with long routes, we find that, on average, the greedy algorithm finds a solution when the load is less than $59\%$.
 
@@
      The random order is the best by far: with a load of $95\%$, there is solution with margin $0$ most of the time.
-Note that, when disallowing waiting times, there were no instances with an asignment for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the \pall problem.
+Note that, when disallowing waiting times, there were no instances with an assignment for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the \pall problem.
 We now want to compare the performances of the three different algorithms used in the second stage.
@@
       \vspace{-1cm}
-      \caption{First and third quartile of the margin of statistical multiplexing}
+      \caption{Cumulative distribution of the margin of statistical multiplexing}
       \label{fig:sto}

### 2017-07-25 code/Sources/main.c

@@ -17,7 +17,7 @@ int main()
 	/*****
 	Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
 	*****/
-	//simuls_periode_PAZL(12,2500,700,1000);
+	//simuls_periode_PAZL(8,2500,700,1000);
 
 	/******************************************/	
 
@@ -43,7 +43,7 @@ int main()
 	/*****
 	Taux de reussite de départ PALL avec un retour GP sur une periode donnée (on fait varier la marge)
 	*****/
-	//sucess_aller_PALL(8,2500,20000,3000,10000,21052);
+	sucess_aller_PALL(8,2500,20000,3000,10000,25000);
 
 
 
@@ -71,7 +71,7 @@ int main()
 	Tmax moyen pour sto vs sp
 	*******/
 
-	marge_PALL_stochastique(8,2500,20000,1000,50000);
+	//marge_PALL_stochastique(8,2500,20000,1000,50000);
 
 
 

### 2017-07-25 code/Sources/simulations.c

@@ -46,7 +46,8 @@ void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,in
 			}
 			//else printf("error (3nt = -1)\n");
 
-			res_brute = linear_brute(g,taille_message);
+			//res_brute = linear_brute(g,taille_message);
+			res_brute = 1;
 			//if(res_brute > total_brute)total_brute = res_brute;
 			if(res_brute != -1){
 				#pragma omp atomic
@@ -61,7 +62,8 @@ void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,in
 				total_sl+=res_sl;
 			}
 			//else printf("error (Sl = -1)\n");
-			res_search = linear_search(g,taille_message);
+			//res_search = linear_search(g,taille_message);
+			res_search = 1;
 			//res_brute = res_search;
 			//if(res_sl > total_sl)total_sl = res_sl;
 			if(res_search != -1){

### 2017-07-26 infocom/infocom_long.tex
intro olivier

--- 2017-07-25 infocom/infocom.tex
@@
 
-%\section{Introduction}
-%
-%Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost ownership.
-The main challenge for this type of architecture is the latency in the periodic transfer process that is an important factor for dimensioning the network.
-The latency is measured between the sending of a message by the Remote Radio Heads (RRHs) on the field and the receptions of the answers, computed by real-time virtualized network functions on Baseband Units (BBUs), in the cloud.
-For example, even if next radio protocols are less stringent, some standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in $3$ms~\cite{bouguen2012lte}.
-The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer in the \emph{frontaul} network between RRHs and BBUs.
-%
-%Let us expose briefly our model: the network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs).
-Time is discretized and a unit of time or slot corresponds to the transmission of a minimal unit of data over the network.
-The process must be  predictable (i.e.
-the date of arrival of packets is known beforehand).
-For simplicity, in this article we assume that the process is periodic.
-That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
-Moreover, we want to avoid any  buffering in internal nodes of the graph.
-Hence we need to design a periodic process with no collision between messages.
-To ensure that this property is always true we propose a deterministic process.
-We have two sets of values that we can choose when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
-When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods inapplicable.
-Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.
-Moreover the latency, that is the time between the emission of a message and the complete return of its answer, must be minimized.
-It means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long.
-The aim is to operate a C-RAN on a low-cost shared switched network.
-The model is also compatible with an optical network with a fixed packet size.
-
 \section{Introduction}
@@
 
-\footnote{Others terminologies and functional splits exist in the literature.
-We choose the most classical one for sake of clarity.
-The results of this work is fully compatible with any C-RAN architecture definition.}
-
 Our main contributions are the following.
- In Sec.~\ref{sec:def} we propose a model of the network and the periodic sending of messages along its routes  and we introduce the star routed network that we study in this article. 
- We formalize the problem of finding a periodic assignment for sending messages without buffering (\pazl) or with buffering in the processing unit only (\pall) and shows that they are $\NP$-hard even to approximate.
-In Sec.~\ref{sec:PAZL}, we propose two algorithms solving \pazl when the routes between RRHs and BBUs are small or when the load is light.
-Using a compact representation of an assignment, we show that \pazl is fixed parameter tractable when parametrized by the number of antenna on star routed networks.
-Finally in Sec.~\ref{sec:PALL}, we introduce a family of algorithms to solve \pall and our experimentation allows to select one which works extremely well even in very loaded networks.
-In particular we show that the deterministic communication schemes we design vastly outperform the traditional statistical multiplexing with regard to latency.
+ In Sec.~\ref{sec:def} we propose a model of the network and the periodic sending of messages along its routes
+ We then formalize our two problems of finding a periodic assignment for sending messages without collisions: PRA (sending of the message only) and PALL (sending of the message and of the answer).  
+In Sec.~\ref{sec:complexity}, we prove that the problem PRA and PALL are $\NP$-hard and cannot be approximated even for very
+restricted classes of graphs. 
+Therefore in the next two sections, we study a simple but very common topology, that we call the
+star routed network, where all messages can collide on a single arc.
+In Sec.\ref{sec:PAZL}, we study a variant of PALL called PAZL  where the waiting times must all be zero.
+We provide several algorithms, some of their theoretical properties and give experimental evidences that they find periodic assignments when the network is not too loaded.
+Finally in Sec.\ref{sec:PALL}, we propose algorithms for the general PALL problem and exhibit one which works extremely well in our experiments even in loaded networks.
+In particular we show that the deterministic communication schemes we design largely outperform the traditional stochastic multiplexing with regard to latency.
 
@@
 Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches.
-This architecture is very expensive and hardly scales in the case of a mobile network composed of tenths of thousands of deployment sites.
+This architecture is very expensive and hardly scales in the case of a mobile network composed of about $10,000$ base stations.
 The deterministic approach we propose has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}.
@@
 The network is modeled as a directed graph $G=(V,A)$.
-Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time taken by a message to go from $u$ to $v$ using this arc.
-A {\bf route} $r$ in $G$ is a path, that is, a sequence of adjacent vertices $u_0, \ldots , u_{k}$, with $(u_i,u_{i+1}) \in A$.
-The {\bf latency} of a vertex $u_i$ in a path $r$ is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} \omega(u_j, u_{j+1})$.
-% We also define $\lambda(u_0,r)=0$. 
+Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time slots taken by a signal to go from $u$ to $v$ using this arc.
+A {\bf route} $r$ in $G$ is a path, that is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.
+The {\bf latency} of a vertex $u_i$ in a path $r$, with $i \geq 1$, is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} \omega(u_j, u_{j+1})$.
+We also define $\lambda(u_0,r)=0$.
 The length of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
@@
 
-   In the context of cloud-RAN applications, we need to send message from a RRH $u$ to a BBU $v$ and then 
-      we must send the answer from $v$ back to $u$. Therefore we assume that all considered routed networks 
-      are \emph{symmetric}, that is for every arc $(u,v)$ there is an arc $(v,u)$ with the same weight.
-      We define the function $\rho$ which associates to a route $r = u_0,\dots,u_k$ the symmetric route $\rho(r) = u_k,\dots,u_0$.
-      The set ${\cal R}$ is partitioned into $F$ and $B$ such that $\rho$ is a bijection from $F$ to $B$.
-      The routes of $F$ are called \textbf{forward} routes and those of $B$ are called \textbf{backward} routes.
-%       
-%       We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of forward routes and $B$ of backward routes.
-Moreover there is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
-%       In all practical cases the routes $r$ and $\rho(r)$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we need not to enforce this property.
-
    \subsection{Messages dynamic}
 
-      In the process we study, a message is sent on each route at each period, denoted by $P$.
-      Let $r$ be a route, if a message is sent at time $m$ from $s$ the first vertex of $r$ then it will arrive at vertex $v$ in $r$ at time $m + \lambda(v,r)$.
-Since the process is periodic, if we look at the messages going through an arc between time $0$ and $P-1$, then we see the same messages in the same order and position between time $kP$ and $(k+1)P -1$ for all $k$.
-      Therefore, the first time slot at which a message sent at time $m$ on $r$ reaches a vertex $v$ in $r$ is $t(v,r) = m + \lambda(v,r) \mod P$.
+      Consider a route $r$, if a message is sent at time $m$ from $s$ the first vertex of $r$ then it will arrive at vertex $v$ in $r$ at time $m + \lambda(v,r)$.
+In our problem, we send one message on each route periodically and we denote the period by $P$.
+      Periodicity means that if we look at the messages going through an arc between time $0$ and $P-1$, then we would observe the same messages in the same order and position between time $kP$ and $(k+1)P -1$ for all $k$.
+      Therefore, we will always consider a period of $P$ discrete slots of time at each arc to characterize the working of the network.
+We define the first time slot at which a message sent from the first vertex of $r$ will reach a vertex $v$ in $r$ by $t(v,r) = m + \lambda(v,r) \mod P$.
 
@@
 
-         A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a function that associates to each route 
-         $r \in \cal R$ its \textbf{offset} $m_r$ that is the time at which a message is emitted at the first vertex of the route $r$.
-\emph{No pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
-	 An assignment represents the following process: first a message is sent at $u$, through the forward route $r$, at time $m_r$.
+      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  $m=(m_0, \ldots ,m_{n-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
+The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
+We will always consider that the $m_{i}$ are between $0$ and $P-1$.
+Moreover, \emph{no pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
+
+      As an example of a $(2,1)$-periodic assignment, let us consider a routed network 
+      where all pairs of routes intersect at a different arc.
+It is easy to design such a network and an example is given in Fig.~\ref{fig:example}.
+We set $\tau = 1$ and the weights are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.
+There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.
+
+      \begin{figure}[ht]
       \begin{center}
-     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{rrh.pdf}
+          \scalebox{0.47}{
+
+\begin{tikzpicture}
+
+\tikzset{
+  LabelStyle/.style = { rectangle, rounded corners, draw,
+                       font = \bfseries },
+  EdgeStyle/.append style = {->} }
+  \SetGraphUnit{5}
+  \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
+  \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
+  \node[draw,circle] (s1) at (0, 6) {$s_0$};
+
+  \node[draw,circle] (t3) at (14, 7) {$t_2$}; 
+  \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
+  \node[draw,circle] (t1) at (10, 2) {$t_0$};
+
+  \SetVertexNoLabel
+  \Vertex[x=2,y=5]{A}
+  \Vertex[x=4,y=5]{B}
+  \Vertex[x=10,y=5]{C}
+  \Vertex[x=12,y=5]{D}
+  \Vertex[x=6,y=3]{E}
+  \Vertex[x=8,y=3]{F}
+  \tikzset{
+  EdgeStyle/.append style = {green} }
+  \Edge[label = 2](s2)(A)
+  \Edge[label = 1](A)(B)
+  \Edge[label = 2](B)(C)
+  \Edge[label = 1](C)(D)
+  \Edge[label = 1](D)(t2)
+
+   \tikzset{
+  EdgeStyle/.append style = {red} }
+  \Edge[label = 2](s3)(E)
+  \Edge[label = 1](E)(F)
+  \Edge[label = 1](F)(C)
+  \Edge[label = 1](C)(D)
+  \Edge[label = 1](D)(t3) 
+     \tikzset{
+  EdgeStyle/.append style = {blue} }
+  \Edge[label = 1](s1)(A)
+  \Edge[label = 1](A)(B)
+  \Edge[label = 1](B)(E)
+  \Edge[label = 1](E)(F)
+  \Edge[label = 1](F)(t1)
+
+\end{tikzpicture}
+
+}
+     \end{center}
+       \caption{A routed network with $(0,0,0)$ as a $(2,1)$-periodic assignment}
+       \label{fig:example}
+      \end{figure}
+
+      \subsection{Periodic route assignment}\label{nonmonotone}
+
+    We want to find an assignment which allows to send periodic messages from sources to targets
+    without collisions. We introduce the following associated decision problem, useful for hardness proofs.
+
+      \noindent {\bf  Periodic Routes Assignment (PRA)}
+
+      \noindent {\bf Input:} a routed network $(G,\cal R)$, an integer $\tau$ and an integer $P$.
+
+      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment of $(G,\cal R)$ ?
+
+      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
+      In fact, approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic assignment is already hard.
+
+      An unusual property of assignment is that given a routed network, we may have a $(P,\tau)$-periodic assignment but no
+      $(P',\tau)$-periodic assignment with $P' > P$: the existence of an assignment is not monotone with regard to $P$.
+
+	\begin{lemma} \label{lemma:monotonic}
+	 For any odd $P$, there is a routed network such that there is $(2,1)$-periodic assignment but no $(P,1)$-periodic assignment.
+	\end{lemma}
+\begin{proof}
+
+      Consider the routed network $(G,{\cal R})$ given in the previous subsection. 
+      We change the weights so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
+      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$.
+In such a graph, there is no $(P,\tau)$-periodic assignment, since the problem reduces to finding a $P$-coloring in a complete graph with $n > P$ vertices, the colors being the offsets of the routes.\\
+      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic assignment of ${\cal R}$.      
+\end{proof}
+
+      \subsection{Periodic assignment for low latency}
+      In the context of cloud-RAN applications, we need to send message from a RRH $u$ to a BBU $v$ and then 
+      we must send the answer from $v$ back to $u$.
+We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of forward routes and $B$ of backward routes.
+Moreover there is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
+In all practical cases the routes $r$ and $\rho(r)$ will be the same with the orientation of the arcs reversed, which corresponds to bidirectional links in the networks, but we need not to enforce this property.
+
+         We now give a new interpretation of a $(P,\tau)$-periodic assignment of a $(G,{\cal R})$ symmetric routed network, so that it represents the sending of a message and of its answer.
+	This assignment represents the following process: first a message is sent at $u$, through the route $r \in F$, at time $m_r$.
+
+      \begin{center}
+      \includegraphics[width=0.47\textwidth]{rrh.pdf}
       \end{center}
@@
        \begin{center}
-     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{BBU.pdf}
+      \includegraphics[width=0.47\textwidth]{BBU.pdf}
       \end{center}
@@
       In the process time, we count the time between the first time at which a message is emitted and the first time at which the message comes back.
-%       Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
-%       However, since all messages are of size $\tau$, it will not change the problems we consider in the rest of the article.
-      Finally, we should add to the process time the computation time that a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
-
-      \subsection{Periodic assignment for low latency}
+Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
+      However, since all messages are of size $\tau$, it will not change the problems we consider in the rest of the article.
+      Finally, we could add to the process time the computation time a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
 
@@
 
-      \noindent {\bf Periodic Assignment for Low Latency (\pall)}
-
-      \noindent {\bf Input:}  A routed network $(G,{\cal R})$, the integers $P$, $\tau$ and $T_{max}$.
+      \noindent {\bf Periodic Assignment for Low Latency (PALL)}
+
+      \noindent {\bf Input:}  A symmetric routed network $(G,{\cal R})$, the integers $P$, $\tau$ and $T_{max}$.
 
@@
 
-%       In Sec.~\ref{sec:\pall} we will study algorithms which solve the search version of \pall (computing an assignment), also denoted by \pall for simplicity. \todo{phrase utile finalement ?} 
-      It turns out that the problem \pall is hard to solve for \emph{general} routed networks.
-The long version of this article contains complete proofs of the $\NP$-hardness or hardness of approximation of \pall and of several of its variants.
+      As a consequence of the $\NP$-hardness of PRA, we show in the next subsection that this problem is $\NP$-hard. 
+      In Sec.~\ref{sec:PALL} we will study heuristics which try to solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity.
+
+      The following table summarize the main notations used in the paper.
+      \begin{center}
+   \begin{tabularx}{0.5\textwidth}{|c|X|}
+    \hline
+     $(G,\cal R)$ & Routed network \\
+     \hline
+      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
+      \hline
+      $\lambda(u_i,r)$ & Latency of the vertex $u_i$ in $r$\\
+         \hline
+         $\lambda(r)$ & Length of the route $r$\\
+         \hline
+         $P$ & Period\\
+         \hline
+         $\tau$ & Size of a message\\
+         \hline
+         $ [t(v,r)]$& Set of time slots used by route $r$ at vertex $v$ \\
+         & in a period $P$\\
+         \hline 
+         $m=(m_0, \ldots ,m_{n-1})$& Assignment: an offset for each route\\
+              \hline 
+         $w_r$& Waiting time of the route $r$\\
+            \hline 
+         $PT(r)$& Process time of the route $r$\\
+           \hline 
+         $MPT(m)$& Maximum process time of the assignment\\
+    \hline
+
+      \end{tabularx}
+      \end{center}
+
+\section{Hardness of PRA}
+  \label{sec:complexity}
+
+ In this section we always assume that the size of a message $\tau$ is equal to one. 
+ We will prove the hardness of PRA and PALL for $\tau =1$ which implies the hardness of the general problems. 
+Consider an instance of the problem PRA, i.e., a routed network $(G,\cal{R})$ and a period $P$.
+The {\bf conflict depth} of a route is the number of arcs of the route which also belong to other routes.
+The conflict depth of a routed network $(G,\cal{R})$ is the maximum of the conflict depth of its routes.
+The {\bf load} of a routed network is the maximal number of routes sharing the same arc.
+Remark that a $(P,1)$-periodic assignment must satisfy that $P$ is larger or equal to the load.
+
+We give two alternate proofs that PRA is $\NP$-complete.
+The first proof works already for conflict depth two. Remark that for conflict depth one,
+the graph can be seen as a set of disjoint pair of routes, on which PRA and PALL can be solved in linear time. 
+ The second proof reduces the problem to graph coloring and implies inapproximability when one tries to find the smallest possible $P$. \\
+ Finally, it is easy to see that PRA is easy on trees and it may be interesting to study its complexity on 
+ bounded treewidth networks, since it is a common property of real networks~\cite{de2011treewidth}.
 
  \begin{theorem}
-Problem \pall is $\NP$-complete.
+Problem PRA is $\NP$-complete on the class of routed networks with conflict depth two.
 \end{theorem}
-
-\noindent \emph{Sketch of proof:}
- First, by a symmetry argument, the problem of finding an assignment with no collisions for the forward routes only
- can be reduced to \pall.
- We fix $\tau$ the size of messages to $1$ and we reduce the problem of $k$-coloring to the 
- problem of finding an assignment without collisions for the forward routes.
- Let $H$ be a graph instance of the $k$-coloring problem, from it we build a routed network $(G,{\cal R})$. 
- For each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
+ \begin{proof}
+ Problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of arcs whether there are collisions.
+
+  Let $H=(V,E)$ be an undirected graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is arc-colorable
+  with $d$ or $d+1$ colors.
+The arc coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness.
+To do that, we define from $H$ a routed network $(G,{\cal R})$ as follows.
+  The vertices of $G$ are $v_1, v_2$ for each $v$ in $V$ and $s_{u,v}, t_{u,v}$ for each $(u,v) \in E$.
+  For each arc $(u,v) \in E$, there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
+
+   To define ${\cal R}$ an arbitrary orientation of each arc $(u,v)$ is chosen. 
+   Then for each arc $(u,v)$ there is a route $s_{u,v},u_1,u_2,v_1,v_2,t_{u,v}$ in ${\cal R}$.
+  All these arcs are of weight $0$. The set of arcs of G is the union between all the arcs of the previously defined routes.
+
+  Observe that the existence of a $d$-coloring of $H$ is equivalent to the existence of a $(d,1)$-periodic assignment
+  of $(G,{\cal R})$. Indeed, a $d$-coloring of $H$ can be seen as a labeling of its arcs by the integers
+  in $\{0,\dots,d-1\}$ and we have a bijection between $d$-colorings of $H$ and offsets of the routes of ${\cal R}$.
+  By construction, the constraint of having no collision between the routes is equivalent to the fact that no two adjacent arcs have the same color.
+Therefore we have reduced arc coloring to PRA by a polynomial time transformation which concludes the proof.
+ \end{proof}
+
+ Remark that we have used zero weights in the proof. If we ask the weights to be strictly positive, which makes sense in our model since
+they represent the delay of physical links, it is easy to adapt the proof.
+We just have to set them so that in any route the weight at $u_1$ is equal to $d$ and thus equal to $0$ modulo $d$.
+We now lift this hardness result to the problem PALL.
+
+\begin{corollary}
+Problem PALL is $\NP$-complete on the class of routed networks of conflict depth two.
+\end{corollary}
+\begin{proof}
+ We consider $((G,{\cal R}),P,\tau)$ an instance of $PRA$.
+We assume that no vertex is the first of some route and the last of another one.
+Remark that this condition is satisfied in the previous proof, which makes the problem $PRA$ restricted to this kind of instance $\NP$-complete.
+ Let us define $T_{max} = 2 \times \max_{r \in {\cal R}} \lambda(r) + P$.
+We define $(G',{\cal R}')$ a symmetric routed network from $(G,{\cal R})$ where for every route we add a symmetric route with new arcs of opposite orientation and the same weights.
+ We prove that the instance $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL if and only if $((G,{\cal R}),P,\tau)$ is in $PRA$.
+ If $((G',{\cal R'}),P,\tau,T_{max})$ is in PALL, then a $(P,\tau)$-assignment of $(G',{\cal R'})$ restricted to $\R$ is a $(P,\tau)$-assignment of $((G,{\cal R})$ since they cannot be any collision between routes of ${\cal R}$.
+
+ Assume now that $((G,{\cal R}),P,\tau)$ is in $PRA$.
+First remark that the waiting time of each route is by definition less than $P$ and thus the maximal process time is always less than $T_{max}$, therefore the constraint on $T_{max}$ is satisfied.
+Moreover a $(P,\tau)$-assignment of $(G,{\cal R})$ can be extended into a $(P,\tau)$-assignment of $(G',{\cal R'})$ in the following way.
+For each route $r \in \cal{R}$ of last vertex $v$, the time at which the message arrives is $t(v,r)$, then we choose as offset for $\rho(r) \in \cal{R}'$ $-t(v,r) \mod P$.
+The symmetry ensures that each new route $\rho(r)$ in ${\cal R'}$ uses exactly the same times slot as $r$ one each of its node and thus avoid collisions.
+\end{proof}
+
+Let MIN-PRA be the problem, given a routed network and an assignment, to find the minimal period $P$ such that there is a $P$-periodic assignment.
+
+\begin{theorem}\label{th:inapprox}
+If $\P \neq \NP$, problem MIN-PRA on the classes of routed networks of load two cannot be approximated in polynomial time within a factor $n^{1-o(1)}$ where $n$ is the number of routes.
+\end{theorem}
+
+\begin{proof}
+ We reduce graph coloring to PRA. Let $H$ be a graph instance of the $k$-coloring problem. 
+ We define ${\cal R}$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in ${\cal R}$.
  Two routes $r_v$ and $r_u$ share an arc if and only if $(u,v)$ is an arc in $H$; this arc is the only one shared by these two routes.
 All arcs are of weight $0$.
+Note that it is easy to build a graph with such routes as in Fig.~\ref{fig:reduction}.
+
  Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic assignment in $G$, 
- by converting an offset of a route into a color of a vertex and reciprocally. \qed
-
-       We also consider a simpler version of \pall, that we call {\bf Periodic Assignment for Zero Latency} or \pazl: we ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$}.
-We introduce \pazl because it is simpler to study and we are able to prove theoretical results and find better algorithms than for \pall.
-As we  experimentally show in Sec.~\ref{sec:exp_PAZL}, this problem can often be solved positively albeit less often than the general problem.
-Finally, a solution to \pazl is simpler to implement in real telecommunication networks, since we do not need any buffering at all.
+ by converting an offset of a route into a color of a vertex and reciprocally.
+Therefore if we can approximate the minimum value of $P$ within some factor, we could approximate the minimal number of colors needed to color a graph within the same factor.
+The proof follows from the hardness of approximability of finding a minimal coloring~\cite{zuckerman2006linear}.
+\end{proof}
+
+In particular, this reduction shows that even with small maximal load, the minimal period can be large.
+
+    \begin{figure}[ht]
+    \centering
+    \scalebox{0.37}{
+    \begin{tikzpicture}
+    \tikzset{
+      LabelStyle/.style = { rectangle, rounded corners, draw,
+			  font = \bfseries },
+      EdgeStyle/.append style = {->} }
+      \SetGraphUnit{5}
+
+      \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
+      \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
+      \node[draw,circle] (s1) at (0, 6) {$s_0$};
+
+      \node[draw,circle] (t3) at (12, 3) {$t_2$}; 
+      \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
+      \node[draw,circle] (t1) at (10, 2) {$t_0$};
+
+      \tikzstyle{VertexStyle}=[shape = circle, draw, minimum size = 20pt]
+	\tikzset{
+      VertexStyle/.append style = {blue} }
+	\Vertex[x=-8,y=3]{1}
+	      \tikzset{
+      VertexStyle/.append style = {green} }
+	  \Vertex[x=-7,y=5]{2}
+
+	    \tikzset{
+      VertexStyle/.append style = {red} }
+	  \Vertex[x=-6,y=4]{3}
+		\tikzset{
+      VertexStyle/.append style = {black} }
+
+      \SetVertexNoLabel
+      \Vertex[x=2,y=5]{A}
+      \Vertex[x=4,y=5]{B}
+      \Vertex[x=10,y=5]{C}
+      \Vertex[x=12,y=5]{D}
+      \Vertex[x=6,y=3]{E}
+      \Vertex[x=8,y=3]{F}
+      \tikzset{
+      EdgeStyle/.append style = {green} }
+      \Edge(s2)(A)
+      \Edge(A)(B)
+      \Edge(B)(C)
+      \Edge(C)(D)
+      \Edge(D)(t2)
+
+      \tikzset{
+      EdgeStyle/.append style = {red} }
+      \Edge(s3)(E)
+      \Edge(E)(F)
+      \Edge(F)(t3) 
+	\tikzset{
+      EdgeStyle/.append style = {blue} }
+      \Edge(s1)(A)
+      \Edge(A)(B)
+      \Edge(B)(E)
+      \Edge(E)(F)
+      \Edge(F)(t1)
+
+	\tikzset{
+      EdgeStyle/.append style = {black,-} }
+
+      \Edge(1)(2)
+      \Edge(1)(3)
+    \node (1) at (-3,4){\Huge $\rightarrow$};
+%     
+%     \node (2) at (-7,0){\Huge H};
+%     \node (3) at (10,0){\Huge G};
+    \end{tikzpicture}
+    }
+    \caption{Reduction from k-coloring to MIN-PRA}
+    \label{fig:reduction}
+    \end{figure}
+
+\section{The Star Routed Network: No Waiting Time} \label{sec:PAZL}
 
@@
 
-      Let us define a family of simple routed networks modeling a Point-to-Multipoint fronthaul (PtMP), which has been designed for C-RAN \cite{tayq2017real}. 
-      The graph $G$ has two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes, the central source node $c_s$ and the central target node $c_t$.
-      There is an arc between $c_s$ and  $c_t$ called the central arc and for all $i<n$ there is an arc between $s_i$ and $c_s$ and between $t_i$ and $c_t$.
+      Let us define a family of simple symmetric routed networks. 
+      The graph $G$ has two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$ of cardinality $n$ and two special nodes:
+      the central source node {\bf $c_s$} and the central target node {\bf $c_t$}.
+      There is an arc between {\bf $c_s$} and {\bf $c_t$} and for all $i$, there is an arc between $s_i$ and $c_s$ and between $t_i$ and $c_t$.
       All the symmetric arcs are also in the graph with the same weights.
-      The forward routes are the directed paths $r_i = (s_i,c_s,c_t,t_i)$ and the backward routes are $\rho(r_i) =(t_i,c_t,c_s,s_i)$.
-The routed network $(G, \{r_i,\rho(r_i)\}_{i<n})$ is called a \textbf{star routed network}.
+      The forward routes are the directed paths $r_i = (s_i,c_s,c_t,t_i)$ and $\rho(r_i) = (t_i,c_t,c_s,s_i)$ which defines a symmetric routed network. 
+      The symmetric routed networks $(G, \{r_i,\rho(r_i)\}_{i<n})$ is called a \textbf{star routed network}.
 
        \begin{center}
-	 \scalebox{0.6}{
+	 \scalebox{0.8}{
 \begin{tikzpicture}
@@
 
-  \Edge[label = $\omega({s_0,c_s})$](s1)(cs)
-  \Edge[label = $\omega({s_1,c_s})$](s2)(cs)
-  \Edge[label = $\omega({s_2,c_s})$](s3)(cs)
-
-  \Edge[label = $\omega({c_t,t_0})$](ct)(t1)
-  \Edge[label = $\omega({c_t,t_1})$](ct)(t2)
-  \Edge[label = $\omega({c_t,t_2})$](ct)(t3)
+  \Edge[label = $\omega(s_1\,c_s)$](s1)(cs)
+  \Edge[label = $\omega(...)$](s2)(cs)
+  \Edge[label = $\omega(...)$](s3)(cs)
+
+  \Edge[label = $\omega(...)$](ct)(t1)
+  \Edge[label = $\omega(...)$](ct)(t2)
+  \Edge[label = $\omega(...)$](ct)(t3)
 
@@
       Since the central arc appears in every route, its value does not matter when considering the process time of an assignment.
-  Moreover an assignment without collisions is also an assignment without collisions of the same star routed network with the weight of the central arc set to $0$.
-Hence, we assume from now on that the weight of the central arc is $0$.
-
-  Collisions between messages can only appear on the arc $(c_s,c_t)$ between forward routes or on the arc $(c_t,c_s)$
-  between backward routes.
+      Moreover an assignment without collisions is also an assignment without collisions if the weight of the central arc 
+      is set to $0$, therefore we assume from now on it is indeed $0$.
+
+      Collisions between messages can only appear in the arc $(c_s,c_t)$ on the way forward and in the arc $(c_t,c_s)$ on the way back.
 The flow of messages in a star routed network is completely described by their repartition in two time windows of size $P$ that we call the {\bf forward period} (at $(c_s,c_t)$), and the {\bf backward period} (at $(c_t,c_s)$).
 
-  Star routed networks seem really simple, but \pall or \pazl may be $\NP$-hard restricted to these networks.
-  We conjecture it is the case since  a variant of \pazl where the central link is unidirectional (collisions can happen between forward and backward routes) can be shown to be $\NP$-complete.
-It is done by a reduction from the subset sum problem as for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
-
-%
-%      
-%      A {\bf $(P,\tau)$-periodic assignment} of a routed network $(G,\cal R)$ is a sequence  $m=(m_0, \ldots ,m_{n-1})$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$.
-The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$.
-We will always consider that the $m_{i}$ are between $0$ and $P-1$.
-Moreover, \emph{no pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
-%
-%      As an example of a $(2,1)$-periodic assignment, let us consider a routed network 
-%      where all pairs of routes intersect at a different arc.
-It is easy to design such a network and an example is given in Fig.~\ref{fig:example}.
-We set $\tau = 1$ and the weights are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.
-There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.
-%
-%  
-%      \begin{figure}[ht]
-%      \begin{center}
-%          \scalebox{0.5}{
-%          
-%\begin{tikzpicture}
-%
-%
-%\tikzset{
-%  LabelStyle/.style = { rectangle, rounded corners, draw,
-%                       font = \bfseries },
-%  EdgeStyle/.append style = {->} }
-%  \SetGraphUnit{5}
-%  \node[draw,circle] (s3) at (4, 2) {$s_2$}; 
-%  \node[draw,circle] (s2) at (0, 4) {$s_1$}; 
-%  \node[draw,circle] (s1) at (0, 6) {$s_0$}; 
-%
-%  \node[draw,circle] (t3) at (14, 7) {$t_2$}; 
-%  \node[draw,circle] (t2) at (14, 4) {$t_1$}; 
-%  \node[draw,circle] (t1) at (10, 2) {$t_0$}; 
-%
-%  
-%  \SetVertexNoLabel
-%  \Vertex[x=2,y=5]{A}
-%  \Vertex[x=4,y=5]{B}
-%  \Vertex[x=10,y=5]{C}
-%  \Vertex[x=12,y=5]{D}
-%  \Vertex[x=6,y=3]{E}
-%  \Vertex[x=8,y=3]{F}
-%  \tikzset{
-%  EdgeStyle/.append style = {green} }
-%  \Edge[label = 2](s2)(A)
-%  \Edge[label = 1](A)(B)
-%  \Edge[label = 2](B)(C)
-%  \Edge[label = 1](C)(D)
-%  \Edge[label = 1](D)(t2)
-%
-%  
-%   \tikzset{
-%  EdgeStyle/.append style = {red} }
-%  \Edge[label = 2](s3)(E)
-%  \Edge[label = 1](E)(F)
-%  \Edge[label = 1](F)(C)
-%  \Edge[label = 1](C)(D)
-%  \Edge[label = 1](D)(t3) 
-%     \tikzset{
-%  EdgeStyle/.append style = {blue} }
-%  \Edge[label = 1](s1)(A)
-%  \Edge[label = 1](A)(B)
-%  \Edge[label = 1](B)(E)
-%  \Edge[label = 1](E)(F)
-%  \Edge[label = 1](F)(t1)
-%
-%\end{tikzpicture}
-%
-%}
-%     \end{center}
-%       \caption{A routed network with $(0,0,0)$ as a $(2,1)$-periodic assignment}
-%       \label{fig:example}
-%      \end{figure}
-%
-%      \subsection{Periodic route assignment}\label{nonmonotone}
-%
-%    We want to find an assignment which allows to send periodic messages from sources to targets
-%    without collisions. We introduce the following associated decision problem, useful for hardness proofs.
-%    
-%
-%      \noindent {\bf  Periodic Routes Assignment (PRA)} 
-%
-%      \noindent {\bf Input:} a routed network $(G,\cal R)$, an integer $\tau$ and an integer $P$.
-%
-%      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic assignment of $(G,\cal R)$ ?
-%
-%
-%      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
-%      In fact, approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic assignment is already hard.
-%        
-%   An unusual property of assignment is that given a routed network, we may have a $(P,\tau)$-periodic assignment but no
-%	\begin{lemma} \label{lemma:monotonic}
-%	 For any odd $P$, there is a routed network such that there is $(2,1)$-periodic assignment but no $(P,1)$-periodic assignment.
-%	\end{lemma}
-%\begin{proof}
-%
-%      Consider the routed network $(G,{\cal R})$ given in the previous subsection. 
-%      We change the weights so that for $v$, the first vertex which belongs to $r_i$ and $r_j$,
-%      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $n$, the number of routes in ${\cal R_{\cal C}}$.
-In such a graph, there is no $(P,\tau)$-periodic assignment, since the problem reduces to finding a $P$-coloring in a complete graph with $n > P$ vertices, the colors being the offsets of the routes.\\
-%      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) \mod 2 = 1$ . Therefore $(0,\dots,0)$ is a $(2,1)$-periodic assignment of ${\cal R}$.      
-%\end{proof}
-
-         \section{Solving \pazl on Star Routed Networks}\label{sec:PAZL}
-
-       In this section, we deal with the problem PAZL on star routed networks.
-Since we want an assignment with waiting times zero, $MPT(m)$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
-Moreover choosing the offset $m_r$ of a forward route $r$ also sets the offset of the backward route $\rho(r)$ to $m_{\rho(r)} = m_{r} + \lambda(r) \mod P$.
-Consider an assignment $m$ of a star routed network and let $m'_r= m_{r} - t(c_s,r) \mod P$.
-Then $m'$ is an assignment of the same star routed network where, for all $i$, the weights of the arcs $(s_i,c_s)$ are set to $0$.
-Therefore we assume from now on that the \emph{weight of the arcs $(s_i,c_s)$ are all equal to $0$}.
+  \subsection{Solving PAZL}
+
+  In this subsection, we deal with a simpler version of the problem PALL.
+  We ask for a $(P,\tau)$-periodic assignment {\bf with all waiting times equal to $0$} and we call this restricted problem {\bf Periodic Assignment for Zero Latency} or PAZL.
+We consider PAZL since it is simpler to get theoretical results and good algorithms
+  than for PALL.
+Moreover, as we show in our experimentations of Sec.\ref{sec:exp_PAZL}, this problem can often be solved positively (albeit less often than the general problem).
+Finally, a solution to PAZL is simpler to implement in real telecommunication networks, since we do not need to implement any buffering at all.
+
+  When the waiting times are zero, $MPT(m)$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore.
+For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ to $m_{\rho(r)} = m_{r} + \lambda(r) \mod P$.
+  Consider an assignment $(m_0,\dots,m_{n-1})$ of a star routed network and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
+  Then $\{m_0',\dots,m_{n-1}'\}$ is an assignment of the same star routed network where the weights of the arcs from $s_i$ to $c_s$ are $0$ for all $i$.
+Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
+
+  One may consider a variant of PAZL where the central link is unidirectional, that is collisions can happen between messages going from $c_s$ to $c_t$ and messages  going from $c_t$ to $c_s$.
+This problem can be shown to be $\NP$-complete by a reduction from the subset sum problem as it is done for a similar problem of scheduling pair of tasks~\cite{orman1997complexity}.
+We conjecture that the problem PAZL is also $\NP$-complete,  but we have yet not been able to prove it.
+  On the other hand we show positive results:  when the period is large or when the routes are short there is always a solution to PAZL and it can be found in polynomial time.
+We then give an exponential time exhaustive search algorithm which always finds a solution if there is one.
 
@@
        Since $ \lambda(r_{i}) \leq  \lambda(r_{i+1})$ by construction, we have  $2 \lambda(r_{i}) + i\tau -1 < 2 \lambda(r_{i+1}) + (i+1)\tau$ which proves that there are no collision on the backward period.
-%        The complexity of the algorithm is dominated by the sorting of the routes in $O(n\log(n))$. 
+ The complexity of the algorithm is dominated by the sorting of the routes in $O(n\log(n))$. 
       \end{proof}
@@
     \begin{proposition}
-    There is a $(P,\tau)$-periodic assignment of a star routed network with waiting times $0$ if the load is less than $1/3$.
-%     and it can be found in time $O(n^2)$.
+    There is a $(P,\tau)$-periodic assignment of a star routed network with waiting times $0$ if the load is less than $1/3$ and it can be found in time $O(n^2)$.
     \end{proposition}
@@
 Since $k < n$, $3n - k -2k \geq 1$, which proves that the algorithm terminates and find a  $(P,\tau)$-periodic assignment.
-%      
-%      This algorithm works with a complexity $O(n^2)$, since for the $k^{\text{th}}$ route we have to try at most $2k$ offsets before finding a correct one.
+
+     This algorithm works with a complexity $O(n^2)$, since for the $k^{\text{th}}$ route we have to try at most $2k$ offsets before finding a correct one.
 We can test the $2k$ offsets of the backward period in time $O(k)$ by maintaining an ordered list of the intervals used by already set routes.
@@
 	 Let $(G,{\cal R})$ be a star routed network with $n$ routes and let $P \geq n\tau$.
-If there is a constant $c$ such that $\forall i < n, \,\omega(s_i,c_s) = c$, then there is a $(P,\tau)$-periodic assignment with process time $2\, \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$.
-% 	 and it can be built in time $O(n)$.
+If there is a constant $c$ such that $\forall i < n, \,\omega(s_i,c_s) = c$, then there is a $(P,\tau)$-periodic assignment with process time $2\, \displaystyle{\max_{r\in {\cal R}} \lambda(r)}$ and it can be built in time $O(n)$.
 	 \end{theorem}
@@
 We obtain $PT(r_i) = 2\lambda(r_{0})$ and thus the maximum process time of the assignment is also equal to $2\lambda(r_0)$.
-% 	Finally the complexity is $O(n)$ since we have to find the maximum of the length of the $n$ routes and the computation of each $w_i$ is done by a constant number of arithmetic operations.
+Finally the complexity is $O(n)$ since we have to find the maximum of the length of the $n$ routes and the computation of each $w_i$ is done by a constant number of arithmetic operations.
      \end{proof}
@@
 Using the same idea as in Th.~\ref{th:asym}, there is an assignment with maximum process time bounded by  $2l + d$
+
+     \subsection{A two stage approach}
+
+     We can decompose any algorithm solving the PALL problem in two parts: first set the offsets of the forward routes and then knowing this information set the offset of the backward routes or equivalently the waiting times.
+     The offsets of the forward routes will be chosen so that all messages have no collision on the central arc and such that there are no free slots inbeetween the end of a message on the central arc and the beginning of the next one.
+     It is done to minimize the period needed to send the messages of the forward route.
+     We tried the five following orders. 
+	\begin{itemize}
+
+	 \item Longest-Shortest on Routes (LSR): Decreasing order on the length of the routes.
+	 \item Shortest-Longest on Routes (SLR): Increasing order on the length of the routes. 
+	 \item Longest-Shortest on last Arc (LSA): Decreasing order on the length of the arcs $(c_t,t_i)$.
+	 \item Shortest-Longest on last Arc (SLA): Increasing order on the length of the arcs $(c_t,t_i)$.
+This sending order yields a $(P,\tau)$ periodic assignment in which all the $w_i = 0$, if the period is large enough (see proposition \ref{prop:SL}).
+	 \item Random: A random order of the routes.
+	\end{itemize}
+
+   In the rest of the section we will study different methods to compute the offsets of the backward routes, once
+   the offsets of the forward routes are fixed by one of the previous orders.
 
@@
 
-%     
-%      \begin{algorithm}
-%     \caption{ Greedy deadline ({\bf GD}) }
-%     \begin{algorithmic}
-%     \REQUIRE A routed network $(G,{\cal R})$, a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
-%     \ENSURE $(P,\tau)$-periodic assignment of $(G,{\cal R})$, or failure
-%    \STATE  ${\cal H} \leftarrow$ empty set //{\em set of eligible routes}
-%        \STATE  free\_ intervals $\leftarrow$ [0,$P$] //{\em list of intervals of free slots}
-%   
-%     \FORALL{route $r_{i}$}
-%     \STATE  deadline[$r_i$]  $\leftarrow$  $m_{i} + T_{max} - \omega(s_i,c_s)$
-%     \STATE  eligible\_time[$r_i$] $\leftarrow$ $m_{i} +  \lambda(r_i) + \omega(c_t,t_i)$
-%       \ENDFOR
-%       
-%       \WHILE{There is some non-assigned routes}
-%       \IF{${\cal H}$ is empty}
-%       \STATE $r_i$ $\leftarrow $ min\_non\_assigned(eligible\_time)
-%       \ENDIF
-%      
-%       \STATE $r \leftarrow $ extract\_min(${\cal H}$)
-%       \STATE t $\leftarrow$ next\_free\_interval(free\_intervals, t) //{\em if there is no more free intervals of size $\tau$, the algorithm fails}
-%       \STATE $w_i \leftarrow$ t - eligible\_time[$r_i$]
-%       \STATE update(t,free\_ intervals)
-%       \STATE t $\leftarrow$ t + $\tau$
-%       \FORALL{routes $r_i$ with  eligible\_time[$r_i$] $\leq$ t}
-%       \STATE insert ( ${\cal H}$,$r_i$).
-%       \ENDFOR
-%       \ENDWHILE
-% %    \STATE  $w_i \leftarrow 0$
-% %    \FORALL{route $r_{t_i}$}
-% %    \STATE  $w_i \leftarrow 0$
-% %    \STATE period-end $\leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
-% %    \FORALL{route $r_{t_j}$}
-% %    \STATE deadline-route$ \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
-% %    \STATE $deadline \leftarrow$ min(deadline-route,period-end)
-% %    \ENDFOR
-%     
-% 
-%     \end{algorithmic}
-%     \end{algorithm}
-%     The function  min\_non\_assigned(eligible\_time) returns the route with lowest time in eligible\_time, which is not assigned yet.
+      \begin{algorithm}
+     \caption{ Greedy deadline ({\bf GD}) }
+     \begin{algorithmic}
+     \REQUIRE A routed network $(G,{\cal R})$, a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
+     \ENSURE $(P,\tau)$-periodic assignment of $(G,{\cal R})$, or failure
+    \STATE  ${\cal H} \leftarrow$ empty set //{\em set of eligible routes}
+        \STATE  free\_ intervals $\leftarrow$ [0,$P$] //{\em list of intervals of free slots}
+
+     \FORALL{route $r_{i}$}
+     \STATE  deadline[$r_i$]  $\leftarrow$  $m_{i} + T_{max} - \omega(s_i,c_s)$
+     \STATE  eligible\_time[$r_i$] $\leftarrow$ $m_{i} +  \lambda(r_i) + \omega(c_t,t_i)$
+       \ENDFOR
+
+       \WHILE{There is some non-assigned routes}
+       \IF{${\cal H}$ is empty}
+       \STATE $r_i$ $\leftarrow $ min\_non\_assigned(eligible\_time)
+       \STATE insert ( ${\cal H}$,$r_i$).
+       \ENDIF
+
+       \STATE $r \leftarrow $ extract\_min(${\cal H}$)
+       \STATE t $\leftarrow$ next\_free\_interval(free\_intervals, t) //{\em if there is no more free intervals of size $\tau$, the algorithm fails}
+       \STATE $w_i \leftarrow$ t - eligible\_time[$r_i$]
+       \STATE update(t,free\_ intervals)
+       \STATE t $\leftarrow$ t + $\tau$
+       \FORALL{routes $r_i$ with  eligible\_time[$r_i$] $\leq$ t}
+ \STATE insert ( ${\cal H}$,$r_i$).
+       \ENDFOR
+       \ENDWHILE
+
+     \end{algorithmic}
+     \end{algorithm}
+     The function  min\_non\_assigned(eligible\_time) returns the route with lowest time in eligible\_time, which is not assigned yet.
 The function update(t,free\_intervals) removes an interval of size $\tau$ beginning at t, which correspond to the message,  from free\_intervals.
@@
     of time at which a message can be sent on the arc $(c_t,c_s)$.
-%    To do that the set of eligible routes must be maintained in a binary heap
-%    to be able to find the one with smallest deadline in time $O(\log(n))$. 
-%    To deal with the possible collisions, one can maintain a list of the intervals
-%    of time at which a message can be sent on the arc $(c_t,c_s)$. Each time the offset of a 
-%    route is fixed an interval is split into at most two intervals in constant time. 
-%    Since the algorithm goes over the elements of the list at most twice when doing an insertion
-%    or looking for the next free interval, the time needed to maintain it is $O(n)$. 
+    To do that the set of eligible routes must be maintained in a binary heap
+    to be able to find the one with smallest deadline in time $O(\log(n))$. 
+    To deal with the possible collisions, one can maintain a list of the intervals
+    of time at which a message can be sent on the arc $(c_t,c_s)$. Each time the offset of a 
+    route is fixed an interval is split into at most two intervals in constant time. 
+    Since the algorithm goes over the elements of the list at most twice when doing an insertion
+    or looking for the next free interval, the time needed to maintain it is $O(n)$. 
 %    
@@
     For a given routed network, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
-    Hence, for a given routed network choosing the margin or $T_{max}$ is the same, but since we will consider many networks whith different longest route's size, it will be more meaningful to set a global margin rather than $T_{max}$.
+    Hence, for a given routed network choosing the margin or $T_{max}$ is the same, but since we will consider many networks with different longest route's size, it will be more meaningful to set a global margin rather than $T_{max}$.
     In fact the margin represents the latency imposed by the communication process without taking into account the physical length of the network which cannot be changed.
@@
    We first try to understand what is the best choice of order for the first stage of the algorithm which is followed by the GD algorithm in this experiment.
-We try the following ones: decreasing order on the length of the routes (LSR), decreasing order on the weigths of the arcs $(c_t,t_i)$ (LSA), increasing order on the length of the routes (SLR), increasing order on the weigths of the arcs $(c_t,t_i)$ (SLA).
-We also consider the random order, which means we compute $1,000$ random orders and stop as soon one yields an assignment.
-   In Fig.~\ref{fig:success95} , we represent the success rate of the five kind of orders with regards to the margin. The value is an average computed over $10,000$ random star routed networks.
+In Fig.~\ref{fig:success95} , we represent the success rate of the five kind of orders with regards to the margin.
+The value is an average computed over $10,000$ random star routed networks.
+Note that for the random order, we compute $1000$ random orders and count it as a success as soon as there is a solution for one order.
 
@@
 
-%\begin{figure}[h] 
-%          \includegraphics[width=0.4\textwidth]{departs_gp_25000.pdf}
-%          \vspace{-0.5cm}
-%      \caption{Success rate of different orders, $80\%$ load.}
-%           \label{fig:success80}
-%     \end{figure}
+\begin{figure}[h] 
+  \centering
+          \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
+          \vspace{-0.5cm}
+      \caption{Success rate of different orders, $80\%$ load.}
+           \label{fig:success80}
+     \end{figure}
 

### 2017-07-26 infocom/infocom.tex
améliorations marginales

@@
 \begin{abstract}
-A recent trend in mobile networks is to centralize in distant data-centers the processing units which were attached to 
-antennas. The main challenge is to guarantee that the latency of the periodic messages sent from the antennas to their processing
-units and back fulfills protocol time constraints.
-We show that traditional statistical multiplexing does not allow such a low latency, due to collisions and buffering at nodes.
-Hence, we propose in this article to use a deterministic scheme for sending periodic messages without collisions in the network thus without buffering and the resulting additional latency.
+A recent trend in mobile networks is to centralize in distant data-centers the processing units which were attached to antennas.
+The main challenge is to guarantee that the latency of the periodic messages sent from the antennas to their processing units and back fulfills protocol time constraints.
+We show that statistical multiplexing does not allow such a low latency, due to collisions and buffering at nodes.
+Hence, we propose to use a deterministic scheme for sending periodic messages without collisions in the network to avoid buffering and the resulting additional latency.
 We give several algorithms to compute such schemes for a common topology where one link is shared by all antennas.
-We show that there is always a solution when the routes are short or the load is small. When the parameters are unconstrained,
-and some buffering is allowed in the processing units, we propose an algorithm (PMLS) adapted from a classical scheduling method.
-The experimental results show that even under full load, most of the time PMLS finds a deterministic sending scheme with no latency.
+We show that there is always a solution when the routes are short or the load is small.
+When the parameters are unconstrained, and some buffering is allowed in the processing units, we propose an algorithm (PMLS) adapted from a classical scheduling method.
+The experimental results show that even under full load, PMLS finds most of the time a deterministic sending scheme with no latency.
 \end{abstract}
@@
 
-Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost of ownership.
-The main challenge for this type of architecture is to reach a latency compatible with transported protocols.
-The latency is measured between the sending of a message by the Remote Radio Heads (RRHs) on the field and the receptions of the answers, computed by real-time virtualized network functions of BaseBand Units (BBUs), in the cloud.
-For example, LTE standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in $3$ms~\cite{bouguen2012lte}.
-In 5G, some services need end to end latency as low as 1ms~\cite{3gpp5g}.
-The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer in the \emph{frontaul} network between RRHs and BBUs: frames need to be emitted and received every milliseconds~\cite{bouguen2012lte}.
+Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN for Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost of ownership.
+The main challenge for this type of architecture is to reach a latency compatible with transport protocols.
+The latency is measured between the sending of a message by a Remote Radio Head (RRH) and the receptions of the answer, computed by real-time virtualized network functions of a BaseBand Unit (BBU) in the cloud.
+For example, LTE standards requires to process functions like HARQ (Hybrid Automatic Repeat reQuest) in $3$ms~\cite{bouguen2012lte}.
+In 5G, some services need end to end latency as low as $1$ms~\cite{3gpp5g}.
+The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer in the \emph{frontaul} network between RRHs and BBUs: frames need to be emitted and received each millisecond~\cite{bouguen2012lte}.
 Our aim is to operate a C-RAN on a low-cost shared switched network.
-The question we address is the following : is it possible to schedule messages emission such that there is no collision, then no buffering nor latency corresponding to queuing delays ?
+The question we address is the following: is it possible to schedule messages such that there is no collisions to avoid latency caused by queuing delays? 
+Eliminating this source of latency leaves us with more time budget for latency coming from the physical length of the routes in the network, and thus allows for wider deployment areas.
 
@@
 The process must be  predictable (i.e.
-the date of arrival of packets is known beforehand).Following LTE standard~\cite{bouguen2012lte}, in this article we assume that the process is periodic.
+the date of arrival of packets is known beforehand).
+Following LTE standard~\cite{bouguen2012lte}, in this article we assume that the process is periodic.
 That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
@@
 To ensure that this property is always true we propose a deterministic process.
-We have two sets of values that we can choose when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
-When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods inapplicable.
-Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.The latency, that is the time between the emission of a message and the complete return of its answer, must be minimized: this lefts budget for other latency causes, and leads to larger fiber lengths, then wider deployment areas.This means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long.
-Note that the
-model is technology agnostic, i.e. it is compatible with an optical network with a fixed packet size.
-
-\footnote{Others terminologies and functional splits exist in the literature.
+We have two sets of values that we can set when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
+When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods unusable.
+Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.
+The latency, that is the time between the emission of a message and the complete return of its answer must be minimized.
+This means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long.
+Note that the model is technology agnostic, i.e.
+it is compatible with an optical network with a fixed packet size.
+
+%\footnote{Others terminologies and functional splits exist in the literature.
 We choose the most classical one for sake of clarity.
@@
 In Sec.~\ref{sec:PAZL}, we propose two algorithms solving \pazl when the routes between RRHs and BBUs are small or when the load is light.
-Using a compact representation of an assignment, we show that \pazl is fixed parameter tractable when parametrized by the number of antenna on star routed networks.
-Finally in Sec.~\ref{sec:PALL}, we introduce a family of algorithms to solve \pall and our experimentation allows to select one which works extremely well even in very loaded networks.
+Using a compact representation of an assignment, we show that \pazl is fixed parameter tractable when parametrized by the number of antennas on star routed networks.
+Finally in Sec.~\ref{sec:PALL}, we introduce a family of algorithms to solve \pall and our experimentations allow to select one which works extremely well even in loaded networks.
 In particular we show that the deterministic communication schemes we design vastly outperform the traditional statistical multiplexing with regard to latency.
@@
 Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits for the fronthaul.
-Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches.
+Each end-point, RRH or BBU, is connected through direct fiber or full optical switches.
 This architecture is very expensive and hardly scales in the case of a mobile network composed of tenths of thousands of deployment sites.
-The deterministic approach we propose has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}.
+The deterministic approach we propose has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, and in  IETF DetNet working group~\cite{ieee802}.
 Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}.
@@
 The algorithmic problem we focus on may look like wormhole problems~\cite{cole1996benefit}, but  we want to minimize the time lost in buffers and not just to avoid deadlocks.
-Several graph colorings have been introduced to model similar problems such as the allocation of frequencies~\cite{borndorfer1998frequency}, bandwidths~\cite{erlebach2001complexity} or routes~\cite{cole1996benefit} in a network or train schedules~\cite{strotmann2007railway}.
+Several graph colorings have been introduced to model similar problems such as the allocation of frequencies~\cite{borndorfer1998frequency}
+% bandwidths~\cite{erlebach2001complexity}
+or routes~\cite{cole1996benefit} in a network or train schedules~\cite{strotmann2007railway}.
 Unfortunately, they do not take into account the periodicity of the scheduling and the associated problems are already $\NP$-complete.
@@
  Observe that the existence of a $k$-coloring of $H$ is equivalent to the existence of a $(k,1)$-periodic assignment in $G$, 
- by converting an offset of a route into a color of a vertex and reciprocally. \qed
+ by converting an offset of a route into a color of a vertex.\qed
+%  and reciprocally. \qed
 
@@
 As we  experimentally show in Sec.~\ref{sec:exp_PAZL}, this problem can often be solved positively albeit less often than the general problem.
-Finally, a solution to \pazl is simpler to implement in real telecommunication networks, since we do not need any buffering at all.
+Finally, a solution to \pazl is simpler to implement in real telecommunication networks, since we do not need buffering at all.
 
@@
       Finally, note that the greedy algorithm works on average when the load is less than $2/3$ which is twice better than the theoretical bound.
-This algorithm seems to depends on the load only and not on the number of routes.
+This algorithm seems to depend on the load only and not on the number of routes.
 
@@
 On the other hand, the greedy algorithm has a performance not so far from the case of short routes, which is expected since it does not directly depend on the size of the route.
-In fact, if we do the previous experiment
-      for short routes but with long routes, we find that, on average, the greedy algorithm finds a solution when the load is less than $59\%$.
+In fact, if we do the experiment of Fig.~\ref{fig:short} for long routes, on average the greedy algorithm finds a solution when the load is less than $59\%$.
 
       When the load is larger than $50\%$, the exhaustive search finds more solutions than the greedy algorithms which justifies its use.
-However, for load larger than $80\%$ there are many instances for which there are no solutions to \pazl.
-      It means that with long routes and high load, looking for an assignment without waiting time is far too restrictive.
-That is why we present algorithms for the general \pall problem in our next section.
-We will test them on $8$ long routes and a load between $100\%$ and $80\%$ for which, as shown here, there are often no assignment without waiting times.
-
-      The computation time of the exhaustive search is in $O(n!)$ as shown int Th.~\ref{th:FPT}, hence we need to study its scalability when $n$ grows.
-In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $20,000$ slots.
-We chose  $95\%$ of load.
+However, for loads larger than $80\%$ there are many instances for which there are no solutions to \pazl: \emph{with long routes and high load}, looking for an assignment without waiting time is far too restrictive.
+That is why we present algorithms for the general \pall problem in the next section.
+We will test them on $8$ long routes and a load between $100\%$ and $80\%$ for which, as shown here, there are often no assignments without waiting times.
+
+      The computation time of the exhaustive search is in $O(n!)$ as shown int Th.~\ref{th:FPT}, hence we need to study its scalability when $n$ grows. We set the load at $95\%$.
+%       
+%       In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $20,000$ slots. We chose  $95\%$ of load.
 %       , that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
-      The following table shows the time before the exhaustive search ends, for $8$ to $16$ routes, averaged on $100$ random star routed networks.
-This shows that for less than $15$ routes, which corresponds to all current topologies, the algorithm is efficient enough, but we should improve it further to work on more routes.
+      The following table shows the time before the exhaustive search ends, for $8$ to $16$ routes, averaged on $100$ random star routed networks drawn as in the previous experiment.
+It shows that for less than $15$ routes, which corresponds to all current topologies, the algorithm is efficient enough, but it should be further improved to work on more routes.
          \begin{center}
@@
         We can simplify the weights on the arcs $(s_i,c_s)$ by setting them all to $0$.
-        We find the route with maximal length, say that it is $\lambda(r_0)$. The idea is to 
+        Let assume that the route with maximal length is $r_0$. The idea is to 
         set the waiting times of all routes so they behave exactly as the message in $r_0$.
@@
 
-    We can decompose any algorithm solving the \pall problem in two stages: first set the offsets of the forward routes and then, knowing this information set the offset of the backward routes or equivalently the waiting times.
+    We can decompose any algorithm solving the \pall problem in two stages: first set the offsets of the forward routes and then set the offset of the backward routes or equivalently the waiting times.
     The offsets of the forward routes are chosen so that they have no collisions and such that there are no free slots in between the end of a message on the central arc and the beginning of the next one.
-    It is done to minimize the period needed to send the messages of the forward routes. For this section and the next, we assume that the offsets of the forward routes are fixed by some order.
+It is done to minimize the period needed to send the messages of the forward routes.
+Remark that an order on the routes is enough to determine the offsets of the forward routes with the previous property.
+In this subsection and the next, we assume that the offsets of the forward routes are fixed by some order.
 
@@
 
-    The first algorithm we propose is a greedy algorithm which sets the offset $m_{\rho(r_i)}$ of the 
-    backward routes. It prioritizes the routes with the earliest deadline to best satisfy the
-    constraint on the process time.
+    The first algorithm we propose is a greedy algorithm which sets the offset $m_{\rho(r_i)}$ of the backward routes. It prioritizes the routes with the earliest deadline to best satisfy the
+    constraint on the process time, hence we call it \textbf{Greedy Deadline (GD)}.
 Set $t=0$ and repeat the following: find $s \geq t$ the first time for which there is an eligible route with its offset not fixed.
@@
 
-    The greedy algorithm can be made to work in time $O(n\log(n))$ by using a binary heap for the set of eligible routes, and a list to maintain a list of the intervals
-    of time at which a message can be sent on the arc $(c_t,c_s)$.
+    Algorithm GD can be made to work in time $O(n\log(n))$ by using a binary heap for the set of eligible routes, and a list to maintain a list of the intervals of time at which a message can be sent on the arc $(c_t,c_s)$.
 %    To do that the set of eligible routes must be maintained in a binary heap
@@
 On the other hand if the running times are different the problem is $\NP$-complete~\cite{lenstra1977complexity}.
-     The  polynomial time algorithm  which solves this scheduling problem is similar to the Greedy algorithm presented in the previous section.
+     The  polynomial time algorithm  which solves this scheduling problem is similar to the greedy algorithm presented in the previous section.
 However, when it fails because a job finishes after its deadline, it changes the schedule of the last messages to find a possible schedule for the problematic job.
@@
       \end{center}
-      \vspace{-1cm}
       \caption{Cumulative distribution of the margin of statistical multiplexing}
@@
 
-     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Figure~\ref{fig:sto} since even the third quartile was always at $0$ for a load of $100\%$.
+     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Fig.~\ref{fig:sto} since even the third quartile was always at $0$ for a load of $100\%$.
 There is around $20\%$ of the instances for which the margin is larger than $0$ for a load of $100\%$ and $2\%$ for a load of $95\%$.

### 2017-07-26 infocom/infocom.tex
bricoles à la fin

@@
 It works when the routes are short (Longest-Shortest policy) or when the load is less than $80\%$ (Exhaustive search of compact assignments).
-When the load is higher, buffering is allowed in the BBUs and we are able to find a determinstic communication scheme 
-with no additionnal latency most of the time using our PMLS algorithm. 
+When the load is higher, buffering is allowed in the BBUs and we propose the algorithm PMLS which  finds a deterministic communication scheme with almost no additionnal latency.
+
 We plan to study other commons fronthaul topologies such as caterpillars, trees or ring; the latter being different since 
 the forward and backward routes are not symmetric.
-For other applications, it could be interesting to to optimize the average latency of the routes rather than the worst latency, a problem which could be solved using linear optimization.
+For other applications, it could be interesting to optimize the average latency of the routes rather than the worst latency, a problem which may be solved using linear optimization.
 

### 2017-07-26 infocom/infocom.tex
merge

--- 2017-07-25 infocom/infocom.tex
@@
 Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost of ownership.
-The main challenge for this type of architecture is to reach a latency compatible with transported protocols.
-The latency is measured between the sending of a message by the Remote Radio Heads (RRHs) on the field and the receptions of the answers, computed by real-time virtualized network functions of BaseBand Units (BBUs), in the cloud.
+The main challenge for this type of architecture is to reach a latency compatible with transport protocols.
+The latency is measured between the sending of a message by a Remote Radio Head (RRH) and the receptions of the answer, computed by real-time virtualized network functions of a BaseBand Unit (BBU) in the cloud.
 For example, LTE standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in $3$ms~\cite{bouguen2012lte}.
@@
 Our aim is to operate a C-RAN on a low-cost shared switched network.
-The question we address is the following : is it possible to schedule messages emission such that there is no collision, then no buffering nor latency corresponding to queuing delays ?
+The question we address is the following: is it possible to schedule messages such that there is no collisions to avoid latency caused by queuing delays? 
+Eliminating this source of latency leaves us with more time budget for latency coming from the length of the network, and thus allows for wider deployment areas.
 
@@
       \end{center}
-      \vspace{-1cm}
       \caption{Cumulative distribution of the margin of statistical multiplexing}
       \label{fig:sto}
+      \vspace{-0.5cm}
      \end{figure}
 
-     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Figure~\ref{fig:sto} since even the third quartile was always at $0$ for a load of $100\%$.
+     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Fig.~\ref{fig:sto} since even the third quartile was always at $0$ for a load of $100\%$.
 There is around $20\%$ of the instances for which the margin is larger than $0$ for a load of $100\%$ and $2\%$ for a load of $95\%$.

### 2017-07-26 code/Sources/main.c

@@ -43,7 +43,7 @@ int main()
 	/*****
 	Taux de reussite de départ PALL avec un retour GP sur une periode donnée (on fait varier la marge)
 	*****/
-	sucess_aller_PALL(8,2500,20000,3000,10000,25000);
+	//sucess_aller_PALL(8,2500,20000,3000,10000,25000);
 
 
 
@@ -71,7 +71,7 @@ int main()
 	Tmax moyen pour sto vs sp
 	*******/
 
-	//marge_PALL_stochastique(8,2500,20000,1000,50000);
+	marge_PALL_stochastique(8,2500,20000,1000,50000);
 
 
 

### 2017-07-26 code/Sources/simulations.c

@@ -430,17 +430,17 @@ void marge_PALL_stochastique(int nb_routes,int taille_paquets,int taille_route, 
 	int nb_rand = 1000;
 
 	int periode;
-	int distrib[300];
+	int distrib[200];
+	int distribsp[200];
 
 	//for(int periode=taille_paquets*nb_routes;periode<periode_max ;periode+=1000)
-	for(float load = 0.95;load >=0.65;load-=0.15)
+	for(float load = 0.95;load >=0.39;load-=0.55)
 	{
 		periode = (int)(taille_paquets*nb_routes / load);
-		if(periode == 30769)periode = 50000;
 		total_sto = 0;
 		total_sp = 0;
-		for(int i=0;i<300;i++)distrib[i]=0;
-	
+		for(int i=0;i<200;i++){distrib[i]=0;distribsp[i]=0;}
+		printf("load = %f %d\n",load, periode);
 		#pragma omp parallel for private(ressp,ressto,g) if (PARALLEL) schedule (static)
 		for(int i = 0;i<nb_simuls;i++)
 		{
@@ -448,31 +448,35 @@ void marge_PALL_stochastique(int nb_routes,int taille_paquets,int taille_route, 
 			graphe_etoile(g,taille_route);
 	
 
-		 	//ressp = linear_simons_per(g, periode, taille_paquets,nb_rand);
-		 	ressp = 0;
+		 	ressp = linear_simons_per(g, periode, taille_paquets,nb_rand);
+		 	
 		 	#pragma omp atomic
 				total_sp+= ressp;
-
+			if(ressp<15000)
+			{
+				if(periode == 21052)	
+				{
+					#pragma omp atomic
+					distribsp[ressp/150]++;
+				}
+				else{
+					#pragma omp atomic
+					distribsp[ressp/150+100]++;
+				}
+			}
 			ressto=stochastic(g,taille_paquets,periode,1000,1);
 			ressto -=  longest_route(g);
 			if(ressto<15000)
 			{
-				//printf("load = %f %d\n",load, periode);
+				
 				if(periode == 21052)	
 				{
-					//printf("{%d} \n",ressto/150);
+					#pragma omp atomic
 					distrib[ressto/150]++;
 				}
-				if(periode == 25000)
-				{	
-					//printf("{%d} \n",ressto/150+100);
+				else{
+					#pragma omp atomic
 					distrib[ressto/150+100]++;
-				}
[…]

### 2017-07-26 infocom/infocom.tex
courbes
commentaires de la dernière figure

--- 2017-07-26 infocom/infocom.tex
@@
       \end{center}
+         \vspace{-0.5cm}
       \caption{Minimum period averaged over $1,000$ random instances}\label{fig:short}
@@
       \end{center}
-
+          \vspace{-0.5cm}
       \caption{Success rate for $8$ routes over $1,000$ random instances}\label{fig:long}
@@
     \includegraphics[width=0.5\textwidth]{departs_gp_21000.pdf}
+       \vspace{-0.5cm}
       \caption{Success rate of different orders, $95\%$ load.}
@@
       \end{center}
+         \vspace{-0.5cm}
       \caption{Success rate of GD, MLS and PMLS, $95\%$ load}
@@
 
-     Now that we have found the best amongst the algorithms solving \pall, we need to compare its performances against the actual way to manage the messages in a network:  statistical multiplexing, where there is a FIFO buffer in each node of the network to deal with the collisions.
+     Now that we have found the best amongst the algorithms solving \pall, we need to compare its performances against the actual way to manage the messages in a network:  statistical multiplexing, where there is a FIFO buffer in each node of the network to resolve collisions.
 The time at which the messages are sent in the network is not computed as in our approach, thus we fix the offsets of each route to some random value.
@@
 
-     We draw $1000$ star routed networks with $8$ routes, with weights on the arcs drawn between $0$ and $20,000$.
-Note that the results are almost the same when the arcs are small.
-We measure, for load from $100\%$ down to $40\%$, the median, the first, and the third quartile of the margins computed in $1,000$ simulations using FIFO buffer to resolve collisions.
+     In Fig.~\ref{fig:sto}, we represent the cumulative distribution of margins for 
+     statistical multiplexing and PMLS.
+The distribution is computed from $1000$ star routed networks drawn with the same parameters as before.
+We represent the distribution under high and light load for statistical multiplexing and under high load only for PMLS since under light load the margin is always $0$.
 
@@
       \end{center}
+         \vspace{-0.5cm}
       \caption{Cumulative distribution of the margin of statistical multiplexing}
@@
 
-     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Fig.~\ref{fig:sto} since even the third quartile was always at $0$ for a load of $100\%$.
-There is around $20\%$ of the instances for which the margin is larger than $0$ for a load of $100\%$ and $2\%$ for a load of $95\%$.
-For the instances with a margin larger than $0$, the margin is on average $400$.
-
-     The simulations show clearly that the stochastic policy does not ensure a minimal latency.
-As we can see in Fig~\ref{fig:sto}, the more the network is loaded, the higher the latency is.
-When the network is highly loaded, we have instances with a margin of about $10,000$ which corresponds to half the period, that is $0.5$ms.
-Even when the network is lightly loaded, a quarter of the instances have a margin of more than $2,000$ which is more than what PMLS finds for the worst instance and a network fully loaded!
+     The experiment clearly shows that statistical multiplexing does not ensure a minimal latency. 
+     The latency is extremely high when the load is high, with a margin of about $10,000$ for the worst $10\%$ which corresponds to half the period, that is $0.5$ms.
+Even when the network is lightly loaded, $20\%$ of the instances have a margin of more than $2,000$.
+On the other hand, PMLS finds an assignment with margin $0$ in a highly loaded $97\%$ of the time!
+     For each $1000$ slots of latency we are able to win with regard to , we are able to
+
      We feel that it strongly justifies the use of a deterministic sending scheme for latency critical applications such as our C-RAN motivating problem.

### 2017-07-27 infocom/infocom.tex
long a relire

@@
 
-\renewcommand{\thefootnote}{\*}
+%\renewcommand{\thefootnote}{\*}
 
@@
 The main challenge for this type of architecture is to reach a latency compatible with transport protocols.
-The latency is measured between the sending of a message by a Remote Radio Head (RRH) and the receptions of the answer, computed by real-time virtualized network functions of a BaseBand Unit (BBU) in the cloud.
+The latency is measured between the sending of a message by a Remote Radio Head (RRH) and the receptions of the answer, computed by real-time virtualized network functions of a BaseBand Unit (BBU)\footnote{Others terminologies exist in the literature.
+The results of this work are fully compatible with any C-RAN architecture definition.} in the cloud .
 For example, LTE standards requires to process functions like HARQ (Hybrid Automatic Repeat reQuest) in $3$ms~\cite{bouguen2012lte}.
@@
 it is compatible with an optical network with a fixed packet size.
-
-%\footnote{Others terminologies and functional splits exist in the literature.
-We choose the most classical one for sake of clarity.
-The results of this work is fully compatible with any C-RAN architecture definition.}
 
@@
 On the other hand, PMLS finds an assignment with margin $0$ in a highly loaded $97\%$ of the time!
-     For each $1000$ slots of latency we are able to win with regard to , we are able to
-
+     For each $1000$ slots of latency we remove from the periodic process, we are able to lengthen the routes of $10$km, which has a huge economic impact.
      We feel that it strongly justifies the use of a deterministic sending scheme for latency critical applications such as our C-RAN motivating problem.
@@
 It works when the routes are short (Longest-Shortest policy) or when the load is less than $80\%$ (Exhaustive search of compact assignments).
-When the load is higher, buffering is allowed in the BBUs and we propose the algorithm PMLS which  finds a deterministic communication scheme with almost no additionnal latency.
+When the load is higher, buffering is allowed in the BBUs and we propose the algorithm PMLS which  finds a deterministic communication scheme with almost no additional latency.
 

### 2017-07-27 infocom/infocom_long.tex
frnij
long a relire

@@
 
-Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN, or Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost of ownership.
-The main challenge for this type of architecture is to reach a latency compatible with transported protocols.
-The latency is measured between the sending of a message by the Remote Radio Heads (RRHs) on the field and the receptions of the answers, computed by real-time virtualized network functions of BaseBand Units (BBUs), in the cloud.
-For example, LTE standards requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in $3$ms~\cite{bouguen2012lte}.
-In 5G, some services need end to end latency as low as 1ms~\cite{3gpp5g}.
-The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer in the \emph{frontaul} network between RRHs and BBUs: frames need to be emitted and received every milliseconds~\cite{bouguen2012lte}.
+Next generations of mobile network architectures evolve toward centralized radio network architectures called C-RAN for Cloud Radio Access Network, to reduce energy consumption costs~\cite{mobile2011c} and more generally the total cost of ownership.
+The main challenge for this type of architecture is to reach a latency compatible with transport protocols.
+The latency is measured between the sending of a message by a Remote Radio Head (RRH) and the receptions of the answer, computed by real-time virtualized network functions of a BaseBand Unit (BBU)\footnote{Others terminologies exist in the literature.
+The results of this work are fully compatible with any C-RAN architecture definition.} in the cloud .
+For example, LTE standards requires to process functions like HARQ (Hybrid Automatic Repeat reQuest) in $3$ms~\cite{bouguen2012lte}.
+In 5G, some services need end to end latency as low as $1$ms~\cite{3gpp5g}.
+The specificity of the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer in the \emph{frontaul} network between RRHs and BBUs: frames need to be emitted and received each millisecond~\cite{bouguen2012lte}.
 Our aim is to operate a C-RAN on a low-cost shared switched network.
-The question we address is the following : is it possible to schedule messages emission such that there is no collision, then no buffering nor latency corresponding to queuing delays ?
+The question we address is the following: is it possible to schedule messages such that there is no collisions to avoid latency caused by queuing delays? 
+Eliminating this source of latency leaves us with more time budget for latency coming from the physical length of the routes in the network, and thus allows for wider deployment areas.
 
@@
 To ensure that this property is always true we propose a deterministic process.
-We have two sets of values that we can choose when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
-When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods inapplicable.
-Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.The latency, that is the time between the emission of a message and the complete return of its answer, must be minimized: this lefts budget for other latency causes, and leads to larger fiber lengths, then wider deployment areas.This means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long.
-Note that the
-model is technology agnostic, i.e. it is compatible with an optical network with a fixed packet size.
+We have two sets of values that we can set when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH.
+When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods unusable.
+Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.
+The latency, that is the time between the emission of a message and the complete return of its answer must be minimized.
+This means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long.
+Note that the model is technology agnostic, i.e.
+it is compatible with an optical network with a fixed packet size.
 
@@
       \end{center}
-      \vspace{-1cm}
+         \vspace{-0.5cm}
       \caption{Cumulative distribution of the margin of statistical multiplexing}
@@
 
-     We have also computed the minimum margin needed by PMLS to find a solution but we have not represented it in Figure~\ref{fig:sto} since even the third quartile was always at $0$ for a load of $100\%$.
-There is around $20\%$ of the instances for which the margin is larger than $0$ for a load of $100\%$ and $2\%$ for a load of $95\%$.
-For the instances with a margin larger than $0$, the margin is on average $400$.
-
-     The simulations show clearly that the stochastic policy does not ensure a minimal latency.
-As we can see in Fig~\ref{fig:sto}, the more the network is loaded, the higher the latency is.
-When the network is highly loaded, we have instances with a margin of about $10,000$ which corresponds to half the period, that is $0.5$ms.
-Even when the network is lightly loaded, a quarter of the instances have a margin of more than $2,000$ which is more than what PMLS finds for the worst instance and a network fully loaded!
+     The experiment clearly shows that statistical multiplexing does not ensure a minimal latency. 
+     The latency is extremely high when the load is high, with a margin of about $10,000$ for the worst $10\%$ which corresponds to half the period, that is $0.5$ms.
+Even when the network is lightly loaded, $20\%$ of the instances have a margin of more than $2,000$.
+On the other hand, PMLS finds an assignment with margin $0$ in a highly loaded $97\%$ of the time!
+     For each $1000$ slots of latency we remove from the periodic process, we are able to lengthen the routes of $10$km, which has a huge economic impact.
      We feel that it strongly justifies the use of a deterministic sending scheme for latency critical applications such as our C-RAN motivating problem.
@@
 It works when the routes are short (Longest-Shortest policy) or when the load is less than $80\%$ (Exhaustive search of compact assignments).
-When the load is higher, buffering is allowed in the BBUs and we are able to find a determinstic communication scheme 
-with no additionnal latency most of the time using our PMLS algorithm. 
+When the load is higher, buffering is allowed in the BBUs and we propose the algorithm PMLS which  finds a deterministic communication scheme with almost no additional latency.
+
 We plan to study other commons fronthaul topologies such as caterpillars, trees or ring; the latter being different since 
 the forward and backward routes are not symmetric.
-For other applications, it could be interesting to to optimize the average latency of the routes rather than the worst latency, a problem which could be solved using linear optimization.
+For other applications, it could be interesting to optimize the average latency of the routes rather than the worst latency, a problem which may be solved using linear optimization.
 

### 2017-07-27 infocom/infocom.tex
avoid
corrections typos, phrases plus précises

@@
 The latency is measured between the sending of a message by a Remote Radio Head (RRH) and the receptions of the answer, computed by real-time virtualized network functions of a BaseBand Unit (BBU)\footnote{Others terminologies exist in the literature.
-The results of this work are fully compatible with any C-RAN architecture definition.} in the cloud .
-For example, LTE standards requires to process functions like HARQ (Hybrid Automatic Repeat reQuest) in $3$ms~\cite{bouguen2012lte}.
+The results of this work are fully compatible with any C-RAN architecture definition.} in the cloud.
+For example, LTE standard requires to process functions like HARQ (Hybrid Automatic Repeat reQuest) in $3$ms~\cite{bouguen2012lte}.
 In 5G, some services need end to end latency as low as $1$ms~\cite{3gpp5g}.
@@
 That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
-As we want to avoid any  buffering in internal nodes of the graph.
-Hence we need to design a periodic process with no collision between messages.
+We want to avoid any  buffering in internal nodes of the graph, hence we need to design a periodic process with no collisions between messages.
 To ensure that this property is always true we propose a deterministic process.
@@
 Using a compact representation of an assignment, we show that \pazl is fixed parameter tractable when parametrized by the number of antennas on star routed networks.
-Finally in Sec.~\ref{sec:PALL}, we introduce a family of algorithms to solve \pall and our experimentations allow to select one which works extremely well even in loaded networks.
+Finally in Sec.~\ref{sec:PALL}, we introduce a family of algorithms to solve \pall and our experimentations allow to select one which works well, even in loaded networks.
 In particular we show that the deterministic communication schemes we design vastly outperform the traditional statistical multiplexing with regard to latency.
@@
       Let $r$ be a route, if a message is sent at time $m$ from $s$ the first vertex of $r$ then it will arrive at vertex $v$ in $r$ at time $m + \lambda(v,r)$.
-Since the process is periodic, if we look at the messages going through an arc between time $0$ and $P-1$, then we see the same messages in the same order and position between time $kP$ and $(k+1)P -1$ for all $k$.
-      Therefore, the first time slot at which a message sent at time $m$ on $r$ reaches a vertex $v$ in $r$ is $t(v,r) = m + \lambda(v,r) \mod P$.
+Since the process is periodic, if the message from $r$ goes through an arc at time $t\in [0,P-1]$,
+      then it goes through the same arc at time $t+kP$ for all positive integers $k$.
+Therefore, every time value can be computed modulo $P$ and we say that the first time slot at which a message sent at time $m$ on $r$ reaches a vertex $v$ in $r$ is $t(v,r) = m + \lambda(v,r) \mod P$.
 
@@
 \emph{No pair of routes must have a collision} in a $(P,\tau)$-periodic assignment.
-	 An assignment represents the following process: first a message is sent at $u$, through the forward route $r$, at time $m_r$.
+	 An assignment $m$ represents the following process: first a message is sent at $u$, through the forward route $r$, at time $m_r$.
       \begin{center}
@@
        \begin{center}
-     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{BBU.pdf}
+       \hspace{-1cm}
+      \includegraphics[width=0.48\textwidth]{BBU.pdf}
+     \hspace{-1cm}
      \end{center}
 
-      Thus, the whole process time for a message sent on the route $r$ is equal to
-      $PT(r)=\lambda(r)+ w_r+\lambda(r)$.      
-      In the process time, we count the time between the first time at which a message is emitted and the first time at which the message comes back. 
+      The process time for a message sent on the route $r$ is equal to
+      $PT(r)=\lambda(r)+ w_r+\lambda(r)$ that is the time elapsed between the time at which a message is emitted and the first time at which the message comes back. 
 %       Alternatively we could consider the time between the emission of the first slot and the reception of the last slot of the message, which would add $\tau$ to the process time.
 %       However, since all messages are of size $\tau$, it will not change the problems we consider in the rest of the article.
-      Finally, we should add to the process time the computation time that a BBU needs to deal with one message, but it can be encoded  in the weight of the last arc leading to the BBU and thus we need not to consider it explicitly in our model.
+      The time a BBU needs to process one message should be added to the process time, however it can be encoded in the weight of the last arc leading to the BBU and thus it needs not to be considered explicitly in the model.
 
@@
   between backward routes.
-The flow of messages in a star routed network is completely described by their repartition in two time windows of size $P$ that we call the {\bf forward period} (at $(c_s,c_t)$), and the {\bf backward period} (at $(c_t,c_s)$).
+The flow of messages in a star routed network is completely described by their repartition in two time windows of size $P$, the {\bf forward period} which contains all $[t(c_s,r)]$ with $r$ a forward route and the {\bf backward period} which contains all $[t(c_t,r)]$ with $r$ a backward route.
 
@@
 Then $m'$ is an assignment of the same star routed network where, for all $i$, the weights of the arcs $(s_i,c_s)$ are set to $0$.
-Therefore we assume from now on that the \emph{weight of the arcs $(s_i,c_s)$ are all equal to $0$}.
+Therefore we assume in this section that the \emph{weight of the arcs $(s_i,c_s)$ are all equal to $0$}.
 
@@
 
-    We first present a simple policy, which works when the period is large with regard to the lengths of the routes.
+    We first present a simple policy, which works when the period is large with regard to the length of the routes.
     The messages are sent in order from the shortest route to the longest route, without any gap between two messages in the forward period.
@@
 
-      If the period is slightly smaller that the bound of Proposition~\ref{prop:SL}, a collision will occur on the first route in the backward period.
-Hence, this policy is not useful even as a heuristic for longer routes as confirmed by the experimental results of Subsection~\ref{sec:exp_PAZL}.
+      If the period is slightly smaller that the bound of Proposition~\ref{prop:SL}, a collision will occur with the route $\rho(r_0)$.
+Hence, this policy is not useful even as a heuristic for longer routes as confirmed by the experimental results of Sec.~\ref{sec:exp_PAZL}.
 
@@
      period.
-Since the choice of an offset also fixes the position of the message in the backward period, chose the first one which does not create a collision.
+Since the choice of an offset also fixes the position of the message in the backward period, choose the first one which does not create a collision.
 We now prove that this algorithm always finds a $(P,\tau)$-periodic assignment without waiting time when $P \geq 3n\tau$ that is the load is less than $1/3$.
@@
    \subsection{Experimental evaluation}\label{sec:exp_PAZL}
-      The following experimental results compare the three presented algorithms.
+      In this section, we experimentally compare the three proposed algorithms.
       Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithms but are not always able to find a solution, depending on the load or the size of the routes.
@@
 To change the load, we fix the parameters $\tau$ and $n$ and modify the period $P$, which allows for a smoother control of the load and does not change the run time of our algorithms.
+The period varies from $20,000$ to $50,000$ slots that is from $1$ms to $2.5$ms.
 
@@
       First we consider routes which are shorter than $\tau$: a message cannot be contained completely in a single arc which is very common in our applications.
-We generate star routed networks in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ which corresponds to links of less than $5$km between the BBU and the RRH.
+We generate star routed networks in which the weights of the arcs $(c_t,t_i)$ are drawn uniformly between $0$ and $700$ (links of less than $5$km between the BBU and the RRH).
 
@@
 We represent in Fig.~\ref{fig:short} the average maximal possible load, for which each algorithm finds a solution.
-Remind that the exhaustive search always finds the highest load for a given instance.
+Remind that the exhaustive search always finds the highest possible load for a given instance.
 %       The lower and upper bound $n\tau$ and $3n\tau$ are also represented.
@@
       Second, remark that the Shortest-Longest algorithm is as good as the exhaustive search.
-While it was expected to be good with short routes, it turns out to be optimal for all the the random star routed networks we have tried.
+While it was expected to be good with short routes, it turns out to be optimal for all the random star routed networks we have tried.
 Therefore, we should use it in practical applications with short routes, instead of the exhaustive search which is much more computationally expensive.
@@
  %A more realistic assumption would be that all weigths of the arcs $(s_i,c_s)$ are the same. It would correspond to a situation where all the BBUs are in the same datacenter.
-	Another possible assumption would be that all weights of the arcs $(s_i,c_s)$ are the same.
+	Another possible assumption is that all weights of the arcs $(s_i,c_s)$ are the same.
 
@@
 
-     Assume that for any pair of indices $(i,j)$ the difference between the weights of the arcs $(s_i,c_s)$ and $(s_j,c_s)$ is bounded by $d$ and the length of the longest route is $l$.
+     Assume that for any pair of indices $(i,j)$ the difference between the weight of the arc $(s_i,c_s)$ and of $(s_j,c_s)$ is bounded by $d$ and the length of the longest route is $l$.
 Using the same idea as in Th.~\ref{th:asym}, there is an assignment with maximum process time bounded by  $2l + d$
@@
 
-    Algorithm GD can be made to work in time $O(n\log(n))$ by using a binary heap for the set of eligible routes, and a list to maintain a list of the intervals of time at which a message can be sent on the arc $(c_t,c_s)$.
+    Algorithm GD can be made to work in time $O(n\log(n))$ by using a binary heap for the set of eligible routes, and a list to maintain the intervals of time at which a message can be sent on the arc $(c_t,c_s)$.
 %    To do that the set of eligible routes must be maintained in a binary heap
@@
    We first try to understand what is the best choice of order for the first stage of the algorithm which is followed by the GD algorithm in this experiment.
-We try the following ones: decreasing order on the length of the routes (LSR), decreasing order on the weigths of the arcs $(c_t,t_i)$ (LSA), increasing order on the length of the routes (SLR), increasing order on the weigths of the arcs $(c_t,t_i)$ (SLA).
+We try the following ones: decreasing order on the length of the routes (LSR), decreasing order on the weigth of the arcs $(c_t,t_i)$ (LSA), increasing order on the length of the routes (SLR), increasing order on the weigth of the arcs $(c_t,t_i)$ (SLA).
 We also consider the random order, which means we compute $1,000$ random orders and stop as soon one yields an assignment.
@@
 The choice of the number of random orders drawn yields a trade-off between the computation time and the success rate.
-Up to now, we chose $1,000$ random orders arbitrarily.
-We investigate the success rate of our algorithm with regards to the number of random orders drawn, a load of $95\%$ and a margin $0$.
-The following tables presents the average success rate for each number of sending orders, on $10,000$ instances, for GD and PMLS.
+We investigate the success rate of our algorithms with regards to the number of random orders drawn, a load of $95\%$ and a margin $0$.
+The following tables presents the average success rate for different numbers of sending orders, on $10,000$ instances, for GD and PMLS.
          \begin{figure}[h] 
@@
 Even when the network is lightly loaded, $20\%$ of the instances have a margin of more than $2,000$.
-On the other hand, PMLS finds an assignment with margin $0$ in a highly loaded $97\%$ of the time!
-     For each $1000$ slots of latency we remove from the periodic process, we are able to lengthen the routes of $10$km, which has a huge economic impact.
+On the other hand, PMLS finds an assignment with margin $0$ and a high load $97\%$ of the time!
+     For each $1000$ slots of latency we save from the periodic process, we are able to lengthen the routes of $10$km, which has a huge economic impact.
 We feel that it strongly justifies the use of a deterministic sending scheme for latency critical applications such as our C-RAN motivating problem.

### 2017-07-28 infocom/infocom.tex
avant pull vendredi matin

--- 2017-07-27 infocom/infocom.tex
@@
 \usepackage{authblk}
-% \usepackage{hyperref}
+\usepackage{hyperref}
 
@@
 it is compatible with an optical network with a fixed packet size.
+\renewcommand{\thefootnote}{\*}
+\footnote{\href{https://onedrive.live.com/?authkey=\%21AJIgVoXRuxz1jMU&cid=295858CA35B5113F&id=295858CA35B5113F\%21429&parId=root&o=OneUp}{Please click here to download an extended version with details of mathematical proofs.}}
 
@@
 On the other hand, PMLS finds an assignment with margin $0$ in a highly loaded $97\%$ of the time!
-     For each $1000$ slots of latency we remove from the periodic process, we are able to lengthen the routes of $10$km, which has a huge economic impact.
+     For each $1000$ slots of latency we avoid from the periodic process, we are able to lengthen the routes of $10$km, which has a huge economic impact.
      We feel that it strongly justifies the use of a deterministic sending scheme for latency critical applications such as our C-RAN motivating problem.

### 2017-07-28 infocom/infocom.tex

--- 2017-07-27 infocom/infocom.tex
@@
 That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network.
-We want to avoid any  buffering in internal nodes of the graph, hence we need to design a periodic process with no collisions between messages.
+As we want to avoid any  buffering in internal nodes of the graph.
+Hence we need to design a periodic process with no collision between messages.
 To ensure that this property is always true we propose a deterministic process.
@@
 it is compatible with an optical network with a fixed packet size.
+\renewcommand{\thefootnote}{\*}
+\footnote{\href{https://1drv.ms/b/s!Aj8RtTXKWFgpgy9SiBowQNfvH-r9}{Please click here to download an extended version with details of mathematical proofs.}}
 

### 2017-09-28 Papier NGreen/model.tex
rangement

--- 2017-03-28 modeleanneau/model.tex
@@
 \maketitle
+\section*{Problem}
+The application we study takes place in the C-Ran context.
+We want to centralise calculations into a common data-center for an area of antennas distributed on the territory.
+The data between the RRH (antennas) and the BBU (data-center) are transiting through an optical ring.
+We study here only the behaviour of the ring.
+First, for an easier model, we consider a ring in which one or two nodes are the data-centers, and the other nodes of the ring sends some data coming from the RRH.
 
-\section*{Definitions, model}
-We consider an optical ring composed of $k$ nodes.
-We are in a discrete time model: The time is split in $N$ slot, rotating to the following position each time step $t$.
-The number of slots is given by the length of the ring, and the time step $t$ is the switching granularity.
-\begin{center}
-
-      \includegraphics[scale=0.5]{anneau1.pdf}
-      \hspace{3cm}
-      \includegraphics[scale=0.5]{anneau2.pdf}
-
-\end{center}
-
-We consider a ring as a graph model.
-The weight of the arcs is the time taken by a slot to travel the link, i.e.
-a multiple of $t$.
-The sum of all the weight of the arcs in the graph is equal to $t.N$.
-
-\section*{Periodic process}
-We define a set $\cal C$ of couple of vertices $(u,v) \in V$. Between each couple of $\cal C$, the following periodic process of period $P$ ($P$ is a multiple of $N$) is observed.
+Every millisecond, between each couple RRH-BBU, the following periodic process is observed:
 \begin{enumerate}
- \item The node $u$ receives (from another source) some latency critical data addressed to $v$.
- \item Those data are transferred to $v$ through the ring .
- \item After a computation time of the message, the node $v$ sends an answer to $u$.
+ \item The RRH sends some latency critical data to its BBU.
+ \item Those data are transferred to the BBU through the ring .
+ \item After a computation time of the message, the BBU sends an answer to its RRH.
 \end{enumerate}
  This periodic process has a critical end to end latency, thus a messages has to be as little buffered as possible before being sent in the ring.
+ Every messages will browse the entire ring during the process. Since the ring is approximately 50km long, a messages needs $250 \mu s$ to travel this length.
+ Considering that the periodicity of the emissions ($1ms$) is greater than a ride of the ring, we take $P$ a multiple of the time needed to travel the ring.
 
 \section*{Sending policy}
-In the studied model, the nodes of the ring have a {\bf broadcast and select} policy.
+In the studied model, the nodes of the ring have a {\bf broadcast and select} policy. Then, the physical times needed to insert the data in the ring are negligible in regard of the other times.
 When a node sends a packet on the ring, it contains data for several destinations.
@@
 
-We can consider two buffers containing $x$ and $y$ amount of data, respectively for the C-RAN flow and the best effort flow.
-The data in the first buffer are inserted first in the buffer of the node, and comes periodically in regard of the period $P$. 
+We can consider two buffers containing $x$ and $y$ amount of data.
+The first one is filled with the C-Ran data in priority, and the best effort flow if needed, the second one takes the rest of best effort flow.
+We consider that, even if a lot of RRH are represented by a node on the ring, the amount of C-Ran data incoming to a node is strongly lower than the capacity of a packet ($\simeq 1.2$ Gbps for each RRH, 100 Gbps into the ring).
+The C-RAN data comes periodically in regard of the period $P = 1ms$. 
 The best effort data comes more randomly (can be modelled by a Poisson distribution, for example), and are inserted in the buffer if $x = 0$.
@@
 
-      \includegraphics[scale=0.7]{insertion.pdf}
+      \includegraphics[scale=0.7]{insertion1.pdf}
 
 \end{center}
+
+\section*{Model}
+We consider an optical ring composed of $k$ nodes ($k={3,...,10}$).
+We are in a discrete time model: the time is split in $N$ slot, rotating to the following position each time step $t = 10 \mu s$. This value is the switching granularity.
+\begin{center}
+
+      \includegraphics[scale=0.5]{anneau1.pdf}
+      \hspace{3cm}
+      \includegraphics[scale=0.5]{anneau2.pdf}
+
+\end{center}
+
+Considering a length of 50 km for the ring, we evaluate the number of slots about 25 into the ring.
 
@@
 
-\section*{Parameters}
-The following parameters are considered for the study:
-\begin{itemize}
- \item $k \in {3,..,10}$ nodes on the ring.
- \item The switching granularity $t = 10\mu s$. 
- \item The length of the ring = 50km. Thus $N = 25$ slots.
- \item Capacity of one slot $= 1Mb$.
- \item One slot of the ring can carry all the data stacked in $Q$ ($Q < 1Mb$).
-
-\end{itemize}
-
 \end{document}

### 2017-09-28 code/Calculs autres/ecart_type.c

@@ -1,255 +1,0 @@
-#include <stdio.h> 
-#include <stdlib.h>
-#include <math.h>
-
-#define taille 1000
-#define nb_periodes 30
-
-int donnes[nb_periodes][taille];
-float moyennes[nb_periodes];
-float en[nb_periodes];
-float ep[nb_periodes];
-
-
-
-//trié de la plus courte a la plus longue
-void tri_bulles(int* tab,int t)
-{
-	int sorted;
-	int tmp;
-
-	for(int i=t-1;i>=1;i--)
-	{
-		sorted = 1;
-		for(int j = 0;j<=i-1;j++)
-		{
-			if(tab[j+1]<tab[j])
-			{
-				tmp = tab[j+1];
-				tab[j+1]= tab[j];
-				tab[j]= tmp;
-				sorted = 0;
-			}
-		}
-		if(sorted){return;}
-	}
-
-}
-
-
-
-
-void lire_fichier()
-{
-	FILE * f = fopen("../datas/donnes_random.data","r");
-	if(!f){perror("Error opening file");exit(5);}
-	int trash;
-	for(int i=0;i<nb_periodes;i++)
-	{
-		for(int j=0;j<taille;j++)
-		{
-			//fscanf(f,"%d %d %d",&trash,&trash,&donnes[i][j]);
-			fscanf(f,"%d %d %d",&trash,&donnes[i][j],&trash);
-
-		}
-	}
-	fclose(f);
-
-}
-float moyenne(int numero_periode)
-{
-	float moy = 0;
-	for(int i=0;i<taille;i++)
-	{
-		moy += donnes[numero_periode][i];
-	}
-	return moy/taille;
-}
-float ecart_type_negatif(int numero_periode)
-{
-	float e = 0;
-	int t;
-	for(int i=0;i<taille;i++)
-	{
-		if(donnes[numero_periode][i] < moyennes[numero_periode])
-		{
-			e += ((donnes[numero_periode][i]-moyennes[numero_periode])*((donnes[numero_periode][i]-moyennes[numero_periode])));
-			t++;
-		}
-	}
-
-
-	e /= t;
-
-	return sqrt(e);
-}
-float ecart_type_positif(int numero_periode)
-{
-	float e = 0;
-	int t;
-	for(int i=0;i<taille;i++)
-	{
-		if(donnes[numero_periode][i] > moyennes[numero_periode])
-		{
[…]

### 2017-09-28 code/Calculs autres/liste.c

@@ -1,549 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-#include <time.h>
-#define DEBUT 0
-#define FIN 1
-#define TRIE 2
-
-
-struct elem{
-	int val;
-	struct elem *suiv;
-};
-
-typedef struct elem* liste;
-
-
-struct elem_liste{
-	liste l;
-	struct elem_liste *suiv;
-};
-
-typedef struct elem_liste* liste_liste;
-
-
-//Genere un entier entre 0 et n
-int alea(int n)
-{
-	return rand()%(n+1);
-}
-liste creer_liste(){return NULL;}
-
-int est_vide(liste l)
-{
-	if(l == NULL)
-		return 1;
-	return 0;
-}
-
-void affiche_liste(liste l)
-{
-	
-	if(est_vide(l))
-	{
-		printf("La liste est vide \n");
-		return;
-	}
-	while(l)
-	{
-		printf("%d ",l->val);
-		l = l->suiv;
-	}
-	printf("\n");
-}
-
-liste libere_liste(liste l)
-{
-	liste tmp;
-	while(l)
-	{
-		tmp = l->suiv;
-		//printf("libération de %d\n",l->val);
-		free(l);
-		l = tmp;
-	}
-	return NULL;
-}
-liste ajoute_elem_debut(liste l,int i)
-{
-	liste new = malloc(sizeof(struct elem));
-	new->val = i;
-	new->suiv = l;
-	return new;
-}
-
-liste ajoute_elem_fin(liste l, int i)
-{
-	liste new = malloc(sizeof(struct elem));
-	new->val = i;
-	new->suiv = NULL;
-	if(est_vide(l))
-	{
-		return new;
-	}
-	liste debut = l;
-	//on place le pointeur sur le dernier element de la liste
-	while(l->suiv)
-		l = l->suiv;
-	l->suiv = new;
-	return debut;
-}
-
-liste ajoute_elem_trie(liste l,int i)
-{
-	liste new = malloc(sizeof(struct elem));
-	new->val = i;
-	if(est_vide(l))//la liste est vide
-	{
-		new->suiv = NULL;
-		return new;
-	}
-
-	if(l->val > i)//insertion au debut
-	{
-		new->suiv = l;
-		return new;
-	}
-	liste debut = l;
-	//on sarrête soit quand on est au bout, soit quand on doit ajouter l'element
[…]

### 2017-09-28 code/Calculs autres/regression.c

@@ -1,109 +1,0 @@
-#include <stdio.h> 
-#include <stdlib.h>
-#include <math.h>
-#define nb_points 13
-
-
-float x[nb_points];
-float y[nb_points];
-
-
-void lire_fichier(int algo_choisi)
-{
-	FILE * f = fopen("../datas/results_periode.data","r");
-
-	int nombre_lu;
-	int colonne=0;
-	int ligne = 0;
-	while(fscanf(f,"%d",&nombre_lu))
-	{
-		if(colonne == 0)
-			x[ligne] = (float)nombre_lu;
-
-		if(colonne == algo_choisi)
-		{
-			y[ligne] = (x[ligne]*2500)/((float)nombre_lu);
-			//printf("%f %f \n",x[ligne], y[ligne]);
-		}
-		colonne++;
-
-		if(colonne == 7)
-		{
-			colonne = 0;
-			ligne ++;
-			if(ligne == nb_points)
-				break;
-		}
-	}
-	fclose(f);
-
-}
-
-
-void affiche_tab(float *tab)
-{
-	printf("[");
-	for(int i=0;i<nb_points;i++)
-	{
-		if(i < nb_points-1)
-			printf("%f;",tab[i]);
-		else
-			printf("%f]",tab[i]);
-	}
-	printf("\n");
-}
-
-float moyenne(float * tab)
-{
-	float moy=0;
-	for(int i =0;i<nb_points;i++)
-	{
-		moy += tab[i];
-	}
-	return moy/nb_points;
-}
-float variance(float * tab)
-{
-	float var = 0;
-	for(int i=0;i<nb_points;i++)
-	{
-		var += tab[i]*tab[i];
-	}
-	var /= nb_points;
-	return (float)(var - moyenne(tab)*moyenne(tab));
-
-}
-float covariance()
-{
-	float co_var = 0;
-	for(int i=0;i<nb_points;i++)
-	{
-		co_var += x[i]*y[i];
-	}
-	co_var /= nb_points;
-	return (float)(co_var - moyenne(x)*moyenne(y));
-
-}
-float coef_dir()
-{
-	return covariance()/variance(x);
-}
-
-float ordonee_origine()
-{
-	return moyenne(y)-coef_dir()*moyenne(x);
-}
-
-float coefficient_correlation()
-{
-	return covariance()/(sqrt(variance(x)*variance(y)));
-}
-int main()
-{
-	for(int i=1;i<5;i++)
-	{
-		lire_fichier(i);
[…]

### 2017-09-28 code/Calculs autres/variance.c

@@ -1,48 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-#include <time.h>
-#include <math.h>
-
-#define LAMBDA 14
-
-int loi_de_poisson_naif(float u)
-{
-	double p = exp (- LAMBDA);
-	int x = 0;
-	double f = p;
-	do
-	{
-		x += 1;
-		p = p*LAMBDA/x;
-		f += p;
-	} while (u > f);
-	return x;
-}
-
-
-int main(){
-	srand(time(NULL));
-	double variance = 0.0;
-	double moyenne = 0.0;
-
-	int nb_simuls = 1000000;
-	int result;
-	int max = 0;
-	float tirage; 
-	for(int i=0;i<nb_simuls;i++)
-	{
-		tirage = (float)rand() / RAND_MAX ;
-		result = loi_de_poisson_naif(tirage);
-		if(result*5 > max)max=result*5;
-		variance += (result*result);
-		moyenne += result;
-	}
-	moyenne /= nb_simuls;
-
-
-	variance /= nb_simuls;
-	variance -= (moyenne*moyenne);
-
-	printf("Variance = %f, Moyenne = %f, MAX = %d\n",variance,moyenne,max);
-	return 0;
-}

### 2017-09-28 code/Sources/PALL.h

@@ -1,5 +1,0 @@
-int longest_etoile_2(Graphe g,int taille_paquets,int periode, int Tmax,int mode);
-int longest_etoile_periodique(Graphe g,int taille_paquets,int periode, int Tmax,int mode);
-//int stochastic(Graphe g, int taille_paquets, int periode, int tmax);
-int linear_simons_per(Graphe g,int periode,int taille_message,int nb_rand);
-//int linear_stochastic(Graphe g,int periode,int taille_message);

### 2017-09-28 code/Sources/PAZL.h

@@ -1,23 +1,0 @@
-
-
-
-int algo_shortest_longest(Graphe g,int periode,int taille_message);
-int algo_3NT(Graphe g,int periode,int taille_message);
-
-
-int algo_prime(Graphe g,int periode,int taille_message);
-
-int bruteforceiter(Graphe g, int periode,int taille_paquets);
-
-int search(Graphe g,int message_size, int period);
-
-int linear_3NT(Graphe g,int taille_message);
-
-
-int linear_prime(Graphe g,int taille_message);
-
-
-
-int linear_brute(Graphe g,int taille_message);
-
-int linear_search(Graphe g,int taille_message);

### 2017-09-28 code/Sources/init.c

@@ -1,99 +1,0 @@
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <assert.h>
-#include <time.h>
-
-
-#include "struct.h"
-#include "tests.h"
-
-//Déclare une matrice remplie de 0 de taille N*N
-int ** declare_matrice(int N)
-{
-	int ** matrice;
-	assert(matrice = malloc(sizeof(int*)*N));
-	for(int i = 0;i<N;i++)
-	{
-		assert(matrice[i]= calloc(N,sizeof(int)));
-	}
-	return matrice;
-}
-
-
-Graphe init_graphe(int N)
-{
-	Graphe g;
-	g.N = N;
-	g.matrice = declare_matrice(N);
-	return g;
-}
-void libere_matrice(Graphe g)
-{
-	for(int i=0;i<g.N;i++)
-	{
-		free(g.matrice[i]);
-	}
-	free(g.matrice);
-}
-
-//prends un graphe vide en argument et le transforme en etoile
-void graphe_etoile(Graphe g,int taille_liens)
-{
-	if(!(g.N%2)){printf("Impossible de générer une étoile avec un nombre pair de sommets\n");exit(5);}
-	int pivot = g.N/2;
-	int alea;
-
-	for(int i=0;i<g.N;i++)
-	{
-		alea = rand()%taille_liens;
-
-		g.matrice[pivot][i] = alea;
-		g.matrice[i][pivot] = alea;
-	}
-	g.matrice[pivot][pivot] = 0;
-}
-//prends un graphe vide en argument et le transforme en etoile Dans laquelle les arcs Ct-ti sont nuls
-void graphe_etoile_opti(Graphe g,int taille_liens)
-{
-	if(!(g.N%2)){printf("Impossible de générer une étoile avec un nombre pair de sommets\n");exit(5);}
-	int pivot = g.N/2;
-	int alea;
-	for(int i=0;i<pivot;i++)
-	{
-		alea = rand()%taille_liens;
-		g.matrice[pivot][i] = alea;
-		g.matrice[i][pivot] = alea;
-	}
-	g.matrice[pivot][pivot] = 0;
-}
-
-//prends un graphe vide en argument et le transforme en etoile dure a resoudre
-void graphe_etoile_dur(Graphe g,int taille_liens,int diff)
-{
[…]

### 2017-09-28 code/Sources/init.h

@@ -1,14 +1,0 @@
-
-
-int ** declare_matrice(int N);
-
-
-
-Graphe init_graphe(int N);
-
-void libere_matrice(Graphe g);
-
-void graphe_etoile(Graphe g,int taille_liens);
-
-void graphe_etoile_opti(Graphe g,int taille_liens);
-void graphe_etoile_dur(Graphe g,int taille_liens,int diff);

### 2017-09-28 code/Sources/random.c

@@ -1,192 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-
-#include "struct.h"
-#include "operations.h"
-#include "tests.h"
-
-struct elem{
-	int numero_route;
-	int depart;
-	int arrivee;
-	struct elem *suiv;
-};
-
-typedef struct elem* liste;
-
-typedef struct{
-	liste pile;
-	int taille;
-}Pile;
-
-int est_vide(liste l)
-{
-	if(l == NULL)
-		return 1;
-	return 0;
-}
-
-
-liste ajoute_elem_trie(liste l,int depart,int arrivee, int numero_route)
-{
-	liste new = malloc(sizeof(struct elem));
-	new->numero_route = numero_route;
-	new->depart = depart;
-	new->arrivee = arrivee;
-	if(est_vide(l))//la liste est vide
-	{
-		new->suiv = NULL;
-		return new;
-	}
-
-	if(l->arrivee > arrivee)//insertion au debut
-	{
-		new->suiv = l;
-		return new;
-	}
-	liste debut = l;
-	//on sarrête soit quand on est au bout, soit quand on doit ajouter l'element
-	while(l->suiv)
-	{
-		if(l->suiv->arrivee > arrivee)//insertion au milieu
-		{
-			new->suiv = l->suiv;
-			l->suiv = new;
-			return debut;
-		}
-		l = l->suiv;
-	}
-	//Si on arrive la, c'est qu'on est à la fin.
-	l->suiv = new;
-	new->suiv = NULL;
-	return debut;
-}
-//supprime l'element d'indice i
-liste supprime_elem(liste l, int i)
-{
-	if(est_vide(l))return l;
-	//Premier element
-	liste tmp;
-	if(i == 0)
-	{
-		tmp = l->suiv;
-		free(l);
-		return tmp;
-	}
-	liste debut = l;
-	int compteur = 0;
-	while(l->suiv->suiv)
-	{
-		if(compteur == i-1)
-		{
-			tmp = l->suiv;
-			l->suiv = l->suiv->suiv;
-			free(tmp);
-			return debut;
-		}
-		compteur++;
-		l = l->suiv;
-	}
-	//cas du dernier element
-	if(compteur == i-1)
-	{
-		tmp = l->suiv;
-		l->suiv = NULL;
-		free(tmp);
-	}
-	return debut;
-	
-}
-
-liste libere_liste(liste l)
-{
-	liste tmp;
-	while(l)
-	{
-		tmp = l->suiv;
[…]

### 2017-09-28 code/Sources/random.h

@@ -1,1 +1,0 @@
-int stochastic(Graphe g, int taille_paquets, int periode, int nombre_periodes, int mode);

### 2017-09-28 code/Sources/simons.c

@@ -1,1516 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-#include <limits.h>
-#include <math.h>
-
-#include "struct.h"
-#include "operations.h"
-
-typedef struct element{
-	int index;
-	int release;
-	int deadline;
-	struct element * next;
-} Element;
-
-typedef struct ensemble{
-	int numero_element; // vaut -1 si c'est un ensemble
-	int temps_depart;
-	struct ensemble * filsG;
-	struct ensemble * frereG;
-	struct ensemble * frereD;
-} Ensemble;
-
-
-Ensemble * crisis(Ensemble * ens,Element * crisise, Element * elemspere,Element * touselems, int taille_paquet,int periode);
-Ensemble * init_ensemble(){return NULL;}
-Element * init_element(){return NULL;}
-
-
-
-/** Fonctions d'affichage pour simons *
-
-
-*****************/
-
-void affiche_ensemble_unique(Ensemble * ens)
-{
-	if(!ens)
-	{
-		printf("VIDE\n");return;
-	}
-	printf("(%p) num %d / date %d /fils g %p /frereG %p /frereD %p\n",ens,ens->numero_element,ens->temps_depart,ens->filsG,ens->frereG,ens->frereD);
-}
-void affiche_ensemble(Ensemble * ens)
-{
-	//affiche_1_ensemble(ens);
-	if(ens == NULL)
-	{
-		printf("ENSEMBLE VIDE");
-		return;
-	}
-	if(ens->numero_element == -1) // si c'est un ensemble
-	{
-		//si c'est un ensemble, par définition il a forcement un fils gauche
-		//qui est soit un élément, soit un ensemble, donc appel recursif sur le fils gauche
-		printf("Sous ensemble(%d){ ",ens->temps_depart);
-		affiche_ensemble(ens->filsG);
-		printf("} ");
-		
-	}
-	else //si c'est un élément
-	{
-		printf("%d(%d) ",ens->numero_element,ens->temps_depart);
-	}
-	ens = ens->frereD;
-	while(ens)
-	{
-		if(ens->numero_element == -1)
-		{
-			affiche_ensemble(ens);
-			return;
-		}
-		else
-		{
-			printf("%d(%d) ",ens->numero_element,ens->temps_depart);
-		}
-		ens = ens->frereD;
-	}
-	
-}
-
-
-
-
[…]

### 2017-09-28 code/Sources/simons.h

@@ -1,6 +1,0 @@
-
-int simons(Graphe g, int taille_paquet, int TMAX,int periode, int mode);
-int simons_periodique(Graphe g, int taille_paquet,int TMAX, int periode, int mode);
-
-
-

### 2017-09-28 code/Sources/simulations.c

@@ -1,711 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-#include <omp.h>
-#include <limits.h>
-#include <math.h>
-#include <sys/time.h>
-
-#include "struct.h"
-#include "PAZL.h"
-#include "PALL.h"
-#include "simons.h"
-#include "init.h"
-#include "operations.h"
-#include "tests.h"
-#include "random.h"
-
-#define PARALLEL 1
-
-//Effectue une recherche linéaire pour les algos PAZL afin de trouver la plus petite periode moyenne
-void simuls_periode_PAZL(int nb_routes, int taille_message, int taille_routes,int nb_simuls)
-{
-	FILE * F = fopen("../datas/results_periode.data","w");
-	Graphe g;
-	long long int total_3NT, total_brute,total_sl,total_search;
-	int res_sl,res_brute,res_3NT,res_search;
-
-	
-	for(int j = 2 ; j<=nb_routes;j++)
-	{
-		printf("Calculs pour %d routes: \n",j);
-		
-		total_3NT = 0;
-		total_brute = 0;
-		total_sl =0;
-		total_search = 0;
-		#pragma omp parallel for private(res_sl,res_brute,res_3NT,res_search,g) if (PARALLEL) schedule (static)
-		for(int i = 0;i<nb_simuls;i++)
-		{
-			g = init_graphe(j*2 + 1);
-			graphe_etoile(g,taille_routes);
-			res_3NT = linear_3NT(g,taille_message);
-			//if(res_3NT > total_3NT)total_3NT = res_3NT;
-			if(res_3NT != -1){
-				#pragma omp atomic
-				total_3NT+=res_3NT;
-			}
-			//else printf("error (3nt = -1)\n");
-
-			//res_brute = linear_brute(g,taille_message);
-			res_brute = 1;
-			//if(res_brute > total_brute)total_brute = res_brute;
-			if(res_brute != -1){
-				#pragma omp atomic
-				total_brute+=res_brute;
-			}
-			//else printf("error (brute = -1)\n");
-
-			res_sl = algo_shortest_longest(g,3*taille_message*nb_routes,taille_message);
-			//if(res_sl > total_sl)total_sl = res_sl;
-			if(res_sl != -1){
-				#pragma omp atomic
-				total_sl+=res_sl;
-			}
-			//else printf("error (Sl = -1)\n");
[…]

### 2017-10-20 Papier NGreen/model.tex
img dans papier model

@@
 \usepackage{graphicx,graphics}
+
+\graphicspath{{img/}}
 
@@
 \maketitle
-\section*{Problem}
+\section{Introduction}
+Blabla sur le contexte du projet NGREEN
+
+\section{Model}
+
+  \subsection{Optical ring}
+    Graphe oriente representant un anneau, definition des terme delay
+  \subsection{Discrete time model}
+    temps slotte correspondant a un tick d'horloge
+  \subsection{Into the node : Two kind of traffics}
+    Descripion buffers/ on prepare des conteneurs.definition des therme paquet slot buffers
+    Description CRAN-BE, precision sur le modele de generation
+    presentation des differentes politiques d'insertion.
+
+  \subsection{Objectives}
+    Etudier Le comportement de nos politiques
+    Trouver une solution deterministe et etudier l'impact sur les BE
+
+\section{Study of the different insertion policies}
+
+  \subsection{Parameters}
+  Peut etre attendre les resultats de youssef pour fixer les deadline et seuil d'envoi dans les simuls.
+  \subsection{No management}
+  \subsection{CRAN priority}
+  Conclure que c'est pas top top, même si c'est clairement mieux en CRAN, et qu'on va faire du determinisme.
+
+\section{Deterministic approach for 0 latency on CRAN}
+  \subsection{Packing}
+  \subsection{Spreading}
+  Pour ces deux la, ecrire proprement les ``algos''
+  \subsection{Impact on the BE}
+  REsultats de simuls
+
 The application we study takes place in the C-Ran context.

### 2017-10-23 Papier NGreen/model.tex
debut implem

@@
 \usepackage{graphicx,graphics} 
+\usepackage{hyperref}
+
+\usepackage{algorithm2e}
+\SetAlgoLined
+\SetKwProg{MyStruct}{Struct}{ contains}{end}
 
@@
 \section{Deterministic approach for 0 latency on CRAN}
+\label{det}
   \subsection{Packing}
@@
   REsultats de simuls
+
+\section{ Implementation details}
+
+	The source code int C of the simulator used for our experimental results is available on the \href{https://github.com/Mael-Guiraud/Ngreen.git}{ author's github page}.
+	\subsection{Initialisation}
+	First, we need to put coherent parameters , considering the model. For instance, with the parameters of NGREEN, we can not set more than 10 antennas on the ring. 
+	The ring is modeled by a table of packets.
+
+	\begin{algorithm}[H]
+	\MyStruct{packet}{
+ 		int id\_owner\; \tcp{-1 if there is no packet on the slot.}
+  		int size\_CRAN\; \tcp{Nb messages CRAN in the packet\, useful to generate the answers.}
+  		int id\_reservation\; \tcp{Useful in the reservation model\, -1 otherwise.}
+	}
+	\end{algorithm}
+
+	We then, for each antenna, initialize the first date $t$ on which the antenna send some traffic.
+The antenna will then send a message every 10 slots after $t$, during a fixed total time, depending of the throughput of the antenna.
+	 In the Insertion Policy models, this date $t$ is randomly drawn with the rand() functions of stdlib.
+In the Reservation model, this date $t$ is set by the scheduling algorithms described in sec~\ref{det}.
+
+	Since the time is discretized, a slot (a unit of time) correspond to one round of a loop.
+The duration of the loop is set to be large enough to obtain some confident experimental results.
+Each round of the simulation loop, ...
 

### 2017-10-23 Papier NGreen/model.tex
pull dessin

@@
 	First, we need to put coherent parameters , considering the model. For instance, with the parameters of NGREEN, we can not set more than 10 antennas on the ring. 
-	The ring is modeled by a table of packets.
+	The ring is modeled by a circular table of struct packets.
 
@@
 	We then, for each antenna, initialize the first date $t$ on which the antenna send some traffic.
-The antenna will then send a message every 10 slots after $t$, during a fixed total time, depending of the throughput of the antenna.
+The antenna will then send a message every 10 slots after $t$, during a fixed total emission time, depending of the throughput of the antenna.
 	 In the Insertion Policy models, this date $t$ is randomly drawn with the rand() functions of stdlib.

### 2017-10-23 Papier NGreen/model.tex
Crangeneration dans la description du code

@@
 \section{Model}
-
+  \label{model}
   \subsection{Optical ring}
@@
 	\MyStruct{packet}{
- 		int id\_owner\; \tcp{-1 if there is no packet on the slot.}
+ 		int owner\_id\; \tcp{-1 if there is no packet on the slot.}
   		int size\_CRAN\; \tcp{Nb messages CRAN in the packet\, useful to generate the answers.}
-  		int id\_reservation\; \tcp{Useful in the reservation model\, -1 otherwise.}
+  		int reservation\_id\; \tcp{Useful in the reservation model\, -1 otherwise.}
 	}
@@
 
-	We then, for each antenna, initialize the first date $t$ on which the antenna send some traffic.
+	For each antenna, we initialize the first date $t$ on which the antenna send some traffic.
 The antenna will then send a message every 10 slots after $t$, during a fixed total emission time, depending of the throughput of the antenna.
+
+\begin{center}
+
+      \includegraphics[width=\textwidth]{emission_antenna.pdf}
+
+\end{center}
+
 	 In the Insertion Policy models, this date $t$ is randomly drawn with the rand() functions of stdlib.
@@
 The duration of the loop is set to be large enough to obtain some confident experimental results.
-Each round of the simulation loop, ...
+During each round of the simulation loop, we first generate the best effort and CRAN traffic, following the laws described in sec~\ref{model}.
+
+	Then, we call the \texttt{insert\_packets()} function to send the packets on the ring, if needed (i.e, if some CRAN has been generated, or the BE buffer is large, or old enough).
+	Finally, the function \texttt{rotate\_ring()} is called, and every struct packets of the circular ring takes the following position in the table (the last cell of the table take the position 1).
+	Afterwards, we call the \texttt{remove\_packets()} function, that free the reading\_slot of a node, if the packet on it has been sent by this node.
+	\subsection{BE-Generation}
+	The best effort generation follows the SBBP decribed in sec~\ref{model}.
+Since the batch process have, at the most 10 states, this functions runs in $O(1)$: one random drawing for the transition in the markov chain, another random drawing for the batch process, and the Inverse transform sampling, which is bounded by the number of states.
+	\subsection{CRAN-Generation}
+	We splitted the CRAN-Generation in two steps.
+First, the nodes which are not the BBU adds their messages from antennas to buffers, if needed.
+In a second time, the BBU generates and answer in it's buffer, if there is a CRAN packet in the reading\_slot of the BBU.
 

### 2017-11-05 Papier NGreen/model.tex
description code

@@
 In a second time, the BBU generates and answer in it's buffer, if there is a CRAN packet in the reading\_slot of the BBU.
+	\subsection{Insertion packet}
+	A node emits a packet on the ring, in its writting\_slot, if :
+\begin{itemize}
+\item In no management mode :  if the size of the buffer is greater or equal to $\beta .Q $ ($\beta \in ]0;1] , Q$ is the size of the buffer) , or if the oldest datas has arrived in the buffer before or to $t-\alpha$, ( $t$ is the current slot, and $\alpha$ is the deadline, expressed in slot).
+\item In CRAN priority mode : 
+	\begin{itemize}
+	\item If the BE-buffer satisfy one of the latter condition,
+	\item Or if there is some CRAN in the CRAN\_buffer. The packet emitted contains all the CRAN possible, filled with as much BE as possible. 
+	\end{itemize}
+\item in reservation mode, the slot on the writting\_slot of the node must be not reserved, or reserved for the node. Then the constraints are the same than the CRAN-priority mode.
+\end{itemize} 	
+\subsection{Slot Reservation}
+In reservation mode, the main challenge is to reserve the slots for the nodes.
+Indeed, if a nodes $i$ needs the slot in his wrtting\_slot at time $t$, this slot needs to be reserved at time $t - size\_ring$ by $i$.
+In this situation, if the slot is already taken by a packet which has been sent by the node $k$, $k$ will remove the packet of the slot during the next lap of the ring, and no other nodes are able to write in this slot before it cames back to the node $i$ a date $t$.
+
+One must study the impact of the reservation on the behavior of the ring.
+If we want to send a packet in a slot at time $t$, as we described upper, the slot must be reserved one $size\_ring$ before, by the nodes which needs to send the packet.
+This is the job of the reservation : avoiding others nodes to write in a slot which will be used by the node $i$ at time $t$.
+Though his reservation allows the CRAN messages to have 0 latency, it impacts the best effort, by avoiding them to use free slots; For the best efforts packets, a slot full represents the same thing as a reserved slot.
+
+Another behavior of a packet on the ring that we must consider is the following one:
+ if a node $i$ sends a packet at time $t$, the slot will be used during $t+ size\_ring$ slots.
+Thus, even if a node emits once, we must take into consideration the fact that the slot is used in the entire ring during $size\_ring$ slots.
+This means that no others nodes can use this slot to emit a packet on the ring.
+This case is problematic if we have $ET =P/2$.
+For instance, if we want to send a periodic message of size $50$ each $100$ slots on two nodes on a ring, If the node $u$ sends the first packet of it's message at date $0$.
+Thus, $u$ will emit some packets every periods, during $100$ slots, that is $[kP;ET+kP[, k \in N$.
+Then, the node $v$ will receive the messages from $u$ each period at time $[kP + \lambda(u,v);ET+kP+\lambda(u,v)[$.
+Thus, $b$ will emit on the ring at time $[ET + kP + \lambda(u,v);ET+kP+\lambda(u,v) + ET[$, and $a$ will receive those packets from $b$ to $[ET + kP + \lambda(u,v) + \lambda(v,u);ET+kP+\lambda(u,v) + ET + \lambda(v,u)[$, that is $[ET + kP + RS; (k+1)P+RS[$.
+If we take $k=0$, then $a$ will emit at time $[0;ET[$ then $[P;ET+P[$, and receive the first message of $b$ at time $[ET + RS;  P+RS[$.
+He one can observe that, during $RS$ slots after $ET$ in $a$, the ring is used by $b$ and then $a$ cannot emit on the ring.
+Thus, the maximum size that two nodes can share on the ring is $P/2 -RS$.
+
+We distinguish tree cases for the reservation model:
+\begin{enumerate}
+\item If $2n < EP $.
+\item If $2n >EP . \frac{P}{ET+RS}$
+\item if $ET = P/2$
+\end{enumerate}
+
+In the first case, since we have enough frequencies to order the antennas and theirs answers, we only give one block of frequency to each antennas.
+For instance, if we have $EP = 10$ and $3$ antennas, we give frequencies $0$ and $1$ to the first antenna, $2$ ans $3$ to the second antenna, and $4$ and $5$ to the third antenna.
+
+One can use a smarter method to order k antennas on n frequencies.
+By expressing $n = q.k + r$, we put a gap of q frequencies between each antennas, except the last r antennas that are spaced by $q+1$ frequencies.
+
+In the second cases, each bloc of $\frac{P}{ET+RS}$ behave like the first case, and we split the different antennas between the different blocks by using the repartition algorithm described above.
+
+In the third case, if $ET = P/2$, we can not schedule the entire emission of a message on the same frequency, because there will be $RS$ slots during while there will be some conflict at the insertion.
+Thus, we need to reserve some frequencies to carry the last packet of the messages.
+The number of frequencies reserved is $2 .\lceil \frac{2.RS.N}{P}\rceil$.
 

### 2017-11-23 Papier NGreen/model.tex
tex

@@
 \usepackage{hyperref} 
+\usepackage{mathtools, bm}
+\usepackage{amssymb, bm}
 
@@
   \subsection{Optical ring}
-    Graphe oriente representant un anneau, definition des terme delay
-  \subsection{Discrete time model}
-    temps slotte correspondant a un tick d'horloge
+  Consider a directed circular graph $C_N$ representing an optical ring.
+$N$ is the number of nodes on the ring/the graph.
+Each arc $(u,v)$ is labeled by an integer distance $d(u,v)$ corresponding to the physical delay of the link in the ring, i.e.
+the time taken by a signal to go from $u$ to $v$ using this arc.
+
+  \subsection{Message Granularity}
+    The time is discretized.
+The unit of time is the {\bf time slot}.
+Each arc $(u,v)$ can be represented as a sequence of {\bf slots} $\{s_1, ...
+, s_k\}$, with $k = d(u,v)$.
+We denote by $s_n(u,v)$ the $n^{th}$ slot of the arc $(u,v)$.
+$s_i(v), i\in \{-d(u,v), ...
+, -1\} \cup \{1 , ...
+, d(v,w)\}$ is the $i^{th}$ slot after (before if $i<0$) v on the ring.
+    On the following example, the red slot can be denoted by $s_2(u,v)$, $s_2(u)$ or $s_{-6}(v)$. 
+    \begin{figure}[h]
+    \centering
+      \includegraphics[scale=0.5]{suv.pdf}
+
+      \caption{A link $(u,v)$ represented as a sequence of slots}
+  \end{figure}
+
+  Each node $v$ has a reading access on $s_{-1}(v)$ and a writing access on $s_{1}(v)$.
+Those slots are named respectively the reading and writing slots of $v$.
+Thus, during a time slot, a node $v$ can insert a {\bf packet} on it's writing slot, if it is allowed to.
+We will define the right of the nodes later on this paper.
+Then, at the end of the time slot, each packets skip to the next slot.
+A packet emitted by a node $u$ on it's writing slot $s_1(u)$ will be available in reading for a node $v$ on it's reading slot $s_{-1}(v)$ $d(u,v) -1$  time slot later.
+\begin{figure}[h!]
+      \includegraphics[scale=0.5]{anneau1.pdf}
+      \hspace{3cm}
+      \includegraphics[scale=0.5]{anneau2.pdf}
+      \caption{One rotation of the ring}
+  \end{figure}
+  \subsection{Broadcast and select policy}
+  The ring follows a broadcast and select behavior.
+When a packet is inserted in a slot on the ring, by a node, no other nodes are able to write on this slot.
+This packets can contain some data from several nodes on the ring, that are able to read in the packet.
+The only node which has the right to remove the packet from the slot is the owner.
+This mean that every packet makes exactly one lap of the ring.
+Furthermore, to write on a slot, a node has to have an empty slot in it's writing slot.
+
+    \subsection{CRAN Context}
+    Our study takes place in the C-RAN context.
+The purpose is to centralise the calculation units of some antennas, distributed on the field.
+To each antenna, called RRH (Remote Radio Head), is associated a BBU (BaseBand Unit) in the datacenter.
+      The periodic process is the following: each {\bf period $P$}, every RRH send some datas thought the ring to it's BBU, then, after a computation time in the BBU, this latter answers to the corresponding RRH.
+      The time between the emission of the message by the RRH and the reception of the answers by the same RRH is called {\bf process time} and must not be too large, considering some 5G standards.
+      In this paper we will consider that all the BBU are grouped in the same node, called {\bf datacenter}, and that the antennas are distributed on the others node of the ring.
+
   \subsection{Into the node : Two kind of traffics}
-    Descripion buffers/ on prepare des conteneurs.definition des therme paquet slot buffers
-    Description CRAN-BE, precision sur le modele de generation
-    presentation des differentes politiques d'insertion.
+    To build the packets that are sent in the ring, the nodes have to deal with two kinds of traffic: 
+    \begin{itemize}
+    \item The {\bf Best effort traffic}, representing the internet flow.
+    \item The {\bf C-RAN traffic}, representing the high priority flow.
+    \end{itemize}
+    Let us denote {\bf BE-message} and {\bf CRAN-message} the unit of data of this flows. A packet is made of several BE-messages or CRAN-messages, and can be a combination of both kind of messages.
+    The messages coming to a node are buffered, and the nodes send a packet with the messages if : 
+     \begin{itemize}
+    \item The oldest message has arrived on the buffer before $t - \alpha$, if  $t$ is the actual time.
+    \item The fill rate of the buffer is greater or equal than $\beta$.
+    \end{itemize}
+    Those parameters $\alpha$ and $\beta$ are fixed by the network specification.
+
+    \begin{figure}[h!]
+        \begin{center}
+      \includegraphics[scale=0.5]{insertionbuff.pdf}
+
+      \caption{The packet creation buffer}
+      \end{center}
+  \end{figure}
+
+This behavior is the basic one, the buffer of a node is filled following the FIFO rule by the BE and C-RAN traffics.
+Then, when the node has an available free slot, the packet is created and inserted in the slot if one of the previous constraints are satisfied.
+Otherwise the node does not send anything in the ring and wait for the next free slot.
+
+    \begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.7]{insertion0.pdf}
+
+     \caption{No management mode.}
+\end{center}
+  \end{figure}
+
+  In order to improve the CRAN-messages latency, we first imagined the following solution.
+Each nodes have two buffers.
+One for the BE-messages, and one fore the CRAN-messages.
+When a node is able to send some messages on the ring, i.e.
+the slot on it's writing slot is free, the packet is filled with the CRAN-messages first.
+
+    \begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.7]{insertion1.pdf}
+
+     \caption{CRAN priorirty mode.}
+\end{center}
+  \end{figure}
+
+ In the next section, one can find the experimental performance evaluation of those two modes which show that, even for the CRAN priority mode, when the network is loaded, the latency of the CRAN messages is not low enough.
+
+ Thus, we propose a deterministic approach in which we set the first date at which the antenna starts to emit and then we reserve the slots needed for the CRAN-message by preventing the others node to write in those slots during the previous ring lap of the slot.
 
   \subsection{Objectives}
-    Etudier Le comportement de nos politiques
-    Trouver une solution deterministe et etudier l'impact sur les BE
+    The main challenge of our study is to improve the CRAN-messages latency, such that the process time does not exceed a given time ${\bf T_{max}} $ while not penalizing too much the BE-messages.
+
+    To understand the deterministic algorithm, one must introduce the behavior of the antennas.
+    \subsection{CRAN message generation}
+    The antennas send some heavy packets in the network.
+First, those packets are carried to the node of the right through an electronic network.
+Thus, the node is able to transform an electronic packet of $10\mu s$ in an optical packet of $1\mu s$.
+This multiplexing is explained in (DOC).
+
+        \begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.3]{slot1.pdf}
+  \includegraphics[scale=0.3]{slot2.pdf}
+     \caption{Electronic-optical interface.}
+
+\end{center}
+  \end{figure}
+    Thus, an antenna can not send of the ring more than every $10\mu s$. This time is called $EP$ (Emission Period).
+    We denote by $ET<P$ (Emission time) the time of the emission of an antenna. Thus, an antenna emits ET/EP packets on the ring, during a period $P$.
+
+        \begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[width=\textwidth]{emission_antenna.pdf}
+     \caption{Antenna traffic on the ring.}
+
+\end{center}
+  \end{figure}
+    \subsection{BE message generation}
+    	The BE message flow is modeled with a Switch Bernoulli Batch Process (SBBP). Ajouter Doc et details
 
@@
 \label{det}
-  \subsection{Packing}
-  \subsection{Spreading}
-  Pour ces deux la, ecrire proprement les ``algos''
-  \subsection{Impact on the BE}
-  REsultats de simuls
-
-\section{ Implementation details}
-
-	The source code int C of the simulator used for our experimental results is available on the \href{https://github.com/Mael-Guiraud/Ngreen.git}{ author's github page}.
-	\subsection{Initialisation}
-	First, we need to put coherent parameters , considering the model. For instance, with the parameters of NGREEN, we can not set more than 10 antennas on the ring. 
-	The ring is modeled by a circular table of struct packets.
-
-	\begin{algorithm}[H]
-	\MyStruct{packet}{
- 		int owner\_id\; \tcp{-1 if there is no packet on the slot.}
-  		int size\_CRAN\; \tcp{Nb messages CRAN in the packet\, useful to generate the answers.}
-  		int reservation\_id\; \tcp{Useful in the reservation model\, -1 otherwise.}
-	}
-	\end{algorithm}
-
-	For each antenna, we initialize the first date $t$ on which the antenna send some traffic.
-The antenna will then send a message every 10 slots after $t$, during a fixed total emission time, depending of the throughput of the antenna.
-
-\begin{center}
-
-      \includegraphics[width=\textwidth]{emission_antenna.pdf}
-
-\end{center}
-
-	 In the Insertion Policy models, this date $t$ is randomly drawn with the rand() functions of stdlib.
-In the Reservation model, this date $t$ is set by the scheduling algorithms described in sec~\ref{det}.
-
-	Since the time is discretized, a slot (a unit of time) correspond to one round of a loop.
-The duration of the loop is set to be large enough to obtain some confident experimental results.
-During each round of the simulation loop, we first generate the best effort and CRAN traffic, following the laws described in sec~\ref{model}.
-
-	Then, we call the \texttt{insert\_packets()} function to send the packets on the ring, if needed (i.e, if some CRAN has been generated, or the BE buffer is large, or old enough).
-	Finally, the function \texttt{rotate\_ring()} is called, and every struct packets of the circular ring takes the following position in the table (the last cell of the table take the position 1).
-	Afterwards, we call the \texttt{remove\_packets()} function, that free the reading\_slot of a node, if the packet on it has been sent by this node.
-	\subsection{BE-Generation}
-	The best effort generation follows the SBBP decribed in sec~\ref{model}.
-Since the batch process have, at the most 10 states, this functions runs in $O(1)$: one random drawing for the transition in the markov chain, another random drawing for the batch process, and the Inverse transform sampling, which is bounded by the number of states.
-	\subsection{CRAN-Generation}
-	We splitted the CRAN-Generation in two steps.
-First, the nodes which are not the BBU adds their messages from antennas to buffers, if needed.
-In a second time, the BBU generates and answer in it's buffer, if there is a CRAN packet in the reading\_slot of the BBU.
-	\subsection{Insertion packet}
-	A node emits a packet on the ring, in its writting\_slot, if :
-\begin{itemize}
-\item In no management mode :  if the size of the buffer is greater or equal to $\beta .Q $ ($\beta \in ]0;1] , Q$ is the size of the buffer) , or if the oldest datas has arrived in the buffer before or to $t-\alpha$, ( $t$ is the current slot, and $\alpha$ is the deadline, expressed in slot).
-\item In CRAN priority mode : 
-	\begin{itemize}
-	\item If the BE-buffer satisfy one of the latter condition,
-	\item Or if there is some CRAN in the CRAN\_buffer. The packet emitted contains all the CRAN possible, filled with as much BE as possible. 
-	\end{itemize}
-\item in reservation mode, the slot on the writting\_slot of the node must be not reserved, or reserved for the node. Then the constraints are the same than the CRAN-priority mode.
-\end{itemize} 	
 \subsection{Slot Reservation}
@@
 
-The application we study takes place in the C-Ran context.
-We want to centralise calculations into a common data-center for an area of antennas distributed on the territory.
-The data between the RRH (antennas) and the BBU (data-center) are transiting through an optical ring.
-We study here only the behaviour of the ring.
-First, for an easier model, we consider a ring in which one or two nodes are the data-centers, and the other nodes of the ring sends some data coming from the RRH.
+  \subsection{Packing}
+  \subsection{Spreading}
+  Pour ces deux la, ecrire proprement les ``algos''
+  \subsection{Impact on the BE}
+  REsultats de simuls
 
-Every millisecond, between each couple RRH-BBU, the following periodic process is observed:
-\begin{enumerate}
- \item The RRH sends some latency critical data to its BBU.
- \item Those data are transferred to the BBU through the ring .
- \item After a computation time of the message, the BBU sends an answer to its RRH.
-\end{enumerate}
- This periodic process has a critical end to end latency, thus a messages has to be as little buffered as possible before being sent in the ring.
- Every messages will browse the entire ring during the process. Since the ring is approximately 50km long, a messages needs $250 \mu s$ to travel this length.
- Considering that the periodicity of the emissions ($1ms$) is greater than a ride of the ring, we take $P$ a multiple of the time needed to travel the ring.
+\section{ Implementation details}
 
-\section*{Sending policy}
-In the studied model, the nodes of the ring have a {\bf broadcast and select} policy. Then, the physical times needed to insert the data in the ring are negligible in regard of the other times.
-When a node sends a packet on the ring, it contains data for several destinations.
-Every node of the ring reads all the slots and keep the data addressed to it.
-It copy the data of the packet in the slot, but does not remove anything.
-The only node that can free a slot is the one which send a packet in it.
+	The source code int C of the simulator used for our experimental results is available on the \href{https://github.com/Mael-Guiraud/Ngreen.git}{ author's github page}.
+	\subsection{Initialisation}
+	First, we need to put coherent parameters , considering the model. For instance, with the parameters of NGREEN, we can not set more than 10 antennas on the ring. 
+	The ring is modeled by a circular table of struct packets.
 
-%when a node sends some data in a slot, this slot is {\em taken} by this node for an entire ride of the ring.
-This means that every nodes of the ring can collect the information addressed to it, but it does not delete the data in the slot.
-The slot is fully cleared by the node that sent it, when it came back after a ride of the ring.
+	\begin{algorithm}[H]
+	\MyStruct{packet}{
+ 		int owner\_id\; \tcp{-1 if there is no packet on the slot.}
+  		int size\_CRAN\; \tcp{Nb messages CRAN in the packet\, useful to generate the answers.}
+  		int reservation\_id\; \tcp{Useful in the reservation model\, -1 otherwise.}
+	}
+	\end{algorithm}
 
-Thus, a node has to wait for a free slot before sending a packet in the ring. To avoid overloading the ring, a node sends a packet only if some criteria  are satisfied.
-We define by $Q$ the capacity of the buffer of a node, $\alpha$ the {\em minimum load} of the buffer, $0 \leq  \alpha \leq 1$, and $\delta$ the {\em maximum delay}.
+	For each antenna, we initialize the first date $t$ on which the antenna send some traffic.
+The antenna will then send a message every 10 slots after $t$, during a fixed total emission time, depending of the throughput of the antenna.
 
-The node sends a packet in a slot if:
+	 In the Insertion Policy models, this date $t$ is randomly drawn with the rand() functions of stdlib.
+In the Reservation model, this date $t$ is set by the scheduling algorithms described in sec~\ref{det}.
+
+	Since the time is discretized, a slot (a unit of time) correspond to one round of a loop.
+The duration of the loop is set to be large enough to obtain some confident experimental results.
+During each round of the simulation loop, we first generate the best effort and CRAN traffic, following the laws described in sec~\ref{model}.
+
+	Then, we call the \texttt{insert\_packets()} function to send the packets on the ring, if needed (i.e, if some CRAN has been generated, or the BE buffer is large, or old enough).
+	Finally, the function \texttt{rotate\_ring()} is called, and every struct packets of the circular ring takes the following position in the table (the last cell of the table take the position 1).
+	Afterwards, we call the \texttt{remove\_packets()} function, that free the reading\_slot of a node, if the packet on it has been sent by this node.
+	\subsection{BE-Generation}
+	The best effort generation follows the SBBP decribed in sec~\ref{model}.
+Since the batch process have, at the most 10 states, this functions runs in $O(1)$: one random drawing for the transition in the markov chain, another random drawing for the batch process, and the Inverse transform sampling, which is bounded by the number of states.
+	\subsection{CRAN-Generation}
+	We splitted the CRAN-Generation in two steps.
+First, the nodes which are not the BBU adds their messages from antennas to buffers, if needed.
+In a second time, the BBU generates and answer in it's buffer, if there is a CRAN packet in the reading\_slot of the BBU.
+	\subsection{Insertion packet}
+	A node emits a packet on the ring, in its writting\_slot, if :
 \begin{itemize}
- \item The amount of data $q$ in the buffer is greater than $\alpha . Q$,
- \item or the older data in the buffer is waiting for more than $\delta$.
+\item In no management mode :  if the size of the buffer is greater or equal to $\beta .Q $ ($\beta \in ]0;1] , Q$ is the size of the buffer) , or if the oldest datas has arrived in the buffer before or to $t-\alpha$, ( $t$ is the current slot, and $\alpha$ is the deadline, expressed in slot).
+\item In CRAN priority mode : 
+	\begin{itemize}
+	\item If the BE-buffer satisfy one of the latter condition,
+	\item Or if there is some CRAN in the CRAN\_buffer. The packet emitted contains all the CRAN possible, filled with as much BE as possible. 
+	\end{itemize}
+\item in reservation mode, the slot on the writting\_slot of the node must be not reserved, or reserved for the node. Then the constraints are the same than the CRAN-priority mode.
 \end{itemize}
 
-The buffer of a node is filled with the FIFO rule by a traffic coming from external sources.
-Then, when the node has an available free slot, the packet is inserted in the slot if one of the previous constraints are satisfied.
-Otherwise the node does not send anything in the ring and wait for the next free slot.
-
-\begin{center}
-
-      \includegraphics[scale=0.7]{insertion0.pdf}
-
-\end{center}
-
-\section{C-RAN context}
-
-In C-RAN context, this amount of data $q$ contains two kinds of data: the latency critical flow coming from RRH or BBU, and an other flow, called {\em best effort}.
-
-We can consider two buffers containing $x$ and $y$ amount of data.
-The first one is filled with the C-Ran data in priority, and the best effort flow if needed, the second one takes the rest of best effort flow.
-We consider that, even if a lot of RRH are represented by a node on the ring, the amount of C-Ran data incoming to a node is strongly lower than the capacity of a packet ($\simeq 1.2$ Gbps for each RRH, 100 Gbps into the ring).
-The C-RAN data comes periodically in regard of the period $P = 1ms$. 
-The best effort data comes more randomly (can be modelled by a Poisson distribution, for example), and are inserted in the buffer if $x = 0$.
-
-\begin{center}
-
-      \includegraphics[scale=0.7]{insertion1.pdf}
-
-\end{center}
-
-\section*{Model}
-We consider an optical ring composed of $k$ nodes ($k={3,...,10}$).
-We are in a discrete time model: the time is split in $N$ slot, rotating to the following position each time step $t = 10 \mu s$. This value is the switching granularity.
-\begin{center}
-
-      \includegraphics[scale=0.5]{anneau1.pdf}
-      \hspace{3cm}
-      \includegraphics[scale=0.5]{anneau2.pdf}
-
-\end{center}
-
-Considering a length of 50 km for the ring, we evaluate the number of slots about 25 into the ring.
-
-\section*{Study}
-The purpose is here to reduce the latency of the C-RAN data. Two event can increase this latency: 
-\begin{enumerate}
-  \item The node has enough data $q$ to emit in the ring, but no slots are available.
- \item The node does not have enough data $q$ to emit and a data from $x$ is waiting for less than $\delta$.
-\end{enumerate}
-
-In a first time, we will look at the first problem, and try to determine from what load of the ring, the time taken to wait a free slot in the ring is too long.
-
 \end{document}

### 2018-02-08 Papier NGreen/model.tex
papier ngreen

--- 2017-10-23 Papier NGreen/model.tex
@@
-\documentclass[a4paper,10pt]{article}
+\documentclass[a4paper,10pt,french,english]{article}
 \usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+
+\usepackage[french]{babel}
+
 \usepackage{xspace}
@@
 \usepackage{hyperref} 
+\usepackage{mathtools, bm}
+\usepackage{amssymb, bm}
+\usepackage{complexity}
+\usepackage{amsthm}
+\usepackage{authblk}
+\usepackage{color}
+\usepackage{amsmath}
 
+\newcommand\pall{\textsc{pall}\xspace}
 \usepackage{algorithm2e}
@@
 
+\newcommand{\todo}[1]{{\color{red} TODO: {#1}}}
+\newtheorem{prop}{Proposition}
+
 \graphicspath{{img/}}
@@
 %opening
-\title{Algorithmic model for N-GREEN optical ring}
+\title{Contention management for Cloud Ran over an optical ring}
+
+\author[1]{Dominique Barth}
+\author[2]{Dominique Chiaroni ?}
+\author[1]{Ma\"el Guiraud}
+\author[1]{Yann Strozecki}
+\affil[1]{David Laboratory, UVSQ}
+\affil[2]{Nokia Bell Labs France}
 
@@
 \maketitle
+
+\begin{abstract}
+\todo{reprendre le debut de l'autre abstract, ou commencer par parler de N-GREEN?}
+\end{abstract}
+
 \section{Introduction}
-Blabla sur le contexte du projet NGREEN
+\todo{dire que c'est un modele deja etudie}
+\todo{introduire CRAN, NGREEN, presentation du model, contributions}
+\subsection*{Related work}
+\todo{?}
 
-\section{Model}
-  \label{model}
-  \subsection{Optical ring}
-    Graphe oriente representant un anneau, definition des terme delay
-  \subsection{Discrete time model}
-    temps slotte correspondant a un tick d'horloge
+\section{Description of the network, model, problem}
+    \subsection{Cloud-RAN Context}
+    Our study takes place in the Cloud-RAN context.
+The purpose is to centralise the calculation units of some antennas, distributed on the field.
+To each antenna, called RRH (Remote Radio Head), is associated a BBU (BaseBand Unit) in the datacenter.
+      The periodic process is the following: each {\bf period $P$}, every RRH (also called antennas) send some datas thought the ring to it's BBU, then, after a computation time in the BBU, this latter answers to the corresponding RRH.
+      The time between the emission of the message by the RRH and the reception of the answers by the same RRH is called {\bf process time} and must not be too large, considering some 5G standards.
+That is why the message might be as less buffered as possible into the nodes, in order to decrease the latency, and thus, the process time of the messages.
+      In this paper we will consider that all the BBU are grouped in the same node, called {\bf datacenter}, and that the antennas are distributed on the others node of the ring.
+      \todo{je pense que ce paragraphe n'est utile que dans le deliverable, sinon je dois mettre l'equivalent dans l'intro}
+
+  \subsection{Network modeling}
+
+The model exposed here has already been studied for another particular topology of network and with different problematics from the ones of this paper.
+One can find in \cite{latency2017} the complexity results on the problem proposed, and some algorithmic solutions to solve it in star networks.
+
+The network is modeled as a directed graph $G=(V,A)$.
+Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time taken by a message to go from $u$ to $v$ using this arc.
+A {\bf route} $r$ in $G$ is a directed path, that is, a sequence of adjacent vertices $u_0, \ldots , u_{k}$, with $(u_i,u_{i+1}) \in A$.
+The {\bf latency} of a vertex $u_i$ in a path $r$ is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} \omega(u_j, u_{j+1})$.
+We also define $\lambda(u_0,r)=0$.
+The length of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
+We denote by $\cal R$ a set of routes, the pair $(G,\cal R)$ is called a {\bf routed network} and represents our telecommunication network.
+
+   In the context of Cloud-RAN applications, we need to send a message from an RRH $u$ to a BBU $v$ and then 
+      we must send the answer from $v$ back to $u$.
+We denote by $n$ the number of couple RRH-BBU.
+We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of \textbf{forward routes} and $B$ of \textbf{backward routes}.
+There is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.
+
+\subsection{Messages dynamic}
+
+      In the process we study, a message is sent on each route at each period, denoted by $P$. The time is discretized, i.e. a period is sliced into $P$ {\bf slots}. 
+      Let $r$ be a route, if a message is sent at time $m$ from $s$ the first vertex of $r$ then it will arrive at vertex $v$ in $r$ at time $m + \lambda(v,r)$.
+Since the process is periodic, if the message from $r$ goes through an arc at time $t\in [0,P-1]$, then it goes through the same arc at time $t+kP$ for all positive integers $k$.
+Therefore, every time value can be computed modulo $P$ and we say that the first time slot at which a message sent at time $m$ on $r$ reaches a vertex $v$ in $r$ is $t(v,r) = m + \lambda(v,r)\mod P$.
+
+ A message usually cannot be transported in a single time slot.
+Let us call $[t(v,r)]_{P}$ the set of time slots used by route $r$ at vertex $v$ in a period $P$, that is $[t(v,r)]_{P} = t(v,r)  \mod P $.
+Let $r_1$ and $r_2$ be two routes, on which messages are sent at time $m_1$ and $m_2$ in their first vertex.
+      We say that the two routes have a {\bf collision} if they share an arc $(v,w)$ and $[t(v,r_{1})]_{P} \cap [t(v,r_{2})]_{P} \neq \emptyset$.
+
+         A {\bf $P$-periodic assignment} of a routed network $(G,\cal R)$ is a function that associates to each route 
+         $r \in \cal R$ its \textbf{offset} $m_r$ that is the time at which a message is emitted at the first vertex of the route $r$.
+In a $P$-periodic assignment, \emph{no pair of routes has a collision}.
+
+                     Let us give an interpretation of a $P$-periodic assignment of $(G,{\cal R})$ a symmetric routed network, so that it represents the sending of a message and of its answer.
+	First a message is sent at $u$, through the route $r \in F$, at time $m_r$.
+      This message is received by $v$, i.e., the last vertex of $r$ at time $t(v,r)$.
+It is then sent back to $u$ on the route $\rho(r)$ in the same period at time $m_{\rho(r)}$ if $m_{\rho(r)} > t(v,r)$, otherwise at time $m_{\rho(r)}$ in the next period.
+The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_r = m_{\rho(r)} - t(v,r)$ if $m_{\rho(r)} > t(v,r)$ and $w_r = m_{\rho(r)} + P - t(v,r)$ otherwise.
+      \begin{figure}[h]
+      \begin{center}
+      \includegraphics[width=0.9\textwidth]{rrh.pdf}
+      \end{center}
+      \caption{The process defined by a $P$-periodic assignment}
+      \end{figure}
+
+The process time for a message sent on the route $r$ is equal to $PT(r)=\lambda(r)+ w_r+\lambda(r)$.
+Each route must respect some time limit that we call a \emph{deadline}.
+To represent these deadlines,
+      we use a deadline function $d$, which maps to each route $r$ an integer such that $PT(r)$ must be less than $d(r)$.
+    We can now define a first problem:
+
+      \noindent {\bf Periodic Assignment for Low Latency (\pall)}
+
+      \noindent {\bf Input:}  A symmetric routed network $(G,{\cal R})$, the integers $P$ and a deadline function $d$.
+
+      \noindent {\bf Question:} does there exist a $P$-periodic assignment $m$ of $(G,{\cal R})$ such that for all $r \in {\cal R}$, $PT(r) \leq d(r)$?
+
+It turns out that the problem \pall is $\NP$-hard to solve and even to approximate for \emph{general} routed networks, and for the simplified version presented here~\cite{latency2017}.
+
+  \subsection{N-GREEN Optical ring}
+  In this paper, we consider $G$ as a circular digraph $C_N$ representing an unidirectional optical ring.
+The vertices of the graph represents the nodes of the ring.
+In our study, we want to focus on the ring only.
+Thus, we ignore the external network and we consider that, the first and last vertex , $u$ and $v$ of the routes are some nodes of the ring.
+We consider a symmetric routed network.
+For each forward route $r$, the backward route $\rho(r)$ is the other part of the ring.
+Consequently, for each route $r$, $\lambda(r) + \lambda(\rho(r)) = RS$, where $RS$ is the size of the ring.
+In our experiments, we consider only one datacenter into the ring.
+This mean that all the forward routes have the same destination nodes, and all the backward routes have the same source node.
+
+  The ring follows a broadcast and select behavior.
+When a packet is inserted in a slot on the ring, by a node, no other nodes are able to write on this slot.
+This packets can contain some data from several nodes on the ring, that are able to read in the packet.
+The only node which has the right to remove the packet from the slot is the owner.
+This mean that every packet makes exactly one lap of the ring.
+Furthermore, to write on a slot, a node has to have an empty slot in it's writing slot.
+ \subsection{Message Granularity}
+ Each arc $(u,v)$ can be represented as a sequence of slots $\{s_1, ...
+, s_k\}$, with $k = \omega(u,v)$.
+We denote by $s_n(u,v)$ the $n^{th}$ slot of the arc $(u,v)$.
+$s_i(v), i\in \{-\omega(u,v), ...
+, -1\} \cup \{1 , ...
+, \omega(v,w)\}$ is the $i^{th}$ slot after (before if $i<0$) v on the ring.
+    On the following example, the red slot can be denoted by $s_2(u,v)$, $s_2(u)$ or $s_{-6}(v)$. 
+    \begin{figure}[h]
+    \centering
+      \includegraphics[scale=0.5]{suv.pdf}
+
+      \caption{A link $(u,v)$ represented as a sequence of slots}
+  \end{figure}
+
+  Each node $v$ has a reading access on $s_{-1}(v)$ and a writing access on $s_{1}(v)$.
+Those slots are named respectively the reading and writing slots of $v$.
+Thus, during a time slot, a node $v$ can insert a {\bf container} on it's writing slot, if it is allowed to.
+At the end of the time slot, each packets rotate to the next slot.
+A packet emitted by a node $u$ on it's writing slot $s_1(u)$ will be available in reading for a node $v$ on it's reading slot, $s_{-1}(v)$, $d(u,v) -1$  time slots later.
+\begin{figure}[h!]
+      \includegraphics[scale=0.5]{anneau1.pdf}
+      \hspace{3cm}
+      \includegraphics[scale=0.5]{anneau2.pdf}
+      \caption{One rotation of the ring}
+  \end{figure}
+
 \subsection{Into the node : Two kind of traffics}
-    Descripion buffers/ on prepare des conteneurs.definition des therme paquet slot buffers
-    Description CRAN-BE, precision sur le modele de generation
-    presentation des differentes politiques d'insertion.
+  In this study, we focus on the behavior of the N-GREEN optical ring.
+Therefore, we do not want to consider the problems caused by the upstream network.
+We model the arrival of messages in a node by the following way.
+    To build the containers that are sent in the ring, a node has to deal with two kinds of traffic: 
+    \begin{itemize}
+    \item The {\bf Best effort traffic}, representing the internet flow.
+    \item The {\bf C-RAN traffic}, with an higher priority than the best effort.
+    \end{itemize}
+    Let us denote {\bf BE-message} and {\bf CRAN-message} the unit of data of this flows.
+A container can be made of several BE-messages or CRAN-messages, and can be a combination of both kind of messages.
 
-  \subsection{Objectives}
-    Etudier Le comportement de nos politiques
-    Trouver une solution deterministe et etudier l'impact sur les BE
+  \subsection{Messages arrival}
+   To refine our model around the N-GREEN study, one must consider the following.
+The RRHs send some heavy packets in the network.
+Those packets are carried to the node of the right through an electronic link.
+The bandwidth of electronics networks is often smaller that opticals network bandwidths.
+An optical node on the ring is able to transform an electronic packet of size $x1$ measured in$\mu$s in an optical packet of size$x2 < x1$.
+In our study, $x1 = 10$ and $x2 = 1$.
 
-\section{Study of the different insertion policies}
+\begin{figure}[h!]
+\begin{center}
 
-  \subsection{Parameters}
-  Peut etre attendre les resultats de youssef pour fixer les deadline et seuil d'envoi dans les simuls.
-  \subsection{No management}
-  \subsection{CRAN priority}
-  Conclure que c'est pas top top, même si c'est clairement mieux en CRAN, et qu'on va faire du determinisme.
+      \includegraphics[scale=0.3]{slot1.pdf}
+  \includegraphics[scale=0.3]{slot2.pdf}
+     \caption{Electronic-optical interface.}
 
-\section{Deterministic approach for 0 latency on CRAN}
-\label{det}
-  \subsection{Packing}
-  \subsection{Spreading}
-  Pour ces deux la, ecrire proprement les ``algos''
-  \subsection{Impact on the BE}
-  REsultats de simuls
+\end{center}
+  \end{figure}
 
-\section{ Implementation details}
+   We want to look only at the optical ring, thus we consider that an RRH can send no more than a packet every $10\mu s$ on the ring.
+This gap between two messages from the same RRH is called $EP$, for {\bf Emission Period}.
+    The messages of the RRHs cannot be transported in a single packet.
+We denote by $ET<P$,for {\bf Emission time}, the time during which an antenna emits a packet every $EP$ slots on the ring.An antenna emits $\frac{ET}{EP}$ packets on the ring, during a period $P$.
 
-	The source code int C of the simulator used for our experimental results is available on the \href{https://github.com/Mael-Guiraud/Ngreen.git}{ author's github page}.
-	\subsection{Initialisation}
-	First, we need to put coherent parameters , considering the model. For instance, with the parameters of NGREEN, we can not set more than 10 antennas on the ring. 
-	The ring is modeled by a circular table of struct packets.
-
-	\begin{algorithm}[H]
-	\MyStruct{packet}{
- 		int owner\_id\; \tcp{-1 if there is no packet on the slot.}
-  		int size\_CRAN\; \tcp{Nb messages CRAN in the packet\, useful to generate the answers.}
-  		int reservation\_id\; \tcp{Useful in the reservation model\, -1 otherwise.}
-	}
-	\end{algorithm}
-
-	For each antenna, we initialize the first date $t$ on which the antenna send some traffic.
-The antenna will then send a message every 10 slots after $t$, during a fixed total emission time, depending of the throughput of the antenna.
-
+        \begin{figure}[h!]
 \begin{center}
@@
       \includegraphics[width=\textwidth]{emission_antenna.pdf}
+     \caption{Antenna traffic on the ring.}
+\end{center}
+  \end{figure}
 
+  This specificity gives us a new problem, similar to \pall.
+The set of time slots used by route $r$ at vertex $v$ in a period $P$, is now defined by $[t(v,r)]_{P,EP} = \{t(v,r) +k \mod P \mid k \in \{0,EP,2\times EP,...., \frac{ET}{EP}\times EP\} \}$.
+Consequently, we now want to find a $(P,ET)$-periodic assignment that set the offsets of the routes $m_r$, such that there is no collision between two routes $r_1$ and $r_2$, that is, $[t(v,r_{1})]_{P,EP} \cap [t(v,r_{2})]_{P,EP} \neq \emptyset$.
+  The main purpose of this paper is to reduce as much as possible the latency of the C-RAN traffic, without increasing too much the latency of th BE traffic.
+  \pall is a sub-problem of this problem with ET = 1. Thus, we can consider the complexity results for this problem too.
+  \todo{pas sur d'avoir le droit de dire ca}
+
+   \section{Performance evaluation of the N-GREEN optical ring}
+   In a first time, we will look at the performance of the N-GREEN optical ring with an opportunistic insertion policy \cite{refngreen?}.
+When a node decides to send a container on the ring, it uses the first available slot in its writing slot.
+    We study the performance through two messages management algorithms; a full opportunistic algorithm, and an algorithm that prioritize the C-RAN messages.
+   For those two algorithms with opportunistic insertion policy, the offsets $m_r$ of the routes are chosen randomly in the period. 
+   Since we do not manage those offsets, the two following algorithms do not gives us some $(P-ET)$-periodic assignment.
+No choices are made on the offsets and thus, two routes can collides.
+Furthermore, the generation of the BE traffic is given by the numerical analysis of sec~\ref{SECJMF}
+   \todo{Expliquer rapidement sans s'eterniser.}
+
+    \subsection{Full opportunistic algorithm}
+    \label{sec:fullopport}
+    We first want to look at a simple configuration in which we do not manage the messages (BE or CRAN) arriving into the nodes.
+At their arrival, the BE and C-RAN messages are buffered in the node, and a node send a container if :
+     \begin{itemize}
+    \item The oldest message of the buffer has arrived on the buffer before $t - \alpha$, where $t$ is the actual time.
+    \item The fill rate of the buffer is greater or equal than $\beta$.
+    \end{itemize}
+    Those parameters $\alpha$ and $\beta$ are fixed by the network specification.\todo{ref sur les traveaux de jmf et youssef}
+
+    \begin{figure}[h!]
+        \begin{center}
+      \includegraphics[scale=0.5]{insertionbuff.pdf}
+
+      \caption{The packet creation buffer}
       \end{center}
+  \end{figure}
 
-	 In the Insertion Policy models, this date $t$ is randomly drawn with the rand() functions of stdlib.
-In the Reservation model, this date $t$ is set by the scheduling algorithms described in sec~\ref{det}.
+This behavior is the basic one, the buffer of a node is filled following the FIFO rule by the BE and C-RAN messages.
+Then, when the node has an available free slot in its writing slot, the container is created and inserted in the slot if one of the previous constraints are satisfied.
+Otherwise the node does not send anything.
 
-	Since the time is discretized, a slot (a unit of time) correspond to one round of a loop.
-The duration of the loop is set to be large enough to obtain some confident experimental results.
-During each round of the simulation loop, we first generate the best effort and CRAN traffic, following the laws described in sec~\ref{model}.
+The following experiment shows us the performance this {\bf full opportunistic} algorithm with some parameters issued from N-GREEN.
+The optical link has a data flow of $100$Gbps, while a slots has a duration of $1\mu$s.
+The length of the ring is to $20$km in our simulations, this means that the ring has a length of $RS = 100$ slots.
+We denote {\bf latency} of a message the amount of time time the message has waited between its arrival in the node and its sending on the ring.
+On fig~\ref{fig:oport}, one can see the cumulative distribution latency of the different kinds of traffics on the ring.
+We chose to distinguish the traffic of the datacenter to the rest of the traffic, because the datacenter has a different behavior compared to the rest of the nodes.
+Those results are computed on $100$ instances of optical rings that have run during $10,000$ slots.
+We consider some BE messages of $125$B, and we configured the random generator such that each node load the network with an average of $5\%$ of BE traffic.
+We set $ET = 500$ slots and $EP = 10$ slotsn that correspond to respectively a C-RAN traffic of $5$Gbps and some electronic links of $10$Gbps data flow.The period  $P$ is to $1$ms, that is $1000$ slots.
+We set the number of antennas to $n=5$.
+We take $5$ nodes and one of them is the datacenter.
+The antennas are apportioned between the others node.
+With those parameters, the network is theoretically loaded to $75\%$.
+We set the parameters $\alpha = 10 \mu$s and $\beta = 0.7$, following the numerical analysis (see~\ref{sec:JMF}).
 
-	Then, we call the \texttt{insert\_packets()} function to send the packets on the ring, if needed (i.e, if some CRAN has been generated, or the BE buffer is large, or old enough).
-	Finally, the function \texttt{rotate\_ring()} is called, and every struct packets of the circular ring takes the following position in the table (the last cell of the table take the position 1).
-	Afterwards, we call the \texttt{remove\_packets()} function, that free the reading\_slot of a node, if the packet on it has been sent by this node.
-	\subsection{BE-Generation}
-	The best effort generation follows the SBBP decribed in sec~\ref{model}.
-Since the batch process have, at the most 10 states, this functions runs in $O(1)$: one random drawing for the transition in the markov chain, another random drawing for the batch process, and the Inverse transform sampling, which is bounded by the number of states.
-	\subsection{CRAN-Generation}
-	We splitted the CRAN-Generation in two steps.
-First, the nodes which are not the BBU adds their messages from antennas to buffers, if needed.
-In a second time, the BBU generates and answer in it's buffer, if there is a CRAN packet in the reading\_slot of the BBU.
+We chose to distinguish the different traffics; The uplink traffic is the C-RAN traffic going from the RRHs to the BBUs.
+The downlink traffic corresponds to the messages going from the BBUs to the RRHs.
+We also make a difference between the BE messages on the nodes connected to some RRHs (BE) with the BE messages coming from the datacenter(BBU BE).
+In this case, this is not relevant, but some future experiments will reveal a difference between those two kind of BE traffics.
+    \begin{figure}[h!]
+    \label{fig:oport}
+        \begin{center}
+      \includegraphics[scale=0.4]{oport}
 
-The application we study takes place in the C-Ran context.
-We want to centralise calculations into a common data-center for an area of antennas distributed on the territory.
-The data between the RRH (antennas) and the BBU (data-center) are transiting through an optical ring.
-We study here only the behaviour of the ring.
-First, for an easier model, we consider a ring in which one or two nodes are the data-centers, and the other nodes of the ring sends some data coming from the RRH.
+      \caption{Full opportunistic algorithm performances.}
+      \end{center}
+  \end{figure}
 
-Every millisecond, between each couple RRH-BBU, the following periodic process is observed:
-\begin{enumerate}
- \item The RRH sends some latency critical data to its BBU.
- \item Those data are transferred to the BBU through the ring .
- \item After a computation time of the message, the BBU sends an answer to its RRH.
-\end{enumerate}
- This periodic process has a critical end to end latency, thus a messages has to be as little buffered as possible before being sent in the ring.
- Every messages will browse the entire ring during the process. Since the ring is approximately 50km long, a messages needs $250 \mu s$ to travel this length.
- Considering that the periodicity of the emissions ($1ms$) is greater than a ride of the ring, we take $P$ a multiple of the time needed to travel the ring.
+  As we can see on fig~\ref{fig:oport}, the latency for the different kind of traffic is notably similar because we do not manage anything.
+Furthermore, we can remark that about $20\%$ of the C-RAN messages wait over $200$ms, that is the maximum latency allowed for C-RAN \cite{REF}.
 
-\section*{Sending policy}
-In the studied model, the nodes of the ring have a {\bf broadcast and select} policy. Then, the physical times needed to insert the data in the ring are negligible in regard of the other times.
-When a node sends a packet on the ring, it contains data for several destinations.
-Every node of the ring reads all the slots and keep the data addressed to it.
-It copy the data of the packet in the slot, but does not remove anything.
-The only node that can free a slot is the one which send a packet in it.
+\subsection{C-RAN priority algorithm}
+  In order to improve the C-RAN-messages latency, we imagined the following solution.
+Each nodes have two buffers.
+One for the BE messages, and one fore the C-RAN messages.
+When a node is able to send a container on the ring, i.e.
+the slot on it's writing slot is free, the container is filled with the C-RAN messages first.
+The buffer that contains the C-RAN messages does not take into account the parameters $\alpha$ and $\beta$ we described in sec~\ref{sec:fullopport}.
+If there is some C-RAN messages in the buffer, we send it, even if the container is not full enough.
+Nevertheless, in this situation, the nodes always tries to fill the container with some BE messages.
+If there is no C-RAN messages in the buffer, the node have the same behavior as in the full opportunistic algorithm.
+We call this algorithm the {\bf C-RAN priority algorithm}.
 
-%when a node sends some data in a slot, this slot is {\em taken} by this node for an entire ride of the ring.
-This means that every nodes of the ring can collect the information addressed to it, but it does not delete the data in the slot.
-The slot is fully cleared by the node that sent it, when it came back after a ride of the ring.
+    \begin{figure}[h]
+\begin{center}   
+      \includegraphics[scale=0.7]{insertion1.pdf}
+     \caption{C-RAN priority buffer.}
+\end{center}
+  \end{figure}
 
-Thus, a node has to wait for a free slot before sending a packet in the ring. To avoid overloading the ring, a node sends a packet only if some criteria  are satisfied.
-We define by $Q$ the capacity of the buffer of a node, $\alpha$ the {\em minimum load} of the buffer, $0 \leq  \alpha \leq 1$, and $\delta$ the {\em maximum delay}.
+  With this algorithm, one can imagine highly improve the latency of the C-RAN messages.
+Fig~\ref{fig:prior} shows us the performance of the C-RAN priority algorithm for different kinds of traffics.
+The parameters of the simulations are exactly the same as those of the previous experiment.
 
-The node sends a packet in a slot if:
-\begin{itemize}
- \item The amount of data $q$ in the buffer is greater than $\alpha . Q$,
- \item or the older data in the buffer is waiting for more than $\delta$.
-\end{itemize}
-
-The buffer of a node is filled with the FIFO rule by a traffic coming from external sources.
-Then, when the node has an available free slot, the packet is inserted in the slot if one of the previous constraints are satisfied.
-Otherwise the node does not send anything in the ring and wait for the next free slot.
-
+      \begin{figure}[h]
+      \label{fig:prior}
 \begin{center}
 
-      \includegraphics[scale=0.7]{insertion0.pdf}
+      \includegraphics[scale=0.4]{prior.pdf}
 
+     \caption{C-RAN priority algorithm performances.}
 \end{center}
+  \end{figure}
 
-\section{C-RAN context}
+  As expected, the latency of the C-RAN messages is highly decreased compared to the full opportunistic algorithm.
+Nevertheless, there is still $5\%$ of the downlink messages that have more than $200 \mu$s of latency, and the best effort are highly penalized.
+  \todo{il manque une partie sur le travail de karim, au moins pour le deliverable}
+  Thus, we propose a deterministic approach in which we set the offsets of the antennas and we reserve the slots needed for the containers with the CRAN messages.
+For the rest of the section, the policy of slot insertion is the slot reservation.
+\todo{pour l'article, ne pas mettre}
 
-In C-RAN context, this amount of data $q$ contains two kinds of data: the latency critical flow coming from RRH or BBU, and an other flow, called {\em best effort}.
+  \section{Deterministic approach for 0 latency on C-RAN}
+\label{det}
+\subsection{Slot Reservation}
+To decrease the C-RAN messages latency, one plan to reserve the slots for the nodes.
+Indeed, if a nodes $i$ needs to send a container in its wrtting\_slot at time $t$, this slot needs to be reserved during the previous lap of the slot, i.e.
+at time $t - RS$ by $i$.
+In this situation, if the slot is already taken by a packet which has been sent by a node $k$, $k$ will remove the packet of the slot during the next lap of the ring, and no other nodes are able to write in this slot before it comes back to the node $i$ a date $t$.
+By finding a $(P,ET)$-periodic assignment and reserving the corresponding slot, we allow the C-RAN messages to have $0$ latency in nodes.
+Though, it impacts the best effort, by avoiding them to use free reserved slots.
+It is equivalent to increase the load of the network, without increasing the number of messages carried by the network.
 
-We can consider two buffers containing $x$ and $y$ amount of data.
-The first one is filled with the C-Ran data in priority, and the best effort flow if needed, the second one takes the rest of best effort flow.
-We consider that, even if a lot of RRH are represented by a node on the ring, the amount of C-Ran data incoming to a node is strongly lower than the capacity of a packet ($\simeq 1.2$ Gbps for each RRH, 100 Gbps into the ring).
-The C-RAN data comes periodically in regard of the period $P = 1ms$. 
-The best effort data comes more randomly (can be modelled by a Poisson distribution, for example), and are inserted in the buffer if $x = 0$.
+In this section, we explain the different algorithm we use to have $0$ latency on C-RAN messages and we study their impact on the BE messages latency.
 
-\begin{center}
+Unlike the previous algorithms with opportunistic insertion policy, we now want to choose a $(P,ET)$-periodic assignment for the routed network $(G,{\cal R})$.
+An antenna can not emit a message more often than one slot every $EP$ slots.
+We define a {\bf macro slot} as a duration of $EP$ slots, in which each antenna can emit at most once.
+Since all the forward routes have the same last vertex $v$ (the datacenter), which is also the first vertex of all the backward routes, we choose to look at the behavior of the messages in this vertex only.
+The purpose is to determine $t(v,r_i)$ for each routes $i$, such that there is no collisions between the routes.
+Once $t(v,r_i)$ is set, it is easy to compute $m_{r_i} = t(v,r_i) - \lambda(v,r_i)$.
 
-      \includegraphics[scale=0.7]{insertion1.pdf}
+\subsection{N-GREEN parameters adapted algorithms}
+An antenna cannot emit more than once every macro slot, thus, we consider the simple case in which there is less antennas than slots in a macro slot.
+Since a BBU emits an answer to it's RRH, for each antennas, two slots must be reserved.
+Thus, we first study the case $EP \ge 2\times n$.
 
-\end{center}
+ In this section, the algorithms assign two slots to each antenna: one slot for the uplink and one slot for the downlink traffic in the macro slot.
+Since The BBU always send an answer to the RRH, one must consider that the BBU immediately send an answer after receiving a message from an RRH.
+This simplification allows us to reserve a set of two slots for each antennas.
+Let us call {\bf frequency} a set of two slots in a macro slot.
+The purpose is then to assign to each antenna a frequency.
 
-\section*{Model}
-We consider an optical ring composed of $k$ nodes ($k={3,...,10}$).
-We are in a discrete time model: the time is split in $N$ slot, rotating to the following position each time step $t = 10 \mu s$. This value is the switching granularity.
-\begin{center}
+ Because there is at most as much couples BBU-RRH as frequencies, we want to assign one antenna to one frequency.
+We propose the following {\bf naive reservation algorithm}. For each antenna on the route $i, i\in [0;n-1] $, set $t(v,r_i)= 2\times i$ with $v$ the vertex of the BBUs. 
+   \begin{figure}[h]
 
-      \includegraphics[scale=0.5]{anneau1.pdf}
-      \hspace{3cm}
-      \includegraphics[scale=0.5]{anneau2.pdf}
+      \includegraphics[scale=0.7]{freqgrouped.pdf}
+     \caption{Grouped assignment of the frequencies to the antennas.}   \label{fig:freqG}
+  \end{figure}
 
-\end{center}
+We kept the same parameters than in the two previous experiments and we made an experiment to show the impact of this algorithm on the BE traffic.
+Fig~\ref{fig:res1} shows us the performance of this algorithm for different kinds of traffics.
 
-Considering a length of 50 km for the ring, we evaluate the number of slots about 25 into the ring.
+      \begin{figure}[h]
+\centering
+      \includegraphics[scale=0.4]{res1.pdf}
+     \caption{Impact of the naive reservation algorithm on the Best effort flows.}   \label{fig:res1}
+  \end{figure}
 
-\section*{Study}
-The purpose is here to reduce the latency of the C-RAN data. Two event can increase this latency: 
-\begin{enumerate}
-  \item The node has enough data $q$ to emit in the ring, but no slots are available.
- \item The node does not have enough data $q$ to emit and a data from $x$ is waiting for less than $\delta$.
-\end{enumerate}
+As we can see, the BE traffic is highly penalized by this algorithm, indeed, while almost $100\%$ of the BE messages have a latency to less than $300 \mu$s with the full opportunistic algorithm (see fig~\ref{fig:oport}), here, the BE messages coming from the datacenter can be buffered up to $500\mu s$, while half the BE messages of the others node have to wait more in the node before being sent in the ring.
+Those performances are explained by the structure of the algorithm.
+The messages are grouped together, and with our parameters, $EP = 2\times n$.
+It creates a long sequence of slots during which there is no free slots in the ring.
+This explain why half of the BE messages of the datacenter have an acceptable latency, while the other part have up to $500\mu s$ of latency.
 
-In a first time, we will look at the first problem, and try to determine from what load of the ring, the time taken to wait a free slot in the ring is too long.
+There is another remarkable behavior on this experiment.
+The BE messages coming from the nodes with the RRHs have a significantly worst latency than the BE messages coming from the datacenter.
+Indeed, once a node is the owner of a slot, it is the only one that can remove the container from the slot.
+Also, the slot is freed in the reading slot of a node, and can immediately be re-used by the same node in it's writing slot.
+The period is split in two steps : one in which only there is only CRAN messages in the ring, and one in which the BE traffic can uses the ring.
+During the first step, the datacenter uses half of the slots for its CRAN traffic.
+That is why the datacenter can send close to $5$ times more messages than the others node.
+
+To improve the BE latency, we propose then to balance the load of the CRAN traffic over the period.
+Instead of giving the same $t(v,r_i)$ for all routes $i$, with $v$ the datacenter, we now uniformly reppart the different $t(v,r_i)$ in the period.
+\todo{donner un nom a $t(v,r_i)$}
+
+   \begin{figure}[!h]
+
+      \includegraphics[scale=0.7]{freqsplited.pdf}
+     \caption{Splited assignment of the frequencies to the antennas.}   \label{fig:freqS}
+  \end{figure}
+
+  With this algorithm, the load of the CRAN traffic is uniformly distributed on the period.
+There is no more the two steps phenomenon observed with the previous algorithm.
+On fig~\ref{fig:res2} on can observe the performance of this algorithm on the best effort.
+Once again, to have a reference point, we take the same parameters for the simulation.
+
+ \begin{figure}[h]
+\centering
+      \includegraphics[scale=0.4]{res2.pdf}
+     \caption{Impact of the splited reservation algorithm on the Best effort flows.}   \label{fig:res2}
+  \end{figure}
+
+  As we can see, the latency of the BE messages is highly better with this this algorithm.
+Nevertheless, there is still a lack of balancing between the messages coming from the datacenter and the messages coming from the RRH nodes.
+Indeed, the latency of the BBU BE is always less than $100 \mu s$, which is better than the full opportunistic algorithm, while almost $20\%$ of the others BE have a latency greater than $500\mu s$, which is worse than the full opportunistic algorithm.
+Thus, we decreased the latency of every kind of traffic but the BE coming from the RRH, which are, the major part of the BE messages.
+One can imagine a policy that manage the load of the BE traffic on the datacenter, but it is out of our study which focus on CRAN performances.
+
+\subsection{With more antennas}
+ In this section, we study the case $n > \frac{EP}{2}$. Indeed, if we want to assign more than one antenna to a frequency. 
+ Let us consider a particular behavior of the ring.
+Instinctively, we can think that if we have enough space in the period for many traffics on the same frequency that is, $ET \le \frac{P}{2}$, we can assign several antennas to the same frequency, i.e.
+$n > \frac{EP}{2}$.
+In fact, this is not always possible.
+ \begin{prop}
+If $ET = \frac{P}{2}$, there is no $(P,ET)$-periodic assignment if $n > \frac{EP}{2}$.
+ \end{prop}
+ \begin{proof}
+ Let us take $ET =  \frac{P}{2}$ and $n = \frac{EP}{2} + 1$. We assign a frequency to each $EP$ first antennas and we have only one antenna left. Then, we can look at only one frequency.
+
+ We take a ring with two nodes $A$ and $B$.
+We look at the behavior of one frequency, thus, both the nodes emits some packets every slots, during $ET$ slots.
+By construction, we allow $A$ to emit a time $1$ during $ET$ slots.
+This messages arrives in $B$ at $\omega(A,B)$, that is  $[t(B,r_A)]_{P,EP} = [\omega(A,B);\omega(A,B)+ET]$.
+Then, $B$ can imedialty emit its message at time $\omega(A,B)+ET$.
+This messages from $B$ arrives at $A$ at time $\omega(A,B)+ET + \omega(B,A) = ET + RS$, and thus, $[t(A,r_B)]_{P,EP} = [ET + RS;ET + RS + ET] = [ET+RS; RS + P] = [ET + RS; RS] \mod P$.
+Since $[t(A,r_A)]_{P,EP} = [1;ET]$, there is a collision between the two routes $A$ and $B$.
+  \begin{figure}[h]
+\centering
+      \includegraphics[scale=0.7]{rs.pdf}
+     \caption{Collision between two routes on the same frequency when the period is too small.}   \label{fig:proofrs}
+  \end{figure}
+ \end{proof}
+
+ As we have just noted, if several antennas share the same frequency, the period must have an additional budget in addition to the time needed to send the messages.
+Let us study the size of the additional budget.
+ \begin{prop}
+ If several antennas shares a frequency, one might have $P = n\times ET + RS$ , with $a$ the number of antennas.
+ \end{prop}
+ \begin{proof}
+ We seek to show that proposition by induction.
+
+ {\bf Base case:} For $n = 2$, the proof of the previous example shows us that it is possible to assign two routes on the same frequency with $P = 2\times ET + RS$.
+
+ {\bf Induction step:}  We consider that we have a frequency shared by $n$ antennas, with a period of size $P= n\times ET + RS$.
+We want to show that if we want to add one antenna to the frequency, we need a period of size at least $P = (n+1)\times ET + RS$.
+If we look at the sequence period of the frequency with $n$ antennas, we can observe that this sequence is the same in every nodes, shifted of the length of the routes between two nodes.
+For instance, if we take two nodes $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted of $\omega(A,B)$.
+
+   \begin{figure}[h]
+\centering
+      \includegraphics[scale=0.7]{period1.pdf}
+     \caption{An example of sequence with n = 3.}   \label{fig:proofperiod1}
+  \end{figure}
+
+ Thus, if we add $ET$ slots in this frequency, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence.
+
+   \begin{figure}[h]
+\centering
+      \includegraphics[scale=0.7]{period2.pdf}
+     \caption{The same sequence with n = 4.}   \label{fig:proofperiod2}
+  \end{figure}
+  Note that a node can send some traffic from more than one antenna, the figures ~\ref{fig:proofperiod1} and \~ref{fig:proofperiod2} are just an example, but this proof stays the same.
+ \end{proof}
+
+Considering those results, we propose an algorithm to allow several antennas to share the same frequency, as long as $P = n\times ET + RS$. 
+We first compute the number of frequencies needed to carry the number of antennas $n$.
+Then, the algorithms tries to balance those frequencies in all existing ones, i.e.
+it avoids to group the used frequencies in a macro slot.
+
+The used frequencies have $RS$ or more free slots that the BE traffic can fill.
+Thus, the algorithm subsequently balance the first time at which a frequency have some CRAN, with the same idea than the splited algorithm.
+
+   \begin{figure}[h]
+\centering
+      \includegraphics[scale=0.7]{optimalgo.pdf}
+     \caption{Organization of the frequencies with the balancing algorithm.}   \label{fig:optimalgo}
+  \end{figure}
+
+  We want to observe the impact of this algorithm on BE traffics.
+Since our previous parameters did not allow several antennas to share a frequency, we now set $ET = 100$, that correspond to a C-RAN flow of $1$Gbps.
+This is not out of context since the exact split of the C-RAN is not fully determined yet~\cite{REF}.
+To keep a load similar to the load in the previous experiment, we set the number of antennas to $n=25$.
+The others parameters are all the one described in the first experiment.
+  The following experiment shows us the impact of the balancing algorithm on the BE traffics.
+
+   \begin{figure}[h]
+\centering
+      \includegraphics[scale=0.4]{opti.pdf}
+     \caption{Balancing algorithm performance on the N-GREEN optical ring.}   \label{fig:optimres}
+  \end{figure}
+
+  As fig~\ref{fig:optimres} shows, the BE traffics are both impacted by this algorithm, but unlike the previous algorithm, it looks like there is a balancing between the BE of the BBU and the others BE.
+This behavior is probably due to the fact that there is less frequencies assigned to the BBU when there is some C-RAN in the ring.
+Indeed, since we tried to fill as much as possible the frequencies, and we kept the same load, we used less frequencies and thus, the BBU monopolize less resources than with the previous algorithms.
+
+  \bibliographystyle{ieeetr}
+\bibliography{src}
 

### 2018-02-13 Papier NGreen/article.tex
add figures

\documentclass[]{algotel}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{xspace}
\usepackage{graphicx,graphics} 
\usepackage{hyperref} 
\usepackage{mathtools, bm}
\usepackage{amssymb, bm}
\usepackage{complexity}
\usepackage{amsthm}
%\usepackage{authblk}
\usepackage{color}
\usepackage{amsmath}

\newcommand\pall{\textsc{pall}\xspace}

\newcommand{\todo}[1]{{\color{red} TODO: {#1}}}
\newtheorem{prop}{Proposition}

\graphicspath{{img/}}

%opening
\title{Contention management for Cloud Ran over an optical ring}

%\author[1]{Dominique Barth}
%\author[2]{Dominique Chiaroni ?}
%\author[1]{Ma\"el Guiraud}
%\author[1]{Yann Strozecki}
%\affil[1]{David Laboratory, UVSQ}
%\affil[2]{Nokia Bell Labs France}

\author{Dominique Barth\addressmark{1}
  \and Dominique Chiaroni?\addressmark{2}
  \and Ma\"el Guiraud \addressmark{1}
   \and Yann Strozecki \addressmark{1}
  }

\address{\addressmark{1}David Laboratory, UVSQ \\
  \addressmark{2}BNokia Bell Labs France}
\keywords{N-GREEN, Optical ring, Latency, 5G}

\begin{document}

\maketitle

\begin{abstract}
Nowadays challenge for network providers is to design some network which satisfies in the same time a good Quality of Services and a cheap hardware development. This study is a contribution to the N-GREEN project, which has for goal to develop a low cost optical ring technology that ensures some good performances (dataflow, latency,...) without increasing the hardware with some expensive E2E connections. In this paper, we study the compatibility of such a technology with the development of the Cloud Ran, a latency critical application which is a major aspect of the 5G deployment. 
\end{abstract}

\section{Introduction}
Network providers have to design cheapest networks while the amount of datas and online applications significantly increases. Much of these applications have some QoS criteria, like a minimal bandwidth or a maximal latency. The N-GREEN project aims to propose an high performing optical ring while ensuring a minimal cost for providers. Indeed adversely to most of the nowadays solutions to ensure some good QoS [huawei, demander a dominique C], that establish some End to End connection between the nodes, which is extremely expensive, the N-GREEN optical ring is designed to ensure some good performances with few hardware solutions.

This study is based on the Cloud RAN application in the N-GREEN optical ring. Indeed, Cloud RAN is one of the major area of development for 5G, that consists in centralizing the computation units (or {\bf BaseBand Units, BBU}) of the Remote Radio Headers ({\bf RRHs}) in one {\bf datacenter}. The latency of the messages between the BBU and the RRH is critical []. Here, we study the latency of some C-RAN equipment connected through an N-GREEN optical ring.

In the next part of this paper, we expose the specificity of the optical ring, and the model we studied. In sec ~\ref{sec:oportmethods}, we study two method to manage the messages arrivals, and their impact on the latency. Finally, in sec~\ref{sec:deterministicalgorithms}, we propose and study some deterministic algorithm which allows the C-RAN to not be buffered at all, while the QoS of others messages is also increased.
\todo{Je sais pas si il faut parler de SDN, qui est un keyword a la mode mais peut etre que l'architecture ngreen nous propose, demander a chiaroni}
\subsection*{Related work}
\todo{?}

\section{Description of the network, model, problematic}

  \subsection{Network modeling}

The model exposed here has already been studied for another particular topology of network and with different problematics from the ones of this paper. One can find in \cite{latency2017} the complexity results on the problem proposed, and some algorithmic solutions to solve it in star networks.

  \subsection{N-GREEN Optical ring}

 We consider a circular digraph $G = (V,A)$ representing an unidirectional optical ring. The vertices of the graph represents the nodes of the ring. Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time taken by a message to go from $u$ to $v$ using this arc.  A {\bf route} $r$ in $G$ is a directed path, that is, a sequence of adjacent vertices. 
 We assume that each RRH has an associated BBU.
  In the process we study, a message is sent from an RRH to a BBU on each route at each period, denoted by $P$. The time is discretized, i.e. a period is sliced into $P$ {\bf slots}. We call forward routes the routes going from the RRH to the BBU and Backward routes the routes going from the BBU to the RRH. The addition of the weight of the two routes is then equal to $RS$, the size of the ring. 
 We only consider one datacenter into the ring. This mean that all the forward routes have the same destination nodes, and all the backward routes have the same source node.

   In this entire subsection, the ring is in broadcast and select mode with an emission release policy. We first propose an algorithmic model for the ring. In ~\ref{sec:oportmethods}, we study the behavior of the ring with an opportunistic insertion policies, in which the insertion buffer is managed by two different methods. Finally, we propose and study in ~\ref{sec:deterministicalgorithms} some algorithm allowing the C-RAN PDUs to have $0$ sojourn time in the stations, while the BE PDUs are as little buffered as possible.

\subsection{Into the node : Two kind of traffics}
  In this study, we focus on the behavior of the N-GREEN optical ring. Therefore, we do not want to consider the issues caused by the upstream network. 
   To refine our model around the N-GREEN study, one must consider the opto-electronic stations behavior.
   Each N-GREEN station is connected to at least one electronic interface of rate $D$. as mentioned in sec.\ref{com-mod} a station is able to use all the $K$ channels during a slot of duration $Z/KD$ to send a container of capacity $Z$ which contain all the data received  by an electronic interface during a macro-slot, that is, the time needed to fill a container at rate $D$, i.e. $Z/D$
  In other words, an N-GREEN station is able to fill a PDU with the datas received during a macro-slot in the electronic domain.

\begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.3]{slot1.pdf}
  \includegraphics[scale=0.3]{slot2.pdf}
     \caption{Opto-electronic interface.}

\end{center}
  \end{figure}

      An N-GREEN station deals with two kinds of traffics. Some C-RAN and some Best Effort. We assume that each traffic has its corresponding electronic interface. Also, a C-RAN message is of size $Z $ and completely fills a container let us call {\bf C-RAN PDU} such a message. In the same time, the Best Effort SDUs are buffered in a first {\em gathering buffer} before being gathered together into a {\bf BE PDU}. Once the PDUs are created, there join the {\em contention buffer} before being sent in the ring.
      \begin{figure}[h!]
\begin{center}   
  \includegraphics[scale=0.7]{buffers.pdf}
     \caption{An N-GREEN station.}

\end{center}
  \end{figure}

 In this study, we measure the sojourn time $W$ of a PDU in a station. The model we consider in our experiments to generate the BE PDUs is described in sec~\ref{jmf}.

 \paragraph{C-RAN PDU generation model} An RRH usually emit an huge quantity of information during a long time. Also, as we just see, an RRH can send no more than a PDU every $10\mu s$ on the ring. This gap between two PDU from the same RRH is defined by $K$, the number of channels considered in the ring.
 We denote by $ET$,for {\bf Emission time}, the time during which an RRH emits a PDU every $K$ slots on the ring. An RRH emits $\frac{ET}{K}$ PDUs on the ring, every period $P$.

        \begin{figure}[h!]
\begin{center}

      \includegraphics[width=\textwidth]{emission_antenna.pdf}
     \caption{C-RAN PDU generation.}
\end{center}
  \end{figure}
  \paragraph{Back and forth communications} As we explained in the introduction of this section, once the datacenter receives some PDUs from an RRH, it computes an answer and send it to the RRH through the ring. To simplify our model, we assume that the computation times is the same for all BBUs and that it is a multiple of the period. In this situation, we can assume that, each time the datacenter receives a container with a C-RAN PDU from an RRH, it immediately sends an answer (which is in fact the answer to the two periods ago C-RAN PDU's).

 The behavior of the C-RAN PDU generation leads us a new problem, similar to \pall. The set of time slots used by route $r$ at vertex $v$ in a period $P$, is now defined by $[t(v,r)]_{P,K} = \{t(v,r) +i \mod P \mid i \in \{0,EP,2\times K,...., \frac{ET}{K}\times K\} \}$. Consequently, we now want to find a $(P,ET)$-periodic assignment that set the offsets of the routes $m_r$, such that there is no collision between two routes $r_1$ and $r_2$, that is, $[t(v,r_{1})]_{P,K} \cap [t(v,r_{2})]_{P,K} \neq \emptyset$.

 The rest of this study is divided in two parts. In a first time, we look at the behavior of the ring and the impact of the PDUs sojourn time with two different method of managing the contention buffer. Then, we propose some algorithms that solve the previous problem of finding a $(P,ET)$-periodic assignment for the C-RAN PDUs and we compare the impact of those different algorithms on the BE PDUs sojourn time.

  \subsection{Parameters of the study}
  \label{sec:parameters} The experiment of this subsections are made following the same parameters, until sec~\ref{sec:optialgo}. We set $K = 10$ chanels, some electronic interface of rate $D=10$Gbps and $Z = 12500$B so, $Z/KD = 1\mu$s. The optical ring has a rate $KD=100$Gbps, while a slots has a duration of $1\mu$s. The length of the ring is to $20$km in our simulations, this means that the ring has a length of $RS = 100$ slots. We consider some BE SDUs of $125$B, and we parametrized BE PDU generator of sec~\ref{jmf} such that each station load the network with an average of $3,5\%$ of BE traffic. We set $ET = 500$ slots, that correspond to a C-RAN traffic of $5$Gbps. The period  $P$ is to $1$ms, that is $1000$ slots. We set the number of RRH to $n=5$. We take $5$ stations and one of them is the datacenter. The antennas are apportioned between the others station. With those parameters, the network is theoretically loaded to $67.5\%$.

  \begin{figure}
  \centering
  \begin{tabular}{|c|c|}
  \hline
 Number of channels $K$ & $10$  \tabularnewline
  \hline
  Rate of an electronic interface $D$ & $10$ Gbps \tabularnewline
  \hline
  Container size  $Z$ & $12,500$ B  \tabularnewline
  \hline
  Slot duration $Z/KD$ & $1\mu$s \tabularnewline
  \hline
  Optical ring rate $KD$ & $100$ Gbps \tabularnewline
  \hline
  Length of the ring $RS$ & $100$ slots \tabularnewline
  \hline
  BE SDU size & $125$B \tabularnewline
  \hline
  C-RAN PDU size & $12,500$B$=Z$ \tabularnewline
  \hline
  Emission time $ET$ & $500$ slots \tabularnewline
  \hline
   Period $P$ & $1,000$ slots \tabularnewline
  \hline
  Number of RRH & $5$  \tabularnewline
  \hline
  Number of stations $n$ & $5$  \tabularnewline
  \hline

  \end{tabular}
  \caption{Parameters of the following experiments based on N-GREEN}\label{parameters}
  \end{figure}

   \section{Performance evaluation of the N-GREEN optical ring}
   \label{sec:oportmethods}
   In a first time, we will look at the performance of the N-GREEN optical ring with an opportunistic insertion policy \ref{com-mod}. When a station wants to send a PDU on the ring, it uses the first available container .
    We study the performance of the ring through two methods; a full opportunistic method, and a method that prioritize the C-RAN PDUs. Since we only consider some PDUs arrivals, those two methods are some variants of the management of the PDUs in the station.
   For those two methods, the offsets $m_r$ of the routes are chosen randomly in the period, i.e. we do not choose the first time at which the RRH start to emit.
   Since we do not manage those offsets, the two following methods do not gives us some $(P-ET)$-periodic assignment. No choices are made on the offsets and thus, two routes can collides.

    \subsection{Full opportunistic method}
    \label{sec:fullopport}
    We first want to look at a simple configuration in which we do not manage the PUDs (BE or C-RAN) arriving into a station. At their arrival, the BE and C-RAN PDUS are buffered in the contention buffer, and this buffer is emptied following the FIFO rule.

The following experiment shows us the performance this {\bf full opportunistic method} with some parameters issued from N-GREEN. 
On fig~\ref{fig:oport}, one can see the cumulative distribution of the sojourn times of the C-RAN and BE PDUs. Those results are computed on $100$ instances of optical rings that have run during $10,000,000$ slots. The measures are taken after $3,000$ slots of simulation, to let the ring initialize it's behavior. The parameters of the simulations are stated in sec~\ref{sec:parameters}.

    \begin{figure}[h!]
    \label{fig:oport}
        \begin{center}
      \includegraphics[scale=0.4]{oport}

      \caption{Full opportunistic method performances.}
      \end{center}
  \end{figure}

  As we can see on fig~\ref{fig:oport}, the sojourn times for the different kind of PDU is notably similar because we do not manage anything. Furthermore, we can remark that about $10\%$ of the C-RAN messages wait over $100\mu$s, that is already critical for C-RAN \todo{ref}.

\subsection{C-RAN priority method}
\label{sec:cranprio}
  In order to improve the C-RAN PDUs sojourn time, we imagined the following solution, called {\bf C-RAN priority method}. Each stations have two contention buffers. One for the BE PDUs, and one fore the C-RAN PDUs. When a station is able to send a PDU on the ring, i.e. its available container free, the container is filled with the C-RAN PDUs first.

    \begin{figure}[h]
\begin{center}   
      \includegraphics[scale=0.7]{cranprio.pdf}
     \caption{C-RAN priority method.}
\end{center}
  \end{figure}

  With this method, one can imagine improve the sojour time of the C-RAN PDUs. Fig~\ref{fig:prior} shows us the performance of the C-RAN priority algorithm for different kinds of traffics. The parameters of the simulations still the same, stated in sec~\ref{sec:parameters}.
      \begin{figure}[h]
      \label{fig:prior}
\begin{center}

      \includegraphics[scale=0.4]{prior.pdf}

     \caption{C-RAN priority method performances.}
\end{center}
  \end{figure}

  As expected, the sojourn time of the C-RAN PDUs is decreased compared to the full opportunistic method. Nevertheless, there is still $10\%$ of the C-RAN PDUs that have more than $50 \mu$s of latency, and the best effort PDUs are penalized, indeed, close to $10\%$ of the BE PDUs awaits more than $150\mu$s before being sent in the ring, versus close to $0\%$ with the previous method..
  Thus, we propose a deterministic approach in which we set the offsets of the RRH and we reserve the containers needed for the C-RAN PDUs.
   \todo{il manque une partie sur le travail de karim, }
  \section{Deterministic approach for $0$ latency on C-RAN}
\label{sec:deterministicalgorithms}

 For the rest of the subsection, the policy of slot insertion is the slot reservation. We are still in emission release policy. We present three algorithms that allows the C-RAN PDUs to have $0$ sojourn time in the insertion buffers by establishing a static reservation of the slots in the period.
 Those algorithm are {\bf Centralized} and requires a global supervisor of the network to be implemented .\todo{phrase + ref sdn?}

\paragraph{Slot reservation} To decrease the C-RAN messages sojourn time, one plan to reserve the container for the stations. Indeed, if a station $i$ needs to send a PDU at time $t$, a container needs to be reserved since the previous lap of the container, i.e. at time $t - RS$ by $i$. In this situation, if the container is already taken by a PDU which has been sent by a station $j$, $j$ will remove the PDU of the container during the next lap of the ring, and no other stations are able to write in this container before it comes back to the station $i$ a date $t$. By finding a $(P,ET)$-periodic assignment and reserving the corresponding container, we allow the C-RAN PDUs to have $0$ sojourn time in the stations. Though, it impacts the best effort PDUs, by avoiding them to use free reserved containers. It is equivalent to increase the load of the network, without increasing the number of PDUs carried by the network.

\paragraph{RRHs synchronisations}
This slot reservation implies that the RRHs are synchronized with the ring. The following proposed algorithms set a sequence of reserved slots for each RRH in each period. A technical application implies to simultaneously ensure the reservation of the slot to the given dates, and the synchronization of the RRH with those reserved slot. One must ensure that the C-RAN PDU arrives in the contention buffer of the station just before the reserved container.

In this section, we explain the different algorithm we use to ensure $0$ sojourn time on C-RAN PDUs and we study their impact on the BE PDUs sojourn times.

Unlike the previous methods with opportunistic insertion policy, we now want to choose a $(P,ET)$-periodic assignment for the routed network $(G,{\cal R})$. Since all the forward routes have the same last vertex $v$ (the datacenter), which is also the first vertex of all the backward routes, we choose to manage the collision in this vertex only. The purpose is to determine the time $t(v,r_i)$ at which the first C-RAN PDU of the route $i$ arrives at the datacenter $v$ for each routes $i$, such that there is no collisions between the routes. Let us call BBU-offset this time. Once the BBU-offsets are set, for all routes $i$, it is easy to compute $m_{r_i} = t(v,r_i) - \lambda(v,r_i)$.

\subsection{N-GREEN parameters adapted algorithms}
An RRH can not emit a message more often than once slot every $K$ slots. Remember that {\bf macro slot} is a duration of $K$ slots, during which each RRH can emit at most once. Thus, we consider the simple case in which there is less C-RAN traffic than slots in a macro slot. Indeed, in that case, if we manage the collision in one macro slot, i.e. we assign a C-RAN traffic to each slot of the macro-slot, we find a  $(P,ET)$-periodic assignment. Since a BBU always instantly emits an answer to it's RRH, for each RRH, a group of two following containers (called {\bf bunch}) can be reserved. Thus, we first study the case $K \ge 2\times n$. As a reminder, $n$ is the number of couple BBU-RRH.

 Because there is at most as much couples BBU-RRH as bunches, we want to assign one RRH to one bunch.
We propose the following {\bf naive reservation algorithm}. For each RRH $i, i\in \{0,...,n-1\} $, set $t(v,r_i)= 2\times i$ with $v$ the vertex of the BBUs. The model automatically fixes the offset of the backward route $\rho(r_i)$ to $m_{\rho(r_i)}= 2\times i +1$. This is the reason why we do not care about the backward routes anymore, and we only deal with the BBU-offsets of the forward routes..
   \begin{figure}[h]
\centering
      \includegraphics[scale=0.7]{freqgrouped.pdf}
     \caption{Grouped assignment of the bunches to the RRH.}   \label{fig:freqG}
  \end{figure}

We kept the same parameters than in the two previous experiments (see~\ref{sec:parameters}) and we made an experiment to show the impact of this algorithm on the BE traffic. Fig~\ref{fig:res1} shows us the distribution of the sojourn time for BE PDUs with this algorithm.

      \begin{figure}[h]
\centering
      \includegraphics[scale=0.4]{res1.pdf}
     \caption{Impact of the naive reservation algorithm on the Best effort PDUs.}   \label{fig:res1}
  \end{figure}

As we can see, the BE traffic is highly penalized by this algorithm, indeed, while almost $100\%$ of the BE PDUs have a sojourn time to less than $200 \mu$s with the full opportunistic method (see fig~\ref{fig:oport}), here, more than half of the BE PDUs are be buffered more than $200\mu s$. Those performances are explained by the structure of the algorithm. The messages are grouped together, and with our parameters, $K = 2\times n$. It creates a long sequence of slots during which there is no free containers in the ring.

To improve the BE PDUs sojourn time, we propose a {\bf splited reservation algorithm} that balances the load of the CRAN traffic over the period. Instead of giving some close BBU-offsets for all routes $i$, with $v$ the datacenter, we now uniformly distribute the different BBU-offsets in the period. Each couple BBU-RRH is still assigned to its bunch, but we split the BBU-offsets of $\frac{P}{n}$. Also, if $2 \times n < K$, the RRH are balanced over the bunches by the same way, we try to give a bunch to a RRH each $\frac{K}{2\times n}$ buches.

   \begin{figure}[!h]
\centering
      \includegraphics[scale=0.7]{freqsplited.pdf}
     \caption{Splited assignment of the bunches to the RRH.}   \label{fig:freqS}
  \end{figure}

  On fig~\ref{fig:res2} one can observe the performance of this algorithm on the BE PDUs sojourn time. Once again, to have a reference point, we take the same parameters for the simulation.

 \begin{figure}[h]
\centering
      \includegraphics[scale=0.4]{res2.pdf}
     \caption{Impact of the splited reservation algorithm on the Best effort.}   \label{fig:res2}
  \end{figure}

  As we can see, the sojourn time of the BE PDUs is highly better with this this algorithm. Indeed almost $100\%$ of CRAN PDUs have a sojourn time of less than $50\mu$s which is better than the full opportunistic method. Thus, we decreased the latency of every kind of traffic.

\subsection{With more antennas}
\label{sec:optialgo}
 In this section, we study the case $n > \frac{K}{2}$, we want to assign more than one RRH to a bunch. 
 Let us consider a particular behavior of the ring. Instinctively, we can think that if we have enough space in the period for many traffics on the same frequency that is, $ET \le \frac{P}{2}$, we can assign several couples BBU-RRH to the same bunch.

 Let us take $ET =  \frac{P}{2}$ and $n = \frac{K}{2} + 1$. We assign a bunch to each $\frac{K}{2}$ first RRH and we have only one RRH left. Then, we only look at one bunch, on which we want to add the new couple BBU-RRH.

 We take a ring with two stations $A$ and $B$. We simplify the model to only look at the behavior of one bunch, thus, both of the nodes alternatively emits some containers every slots, during $ET$ slots in the period $P$. By construction, we allow $A$ to emit a time $1$ during $ET$ slots. This container arrives in $B$ at $\omega(A,B)$, that is  $[t(B,r_A)]_{P,K} = [\omega(A,B);\omega(A,B)+ET]$. Then, $B$ can immediately emit its containers at time $\omega(A,B)+ET$. This containers from $B$ arrives at $A$ at time $\omega(A,B)+ET + \omega(B,A) = ET + RS$, and thus, $[t(A,r_B)]_{P,K} = [ET + RS;ET + RS + ET] = [ET+RS; RS + P] = [ET + RS; RS] \mod P$. Since $[t(A,r_A)]_{P,K} = [1;ET]$, there is a collision at the interval $[1;RS]$ in the period between the two routes $A$ and $B$.
  \begin{figure}[h]
\centering
      \includegraphics[scale=0.7]{rs.pdf}
     \caption{Collision between two routes on the same bunch when the period is too small.}   \label{fig:proofrs}
  \end{figure}

 As we have just noted, if several RRH share the same bunch, the period must have an additional budget in addition to the time needed to send the messages. Let us study the size of the additional budget.
 \begin{prop}
 If several RRH shares a bunch, it is possible to find a $(P,ET)$-periodic assignment if $P \ge n\times ET + RS$ , with $n$ the number of RRHs.
 \end{prop}
 \begin{proof}
 We seek to show that proposition by induction.

 {\bf Base case:} For $n = 2$, the proof of the previous example shows us that it is possible to assign two RRH on the same bunch with $P = 2\times ET + RS$.

 {\bf Induction step:}  We consider that we have a frequency shared by $n$ RRH, with a period of size $P= n\times ET + RS$. We want to show that if we want to add one antenna to the bunch, we need a period of size at least $P = (n+1)\times ET + RS$. If we look at the sequence period of the bunch with $n$ RRH. We can observe that this sequence is the same in every station, shifted of the length of the routes between two stations. For instance, if we take two stations $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted of $\omega(A,B)$.

   \begin{figure}[h]
\centering
      \includegraphics[scale=0.7]{period1.pdf}
     \caption{An example of sequence with n = 3.}   \label{fig:proofperiod1}
  \end{figure}

 Thus, if we add $ET$ slots in this frequency, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence.

   \begin{figure}[h]
\centering
      \includegraphics[scale=0.7]{period2.pdf}
     \caption{The same sequence with n = 4.}   \label{fig:proofperiod2}
  \end{figure}
  Note that a station can send some traffic from more than one antenna, the figures ~\ref{fig:proofperiod1} and \~ref{fig:proofperiod2} are just an example, but this proof stays the same.
 \end{proof}

Considering those results, we propose an algorithm to allow several RRH to share the same bunch, as long as $P \ge n\times ET + RS$. 
Since we need $RS$ slots on a each bunch with at least an RRH to assign another RRH to this latter, it is interesting to fill as far as possible the bunches. We then compute the number of bunches needed to carry the number of RRH $n$. Then, the algorithms tries to balance those bunches into the macro-slot, i.e. it avoids to group the used bunches together.
The used bunches have $RS$ or more free slots in the period. Thus, the algorithm subsequently balance BBU-offsets of the first RRH of each bunch, with the same idea than the splited algorithm. We call this algorithm the {\bf full repartition algorithm}.

   \begin{figure}[h]
\centering
      \includegraphics[scale=0.7]{optimalgo.pdf}
     \caption{Organization of the bunches with the balancing algorithm.}   \label{fig:optimalgo}
  \end{figure}

  We want to observe the impact of this algorithm on BE traffic. Since our previous parameters did not allow several RRH to share a frequency, we now set $ET = 200$, that correspond to a C-RAN flow of $2$Gbps. This is not out of context since the exact split (the C-RAN split is the degree of centralization of the computation units in the cloud) of the C-RAN is not fully determined yet~\cite{REF}.\todo {la ref} To keep a load similar to the load in the previous experiment, we set the number of antennas to $n=12$. The others parameters are all the one described in the sec~\ref{sec:parameters}.
  The following experiment shows us the impact of the balancing algorithm on the BE traffics. We chose to compare those results to a simulation with the same parameters but with the full opportunistic method of sec~\ref{sec:cranprio}.

   \begin{figure}[h]
\centering
      \includegraphics[scale=0.4]{optim.pdf}
     \caption{Balancing algorithm performance on the N-GREEN optical ring.}   \label{fig:optimres}
  \end{figure}

  As fig~\ref{fig:optimres} shows, the full repartition algorithm ensures a lower sojourn time to BE PDUs than the full opportunistic method, which gave the best result for the BE traffic. Indeed, since we remove the random aspect of the C-RAN PDUs generation, we balanced the load over the period an then increased the BE performances while we totally removed the C-RAN PDUs sojourn time.

  \bibliographystyle{ieeetr}
\bibliography{src}

\end{document}

### 2018-02-14 Papier NGreen/article.tex
Model + noms

@@
 The vertices of the graph represents the nodes of the ring.
-Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time taken by a message to go from $u$ to $v$ using this arc.
 A {\bf route} $r$ in $G$ is a directed path, that is, a sequence of adjacent vertices.
- We assume that each RRH has an associated BBU.
-  In the process we study, a message is sent from an RRH to a BBU on each route at each period, denoted by $P$.
+We denote by $\omega(u,v)$ the weight of a route, i.e.
+the time taken by a message to go from $u$ to $v$.
+  In the process we study, a message is sent on each route at each period, denoted by $P$.
 The time is discretized, i.e.
 a period is sliced into $P$ {\bf slots}.
-We call forward routes the routes going from the RRH to the BBU and Backward routes the routes going from the BBU to the RRH.
-The addition of the weight of the two routes is then equal to $RS$, the size of the ring.
+The ring can be seen as a suit of {\bf containers}, of capacity $Z$, expressed in Bytes that rotates each slots to the following position.
+The containers are filled with some packets created by the nodes, called {\bf Packet Data Unit, or PDU}.
+  The optical ring has a particularity.
+Each node has an access to one container per slot.
+When a node wants to insert a PDU on the ring, the container sawn by the ring must be free.
+Otherwise, the node has to wait until it has an access to a free container to emit its PDU.
+The ring follows a {\bf broadcast and select with emission release} policy.
+A container put on the ring by a node can only be removed by the same node, one lap of the ring later.
+
+  This study focuses on the performances of the C-RAN PDUs, thus the route we consider are the routes between the BBUs and the RRHs .We assume that there is a bijection between the RRHs and the BBUs.
+ We call forward routes the routes going from the RRHs to the BBUs and Backward routes the routes going from the BBUs to the RRHs.
+The addition of the weight of the two routes of a couple BBU-RRH is then equal to $RS$, the size of the ring, measured in slots.
+We denote by $n$ the number of couples BBU-RRH.
  We only consider one datacenter into the ring. This mean that all the forward routes have the same destination nodes, and all the backward routes have the same source node.
 
-   In this entire subsection, the ring is in broadcast and select mode with an emission release policy.
-We first propose an algorithmic model for the ring.
-In ~\ref{sec:oportmethods}, we study the behavior of the ring with an opportunistic insertion policies, in which the insertion buffer is managed by two different methods.
-Finally, we propose and study in ~\ref{sec:deterministicalgorithms} some algorithm allowing the C-RAN PDUs to have $0$ sojourn time in the stations, while the BE PDUs are as little buffered as possible.
-
 \subsection{Into the node : Two kind of traffics}
-  In this study, we focus on the behavior of the N-GREEN optical ring. Therefore, we do not want to consider the issues caused by the upstream network. 
-   To refine our model around the N-GREEN study, one must consider the opto-electronic stations behavior.
-   Each N-GREEN station is connected to at least one electronic interface of rate $D$.
-as mentioned in sec.\ref{com-mod} a station is able to use all the $K$ channels during a slot of duration $Z/KD$ to send a container of capacity $Z$ which contain all the data received  by an electronic interface during a macro-slot, that is, the time needed to fill a container at rate $D$, i.e.
-$Z/D$
-  In other words, an N-GREEN station is able to fill a PDU with the datas received during a macro-slot in the electronic domain.
+   To refine our model, one must consider the opto-electronic nodes behaviour.
+   Each node of the ring is connected to some external networks by at least one electronic interface of rate $D$Bps.
+The ring has a rate of $KD$Bps.
+$K$ is called the {\bf acceleration factor} between the electronic and the optical domains.
+A node is able to aggregate the data received on the electronic interface during $Z/D$s to create a PDU, which fills a container in $Z/KD$s.
+In other words, the node transforms the datas received during a time $Z/D$, called {\bf macro-slot}, into a PDU that can be sent in a slot.
+Consequently, a single electronic interface can not emit more than one PDU every $k$ slots on the ring.
 
@@
 
-      An N-GREEN station deals with two kinds of traffics.
+      An node deals with two kinds of traffics.
 Some C-RAN and some Best Effort.
 We assume that each traffic has its corresponding electronic interface.
-Also, a C-RAN message is of size $Z $ and completely fills a container let us call {\bf C-RAN PDU} such a message.
-In the same time, the Best Effort SDUs are buffered in a first {\em gathering buffer} before being gathered together into a {\bf BE PDU}.
+Also, a C-RAN message is of size $Z$ and completely fills a container let us call {\bf C-RAN PDU} such a message.
+In the same time, the Best Effort messages are buffered in a first {\em gathering buffer} before being gathered together into a {\bf BE PDU}.
 Once the PDUs are created, there join the {\em contention buffer} before being sent in the ring.
@@
 
- In this study, we measure the sojourn time $W$ of a PDU in a station. The model we consider in our experiments to generate the BE PDUs is described in sec~\ref{jmf}.
+\paragraph{BE PDU generation model} To Generate the BE PDU, we used the distribution of the time between the generation of two BE PDU given by some numerical analysis work of another study for N-GREEN.
+This distribution was calculated by modelling a gathering buffer.
 
- \paragraph{C-RAN PDU generation model} An RRH usually emit an huge quantity of information during a long time.
-Also, as we just see, an RRH can send no more than a PDU every $10\mu s$ on the ring.
-This gap between two PDU from the same RRH is defined by $K$, the number of channels considered in the ring.
+ \paragraph{C-RAN PDU generation model} An RRH usually emit an huge quantity of information during a long time. Also, as we just see, an RRH can send no more than a PDU every $K$ slots on the ring.
  We denote by $ET$,for {\bf Emission time}, the time during which an RRH emits a PDU every $K$ slots on the ring. An RRH emits $\frac{ET}{K}$ PDUs on the ring, every period $P$.
@@
 
- The behavior of the C-RAN PDU generation leads us a new problem, similar to \pall.
-The set of time slots used by route $r$ at vertex $v$ in a period $P$, is now defined by $[t(v,r)]_{P,K} = \{t(v,r) +i \mod P \mid i \in \{0,EP,2\times K,...., \frac{ET}{K}\times K\} \}$.
-Consequently, we now want to find a $(P,ET)$-periodic assignment that set the offsets of the routes $m_r$, such that there is no collision between two routes $r_1$ and $r_2$, that is, $[t(v,r_{1})]_{P,K} \cap [t(v,r_{2})]_{P,K} \neq \emptyset$.
-
+  The time at which an RRH on the route $r_i$ sends its first PDU is called {\bf offset} and can be expressed by $m_{r_i}$.
+The time at which this first PDU arrives to its BBU is the {\bf BBU-offset}, $t(v,r_i) = m_{r_i} + \omega(u,v)$, where $u$ is the RRH and $v$ the BBU of the route $r_i$.
+  We denote by {\bf latency} of a PDU the time sojourn time of a PDU in the contention buffer.
+  We want to ensure a good latency for the C-RAN PDUs.
+If there is no BE PDUs on the ring, the challenge is to fix the offsets (that directly fixes the BBU-offsets) of the routes such that two messages never collides each others.
+Nevertheless, we have ton consider the BE PDUs in our model.
  The rest of this study is divided in two parts.
-In a first time, we look at the behavior of the ring and the impact of the PDUs sojourn time with two different method of managing the contention buffer.
-Then, we propose some algorithms that solve the previous problem of finding a $(P,ET)$-periodic assignment for the C-RAN PDUs and we compare the impact of those different algorithms on the BE PDUs sojourn time.
+In a first time, we look at the behaviour of the ring and the impact of the PDUs latency with two different method of managing the contention buffer.
+Then, we propose some algorithms that solve allows us to choose the offsets for the C-RAN PDUs by reserving the containers, and we compare the impact of those different algorithms on the BE PDUs latency.
 
@@
 The length of the ring is to $20$km in our simulations, this means that the ring has a length of $RS = 100$ slots.
-We consider some BE SDUs of $125$B, and we parametrized BE PDU generator of sec~\ref{jmf} such that each station load the network with an average of $3,5\%$ of BE traffic.
+We consider some BE SDUs of $125$B, and we parametrized BE PDU generator of sec~\ref{jmf} such that each node load the network with an average of $3,5\%$ of BE traffic.
 We set $ET = 500$ slots, that correspond to a C-RAN traffic of $5$Gbps.
@@
 We set the number of RRH to $n=5$.
-We take $5$ stations and one of them is the datacenter.
-The antennas are apportioned between the others station.
+We take $5$ nodes and one of them is the datacenter.
+The antennas are apportioned between the others node.
 With those parameters, the network is theoretically loaded to $67.5\%$.
@@
   \hline
-  Number of stations $n$ & $5$  \tabularnewline
+  Number of nodes $n$ & $5$  \tabularnewline
   \hline
@@
    \label{sec:oportmethods}
-   In a first time, we will look at the performance of the N-GREEN optical ring with an opportunistic insertion policy \ref{com-mod}.
-When a station wants to send a PDU on the ring, it uses the first available container .
+   In a first time, we will look at the performance of the N-GREEN optical ring with an opportunistic insertion policy.
+When a node wants to send a PDU on the ring, it uses the first available container .
     We study the performance of the ring through two methods; a full opportunistic method, and a method that prioritize the C-RAN PDUs.
-Since we only consider some PDUs arrivals, those two methods are some variants of the management of the PDUs in the station.
+Since we only consider some PDUs arrivals, those two methods are some variants of the management of the PDUs in the node.
    For those two methods, the offsets $m_r$ of the routes are chosen randomly in the period, i.e. we do not choose the first time at which the RRH start to emit.
-   Since we do not manage those offsets, the two following methods do not gives us some $(P-ET)$-periodic assignment. No choices are made on the offsets and thus, two routes can collides.
 
@@
     \label{sec:fullopport}
-    We first want to look at a simple configuration in which we do not manage the PUDs (BE or C-RAN) arriving into a station.
+    We first want to look at a simple configuration in which we do not manage the PUDs (BE or C-RAN) arriving into a node.
 At their arrival, the BE and C-RAN PDUS are buffered in the contention buffer, and this buffer is emptied following the FIFO rule.
@@
 The following experiment shows us the performance this {\bf full opportunistic method} with some parameters issued from N-GREEN. 
-On fig~\ref{fig:oport}, one can see the cumulative distribution of the sojourn times of the C-RAN and BE PDUs.
+On fig~\ref{fig:oport}, one can see the cumulative distribution of the latency of the C-RAN and BE PDUs.
 Those results are computed on $100$ instances of optical rings that have run during $10,000,000$ slots.
@@
 
-  As we can see on fig~\ref{fig:oport}, the sojourn times for the different kind of PDU is notably similar because we do not manage anything.
+  As we can see on fig~\ref{fig:oport}, the latency for the different kind of PDU is notably similar because we do not manage anything.
 Furthermore, we can remark that about $10\%$ of the C-RAN messages wait over $100\mu$s, that is already critical for C-RAN \todo{ref}.
@@
 \label{sec:cranprio}
-  In order to improve the C-RAN PDUs sojourn time, we imagined the following solution, called {\bf C-RAN priority method}.
-Each stations have two contention buffers.
+  In order to improve the C-RAN PDUs latency, we imagined the following solution, called {\bf C-RAN priority method}.
+Each nodes have two contention buffers.
 One for the BE PDUs, and one fore the C-RAN PDUs.
-When a station is able to send a PDU on the ring, i.e.
-its available container free, the container is filled with the C-RAN PDUs first.
+When a node is able to send a PDU on the ring, i.e.
+its available container is free, the container is filled with the C-RAN PDUs first.
 
@@
 
-  With this method, one can imagine improve the sojour time of the C-RAN PDUs.
+  With this method, one can imagine improve the latency of the C-RAN PDUs.
 Fig~\ref{fig:prior} shows us the performance of the C-RAN priority algorithm for different kinds of traffics.
@@
 
-  As expected, the sojourn time of the C-RAN PDUs is decreased compared to the full opportunistic method.
+  As expected, the latency of the C-RAN PDUs is decreased compared to the full opportunistic method.
 Nevertheless, there is still $10\%$ of the C-RAN PDUs that have more than $50 \mu$s of latency, and the best effort PDUs are penalized, indeed, close to $10\%$ of the BE PDUs awaits more than $150\mu$s before being sent in the ring, versus close to $0\%$ with the previous method..
@@
 
- For the rest of the subsection, the policy of slot insertion is the slot reservation.
-We are still in emission release policy.
-We present three algorithms that allows the C-RAN PDUs to have $0$ sojourn time in the insertion buffers by establishing a static reservation of the slots in the period.
+ In this section We present three algorithms that allows the C-RAN PDUs to have $0$ latency in the insertion buffers by establishing a static reservation of the slots in the period.
  Those algorithm are {\bf Centralized} and requires a global supervisor of the network to be implemented .\todo{phrase + ref sdn?}
 
-\paragraph{Slot reservation} To decrease the C-RAN messages sojourn time, one plan to reserve the container for the stations.
-Indeed, if a station $i$ needs to send a PDU at time $t$, a container needs to be reserved since the previous lap of the container, i.e.
+\paragraph{Slot reservation} To decrease the C-RAN messages latency, one plan to reserve the container for the nodes.
+Indeed, if a node $i$ needs to send a PDU at time $t$, a container needs to be reserved since the previous lap of the container, i.e.
 at time $t - RS$ by $i$.
-In this situation, if the container is already taken by a PDU which has been sent by a station $j$, $j$ will remove the PDU of the container during the next lap of the ring, and no other stations are able to write in this container before it comes back to the station $i$ a date $t$.
-By finding a $(P,ET)$-periodic assignment and reserving the corresponding container, we allow the C-RAN PDUs to have $0$ sojourn time in the stations.
+In this situation, if the container is already taken by a PDU which has been sent by a node $j$, $j$ will remove the PDU of the container during the next lap of the ring, and no other nodes are able to write in this container before it comes back to the node $i$ a date $t$.
+By choosing the offsets of the route and reserving the corresponding containers, we allow the C-RAN PDUs to have $0$ latency in the nodes.
 Though, it impacts the best effort PDUs, by avoiding them to use free reserved containers.
@@
 A technical application implies to simultaneously ensure the reservation of the slot to the given dates, and the synchronization of the RRH with those reserved slot.
-One must ensure that the C-RAN PDU arrives in the contention buffer of the station just before the reserved container.
+One must ensure that the C-RAN PDU arrives in the contention buffer of the node just before the reserved container.
 
-In this section, we explain the different algorithm we use to ensure $0$ sojourn time on C-RAN PDUs and we study their impact on the BE PDUs sojourn times.
-
-Unlike the previous methods with opportunistic insertion policy, we now want to choose a $(P,ET)$-periodic assignment for the routed network $(G,{\cal R})$.
+Unlike the previous methods with opportunistic insertion policy, we now want to choose a the offsets for the routes.
 Since all the forward routes have the same last vertex $v$ (the datacenter), which is also the first vertex of all the backward routes, we choose to manage the collision in this vertex only.
-The purpose is to determine the time $t(v,r_i)$ at which the first C-RAN PDU of the route $i$ arrives at the datacenter $v$ for each routes $i$, such that there is no collisions between the routes.
-Let us call BBU-offset this time.
-Once the BBU-offsets are set, for all routes $i$, it is easy to compute $m_{r_i} = t(v,r_i) - \lambda(v,r_i)$.
+The purpose is then to determine the time BBU offset of the routes.
+Once the BBU-offsets are set, for all routes $i$, it is easy to compute $m_{r_i} = t(v,r_i) - \omega(u,v)$.
 
@@
 Thus, we consider the simple case in which there is less C-RAN traffic than slots in a macro slot.
-Indeed, in that case, if we manage the collision in one macro slot, i.e.
-we assign a C-RAN traffic to each slot of the macro-slot, we find a  $(P,ET)$-periodic assignment.
+Indeed, in that case, we only manage the collision in one macro slot, i.e.
+we assign a C-RAN traffic to each slot of the macro-slot.
 Since a BBU always instantly emits an answer to it's RRH, for each RRH, a group of two following containers (called {\bf bunch}) can be reserved.
@@
 We kept the same parameters than in the two previous experiments (see~\ref{sec:parameters}) and we made an experiment to show the impact of this algorithm on the BE traffic.
-Fig~\ref{fig:res1} shows us the distribution of the sojourn time for BE PDUs with this algorithm.
+Fig~\ref{fig:res1} shows us the distribution of latency for BE PDUs with this algorithm.
 
@@
 
-As we can see, the BE traffic is highly penalized by this algorithm, indeed, while almost $100\%$ of the BE PDUs have a sojourn time to less than $200 \mu$s with the full opportunistic method (see fig~\ref{fig:oport}), here, more than half of the BE PDUs are be buffered more than $200\mu s$.
+As we can see, the BE traffic is highly penalized by this algorithm, indeed, while almost $100\%$ of the BE PDUs have a latency to less than $200 \mu$s with the full opportunistic method (see fig~\ref{fig:oport}), here, more than half of the BE PDUs are be buffered more than $200\mu s$.
 Those performances are explained by the structure of the algorithm.
@@
 
-To improve the BE PDUs sojourn time, we propose a {\bf splited reservation algorithm} that balances the load of the CRAN traffic over the period.
+To improve the BE PDUs latnecy, we propose a {\bf splited reservation algorithm} that balances the load of the CRAN traffic over the period.
 Instead of giving some close BBU-offsets for all routes $i$, with $v$ the datacenter, we now uniformly distribute the different BBU-offsets in the period.
@@
 
-  On fig~\ref{fig:res2} one can observe the performance of this algorithm on the BE PDUs sojourn time. Once again, to have a reference point, we take the same parameters for the simulation.
+  On fig~\ref{fig:res2} one can observe the performance of this algorithm on the BE PDUs latency. Once again, to have a reference point, we take the same parameters for the simulation.
 
@@
 
-  As we can see, the sojourn time of the BE PDUs is highly better with this this algorithm.
-Indeed almost $100\%$ of CRAN PDUs have a sojourn time of less than $50\mu$s which is better than the full opportunistic method.
+  As we can see, thelatency of the BE PDUs is highly better with this this algorithm.
+Indeed almost $100\%$ of CRAN PDUs have a latency of less than $50\mu$s which is better than the full opportunistic method.
 Thus, we decreased the latency of every kind of traffic.
@@
 
- We take a ring with two stations $A$ and $B$.
-We simplify the model to only look at the behavior of one bunch, thus, both of the nodes alternatively emits some containers every slots, during $ET$ slots in the period $P$.
-By construction, we allow $A$ to emit a time $1$ during $ET$ slots.
+ We take a ring with two nodes $A$ and $B$.
+We simplify the model to only look at the behaviour of one bunch, thus, both of the nodes alternatively emits some containers every slots, during $ET$ slots in the period $P$.
+We assume that $A$ emits a time $1$ during $ET$ slots.
 This container arrives in $B$ at $\omega(A,B)$, that is  $[t(B,r_A)]_{P,K} = [\omega(A,B);\omega(A,B)+ET]$.
@@
 This containers from $B$ arrives at $A$ at time $\omega(A,B)+ET + \omega(B,A) = ET + RS$, and thus, $[t(A,r_B)]_{P,K} = [ET + RS;ET + RS + ET] = [ET+RS; RS + P] = [ET + RS; RS] \mod P$.
-Since $[t(A,r_A)]_{P,K} = [1;ET]$, there is a collision at the interval $[1;RS]$ in the period between the two routes $A$ and $B$.
+Since $[t(A,r_A)]_{P,K} = [1;ET]$, there is a collision at the interval $[1;RS]$ in the period between the two traffics from $A$ and $B$.
   \begin{figure}[h]
@@
  \begin{prop}
- If several RRH shares a bunch, it is possible to find a $(P,ET)$-periodic assignment if $P \ge n\times ET + RS$ , with $n$ the number of RRHs.
+ If several RRH shares a bunch, it is possible set the offsets of the routes such that there is no collisions between the messages if $P \ge n\times ET + RS$ , with $n$ the number of RRHs.
  \end{prop}
@@
 
- {\bf Induction step:}  We consider that we have a frequency shared by $n$ RRH, with a period of size $P= n\times ET + RS$.
-We want to show that if we want to add one antenna to the bunch, we need a period of size at least $P = (n+1)\times ET + RS$.
+ {\bf Induction step:}  We consider that we have a bunch shared by $n$ RRH, with a period of size $P= n\times ET + RS$.
+We want to show that if we want to add one RRH to the bunch, we need a period of size at least $P = (n+1)\times ET + RS$.
 If we look at the sequence period of the bunch with $n$ RRH.
-We can observe that this sequence is the same in every station, shifted of the length of the routes between two stations.
-For instance, if we take two stations $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted of $\omega(A,B)$.
+We can observe that this sequence is the same in every nodes, shifted of the length of the routes between two nodes.
+For instance, if we take two nodes $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted of $\omega(A,B)$.
 
@@
 
- Thus, if we add $ET$ slots in this frequency, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence.
+ Thus, if we add $ET$ slots in this bunch, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence.
 
@@
   \end{figure}
-  Note that a station can send some traffic from more than one antenna, the figures ~\ref{fig:proofperiod1} and \~ref{fig:proofperiod2} are just an example, but this proof stays the same.
+  Note that a station can send some traffic from more than one RRH, the figures ~\ref{fig:proofperiod1} and \~ref{fig:proofperiod2} are just an example, but this proof stays the same.
  \end{proof}
@@
   We want to observe the impact of this algorithm on BE traffic.
-Since our previous parameters did not allow several RRH to share a frequency, we now set $ET = 200$, that correspond to a C-RAN flow of $2$Gbps.
-This is not out of context since the exact split (the C-RAN split is the degree of centralization of the computation units in the cloud) of the C-RAN is not fully determined yet~\cite{REF}.\todo {la ref} To keep a load similar to the load in the previous experiment, we set the number of antennas to $n=12$.
+Since our previous parameters did not allow several RRH to share a bunch, we now set $ET = 200$, that correspond to a C-RAN flow of $2$Gbps.
+This is not out of context since the exact split (the C-RAN split is the degree of centralization of the computation units in the cloud) of the C-RAN is not fully determined yet~\cite{REF}.\todo {la ref} To keep a load similar to the load in the previous experiment, we set the number of RRH to $n=12$.
 The others parameters are all the one described in the sec~\ref{sec:parameters}.
   The following experiment shows us the impact of the balancing algorithm on the BE traffics.
-We chose to compare those results to a simulation with the same parameters but with the full opportunistic method of sec~\ref{sec:cranprio}.
+We chose to compare those results to a simulation with the same parameters but with the full opportunistic method of sec~\ref{sec:fullopport}.
 
@@
 
-  As fig~\ref{fig:optimres} shows, the full repartition algorithm ensures a lower sojourn time to BE PDUs than the full opportunistic method, which gave the best result for the BE traffic.
-Indeed, since we remove the random aspect of the C-RAN PDUs generation, we balanced the load over the period an then increased the BE performances while we totally removed the C-RAN PDUs sojourn time.
+  As fig~\ref{fig:optimres} shows, the full repartition algorithm ensures a lower latencye to BE PDUs than the full opportunistic method, which gave the best result for the BE traffic.
+Indeed, since we remove the random aspect of the C-RAN PDUs generation, we balanced the load over the period an then increased the BE performances while we totally removed the C-RAN PDUs latency.
 

### 2018-02-14 Papier NGreen/article.tex
reprise de l'intro

@@
   \and Dominique Chiaroni?\addressmark{2}
-  \and Ma\"el Guiraud \addressmark{1}
+  \and Ma\"el Guiraud \addressmark{1,2}
    \and Yann Strozecki \addressmark{1}
@@
 \begin{abstract}
-Nowadays challenge for network providers is to design some network which satisfies in the same time a good Quality of Services and a cheap hardware development.
-This study is a contribution to the N-GREEN project, which has for goal to develop a low cost optical ring technology that ensures some good performances (dataflow, latency,...) without increasing the hardware with some expensive E2E connections.
+
+% Nowadays challenge for network providers is to design some network which satisfies in the same time a good Quality of Services and a cheap hardware development.
+This study is a contribution to the N-GREEN project, which has for goal to design a low cost optical ring technology with good performances (dataflow, latency,$\dots$) without using expensive end to end connections.
 In this paper, we study the compatibility of such a technology with the development of the Cloud Ran, a latency critical application which is a major aspect of the 5G deployment.
+We show that the latency of the Cloud Rand can be guaranteed by using a deterministic sending scheme without impacting the others traffics.
 \end{abstract}
 
+\todo{ça marque et dans le titre, ça ne devrait pas}
+
 \section{Introduction}
-Network providers have to design cheapest networks while the amount of datas and online applications significantly increases.
-Much of these applications have some QoS criteria, like a minimal bandwidth or a maximal latency.
+
+Network providers have to design inexpensive networks while the amount of data and online applications significantly increases.
+Much of these applications have QoS criteria, like a minimal bandwidth or a maximal latency.
 The N-GREEN project aims to propose an high performing optical ring while ensuring a minimal cost for providers.
-Indeed adversely to most of the nowadays solutions to ensure some good QoS [huawei, demander a dominique C], that establish some End to End connection between the nodes, which is extremely expensive, the N-GREEN optical ring is designed to ensure some good performances with few hardware solutions.
+The current solutions with good QoS [huawei, demander a dominique C], establishes end to end connection (E2E) between the nodes, which is extremely expensive.
+The N-GREEN optical ring is designed to ensure good performances and the hardware it requires scales linearly with the number of nodes while E2E scales quadratically making it impractical for more than a few nodes.
 
-This study is based on the Cloud RAN application in the N-GREEN optical ring.
-Indeed, Cloud RAN is one of the major area of development for 5G, that consists in centralizing the computation units (or {\bf BaseBand Units, BBU}) of the Remote Radio Headers ({\bf RRHs}) in one {\bf datacenter}.
-The latency of the messages between the BBU and the RRH is critical [].
-Here, we study the latency of some C-RAN equipment connected through an N-GREEN optical ring.
+In this article, we study a Cloud RAN application in the N-GREEN optical ring.
+Cloud RAN is one of the major area of development for 5G, that consists in centralizing the computation units (or {\bf BaseBand Units, BBU}) of the Remote Radio Heads ({\bf RRHs}) in one {\bf datacenter}.
+The latency of the messages between the BBU and the RRH is critical \cite{}.
+Here, we study the latency of some C-RAN equipment connected through an N-GREEN optical ring.\todo{mettre les citations, à reprendre de nos précédents articles}
 
-In the next part of this paper, we expose the specificity of the optical ring, and the model we studied.
-In sec ~\ref{sec:oportmethods}, we study two method to manage the messages arrivals, and their impact on the latency.
-Finally, in sec~\ref{sec:deterministicalgorithms}, we propose and study some deterministic algorithm which allows the C-RAN to not be buffered at all, while the QoS of others messages is also increased.
-\todo{Je sais pas si il faut parler de SDN, qui est un keyword a la mode mais peut etre que l'architecture ngreen nous propose, demander a chiaroni}
-\subsection*{Related work}
-\todo{?}
+\todo{Dire un mot sur la forme du traffic cloud RAN, périodique déterministe, aller vers un data center unique, retour, minimisation de la latence ...}
 
-\section{Description of the network, model, problematic}
+In Sec.~\ref{sec:model}, we model the optical ring and the traffic flow we study.
+In Sec.~\ref{sec:oportmethods}, we study the latency when using stochastic multiplexing to manage the messages arrivals on the ring, with or without priority of the C-RAN traffic.
+Finally, in Sec.~\ref{sec:deterministicalgorithms}, we propose deterministic ways to manage the C-RAN without buffers and thus with a minimal latency compared to stochastic multiplexing.
+The best method also improve the latency of the rest of the traffic.
+\todo{Je sais pas si il faut parler de SDN, qui est un keyword a la mode mais peut etre que l'architecture ngreen nous propose, demander a chiaroni, 
+Yann : je pense qu'il faut parler de SDN, reprendre peut être des choses de notre article précédent sur Cloud RAN}
 
-  \subsection{Network modeling}
-
-The model exposed here has already been studied for another particular topology of network and with different problematics from the ones of this paper.
+\section{Model of C-RAN traffic over an optical ring}
+\label{sec:model}
+% 
+%   \subsection{Network modeling}
+% 
+% The model exposed here has already been studied for another particular topology of network and with different problematics from the ones of this paper.
 One can find in \cite{latency2017} the complexity results on the problem proposed, and some algorithmic solutions to solve it in star networks.
@@
 
- We consider a circular digraph $G = (V,A)$ representing an unidirectional optical ring.
-The vertices of the graph represents the nodes of the ring.
-A {\bf route} $r$ in $G$ is a directed path, that is, a sequence of adjacent vertices.
-We denote by $\omega(u,v)$ the weight of a route, i.e.
-the time taken by a message to go from $u$ to $v$.
+  The unidirectional optical ring is represented by an oriented cycle.
+The vertices of the cycle represents the nodes of the ring, where traffic arrives.
+The edges $(u,v)$ of the cycle have an integer weight $\omega(u,v)$ which represents the time to transmit a unit of information from $u$ to $v$.
+One unit of time corresponds to the
+  The process we study are periodic of period $P$, where
+
+  A {\bf route} $r$ in $G$ is a directed path, that is, a sequence of adjacent vertices. We denote by $\omega(u,v)$ the weight of a route, i.e. the time taken by a message to go from $u$ to $v$.
   In the process we study, a message is sent on each route at each period, denoted by $P$.

### 2018-02-14 Papier NGreen/article.tex
un peu de modèle

@@
 The edges $(u,v)$ of the cycle have an integer weight $\omega(u,v)$ which represents the time to transmit a unit of information from $u$ to $v$.
-One unit of time corresponds to the
-  The process we study are periodic of period $P$, where
+We denote by $RS$ (ringsize) the length of the cycle, that is the sum of $\omega(u,v)$ for all arcs $(u,v)$.
+Each arc $(u,v)$ can be seen as a sequence of $\omega(u,v)$ {\bf containers}, of capacity $Z$, expressed in Bytes.
+The containers are filled  by the nodes with smaller packets called {\bf Packet Data Unit}, or PDU.
+  PDUs waiting in the node $u$ can be put in the first container of the arc $(u,v)$ \emph{if it is free}. 
+  The dynamic of the network is simple: at each unit of time PDUs contained in a container go to the next.
+   The ring follows a {\bf broadcast and select with emission release policy}. When a container is filled by some node $u$,
+   it is freed when it comes back at $u$ after a whole round trip.
 
-  A {\bf route} $r$ in $G$ is a directed path, that is, a sequence of adjacent vertices. We denote by $\omega(u,v)$ the weight of a route, i.e. the time taken by a message to go from $u$ to $v$.
-  In the process we study, a message is sent on each route at each period, denoted by $P$.
-The time is discretized, i.e.
-a period is sliced into $P$ {\bf slots}.
-The ring can be seen as a suit of {\bf containers}, of capacity $Z$, expressed in Bytes that rotates each slots to the following position.
-The containers are filled with some packets created by the nodes, called {\bf Packet Data Unit, or PDU}.
-  The optical ring has a particularity.
-Each node has an access to one container per slot.
-When a node wants to insert a PDU on the ring, the container sawn by the ring must be free.
-Otherwise, the node has to wait until it has an access to a free container to emit its PDU.
-The ring follows a {\bf broadcast and select with emission release} policy.
-A container put on the ring by a node can only be removed by the same node, one lap of the ring later.
+   \subsection{C-RAN trafic}
 
-  This study focuses on the performances of the C-RAN PDUs, thus the route we consider are the routes between the BBUs and the RRHs .We assume that there is a bijection between the RRHs and the BBUs.
- We call forward routes the routes going from the RRHs to the BBUs and Backward routes the routes going from the BBUs to the RRHs.
-The addition of the weight of the two routes of a couple BBU-RRH is then equal to $RS$, the size of the ring, measured in slots.
-We denote by $n$ the number of couples BBU-RRH.
- We only consider one datacenter into the ring. This mean that all the forward routes have the same destination nodes, and all the backward routes have the same source node.
+   We study a C-RAN traffic emitted by each RRH. The data from an antenna arrives into a specific node, then it is routed to 
+   its BBU through the ring. Then after some computation time (which is here supposed to be zero to simplify the model),
+   an answer is sent back from the BBU to the RRH. The same quantity of data is emitted by an antenna at each period $P$. 
+   In our model all BBUs are in the same data-center, thus they are all attached to the same node of the ring. In the following, we will denote by $n$ the number of antennas.
 
-\subsection{Into the node : Two kind of traffics}
+   The antenna are linked to the nodes of the ring through an electronic interface of rate $D$Bps.
+   The ring has a rate of $KD$Bps.
+$K$ is called the {\bf acceleration factor} between the electronic and the optical domains.
+A node aggregates the data received on the electronic interface during a time $Z/D$ to create a PDU, which fills a container in $Z/KD$s.
+In other words, the node transforms the data received during a time $Z/D$, called {\bf macro-slot}, into a PDU that can be sent in a slot.
+Consequently, a single electronic interface can not emit more than one PDU every $k$ slots on the ring.
+
    To refine our model, one must consider the opto-electronic nodes behaviour.
@@
   \end{figure}
+
+%    
+%   The C-RAN PDUs coming from an antenna are sent according to a 
+%   
+%   follows 
+%   This study focuses on the performances of the C-RAN PDUs, thus the route we consider are the routes between the BBUs and the RRHs .We assume that there is a bijection between the RRHs and the BBUs.
+%  We call forward routes the routes going from the RRHs to the BBUs and Backward routes the routes going from the BBUs to the RRHs.
+The addition of the weight of the two routes of a couple BBU-RRH is then equal to $RS$, the size of the ring, measured in slots.
+We denote by $n$ the number of couples BBU-RRH.
+%  We only consider one data center into the ring. This mean that all the forward routes have the same destination nodes, and all the backward routes have the same source node.
+
+\subsection{Into the node : Two kind of traffics}
 

### 2018-02-14 Papier NGreen/article.tex
encore un peu

@@
 
-\todo{ça marque et dans le titre, ça ne devrait pas}
+\todo{ça marque et dans le titre, ça ne devrait pas
+
+Il faut citer l'ANR NGREEN + n'importe quel truc de charoni qui explique leur architecture NGREEN}
 
@@
    The antenna are linked to the nodes of the ring through an electronic interface of rate $D$Bps.
-   The ring has a rate of $KD$Bps.
-$K$ is called the {\bf acceleration factor} between the electronic and the optical domains.
-A node aggregates the data received on the electronic interface during a time $Z/D$ to create a PDU, which fills a container in $Z/KD$s.
-In other words, the node transforms the data received during a time $Z/D$, called {\bf macro-slot}, into a PDU that can be sent in a slot.
-Consequently, a single electronic interface can not emit more than one PDU every $k$ slots on the ring.
-
-   To refine our model, one must consider the opto-electronic nodes behaviour.
-   Each node of the ring is connected to some external networks by at least one electronic interface of rate $D$Bps.
-The ring has a rate of $KD$Bps.
-$K$ is called the {\bf acceleration factor} between the electronic and the optical domains.
-A node is able to aggregate the data received on the electronic interface during $Z/D$s to create a PDU, which fills a container in $Z/KD$s.
-In other words, the node transforms the datas received during a time $Z/D$, called {\bf macro-slot}, into a PDU that can be sent in a slot.
-Consequently, a single electronic interface can not emit more than one PDU every $k$ slots on the ring.
+   The ring has a larger rate of $KD$Bps.
+The integer $K$ is called the {\bf acceleration factor} between the electronic and the optical domains.
+A node aggregates the data received on the electronic interface during $K$ unit of times to create a PDU of size $Z$, that is which can fills one container of the ring.
+As a consequence, we consider that each period, an antenna emits a PDU of size $Z$ each $K$ unit of times during a time $ET$.
 
@@
 
-      \includegraphics[scale=0.3]{slot1.pdf}
-  \includegraphics[scale=0.3]{slot2.pdf}
+      \includegraphics[scale=0.2]{slot1.pdf}
+  \includegraphics[scale=0.2]{slot2.pdf}
      \caption{Opto-electronic interface.}
@@
   \end{figure}
-
-      An node deals with two kinds of traffics.
+  \todo{Améliorer le dessin: un seul schéma avec les notations et horizontal pour pas perdre de place.
+  Éventuellement faire une représentation du ring et en zoom faire l'interface}
+%   
+%       An node deals with two kinds of traffics.
 Some C-RAN and some Best Effort.
@@
 Once the PDUs are created, there join the {\em contention buffer} before being sent in the ring.
-      \begin{figure}[h!]
-\begin{center}   
-  \includegraphics[scale=0.7]{buffers.pdf}
-     \caption{An N-GREEN station.}
-
-\end{center}
-  \end{figure}
+%       \begin{figure}[h!]
+% \begin{center}   
+%   \includegraphics[scale=0.7]{buffers.pdf}
+%      \caption{An N-GREEN station.}
+%      
+% \end{center}
+%   \end{figure}
+%
 
@@
 
-\subsection{Into the node : Two kind of traffics}
+% 
+% 
+% \subsection{Into the node : Two kind of traffics}
+
+\todo{Décrire ici les degrés de liberté -> quand ça part + la latence}
+
+\subsection{Best effort traffic}
+
+\todo{Décrire la génération du best effort}
 
 \paragraph{BE PDU generation model} To Generate the BE PDU, we used the distribution of the time between the generation of two BE PDU given by some numerical analysis work of another study for N-GREEN.
-This distribution was calculated by modelling a gathering buffer.
+This distribution was calculated by modeling a gathering buffer.
 

### 2018-02-19 Papier NGreen/article.tex
abstract

@@
 %opening
-\title{Contention management for Cloud Ran over an optical ring}
+\title{Contention management for Cloud RAN over an optical ring}
 
@@
 \author{Dominique Barth\addressmark{1}
-  \and Dominique Chiaroni?\addressmark{2}
   \and Ma\"el Guiraud \addressmark{1,2}
@@
   \addressmark{2}BNokia Bell Labs France}
-\keywords{N-GREEN, Optical ring, Latency, 5G}
+\keywords{Optical ring, Latency, C-RAN, SDN}
 
@@
 % Nowadays challenge for network providers is to design some network which satisfies in the same time a good Quality of Services and a cheap hardware development.
-This study is a contribution to the N-GREEN project, which has for goal to design a low cost optical ring technology with good performances (dataflow, latency,$\dots$) without using expensive end to end connections.
-In this paper, we study the compatibility of such a technology with the development of the Cloud Ran, a latency critical application which is a major aspect of the 5G deployment.
-We show that the latency of the Cloud Rand can be guaranteed by using a deterministic sending scheme without impacting the others traffics.
+N-GREEN project has for goal to design a low cost optical ring technology with good performances (dataflow, latency,$\dots$) without using expensive end to end connections.
+We study the compatibility of such a technology with the development of the Cloud RAN, a latency critical application which is a major aspect of 5G deployment.
+We show that deterministically managing Cloud RAN traffic minimizes its latency without impacting the latency of others traffics.
 \end{abstract}
@@
 Much of these applications have QoS criteria, like a minimal bandwidth or a maximal latency.
-The N-GREEN project aims to propose an high performing optical ring while ensuring a minimal cost for providers.
+The N-GREEN project aims to propose a high performing optical ring while ensuring a minimal cost for providers.
 The current solutions with good QoS [huawei, demander a dominique C], establishes end to end connection (E2E) between the nodes, which is extremely expensive.
@@
 In this article, we study a Cloud RAN application in the N-GREEN optical ring.
-Cloud RAN is one of the major area of development for 5G, that consists in centralizing the computation units (or {\bf BaseBand Units, BBU}) of the Remote Radio Heads ({\bf RRHs}) in one {\bf datacenter}.
-The latency of the messages between the BBU and the RRH is critical \cite{}.
-Here, we study the latency of some C-RAN equipment connected through an N-GREEN optical ring.\todo{mettre les citations, à reprendre de nos précédents articles}
+Cloud RAN is one of the major area of development for 5G, that consists in centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
+The latency of the messages between the BBU and the RRH is critical.
+\todo{mettre les citations sur la latence dans la 5G, archi ngreen et concurents E2E à reprendre de nos précédents articles}
 
-\todo{Dire un mot sur la forme du traffic cloud RAN, périodique déterministe, aller vers un data center unique, retour, minimisation de la latence ...}
+\todo{Dire un mot sur la forme du traffic cloud RAN, périodique déterministe, aller vers un data center unique, retour, minimisation de la latence ..., + ne pas déranger BE, décrire le pb}
 
 In Sec.~\ref{sec:model}, we model the optical ring and the traffic flow we study.
-In Sec.~\ref{sec:oportmethods}, we study the latency when using stochastic multiplexing to manage the messages arrivals on the ring, with or without priority of the C-RAN traffic.
-Finally, in Sec.~\ref{sec:deterministicalgorithms}, we propose deterministic ways to manage the C-RAN without buffers and thus with a minimal latency compared to stochastic multiplexing.
-The best method also improve the latency of the rest of the traffic.
+In Sec.~\ref{sec:oportmethods}, we study the latency when using stochastic multiplexing to manage packets insertions on the ring, with or without priority for C-RAN packets.
+In Sec.~\ref{sec:deterministicalgorithms}, we propose deterministic ways to manage C-RAN packets without buffers and thus with a minimal latency compared to stochastic multiplexing.
+The best method to do so also improves the latency of best effort packets.
 \todo{Je sais pas si il faut parler de SDN, qui est un keyword a la mode mais peut etre que l'architecture ngreen nous propose, demander a chiaroni, 

### 2018-02-19 Papier NGreen/article.tex
figures et notations C-RAN BE, intro pas revue

@@
 We denote by $RS$ (ringsize) the length of the cycle, that is the sum of $\omega(u,v)$ for all arcs $(u,v)$.
-Each arc $(u,v)$ can be seen as a sequence of $\omega(u,v)$ {\bf containers}, of capacity $Z$, expressed in Bytes.
-The containers are filled  by the nodes with smaller packets called {\bf Packet Data Unit}, or PDU.
-  PDUs waiting in the node $u$ can be put in the first container of the arc $(u,v)$ \emph{if it is free}. 
-  The dynamic of the network is simple: at each unit of time PDUs contained in a container go to the next.
+Each arc $(u,v)$ can be seen as a sequence of $\omega(u,v)$ {\bf containers}, of capacity $C$, expressed in Bytes.
+The containers are filled  by the nodes.
+The node $u$ can put some data in the first container of the arc $(u,v)$ \emph{if it is free}.
+  The dynamic of the network is simple: at each unit of time data contained in a container go to the next.
    The ring follows a {\bf broadcast and select with emission release policy}. When a container is filled by some node $u$,
@@
 
-   We study a C-RAN traffic emitted by each RRH. The data from an antenna arrives into a specific node, then it is routed to 
-   its BBU through the ring. Then after some computation time (which is here supposed to be zero to simplify the model),
-   an answer is sent back from the BBU to the RRH. The same quantity of data is emitted by an antenna at each period $P$. 
+   We study a C-RAN traffic emitted by each RRH.
+The data from an antenna $i$ arrives into a specific node $u$ at time $m_i$, called  {\bf offset}, then it is routed to its BBU at node $v$ through the ring.
+Then after some computation time (which is here supposed to be zero to simplify the model),
+   an answer is sent back from the BBU to the RRH at time $t_i = m_i + \omega(u,v)$, called {\bf BBU-offset}. The same quantity of data is emitted by an antenna at each period $P$. 
    In our model all BBUs are in the same data-center, thus they are all attached to the same node of the ring. In the following, we will denote by $n$ the number of antennas.
+The {\bf latency} of a message is the time it waits into a node before being put in a container.
 
-   The antenna are linked to the nodes of the ring through an electronic interface of rate $D$Bps.
-   The ring has a larger rate of $KD$Bps.
-The integer $K$ is called the {\bf acceleration factor} between the electronic and the optical domains.
-A node aggregates the data received on the electronic interface during $K$ unit of times to create a PDU of size $Z$, that is which can fills one container of the ring.
-As a consequence, we consider that each period, an antenna emits a PDU of size $Z$ each $K$ unit of times during a time $ET$.
+   The antenna are linked to the nodes of the ring through an electronic interface of bit rate $R$Bps.
+   The ring has a larger rate of $FR$Bps.
+The integer $F$ is called the {\bf acceleration factor} between the electronic and the optical domains.
+A node aggregates the data received on the electronic interface during $F$ unit of times to create a PDU of size $C$, that is which can fills one container of the ring.
+As a consequence, we consider that each period, an antenna emits a PDU of size $C$ each $F$ unit of times during a time $ET$.
 
@@
 
-      \includegraphics[scale=0.2]{slot1.pdf}
-  \includegraphics[scale=0.2]{slot2.pdf}
+      \includegraphics[scale=0.8]{interface.pdf}
      \caption{Opto-electronic interface.}
@@
 
-\todo{Décrire la génération du best effort}
-
-\paragraph{BE PDU generation model} To Generate the BE PDU, we used the distribution of the time between the generation of two BE PDU given by some numerical analysis work of another study for N-GREEN.
-This distribution was calculated by modeling a gathering buffer.
-
- \paragraph{C-RAN PDU generation model} An RRH usually emit an huge quantity of information during a long time. Also, as we just see, an RRH can send no more than a PDU every $K$ slots on the ring.
- We denote by $ET$,for {\bf Emission time}, the time during which an RRH emits a PDU every $K$ slots on the ring. An RRH emits $\frac{ET}{K}$ PDUs on the ring, every period $P$.
-
-        \begin{figure}[h!]
-\begin{center}
-
-      \includegraphics[width=\textwidth]{emission_antenna.pdf}
-     \caption{C-RAN PDU generation.}
-\end{center}
-  \end{figure}
-  \paragraph{Back and forth communications} As we explained in the introduction of this section, once the datacenter receives some PDUs from an RRH, it computes an answer and send it to the RRH through the ring.
-To simplify our model, we assume that the computation times is the same for all BBUs and that it is a multiple of the period.
-In this situation, we can assume that, each time the datacenter receives a container with a C-RAN PDU from an RRH, it immediately sends an answer (which is in fact the answer to the two periods ago C-RAN PDU's).
-
-  The time at which an RRH on the route $r_i$ sends its first PDU is called {\bf offset} and can be expressed by $m_{r_i}$.
-The time at which this first PDU arrives to its BBU is the {\bf BBU-offset}, $t(v,r_i) = m_{r_i} + \omega(u,v)$, where $u$ is the RRH and $v$ the BBU of the route $r_i$.
-  We denote by {\bf latency} of a PDU the time sojourn time of a PDU in the contention buffer.
-  We want to ensure a good latency for the C-RAN PDUs.
-If there is no BE PDUs on the ring, the challenge is to fix the offsets (that directly fixes the BBU-offsets) of the routes such that two messages never collides each others.
-Nevertheless, we have ton consider the BE PDUs in our model.
- The rest of this study is divided in two parts.
-In a first time, we look at the behaviour of the ring and the impact of the PDUs latency with two different method of managing the contention buffer.
-Then, we propose some algorithms that solve allows us to choose the offsets for the C-RAN PDUs by reserving the containers, and we compare the impact of those different algorithms on the BE PDUs latency.
+The traffic on the ring is also composed of a best effort traffic, corresponding to the internet flow.
+We model the arrival of best effort messages by a temporal law that gives the distribution of the arrival between two arrivals of containers with best effort message in a node.
+This distribution is obtained by studying the impact of the fill rate and the maximum time to wait before sending a container on a contention buffer.
+This contention buffer is filled by some batch arrivals of data, and creates the containers.
+[ref].
 

### 2018-02-19 Papier NGreen/article.tex
intro et model

@@
 % Nowadays challenge for network providers is to design some network which satisfies in the same time a good Quality of Services and a cheap hardware development.
-N-GREEN project has for goal to design a low cost optical ring technology with good performances (dataflow, latency,$\dots$) without using expensive end to end connections.
+N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency $\dots$) without using expensive end to end connections.
 We study the compatibility of such a technology with the development of the Cloud RAN, a latency critical application which is a major aspect of 5G deployment.
@@
 Network providers have to design inexpensive networks while the amount of data and online applications significantly increases.
-Much of these applications have QoS criteria, like a minimal bandwidth or a maximal latency.
-The N-GREEN project aims to propose a high performing optical ring while ensuring a minimal cost for providers.
+Much of these applications have QoS criteria, like a minimal throughput or a maximal latency.
+The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers.
 The current solutions with good QoS [huawei, demander a dominique C], establishes end to end connection (E2E) between the nodes, which is extremely expensive.
@@
 
-In this article, we study a Cloud RAN application in the N-GREEN optical ring.
-Cloud RAN is one of the major area of development for 5G, that consists in centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
+In this article, we study a Cloud RAN (C-RAN) application in the N-GREEN optical ring.
+C-RAN is one of the major area of development for 5G, that consists in centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
 The latency of the messages between the BBU and the RRH is critical.
-\todo{mettre les citations sur la latence dans la 5G, archi ngreen et concurents E2E à reprendre de nos précédents articles}
+\todo{mettre les citations sur la latence dans la 5G, archi ngreen et concurents E2E à reprendre de nos précédents articles} The aim of the article is to propose simple methods
+to deterministically manage the periodic C-RAN traffic.
+In a previous work~\cite{dominique2018deterministic}, the authors have studied this problem for a star shaped network.
+Here the load due to the CRAN traffic is small which makes the problem easier.
+However, we add several new difficulties: the messages from RRHs are fragmented, there are other traffics which must not be to impacted and the broadcast and select policy of the ring makes reservation of a specific time for emission somewhat wasteful.
 
-\todo{Dire un mot sur la forme du traffic cloud RAN, périodique déterministe, aller vers un data center unique, retour, minimisation de la latence ..., + ne pas déranger BE, décrire le pb}
-
-In Sec.~\ref{sec:model}, we model the optical ring and the traffic flow we study.
+In Sec.~\ref{sec:model}, we model the optical ring and the traffic flow.
 In Sec.~\ref{sec:oportmethods}, we study the latency when using stochastic multiplexing to manage packets insertions on the ring, with or without priority for C-RAN packets.
@@
 
-  \subsection{N-GREEN Optical ring}
+  \paragraph{N-GREEN Optical ring}
 
@@
 The containers are filled by the nodes.
-The node $u$ can put some data in the first container of the arc $(u,v)$ \emph{if it is free}.
+The node $u$ can put some data in the first container of the arc $(u,v)$ \emph{only if it is free}.
   The dynamic of the network is simple: at each unit of time data contained in a container go to the next.
@@
 
-   \subsection{C-RAN trafic}
+   \paragraph{C-RAN traffic}
 
-   We study a C-RAN traffic emitted by each RRH.
-The data from an antenna $i$ arrives into a specific node $u$ at time $m_i$, called  {\bf offset}, then it is routed to its BBU at node $v$ through the ring.
-Then after some computation time (which is here supposed to be zero to simplify the model),
-   an answer is sent back from the BBU to the RRH at time $t_i = m_i + \omega(u,v)$, called {\bf BBU-offset}. The same quantity of data is emitted by an antenna at each period $P$. 
-   In our model all BBUs are in the same data-center, thus they are all attached to the same node of the ring. In the following, we will denote by $n$ the number of antennas.
-The {\bf latency} of a message is the time it waits into a node before being put in a container.
+   There are $n$ RRHs attached to the ring, the RRH $i$ being attached to the vertex $u_i$ (several antennas can be attached to the same vertex).
+The antenna are linked to the nodes of the ring through an electronic interface of bit rate $R$ Bps.
+   The ring has a larger rate of $F\times R$ Bps.
+The integer $F$ is called the {\bf acceleration factor} between the electronic and the optical domains.
+A node aggregates the data received on the electronic interface during $F$ unit of times to create a packet of size $C$ which completely fills one container of the ring.
+An RRH emits a C-RAN traffic during a time $ET$ (emission time) in each period $P$, which consists in a packet of size $C$ each $F$ unit of times.
 
-   The antenna are linked to the nodes of the ring through an electronic interface of bit rate $R$Bps.
-   The ring has a larger rate of $FR$Bps.
-The integer $F$ is called the {\bf acceleration factor} between the electronic and the optical domains.
-A node aggregates the data received on the electronic interface during $F$ unit of times to create a PDU of size $C$, that is which can fills one container of the ring.
-As a consequence, we consider that each period, an antenna emits a PDU of size $C$ each $F$ unit of times during a time $ET$.
+   The data of the RRH $i$ arrives at node $u_i$ at a time $m_i$ called the {\bf offset}. The offset can be determined 
+   by the designer of the system and can be different for each RRH but must remain the same over all periods. We assume that all 
+   BBUs are contained in the same data-center attached to the node $v$.
+The data from $u_i$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u,v)$ if it has been inserted in the ring upon arrival.
+Then after some computation time (which is supposed to be zero to simplify the model), an answer is sent back from the BBU to the RRH.
+The same quantity of data is emitted by each BBU or RRH during any period.
+   The {\bf latency} of a message is the time it waits in a node before being put in a free container on the ring.
+   The aim of our study is to minimize the latency of the C-RAN traffic, both from the RRHs and the BBUs. 
+   In fact in Sec.\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency. 
+   The only downside is that other data used the optical ring and that their latency may be increased. We shortly describe the
+   nature of this additional traffic in the next subsection.
 
@@
 
-\subsection{Best effort traffic}
+\paragraph{Best effort traffic}
 
-The traffic on the ring is also composed of a best effort traffic, corresponding to the internet flow.
-We model the arrival of best effort messages by a temporal law that gives the distribution of the arrival between two arrivals of containers with best effort message in a node.
-This distribution is obtained by studying the impact of the fill rate and the maximum time to wait before sending a container on a contention buffer.
-This contention buffer is filled by some batch arrivals of data, and creates the containers.
-[ref].
+The optical ring supports other traffics, corresponding to the internet flow.
+We call this traffic \textbf{Best Effort} (BE), since it is less critical and one can increase the latency of BE messages to improve the latency of C-RAN messages.
+A contention buffer is filled by a batch arrival process of BE data.
+Then according to some parameters (fill rate and maximum wait time) a container is sent on the ring from the contention buffer.
+The arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a container of BE messages in a node.
+This distribution is obtained by choosing optimal parameters for the contention buffer~\cite{}.
 
-  \subsection{Parameters of the study}
-  \label{sec:parameters} The experiment of this subsections are made following the same parameters, until sec~\ref{sec:optialgo}.
+% 
+% 
+%   \subsection{Parameters of the study}
+%   \label{sec:parameters} The experiment of this subsections are made following the same parameters, until sec~\ref{sec:optialgo}.
 We set $K = 10$ chanels, some electronic interface of rate $D=10$Gbps and $Z = 12500$B so, $Z/KD = 1\mu$s.
@@
 With those parameters, the network is theoretically loaded to $67.5\%$.
-
+%   
   \begin{figure}

### 2018-02-20 Papier NGreen/article.tex
partie 4 a revoir, refs

@@
 \usepackage{mathtools, bm}
+\usepackage{caption}
 \usepackage{amssymb, bm}
@@
 \usepackage{amsmath}
+
+\captionsetup{justification=centering,margin=0.5cm}
 
@@
 
-In this article, we study a Cloud RAN (C-RAN) application in the N-GREEN optical ring.
+In this article, we study a Cloud RAN (C-RAN) application in the N-GREEN optical ring~\cite{ngreenarchitecture}.
 C-RAN is one of the major area of development for 5G, that consists in centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
-The latency of the messages between the BBU and the RRH is critical.
+The latency of the messages between the BBU and the RRH is critical~\cite{bouguen2012lte,3gpp5g}.
 \todo{mettre les citations sur la latence dans la 5G, archi ngreen et concurents E2E à reprendre de nos précédents articles} The aim of the article is to propose simple methods
@@
 The node $u$ can put some data in the first container of the arc $(u,v)$ \emph{only if it is free}.
-  The dynamic of the network is simple: at each unit of time data contained in a container go to the next.
+  The dynamic of the network is simple: at each unit of time, data contained in a container go to the next.
    The ring follows a {\bf broadcast and select with emission release policy}. When a container is filled by some node $u$,
    it is freed when it comes back at $u$ after a whole round trip.
+   \todo{on ne parle pas assez de la periode je trouve}
 
@@
 
-   The data of the RRH $i$ arrives at node $u_i$ at a time $m_i$ called the {\bf offset}. The offset can be determined 
+   The data of the RRH $i$ arrives at node $u$ at a time $m_i$ called the {\bf offset}. The offset can be determined 
    by the designer of the system and can be different for each RRH but must remain the same over all periods. We assume that all 
    BBUs are contained in the same data-center attached to the node $v$.
-The data from $u_i$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u,v)$ if it has been inserted in the ring upon arrival.
+The data from $u$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u,v)$ if it has been inserted in the ring upon arrival.
 Then after some computation time (which is supposed to be zero to simplify the model), an answer is sent back from the BBU to the RRH.
@@
 %
-  \begin{figure}
+
+   \section{Performance evaluation of the N-GREEN optical ring}
+   \label{sec:oportmethods}
+  One first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: when a node wants to send some data, it uses the first free container available on the ring.
+If a node can not send a container, because there is no free slots or several containers must be send at the same time, the containers surplus are buffered in an insertion buffer.
+  Two different method to manage this insertion buffer are proposed here.
+The FIFO rule is compared to another method that uses two insertion buffers: one for the containers with BE, and another for the containers with C-RAN.
+If there is a free container on the ring, the node wants to empty the insertion buffer with C-RAN containers first.
+  Fig~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule or the C-RAN first rule.
+On this experiment, the offsets of the RRH are randomly drawn in the period.
+The parameters of the ring are given by fig~\ref{fig:params}.
+Those results are computed over $100$ instances of optical rings that have ran during $10,000,000$ unit of time.
+
+    \begin{minipage}[b]{0.50\linewidth}
+
+        \begin{center}
+      \includegraphics[scale=0.3]{opport.pdf}
+
+      \captionof{figure}{Performances of FIFO compared to C-RAN first.}    \label{fig:resultopport}
+      \end{center} 
+  \end{minipage}
+\hfill
+  \begin{minipage}[b]{0.40\linewidth}
+  \vspace{-2cm}
+  \scalebox{0.7}
+  {
   \centering
@@
   \hline
- Number of channels $K$ & $10$  \tabularnewline
+ Acceleration factor $F$ & $10$  \tabularnewline
   \hline
-  Rate of an electronic interface $D$ & $10$ Gbps \tabularnewline
+  Bit rate of an electronic interface $R$ & $10$ Gbps \tabularnewline
   \hline
-  Container size  $Z$ & $12,500$ B  \tabularnewline
+  Container size  $C$ & $12,500$ B  \tabularnewline
   \hline
-  Slot duration $Z/KD$ & $1\mu$s \tabularnewline
+  Slot duration $C/F\times R$ & $1\mu$ s \tabularnewline
   \hline
-  Optical ring rate $KD$ & $100$ Gbps \tabularnewline
+  Optical ring bit rate $F\times R$ & $100$ Gbps \tabularnewline
   \hline
-  Length of the ring $RS$ & $100$ slots \tabularnewline
+  Length of the ring $RS$ & $100$ \tabularnewline
   \hline
-  BE SDU size & $125$B \tabularnewline
+  Emission time $ET$ & $500$ \tabularnewline
   \hline
-  C-RAN PDU size & $12,500$B$=Z$ \tabularnewline
-  \hline
-  Emission time $ET$ & $500$ slots \tabularnewline
-  \hline
-   Period $P$ & $1,000$ slots \tabularnewline
+   Period $P$ & $1,000$ \tabularnewline
   \hline
@@
   \hline
+  \end{tabular}
+  }
+  \vspace{1cm}
+  \captionof{figure}{Parameters experiments, based on N-GREEN.}\label{fig:params}
 
-  \end{tabular}
-  \caption{Parameters of the following experiments based on N-GREEN}\label{parameters}
-  \end{figure}
+  \end{minipage}
 
-   \section{Performance evaluation of the N-GREEN optical ring}
-   \label{sec:oportmethods}
-   In a first time, we will look at the performance of the N-GREEN optical ring with an opportunistic insertion policy.
-When a node wants to send a PDU on the ring, it uses the first available container .
-    We study the performance of the ring through two methods; a full opportunistic method, and a method that prioritize the C-RAN PDUs.
-Since we only consider some PDUs arrivals, those two methods are some variants of the management of the PDUs in the node.
-   For those two methods, the offsets $m_r$ of the routes are chosen randomly in the period, i.e. we do not choose the first time at which the RRH start to emit.
+Unsurprisingly, the latency of the C-RAN traffic is better when we prioritize the C-RAN messages, while the BE traffic is penalized.
+Nevertheless, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s.
 
-    \subsection{Full opportunistic method}
-    \label{sec:fullopport}
-    We first want to look at a simple configuration in which we do not manage the PUDs (BE or C-RAN) arriving into a node.
+%    
+%    
+%    \subsection{Full opportunistic method}
+%    \label{sec:fullopport}
+%    We first want to look at a simple configuration in which we do not manage the PUDs (BE or C-RAN) arriving into a node.
 At their arrival, the BE and C-RAN PDUS are buffered in the contention buffer, and this buffer is emptied following the FIFO rule.
-
-The following experiment shows us the performance this {\bf full opportunistic method} with some parameters issued from N-GREEN. 
-On fig~\ref{fig:oport}, one can see the cumulative distribution of the latency of the C-RAN and BE PDUs.
-Those results are computed on $100$ instances of optical rings that have run during $10,000,000$ slots.
+%
+%The following experiment shows us the performance this {\bf full opportunistic method} with some parameters issued from N-GREEN. 
+%On fig~\ref{fig:oport}, one can see the cumulative distribution of the latency of the C-RAN and BE PDUs.
 The measures are taken after $3,000$ slots of simulation, to let the ring initialize it's behavior.
 The parameters of the simulations are stated in sec~\ref{sec:parameters}.
-
-    \begin{figure}[h!]
-    \label{fig:oport}
-        \begin{center}
-      \includegraphics[scale=0.4]{oport}
-
-      \caption{Full opportunistic method performances.}
-      \end{center}
-  \end{figure}
-
-  As we can see on fig~\ref{fig:oport}, the latency for the different kind of PDU is notably similar because we do not manage anything.
+%
+%
+%    \begin{figure}[h!]
+%    \label{fig:oport}
+%        \begin{center}
+%      \includegraphics[scale=0.4]{oport}
+%
+%      \caption{Full opportunistic method performances.}
+%      \end{center}
+%  \end{figure}
+%  
+%  As we can see on fig~\ref{fig:oport}, the latency for the different kind of PDU is notably similar because we do not manage anything.
 Furthermore, we can remark that about $10\%$ of the C-RAN messages wait over $100\mu$s, that is already critical for C-RAN \todo{ref}.
-
-\subsection{C-RAN priority method}
-\label{sec:cranprio}
-  In order to improve the C-RAN PDUs latency, we imagined the following solution, called {\bf C-RAN priority method}.
+%
+%\subsection{C-RAN priority method}
+%\label{sec:cranprio}
+%  In order to improve the C-RAN PDUs latency, we imagined the following solution, called {\bf C-RAN priority method}.
 Each nodes have two contention buffers.
@@
 its available container is free, the container is filled with the C-RAN PDUs first.
-
-    \begin{figure}[h]
-\begin{center}   
-      \includegraphics[scale=0.7]{cranprio.pdf}
-     \caption{C-RAN priority method.}
-\end{center}
-  \end{figure}
-
-  With this method, one can imagine improve the latency of the C-RAN PDUs.
+%  
+%    \begin{figure}[h]
+%\begin{center}   
+%      \includegraphics[scale=0.7]{cranprio.pdf}
+%     \caption{C-RAN priority method.}
+%\end{center}
+%  \end{figure}
+%  
+%  With this method, one can imagine improve the latency of the C-RAN PDUs.
 Fig~\ref{fig:prior} shows us the performance of the C-RAN priority algorithm for different kinds of traffics.
 The parameters of the simulations still the same, stated in sec~\ref{sec:parameters}.
-      \begin{figure}[h]
-      \label{fig:prior}
-\begin{center}
+%      \begin{figure}[h]
+%      \label{fig:prior}
+%\begin{center}   
+%
+%      \includegraphics[scale=0.4]{prior.pdf}
+%
+%     \caption{C-RAN priority method performances.}
+%\end{center}
+%  \end{figure}
+%  
+%  As expected, the latency of the C-RAN PDUs is decreased compared to the full opportunistic method.
+Nevertheless, there is still $10\%$ of the C-RAN PDUs that have more than $50 \mu$s of latency, and the best effort PDUs are penalized, indeed, close to $10\%$ of the BE PDUs awaits more than $150\mu$s before being sent in the ring, versus close to $0\%$ with the previous method..
+%  Thus, we propose a deterministic approach in which we set the offsets of the RRH and we reserve the containers needed for the C-RAN PDUs.
+%   \todo{il manque une partie sur le travail de karim, }
 
-      \includegraphics[scale=0.4]{prior.pdf}
-
-     \caption{C-RAN priority method performances.}
-\end{center}
-  \end{figure}
-
-  As expected, the latency of the C-RAN PDUs is decreased compared to the full opportunistic method.
-Nevertheless, there is still $10\%$ of the C-RAN PDUs that have more than $50 \mu$s of latency, and the best effort PDUs are penalized, indeed, close to $10\%$ of the BE PDUs awaits more than $150\mu$s before being sent in the ring, versus close to $0\%$ with the previous method..
-  Thus, we propose a deterministic approach in which we set the offsets of the RRH and we reserve the containers needed for the C-RAN PDUs.
-   \todo{il manque une partie sur le travail de karim, }
   \section{Deterministic approach for $0$ latency on C-RAN}
@@
 
- In this section We present three algorithms that allows the C-RAN PDUs to have $0$ latency in the insertion buffers by establishing a static reservation of the slots in the period.
- Those algorithm are {\bf Centralized} and requires a global supervisor of the network to be implemented .\todo{phrase + ref sdn?}
+Some studies have already been made in order to set the offsets of C-RAN traffic for a different topology~\cite{dominique2018deterministic}.
+It appears that this problem is not hard in the N-GREEN optical ring.
+Therefore, one must try to set the offsets for C-RAN traffic such that the BE-traffic latency be not impacted too much.
 
-\paragraph{Slot reservation} To decrease the C-RAN messages latency, one plan to reserve the container for the nodes.
+In order to ensure $0$ latency for C-RAN, the container needed to send a C-RAN message of the RRH $i$ must be free at time $m_i$.
+Consequently the node reserve the written access this container at time $m_i - RS$.
+Thus, during the last round trip of the container before $m_i$, the others nodes can only free the reserved containers.
+
+Since the computation time of the BBU is supposed to be zero (or a multiple of the period), setting the offsets $m_i$ for all RRH $i$ also sets the time $m_i + \omega(u,v)$, called {\bf BBU offset}.
+Because all the BBU are located in the same datacenter, setting the BBU-offsets without coliisions directly avoid the collision between the C-RAN.
+A {\bf macro slot} is a sequence of $F$ slots.
+A RRH can emit at most once every macro slot but requires two free containers (one for the uplink message, and one for the downlink one) to ensure zero latency.
+A {\bf pair} is a sequence of two consecutive slots in the macro slot, the messages of two RRH assigned to different pair can not collide.
+
+\begin{prop}
+ If several RRH shares a pair, it is possible to set the BBU-offsets such that there is no collisions between the messages if $P \ge n\times ET + RS$.
+ \end{prop}
+ \begin{proof}
+ The objective is to show that proposition by induction.
+ The model is simplified in order to study the behavior of one pair, thus, both of the RRH emits some containers every slots, during $ET$ slots in the period $P$.
+ {\bf Base case:} 
+ Consider $ET =  \frac{P}{2}$ and two RRH each connected to the nodes $A$ and $B$.
+ We assume that $A$ starts to emit a time $1$ during $ET$ slots.
+The containers of $A$ arrive in $B$ during the interval $[\omega(A,B);\omega(A,B)+ET[$.
+Then, $B$ can immediately emits its containers at time $\omega(A,B)+ET$.
+Those containers from $B$ arrives at $A$ at during  $ [\omega(A,B)+ET + \omega(B,A) ;ET + RS + ET] = [ET+RS; RS + P] = [ET + RS; RS] \mod P$.
+When $A$ tries to emit in the next period, there is a collision at the interval $[1;RS]$ in the period between the two traffics from $A$ and $B$.
+Thus, for $n = 2$, it is possible to assign two RRH on the same pair if $P = 2\times ET + RS$.
+
+ {\bf Induction step:}  \todo{A ecrire sans dessins}
+ \end{proof}
+
+For the purpose of decreasing the BE traffic latency, it is interesting to regularly ensure some free pairs for the BE messages.
+To this end, the pairs must be filled with as much RRH as possible.
+Then, the free pairs are uniformly apportioned into the macro slot.
+Nevertheless, this is not always enough to ensure a good BE traffic latency.
+Indeed, with the previous parameters, with $ET = \frac{P}{2}$, $F = 10$ and $n = 5$, a pair is given to each antenna, and if all the RRH starts to emit in the same macro slots, a long sequence of reserved container will highly impact the latency of the BE traffic.
+The solution to this issue is to uniformly distribute the BBU-offset of the first RRH of a pair on the period.
+In this situation, the number of free pairs in a macro slot is balanced on the period, that allows a more regular BE traffic.
+
+   \begin{figure}[h]
+\centering
+      \includegraphics[scale=0.4]{optim.pdf}
+     \caption{Balancing algorithm performance on the N-GREEN optical ring.}   \label{fig:optimres}
+  \end{figure}
+
+%% In this section We present three algorithms that allows the C-RAN PDUs to have $0$ latency in the insertion buffers by establishing a static reservation of the slots in the period.
+%% Those algorithm are {\bf Centralized} and requires a global supervisor of the network to be implemented .\todo{phrase + ref sdn?}
+%% 
+%%\paragraph{Slot reservation} To decrease the C-RAN messages latency, one plan to reserve the container for the nodes.
 Indeed, if a node $i$ needs to send a PDU at time $t$, a container needs to be reserved since the previous lap of the container, i.e.
@@
 It is equivalent to increase the load of the network, without increasing the number of PDUs carried by the network.
-
-\paragraph{RRHs synchronisations}
-This slot reservation implies that the RRHs are synchronized with the ring.
+%%
+%%\paragraph{RRHs synchronisations}
+%%This slot reservation implies that the RRHs are synchronized with the ring.
 The following proposed algorithms set a sequence of reserved slots for each RRH in each period.
@@
 One must ensure that the C-RAN PDU arrives in the contention buffer of the node just before the reserved container.
+%%
 
-Unlike the previous methods with opportunistic insertion policy, we now want to choose a the offsets for the routes.
+%Unlike the previous methods with opportunistic insertion policy, we now want to choose a the offsets for the routes.
 Since all the forward routes have the same last vertex $v$ (the datacenter), which is also the first vertex of all the backward routes, we choose to manage the collision in this vertex only.
@@
 Once the BBU-offsets are set, for all routes $i$, it is easy to compute $m_{r_i} = t(v,r_i) - \omega(u,v)$.
-
-\subsection{N-GREEN parameters adapted algorithms}
-An RRH can not emit a message more often than once slot every $K$ slots.
+%
+%
+%\subsection{N-GREEN parameters adapted algorithms}
+%An RRH can not emit a message more often than once slot every $K$ slots.
 Remember that {\bf macro slot} is a duration of $K$ slots, during which each RRH can emit at most once.
@@
 As a reminder, $n$ is the number of couple BBU-RRH.
-
- Because there is at most as much couples BBU-RRH as bunches, we want to assign one RRH to one bunch.
-We propose the following {\bf naive reservation algorithm}.
+%
+% 
+% Because there is at most as much couples BBU-RRH as bunches, we want to assign one RRH to one bunch.
+%We propose the following {\bf naive reservation algorithm}.
 For each RRH $i, i\in \{0,...,n-1\} $, set $t(v,r_i)= 2\times i$ with $v$ the vertex of the BBUs.
@@
 This is the reason why we do not care about the backward routes anymore, and we only deal with the BBU-offsets of the forward routes..
-   \begin{figure}[h]
-\centering
-      \includegraphics[scale=0.7]{freqgrouped.pdf}
-     \caption{Grouped assignment of the bunches to the RRH.}   \label{fig:freqG}
-  \end{figure}
-
-We kept the same parameters than in the two previous experiments (see~\ref{sec:parameters}) and we made an experiment to show the impact of this algorithm on the BE traffic.
+%   \begin{figure}[h]
+%\centering
+%      \includegraphics[scale=0.7]{freqgrouped.pdf}
+%     \caption{Grouped assignment of the bunches to the RRH.}   \label{fig:freqG}
+%  \end{figure}
+%
+%
+%We kept the same parameters than in the two previous experiments (see~\ref{sec:parameters}) and we made an experiment to show the impact of this algorithm on the BE traffic.
 Fig~\ref{fig:res1} shows us the distribution of latency for BE PDUs with this algorithm.
-
-      \begin{figure}[h]
-\centering
-      \includegraphics[scale=0.4]{res1.pdf}
-     \caption{Impact of the naive reservation algorithm on the Best effort PDUs.}   \label{fig:res1}
-  \end{figure}
-
-As we can see, the BE traffic is highly penalized by this algorithm, indeed, while almost $100\%$ of the BE PDUs have a latency to less than $200 \mu$s with the full opportunistic method (see fig~\ref{fig:oport}), here, more than half of the BE PDUs are be buffered more than $200\mu s$.
+%
+%      \begin{figure}[h]
+%\centering
+%      \includegraphics[scale=0.4]{res1.pdf}
+%     \caption{Impact of the naive reservation algorithm on the Best effort PDUs.}   \label{fig:res1}
+%  \end{figure}
+%
+%As we can see, the BE traffic is highly penalized by this algorithm, indeed, while almost $100\%$ of the BE PDUs have a latency to less than $200 \mu$s with the full opportunistic method (see fig~\ref{fig:oport}), here, more than half of the BE PDUs are be buffered more than $200\mu s$.
 Those performances are explained by the structure of the algorithm.
@@
 It creates a long sequence of slots during which there is no free containers in the ring.
-
-To improve the BE PDUs latnecy, we propose a {\bf splited reservation algorithm} that balances the load of the CRAN traffic over the period.
+%
+%To improve the BE PDUs latnecy, we propose a {\bf splited reservation algorithm} that balances the load of the CRAN traffic over the period.
 Instead of giving some close BBU-offsets for all routes $i$, with $v$ the datacenter, we now uniformly distribute the different BBU-offsets in the period.
@@
 Also, if $2 \times n < K$, the RRH are balanced over the bunches by the same way, we try to give a bunch to a RRH each $\frac{K}{2\times n}$ buches.
-
-   \begin{figure}[!h]
-\centering
-      \includegraphics[scale=0.7]{freqsplited.pdf}
-     \caption{Splited assignment of the bunches to the RRH.}   \label{fig:freqS}
-  \end{figure}
-
-  On fig~\ref{fig:res2} one can observe the performance of this algorithm on the BE PDUs latency. Once again, to have a reference point, we take the same parameters for the simulation.
-
- \begin{figure}[h]
-\centering
-      \includegraphics[scale=0.4]{res2.pdf}
-     \caption{Impact of the splited reservation algorithm on the Best effort.}   \label{fig:res2}
-  \end{figure}
-
-  As we can see, thelatency of the BE PDUs is highly better with this this algorithm.
+%
+%   \begin{figure}[!h]
+%\centering
+%      \includegraphics[scale=0.7]{freqsplited.pdf}
+%     \caption{Splited assignment of the bunches to the RRH.}   \label{fig:freqS}
+%  \end{figure}
+%  
+%  On fig~\ref{fig:res2} one can observe the performance of this algorithm on the BE PDUs latency. Once again, to have a reference point, we take the same parameters for the simulation. 
+%
+% \begin{figure}[h]
+%\centering
+%      \includegraphics[scale=0.4]{res2.pdf}
+%     \caption{Impact of the splited reservation algorithm on the Best effort.}   \label{fig:res2}
+%  \end{figure}
+%  
+%  As we can see, thelatency of the BE PDUs is highly better with this this algorithm.
 Indeed almost $100\%$ of CRAN PDUs have a latency of less than $50\mu$s which is better than the full opportunistic method.
 Thus, we decreased the latency of every kind of traffic.
-
-\subsection{With more antennas}
-\label{sec:optialgo}
- In this section, we study the case $n > \frac{K}{2}$, we want to assign more than one RRH to a bunch. 
- Let us consider a particular behavior of the ring.
+%
+%\subsection{With more antennas}
+%\label{sec:optialgo}
+% In this section, we study the case $n > \frac{K}{2}$, we want to assign more than one RRH to a bunch. 
+% Let us consider a particular behavior of the ring.
 Instinctively, we can think that if we have enough space in the period for many traffics on the same frequency that is, $ET \le \frac{P}{2}$, we can assign several couples BBU-RRH to the same bunch.
-
- Let us take $ET =  \frac{P}{2}$ and $n = \frac{K}{2} + 1$.
+%
+% Let us take $ET =  \frac{P}{2}$ and $n = \frac{K}{2} + 1$.
 We assign a bunch to each $\frac{K}{2}$ first RRH and we have only one RRH left.
 Then, we only look at one bunch, on which we want to add the new couple BBU-RRH.
-
- We take a ring with two nodes $A$ and $B$.
+% 
+% We take a ring with two nodes $A$ and $B$.
 We simplify the model to only look at the behaviour of one bunch, thus, both of the nodes alternatively emits some containers every slots, during $ET$ slots in the period $P$.
@@
 Since $[t(A,r_A)]_{P,K} = [1;ET]$, there is a collision at the interval $[1;RS]$ in the period between the two traffics from $A$ and $B$.
-  \begin{figure}[h]
-\centering
-      \includegraphics[scale=0.7]{rs.pdf}
-     \caption{Collision between two routes on the same bunch when the period is too small.}   \label{fig:proofrs}
-  \end{figure}
-
- As we have just noted, if several RRH share the same bunch, the period must have an additional budget in addition to the time needed to send the messages.
+%  \begin{figure}[h]
+%\centering
+%      \includegraphics[scale=0.7]{rs.pdf}
+%     \caption{Collision between two routes on the same bunch when the period is too small.}   \label{fig:proofrs}
+%  \end{figure}
+%
+% 
+% 
+% As we have just noted, if several RRH share the same bunch, the period must have an additional budget in addition to the time needed to send the messages.
 Let us study the size of the additional budget.
- \begin{prop}
- If several RRH shares a bunch, it is possible set the offsets of the routes such that there is no collisions between the messages if $P \ge n\times ET + RS$ , with $n$ the number of RRHs.
- \end{prop}
- \begin{proof}
- We seek to show that proposition by induction.
-
- {\bf Base case:} For $n = 2$, the proof of the previous example shows us that it is possible to assign two RRH on the same bunch with $P = 2\times ET + RS$.
-
- {\bf Induction step:}  We consider that we have a bunch shared by $n$ RRH, with a period of size $P= n\times ET + RS$.
+% \begin{prop}
+% If several RRH shares a bunch, it is possible set the offsets of the routes such that there is no collisions between the messages if $P \ge n\times ET + RS$ , with $n$ the number of RRHs.
+% \end{prop}
+% \begin{proof}
+% We seek to show that proposition by induction.
+% 
+% {\bf Base case:} For $n = 2$, the proof of the previous example shows us that it is possible to assign two RRH on the same bunch with $P = 2\times ET + RS$.
+% 
+% {\bf Induction step:}  We consider that we have a bunch shared by $n$ RRH, with a period of size $P= n\times ET + RS$.
 We want to show that if we want to add one RRH to the bunch, we need a period of size at least $P = (n+1)\times ET + RS$.
@@
 For instance, if we take two nodes $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted of $\omega(A,B)$.
-
-   \begin{figure}[h]
-\centering
-      \includegraphics[scale=0.7]{period1.pdf}
-     \caption{An example of sequence with n = 3.}   \label{fig:proofperiod1}
-  \end{figure}
-
- Thus, if we add $ET$ slots in this bunch, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence.
-
-   \begin{figure}[h]
-\centering
-      \includegraphics[scale=0.7]{period2.pdf}
-     \caption{The same sequence with n = 4.}   \label{fig:proofperiod2}
-  \end{figure}
-  Note that a station can send some traffic from more than one RRH, the figures ~\ref{fig:proofperiod1} and \~ref{fig:proofperiod2} are just an example, but this proof stays the same.
- \end{proof}
-
-Considering those results, we propose an algorithm to allow several RRH to share the same bunch, as long as $P \ge n\times ET + RS$. 
-Since we need $RS$ slots on a each bunch with at least an RRH to assign another RRH to this latter, it is interesting to fill as far as possible the bunches.
+% 
+%   \begin{figure}[h]
+%\centering
+%      \includegraphics[scale=0.7]{period1.pdf}
+%     \caption{An example of sequence with n = 3.}   \label{fig:proofperiod1}
+%  \end{figure}
+%   
+% Thus, if we add $ET$ slots in this bunch, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence.
+% 
+%   \begin{figure}[h]
+%\centering
+%      \includegraphics[scale=0.7]{period2.pdf}
+%     \caption{The same sequence with n = 4.}   \label{fig:proofperiod2}
+%  \end{figure}
+%  Note that a station can send some traffic from more than one RRH, the figures ~\ref{fig:proofperiod1} and \~ref{fig:proofperiod2} are just an example, but this proof stays the same.
+% \end{proof}
+% 
+%Considering those results, we propose an algorithm to allow several RRH to share the same bunch, as long as $P \ge n\times ET + RS$. 
+%Since we need $RS$ slots on a each bunch with at least an RRH to assign another RRH to this latter, it is interesting to fill as far as possible the bunches.
 We then compute the number of bunches needed to carry the number of RRH $n$.
@@
 it avoids to group the used bunches together.
-The used bunches have $RS$ or more free slots in the period.
+%The used bunches have $RS$ or more free slots in the period.
 Thus, the algorithm subsequently balance BBU-offsets of the first RRH of each bunch, with the same idea than the splited algorithm.
 We call this algorithm the {\bf full repartition algorithm}.
-
-   \begin{figure}[h]
-\centering
-      \includegraphics[scale=0.7]{optimalgo.pdf}
-     \caption{Organization of the bunches with the balancing algorithm.}   \label{fig:optimalgo}
-  \end{figure}
-
-  We want to observe the impact of this algorithm on BE traffic.
+%
+%   \begin{figure}[h]
+%\centering
+%      \includegraphics[scale=0.7]{optimalgo.pdf}
+%     \caption{Organization of the bunches with the balancing algorithm.}   \label{fig:optimalgo}
+%  \end{figure}
+%  
+%  We want to observe the impact of this algorithm on BE traffic.
 Since our previous parameters did not allow several RRH to share a bunch, we now set $ET = 200$, that correspond to a C-RAN flow of $2$Gbps.
@@
 The others parameters are all the one described in the sec~\ref{sec:parameters}.
-  The following experiment shows us the impact of the balancing algorithm on the BE traffics.
+%  The following experiment shows us the impact of the balancing algorithm on the BE traffics.
 We chose to compare those results to a simulation with the same parameters but with the full opportunistic method of sec~\ref{sec:fullopport}.
-
-   \begin{figure}[h]
-\centering
-      \includegraphics[scale=0.4]{optim.pdf}
-     \caption{Balancing algorithm performance on the N-GREEN optical ring.}   \label{fig:optimres}
-  \end{figure}
-
-  As fig~\ref{fig:optimres} shows, the full repartition algorithm ensures a lower latencye to BE PDUs than the full opportunistic method, which gave the best result for the BE traffic.
+%  
+%   \begin{figure}[h]
+%\centering
+%      \includegraphics[scale=0.4]{optim.pdf}
+%     \caption{Balancing algorithm performance on the N-GREEN optical ring.}   \label{fig:optimres}
+%  \end{figure}
+%  
+%  As fig~\ref{fig:optimres} shows, the full repartition algorithm ensures a lower latencye to BE PDUs than the full opportunistic method, which gave the best result for the BE traffic.
 Indeed, since we remove the random aspect of the C-RAN PDUs generation, we balanced the load over the period an then increased the BE performances while we totally removed the C-RAN PDUs latency.

### 2018-02-20 Papier NGreen/article.tex
petites typos

@@
 \usepackage{graphicx,graphics} 
-\usepackage{hyperref} 
 \usepackage{mathtools, bm}
@@
 \usepackage{amsmath}
+\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
 
@@
 \newtheorem{prop}{Proposition}
+\renewcommand{\thefootnote}{\*}
 
@@
 \address{\addressmark{1}David Laboratory, UVSQ \\
-  \addressmark{2}BNokia Bell Labs France}
+  \addressmark{2}Nokia Bell Labs France}
 \keywords{Optical ring, Latency, C-RAN, SDN}
@@
 \section{Introduction}
+ \footnote{ This work was developed around the ANR N-GREEN project. The authors thanks all the Nokia Bell Labs team for their collaboration.}
 
@@
 If there is a free container on the ring, the node wants to empty the insertion buffer with C-RAN containers first.
-  Fig~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule or the C-RAN first rule.
+  Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule or the C-RAN first rule.
 On this experiment, the offsets of the RRH are randomly drawn in the period.
-The parameters of the ring are given by fig~\ref{fig:params}.
+The parameters of the ring are given by Fig.~\ref{fig:params}.
 Those results are computed over $100$ instances of optical rings that have ran during $10,000,000$ unit of time.

### 2018-02-20 Papier NGreen/article.tex
figure et partie 4 reprise

@@
 The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers.
-The current solutions with good QoS [huawei, demander a dominique C], establishes end to end connection (E2E) between the nodes, which is extremely expensive.
+The current solutions with good QoS~\cite{pizzinat2015things}, establishes end to end connection (E2E) between the nodes, which is extremely expensive.
 The N-GREEN optical ring is designed to ensure good performances and the hardware it requires scales linearly with the number of nodes while E2E scales quadratically making it impractical for more than a few nodes.
@@
   One first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: when a node wants to send some data, it uses the first free container available on the ring.
-If a node can not send a container, because there is no free slots or several containers must be send at the same time, the containers surplus are buffered in an insertion buffer.
+If a node can not send a container, because there is no free slots or several containers must be sent at the same time, the containers surplus are buffered in an insertion buffer.
   Two different method to manage this insertion buffer are proposed here.
 The FIFO rule is compared to another method that uses two insertion buffers: one for the containers with BE, and another for the containers with C-RAN.
-If there is a free container on the ring, the node wants to empty the insertion buffer with C-RAN containers first.
-  Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule or the C-RAN first rule.
+If there is a free container on the ring, the node wants to empty the C-RAN insertion buffer first.
+  Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule and the "C-RAN first" rule.
 On this experiment, the offsets of the RRH are randomly drawn in the period.
@@
 
-In order to ensure $0$ latency for C-RAN, the container needed to send a C-RAN message of the RRH $i$ must be free at time $m_i$.
+In order to ensure $0$ latency for C-RAN, the container needed to send a C-RAN message from the RRH $i$ must be free at time $m_i$.
 Consequently the node reserve the written access this container at time $m_i - RS$.
@@
  \begin{proof}
- The objective is to show that proposition by induction.
- The model is simplified in order to study the behavior of one pair, thus, both of the RRH emits some containers every slots, during $ET$ slots in the period $P$.
+One show that proposition by induction.
+ In this proof, the model is simplified in order to study the behavior of one pair, thus, both of the RRH emit some containers every slots, during $ET$ slots in the period $P$.
  {\bf Base case:} 
- Consider $ET =  \frac{P}{2}$ and two RRH each connected to the nodes $A$ and $B$.
+ Consider $P =  2.ET+RS$ and two RRH each connected to the nodes $A$ and $B$.
  We assume that $A$ starts to emit a time $1$ during $ET$ slots.
@@
 Then, $B$ can immediately emits its containers at time $\omega(A,B)+ET$.
-Those containers from $B$ arrives at $A$ at during  $ [\omega(A,B)+ET + \omega(B,A) ;ET + RS + ET] = [ET+RS; RS + P] = [ET + RS; RS] \mod P$.
-When $A$ tries to emit in the next period, there is a collision at the interval $[1;RS]$ in the period between the two traffics from $A$ and $B$.
+Those containers from $B$ arrives at $A$ at during  $ [\omega(A,B)+ET + \omega(B,A) ;\omega(A,B)+ET + \omega(B,A) + ET ] = [ET+RS;2.ET+RS] = [ET + RS; P]$.
+Then, $A$ can emit in the next period, without collisions.
 Thus, for $n = 2$, it is possible to assign two RRH on the same pair if $P = 2\times ET + RS$.
 
- {\bf Induction step:}  \todo{A ecrire sans dessins}
+ {\bf Induction step:}  A ring can support $n$ RRH with a period of size $P= n\times ET + RS$.
+One must show that if there is one more RRH on the ring, the period must be at least $P = (n+1)\times ET + RS$.
+
+Take a sequence of container of size $P$ on a ring with $n$ RRH.
+One can observe that this sequence is the same at every nodes, shifted of the length of the routes between the nodes.
+For instance, with two nodes $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted by $\omega(A,B)$.
+In addition if the sequence is increased by $ET$ free containers, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence to carry the traffic of a new RRH.
+Thus a period $P = (n+1)\times ET + RS$ is enough to carry the traffic of $n+1$ RRH.
  \end{proof}

### 2018-02-20 Papier NGreen/article.tex
figures et partie 4

@@
   }
-  \vspace{1cm}
+  \vspace{0.75cm}
   \captionof{figure}{Parameters experiments, based on N-GREEN.}\label{fig:params}
@@
 In this situation, the number of free pairs in a macro slot is balanced on the period, that allows a more regular BE traffic.
-
+Fig.~\ref{fig:optimres} is a compariason between the cumulative distribution of the BE traffic latency with the FIFO rule or with the reservation algorithm proposed here.
+Since the previous parameters were too restrictive to put several RRH on the same pair, the parameters $ET$, and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
    \begin{figure}[h]
 \centering
-      \includegraphics[scale=0.4]{optim.pdf}
-     \caption{Balancing algorithm performance on the N-GREEN optical ring.}   \label{fig:optimres}
+      \includegraphics[scale=0.3]{optim.pdf}
+     \caption{Impact of the reservation of the traffics.}   \label{fig:optimres}
   \end{figure}
+  The performances are excellent, since the C-RAN traffic have $0$ latency and the BE traffic have a better latency with reservation than with the FIFO rule.
+Indeed, our algorithm balanced the load of the C-RAN traffic over the period , that helps the BE traffic to not aggregate and create additional latency.
 

### 2018-02-20 Papier NGreen/article.tex
petites corrections et merge

--- 2018-02-20 Papier NGreen/article.tex
@@
 % Nowadays challenge for network providers is to design some network which satisfies in the same time a good Quality of Services and a cheap hardware development.
-N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency $\dots$) without using expensive end to end connections.
+N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency$\dots$) without using expensive end to end connections.
 We study the compatibility of such a technology with the development of the Cloud RAN, a latency critical application which is a major aspect of 5G deployment.
@@
 
-\todo{ça marque et dans le titre, ça ne devrait pas
-
-Il faut citer l'ANR NGREEN + n'importe quel truc de charoni qui explique leur architecture NGREEN}
-
 \section{Introduction}
- \footnote{ This work was developed around the ANR N-GREEN project. The authors thanks all the Nokia Bell Labs team for their collaboration.}
+ \footnote{ This work was developed around the ANR N-GREEN project. The authors thank the Nokia Bell Labs team for their collaboration.}
 
@@
 
-In this article, we study a Cloud RAN (C-RAN) application in the N-GREEN optical ring~\cite{ngreenarchitecture}.
+In this article, we study a Cloud RAN (C-RAN) application in the N-GREEN optical ring described in~\cite{ngreenarchitecture}.
 C-RAN is one of the major area of development for 5G, that consists in centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
 The latency of the messages between the BBU and the RRH is critical~\cite{bouguen2012lte,3gpp5g}.
-\todo{mettre les citations sur la latence dans la 5G, archi ngreen et concurents E2E à reprendre de nos précédents articles} The aim of the article is to propose simple methods
+The aim of the article is to propose a simple yet efficient method
 to deterministically manage the periodic C-RAN traffic.
@@
 The edges $(u,v)$ of the cycle have an integer weight $\omega(u,v)$ which represents the time to transmit a unit of information from $u$ to $v$.
-We denote by $RS$ (ringsize) the length of the cycle, that is the sum of $\omega(u,v)$ for all arcs $(u,v)$.
+By extension, if $u$ and $v$ are not adjacent, we denote by $\omega(u,v)$ the size of the directed path from $u$ to $v$.
+We denote by $RS$ (ringsize) the length of the cycle, that is $\omega(u,u)$.
 Each arc $(u,v)$ can be seen as a sequence of $\omega(u,v)$ {\bf containers}, of capacity $C$, expressed in Bytes.
@@
    it is freed when it comes back at $u$ after a whole round trip.
-   \todo{on ne parle pas assez de la periode je trouve}
+%    \todo{on ne parle pas assez de la periode je trouve}
 
@@
    There are $n$ RRHs attached to the ring, the RRH $i$ being attached to the vertex $u_i$ (several antennas can be attached to the same vertex).
-The antenna are linked to the nodes of the ring through an electronic interface of bit rate $R$ Bps.
+An RRH is linked to a node of the ring through an electronic interface of bit rate $R$ Bps.
    The ring has a larger rate of $F\times R$ Bps.
@@
 
-   The data of the RRH $i$ arrives at node $u$ at a time $m_i$ called the {\bf offset}. The offset can be determined 
+   The data of the RRH $i$ arrives at node $u_i$ at a time $m_i$ called its {\bf offset}. The offsets can be determined 
    by the designer of the system and can be different for each RRH but must remain the same over all periods. We assume that all 
    BBUs are contained in the same data-center attached to the node $v$.
-The data from $u$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u,v)$ if it has been inserted in the ring upon arrival.
+The data from $u_i$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u_i,v)$ if it has been inserted in the ring upon arrival.
 Then after some computation time (which is supposed to be zero to simplify the model), an answer is sent back from the BBU to the RRH.
@@
    In fact in Sec.\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency. 
-   The only downside is that other data used the optical ring and that their latency may be increased. We shortly describe the
+   The only downside is that other data use the optical ring and their latency may be increased. We shortly describe the
    nature of this additional traffic in the next subsection.
@@
 % \subsection{Into the node : Two kind of traffics}
-
-\todo{Décrire ici les degrés de liberté -> quand ça part + la latence}
 

### 2018-02-20 Papier NGreen/article.tex
partie jusqu'à 3 relue

@@
 \author{Dominique Barth\addressmark{1}
-  \and Ma\"el Guiraud \addressmark{1,2}
-   \and Yann Strozecki \addressmark{1}
+  \and Ma\"el Guiraud\addressmark{1}
+   \and Yann Strozecki\addressmark{1}
   }
 
-\address{\addressmark{1}David Laboratory, UVSQ \\
-  \addressmark{2}Nokia Bell Labs France}
+\address{\addressmark{1}David Laboratory, UVSQ}
+% \\
+%   \addressmark{2}Nokia Bell Labs France}
 \keywords{Optical ring, Latency, C-RAN, SDN}
@@
 The latency of the messages between the BBU and the RRH is critical~\cite{bouguen2012lte,3gpp5g}.
-The aim of the article is to propose a simple yet efficient method
-to deterministically manage the periodic C-RAN traffic.
+In this article we propose a SDN approach to deterministically manage the periodic C-RAN traffic by chosing emmission timing and reserving containers on the ring.
 In a previous work~\cite{dominique2018deterministic}, the authors have studied this problem for a star shaped network.
 Here the load due to the CRAN traffic is small which makes the problem easier.
-However, we add several new difficulties: the messages from RRHs are fragmented, there are other traffics which must not be to impacted and the broadcast and select policy of the ring makes reservation of a specific time for emission somewhat wasteful.
+However, we add several new difficulties: the messages from RRHs are fragmented, there are other traffics which must not be impacted and the broadcast and select policy of the ring makes reservation of a specific time for emission somewhat wasteful.
 
@@
 The best method to do so also improves the latency of best effort packets.
-\todo{Je sais pas si il faut parler de SDN, qui est un keyword a la mode mais peut etre que l'architecture ngreen nous propose, demander a chiaroni, 
-Yann : je pense qu'il faut parler de SDN, reprendre peut être des choses de notre article précédent sur Cloud RAN}
 
@@
 
+   The RRH are the source of the \emph{deterministic and periodic} C-RAN traffic.
    There are $n$ RRHs attached to the ring, the RRH $i$ being attached to the vertex $u_i$ (several antennas can be attached to the same vertex).
@@
 A node aggregates the data received on the electronic interface during $F$ unit of times to create a packet of size $C$ which completely fills one container of the ring.
-An RRH emits a C-RAN traffic during a time $ET$ (emission time) in each period $P$, which consists in a packet of size $C$ each $F$ unit of times.
+Each period $P$, an RRH emits a C-RAN traffic
+   during a time $ET$ (emission time), which consists in a packet of size $C$ each $F$ unit of times.
 
@@
 The data from $u_i$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u_i,v)$ if it has been inserted in the ring upon arrival.
-Then after some computation time (which is supposed to be zero to simplify the model), an answer is sent back from the BBU to the RRH.
+Then after some computation time (which is supposed to be zero to simplify the presentation), an answer is sent back from the BBU to the RRH.
 The same quantity of data is emitted by each BBU or RRH during any period.
@@
    The aim of our study is to minimize the latency of the C-RAN traffic, both from the RRHs and the BBUs. 
-   In fact in Sec.\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency. 
+   In Sec.\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency. 
    The only downside is that other data use the optical ring and their latency may be increased. We shortly describe the
@@
   \end{figure}
-  \todo{Améliorer le dessin: un seul schéma avec les notations et horizontal pour pas perdre de place.
-  Éventuellement faire une représentation du ring et en zoom faire l'interface}
-%   
+
 %       An node deals with two kinds of traffics.
@@
    \label{sec:oportmethods}
+
   One first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: when a node wants to send some data, it uses the first free container available on the ring.
-If a node can not send a container, because there is no free slots or several containers must be sent at the same time, the containers surplus are buffered in an insertion buffer.
-  Two different method to manage this insertion buffer are proposed here.
-The FIFO rule is compared to another method that uses two insertion buffers: one for the containers with BE, and another for the containers with C-RAN.
-If there is a free container on the ring, the node wants to empty the C-RAN insertion buffer first.
+  If a node cannot send a container, because there is no free slot or because several containers must be sent at the same time, the remaining containers are stored in an insertion buffer.
+Two different methods to manage this insertion buffer are experimentally compared.
+The FIFO rule is compared to another method that uses two insertion buffers: one for the containers with BE data, and another for the containers with C-RAN data.
+If there is a free container on the ring, the node empties the C-RAN insertion buffer first.
 Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule and the "C-RAN first" rule.
-On this experiment, the offsets of the RRH are randomly drawn in the period.
-The parameters of the ring are given by Fig.~\ref{fig:params}.
-Those results are computed over $100$ instances of optical rings that have ran during $10,000,000$ unit of time.
+On this experiment, the offsets of the RRH are not fixed but randomly drawn in the period.
+The experimental parameters are given by Fig.~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
+The results are computed over $100$ instances of optical rings that are simulated during $10,000,000$ unit of time.
 
@@
 
-      \captionof{figure}{Performances of FIFO compared to C-RAN first.}    \label{fig:resultopport}
+      \captionof{figure}{Performances of FIFO and C-RAN first.}    \label{fig:resultopport}
       \end{center} 
@@
   \vspace{0.75cm}
-  \captionof{figure}{Parameters experiments, based on N-GREEN.}\label{fig:params}
+  \captionof{figure}{Parameters experiments from the N-GREEN architecture}\label{fig:params}
 
@@
 Unsurprisingly, the latency of the C-RAN traffic is better when we prioritize the C-RAN messages, while the BE traffic is penalized.
-Nevertheless, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s.
+Nevertheless, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s, a problem we address in the next section.
 

### 2018-02-21 Papier NGreen/article.tex
text avec figures

@@
 \section{Introduction}
- \footnote{ This work was developed around the ANR N-GREEN project. The authors thank the Nokia Bell Labs team for their collaboration.}
 
-Network providers have to design inexpensive networks while the amount of data and online applications significantly increases.
+Network\footnote{ This work was developed around the ANR N-GREEN project.
+The authors thank the Nokia Bell Labs team for their collaboration.} providers have to design inexpensive networks while the amount of data and online applications significantly increases.
 Much of these applications have QoS criteria, like a minimal throughput or a maximal latency.
@@
   \hline
+   Load induced by C-RAN & $50\%$  \tabularnewline
+  \hline
   \end{tabular}
   }
-  \vspace{0.75cm}
+  \vspace{0.55cm}
   \captionof{figure}{Parameters experiments from the N-GREEN architecture}\label{fig:params}
@@
 
-For the purpose of decreasing the BE traffic latency, it is interesting to regularly ensure some free pairs for the BE messages.
-To this end, the pairs must be filled with as much RRH as possible.
-Then, the free pairs are uniformly apportioned into the macro slot.
-Nevertheless, this is not always enough to ensure a good BE traffic latency.
-Indeed, with the previous parameters, with $ET = \frac{P}{2}$, $F = 10$ and $n = 5$, a pair is given to each antenna, and if all the RRH starts to emit in the same macro slots, a long sequence of reserved container will highly impact the latency of the BE traffic.
-The solution to this issue is to uniformly distribute the BBU-offset of the first RRH of a pair on the period.
-In this situation, the number of free pairs in a macro slot is balanced on the period, that allows a more regular BE traffic.
-Fig.~\ref{fig:optimres} is a compariason between the cumulative distribution of the BE traffic latency with the FIFO rule or with the reservation algorithm proposed here.
+For the purpose of decreasing the BE traffic latency, it is interesting to regularly ensure some free containers for the BE messages.
+The first idea, illustrated by Fig.~\ref{fig:repart1} is to uniformly apportion the first BBU-offset of each pair in order to balance the load of the C-RAN traffic over the period.
+The reservation of the containers for the C-RAN traffic increases the load incurred for the BE traffic, since it does not allow the nodes to use some empty containers to send some BE messages.
+Thus the pairs must be filled with as much RRH as possible..
+Then, the free pairs are uniformly apportioned into the macro slot, as illustrated in Fig.~\ref{fig:repart2}.
+Fig.~\ref{fig:optimres} is a comparison between the cumulative distribution of the BE traffic latency with the FIFO rule or with the reservation algorithm proposed here.
 Since the previous parameters were too restrictive to put several RRH on the same pair, the parameters $ET$, and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
-   \begin{figure}[h]
+
+  \begin{minipage}[b]{0.4\linewidth}
 \centering
-      \includegraphics[scale=0.3]{optim.pdf}
-     \caption{Impact of the reservation of the traffics.}   \label{fig:optimres}
-  \end{figure}
+      \includegraphics[scale=0.25]{optim.pdf}
+     \captionof{figure}{Impact of the reservation of the traffics.}   \label{fig:optimres}
+  \end{minipage} 
+    \begin{minipage}[b]{0.30\linewidth}
+        \begin{center}
+      \includegraphics[scale=0.55]{repart1}
+      \vspace{1cm}
+      \captionof{figure}{Repartition in the period}    \label{fig:repart1}
+      \end{center} 
+  \end{minipage}
+    \begin{minipage}[b]{0.3\linewidth}
+        \begin{center}
+      \includegraphics[scale=0.55]{repart2}
+            \vspace{0.5cm}
+      \captionof{figure}{Repartition in the macro slot.}    \label{fig:repart2}
+      \end{center} 
+  \end{minipage}
+
   The performances are excellent, since the C-RAN traffic have $0$ latency and the BE traffic have a better latency with reservation than with the FIFO rule.

### 2018-02-21 Papier NGreen/article.tex
réécriture partie 4

--- 2018-02-20 Papier NGreen/article.tex
@@
 \begin{abstract}
-
 % Nowadays challenge for network providers is to design some network which satisfies in the same time a good Quality of Services and a cheap hardware development.
@@
 
-   \section{Performance evaluation of the N-GREEN optical ring}
+   \section{Evaluation of the latency on the N-GREEN optical ring}
    \label{sec:oportmethods}
@@
 
-  \section{Deterministic approach for $0$ latency on C-RAN}
-\label{sec:deterministicalgorithms}
+\section{Deterministic approach for zero lantency} \label{sec:deterministicalgorithms}
 
-Some studies have already been made in order to set the offsets of C-RAN traffic for a different topology~\cite{dominique2018deterministic}.
-It appears that this problem is not hard in the N-GREEN optical ring.
-Therefore, one must try to set the offsets for C-RAN traffic such that the BE-traffic latency be not impacted too much.
+The complexity of finding good offsets for the C-RAN traffic for a different topology has been investigated in~\cite{dominique2018deterministic} without best effort traffic.
+This problem is easy in the N-GREEN optical ring (see the solution in this section).
+However, we must adapt our method to minimize the latency of the BE traffic.
 
-In order to ensure $0$ latency for C-RAN, the container needed to send a C-RAN message from the RRH $i$ must be free at time $m_i$.
-Consequently the node reserve the written access this container at time $m_i - RS$.
-Thus, during the last round trip of the container before $m_i$, the others nodes can only free the reserved containers.
+In order to ensure zero latency for the C-RAN traffic, the container needed to send a C-RAN message from the RRH $i$ must be free at time $m_i$.
+Hence the node $u_i$ \textbf{reserves} the container at time $m_i - RS$.
+A container which is reserved cannot be filled by any node except the one which has reserved it.
+We assume that the message sent by the RRH $i$ arrives at its BBU at time $m_i + \omega(u,v)$ and the answer is sent from the BBU at time $m_i + \omega(u,v) +1$ (with no waiting time).
 
-Since the computation time of the BBU is supposed to be zero (or a multiple of the period), setting the offsets $m_i$ for all RRH $i$ also sets the time $m_i + \omega(u,v)$, called {\bf BBU offset}.
-Because all the BBU are located in the same datacenter, setting the BBU-offsets without coliisions directly avoid the collision between the C-RAN.
+Recall that an RRH emits a packet every $F$ containers, during a time $ET$. 
+Thus if we divide the period $P$ into \textbf{slots} of $F$ containers, an RRH needs one container by slot.
+Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position in the slot during all the period.
+If an RRH emits at time $m_i < P$, then we say it has \textbf{position} $m_i \mod F$.
+If an RRH is at position $i$, then by construction, the corresponding $BBU$ is at position $i+1 \mod F$.
+
+The problem we solve now is to find an \textbf{assignment} of values of the $m_i$ which is \textbf{valid}: no two RRH reserve the same container in a period.
+Moreover we want to preserve the latency of the BE traffic.
+It means that the time to wait for a
+free container at any moment of the period and in any node of the ring must be minimized. 
+Remark that two RRHs which are not at the same position do not use the same container. Moreover, without loss of generality, 
+if we can fix the offsets of the RRHs to even positions so that they do not reserve the same containers, then it will fix the offsets of the BBUs to odd positions which do not reserve the same containers.
+
+% 
+% Since the computation time of the BBU is supposed to be zero (or a multiple of the period), setting the offsets $m_i$ for all RRH $i$ also sets the time $m_i + \omega(u,v)$, called {\bf BBU offset}.
+Because all the BBU are located in the same datacenter, setting the BBU-offsets without collisions directly avoid the collision between the C-RAN.
 A {\bf macro slot} is a sequence of $F$ slots.
@@
 \begin{prop}
- If several RRH shares a pair, it is possible to set the BBU-offsets such that there is no collisions between the messages if $P \ge n\times ET + RS$.
+There is an assignation for the offsets $m_1, \dots, m_k$ on the same position if  $k\times ET + RS \leq P$.
 \end{prop}
 \begin{proof}
-One show that proposition by induction.
- In this proof, the model is simplified in order to study the behavior of one pair, thus, both of the RRH emit some containers every slots, during $ET$ slots in the period $P$.
- {\bf Base case:} 
- Consider $P =  2.ET+RS$ and two RRH each connected to the nodes $A$ and $B$.
- We assume that $A$ starts to emit a time $1$ during $ET$ slots.
+ First assume w.l.o.g. that the position of the offsets is zero. Then we fix $m_1 = 0$. We also assume that the 
+ nodes $u_1,\dots,u_n$ are in the order of the ring.
+The last message emitted by $1$ arrives at $u_2$ at time $ET - 1 + \omega(u_1,u_2)$.
+Therefore we can fix $m_2 =  ET  + \omega(u_1,u_2)$.
+In general we can set $m_i = (i-1) \times ET + \omega(u_1,u_i)$ and all RRHs will use different containers at position $0$.
+The assignation is correct, if the second period
+ RRH $1$ must emit something, a container is at position $0$ is free. It implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.
+\end{proof}
+
+Remark that for each position which is used by some RRH, we lose $2RS$ because of the reservation of the RRH and of its BBU.
+Therefore to not waste bandwith, it is relevant to put as many RRH as possible on the same positions.
+Moreover unused position in an assignment are useful to guarantee a good latency to BE traffic.
+The unused positions can be chosen uniformly over a slot, to minimize the time to wait before a free slot, as in Fig.~\ref{}.
+
+However, for some parameters, there is no unused position. In particular, with the current parameters of the N-GREEN ring,
+$ET = \frac{P}{2}$, $F = 10$ and $n = 5$.
+Hence there is a BBU or an RRH at each position.
+If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for $BE$-traffic.
+To mitigate this problem, the free containers of each position must be uniformly distributed over the period as in Fig.~\ref{}.
+
+We present the cumulative of the latency of the BE traffic latency using the FIFO rule or the reservation algorithm proposed here in
+Fig.~\ref{fig:optimres}.
+Since the previous parameters were too restrictive to put several RRH on the same pair, the parameters $ET$, and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
+% 
+% \begin{prop}
+%  If several RRH shares a pair, it is possible to set the BBU-offsets such that there is no collisions between the messages if $P \ge n\times ET + RS$.
+%  \end{prop}
+% %  \begin{proof}
+% One show that proposition by induction.
+%  In this proof, the model is simplified in order to study the behavior of one pair, thus, both of the RRH emit some containers every slots, during $ET$ slots in the period $P$.
+%  {\bf Base case:} 
+%  Consider $P =  2.ET+RS$ and two RRH each connected to the nodes $A$ and $B$.
+%  We assume that $A$ starts to emit a time $1$ during $ET$ slots.
 The containers of $A$ arrive in $B$ during the interval $[\omega(A,B);\omega(A,B)+ET[$.
@@
 Then, $A$ can emit in the next period, without collisions.
-Thus, for $n = 2$, it is possible to assign two RRH on the same pair if $P = 2\times ET + RS$.
-
- {\bf Induction step:}  A ring can support $n$ RRH with a period of size $P= n\times ET + RS$.
+% Thus, for $n = 2$, it is possible to assign two RRH on the same pair if $P = 2\times ET + RS$.
+%  
+%  {\bf Induction step:}  A ring can support $n$ RRH with a period of size $P= n\times ET + RS$.
 One must show that if there is one more RRH on the ring, the period must be at least $P = (n+1)\times ET + RS$.
-
-Take a sequence of container of size $P$ on a ring with $n$ RRH.
+%  
+% Take a sequence of container of size $P$ on a ring with $n$ RRH.
 One can observe that this sequence is the same at every nodes, shifted of the length of the routes between the nodes.
 For instance, with two nodes $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted by $\omega(A,B)$.
-In addition if the sequence is increased by $ET$ free containers, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence to carry the traffic of a new RRH.
+% In addition if the sequence is increased by $ET$ free containers, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence to carry the traffic of a new RRH.
 Thus a period $P = (n+1)\times ET + RS$ is enough to carry the traffic of $n+1$ RRH.
- \end{proof}
-
-For the purpose of decreasing the BE traffic latency, it is interesting to regularly ensure some free pairs for the BE messages.
+% %  \end{proof}
+% 
+% For the purpose of decreasing the BE traffic latency, it is interesting to regularly ensure some free pairs for the BE messages.
 To this end, the pairs must be filled with as much RRH as possible.
@@
   \end{figure}
-  The performances are excellent, since the C-RAN traffic have $0$ latency and the BE traffic have a better latency with reservation than with the FIFO rule.
-Indeed, our algorithm balanced the load of the C-RAN traffic over the period , that helps the BE traffic to not aggregate and create additional latency.
+
+  The performance of the reservation algorithm is excellent, since the C-RAN traffic have $0$ latency and the BE traffic have a better latency with reservation than with the FIFO rule.
+It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth to the BE traffic.
 

### 2018-02-21 Papier NGreen/article.tex

@@
 
-      \captionof{figure}{Performances of FIFO and C-RAN first.}    \label{fig:resultopport}
+      \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}
       \end{center} 
@@
   \hline
+   Load induced by C-RAN & $50\%$  \tabularnewline
+  \hline
   \end{tabular}
   }
-  \vspace{0.75cm}
-  \captionof{figure}{Parameters experiments from the N-GREEN architecture}\label{fig:params}
+  \vspace{0.55cm}
+  \captionof{figure}{Experimental parameters from the N-GREEN architecture}\label{fig:params}
 
@@
 Remark that for each position which is used by some RRH, we lose $2RS$ because of the reservation of the RRH and of its BBU.
-Therefore to not waste bandwith, it is relevant to put as many RRH as possible on the same positions.
+Therefore to not waste bandwidth, it is relevant to put as many RRH as possible on the same positions.
 Moreover unused position in an assignment are useful to guarantee a good latency to BE traffic.
-The unused positions can be chosen uniformly over a slot, to minimize the time to wait before a free slot, as in Fig.~\ref{}.
+The unused positions can be chosen uniformly over a slot, to minimize the time to wait before a free slot, as in Fig.~\ref{fig:repart1}.
 
-However, for some parameters, there is no unused position. In particular, with the current parameters of the N-GREEN ring,
+However, it is possible that there are no unused position. It happens with the current parameters of the N-GREEN ring,
 $ET = \frac{P}{2}$, $F = 10$ and $n = 5$.
-Hence there is a BBU or an RRH at each position.
+Hence there is exactly one  BBU or RRH at each position.
 If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for $BE$-traffic.
-To mitigate this problem, the free containers of each position must be uniformly distributed over the period as in Fig.~\ref{}.
+To mitigate this problem, the free containers of each position must be uniformly distributed over the period as in Fig.~\ref{fig:repart2}.
 
@@
 Since the previous parameters were too restrictive to put several RRH on the same pair, the parameters $ET$, and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
-   \begin{figure}[h]
+
+  \begin{minipage}[b]{0.4\linewidth}
 \centering
-      \includegraphics[scale=0.3]{optim.pdf}
-     \caption{Impact of the reservation of the traffics.}   \label{fig:optimres}
-  \end{figure}
+      \includegraphics[scale=0.25]{optim.pdf}
+     \captionof{figure}{Impact of the reservation of the traffics.}   \label{fig:optimres}
+  \end{minipage} 
+     \begin{minipage}[b]{0.3\linewidth}
+        \begin{center}
+      \includegraphics[scale=0.55]{repart2}
+            \vspace{0.5cm}
+      \captionof{figure}{Repartition in the slot}    \label{fig:repart1}
+      \end{center} 
+  \end{minipage}
+    \begin{minipage}[b]{0.30\linewidth}
+        \begin{center}
+      \includegraphics[scale=0.55]{repart1}
+      \vspace{1cm}
+      \captionof{figure}{Repartition in the period}    \label{fig:repart2}
+      \end{center} 
+  \end{minipage}
 
-  The performance of the reservation algorithm is excellent, since the C-RAN traffic have $0$ latency and the BE traffic have a better latency with reservation than with the FIFO rule.
-It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth to the BE traffic.
+  The performances are excellent, since the C-RAN traffic have $0$ latency and the BE traffic have a better latency with reservation than with the FIFO rule.
+Indeed, our algorithm balanced the load of the C-RAN traffic over the period , that helps the BE traffic to not aggregate and create additional latency.
 

### 2018-02-22 Papier NGreen/article.tex
figures

@@
 
-Network\footnote{ This work was developed around the ANR N-GREEN project.
+Network\footnote{This work was developed around the ANR N-GREEN project.
 The authors thank the Nokia Bell Labs team for their collaboration.} providers have to design inexpensive networks while the amount of data and online applications significantly increases.
@@
 On this experiment, the offsets of the RRH are not fixed but randomly drawn in the period.
-The experimental parameters are given by Fig.~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
+The experimental\footnote{The source code in C of the experiments can be found on the author's webpage~\cite{webpage}.} parameters are given by Fig.~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
 The results are computed over $100$ instances of optical rings that are simulated during $10,000,000$ unit of time.
@@
   \hline
-   Load induced by C-RAN & $50\%$  \tabularnewline
+   Load induced by C-RAN traffic & $50\%$  \tabularnewline
+  \hline
+    Load induced by BE traffic & $40\%$  \tabularnewline
   \hline
@@
   }
-  \vspace{0.55cm}
+  \vspace{0.3cm}
   \captionof{figure}{Experimental parameters from the N-GREEN architecture}\label{fig:params}

### 2018-02-22 Papier NGreen/article.tex
version finale

@@
 \usepackage[english]{babel}
-
 \usepackage{xspace}
@@
 \usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
-
 \captionsetup{justification=centering,margin=0.5cm}
-
 \newcommand\pall{\textsc{pall}\xspace}
-
 \newcommand{\todo}[1]{{\color{red} TODO: {#1}}}	
@@
 \graphicspath{{img/}}
-
-%opening
 \title{Contention management for Cloud RAN over an optical ring}
-
-%\author[1]{Dominique Barth}
-%\author[2]{Dominique Chiaroni ?}
-%\author[1]{Ma\"el Guiraud}
-%\author[1]{Yann Strozecki}
-%\affil[1]{David Laboratory, UVSQ}
-%\affil[2]{Nokia Bell Labs France}
-
 \author{Dominique Barth\addressmark{1}
@@
 \address{\addressmark{1}David Laboratory, UVSQ}
-% \\
-%   \addressmark{2}Nokia Bell Labs France}
+
 \keywords{Optical ring, Latency, C-RAN, SDN}
@@
 \begin{abstract}
-% Nowadays challenge for network providers is to design some network which satisfies in the same time a good Quality of Services and a cheap hardware development.
 N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency$\dots$) without using expensive end to end connections.
@@
 Network\footnote{This work was developed around the ANR N-GREEN project.
-The authors thank the Nokia Bell Labs team for their collaboration.} providers have to design inexpensive networks while the amount of data and online applications significantly increases.
+The authors thank the Nokia Bell Labs team for their collaboration.} providers have to design inexpensive networks supporting an increasing the amount of data and online applications.
 Much of these applications have QoS criteria, like a minimal throughput or a maximal latency.
 The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers.
-The current solutions with good QoS~\cite{pizzinat2015things}, establishes end to end connection (E2E) between the nodes, which is extremely expensive.
-The N-GREEN optical ring is designed to ensure good performances and the hardware it requires scales linearly with the number of nodes while E2E scales quadratically making it impractical for more than a few nodes.
+The current solutions with good QoS~\cite{pizzinat2015things}, establishe end to end connection (E2E) between the nodes, which is extremely expensive.
+The N-GREEN optical ring is designed to ensure good performances: the hardware it requires scales linearly with the number of nodes while E2E scales quadratically making it impractical for more than a few nodes.
 
 In this article, we study a Cloud RAN (C-RAN) application in the N-GREEN optical ring described in~\cite{ngreenarchitecture}.
-C-RAN is one of the major area of development for 5G, that consists in centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
-The latency of the messages between the BBU and the RRH is critical~\cite{bouguen2012lte,3gpp5g}.
-In this article we propose a SDN approach to deterministically manage the periodic C-RAN traffic by chosing emmission timing and reserving containers on the ring.
-In a previous work~\cite{dominique2018deterministic}, the authors have studied this problem for a star shaped network.
-Here the load due to the CRAN traffic is small which makes the problem easier.
-However, we add several new difficulties: the messages from RRHs are fragmented, there are other traffics which must not be impacted and the broadcast and select policy of the ring makes reservation of a specific time for emission somewhat wasteful.
+C-RAN is one of the major area of development for 5G; it consists in centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
+The latency of the messages between the BBU and the RRH is critical~\cite{3gpp5g}.
+In this article we propose an SDN approach to deterministically manage the periodic C-RAN traffic by choosing emission timing and reserving containers on the ring.
+In a previous work~\cite{dominique2018deterministic}, the authors have studied a similar problem for a star shaped network.
+Here the load due to the CRAN traffic is small enough to make the problem easy.
+However, we add several new difficulties: the messages from RRHs are scattered, there are other traffics whose latency must be preserved and the need to make reservation of containers on the ring requires additional bandwidth.
 
 In Sec.~\ref{sec:model}, we model the optical ring and the traffic flow.
-In Sec.~\ref{sec:oportmethods}, we study the latency when using stochastic multiplexing to manage packets insertions on the ring, with or without priority for C-RAN packets.
-In Sec.~\ref{sec:deterministicalgorithms}, we propose deterministic ways to manage C-RAN packets without buffers and thus with a minimal latency compared to stochastic multiplexing.
-The best method to do so also improves the latency of best effort packets.
+In Sec.~\ref{sec:oportmethods}, we experimentally evaluate the latency when using stochastic multiplexing to manage packets insertions on the ring, with or without priority for C-RAN packets.
+In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantees the lowest possible latency.
+It turns out that it also improves the latency of best effort packets.
 
@@
 \label{sec:model}
-% 
-%   \subsection{Network modeling}
-% 
-% The model exposed here has already been studied for another particular topology of network and with different problematics from the ones of this paper.
-One can find in \cite{latency2017} the complexity results on the problem proposed, and some algorithmic solutions to solve it in star networks.
 
@@
 The containers are filled by the nodes.
-The node $u$ can put some data in the first container of the arc $(u,v)$ \emph{only if it is free}.
+The node $u$ can put a packet of data of size less than $C$ Bytes in the first container of the arc $(u,v)$ {\bf only if it is free}.
   The dynamic of the network is simple: at each unit of time, data contained in a container go to the next.
-   The ring follows a {\bf broadcast and select with emission release policy}. When a container is filled by some node $u$,
+   The ring follows a {\bf broadcast and select with emission release policy}: When a container is filled by some node $u$,
    it is freed when it comes back at $u$ after a whole round trip.
-%    \todo{on ne parle pas assez de la periode je trouve}
 
@@
 
-   The RRH are the source of the \emph{deterministic and periodic} C-RAN traffic.
-   There are $n$ RRHs attached to the ring, the RRH $i$ being attached to the vertex $u_i$ (several antennas can be attached to the same vertex).
-An RRH is linked to a node of the ring through an electronic interface of bit rate $R$ Bps.
+   The RRH are the source of the {\bf deterministic and periodic} C-RAN traffic.
+   There are $n$ RRHs attached to the ring and several RRHs can be attached to the same vertex. An RRH is linked to a node of the ring through an electronic interface of bit rate $R$ Bps.
    The ring has a larger rate of $F\times R$ Bps.
@@
 A node aggregates the data received on the electronic interface during $F$ unit of times to create a packet of size $C$ which completely fills one container of the ring.
-Each period $P$, an RRH emits a C-RAN traffic
-   during a time $ET$ (emission time), which consists in a packet of size $C$ each $F$ unit of times.
+Each period $P$, an RRH emits $ET / F$ packets, i.e.
+a packet of size $C$ each $F$ units of time during a time $ET$ (emission time), see Fig.~\ref{fig:interface}.
 
-   The data of the RRH $i$ arrives at node $u_i$ at a time $m_i$ called its {\bf offset}. The offsets can be determined 
+   The data of the RRH $i$ arrives at node $u$ at a time $m_i$ called its {\bf offset}. The offsets can be determined 
    by the designer of the system and can be different for each RRH but must remain the same over all periods. We assume that all 
    BBUs are contained in the same data-center attached to the node $v$.
-The data from $u_i$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u_i,v)$ if it has been inserted in the ring upon arrival.
+The data from $u$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u,v)$ if it has been inserted in the ring upon arrival.
 Then after some computation time (which is supposed to be zero to simplify the presentation), an answer is sent back from the BBU to the RRH.
@@
    The aim of our study is to minimize the latency of the C-RAN traffic, both from the RRHs and the BBUs. 
-   In Sec.\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency. 
-   The only downside is that other data use the optical ring and their latency may be increased. We shortly describe the
-   nature of this additional traffic in the next subsection.
+   In Sec.~\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency which preserves the latency of other data using the optical ring.
+We shortly describe the nature of this additional traffic in the next subsection.
 
@@
       \includegraphics[scale=0.8]{interface.pdf}
-     \caption{Opto-electronic interface.}
+     \caption{Opto-electronic interface.}\label{fig:interface}
 
@@
   \end{figure}
-
-%       An node deals with two kinds of traffics.
-Some C-RAN and some Best Effort.
-We assume that each traffic has its corresponding electronic interface.
-Also, a C-RAN message is of size $Z$ and completely fills a container let us call {\bf C-RAN PDU} such a message.
-In the same time, the Best Effort messages are buffered in a first {\em gathering buffer} before being gathered together into a {\bf BE PDU}.
-Once the PDUs are created, there join the {\em contention buffer} before being sent in the ring.
-%       \begin{figure}[h!]
-% \begin{center}   
-%   \includegraphics[scale=0.7]{buffers.pdf}
-%      \caption{An N-GREEN station.}
-%      
-% \end{center}
-%   \end{figure}
-%
-
-%    
-%   The C-RAN PDUs coming from an antenna are sent according to a 
-%   
-%   follows 
-%   This study focuses on the performances of the C-RAN PDUs, thus the route we consider are the routes between the BBUs and the RRHs .We assume that there is a bijection between the RRHs and the BBUs.
-%  We call forward routes the routes going from the RRHs to the BBUs and Backward routes the routes going from the BBUs to the RRHs.
-The addition of the weight of the two routes of a couple BBU-RRH is then equal to $RS$, the size of the ring, measured in slots.
-We denote by $n$ the number of couples BBU-RRH.
-%  We only consider one data center into the ring. This mean that all the forward routes have the same destination nodes, and all the backward routes have the same source node.
-
-% 
-% 
-% \subsection{Into the node : Two kind of traffics}
 
@@
 We call this traffic \textbf{Best Effort} (BE), since it is less critical and one can increase the latency of BE messages to improve the latency of C-RAN messages.
-A contention buffer is filled by a batch arrival process of BE data.
-Then according to some parameters (fill rate and maximum wait time) a container is sent on the ring from the contention buffer.
-The arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a container of BE messages in a node.
-This distribution is obtained by choosing optimal parameters for the contention buffer~\cite{}.
-
-% 
-% 
-%   \subsection{Parameters of the study}
-%   \label{sec:parameters} The experiment of this subsections are made following the same parameters, until sec~\ref{sec:optialgo}.
-We set $K = 10$ chanels, some electronic interface of rate $D=10$Gbps and $Z = 12500$B so, $Z/KD = 1\mu$s.
-The optical ring has a rate $KD=100$Gbps, while a slots has a duration of $1\mu$s.
-The length of the ring is to $20$km in our simulations, this means that the ring has a length of $RS = 100$ slots.
-We consider some BE SDUs of $125$B, and we parametrized BE PDU generator of sec~\ref{jmf} such that each node load the network with an average of $3,5\%$ of BE traffic.
-We set $ET = 500$ slots, that correspond to a C-RAN traffic of $5$Gbps.
-The period  $P$ is to $1$ms, that is $1000$ slots.
-We set the number of RRH to $n=5$.
-We take $5$ nodes and one of them is the datacenter.
-The antennas are apportioned between the others node.
-With those parameters, the network is theoretically loaded to $67.5\%$.
-%
+At each node of the ring, a contention buffer is filled by a batch arrival process of BE data.
+Then according to some parameters (fill rate and maximum wait time) data on the contention buffer are aggregated in a packet of size at most $C$.
+The node fills the first free container it sees with this packets.
+Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a packet of BE messages in a node.
+This distribution is obtained by choosing optimal parameters for the contention buffer~\cite{youssef2018}.
 
@@
 
-  One first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: when a node wants to send some data, it uses the first free container available on the ring.
-  If a node cannot send a container, because there is no free slot or because several containers must be sent at the same time, the remaining containers are stored in an insertion buffer.
+  One first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node wants to send some packets, it uses the first free container available on the ring.
+  If a node cannot send a packet, because there is no free slot or because several packets must be sent at the same time, the remaining packet are stored in an insertion buffer.
 Two different methods to manage this insertion buffer are experimentally compared.
-The FIFO rule is compared to another method that uses two insertion buffers: one for the containers with BE data, and another for the containers with C-RAN data.
-If there is a free container on the ring, the node empties the C-RAN insertion buffer first.
+The FIFO rule is compared to a method that uses two insertion buffers: one for the BE packets, and another for the C-RAN packets.
+When the node see a free container it empties the C-RAN insertion buffer first.
 Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule and the "C-RAN first" rule.
-On this experiment, the offsets of the RRH are not fixed but randomly drawn in the period.
-The experimental\footnote{The source code in C of the experiments can be found on the author's webpage~\cite{webpage}.} parameters are given by Fig.~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
-The results are computed over $100$ instances of optical rings that are simulated during $10,000,000$ unit of time.
+In this experiment, the offsets of the RRH are not fixed but randomly drawn in the period.
+The experimental parameters are given by Fig.~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
+The results are computed over $100$ instances of optical rings that are simulated during $10,000,000$ units of time.
+The source code in C of the experiments can be found on the author's webpage~\cite{webpage}.
 
@@
   \hline
+  Bit rate of an electronic interface $R$ & $10$ Gbps \tabularnewline
+  \hline
+  Optical ring bit rate $F\times R$ & $100$ Gbps \tabularnewline
+  \hline
     Acceleration factor $F$ & $10$  \tabularnewline
   \hline
-  Bit rate of an electronic interface $R$ & $10$ Gbps \tabularnewline
+  Container size  $C$ & $100$ kb  \tabularnewline
   \hline
-  Container size  $C$ & $12,500$ B  \tabularnewline
-  \hline
-  Slot duration $C/F\times R$ & $1\mu$ s \tabularnewline
-  \hline
-  Optical ring bit rate $F\times R$ & $100$ Gbps \tabularnewline
+  Unit of time $C/(F\times R)$ & $1~\mu$s \tabularnewline
   \hline
@@
 
-%    
-%    
-%    \subsection{Full opportunistic method}
-%    \label{sec:fullopport}
-%    We first want to look at a simple configuration in which we do not manage the PUDs (BE or C-RAN) arriving into a node.
-At their arrival, the BE and C-RAN PDUS are buffered in the contention buffer, and this buffer is emptied following the FIFO rule.
-%
-%The following experiment shows us the performance this {\bf full opportunistic method} with some parameters issued from N-GREEN. 
-%On fig~\ref{fig:oport}, one can see the cumulative distribution of the latency of the C-RAN and BE PDUs.
-The measures are taken after $3,000$ slots of simulation, to let the ring initialize it's behavior.
-The parameters of the simulations are stated in sec~\ref{sec:parameters}.
-%
-%
-%    \begin{figure}[h!]
-%    \label{fig:oport}
-%        \begin{center}
-%      \includegraphics[scale=0.4]{oport}
-%
-%      \caption{Full opportunistic method performances.}
-%      \end{center}
-%  \end{figure}
-%  
-%  As we can see on fig~\ref{fig:oport}, the latency for the different kind of PDU is notably similar because we do not manage anything.
-Furthermore, we can remark that about $10\%$ of the C-RAN messages wait over $100\mu$s, that is already critical for C-RAN \todo{ref}.
-%
-%\subsection{C-RAN priority method}
-%\label{sec:cranprio}
-%  In order to improve the C-RAN PDUs latency, we imagined the following solution, called {\bf C-RAN priority method}.
-Each nodes have two contention buffers.
-One for the BE PDUs, and one fore the C-RAN PDUs.
-When a node is able to send a PDU on the ring, i.e.
-its available container is free, the container is filled with the C-RAN PDUs first.
-%  
-%    \begin{figure}[h]
-%\begin{center}   
-%      \includegraphics[scale=0.7]{cranprio.pdf}
-%     \caption{C-RAN priority method.}
-%\end{center}
-%  \end{figure}
-%  
-%  With this method, one can imagine improve the latency of the C-RAN PDUs.
-Fig~\ref{fig:prior} shows us the performance of the C-RAN priority algorithm for different kinds of traffics.
-The parameters of the simulations still the same, stated in sec~\ref{sec:parameters}.
-%      \begin{figure}[h]
-%      \label{fig:prior}
-%\begin{center}   
-%
-%      \includegraphics[scale=0.4]{prior.pdf}
-%
-%     \caption{C-RAN priority method performances.}
-%\end{center}
-%  \end{figure}
-%  
-%  As expected, the latency of the C-RAN PDUs is decreased compared to the full opportunistic method.
-Nevertheless, there is still $10\%$ of the C-RAN PDUs that have more than $50 \mu$s of latency, and the best effort PDUs are penalized, indeed, close to $10\%$ of the BE PDUs awaits more than $150\mu$s before being sent in the ring, versus close to $0\%$ with the previous method..
-%  Thus, we propose a deterministic approach in which we set the offsets of the RRH and we reserve the containers needed for the C-RAN PDUs.
-%   \todo{il manque une partie sur le travail de karim, }
+\section{Deterministic approach for zero latency} \label{sec:deterministicalgorithms}
 
-\section{Deterministic approach for zero lantency} \label{sec:deterministicalgorithms}
+Finding good offsets for the C-RAN traffic is a hard problem even for simple topologies and without BE traffic, see~\cite{dominique2018deterministic}.
+On this section, we give simple solution to this problem in the N-GREEN optical ring, and we adapt it to minimize the latency of the BE traffic.
 
-The complexity of finding good offsets for the C-RAN traffic for a different topology has been investigated in~\cite{dominique2018deterministic} without best effort traffic.
-This problem is easy in the N-GREEN optical ring (see the solution in this section).
-However, we must adapt our method to minimize the latency of the BE traffic.
-
-In order to ensure zero latency for the C-RAN traffic, the container needed to send a C-RAN message from the RRH $i$ must be free at time $m_i$.
-Hence the node $u_i$ \textbf{reserves} the container at time $m_i - RS$.
+In order to ensure zero latency for the C-RAN traffic, the first container after node $u$, to which is attached the RRH $i$, must be free at time $m_i$.
+Hence the node $u$ \textbf{reserves} the container at time $m_i - RS$.
 A container which is reserved cannot be filled by any node except the one which has reserved it.
-We assume that the message sent by the RRH $i$ arrives at its BBU at time $m_i + \omega(u,v)$ and the answer is sent from the BBU at time $m_i + \omega(u,v) +1$ (with no waiting time).
+In the method we now describe, the C-RAN packets never wait in the node: The message sent by the RRH $i$ arrives at its BBU at time $m_i + \omega(u,v)$ and the answer is sent from the BBU at time $m_i + \omega(u,v) +1$.
 
 Recall that an RRH emits a packet every $F$ containers, during a time $ET$. 
-Thus if we divide the period $P$ into \textbf{slots} of $F$ containers, an RRH needs one container by slot.
-Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position in the slot during all the period.
+Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive unit of time, an RRH needs one container by slot.
  If an RRH emits at time $m_i < P$, then we say it has \textbf{position} $m_i \mod F$.
-If an RRH is at position $i$, then by construction, the corresponding $BBU$ is at position $i+1 \mod F$.
+If an RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1 \mod F$.
+Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position during all the period.
 
-The problem we solve now is to find an \textbf{assignment} of values of the $m_i$ which is \textbf{valid}: no two RRH reserve the same container in a period.
+The problem we solve now is to find an \textbf{assignment} of values of the $m_i$s which is \textbf{valid}: no two RRHs reserve the same container in a period.
 Moreover we want to preserve the latency of the BE traffic.
-It means that the time to wait for a
-free container at any moment of the period and in any node of the ring must be minimized. 
-Remark that two RRHs which are not at the same position do not use the same container. Moreover, without loss of generality, 
+It means that the time a node waits for a free container at any point of the period must be minimized.
+Remark that two RRHs which are not at the same position never use the same containers. Moreover, without loss of generality, 
 if we can fix the offsets of the RRHs to even positions so that they do not reserve the same containers, then it will fix the offsets of the BBUs to odd positions which do not reserve the same containers.
 
-% 
-% Since the computation time of the BBU is supposed to be zero (or a multiple of the period), setting the offsets $m_i$ for all RRH $i$ also sets the time $m_i + \omega(u,v)$, called {\bf BBU offset}.
-Because all the BBU are located in the same datacenter, setting the BBU-offsets without collisions directly avoid the collision between the C-RAN.
-A {\bf macro slot} is a sequence of $F$ slots.
-A RRH can emit at most once every macro slot but requires two free containers (one for the uplink message, and one for the downlink one) to ensure zero latency.
-A {\bf pair} is a sequence of two consecutive slots in the macro slot, the messages of two RRH assigned to different pair can not collide.
-
 \begin{prop}
-There is an assignation for the offsets $m_1, \dots, m_k$ on the same position if  $k\times ET + RS \leq P$.
+There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if  $k\times ET + RS \leq P$.
 \end{prop}
 \begin{proof}
- First assume w.l.o.g. that the position of the offsets is zero. Then we fix $m_1 = 0$. We also assume that the 
- nodes $u_1,\dots,u_n$ are in the order of the ring.
-The last message emitted by $1$ arrives at $u_2$ at time $ET - 1 + \omega(u_1,u_2)$.
+ We fix $m_1 = 0$ and all the offsets will also be at position $0$. 
+ Let $u_1,\dots,u_k$ be the nodes attached to the RRHs $1,\dots,k$.
+We assume that $u_1,\dots,u_k$ are in the order of the ring.
+The last message emitted by the RRH $1$ arrives at $u_2$ at time $ET - 1 + \omega(u_1,u_2)$.
 Therefore we can fix $m_2 =  ET  + \omega(u_1,u_2)$.
 In general we can set $m_i = (i-1) \times ET + \omega(u_1,u_i)$ and all RRHs will use different containers at position $0$.
-The assignation is correct, if the second period
- RRH $1$ must emit something, a container is at position $0$ is free. It implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.
+The assignment is correct, if when the RRH $1$ must emit something in the second period, there is a free container.
+It implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.
 \end{proof}
@@
 Remark that for each position which is used by some RRH, we lose $2RS$ because of the reservation of the RRH and of its BBU.
-Therefore to not waste bandwidth, it is relevant to put as many RRH as possible on the same positions.
-Moreover unused position in an assignment are useful to guarantee a good latency to BE traffic.
-The unused positions can be chosen uniformly over a slot, to minimize the time to wait before a free slot, as in Fig.~\ref{fig:repart1}.
+Therefore to not waste bandwidth, it is relevant to put as many RRH as possible on the same position.
+Moreover unused positions in an assignment are useful to guarantee a good latency to BE traffic.
+The unused positions can be distributed uniformly over a slot, to minimize the time to wait before a free slot, as in Fig.~\ref{fig:repart1}.
 
@@
 Hence there is exactly one  BBU or RRH at each position.
-If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for $BE$-traffic.
-To mitigate this problem, the free containers of each position must be uniformly distributed over the period as in Fig.~\ref{fig:repart2}.
+If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for BE traffic.
+To mitigate this problem, the time with free containers of each position must be uniformly distributed over the period as in Fig.~\ref{fig:repart2}.
 
-We present the cumulative of the latency of the BE traffic latency using the FIFO rule or the reservation algorithm proposed here in
+We present the cumulative distribution of the latency of the BE traffic latency using the FIFO rule or the reservation algorithm proposed here in
 Fig.~\ref{fig:optimres}.
-Since the previous parameters were too restrictive to put several RRH on the same pair, the parameters $ET$, and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
-% 
-% \begin{prop}
-%  If several RRH shares a pair, it is possible to set the BBU-offsets such that there is no collisions between the messages if $P \ge n\times ET + RS$.
-%  \end{prop}
-% %  \begin{proof}
-% One show that proposition by induction.
-%  In this proof, the model is simplified in order to study the behavior of one pair, thus, both of the RRH emit some containers every slots, during $ET$ slots in the period $P$.
-%  {\bf Base case:} 
-%  Consider $P =  2.ET+RS$ and two RRH each connected to the nodes $A$ and $B$.
-%  We assume that $A$ starts to emit a time $1$ during $ET$ slots.
-The containers of $A$ arrive in $B$ during the interval $[\omega(A,B);\omega(A,B)+ET[$.
-Then, $B$ can immediately emits its containers at time $\omega(A,B)+ET$.
-Those containers from $B$ arrives at $A$ at during  $ [\omega(A,B)+ET + \omega(B,A) ;\omega(A,B)+ET + \omega(B,A) + ET ] = [ET+RS;2.ET+RS] = [ET + RS; P]$.
-Then, $A$ can emit in the next period, without collisions.
-% Thus, for $n = 2$, it is possible to assign two RRH on the same pair if $P = 2\times ET + RS$.
-%  
-%  {\bf Induction step:}  A ring can support $n$ RRH with a period of size $P= n\times ET + RS$.
-One must show that if there is one more RRH on the ring, the period must be at least $P = (n+1)\times ET + RS$.
-%  
-% Take a sequence of container of size $P$ on a ring with $n$ RRH.
-One can observe that this sequence is the same at every nodes, shifted of the length of the routes between the nodes.
-For instance, with two nodes $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted by $\omega(A,B)$.
-% In addition if the sequence is increased by $ET$ free containers, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence to carry the traffic of a new RRH.
-Thus a period $P = (n+1)\times ET + RS$ is enough to carry the traffic of $n+1$ RRH.
-% %  \end{proof}
-% 
-% For the purpose of decreasing the BE traffic latency, it is interesting to regularly ensure some free pairs for the BE messages.
-To this end, the pairs must be filled with as much RRH as possible.
-Then, the free pairs are uniformly apportioned into the macro slot.
-Nevertheless, this is not always enough to ensure a good BE traffic latency.
-Indeed, with the previous parameters, with $ET = \frac{P}{2}$, $F = 10$ and $n = 5$, a pair is given to each antenna, and if all the RRH starts to emit in the same macro slots, a long sequence of reserved container will highly impact the latency of the BE traffic.
-The solution to this issue is to uniformly distribute the BBU-offset of the first RRH of a pair on the period.
-In this situation, the number of free pairs in a macro slot is balanced on the period, that allows a more regular BE traffic.
-Fig.~\ref{fig:optimres} is a compariason between the cumulative distribution of the BE traffic latency with the FIFO rule or with the reservation algorithm proposed here.
-Since the previous parameters were too restrictive to put several RRH on the same pair, the parameters $ET$, and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
+Since the previous parameters were too restrictive to put several RRHs on the same position, the parameters $ET$ and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
+With these parameters, the loss of bandwidth due to reservation is at most $6\%$.
 
@@
       \includegraphics[scale=0.25]{optim.pdf}
-     \captionof{figure}{Impact of the reservation of the traffics.}   \label{fig:optimres}
+     \captionof{figure}{Impact of the deterministic method on the traffics.}   \label{fig:optimres}
   \end{minipage} 
@@
 
-  The performances are excellent, since the C-RAN traffic have $0$ latency and the BE traffic have a better latency with reservation than with the FIFO rule.
-Indeed, our algorithm balanced the load of the C-RAN traffic over the period , that helps the BE traffic to not aggregate and create additional latency.
-
-%% In this section We present three algorithms that allows the C-RAN PDUs to have $0$ latency in the insertion buffers by establishing a static reservation of the slots in the period.
-%% Those algorithm are {\bf Centralized} and requires a global supervisor of the network to be implemented .\todo{phrase + ref sdn?}
-%% 
-%%\paragraph{Slot reservation} To decrease the C-RAN messages latency, one plan to reserve the container for the nodes.
-Indeed, if a node $i$ needs to send a PDU at time $t$, a container needs to be reserved since the previous lap of the container, i.e.
-at time $t - RS$ by $i$.
-In this situation, if the container is already taken by a PDU which has been sent by a node $j$, $j$ will remove the PDU of the container during the next lap of the ring, and no other nodes are able to write in this container before it comes back to the node $i$ a date $t$.
-By choosing the offsets of the route and reserving the corresponding containers, we allow the C-RAN PDUs to have $0$ latency in the nodes.
-Though, it impacts the best effort PDUs, by avoiding them to use free reserved containers.
-It is equivalent to increase the load of the network, without increasing the number of PDUs carried by the network.
-%%
-%%\paragraph{RRHs synchronisations}
-%%This slot reservation implies that the RRHs are synchronized with the ring.
-The following proposed algorithms set a sequence of reserved slots for each RRH in each period.
-A technical application implies to simultaneously ensure the reservation of the slot to the given dates, and the synchronization of the RRH with those reserved slot.
-One must ensure that the C-RAN PDU arrives in the contention buffer of the node just before the reserved container.
-%%
-
-%Unlike the previous methods with opportunistic insertion policy, we now want to choose a the offsets for the routes.
-Since all the forward routes have the same last vertex $v$ (the datacenter), which is also the first vertex of all the backward routes, we choose to manage the collision in this vertex only.
-The purpose is then to determine the time BBU offset of the routes.
-Once the BBU-offsets are set, for all routes $i$, it is easy to compute $m_{r_i} = t(v,r_i) - \omega(u,v)$.
-%
-%
-%\subsection{N-GREEN parameters adapted algorithms}
-%An RRH can not emit a message more often than once slot every $K$ slots.
-Remember that {\bf macro slot} is a duration of $K$ slots, during which each RRH can emit at most once.
-Thus, we consider the simple case in which there is less C-RAN traffic than slots in a macro slot.
-Indeed, in that case, we only manage the collision in one macro slot, i.e.
-we assign a C-RAN traffic to each slot of the macro-slot.
-Since a BBU always instantly emits an answer to it's RRH, for each RRH, a group of two following containers (called {\bf bunch}) can be reserved.
-Thus, we first study the case $K \ge 2\times n$.
-As a reminder, $n$ is the number of couple BBU-RRH.
-%
-% 
-% Because there is at most as much couples BBU-RRH as bunches, we want to assign one RRH to one bunch.
-%We propose the following {\bf naive reservation algorithm}.
-For each RRH $i, i\in \{0,...,n-1\} $, set $t(v,r_i)= 2\times i$ with $v$ the vertex of the BBUs.
-The model automatically fixes the offset of the backward route $\rho(r_i)$ to $m_{\rho(r_i)}= 2\times i +1$.
-This is the reason why we do not care about the backward routes anymore, and we only deal with the BBU-offsets of the forward routes..
-%   \begin{figure}[h]
-%\centering
-%      \includegraphics[scale=0.7]{freqgrouped.pdf}
-%     \caption{Grouped assignment of the bunches to the RRH.}   \label{fig:freqG}
-%  \end{figure}
-%
-%
-%We kept the same parameters than in the two previous experiments (see~\ref{sec:parameters}) and we made an experiment to show the impact of this algorithm on the BE traffic.
-Fig~\ref{fig:res1} shows us the distribution of latency for BE PDUs with this algorithm.
-%
-%      \begin{figure}[h]
-%\centering
-%      \includegraphics[scale=0.4]{res1.pdf}
-%     \caption{Impact of the naive reservation algorithm on the Best effort PDUs.}   \label{fig:res1}
-%  \end{figure}
-%
-%As we can see, the BE traffic is highly penalized by this algorithm, indeed, while almost $100\%$ of the BE PDUs have a latency to less than $200 \mu$s with the full opportunistic method (see fig~\ref{fig:oport}), here, more than half of the BE PDUs are be buffered more than $200\mu s$.
-Those performances are explained by the structure of the algorithm.
-The messages are grouped together, and with our parameters, $K = 2\times n$.
-It creates a long sequence of slots during which there is no free containers in the ring.
-%
-%To improve the BE PDUs latnecy, we propose a {\bf splited reservation algorithm} that balances the load of the CRAN traffic over the period.
-Instead of giving some close BBU-offsets for all routes $i$, with $v$ the datacenter, we now uniformly distribute the different BBU-offsets in the period.
-Each couple BBU-RRH is still assigned to its bunch, but we split the BBU-offsets of $\frac{P}{n}$.
-Also, if $2 \times n < K$, the RRH are balanced over the bunches by the same way, we try to give a bunch to a RRH each $\frac{K}{2\times n}$ buches.
-%
-%   \begin{figure}[!h]
-%\centering
-%      \includegraphics[scale=0.7]{freqsplited.pdf}
-%     \caption{Splited assignment of the bunches to the RRH.}   \label{fig:freqS}
-%  \end{figure}
-%  
-%  On fig~\ref{fig:res2} one can observe the performance of this algorithm on the BE PDUs latency. Once again, to have a reference point, we take the same parameters for the simulation. 
-%
-% \begin{figure}[h]
-%\centering
-%      \includegraphics[scale=0.4]{res2.pdf}
-%     \caption{Impact of the splited reservation algorithm on the Best effort.}   \label{fig:res2}
-%  \end{figure}
-%  
-%  As we can see, thelatency of the BE PDUs is highly better with this this algorithm.
-Indeed almost $100\%$ of CRAN PDUs have a latency of less than $50\mu$s which is better than the full opportunistic method.
-Thus, we decreased the latency of every kind of traffic.
-%
-%\subsection{With more antennas}
-%\label{sec:optialgo}
-% In this section, we study the case $n > \frac{K}{2}$, we want to assign more than one RRH to a bunch. 
-% Let us consider a particular behavior of the ring.
-Instinctively, we can think that if we have enough space in the period for many traffics on the same frequency that is, $ET \le \frac{P}{2}$, we can assign several couples BBU-RRH to the same bunch.
-%
-% Let us take $ET =  \frac{P}{2}$ and $n = \frac{K}{2} + 1$.
-We assign a bunch to each $\frac{K}{2}$ first RRH and we have only one RRH left.
-Then, we only look at one bunch, on which we want to add the new couple BBU-RRH.
-% 
-% We take a ring with two nodes $A$ and $B$.
-We simplify the model to only look at the behaviour of one bunch, thus, both of the nodes alternatively emits some containers every slots, during $ET$ slots in the period $P$.
-We assume that $A$ emits a time $1$ during $ET$ slots.
-This container arrives in $B$ at $\omega(A,B)$, that is  $[t(B,r_A)]_{P,K} = [\omega(A,B);\omega(A,B)+ET]$.
-Then, $B$ can immediately emit its containers at time $\omega(A,B)+ET$.
-This containers from $B$ arrives at $A$ at time $\omega(A,B)+ET + \omega(B,A) = ET + RS$, and thus, $[t(A,r_B)]_{P,K} = [ET + RS;ET + RS + ET] = [ET+RS; RS + P] = [ET + RS; RS] \mod P$.
-Since $[t(A,r_A)]_{P,K} = [1;ET]$, there is a collision at the interval $[1;RS]$ in the period between the two traffics from $A$ and $B$.
-%  \begin{figure}[h]
-%\centering
-%      \includegraphics[scale=0.7]{rs.pdf}
-%     \caption{Collision between two routes on the same bunch when the period is too small.}   \label{fig:proofrs}
-%  \end{figure}
-%
-% 
-% 
-% As we have just noted, if several RRH share the same bunch, the period must have an additional budget in addition to the time needed to send the messages.
-Let us study the size of the additional budget.
-% \begin{prop}
-% If several RRH shares a bunch, it is possible set the offsets of the routes such that there is no collisions between the messages if $P \ge n\times ET + RS$ , with $n$ the number of RRHs.
-% \end{prop}
-% \begin{proof}
-% We seek to show that proposition by induction.
-% 
-% {\bf Base case:} For $n = 2$, the proof of the previous example shows us that it is possible to assign two RRH on the same bunch with $P = 2\times ET + RS$.
-% 
-% {\bf Induction step:}  We consider that we have a bunch shared by $n$ RRH, with a period of size $P= n\times ET + RS$.
-We want to show that if we want to add one RRH to the bunch, we need a period of size at least $P = (n+1)\times ET + RS$.
-If we look at the sequence period of the bunch with $n$ RRH.
-We can observe that this sequence is the same in every nodes, shifted of the length of the routes between two nodes.
-For instance, if we take two nodes $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted of $\omega(A,B)$.
-% 
-%   \begin{figure}[h]
-%\centering
-%      \includegraphics[scale=0.7]{period1.pdf}
-%     \caption{An example of sequence with n = 3.}   \label{fig:proofperiod1}
-%  \end{figure}
-%   
-% Thus, if we add $ET$ slots in this bunch, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence.
-% 
-%   \begin{figure}[h]
-%\centering
-%      \includegraphics[scale=0.7]{period2.pdf}
-%     \caption{The same sequence with n = 4.}   \label{fig:proofperiod2}
-%  \end{figure}
-%  Note that a station can send some traffic from more than one RRH, the figures ~\ref{fig:proofperiod1} and \~ref{fig:proofperiod2} are just an example, but this proof stays the same.
-% \end{proof}
-% 
-%Considering those results, we propose an algorithm to allow several RRH to share the same bunch, as long as $P \ge n\times ET + RS$. 
-%Since we need $RS$ slots on a each bunch with at least an RRH to assign another RRH to this latter, it is interesting to fill as far as possible the bunches.
-We then compute the number of bunches needed to carry the number of RRH $n$.
-Then, the algorithms tries to balance those bunches into the macro-slot, i.e.
-it avoids to group the used bunches together.
-%The used bunches have $RS$ or more free slots in the period.
-Thus, the algorithm subsequently balance BBU-offsets of the first RRH of each bunch, with the same idea than the splited algorithm.
-We call this algorithm the {\bf full repartition algorithm}.
-%
-%   \begin{figure}[h]
-%\centering
-%      \includegraphics[scale=0.7]{optimalgo.pdf}
-%     \caption{Organization of the bunches with the balancing algorithm.}   \label{fig:optimalgo}
-%  \end{figure}
-%  
-%  We want to observe the impact of this algorithm on BE traffic.
-Since our previous parameters did not allow several RRH to share a bunch, we now set $ET = 200$, that correspond to a C-RAN flow of $2$Gbps.
-This is not out of context since the exact split (the C-RAN split is the degree of centralization of the computation units in the cloud) of the C-RAN is not fully determined yet~\cite{REF}.\todo {la ref} To keep a load similar to the load in the previous experiment, we set the number of RRH to $n=12$.
-The others parameters are all the one described in the sec~\ref{sec:parameters}.
-%  The following experiment shows us the impact of the balancing algorithm on the BE traffics.
-We chose to compare those results to a simulation with the same parameters but with the full opportunistic method of sec~\ref{sec:fullopport}.
-%  
-%   \begin{figure}[h]
-%\centering
-%      \includegraphics[scale=0.4]{optim.pdf}
-%     \caption{Balancing algorithm performance on the N-GREEN optical ring.}   \label{fig:optimres}
-%  \end{figure}
-%  
-%  As fig~\ref{fig:optimres} shows, the full repartition algorithm ensures a lower latencye to BE PDUs than the full opportunistic method, which gave the best result for the BE traffic.
-Indeed, since we remove the random aspect of the C-RAN PDUs generation, we balanced the load over the period an then increased the BE performances while we totally removed the C-RAN PDUs latency.
+  The performance of the reservation algorithm is excellent, since the C-RAN traffic has {\bf zero latency} and the BE traffic has a \textbf{better latency} with reservation than with the FIFO rule.
+It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth for the BE traffic.
 

### 2018-02-23 Papier NGreen/article.tex
typos

@@
 \begin{abstract}
-N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency$\dots$) without using expensive end to end connections.
+The N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency$\dots$) without using expensive end to end connections.
 We study the compatibility of such a technology with the development of the Cloud RAN, a latency critical application which is a major aspect of 5G deployment.
@@
 Network\footnote{This work was developed around the ANR N-GREEN project.
-The authors thank the Nokia Bell Labs team for their collaboration.} providers have to design inexpensive networks supporting an increasing the amount of data and online applications.
+The authors thank the Nokia Bell Labs team for their collaboration.} providers have to design inexpensive networks supporting an increasing amount of data and online applications.
 Much of these applications have QoS criteria, like a minimal throughput or a maximal latency.
 The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers.
-The current solutions with good QoS~\cite{pizzinat2015things}, establishe end to end connection (E2E) between the nodes, which is extremely expensive.
-The N-GREEN optical ring is designed to ensure good performances: the hardware it requires scales linearly with the number of nodes while E2E scales quadratically making it impractical for more than a few nodes.
+The current solutions with good QoS~\cite{pizzinat2015things}, establish end to end direct connections (E2DE) between the nodes, which is extremely expensive.
+The N-GREEN optical ring is designed to ensure good performance: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.
 
-In this article, we study a Cloud RAN (C-RAN) application in the N-GREEN optical ring described in~\cite{ngreenarchitecture}.
-C-RAN is one of the major area of development for 5G; it consists in centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
+In this article, we study a Cloud RAN (C-RAN) application based on the N-GREEN optical ring described in~\cite{ngreenarchitecture}.
+C-RAN is one of the major area of development for 5G; it consists in centralizing or partially centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
 The latency of the messages between the BBU and the RRH is critical~\cite{3gpp5g}.
@@
   The unidirectional optical ring is represented by an oriented cycle.
-The vertices of the cycle represents the nodes of the ring, where traffic arrives.
-The edges $(u,v)$ of the cycle have an integer weight $\omega(u,v)$ which represents the time to transmit a unit of information from $u$ to $v$.
+The vertices of the cycle represent the nodes of the ring, where the traffic arrives.
+The edges $(u,v)$ of the cycle have an integer weight $\omega(u,v)$ which represents the time to transmit an unit of information from $u$ to $v$.
 By extension, if $u$ and $v$ are not adjacent, we denote by $\omega(u,v)$ the size of the directed path from $u$ to $v$.
@@
 The containers are filled by the nodes.
-The node $u$ can put a packet of data of size less than $C$ Bytes in the first container of the arc $(u,v)$ {\bf only if it is free}.
-  The dynamic of the network is simple: at each unit of time, data contained in a container go to the next.
-   The ring follows a {\bf broadcast and select with emission release policy}: When a container is filled by some node $u$,
+The node $u$ can put a data packet of size less than $C$ Bytes in the first container of the arc $(u,v)$ {\bf only if it is free}.
+  The dynamic of the network is simple: at each unit of time, the packet of a container go to the next container.
+   The ring follows a {\bf broadcast and select scheme with emission release policy}: When a container is filled by some node $u$,
    it is freed when it comes back at $u$ after a whole round trip.
@@
 
-   The RRH are the source of the {\bf deterministic and periodic} C-RAN traffic.
-   There are $n$ RRHs attached to the ring and several RRHs can be attached to the same vertex. An RRH is linked to a node of the ring through an electronic interface of bit rate $R$ Bps.
+   The RRHs are the source of the {\bf deterministic and periodic} C-RAN traffic.
+   There are $n$ RRHs attached to the ring and several RRHs can be attached to the same vertex. A RRH is linked to a node of the ring through an electronic interface of bit rate $R$ Bps.
    The ring has a larger rate of $F\times R$ Bps.
@@
 
-   The data of the RRH $i$ arrives at node $u$ at a time $m_i$ called its {\bf offset}. The offsets can be determined 
+   The data of the RRH $i$ arrives at node $u$ at a time $m_i$ called {\bf offset}. The offsets can be determined 
    by the designer of the system and can be different for each RRH but must remain the same over all periods. We assume that all 
@@
 The same quantity of data is emitted by each BBU or RRH during any period.
-   The {\bf latency} of a message is the time it waits in a node before being put in a free container on the ring.
+   In this study the {\bf latency} of a message is defined as the time it waits in a node before being put in a free container on the ring.
    The aim of our study is to minimize the latency of the C-RAN traffic, both from the RRHs and the BBUs. 
@@
       \includegraphics[scale=0.8]{interface.pdf}
-     \caption{Opto-electronic interface.}\label{fig:interface}
+     \caption{Access node of the N-GREEN optical ring.}\label{fig:interface}
 
@@
 The optical ring supports other traffics, corresponding to the internet flow.
-We call this traffic \textbf{Best Effort} (BE), since it is less critical and one can increase the latency of BE messages to improve the latency of C-RAN messages.
+We call this traffic \textbf{Best Effort} (BE): We give no guarantee on its latency since it is less critical than C-RAN traffic.
 At each node of the ring, a contention buffer is filled by a batch arrival process of BE data.
-Then according to some parameters (fill rate and maximum wait time) data on the contention buffer are aggregated in a packet of size at most $C$.
-The node fills the first free container it sees with this packets.
+Then according to some parameters (fill rate and maximum waiting time) data on the contention buffer are aggregated in a packet of size at most $C$.
+The node fills the first free container it sees with this packet.
 Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a packet of BE messages in a node.
@@
 
-  One first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node wants to send some packets, it uses the first free container available on the ring.
-  If a node cannot send a packet, because there is no free slot or because several packets must be sent at the same time, the remaining packet are stored in an insertion buffer.
+  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node wants to send some packets, it uses the first free container available on the ring.
+  If a node cannot send a packet, because there is no free slot or because several packets must be sent at the same time, the remaining packets are stored in an insertion buffer.
 Two different methods to manage this insertion buffer are experimentally compared.
@@
 Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule and the "C-RAN first" rule.
-In this experiment, the offsets of the RRH are not fixed but randomly drawn in the period.
+In this experiment, the offsets of the RRH are not fixed but randomly distributed in the period.
 The experimental parameters are given by Fig.~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
@@
 Recall that an RRH emits a packet every $F$ containers, during a time $ET$. 
-Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive unit of time, an RRH needs one container by slot.
- If an RRH emits at time $m_i < P$, then we say it has \textbf{position} $m_i \mod F$.
-If an RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1 \mod F$.
+Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive unit of time, a RRH needs one container by slot.
+ If a RRH emits at time $m_i < P$, then we say it has \textbf{position} $m_i \mod F$.
+If a RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1 \mod F$.
 Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position during all the period.
 
-The problem we solve now is to find an \textbf{assignment} of values of the $m_i$s which is \textbf{valid}: no two RRHs reserve the same container in a period.
+The problem we solve now is to find an \textbf{assignment} of values of the $m_i$s which is \textbf{valid}: two RRHs never reserve the same container in a period.
 Moreover we want to preserve the latency of the BE traffic.

### 2018-06-04 ISCIS/article.tex
iscis

--- 2018-02-23 Papier NGreen/article.tex
@@
-\documentclass[]{algotel}
+%\documentclass[]{algotel}
+%\usepackage[utf8]{inputenc}
+
+%\usepackage{xspace}
+%\usepackage{graphicx,graphics} 
+%\usepackage{mathtools, bm}
+%\usepackage{caption}
+%\usepackage{amssymb, bm}
+%\usepackage{complexity}
+%\usepackage{amsthm}
+%%\usepackage{authblk}
+%\usepackage{color}
+%\usepackage{amsmath}
+%\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
+%\captionsetup{justification=centering,margin=0.5cm}
+\documentclass[]{llncs}
+%
 \usepackage[utf8]{inputenc}
 \usepackage[english]{babel}
-\usepackage{xspace}
-\usepackage{graphicx,graphics} 
-\usepackage{mathtools, bm}
 \usepackage{caption}
-\usepackage{amssymb, bm}
-\usepackage{complexity}
-\usepackage{amsthm}
-%\usepackage{authblk}
-\usepackage{color}
-\usepackage{amsmath}
-\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
-\captionsetup{justification=centering,margin=0.5cm}
+
+\usepackage{graphicx}
+
 \newcommand\pall{\textsc{pall}\xspace}
@@
 \title{Contention management for Cloud RAN over an optical ring}
-\author{Dominique Barth\addressmark{1}
-  \and Ma\"el Guiraud\addressmark{1}
-   \and Yann Strozecki\addressmark{1}
+\author{Dominique Barth \inst{1}
+  \and Ma\"el Guiraud \inst{1}
+   \and Yann Strozecki \inst{1}
   }
 
-\address{\addressmark{1}David Laboratory, UVSQ}
-
-\keywords{Optical ring, Latency, C-RAN, SDN}
+\institute{David Laboratory, UVSQ}
 
@@
 We show that deterministically managing Cloud RAN traffic minimizes its latency without impacting the latency of others traffics.
+\keywords{Optical ring \and Latency \and C-RAN \and SDN}
 \end{abstract}
@@
 The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers.
-The current solutions with good QoS~\cite{pizzinat2015things}, establish end to end direct connections (E2DE) between the nodes, which is extremely expensive.
+The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end to end direct connections (E2DE) between the nodes, which is extremely expensive.
 The N-GREEN optical ring is designed to ensure good performance: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.
 
-In this article, we study a Cloud RAN (C-RAN) application based on the N-GREEN optical ring described in~\cite{ngreenarchitecture}.
+In this article, we study a Cloud RAN (C-RAN) application based on the N-GREEN optical ring described in~\cite{ngreenarchitecture,uscumlicscalable}.
 C-RAN is one of the major area of development for 5G; it consists in centralizing or partially centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
@@
 The vertices of the cycle represent the nodes of the ring, where the traffic arrives.
-The edges $(u,v)$ of the cycle have an integer weight $\omega(u,v)$ which represents the time to transmit an unit of information from $u$ to $v$.
+The edges $(u,v)$ of the cycle have an integer weight $\omega(u,v)$ which represents the time to transmit a unit of information from $u$ to $v$.
 By extension, if $u$ and $v$ are not adjacent, we denote by $\omega(u,v)$ the size of the directed path from $u$ to $v$.
-We denote by $RS$ (ringsize) the length of the cycle, that is $\omega(u,u)$.
+The \textbf{ring size} is the length of the cycle, that is $\omega(u,u)$ and we denote it by $RS$.
 Each arc $(u,v)$ can be seen as a sequence of $\omega(u,v)$ {\bf containers}, of capacity $C$, expressed in Bytes.
@@
    The RRHs are the source of the {\bf deterministic and periodic} C-RAN traffic.
-   There are $n$ RRHs attached to the ring and several RRHs can be attached to the same vertex. A RRH is linked to a node of the ring through an electronic interface of bit rate $R$ Bps.
+   There are $n$ RRHs attached to the ring and several RRHs can be attached to the same vertex. An RRH is linked to a node of the ring through an electronic interface of bit rate $R$ Bps.
    The ring has a larger rate of $F\times R$ Bps.
@@
 A node aggregates the data received on the electronic interface during $F$ unit of times to create a packet of size $C$ which completely fills one container of the ring.
-Each period $P$, an RRH emits $ET / F$ packets, i.e.
-a packet of size $C$ each $F$ units of time during a time $ET$ (emission time), see Fig.~\ref{fig:interface}.
+  In each period $P$, an RRH emits data during a time called \textbf{emission time} or $ET$.
+Hence the RRH emits $ET / F$ packets, i.e.
+a packet of size $C$ each $F$ units of time during the emission time, see Fig.~\ref{fig:interface}.
+   %Each period $P$, an RRH emits $ET / F$ packets, i.e. a packet of size $C$ each $F$ units of time during a time $ET$ (emission time),
 
@@
 
-      \includegraphics[scale=0.8]{interface.pdf}
+      \includegraphics[scale=0.7]{interface.pdf}
      \caption{Access node of the N-GREEN optical ring.}\label{fig:interface}
@@
 The optical ring supports other traffics, corresponding to the internet flow.
-We call this traffic \textbf{Best Effort} (BE): We give no guarantee on its latency since it is less critical than C-RAN traffic.
+We call this traffic \textbf{Best Effort} (BE).
+We want it to have the best possible distribution of latency, but since is less critical than C-RAN traffic, we impose no hard constraint on the latency of BE traffic.
 At each node of the ring, a contention buffer is filled by a batch arrival process of BE data.
-Then according to some parameters (fill rate and maximum waiting time) data on the contention buffer are aggregated in a packet of size at most $C$.
-The node fills the first free container it sees with this packet.
-Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a packet of BE messages in a node.
-This distribution is obtained by choosing optimal parameters for the contention buffer~\cite{youssef2018}.
+Then according to some parameters, fill rate and maximum waiting time, data on the contention buffer are aggregated in a packet of size at most $C$.
+The node fills the first container of its arc with this packet as soon as it is free.
+Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a packet of BE messages in a node~\cite{youssef2018}.
+This distribution is obtained by choosing the N-GREEN parameters for the contention buffer.
 
@@
 
+   \vspace{0.5cm}
+  \hspace{-0.75cm}
     \begin{minipage}[b]{0.50\linewidth}
@@
   \begin{minipage}[b]{0.40\linewidth}
-  \vspace{-2cm}
-  \scalebox{0.7}
+
+  \scalebox{0.65}
   {
+
   \centering
@@
   }
-  \vspace{0.3cm}
+
   \captionof{figure}{Experimental parameters from the N-GREEN architecture}\label{fig:params}
@@
 A container which is reserved cannot be filled by any node except the one which has reserved it.
-In the method we now describe, the C-RAN packets never wait in the node: The message sent by the RRH $i$ arrives at its BBU at time $m_i + \omega(u,v)$ and the answer is sent from the BBU at time $m_i + \omega(u,v) +1$.
+In the method we now describe, the C-RAN packets never wait in the node: The message sent by the RRH $i$ arrives at its BBU at node $v$ at time $m_i + \omega(u,v)$ and the answer is sent from the BBU at time $m_i + \omega(u,v) +1$.
 
@@
 Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive unit of time, a RRH needs one container by slot.
- If a RRH emits at time $m_i < P$, then we say it has \textbf{position} $m_i \mod F$.
-If a RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1 \mod F$.
+ If a RRH emits at time $m_i < P$, then we say it has \textbf{position} $m_i~mod~F$.
+If a RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1~mod~F$.
 Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position during all the period.
@@
 \begin{prop}
+\label{prop:assign}
 There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if  $k\times ET + RS \leq P$.
@@
 The assignment is correct, if when the RRH $1$ must emit something in the second period, there is a free container.
-It implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.
+It implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.\qed
 \end{proof}
 
-Remark that for each position which is used by some RRH, we lose $2RS$ because of the reservation of the RRH and of its BBU.
-Therefore to not waste bandwidth, it is relevant to put as many RRH as possible on the same position.
-Moreover unused positions in an assignment are useful to guarantee a good latency to BE traffic.
-The unused positions can be distributed uniformly over a slot, to minimize the time to wait before a free slot, as in Fig.~\ref{fig:repart1}.
+\begin{corollary}
+The number of antennas supported by a ring is $K = \lfloor\frac{P- RS}{ET}\rfloor \times \frac{F}{2}$
+\end{corollary}
+\begin{proof}
+Following Prop.~\ref{prop:assign}, the number of antennas on a position is $k = \lfloor\frac{P- RS}{ET}\rfloor $.
+Since we need two positions for $k$ antennas, in order to carry the traffic coming from the RRHs and the BBUs, and we got $F$ positions in the slot, the number of antennas supported by the ring is thus equal to $k \times \frac{F}{2}$.\qed
+\end{proof}
+Remark that for each position which is used by some RRH, $RS$ containers are reserved before starting to emit some C-RAN traffic.
+Those containers which are reserved could either be free or freed during the next round trip.
+Thus, those containers are seen by the BE traffic as additional dataflow.
+Therefore to not waste much bandwidth, it is relevant to put as many RRH as possible on the same position.
+Moreover, unused positions in an assignment are useful to guarantee a good latency to BE traffic.
+The unused positions can be distributed uniformly over a slot, to minimize the time to wait before a free container, as shown in Fig.~\ref{fig:repart1}.
 
@@
 
-We present the cumulative distribution of the latency of the BE traffic latency using the FIFO rule or the reservation algorithm proposed here in
-Fig.~\ref{fig:optimres}.
-Since the previous parameters were too restrictive to put several RRHs on the same position, the parameters $ET$ and $n$ have been changed to respectively $200$ and $12$, to keep the same expected load.
-With these parameters, the loss of bandwidth due to reservation is at most $6\%$.
+     \begin{minipage}[b]{0.5\linewidth}
+        \begin{center}
+      \includegraphics[scale=0.55]{repart2}
 
-  \begin{minipage}[b]{0.4\linewidth}
+      \captionof{figure}{Repartition in the slot}    \label{fig:repart1}
+      \end{center} 
+  \end{minipage}
+    \begin{minipage}[b]{0.5\linewidth}
+        \begin{center}
+      \includegraphics[scale=0.55]{repart1}
+
+      \captionof{figure}{Repartition in the period}    \label{fig:repart2}
+      \end{center} 
+  \end{minipage}
+
+In order to evaluate the performances of those methods, we present the cumulative distribution of the latency of the BE traffic latency when the C-RAN traffic is distributed in the slot, or in the period in Fig.~\ref{fig:algocmp}.
+Since the previous N-GREEN parameters were too restrictive to put several RRHs on the same position, the parameters $ET$ and has been changed to $400$.
+
+As expected, both of the presented method to optimize the BE traffic latency in the ring are efficient.
+Indeed, if all the C-RAN packets are sent in the same moment of the period, the chances of having a free container for a BE packet are low.
+Here, we try to distribute as much as possible the free containers.
+However, it is important to precise that the parameters induce that there is no free positions during $ET+RS$ unit of time when no repartition is done.
+This is why the performances of the corresponding curve are so weak.
+
+Since we have observe that the two repartitions are effective, we want to combine them for our {\em reservation algorithm}.
+We compare the cumulative distribution of the latency of the BE traffic using the FIFO rule or the reservation algorithm proposed here in Fig.~\ref{fig:optimres}.
+To keep the same expected load than the load of the experiment if Fig.~\ref{fig:resultopport}, we set $ET = 200$ and $n = 12$.
+This is not out of context since the exact split (the C-RAN split is the degree of centralization of the computation units in the cloud) of the C-RAN is not fully determined yet~\cite{mobile2011c}.
+With these parameters, the loss of bandwidth due to reservation is at most $6\%$
+
+  \begin{minipage}[b]{0.45\linewidth}
+\centering
+      \includegraphics[scale=0.25]{repart1res}
+     \captionof{figure}{Impact of the repartition on the latency.}   \label{fig:algocmp}
+  \end{minipage} 
+  \hfill
+  \begin{minipage}[b]{0.45\linewidth}
 \centering
@@
      \captionof{figure}{Impact of the deterministic method on the traffics.}   \label{fig:optimres}
-  \end{minipage} 
-     \begin{minipage}[b]{0.3\linewidth}
-        \begin{center}
-      \includegraphics[scale=0.55]{repart2}
-            \vspace{0.5cm}
-      \captionof{figure}{Repartition in the slot}    \label{fig:repart1}
-      \end{center} 
-  \end{minipage}
-    \begin{minipage}[b]{0.30\linewidth}
-        \begin{center}
-      \includegraphics[scale=0.55]{repart1}
-      \vspace{1cm}
-      \captionof{figure}{Repartition in the period}    \label{fig:repart2}
-      \end{center} 
   \end{minipage}

### 2018-06-04 ISCIS/model.tex
iscis

\documentclass[a4paper,10pt,english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[english]{babel}

\usepackage{xspace}
\usepackage{graphicx,graphics} 
\usepackage{hyperref} 
\usepackage{mathtools, bm}
\usepackage{amssymb, bm}
\usepackage{complexity}
\usepackage{amsthm}
\usepackage{authblk}
\usepackage{color}
\usepackage{amsmath}

\newcommand\pall{\textsc{pall}\xspace}

\newcommand{\todo}[1]{{\color{red} TODO: {#1}}}
\newtheorem{prop}{Proposition}

\graphicspath{{img/}}

%opening
\title{Contention management for Cloud Ran over an optical ring}

\author[1]{Dominique Barth}
\author[2]{Dominique Chiaroni ?}
\author[1]{Ma\"el Guiraud}
\author[1]{Yann Strozecki}
\affil[1]{David Laboratory, UVSQ}
\affil[2]{Nokia Bell Labs France}

\begin{document}

\maketitle

\section{Description of the network, model, problem}

    Our study takes place in the Cloud-RAN context. The purpose is to centralise the calculation units of some antennas, distributed on the field. To each antenna, called RRH (Remote Radio Head), is associated a BBU (BaseBand Unit) in the datacenter.
      The periodic process is the following: each {\bf period $P$}, every RRH (also called antennas) send some datas thought the ring to it's BBU, then, after a computation time in the BBU, this latter answers to the corresponding RRH. 
      The time between the emission of the message by the RRH and the reception of the answers by the same RRH is called {\bf process time} and must not be too large, considering some 5G standards. That is why the message might be as litle buffered as possible into the nodes, in order to decrease the latency, and thus, the process time of the messages.
      In this paper we will consider that all the BBU are grouped in the same node, called {\bf datacenter}, and that the antennas are distributed on the others node of the ring.
      \todo{je pense que ce paragraphe n'est utile que dans le deliverable, sinon je dois mettre l'equivalent dans l'intro}

  \subsubsection{Network modeling}

   In this entire subsection, the ring is in broadcast and select mode with an emission release policy. We first propose an algorithmic model for the ring. In ~\ref{sec:oportmethods}, we study the behavior of the ring with an opportunistic insertion policies, in which the insertion buffer is managed by two different methods. Finally, we propose and study in ~\ref{sec:deterministicalgorithms} some algorithm allowing the C-RAN PDUs to have $0$ sojourn time in the stations, while the BE PDUs are as little buffered as possible.

The model exposed here has already been studied for another particular topology of network and with different problematics from the ones of this paper. One can find in \cite{latency2017} the complexity results on the problem proposed, and some algorithmic solutions to solve it in star networks.

The network is modeled as a directed graph $G=(V,A)$. Each arc  $(u,v)$ in $A$ is labeled by an integer weight $\omega(u,v)$ which represents the time taken by a message to go from $u$ to $v$ using this arc. A {\bf route} $r$ in $G$ is a directed path, that is, a sequence of adjacent vertices $u_0, \ldots , u_{k}$, with $(u_i,u_{i+1}) \in A$.  The {\bf latency} of a vertex $u_i$ in a path $r$ is defined by $\lambda(u_i,r)= \sum\limits_{0 \leq j <i} \omega(u_j, u_{j+1})$. We also define $\lambda(u_0,r)=0$. The length of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.
We denote by $\cal R$ a set of routes, the pair $(G,\cal R)$ is called a {\bf routed network} and represents our telecommunication network.

   In the context of Cloud-RAN applications, we need to send a message from an RRH $u$ to a BBU $v$ and then 
      we must send the answer from $v$ back to $u$. We denote by $n$ the number of couple RRH-BBU. We say that a routed network $(G, {\cal R})$ is \textbf{symmetric} if the set of routes is partitioned into the sets $F$ of \textbf{forward routes} and $B$ of \textbf{backward routes}. There is a bijection $\rho$ between $F$ and $B$ such that for any forward route $r \in F$ with first vertex $u$ and last vertex $v$, the backward route $\rho(r) \in B$ has first vertex $v$ and last vertex $u$.

\paragraph{Messages dynamic}

      In the process we study, a message is sent on each route at each period, denoted by $P$. The time is discretized, i.e. a period is sliced into $P$ {\bf slots}. 
      Let $r$ be a route, if a message is sent at time $m$ from $s$ the first vertex of $r$ then it will arrive at vertex $v$ in $r$ at time $m + \lambda(v,r)$. Since the process is periodic, if the message from $r$ goes through an arc at time $t\in [0,P-1]$, then it goes through the same arc at time $t+kP$ for all positive integers $k$. Therefore, every time value can be computed modulo $P$ and we say that the first time slot at which a message sent at time $m$ on $r$ reaches a vertex $v$ in $r$ is $t(v,r) = m + \lambda(v,r)\mod P$.

 A message usually cannot be transported in a single time slot. Let us call $[t(v,r)]_{P}$ the set of time slots used by route $r$ at vertex $v$ in a period $P$, that is $[t(v,r)]_{P} = t(v,r)  \mod P $. Let $r_1$ and $r_2$ be two routes, on which messages are sent at time $m_1$ and $m_2$ in their first vertex.
      We say that the two routes have a {\bf collision} if they share an arc $(v,w)$ and $[t(v,r_{1})]_{P} \cap [t(v,r_{2})]_{P} \neq \emptyset$.

         A {\bf $P$-periodic assignment} of a routed network $(G,\cal R)$ is a function that associates to each route 
         $r \in \cal R$ its \textbf{offset} $m_r$ that is the time at which a message is emitted at the first vertex of the route $r$.  In a $P$-periodic assignment, \emph{no pair of routes has a collision}.

                     Let us give an interpretation of a $P$-periodic assignment of $(G,{\cal R})$ a symmetric routed network, so that it represents the sending of a message and of its answer.
	First a message is sent at $u$, through the route $r \in F$, at time $m_r$.
      This message is received by $v$, i.e., the last vertex of $r$ at time $t(v,r)$. It is then sent back to $u$ on the route $\rho(r)$ in the same period at time $m_{\rho(r)}$ if $m_{\rho(r)} > t(v,r)$, otherwise at time $m_{\rho(r)}$ in the next period. The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_r = m_{\rho(r)} - t(v,r)$ if $m_{\rho(r)} > t(v,r)$ and $w_r = m_{\rho(r)} + P - t(v,r)$ otherwise.
      \begin{figure}[h]
      \begin{center}
      \includegraphics[width=0.9\textwidth]{rrh.pdf}
      \end{center}
      \caption{The process defined by a $P$-periodic assignment}
      \end{figure}

The process time for a message sent on the route $r$ is equal to $PT(r)=\lambda(r)+ w_r+\lambda(r)$. Each route must respect some time limit that we call a \emph{deadline}. To represent these deadlines, 
      we use a deadline function $d$, which maps to each route $r$ an integer such that $PT(r)$ must be less than $d(r)$.
    We can now define a first problem:

      \noindent {\bf Periodic Assignment for Low Latency (\pall)}

      \noindent {\bf Input:}  A symmetric routed network $(G,{\cal R})$, the integers $P$ and a deadline function $d$.

      \noindent {\bf Question:} does there exist a $P$-periodic assignment $m$ of $(G,{\cal R})$ such that for all $r \in {\cal R}$, $PT(r) \leq d(r)$?

It turns out that the problem \pall is $\NP$-hard to solve and even to approximate for \emph{general} routed networks, and for the simplified version presented here~\cite{latency2017}.

  \paragraph{N-GREEN Optical ring}

 We now consider $G$ as a circular digraph $C_N$ representing an unidirectional optical ring. The vertices of the graph represents the nodes of the ring. In our study, we want to focus on the ring only. Thus, we ignore the external network and we consider that, the first and last vertex , $u$ and $v$ of the routes are some nodes of the ring. We consider a symmetric routed network. For each forward route $r$, the backward route $\rho(r)$ is the other part of the ring. Consequently, for each route $r$, $\lambda(r) + \lambda(\rho(r)) = RS$, where $RS$ is the size of the ring. In our experiments, we consider only one datacenter into the ring. This mean that all the forward routes have the same destination nodes, and all the backward routes have the same source node.

  % Once a packet is inserted in a slot on the ring, by a node, no other nodes are able to write on this slot. This packets can contain some data from several nodes on the ring, that are able to read in the packet. The only node which has the right to remove the packet from the slot is the owner. This mean that every packet makes exactly one lap of the ring. Furthermore, to write on a slot, a node has to have an empty slot in it's writing slot.
% \subsection{Message Granularity}
% Each arc $(u,v)$ can be represented as a sequence of slots $\{s_1, ... , s_k\}$, with $k = \omega(u,v)$. We denote by $s_n(u,v)$ the $n^{th}$ slot of the arc $(u,v)$. $s_i(v), i\in \{-\omega(u,v), ... , -1\} \cup \{1 , ... , \omega(v,w)\}$ is the $i^{th}$ slot after (before if $i<0$) v on the ring.
%    On the following example, the red slot can be denoted by $s_2(u,v)$, $s_2(u)$ or $s_{-6}(v)$. 
%    \begin{figure}[h]
%    \centering
%      \includegraphics[scale=0.5]{suv.pdf}
%
%      \caption{A link $(u,v)$ represented as a sequence of slots}
%  \end{figure}
%  
%  Each node $v$ has a reading access on $s_{-1}(v)$ and a writing access on $s_{1}(v)$. Those slots are named respectively the reading and writing slots of $v$. Thus, during a time slot, a node $v$ can insert a {\bf container} on it's writing slot, if it is allowed to. At the end of the time slot, each packets rotate to the next slot. A packet emitted by a node $u$ on it's writing slot $s_1(u)$ will be available in reading for a node $v$ on it's reading slot, $s_{-1}(v)$, $d(u,v) -1$  time slots later.
%\begin{figure}[h!]
%      \includegraphics[scale=0.5]{anneau1.pdf}
%      \hspace{3cm}
%      \includegraphics[scale=0.5]{anneau2.pdf}
%      \caption{One rotation of the ring}
%  \end{figure}

\paragraph{Into the node : Two kind of traffics}
  In this study, we focus on the behavior of the N-GREEN optical ring. Therefore, we do not want to consider the issues caused by the upstream network. 
   To refine our model around the N-GREEN study, one must consider the opto-electronic stations behavior.
   Each N-GREEN station is connected to at least one electronic interface of rate $D$. as mentioned in sec.\ref{com-mod} a station is able to use all the $K$ channels during a slot of duration $Z/KD$ to send a container of capacity $Z$ which contain all the data received  by an electronic interface during a macro-slot, that is, the time needed to fill a container at rate $D$, i.e. $Z/D$
  In other words, an N-GREEN station is able to fill a PDU with the datas received during a macro-slot in the electronic domain.

\begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.3]{slot1.pdf}
  \includegraphics[scale=0.3]{slot2.pdf}
     \caption{Opto-electronic interface.}

\end{center}
  \end{figure}

      An N-GREEN station deals with two kinds of traffics. Some C-RAN and some Best Effort. We assume that each traffic has its corresponding electronic interface. Also, a C-RAN message is of size $Z $ and completely fills a container let us call {\bf C-RAN PDU} such a message. In the same time, the Best Effort SDUs are buffered in a first {\em gathering buffer} before being gathered together into a {\bf BE PDU}. Once the PDUs are created, there join the {\em contention buffer} before being sent in the ring.
      \begin{figure}[h!]
\begin{center}   
  \includegraphics[scale=0.7]{buffers.pdf}
     \caption{An N-GREEN station.}

\end{center}
  \end{figure}

 In this study, we measure the sojourn time $W$ of a PDU in a station. The model we consider in our experiments to generate the BE PDUs is described in sec~\ref{jmf}.

 \paragraph{C-RAN PDU generation model} An RRH usually emit an huge quantity of information during a long time. Also, as we just see, an RRH can send no more than a PDU every $10\mu s$ on the ring. This gap between two PDU from the same RRH is defined by $K$, the number of channels considered in the ring.
 We denote by $ET$,for {\bf Emission time}, the time during which an RRH emits a PDU every $K$ slots on the ring. An RRH emits $\frac{ET}{K}$ PDUs on the ring, every period $P$.

        \begin{figure}[h!]
\begin{center}

      \includegraphics[width=\textwidth]{emission_antenna.pdf}
     \caption{C-RAN PDU generation.}
\end{center}
  \end{figure}
  \paragraph{Back and forth communications} As we explained in the introduction of this section, once the datacenter receives some PDUs from an RRH, it computes an answer and send it to the RRH through the ring. To simplify our model, we assume that the computation times is the same for all BBUs and that it is a multiple of the period. In this situation, we can assume that, each time the datacenter receives a container with a C-RAN PDU from an RRH, it immediately sends an answer (which is in fact the answer to the two periods ago C-RAN PDU's).

 The behavior of the C-RAN PDU generation leads us a new problem, similar to \pall. The set of time slots used by route $r$ at vertex $v$ in a period $P$, is now defined by $[t(v,r)]_{P,K} = \{t(v,r) +i \mod P \mid i \in \{0,EP,2\times K,...., \frac{ET}{K}\times K\} \}$. Consequently, we now want to find a $(P,ET)$-periodic assignment that set the offsets of the routes $m_r$, such that there is no collision between two routes $r_1$ and $r_2$, that is, $[t(v,r_{1})]_{P,K} \cap [t(v,r_{2})]_{P,K} \neq \emptyset$.

 The rest of this study is divided in two parts. In a first time, we look at the behavior of the ring and the impact of the PDUs sojourn time with two different method of managing the contention buffer. Then, we propose some algorithms that solve the previous problem of finding a $(P,ET)$-periodic assignment for the C-RAN PDUs and we compare the impact of those different algorithms on the BE PDUs sojourn time.

  \paragraph{Parameters of the study}
  \label{sec:parameters} The experiment of this subsections are made following the same parameters, until sec~\ref{sec:optialgo}. We set $K = 10$ chanels, some electronic interface of rate $D=10$Gbps and $Z = 12500$B so, $Z/KD = 1\mu$s. The optical ring has a rate $KD=100$Gbps, while a slots has a duration of $1\mu$s. The length of the ring is to $20$km in our simulations, this means that the ring has a length of $RS = 100$ slots. We consider some BE SDUs of $125$B, and we parametrized BE PDU generator of sec~\ref{jmf} such that each station load the network with an average of $3,5\%$ of BE traffic. We set $ET = 500$ slots, that correspond to a C-RAN traffic of $5$Gbps. The period  $P$ is to $1$ms, that is $1000$ slots. We set the number of RRH to $n=5$. We take $5$ stations and one of them is the datacenter. The antennas are apportioned between the others station. With those parameters, the network is theoretically loaded to $67.5\%$.

  \begin{figure}
  \centering
  \begin{tabular}{|c|c|}
  \hline
 Number of channels $K$ & $10$  \tabularnewline
  \hline
  Rate of an electronic interface $D$ & $10$ Gbps \tabularnewline
  \hline
  Container size  $Z$ & $12,500$ B  \tabularnewline
  \hline
  Slot duration $Z/KD$ & $1\mu$s \tabularnewline
  \hline
  Optical ring rate $KD$ & $100$ Gbps \tabularnewline
  \hline
  Length of the ring $RS$ & $100$ slots \tabularnewline
  \hline
  BE SDU size & $125$B \tabularnewline
  \hline
  C-RAN PDU size & $12,500$B$=Z$ \tabularnewline
  \hline
  Emission time $ET$ & $500$ slots \tabularnewline
  \hline
   Period $P$ & $1,000$ slots \tabularnewline
  \hline
  Number of RRH & $5$  \tabularnewline
  \hline
  Number of stations $n$ & $5$  \tabularnewline
  \hline

  \end{tabular}
  \caption{Parameters of the following experiments based on N-GREEN}\label{parameters}
  \end{figure}

   \subsubsection{Performance evaluation of the N-GREEN optical ring}
   \label{sec:oportmethods}
   In a first time, we will look at the performance of the N-GREEN optical ring with an opportunistic insertion policy \ref{com-mod}. When a station wants to send a PDU on the ring, it uses the first available container .
    We study the performance of the ring through two methods; a full opportunistic method, and a method that prioritize the C-RAN PDUs. Since we only consider some PDUs arrivals, those two methods are some variants of the management of the PDUs in the station.
   For those two methods, the offsets $m_r$ of the routes are chosen randomly in the period, i.e. we do not choose the first time at which the RRH start to emit.
   Since we do not manage those offsets, the two following methods do not gives us some $(P-ET)$-periodic assignment. No choices are made on the offsets and thus, two routes can collides.

    \paragraph{Full opportunistic method}
    \label{sec:fullopport}
    We first want to look at a simple configuration in which we do not manage the PUDs (BE or C-RAN) arriving into a station. At their arrival, the BE and C-RAN PDUS are buffered in the contention buffer, and this buffer is emptied following the FIFO rule.

The following experiment shows us the performance this {\bf full opportunistic method} with some parameters issued from N-GREEN. 
On fig~\ref{fig:oport}, one can see the cumulative distribution of the sojourn times of the C-RAN and BE PDUs. Those results are computed on $100$ instances of optical rings that have run during $10,000,000$ slots. The measures are taken after $3,000$ slots of simulation, to let the ring initialize it's behavior. The parameters of the simulations are stated in sec~\ref{sec:parameters}.

    \begin{figure}[h!]
    \label{fig:oport}
        \begin{center}
      \includegraphics[scale=0.4]{oport}

      \caption{Full opportunistic method performances.}
      \end{center}
  \end{figure}

  As we can see on fig~\ref{fig:oport}, the sojourn times for the different kind of PDU is notably similar because we do not manage anything. Furthermore, we can remark that about $10\%$ of the C-RAN messages wait over $100$ms, that is already critical for C-RAN \todo{ref}.

\paragraph{C-RAN priority method}
\label{sec:cranprio}
  In order to improve the C-RAN PDUs sojourn time, we imagined the following solution, called {\bf C-RAN priority method}. Each stations have two contention buffers. One for the BE PDUs, and one fore the C-RAN PDUs. When a station is able to send a PDU on the ring, i.e. its available container free, the container is filled with the C-RAN PDUs first.

    \begin{figure}[h]
\begin{center}   
      \includegraphics[scale=0.7]{cranprio.pdf}
     \caption{C-RAN priority method.}
\end{center}
  \end{figure}

  With this method, one can imagine improve the sojour time of the C-RAN PDUs. Fig~\ref{fig:prior} shows us the performance of the C-RAN priority algorithm for different kinds of traffics. The parameters of the simulations still the same, stated in sec~\ref{sec:parameters}.
      \begin{figure}[h]
      \label{fig:prior}
\begin{center}

      \includegraphics[scale=0.4]{prior.pdf}

     \caption{C-RAN priority method performances.}
\end{center}
  \end{figure}

  As expected, the sojourn time of the C-RAN PDUs is decreased compared to the full opportunistic method. Nevertheless, there is still $10\%$ of the C-RAN PDUs that have more than $50 \mu$s of latency, and the best effort PDUs are penalized, indeed, close to $10\%$ of the BE PDUs awaits more than $150\mu$s before being sent in the ring, versus close to $0\%$ with the previous method..
  Thus, we propose a deterministic approach in which we set the offsets of the RRH and we reserve the containers needed for the C-RAN PDUs.
   \todo{il manque une partie sur le travail de karim, }
  \subsubsection{Deterministic approach for $0$ sojourn time on C-RAN}
\label{sec:deterministicalgorithms}

 For the rest of the subsection, the policy of slot insertion is the slot reservation. We are still in emission release policy. We present three algorithms that allows the C-RAN PDUs to have $0$ sojourn time in the insertion buffers by establishing a static reservation of the slots in the period.
 Those algorithm are {\bf Centralized} and requires a global supervisor of the network to be implemented .\todo{phrase + ref sdn?}

\paragraph{Slot reservation} To decrease the C-RAN messages sojourn time, one plan to reserve the container for the stations. Indeed, if a station $i$ needs to send a PDU at time $t$, a container needs to be reserved since the previous lap of the container, i.e. at time $t - RS$ by $i$. In this situation, if the container is already taken by a PDU which has been sent by a station $j$, $j$ will remove the PDU of the container during the next lap of the ring, and no other stations are able to write in this container before it comes back to the station $i$ a date $t$. By finding a $(P,ET)$-periodic assignment and reserving the corresponding container, we allow the C-RAN PDUs to have $0$ sojourn time in the stations. Though, it impacts the best effort PDUs, by avoiding them to use free reserved containers. It is equivalent to increase the load of the network, without increasing the number of PDUs carried by the network.

\paragraph{RRHs synchronisations}
This slot reservation implies that the RRHs are synchronized with the ring. The following proposed algorithms set a sequence of reserved slots for each RRH in each period. A technical application implies to simultaneously ensure the reservation of the slot to the given dates, and the synchronization of the RRH with those reserved slot. One must ensure that the C-RAN PDU arrives in the contention buffer of the station just before the reserved container.

In this section, we explain the different algorithm we use to ensure $0$ sojourn time on C-RAN PDUs and we study their impact on the BE PDUs sojourn times.

Unlike the previous methods with opportunistic insertion policy, we now want to choose a $(P,ET)$-periodic assignment for the routed network $(G,{\cal R})$. Since all the forward routes have the same last vertex $v$ (the datacenter), which is also the first vertex of all the backward routes, we choose to manage the collision in this vertex only. The purpose is to determine the time $t(v,r_i)$ at which the first C-RAN PDU of the route $i$ arrives at the datacenter $v$ for each routes $i$, such that there is no collisions between the routes. Let us call BBU-offset this time. Once the BBU-offsets are set, for all routes $i$, it is easy to compute $m_{r_i} = t(v,r_i) - \lambda(v,r_i)$.

\paragraph{An approach based on N-GREEN parameters}
An RRH can not emit a message more often than once slot every $K$ slots. Remember that {\bf macro slot} is a duration of $K$ slots, during which each RRH can emit at most once. Thus, we consider the simple case in which there is less C-RAN traffic than slots in a macro slot. Indeed, in that case, if we manage the collision in one macro slot, i.e. we assign a C-RAN traffic to each slot of the macro-slot, we find a  $(P,ET)$-periodic assignment. Since a BBU always instantly emits an answer to it's RRH, for each RRH, a group of two following containers (called {\bf bunch}) can be reserved. Thus, we first study the case $K \ge 2\times n$. As a reminder, $n$ is the number of couple BBU-RRH.

 Because there is at most as much couples BBU-RRH as bunches, we want to assign one RRH to one bunch.
We propose the following {\bf naive reservation algorithm}. For each RRH $i, i\in \{0,...,n-1\} $, set $t(v,r_i)= 2\times i$ with $v$ the vertex of the BBUs. The model automatically fixes the offset of the backward route $\rho(r_i)$ to $m_{\rho(r_i)}= 2\times i +1$. This is the reason why we do not care about the backward routes anymore, and we only deal with the BBU-offsets of the forward routes..
   \begin{figure}[h]

      \includegraphics[scale=0.7]{freqgrouped.pdf}
     \caption{Grouped assignment of the bunches to the RRH.}   \label{fig:freqG}
  \end{figure}

We kept the same parameters than in the two previous experiments (see~\ref{sec:parameters}) and we made an experiment to show the impact of this algorithm on the BE traffic. Fig~\ref{fig:res1} shows us the distribution of the sojourn time for BE PDUs with this algorithm.

      \begin{figure}[h]
\centering
      \includegraphics[scale=0.4]{res1.pdf}
     \caption{Impact of the naive reservation algorithm on the Best effort PDUs.}   \label{fig:res1}
  \end{figure}

As we can see, the BE traffic is highly penalized by this algorithm, indeed, while almost $100\%$ of the BE PDUs have a sojourn time to less than $200 \mu$s with the full opportunistic method (see fig~\ref{fig:oport}), here, more than half of the BE PDUs are be buffered more than $200\mu s$. Those performances are explained by the structure of the algorithm. The messages are grouped together, and with our parameters, $K = 2\times n$. It creates a long sequence of slots during which there is no free containers in the ring.

To improve the BE PDUs sojourn time, we propose a {\bf splited reservation algorithm} that balances the load of the CRAN traffic over the period. Instead of giving some close BBU-offsets for all routes $i$, with $v$ the datacenter, we now uniformly distribute the different BBU-offsets in the period. Each couple BBU-RRH is still assigned to its bunch, but we split the BBU-offsets of $\frac{P}{n}$, that is $t(v,r_i)= 2\times i+ i\times \frac{P}{n}$, with $i \in \{0,...,n-1\}$.

   \begin{figure}[!h]

      \includegraphics[scale=0.7]{freqsplited.pdf}
     \caption{Splited assignment of the bunches to the RRH.}   \label{fig:freqS}
  \end{figure}

  On fig~\ref{fig:res2} one can observe the performance of this algorithm on the BE PDUs sojourn time. Once again, to have a reference point, we take the same parameters for the simulation.

 \begin{figure}[h]
\centering
      \includegraphics[scale=0.4]{res2.pdf}
     \caption{Impact of the splited reservation algorithm on the Best effort.}   \label{fig:res2}
  \end{figure}

  As we can see, the sojourn time of the BE PDUs is highly better with this this algorithm. Indeed almost $100\%$ of CRAN PDUs have a sojourn time of less than $50\mu$s which is better than the full opportunistic method. Thus, we decreased the latency of every kind of traffic.

\paragraph{With more antennas}
\label{sec:optialgo}
 In this section, we study the case $n > \frac{K}{2}$, we want to assign more than one RRH to a bunch. 
 Let us consider a particular behavior of the ring. Instinctively, we can think that if we have enough space in the period for many traffics on the same frequency that is, $ET \le \frac{P}{2}$, we can assign several couples BBU-RRH to the same bunch.

 Let us take $ET =  \frac{P}{2}$ and $n = \frac{K}{2} + 1$. We assign a bunch to each $\frac{K}{2}$ first RRH and we have only one RRH left. Then, we only look at one bunch, on which we want to add the new couple BBU-RRH.

 We take a ring with two stations $A$ and $B$. We simplify the model to only look at the behavior of one bunch, thus, both of the nodes alternatively emits some containers every slots, during $ET$ slots in the period $P$. By construction, we allow $A$ to emit a time $1$ during $ET$ slots. This container arrives in $B$ at $\omega(A,B)$, that is  $[t(B,r_A)]_{P,K} = [\omega(A,B);\omega(A,B)+ET]$. Then, $B$ can immediately emit its containers at time $\omega(A,B)+ET$. This containers from $B$ arrives at $A$ at time $\omega(A,B)+ET + \omega(B,A) = ET + RS$, and thus, $[t(A,r_B)]_{P,K} = [ET + RS;ET + RS + ET] = [ET+RS; RS + P] = [ET + RS; RS] \mod P$. Since $[t(A,r_A)]_{P,K} = [1;ET]$, there is a collision at the interval $[1;RS]$ in the period between the two routes $A$ and $B$.
  \begin{figure}[h]
\centering
      \includegraphics[scale=0.7]{rs.pdf}
     \caption{Collision between two routes on the same bunch when the period is too small.}   \label{fig:proofrs}
  \end{figure}

 As we have just noted, if several RRH share the same bunch, the period must have an additional budget in addition to the time needed to send the messages. Let us study the size of the additional budget.
 \begin{prop}
 If several RRH shares a bunch, it is possible to find a $(P,ET)$-periodic assignment if $P \ge n\times ET + RS$ , with $n$ the number of RRHs.
 \end{prop}
 \begin{proof}
 We seek to show that proposition by induction.

 {\bf Base case:} For $n = 2$, the proof of the previous example shows us that it is possible to assign two RRH on the same bunch with $P = 2\times ET + RS$.

 {\bf Induction step:}  We consider that we have a frequency shared by $n$ RRH, with a period of size $P= n\times ET + RS$. We want to show that if we want to add one antenna to the bunch, we need a period of size at least $P = (n+1)\times ET + RS$. If we look at the sequence period of the bunch with $n$ RRH. We can observe that this sequence is the same in every station, shifted of the length of the routes between two stations. For instance, if we take two stations $A$ and $B$, the sequence in $A$ is the same that the sequence in $B$ shifted of $\omega(A,B)$.

   \begin{figure}[h]
\centering
      \includegraphics[scale=0.7]{period1.pdf}
     \caption{An example of sequence with n = 3.}   \label{fig:proofperiod1}
  \end{figure}

 Thus, if we add $ET$ slots in this frequency, the periodic emissions of all others nodes are not impacted, there is just a new interval in the sequence.

   \begin{figure}[h]
\centering
      \includegraphics[scale=0.7]{period2.pdf}
     \caption{The same sequence with n = 4.}   \label{fig:proofperiod2}
  \end{figure}
  Note that a station can send some traffic from more than one antenna, the figures ~\ref{fig:proofperiod1} and \~ref{fig:proofperiod2} are just an example, but this proof stays the same.
 \end{proof}

Considering those results, we propose an algorithm to allow several RRH to share the same bunch, as long as $P \ge n\times ET + RS$. 
Since we need $RS$ slots on a each bunch with at least an RRH to assign another RRH to this latter, it is interesting to fill as far as possible the bunches. We then compute the number of bunches needed to carry the number of RRH $n$. Then, the algorithms tries to balance those bunches into the macro-slot, i.e. it avoids to group the used bunches together.
The used bunches have $RS$ or more free slots in the period. Thus, the algorithm subsequently balance BBU-offsets of the first RRH of each bunch, with the same idea than the splited algorithm. We call this algorithm the {\bf full repartition algorithm}.

   \begin{figure}[h]
\centering
      \includegraphics[scale=0.7]{optimalgo.pdf}
     \caption{Organization of the bunches with the balancing algorithm.}   \label{fig:optimalgo}
  \end{figure}

  We want to observe the impact of this algorithm on BE traffic. Since our previous parameters did not allow several RRH to share a frequency, we now set $ET = 200$, that correspond to a C-RAN flow of $2$Gbps. This is not out of context since the exact split (the C-RAN split is the degree of centralization of the computation units in the cloud) of the C-RAN is not fully determined yet~\cite{REF}.\todo {la ref} To keep a load similar to the load in the previous experiment, we set the number of antennas to $n=12$. The others parameters are all the one described in the sec~\ref{sec:parameters}.
  The following experiment shows us the impact of the balancing algorithm on the BE traffics. We chose to compare those results to a simulation with the same parameters but with the full opportunistic method of sec~\ref{sec:cranprio}.

   \begin{figure}[h]
\centering
      \includegraphics[scale=0.4]{optim.pdf}
     \caption{Balancing algorithm performance on the N-GREEN optical ring.}   \label{fig:optimres}
  \end{figure}

  As fig~\ref{fig:optimres} shows, the full repartition algorithm ensures a lower sojourn time to BE PDUs than the full opportunistic method, which gave the best result for the BE traffic. Indeed, since we remove the random aspect of the C-RAN PDUs generation, we balanced the load over the period an then increased the BE performances while we totally removed the C-RAN PDUs sojourn time.

  \bibliographystyle{ieeetr}
\bibliography{src}

\end{document}

### 2018-06-06 ISCIS/article.tex

@@
 We study the compatibility of such a technology with the development of the Cloud RAN, a latency critical application which is a major aspect of 5G deployment.
-We show that deterministically managing Cloud RAN traffic minimizes its latency without impacting the latency of others traffics.
+We show that deterministically managing Cloud RAN traffic minimizes its latency while also improving the latency of the others traffics.
 \keywords{Optical ring \and Latency \and C-RAN \and SDN}
@@
 
-Network\footnote{This work was developed around the ANR N-GREEN project.
-The authors thank the Nokia Bell Labs team for their collaboration.} providers have to design inexpensive networks supporting an increasing amount of data and online applications.
+\footnote{This work was developed around the ANR N-GREEN project.
+The authors thank the Nokia Bell Labs team for their collaboration.}Network providers have to design inexpensive networks supporting an increasing amount of data and online applications.
 Much of these applications have QoS criteria, like a minimal throughput or a maximal latency.
@@
 C-RAN is one of the major area of development for 5G; it consists in centralizing or partially centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
-The latency of the messages between the BBU and the RRH is critical~\cite{3gpp5g}.
+The latency of the messages between the BBU and the RRH is critical since some services need end-to-end latency as low as $1$ms~\cite{3gpp5g,boccardi2014five}.
 In this article we propose an SDN approach to deterministically manage the periodic C-RAN traffic by choosing emission timing and reserving containers on the ring.
 In a previous work~\cite{dominique2018deterministic}, the authors have studied a similar problem for a star shaped network.
-Here the load due to the CRAN traffic is small enough to make the problem easy.
+In contrast with our previous work, finding emmission timings so that different peridoic sources do not use the same ressource is easy in the context of the N-GREEN optical ring.
 However, we add several new difficulties: the messages from RRHs are scattered, there are other traffics whose latency must be preserved and the need to make reservation of containers on the ring requires additional bandwidth.
@@
 In Sec.~\ref{sec:model}, we model the optical ring and the traffic flow.
-In Sec.~\ref{sec:oportmethods}, we experimentally evaluate the latency when using stochastic multiplexing to manage packets insertions on the ring, with or without priority for C-RAN packets.
-In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantees the lowest possible latency.
-It turns out that it also improves the latency of best effort packets.
+In Sec.~\ref{sec:oportmethods}, we experimentally evaluate the latency when using stochastic multiplexing to manage packet insertions on the ring, with or without priority for C-RAN packets.
+In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantee to have zero latency from buffering.
+We propose several refinments of this determistic sending scheme to spread the load over time, which improves the latency of best effort packets.
 
@@
 The \textbf{ring size} is the length of the cycle, that is $\omega(u,u)$ and we denote it by $RS$.
-Each arc $(u,v)$ can be seen as a sequence of $\omega(u,v)$ {\bf containers}, of capacity $C$, expressed in Bytes.
-The containers are filled by the nodes.
-The node $u$ can put a data packet of size less than $C$ Bytes in the first container of the arc $(u,v)$ {\bf only if it is free}.
-  The dynamic of the network is simple: at each unit of time, the packet of a container go to the next container.
-   The ring follows a {\bf broadcast and select scheme with emission release policy}: When a container is filled by some node $u$,
-   it is freed when it comes back at $u$ after a whole round trip.
+A {\bf container}, of capacity $C$  expressed in Bytes, is a basic unit of data in the optical ring.
+
+  A unit of time corresponds to the time needed to fill a container with data:
+  The node $u$ can fill a container with a data packet of size less than $C$ Bytes at time $t$ if the container 
+  at position $u$ at time $t$ is \emph{free}.
+A container goes from $u$ to $v$ in $\omega(u,v)$ units of time.
+The ring follows a {\bf broadcast and select scheme with emission release policy}: When a container is filled by some node $u$, it is freed when it comes back at $u$ after a whole round trip.
 
@@
 The integer $F$ is called the {\bf acceleration factor} between the electronic and the optical domains.
-A node aggregates the data received on the electronic interface during $F$ unit of times to create a packet of size $C$ which completely fills one container of the ring.
+A node aggregates the data received on the electronic interface during $F$ units of time to create a packet of data of size $C$ and then fills a container of the ring with this data.
   In each period $P$, an RRH emits data during a time called \textbf{emission time} or $ET$.
 Hence the RRH emits $ET / F$ packets, i.e.
-a packet of size $C$ each $F$ units of time during the emission time, see Fig.~\ref{fig:interface}.
+a container of size $C$ each $F$ units of time during the emission time, see Fig.~\ref{fig:interface}.
    %Each period $P$, an RRH emits $ET / F$ packets, i.e. a packet of size $C$ each $F$ units of time during a time $ET$ (emission time),
 
-   The data of the RRH $i$ arrives at node $u$ at a time $m_i$ called {\bf offset}. The offsets can be determined 
-   by the designer of the system and can be different for each RRH but must remain the same over all periods. We assume that all 
-   BBUs are contained in the same data-center attached to the node $v$.
+   The data of the RRH $i$ arrives at some node $u$ at a time $m_i$ called {\bf offset}. The offsets can be determined 
+   by the designer of the system and can be different for each RRH but must remain the same over all periods.
+We assume that all BBUs are contained in the same data-center attached to the node $v$.
 The data from $u$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u,v)$ if it has been inserted in the ring upon arrival.
-Then after some computation time (which is supposed to be zero to simplify the presentation), an answer is sent back from the BBU to the RRH.
+Then after some computation time (which w.l.o.g.
+is supposed to be zero), an answer is sent back from the BBU to the RRH.
 The same quantity of data is emitted by each BBU or RRH during any period.
-   In this study the {\bf latency} of a message is defined as the time it waits in a node before being put in a free container on the ring.
-   The aim of our study is to minimize the latency of the C-RAN traffic, both from the RRHs and the BBUs. 
+   In this study the {\bf latency} of a message is defined as the time it waits in a node before being sent on the ring.
+   The aim of our study is to minimize the latency of the C-RAN traffic, both of the RRHs and the BBUs. 
    In Sec.~\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency which preserves the latency of other data using the optical ring.
@@
 At each node of the ring, a contention buffer is filled by a batch arrival process of BE data.
-Then according to some parameters, fill rate and maximum waiting time, data on the contention buffer are aggregated in a packet of size at most $C$.
-The node fills the first container of its arc with this packet as soon as it is free.
-Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a packet of BE messages in a node~\cite{youssef2018}.
-This distribution is obtained by choosing the N-GREEN parameters for the contention buffer.
+Then according to some parameters, fill rate and maximum waiting time, data on the contention buffer are aggregated in a container of size at most $C$.
+The node sends this container on the ring as soon as possible.
+Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a packet of BE messages in a node.
+The computation of this distribution for the parameters of the contention buffer used in the N-GREEN optical ring is described in ~\cite{youssef2018}.
 
@@
 
-  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node wants to send some packets, it uses the first free container available on the ring.
-  If a node cannot send a packet, because there is no free slot or because several packets must be sent at the same time, the remaining packets are stored in an insertion buffer.
+  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node wants to send some container, it does it as soon as it can. 
+  If a node cannot send a container, because the ring is not free free or because several containers must be sent at the same time from the same node, the remaining containers are stored in an insertion buffer.
 Two different methods to manage this insertion buffer are experimentally compared.
-The FIFO rule is compared to a method that uses two insertion buffers: one for the BE packets, and another for the C-RAN packets.
-When the node see a free container it empties the C-RAN insertion buffer first.
+The FIFO rule is compared to a method that uses two insertion buffers: one for the BE packets, and another for the C-RAN containers.
+The C-RAN insertion buffer first has the priority and is used to send containers on the ring while it is non empty before considering the BE insertion buffer.
 Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule and the "C-RAN first" rule.
@@
 
-  \captionof{figure}{Experimental parameters from the N-GREEN architecture}\label{fig:params}
+  \captionof{figure}{Experimental parameters of the N-GREEN architecture}\label{fig:params}
 
@@
 Finding good offsets for the C-RAN traffic is a hard problem even for simple topologies and without BE traffic, see~\cite{dominique2018deterministic}.
-On this section, we give simple solution to this problem in the N-GREEN optical ring, and we adapt it to minimize the latency of the BE traffic.
+In this section, we give a simple solution to this problem in the N-GREEN optical ring, and we adapt it to minimize the latency of the BE traffic.
 
@@
 
-Recall that an RRH emits a packet every $F$ containers, during a time $ET$. 
+Recall that an RRH emits every $F$ containers, during a time $ET$. 
 Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive unit of time, a RRH needs one container by slot.

### 2018-06-06 ISCIS/article.tex
suite corrections

@@
 The \textbf{ring size} is the length of the cycle, that is $\omega(u,u)$ and we denote it by $RS$.
-A {\bf container}, of capacity $C$  expressed in Bytes, is a basic unit of data in the optical ring.
+A {\bf container}, of capacity $C$  expressed in bytes, is a basic unit of data in the optical ring.
 
   A unit of time corresponds to the time needed to fill a container with data:
-  The node $u$ can fill a container with a data packet of size less than $C$ Bytes at time $t$ if the container 
+  The node $u$ can fill a container with a data packet of size less than $C$ bytes at time $t$ if the container 
   at position $u$ at time $t$ is \emph{free}.
@@
 We call this traffic \textbf{Best Effort} (BE).
-We want it to have the best possible distribution of latency, but since is less critical than C-RAN traffic, we impose no hard constraint on the latency of BE traffic.
+We want it to have the best possible distribution of latency, but since BE traffic is less critical than C-RAN traffic, we impose no hard constraint on its latency.
 At each node of the ring, a contention buffer is filled by a batch arrival process of BE data.
-Then according to some parameters, fill rate and maximum waiting time, data on the contention buffer are aggregated in a container of size at most $C$.
-The node sends this container on the ring as soon as possible.
+Then according to some parameters, fill rate and maximum waiting time, data on the contention buffer are aggregated in a packet of size at most $C$.
+The node fills a container on the ring with this packet as soon as possible.
 Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a packet of BE messages in a node.
@@
 
-  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node wants to send some container, it does it as soon as it can. 
-  If a node cannot send a container, because the ring is not free free or because several containers must be sent at the same time from the same node, the remaining containers are stored in an insertion buffer.
+  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node wants to fill some container, it does it as soon as it can. 
+  If there are several data packets in a node or if a node cannot fill a container, because it is not free, 
+  the remaining packets are stored in an insertion buffer.
 Two different methods to manage this insertion buffer are experimentally compared.
-The FIFO rule is compared to a method that uses two insertion buffers: one for the BE packets, and another for the C-RAN containers.
-The C-RAN insertion buffer first has the priority and is used to send containers on the ring while it is non empty before considering the BE insertion buffer.
+The FIFO rule is compared to a method that uses two insertion buffers: one for the BE packets, and another for the C-RAN packets.
+The C-RAN insertion buffer first has the priority and is used to fill containers on the ring while it is non empty before considering the BE insertion buffer.
 Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule and the "C-RAN first" rule.
@@
 The experimental parameters are given by Fig.~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
-The results are computed over $100$ instances of optical rings that are simulated during $10,000,000$ units of time.
-The source code in C of the experiments can be found on the author's webpage~\cite{webpage}.
+The results are computed over $100$ experiments (with different random offsets) where the optical ring is simulated during $10,000,000$ units of time.
+The source code in C of the experiments can be found on one of the authors webpage~\cite{webpage}.
 
@@
 
-In order to ensure zero latency for the C-RAN traffic, the first container after node $u$, to which is attached the RRH $i$, must be free at time $m_i$.
-Hence the node $u$ \textbf{reserves} the container at time $m_i - RS$.
-A container which is reserved cannot be filled by any node except the one which has reserved it.
+Let $u$ be the node to which is attached the RRH $i$, to ensure zero latency for the C-RAN traffic, then the container which arrives at $u$ at time $m_i$ must be free so that the data from the RRH can be sent immediately on the optical ring.
+
+To avoid latency between the arrival of the data from the RRH and its insertion on the optical ring, 
+we allow nodes to \textbf{reserve} a container one round before using it.
+A container which is reserved cannot be filled by any node except the one which has reserved it (but it may contain data when it is reserved).
+Let $u$ be the node to which is attached the RRH $i$, if $u$ reserves the container $u$ at time $m_i - RS$, then it is guaranteed that $u$ can fill a free container at time $m_i$ with the data of the RRH $i$.
 In the method we now describe, the C-RAN packets never wait in the node: The message sent by the RRH $i$ arrives at its BBU at node $v$ at time $m_i + \omega(u,v)$ and the answer is sent from the BBU at time $m_i + \omega(u,v) +1$.
@@
 Recall that an RRH emits every $F$ containers, during a time $ET$. 
-Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive unit of time, a RRH needs one container by slot.
- If a RRH emits at time $m_i < P$, then we say it has \textbf{position} $m_i~mod~F$.
-If a RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1~mod~F$.
+Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive unit of time, an RRH needs to use at most one container by slot.
+If an RRH emits at time $m_i$, then we say it has \textbf{position} $m_i + \omega(u,v)\pmod F$.
+emitted by the RRH, when it arrives at the data center in node $v$.
+If an RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1\pmod F$.
 Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position during all the period.
 
-The problem we solve now is to find an \textbf{assignment} of values of the $m_i$s which is \textbf{valid}: two RRHs never reserve the same container in a period.
+The problem we solve now is to find an \textbf{assignment} of values of the $m_i$s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
 Moreover we want to preserve the latency of the BE traffic.
 It means that the time a node waits for a free container at any point of the period must be minimized.
-Remark that two RRHs which are not at the same position never use the same containers. Moreover, without loss of generality, 
-if we can fix the offsets of the RRHs to even positions so that they do not reserve the same containers, then it will fix the offsets of the BBUs to odd positions which do not reserve the same containers.
+Remark that two RRHs which are not at the same position never use the same containers.
+Moreover, if we fix the offsets of the RRHs to even positions so that they do not reserve the same containers, then it will fix the offsets of the BBUs to odd positions which do not reserve the same containers.
+Hence we need to deal with the RRHs only.
 

### 2018-06-06 ISCIS/article.tex
orthographe

@@
 In a previous work~\cite{dominique2018deterministic}, the authors have studied a similar problem for a star shaped network.
-In contrast with our previous work, finding emmission timings so that different peridoic sources do not use the same ressource is easy in the context of the N-GREEN optical ring.
+In contrast with our previous work, finding emission timings so that different periodic sources do not use the same resource is easy in the context of the N-GREEN optical ring.
 However, we add several new difficulties: the messages from RRHs are scattered, there are other traffics whose latency must be preserved and the need to make reservation of containers on the ring requires additional bandwidth.
@@
 In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantee to have zero latency from buffering.
-We propose several refinments of this determistic sending scheme to spread the load over time, which improves the latency of best effort packets.
+We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packets.
 

### 2018-06-06 ISCIS/article.tex
fig tex
merge de la figure

@@
 
-Recall that an RRH emits every $F$ containers, during a time $ET$. 
-Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive unit of time, an RRH needs to use at most one container by slot.
-If an RRH emits at time $m_i$, then we say it has \textbf{position} $m_i + \omega(u,v)\pmod F$.
-emitted by the RRH, when it arrives at the data center in node $v$.
+Recall that an RRH fills a container every $F$ units of time, during a time $ET$. 
+Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive units of time, an RRH needs to use at most one container by slot.
+If an RRH emits at time $m_i$, then we say it is at \textbf{position} $m_i + \omega(u,v)\pmod F$.
+The position of an RRH corresponds to the position in a slot of the container it has emitted, when it arrives at $u$. 
 If an RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1\pmod F$.
@@
 
-The problem we solve now is to find an \textbf{assignment} of values of the $m_i$s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
+The problem we solve now is to find an \textbf{assignment} of values of the $m_i$'s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
 Moreover we want to preserve the latency of the BE traffic.

### 2018-06-06 ISCIS/article.tex
conflits

@@
 \label{prop:assign}
-There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if  $k\times ET + RS \leq P$.
+There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if and only if $k\times ET + RS \leq P$, t
 \end{prop}
@@
 Therefore we can fix $m_2 =  ET  + \omega(u_1,u_2)$.
-In general we can set $m_i = (i-1) \times ET + \omega(u_1,u_i)$ and all RRHs will use different containers at position $0$.
-The assignment is correct, if when the RRH $1$ must emit something in the second period, there is a free container.
-It implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.\qed
+In general we can set $m_i = (i-1) \times ET + \omega(u_1,u_i)$ and all RRHs will use different containers at position $0$ during a period.
+The assignment is correct, since when the RRH $1$ must emit something in the second period, there is a free container.
+This later constraint implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.\qed
 \end{proof}
@@
 \begin{corollary}
-The number of antennas supported by a ring is $K = \lfloor\frac{P- RS}{ET}\rfloor \times \frac{F}{2}$
+The maximal number of antennas supported by a ring is $K = \lfloor\frac{P- RS}{ET}\rfloor \times \frac{F}{2}$
 \end{corollary}

### 2018-06-06 ISCIS/article.tex
corrections fin

@@
 We study the compatibility of such a technology with the development of the Cloud RAN, a latency critical application which is a major aspect of 5G deployment.
-We show that deterministically managing Cloud RAN traffic minimizes its latency while also improving the latency of the others traffics.
+We show that deterministically managing Cloud RAN traffic minimizes its latency while also improving the latency of the other traffics.
 \keywords{Optical ring \and Latency \and C-RAN \and SDN}
@@
 
+From this proposition, it is easy to derive the maximal number of antennas which can be supported by an optical ring,
+when using reservation and the same position for an RRH for the whole period.
+
 \begin{corollary}
-The maximal number of antennas supported by a ring is $K = \lfloor\frac{P- RS}{ET}\rfloor \times \frac{F}{2}$
+The maximal number of antennas such that there is an assignment is $ \lfloor\frac{P- RS}{ET}\rfloor \times \frac{F}{2}$.
 \end{corollary}
@@
 \end{proof}
-Remark that for each position which is used by some RRH, $RS$ containers are reserved before starting to emit some C-RAN traffic.
-Those containers which are reserved could either be free or freed during the next round trip.
-Thus, those containers are seen by the BE traffic as additional dataflow.
-Therefore to not waste much bandwidth, it is relevant to put as many RRH as possible on the same position.
-Moreover, unused positions in an assignment are useful to guarantee a good latency to BE traffic.
-The unused positions can be distributed uniformly over a slot, to minimize the time to wait before a free container, as shown in Fig.~\ref{fig:repart1}.
 
-However, it is possible that there are no unused position. It happens with the current parameters of the N-GREEN ring,
-$ET = \frac{P}{2}$, $F = 10$ and $n = 5$.
-Hence there is exactly one  BBU or RRH at each position.
-If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for BE traffic.
-To mitigate this problem, the time with free containers of each position must be uniformly distributed over the period as in Fig.~\ref{fig:repart2}.
+\paragraph{Packing}
+
+Remark that for each position which is used by some RRH, and during each period, $RS$ containers are reserved before starting to emit some C-RAN traffic, while they are free.
+Hence, it decreases the maximal load the system can handle.
+Therefore to not waste bandwidth, it is relevant to put as many RRHs as possible on the same position as in Fig.~\ref{fig:repart0}.
+Indeed, for any position which is not used at all, $RS$ containers need not to be reserved.
+This strategy is also good for the latency of the BE traffic. If a position is unused, then there is always a container free of C-RAN traffic each $F$ unit of times.
+
+\paragraph{Balancing inside the slot}
+
+The free positions can be distributed uniformly over a slot, to minimize the time to wait before a node 
+has access to a free container, as shown in Fig.~\ref{fig:repart1}. It is a small optimization, since 
+it decreases the latency of at most $F/2$.
+
+\paragraph{Balancing inside the period}
+However, it is possible that there are no unused position as it happens with the parameters of the N-GREEN ring given in Fig.~\ref{fig:params}: $ET = \frac{P}{2}$, $F = 10$ and $n = 5$.
+Any assignment has exactly one  BBU or RRH at each position.
+If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for the BE traffic.
+To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in Fig.~\ref{fig:repart2}.
 
@@
 
+  \paragraph{Experimental evaluation}
 In order to evaluate the performances of those methods, we present the cumulative distribution of the latency of the BE traffic latency when the C-RAN traffic is distributed in the slot, or in the period in Fig.~\ref{fig:algocmp}.
-Since the previous N-GREEN parameters were too restrictive to put several RRHs on the same position, the parameters $ET$ and has been changed to $400$.
+Since the previous N-GREEN parameters were too restrictive to put several RRHs on the same position, the parameter $ET$ and has been changed to $400$.
 

### 2018-06-06 ISCIS/article.tex
commentaires expériences

@@
 \label{prop:assign}
-There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if and only if $k\times ET + RS \leq P$, t
+There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if  $k\times ET + RS \leq P$.
 \end{prop}
 \begin{proof}
- We fix $m_1 = 0$ and all the offsets will also be at position $0$. 
+ W.l.o.g we fix $m_1$ so that it is at position $0$ and all the other offsets will then be chosen at position $0$. 
  Let $u_1,\dots,u_k$ be the nodes attached to the RRHs $1,\dots,k$.
@@
 In general we can set $m_i = (i-1) \times ET + \omega(u_1,u_i)$ and all RRHs will use different containers at position $0$ during a period.
-The assignment is correct, since when the RRH $1$ must emit something in the second period, there is a free container.
-This later constraint implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.\qed
+Since $k \times ET + \omega(u_1,u_1) \leq P$ by hypothesis,
+ the containers filled by the $k$th RRH are freed before $P$. Hence when the RRH $1$ must emit something in the second period, there is a free container.\qed
 \end{proof}
@@
   \paragraph{Experimental evaluation}
-In order to evaluate the performances of those methods, we present the cumulative distribution of the latency of the BE traffic latency when the C-RAN traffic is distributed in the slot, or in the period in Fig.~\ref{fig:algocmp}.
+
+  In order to understand the interest of the several refinements of our presented before,
+
+performances of our method, we present the cumulative distribution of the latency of the BE traffic latency in Fig.~\ref{fig:algocmp}.
 Since the previous N-GREEN parameters were too restrictive to put several RRHs on the same position, the parameter $ET$ and has been changed to $400$.
 
-As expected, both of the presented method to optimize the BE traffic latency in the ring are efficient.
-Indeed, if all the C-RAN packets are sent in the same moment of the period, the chances of having a free container for a BE packet are low.
-Here, we try to distribute as much as possible the free containers.
-However, it is important to precise that the parameters induce that there is no free positions during $ET+RS$ unit of time when no repartition is done.
-This is why the performances of the corresponding curve are so weak.
+The performance when we do no packing is really bad, even worst than the methods using an insertion buffer.
+It is explained by the parameters of the N-GREEN ring: all positions are used and thus, there are no free containers available to BE traffic during $ET+RS$ units of time.
+When packing the RRHs on a minimal number of positions, the latency decreases dramatically and becomes much better than in the previous methods.
+The optimizations of spacing inside the slot or inside the period further improve the latency but only marginally.
+However, in other settings, spacing inside the period is critical as explained before.
 
-Since we have observe that the two repartitions are effective, we want to combine them for our {\em reservation algorithm}.
   We compare the cumulative distribution of the latency of the BE traffic using the FIFO rule or the reservation algorithm proposed here in Fig.~\ref{fig:optimres}.
-To keep the same expected load than the load of the experiment if Fig.~\ref{fig:resultopport}, we set $ET = 200$ and $n = 12$.
-This is not out of context since the exact split (the C-RAN split is the degree of centralization of the computation units in the cloud) of the C-RAN is not fully determined yet~\cite{mobile2011c}.
+To keep the load at $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}, we set $ET = 200$ and $n = 12$.
+This is not out of context since the exact split of the C-RAN (the degree of centralization of the computation units in the cloud) is not fully determined yet~\cite{mobile2011c}.
 With these parameters, the loss of bandwidth due to reservation is at most $6\%$

### 2018-06-06 ISCIS/article.tex

@@
 
+We now present an algorithm to determine an assignment of the $m_i$, using the method of Prop.\ref{prop:assign} to set the offset at the same positions.
+We propose three variations to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.
+
 \paragraph{Packing}
 
-Remark that for each position which is used by some RRH, and during each period, $RS$ containers are reserved before starting to emit some C-RAN traffic, while they are free.
+For each position which is used by some RRH, and during each period, $RS$ containers are reserved before starting to emit some C-RAN traffic, while they are free.
 Hence, it decreases the maximal load the system can handle.
@@
 Indeed, for any position which is not used at all, $RS$ containers need not to be reserved.
-This strategy is also good for the latency of the BE traffic. If a position is unused, then there is always a container free of C-RAN traffic each $F$ unit of times.
+This strategy is also good for the latency of the BE traffic.
+If a position is unused, then there is always a container free of C-RAN traffic each $F$ unit of times.
 
@@
 \paragraph{Balancing inside the period}
-However, it is possible that there are no unused position as it happens with the parameters of the N-GREEN ring given in Fig.~\ref{fig:params}: $ET = \frac{P}{2}$, $F = 10$ and $n = 5$.
+
+It is possible that there are no unused position as it happens with the parameters of the N-GREEN ring given in Fig.~\ref{fig:params}: $ET = \frac{P}{2}$, $F = 10$ and $n = 5$.
 Any assignment has exactly one  BBU or RRH at each position.
@@
 
-  In order to understand the interest of the several refinements of our presented before,
-
-performances of our method, we present the cumulative distribution of the latency of the BE traffic latency in Fig.~\ref{fig:algocmp}.
-Since the previous N-GREEN parameters were too restrictive to put several RRHs on the same position, the parameter $ET$ and has been changed to $400$.
+  In order to understand the contribution of the three ideas presented in the previous subsection,
+   we present the cumulative distribution of the latency of the BE traffic latency in Fig.~\ref{fig:algocmp}.
+Since the previous N-GREEN parameters were too restrictive to put several RRHs on the same position, the parameter $ET$ has been changed to $400$.
 
@@
 When packing the RRHs on a minimal number of positions, the latency decreases dramatically and becomes much better than in the previous methods.
-The optimizations of spacing inside the slot or inside the period further improve the latency but only marginally.
-However, in other settings, spacing inside the period is critical as explained before.
+The optimizations of spacing inside the slot brings almost no benefit as expected.
+The spacing over a period improves the latency marginally.
+In settings with an higher load, spacing inside a period would have a much larger effect.
 
-  We compare the cumulative distribution of the latency of the BE traffic using the FIFO rule or the reservation algorithm proposed here in Fig.~\ref{fig:optimres}.
+In Fig.~\ref{fig:optimres}, we compare the cumulative distribution of the latency of the BE traffic using the FIFO rule or the reservation algorithm proposed here.
 To keep the load at $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}, we set $ET = 200$ and $n = 12$.

### 2018-06-06 ISCIS/article.tex
figures

@@
 The ring follows a {\bf broadcast and select scheme with emission release policy}: When a container is filled by some node $u$, it is freed when it comes back at $u$ after a whole round trip.
+
+  \begin{figure}[h!]
+       \begin{minipage}[b]{0.5\linewidth}
+        \begin{center}
+      \includegraphics[scale=0.7]{containers}
+
+      \end{center} 
+  \end{minipage}
+    \begin{minipage}[b]{0.5\linewidth}
+        \begin{center}
+      \includegraphics[scale=0.7]{containers2}
+
+      \end{center} 
+  \end{minipage}
+
+     \caption{Behavior of the containers on the ring.}\label{fig:containers}
+
+  \end{figure}
 
@@
 
+\begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.55]{repart0}
+     \caption{Packing.}\label{fig:packing}
+
+\end{center}
+  \end{figure}
+
 \paragraph{Balancing inside the slot}
@@
 
+\begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.55]{repart1}
+     \caption{Balancing inside the slot.}\label{fig:packing}
+
+\end{center}
+  \end{figure}
 \paragraph{Balancing inside the period}
@@
 To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in Fig.~\ref{fig:repart2}.
+\begin{figure}[h!]
+\begin{center}
 
-     \begin{minipage}[b]{0.5\linewidth}
-        \begin{center}
       \includegraphics[scale=0.55]{repart2}
+     \caption{Balancing inside the period.}\label{fig:packing}
 
-      \captionof{figure}{Repartition in the slot}    \label{fig:repart1}
 \end{center}
-  \end{minipage}
-    \begin{minipage}[b]{0.5\linewidth}
-        \begin{center}
-      \includegraphics[scale=0.55]{repart1}
-
-      \captionof{figure}{Repartition in the period}    \label{fig:repart2}
-      \end{center} 
-  \end{minipage}
-
+  \end{figure}  
   \paragraph{Experimental evaluation}

### 2018-06-06 ISCIS/article.tex
nzij

@@
 
-  A unit of time corresponds to the time needed to fill a container with data:
-  The node $u$ can fill a container with a data packet of size less than $C$ bytes at time $t$ if the container 
+  A unit of time corresponds to the time needed to fill a container with data.
+  As shown in Fig.~\ref{fig:containers}, the node $u$ can fill a container with a data packet of size less than $C$ bytes at time $t$ if the container 
   at position $u$ at time $t$ is \emph{free}.
@@
 
-     \caption{Behavior of the containers on the ring.}\label{fig:containers}
+     \caption{Dynamic behavior of the ring.}\label{fig:containers}
 
@@
       \includegraphics[scale=0.7]{interface.pdf}
-     \caption{Access node of the N-GREEN optical ring.}\label{fig:interface}
+     \caption{Insertion in the N-GREEN optical ring.}\label{fig:interface}
 
@@
 Hence, it decreases the maximal load the system can handle.
-Therefore to not waste bandwidth, it is relevant to put as many RRHs as possible on the same position as in Fig.~\ref{fig:repart0}.
+Therefore to not waste bandwidth, it is relevant to put as many RRHs as possible on the same position as in Fig.~\ref{fig:packing}.
 Indeed, for any position which is not used at all, $RS$ containers need not to be reserved.
@@
 The free positions can be distributed uniformly over a slot, to minimize the time to wait before a node 
-has access to a free container, as shown in Fig.~\ref{fig:repart1}. It is a small optimization, since 
+has access to a free container, as shown in Fig.~\ref{fig:slotbal}. It is a small optimization, since 
 it decreases the latency of at most $F/2$.
@@
       \includegraphics[scale=0.55]{repart1}
-     \caption{Balancing inside the slot.}\label{fig:packing}
+     \caption{Balancing inside the slot.}\label{fig:slotbal}
 
@@
 If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for the BE traffic.
-To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in Fig.~\ref{fig:repart2}.
+To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in Fig.~\ref{fig:periodbal}.
 \begin{figure}[h!]
@@
       \includegraphics[scale=0.55]{repart2}
-     \caption{Balancing inside the period.}\label{fig:packing}
+     \caption{Balancing inside the period.}\label{fig:periodbal}
 

### 2018-07-30 ISCIS/article.tex
papier format conf

@@
 %\usepackage[utf8]{inputenc}
-
-%\usepackage{xspace}
-%\usepackage{graphicx,graphics} 
-%\usepackage{mathtools, bm}
-%\usepackage{caption}
-%\usepackage{amssymb, bm}
-%\usepackage{complexity}
-%\usepackage{amsthm}
-%%\usepackage{authblk}
-%\usepackage{color}
-%\usepackage{amsmath}
-%\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
-%\captionsetup{justification=centering,margin=0.5cm}
-\documentclass[]{llncs}
+\documentclass[10pt, conference, letterpaper]{IEEEtran}
 %
@@
 \usepackage{caption}
+\usepackage{authblk}
+\usepackage{graphicx}
 
-\usepackage{graphicx}
+\usepackage{xspace}
+\usepackage{graphics} 
+\usepackage{mathtools, bm}
+
+\usepackage{amssymb, bm}
+\usepackage{complexity}
+\usepackage{amsmath,amsthm}
+
+\usepackage{color}
+\usepackage{amsmath}
+%\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
+\captionsetup{justification=centering,margin=0.5cm}
 
@@
 \newtheorem{prop}{Proposition}
+
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}[theorem]
+
 \renewcommand{\thefootnote}{\*}
@@
 \title{Contention management for Cloud RAN over an optical ring}
-\author{Dominique Barth \inst{1}
-  \and Ma\"el Guiraud \inst{1}
-   \and Yann Strozecki \inst{1}
-  }
 
-\institute{David Laboratory, UVSQ}
+\author[1]{Dominique Barth}
+\author[1,2]{Ma\"el Guiraud}
+\author[1]{Yann Strozecki}
+\affil[1]{David Laboratory, UVSQ}
+\affil[2]{Nokia Bell Labs France}
 
@@
 We show that deterministically managing Cloud RAN traffic minimizes its latency while also improving the latency of the other traffics.
-\keywords{Optical ring \and Latency \and C-RAN \and SDN}
+
 \end{abstract}
@@
   \begin{figure}[h!]
-       \begin{minipage}[b]{0.5\linewidth}
+
         \begin{center}
-      \includegraphics[scale=0.7]{containers}
+      \hspace{-2.3cm}\includegraphics[scale=0.7]{containers}
 
+   \vspace{0.5cm}
+
+      \includegraphics[scale=0.7]{containers2}
       \end{center}
-  \end{minipage}
-    \begin{minipage}[b]{0.5\linewidth}
-        \begin{center}
-      \includegraphics[scale=0.7]{containers2}
-
-      \end{center} 
-  \end{minipage}
 
@@
   \hspace{-0.75cm}
-    \begin{minipage}[b]{0.50\linewidth}
 
@@
      \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}
-      \end{center} 
-  \end{minipage}
-\hfill
-  \begin{minipage}[b]{0.40\linewidth}
 
@@
 
-  \centering
   \begin{tabular}{|c|c|}
@@
   \captionof{figure}{Experimental parameters of the N-GREEN architecture}\label{fig:params}
-
-  \end{minipage}
+      \end{center}
 
@@
 
-We now present an algorithm to determine an assignment of the $m_i$, using the method of Prop.\ref{prop:assign} to set the offset at the same positions.
-We propose three variations to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.
+We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets at the same position.
+In the naive version of the algorithm, we put each RRH in an arbitrary position, for instance one RRH by position.
+ We then propose three ideas to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.
 
@@
 
-      \includegraphics[scale=0.55]{repart0}
+      \includegraphics[scale=0.5]{repart0}
      \caption{Packing.}\label{fig:packing}
@@
 
-  \begin{minipage}[b]{0.45\linewidth}
-\centering
+\begin{center}
       \includegraphics[scale=0.25]{repart1res}
      \captionof{figure}{Impact of the repartition on the latency.}   \label{fig:algocmp}
-  \end{minipage} 
-  \hfill
-  \begin{minipage}[b]{0.45\linewidth}
-\centering
+
+\vspace{0.5cm}
+
       \includegraphics[scale=0.25]{optim.pdf}
      \captionof{figure}{Impact of the deterministic method on the traffics.}   \label{fig:optimres}
-  \end{minipage}
 
+\end{center}
   The performance of the reservation algorithm is excellent, since the C-RAN traffic has {\bf zero latency} and the BE traffic has a \textbf{better latency} with reservation than with the FIFO rule.

### 2018-12-13 ISCIS/article.tex
merge

--- 2018-06-06 ISCIS/article.tex
@@
 The ring follows a {\bf broadcast and select scheme with emission release policy}: When a container is filled by some node $u$, it is freed when it comes back at $u$ after a whole round trip.
-
-  \begin{figure}[h!]
-       \begin{minipage}[b]{0.5\linewidth}
-        \begin{center}
-      \includegraphics[scale=0.7]{containers}
-
-      \end{center} 
-  \end{minipage}
-    \begin{minipage}[b]{0.5\linewidth}
-        \begin{center}
-      \includegraphics[scale=0.7]{containers2}
-
-      \end{center} 
-  \end{minipage}
-
-     \caption{Behavior of the containers on the ring.}\label{fig:containers}
-
-  \end{figure}
 
@@
 
-We now present an algorithm to determine an assignment of the $m_i$, using the method of Prop.\ref{prop:assign} to set the offset at the same positions.
-We propose three variations to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.
+We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets at the same positions.
+In the naive version of the algorithm, we put each RRH in an aribtrary position, for instance one RRH by position.
+ We then propose three ideas to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.
 
@@
 
-\begin{figure}[h!]
-\begin{center}
-
-      \includegraphics[scale=0.55]{repart0}
-     \caption{Packing.}\label{fig:packing}
-
-\end{center}
-  \end{figure}
-
 \paragraph{Balancing inside the slot}
@@
 
-\begin{figure}[h!]
-\begin{center}
-
-      \includegraphics[scale=0.55]{repart1}
-     \caption{Balancing inside the slot.}\label{fig:packing}
-
-\end{center}
-  \end{figure}
 \paragraph{Balancing inside the period}
@@
 To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in Fig.~\ref{fig:repart2}.
-\begin{figure}[h!]
+
+     \begin{minipage}[b]{0.5\linewidth}
         \begin{center}
+      \includegraphics[scale=0.55]{repart2}
 
-      \includegraphics[scale=0.55]{repart2}
-     \caption{Balancing inside the period.}\label{fig:packing}
+      \captionof{figure}{Repartition in the slot}    \label{fig:repart1}
+      \end{center} 
+  \end{minipage}
+    \begin{minipage}[b]{0.5\linewidth}
+        \begin{center}
+      \includegraphics[scale=0.55]{repart1}
 
+      \captionof{figure}{Repartition in the period}    \label{fig:repart2}
       \end{center} 
-  \end{figure}  
+  \end{minipage}
+
   \paragraph{Experimental evaluation}

### 2018-12-17 ISCIS/articleV3.tex
v3

--- 2018-07-30 ISCIS/article.tex
@@
 \newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{corollary}{Corollary}
 
@@
 \footnote{This work was developed around the ANR N-GREEN project.
-The authors thank the Nokia Bell Labs team for their collaboration.}Network providers have to design inexpensive networks supporting an increasing amount of data and online applications.
-Much of these applications have QoS criteria, like a minimal throughput or a maximal latency.
+The authors thank the Nokia Bell Labs team for their collaboration.} Telecommunication network providers have to design inexpensive networks supporting an increasing amount of data and online applications.
+Many of these applications require QoS guarantees, like minimal throughput and/or  maximal latency.
 The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers.
@@
 In this article, we study a Cloud RAN (C-RAN) application based on the N-GREEN optical ring described in~\cite{ngreenarchitecture,uscumlicscalable}.
-C-RAN is one of the major area of development for 5G; it consists in centralizing or partially centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.
-The latency of the messages between the BBU and the RRH is critical since some services need end-to-end latency as low as $1$ms~\cite{3gpp5g,boccardi2014five}.
-In this article we propose an SDN approach to deterministically manage the periodic C-RAN traffic by choosing emission timing and reserving containers on the ring.
-In a previous work~\cite{dominique2018deterministic}, the authors have studied a similar problem for a star shaped network.
+C-RAN is one of the major area of development for 5G; it consists in centralizing or partially centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.\todo{ref CRAN} The latency of the messages between the BBU and the RRH is critical since some services need end-to-end latency as low as $1$ms~\cite{3gpp5g,boccardi2014five}.
+\todo{Decrire le process periodique, periode latence max et uplink downlink,meme taille de frame}
+
+In this article we propose an SDN approach to {\bf deterministically} manage the periodic C-RAN traffic by choosing emission timing.\todo{dire que pour l'instant on gere le traffic par statistical multiplexing(refs) + chercher ring SDN mots clefs + detNet ?} In a previous work~\cite{dominique2018deterministic}, the authors have studied a similar problem for a star shaped network.
 In contrast with our previous work, finding emission timings so that different periodic sources do not use the same resource is easy in the context of the N-GREEN optical ring.
 However, we add several new difficulties: the messages from RRHs are scattered, there are other traffics whose latency must be preserved and the need to make reservation of containers on the ring requires additional bandwidth.
+\todo{on met la latence CRAN a 0, on minimise le BE car on lisse bien le traffic, mais par contre ca coute de la bandiwth de faire de la reservation}
+\todo{parler du slicing (virtual circuit switching) }
 
@@
 
-  A unit of time corresponds to the time needed to fill a container with data.
+  The time is discretized : a unit of time corresponds to the time needed to fill a container with data.
   As shown in Fig.~\ref{fig:containers}, the node $u$ can fill a container with a data packet of size less than $C$ bytes at time $t$ if the container 
   at position $u$ at time $t$ is \emph{free}. 
+  If there are several packets in a node or if a node cannot fill a container, because it is not free, 
+  the remaining packets are stored in the {\bf insertion buffer} of the node. 
   A container goes from $u$ to $v$ in $\omega(u,v)$ units of time.
@@
 The integer $F$ is called the {\bf acceleration factor} between the electronic and the optical domains.
-A node aggregates the data received on the electronic interface during $F$ units of time to create a packet of data of size $C$ and then fills a container of the ring with this data.
+A node aggregates the data received on the electronic interface during $F$ units of time to create a packet of size $C$ and then puts it in the insertion buffer.
+%   fills a container of the ring with this data. 
   In each period $P$, an RRH emits data during a time called \textbf{emission time} or $ET$.
@@
    In this study the {\bf latency} of a message is defined as the time it waits in a node before being sent on the ring.
+\todo{dire qu'il y a aussi le temps physique, mais qu'on ne peux minimiser que la latence du buffer d'insertion et que donc, parler de "zero latency veut en realité dire "zero logical latency"}
    The aim of our study is to minimize the latency of the C-RAN traffic, both of the RRHs and the BBUs. 
@@
 We want it to have the best possible distribution of latency, but since BE traffic is less critical than C-RAN traffic, we impose no hard constraint on its latency.
-At each node of the ring, a contention buffer is filled by a batch arrival process of BE data.
+At each node of the ring, a {\bf contention buffer} is filled by a batch arrival process of BE data.
 Then according to some parameters, fill rate and maximum waiting time, data on the contention buffer are aggregated in a packet of size at most $C$.
-The node fills a container on the ring with this packet as soon as possible.
+This packet is then put in the insertion buffer of the node.
 Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a packet of BE messages in a node.
-The computation of this distribution for the parameters of the contention buffer used in the N-GREEN optical ring is described in ~\cite{youssef2018}.
+The computation of this distribution for the parameters of the contention buffer used in the N-GREEN optical ring is described in ~\cite{youssef2018}\todo{mettre la bonne ref}.
 
@@
 
-  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node wants to fill some container, it does it as soon as it can. 
-  If there are several data packets in a node or if a node cannot fill a container, because it is not free, 
-  the remaining packets are stored in an insertion buffer.
-Two different methods to manage this insertion buffer are experimentally compared.
-The FIFO rule is compared to a method that uses two insertion buffers: one for the BE packets, and another for the C-RAN packets.
+  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node has a free container available, it fills it with a packet of its insertion buffer, if it exists one.\todo{peut etre reprendre}
+ Two different methods to manage the insertion buffer are experimentally compared.
+The FIFO rule is compared to a method that uses two insertion buffers:\todo{decrire fifo rule, plus clair} one for the BE packets, and another for the C-RAN packets.
 The C-RAN insertion buffer first has the priority and is used to fill containers on the ring while it is non empty before considering the BE insertion buffer.
@@
 The source code in C of the experiments can be found on one of the authors webpage~\cite{webpage}.
+\todo{revoir 100 1000000}
 
@@
   }
+\todo{revoir table au lieu de figure}
+  \captionof{figure}{Parameters of the N-GREEN architecture}\label{fig:params}
+      \end{center} \todo{premier tableau longueur parcourue en une unite of time 200m, deux tableaux Un N-Green parametres, un valuers choisie}
 
-  \captionof{figure}{Experimental parameters of the N-GREEN architecture}\label{fig:params}
-      \end{center}
-
-Unsurprisingly, the latency of the C-RAN traffic is better when we prioritize the C-RAN messages, while the BE traffic is penalized.
+Unsurprisingly, the latency of the C-RAN traffic is better when we prioritize the C-RAN messages, while the BE traffic is heavily penalized.
 Nevertheless, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s, a problem we address in the next section.
+\todo{expliquer que le CRAN se concentre sur la moitié de la periode donc il mange plus que les BE en FIFO, + parler du fait que y'a un moment dans l'anneau ou on aura un peu plus de cRAN}
 
@@
 
-The problem we solve now is to find an \textbf{assignment} of values of the $m_i$'s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
+Given, ....
+\todo{entrees du problemes} The problem we solve now is to find an \textbf{assignment} of values of the $m_i$'s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
 Moreover we want to preserve the latency of the BE traffic.
-It means that the time a node waits for a free container at any point of the period must be minimized.
+It means that the time a node waits for a free container at any point of the period must be minimized.\todo{to minimize the time a node ......., we must minimize the time in the insertion buffer, en placant le traffic CRan de facon a avoir en moyenne le moins de temps possible}
+\todo{dessin represnetation d'un assignement}
+
 Remark that two RRHs which are not at the same position never use the same containers.
@@
 Since $k \times ET + \omega(u_1,u_1) \leq P$ by hypothesis,
- the containers filled by the $k$th RRH are freed before $P$. Hence when the RRH $1$ must emit something in the second period, there is a free container.\qed
+ the containers filled by the $k$th RRH are freed before $P$. Hence when the RRH $1$ must emit something in the second period, there is a free container.
 \end{proof}
+\todo{on perds pas trop pck on a fait dans l'odre mais on perds quand meme RS * F en bandwidth}
 
@@
 \begin{proof}
-Following Prop.~\ref{prop:assign}, the number of antennas on a position is $k = \lfloor\frac{P- RS}{ET}\rfloor $.
-Since we need two positions for $k$ antennas, in order to carry the traffic coming from the RRHs and the BBUs, and we got $F$ positions in the slot, the number of antennas supported by the ring is thus equal to $k \times \frac{F}{2}$.\qed
+Following Prop.~\ref{prop:assign}, the number of antennas for which there is an assignment on the same position is $k = \lfloor\frac{P- RS}{ET}\rfloor $.
+In such an assignment, we need a second position to deal with the traffic coming from the BBUs coming back to those k antennas.
+Since we got  $F$ positions in the slot, the number of antennas supported by the ring is thus equal to $k \times \frac{F}{2}$.
 \end{proof}
+\todo{dire qu'on perds de la place a cause de la partie entire (p / et * f/2 avec le statistical multuplexing), on peut eventuellement s'arranger pour caler un peu plus d'antennes quand meme en deterministic}
 
 We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets at the same position.
-In the naive version of the algorithm, we put each RRH in an arbitrary position, for instance one RRH by position.
+In the basline version of the algorithm, we put each RRH in an arbitrary position, for instance one RRH by position.
  We then propose three ideas to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.
@@
 If a position is unused, then there is always a container free of C-RAN traffic each $F$ unit of times.
-
+\todo{c bon deja pour la bandwith et aussi on s'assure d'avoir un container tout les F unit+ packing bof comme nom}
 \begin{figure}[h!]
@@
 it decreases the latency of at most $F/2$.
-
+\todo{dire trois mots sur les restes des restes etc}
 \begin{figure}[h!]

### 2018-12-17 ISCIS/articlev2.tex
v3

%\documentclass[]{algotel}
%\usepackage[utf8]{inputenc}
\documentclass[10pt, conference, letterpaper]{IEEEtran}
%
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{caption}
\usepackage{authblk}
\usepackage{graphicx}

\usepackage{xspace}
\usepackage{graphics}
\usepackage{mathtools, bm}

\usepackage{amssymb, bm}
\usepackage{complexity}
\usepackage{amsmath,amsthm}

\usepackage{color}
\usepackage{amsmath}
%\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
\captionsetup{justification=centering,margin=0.5cm}

\newcommand\pall{\textsc{pall}\xspace}
\newcommand{\todo}[1]{{\color{red} TODO: {#1}}}
\newtheorem{prop}{Proposition}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]

\renewcommand{\thefootnote}{\*}

\graphicspath{{img/}}
\title{Deterministic latency for Cloud RAN over an optical ring}

\author[1]{Dominique Barth}
\author[1,2]{Ma\"el Guiraud}
\author[1]{Yann Strozecki}
\affil[1]{David Laboratory, UVSQ}
\affil[2]{Nokia Bell Labs France}

\begin{document}

\maketitle

\begin{abstract}
The N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency$\dots$) without using expensive end to end connections. We study the compatibility of such a technology with the development of the Cloud RAN, a latency critical application which is a major aspect of 5G deployment. We show that deterministically managing Cloud RAN traffic minimizes its latency while also improving the latency of the other traffics.

\end{abstract}

\section{Introduction}

\footnote{This work was developed around the ANR N-GREEN project.}  Telecommunication network providers have to design inexpensive networks supporting an increasing amount of data and online applications. Much of these applications require QoS guarantees, like a minimal throughput and/or  a maximal latency. The N-GREEN project aims to design a high performing packet-switching optical ring while ensuring a minimal cost for providers. The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end to end direct connections (E2DE) between the nodes, which is extremely expensive. The N-GREEN optical ring is designed to ensure good performance: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.

In this article, we focus on a Cloud RAN application (C-RAN) on the N-GREEN optical ring described in ~ \cite{ngreenarchitecture, uscumlicscalable}. C-RAN is one of the main areas of development of 5G; it consists in centralizing or partially centralizing the computation units or BaseBand Units (BBU) of the Remote Radio Heads (RRH) in a datacenter. This application therefore requires periodic uplink and downlink communications of data frames between  all the  RRH and their corresponding BBU; the period and the latency must be fixed in time, if possible  minimum, in order to respect the time constraints of the application. In particular, the end-to-end latency must be less than or equal to $ 1 $ ms ~ \cite{3gpp5g, boccardi2014five}. In addition, the sizes of the uplink C-RAN frames are the same for all the RRHs and all the periods, and it also the case for all the downlink BBU frames.\\

The optical multi-wavelength network considered here consists of a cyclic sequence of slot of fixed duration, each slot corresponding to a vertical container, ie using simultaneously all wavelengths..
The bandwidth in the ring, ie the sum of the capacities of all the containers, is equal to the sum of the incoming bandwidths of each of the nodes on the ring. We consider  an SDN approach on the ring to deterministically manage periodic C-RAN traffic by choosing the synchronization of emissions and reserving containers.

We propose a method of periodic allocation of container on the ring which allows to obtain a minimal uplink and downlink latency, without negative impact on the latency of the  best effort traffic using the non allocated containers. Such an approach can be seen as  the use of virtual circuit switching in a fixed size optical packet network to insure deterministic latency \cite{Sz16}. Such an approach has been considered also in a star network topology but in the case where the frames to be sent require a large number of consecutive slots and without considering BE traffic \cite{dominique2018deterministic}. We also show here that priority multiplexing strategies without resource allocation can not guarantee minimum deterministic periodic latency.\\

% Unlike our previous work, it is easy to find transmission timings so that different periodic sources do not use the same resource in the context of the N-GREEN optical ring. However, we add several new difficulties: the messages of the RRH are scattered, there are other traffics whose latency must be preserved and the need to reserve containers on the ring requires additional bandwidth.

In Section \ref{sec:model}, we model the optical ring and the traffic flow. In Section \ref{sec:oportmethods}, we experimentally evaluate the latency when using stochastic multiplexing to manage packet insertions on the ring, with or without priority for C-RAN packets. In Section \ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantee to have zero latency from buffering. We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packets.

\section{Model of C-RAN traffic over an optical ring}
\label{sec:model}

  \paragraph{N-GREEN Optical ring}

  The target optical ring is modeled by a digraph which topology is a ring in which each vertex models a node that can be the origin and the destination of traffic.  Each arc $(u,v)$  is characterized by the number of slots $\omega(u,v)$, correponding also to the number of containers of each   moving from $u$ to $v$.  By extension, if $u$ and $v$ are not adjacent, we denote by $\omega(u,v)$ the number of slots on the directed path from $u$ to $v$.  The \textbf{ring size} $RS$ is the number of slots for a complete turn of a container on the ring, that is $\omega(u,u)$. A such complete turn is called a round. Each  {\bf container} on the ring has a capacity $C$  expressed in bytes. We consider a {\bf broadcast and select scheme with emission release policy} : during each unit of time, each node can fill its outgoing container   if it is empty with packets destinated to one same node and it can empty its incoming container  if it is the destination of all the packets in it (see Figure \ref{fig:containers}).

  \begin{figure}[h!]

        \begin{center}
      \hspace{-2.3cm}\includegraphics[scale=0.7]{containers}

   \vspace{0.5cm}

      \includegraphics[scale=0.7]{containers2}
      \end{center}
delay

     \caption{Dynamic behavior of the ring.}\label{fig:containers}

  \end{figure}

     \paragraph{C-RAN traffic}

  We consider a set of $RRH$, each one connected to a node on the ring through an electronic interface of bit rate $R$ Bps (note that several RRHs can be attached to the same vertex). The RRHs are the source of the {\bf deterministic and periodic} C-RAN traffic.
Assume also that the bandwidth of the ring (i.e., the sum of capacities of all the containers) is at least equal to $F\times R$ Bps. The integer $F$ is called the {\bf acceleration factor} between the electronic and the optical domains. A node aggregates the data received on the electronic interface during $F$ units of time to create a  frame of data of size $C$ and then fills a container of the ring with this frame.

A period is fixed number of consecutive slots of time.  In each period $P$, an RRH emits data during a slot called \textbf{emission time} or $ET$. Hence the RRH emits $ET / F$ packets, i.e., a container of size $C$ each $F$ units of time during the emission time, see Figure \ref{fig:interface}. Consider that he data of the RRH $i$ arrives in a period at some node $u$ at a time $m_i$  called {\bf offset}. The offsets can be determined  by the designer of the system and can be different for each RRH but must remain the same over all periods. We assume that all BBUs are contained in the same data-center attached to a node $v$. The data from $u$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u,v)$ if it has been inserted in the ring upon arrival. Then after some computation time (which w.l.o.g. is supposed to be zero), an answer is sent back from the BBU to the RRH. The same quantity of data (i.e. size of frame) is emitted by each BBU or RRH during any period.

   In this study the {\bf delay} of a message is defined as the time it waits in the origin node $u$   before being sent on the ring. The latency is thus the sum of the delay plus $\omega(u,v) $  where $v$ is the destination node.
   The aim of our study is to deterministically minimize the delay of the C-RAN traffic, both from the node connected to a target RRHs to the node connected to its  BBUs then from the BBU to the RRH (uplink and downlink traffic).
   In Section \ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero delay which preserves the latency of other data using the optical ring. We shortly describe the nature of this additional traffic in the next subsection.

\begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.7]{interface.pdf}
     \caption{Insertion in the N-GREEN optical ring.}\label{fig:interface}

\end{center}
  \end{figure}

\paragraph{Best effort traffic}

The optical ring has to serve not only C-RAN traffic but also a Best effort traffic (BE).  This BE traffic has no latency constraints to be respected, but the  distribution of delays for this BE traffic is a measure of quality of the ring.  At each node of the ring, a insertion buffer is filled with BE packets to be sent on the ring by a batch arrival process generation. Indeed, as it is generated, each BE packet is inserted in a frame associated with its destination on the ring. When a frame is enough filled or enough old (depending on chosen fill rate and maximum waiting time parameters), it is ready to be inserted into an empty container on the ring.  The generation of BE packets is modeled by a temporal law that gives the distribution of times between two arrivals of a set  of BE packets in a node. The computation of this distribution for the parameters of the insertion buffer used in the N-GREEN optical ring is described in ~\cite{youssef2018}.

   \section{Evaluation of the delay on the N-GREEN optical ring}
   \label{sec:oportmethods}
   We considered different insertion policies of C-RAN and BE frames in empty containers on the ring.   BE frames obey an opportunistic insertion policy :  when BE frames are ready to be sent, the corresponding node insert them in a outgoing  empty container as soon as it can. If there are several  such waiting BE frames in  a node,  they are stored in an insertion buffer. Two different methods to manage this insertion buffer are experimentally compared. The FIFO rule is compared to a method that uses two insertion buffers : one for the BE frames, and another for the C-RAN frames. The C-RAN insertion buffer has priority  on the BE insertion buffer.  Figure \ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule and the "C-RAN first" rule. In this experiment, the offsets of the RRH are not fixed but randomly distributed in the period. The experimental parameters are given by Figure \ref{fig:params} and chosen following~\cite{ngreenarchitecture}. The results are computed over $100$ experiments (with different random offsets) where the optical ring is simulated during $10,000,000$ units of time. The source code in C of the experiments can be found in ~\cite{webpage}.

   \vspace{0.5cm}
  \hspace{-0.75cm}

        \begin{center}
      \includegraphics[scale=0.3]{opport.pdf}

     \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}

  \scalebox{0.65}
  {

  \begin{tabular}{|c|c|}
  \hline
  Bit rate of an electronic interface $R$ & $10$ Gbps \tabularnewline
  \hline
  Optical ring bit rate $F\times R$ & $100$ Gbps \tabularnewline
  \hline
    Acceleration factor $F$ & $10$  \tabularnewline
  \hline
  Container size  $C$ & $100$ kb  \tabularnewline
  \hline
  Unit of time $C/(F\times R)$ & $1~\mu$s \tabularnewline
  \hline
  Length of the ring $RS$ & $100$ \tabularnewline
  \hline
  Emission time $ET$ & $500$ \tabularnewline
  \hline
   Period $P$ & $1,000$ \tabularnewline
  \hline
  Number of RRH & $5$  \tabularnewline
  \hline
  Number of nodes $n$ & $5$  \tabularnewline
  \hline
   Load induced by C-RAN traffic & $50\%$  \tabularnewline
  \hline
    Load induced by BE traffic & $40\%$  \tabularnewline
  \hline
  \end{tabular}
  }

  \captionof{figure}{Experimental parameters of the N-GREEN architecture}\label{fig:params}
      \end{center}

Unsurprisingly, the delay of the C-RAN traffic is better when we prioritize the C-RAN traffic, while the BE traffic is penalized. Nevertheless, there is still $10\%$ of the C-RAN traffic with a delay higher than $50 \mu$s, a problem we address in the next section.

\section{Deterministic approach for zero delay} \label{sec:deterministicalgorithms}

Finding good offsets for the C-RAN traffic is a hard problem even for simple topologies and without BE traffic, see~\cite{dominique2018deterministic}. In this section, we give a simple solution to this problem in the N-GREEN optical ring, and we adapt it to minimize the delay of the BE traffic.

Let $u$ be the node to which is attached the RRH $i$, to ensure zero delay for the C-RAN traffic, then the container which arrives at $u$ at time $m_i$ must be free so that the data from the RRH can be sent immediately on the optical ring.

To avoid delay between the arrival of the data from the RRH and its insertion on the optical ring,
we allow nodes to \textbf{reserve} a container one round before using it. A container which is reserved cannot be filled by any node except the one which has reserved it (but it may contain data when it is reserved).
Let $u$ be the node to which is attached the RRH $i$, if $u$ reserves the container $u$ at time $m_i - RS$, then it is guaranteed that $u$ can fill a free container at time $m_i$ with the data of the RRH $i$.
In the method we now describe, the C-RAN packets never wait in the node: the message sent by the RRH $i$ arrives at its BBU at node $v$ at time $m_i + \omega(u,v)$ and the answer is sent from the BBU at time $m_i + \omega(u,v) +1$.

Recall that an RRH fills a container every $F$ units of time, during a time $ET$.
Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive units of time, an RRH needs to use at most one container by slot. If an RRH emits at time $m_i$, then we say it is at \textbf{position} $m_i + \omega(u,v)\pmod F$.
The position of an RRH corresponds to the position in a slot of the container it has emitted, when it arrives at $u$.
If an RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1\pmod F$. Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position during all the period.

The problem we solve now is to find an \textbf{assignment} of values of the $m_i$'s which is \textbf{valid}: two RRHs never reserve or use the same container in a period. Moreover we want to preserve the delay of the BE traffic. It means that the time a node waits for a free container at any point of the period must be minimized.
Remark that two RRHs which are not connected to a same node on the ring never use the same containers. Moreover, if we fix the offsets of the RRHs to even positions so that they do not reserve the same containers, then it will fix the offsets of the BBUs to odd positions which do not reserve the same containers. Hence we need to deal with the RRHs only.

\begin{prop}
\label{prop:assign}
There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if  $k\times ET + RS \leq P$.
\end{prop}
\begin{proof}
 W.l.o.g we fix $m_1$ so that it is at position $0$ and all the other offsets will then be chosen at position $0$.
 Let $u_1,\dots,u_k$ be the nodes attached to the RRHs $1,\dots,k$. We assume that $u_1,\dots,u_k$ are in the order of the ring. The last message emitted by the RRH $1$ arrives at $u_2$ at time $ET - 1 + \omega(u_1,u_2)$. Therefore we can fix $m_2 = ET  + \omega(u_1,u_2)$. In general we can set $m_i = (i-1) \times ET + \omega(u_1,u_i)$ and all RRHs will use different containers at position $0$ during a period. Since $k \times ET + \omega(u_1,u_1) \leq P$ by hypothesis,
 the containers filled by the $k$th RRH are freed before $P$. Hence when the RRH $1$ must emit something in the second period, there is a free container.\qed
\end{proof}

From this proposition, it is easy to derive the maximal number of antennas which can be supported by an optical ring,
when using reservation and the same position for an RRH for the whole period.

\begin{corollary}
The maximal number of RRH such that there is an assignment is $ \lfloor\frac{P- RS}{ET}\rfloor \times \frac{F}{2}$.
\end{corollary}
\begin{proof}
Following Prop.~\ref{prop:assign}, the number of antennas on a position is $k = \lfloor\frac{P- RS}{ET}\rfloor $.
Since we need two positions for $k$ antennas, in order to carry the traffic coming from the RRHs and the BBUs, and we got $F$ positions in the slot, the number of antennas supported by the ring is thus equal to $k \times \frac{F}{2}$.\qed
\end{proof}

We now present an algorithm using reservation as in Proposition \ref{prop:assign} to set the offsets at the same position.
In the naive version of the algorithm, we put each RRH in an arbitrary position, for instance one RRH by position.
 We then propose three ideas to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.

\paragraph{Packing}

For each position which is used by some RRH, and during each period, $RS$ containers are reserved before starting to emit some C-RAN traffic, while they are free. Hence, it decreases the maximal load the system can handle.
Therefore to not waste bandwidth, it is relevant to put as many RRHs as possible on the same position as in Figure \ref{fig:packing}. Indeed, for any position which is not used at all, $RS$ containers need not to be reserved. This strategy is also good for the latency of the BE traffic. If a position is unused, then there is always a container free of C-RAN traffic each $F$ unit of times.

\begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.5]{repart0}
     \caption{Packing.}\label{fig:packing}

\end{center}
  \end{figure}

\paragraph{Balancing inside the slot}

The free positions can be distributed uniformly over a slot, to minimize the time to wait before a node
has access to a free container, as shown in Figure~\ref{fig:slotbal}. It is a small optimization, since
it decreases the delay of at most $F/2$.

\begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.55]{repart1}
     \caption{Balancing inside the slot.}\label{fig:slotbal}

\end{center}
  \end{figure}
\paragraph{Balancing inside the period}

It is possible that there are no unused position as it happens with the parameters of the N-GREEN ring given in Figure~\ref{fig:params}: $ET = \frac{P}{2}$, $F = 10$ and $n = 5$. Any assignment has exactly one  BBU or RRH at each position. If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge delay for the BE traffic.
To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in  Figure~\ref{fig:periodbal}.
\begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.55]{repart2}
     \caption{Balancing inside the period.}\label{fig:periodbal}

\end{center}
  \end{figure}
  \paragraph{Experimental evaluation}

To evaluate the effectiveness of the allocation approach proposed here, we will compare its performances in terms of delays with the ones of several methods without allocation. So in order to understand the contribution of the three approaches presented in the previous subsection, we first give the cumulative distribution of the delay of the BE traffic  in Figure \ref{fig:algocmp}. To evaluate the performances of  the  N-GREEN ring when   several RRHs are connected to a same node on the ring, the parameter $ET$ has been set to $400$.

The performance with the no packing approach is really bad, even worst than the methods using an insertion buffer. It is explained by the parameters of the N-GREEN ring: all positions are used and thus, there are no free containers available to BE traffic during $ET+RS$ units of time. When packing the RRHs on a minimal number of positions, the delay decreases dramatically and becomes much better than in the previous methods. The optimizations of spacing inside the slot brings almost no benefit as expected. The spacing over a period improves the delay marginally. In settings with an higher load, spacing inside a period would have a much larger effect.

In Figure \ref{fig:optimres}, we compare the cumulative distribution of the delay of the BE traffic using the FIFO rule or the reservation algorithm proposed here. To keep the load at $90\%$ as in the experiment of  Figure~\ref{fig:resultopport}, we set $ET = 200$ and $n = 12$. This is not out of context since the exact split of the C-RAN (the degree of centralization of the computation units in the cloud) is not fully determined yet~\cite{mobile2011c}. With these parameters, the loss of bandwidth due to reservation is at most $6\%$

\begin{center}
      \includegraphics[scale=0.25]{repart1res}
     \captionof{figure}{Impact of the repartition on the delay.} \label{fig:algocmp}

\vspace{0.5cm}

      \includegraphics[scale=0.25]{optim.pdf}
     \captionof{figure}{Impact of the deterministic method on the traffics.}   \label{fig:optimres}

\end{center}
  The performance of the reservation algorithm is excellent, since the C-RAN traffic has {\bf zero delay} and the BE traffic has a \textbf{better delay} with reservation than with the FIFO rule. It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth for the BE traffic.

  \bibliographystyle{ieeetr}
\bibliography{src}

\end{document}
\bibitem{Sz16} T. H. Szymanski. An Ultra-Low-Latency Guaranteed-Rate Internet for Cloud Services. IEEE/ACM TRANSACTIONS ON NETWORKING, VOL. 24, NO. 1, FEBRUARY 2016

### 2018-12-17 v3/img/anneau1.tex
v3

 \usepackage[usenames,dvipsnames]{pstricks}
 \usepackage{epsfig}
 \usepackage{pst-grad} % For gradients
 \usepackage{pst-plot} % For axes
 \usepackage[space]{grffile} % For spaces in paths
 \usepackage{etoolbox} % For spaces in paths
 \makeatletter % For spaces in paths
 \patchcmd\Gread@eps{\@inputcheck#1 }{\@inputcheck"#1"\relax}{}{}
 \makeatother
 \psscalebox{1.0 1.0} % Change this value to rescale the drawing.
{
\begin{pspicture}(0,-4.384483)(7.640009,4.384483)
\definecolor{colour1}{rgb}{0.99607843,0.99607843,0.99607843}
\definecolor{colour2}{rgb}{0.0,0.21960784,1.0}
\definecolor{colour0}{rgb}{0.003921569,0.003921569,0.003921569}
\pscircle[linecolor=black, linewidth=0.04, dimen=outer](3.9169683,-0.7844828){3.6}
\psline[linecolor=black, linewidth=0.04](3.2710423,3.40811)(3.2710423,3.0881097)(3.9110425,3.0881097)(3.9110425,3.40811)(3.9110425,3.0881097)
\psline[linecolor=black, linewidth=0.04](4.2497125,3.3680239)(4.2118726,3.050269)(4.8473825,2.9745896)(4.885222,3.2923446)(4.8473825,2.9745896)
\psline[linecolor=black, linewidth=0.04](5.1756554,3.2069407)(5.0436735,2.915426)(5.626703,2.6514623)(5.7586846,2.942977)(5.626703,2.6514623)
\psdots[linecolor=black, dotsize=0.4](3.531783,2.756258)
\psdots[linecolor=black, dotsize=0.4](0.346598,-0.88818645)
\psdots[linecolor=black, dotsize=0.4](1.9910425,-3.8215199)
\psdots[linecolor=black, dotsize=0.4](6.1688204,-3.6141124)
\psdots[linecolor=black, dotsize=0.4](7.4428945,-0.058556832)
\psline[linecolor=black, linewidth=0.04](5.9804435,2.86024)(5.803907,2.5933414)(6.3377037,2.2402682)(6.5142403,2.5071669)(6.3377037,2.2402682)
\psframe[linecolor=colour1, linewidth=0.002, fillstyle=solid,fillcolor=red, dimen=outer](3.8861992,3.4001327)(3.2913275,3.1026967)
\rput{-5.980281}(-0.30656177,0.4910689){\psframe[linecolor=colour1, linewidth=0.002, fillstyle=solid,fillcolor=colour2, dimen=outer](4.8498363,3.3338156)(4.244708,3.0261233)}
\psbezier[linecolor=colour0, linewidth=0.04, arrowsize=0.05291667cm 2.0,arrowlength=1.4,arrowinset=2.0]{<-}(1.5919684,2.9530172)(-0.19553162,2.4530172)(0.041968383,0.50301725)(0.041968383,1.303017241379314)
\rput[bl](3.0342097,-0.03965517){\textcolor{colour0}{$k$ nodes}}
\rput[bl](3.1859338,4.0844827){\textcolor{colour0}{Step $t = 0$}}
\psline[linecolor=colour0, linewidth=0.04, arrowsize=0.05291667cm 2.0,arrowlength=1.4,arrowinset=2.0]{<-}(3.5445545,2.3051724)(3.5583477,0.37413794)(3.5721407,0.38793105)
\psline[linecolor=colour0, linewidth=0.04, arrowsize=0.05291667cm 2.0,arrowlength=1.4,arrowinset=2.0]{<-}(0.799727,-0.7982759)(2.7445545,-0.10862069)
\psline[linecolor=colour0, linewidth=0.04, arrowsize=0.05291667cm 2.0,arrowlength=1.4,arrowinset=2.0]{<-}(2.3307614,-3.3637931)(3.1859338,-0.42586207)
\psline[linecolor=colour0, linewidth=0.04, arrowsize=0.05291667cm 2.0,arrowlength=1.4,arrowinset=2.0]{<-}(5.751451,-3.1982758)(3.7790372,-0.42586207)
\psline[linecolor=colour0, linewidth=0.04, arrowsize=0.05291667cm 2.0,arrowlength=1.4,arrowinset=2.0]{<-}(7.075589,-0.08103448)(4.385934,-0.02586207)
\end{pspicture}
}

### 2018-12-18 v3/articleV3.tex

--- 2018-12-17 ISCIS/articleV3.tex
@@
 In this article, we study a Cloud RAN (C-RAN) application based on the N-GREEN optical ring described in~\cite{ngreenarchitecture,uscumlicscalable}.
-C-RAN is one of the major area of development for 5G; it consists in centralizing or partially centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter.\todo{ref CRAN} The latency of the messages between the BBU and the RRH is critical since some services need end-to-end latency as low as $1$ms~\cite{3gpp5g,boccardi2014five}.
-\todo{Decrire le process periodique, periode latence max et uplink downlink,meme taille de frame}
+C-RAN is one of the major area of development for 5G; it consists in centralizing or partially centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter~\cite{mobile2011c}.
+Periodically, each RRH on the field send some uplink traffic to its associated BBU in the datacenter, then, after a computation, the BBU send the same quantity of downlink traffic back to the RRH.
+The latency of the messages between the BBU and the RRH is critical since some services need end-to-end latency as low as $1$ms~\cite{3gpp5g,boccardi2014five}.
 
-In this article we propose an SDN approach to {\bf deterministically} manage the periodic C-RAN traffic by choosing emission timing.\todo{dire que pour l'instant on gere le traffic par statistical multiplexing(refs) + chercher ring SDN mots clefs + detNet ?} In a previous work~\cite{dominique2018deterministic}, the authors have studied a similar problem for a star shaped network.
+Nowadays, the traffic is managed by statistical multiplexing \todo{ref}.
+Here, we propose an SDN approach to {\bf deterministically} manage the periodic C-RAN traffic by choosing emission timing.
+Indeed, Deterministic Networking is one of the strong current aspects considered to reduce the E2E latency~\cite{finn-detnet-architecture-08}.
+In a previous work~\cite{dominique2018deterministic}, the authors have studied a similar problem for a star shaped network.
 In contrast with our previous work, finding emission timings so that different periodic sources do not use the same resource is easy in the context of the N-GREEN optical ring.
-However, we add several new difficulties: the messages from RRHs are scattered, there are other traffics whose latency must be preserved and the need to make reservation of containers on the ring requires additional bandwidth.
-\todo{on met la latence CRAN a 0, on minimise le BE car on lisse bien le traffic, mais par contre ca coute de la bandiwth de faire de la reservation}
-\todo{parler du slicing (virtual circuit switching) }
+However, we add several new difficulties: the messages from RRHs are scattered, there are other traffics whose latency must be preserved.
+Indeed, even if we find some solutions to reduce the latency of CRAN traffic to the physical delay of the routes, we managed to reduce the latency of the other traffic by smoothing the load of the ring in the time.
+Also, to reduce the latency of the CRAN traffic, some ressource reservation need to be made and thus induce an additional load of the network.
+Such an approach of reservation of the network for an application (CRAN in our context) relate to the network slicing~\cite{jiang2016network}.
 
@@
 The same quantity of data is emitted by each BBU or RRH during any period.
-   In this study the {\bf latency} of a message is defined as the time it waits in a node before being sent on the ring.
-\todo{dire qu'il y a aussi le temps physique, mais qu'on ne peux minimiser que la latence du buffer d'insertion et que donc, parler de "zero latency veut en realité dire "zero logical latency"}
+   In this study the {\bf latency} of a packet is defined as the time it waits in a node before being sent on the ring.
+In practice, the latency is equal to the physical transmission delay of the message plus the buffering time of this message in the network.
+Since we can not reduce the physical delay, and there is only one buffering point (in the insertion buffer of the node), we will call latency of a packet the time spent by this packet in the insertion buffer.
+
    The aim of our study is to minimize the latency of the C-RAN traffic, both of the RRHs and the BBUs. 
@@
 
-  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node has a free container available, it fills it with a packet of its insertion buffer, if it exists one.\todo{peut etre reprendre}
+  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node has a free container available, it fills it with a packet of its insertion buffer, if it exists one.
  Two different methods to manage the insertion buffer are experimentally compared.
-The FIFO rule is compared to a method that uses two insertion buffers:\todo{decrire fifo rule, plus clair} one for the BE packets, and another for the C-RAN packets.
-The C-RAN insertion buffer first has the priority and is used to fill containers on the ring while it is non empty before considering the BE insertion buffer.
-Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO rule and the "C-RAN first" rule.
+First, the \textbf{FIFO} rule, that consist to manage all the C-RAN and BE packets in a same insertion buffer.
+Then, when a free container is available, the node fills it with the oldest packet of the insertion buffer, without distinction between C-RAN and BE.
+This method is compared to a method called \textbf{C-RAN prio} that uses two insertion buffers: one for the BE packets, and another for the C-RAN packets.
+The C-RAN insertion buffer has the priority and is used to fill containers on the ring while it is non empty before considering the BE insertion buffer.
+Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO and the C-RAN prio methods.
 In this experiment, the offsets of the RRH are not fixed but randomly distributed in the period.
@@
      \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}
+\end{center}
 
-  \scalebox{0.65}
+\begin{minipage}[t]{.46\linewidth}
+
+  \scalebox{.55}
   {
-
   \begin{tabular}{|c|c|}
@@
   \hline
-  Unit of time $C/(F\times R)$ & $1~\mu$s \tabularnewline
+  Unit of time (UoT) $C/(F\times R)$ & $1~\mu$s \tabularnewline
   \hline
-  Length of the ring $RS$ & $100$ \tabularnewline
+  Length travelled during one UoT & $200$m \tabularnewline
   \hline
-  Emission time $ET$ & $500$ \tabularnewline
+    \end{tabular}
+  }
+
+\end{minipage} % ne pas sauter de ligne
+\begin{minipage}[t]{.46\linewidth}
+   \scalebox{.55}
+  {
+  \begin{tabular}{|c|c|}
   \hline
-   Period $P$ & $1,000$ \tabularnewline
+  Length of the ring $RS$ & $100$UoT \tabularnewline
+  \hline
+  Emission time $ET$ & $500$UoT \tabularnewline
+  \hline
+   Period $P$ & $1,000$UoT \tabularnewline
   \hline
@@
 }
-\todo{revoir table au lieu de figure}
-  \captionof{figure}{Parameters of the N-GREEN architecture}\label{fig:params}
-      \end{center} \todo{premier tableau longueur parcourue en une unite of time 200m, deux tableaux Un N-Green parametres, un valuers choisie}
+\end{minipage}
+
+  \captionof{table}{Parameters of the N-GREEN architecture}\label{fig:params}
 
 Unsurprisingly, the latency of the C-RAN traffic is better when we prioritize the C-RAN messages, while the BE traffic is heavily penalized.
-Nevertheless, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s, a problem we address in the next section.
-\todo{expliquer que le CRAN se concentre sur la moitié de la periode donc il mange plus que les BE en FIFO, + parler du fait que y'a un moment dans l'anneau ou on aura un peu plus de cRAN}
+Furthermore, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s, a problem we address in the next section.
+Remark that the C-RAN and BE traffic latency distribution is not the same with the FIFO method.
+Indeed, the offset of the C-RAN traffic is uniformly drawn in the period, thus, statistically, there is a moment in the period during which there is several C-RAN traffics simultaneously.
+Also, the C-RAN traffic is heavy and concentrated on half of the period, thus, those two phenomena induce some higher latencies for C-RAN traffic, while the BE traffic is generated uniformly during all the period.
 
@@
 
-Given, ....
-\todo{entrees du problemes} The problem we solve now is to find an \textbf{assignment} of values of the $m_i$'s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
+Given, a ring, a set of RRH, a period and an acceleration factor $F$, the problem we solve here is to find an \textbf{assignment} of values of the $m_i$'s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
 Moreover we want to preserve the latency of the BE traffic.
-It means that the time a node waits for a free container at any point of the period must be minimized.\todo{to minimize the time a node ......., we must minimize the time in the insertion buffer, en placant le traffic CRan de facon a avoir en moyenne le moins de temps possible}
+It means that the time a BE packet spent in the insertion buffer must be minimized.
+To do so, we must minimize the time a node waits for a free container at any point of the period, by spreading the C-RAN traffic in order to give to the nodes an available container in a minimal average time..
 \todo{dessin represnetation d'un assignement}

### 2018-12-19 v3/articleV3.tex
petits comléments et corrections

@@
 The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end to end direct connections (E2DE) between the nodes, which is extremely expensive.
-The N-GREEN optical ring is designed to ensure good performance: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.
+The N-GREEN optical ring is designed to ensure good performance for a low cost: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.
 
@@
 In contrast with our previous work, finding emission timings so that different periodic sources do not use the same resource is easy in the context of the N-GREEN optical ring.
-However, we add several new difficulties: the messages from RRHs are scattered, there are other traffics whose latency must be preserved.
-Indeed, even if we find some solutions to reduce the latency of CRAN traffic to the physical delay of the routes, we managed to reduce the latency of the other traffic by smoothing the load of the ring in the time.
-Also, to reduce the latency of the CRAN traffic, some ressource reservation need to be made and thus induce an additional load of the network.
-Such an approach of reservation of the network for an application (CRAN in our context) relate to the network slicing~\cite{jiang2016network}.
+However, we add two new difficulties arising from practice: the messages from RRHs are scattered and there are other traffics whose latency must be preserved.
+It turns out that the deterministic management of CRAN traffic
+we propose reduce the latency of CRAN traffic to the physical delay of the routes, while reducing the latency of the other traffics by smoothing the load of the ring in the period.
+However, to achieve such a good latency, our solution needs to reserve ressource in advance, which slightly decreases the maximal load the N-GREEN optical ring can manage.
+Such an approach of reservation of the network for an application (CRAN in our context) relates to network slicing~\cite{jiang2016network}.
 
@@
 In Sec.~\ref{sec:oportmethods}, we experimentally evaluate the latency when using stochastic multiplexing to manage packet insertions on the ring, with or without priority for C-RAN packets.
-In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantee to have zero latency from buffering.
+In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantees to have zero latency from buffering.
 We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packets.
@@
 The vertices of the cycle represent the nodes of the ring, where the traffic arrives.
-The edges $(u,v)$ of the cycle have an integer weight $\omega(u,v)$ which represents the time to transmit a unit of information from $u$ to $v$.
+The arcs $(u,v)$ of the cycle have an integer weight $\omega(u,v)$ which represents the time to transmit a unit of information from $u$ to $v$.
 By extension, if $u$ and $v$ are not adjacent, we denote by $\omega(u,v)$ the size of the directed path from $u$ to $v$.
@@
 
-  The time is discretized : a unit of time corresponds to the time needed to fill a container with data.
-  As shown in Fig.~\ref{fig:containers}, the node $u$ can fill a container with a data packet of size less than $C$ bytes at time $t$ if the container 
-  at position $u$ at time $t$ is \emph{free}. 
+  The time is discretized: a unit of time corresponds to the time needed to fill a container with data.
+  As shown in Fig.~\ref{fig:containers}, the node $u$ can fill a container with a data packet of size less than $C$ bytes at time $t$ if the container at position $u$ at time $t$ is \emph{free}. 
   If there are several packets in a node or if a node cannot fill a container, because it is not free, 
@@
   A container goes from $u$ to $v$ in $\omega(u,v)$ units of time.
-The ring follows a {\bf broadcast and select scheme with emission release policy}: When a container is filled by some node $u$, it is freed when it comes back at $u$ after a whole round trip.
+The ring follows a {\bf broadcast and select scheme with emission release policy}: When a container is filled by some node $u$, it is freed when it comes back at $u$ after going through the whole cycle.
 
@@
    There are $n$ RRHs attached to the ring and several RRHs can be attached to the same vertex. An RRH is linked to a node of the ring through an electronic interface of bit rate $R$ Bps.
-   The ring has a larger rate of $F\times R$ Bps.
+   The ring has a larger bit rate of $F\times R$ Bps.
 The integer $F$ is called the {\bf acceleration factor} between the electronic and the optical domains.
@@
 The same quantity of data is emitted by each BBU or RRH during any period.
-   In this study the {\bf latency} of a packet is defined as the time it waits in a node before being sent on the ring.
-In practice, the latency is equal to the physical transmission delay of the message plus the buffering time of this message in the network.
-Since we can not reduce the physical delay, and there is only one buffering point (in the insertion buffer of the node), we will call latency of a packet the time spent by this packet in the insertion buffer.
 
-   The aim of our study is to minimize the latency of the C-RAN traffic, both of the RRHs and the BBUs. 
-   In Sec.~\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency which preserves the latency of other data using the optical ring.
+   The {\bf latency} of a data packet is defined as the time it waits in an insertion buffer.
+   Indeed, the routing is fixed, thus we cannot reduce the physical transmission delay of a data which depends only on the size of the arcs used.
+Moreover, there is only one buffering point in the N-GREEN optical ring, the insertion buffer of the node at which the data arrives.
+Hence, in this context, to minimize the time data need to go from source to destination, we need to minimize their (logical) latency.
+   In particular, we want to reduce the latency of the C-RAN traffic to \textbf{zero}, both for the RRHs (uplink) and the BBUs (downlink).
+In Sec.~\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency for C-RAN which also improves the latency of other data going through the optical ring.
 We shortly describe the nature of this additional traffic in the next subsection.
@@
 At each node of the ring, a {\bf contention buffer} is filled by a batch arrival process of BE data.
-Then according to some parameters, fill rate and maximum waiting time, data on the contention buffer are aggregated in a packet of size at most $C$.
+\todo{dire plus précisément ce qu'est ce processus d'arrivée -> un truc qui simule du traffic de réseau avec burst en citant youssef pour les détails.
+Insister sur le fait que c'est donc un traffic aléatoire contrairement au C-RAN}
+Then, according to the fill rate of the contention buffer and the maximum waiting time of the data, 
+a packet of size at most $C$ is created by aggregating data in the contention buffer.
 This packet is then put in the insertion buffer of the node.
@@
  Two different methods to manage the insertion buffer are experimentally compared.
-First, the \textbf{FIFO} rule, that consist to manage all the C-RAN and BE packets in a same insertion buffer.
+First, the \textbf{FIFO} rule, that consist in managing the C-RAN and BE packets in the same insertion buffer.
 Then, when a free container is available, the node fills it with the oldest packet of the insertion buffer, without distinction between C-RAN and BE.
@@
 Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO and the C-RAN prio methods.
-In this experiment, the offsets of the RRH are not fixed but randomly distributed in the period.
+In this experiment, the offsets of the RRH have been randomly distributed in the period.
 The experimental parameters are given by Fig.~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
@@
   \hline
-  Length travelled during one UoT & $200$m \tabularnewline
+  Length traveled during one UoT & $200$ m \tabularnewline
   \hline
@@
   \hline
-  Length of the ring $RS$ & $100$UoT \tabularnewline
+  Time to go through the cycle $RS$ & $100$ UoT \tabularnewline
   \hline
-  Emission time $ET$ & $500$UoT \tabularnewline
+  Emission time $ET$ & $500$ UoT \tabularnewline
   \hline
-   Period $P$ & $1,000$UoT \tabularnewline
+   Period $P$ & $1,000$ UoT \tabularnewline
   \hline
@@
 Remark that the C-RAN and BE traffic latency distribution is not the same with the FIFO method.
-Indeed, the offset of the C-RAN traffic is uniformly drawn in the period, thus, statistically, there is a moment in the period during which there is several C-RAN traffics simultaneously.
-Also, the C-RAN traffic is heavy and concentrated on half of the period, thus, those two phenomena induce some higher latencies for C-RAN traffic, while the BE traffic is generated uniformly during all the period.
+This comes from the fact that these two sources of traffic are of different nature.
+With high probability, there are some part of the period which have more
+BE data arrivals (or C-RAN traffic) than average.
+In both cases, it makes the latency higher during these times.
+However a C-RAN emission from an RRH takes half the period while a BE arrival corresponds to only a few unit of times, which explains why the C-RAN traffic suffers  more from this phenomena.
 
@@
 
-Given, a ring, a set of RRH, a period and an acceleration factor $F$, the problem we solve here is to find an \textbf{assignment} of values of the $m_i$'s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
+Given a ring, a set of RRH's, a period and an acceleration factor $F$, the problem we solve here is to find an \textbf{assignment} of values of the $m_i$'s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
 Moreover we want to preserve the latency of the BE traffic.
 It means that the time a BE packet spent in the insertion buffer must be minimized.
-To do so, we must minimize the time a node waits for a free container at any point of the period, by spreading the C-RAN traffic in order to give to the nodes an available container in a minimal average time..
+To do so, we must minimize the time a node waits for a free container at any point in the period, by spreading the C-RAN traffic as uniformly as possible over the period in order to give the nodes an available container in a minimal average time.
 \todo{dessin represnetation d'un assignement}
@@
 Moreover, if we fix the offsets of the RRHs to even positions so that they do not reserve the same containers, then it will fix the offsets of the BBUs to odd positions which do not reserve the same containers.
-Hence we need to deal with the RRHs only.
+Hence, we need to deal with the RRHs only.
 
@@
 \end{proof}
-\todo{on perds pas trop pck on a fait dans l'odre mais on perds quand meme RS * F en bandwidth}
 
-From this proposition, it is easy to derive the maximal number of antennas which can be supported by an optical ring,
-when using reservation and the same position for an RRH for the whole period.
+Remark that the loss of containers from reservation is modest: only $RS$ by period. 
+This comes from the choice of emission times of the RRHs which are taken in the order of the cycle so that there are no free containers at position zero except at the end of the period.
+From this proposition, it is easy to derive the maximal number of antennas which can be supported by an optical ring, when using reservation and the same position for an RRH for the whole period.
 
@@
 \end{proof}
-\todo{dire qu'on perds de la place a cause de la partie entire (p / et * f/2 avec le statistical multuplexing), on peut eventuellement s'arranger pour caler un peu plus d'antennes quand meme en deterministic}
+
+There are two sources of inefficiency in this method.
+The first comes from the reservation and cannot be avoided to guarantee the latency of the C-RAN traffic.
+The second however comes from the fact that we chose
+to emit all data coming from an antenna at the same position (to guarantee zero latency).
+If we relax this constraint and allows to change the position of data coming from the same source during the period,
+we can use \emph{all} containers at some position and we could support $\frac{P- RS}{ET} \times \frac{F}{2}$ antennas (losing the floor in the formula).
 
 We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets at the same position.
-In the basline version of the algorithm, we put each RRH in an arbitrary position, for instance one RRH by position.
+In the baseline version of the algorithm, we put each RRH in an arbitrary position, for instance one RRH by position.
 We then propose three ideas to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.

### 2018-12-21 v3/articleV3.tex
version quazi finale

@@
 \title{Contention management for Cloud RAN over an optical ring}
+\makeatletter
+\renewcommand*{\thetable}{\arabic{table}}
+\renewcommand*{\thefigure}{\arabic{figure}}
+\let\c@table\c@figure
+\makeatother
 
@@
 
-In this article, we study a Cloud RAN (C-RAN) application based on the N-GREEN optical ring described in~\cite{ngreenarchitecture,uscumlicscalable}.
+In this article, we study a Cloud RAN (C-RAN) application based on the N-GREEN optical ring described in~\cite{ngreenarchitecture,uscumlic2018scalable}.
 C-RAN is one of the major area of development for 5G; it consists in centralizing or partially centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter~\cite{mobile2011c}.
@@
 
-Nowadays, the traffic is managed by statistical multiplexing \todo{ref}.
+Nowadays, the traffic is managed by statistical multiplexing~\cite{kern2006applying}.
 Here, we propose an SDN approach to {\bf deterministically} manage the periodic C-RAN traffic by choosing emission timing.
@@
 However, to achieve such a good latency, our solution needs to reserve ressource in advance, which slightly decreases the maximal load the N-GREEN optical ring can manage.
-Such an approach of reservation of the network for an application (CRAN in our context) relates to network slicing~\cite{jiang2016network}.
+Such an approach of reservation of the network for an application (CRAN in our context) relates to network slicing~\cite{jiang2016network} or virtual-circuit-switched  connections in optical networks~\cite{cadere2010virtual,szymanski2016ultra}.
 
@@
         \begin{center}
-      \hspace{-2.3cm}\includegraphics[scale=0.7]{containers}
+      \hspace{-2.3cm}\includegraphics[scale=0.65]{containers}
 
-   \vspace{0.5cm}
+  % \vspace{0.5cm}
 
-      \includegraphics[scale=0.7]{containers2}
+      %\includegraphics[scale=0.7]{containers2}
       \end{center}
@@
    The {\bf latency} of a data packet is defined as the time it waits in an insertion buffer.
-   Indeed, the routing is fixed, thus we cannot reduce the physical transmission delay of a data which depends only on the size of the arcs used.
+   Indeed, because of the ring topology, the routes between RRHs and BBUs are fixed, thus we cannot reduce the physical transmission delay of a data which depends only on the size of the arcs used.
 Moreover, there is only one buffering point in the N-GREEN optical ring, the insertion buffer of the node at which the data arrives.
-Hence, in this context, to minimize the time data need to go from source to destination, we need to minimize their (logical) latency.
+Hence, in this context, to minimize the end-to-end delay, we need to minimize the (logical) latency.
    In particular, we want to reduce the latency of the C-RAN traffic to \textbf{zero}, both for the RRHs (uplink) and the BBUs (downlink).
@@
 At each node of the ring, a {\bf contention buffer} is filled by a batch arrival process of BE data.
-\todo{dire plus précisément ce qu'est ce processus d'arrivée -> un truc qui simule du traffic de réseau avec burst en citant youssef pour les détails.
-Insister sur le fait que c'est donc un traffic aléatoire contrairement au C-RAN}
+This batch arrival process consist in generating, at each unit of time, a quantity of data drawn from a bimodal distribution to modelize the fact that internet traffic is sometimes bursty.
 Then, according to the fill rate of the contention buffer and the maximum waiting time of the data,
@@
 This packet is then put in the insertion buffer of the node.
-Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a packet of BE messages in a node.
-The computation of this distribution for the parameters of the contention buffer used in the N-GREEN optical ring is described in ~\cite{youssef2018}\todo{mettre la bonne ref}.
+Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a BE packet in the insertion buffer.
+The computation of this distribution for the parameters of the contention buffer used in the N-GREEN optical ring is described in~\cite{Cast1810:Performance}.
 
@@
 Then, when a free container is available, the node fills it with the oldest packet of the insertion buffer, without distinction between C-RAN and BE.
-This method is compared to a method called \textbf{C-RAN prio} that uses two insertion buffers: one for the BE packets, and another for the C-RAN packets.
+This method is compared to a method called \textbf{C-RAN priority} that uses two insertion buffers: one for the BE packets, and another for the C-RAN packets.
 The C-RAN insertion buffer has the priority and is used to fill containers on the ring while it is non empty before considering the BE insertion buffer.
-Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO and the C-RAN prio methods.
+
+We compare experimentally these two methods in the simplest topology: The lengths of the arcs between nodes are equal and there is one RRH by node.
+The experimental parameters are given in Table~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
 In this experiment, the offsets of the RRH have been randomly distributed in the period.
-The experimental parameters are given by Fig.~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
-The results are computed over $100$ experiments (with different random offsets) where the optical ring is simulated during $10,000,000$ units of time.
+The results are computed over $1,000$ experiments (with different random offsets) where the optical ring is simulated during $1,000,000$ units of time.
+Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO and the C-RAN priority methods.
 The source code in C of the experiments can be found on one of the authors webpage~\cite{webpage}.
-\todo{revoir 100 1000000}
-
    \vspace{0.5cm}
@@
 
+\begin{figure}[h]
 \begin{minipage}[t]{.46\linewidth}
@@
 \end{minipage}
-
   \captionof{table}{Parameters of the N-GREEN architecture}\label{fig:params}
+\end{figure}
 
@@
 To do so, we must minimize the time a node waits for a free container at any point in the period, by spreading the C-RAN traffic as uniformly as possible over the period in order to give the nodes an available container in a minimal average time.
-\todo{dessin represnetation d'un assignement}
+
+Figure~\ref{fig:assignment} represent an assignment of three couples RRH-BBU.
+each slot has a duration $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in the time, during $ET$ UoT.
+Also, if we take a date $t$ in the period $P$, then $t$ is in the slot $\frac{P}{F}$ and is at position $P \mod F$.
+
+\begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.65]{assignment}
+     \caption{Representation of an assignment with $F = 6$.}\label{fig:assignment}
+
+\end{center}
+  \end{figure}
 
 Remark that two RRHs which are not at the same position never use the same containers.
-Moreover, if we fix the offsets of the RRHs to even positions so that they do not reserve the same containers, then it will fix the offsets of the BBUs to odd positions which do not reserve the same containers.
+Moreover, if we fix the offsets of the RRHs to even positions so that they do not reserve the same containers, then, because the answers of the BBU are sent without delay in our model, it will fix the offsets of the BBUs to odd positions which do not reserve the same containers.
 Hence, we need to deal with the RRHs only.
@@
 
-Remark that the loss of containers from reservation is modest: only $RS$ by period. 
-This comes from the choice of emission times of the RRHs which are taken in the order of the cycle so that there are no free containers at position zero except at the end of the period.
-From this proposition, it is easy to derive the maximal number of antennas which can be supported by an optical ring, when using reservation and the same position for an RRH for the whole period.
+Remark reserving free containers make them unusable for BE traffic which is akin to a loss of bandwidth.
+However, with our choice of emission times of the RRHs in the order of the cycle, we reserve $ (k-1)\times RS$ containers used by other RRHs and only $RS$ free containers are wasted.
+
+From Proposition~\ref{prop:assign}, it is easy to derive the maximal number of antennas which can be supported by an optical ring, when using reservation and the same position for an RRH for the whole period.
 
@@
 The first comes from the reservation and cannot be avoided to guarantee the latency of the C-RAN traffic.
-The second however comes from the fact that we chose
-to emit all data coming from an antenna at the same position (to guarantee zero latency).
-If we relax this constraint and allows to change the position of data coming from the same source during the period,
-we can use \emph{all} containers at some position and we could support $\frac{P- RS}{ET} \times \frac{F}{2}$ antennas (losing the floor in the formula).
+The second however comes from the fact that an RRH must emit at the same position during all the emission time (to guarantee zero latency).
+If we allow to change the position of data coming from the same RRH during the period,
+we can use \emph{all} containers in a position and hence we could support $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$ antennas.
 
@@
 
-\paragraph{Packing}
+\paragraph{Compacting positions}
 
-For each position which is used by some RRH, and during each period, $RS$ containers are reserved before starting to emit some C-RAN traffic, while they are free.
+For each position which is used by some RRH, and during each period, $RS$ containers are reserved before starting to emit some C-RAN traffic, while they can be free.
 Hence, it decreases the maximal load the system can handle.
@@
 If a position is unused, then there is always a container free of C-RAN traffic each $F$ unit of times.
-\todo{c bon deja pour la bandwith et aussi on s'assure d'avoir un container tout les F unit+ packing bof comme nom}
 \begin{figure}[h!]
@@
       \includegraphics[scale=0.5]{repart0}
-     \caption{Packing.}\label{fig:packing}
+     \caption{Compacting positions.}\label{fig:packing}
 
@@
 
-\paragraph{Balancing inside the slot}
+\paragraph{Balancing used positions}
 
 The free positions can be distributed uniformly over a slot, to minimize the time to wait before a node 
-has access to a free container, as shown in Fig.~\ref{fig:slotbal}. It is a small optimization, since 
+has access to a free container, as shown in Fig.~\ref{fig:slotbal}.
+To do so, compute the number of needed frequencies $x = \lceil k\times \frac{ET}{P - RS}\rceil$, with k the number of antennas.
+Then, choose the $x$ positions in the following way: $\frac{F}{x} -1 $ free positions are set between each used positions.
+If $\frac{F}{x}$ has a reminder, then let one more free position between the $F \mod x$ first used position.
+It is a small optimization, since
 it decreases the latency of at most $F/2$.
-\todo{dire trois mots sur les restes des restes etc}
+
 \begin{figure}[h!]
@@
       \includegraphics[scale=0.55]{repart1}
-     \caption{Balancing inside the slot.}\label{fig:slotbal}
+     \caption{Balancing used positions.}\label{fig:slotbal}
 
@@
 
-The performance when we do no packing is really bad, even worst than the methods using an insertion buffer.
+The performance when we do no compacting positions is really bad, even worst than the methods using an insertion buffer.
 It is explained by the parameters of the N-GREEN ring: all positions are used and thus, there are no free containers available to BE traffic during $ET+RS$ units of time.
-When packing the RRHs on a minimal number of positions, the latency decreases dramatically and becomes much better than in the previous methods.
+When compacting the RRHs on a minimal number of positions, the latency decreases dramatically and becomes much better than in the previous methods.
 The optimizations of spacing inside the slot brings almost no benefit as expected.
@@
 In Fig.~\ref{fig:optimres}, we compare the cumulative distribution of the latency of the BE traffic using the FIFO rule or the reservation algorithm proposed here.
-To keep the load at $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}, we set $ET = 200$ and $n = 12$.
+To keep the load around $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}, we set $ET = 200$ and $n = 12$.
 This is not out of context since the exact split of the C-RAN (the degree of centralization of the computation units in the cloud) is not fully determined yet~\cite{mobile2011c}.
@@
 \vspace{0.5cm}
-
+\todo{packing seul programmé, a voir comment on l'integre dans les resultats}
       \includegraphics[scale=0.25]{optim.pdf}

### 2019-01-08 v3/articleV3.tex
plein de petites corrections

@@
 \graphicspath{{img/}}
-\title{Contention management for Cloud RAN over an optical ring}
+\title{Deterministic contention management for low latency Cloud RAN over an optical ring}
 \makeatletter
@@
 \begin{abstract}
-The N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency$\dots$) without using expensive end to end connections.
+The N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency$\dots$) without using expensive end-to-end connections.
 We study the compatibility of such a technology with the development of the Cloud RAN, a latency critical application which is a major aspect of 5G deployment.
@@
 The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers.
-The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end to end direct connections (E2DE) between the nodes, which is extremely expensive.
+The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end-to-end direct connections (E2DE) between the nodes, which is extremely expensive.
 The N-GREEN optical ring is designed to ensure good performance for a low cost: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.
@@
 C-RAN is one of the major area of development for 5G; it consists in centralizing or partially centralizing the computation units or {\bf BaseBand Units} (BBU) of the {\bf Remote Radio Heads} (RRH) in one datacenter~\cite{mobile2011c}.
-Periodically, each RRH on the field send some uplink traffic to its associated BBU in the datacenter, then, after a computation, the BBU send the same quantity of downlink traffic back to the RRH.
+Periodically, each RRH on the field sends some uplink traffic to its associated BBU in the datacenter, then, after a computation, the BBU sends the same quantity of downlink traffic back to the RRH.
 The latency of the messages between the BBU and the RRH is critical since some services need end-to-end latency as low as $1$ms~\cite{3gpp5g,boccardi2014five}.
@@
 Here, we propose an SDN approach to {\bf deterministically} manage the periodic C-RAN traffic by choosing emission timing.
-Indeed, Deterministic Networking is one of the strong current aspects considered to reduce the E2E latency~\cite{finn-detnet-architecture-08}.
+Indeed, Deterministic Networking is one of the main method considered to reduce the E2E latency~\cite{finn-detnet-architecture-08}.
 In a previous work~\cite{dominique2018deterministic}, the authors have studied a similar problem for a star shaped network.
@@
 It turns out that the deterministic management of CRAN traffic
-we propose reduce the latency of CRAN traffic to the physical delay of the routes, while reducing the latency of the other traffics by smoothing the load of the ring in the period.
-However, to achieve such a good latency, our solution needs to reserve ressource in advance, which slightly decreases the maximal load the N-GREEN optical ring can manage.
+we propose reduce the latency of CRAN traffic to the physical delay of the routes, while reducing the latency of the other traffics by smoothing the load of the ring over the period.
+To achieve such a good latency, our solution needs to reserve ressources in advance, which slightly decreases the maximal load the N-GREEN optical ring can handle.
 Such an approach of reservation of the network for an application (CRAN in our context) relates to network slicing~\cite{jiang2016network} or virtual-circuit-switched connections in optical networks~\cite{cadere2010virtual,szymanski2016ultra}.
@@
 Hence the RRH emits $ET / F$ packets, i.e.
-a container of size $C$ each $F$ units of time during the emission time, see Fig.~\ref{fig:interface}.
+a container of size $C$ each $F$ units of time during the emission time, as shown in Fig.~\ref{fig:interface}.
    %Each period $P$, an RRH emits $ET / F$ packets, i.e. a packet of size $C$ each $F$ units of time during a time $ET$ (emission time),
 
-   The data of the RRH $i$ arrives at some node $u$ at a time $m_i$ called {\bf offset}. The offsets can be determined 
-   by the designer of the system and can be different for each RRH but must remain the same over all periods.
+   The data of the RRH $i$ arrives at some node $u$ at a time $m_i$ in a period called {\bf offset}.
+The offsets can be determined by the designer of the system and can be different for each RRH but must remain the same over all periods.
 We assume that all BBUs are contained in the same data-center attached to the node $v$.
@@
 At each node of the ring, a {\bf contention buffer} is filled by a batch arrival process of BE data.
-This batch arrival process consist in generating, at each unit of time, a quantity of data drawn from a bimodal distribution to modelize the fact that internet traffic is sometimes bursty.
-Then, according to the fill rate of the contention buffer and the maximum waiting time of the data,
-a packet of size at most $C$ is created by aggregating data in the contention buffer.
+This batch arrival process consists in generating, at each unit of time, a quantity of data drawn from a bimodal distribution to modelize the fact that internet traffic is bursty.
+Then, according to the fill rate of the contention buffer and the maximum waiting time of the data, a packet of size at most $C$ is created by aggregating data in the contention buffer.
 This packet is then put in the insertion buffer of the node.
-Hence, the arrival of BE messages is modeled by a temporal law that gives the distribution of times between two arrivals of a BE packet in the insertion buffer.
+Hence, the arrival of BE messages can be modeled by a temporal law that gives the distribution of times between two arrivals of a BE packet in the insertion buffer.
 The computation of this distribution for the parameters of the contention buffer used in the N-GREEN optical ring is described in~\cite{Cast1810:Performance}.
+We use this distribution in our experiments to modelize BE packet arrival in the insertion buffer.
 
@@
 
-  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a node has a free container available, it fills it with a packet of its insertion buffer, if it exists one.
+  We first study the latency of the C-RAN and BE traffics when the ring follows an opportunistic insertion policy: When a free container goes through a node, it is filled with a packet of its insertion buffer, if there is one.
  Two different methods to manage the insertion buffer are experimentally compared.
@@
 Unsurprisingly, the latency of the C-RAN traffic is better when we prioritize the C-RAN messages, while the BE traffic is heavily penalized.
-Furthermore, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s, a problem we address in the next section.
+Furthermore, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s, a problem we address with the method of the next section.
 Remark that the C-RAN and BE traffic latency distribution is not the same with the FIFO method.
@@
 we allow nodes to \textbf{reserve} a container one round before using it.
-A container which is reserved cannot be filled by any node except the one which has reserved it (but it may contain data when it is reserved).
-Let $u$ be the node to which is attached the RRH $i$, if $u$ reserves the container $u$ at time $m_i - RS$, then it is guaranteed that $u$ can fill a free container at time $m_i$ with the data of the RRH $i$.
+A container which is reserved cannot be filled by any node except the one which has reserved it (but it may not be free when it is reserved).
+If $u$ reserves a container at time $m_i - RS$, then it is guaranteed that $u$ can fill a free container at time $m_i$ with the data of the RRH $i$.
 In the method we now describe, the C-RAN packets never wait in the node: The message sent by the RRH $i$ arrives at its BBU at node $v$ at time $m_i + \omega(u,v)$ and the answer is sent from the BBU at time $m_i + \omega(u,v) +1$.
@@
 If an RRH emits at time $m_i$, then we say it is at \textbf{position} $m_i + \omega(u,v)\pmod F$.
-The position of an RRH corresponds to the position in a slot of the container it has emitted, when it arrives at $u$. 
-If an RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1\pmod F$.
-Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position during all the period.
+By construction, if an RRH is at position $p$, the corresponding $BBU$ is at position $p+1\pmod F$.
+Since we do not allow waiting times in buffer for C-RAN traffic, each RRH uses a container at the same position during all its emission time in a period.
 
-Given a ring, a set of RRH's, a period and an acceleration factor $F$, the problem we solve here is to find an \textbf{assignment} of values of the $m_i$'s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
+Given a ring, a set of RRH's, a period and an acceleration factor $F$, the problem we solve here is to find an \textbf{assignment} of values of the offsets $m_i$'s which is \textbf{valid}: two RRHs never use the same container in a period.
 Moreover we want to preserve the latency of the BE traffic.
-It means that the time a BE packet spent in the insertion buffer must be minimized.
+It means that the time a BE packet waits in the insertion buffer must be minimized.
 To do so, we must minimize the time a node waits for a free container at any point in the period, by spreading the C-RAN traffic as uniformly as possible over the period in order to give the nodes an available container in a minimal average time.
 
-Figure~\ref{fig:assignment} represent an assignment of three couples RRH-BBU.
-each slot has a duration $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in the time, during $ET$ UoT.
-Also, if we take a date $t$ in the period $P$, then $t$ is in the slot $\frac{P}{F}$ and is at position $P \mod F$.
+Figure~\ref{fig:assignment} represents an assignment of three couples of RRH and BBU.
+Each slot has a duration of $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in our representation, during $ET/F$ slots.
+A date $t$ in the period corresponds in Figure~\ref{fig:assignment} to the slot $t/F$ and is at position $t \mod F$.
 
@@
       \includegraphics[scale=0.65]{assignment}
-     \caption{Representation of an assignment with $F = 6$.}\label{fig:assignment}
+     \caption{An assignment with $F = 6$.}\label{fig:assignment}
 
@@
 \begin{proof}
- W.l.o.g we fix $m_1$ so that it is at position $0$ and all the other offsets will then be chosen at position $0$. 
+ W.l.o.g we fix $m_1$ to $0$ and all the other offsets will then be chosen at position $0$.
 Let $u_1,\dots,u_k$ be the nodes attached to the RRHs $1,\dots,k$.
-We assume that $u_1,\dots,u_k$ are in the order of the ring.
+We assume that $u_1,\dots,u_k$ are in the order of the oriented cycle.
 The last message emitted by the RRH $1$ arrives at $u_2$ at time $ET - 1 + \omega(u_1,u_2)$.
@@
 Since $k \times ET + \omega(u_1,u_1) \leq P$ by hypothesis,
- the containers filled by the $k$th RRH are freed before $P$. Hence when the RRH $1$ must emit something in the second period, there is a free container.
+ the containers filled by the $k$th RRH are freed before $P$. Hence when the RRH $1$ must emit something at the first unit of time of the second period, there is a free container.
 \end{proof}
 
-Remark reserving free containers make them unusable for BE traffic which is akin to a loss of bandwidth.
+Remark that reserving free containers make them unusable for BE traffic which is akin to a loss of bandwidth.
 However, with our choice of emission times of the RRHs in the order of the cycle, we reserve $ (k-1)\times RS$ containers used by other RRHs and only $RS$ free containers are wasted.
@@
 The first comes from the reservation and cannot be avoided to guarantee the latency of the C-RAN traffic.
-The second however comes from the fact that an RRH must emit at the same position during all the emission time (to guarantee zero latency).
+The second comes from the fact that an RRH must emit at the same position during all the emission time (to guarantee zero latency).
 If we allow to change the position of data coming from the same RRH during the period,
-we can use \emph{all} containers in a position and hence we could support $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$ antennas.
+we can use \emph{all} containers in a given position and hence we could support $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$ antennas.
 
@@
 has access to a free container, as shown in Fig.~\ref{fig:slotbal}.
-To do so, compute the number of needed frequencies $x = \lceil k\times \frac{ET}{P - RS}\rceil$, with k the number of antennas.
-Then, choose the $x$ positions in the following way: $\frac{F}{x} -1 $ free positions are set between each used positions.
-If $\frac{F}{x}$ has a reminder, then let one more free position between the $F \mod x$ first used position.
-It is a small optimization, since
-it decreases the latency of at most $F/2$.
+To do so, compute the number of needed positions $x = \lceil k\times \frac{ET}{P - RS}\rceil$, with k the number of antennas.
+Then, set the $x$ used positions in the following way: $\lfloor\frac{F}{x}\rfloor -1 $ free positions are set between each used positions.
+If $\frac{F}{x}$ has a reminder $r$, then we set the $r$ free remaining positions uniformly over the interval in the same way and so on until there are no more free position.
+It is a small optimization, since it decreases the latency by at most $F/2$.
 
@@
 
-The performance when we do no compacting positions is really bad, even worst than the methods using an insertion buffer.
+The performance when we do not use the heuristic of compacting positions is really bad, even worst than the methods using an insertion buffer.
 It is explained by the parameters of the N-GREEN ring: all positions are used and thus, there are no free containers available to BE traffic during $ET+RS$ units of time.
@@
 The optimizations of spacing inside the slot brings almost no benefit as expected.
-The spacing over a period improves the latency marginally.
+The spacing over a period improves the latency slightly.
 In settings with an higher load, spacing inside a period would have a much larger effect.
@@
       \includegraphics[scale=0.25]{repart1res}
-     \captionof{figure}{Impact of the repartition on the latency.}   \label{fig:algocmp}
+     \captionof{figure}{Effect of the heuristics on the latency of BE traffic.}   \label{fig:algocmp}
 
@@
       \includegraphics[scale=0.25]{optim.pdf}
-     \captionof{figure}{Impact of the deterministic method on the traffics.}   \label{fig:optimres}
+     \captionof{figure}{Latencies for the deterministic and the stochastic methods.}   \label{fig:optimres}
 

### 2019-01-11 v3/articleV3.tex
avant chgt ordre

--- 2018-12-21 v3/articleV3.tex
@@
 The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers.
-The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end to end direct connections (E2DE) between the nodes, which is extremely expensive.
+The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end to end direct connections between the nodes, which is extremely expensive.
 The N-GREEN optical ring is designed to ensure good performance for a low cost: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.
@@
 In both cases, it makes the latency higher during these times.
-However a C-RAN emission from an RRH takes half the period while a BE arrival corresponds to only a few unit of times, which explains why the C-RAN traffic suffers  more from this phenomena.
+Furthermore, C-RAN taffic both represent an higher load than BE traffic and it is concentrated on half the period, while BE traffic is distributed in all the period.
+% However a C-RAN emission from an RRH takes half the period while a BE arrival corresponds to only a few unit of times,
+It explains why the C-RAN traffic suffers more from this phenomena.
+Also, we observed that the Uplink (from RRH to BBU) and Downlink (BBU to RRH) C-RAN traffics have the same latencies, that is why we chose to represent both indistinctly.
 
@@
 
-Figure~\ref{fig:assignment} represent an assignment of three couples RRH-BBU.
+Fig.~\ref{fig:assignment} represent an assignment of three couples RRH-BBU.
 each slot has a duration $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in the time, during $ET$ UoT.

### 2019-01-11 v3/articleV3.tex
avant chgt ordre

@@
 
+\paragraph{Balancing inside the period}
+
+With the parameters of the N-GREEN ring given in Fig.~\ref{fig:params} ($ET = \frac{P}{2}$, $F = 10$ and $n = 5$), It is possible that there are no unused position.
+Any assignment has exactly one  BBU or RRH at each position.
+If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for the BE traffic.
+To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in Fig.~\ref{fig:periodbal}.
+\begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.55]{repart2}
+     \caption{Balancing inside the period.}\label{fig:periodbal}
+
+\end{center}
+  \end{figure}
+
 \paragraph{Compacting positions}
@@
   \end{figure}
-
+In order to evaluate the impact of 
 \paragraph{Balancing used positions}
@@
   \end{figure}
-\paragraph{Balancing inside the period}
 
-It is possible that there are no unused position as it happens with the parameters of the N-GREEN ring given in Fig.~\ref{fig:params}: $ET = \frac{P}{2}$, $F = 10$ and $n = 5$.
-Any assignment has exactly one  BBU or RRH at each position.
-If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for the BE traffic.
-To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in Fig.~\ref{fig:periodbal}.
-\begin{figure}[h!]
-\begin{center}
-
-      \includegraphics[scale=0.55]{repart2}
-     \caption{Balancing inside the period.}\label{fig:periodbal}
-
-\end{center}
-  \end{figure}  
   \paragraph{Experimental evaluation}

### 2019-01-11 v3/articleV3.tex
modifs vendredi 11

@@
    The RRHs are the source of the {\bf deterministic and periodic} C-RAN traffic.
-   There are $n$ RRHs attached to the ring and several RRHs can be attached to the same vertex. An RRH is linked to a node of the ring through an electronic interface of bit rate $R$ Bps.
+   There are $k$ RRHs attached to the ring and several RRHs can be attached to the same vertex. An RRH is linked to a node of the ring through an electronic interface of bit rate $R$ Bps.
    The ring has a larger bit rate of $F\times R$ Bps.
@@
   \hline
-  Number of nodes $n$ & $5$  \tabularnewline
+  Number of nodes $k$ & $5$  \tabularnewline
   \hline
@@
 If an RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1\pmod F$.
-Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position during all the period.
+Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position during all the emission time.
 
@@
 
-We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets at the same position.
+We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets of several RRH at the same position.
 In the baseline version of the algorithm, we put each RRH in an arbitrary position, for instance one RRH by position.
@@
   \end{figure}
-In order to evaluate the impact of 
+
 \paragraph{Balancing used positions}
@@
   In order to understand the contribution of the three ideas presented in the previous subsection,
-   we present the cumulative distribution of the latency of the BE traffic latency in Fig.~\ref{fig:algocmp}.
-Since the previous N-GREEN parameters were too restrictive to put several RRHs on the same position, the parameter $ET$ has been changed to $400$.
+   we present the cumulative distribution of the latency of the BE traffic latency.
 
-The performance when we do no compacting positions is really bad, even worst than the methods using an insertion buffer.
-It is explained by the parameters of the N-GREEN ring: all positions are used and thus, there are no free containers available to BE traffic during $ET+RS$ units of time.
-When compacting the RRHs on a minimal number of positions, the latency decreases dramatically and becomes much better than in the previous methods.
-The optimizations of spacing inside the slot brings almost no benefit as expected.
-The spacing over a period improves the latency marginally.
-In settings with an higher load, spacing inside a period would have a much larger effect.
+Fig.~\ref{fig:periodonly} shows the performance of balancing the C-RAN traffic inside the period against a baseline version in which all the RRH emits at the same moment of the period.
+We keep the same parameters as in the previous experiment, described in Table~\ref{fig:params}.
+The BE traffic latency is highly decreased when we balance the C-RAN traffic inside the period.
 
-In Fig.~\ref{fig:optimres}, we compare the cumulative distribution of the latency of the BE traffic using the FIFO rule or the reservation algorithm proposed here.
-To keep the load around $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}, we set $ET = 200$ and $n = 12$.
+ Since the N-GREEN parameters does not allow us to put several RRH in the same positions, we changed the emission time to $ET = 200$ To keep the load around $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}, we set $n = 12$.
 This is not out of context since the exact split of the C-RAN (the degree of centralization of the computation units in the cloud) is not fully determined yet~\cite{mobile2011c}.
@@
 
+As show in Fig.\ref{fig:algocmp}, the performance when we do no compacting positions is really bad, even worst than the methods using an insertion buffer.
+It is explained by the parameters of the N-GREEN ring: all positions are used and thus, there are no free containers available to BE traffic during $ET+RS$ units of time.
+When compacting the RRHs on a minimal number of positions, the latency decreases dramatically and becomes much better than in the previous methods.
+The optimizations of balancing inside the slot brings almost no benefit as expected (the maximum latency for BE traffic is $44\mu$s instead of $48\mu$s with compacting position only .
+The balancing over a period improves the latency marginally when compacting positions is possible.
+
+In Fig.~\ref{fig:optimres}, we compare the cumulative distribution of the latency of the BE traffic using the FIFO rule or the reservation algorithm proposed here.
+
+  The performance of the reservation algorithm is excellent, since the C-RAN traffic has {\bf zero latency} and the BE traffic has a \textbf{better latency} with reservation than with the FIFO rule.
+It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth for the BE traffic.
+
+\begin{figure}[h!]
 \begin{center}
-      \includegraphics[scale=0.25]{repart1res}
-     \captionof{figure}{Impact of the repartition on the latency.}   \label{fig:algocmp}
 
-\vspace{0.5cm}
-\todo{packing seul programmé, a voir comment on l'integre dans les resultats}
-      \includegraphics[scale=0.25]{optim.pdf}
-     \captionof{figure}{Impact of the deterministic method on the traffics.}   \label{fig:optimres}
+      \includegraphics[scale=0.25]{periodonly}
+     \caption{Impact of balancing the inside the period on the BE traffic latency.}\label{fig:periodonly}
 
 \end{center}
-  The performance of the reservation algorithm is excellent, since the C-RAN traffic has {\bf zero latency} and the BE traffic has a \textbf{better latency} with reservation than with the FIFO rule.
-It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth for the BE traffic.
+  \end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.25]{repart1res}
+     \caption{Impact of compacting position on the BE traffic latency.}   \label{fig:algocmp}
+
+\end{center}
+  \end{figure}
+
+  \begin{figure}[h!]
+\begin{center}
+
+     \includegraphics[scale=0.25]{optim.pdf}
+     \caption{Impact of the deterministic method on the traffics.}   \label{fig:optimres}
+
+\end{center}
+  \end{figure}
 

### 2019-01-11 v3/articleV3.tex

@@
 
-Given a ring, a set of RRH's, a period and an acceleration factor $F$, the problem we solve here is to find an \textbf{assignment} of values of the $m_i$'s which is \textbf{valid}: two RRHs never reserve or use the same container in a period.
+Given a ring, a set of RRH's, a period and an acceleration factor $F$, the problem we solve here is to find an \textbf{assignment} of values of the offsets $m_i$'s which is \textbf{valid}: two RRHs never use the same container in a period.
 Moreover we want to preserve the latency of the BE traffic.
-It means that the time a BE packet spent in the insertion buffer must be minimized.
+It means that the time a BE packet waits in the insertion buffer must be minimized.
 To do so, we must minimize the time a node waits for a free container at any point in the period, by spreading the C-RAN traffic as uniformly as possible over the period in order to give the nodes an available container in a minimal average time.
 
-Fig.~\ref{fig:assignment} represent an assignment of three couples RRH-BBU.
-each slot has a duration $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in the time, during $ET$ UoT.
-Also, if we take a date $t$ in the period $P$, then $t$ is in the slot $\frac{P}{F}$ and is at position $P \mod F$.
+Figure~\ref{fig:assignment} represents an assignment of three couples of RRH and BBU.
+Each slot has a duration of $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in our representation, during $ET/F$ slots.
+A date $t$ in the period corresponds in Figure~\ref{fig:assignment} to the slot $t/F$ and is at position $t \mod F$.
 
@@
      \caption{Impact of compacting position on the BE traffic latency.}   \label{fig:algocmp}
-
 \end{center}

### 2019-01-16 v3/articleV3.tex
modifs mercredi

@@
 In both cases, it makes the latency higher during these times.
-Furthermore, C-RAN taffic both represent an higher load than BE traffic and it is concentrated on half the period, while BE traffic is distributed in all the period.
+Furthermore, C-RAN traffic is concentrated on half the period, while BE traffic is distributed in all the period.
 % However a C-RAN emission from an RRH takes half the period while a BE arrival corresponds to only a few unit of times,
 It explains why the C-RAN traffic suffers more from this phenomena.
-Also, we observed that the Uplink (from RRH to BBU) and Downlink (BBU to RRH) C-RAN traffics have the same latencies, that is why we chose to represent both indistinctly.
+Also, represent indistinclty the Uplink (from RRH to BBU) and Downlink (BBU to RRH) C-RAN traffics.
+Indeed, due to the broadcast and select mode, a message coming from a BBU or an RRH induces the same load for all the node of the ring, thus, the fact that all the BBU are connected to a same node does not impact the latency of the downlink traffic.
 
@@
 
-Figure~\ref{fig:assignment} represents an assignment of three couples of RRH and BBU.
+Figure~\ref{fig:assignment} represents an assignment of two couples of RRH and BBU.
 Each slot has a duration of $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in our representation, during $ET/F$ slots.
@@
 When compacting the RRHs on a minimal number of positions, the latency decreases dramatically and becomes much better than in the previous methods.
-The optimizations of balancing inside the slot brings almost no benefit as expected (the maximum latency for BE traffic is $44\mu$s instead of $48\mu$s with compacting position only .
-The balancing over a period improves the latency marginally when compacting positions is possible.
+The optimizations of balancing used positions brings almost no benefit as expected: The average (respectively maximum) latency for BE traffic is $4.43\mu$s (resp.
+$44\mu$s) instead of $4.76\mu$s (resp.
+$48\mu$s) with compacting position only.
+Also, the balancing over a period improves the latency marginally when compacting positions is possible.
 

### 2019-01-17 v3/articleV3.tex
debut texte

@@
 The second comes from the fact that an RRH must emit at the same position during all the emission time (to guarantee zero latency).
-If we allow to change the position of data coming from the same RRH during the period,
-we can use \emph{all} containers in a given position and hence we could support $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$ antennas.
+In Sec.~\ref{sec:maxant}, we propose an approach to allow to change the position of data coming from the same RRH during the period, that helps to maximize the number of antennas supported by the ring.
 
@@
 
+\section{A smarter approach for N-GREEN parameters}
+\label{sec:maxant}
+
+The previous approach limits the number of antennas supported by the ring when $ET \geq \frac{P-RS}{2}$ which is the case with N-GREEN parameters.
+In order to maximize the number of antennas, we now want to allow the datas from a same RRH to use different positions in the slot.
+
+In order to allow as much antennas as possible on the ring, the idea is to use \emph{all} containers in a given position.
+To do so we do the compacting positions of previous section and when less than $ET$ free containers remain in a position ( let us call $x$ this number of free containers), then the $x$ first containers of an antenna are assigned to this position, and the $ET - x$ last containers of this antennas are assigned to the next position.
+Fig.~\ref{fig:split} illustrates this manner to find an assignment with a maximal number of antennas.
+The number of antennas supported by the ring is now  $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$.
+
+\begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.8]{split}
+     \caption{Assignment with $9$ antennas with the N-GREEN parameters.}   \label{fig:split}
+\end{center}
+  \end{figure}
+
   \bibliographystyle{ieeetr}

### 2019-01-17 v3/articleV3.tex
modif fulfill pos

@@
 In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantees to have zero latency from buffering.
-We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packets.
+We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packet, or to allow the ring to support a maximal number of antennas, regardless the parameters.
 
@@
 \section{Deterministic approach for zero latency} \label{sec:deterministicalgorithms}
-
+\subsection{Reservation, assignment}
 Finding good offsets for the C-RAN traffic is a hard problem even for simple topologies and without BE traffic, see~\cite{dominique2018deterministic}.
@@
 
-\section{A smarter approach for N-GREEN parameters}
+\subsection{A smarter approach for N-GREEN parameters}
 \label{sec:maxant}
@@
 
+\paragraph{Fulfilling positions}
 In order to allow as much antennas as possible on the ring, the idea is to use \emph{all} containers in a given position.
-To do so we do the compacting positions of previous section and when less than $ET$ free containers remain in a position ( let us call $x$ this number of free containers), then the $x$ first containers of an antenna are assigned to this position, and the $ET - x$ last containers of this antennas are assigned to the next position.
+To do so we assign the antennas to the first position which is not full.
+When less than $ET$ free containers remain in this position ( let us call $x$ this number of free containers), then the $x$ first containers of an antenna are assigned to this position, and the $ET - x$ last containers of this antennas are assigned to the next position.
 Fig.~\ref{fig:split} illustrates this manner to find an assignment with a maximal number of antennas.
-The number of antennas supported by the ring is now  $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$.
+
+Remark that we consider only the even positions, because the BBU are set by definitions on the odd positions.
+This mean that a container reserved to the next position means in reality that this container is reserved $2$ positions after.
+Thus, a message arriving in a node from an RRH at time $m_i$ can see its reserved container at time $m_i +2$ which introduce a bit of additional latency of $2\mu$s for a part of the CRAN traffic.
+However, the number of antennas supported by the ring is now  $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$, which is a considerable gain with our N-GREEN parameters ($9$ antennas instead of $5$).
 
@@
 
+  Since the N-GREEN parameters only allows to do balancing into the period of the previous section, we want to compare the impact on the best effort traffic of fulfilling positions against balancing into the period and FIFO rule.
+Fig.~\ref{fig:splitres} represent the cumulative distribution of the best effort traffic with those three methods, and with the N-GREEN parameters.
+
+\begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.25]{splitres}
+     \caption{Impact of fulfilling positions on BE traffic.}   \label{fig:splitres}
+\end{center}
+  \end{figure}
+
   \bibliographystyle{ieeetr}

### 2019-01-17 v3/articleV3.tex
jeudi soir

@@
 To do so we assign the antennas to the first position which is not full.
-When less than $ET$ free containers remain in this position ( let us call $x$ this number of free containers), then the $x$ first containers of an antenna are assigned to this position, and the $ET - x$ last containers of this antennas are assigned to the next position.
+When less than $ET$ free containers remain in this position ( let us call $x$ this number of free containers), then the $x$ first packets of an antenna are assigned to this position, and the $ET - x$ last packets of this antennas are assigned to the next position.
 Fig.~\ref{fig:split} illustrates this manner to find an assignment with a maximal number of antennas.
 
-Remark that we consider only the even positions, because the BBU are set by definitions on the odd positions.
-This mean that a container reserved to the next position means in reality that this container is reserved $2$ positions after.
-Thus, a message arriving in a node from an RRH at time $m_i$ can see its reserved container at time $m_i +2$ which introduce a bit of additional latency of $2\mu$s for a part of the CRAN traffic.
-However, the number of antennas supported by the ring is now  $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$, which is a considerable gain with our N-GREEN parameters ($9$ antennas instead of $5$).
+Remark that we only consider the even positions, because the BBU are set by definitions on the odd positions.
+This mean that if a container is reserved in the next position, it is, in reality reserved $2$ positions after.
+Thus, a packet arriving in a node from an RRH at time $m_i$ can see its reserved container at time $m_i +2$, which introduce a bit of additional latency of $2$ unit of time for a part of the CRAN traffic.
+However, this cost is worth because the number of antennas supported by the ring is now  $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$, which is a considerable gain with our N-GREEN parameters ($9$ antennas instead of $5$).
 
@@
 
+  This reservation algorithm naturally apply the compacting position of the previous subsection.
+Also, there is no balancing into the period to do because all the used position (except the last) are full.
+The only possible optimisation for the best effort traffic would be to balance the used positions, but, it would add some additional latency on the packet which are already assigned with $2$ unit of time of delay.
   Since the N-GREEN parameters only allows to do balancing into the period of the previous section, we want to compare the impact on the best effort traffic of fulfilling positions against balancing into the period and FIFO rule.

### 2019-01-17 v3/articleV3.tex
corrections en cours, je fini demain

--- 2019-01-17 v3/articleV3.tex
@@
 The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers.
-The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end to end direct connections between the nodes, which is extremely expensive.
+The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end-to-end direct connections (E2DE) between the nodes, which is extremely expensive.
 The N-GREEN optical ring is designed to ensure good performance for a low cost: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.
@@
 In a previous work~\cite{dominique2018deterministic}, the authors have studied a similar problem for a star shaped network.
-In contrast with our previous work, finding emission timings so that different periodic sources do not use the same resource is easy in the context of the N-GREEN optical ring.
-However, we add two new difficulties arising from practice: the messages from RRHs are scattered and there are other traffics whose latency must be preserved.
-It turns out that the deterministic management of CRAN traffic
-we propose reduce the latency of CRAN traffic to the physical delay of the routes, while reducing the latency of the other traffics by smoothing the load of the ring over the period.
+In contrast with our previous work, finding emission timings so that different periodic sources do not use the same resource is easy in the context of the N-GREEN optical ring with a single data-center.
+However, we deal with two additional difficulties arising from practice: the messages from RRHs are scattered (because of the electronic to optic interface) and there are other traffics whose latency must be preserved.
+It turns out that the deterministic management of CRAN traffic we propose reduces the latency of CRAN traffic to the physical delay of the routes, while reducing the latency of the other traffics by smoothing the load of the ring over the period.
 To achieve such a good latency, our solution needs to reserve ressources in advance, which slightly decreases the maximal load the N-GREEN optical ring can handle.
@@
 In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantees to have zero latency from buffering.
-We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packet, or to allow the ring to support a maximal number of antennas, regardless the parameters.
+We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packet, or in Sec.~\ref{sec:maxant} to allow the ring to support a maximal number of antennas at the cost of a very small latency for the C-RAN traffic.
 
@@
 Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO and the C-RAN priority methods.
-The source code in C of the experiments can be found on one of the authors webpage~\cite{webpage}.
+The source code in C of the experiments can be found on one of the authors' webpage~\cite{webpage}.
    \vspace{0.5cm}
@@
 In both cases, it makes the latency higher during these times.
-Furthermore, C-RAN traffic is concentrated on half the period, while BE traffic is distributed in all the period.
+Furthermore, C-RAN traffic is concentrated on half the period, while BE traffic is distributed in all the period.\todo{revoir cette explication}
 % However a C-RAN emission from an RRH takes half the period while a BE arrival corresponds to only a few unit of times,
 It explains why the C-RAN traffic suffers more from this phenomena.
-Also, represent indistinclty the Uplink (from RRH to BBU) and Downlink (BBU to RRH) C-RAN traffics.
-Indeed, due to the broadcast and select mode, a message coming from a BBU or an RRH induces the same load for all the node of the ring, thus, the fact that all the BBU are connected to a same node does not impact the latency of the downlink traffic.
+
+Remark that, due to the broadcast and select mode, a message coming from any node induces the same load for all the nodes of the ring.
+Hence the latency of the traffics coming from any RRHs or from the BBU are the same, which may seem couterintuitive knowing that the BBU generates more traffic.
+This is why in Fig.~\ref{fig:params} we do not ditinguish between uplink C-RAN traffic (RRH to BBU) and downlink  C-RAN traffic (BBU to RRH).
 
 \section{Deterministic approach for zero latency} \label{sec:deterministicalgorithms}
-\subsection{Reservation, assignment}
+\subsection{Reservation}
 Finding good offsets for the C-RAN traffic is a hard problem even for simple topologies and without BE traffic, see~\cite{dominique2018deterministic}.
@@
 Recall that an RRH fills a container every $F$ units of time, during a time $ET$. 
-Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive units of time, an RRH needs to use at most one container by slot.
+Thus if we divide the period $P$ into \textbf{slots} of $F$ consecutive units of time, an RRH needs to fill at most one container each slot.
 If an RRH emits at time $m_i$, then we say it is at \textbf{position} $m_i + \omega(u,v)\pmod F$.
@@
 If an RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1\pmod F$.
-Since we do not allow waiting times for C-RAN traffic, each RRH uses a container at the same position during all the emission time.
+For now, we do not allow waiting times for C-RAN traffic, hence each RRH uses a container at the same position during all the emission time.
 
@@
 It means that the time a BE packet waits in the insertion buffer must be minimized.
-To do so, we must minimize the time a node waits for a free container at any point in the period, by spreading the C-RAN traffic as uniformly as possible over the period in order to give the nodes an available container in a minimal average time.
+To do so, we must minimize the time a node waits for a free container at any point in the period, by spreading the C-RAN traffic as uniformly as possible over the period.
+% in order to give the nodes an available container in a minimal average time.
 
-Figure~\ref{fig:assignment} represents an assignment of two couples of RRH and BBU.
+Figure~\ref{fig:assignment} represents an assignment of two couples of RRH and BBU as the containers going through the node of the BBU during a period.
 Each slot has a duration of $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in our representation, during $ET/F$ slots.
@@
 
+ \subsection{Building valid assignment with zero latency}
 Remark that two RRHs which are not at the same position never use the same containers.
@@
 Hence, we need to deal with the RRHs only.
+The next proposition gives a simple method to find an assignment.
 
@@
 \label{prop:assign}
-There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if  $k\times ET + RS \leq P$.
+There is a valid assignment of the offsets $m_1, \dots, m_k$ on the same position if  $k ET + RS \leq P$.
 \end{prop}
@@
 Remark that reserving free containers make them unusable for BE traffic which is akin to a loss of bandwidth.
-However, with our choice of emission times of the RRHs in the order of the cycle, we reserve $ (k-1)\times RS$ containers used by other RRHs and only $RS$ free containers are wasted.
+However, with our choice of emission times of the RRHs in the order of the cycle, most of the container we reserve are used by the data from some RRH.
+If all containers at some position are used, that is $kET +RS = P$, then there are only $RS$ free containers wasted.
+In the worst case, less than $2RS$ containers are wasted.
 
@@
 \begin{corollary}
-The maximal number of antennas such that there is an assignment is $ \lfloor\frac{P- RS}{ET}\rfloor \times \frac{F}{2}$.
+There is a valid assignment with $ \lfloor\frac{P- RS}{ET}\rfloor \times \frac{F}{2}$ antennas and zero latency.
 \end{corollary}
 \begin{proof}
-Following Prop.~\ref{prop:assign}, the number of antennas for which there is an assignment on the same position is $k = \lfloor\frac{P- RS}{ET}\rfloor $.
+Following Prop.~\ref{prop:assign}, the maximal number of antennas for which there is an assignment on the same position is $k = \lfloor\frac{P- RS}{ET}\rfloor $.
 In such an assignment, we need a second position to deal with the traffic coming from the BBUs coming back to those k antennas.
@@
 The second comes from the fact that an RRH must emit at the same position during all the emission time (to guarantee zero latency).
-In Sec.~\ref{sec:maxant}, we propose an approach to allow to change the position of data coming from the same RRH during the period, that helps to maximize the number of antennas supported by the ring.
+In Sec.~\ref{sec:maxant}, we will relax this constraint to maximize the number of antennas supported by the ring, while minimizing the loss of bandwith due to reservation.
 
@@
 
-With the parameters of the N-GREEN ring given in Fig.~\ref{fig:params} ($ET = \frac{P}{2}$, $F = 10$ and $n = 5$), It is possible that there are no unused position.
+With the parameters of the N-GREEN ring given in Fig.~\ref{fig:params} ($ET = \frac{P}{2}$, $F = 10$ and $n = 5$), there are no unused position.
 Any assignment has exactly one  BBU or RRH at each position.
-If all the RRHs start to emit in the first slot, then during $ET$ there will be no free containers anywhere on the ring, inducing a huge latency for the BE traffic.
+If all the RRHs start to emit at the first slot, then during $ET$ there will be no free container anywhere on the ring, inducing a huge latency for the BE traffic.
 To mitigate this problem, in a period, the time with free containers in each position must be uniformly distributed over the period as shown in Fig.~\ref{fig:periodbal}.
@@
 
-Fig.~\ref{fig:periodonly} shows the performance of balancing the C-RAN traffic inside the period against a baseline version in which all the RRH emits at the same moment of the period.
+Fig.~\ref{fig:periodonly} shows the performance of balancing the C-RAN traffic inside the period against a baseline version in which all the RRH begin to emit at the same slot.
 We keep the same parameters as in the previous experiment, described in Table~\ref{fig:params}.
@@
 
- Since the N-GREEN parameters does not allow us to put several RRH in the same positions, we changed the emission time to $ET = 200$ To keep the load around $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}, we set $n = 12$.
+ Since the N-GREEN parameters does not allow us to put several RRH at the same position, we changed the emission time to $ET = 200$ To keep the load around $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}, we set $n = 12$.
 This is not out of context since the exact split of the C-RAN (the degree of centralization of the computation units in the cloud) is not fully determined yet~\cite{mobile2011c}.
@@
 
-\subsection{A smarter approach for N-GREEN parameters}
+\subsection{Valid assignment with small C-RAN latency}
 \label{sec:maxant}
 
-The previous approach limits the number of antennas supported by the ring when $ET \geq \frac{P-RS}{2}$ which is the case with N-GREEN parameters.
-In order to maximize the number of antennas, we now want to allow the datas from a same RRH to use different positions in the slot.
+The previous approach limits the number of antennas supported by the ring when $P-RS \mod ET \neq 0$, which is the case with N-GREEN parameters.
+In order to maximize the number of supported antennas (and to minimize the reserved containers), we now \emph{allow the data from an RRH to use different positions}.
 
-\paragraph{Fulfilling positions}
-In order to allow as much antennas as possible on the ring, the idea is to use \emph{all} containers in a given position.
+\todo{dire le tradoff -> en échange de plus d'antennes et d'une meilleure latence BE on a une 
+petite perte sur les C-Rans et une augmentation raisonnable de complexité (buffering pour les CRAN).}
+
+\paragraph{Filling positions}
+
+In order to support as much antennas as possible on the ring, we use \emph{all} containers in a given position, improving on the compacting position heuristic.
+
+\begin{prop}
+ There is a valid assignment for $k$ antennas when $k \leq \lfloor \frac{P- RS}{ET} \times \frac{F}{2}\rfloor$.
+\end{prop}
+
 To do so we assign the antennas to the first position which is not full.
-When less than $ET$ free containers remain in this position ( let us call $x$ this number of free containers), then the $x$ first containers of an antenna are assigned to this position, and the $ET - x$ last containers of this antennas are assigned to the next position.
+When less than $ET$ free containers remain in this position (let us call $x$ this number of free containers), then the $x$ first containers of an antenna are assigned to this position, and the $ET - x$ last containers of this antennas are assigned to the next position.
 Fig.~\ref{fig:split} illustrates this manner to find an assignment with a maximal number of antennas.
@@
 
+  \section*{Conclusion}
+
   \bibliographystyle{ieeetr}

### 2019-01-18 v3/articleV3.tex
début derniere section

@@
 
-\subsection{Valid assignment with small C-RAN latency}
+\subsection{Valid assignment with additional C-RAN latency}
 \label{sec:maxant}
@@
 The previous approach limits the number of antennas supported by the ring when $P-RS \mod ET \neq 0$, which is the case with N-GREEN parameters.
-In order to maximize the number of supported antennas (and to minimize the reserved containers), we now \emph{allow the data from an RRH to use different positions}.
-
-\todo{dire le tradoff -> en échange de plus d'antennes et d'une meilleure latence BE on a une 
-petite perte sur les C-Rans et une augmentation raisonnable de complexité (buffering pour les CRAN).}
+In order to maximize the number of supported antennas, we now \emph{allow the data from an RRH to use different positions}.
+The method we present in this section enables us to support more antennas and improves the latency of BE traffic (it reserves less free containers)
+by \emph{allowing the data from an RRH to use different positions}.
+It is a the cost of a slightly worse latency for C-RAN traffic and it requires to implement some buffering for the C-RAN containers.
 

### 2019-01-18 v3/articleV3.tex

--- 2019-01-17 v3/articleV3.tex
@@
 
-Remark that we consider only the even positions, because the BBU are set by definitions on the odd positions.
-This mean that a container reserved to the next position means in reality that this container is reserved $2$ positions after.
-Thus, a message arriving in a node from an RRH at time $m_i$ can see its reserved container at time $m_i +2$ which introduce a bit of additional latency of $2\mu$s for a part of the CRAN traffic.
-However, the number of antennas supported by the ring is now  $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$, which is a considerable gain with our N-GREEN parameters ($9$ antennas instead of $5$).
-
 \begin{figure}[h!]

### 2019-01-18 v3/articleV3.tex
merge

@@
 The N-GREEN project aims to design a high performing optical ring while ensuring a minimal cost for providers.
-The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end-to-end direct connections (E2DE) between the nodes, which is extremely expensive.
-The N-GREEN optical ring is designed to ensure good performance for a low cost: the hardware it requires scales linearly with the number of nodes while E2DE scales quadratically making it impractical for more than a few nodes.
+The current solutions with good QoS~\cite{pizzinat2015things,tayq2017real}, establish end-to-end direct connections between the nodes, which is extremely expensive.
+The N-GREEN optical ring is designed to ensure good performance for a low cost: the hardware it requires scales linearly with the number of nodes while direct connection scales quadratically making it impractical for more than a few nodes.
 
@@
 Here, we propose an SDN approach to {\bf deterministically} manage the periodic C-RAN traffic by choosing emission timing.
-Indeed, Deterministic Networking is one of the main method considered to reduce the E2E latency~\cite{finn-detnet-architecture-08}.
+Indeed, Deterministic Networking is one of the main method considered to reduce the end-to-end latency~\cite{finn-detnet-architecture-08}.
 In a previous work~\cite{dominique2018deterministic}, the authors have studied a similar problem for a star shaped network.
 In contrast with our previous work, finding emission timings so that different periodic sources do not use the same resource is easy in the context of the N-GREEN optical ring with a single data-center.
-However, we deal with two additional difficulties arising from practice: the messages from RRHs are scattered (because of the electronic to optic interface) and there are other traffics whose latency must be preserved.
+However, we deal with two additional difficulties arising from practice: the messages from RRHs are scattered because of the electronic to optic interface and there are other traffics whose latency must be preserved.
 It turns out that the deterministic management of CRAN traffic we propose reduces the latency of CRAN traffic to the physical delay of the routes, while reducing the latency of the other traffics by smoothing the load of the ring over the period.
@@
 
-Figure~\ref{fig:assignment} represents an assignment of two couples of RRH and BBU as the containers going through the node of the BBU during a period.
+Figure~\ref{fig:assignment} represents an assignment of two couples of RRH and BBU by showing the containers going through the node of the BBU during a period.
 Each slot has a duration of $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in our representation, during $ET/F$ slots.
@@
 
- \subsection{Building valid assignment with zero latency}
+ \subsection{Building valid assignment with zero C-RAN latency}
 Remark that two RRHs which are not at the same position never use the same containers.
@@
 
-\subsection{Valid assignment with additional C-RAN latency}
+\subsection{Building valid assignment with some C-RAN latency}
 \label{sec:maxant}

### 2019-01-19 v3/articleV3.tex
corrections de la fin

@@
 
-Figure~\ref{fig:assignment} represents an assignment of two couples of RRH and BBU by showing the containers going through the node of the BBU during a period.
+Fig.~\ref{fig:assignment} represents an assignment of two couples of RRH and BBU by showing the containers going through the node of the BBU during a period.
 Each slot has a duration of $F$ unit of times, and, since an RRH/BBU emits a packet each $F$ UoT during $ET$ UoT, if we take the granularity of a slot to represent the time, the emission of a BBU/RRH is continuous in our representation, during $ET/F$ slots.
-A date $t$ in the period corresponds in Figure~\ref{fig:assignment} to the slot $t/F$ and is at position $t \mod F$.
+A date $t$ in the period corresponds in Fig.~\ref{fig:assignment} to the slot $t/F$ and is at position $t \mod F$.
 
@@
 
- \subsection{Building valid assignment with zero C-RAN latency}
+ \subsection{Building valid assignment with zero C-RAN latency}\ref{sec:zerolatency}
 Remark that two RRHs which are not at the same position never use the same containers.
@@
 If all containers at some position are used, that is $kET +RS = P$, then there are only $RS$ free containers wasted.
-In the worst case, less than $2RS$ containers are wasted.
+In the worst case, less than $2RS$ containers are wasted by the assignment of Prop.~\ref{prop:assign}.
 
-From Proposition~\ref{prop:assign}, it is easy to derive the maximal number of antennas which can be supported by an optical ring, when using reservation and the same position for an RRH for the whole period.
+It is now easy to derive the maximal number of antennas which can be supported by an optical ring, when using reservation and the same position for an RRH for the whole period.
 
@@
 
-There are two sources of inefficiency in this method.
+With the parameters of the N-GREEN ring given in Fig.~\ref{fig:params}, we can support $5$ antennas, while stochastic 
+multiplexing can support $10$ antennas albeit extremely inefficiently.
+There are two sources of inefficiency in our method.
 The first comes from the reservation and cannot be avoided to guarantee the latency of the C-RAN traffic.
 The second comes from the fact that an RRH must emit at the same position during all the emission time (to guarantee zero latency).
-In Sec.~\ref{sec:maxant}, we will relax this constraint to maximize the number of antennas supported by the ring, while minimizing the loss of bandwith due to reservation.
+We relax this constraint in Sec.~\ref{sec:maxant} to maximize the number of antennas supported by the ring, while minimizing the loss of bandwith due to reservation.
 
@@
 
-For each position which is used by some RRH, and during each period, $RS$ containers are reserved before starting to emit some C-RAN traffic, while they can be free.
-Hence, it decreases the maximal load the system can handle.
-Therefore to not waste bandwidth, it is relevant to put as many RRHs as possible on the same position as in Fig.~\ref{fig:packing}.
+For each position which is used by some RRH, and for each period, $RS$ free containers are reserved before starting to emit some C-RAN traffic which decreases the maximal load the system can handle.
+Therefore to not waste bandwidth, it is important to put as many RRHs as possible on the same position as shown in Fig.~\ref{fig:packing}.
 Indeed, for any position which is not used at all, $RS$ containers need not to be reserved.
-This strategy is also good for the latency of the BE traffic.
-If a position is unused, then there is always a container free of C-RAN traffic each $F$ unit of times.
+This strategy is also good to spread the load during the period since it maximizes the number of unused positions.
+It helps the latency of the BE traffic, since for each unused position, there is always a container free of C-RAN traffic each $F$ unit of times. 
 \begin{figure}[h!]
@@
 
-  In order to understand the contribution of the three ideas presented in the previous subsection,
-   we present the cumulative distribution of the latency of the BE traffic latency.
+  In order to understand the interest of the three improvements presented in the previous subsection,
+   we present the cumulative distribution of the latency of the BE traffic using them either alone or in conjunction.
 
 Fig.~\ref{fig:periodonly} shows the performance of balancing the C-RAN traffic inside the period against a baseline version in which all the RRH begin to emit at the same slot.
-We keep the same parameters as in the previous experiment, described in Table~\ref{fig:params}.
-The BE traffic latency is highly decreased when we balance the C-RAN traffic inside the period.
+We keep the same parameters of Sec.~\ref{sec:oportmethods} described in Table~\ref{fig:params}.
+As expected, the BE traffic latency much better when we balance the C-RAN traffic inside the period.
 
- Since the N-GREEN parameters does not allow us to put several RRH at the same position, we changed the emission time to $ET = 200$ To keep the load around $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}, we set $n = 12$.
+ Since the N-GREEN parameters does not allow us to put several RRH at the same position, we change the emission time to $ET = 200$ and we set the number of antennas to $k = 12$ to keep the load around $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}.
 This is not out of context since the exact split of the C-RAN (the degree of centralization of the computation units in the cloud) is not fully determined yet~\cite{mobile2011c}.
-With these parameters, the loss of bandwidth due to reservation is at most $6\%$
+%With these parameters, the loss of bandwidth due to reservation is at most $6\%$.
 
-As show in Fig.\ref{fig:algocmp}, the performance when we do no compacting positions is really bad, even worst than the methods using an insertion buffer.
+As shown in Fig.\ref{fig:algocmp}, the performance when we do not compact positions is really bad, even worst than the methods using an insertion buffer.
 It is explained by the parameters of the N-GREEN ring: all positions are used and thus, there are no free containers available to BE traffic during $ET+RS$ units of time.
@@
 In order to maximize the number of supported antennas, we now \emph{allow the data from an RRH to use different positions}.
-The method we present in this section enables us to support more antennas and improves the latency of BE traffic (it reserves less free containers)
-by \emph{allowing the data from an RRH to use different positions}.
-It is a the cost of a slightly worse latency for C-RAN traffic and it requires to implement some buffering for the C-RAN containers.
+The method we present in this section enables us to support more antennas and improves the latency of BE traffic (it reserves less free containers) by \emph{allowing the data from an RRH to use different positions}.
+It is a the cost of a slightly worse latency for C-RAN traffic and it also requires to implement some buffering for the C-RAN containers.
 
@@
 \end{prop}
+\begin{proof}
+ We consider the RRHs in the order of the ring and set their offsets as in Prop.\ref{prop:assign}.
+ If $l = \lfloor \frac{P- RS}{ET}\rfloor$, $l$ RRHs can be at position zero, and the $l+1$th
+ RRH will also emit at position zero, with offset $m_{l+1} = l*ET + \omega(u_0,u_{l+1})$. 
+ After emitting up to time $x = P - \omega(u_{l+1},u_{0})$ at position zero, it emits during a time $ET -x $  at position $2$.
+Then the next RRHs are assigned to position two, and begin to emit at time $x$ instead of zero.
+This assignment is build in this way filling completely all first positions, until there are no more RRH.
+\end{proof}
 
-To do so we assign the antennas to the first position which is not full.
-When less than $ET$ free containers remain in this position (let us call $x$ this number of free containers), then the $x$ first containers of an antenna are assigned to this position, and the $ET - x$ last containers of this antennas are assigned to the next position.
-Fig.~\ref{fig:split} illustrates this manner to find an assignment with a maximal number of antennas.
+Fig.~\ref{fig:split} illustrates this construction for the N-GREEN parameters. 
+It is possible to support $9$ antennas (but no BE traffic in this extreme case),
+rather than $5$ with the method of Sec.~\ref{sec:zerolatency}.
 
@@
       \includegraphics[scale=0.8]{split}
-     \caption{Assignment with $9$ antennas with the N-GREEN parameters.}   \label{fig:split}
+     \caption{Valid assignment for $9$ antennas and the N-GREEN parameters.}   \label{fig:split}
 \end{center}
@@
 
+  Dire que c'est trop bien parce qu'on gagne sur tous les fronts par rapport à des classiques
+  buffer FIFO, même avec de la priorité:
+  pas besoin ou presque de buffer-> simplicité, pas de latence pour C RAN et meilleur latence
+  pour BE. 
+    Même utilisable en pratique, d'ailleurs on va faire un prototype..
+  Ouverture sur le cas avec plusieurs data centers (plus compliqué, car on doit réutiliser les méthodes de l'autre article mais tant que la charge de CRAN n'est pas trop importante, ça devrait aller).
   \bibliographystyle{ieeetr}

### 2019-01-20 v3/articleV3.tex
suite de la relecture partie 5

@@
 
- \subsection{Building valid assignment with zero C-RAN latency}\ref{sec:zerolatency}
+ \subsection{Building valid assignment with zero C-RAN latency}\label{sec:zerolatency}
 Remark that two RRHs which are not at the same position never use the same containers.
@@
 
- Since the N-GREEN parameters does not allow us to put several RRH at the same position, we change the emission time to $ET = 200$ and we set the number of antennas to $k = 12$ to keep the load around $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}.
+To show the interest of compacting the positions, we must be able to put several RRH at the same position.
+Hence, we change the emission time to $ET = 200$ and the number of antennas to $k = 12$ to keep the load around $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}.
 This is not out of context since the exact split of the C-RAN (the degree of centralization of the computation units in the cloud) is not fully determined yet~\cite{mobile2011c}.
+
 %With these parameters, the loss of bandwidth due to reservation is at most $6\%$.
 
-As shown in Fig.\ref{fig:algocmp}, the performance when we do not compact positions is really bad, even worst than the methods using an insertion buffer.
-It is explained by the parameters of the N-GREEN ring: all positions are used and thus, there are no free containers available to BE traffic during $ET+RS$ units of time.
-When compacting the RRHs on a minimal number of positions, the latency decreases dramatically and becomes much better than in the previous methods.
-The optimizations of balancing used positions brings almost no benefit as expected: The average (respectively maximum) latency for BE traffic is $4.43\mu$s (resp.
-$44\mu$s) instead of $4.76\mu$s (resp.
-$48\mu$s) with compacting position only.
-Also, the balancing over a period improves the latency marginally when compacting positions is possible.
+As shown in Fig.\ref{fig:algocmp}, the performance of the baseline algorithm is really bad, even worst than the methods using an insertion buffer.
+Compacting the RRHs on a minimal number of positions decreases dramatically the latency.
+If in addition, we balance over a period, we get yet another gain of latency of smaller magnitude.
+We did not represent the benefit of balancing used positions because the reduction in latency it 
+yields is small as expected: The average (respectively maximum) latency for BE traffic goes from $4.76$ UoT (resp. $48$ UoT) to $4.43\mu$s (resp. $44\mu$s).
 
-In Fig.~\ref{fig:optimres}, we compare the cumulative distribution of the latency of the BE traffic using the FIFO rule or the reservation algorithm proposed here.
-
-  The performance of the reservation algorithm is excellent, since the C-RAN traffic has {\bf zero latency} and the BE traffic has a \textbf{better latency} with reservation than with the FIFO rule.
+In Fig.~\ref{fig:optimres}, we compare the cumulative distribution of the latency of the BE traffic using the FIFO rule to our reservation algorithm with the three proposed improvements.
+The parameter are the same as in the previous experiment.
+The performance of the reservation algorithm is \emph{excellent}, since the C-RAN traffic has {\bf zero latency} and the BE traffic has a \textbf{better latency} with reservation than with the FIFO rule.
 It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth for the BE traffic.
@@
       \includegraphics[scale=0.25]{periodonly}
-     \caption{Impact of balancing the inside the period on the BE traffic latency.}\label{fig:periodonly}
-
+     \caption{Latencies of a baseline assignment and of balancing inside the period for $5$ antennas.}  
+     \label{fig:periodonly}
   \end{center}
@@
       \includegraphics[scale=0.25]{repart1res}
-     \caption{Impact of compacting position on the BE traffic latency.}   \label{fig:algocmp}
+     \caption{Compacting and balancing inside the period for $12$ antennas.}   \label{fig:algocmp}
 \end{center}
@@
      \includegraphics[scale=0.25]{optim.pdf}
-     \caption{Impact of the deterministic method on the traffics.}   \label{fig:optimres}
-
+     \caption{FIFO buffer compared to the best method with reservation for $12$ antennas.} \label{fig:optimres}
 \end{center}
@@
 
-  This reservation algorithm naturally apply the compacting position of the previous subsection.
+  This reservation algorithm naturally applies the compacting position of the previous subsection.
 Also, there is no balancing into the period to do because all the used position (except the last) are full.
@@
 
-  Dire que c'est trop bien parce qu'on gagne sur tous les fronts par rapport à des classiques
-  buffer FIFO, même avec de la priorité:
-  pas besoin ou presque de buffer-> simplicité, pas de latence pour C RAN et meilleur latence
-  pour BE. 
-    Même utilisable en pratique, d'ailleurs on va faire un prototype..
-  Ouverture sur le cas avec plusieurs data centers (plus compliqué, car on doit réutiliser les méthodes de l'autre article mais tant que la charge de CRAN n'est pas trop importante, ça devrait aller).
+  As a conclusion, we want to stress the fact that to deal with a deterministic 
+  dataflow as C-RAN, we must use a deterministic managment rather than a classical.
+  Using a simple scheme which requires only to set the emission timing of the RRHs and to allow reservation 
+  on the optic ring, which is easy to do in practice, we remove all logical latencies. It also improves 
+  significantly the latencies of the BE traffic by spreading the load of the C-RAN traffic in a very uniform manner.
+We are currently working on a prototype implementing this method on the NGREEN ring.
+  We plan to deal with the case of several different data-centers. The algorithmic methods to find 
+  good emission timings in this case are more complicated similar to what is developped in~\cite{dominique2018deterministic}, but while the load due to the C-RAN traffic is not too high it should work very well.
 \bibliographystyle{ieeetr}

### 2019-01-21 v3/articleV3.tex
corrections du lundi

@@
 
-   The data of the RRH $i$ arrives at some node $u$ at a time $m_i$ in a period called {\bf offset}.
+   At each period, the data of the RRH $i$ begins to arrive in the insertion buffer at a time $m_i$  called {\bf offset}.
 The offsets can be determined by the designer of the system and can be different for each RRH but must remain the same over all periods.
@@
 In this experiment, the offsets of the RRH have been randomly distributed in the period.
-The results are computed over $1,000$ experiments (with different random offsets) where the optical ring is simulated during $1,000,000$ units of time.
+The results are computed over $1,000$ experiments (with different random offsets) in which the optical ring is simulated during $1,000,000$ units of time.
 Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO and the C-RAN priority methods.
 The source code in C of the experiments can be found on one of the authors' webpage~\cite{webpage}.
-   \vspace{0.5cm}
-  \hspace{-0.75cm}
+%    \vspace{0.5cm}
+%   \hspace{-0.75cm}
 
@@
       \includegraphics[scale=0.3]{opport.pdf}
-
      \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}
 \end{center} 
-
 \begin{figure}[h]
@@
 Remark that, due to the broadcast and select mode, a message coming from any node induces the same load for all the nodes of the ring.
-Hence the latency of the traffics coming from any RRHs or from the BBU are the same, which may seem couterintuitive knowing that the BBU generates more traffic.
+Hence the latency of the traffics coming from any RRHs or from the BBUs are the same, which may seem couterintuitive knowing that all BBUs share the same node on the ring.
 This is why in Fig.~\ref{fig:params} we do not ditinguish between uplink C-RAN traffic (RRH to BBU) and downlink  C-RAN traffic (BBU to RRH).
@@
 
-Given a ring, a set of RRH's, a period and an acceleration factor $F$, the problem we solve here is to find an \textbf{assignment} of values of the offsets $m_i$'s which is \textbf{valid}: two RRHs never use the same container in a period.
+Given a ring, a set of RRH's, a period and an acceleration factor $F$, the problem we solve here is to find an \textbf{assignment} of values of the offsets $m_i$'s which is \textbf{valid}: two RRHs must never use the same container in a period.
 Moreover we want to preserve the latency of the BE traffic.
@@
 
-With the parameters of the N-GREEN ring given in Fig.~\ref{fig:params}, we can support $5$ antennas, while stochastic 
-multiplexing can support $10$ antennas albeit extremely inefficiently.
+With the parameters of the N-GREEN ring given in Fig.~\ref{fig:params}, we can support $5$ antennas, while stochastic multiplexing can support $10$ antennas albeit with extreme latency.
 There are two sources of inefficiency in our method.
@@
 
-We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets of several RRH at the same position.
+We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets of several RRHs at the same position.
 In the baseline version of the algorithm, we put each RRH in an arbitrary position, for instance one RRH by position.
@@
 
-For each position which is used by some RRH, and for each period, $RS$ free containers are reserved before starting to emit some C-RAN traffic which decreases the maximal load the system can handle.
+For each position which is used by some RRH, and for each period, at least $RS$ free containers are reserved which decreases the maximal load the system can handle.
 Therefore to not waste bandwidth, it is important to put as many RRHs as possible on the same position as shown in Fig.~\ref{fig:packing}.
-Indeed, for any position which is not used at all, $RS$ containers need not to be reserved.
-This strategy is also good to spread the load during the period since it maximizes the number of unused positions.
-It helps the latency of the BE traffic, since for each unused position, there is always a container free of C-RAN traffic each $F$ unit of times. 
+Indeed, for any position which is not used at all, no container needs to be reserved.
+This strategy is also good to spread the load during the period since it maximizes the number of unused positions and for each unused position there is a container free of C-RAN traffic each $F$ unit of times.
 \begin{figure}[h!]
@@
 
-The free positions can be distributed uniformly over a slot, to minimize the time to wait before a node 
-has access to a free container, as shown in Fig.~\ref{fig:slotbal}.
-To do so, compute the number of needed positions $x = \lceil k\times \frac{ET}{P - RS}\rceil$, with k the number of antennas.
+The free positions can be distributed uniformly over a slot, to minimize the time to wait before a node has access to a free container from a free free position, as shown in Fig.~\ref{fig:slotbal}.
+To do so, compute the number of needed positions $x = \lceil k\times \frac{ET}{P - RS}\rceil$, with k the number of antennas using the previous strategy.
 Then, set the $x$ used positions in the following way: $\lfloor\frac{F}{x}\rfloor -1 $ free positions are set between each used positions.
@@
 
-  In order to understand the interest of the three improvements presented in the previous subsection,
-   we present the cumulative distribution of the latency of the BE traffic using them either alone or in conjunction.
+  Our method combine the three ways we have described to spread the load over the period.
+  In order to understand the interest of these three improvements, we present the cumulative distribution of the latency of the BE traffic using them either alone or in conjunction and 
+  we compare our method to stochastic multiplexing.
 
-Fig.~\ref{fig:periodonly} shows the performance of balancing the C-RAN traffic inside the period against a baseline version in which all the RRH begin to emit at the same slot.
-We keep the same parameters of Sec.~\ref{sec:oportmethods} described in Table~\ref{fig:params}.
-As expected, the BE traffic latency much better when we balance the C-RAN traffic inside the period.
+Fig.~\ref{fig:periodonly} shows the performance of balancing the C-RAN traffic inside the period against a naive assignment in which all the RRH begin to emit at the same slot.
+We keep the same parameters as in Sec.~\ref{sec:oportmethods} (see Table~\ref{fig:params}).
+As expected, the BE traffic latency is much better when we balance the C-RAN traffic inside the period and already better than stochastic multiplexing.
 
-To show the interest of compacting the positions, we must be able to put several RRH at the same position.
+To show the interest of compacting the positions, we must be able to put several RRHs at the same position.
 Hence, we change the emission time to $ET = 200$ and the number of antennas to $k = 12$ to keep the load around $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}.
@@
 
-As shown in Fig.\ref{fig:algocmp}, the performance of the baseline algorithm is really bad, even worst than the methods using an insertion buffer.
+As shown in Fig.\ref{fig:algocmp}, the performance of the naive assignment is really bad, even worst than the methods using an insertion buffer.
 Compacting the RRHs on a minimal number of positions decreases dramatically the latency.
-If in addition, we balance over a period, we get yet another gain of latency of smaller magnitude.
+If in addition, we balance over a period, we get another gain of latency of smaller magnitude.
 We did not represent the benefit of balancing used positions because the reduction in latency it 
-yields is small as expected: The average (respectively maximum) latency for BE traffic goes from $4.76$ UoT (resp. $48$ UoT) to $4.43\mu$s (resp. $44\mu$s).
+yields is small as expected: The average (respectively maximum) latency for BE traffic goes from $4.76 \mu$s (resp. $48 \mu$s) to $4.43 \mu$s (resp. $44 \mu$s).
 
@@
 The parameter are the same as in the previous experiment.
-The performance of the reservation algorithm is \emph{excellent}, since the C-RAN traffic has {\bf zero latency} and the BE traffic has a \textbf{better latency} with reservation than with the FIFO rule.
+The performance of the reservation algorithm is excellent, since the C-RAN traffic has \emph{zero latency} and the BE traffic has a \emph{better latency} with reservation than with the FIFO rule.
 It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth for the BE traffic.
@@
       \includegraphics[scale=0.25]{periodonly}
-     \caption{Latencies of a baseline assignment and of balancing inside the period for $5$ antennas.}  
+     \caption{Latencies of a naive assignment and of balancing inside the period for $5$ antennas.}  
      \label{fig:periodonly}
@@
 The previous approach limits the number of antennas supported by the ring when $P-RS \mod ET \neq 0$, which is the case with N-GREEN parameters.
-In order to maximize the number of supported antennas, we now \emph{allow the data from an RRH to use different positions}.
-The method we present in this section enables us to support more antennas and improves the latency of BE traffic (it reserves less free containers) by \emph{allowing the data from an RRH to use different positions}.
-It is a the cost of a slightly worse latency for C-RAN traffic and it also requires to implement some buffering for the C-RAN containers.
+The method we present in this section enables us to support more antennas and improves the latency of BE traffic (it reserves less free containers) by \emph{allowing the data from an RRH to use two positions}.
+It is a the cost of a slightly worse latency for C-RAN traffic and it also requires in practice to implement some buffering for the C-RAN containers.
 
@@
 
-\begin{prop}
+\begin{prop}\label{prop:filling}
  There is a valid assignment for $k$ antennas when $k \leq \lfloor \frac{P- RS}{ET} \times \frac{F}{2}\rfloor$.
@@
 \begin{proof}
- We consider the RRHs in the order of the ring and set their offsets as in Prop.\ref{prop:assign}.
- If $l = \lfloor \frac{P- RS}{ET}\rfloor$, $l$ RRHs can be at position zero, and the $l+1$th
- RRH will also emit at position zero, with offset $m_{l+1} = l*ET + \omega(u_0,u_{l+1})$. 
+ We consider the RRHs in the order of the ring and set their offsets as in Prop.~\ref{prop:assign}.
+ If $l = \lfloor \frac{P- RS}{ET}\rfloor$, $l$ RRHs can be at position zero. The $(l+1)$th
+ RRH also emit first at position zero, with offset $m_{l+1} = l*ET + \omega(u_0,u_{l+1})$. 
  After emitting up to time $x = P - \omega(u_{l+1},u_{0})$ at position zero, it emits during a time $ET -x $  at position $2$.
-Then the next RRHs are assigned to position two, and begin to emit at time $x$ instead of zero.
-This assignment is build in this way filling completely all first positions, until there are no more RRH.
+Then the next RRH is assigned to position two, and begin to emit at time $x$ instead of zero.
+The rest of the assignment is built in the same way filling completely all first positions, until there are no more RRH.
 \end{proof}
 
-Fig.~\ref{fig:split} illustrates this construction for the N-GREEN parameters. 
-It is possible to support $9$ antennas (but no BE traffic in this extreme case),
+Fig.~\ref{fig:split} illustrates the construction of Prop.~\ref{prop:filling} for the N-GREEN parameters. It is possible to support $9$ antennas (but no BE traffic in this extreme case),
 rather than $5$ with the method of Sec.~\ref{sec:zerolatency}.
@@
   As a conclusion, we want to stress the fact that to deal with a deterministic 
-  dataflow as C-RAN, we must use a deterministic managment rather than a classical.
-  Using a simple scheme which requires only to set the emission timing of the RRHs and to allow reservation 
-  on the optic ring, which is easy to do in practice, we remove all logical latencies. It also improves 
-  significantly the latencies of the BE traffic by spreading the load of the C-RAN traffic in a very uniform manner.
+  dataflow as C-RAN, we must use a deterministic policy rather than a classical stochastic one.
+  Using a simple scheme which requires only to set the emission timing of the RRHs and to allow reservation on the optical ring, which is easy to do in practice, we remove all logical latencies.
+It also improves significantly the latencies of the BE traffic by spreading the load of the C-RAN traffic uniformly over the period.
 We are currently working on a prototype implementing this method on the NGREEN ring.
-  We plan to deal with the case of several different data-centers. The algorithmic methods to find 
-  good emission timings in this case are more complicated similar to what is developped in~\cite{dominique2018deterministic}, but while the load due to the C-RAN traffic is not too high it should work very well.
+  We also plan to deal with the case of several data-centers containing the BBUs instead of one.
+The algorithmic methods to find good emission timings in this generalization are more complicated and similar to what was proposed in~\cite{dominique2018deterministic}, but while the load due to the C-RAN traffic is not too high it should work very well.
 \bibliographystyle{ieeetr}

### 2019-01-21 v3/articleV3.tex
merge

@@
 Furthermore, there is still $10\%$ of the C-RAN traffic with a latency higher than $50 \mu$s, a problem we address in the next section.
-Remark that the C-RAN and BE traffic latency distribution is not the same with the FIFO method.
+
+% Remark that the C-RAN and BE traffic latency distribution is not the same with the FIFO method.
 This comes from the fact that these two sources of traffic are of different nature.
 With high probability, there are some part of the period which have more
-BE data arrivals (or C-RAN traffic) than average.
+% BE data arrivals (or C-RAN traffic) than average.
 In both cases, it makes the latency higher during these times.
 Furthermore, C-RAN traffic is concentrated on half the period, while BE traffic is distributed in all the period.\todo{revoir cette explication}
-% However a C-RAN emission from an RRH takes half the period while a BE arrival corresponds to only a few unit of times,
-It explains why the C-RAN traffic suffers more from this phenomena.
+% % However a C-RAN emission from an RRH takes half the period while a BE arrival corresponds to only a few unit of times,
+% It explains why the C-RAN traffic suffers more from this phenomena.
 

### 2019-01-22 v3/articleV3.tex
modifs

--- 2019-01-21 v3/articleV3.tex
@@
 Fig.~\ref{fig:splitres} represent the cumulative distribution of the best effort traffic with those three methods, and with the N-GREEN parameters.
+Filling positions reduces the BE traffic latency more than balancing into the period.
+Indeed, with filling positions, the loss of bandwidth due to reservation is minimized.
 
@@
       \includegraphics[scale=0.25]{splitres}
-     \caption{Impact of fulfilling positions on BE traffic.}   \label{fig:splitres}
+     \caption{Latencies of filling positions compared to FIFO buffer and balancing into the period for 5 antennas.}   \label{fig:splitres}
 \end{center}

### 2019-01-24 v3/articleV3.tex
merge
last modifs

@@
 \usepackage{amsmath,amsthm}
+\usepackage{url}
 
@@
 Hence the RRH emits $ET / F$ packets, i.e.
-a container of size $C$ each $F$ units of time during the emission time, as shown in Fig.~\ref{fig:interface}.
+requires a container of size $C$ each $F$ units of time during the emission time, as shown in Fig.~\ref{fig:interface}.
    %Each period $P$, an RRH emits $ET / F$ packets, i.e. a packet of size $C$ each $F$ units of time during a time $ET$ (emission time),
@@
 In Sec.~\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency for C-RAN which also improves the latency of other data going through the optical ring.
-We shortly describe the nature of this additional traffic in the next subsection.
+We shortly describe the nature of this additional traffic in the next paragraph.
 
@@
 The source code in C of the experiments can be found on one of the authors' webpage~\cite{webpage}.
-%    \vspace{0.5cm}
-%   \hspace{-0.75cm}
-
+   \vspace{-1cm}
         \begin{center}
       \includegraphics[scale=0.3]{opport.pdf}
+         \vspace{-1cm}
      \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}
+
 \end{center} 
@@
 \begin{minipage}[t]{.46\linewidth}
-
   \scalebox{.55}
@@
 
-Let $u$ be the node to which is attached the RRH $i$, to ensure zero latency for the C-RAN traffic, then the container which arrives at $u$ at time $m_i$ must be free so that the data from the RRH can be sent immediately on the optical ring.
+Let $u$ be the node to which is attached the RRH $i$.
+To ensure zero latency for the C-RAN traffic, then the container which arrives at $u$ at time $m_i$ must be free so that the data from the RRH can be sent immediately on the optical ring.
 
@@
 If an RRH emits at time $m_i$, then we say it is at \textbf{position} $m_i + \omega(u,v)\pmod F$.
-The position of an RRH corresponds to the position in a slot of the container it has emitted, when it arrives at $u$. 
+The position of an RRH corresponds to the position in a slot of the container it has emitted, when it arrives at $u$, the node of the BBU. 
 If an RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1\pmod F$.
@@
 
+   \vspace{-0,5cm}
 \begin{figure}[h!]
@@
   \end{figure}
+     \vspace{-0.75cm}
 
@@
 We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets of several RRHs at the same position.
-In the baseline version of the algorithm, we put each RRH in an arbitrary position, for instance one RRH by position.
+In a naive assignment, we put each RRH in an arbitrary position, for instance one RRH by position.
 We then propose three ideas to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.
@@
 
-The free positions can be distributed uniformly over a slot, to minimize the time to wait before a node has access to a free container from a free free position, as shown in Fig.~\ref{fig:slotbal}.
+The free positions can be distributed uniformly over a slot, to minimize the time to wait before a node has access to a container from a free position, as shown in Fig.~\ref{fig:slotbal}.
 To do so, compute the number of needed positions $x = \lceil k\times \frac{ET}{P - RS}\rceil$, with k the number of antennas using the previous strategy.
@@
   In order to understand the interest of these three improvements, we present the cumulative distribution of the latency of the BE traffic using them either alone or in conjunction and 
-  we compare our method to stochastic multiplexing.
+  we compare our method to stochastic multiplexing with C-RAN priority.
 
@@
 
-\begin{figure}[h!]
+\begin{figure}[h]
 \begin{center}
@@
   \end{figure}
-
-  \begin{figure}[h!]
+  \begin{figure}[h]
 \begin{center}   
-
      \includegraphics[scale=0.25]{optim.pdf}
@@
 The method we present in this section enables us to support more antennas and improves the latency of BE traffic (it reserves less free containers) by \emph{allowing the data from an RRH to use two positions}.
-It is a the cost of a slightly worse latency for C-RAN traffic and it also requires in practice to implement some buffering for the C-RAN containers.
+It is a the cost of a slightly worse latency for C-RAN traffic and it also requires in practice to implement some buffering for the C-RAN packets.
 
@@
 Also, there is no balancing into the period to do because all the used position (except the last) are full.
-The only possible optimisation for the best effort traffic would be to balance the used positions, but, it would add some additional latency on the packet which are already assigned with $2$ unit of time of delay.
+The only possible optimisation for the best effort traffic would be to balance the used positions, but, it would add some additional latency on the packet which are already assigned with $2$ unit of time of latency.
   Since the N-GREEN parameters only allows to do balancing into the period of the previous section, we want to compare the impact on the best effort traffic of fulfilling positions against balancing into the period and FIFO rule.
@@
   dataflow as C-RAN, we must use a deterministic policy rather than a classical stochastic one.
-  Using a simple scheme which requires only to set the emission timing of the RRHs and to allow reservation on the optical ring, which is easy to do in practice, we remove all logical latencies.
+  By using a simple scheme which requires only to set the emission timing of the RRHs and to allow reservation on the optical ring, which is easy to do in practice, we remove all logical latencies.
 It also improves significantly the latencies of the BE traffic by spreading the load of the C-RAN traffic uniformly over the period.
@@
 The algorithmic methods to find good emission timings in this generalization are more complicated and similar to what was proposed in~\cite{dominique2018deterministic}, but while the load due to the C-RAN traffic is not too high it should work very well.
+
       \bibliographystyle{ieeetr}

### 2019-01-28 v3/articleV3.tex
derniers changement, je n'y touche plus

@@
 It turns out that the deterministic management of CRAN traffic we propose reduces the latency of CRAN traffic to the physical delay of the routes, while reducing the latency of the other traffics by smoothing the load of the ring over the period.
-To achieve such a good latency, our solution needs to reserve ressources in advance, which slightly decreases the maximal load the N-GREEN optical ring can handle.
+To achieve such a good latency, our solution needs to reserve resources in advance, which slightly decreases the maximal load the N-GREEN optical ring can handle.
 Such an approach of reservation of the network for an application (CRAN in our context) relates to network slicing~\cite{jiang2016network} or virtual-circuit-switched connections in optical networks~\cite{cadere2010virtual,szymanski2016ultra}.
@@
 In Sec.~\ref{sec:model}, we model the optical ring and the traffic flow.
-In Sec.~\ref{sec:oportmethods}, we experimentally evaluate the latency when using stochastic multiplexing to manage packet insertions on the ring, with or without priority for C-RAN packets.
+In Sec.~\ref{sec:oportmethods}, we experimentally evaluate the latency when using stochastic multiplexing to manage packets insertion on the ring, with or without priority for C-RAN packets.
 In Sec.~\ref{sec:deterministicalgorithms}, we propose a deterministic way to manage C-RAN packets without buffers, which guarantees to have zero latency from buffering.
-We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packet, or in Sec.~\ref{sec:maxant} to allow the ring to support a maximal number of antennas at the cost of a very small latency for the C-RAN traffic.
+We propose several refinements of this deterministic sending scheme to spread the load over time, which improves the latency of best effort packet, or in Sec.~\ref{sec:maxant}, to allow the ring to support a maximal number of antennas at the cost of a very small latency for the C-RAN traffic.
 
@@
 The data from $u$ is routed to its BBU at node $v$ through the ring and arrives at time $m_i + \omega(u,v)$ if it has been inserted in the ring upon arrival.
-Then after some computation time (which w.l.o.g.
-is supposed to be zero), an answer is sent back from the BBU to the RRH.
+Then after some computation time, which w.l.o.g.
+is supposed to be zero, an answer is sent back from the BBU to the RRH.
 The same quantity of data is emitted by each BBU or RRH during any period.
@@
 Hence, in this context, to minimize the end-to-end delay, we need to minimize the (logical) latency.
-   In particular, we want to reduce the latency of the C-RAN traffic to \textbf{zero}, both for the RRHs (uplink) and the BBUs (downlink).
+   More precisely, we want to reduce the latency of the C-RAN traffic to \textbf{zero}, both for the RRHs (uplink) and the BBUs (downlink).
 In Sec.~\ref{sec:deterministicalgorithms} we propose a deterministic mechanism with zero latency for C-RAN which also improves the latency of other data going through the optical ring.
@@
       \includegraphics[scale=0.7]{interface.pdf}
-     \caption{Insertion in the N-GREEN optical ring.}\label{fig:interface}
+     \caption{Insertion of C-RAN traffic in the N-GREEN optical ring.}\label{fig:interface}
 
@@
 This batch arrival process consists in generating, at each unit of time, a quantity of data drawn from a bimodal distribution to modelize the fact that internet traffic is bursty.
-Then, according to the fill rate of the contention buffer and the maximum waiting time of the data, a packet of size at most $C$ is created by aggregating data in the contention buffer.
+Then, according to the fill rate of the contention buffer and the maximum waiting time of the data, a packet of size at most $C$ may be created by aggregating data in the contention buffer.
 This packet is then put in the insertion buffer of the node.
@@
  Two different methods to manage the insertion buffer are experimentally compared.
-First, the \textbf{FIFO} rule, that consist in managing the C-RAN and BE packets in the same insertion buffer.
+First, the \textbf{FIFO} rule, which consists in managing the C-RAN and BE packets in the same insertion buffer.
 Then, when a free container is available, the node fills it with the oldest packet of the insertion buffer, without distinction between C-RAN and BE.
@@
 The experimental parameters are given in Table~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}.
-In this experiment, the offsets of the RRH have been randomly distributed in the period.
-The results are computed over $1,000$ experiments (with different random offsets) in which the optical ring is simulated during $1,000,000$ units of time.
+In each experiment, the offsets of the RRHs are drawn uniformly at random in the period.
+The results are computed over $1,000$ experiments in which the optical ring is simulated during $1,000,000$ units of time.
 Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO and the C-RAN priority methods.
@@
 If an RRH emits at time $m_i$, then we say it is at \textbf{position} $m_i + \omega(u,v)\pmod F$.
-The position of an RRH corresponds to the position in a slot of the container it has emitted, when it arrives at $u$, the node of the BBU. 
+The position of an RRH corresponds to the position in a slot of the container it has emitted, when it arrives at $v$, the node of the BBU. 
 If an RRH is at position $p$, then by construction, the corresponding $BBU$ is at position $p+1\pmod F$.
-For now, we do not allow waiting times for C-RAN traffic, hence each RRH uses a container at the same position during all the emission time.
+For now, we do not allow waiting times for C-RAN traffic, hence each RRH uses a container at \emph{the same position during all the emission time}.
 
@@
       \includegraphics[scale=0.65]{assignment}
-     \caption{An assignment with $F = 6$.}\label{fig:assignment}
+     \caption{A valid assignment with $F = 6$.}\label{fig:assignment}
 
@@
 
-  Our method combine the three ways we have described to spread the load over the period.
-  In order to understand the interest of these three improvements, we present the cumulative distribution of the latency of the BE traffic using them either alone or in conjunction and 
-  we compare our method to stochastic multiplexing with C-RAN priority.
+  Our algorithm \emph{combines the three methods} we have described to spread the load over the period.
+  In order to understand the interest of each improvement, we present the cumulative distribution of the latency of the BE traffic using them either alone or in conjunction and we compare our algorithm to stochastic multiplexing with C-RAN priority.
 
@@
 We keep the same parameters as in Sec.~\ref{sec:oportmethods} (see Table~\ref{fig:params}).
-As expected, the BE traffic latency is much better when we balance the C-RAN traffic inside the period and already better than stochastic multiplexing.
+As expected, the BE traffic latency is much better when we balance the C-RAN traffic inside the period and already much better than stochastic multiplexing.
 
@@
 
-As shown in Fig.\ref{fig:algocmp}, the performance of the naive assignment is really bad, even worst than the methods using an insertion buffer.
+As shown in Fig.\ref{fig:algocmp}, the performance of the naive assignment is really bad.
 Compacting the RRHs on a minimal number of positions decreases dramatically the latency.
-If in addition, we balance over a period, we get another gain of latency of smaller magnitude.
-We did not represent the benefit of balancing used positions because the reduction in latency it 
-yields is small as expected: The average (respectively maximum) latency for BE traffic goes from $4.76 \mu$s (resp. $48 \mu$s) to $4.43 \mu$s (resp. $44 \mu$s).
+If in addition, we balance over a period, we get another gain of latency of smaller magnitude: the average (respectively maximum) latency for BE traffic goes from $4.76 \mu$s (resp.
+$48 \mu$s) to $3.28 \mu$s (resp.
+$37 \mu$s).
+We did not represent the benefit of balancing used positions because the reduction in latency it yields is small as expected: The average (respectively maximum) latency for BE traffic goes from $4.76 \mu$s (resp.
+$48 \mu$s) to $4.43 \mu$s (resp.
+$44 \mu$s).
 
@@
 The parameter are the same as in the previous experiment.
-The performance of the reservation algorithm is excellent, since the C-RAN traffic has \emph{zero latency} and the BE traffic has a \emph{better latency} with reservation than with the FIFO rule.
+The performance of our reservation algorithm is excellent, since the C-RAN traffic has \emph{zero latency} and the BE traffic has a \emph{better latency} than with the FIFO rule despite the cost of reservation.
 It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth for the BE traffic.
@@
       \includegraphics[scale=0.25]{periodonly}
-     \caption{Latencies of a naive assignment and of balancing inside the period for $5$ antennas.}  
+     \caption{BE latencies of a naive assignment and balancing inside the period for $5$ antennas.}  
      \label{fig:periodonly}
@@
       \includegraphics[scale=0.25]{repart1res}
-     \caption{Compacting and balancing inside the period for $12$ antennas.}   \label{fig:algocmp}
+     \caption{BE latencies of compacting positions and balancing inside the period for $12$ antennas.}   \label{fig:algocmp}
 \end{center}
@@
 The method we present in this section enables us to support more antennas and improves the latency of BE traffic (it reserves less free containers) by \emph{allowing the data from an RRH to use two positions}.
-It is a the cost of a slightly worse latency for C-RAN traffic and it also requires in practice to implement some buffering for the C-RAN packets.
-
-\paragraph{Filling positions}
+It is at the cost of a slightly worse latency for C-RAN traffic and it also requires in practice to implement some buffering for the C-RAN packets.
 
@@
 \begin{proof}
- We consider the RRHs in the order of the ring and set their offsets as in Prop.~\ref{prop:assign}.
- If $l = \lfloor \frac{P- RS}{ET}\rfloor$, $l$ RRHs can be at position zero. The $(l+1)$th
- RRH also emit first at position zero, with offset $m_{l+1} = l*ET + \omega(u_0,u_{l+1})$. 
- After emitting up to time $x = P - \omega(u_{l+1},u_{0})$ at position zero, it emits during a time $ET -x $  at position $2$.
-Then the next RRH is assigned to position two, and begin to emit at time $x$ instead of zero.
+ We consider the RRHs in the order of the ring.
+ Let $l = \lfloor \frac{P- RS}{ET}\rfloor$, then we set the offsets of the first $l$ RRHs as in Prop.~\ref{prop:assign}.
+These RRHs are at position zero and the $(l+1)$th RRH first emits at position zero, with offset $m_{l+1} = l*ET + \omega(u_0,u_{l+1})$.
+
+ The $(l+1)$th RRH emits up to time $P - \omega(u_{l+1},u_{0})$ at position zero, so that there is no conflict with RRH $0$ during the next period.
+ Hence, it has used the position zero during $x = P - \omega(u_{l+1},u_{0}) - l*ET - \omega(u_0,u_{l+1}) = P - l*ET - RS$.
+From time $P - \omega(u_{l+1},u_{0}) + 2$, the $(l+1)$th RRH emits at position $2$ and during a time $ET - x$.
+Then the next RRH in the order is assigned to position $2$, and begins to emit at time $P - \omega(u_{l+1},u_{0}) + ET -x$ instead of zero.
 The rest of the assignment is built in the same way filling completely all first positions, until there are no more RRH.
@@
 
-Fig.~\ref{fig:split} illustrates the construction of Prop.~\ref{prop:filling} for the N-GREEN parameters. It is possible to support $9$ antennas (but no BE traffic in this extreme case),
+Fig.~\ref{fig:split} illustrates the construction of Prop.~\ref{prop:filling} for the N-GREEN parameters.
+The loss due to reservation is exactly $RS$ containers by used positions.
+Hence, it is possible to support $9$ antennas (but no BE traffic in this extreme case),
 rather than $5$ with the method of Sec.~\ref{sec:zerolatency}.
+
+ We call this new reservation algorithm \textbf{saturating positions} since it improves on compacting positions of the previous subsection.
+Moreover, there are no free slots in used positions, hence the idea of balancing into the period is not relevant.
+The only possible optimisation would be to balance the used positions, but it is not worth it since it adds additional latency for the RRHs using two different positions.
+%  
+%   Since the N-GREEN parameters only allows to do balancing into the period of the previous section, we want to compare the impact on the best effort traffic of fulfilling positions against balancing into the period and FIFO rule.
 
@@
 
-  This reservation algorithm naturally applies the compacting position of the previous subsection.
-Also, there is no balancing into the period to do because all the used position (except the last) are full.
-The only possible optimisation for the best effort traffic would be to balance the used positions, but, it would add some additional latency on the packet which are already assigned with $2$ unit of time of latency.
-  Since the N-GREEN parameters only allows to do balancing into the period of the previous section, we want to compare the impact on the best effort traffic of fulfilling positions against balancing into the period and FIFO rule.
-Fig.~\ref{fig:splitres} represent the cumulative distribution of the best effort traffic with those three methods, and with the N-GREEN parameters.
-Filling positions reduces the BE traffic latency more than balancing into the period.
-Indeed, with filling positions, the loss of bandwidth due to reservation is minimized.
+Fig.~\ref{fig:splitres} represents the cumulative distribution of the latency of BE traffic for the FIFO rule, saturating position, and balancing into the period using the N-GREEN parameters.
+Saturating positions reduces the BE traffic latency more than balancing into the period.
+This is easily explained by its lesser use of reservation.
+It is at the cost of a maximal latency of $2$ $\mu$s for C-RAN traffic, so the designer can chose to use any of the two algorithms, according to what latency must be guaranteed to C-RAN or BE traffic.
 
@@
       \includegraphics[scale=0.25]{splitres}
-     \caption{Latencies of filling positions compared to FIFO buffer and balancing into the period for 5 antennas.}   \label{fig:splitres}
+     \caption{Latencies of saturating positions, balancing into the period and FIFO rule for 5 antennas.}   \label{fig:splitres}
 \end{center}
@@
 
-  As a conclusion, we want to stress the fact that to deal with a deterministic 
-  dataflow as C-RAN, we must use a deterministic policy rather than a classical stochastic one.
-  By using a simple scheme which requires only to set the emission timing of the RRHs and to allow reservation on the optical ring, which is easy to do in practice, we remove all logical latencies.
+  As a conclusion, we want to stress the fact that to deal with a deterministic  dataflow as C-RAN, we must use a deterministic policy rather than a classical stochastic one.
+  By using a simple practical SDN scheme, which requires only to set the emission timing of the RRHs and to allow reservation on the optical ring, we remove all logical latencies.
 It also improves significantly the latencies of the BE traffic by spreading the load of the C-RAN traffic uniformly over the period.

### 2019-01-28 v3/articleV3.tex
modifs format
majuscule

@@
 \captionsetup{justification=centering,margin=0.5cm}
+\usepackage[pscoord]{eso-pic}
+\newcommand{\placetextbox}[3]{
+\setbox0=\hbox{#3} 
+\AddToShipoutPictureFG*{ 
+\put(\LenToUnit{#1\paperwidth},\LenToUnit{#2\paperheight}){ 
+\vtop{{\null}\makebox[0pt][c]{#3}}}
+}
+}
+\placetextbox{.2}{0.055}{XXX-X-XXXXX-XX-X~\copyright~2018 IFIP}
 
@@
         \begin{center}
-      \hspace{-2.3cm}\includegraphics[scale=0.65]{containers}
+   \includegraphics[scale=0.65]{containers}
 
@@
 \begin{center}  
-
       \includegraphics[scale=0.7]{interface.pdf}
      \caption{Insertion of C-RAN traffic in the N-GREEN optical ring.}\label{fig:interface}
-
 \end{center}
   \end{figure}
-
+\vspace{-0.5cm}
 \paragraph{Best effort traffic}
@@
 The source code in C of the experiments can be found on one of the authors' webpage~\cite{webpage}.
-   \vspace{-1cm}
+   \vspace{-1.3cm}
+   \begin{figure}[h]
         \begin{center}
@@
 \end{center} 
+\end{figure}
+   \vspace{-1cm}
 \begin{figure}[h]
@@
   \end{figure}  
+     \vspace{-0.4cm}
 
@@
   \end{figure}
+       \vspace{-0.4cm}
 
@@
 It is a small optimization, since it decreases the latency by at most $F/2$.
-
+     \vspace{-0.4cm}
 \begin{figure}[h!]
 \begin{center}   
-
       \includegraphics[scale=0.55]{repart1}
      \caption{Balancing used positions.}\label{fig:slotbal}
-
 \end{center}
   \end{figure}
-
+     \vspace{-0.4cm}
   \paragraph{Experimental evaluation}
@@
   In order to understand the interest of each improvement, we present the cumulative distribution of the latency of the BE traffic using them either alone or in conjunction and we compare our algorithm to stochastic multiplexing with C-RAN priority.
+
+       \vspace{-0.4cm}
+\begin{figure}[h!]
+\begin{center}
+
+      \includegraphics[scale=0.25]{periodonly}
+     \caption{BE latencies of a naive assignment and balancing inside the period for $5$ antennas.}  
+     \label{fig:periodonly}
+  \end{center}
+  \end{figure}
+    \vspace{-0.4cm}
 
@@
 $37 \mu$s).
-We did not represent the benefit of balancing used positions because the reduction in latency it yields is small as expected: The average (respectively maximum) latency for BE traffic goes from $4.76 \mu$s (resp.
+We did not represent the benefit of balancing used positions because the reduction in latency it yields is small as expected: the average (respectively maximum) latency for BE traffic goes from $4.76 \mu$s (resp.
 $48 \mu$s) to $4.43 \mu$s (resp.
 $44 \mu$s).
+
+\begin{figure}[h!]
+\begin{center}   
+      \includegraphics[scale=0.25]{repart1res}
+     \caption{BE latencies of compacting positions and balancing inside the period for $12$ antennas.}   \label{fig:algocmp}
+\end{center}
+  \end{figure}
 
@@
 
-\begin{figure}[h]
-\begin{center}
-
-      \includegraphics[scale=0.25]{periodonly}
-     \caption{BE latencies of a naive assignment and balancing inside the period for $5$ antennas.}  
-     \label{fig:periodonly}
-  \end{center}
-  \end{figure}
-
-\begin{figure}[h]
-\begin{center}
-
-      \includegraphics[scale=0.25]{repart1res}
-     \caption{BE latencies of compacting positions and balancing inside the period for $12$ antennas.}   \label{fig:algocmp}
-\end{center}
-  \end{figure}
-  \begin{figure}[h]
+  \begin{figure}[h!]
 \begin{center}   
@@
 \end{proof}
+ \vspace{-0.4cm}
+\begin{figure}[h]
+\begin{center}
+
+      \includegraphics[scale=0.8]{split}
+     \caption{Valid assignment for $9$ antennas and the N-GREEN parameters.}   \label{fig:split}
+\end{center}
+  \end{figure}
+  \vspace{-0.4cm}
 
@@
 
-\begin{figure}[h]
-\begin{center}
-
-      \includegraphics[scale=0.8]{split}
-     \caption{Valid assignment for $9$ antennas and the N-GREEN parameters.}   \label{fig:split}
-\end{center}
-  \end{figure}
-
-Fig.~\ref{fig:splitres} represents the cumulative distribution of the latency of BE traffic for the FIFO rule, saturating position, and balancing into the period using the N-GREEN parameters.
-Saturating positions reduces the BE traffic latency more than balancing into the period.
-This is easily explained by its lesser use of reservation.
-It is at the cost of a maximal latency of $2$ $\mu$s for C-RAN traffic, so the designer can chose to use any of the two algorithms, according to what latency must be guaranteed to C-RAN or BE traffic.
-
+ \vspace{-0.4cm}
 \begin{figure}[h]
@@
   \end{figure}
+    \vspace{-0.4cm}
+
+Fig.~\ref{fig:splitres} represents the cumulative distribution of the latency of BE traffic for the FIFO rule, saturating position, and balancing into the period using the N-GREEN parameters.
+Saturating positions reduces the BE traffic latency more than balancing into the period.
+This is easily explained by its lesser use of reservation.
+It is at the cost of a maximal latency of $2$ $\mu$s for C-RAN traffic, so the designer can chose to use any of the two algorithms, according to what latency must be guaranteed to C-RAN or BE traffic.
 
